### 2014-03-04 writeup/gz_hubble_data.tex
Started writing paper!

%\documentclass[twocolumn]{emulateapj}
%\documentclass[12pt,preprint]{aastex}

\documentclass[usenatbib]{mn2e}

\newcommand{\s}{$_{\rm s}$}
\newcommand{\kms}{km~s$^{-1}$}
\newcommand{\msun}{{\it M}$_{\odot}$}
\newcommand{\lsun}{{\it L}$_{\odot}$}
\newcommand{\mear}{{\it M}$_{\oplus}$}
\newcommand{\etal}{{\it et al.}}
\newcommand{\ie}{{\it i.e.}}
\newcommand{\eg}{{\it e.g.}}
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\magarc}{{\rm mag\,arcsec$^{-2}$}}
\newcommand{\MK}{{{\rm M}_{\rm ext,K}-5\log h}}
\newcommand{\ri}{{$r_{21}$}}
\newcommand{\ra}{$R_A$}
\newcommand{\vobs}{{v_{\rm obs}}}
\newcommand{\kmsMpc}{km~s$^{-1}$ Mpc$^{-1}$}
\newcommand{\h}{$h_{70}$}
\newcommand{\vpec}{v_{\rm pec}}
\newcommand{\like}{{\mathcal L}}
\newcommand{\vs}{\vspace*{5pt}}
\newcommand{\continued}{ (Continued)}

% Journals
\newcommand{\mnras}{MNRAS}
\newcommand{\apj}{ApJ}
\newcommand{\apjl}{ApJL}
\newcommand{\aj}{AJ}
\newcommand{\pasp}{PASP}
\newcommand{\aaps}{A\&AS}
\newcommand{\aap}{A\&A}
\newcommand{\apjs}{ApJS}
\newcommand{\araa}{ARA\&A}
\newcommand{\pbar}{p_{\rm bar}}
\newcommand{\fHI}{f_{\rm HI}}

\voffset-1.25cm

\usepackage{epsfig}
\begin{document}

\title[Galaxy Zoo Hubble Data]{Galaxy Zoo: Classifications for Galaxies in HST Legacy Imaging}
%Bars Regulating Star Formation though the Atomic Gas Content of Disc Galaxies}
%The Atomic Gas Content of Barred Galaxies from ALFALFA$^*$: Bar Feedback in Intermediate Mass Disc Galaxies }
\author[Lead Author \etal]{Lead Author and other Galaxy Zoo science team\\
%$^1$Institute for Cosmology and Gravitation, University of Portsmouth, Dennis Sciama Building, Burnaby Road, Portsmouth, PO1 3FX, UK \\
%$^2$South East Physics Network, www.sepnet.ac.uk\\
%$^3$Dept. of Astronomy, Cornell University, Space Sciences Building, Ithaca, NY 14850, USA\\
 %$^2$Institute for Sciences of the Cosmos (ICCUB), University of Barcelona, Marti i Franques 1, Barcelona, 08024 Spain\\
% $^{4}$Oxford Astrophysics, Department of Physics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK\\
%$^{5}$Yale Center for Astronomy and Astrophysics, Yale University, P.O. Box 208121, New Haven, CT 06520, USA \\
%$^6$Steward Observatory, University of Arizona, 933 N. Cherry Ave, Tuscon, AZ 85721, USA\\
 %$^4$Astronomy Department, Adler Planetarium and Astronomy Museum, 1300 Lake Shore Drive, Chicago, IL 60605, USA\\
 % $^7$Centre for Astronomy \& Particle Theory, University of Nottingham, University Park, Nottingham, NG7 2RD, UK\\
 %$^6$School of Physics and Astronomy, University of Minnesota, Minneapolis, MN 55455, USA\\
 %$^7$Department of Physics \& Astronomy, 206 Gallalee Hall, 514 University Blvd., University of Alabama, Tuscaloosa, AL 35487-0234, USA\\
% $^8$Einstein Fellow\\ 
\\
 $^*$This publication has been made possible by the participation of more than 200,000 volunteers in the Galaxy Zoo project. \\ Their contributions are individually acknowledged at \texttt{http://www.galaxyzoo.org/volunteers}. \\
\\
{\tt E-mail: lead.author@university.edu}
 }

%\date{Accepted for publication in MNRAS, 7th October 2010.}
%\pagerange{1--10} \pubyear{2010}

\maketitle

\begin{abstract}

Data release paper for GZ Hubble

\end{abstract}

%\keywords{galaxies: distances and redshifts --- galaxies: clusters --- galaxies: fundamental parameters --- distance scale --- cosmological parameters}

\section{Introduction}

%\begin{figure}
%\includegraphics[width=84mm]{barfraction_gasfraction.ps}
%\includegraphics[height=80mm,angle=-90]{TuningFork.ps}
%\caption{The Hubble Sequence illustrated by the examples suggested by Hubble (1926) with images from the SDSS.  The galaxies are: : E0 Ð NGC 3379; E5 Ð NGC 4621;  Sa - NGC 4594 (``The Sombrero");  Sb - NGC 2841; Sc -  NGC 5447 (``The Pinwheel"); SBa - NGC 2859; SBb - NGC 3351 (or M95); SBc - 7479. We have also included an S0 (NGC 6278), not in HubbleÕs original scheme.) \label{sequence}}
%\end{figure}

\section{Sample and Data}

\subsection{Summary of HST Legacy Survey Imaging}

AEGIS has1 orbit each (~2200 seconds) in F606W (V band) and F814W filter and has been dithered to 0.03 ''/pixel; the imaging covers ~710 arcmin$^2$.

GOODS targeted 2 fields, GOODS-N and GOODS-S, imaging in 4 filters -- F435W (B), F606W (V), F775W (i), and F850LP (z). The mean exposure times vary, from 1000 - 2100 seconds. The images have been dithered to a pixel scale of 0.03 ''/pixel and covers at total area of ~320 arcmin$^2$ (160 arcmin$^2$ per field). The filters that Griffith et al uses for the colored images were F606W and F775W for GOODS-N and F606W and F850LP for GOODS-S.

COSMOS has 1 orbit (2028 seconds) in the F814W (I band) filter and has been dithered to 0.05 ''/pixel; it covers the largest area, ~1.8 deg$^2$.

GEMS has 1 orbit (2160 and 2286 seconds) in the F606W and F850LP filters, with a pixel scale of 0.03 ''/pixel; it covers ~800 arcmin$^2$

\section{Redshift Dependent Classification Bias}

We can't do what we did in Bamford et al. (2009) for the original GZ or Willett et al. (2013) for GZ2 because these both depended on the assumption of no redshift bias. In the GZH samples the redshift range is so large that we expect to find redshift evolution of the types and morphologies of galaxies which are seen.

So we made images of the same galaxy at a variety of redshifts using input images from the SDSS (cite the SDSS) and the FERENGI code (cite Ferengi).

\subsection{Selection of Input Galaxies}

We select 288 different galaxies in SDSS imaging to run through the FERENGI code.

The selection spanned a variety of galaxy morphologies (as indicated by GZ2 classifications) and surface brightnesses, and also picked ideal something for different target redshifts in HST imaging.

 Here are the selection criteria for the categories

1. Features (Q1): Clean Yes, Int, Clean No: 
No: p_smooth > 0.8
Int: 0.3 < p_smooth < 0.6
Yes: p_features_or_disk > 0.8. 
To make sure they're not mergers, I also suggest requiring p_odd < 0.1

2. Mergers: Clean No, Int, Clean Yes (3 galaxies - some overlap with above)
No: p_features_or_disk > 0.8 & p_odd < 0.1 & p_merger < 0.1
Int: p_odd > 0.5 & 0.1< p_merger < 0.4 
Yes: p_odd > 0.5 & p_merger > 0.4

3. Edge-on: clean no, int, clean yes
Yes: p_edgeon > 0.8
Int: 0.4 < p_edgeon < 0.8
No: p_edgeon < 0.2
Also require p_features_or_disk > 0.5

4. Bars (from clean no edge-on sample): clean no, int, clean yes
No: p_bar < 0.1
Int: 0.2 < p_bar < 0.4
Yes: p_bar > 0.8
Also require p_features_or_disk > 0.5 and p_edgeon < 0.2
This category is run twice.

5. Spirals (clean not edge-on, and bar-less): clean no, int, clean yes
No: p_spiral < 0.2
Int: 0.2 < p_spiral < 0.8
Yes: p_spiral > 0.8
Also require p_features_or_disk > 0.5 and p_edgeon < 0.2 and p_bar < 0.1

6. Bulges (clean not edge-on, and bar-less): 
No: p_nobulge>0.6
Int: p_justnoticeable>0.6
Yes: p_obvious/dominent>0.5 * ask Edmond what this means p_ob+p_dom>0.5 or p_ob OR p_dom >0.5
Also require p_features_or_disk > 0.5 and p_edgeon < 0.5 and p_bar < 0.2

7. Edge-on bulge shape: 
Round: p_rounded>0.5, p_features_or_disk > 0.5 and p_edgeon > 0.5
Boxy: p_boxy>0.4, p_features_or_disk > 0.5 and p_edgeon > 0.2
Non: p_nobulge>0.5, p_features_or_disk > 0.5 and p_edgeon > 0.5

Input galaxies are done at three surface brightnesses:

mu > 21.5 (low)
20.5 < mu < 21.5 (mid)
mu < 20.5 (high)

\begin{table*}
\caption{Summary of FERENGI parameters\label{ferengi}}
\begin{tabular}{lccccc}
\hline\hline
Starting redshift &  $N_{z {\rm bins}}$ & $N_{\rm evolution}$ & $N_{\rm per input galaxy}$ & $N_{\rm total}$\\
\hline
0.3 & 8 & 7 & 56 & 4031 \\
0.5 & 6 & 4 & 24 & 1728 \\
0.8 & 3 & 3 & 9 & 648 \\
1.0 & 1 & 3 & 3 & 216 \\
\hline\hline
\end{tabular}
\end{table*}

\section{Summary}

\paragraph*{ACKNOWLEDGEMENTS.}

This publication has been made possible by the participation of more than 200,000 volunteers in the Galaxy Zoo project. Their contributions are individually acknowledged at \texttt{http://www.galaxyzoo.org/volunteers}. Galaxy Zoo 2 was developed with the help of a grant from The Leverhulme Trust.

HST acknowledgements.

Funding for the SDSS and SDSS-II has been provided by the Alfred P. Sloan Foundation, the Participating Institutions, the National Science Foundation, the U.S. Department of Energy, the National Aeronautics and Space Administration, the Japanese Monbukagakusho, the Max Planck Society, and the Higher Education Funding Council for England. The SDSS Web Site is http://www.sdss.org/.

The SDSS is managed by the Astrophysical Research Consortium for the Participating Institutions. The Participating Institutions are the American Museum of Natural History, Astrophysical  Institute Potsdam, University of Basel, University of Cambridge, 
Case Western Reserve University, University of Chicago, Drexel University, Fermilab, the Institute for Advanced Study, the Japan 
Participation Group, Johns Hopkins University, the Joint Institute for Nuclear Astrophysics, the Kavli Institute for Particle Astrophysics and Cosmology, the Korean Scientist Group, the Chinese Academy of Sciences (LAMOST), Los Alamos National Laboratory, the Max-Planck-Institute for Astronomy (MPIA), the Max-Planck-Institute for Astrophysics (MPA), New Mexico State Uni- 
versity, Ohio State University, University of Pittsburgh, University of Portsmouth, Princeton University, the United States Naval Observatory and the University of Washington.

\begin{thebibliography}{}

\end{thebibliography}

\end{document}

### 2014-03-04 writeup/gz_hubble_data.tex
Updated my grant acknowledgement
and testing what happens!
Small edits

@@
 
-AEGIS has1 orbit each (~2200 seconds) in F606W (V band) and F814W filter and has been dithered to 0.03 ''/pixel; the imaging covers ~710 arcmin$^2$.
+\begin{itemize}
+\item AEGIS has1 orbit each (~2200 seconds) in F606W (V band) and F814W filter and has been dithered to 0.03 ''/pixel; the imaging covers ~710 arcmin$^2$.
 
-GOODS targeted 2 fields, GOODS-N and GOODS-S, imaging in 4 filters -- F435W (B), F606W (V), F775W (i), and F850LP (z).
+\item GOODS targeted 2 fields, GOODS-N and GOODS-S, imaging in 4 filters -- F435W (B), F606W (V), F775W (i), and F850LP (z).
 The mean exposure times vary, from 1000 - 2100 seconds.
@@
 
-COSMOS has 1 orbit (2028 seconds) in the F814W (I band) filter and has been dithered to 0.05 ''/pixel; it covers the largest area, ~1.8 deg$^2$.
+\item COSMOS has 1 orbit (2028 seconds) in the F814W (I band) filter and has been dithered to 0.05 ''/pixel; it covers the largest area, ~1.8 deg$^2$.
 
-GEMS has 1 orbit (2160 and 2286 seconds) in the F606W and F850LP filters, with a pixel scale of 0.03 ''/pixel; it covers ~800 arcmin$^2$
+\item GEMS has 1 orbit (2160 and 2286 seconds) in the F606W and F850LP filters, with a pixel scale of 0.03 ''/pixel; it covers ~800 arcmin$^2$
+\end{itemize}
 
@@
 
-So we made images of the same galaxy at a variety of redshifts using input images from the SDSS (cite the SDSS) and the FERENGI code (cite Ferengi).
+So we made images of the same galaxy at a variety of redshifts using input images from the SDSS (cite the SDSS) and the FERENGI code (cite Ferengi) to produce images from these typical of those observed in the HST surveys.
 
@@
 
-The selection spanned a variety of galaxy morphologies (as indicated by GZ2 classifications) and surface brightnesses, and also picked ideal something for different target redshifts in HST imaging.
+The selection spanned a variety of galaxy morphologies (as indicated by GZ2 classifications), with a range of surface brightnesses, and also picked ideal something for different target redshifts in HST imaging.
 
- Here are the selection criteria for the categories
+ The selection criteria for the different morphological categories
 
@@
 Galaxy Zoo 2 was developed with the help of a grant from The Leverhulme Trust.
+KS gratefully acknowledges support from Swiss National Science Foundation Grant PP00P2\_138979/1.
 

### 2014-03-04 writeup/gz_hubble_data.tex
Edits to writeup of Ferengi stuff

@@
 
-The selection spanned a variety of galaxy morphologies (as indicated by GZ2 classifications), with a range of surface brightnesses, and also picked ideal something for different target redshifts in HST imaging.
+The selection spanned a variety of galaxy morphologies (as indicated by GZ2 classifications), with a range of surface brightnesses, and also picked ideal {\bf need Edmond to fill in} for different target redshifts in HST imaging.
 
- The selection criteria for the different morphological categories
-
-1. Features (Q1): Clean Yes, Int, Clean No: 
-No: p_smooth > 0.8
-Int: 0.3 < p_smooth < 0.6
-Yes: p_features_or_disk > 0.8. 
-To make sure they're not mergers, I also suggest requiring p_odd < 0.1
-
-2. Mergers: Clean No, Int, Clean Yes (3 galaxies - some overlap with above)
-No: p_features_or_disk > 0.8 & p_odd < 0.1 & p_merger < 0.1
-Int: p_odd > 0.5 & 0.1< p_merger < 0.4 
-Yes: p_odd > 0.5 & p_merger > 0.4
-
-3. Edge-on: clean no, int, clean yes
-Yes: p_edgeon > 0.8
-Int: 0.4 < p_edgeon < 0.8
-No: p_edgeon < 0.2
-Also require p_features_or_disk > 0.5
-
-4. Bars (from clean no edge-on sample): clean no, int, clean yes
-No: p_bar < 0.1
-Int: 0.2 < p_bar < 0.4
-Yes: p_bar > 0.8
-Also require p_features_or_disk > 0.5 and p_edgeon < 0.2
-This category is run twice.
-
-5. Spirals (clean not edge-on, and bar-less): clean no, int, clean yes
-No: p_spiral < 0.2
-Int: 0.2 < p_spiral < 0.8
-Yes: p_spiral > 0.8
-Also require p_features_or_disk > 0.5 and p_edgeon < 0.2 and p_bar < 0.1
-
-6. Bulges (clean not edge-on, and bar-less): 
-No: p_nobulge>0.6
-Int: p_justnoticeable>0.6
-Yes: p_obvious/dominent>0.5 * ask Edmond what this means p_ob+p_dom>0.5 or p_ob OR p_dom >0.5
-Also require p_features_or_disk > 0.5 and p_edgeon < 0.5 and p_bar < 0.2
-
-7. Edge-on bulge shape: 
-Round: p_rounded>0.5, p_features_or_disk > 0.5 and p_edgeon > 0.5
-Boxy: p_boxy>0.4, p_features_or_disk > 0.5 and p_edgeon > 0.2
-Non: p_nobulge>0.5, p_features_or_disk > 0.5 and p_edgeon > 0.5
-
-Input galaxies are done at three surface brightnesses:
-
-mu > 21.5 (low)
-20.5 < mu < 21.5 (mid)
-mu < 20.5 (high)
+ The selection criteria for the different morphological categories is summarised in Table \ref{morphologies}.
+The surface brightness selection was (1) low: $\mu > 21.5 {\rm mag arsec}^2$;  (2) mid: $20.5 < \mu < 21.5 {\rm mag arsec}^2$; and (3) high: $\mu < 20.5 {\rm mag arsec}^2$.
 
 \begin{table*}
-\caption{Summary of FERENGI parameters\label{ferengi}}
+\caption{Summary of morphological categories \label{morphologies}}
+\begin{tabular}{lllc}
+\hline\hline
+Morphology & Label &  Selection & $N_{\rm objects}$ \\
+\hline
+Features & Yes & $p_{\rm features} > 0.8$, $p_{rm odd} < 0.1$ & 12 \\ 
+ & Int & $0.3 < p_{\rm smooth} < 0.6$, $p_{\rm odd} < 0.1$ & 12 \\ 
+ & No &  $p_{\rm smooth} > 0.8$, $p_{\rm odd} < 0.1$ & 12 \\ 
+Merger & No & $p_{\rm features} > 0.8$, $p_{\rm odd < 0.1}$, $p_{\rm merger} < 0.1$ & 12\\
+& Int & $p_{\rm odd} > 0.5$, $0.1< p_{\rm merger} < 0.4$ & 12 \\ 
+& Yes & $p_{\rm odd} > 0.5$, $p_{\rm merger} > 0.4$ & 12\\
+Edge-on & Yes &  $p_{\rm edgeon} > 0.8$, $p_{\rm features} > 0.5$ & 12 \\
+& Int & $0.4 < p_{\rm edgeon} < 0.8$ , $p_{\rm features} > 0.5$ & 12 \\
+& No & $p_{\rm edgeon} < 0.2$, $p_{\rm features} > 0.5$ & 12 \\
+Bar & No & $p_{\rm bar} < 0.1$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$ & 24 \\
+& Int & $0.2 < p_{\rm bar} < 0.4$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$ & 24 \\
+& Yes&  $p_{\rm bar} > 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$ & 24 \\
+Visible spiral & No & $p_{\rm spiral} < 0.2$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$ & 12 \\
+& Int &  $0.2 < p_{\rm spiral} < 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$ & 12 \\
+& Yes &  $p_{\rm spiral} > 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$ & 12 \\
+Oblique Bulge Size & No & $p_{\rm nobulge>0.6}$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$ & 12 \\
+& Int &  $p_{\rm justnoticeable}>0.6$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$ & 12 \\
+& Yes & $p_{\rm obvious/dominent}>0.5$\footnote{Edmond does this means $p_{\rm obv}+p_{\rm dom}>0.5$ or $p_{\rm ob} OR p_{\rm dom} >0.5$?
+}, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$ & 12 \\
+Edge-on bulge shape 
+& Round & $p_{\rm rounded}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.5$ & 12\\
+& Boxy & $p_{\rm boxy}>0.4$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.2$ & 12\\
+& Non & $p_{\rm nobulge}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.5$ & 12\\
+\hline\hline
+\end{tabular}
+\end{table*}
+
+There were four ``target redshifts" ($z = 0.3, 0.5, 0.8$ and 1.0), and from these points the images were redshifted in $\Delta z = 0.1$ bins up to $z=1.0$.
+In addition different evolution models were assumed in FERENGI.
+This evolution is a crude mechanism that is suppose to mimic the brightness increase of galaxies with increasing redshift.
+The evolution mechanism allows us to make galaxies brighter as linear function of redshift, and that is it.
+It is an empirical addition to the magnitude of a galaxy of the form $M' = e z + M$, where $M'$ is the corrected magnitude, $e$ is the evolutionary correction in magnitudes.
+(i.e.
+$e=-1$ essentially brightens the galaxy by 1 magnitude by $z=1$).
+{\bf What values of $e$ did we use?} Depending on the target, or starting redshift we ran FERENGI for several final redshifts and different evolution models as summarized in Table \ref{ferengi}.
+
+\begin{table}
+\caption{Summary of FERENGI runs \label{ferengi}}
 \begin{tabular}{lccccc}
 \hline\hline
-Starting redshift &  $N_{z {\rm bins}}$ & $N_{\rm evolution}$ & $N_{\rm per input galaxy}$ & $N_{\rm total}$\\
+Starting redshift &  $N_{z {\rm bins}}$ & $N_{\rm evolution}$ & $N_{\rm runs}$ & $N_{\rm total}$\\
 \hline
@@
 \end{tabular}
-\end{table*}
+\end{table}
+
+An example redshifted image is shown in Figure \ref{exampleFERENGI}.
 

### 2014-03-04 writeup/gz_hubble_data.tex
Added fake results figure to paper
Shows the current fake results figure from v1/ of the FERENGI analysis.
Warning: FAKE.
Added example ferengi images

@@
 
-%\begin{figure}
-%\includegraphics[width=84mm]{barfraction_gasfraction.ps}
-%\includegraphics[height=80mm,angle=-90]{TuningFork.ps}
-%\caption{The Hubble Sequence illustrated by the examples suggested by Hubble (1926) with images from the SDSS.
-The galaxies are: : E0 Ð NGC 3379; E5 Ð NGC 4621;  Sa - NGC 4594 (``The Sombrero");  Sb - NGC 2841; Sc -  NGC 5447 (``The Pinwheel"); SBa - NGC 2859; SBb - NGC 3351 (or M95); SBc - 7479.
-We have also included an S0 (NGC 6278), not in HubbleÕs original scheme.) \label{sequence}}
-%\end{figure}
-
 \section{Sample and Data}
@@
 
-\section{Redshift Dependent Classification Bias}
+\section{Correcting for Redshift Dependent Classification Bias}
 
@@
 \subsection{Selection of Input Galaxies}
+
+%-----------------------------------------------------------------------------------------------------------------------------------
+\begin{figure}
+\begin{center}
+
+\includegraphics[width=0.49\textwidth]{fake_results.pdf}
+
+\caption{Fake results of the FERENGI redshifting exercise.
+For three vote fraction levels and thee surface-brightness levels each, we show the evolution of the 7 evolutionary corrections used with redshift.}
+
+\label{fig:ferengi_results_fake}
+
+\end{center}
+\end{figure}
+%-----------------------------------------------------------------------------------------------------------------------------------
 
@@
 
-An example redshifted image is shown in Figure \ref{exampleFERENGI}.
+Two series of example redshifted images are shown in Figure \ref{exampleFERENGI}.
+
+\begin{figure*}
+\includegraphics[width=84mm]{example_ferengi.ps}
+%\includegraphics[height=80mm,angle=-90]{TuningFork.ps}
+\caption{Examples of two galaxies which have been run through the FERENGI code to produce simulated HST images. \label{exampleFERENGI}}
+\end{figure*}
 

### 2014-03-04 writeup/gz_hubble_data.tex
Added example images to paper

@@
 
+We also expect to see changes in the apparent morphology of galaxies due to band shifting and surface brightness effects (e.g.
+see Figure \ref{redshift} which illustrates one possible effect of losing features in spiral galaxies at high redshift).
+So we need to measure this.
+
+\begin{figure}
+\includegraphics[width=60mm]{example_ferengi2.ps}
+%\includegraphics[height=80mm,angle=-90]{TuningFork.ps}
+\caption{Examples of an obvious spiral and obvious elliptical at $z=0$ which both look similar when redshifted to $z=0.8$.
+See below for the description of the method for redshirting.
+\label{exampleFERENGI}}
+\end{figure}
+
 So we made images of the same galaxy at a variety of redshifts using input images from the SDSS (cite the SDSS) and the FERENGI code (cite Ferengi) to produce images from these typical of those observed in the HST surveys.
@@
 \begin{figure*}
-\includegraphics[width=84mm]{example_ferengi.ps}
+\includegraphics[width=160mm]{example_ferengi.ps}
 %\includegraphics[height=80mm,angle=-90]{TuningFork.ps}

### 2014-03-04 writeup/gz_hubble_data.tex
Put fake results in as .ps

@@
 
-\subsection{Selection of Input Galaxies}
-
-%-----------------------------------------------------------------------------------------------------------------------------------
-\begin{figure}
-\begin{center}
-
-\includegraphics[width=0.49\textwidth]{fake_results.pdf}
-
-\caption{Fake results of the FERENGI redshifting exercise.
-For three vote fraction levels and thee surface-brightness levels each, we show the evolution of the 7 evolutionary corrections used with redshift.}
-
-\label{fig:ferengi_results_fake}
-
-\end{center}
-\end{figure}
-%-----------------------------------------------------------------------------------------------------------------------------------
+\subsection{Selection of FERENGI Input Galaxies}
 
@@
 
+\subsection{Results of FERENGI Analysis}
+
+We show here the {\bf currently fake} results of citizen scientist classifications of images of galaxies placed at artificial redshifts.
+Figure \ref{results1} shows the {\bf currently fake} change of vote fractions for feature X with redshift, for three vote fraction levels with three surface-brightness levels and 7 evolutionary corrections.
+
+%-----------------------------------------------------------------------------------------------------------------------------------
+\begin{figure}
+\begin{center}
+
+\includegraphics[width=0.35\textwidth,angle=90]{fake_results.ps}
+
+\caption{Fake results of the FERENGI redshifting exercise.
+For three vote fraction levels with three surface-brightness levels and 7 evolutionary corrections each, we show the evolution of the vote fractions for feature X with redshift.}
+
+\label{fig:ferengi_results_fake}
+
+\end{center}
+\end{figure}
+%-----------------------------------------------------------------------------------------------------------------------------------
+
 \section{Summary}

### 2014-03-05 writeup/gz_hubble_data.tex
Added more details on Ferengi choices

@@
 
-The selection spanned a variety of galaxy morphologies (as indicated by GZ2 classifications), with a range of surface brightnesses, and also picked ideal {\bf need Edmond to fill in} for different target redshifts in HST imaging.
+The selection spanned a variety of galaxy morphologies (as indicated by GZ2 classifications), with a range of surface brightnesses, and also spanned the redshift range of SDSS targets (in $N_z = 4$ bins) in order to be optimised for different target redshifts in HST imaging.
 
  The selection criteria for the different morphological categories is summarised in Table \ref{morphologies}.
-The surface brightness selection was (1) low: $\mu > 21.5 {\rm mag arsec}^2$;  (2) mid: $20.5 < \mu < 21.5 {\rm mag arsec}^2$; and (3) high: $\mu < 20.5 {\rm mag arsec}^2$.
+The surface brightness selection ($N_\mu = 3$) was (1) low: $\mu > 21.5 {\rm mag arsec}^2$;  (2) mid: $20.5 < \mu < 21.5 {\rm mag arsec}^2$; and (3) high: $\mu < 20.5 {\rm mag arsec}^2$.
 
@@
 Morphology & Label &  Selection & $N_{\rm objects}$ \\
+ & & & ($N_z \times N_\mu$) \\
 \hline
@@
 
-There were four ``target redshifts" ($z = 0.3, 0.5, 0.8$ and 1.0), and from these points the images were redshifted in $\Delta z = 0.1$ bins up to $z=1.0$.
+For each of the four ``target redshifts" ($z = 0.3, 0.5, 0.8$ and 1.0), the images were redshifted in $\Delta z = 0.1$ bins up to $z=1.0$.
 In addition different evolution models were assumed in FERENGI.
@@
 $e=-1$ essentially brightens the galaxy by 1 magnitude by $z=1$).
-{\bf What values of $e$ did we use?} Depending on the target, or starting redshift we ran FERENGI for several final redshifts and different evolution models as summarized in Table \ref{ferengi}.
+We ran FERENGI for values of $e$ starting from $e=0$ and increasing up to $e=3.5$ in $\Delta e = 0.5$ steps.
+Depending on the target, or starting redshift we ran FERENGI for several final redshifts and different evolution models as summarized in Table \ref{ferengi}.
 
@@
 \caption{Summary of FERENGI runs \label{ferengi}}
-\begin{tabular}{lccccc}
+\begin{tabular}{lcccccc}
 \hline\hline
-Starting redshift &  $N_{z {\rm bins}}$ & $N_{\rm evolution}$ & $N_{\rm runs}$ & $N_{\rm total}$\\
+Starting redshift &  $N_{z {\rm bins}}$ & $N_{\rm evolution}$ & $e_{\rm max}$ & $N_{\rm runs}$ & $N_{\rm total}$\\
 \hline
-0.3 & 8 & 7 & 56 & 4031 \\
-0.5 & 6 & 4 & 24 & 1728 \\
-0.8 & 3 & 3 & 9 & 648 \\
-1.0 & 1 & 3 & 3 & 216 \\
+0.3 & 8 & 7 & 3.5 & 56 & 4031 \\
+0.5 & 6 & 4 & 2.0 & 24 & 1728 \\
+0.8 & 3 & 3 & 1.5 & 9 & 648 \\
+1.0 & 1 & 3 & 1.5 & 3 & 216 \\
 \hline\hline
@@
 We show here the {\bf currently fake} results of citizen scientist classifications of images of galaxies placed at artificial redshifts.
-Figure \ref{results1} shows the {\bf currently fake} change of vote fractions for feature X with redshift, for three vote fraction levels with three surface-brightness levels and 7 evolutionary corrections.
+Figure \ref{results1} shows the {\bf currently fake} change of vote fractions for the change of $p_{\rm features}$ with redshift, for three galaxies with different vote fraction levels, three surface-brightness levels and 7 evolutionary corrections.
 

### 2014-03-07 writeup/gz_hubble_data.tex
small changes
minor edits
edits to description

@@
 
-Data release paper for GZ Hubble
+This will be the data release paper for GZ Hubble. We present the classifications, the methodology for data reduction and corrections for redshift dependent biases in the observed morphologies.
 
@@
 \begin{itemize}
-\item AEGIS has1 orbit each (~2200 seconds) in F606W (V band) and F814W filter and has been dithered to 0.03 ''/pixel; the imaging covers ~710 arcmin$^2$.
+\item AEGIS has 1 orbit each (~2200 seconds) in F606W (V band) and F814W filter and has been dithered to 0.03 ''/pixel; the imaging covers ~710 arcmin$^2$.
 
@@
 \end{itemize}
+
+\begin{table*}
+\caption{Summary of GZ Hubble Samples \label{ferengi}}
+\begin{tabular}{lclccc}
+\hline\hline
+Survey &  $t_{\rm exp}$ & Filters & Resolution & Area & $N_{\rm galaxies}$ \\
+ & seconds & & \arcsec/pix & sq arcmin \\
+\hline
+AEGIS & 2200 & F606W (V) and F814W (I) & 0.03 & 710 \\
+COSMOS & 2028 & F814W (I) & 0.05 & 6480\\
+GEMS & 2160/2286 & F606W (V) and F850LP (z) & 0.03 & 800 \\
+GOODS & 1000-2100s & F435W (B), F606W (V), F775W (i), F850LP (z) & 0.03 & 320 \\
+\hline\hline
+\end{tabular}
+\end{table*}
 
@@
 
+%-----------------------------------------------------------------------------------------------------------------------------------
 \begin{figure}
+\begin{center}
 \includegraphics[width=60mm]{example_ferengi2.ps}
@@
 \label{exampleFERENGI}}
+\end{center}
 \end{figure}
+ %-----------------------------------------------------------------------------------------------------------------------------------
 
@@
 
-The selection spanned a variety of galaxy morphologies (as indicated by GZ2 classifications), with a range of surface brightnesses, and also spanned the redshift range of SDSS targets (in $N_z = 4$ bins) in order to be optimised for different target redshifts in HST imaging.
+The selection spanned a variety of galaxy morphologies (as indicated by GZ2 classifications), with a range of surface brightnesses, and also spanned the redshift range of SDSS targets (in $N_z = 4$ bins) in order to be optimised for different target minimum redshifts in HST imaging.
 
@@
 \begin{table*}
-\caption{Summary of morphological categories \label{morphologies}}
+\caption{Summary of morphological categories selected for FERENGI sample \label{morphologies}}
 \begin{tabular}{lllc}
@@
 \hline
-Features & Yes & $p_{\rm features} > 0.8$, $p_{rm odd} < 0.1$ & 12 \\ 
+Features & Yes & $p_{\rm features} > 0.8$, $p_{\rm odd} < 0.1$ & 12 \\ 
  & Int & $0.3 < p_{\rm smooth} < 0.6$, $p_{\rm odd} < 0.1$ & 12 \\ 
@@
 $e=-1$ essentially brightens the galaxy by 1 magnitude by $z=1$).
-We ran FERENGI for values of $e$ starting from $e=0$ and increasing up to $e=3.5$ in $\Delta e = 0.5$ steps.
+We ran FERENGI for values of $e$ starting from $e=0$ and decreasing to $e=-3.5$ in $\Delta e = 0.5$ steps.
 Depending on the target, or starting redshift we ran FERENGI for several final redshifts and different evolution models as summarized in Table \ref{ferengi}.
@@
 \hline\hline
-Starting redshift &  $N_{z {\rm bins}}$ & $N_{\rm evolution}$ & $e_{\rm max}$ & $N_{\rm runs}$ & $N_{\rm total}$\\
+$z_{\rm target}$ &  $N_{z {\rm bins}}$ & $N_{\rm evolution}$ & $e_{\rm max}$ & $N_{\rm runs}$ & $N_{\rm total}$\\
 \hline
-0.3 & 8 & 7 & 3.5 & 56 & 4031 \\
-0.5 & 6 & 4 & 2.0 & 24 & 1728 \\
-0.8 & 3 & 3 & 1.5 & 9 & 648 \\
-1.0 & 1 & 3 & 1.5 & 3 & 216 \\
+0.3 & 8 & 7 & -3.0 & 56 & 4031 \\
+0.5 & 6 & 4 & -1.5 & 24 & 1728 \\
+0.8 & 3 & 3 & -1.0 & 9 & 648 \\
+1.0 & 1 & 3 & -1.0 & 3 & 216 \\
 \hline\hline
@@
 
-Two series of example redshifted images are shown in Figure \ref{exampleFERENGI}.
+Two series of example redshifted images are shown in Figure \ref{exampleFERENGI}, both for runs with no evolution ($e=0$).
 
@@
 
+\subsubsection{TODO LIST}
+We need to do: 
+\begin{itemize}
+\item Calculate the magnitudes, surface brightnesses and sizes of the galaxies in the FERENGI images....
+\item Plot of magnitude distribution of galaxies in each of the four GZH subsamples with the magnitudes of our fake galaxies over plotted. 
+\item Instructions of how to link the $z=0$ $p_X$ values for galaxies with a given size, magnitude (surface brightness) in the GZH images. 
+\end{itemize}
+
 \section{Summary}
+
+Now people go and do science with these awesome Galaxy Zoo Hubble classifications.
 
@@
 KS gratefully acknowledges support from Swiss National Science Foundation Grant PP00P2\_138979/1.
+
+KS, KLM, BS, CL thank ASIAA for hosting the ``Citizen Science in Astronomy" workshop at which some of this analysis was done.
 

### 2014-03-07 writeup/gz_hubble_data.tex
edits to paper

@@
 
+\subsection{User Weighting}
+
+The votes of individual users who classified galaxies in Galaxy Zoo Hubble are combined to make a vote fraction for each question on the classification tree.
+Users votes are weighted slightly (in a method identical to that described in Willett et al.
+2013) such that users who frequently disagree with all other users end up having very low weights.
+The majority of users have weights very close to 1.0 ({\bf STEVEN: Is this true for GZH - do you have a plot of the distribution of user weights or consistencies we can include here?}.
+
 \section{Correcting for Redshift Dependent Classification Bias}
 
-We can't do what we did in Bamford et al.
-(2009) for the original GZ or Willett et al.
-(2013) for GZ2 because these both depended on the assumption of no redshift bias.
+Previous version of Galaxy Zoo morphology classifications (Lintott et al.
+2011, Willett et al.
+2013) were based on observations of galaxies in the Sloan Digital Sky Survey (SDSS) which are typically at $z<0.1$.
+In these cases it could be assumed that there was no real evolution of the morphologies of galaxies and therefore any observed changes in the distribution of galaxies with different consensus morphologies was assumed to be due to the effects of redshift on the image quality (\ie.
+the reduction in physical resolution, surface brightness dimming etc).
+So for both previous releases of GZ morphogloies, a correction was provided for redshift dependent bias based on matching the classification fractions at the highest redshfts with those at the lowest redshift.
+See Bamford et al.
+(2009) and Willett et al.
+(2013) for the details.
+
 In the GZH samples the redshift range is so large that we expect to find redshift evolution of the types and morphologies of galaxies which are seen.
-
-We also expect to see changes in the apparent morphology of galaxies due to band shifting and surface brightness effects (e.g.
-see Figure \ref{redshift} which illustrates one possible effect of losing features in spiral galaxies at high redshift).
-So we need to measure this.
+So the previous methods of correcting for redshift dependent bias will not work.
+In addition the effects of band shifting will change the images even more across these redshift ranges.
+Figure \ref{redshift} which illustrates one possible effect of losing features in spiral galaxies at high redshift).
 
@@
 
-So we made images of the same galaxy at a variety of redshifts using input images from the SDSS (cite the SDSS) and the FERENGI code (cite Ferengi) to produce images from these typical of those observed in the HST surveys.
+In order to test the effects of redshift we made images of the same galaxy at a variety of redshifts using input images from the SDSS (cite the SDSS) and the FERENGI code (cite Ferengi) to produce images from these typical of those observed in the HST surveys.
 

### 2014-03-07 writeup/gz_hubble_data.tex
edits
stuff

@@
 %\includegraphics[height=80mm,angle=-90]{TuningFork.ps}
-\caption{Examples of two galaxies which have been run through the FERENGI code to produce simulated HST images. \label{exampleFERENGI}}
+\caption{Examples of two galaxies which have been run through the FERENGI code to produce simulated HST images.
+The value of $p_{\rm features}$ for each panel is (1) Top row: $p_{\rm features}=$ 0.9, 0.625, 0.35, 0.35, 0.225 and (2) Bottom row: $p_{\rm features}=$ 1.00, 0.875, 0.875, 0.625, 0.375.
+\label{exampleFERENGI}}
 \end{figure*}
@@
 
-We show here the {\bf currently fake} results of citizen scientist classifications of images of galaxies placed at artificial redshifts.
-Figure \ref{results1} shows the {\bf currently fake} change of vote fractions for the change of $p_{\rm features}$ with redshift, for three galaxies with different vote fraction levels, three surface-brightness levels and 7 evolutionary corrections.
+We show here the {\bf preliminary} results of citizen scientist classifications of images of galaxies placed at artificial redshifts.
+Figure \ref{results1} shows the {\bf preliminary} range of change of vote fractions for the change of $p_{\rm features}$ with redshift, for galaxies with different vote fraction levels, three ranges of surface-brightness levels and 7 evolutionary corrections (this last bit is indicated by the colour).
 
@@
 
-\includegraphics[width=0.35\textwidth,angle=90]{fake_results.ps}
+\includegraphics[width=0.35\textwidth,angle=90]{somewhat_fake_results.ps}
 
-\caption{Fake results of the FERENGI redshifting exercise.
-For three vote fraction levels with three surface-brightness levels and 7 evolutionary corrections each, we show the evolution of the vote fractions for feature X with redshift.}
+\caption{Preliminary results of the FERENGI redshifting exercise.
+WARNING NO USER WEIGHTING....
+For a range of vote fraction levels with three surface-brightness levels and 7 evolutionary corrections each (the colours indicate evolutionary correction value with green being $e=0$, we show the range of evolution of the vote fractions for featured vs.
+smooth with redshift.}
 
@@
 
-KS, KLM, BS, CL thank ASIAA for hosting the ``Citizen Science in Astronomy" workshop at which some of this analysis was done.
+We thank ASIAA for hosting the ``Citizen Science in Astronomy" workshop, Mar 3-7th 2014 in Taipei, Taiwan, at which some of this analysis was done.
 

### 2015-08-05 writeup/gz_hubble_data.tex
mel writeup stuff, probably delete after figuring out ps vs pdf

@@
 % Journals
-\newcommand{\mnras}{MNRAS}
-\newcommand{\apj}{ApJ}
-\newcommand{\apjl}{ApJL}
-\newcommand{\aj}{AJ}
-\newcommand{\pasp}{PASP}
-\newcommand{\aaps}{A\&AS}
-\newcommand{\aap}{A\&A}
-\newcommand{\apjs}{ApJS}
-\newcommand{\araa}{ARA\&A}
-\newcommand{\pbar}{p_{\rm bar}}
-\newcommand{\fHI}{f_{\rm HI}}
+%\newcommand{\mnras}{MNRAS}
+%\newcommand{\apj}{ApJ}
+%\newcommand{\apjl}{ApJL}
+%\newcommand{\aj}{AJ}
+%\newcommand{\pasp}{PASP}
+%\newcommand{\aaps}{A\&AS}
+%\newcommand{\aap}{A\&A}
+%\newcommand{\apjs}{ApJS}
+%\newcommand{\araa}{ARA\&A}
+%\newcommand{\pbar}{p_{\rm bar}}
+%\newcommand{\fHI}{f_{\rm HI}}
 
@@
 \usepackage{epsfig}
+%\usepackage{epstopdf}
 \begin{document}
@@
 \begin{center}
-\includegraphics[width=60mm]{example_ferengi2.ps}
-%\includegraphics[height=80mm,angle=-90]{TuningFork.ps}
+\includegraphics[width=60mm]{example_ferengi2.pdf}
+%\includegraphics[height=80mm,angle=-90]{TuningFork.pdf}
 \caption{Examples of an obvious spiral and obvious elliptical at $z=0$ which both look similar when redshifted to $z=0.8$.
@@
 \begin{figure*}
-\includegraphics[width=160mm]{example_ferengi.ps}
-%\includegraphics[height=80mm,angle=-90]{TuningFork.ps}
+\includegraphics[width=160mm]{example_ferengi.pdf}
+%\includegraphics[height=80mm,angle=-90]{TuningFork.pdf}
 \caption{Examples of two galaxies which have been run through the FERENGI code to produce simulated HST images.
@@
 
-\includegraphics[width=0.35\textwidth,angle=90]{somewhat_fake_results.ps}
+\includegraphics[width=0.35\textwidth]{somewhat_fake_results.pdf}
 
@@
 %-----------------------------------------------------------------------------------------------------------------------------------
+\subsubsection{Results of Zeta Approach (Mel stuff)}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=8in]{p_vs_p_SB_redshift.pdf}
+\caption{a caption. Add scale in $p_{\rm features}$ somehow that doesn't clutter the plot even more. }
+\label{fig:p_vs_p}
+\end{center}
+\end{figure*}
+
+In Figure \ref{fig:p_vs_p} we examine the change in $p_{\rm features}$ for the FERENGI images relative to their lowest simulated redshift ($\rm z_{sim}=0.3$).
+For each simulated redshift value $z$, and at fixed surface brightness $\mu$, we plot $p_{\rm features,z}$, the value measured at that simulated redshift, vs $p_{\rm features,z=0.3}$, the value measured for the same galaxy imaged at $z=0.3$.
+Only images corresponding to galaxies which also had FERENGI images at $z=0.3$ were included in this plot, which include 4031 out of the total 6624.
+
+Our objective is to use these data to predict, for a galaxy with a measured $p_{\rm features,z}$ value, what its $p_{\rm features}$ value would have been if it had been viewed at $z=0.3$.
+This predicted value is defined as the debiased vote fraction $p_{\rm features,debiased}$, and is calculated by applying a correction to the measured value of $p_{\rm features}$, determined by the $\zeta$ function described in the previous section.
+We determine that a predicted value can be obtained so long as the relationship between $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$ is single-valued; that is, for a given $p_{\rm features,z}$, there is one corresponding value of $p_{\rm features}$ at $z=0.3$.
+
+In Figure \ref{fig:p_vs_p} we see that the relationship between $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$ is \emph{not} always single valued; hence we do not find it appropriate to correct galaxies that lie in these regions of surface brightness/redshift/$p_{\rm features}$ space.
+Our criteria for determining whether a region of this space is correctable is as follows: For each surface brightness and redshift bin, we examine the distribution of $p_{\rm features,z=0.3}$ for fixed $p_{\rm features,z}$ in bins of $\Delta p_{\rm features,z} = 0.1$.
+These sub-bins are marked by the horizontal lines within each larger, surface brightness/redshift bin.
+First, we require at least 5 points in each sub-bin to determine with confidence whether that region is correctable or uncorrectable.
+For the region to be considered correctable, we require that the inner two quartiles of the distribution of $p_{\rm features,z=0.3}$ within these sub-bins span a range less than 0.2.
+These regions are coloured purple, and the inner two quartile ranges are indicated by the black error bars within each sub-bin.If the spread is greater than 0.2, the region is considered uncorrectable; these are marked in green.
+Any region with fewer than 5 points is considered to have ``not enough information (NEI)'', and left uncoloured on the plot.
+
+Stuff to do in this section:
+
+\begin{itemize}
+\item talk about where purple and green tend to be on plot, and about how green areas are primarily ellipticals and disks with all the features washed out - can't tell them apart! hence, can't debias
+\item talk about where the Hubble sample falls in this space, reference table \ref{hubble_debiasable} 
+\item justify N>5 and spread < 0.2 (or find a better way to choose criteria)
+\item check out corrections for correctable and NEI, show some sample images of corrected galaxies
+\item show some data for $p_{bar}$, determine or justify why we won't debiase them  
+\end{itemize}
+
+\begin{table}
+\caption{Debiasable Hubble Stuff.
+Doesn't include SDSS yet.
+Note: stuff without good redshift info automatically gets put in uncorrectable category - which is about 25,000 galaxies.
+Might increase correctable number if we can get these measurements.
+\label{hubble_debiasable}}
+\begin{tabular}{lrr}
+\hline\hline
+Category &  N & \% \\
+\hline
+Correctable   & 7408 & 6 \%  \\
+Uncorrectable & 58526 & 50 \%\\
+NEI           & 52149 & 44 \% \\
+Total         & 118083 & 100 \% \\
+\hline\hline
+\end{tabular}
+\end{table}
 

### 2015-08-05 writeup/gz_hubble_data.tex
Small fixes on intro sections.

--- 2014-03-07 writeup/gz_hubble_data.tex
@@
 
+\newcommand{\ferengi}{\textsc{ferengi}}
+
 % Journals
-\newcommand{\mnras}{MNRAS}
-\newcommand{\apj}{ApJ}
-\newcommand{\apjl}{ApJL}
-\newcommand{\aj}{AJ}
-\newcommand{\pasp}{PASP}
-\newcommand{\aaps}{A\&AS}
-\newcommand{\aap}{A\&A}
-\newcommand{\apjs}{ApJS}
-\newcommand{\araa}{ARA\&A}
-\newcommand{\pbar}{p_{\rm bar}}
-\newcommand{\fHI}{f_{\rm HI}}
+%\newcommand{\mnras}{MNRAS}
+%\newcommand{\apj}{ApJ}
+%\newcommand{\apjl}{ApJL}
+%\newcommand{\aj}{AJ}
+%\newcommand{\pasp}{PASP}
+%\newcommand{\aaps}{A\&AS}
+%\newcommand{\aap}{A\&A}
+%\newcommand{\apjs}{ApJS}
+%\newcommand{\araa}{ARA\&A}
+%\newcommand{\pbar}{p_{\rm bar}}
+%\newcommand{\fHI}{f_{\rm HI}}
 
@@
 \usepackage{epsfig}
+\usepackage{color,soul}
 \begin{document}
 
-\title[Galaxy Zoo Hubble Data]{Galaxy Zoo: Classifications for Galaxies in HST Legacy Imaging}
-%Bars Regulating Star Formation though the Atomic Gas Content of Disc Galaxies}
-%The Atomic Gas Content of Barred Galaxies from ALFALFA$^*$: Bar Feedback in Intermediate Mass Disc Galaxies }
-\author[Lead Author \etal]{Lead Author and other Galaxy Zoo science team\\
+\title[Galaxy Zoo Hubble Data]{Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging}
+\author[Lead Author \etal]{Lead Author and other Galaxy Zoo science team members\\
 %$^1$Institute for Cosmology and Gravitation, University of Portsmouth, Dennis Sciama Building, Burnaby Road, Portsmouth, PO1 3FX, UK \\
@@
  $^*$This publication has been made possible by the participation of more than 200,000 volunteers in the Galaxy Zoo project.
-\\ Their contributions are individually acknowledged at \texttt{http://www.galaxyzoo.org/volunteers}.
+\\ Their contributions are individually acknowledged at \texttt{http://authors.galaxyzoo.org/authors.html}.
 \\
@@
 \begin{itemize}
-\item AEGIS has 1 orbit each (~2200 seconds) in F606W (V band) and F814W filter and has been dithered to 0.03 ''/pixel; the imaging covers ~710 arcmin$^2$.
+\item AEGIS has 1 orbit each (~2200 seconds) in F606W (V band) and F814W filter and has been dithered to 0.03 ''/pixel; the imaging covers $\sim710$~arcmin$^2$.
 
@@
 The images have been dithered to a pixel scale of 0.03 ''/pixel and covers at total area of ~320 arcmin$^2$ (160 arcmin$^2$ per field).
-The filters that Griffith et al uses for the colored images were F606W and F775W for GOODS-N and F606W and F850LP for GOODS-S.
+The filters that \citet{gri12} uses for the colored images were F606W and F775W for GOODS-N and F606W and F850LP for GOODS-S.
 
@@
 \begin{table*}
-\caption{Summary of GZ Hubble Samples \label{ferengi}}
+\caption{Summary of GZ Hubble Samples \label{gzh_numbers}}
 \begin{tabular}{lclccc}
@@
 The votes of individual users who classified galaxies in Galaxy Zoo Hubble are combined to make a vote fraction for each question on the classification tree.
-Users votes are weighted slightly (in a method identical to that described in Willett et al.
-2013) such that users who frequently disagree with all other users end up having very low weights.
+Users votes are weighted slightly \citep[in a method identical to that described in][]{wil13} such that users who frequently disagree with all other users end up having very low weights.
 The majority of users have weights very close to 1.0 ({\bf STEVEN: Is this true for GZH - do you have a plot of the distribution of user weights or consistencies we can include here?}.
@@
 
-Previous version of Galaxy Zoo morphology classifications (Lintott et al.
-2011, Willett et al.
-2013) were based on observations of galaxies in the Sloan Digital Sky Survey (SDSS) which are typically at $z<0.1$.
+Previous version of Galaxy Zoo morphology classifications \citep{lin08,wil13} were based on observations of galaxies in the Sloan Digital Sky Survey (SDSS) which are typically at $z<0.1$.
 In these cases it could be assumed that there was no real evolution of the morphologies of galaxies and therefore any observed changes in the distribution of galaxies with different consensus morphologies was assumed to be due to the effects of redshift on the image quality (\ie.
@@
 So for both previous releases of GZ morphogloies, a correction was provided for redshift dependent bias based on matching the classification fractions at the highest redshfts with those at the lowest redshift.
-See Bamford et al.
-(2009) and Willett et al.
-(2013) for the details.
+See \citet{bam09} and \citet{wil13} for the details.
 
@@
 \caption{Examples of an obvious spiral and obvious elliptical at $z=0$ which both look similar when redshifted to $z=0.8$.
-See below for the description of the method for redshirting.
-\label{exampleFERENGI}}
+See below for the description of the method for redshifting.\label{exampleFERENGI}}
 \end{center}
@@
 
-In order to test the effects of redshift we made images of the same galaxy at a variety of redshifts using input images from the SDSS (cite the SDSS) and the FERENGI code (cite Ferengi) to produce images from these typical of those observed in the HST surveys.
+In order to test the effects of redshift we made images of the same galaxy at a variety of redshifts using input images from the SDSS \citep{yor00,str02} and the \ferengi{} code \citep{bar08a} to produce images that match the observational properties of those observed in the HST surveys.
 
@@
 
-We select 288 different galaxies in SDSS imaging to run through the FERENGI code.
+We selected 288 unique galaxies from SDSS imaging to run through the \ferengi{} code.
 
@@
 \begin{table*}
-\caption{Summary of morphological categories selected for FERENGI sample \label{morphologies}}
+\caption{Summary of morphological categories selected for FERENGI sample.
+\hl{For Edmond: does $p_{\rm obvious/dominant}>0.5$ mean ($p_{\rm obv}+p_{\rm dom}>0.5$) or ($p_{\rm ob}$ OR $p_{\rm dom} >0.5$)?}\label{morphologies}}
 \begin{tabular}{lllc}
@@
 Morphology          & Label &  Selection                                                                                            & $N_{\rm objects}$ \\
- & & & ($N_z \times N_\mu$) \\
+                    &       &                                                                                                       & [$N_z \times N_\mu$] \\
 \hline
@@
                     & No    & $p_{\rm smooth} > 0.8$, $p_{\rm odd} < 0.1$                                                           & 12 \\ 
-Merger & No & $p_{\rm features} > 0.8$, $p_{\rm odd < 0.1}$, $p_{\rm merger} < 0.1$ & 12\\
+Merger              & No    & $p_{\rm features} > 0.8$, $p_{\rm odd < 0.1}$, $p_{\rm merger} < 0.1$                                 & 12 \\
                     & Int   & $p_{\rm odd} > 0.5$, $0.1< p_{\rm merger} < 0.4$                                                      & 12 \\ 
-& Yes & $p_{\rm odd} > 0.5$, $p_{\rm merger} > 0.4$ & 12\\
+                    & Yes   & $p_{\rm odd} > 0.5$, $p_{\rm merger} > 0.4$                                                           & 12 \\
 Edge-on             & Yes   & $p_{\rm edgeon} > 0.8$, $p_{\rm features} > 0.5$                                                      & 12 \\
@@
                     & Int   & $0.2 < p_{\rm bar} < 0.4$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                           & 24 \\
-& Yes&  $p_{\rm bar} > 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$ & 24 \\
+                    & Yes   & $p_{\rm bar} > 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                                 & 24 \\
 Visible spiral      & No    & $p_{\rm spiral} < 0.2$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$         & 12 \\
@@
                     & Yes   & $p_{\rm spiral} > 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$         & 12 \\
-Oblique Bulge Size & No & $p_{\rm nobulge>0.6}$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$ & 12 \\
+Oblique bulge size  & No    & $p_{\rm nobulge>0.6}$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$          & 12 \\
                     & Int   & $p_{\rm justnoticeable}>0.6$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$   & 12 \\
-& Yes & $p_{\rm obvious/dominent}>0.5$\footnote{Edmond does this means $p_{\rm obv}+p_{\rm dom}>0.5$ or $p_{\rm ob} OR p_{\rm dom} >0.5$?
-}, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$ & 12 \\
-Edge-on bulge shape 
-& Round & $p_{\rm rounded}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.5$ & 12\\
-& Boxy & $p_{\rm boxy}>0.4$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.2$ & 12\\
-& Non & $p_{\rm nobulge}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.5$ & 12\\
+                    & Yes   & $p_{\rm obvious/dominant}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$ & 12 \\
+Edge-on bulge shape & Round & $p_{\rm rounded}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.5$                               & 12 \\
+                    & Boxy  & $p_{\rm boxy}>0.4$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.2$                                  & 12 \\
+                    & Non   & $p_{\rm nobulge}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.5$                               & 12 \\
 \hline\hline
@@
 
-For each of the four ``target redshifts" ($z = 0.3, 0.5, 0.8$ and 1.0), the images were redshifted in $\Delta z = 0.1$ bins up to $z=1.0$.
-In addition different evolution models were assumed in FERENGI.
+For each of the four ``target redshifts'' ($z = 0.3, 0.5, 0.8$ and $1.0$), the images were redshifted in $\Delta z = 0.1$ bins up to $z=1.0$.
+In addition different evolution models were assumed in \ferengi{}.
 This evolution is a crude mechanism that is suppose to mimic the brightness increase of galaxies with increasing redshift.
 The evolution mechanism allows us to make galaxies brighter as linear function of redshift, and that is it.
-It is an empirical addition to the magnitude of a galaxy of the form $M' = e z + M$, where $M'$ is the corrected magnitude, $e$ is the evolutionary correction in magnitudes.
+It is an empirical addition to the magnitude of a galaxy of the form $M' = e\times z + M$, where $M'$ is the corrected magnitude, $e$ is the evolutionary correction in magnitudes.
 (i.e.
-$e=-1$ essentially brightens the galaxy by 1 magnitude by $z=1$).
-We ran FERENGI for values of $e$ starting from $e=0$ and decreasing to $e=-3.5$ in $\Delta e = 0.5$ steps.
-Depending on the target, or starting redshift we ran FERENGI for several final redshifts and different evolution models as summarized in Table \ref{ferengi}.
+$e=-1$ essentially brightens the galaxy by 1~magnitude by $z=1$).
+We ran \ferengi{} for values of $e$ starting from $e=0$ and decreasing to $e=-3.5$ in $\Delta e = 0.5$ steps.
+Depending on the target, or starting redshift we ran \ferengi{} for several final redshifts and different evolution models as summarized in Table~\ref{ferengivalues}.
 
 \begin{table}
-\caption{Summary of FERENGI runs \label{ferengi}}
+\caption{Summary of FERENGI runs \label{ferengivalues}}
 \begin{tabular}{lcccccc}

### 2015-08-05 writeup/gz_hubble_data.tex

@@
 %\newcommand{\araa}{ARA\&A}
-%\newcommand{\pbar}{p_{\rm bar}}
-%\newcommand{\fHI}{f_{\rm HI}}
+\newcommand{\pbar}{p_{\rm bar}}
+\newcommand{\fHI}{f_{\rm HI}}
 
@@
 %-----------------------------------------------------------------------------------------------------------------------------------
+\subsubsection{Results of Zeta Approach (Mel stuff)}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\textwidth]{p_vs_p_SB_redshift.ps}
+\caption{a caption. Add scale in $p_{\rm features}$ somehow that doesn't clutter the plot even more. }
+\label{fig:p_vs_p}
+\end{center}
+\end{figure*}
+
+In Figure \ref{fig:p_vs_p} we examine the change in $p_{\rm features}$ for the FERENGI images relative to their lowest simulated redshift ($\rm z_{sim}=0.3$).
+For each simulated redshift value $z$, and at fixed surface brightness $\mu$, we plot $p_{\rm features,z}$, the value measured at that simulated redshift, vs $p_{\rm features,z=0.3}$, the value measured for the same galaxy imaged at $z=0.3$.
+Only images corresponding to galaxies which also had FERENGI images at $z=0.3$ were included in this plot, which include 4031 out of the total 6624.
+
+Our objective is to use these data to predict, for a galaxy with a measured $p_{\rm features,z}$ value, what its $p_{\rm features}$ value would have been if it had been viewed at $z=0.3$.
+This predicted value is defined as the debiased vote fraction $p_{\rm features,debiased}$, and is calculated by applying a correction to the measured value of $p_{\rm features}$, determined by the $\zeta$ function described in the previous section.
+We determine that a predicted value can be obtained so long as the relationship between $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$ is single-valued; that is, for a given $p_{\rm features,z}$, there is one corresponding value of $p_{\rm features}$ at $z=0.3$.
+
+In Figure \ref{fig:p_vs_p} we see that the relationship between $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$ is \emph{not} always single valued; hence we do not find it appropriate to correct galaxies that lie in these regions of surface brightness/redshift/$p_{\rm features}$ space.
+Our criteria for determining whether a region of this space is correctable is as follows: For each surface brightness and redshift bin, we examine the distribution of $p_{\rm features,z=0.3}$ for fixed $p_{\rm features,z}$ in bins of $\Delta p_{\rm features,z} = 0.1$.
+These sub-bins are marked by the horizontal lines within each larger, surface brightness/redshift bin.
+First, we require at least 5 points in each sub-bin to determine with confidence whether that region is correctable or uncorrectable.
+For the region to be considered correctable, we require that the inner two quartiles of the distribution of $p_{\rm features,z=0.3}$ within these sub-bins span a range less than 0.2.
+These regions are coloured purple, and the inner two quartile ranges are indicated by the black error bars within each sub-bin.If the spread is greater than 0.2, the region is considered uncorrectable; these are marked in green.
+Any region with fewer than 5 points is considered to have ``not enough information (NEI)'', and left uncoloured on the plot.
+
+Stuff to do in this section:
+
+\begin{itemize}
+\item talk about where purple and green tend to be on plot, and about how green areas are primarily ellipticals and disks with all the features washed out - can't tell them apart! hence, can't debias
+\item talk about where the Hubble sample falls in this space, reference table \ref{hubble_debiasable} 
+\item justify N>5 and spread < 0.2 (or find a better way to choose criteria)
+\item check out corrections for correctable and NEI, show some sample images of corrected galaxies
+\item show some data for $p_{bar}$, determine or justify why we won't debiase them  
+\end{itemize}
+
+\begin{table}
+\caption{Debiasable Hubble Stuff.
+Doesn't include SDSS yet.
+Note: stuff without good redshift info automatically gets put in uncorrectable category - which is about 25,000 galaxies.
+Might increase correctable number if we can get these measurements.
+\label{hubble_debiasable}}
+\begin{tabular}{lrr}
+\hline\hline
+Category &  N & \% \\
+\hline
+Correctable   & 7408 & 6 \%  \\
+Uncorrectable & 58526 & 50 \%\\
+NEI           & 52149 & 44 \% \\
+Total         & 118083 & 100 \% \\
+\hline\hline
+\end{tabular}
+\end{table}
 

### 2015-08-05 writeup/gz_hubble_data.tex
First paragraph of Sec 3.2

@@
 \usepackage{color,soul}
+\usepackage{natbib}
+\bibliographystyle{mn2e}
+
 \begin{document}
@@
 \hline
-0.3 & 8 & 7 & -3.0 & 56 & 4031 \\
-0.5 & 6 & 4 & -1.5 & 24 & 1728 \\
-0.8 & 3 & 3 & -1.0 & 9 & 648 \\
-1.0 & 1 & 3 & -1.0 & 3 & 216 \\
+0.3              & 8                  & 7                   & $-3.0$        & 56             & 4031 \\
+0.5              & 6                  & 4                   & $-1.5$        & 24             & 1728 \\
+0.8              & 3                  & 3                   & $-1.0$        &  9             &  648 \\
+1.0              & 1                  & 3                   & $-1.0$        &  3             &  216 \\
 \hline\hline
@@
 %\includegraphics[height=80mm,angle=-90]{TuningFork.ps}
-\caption{Examples of two galaxies which have been run through the FERENGI code to produce simulated HST images.
+\caption{Examples of two galaxies which have been run through the \ferengi{} code to produce simulated HST images.
 The value of $p_{\rm features}$ for each panel is (1) Top row: $p_{\rm features}=$ 0.9, 0.625, 0.35, 0.35, 0.225 and (2) Bottom row: $p_{\rm features}=$ 1.00, 0.875, 0.875, 0.625, 0.375.
@@
 We show here the {\bf preliminary} results of citizen scientist classifications of images of galaxies placed at artificial redshifts.
-Figure \ref{results1} shows the {\bf preliminary} range of change of vote fractions for the change of $p_{\rm features}$ with redshift, for galaxies with different vote fraction levels, three ranges of surface-brightness levels and 7 evolutionary corrections (this last bit is indicated by the colour).
+Figure \ref{results1} shows the {\bf preliminary} range of change of vote fractions for the change of $p_{\rm features}$ with redshift, for galaxies with different vote fraction levels, three ranges of surface-brightness levels and 7~evolutionary corrections (this last bit is indicated by the colour).
 
@@
 
-\caption{Preliminary results of the FERENGI redshifting exercise.
+\caption{Preliminary results of the \ferengi{} redshifting exercise.
 WARNING NO USER WEIGHTING....
@@
 %-----------------------------------------------------------------------------------------------------------------------------------
-\subsubsection{Results of Zeta Approach (Mel stuff)}
+
+\subsection{Approach to debiasing morphological classifications}
+
+The approach used in GZH for correcting the weighted classifications for user bias rests on the assumption that the \emph{amount} of bias is a function of the apparent size and brightness of the image as seen on screen.
+This is controlled by two types of parameters: \textbf{intrinsic} properties of the galaxy itself, such as its physical diameter and luminosity, and \textbf{extrinsic} properties, such as the distance (redshift) of the galaxy and its relative orientation.
+There are likely other parameters that affect user accuracy, such as the proximity of close companions \citep[``distraction bias''; see][]{joh15} or those that vary by individual user.
+The combination of all such parameters forms a high-dimensional space, and we have insufficient test galaxies to measure the individual effects of each.
+Instead, we use just two parameters that are intended to capture the bulk of the change in bias (based on GZ1/GZ2): one
+
+\subsection{Results of Zeta Approach (Mel stuff)}
 
@@
 \item talk about where the Hubble sample falls in this space, reference table \ref{hubble_debiasable} 
-\item justify N>5 and spread < 0.2 (or find a better way to choose criteria)
+\item justify $N>5$ and spread $< 0.2$ (or find a better way to choose criteria)
 \item check out corrections for correctable and NEI, show some sample images of corrected galaxies
-\item show some data for $p_{bar}$, determine or justify why we won't debiase them  
+\item show some data for $\pbar$, determine or justify why we won't debiase them  
 \end{itemize}
@@
 
-\begin{thebibliography}{}
-
-\end{thebibliography}
+\bibliography{kwrefs}
 

### 2015-08-05 writeup/gz_hubble_data.tex
Small changes

@@
 \begin{figure*}
-\includegraphics[width=160mm]{example_ferengi.ps}
-%\includegraphics[height=80mm,angle=-90]{TuningFork.ps}
-\caption{Examples of two galaxies which have been run through the \ferengi{} code to produce simulated HST images.
+\includegraphics[width=160mm]{example_ferengi.pdf}
+%\includegraphics[height=80mm]{TuningFork.pdf}
+\caption{Examples of two galaxies which have been run through the FERENGI code to produce simulated HST images.
 The value of $p_{\rm features}$ for each panel is (1) Top row: $p_{\rm features}=$ 0.9, 0.625, 0.35, 0.35, 0.225 and (2) Bottom row: $p_{\rm features}=$ 1.00, 0.875, 0.875, 0.625, 0.375.
@@
 The combination of all such parameters forms a high-dimensional space, and we have insufficient test galaxies to measure the individual effects of each.
-Instead, we use just two parameters that are intended to capture the bulk of the change in bias (based on GZ1/GZ2): one
+Instead, we use just two parameters that are intended to capture the bulk of the change in bias (based on GZ1/GZ2): surface brightness (intrinsic) and redshift (extrinsic).
 
@@
 \begin{center}
-\includegraphics[width=\textwidth]{p_vs_p_SB_redshift.ps}
+\includegraphics[width=\textwidth]{p_vs_p_SB_redshift.pdf}
 \caption{a caption. Add scale in $p_{\rm features}$ somehow that doesn't clutter the plot even more. }

### 2015-08-05 writeup/gz_hubble_data.tex

@@
 
-\subsection{Results of FERENGI Analysis}
-
-We show here the {\bf preliminary} results of citizen scientist classifications of images of galaxies placed at artificial redshifts.
-Figure \ref{results1} shows the {\bf preliminary} range of change of vote fractions for the change of $p_{\rm features}$ with redshift, for galaxies with different vote fraction levels, three ranges of surface-brightness levels and 7~evolutionary corrections (this last bit is indicated by the colour).
-
-%-----------------------------------------------------------------------------------------------------------------------------------
-\begin{figure}
-\begin{center}
-
-\includegraphics[width=0.35\textwidth]{somewhat_fake_results.pdf}
-
-\caption{Preliminary results of the \ferengi{} redshifting exercise.
-WARNING NO USER WEIGHTING....
-For a range of vote fraction levels with three surface-brightness levels and 7 evolutionary corrections each (the colours indicate evolutionary correction value with green being $e=0$, we show the range of evolution of the vote fractions for featured vs.
-smooth with redshift.}
-
-\label{fig:ferengi_results_fake}
-
-\end{center}
-\end{figure}
-%-----------------------------------------------------------------------------------------------------------------------------------
-
 \subsection{Approach to debiasing morphological classifications}
@@
 The combination of all such parameters forms a high-dimensional space, and we have insufficient test galaxies to measure the individual effects of each.
-Instead, we use just two parameters that are intended to capture the bulk of the change in bias (based on GZ1/GZ2): surface brightness (intrinsic) and redshift (extrinsic).
+Instead, we use just two parameters that are intended to capture the bulk of the change in bias (based on GZ1/GZ2): a galaxy's $r$-band surface brightness ($\mu_r$; intrinsic) and redshift ($z$; extrinsic).
+
+The change in bias as a function of $\mu_r$ and $z$ is measured using the \ferengi{} images at all evolutionary corrected factors.
+We assume that the ``true'' (ie, debiased) vote fraction $f_{\mu,z}$ for a galaxy can be expressed as:
+
+\begin{equation}
+f_{\mu,z} = \left(f_{\mu,z=0.3}\right) \times e^{{\frac{z-z_0}{\zeta}}},
+\label{eqn:fzeta}
+\end{equation}
+
+\noindent where $f_{\mu,z=0.3}$ is the ``calibrated'' vote fraction at the lowest redshift in the \ferengi{} bins, which is at redshift $z=0.3$ and $\zeta$ is a positive parameter that controls the rate at which $f$ drops off with increasing redshift.
+This formula fits the data relatively well (with almost no exceptions, the vote fractions for featured galaxies decrease monotonically with increasing redshift), and the exponential function bounds the observed vote fractions between $f_{\mu,z=0.3}$ and zero.
+Figure~\ref{fig:zeta_examples} show examples of the change in vote fraction and their fits to Equation~\ref{eqn:fzeta} for a random selection of galaxies in the \ferengi{} images.
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\textwidth]{zeta_examples.pdf}
+\caption{Behavior of the normalized, weighted vote fractions of features visible in a galaxy ($f_\textrm{features}$) as a function of redshift in the artifical \ferengi{} images.
+Galaxies are a random selection of images with $e=0$ and at least three detectable images in redshift bins of $z\ge0.3$.
+The measured vote fractions (red points) are fit with an exponential function (Equation~\ref{eqn:fzeta}); the best-fit parameters are given above each plot.
+Error bars are Poissonian, assuming a median of 40~votes per galaxy.}
+\label{fig:zeta_examples}
+\end{center}
+\end{figure*}
+
+We then take the values of $\zeta$ for \emph{all} sets of artifically redshifted galaxies and use them to fit the overall distribution of $\zeta$ as a function of surface brightness (since we expect the correction being applied to vary as a function of the intrinsic galaxy properties).
+We restrict the galaxies that can be used to measure the calibration to those with data at the pivot redshift of $z=0.3$, those with non-zero $f_\textrm{features}$ at $z=0.3$, and with a reasonable fit to the exponential model ($\Delta \chi^2 > 3.0$).
+
+Figure~\ref{fig:zeta_mu} shows the results of the sample; the correction is a weak function of surface brightness overall.
+Higher-surface brightness galaxies have stronger average corrections, likely because these galaxies are more likely to have larger $f_\textrm{features}$ values at high redshifts.
+Low surface brightness galaxies are more likely to begin low and remain low; the bounded nature of the dropoff (and Poissonian-like variance among the individual voters) means that the average magnitude of $\zeta$ will be less.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.50\textwidth]{zeta_mu.pdf}
+\caption{All fits for the vote fraction dropoff parameter $\zeta$ for $f_\textrm{features}$ in the \ferengi{} galaxies as a function of surface brightness.
+This includes only the 51~galaxies with a reasonably bounded range on the dropoff ($-10<\log(\zeta)<10$) and sufficient points to fit the function.}
+\label{fig:zeta_mu}
+\end{center}
+\end{figure}
+
+We fit the data in Figure~\ref{fig:zeta_mu} with a linear function such that:
+
+\begin{equation}
+\log_{10}(\hat\zeta) = \zeta_0 + \zeta_1 \times \mu,
+\label{eqn:zetafit}
+\end{equation}
+
+\noindent where $\hat\zeta$ is the correction factor that will be applied to each galaxy as a function of surface brightness.
+The best-fit parameters to the linear fit (from least-squares optimization) are $\zeta_0 = 0.1, \zeta_1=1.4$.
+To make the final debiased correction, we modify the simple exponential form of Equation~\ref{eqn:fzeta} to bound the debiased vote fractions between $f$ and 1:
+
+\begin{equation}
+f_\textrm{debiased} = 1 - (1 - f)e^{\frac{z-z_0}{\hat\zeta}}.
+\label{eqn:fzeta_mod}
+\end{equation}
 
@@
 
+\subsection{Results of FERENGI Analysis}
+
+We show here the {\bf preliminary} results of citizen scientist classifications of images of galaxies placed at artificial redshifts.
+Figure \ref{results1} shows the {\bf preliminary} range of change of vote fractions for the change of $p_{\rm features}$ with redshift, for galaxies with different vote fraction levels, three ranges of surface-brightness levels and 7~evolutionary corrections (this last bit is indicated by the colour).
+
+%-----------------------------------------------------------------------------------------------------------------------------------
+\begin{figure}
+\begin{center}
+
+\includegraphics[width=0.45\textwidth]{somewhat_fake_results.pdf}
+
+\caption{Preliminary results of the \ferengi{} redshifting exercise.
+WARNING NO USER WEIGHTING....
+For a range of vote fraction levels with three surface-brightness levels and 7 evolutionary corrections each (the colours indicate evolutionary correction value with green being $e=0$, we show the range of evolution of the vote fractions for featured vs.
+smooth with redshift.}
+
+\label{fig:ferengi_results_fake}
+
+\end{center}
+\end{figure}
+%-----------------------------------------------------------------------------------------------------------------------------------
+
 \subsubsection{TODO LIST}
@@
 Galaxy Zoo 2 was developed with the help of a grant from The Leverhulme Trust.
-KS gratefully acknowledges support from Swiss National Science Foundation Grant PP00P2\_138979/1.
 
-We thank ASIAA for hosting the ``Citizen Science in Astronomy" workshop, Mar 3-7th 2014 in Taipei, Taiwan, at which some of this analysis was done.
+We thank ASIAA for hosting the ``Citizen Science in Astronomy'' workshop, Mar 3-7 2014 in Taipei, Taiwan, at which some of this analysis was done.
 
@@
 The SDSS is managed by the Astrophysical Research Consortium for the Participating Institutions.
-The Participating Institutions are the American Museum of Natural History, Astrophysical  Institute Potsdam, University of Basel, University of Cambridge,
-Case Western Reserve University, University of Chicago, Drexel University, Fermilab, the Institute for Advanced Study, the Japan 
-Participation Group, Johns Hopkins University, the Joint Institute for Nuclear Astrophysics, the Kavli Institute for Particle Astrophysics and Cosmology, the Korean Scientist Group, the Chinese Academy of Sciences (LAMOST), Los Alamos National Laboratory, the Max-Planck-Institute for Astronomy (MPIA), the Max-Planck-Institute for Astrophysics (MPA), New Mexico State Uni-
-versity, Ohio State University, University of Pittsburgh, University of Portsmouth, Princeton University, the United States Naval Observatory and the University of Washington.
+The Participating Institutions are the American Museum of Natural History, Astrophysical  Institute Potsdam, University of Basel, University of Cambridge, Case Western Reserve University, University of Chicago, Drexel University, Fermilab, the Institute for Advanced Study, the Japan Participation Group, Johns Hopkins University, the Joint Institute for Nuclear Astrophysics, the Kavli Institute for Particle Astrophysics and Cosmology, the Korean Scientist Group, the Chinese Academy of Sciences (LAMOST), Los Alamos National Laboratory, the Max-Planck-Institute for Astronomy (MPIA), the Max-Planck-Institute for Astrophysics (MPA), New Mexico State University, Ohio State University, University of Pittsburgh, University of Portsmouth, Princeton University, the United States Naval Observatory and the University of Washington.
 

### 2015-08-08 writeup/gz_hubble_data.tex
updating writing_catalog with master stuff
added table of stuff

@@
 \begin{center}
-\includegraphics[width=60mm]{example_ferengi2.pdf}
-%\includegraphics[height=80mm,angle=-90]{TuningFork.pdf}
+\includegraphics[width=60mm]{figures/example_ferengi2.pdf}
 \caption{Examples of an obvious spiral and obvious elliptical at $z=0$ which both look similar when redshifted to $z=0.8$.
@@
 \begin{figure*}
-\includegraphics[width=160mm]{example_ferengi.pdf}
-%\includegraphics[height=80mm]{TuningFork.pdf}
+\includegraphics[width=160mm]{figures/example_ferengi.pdf}
 \caption{Examples of two galaxies which have been run through the FERENGI code to produce simulated HST images.
@@
 \begin{center}
-\includegraphics[width=\textwidth]{zeta_examples.pdf}
+\includegraphics[width=\textwidth]{figures/zeta_examples.pdf}
 \caption{Behavior of the normalized, weighted vote fractions of features visible in a galaxy ($f_\textrm{features}$) as a function of redshift in the artifical \ferengi{} images.
@@
 \begin{center}
-\includegraphics[width=0.50\textwidth]{zeta_mu.pdf}
+\includegraphics[width=0.50\textwidth]{figures/zeta_mu.pdf}
 \caption{All fits for the vote fraction dropoff parameter $\zeta$ for $f_\textrm{features}$ in the \ferengi{} galaxies as a function of surface brightness.
@@
 \begin{center}
-\includegraphics[width=\textwidth]{p_vs_p_SB_redshift.pdf}
+\includegraphics[width=\textwidth]{figures/p_vs_p_SB_redshift.pdf}
 \caption{a caption. Add scale in $p_{\rm features}$ somehow that doesn't clutter the plot even more. }
@@
 In Figure \ref{fig:p_vs_p} we see that the relationship between $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$ is \emph{not} always single valued; hence we do not find it appropriate to correct galaxies that lie in these regions of surface brightness/redshift/$p_{\rm features}$ space.
-Our criteria for determining whether a region of this space is correctable is as follows: For each surface brightness and redshift bin, we examine the distribution of $p_{\rm features,z=0.3}$ for fixed $p_{\rm features,z}$ in bins of $\Delta p_{\rm features,z} = 0.1$.
-These sub-bins are marked by the horizontal lines within each larger, surface brightness/redshift bin.
-First, we require at least 5 points in each sub-bin to determine with confidence whether that region is correctable or uncorrectable.
-For the region to be considered correctable, we require that the inner two quartiles of the distribution of $p_{\rm features,z=0.3}$ within these sub-bins span a range less than 0.2.
-These regions are coloured purple, and the inner two quartile ranges are indicated by the black error bars within each sub-bin.If the spread is greater than 0.2, the region is considered uncorrectable; these are marked in green.
-Any region with fewer than 5 points is considered to have ``not enough information (NEI)'', and left uncoloured on the plot.
+These regions tend to have low $p_{\rm features}$ values at high redshift, but a wide range of values at $z=0.3$.
+These regions contain two morphological types of galaxies: First are genuine ellipticals, which have low values of $p_{\rm features}$ at both high and low redshift.
+Second are disks whose features become washed out at high redshift; hence their $p_{\rm freatures}$ value at $z=0.3$ may be quite high, while the value observed at high redshift is very low.
+This effect is strongest at the highest redshift and the lowest surface brightnesses, where features become near impossible to discern from the images.
+From this information we conclude that, for the Hubble galaxies, we cannot distinguish between genuine ellipticals and disks if the measured value of $p_{\rm features}$ is too low for a given surface brightness and redshift, because the relationship between the measured value and the ``original'' ($z=0.3$) value is not single-valued.
+
+Our criteria for determining whether a region of this space is single-valued, and therefore correctable, is as follows: For each surface brightness and redshift bin, we examine the distribution of $p_{\rm features,z=0.3}$ in four bins of $p_{\rm features,z}$.
+These sub-bins are marked by the horizontal lines within each larger, surface brightness/redshift bin in Figure \ref{fig:p_vs_p}.
+First, we compute the interquartile range (IQR) of the distribution of $p_{\rm features,z=0.3}$ in each sub-bin, which are indicated by the orange bars.
+For the region to be considered correctable, we require that the IQR of the distribution within these sub-bins is less than the sub-bin height.
+Regions which fit these criteria are uncouloured in the plot.
+If the IQR is greater than the bin height, the region is considered uncorrectable; these are marked in green.
+Any region with fewer than 5 points is considered to have ``not enough information (NEI)'', and are shown in purple.
 
@@
 \begin{itemize}
-\item talk about where purple and green tend to be on plot, and about how green areas are primarily ellipticals and disks with all the features washed out - can't tell them apart! hence, can't debias
 \item talk about where the Hubble sample falls in this space, reference table \ref{hubble_debiasable} 
-\item justify $N>5$ and spread $< 0.2$ (or find a better way to choose criteria)
 \item check out corrections for correctable and NEI, show some sample images of corrected galaxies
@@
 \label{hubble_debiasable}}
-\begin{tabular}{lrr}
+\begin{tabular}{lrrrrrrr}
 \hline\hline
-Category &  N & \% \\
+                                   & AEGIS   & COSMOS & GEMS & GOODS-N & GOODS-S & SDSS    & Total \\
 \hline
-Correctable   & 7408 & 6 \%  \\
-Uncorrectable & 58526 & 50 \%\\
-NEI           & 52149 & 44 \% \\
-Total         & 118083 & 100 \% \\
+Correctable                        & 2,438   & 21,522 & 28,52 & 1,146  & 1,040   & 0       & 28,998\\
+Uncorrectable                      & 1,403   & 19,626 & 1,832 & 271    & 980     & 0       & 24,112\\
+No Correction Needed ($z \le 0.3$) & 854     & 10,840 & 1,086 & 208    & 229     & 37,545  & 50,762\\ 
+NEI                                & 2,464   & 33,727 & 1,886 & 691    & 2,023   & 0       & 40,791\\
+No Redshift Information            & 1,348   & 7,093  & 1,648 & 235    & 641     & 14,316  & 25,281\\
+Total                              & 8,507   & 92,808 & 9,304 & 2,551  & 4,913   & 51,861  & 169,944\\
 \hline\hline
@@
 
-\includegraphics[width=0.45\textwidth]{somewhat_fake_results.pdf}
+\includegraphics[width=0.45\textwidth]{figures/somewhat_fake_results.pdf}
 

### 2015-08-11 writeup/gz_hubble_data.tex
fixed table 4

@@
 
-\begin{table}
-\caption{Debiasable Hubble Stuff.
-Doesn't include SDSS yet.
-Note: stuff without good redshift info automatically gets put in uncorrectable category - which is about 25,000 galaxies.
-Might increase correctable number if we can get these measurements.
-\label{hubble_debiasable}}
+\begin{table*}
+\caption{Breakdown of what we can correct out of the Hubble data, by sample. \label{hubble_debiasable}}
 \begin{tabular}{lrrrrrrr}
@@
 Uncorrectable                      & 1,403   & 19,626 & 1,832 & 271    & 980     & 0       & 24,112\\
-No Correction Needed ($z \le 0.3$) & 854     & 10,840 & 1,086 & 208    & 229     & 37,545  & 50,762\\ 
-NEI                                & 2,464   & 33,727 & 1,886 & 691    & 2,023   & 0       & 40,791\\
-No Redshift Information            & 1,348   & 7,093  & 1,648 & 235    & 641     & 14,316  & 25,281\\
+No Correction Needed ($z \le 0.3$) & 698     & 9,679 & 1,012 & 171    & 199     & 37,545  & 50,762\\ 
+NEI                                & 2,621   & 34,888 & 1,960 & 728    & 2,053   & 0       & 40,791\\
+No Redshift Information            & 1,347   & 7,093  & 1,648 & 235    & 641     & 14,316  & 25,281\\
 Total                              & 8,507   & 92,808 & 9,304 & 2,551  & 4,913   & 51,861  & 169,944\\
@@
 \end{tabular}
-\end{table}
+\end{table*}
 

### 2015-08-11 writeup/gz_hubble_data.tex
fixed table 4

@@
 Uncorrectable                      & 1,403   & 19,626 & 1,832 & 271    & 980     & 0       & 24,112\\
-No Correction Needed ($z \le 0.3$) & 698     & 9,679 & 1,012 & 171    & 199     & 37,545  & 50,762\\ 
-NEI                                & 2,621   & 34,888 & 1,960 & 728    & 2,053   & 0       & 40,791\\
-No Redshift Information            & 1,347   & 7,093  & 1,648 & 235    & 641     & 14,316  & 25,281\\
+No Correction Needed ($z \le 0.3$) & 698     & 9,679 & 1,012 & 171    & 199     & 37,545  & 49,034\\ 
+NEI                                & 2,621   & 34,888 & 1,960 & 728    & 2,053   & 0       & 42,250\\
+No Redshift Information            & 1,347   & 7,093  & 1,648 & 235    & 641     & 14,316  & 25,280\\
 Total                              & 8,507   & 92,808 & 9,304 & 2,551  & 4,913   & 51,861  & 169,944\\

### 2015-08-13 writeup/gz_hubble_data.tex
added some figures of hubble debiased data

@@
 \subsection{Approach to debiasing morphological classifications}
+\label{sec:zeta}
 
@@
 
-In Figure \ref{fig:p_vs_p} we examine the change in $p_{\rm features}$ for the FERENGI images relative to their lowest simulated redshift ($\rm z_{sim}=0.3$).
+In Figure \ref{fig:p_vs_p} we examine the change in $p_{\rm features}$ for the \ferengi{} galaxies relative to their lowest simulated redshift.
+In this analysis, only galaxies whose lowest simulated redshift image was ($\rm z_{sim}=0.3$) were used (see Table \ref{ferengivalues}), and only those which had detectable surface brightness measurements in Sextractor; this includes 3,959 of the total 6,466 images.
 For each simulated redshift value $z$, and at fixed surface brightness $\mu$, we plot $p_{\rm features,z}$, the value measured at that simulated redshift, vs $p_{\rm features,z=0.3}$, the value measured for the same galaxy imaged at $z=0.3$.
-Only images corresponding to galaxies which also had FERENGI images at $z=0.3$ were included in this plot, which include 4031 out of the total 6624.
 
@@
 
+Using this approach, 52\% of the \ferengi{} images were found to have single-valued relationships between their $p_{\rm features}$ values at high and low redshift (see Table \ref{ferengi_corrections} for a summary.) Only these images were used in determining the $\zeta$ function (Section \ref{sec:zeta}).
+
+\begin{table}
+\caption{Distribution of \ferengi{} images analysed in Figure \ref{fig:p_vs_p}.
+Correctable images had a single-valued relationship between their measured $p_{\rm features}$ values at high and low redshifts (white regions in Figure \ref{fig:p_vs_p}).
+Uncorrectable images had a non single-valued relationship (green regions).
+NEI images had undetermined relationships due to a lack of data ($N<5$) in their corresponding sub-bins (purple regions).
+\label{ferengi_corrections}}
+\begin{tabular}{lcc}
+\hline \hline
+				   & N     & \% \\
+\hline 
+Correctable                        & 2,057   & 52\% \\
+Uncorrectable                      & 1,732   & 44\% \\
+NEI                                & 170     &  4\%\\
+Total                              & 3,959   & 100\% \\
+\hline \hline
+\end{tabular}
+\end{table}
+
 Stuff to do in this section:
@@
 \hline
-Correctable                        & 2,438   & 21,522 & 28,52 & 1,146  & 1,040   & 0       & 28,998\\
+Correctable                        & 2,325   & 20,669 & 2,748 & 1,074  & 1,022   & 0       & 27,838\\
 Uncorrectable                      & 1,403   & 19,626 & 1,832 & 271    & 980     & 0       & 24,112\\
-No Correction Needed ($z \le 0.3$) & 698     & 9,679 & 1,012 & 171    & 199     & 37,545  & 49,034\\ 
-NEI                                & 2,621   & 34,888 & 1,960 & 728    & 2,053   & 0       & 42,250\\
+No Correction Needed ($z \le 0.3$) & 967     & 11,693 & 1,190 & 280    & 247     & 37,545  & 51,922\\ 
+NEI                                & 2,465   & 33,727 & 1,886 & 691    & 2,023   & 0       & 40,792\\
 No Redshift Information            & 1,347   & 7,093  & 1,648 & 235    & 641     & 14,316  & 25,280\\
@@
 \end{table*}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\textwidth]{figures/hubble_z_mu_p_distributions.pdf}
+\caption{Distribution of things for 3 groups. }
+\label{fig:z_mu_p}
+\end{center}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\textwidth]{figures/debiased_corrections.pdf}
+\caption{Debiased vs weighted values for 3 groups.}
+\label{fig:features_corrections}
+\end{center}
+\end{figure*}
 

### 2015-08-25 writeup/gz_hubble_data.tex
updates to writeup

@@
 \begin{center}
+\includegraphics[width=\textwidth]{figures/eye_of_sauron.pdf}
+\caption{Surface brightness vs.
+redshift of 118,083 galaxies in the ACS Hubble sample.
+The white grid denotes the surface brightness and redshift range of the \ferengi{} images, subdivided in bins corresponding to fixed ranges used for analysis in Figure \ref{fig:p_vs_p}.}
+
+\label{fig:features_corrections}
+\end{center}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
 \includegraphics[width=\textwidth]{figures/p_vs_p_SB_redshift.pdf}
-\caption{a caption. Add scale in $p_{\rm features}$ somehow that doesn't clutter the plot even more. }
+\caption{Effects of redshift bias in 3,959 images in the \ferengi{} sample.
+Each point in a given redshift and surface brightness bin represents a unique galaxy.
+On the y-axis in each bin is the $p_{features}$ value of the image of that galaxy redshifted to the value corresponding to that redshift bin.
+On the x-axis is the $p_{features}$ value of the image of the same galaxy redshifted to $z=0.3$.
+Regions in which there is a nearly one-to-one relationship between $p_{features}$ at high redshift and $z=0.3$ are white; those in which there is not are green, and those with not enough data ($N<5$) are purple.
+}
 \label{fig:p_vs_p}
@@
 \includegraphics[width=\textwidth]{figures/hubble_z_mu_p_distributions.pdf}
-\caption{Distribution of things for 3 groups. }
+\caption{Distributions of redshift, surface brightness, and $p_{features}$ for correctable (purple), uncorrectable (green), and NEI (pink) galaxies in the full Hubble sample.
+The uncorrectable galaxies tend towards higher redshift, slightly lower in surface brightness, and lower values of $p_{features}$ than the correctable galaxies.
+The long tail of NEI galaxies in redshift and surface brightness demonstrates the limits of the \ferengi{} sample, for which there is no data at $z>1$ or $\mu>24$.}
 \label{fig:z_mu_p}
@@
 \includegraphics[width=\textwidth]{figures/debiased_corrections.pdf}
-\caption{Debiased vs weighted values for 3 groups.}
+\caption{Debiased $p_{features}$ corrected to $z=0.3$ vs weighted $p_{features}$ for the correctable (left), uncorrectable (middle), and NEI (right) galaxies in the Hubble sample.}
+
 \label{fig:features_corrections}

### 2015-09-11 writeup/gz_hubble_data.tex
Figures 7 and 8 added

@@
 
-\subsection{Results of Zeta Approach (Mel stuff)}
+\subsection{Results of $\zeta$ approach}
 
@@
 \item talk about where the Hubble sample falls in this space, reference table \ref{hubble_debiasable} 
+\item justify $N>5$ and spread $< 0.2$ (or find a better way to choose criteria)
 \item check out corrections for correctable and NEI, show some sample images of corrected galaxies
@@
 We show here the {\bf preliminary} results of citizen scientist classifications of images of galaxies placed at artificial redshifts.
-Figure \ref{results1} shows the {\bf preliminary} range of change of vote fractions for the change of $p_{\rm features}$ with redshift, for galaxies with different vote fraction levels, three ranges of surface-brightness levels and 7~evolutionary corrections (this last bit is indicated by the colour).
+Figure \ref{fig:ferengi_results_fake} shows the {\bf preliminary} range of change of vote fractions for the change of $p_{\rm features}$ with redshift, for galaxies with different vote fraction levels, three ranges of surface-brightness levels and 7~evolutionary corrections (this last bit is indicated by the colour).
 

### 2016-01-15 writeup/gz_hubble_data.tex

@@
 \begin{itemize}
-\item AEGIS has 1 orbit each (~2200 seconds) in F606W (V band) and F814W filter and has been dithered to 0.03 ''/pixel; the imaging covers $\sim710$~arcmin$^2$.
+\item AEGIS has 1 orbit each ($\sim2200$~seconds) in the F606W (V-band) and F814W (I-band) filters and has been dithered to 0.03~\arcsec/pixel; the imaging covers $\sim710$~arcmin$^2$.
 
 \item GOODS targeted 2 fields, GOODS-N and GOODS-S, imaging in 4 filters -- F435W (B), F606W (V), F775W (i), and F850LP (z).
-The mean exposure times vary, from 1000 - 2100 seconds.
-The images have been dithered to a pixel scale of 0.03 ''/pixel and covers at total area of ~320 arcmin$^2$ (160 arcmin$^2$ per field).
+The mean exposure times vary, from 1000 -- 2100~seconds.
+The images have been dithered to a pixel scale of 0.03~\arcsec/pixel and covers a total area of $\sim320$~arcmin$^2$ (160~arcmin$^2$ per field).
 The filters that \citet{gri12} uses for the colored images were F606W and F775W for GOODS-N and F606W and F850LP for GOODS-S.
 
-\item COSMOS has 1 orbit (2028 seconds) in the F814W (I band) filter and has been dithered to 0.05 ''/pixel; it covers the largest area, ~1.8 deg$^2$.
+\item COSMOS has 1 orbit (2028~seconds) in the F814W (I-band) filter and has been dithered to 0.05~\arcsec/pixel; it covers the largest area, $\sim1.8$~deg$^2$.
 
-\item GEMS has 1 orbit (2160 and 2286 seconds) in the F606W and F850LP filters, with a pixel scale of 0.03 ''/pixel; it covers ~800 arcmin$^2$
+\item GEMS has 1 orbit (2160 and 2286~seconds in the F606W and F850LP filters, respectively) with a pixel scale of 0.03~\arcsec/pixel; it covers $\sim800$~arcmin$^2$
 \end{itemize}
 
+% Note: galaxy counts remove the duplicate observations from gz_hst_table
+
 \begin{table*}
-\caption{Summary of GZ Hubble Samples \label{gzh_numbers}}
-\begin{tabular}{lclccc}
+\caption{Summary of Galaxy Zoo: Hubble imaging \label{gzh_numbers}}
+\begin{tabular}{lclcrr}
 \hline\hline
 Survey &  $t_{\rm exp}$ & Filters & Resolution & Area & $N_{\rm galaxies}$ \\
- & seconds & & \arcsec/pix & sq arcmin \\
+ & [sec] & & [\arcsec/pix] & [arcmin$^2$] & \\
 \hline
-AEGIS & 2200 & F606W (V) and F814W (I) & 0.03 & 710 \\
-COSMOS & 2028 & F814W (I) & 0.05 & 6480\\
-GEMS & 2160/2286 & F606W (V) and F850LP (z) & 0.03 & 800 \\
-GOODS & 1000-2100s & F435W (B), F606W (V), F775W (i), F850LP (z) & 0.03 & 320 \\
+AEGIS                         & 2200        & F606W (V) and F814W (I)                     & 0.03 & 710   & 8157  \\
+COSMOS                        & 2028        & F814W (I)                                   & 0.05 & 6480  & 88530 \\
+GEMS                          & 2160$-$2286 & F606W (V) and F850LP (z)                    & 0.03 & 800   & 9143  \\
+GOODS                         & 1000$-$2100 & F435W (B), F606W (V), F775W (i), F850LP (z) & 0.03 & 320   & 7336  \\
+\hspace{10pt} \emph{GOODS-N}  & $-$         & $-$                                         & $-$  & $-$   & \emph{2551}  \\
+\hspace{10pt} \emph{GOODS-S}  & $-$         & $-$                                         & $-$  & $-$   & \emph{4785}  \\
+\hline
+total                         & $-$         & $-$                                         & $-$  & 8310  & 113166  \\
 \hline\hline
@@
 
-\subsection{User Weighting}
+\subsection{User weighting}
 
@@
 
-\section{Correcting for Redshift Dependent Classification Bias}
+\section{Correcting for redshift-dependent classification bias}
 
@@
 In addition the effects of band shifting will change the images even more across these redshift ranges.
-Figure \ref{redshift} which illustrates one possible effect of losing features in spiral galaxies at high redshift).
+%Figure~\ref{exampleFERENGI} illustrates some of the possible effects of losing features in spiral galaxies at high redshift.
 
 %-----------------------------------------------------------------------------------------------------------------------------------
-\begin{figure}
-\begin{center}
-\includegraphics[width=60mm]{figures/example_ferengi2.pdf}
-\caption{Examples of an obvious spiral and obvious elliptical at $z=0$ which both look similar when redshifted to $z=0.8$.
+%\begin{figure}
+%\begin{center}
+%\includegraphics[width=60mm]{figures/example_ferengi2.pdf}
+%\caption{Examples of an obvious spiral and obvious elliptical at $z=0$ which both look similar when redshifted to $z=0.8$.
 See below for the description of the method for redshifting.\label{exampleFERENGI}}
-\end{center}
-\end{figure}
+%\end{center}
+%\end{figure}
  %-----------------------------------------------------------------------------------------------------------------------------------
@@
 In order to test the effects of redshift we made images of the same galaxy at a variety of redshifts using input images from the SDSS \citep{yor00,str02} and the \ferengi{} code \citep{bar08a} to produce images that match the observational properties of those observed in the HST surveys.
+These images were classified in the Galaxy Zoo interface using the same classification scheme as the original HST images.
 
@@
 We selected 288 unique galaxies from SDSS imaging to run through the \ferengi{} code.
-
-The selection spanned a variety of galaxy morphologies (as indicated by GZ2 classifications), with a range of surface brightnesses, and also spanned the redshift range of SDSS targets (in $N_z = 4$ bins) in order to be optimised for different target minimum redshifts in HST imaging.
+The selection spanned a variety of galaxy morphologies (as selected by GZ2 classifications) and $r^\prime$-band surface brightnesses, and also spanned the redshift range of SDSS targets (in $N_z = 4$ bins) in order to be optimised for different target minimum redshifts in HST imaging.
 
 The selection criteria for the different morphological categories is summarised in Table \ref{morphologies}.
-The surface brightness selection ($N_\mu = 3$) was (1) low: $\mu > 21.5 {\rm mag arsec}^2$;  (2) mid: $20.5 < \mu < 21.5 {\rm mag arsec}^2$; and (3) high: $\mu < 20.5 {\rm mag arsec}^2$.
+The surface brightness selection ($N_\mu = 3$) was (1) low: $\mu > 21.5$~\magarc;  (2) mid: $20.5 < \mu < 21.5$~\magarc; and (3) high: $\mu < 20.5$~\magarc.
+For each of the four ``target redshifts'' ($z = 0.3, 0.5, 0.8$ and $1.0$), the images were redshifted in $\Delta z = 0.1$ bins up to $z=1.0$.
 
@@
 
-For each of the four ``target redshifts'' ($z = 0.3, 0.5, 0.8$ and $1.0$), the images were redshifted in $\Delta z = 0.1$ bins up to $z=1.0$.
-In addition different evolution models were assumed in \ferengi{}.
-This evolution is a crude mechanism that is suppose to mimic the brightness increase of galaxies with increasing redshift.
-The evolution mechanism allows us to make galaxies brighter as linear function of redshift, and that is it.
-It is an empirical addition to the magnitude of a galaxy of the form $M' = e\times z + M$, where $M'$ is the corrected magnitude, $e$ is the evolutionary correction in magnitudes.
-(i.e.
-$e=-1$ essentially brightens the galaxy by 1~magnitude by $z=1$).
-We ran \ferengi{} for values of $e$ starting from $e=0$ and decreasing to $e=-3.5$ in $\Delta e = 0.5$ steps.
-Depending on the target, or starting redshift we ran \ferengi{} for several final redshifts and different evolution models as summarized in Table~\ref{ferengivalues}.
+In addition to the physical parameters of the input images, the \ferengi{} output depends on assumptions of the global galaxy evolution model.
+This evolution is a crude mechanism that mimics the brightness increase of galaxies with increasing redshift (out to at least $z\sim1-2$).
+The effect on the redshifted images is simply an empirical addition to the magnitude of a galaxy of the form $M' = e\times z + M$, where $M'$ is the corrected magnitude, and $e$ is the evolutionary correction in magnitudes (i.e., $e=-1$ essentially brightens the galaxy by 1~magnitude by $z=1$).
+We ran \ferengi{} for values of $e$ starting from $e=0$ and decreasing to $e=-3.5$ in increments of $\Delta e = 0.5$.
+Figure~\ref{exampleFERENGI} shows several examples of the effects of ``losing`` spiral/disc features with increasing redshift for two galaxies with $e=0$.
+
+The final number of \ferengi{} images produced for each galaxy is a ultimately a function of galaxy's redshift, since the code cannot resample the images at better angular resolution than the original SDSS data, and the number of $e$ values selected.
+Table~\ref{ferengivalues} summarizes the total sample of redshifted images produced for GZ: Hubble.
 
 \begin{table}
-\caption{Summary of FERENGI runs \label{ferengivalues}}
-\begin{tabular}{lcccccc}
+\caption{Summary of FERENGI artificial redshifting \label{ferengivalues}}
+\begin{tabular}{lccccr}
 \hline\hline
-$z_{\rm target}$ & $N_{z {\rm bins}}$ & $N_{\rm evolution}$ & $e_{\rm max}$ & $N_{\rm runs}$ & $N_{\rm total}$\\
+$z_{\rm target}$ & $N_{z {\rm bins}}$ & $N_{\rm evolution}$ & $e_{\rm max}$ & $N_{\rm galaxies}$ & $N_{\rm images}$\\
 \hline
-0.3              & 8                  & 7                   & $-3.0$        & 56             & 4031 \\
-0.5              & 6                  & 4                   & $-1.5$        & 24             & 1728 \\
-0.8              & 3                  & 3                   & $-1.0$        &  9             &  648 \\
-1.0              & 1                  & 3                   & $-1.0$        &  3             &  216 \\
+0.3              & 8                  & 7                   & $-3.0$        & 72             & 4032 \\
+0.5              & 6                  & 4                   & $-1.5$        & 72             & 1728 \\
+0.8              & 3                  & 3                   & $-1.0$        & 72             &  648 \\
+1.0              & 1                  & 3                   & $-1.0$        & 72             &  216 \\
 \hline\hline
@@
 \end{table}
-
-Two series of example redshifted images are shown in Figure \ref{exampleFERENGI}, both for runs with no evolution ($e=0$).
 
@@
 
-\subsection{Approach to debiasing morphological classifications}
+\subsection{Correcting GZH morphologies for classification bias}
 \label{sec:zeta}
@@
 The combination of all such parameters forms a high-dimensional space, and we have insufficient test galaxies to measure the individual effects of each.
-Instead, we use just two parameters that are intended to capture the bulk of the change in bias (based on GZ1/GZ2): a galaxy's $r$-band surface brightness ($\mu_r$; intrinsic) and redshift ($z$; extrinsic).
+Instead, we use just two parameters that are intended to capture the bulk of the change in bias (based on GZ1/GZ2): a galaxy's $r^\prime$-band surface brightness ($\mu_r$; intrinsic) and redshift ($z$; extrinsic).
 
-The change in bias as a function of $\mu_r$ and $z$ is measured using the \ferengi{} images at all evolutionary corrected factors.
+The change in bias as a function of $\mu_r$ and $z$ is measured using the \ferengi{} images over all the evolutionary corrected factors.
 We assume that the ``true'' (ie, debiased) vote fraction $f_{\mu,z}$ for a galaxy can be expressed as:
@@
 redshift of 118,083 galaxies in the ACS Hubble sample.
-The white grid denotes the surface brightness and redshift range of the \ferengi{} images, subdivided in bins corresponding to fixed ranges used for analysis in Figure \ref{fig:p_vs_p}.}
+The white grid denotes the surface brightness and redshift range of the \ferengi{} images, subdivided in bins corresponding to fixed ranges used for analysis in Figure~\ref{fig:p_vs_p}.}
 
@@
 
-In Figure \ref{fig:p_vs_p} we examine the change in $p_{\rm features}$ for the \ferengi{} galaxies relative to their lowest simulated redshift.
+In Figure~\ref{fig:p_vs_p} we examine the change in $p_{\rm features}$ for the \ferengi{} galaxies relative to their lowest simulated redshift.
 In this analysis, only galaxies whose lowest simulated redshift image was ($\rm z_{sim}=0.3$) were used (see Table \ref{ferengivalues}), and only those which had detectable surface brightness measurements in Sextractor; this includes 3,959 of the total 6,466 images.
@@
 
-In Figure \ref{fig:p_vs_p} we see that the relationship between $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$ is \emph{not} always single valued; hence we do not find it appropriate to correct galaxies that lie in these regions of surface brightness/redshift/$p_{\rm features}$ space.
+In Figure~\ref{fig:p_vs_p} we see that the relationship between $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$ is \emph{not} always single valued; hence we do not find it appropriate to correct galaxies that lie in these regions of surface brightness/redshift/$p_{\rm features}$ space.
 These regions tend to have low $p_{\rm features}$ values at high redshift, but a wide range of values at $z=0.3$.
@@
 Our criteria for determining whether a region of this space is single-valued, and therefore correctable, is as follows: For each surface brightness and redshift bin, we examine the distribution of $p_{\rm features,z=0.3}$ in four bins of $p_{\rm features,z}$.
-These sub-bins are marked by the horizontal lines within each larger, surface brightness/redshift bin in Figure \ref{fig:p_vs_p}.
+These sub-bins are marked by the horizontal lines within each larger, surface brightness/redshift bin in Figure~\ref{fig:p_vs_p}.
 First, we compute the interquartile range (IQR) of the distribution of $p_{\rm features,z=0.3}$ in each sub-bin, which are indicated by the orange bars.
@@
 \begin{table}
-\caption{Distribution of \ferengi{} images analysed in Figure \ref{fig:p_vs_p}.
-Correctable images had a single-valued relationship between their measured $p_{\rm features}$ values at high and low redshifts (white regions in Figure \ref{fig:p_vs_p}).
+\caption{Distribution of \ferengi{} images analysed in Figure~\ref{fig:p_vs_p}.
+Correctable images had a single-valued relationship between their measured $p_{\rm features}$ values at high and low redshifts (white regions in Figure~\ref{fig:p_vs_p}).
 Uncorrectable images had a non single-valued relationship (green regions).
@@
 We show here the {\bf preliminary} results of citizen scientist classifications of images of galaxies placed at artificial redshifts.
-Figure \ref{fig:ferengi_results_fake} shows the {\bf preliminary} range of change of vote fractions for the change of $p_{\rm features}$ with redshift, for galaxies with different vote fraction levels, three ranges of surface-brightness levels and 7~evolutionary corrections (this last bit is indicated by the colour).
+Figure~\ref{fig:ferengi_results_fake} shows the {\bf preliminary} range of change of vote fractions for the change of $p_{\rm features}$ with redshift, for galaxies with different vote fraction levels, three ranges of surface-brightness levels and 7~evolutionary corrections (this last bit is indicated by the colour).
 
@@
 
+\subsection{Duplicate images}
+
+\subsection{SDSS images}
+
 \section{Summary}

### 2016-01-21 writeup/gz_hubble_data.tex
Small additions to write up; adding sections

@@
 \newcommand{\ferengi}{\textsc{ferengi}}
+\newcommand{\sextractor}{\textsc{sextractor}}
 
@@
 
-This will be the data release paper for GZ Hubble. We present the classifications, the methodology for data reduction and corrections for redshift dependent biases in the observed morphologies.
+This will be the data release paper for GZ:Hubble. We present the classifications, the methodology for data reduction and corrections for redshift dependent biases in the observed morphologies.
 
@@
 \subsection{Summary of HST Legacy Survey Imaging}
+
+Needs: coordinate/location description.
+
+So GZ:CANDELS overlaps with GZ:Hubble in GOODS-S and COSMOS. GZH doesn't
 
@@
 
-The votes of individual users who classified galaxies in Galaxy Zoo Hubble are combined to make a vote fraction for each question on the classification tree.
-Users votes are weighted slightly \citep[in a method identical to that described in][]{wil13} such that users who frequently disagree with all other users end up having very low weights.
-The majority of users have weights very close to 1.0 ({\bf STEVEN: Is this true for GZH - do you have a plot of the distribution of user weights or consistencies we can include here?}.
+The votes of individual users who classified galaxies in GZH are combined to make a vote fraction for each question on the classification tree.
+Users' votes are weighted slightly \citep[in a method identical to that described in][]{wil13} such that users who frequently disagree with all other users end up having very low weights.
+The majority of users have weights very close to $w=1.0$ ({\bf STEVEN: Is this true for GZH - do you have a plot of the distribution of user weights or consistencies we can include here?}.
 
@@
 
-Previous version of Galaxy Zoo morphology classifications \citep{lin08,wil13} were based on observations of galaxies in the Sloan Digital Sky Survey (SDSS) which are typically at $z<0.1$.
-In these cases it could be assumed that there was no real evolution of the morphologies of galaxies and therefore any observed changes in the distribution of galaxies with different consensus morphologies was assumed to be due to the effects of redshift on the image quality (\ie.
-the reduction in physical resolution, surface brightness dimming etc).
-So for both previous releases of GZ morphogloies, a correction was provided for redshift dependent bias based on matching the classification fractions at the highest redshfts with those at the lowest redshift.
+The previous versions of Galaxy Zoo morphology classifications \citep{lin08,wil13} were based on observations of galaxies in the Sloan Digital Sky Survey (SDSS) which are typically at $z<0.1$.
+In these cases it was assumed that there was no cosmological evolution of the morphologies of galaxies and therefore any observed changes in the distribution of galaxies with different consensus morphologies was due to the effects of redshift on the image quality (\ie.
+the reduction in physical resolution, surface brightness dimming, etc).
+For both previous releases of GZ morphologies, we provided a correction for redshift-dependent bias based on matching the classification fractions at the highest redshfts with those at the lowest redshift.
 See \citet{bam09} and \citet{wil13} for the details.
 
-In the GZH samples the redshift range is so large that we expect to find redshift evolution of the types and morphologies of galaxies which are seen.
-So the previous methods of correcting for redshift dependent bias will not work.
-In addition the effects of band shifting will change the images even more across these redshift ranges.
-%Figure~\ref{exampleFERENGI} illustrates some of the possible effects of losing features in spiral galaxies at high redshift.
+In the GZH samples, the redshift range is large enough that we expect to measure cosmological evolution of the types and morphologies of galaxies in the sample.
+As a result, the previous methods of correcting for redshift dependent bias will not work.
+In addition, the effects of band shifting will change the images even more across these redshift ranges.
+%Figure~\ref{fig:exampleFERENGI} illustrates some of the possible effects of losing features in spiral galaxies at high redshift.
 
@@
 %\caption{Examples of an obvious spiral and obvious elliptical at $z=0$ which both look similar when redshifted to $z=0.8$.
-See below for the description of the method for redshifting.\label{exampleFERENGI}}
+See below for the description of the method for redshifting.\label{fig:exampleFERENGI}}
 %\end{center}
@@
 
-In order to test the effects of redshift we made images of the same galaxy at a variety of redshifts using input images from the SDSS \citep{yor00,str02} and the \ferengi{} code \citep{bar08a} to produce images that match the observational properties of those observed in the HST surveys.
+In order to test and correct for the effects of redshift, we generated a set of calibration images.
+These images consist of the same galaxy as it would appear over a variety of redshifts.
+The input images are from the SDSS \citep{yor00,str02} and are processed using the \ferengi{} code \citep{bar08a} to match the observational properties of the HST surveys out to $z=1$.
 These images were classified in the Galaxy Zoo interface using the same classification scheme as the original HST images.
@@
 \begin{table*}
-\caption{Summary of morphological categories selected for FERENGI sample.
-\hl{For Edmond: does $p_{\rm obvious/dominant}>0.5$ mean ($p_{\rm obv}+p_{\rm dom}>0.5$) or ($p_{\rm ob}$ OR $p_{\rm dom} >0.5$)?}\label{morphologies}}
+\caption{Summary of morphological categories selected for FERENGI sample.\label{morphologies}}
 \begin{tabular}{lllc}
@@
 Features            & Yes       & $p_{\rm features} > 0.8$, $p_{\rm odd} < 0.1$                                                         & 12 \\ 
-                    & Int   & $0.3 < p_{\rm smooth} < 0.6$, $p_{\rm odd} < 0.1$                                                     & 12 \\ 
+                    & Int.      & $0.3 < p_{\rm smooth} < 0.6$, $p_{\rm odd} < 0.1$                                                     & 12 \\ 
                     & No        & $p_{\rm smooth} > 0.8$, $p_{\rm odd} < 0.1$                                                           & 12 \\ 
 Merger              & No        & $p_{\rm features} > 0.8$, $p_{\rm odd < 0.1}$, $p_{\rm merger} < 0.1$                                 & 12 \\
-                    & Int   & $p_{\rm odd} > 0.5$, $0.1< p_{\rm merger} < 0.4$                                                      & 12 \\ 
+                    & Int.      & $p_{\rm odd} > 0.5$, $0.1< p_{\rm merger} < 0.4$                                                      & 12 \\ 
                     & Yes       & $p_{\rm odd} > 0.5$, $p_{\rm merger} > 0.4$                                                           & 12 \\
 Edge-on             & Yes       & $p_{\rm edgeon} > 0.8$, $p_{\rm features} > 0.5$                                                      & 12 \\
-                    & Int   & $0.4 < p_{\rm edgeon} < 0.8$ , $p_{\rm features} > 0.5$                                               & 12 \\
+                    & Int.      & $0.4 < p_{\rm edgeon} < 0.8$ , $p_{\rm features} > 0.5$                                               & 12 \\
                     & No        & $p_{\rm edgeon} < 0.2$, $p_{\rm features} > 0.5$                                                      & 12 \\
 Bar                 & No        & $p_{\rm bar} < 0.1$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                                 & 24 \\
-                    & Int   & $0.2 < p_{\rm bar} < 0.4$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                           & 24 \\
+                    & Int.      & $0.2 < p_{\rm bar} < 0.4$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                           & 24 \\
                     & Yes       & $p_{\rm bar} > 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                                 & 24 \\
 Visible spiral      & No        & $p_{\rm spiral} < 0.2$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$         & 12 \\
-                    & Int   & $0.2 < p_{\rm spiral} < 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$   & 12 \\
+                    & Int.      & $0.2 < p_{\rm spiral} < 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$   & 12 \\
                     & Yes       & $p_{\rm spiral} > 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$         & 12 \\
 Oblique bulge size  & No        & $p_{\rm nobulge>0.6}$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$          & 12 \\
-                    & Int   & $p_{\rm justnoticeable}>0.6$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$   & 12 \\
-                    & Yes   & $p_{\rm obvious/dominant}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$ & 12 \\
+                    & Int.      & $p_{\rm justnoticeable}>0.6$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$   & 12 \\
+                    & Yes       & $p_{\rm obvious|dominant}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$ & 12 \\
 Edge-on bulge shape & Round     & $p_{\rm rounded}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.5$                               & 12 \\
                     & Boxy      & $p_{\rm boxy}>0.4$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.2$                                  & 12 \\
-                    & Non   & $p_{\rm nobulge}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.5$                               & 12 \\
+                    & No bulge  & $p_{\rm nobulge}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.5$                               & 12 \\
 \hline\hline
@@
 We ran \ferengi{} for values of $e$ starting from $e=0$ and decreasing to $e=-3.5$ in increments of $\Delta e = 0.5$.
-Figure~\ref{exampleFERENGI} shows several examples of the effects of ``losing`` spiral/disc features with increasing redshift for two galaxies with $e=0$.
+Figure~\ref{fig:exampleFERENGI} shows several examples of the effects of ``losing`` spiral/disc features with increasing redshift for two galaxies with $e=0$.
 
-The final number of \ferengi{} images produced for each galaxy is a ultimately a function of galaxy's redshift, since the code cannot resample the images at better angular resolution than the original SDSS data, and the number of $e$ values selected.
-Table~\ref{ferengivalues} summarizes the total sample of redshifted images produced for GZ: Hubble.
+The final number of \ferengi{} images produced for each galaxy is ultimately a function of galaxy's redshift, since the new images cannot be resampled at better angular resolution than the original SDSS data, as well as the number of $e$ values selected.
+Table~\ref{ferengivalues} summarizes the total sample of redshifted images produced for GZH.
 
@@
 The value of $p_{\rm features}$ for each panel is (1) Top row: $p_{\rm features}=$ 0.9, 0.625, 0.35, 0.35, 0.225 and (2) Bottom row: $p_{\rm features}=$ 1.00, 0.875, 0.875, 0.625, 0.375.
-\label{exampleFERENGI}}
+\label{fig:exampleFERENGI}}
 \end{figure*}
@@
 This is controlled by two types of parameters: \textbf{intrinsic} properties of the galaxy itself, such as its physical diameter and luminosity, and \textbf{extrinsic} properties, such as the distance (redshift) of the galaxy and its relative orientation.
-There are likely other parameters that affect user accuracy, such as the proximity of close companions \citep[``distraction bias''; see][]{joh15} or those that vary by individual user.
-The combination of all such parameters forms a high-dimensional space, and we have insufficient test galaxies to measure the individual effects of each.
+There are likely other parameters that affect user accuracy, such as the proximity of close companions \citep[``distraction bias''; see][]{joh15} or bias as a function of the individual user.
+The combination of all such parameters forms a high-dimensional space, and we have insufficient data to measure their individual effects.
 Instead, we use just two parameters that are intended to capture the bulk of the change in bias (based on GZ1/GZ2): a galaxy's $r^\prime$-band surface brightness ($\mu_r$; intrinsic) and redshift ($z$; extrinsic).
 
-The change in bias as a function of $\mu_r$ and $z$ is measured using the \ferengi{} images over all the evolutionary corrected factors.
+The change in bias as a function of $\mu_r$ and $z$ is measured using the \ferengi{} images over all the evolutionary correction factors.
 We assume that the ``true'' (ie, debiased) vote fraction $f_{\mu,z}$ for a galaxy can be expressed as:
@@
 
-\noindent where $f_{\mu,z=0.3}$ is the ``calibrated'' vote fraction at the lowest redshift in the \ferengi{} bins, which is at redshift $z=0.3$ and $\zeta$ is a positive parameter that controls the rate at which $f$ drops off with increasing redshift.
+\noindent where $f_{\mu,z=0.3}$ is the ``calibrated'' vote fraction at the lowest redshift in the \ferengi{} bins ($z=0.3$) and $\zeta$ is a positive parameter that controls the rate at which $f$ decreases with increasing redshift.
 This formula fits the data relatively well (with almost no exceptions, the vote fractions for featured galaxies decrease monotonically with increasing redshift), and the exponential function bounds the observed vote fractions between $f_{\mu,z=0.3}$ and zero.
@@
 
-We then take the values of $\zeta$ for \emph{all} sets of artifically redshifted galaxies and use them to fit the overall distribution of $\zeta$ as a function of surface brightness (since we expect the correction being applied to vary as a function of the intrinsic galaxy properties).
-We restrict the galaxies that can be used to measure the calibration to those with data at the pivot redshift of $z=0.3$, those with non-zero $f_\textrm{features}$ at $z=0.3$, and with a reasonable fit to the exponential model ($\Delta \chi^2 > 3.0$).
+We use the values of $\zeta$ for \emph{all} sets of artifically redshifted galaxies to fit the overall distribution as a function of surface brightness, since we expect the correction being applied to vary as a function of the intrinsic galaxy properties.
+We restrict the galaxies that can be used to measure the calibration to those with data at the pivot redshift of $z=0.3$, non-zero $f_\textrm{features}$ at $z=0.3$, and with a reasonable fit to the exponential model ($\Delta \chi^2 > 3.0$).
 
-Figure~\ref{fig:zeta_mu} shows the results of the sample; the correction is a weak function of surface brightness overall.
+Figure~\ref{fig:zeta_mu} shows the results of fitting the \ferengi{} images with Equation~\ref{eqn:fzeta}; the correction is a weak function of galaxy surface brightness.
 Higher-surface brightness galaxies have stronger average corrections, likely because these galaxies are more likely to have larger $f_\textrm{features}$ values at high redshifts.
@@
 
-\noindent where $\hat\zeta$ is the correction factor that will be applied to each galaxy as a function of surface brightness.
-The best-fit parameters to the linear fit (from least-squares optimization) are $\zeta_0 = 0.1, \zeta_1=1.4$.
+\noindent where $\hat\zeta$ is the correction factor applied to each galaxy as a function of surface brightness.
+The best-fit parameters to the linear fit (from least-squares optimization) are $\zeta_0=0.1$, $\zeta_1=1.4$.
 To make the final debiased correction, we modify the simple exponential form of Equation~\ref{eqn:fzeta} to bound the debiased vote fractions between $f$ and 1:
@@
 \begin{equation}
-f_\textrm{debiased} = 1 - (1 - f)e^{\frac{z-z_0}{\hat\zeta}}.
+f_\textrm{features,debiased} = 1 - (1 - f)e^{\frac{z-z_0}{\hat\zeta}}.
 \label{eqn:fzeta_mod}
@@
 \caption{Surface brightness vs.
-redshift of 118,083 galaxies in the ACS Hubble sample.
+redshift of 118,083 galaxies in the ACS sample.
 The white grid denotes the surface brightness and redshift range of the \ferengi{} images, subdivided in bins corresponding to fixed ranges used for analysis in Figure~\ref{fig:p_vs_p}.}
@@
 In Figure~\ref{fig:p_vs_p} we examine the change in $p_{\rm features}$ for the \ferengi{} galaxies relative to their lowest simulated redshift.
-In this analysis, only galaxies whose lowest simulated redshift image was ($\rm z_{sim}=0.3$) were used (see Table \ref{ferengivalues}), and only those which had detectable surface brightness measurements in Sextractor; this includes 3,959 of the total 6,466 images.
-For each simulated redshift value $z$, and at fixed surface brightness $\mu$, we plot $p_{\rm features,z}$, the value measured at that simulated redshift, vs $p_{\rm features,z=0.3}$, the value measured for the same galaxy imaged at $z=0.3$.
+In this analysis, only galaxies whose lowest simulated redshift image was ($\rm z_{sim}=0.3$) were used (see Table \ref{ferengivalues}), and only those which had detectable surface brightness measurements in \sextractor{}; this includes 3,959 of the total 6,466 images.
+For each simulated redshift value $z$, and at a fixed surface brightness $\mu$, we plot $p_{\rm features,z}$, the value measured at that simulated redshift, vs $p_{\rm features,z=0.3}$, the value measured for the same galaxy imaged at $z=0.3$.
 
-Our objective is to use these data to predict, for a galaxy with a measured $p_{\rm features,z}$ value, what its $p_{\rm features}$ value would have been if it had been viewed at $z=0.3$.
+Our objective is to use these data to predict, for a galaxy with a measured $p_{\rm features,z}$ value, what its $p_{\rm features}$ value \emph{would have been} if it had been viewed at $z=0.3$.
 This predicted value is defined as the debiased vote fraction $p_{\rm features,debiased}$, and is calculated by applying a correction to the measured value of $p_{\rm features}$, determined by the $\zeta$ function described in the previous section.
-We determine that a predicted value can be obtained so long as the relationship between $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$ is single-valued; that is, for a given $p_{\rm features,z}$, there is one corresponding value of $p_{\rm features}$ at $z=0.3$.
+A reliable predicted value can be obtained so long as the relationship between $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$ is single-valued; that is, for a given $p_{\rm features,z}$, there is exactly one corresponding value of $p_{\rm features}$ at $z=0.3$.
 
-In Figure~\ref{fig:p_vs_p} we see that the relationship between $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$ is \emph{not} always single valued; hence we do not find it appropriate to correct galaxies that lie in these regions of surface brightness/redshift/$p_{\rm features}$ space.
+Figure~\ref{fig:p_vs_p} shows that the relationship between $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$ is \emph{not} always single valued; hence, it is not appropriate to correct galaxies that lie in certain regions of surface brightness/redshift/$p_{\rm features}$ space.
 These regions tend to have low $p_{\rm features}$ values at high redshift, but a wide range of values at $z=0.3$.
 These regions contain two morphological types of galaxies: First are genuine ellipticals, which have low values of $p_{\rm features}$ at both high and low redshift.
-Second are disks whose features become washed out at high redshift; hence their $p_{\rm freatures}$ value at $z=0.3$ may be quite high, while the value observed at high redshift is very low.
-This effect is strongest at the highest redshift and the lowest surface brightnesses, where features become near impossible to discern from the images.
-From this information we conclude that, for the Hubble galaxies, we cannot distinguish between genuine ellipticals and disks if the measured value of $p_{\rm features}$ is too low for a given surface brightness and redshift, because the relationship between the measured value and the ``original'' ($z=0.3$) value is not single-valued.
+Second are disks whose features become washed out at high redshift; hence their $p_{\rm features}$ value at $z=0.3$ may be quite high, while the value observed at high redshift is very low.
+This effect is strongest at high $z$ and low $\mu$, where features become nearly impossible to discern in the images.
 
@@
 \begin{table*}
-\caption{Breakdown of what we can correct out of the Hubble data, by sample. \label{hubble_debiasable}}
+\caption{Breakdown of what we can correct out of the GZH data, by sample. \label{hubble_debiasable}}
 \begin{tabular}{lrrrrrrr}
@@
 \includegraphics[width=\textwidth]{figures/hubble_z_mu_p_distributions.pdf}
-\caption{Distributions of redshift, surface brightness, and $p_{features}$ for correctable (purple), uncorrectable (green), and NEI (pink) galaxies in the full Hubble sample.
+\caption{Distributions of redshift, surface brightness, and $p_{features}$ for correctable (purple), uncorrectable (green), and NEI (pink) galaxies in the full GZH sample.
 The uncorrectable galaxies tend towards higher redshift, slightly lower in surface brightness, and lower values of $p_{features}$ than the correctable galaxies.
@@
 \includegraphics[width=\textwidth]{figures/debiased_corrections.pdf}
-\caption{Debiased $p_{features}$ corrected to $z=0.3$ vs weighted $p_{features}$ for the correctable (left), uncorrectable (middle), and NEI (right) galaxies in the Hubble sample.}
+\caption{Debiased $p_{features}$ corrected to $z=0.3$ vs weighted $p_{features}$ for the correctable (left), uncorrectable (middle), and NEI (right) galaxies in the GZH sample.}
 
@@
 
-\subsection{Results of FERENGI Analysis}
-
-We show here the {\bf preliminary} results of citizen scientist classifications of images of galaxies placed at artificial redshifts.
-Figure~\ref{fig:ferengi_results_fake} shows the {\bf preliminary} range of change of vote fractions for the change of $p_{\rm features}$ with redshift, for galaxies with different vote fraction levels, three ranges of surface-brightness levels and 7~evolutionary corrections (this last bit is indicated by the colour).
-
-%-----------------------------------------------------------------------------------------------------------------------------------
-\begin{figure}
-\begin{center}
-
-\includegraphics[width=0.45\textwidth]{figures/somewhat_fake_results.pdf}
-
-\caption{Preliminary results of the \ferengi{} redshifting exercise.
+%\subsection{Results of FERENGI analysis}
+%
+%{\bf Old text from Taiwan workshop}
+%
+%We show here the preliminary results of GZH classifications of images of galaxies placed at artificial redshifts.
+Figure~\ref{fig:ferengi_results_fake} shows the range of change of vote fractions for the change of $p_{\rm features}$ with redshift, for galaxies with different vote fraction levels, three ranges of surface-brightness levels and 7~evolutionary corrections (this last bit is indicated by the colour).
+%
+%%-----------------------------------------------------------------------------------------------------------------------------------
+%\begin{figure}
+%\begin{center}
+%
+%\includegraphics[width=0.45\textwidth]{figures/somewhat_fake_results.pdf}
+%
+%\caption{Preliminary results of the \ferengi{} redshifting exercise.
 WARNING NO USER WEIGHTING....
@@
 smooth with redshift.}
-
-\label{fig:ferengi_results_fake}
-
-\end{center}
-\end{figure}
-%-----------------------------------------------------------------------------------------------------------------------------------
+%
+%\label{fig:ferengi_results_fake}
+%
+%\end{center}
+%\end{figure}
+%%-----------------------------------------------------------------------------------------------------------------------------------
 
@@
 
+\subsection{Morphological measurements in GZH beyond Task 1}
+
 \subsection{Duplicate images}
 
-\subsection{SDSS images}
+\subsection{Effect of changing depth for GOODS}
+
+\subsection{SDSS Stripe 82 images}
+
+\section{Catalog}
 
@@
 
-Now people go and do science with these awesome Galaxy Zoo Hubble classifications.
+Now people go and do science with these awesome GZH classifications.
 
@@
 
+This project made heavy use of the Astropy packages in Python \citep{ast13}, as well as the seaborn plotting package \citep{was15}.
+
 HST acknowledgements.
@@
 Department of Energy, the National Aeronautics and Space Administration, the Japanese Monbukagakusho, the Max Planck Society, and the Higher Education Funding Council for England.
-The SDSS Web Site is http://www.sdss.org/.
+The SDSS website is http://www.sdss.org/.
 

### 2016-01-22 writeup/gz_hubble_data.tex

@@
 \newcommand{\fHI}{f_{\rm HI}}
+
+% Bands
+
+\newcommand{\Bband}{$B_{435W}$}
+\newcommand{\Vband}{$V_{606W}$}
+\newcommand{\iband}{$I_{775W}$}
+\newcommand{\Iband}{$I_{814W}$}
+\newcommand{\zband}{$I_{850LP}$}
 
@@
 
+\textit{Usual due diligence for an intro science paper. Should cover:}
+
+\begin{enumerate}
+    \item Motivation for studying morphology of galaxies
+    \item Particular scientific questions governed by galaxies at $z\sim1$
+    \item Theoretical predictions for galaxy morphology evolution
+    \item Past imaging and morphology studies at $z\sim1$
+    \item Summary of GZ/citizen science work on galaxy morphology to date
+\end{enumerate}
+
 \section{Sample and Data}
@@
 
-Needs: coordinate/location description.
+\begin{itemize}
+\item Hubble ACS imaging for the All-Wavelength Extended Groth Strip International Survey \citep[AEGIS;][]{dav07} covers a strip centered at $\alpha=14^\textrm{h}17^\textrm{m}, \delta=+52^\circ30^\prime$.
+The strip was originally selected due to low extinction and Galactic/zodiacal emission, making it a prime target for multi-wavelength observations by space-based observatories.
+The ACS images covered 63 separate tiles over a total area of $\sim710$~arcmin$^2$.
+Images were in two bands, with exposure times of 2300~seconds in F606W (\Vband) and 2100~seconds in F814W (\Iband).
+The final mosaic images are dithered to a resolution of 0.03~\arcsec/pixel.
+For extended objects, the limiting magnitudes of sources in AEGIS are 26.23~(AB) in \Vband{} and 25.61 (AB) in \Iband.
 
-So GZ:CANDELS overlaps with GZ:Hubble in GOODS-S and COSMOS. GZH doesn't
+\item The Great Observatories Origins Deep Survey \citep[GOODS;][]{gia04} covers two well-studied fields in the northern and southern hemispheres: the Hubble Deep Field-North ($\alpha=12^\textrm{h}36^\textrm{m}, \delta=+62^\circ14^\prime$) and the Chandra Deep Field-South ($\alpha=03^\textrm{h}32^\textrm{m}, \delta=-27^\circ48^\prime$).
+Data including Hubble ACS images are referred to as GOODS-N and GOODS-S, respectively.
+ACS imaged the GOODS fields in 4 filters -- F435W (\Bband), \Vband, F775W (\iband), and F850LP (\zband).
+The mean exposure times for each epoch vary by band, from 1050--2100~seconds.
+The \Bband{} images were completed in a single epoch at the beginning of the survey, but the \Vband, \iband, and \zband{} images were taken in five separate epochs separated by 40--50~days each.
+The ACS images are dithered to a pixel scale of 0.03~\arcsec/pixel and covers a total area of $\sim320$~arcmin$^2$ (160~arcmin$^2$ per field).
+The $5\sigma$ limiting magnitudes for extended sources are 25.7 for \Vband{} and 25.0 for \iband.
 
-\begin{itemize}
-\item AEGIS has 1 orbit each ($\sim2200$~seconds) in the F606W (V-band) and F814W (I-band) filters and has been dithered to 0.03~\arcsec/pixel; the imaging covers $\sim710$~arcmin$^2$.
+\item The Cosmic Evolution Survey \citep[COSMOS;][]{sco07} covers an area of $\sim1.8$~deg$^2$ centered at $\alpha=10^\textrm{h}00^\textrm{m}28^\textrm{s}, \delta=+02^\circ12^\prime21^{\prime\prime}$.
+Its location near the celestial equator was designed to enable coverage by ground-based telescopes in both the Northern and Southern Hemispheres, as well as the space-based observatories.
+The Hubble ACS data from COSMOS consists of 1 orbit with 2028~seconds per pointing in \Iband, consisting of 590 total pointings.
+The image resolution is dithered to 0.05~\arcsec/pixel.
+The 50\% completeness magnitude for a galaxy with a half-light radius of $0^{\prime\prime}.50$ in \Iband{} is 24.7 mag.
 
-\item GOODS targeted 2 fields, GOODS-N and GOODS-S, imaging in 4 filters -- F435W (B), F606W (V), F775W (i), and F850LP (z).
-The mean exposure times vary, from 1000 -- 2100~seconds.
-The images have been dithered to a pixel scale of 0.03~\arcsec/pixel and covers a total area of $\sim320$~arcmin$^2$ (160~arcmin$^2$ per field).
-The filters that \citet{gri12} uses for the colored images were F606W and F775W for GOODS-N and F606W and F850LP for GOODS-S.
-
-\item COSMOS has 1 orbit (2028~seconds) in the F814W (I-band) filter and has been dithered to 0.05~\arcsec/pixel; it covers the largest area, $\sim1.8$~deg$^2$.
-
-\item GEMS has 1 orbit (2160 and 2286~seconds in the F606W and F850LP filters, respectively) with a pixel scale of 0.03~\arcsec/pixel; it covers $\sim800$~arcmin$^2$
+\item The Galaxy Evolution from Morphologies and SEDS \citep[GEMS;][]{rix04,cal08} survey is also centered on the Chandra Deep Field-South.
+The GEMS data covers $\sim800$~arcmin$^2$, and surrounds the area covered by GOODS-S.
+Images from ACS in GEMS have 1 orbit per pointing for a total of 63~pointings.
+The exposure times are 2160 and 2286~seconds in \Vband{} and \zband{}, respectively.
+The image resolution has a pixel scale of 0.03~\arcsec/pixel.
+The $5\sigma$ limiting magnitudes for source detection are 25.7 AB in \Vband{} and 24.2~AB in \zband.
 \end{itemize}
@@
 \hline
-AEGIS                         & 2200        & F606W (V) and F814W (I)                     & 0.03 & 710   & 8157  \\
-COSMOS                        & 2028        & F814W (I)                                   & 0.05 & 6480  & 88530 \\
-GEMS                          & 2160$-$2286 & F606W (V) and F850LP (z)                    & 0.03 & 800   & 9143  \\
-GOODS                         & 1000$-$2100 & F435W (B), F606W (V), F775W (i), F850LP (z) & 0.03 & 320   & 7336  \\
+AEGIS                         & 2100$-$2300 & \Vband{} and \Iband{}            & 0.03 & 710   & 8157  \\
+COSMOS                        & 2028        & \Iband{}                         & 0.05 & 6480  & 88530 \\
+GEMS                          & 2160$-$2286 & \Vband{} and \zband{}            & 0.03 & 800   & 9143  \\
+GOODS                         & 1000$-$2100 & \Bband, \Vband, \iband, \zband{} & 0.03 & 320   & 7336  \\
 \hspace{10pt} \emph{GOODS-N}  & $-$         & $-$                              & $-$  & $-$   & \emph{2551}  \\
@@
 
+\subsection{Image creation}
+
+The GOODS images in GZH use mosaics constructed from both 2-epoch and 5-epoch sets of data.
+
+The filters that \citet{gri12} uses for the colored images were F606W and F775W for GOODS-N and F606W and F850LP for GOODS-S.
+
+We use different filters for the north and south GOODS fields so that GEMS can be directly compared with GOODS-S.
+
+Fake AGN
+
+Stripe 82
+
+Different treatment of colored noise in COSMOS; creating color gradients with Subaru data and using \Iband{} for illumination map.
+
+FERENGI images.
+
 \subsection{User weighting}
@@
 The majority of users have weights very close to $w=1.0$ ({\bf STEVEN: Is this true for GZH - do you have a plot of the distribution of user weights or consistencies we can include here?}.
+
+\section{Galaxy Zoo interface and classifications}
+
+\begin{figure*}
+\includegraphics[width=160mm]{figures/gzh_interface.png}
+\caption{Screenshot of the Galaxy Zoo: Hubble interface showing an example COSMOS image at the first step in the decision tree.\label{fig:interface}}
+\end{figure*}
 
@@
 
-\subsection{Selection of FERENGI Input Galaxies}
+\subsection{Selection of FERENGI input galaxies}
 
@@
 
-\subsection{Morphological measurements in GZH beyond Task 1}
+\subsection{Morphological measurements in GZH beyond Task 1 - effects of debiasing?}
 
@@
 
+\subsection{Fake AGN}
+
 \section{Catalog}
+
+To include: detailed description of each column in the machine-readable tables.
+
+Needs some test cases for extracting a given set of objects (eg, clump galaxies in a particular redshift range) and evaluation of the results. Possibly include suggested thresholds, \'a la GZ2.
+
+\section{Analysis}
+
+\subsection{Demographics of morphology}
+
+Summarize the broad trends that are seen regarding the fraction of galaxies with various morphologies, how that relates to color, size, etc.
+Briefly discuss results as compared with literature and theory.
+
+\subsection{Comparison to other catalogs}
+
+Compare GZH data to:
+
+\begin{itemize}
+    \item \citet[ZEST;][]{sca07} (COSMOS)
+    \item Tasca (COSMOS)
+    \item Cassata (COSMOS)
+    \item Zajmoski (COSMOS)
+    \item GEMS morphologies?
+    \item AEGIS morphologies?
+    \item GOODS N/S morphologies?
+    \item expert visual inspection?
+\end{itemize}
+
+\textit{Address trends seen in broad morphological classes, possible reasons for difference.
+Also should attempt to map between the GZH vote fractions and whatever classification systems are used in the above systems.}
 
@@
 Their contributions are individually acknowledged at \texttt{http://www.galaxyzoo.org/volunteers}.
-Galaxy Zoo 2 was developed with the help of a grant from The Leverhulme Trust.
 
-We thank ASIAA for hosting the ``Citizen Science in Astronomy'' workshop, Mar 3-7 2014 in Taipei, Taiwan, at which some of this analysis was done.
+We thank Meg Schwamb and the ASIAA for hosting the ``Citizen Science in Astronomy'' workshop, 3-7 Mar 2014 in Taipei, Taiwan, at which some of this analysis was done.
 
-This project made heavy use of the Astropy packages in Python \citep{ast13}, as well as the seaborn plotting package \citep{was15}.
+This project made heavy use of the Astropy packages in Python \citep{ast13}, as well as the \texttt{seaborn} plotting package \citep{was15}.
 

### 2016-01-28 writeup/gz_hubble_data.tex
updated figures and table for writeup

--- 2016-01-15 writeup/gz_hubble_data.tex
@@
 \caption{Breakdown of what we can correct out of the Hubble data, by sample. \label{hubble_debiasable}}
-\begin{tabular}{lrrrrrrr}
+\begin{tabular}{lrrrrrrrr}
 \hline\hline
-                                   & AEGIS   & COSMOS & GEMS & GOODS-N & GOODS-S & SDSS    & Total \\
+                                   & AEGIS   & COSMOS & GEMS & GOODS-N & GOODS-S & GOODS FULL   & SDSS    & Total \\
 \hline
-Correctable                        & 2,325   & 20,669 & 2,748 & 1,074  & 1,022   & 0       & 27,838\\
-Uncorrectable                      & 1,403   & 19,626 & 1,832 & 271    & 980     & 0       & 24,112\\
-No Correction Needed ($z \le 0.3$) & 967     & 11,693 & 1,190 & 280    & 247     & 37,545  & 51,922\\ 
-NEI                                & 2,465   & 33,727 & 1,886 & 691    & 2,023   & 0       & 40,792\\
-No Redshift Information            & 1,347   & 7,093  & 1,648 & 235    & 641     & 14,316  & 25,280\\
-Total                              & 8,507   & 92,808 & 9,304 & 2,551  & 4,913   & 51,861  & 169,944\\
+Correctable                        & 1,628   & 15,120 & 1,811 & 739    & 502     & 1,850	& 0       & 21,650\\
+Uncorrectable                      & 1,869   & 26,184 & 2,407 & 524    & 1,115   & 2,670	& 0       & 34,769\\
+No Correction Needed ($z \le 0.3$) & 944     & 11,781 & 1,193 & 258    & 258     & 1,083	& 37,545  & 53,062\\ 
+NEI                                & 2,753   & 34,432 & 2,271 & 861    & 2,547   & 4,766	& 0       & 47,630\\
+No Redshift Information            & 1,313   & 5,291  & 1,622 & 169    & 491     & 788		& 14,316  & 23,990\\
+Total                              & 8,507   & 92,808 & 9,304 & 2,551  & 4,913   & 11,157	& 51,861  & 181,101\\
 \hline\hline

### 2016-01-29 writeup/gz_hubble_data.tex
updated writeup with new debiasing info

@@
 \caption{All fits for the vote fraction dropoff parameter $\zeta$ for $f_\textrm{features}$ in the \ferengi{} galaxies as a function of surface brightness.
-This includes only the 51~galaxies with a reasonably bounded range on the dropoff ($-10<\log(\zeta)<10$) and sufficient points to fit the function.}
+This includes only the 37~galaxies with a reasonably bounded range on the dropoff ($-10<\log(\zeta)<10$) and sufficient points to fit the function.}
 \label{fig:zeta_mu}
@@
 \includegraphics[width=\textwidth]{figures/p_vs_p_SB_redshift.pdf}
-\caption{Effects of redshift bias in 3,959 images in the \ferengi{} sample.
+\caption{Effects of redshift bias in 3,950 images in the \ferengi{} sample.
 Each point in a given redshift and surface brightness bin represents a unique galaxy.
@@
 On the x-axis is the $p_{features}$ value of the image of the same galaxy redshifted to $z=0.3$.
-Regions in which there is a nearly one-to-one relationship between $p_{features}$ at high redshift and $z=0.3$ are white; those in which there is not are green, and those with not enough data ($N<5$) are purple.
+The dashed black lines represent the best-fit polynomials to the data in each square.
+The solid black line represents $p_{\rm features,z}$ = $p_{\rm features,z=0.3}$.
+Regions in which there is a single-valued relationship between $p_{features}$ at high redshift and $z=0.3$ are white; those in which there is not are blue, and those with not enough data ($N<5$) are gray.
 }
@@
 
-Our criteria for determining whether a region of this space is single-valued, and therefore correctable, is as follows: For each surface brightness and redshift bin, we examine the distribution of $p_{\rm features,z=0.3}$ in four bins of $p_{\rm features,z}$.
-These sub-bins are marked by the horizontal lines within each larger, surface brightness/redshift bin in Figure~\ref{fig:p_vs_p}.
-First, we compute the interquartile range (IQR) of the distribution of $p_{\rm features,z=0.3}$ in each sub-bin, which are indicated by the orange bars.
-For the region to be considered correctable, we require that the IQR of the distribution within these sub-bins is less than the sub-bin height.
-Regions which fit these criteria are uncouloured in the plot.
-If the IQR is greater than the bin height, the region is considered uncorrectable; these are marked in green.
-Any region with fewer than 5 points is considered to have ``not enough information (NEI)'', and are shown in purple.
-
-Using this approach, 52\% of the \ferengi{} images were found to have single-valued relationships between their $p_{\rm features}$ values at high and low redshift (see Table \ref{ferengi_corrections} for a summary.) Only these images were used in determining the $\zeta$ function (Section \ref{sec:zeta}).
+Our criteria for determining whether a region of this space is single-valued, and therefore correctable, is as follows: In each surface brightness and redshift bin, we model the relationship between $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$ by fitting the data with a polynomials of degrees 3, 2, and 1, and use the best fit out of the three.
+These fits are shown as the dashed black lines in figure ~\ref{fig:p_vs_p}.
+Any flat regions of the polynomial fits are areas in which there is not a clear single-valued relationship between $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$; we quantify this by setting a minimum slope cut of 0.4.
+Any data in which the polynomial fit has a slope less than this value is considered \emph{not} one-to-one, and therefore ``uncorrectable.'' These regions are highlighted in blue in figure ~\ref{fig:p_vs_p}.
+Uncolored (white) regions of the plot have sufficiently high slopes for us to consider the relationship to be single-valued; galaxies in these regions are considered ``correctable'', and only these are used in measuring the parameters for the $\zeta$ function (Section \ref{sec:zeta}).
+Only surface brightness/redshift bins with at least 5 galaxies were considered; regions with fewer than 5 galaxies we consider to have 'not enough information' to determine the  $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$ relationship, these are colored gray in figure ~\ref{fig:p_vs_p}.
 
@@
 \label{ferengi_corrections}}
-\begin{tabular}{lcc}
+\begin{tabular}{lrr}
 \hline \hline
@@
 \hline 
-Correctable                        & 2,057   & 52\% \\
-Uncorrectable                      & 1,732   & 44\% \\
-NEI                                & 170     &  4\%\\
-Total                              & 3,959   & 100\% \\
+Correctable                        & 1,884   & 48\% \\
+Uncorrectable                      & 1,986   & 50\% \\
+NEI                                & 80     &  2\%\\
+Total                              & 3,950   & 100\% \\
 \hline \hline

### 2016-01-29 writeup/gz_hubble_data.tex

--- 2016-01-22 writeup/gz_hubble_data.tex
@@
 \begin{table*}
-\caption{Breakdown of what we can correct out of the GZH data, by sample. \label{hubble_debiasable}}
-\begin{tabular}{lrrrrrrr}
+\caption{Breakdown of what we can correct out of the Hubble data, by sample. \label{hubble_debiasable}}
+\begin{tabular}{lrrrrrrrr}
 \hline\hline
-                                   & AEGIS   & COSMOS & GEMS & GOODS-N & GOODS-S & SDSS    & Total \\
+                                   & AEGIS   & COSMOS & GEMS & GOODS-N & GOODS-S & GOODS FULL   & SDSS    & Total \\
 \hline
-Correctable                        & 2,325   & 20,669 & 2,748 & 1,074  & 1,022   & 0       & 27,838\\
-Uncorrectable                      & 1,403   & 19,626 & 1,832 & 271    & 980     & 0       & 24,112\\
-No Correction Needed ($z \le 0.3$) & 967     & 11,693 & 1,190 & 280    & 247     & 37,545  & 51,922\\ 
-NEI                                & 2,465   & 33,727 & 1,886 & 691    & 2,023   & 0       & 40,792\\
-No Redshift Information            & 1,347   & 7,093  & 1,648 & 235    & 641     & 14,316  & 25,280\\
-Total                              & 8,507   & 92,808 & 9,304 & 2,551  & 4,913   & 51,861  & 169,944\\
+Correctable                        & 1,628   & 15,120 & 1,811 & 739    & 502     & 1,850	& 0       & 21,650\\
+Uncorrectable                      & 1,869   & 26,184 & 2,407 & 524    & 1,115   & 2,670	& 0       & 34,769\\
+No Correction Needed ($z \le 0.3$) & 944     & 11,781 & 1,193 & 258    & 258     & 1,083	& 37,545  & 53,062\\ 
+NEI                                & 2,753   & 34,432 & 2,271 & 861    & 2,547   & 4,766	& 0       & 47,630\\
+No Redshift Information            & 1,313   & 5,291  & 1,622 & 169    & 491     & 788		& 14,316  & 23,990\\
+Total                              & 8,507   & 92,808 & 9,304 & 2,551  & 4,913   & 11,157	& 51,861  & 181,101\\
 \hline\hline

### 2016-02-09 writeup/gz_hubble_data.tex
added images to goods analysis
updated some goods analysis

@@
 \newcommand{\pbar}{p_{\rm bar}}
+\newcommand{\pfeatures}{p_{\rm features}}
 \newcommand{\fHI}{f_{\rm HI}}
@@
 
-\begin{table}
+The unshaded regions in figure ~\ref{fig:p_vs_p} define discrete ranges of redshift, surface brightness, and $\pfeatures$ a galaxy must have in order for the $\zeta$ approach to be confidentely applied to a galaxy in the GZH sample.
+While the appropriate correctable regions were defined discretely, we assume the true correctable region is a smooth function of z, $\mu$, and $\pfeatures$.
+To define this smooth space, we use a convex hull method to enclose the correctable and uncorrectable \ferengi{} galaxies is z-$\mu$-$\pfeatures$ space.
+Due to scatter, the boundaries of the resulting hulls overlap.
+The boundaries are then adjusted until the contamination from both groups is minimized.
+We use the resulting hulls to define the correctable and uncorrectable regions for categorizing the Hubble galaxies.
+The results of this method and final categorization of the Hubble sample is displayed in Table~\ref{hubble_debiasable}.
+We find that of the galaxies at redshift higher than $z=z_{0}=0.3$, 17\% of these are able to be debiased using the $\zeta$ method, 27\% cannot be debiased, and 56\% cannot be determined, due to a lack of redshift or information or due to a lack of \ferengi{} data corresponding to those galaxies redshift/surface brightness values.
+
+now talk about how we get low/high limits on pfeatures
+
+\begin{table}ー
 \caption{Distribution of \ferengi{} images analysed in Figure~\ref{fig:p_vs_p}.
@@
 \begin{table*}
-\caption{Breakdown of what we can correct out of the Hubble data, by sample. \label{hubble_debiasable}}
+\caption{Breakdown of what we can correct out of the GZH data, by sample. 
+\label{hubble_debiasable}}
 \begin{tabular}{lrrrrrrrr}

### 2016-02-10 writeup/gz_hubble_data.tex
added redshift info in writeup

@@
 FERENGI images.
+
+\subsection{Redshifts}
+
+We obtain redshifts from a variety of sources: spectroscopic and photometric redshifts from \citet{gri12}, spectroscopic, photometric, and grism redshifts from 3DHST \citep{mom15}, and photometric redshifts from UltraVISTA \citep{ilb13}.
+The distribution is shown in Table~\ref{redshifts}, and are located in the `$\rm Z~BEST$' column of the catalog.
+We first use the \citep{gri12} and \citep{mom15} redshifts if those are available.
+If they are not, then we compare the 1$\sigma$ errors of the photometric and grism redshits from all three catalogs, and use the redshift with the smallest error.
+The source of the redshifts are displayed in the $\rm Z~BEST~SOURCE$ column of the catalog.
+
+\begin{table*}
+\caption{Redshift sources of the Hubble data, by sample.  \label{redshifts}}
+\begin{tabular}{lrrrrrrrr}
+\hline\hline
+                                  & AEGIS   & COSMOS & GEMS & GOODS-N & GOODS-S & GOODS FULL    & SDSS    & Total \\
+\hline
+Griffith specz                  & 3,656    & 7,201  & 387   & 1,997  & 3,016   &           	&         & 16,257\\
+3DHST specz                      & 12       & 35     & 6     & 5      & 103     &               &         & 161\\
+Griffith photoz                 & 4,442    & 82,662 & 8,886 & 218    & 1,662   &               &         & 97,870\\ 
+3DHST grismz                     & 341      & 358    & 9     & 101    & 67      &               &         & 876\\
+UltraVista photoz                & 0        & 2,473  & 0     & 0      & 0       &           	&         & 2,473\\
+3DHST photoz                     & 56       & 79     & 16    & 230    & 65      &           	&         & 446\\
+
+Total                            & 8,507    & 92,808 & 9,304 & 2,551  & 4,913   & 11,157    	& 51,861  & 181,101\\
+\hline\hline
+\end{tabular}
+\end{table*}
 
@@
 \begin{table*}
-\caption{Breakdown of what we can correct out of the GZH data, by sample. 
-\label{hubble_debiasable}}
+\caption{Breakdown of what we can correct out of the GZH data, by sample.  \label{hubble_debiasable}}
 \begin{tabular}{lrrrrrrrr}
@@
 \subsection{Morphological measurements in GZH beyond Task 1 - effects of debiasing?}
-
+blah blah cite \citet{ilb13} \citep{ilb13} \citet{mom15} \citep{mom15}
 \subsection{Duplicate images}

### 2016-02-18 writeup/gz_hubble_data.tex
added debiasing figures and catalog section to writeup

@@
 \usepackage{natbib}
+\usepackage{graphicx}
+\usepackage{subfigure}
+\usepackage{deluxetable}
 \bibliographystyle{mn2e}
@@
 \section{Sample and Data} 
+\label{sec:data}
 
@@
 \subsection{User weighting}
-
+\label{sec:weighting}
 The votes of individual users who classified galaxies in GZH are combined to make a vote fraction for each question on the classification tree.
@@
 \section{Correcting for redshift-dependent classification bias}
-
+\label{sec:debiasing}
 The previous versions of Galaxy Zoo morphology classifications \citep{lin08,wil13} were based on observations of galaxies in the Sloan Digital Sky Survey (SDSS) which are typically at $z<0.1$.
@@
 
-\begin{figure*}
+\begin{figure}
 \begin{center}
-\includegraphics[width=\textwidth]{figures/eye_of_sauron.pdf}
+\includegraphics[width=0.5\textwidth]{figures/eye_of_sauron.pdf}
 \caption{Surface brightness vs.
@@
 \end{center}
-\end{figure*}
+\end{figure}
 
 \begin{figure*}
-\begin{center}
-\includegraphics[width=\textwidth]{figures/p_vs_p_SB_redshift.pdf}
+\centering
+\subfigure{[6a]\label{fig:6a}\includegraphics[width=0.5\textwidth]{figures/p_vs_p_SB_redshift.pdf}}
+\subfigure{[6b]\label{fig:6b}\includegraphics[width=0.4\textwidth]{figures/z1_mu20_subplot1.pdf}}
+\\
+\subfigure{[6c]\label{fig:6c}\includegraphics[width=0.5\textwidth]{figures/orangebars.pdf}}
+\subfigure{[6d]\label{fig:6d}\includegraphics[width=0.4\textwidth]{figures/z1_mu20_subplot2.pdf}}
 \caption{Effects of redshift bias in 3,950 images in the \ferengi{} sample.
-Each point in a given redshift and surface brightness bin represents a unique galaxy.
-On the y-axis in each bin is the $p_{features}$ value of the image of that galaxy redshifted to the value corresponding to that redshift bin.
-On the x-axis is the $p_{features}$ value of the image of the same galaxy redshifted to $z=0.3$.
+[6a]: Each point in a given redshift and surface brightness bin represents a unique galaxy.
+On the y-axis in each bin is the $p_{\rm features}$ value of the image of that galaxy redshifted to the value corresponding to that redshift bin.
+On the x-axis is the $p_{\rm features}$ value of the image of the same galaxy redshifted to $z=0.3$.
 The dashed black lines represent the best-fit polynomials to the data in each square.
 The solid black line represents $p_{\rm features,z}$ = $p_{\rm features,z=0.3}$.
-Regions in which there is a single-valued relationship between $p_{features}$ at high redshift and $z=0.3$ are white; those in which there is not are blue, and those with not enough data ($N<5$) are gray.
-}
+Regions in which there is a single-valued relationship between $p_{\rm features}$ at high redshift and at $z=0.3$ are white; those in which there is not are blue, and those with not enough data ($N<5$) are gray.
+[6b]: A larger version of the dark-outlined square in [6a], containing \ferengi{} galaxies that have been artificially redshifted to $z=1.0$ and have surface brightnesses between $20.3 < \mu < 21.0$ $\rm (mag/arcsec^2)$.
+[6c]: The same data as [6a] is shown.
+Each $z,\mu$ bin is divided into 4 sub-bins to determine the range of intrinsic $p_{\rm features,z=0.3}$ for a given range of observed $p_{\rm features,z}$ values.
+In each sub-bin, the orange bars represent the inner 80th percentiles of the data, the boundaries of which are the lower and upper limits of the debiased values.
+[6d]: The same data as [6b], but highlighting the upper and lower limit regions.}
 \label{fig:p_vs_p}
-\end{center}
 \end{figure*}
@@
 In Figure~\ref{fig:p_vs_p} we examine the change in $p_{\rm features}$ for the \ferengi{} galaxies relative to their lowest simulated redshift.
-In this analysis, only galaxies whose lowest simulated redshift image was ($\rm z_{sim}=0.3$) were used (see Table \ref{ferengivalues}), and only those which had detectable surface brightness measurements in \sextractor{}; this includes 3,959 of the total 6,466 images.
+In this analysis, only galaxies whose lowest simulated redshift image was ($\rm z_{sim}=0.3$) were used (see Table \ref{ferengivalues}), and only those which had detectable surface brightness measurements in \sextractor{}; this includes 3,950 of the total 6,466 images.
 For each simulated redshift value $z$, and at a fixed surface brightness $\mu$, we plot $p_{\rm features,z}$, the value measured at that simulated redshift, vs $p_{\rm features,z=0.3}$, the value measured for the same galaxy imaged at $z=0.3$.
@@
 Our criteria for determining whether a region of this space is single-valued, and therefore correctable, is as follows: In each surface brightness and redshift bin, we model the relationship between $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$ by fitting the data with a polynomials of degrees 3, 2, and 1, and use the best fit out of the three.
-These fits are shown as the dashed black lines in figure ~\ref{fig:p_vs_p}.
+These fits are shown as the dashed black lines in Figure~\ref{fig:6a}.
 Any flat regions of the polynomial fits are areas in which there is not a clear single-valued relationship between $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$; we quantify this by setting a minimum slope cut of 0.4.
-Any data in which the polynomial fit has a slope less than this value is considered \emph{not} one-to-one, and therefore ``uncorrectable.'' These regions are highlighted in blue in figure ~\ref{fig:p_vs_p}.
+Any data in which the polynomial fit has a slope less than this value is considered \emph{not} one-to-one, and therefore ``uncorrectable.'' These regions are highlighted in blue in figure ~\ref{fig:6a}.
 Uncolored (white) regions of the plot have sufficiently high slopes for us to consider the relationship to be single-valued; galaxies in these regions are considered ``correctable'', and only these are used in measuring the parameters for the $\zeta$ function (Section \ref{sec:zeta}).
-Only surface brightness/redshift bins with at least 5 galaxies were considered; regions with fewer than 5 galaxies we consider to have 'not enough information' to determine the  $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$ relationship, these are colored gray in figure ~\ref{fig:p_vs_p}.
+Only surface brightness/redshift bins with at least 5 galaxies were considered; regions with fewer than 5 galaxies we consider to have ``not enough information'' to determine the  $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$ relationship, these are colored gray in Figure~\ref{fig:6a}.
 
-The unshaded regions in figure ~\ref{fig:p_vs_p} define discrete ranges of redshift, surface brightness, and $\pfeatures$ a galaxy must have in order for the $\zeta$ approach to be confidentely applied to a galaxy in the GZH sample.
+The unshaded regions in Figure~\ref{fig:6a} define discrete ranges of redshift, surface brightness, and $\pfeatures$ a galaxy must have in order for the $\zeta$ approach to be confidentely applied to a galaxy in the GZH sample.
 While the appropriate correctable regions were defined discretely, we assume the true correctable region is a smooth function of z, $\mu$, and $\pfeatures$.
@@
 The results of this method and final categorization of the Hubble sample is displayed in Table~\ref{hubble_debiasable}.
-We find that of the galaxies at redshift higher than $z=z_{0}=0.3$, 17\% of these are able to be debiased using the $\zeta$ method, 27\% cannot be debiased, and 56\% cannot be determined, due to a lack of redshift or information or due to a lack of \ferengi{} data corresponding to those galaxies redshift/surface brightness values.
+We find that of the galaxies at redshift higher than $z=z_{0}=0.3$, 17\% of these are able to be debiased using the $\zeta$ method, 27\% cannot be debiased, and 56\% cannot be determined, due to a lack of redshift or information or due to a lack of \ferengi{} data corresponding to those galaxies' redshift/surface brightness values.
 
-now talk about how we get low/high limits on pfeatures
+For the ``uncorrectable'' galaxies, those for which we cannot confidentely assign a single debiased $p_{\rm features}$ value, we instead determine a likely \emph{range} of debiased values, using a method visualized in Figure~\ref{fig:6c}.
+Here we again use the \ferengi{} simulated data to analyze the range of intrinsic $p_{\rm features,z=0.3}$ values for any given observed $p_{\rm features}$ value, again as a function of surface brightness and redshift.
+In each z,$\mu$ bin, we examine the spread of intrinsic values of $p_{\rm features,z=0.3}$ for 4 ranges of observed $p_{\rm features}$.
+We quantify the range of intrinsic values as the inner 80\% of the data; this range is represented by the orange bars in Figure~\ref{fig:6c}.
+For any galaxy which can't be directly debiased by the $\zeta$ method, then, we use these ranges to denote the upper and lower limits on what we expect $p_{features,z=0.3}$ to be for any observed value of $p_{\rm features}$.
 
@@
 Correctable images had a single-valued relationship between their measured $p_{\rm features}$ values at high and low redshifts (white regions in Figure~\ref{fig:p_vs_p}).
-Uncorrectable images had a non single-valued relationship (green regions).
-NEI images had undetermined relationships due to a lack of data ($N<5$) in their corresponding sub-bins (purple regions).
+Uncorrectable images had a non single-valued relationship (blue regions).
+NEI images had undetermined relationships due to a lack of data ($N<5$) in their corresponding z-$\mu$ bins (gray regions).
 \label{ferengi_corrections}}
@@
 \subsection{Morphological measurements in GZH beyond Task 1 - effects of debiasing?}
-blah blah cite \citet{ilb13} \citep{ilb13} \citet{mom15} \citep{mom15}
 \subsection{Duplicate images}
@@
 
-\section{Catalog}
+\section{The Catalog}
+
+The data release for GZH includes morphological data for 181,101 galaxies.
+The full table can be accessed at some website.
+We also include a secondary metadata table, which contains data from a variety of sources explained in Section \ref{sec:data}.
+
+For each galaxy we list its unique objid, as well as the source's RA, DEC, and survey (AEGIS, COSMOS, GEMS, GOODS North (full and shallow depth), GOODS South (full and shallow depth), SDSS.
+For each of the 40 (?) questions in the GZH decision tree, the following classification data is provided: For each question, $\tt N_{votes}$ is the number of users to answer that question.
+For each unique answer, $\tt fraction$ is the fraction of users to select that answer ($\rm N_{answer}/N_{votes}$, and $\tt weighted$ is the weighted fraction, which takes into account user consistency (Section~\ref{sec:weighting}).
+
+The GZH vote fractions can be largely dependent on the resolution of the image.
+Two otherwise morphologically identical galaxies which differ significantly in redshift, brightness, or size may result in very different vote fractions for any given question, given that many features of a galaxy are difficult to discern in less-resolved images (bars, spiral arms, disk structure, etc).
+For this reason, it is necessary to take caution utilizing vote fractions as cut-offs to determine morphological structure; we offer guidelines for careful classification in Section~\ref{sec:cookbook}.
+
+We corrected for the biases described for the first question of the GZH decision tree, which asks ``Is the galaxy smooth and round, with no sign of a disk?'' The method is described in Section~\ref{sec:debiasing}.
+For this question, we provide the additional parameters $\tt debiased$, $\tt lower~limit$, $\tt upper~limit$, and $\tt best$ vote fractions.
+The $\tt best$ fraction for $p_{features}$is chosen based on the categorization of the galaxy: if it is ``correctable'', $\tt best = debiased$, if ``uncorrectable'', $\tt best = lower~limit$, and if neither, $\tt best = weighted$.
+The debiased vote fractions for $\tt p_{smooth}$ were calculated on the critera that vote fractions for all answers must sum to unity.
+Explicitely: $\tt p_{smooth} = 1 - p_{features} - p_{artifact}$.
+
+\tabletypesize{\scriptsize}
+\begin{deluxetable}{lrrllcrrrrrr|c}
+\rotate
+\tablecolumns{12}
+\tablewidth{0pc}
+\tablecaption{GZH morphological classifications} 
+\label{tab:catalog}
+\tabletypesize{\scriptsize}
+\tablehead{
+ &  &   &  &  
+\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
+\multicolumn{6}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
+\colhead{$\dots$}
+\\
+\colhead{OBJNO} & 
+\colhead{RA} & 
+\colhead{DEC} & 
+\colhead{Imaging} & 
+\colhead{Correctable Category} & 
+\colhead{$N_\mathrm{votes}$} & 
+\colhead{fraction} & 
+\colhead{weighted} & 
+\colhead{debiased} & 
+\colhead{lower~limit} & 
+\colhead{upper~limit} &
+\colhead{best} &
+\colhead{}
+}
+\small
+\startdata
+10000034            & 188.93       & 62.23         & AEGIS           &  correctable &  72 &  10 &  10.0 & 0.625 & 0.625 & 0.629 & 0 \\
+10000162            & 160.99      & 11.70          & AEGIS           &  uncorrectable &  84 &  17 &  17.0 & 0.810 & 0.810 & 0.810 & 1 \\
+5001356             & 210.80       & 54.15         & GOODS-N-Shallow &  correctable &  88 &  18 &  18.0 & 0.783 & 0.783 & 0.722 & 0 \\
+9003947835          & 176.54       & 8.74          & GOODS-S-Shallow &  nei &  48 &  16 &  16.0 & 1.000 & 1.000 & 1.000 & 1 \\
+GDS~S~16203         & 186.44       & 47.88         & GOODS-FULL      &  nei &  89 &  17 &  17.0 & 0.739 & 0.739 & 0.739 & 0 \\
+8647474690312438284 & 188.93       & 62.64         & SDSS            &  zlt3 &  91 &   0 &   0.0 & 0.000 & 0.000 & 0.000 & 0 \\
+20061690            & 160.99       & 11.70         & COSMOS          &  nei &  65 &   4 &   3.4 & 0.333 & 0.295 & 0.295 & 0 \\
+20061692            & 176.54       & 8.45          & COSMOS          &  correctable &  75 &  14 &  14.0 & 0.609 & 0.629 & 0.666 & 0 \\
+90022947            & 230.24       & 84.20         & GEMS           &  zlt3 & 129 &  12 &  12.0 & 0.462 & 0.462 & 0.492 & 0 \\
+20063829            & 203.23       & 93.20         & COSMOS         &  correctable &  69 &  18 &  17.0 & 0.900 & 0.895 & 0.840 & 1 \\
+\enddata
+\tablecomments{Full version is online at some website, here are 10 rows out of 181,101 in the full version.\emph{These numbers are super fake right now - put real values in for final version!}}
+\end{deluxetable}
 
@@
 Needs some test cases for extracting a given set of objects (eg, clump galaxies in a particular redshift range) and evaluation of the results. Possibly include suggested thresholds, \'a la GZ2. 
-
+\section{Using the Catalog}
+\label{sec:cookbook}
+Include cookbook for selecting morphologies. 
 \section{Analysis}

### 2016-02-20 writeup/gz_hubble_data.tex
New figure and code for filter curves

--- 2016-02-09 writeup/gz_hubble_data.tex
@@
 
-We use different filters for the north and south GOODS fields so that GEMS can be directly compared with GOODS-S.
+We use different filters for the north and south GOODS fields so that GEMS can be directly compared with GOODS-S (Figure~\ref{fig:filtercurves}).
+
+\begin{figure*}
+\includegraphics[width=160mm]{figures/filter_curves.pdf}
+\caption{Transmission curves of the filters used by \textit{HST} Advanced Camera for Surveys (ACS) in wide-field channel mode for the various surveys in Galaxy Zoo: Hubble.
+The unfilled black curves show the filters for the Suprime Camera on the \textit{Subaru} telescope which were used to create color gradients in the composite images for COSMOS.\label{fig:filtercurves}}
+\end{figure*}
 
@@
 
-This project made heavy use of the Astropy packages in Python \citep{ast13}, as well as the \texttt{seaborn} plotting package \citep{was15}.
+This project made heavy use of the Astropy packages in Python \citep{ast13}, the \texttt{seaborn} plotting package \citep{was15}, and astroML \citep{van12}.
 

### 2016-03-01 writeup/gz_hubble_data.tex
added paragraph about redshifts to writeup and added figure comparing speczs from Griffith 3dhst and MUSYC catalogs

@@
 
-We obtain redshifts from a variety of sources: spectroscopic and photometric redshifts from \citet{gri12}, spectroscopic, photometric, and grism redshifts from 3DHST \citep{mom15}, and photometric redshifts from UltraVISTA \citep{ilb13}.
-The distribution is shown in Table~\ref{redshifts}, and are located in the `$\rm Z~BEST$' column of the catalog.
-We first use the \citep{gri12} and \citep{mom15} redshifts if those are available.
-If they are not, then we compare the 1$\sigma$ errors of the photometric and grism redshits from all three catalogs, and use the redshift with the smallest error.
-The source of the redshifts are displayed in the $\rm Z~BEST~SOURCE$ column of the catalog.
+We compiled redshifts from a variety of sources to include in the GZH catalog.
+For each galaxy, the redshift selected is in the $\tt Z\_Best$ column of the data (see Table~\ref{tab:catalog}), its type (spectroscopic: $\tt SPEC\_Z$, photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column $\tt Z\_BEST\_TYPE$, and the source catalog ($\tt Griffith$ \citep{gri12}, $\tt 3DHST$ \citep{mom15}, $\tt MUSYC$ \citep{car10}, or $\tt UltraVISTA$ \citep{ilb13}) of the redshift is in column $\tt Z\_BEST\_SOURCE$.
 
-\begin{table*}
-\caption{Redshift sources of the Hubble data, by sample.  \label{redshifts}}
-\begin{tabular}{lrrrrrrrr}
-\hline\hline
-                                  & AEGIS   & COSMOS & GEMS & GOODS-N & GOODS-S & GOODS FULL    & SDSS    & Total \\
+For galaxies which have redshifts from multiple sources, we use the following algorithm to select the $\tt Z\_BEST$ redshift.
+We first prioritize spectroscopic redshifts; these are provided in the Griffith, 3DHST, and MUSYC catalogs.
+If a high quality spec-z exists in the Griffith catalog we use that, else 3DHST, else MUSYC.
+We show in Figure~\ref{fig:speczs} that over 98\% of the the spec-z's are consistent with each other, and therefore the priority order of selection makes no negligible difference.
+If no spectroscipic redshifts are available, we compare the 1-$\sigma$ errors of the photometric (Griffith, 3DHST, MUSYC, UltraVISTA) and grism (UltraVISTA) redshifts, and use the redshift with the smallest error.
+Table~\ref{tab:redshifts} shows the results of this selection.
+
+\begin{figure*}
+\includegraphics[width=160mm]{figures/specz_comparison.pdf}
+\caption{Spectroscopic redshifts from Griffith, 3DHST, and MUSYC catalogs.
+The number in the upper left of each plot is the percentage of redshifts which agree within $\Delta z < 0.05$ between the two catalogs being compared in each panel.
+Within this range there is over 98\% agreement in redshifts between all three catalogs.}
+\label{fig:speczs}
+\end{figure*}
+
+\tabletypesize{\scriptsize}
+\begin{deluxetable}{l|rr|rrr|rr|r|rr}
+\centering
+%\rotate
+\tablecolumns{12}
+\tablewidth{0pc}
+\tablecaption{GZH redshifts by survey} 
+\label{tab:redshifts}
+\tabletypesize{\scriptsize}
+\tablehead{
+ &   
+\multicolumn{2}{c}{\underline{Griffith}} &
+\multicolumn{3}{c}{\underline{3DHST}} &
+\multicolumn{2}{c}{\underline{MUSYC}} &
+\multicolumn{1}{c}{\underline{UltraVISTA}}&
+\multicolumn{2}{c}{\underline{Total}} 
+\\
+\colhead{Survey} & 
+\colhead{spec-z} & 
+\colhead{photo-z} & 
+\colhead{spec-z} & 
+\colhead{grism-z} & 
+\colhead{photo-z} & 
+\colhead{spec-z} & 
+\colhead{photo-z} & 
+\colhead{photo-z} & 
+\colhead{with redshift} &
+\colhead{in survey}
+}
+\small
+\startdata
+%Survey     Gs        Gp    3ds    3dg     3dp       Ms      Mp       UVp       total
+AEGIS    & 3,656  & 2,941  & 12  &  515  &  249    & 0     & 0     &  0      & 7,373  & 8,507\\
+COSMOS   & 7,201  & 77,435 & 35  &  358  &  26     & 0     & 0     &  2,665  & 85,020 & 92,808 \\
+GEMS     & 387    & 628    & 6   &  99   &  40     & 279   & 7,304 & 0       & 8,743  & 9,304\\
+GOODS-N  & 1,947  & 37     & 418 & 1,545 &  1,381  & 0     & 0     & 0       & 5,328  & 12,030 \\
+GOODS-S  & 1,080  & 4      & 327 & 1,348 &  281    & 816   & 1,184 & 0       & 5,040  & 10,284 \\
+SDSS     & 0      & 0      & 0   &  0    &  0      & 0     & 0     & 0       & 37,545 & 51,861  \\
 \hline
-Griffith specz                  & 3,656    & 7,201  & 387   & 1,997  & 3,016   &           	&         & 16,257\\
-3DHST specz                      & 12       & 35     & 6     & 5      & 103     &               &         & 161\\
-Griffith photoz                 & 4,442    & 82,662 & 8,886 & 218    & 1,662   &               &         & 97,870\\ 
-3DHST grismz                     & 341      & 358    & 9     & 101    & 67      &               &         & 876\\
-UltraVista photoz                & 0        & 2,473  & 0     & 0      & 0       &           	&         & 2,473\\
-3DHST photoz                     & 56       & 79     & 16    & 230    & 65      &           	&         & 446\\
-
-Total                            & 8,507    & 92,808 & 9,304 & 2,551  & 4,913   & 11,157    	& 51,861  & 181,101\\
-\hline\hline
-\end{tabular}
-\end{table*}
+Total    & 14,271 & 81,045 & 798 & 3,865 & 1,977   & 1,095 & 8,488 & 2,665   & 114,204 & 184,794\\
+\enddata
+\end{deluxetable}
 
@@
 \begin{deluxetable}{lrrllcrrrrrr|c}
-\rotate
+\centering
+%\rotate
 \tablecolumns{12}

### 2016-03-08 writeup/gz_hubble_data.tex
updated hubble catalog with complete set of redshifts

@@
 \begin{table*}
-\caption{Breakdown of what we can correct out of the GZH data, by sample.  \label{hubble_debiasable}}
+\caption{Breakdown of what we can correct out of the GZH data, by sample.
+\emph{updated from 3-8-16: Switching to full depth for all GOODS data.
+Shallow depth information in appendix.}\label{hubble_debiasable}}
 \begin{tabular}{lrrrrrrrr}
 \hline\hline
-                                  & AEGIS   & COSMOS & GEMS & GOODS-N & GOODS-S & GOODS FULL   & SDSS    & Total \\
+                                  & AEGIS   & COSMOS & GEMS & GOODS-N & GOODS-S         & SDSS    & Total \\
 \hline
-Correctable                        & 1,628   & 15,120 & 1,811 & 739    & 502     & 1,850	& 0       & 21,650\\
-Uncorrectable                      & 1,869   & 26,184 & 2,407 & 524    & 1,115   & 2,670	& 0       & 34,769\\
-No Correction Needed ($z \le 0.3$) & 944     & 11,781 & 1,193 & 258    & 258     & 1,083	& 37,545  & 53,062\\ 
-NEI                                & 2,753   & 34,432 & 2,271 & 861    & 2,547   & 4,766	& 0       & 47,630\\
-No Redshift Information            & 1,313   & 5,291  & 1,622 & 169    & 491     & 788		& 14,316  & 23,990\\
-Total                              & 8,507   & 92,808 & 9,304 & 2,551  & 4,913   & 11,157	& 51,861  & 181,101\\
+Correctable                        & 1,654   & 15,170 & 1,837 & 993    & 835     	& 0       & 20,489\\
+Uncorrectable                      & 1,917   & 26,113 & 2,423 & 1,385  & 1,282   	& 0       & 33,120\\
+No Correction Needed ($z \le 0.3$) & 955     & 11,926 & 1,175 & 415    & 400     	& 37,545  & 52,416\\ 
+NEI                                & 2,847   & 34,511 & 3,308 & 2,535  & 2,523   	& 0       & 45,724\\
+No Redshift Information            & 1,134   & 5,088  & 561   & 687    & 102   		& 14,316  & 21,888\\
+Total                              & 8,507   & 92,808 & 9,304 & 6,015  & 5,142   	& 51,861  & 173,637\\
 \hline\hline
@@
 
+\newpage
+\clearpage
+\appendix
+\section{GOODS Shallow Depth data}
+
+GZH used both 5-epoch and 2-epoch sets of data to construct the GOODS set of images.
+The 11,157 full depth 5-epoch images are used in the main catalog; the classifications for the 7,464 shallow depth 2-epoch images are offered as a supplementary table.
+Here we briefly analyze the effect of image depth on the ability of the GZ users to identify features or disk structure in the images.
+
+4,461 galaxies have both full depth and shallow depth classifications. 
 \end{document}

### 2016-03-15 writeup/gz_hubble_data.tex
added to writeup appendices and debiasing higher order questions

@@
 
-\subsection{Redshifts}
-
-We compiled redshifts from a variety of sources to include in the GZH catalog.
-For each galaxy, the redshift selected is in the $\tt Z\_Best$ column of the data (see Table~\ref{tab:catalog}), its type (spectroscopic: $\tt SPEC\_Z$, photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column $\tt Z\_BEST\_TYPE$, and the source catalog ($\tt Griffith$ \citep{gri12}, $\tt 3DHST$ \citep{mom15}, $\tt MUSYC$ \citep{car10}, or $\tt UltraVISTA$ \citep{ilb13}) of the redshift is in column $\tt Z\_BEST\_SOURCE$.
-
-For galaxies which have redshifts from multiple sources, we use the following algorithm to select the $\tt Z\_BEST$ redshift.
-We first prioritize spectroscopic redshifts; these are provided in the Griffith, 3DHST, and MUSYC catalogs.
-If a high quality spec-z exists in the Griffith catalog we use that, else 3DHST, else MUSYC.
-We show in Figure~\ref{fig:speczs} that over 98\% of the the spec-z's are consistent with each other, and therefore the priority order of selection makes no negligible difference.
-If no spectroscipic redshifts are available, we compare the 1-$\sigma$ errors of the photometric (Griffith, 3DHST, MUSYC, UltraVISTA) and grism (UltraVISTA) redshifts, and use the redshift with the smallest error.
-Table~\ref{tab:redshifts} shows the results of this selection.
-
-\begin{figure*}
-\includegraphics[width=160mm]{figures/specz_comparison.pdf}
-\caption{Spectroscopic redshifts from Griffith, 3DHST, and MUSYC catalogs.
-The number in the upper left of each plot is the percentage of redshifts which agree within $\Delta z < 0.05$ between the two catalogs being compared in each panel.
-Within this range there is over 98\% agreement in redshifts between all three catalogs.}
-\label{fig:speczs}
-\end{figure*}
-
 \tabletypesize{\scriptsize}
 \begin{deluxetable}{l|rr|rrr|rr|r|rr}
+
 \centering
@@
 
+\subsection{Redshifts}
+
+We compiled redshifts from a variety of sources to include in the GZH catalog.
+For each galaxy, the redshift selected is in the $\tt Z\_Best$ column of the data (see Table~\ref{tab:catalog}), its type (spectroscopic: $\tt SPEC\_Z$, photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column $\tt Z\_BEST\_TYPE$, and the source catalog ($\tt Griffith$ \citep{gri12}, $\tt 3DHST$ \citep{mom15}, $\tt MUSYC$ \citep{car10}, or $\tt UltraVISTA$ \citep{ilb13}) of the redshift is in column $\tt Z\_BEST\_SOURCE$.
+
+For galaxies which have redshifts from multiple sources, we use the following algorithm to select the $\tt Z\_BEST$ redshift.
+We first prioritize spectroscopic redshifts; these are provided in the Griffith, 3DHST, and MUSYC catalogs.
+If a high quality spec-z exists in the Griffith catalog we use that, else 3DHST, else MUSYC.
+We show in Figure~\ref{fig:speczs} that over 98\% of the the spec-z's are consistent with each other, and therefore the priority order of selection makes no negligible difference.
+If no spectroscipic redshifts are available, we compare the 1-$\sigma$ errors of the photometric (Griffith, 3DHST, MUSYC, UltraVISTA) and grism (UltraVISTA) redshifts, and use the redshift with the smallest error.
+Table~\ref{tab:redshifts} shows the results of this selection.
+
+\begin{figure*}
+\includegraphics[width=160mm]{figures/specz_comparison.pdf}
+\caption{Spectroscopic redshifts from Griffith, 3DHST, and MUSYC catalogs.
+The number in the upper left of each plot is the percentage of redshifts which agree within $\Delta z < 0.05$ between the two catalogs being compared in each panel.
+Within this range there is over 98\% agreement in redshifts between all three catalogs.}
+\label{fig:speczs}
+\end{figure*}
+
 \subsection{User weighting}
@@
 \section{Galaxy Zoo interface and classifications}
+\label{sec:gz_interface}
 
@@
 
-Stuff to do in this section:
+\subsection{Challenges of debiasing questions beyond ``smooth or features''}
+Each FERENGI image does not have the same number of users answering each question, due to the structure of the decision tree.
+Every user answers the first question, ``Is the galaxy smooth and rounded, with no sign of a disk?''; as such the vote fractions $\rm p_{smooth}, p_{features}$, and $\rm p_{artifact}$ are all computed with the minimum statistical error for any question, with roughly 40 total answers (see Section~\ref{sec:gz_interface}).
+The number of users to answer any subsequent question, however, is always equal to or less than the number to answer the preceding question.
+For this reason, some galaxies may have very few (or even zero) answers to a question further down the tree (see Figure make-figure-of-count-distribution-for-each-question).
+To minimize statistical error in computing vote fractions, a cut on the number of answers to a given question is always implemented.
+
+In the FERENGI data, we find that this places large limitations on the amount of information we can extract for the higher order questions.
+We require that at least 5 users answer each question for a galaxy image at $z=0.3$ \emph{and} its image at higher $z$.
+This requirement placed on both images is not met by a significant number of galaxies for questions beyond question 1.
+Without sufficient galaxies in each surface brightness/redshift bin, we cannot accurately measure a relationship between vote fractions and redshift; for this reason we only offer debiased vote fractions for question 1.
+\textbf{perhaps compute number of galaxies that can be fit to zeta for each question, show a table?
+overkill?} In Section \ref{sec:ferengi_bar} we show results of an attempt to measure $\zeta$ for $\rm p_{bar}$.
 
@@
 \centering
-%\rotate
+\rotate
 \tablecolumns{12}
@@
 \startdata
-10000034            & 188.93       & 62.23         & AEGIS           &  correctable &  72 &  10 &  10.0 & 0.625 & 0.625 & 0.629 & 0 \\
-10000162            & 160.99      & 11.70          & AEGIS           &  uncorrectable &  84 &  17 &  17.0 & 0.810 & 0.810 & 0.810 & 1 \\
-5001356             & 210.80       & 54.15         & GOODS-N-Shallow &  correctable &  88 &  18 &  18.0 & 0.783 & 0.783 & 0.722 & 0 \\
-9003947835          & 176.54       & 8.74          & GOODS-S-Shallow &  nei &  48 &  16 &  16.0 & 1.000 & 1.000 & 1.000 & 1 \\
-GDS~S~16203         & 186.44       & 47.88         & GOODS-FULL      &  nei &  89 &  17 &  17.0 & 0.739 & 0.739 & 0.739 & 0 \\
-8647474690312438284 & 188.93       & 62.64         & SDSS            &  zlt3 &  91 &   0 &   0.0 & 0.000 & 0.000 & 0.000 & 0 \\
-20061690            & 160.99       & 11.70         & COSMOS          &  nei &  65 &   4 &   3.4 & 0.333 & 0.295 & 0.295 & 0 \\
-20061692            & 176.54       & 8.45          & COSMOS          &  correctable &  75 &  14 &  14.0 & 0.609 & 0.629 & 0.666 & 0 \\
-90022947            & 230.24       & 84.20         & GEMS           &  zlt3 & 129 &  12 &  12.0 & 0.462 & 0.462 & 0.492 & 0 \\
-20063829            & 203.23       & 93.20         & COSMOS         &  correctable &  69 &  18 &  17.0 & 0.900 & 0.895 & 0.840 & 1 \\
+13035128            & 214.99  & 53.02    & AEGIS   &  correctable  		&  121 &  0.46 &  0.50 & 0.12 & 0.14 & 0.73 & 0.12 \\
+13035131            & 215.01  & 53.02    & AEGIS   &  nei           		&  134 &  0.61 &  0.65 & 0.20 &      &      & 0.65 \\
+    ...             & ...     & ...      &  ...    &  ...              		&  ... & ...   &  ...  & ...  & ...  & ...  & ...  \\
+20055697            & 150.52  & 2.09     & COSMOS  &  correctable   		&  52  &  0.52 &  0.55 & 0.38 & 0.55 & 0.81 & 0.38  \\
+20055698            & 150.50  & 2.09     & COSMOS  &  uncorrectable 		&  31  &  0.61 &  0.70 & 0.47 & 0.47 & 0.80 & 0.70 \\
+    ...             & ...     & ...      &  ...    &  ...              		&  ... & ...   &  ...  & ...  & ...  & ...  & ...  \\
+90021901            & 53.29   & -27.85   & GEMS    &  correctable   		&  131 &  0.21 &  0.21 & 0.15 & 0.14 & 0.35 & 0.15 \\
+90021903            & 53.34   & -27.83   & GEMS    &  $z<0.3$         		&  142 &  0.78 &  0.80 & 1.04 &      &      & 0.80 \\
+    ...             & ...     & ...      &  ...    &  ...              		&  ... & ...   &  ...  & ...  & ...  & ...  & ...  \\
+GDS\_N\_2333        & 189.02  & 62.12    & GOODS-N & $\rm nei\_needs\_redshift$ &  40  &  0.33 &  0.33 & 0.87 &      &      & 0.33 \\
+GDS\_S\_3132        & 53.04   & -27.71   & GOODS-S & uncorrectable              &  40  &  0.83 &  0.83 & 0.45 & 0.38 & 0.85 & 0.83 \\
+    ...             & ...     & ...      &  ...    &  ...              		&  ... & ...   &  ...  & ...  & ...  & ...  & ...  \\
+587731173843665742  & 315.58  & 0.25     & SDSS    & $z<0.3$                    &  48  & 0.79  & 0.89  & 1.23 &      &      & 0.89 \\
+587731173843730515  & 315.61  & 0.30     & SDSS    & $z<0.3$                    &  53  & 0.68  & 0.75  & 1.06 &      &      & 0.75 \\
+
 \enddata
-\tablecomments{Full version is online at some website, here are 10 rows out of 181,101 in the full version.\emph{These numbers are super fake right now - put real values in for final version!}}
+\tablecomments{Full version is online at some website, here are 10 rows out of 181,101 in the full version.}
 \end{deluxetable}
@@
 
+\begin{table}
+\caption{Breakdown of what we can correct out of the GOODS shallow depth data. \label{goods_shallow_categories}}
+\begin{tabular}{lrrrrrrrr}
+\hline\hline
+                                   & GOODS-N & GOODS-S & Total \\
+\hline
+Correctable                        & 748     & 514     & 1,262 \\
+Uncorrectable                      & 526     & 1,143   & 1,669 \\
+No Correction Needed ($z \le 0.3$) & 267     & 267     & 534   \\ 
+NEI                                & 851     & 2,670   & 3,521 \\
+No Redshift Information            & 159     & 319     & 478   \\
+Total                              & 2,551   & 4,913   & 7,464 \\
+\hline\hline
+\end{tabular}
+\end{table}
+
 GZH used both 5-epoch and 2-epoch sets of data to construct the GOODS set of images.
@@
 
-4,461 galaxies have both full depth and shallow depth classifications. 
+\subsection{Comparing shallow and full depth morphologies}.
+Of the 11,157 galaxies in the GOODS-N and GOODS-S full depth sample, 4,461 of these are in the shallow-depth sample.
+In Figure~\ref{fig:shallow_vs_full} we find a strong correlation between $\rm p_{features}$ for both sets of images.
+The mean change in $\rm p_{features}$ from the shallow to full depth images  $\rm p_{features,full} - p_{features,shallow} = \Delta p = 0.00$, with a standard deviation of $\sigma = 0.17$.
+While there is some variance in $\Delta p$ in the whole sample, the change is usually small and not often significant enough to change a morphological classification.
+Defining a clean sample of disk galaxies as those with $p_{features,best}>0.8$, elliptical galaxies as those with  $p_{smooth,best}<0.2$, and intermediate as those in between, we find that 75\% of the sample would not change morphology.
+Of the remaining 25\% that would change morphology, only 0.3\% (representing 10 galaxies total) drastically change morphology from smooth to featured or visa versa, while the rest would transition to or from the ``intermediate'' morphology.
+Details can be seen in Table~\ref{shallow_to_full_stats} and examples of images representing the 9 possible changes (or lack of) in morphology are shown in Figures~\ref{fig:shallow_smooth},\ref{fig:shallow_intermediate}, and \ref{fig:shallow_featured}.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.50\textwidth]{figures/full_shallow_p_plot.pdf}
+\caption{shallowfull}
+\label{fig:shallow_vs_full}
+\end{center}
+\end{figure}
+
+\begin{table}
+\caption{Properties of galaxies whose morphologies changed or stayed the same in the shallow vs full images.
+Featured here is defined as $p_{features,best}>0.8$, intermediate = $0.2<p_{features,best}<0.8$, smooth = $p_{smooth,best}<0.2$.
+\label{shallow_to_full_stats}}
+\begin{tabular}{lrrrrrrrr}
+\hline\hline
+shallow to full morphology    & N       & \%       & $<\Delta p>$ & $<z>$ \\
+\hline
+smooth to smooth              & 758     & 17.0     & -0.00        &  0.69\\
+smooth to intermediate        & 367     & 8.2      & 0.18         &  0.69\\
+smooth to featured            & 7       & 0.2      & 0.76         &  0.57\\ 
+intermediate to smooth        & 214     & 4.8      & -0.18        &  0.65\\
+intermediate to intermediate  & 2,303   & 51.6     & 0.01         &  0.78 \\
+intermediate to featured      & 168     & 3.8      & 0.19         &  0.83\\
+featured to smooth            & 3       & 0.1      & -0.74        &  0.71\\
+featured to intermediate      & 337     & 7.6      & -0.18        &  0.68\\
+featured to featured          & 301     & 6.8      & -0.05        &  0.71\\
+
+Total                         & 4,461   & 100      &              & \\
+\hline\hline
+\end{tabular}
+\end{table}
+
+\begin{figure*}
+\centering
+
+\subfigure{[a]\label{fig:smoothtoint}\includegraphics[width=\textwidth]{figures/smooth_to_smooth.pdf}}
+
+\subfigure{[b]\label{fig:smoothtoint}\includegraphics[width=\textwidth]{figures/smooth_to_intermediate.pdf}}
+
+\subfigure{[c]\label{fig:smoothtoint}\includegraphics[width=\textwidth]{figures/smooth_to_featured.pdf}}
+
+\caption{Galaxies whose shallow images were classified as smooth and full depth images were classified as smooth, intermediate, or featured.}
+\label{fig:shallow_smooth}
+\end{figure*}
+
+\begin{figure*}
+\centering
+
+\subfigure{[b]\label{fig:smoothtoint}\includegraphics[width=\textwidth]{figures/intermediate_to_smooth.pdf}}
+
+\subfigure{[b]\label{fig:smoothtoint}\includegraphics[width=\textwidth]{figures/intermediate_to_intermediate.pdf}}
+
+\subfigure{[b]\label{fig:smoothtoint}\includegraphics[width=\textwidth]{figures/intermediate_to_featured.pdf}}
+
+\caption{Galaxies whose shallow images were classified as intermediate and full depth images were classified as smooth, intermediate, or featured.}
+\label{fig:shallow_intermediate}
+\end{figure*}
+
+\begin{figure*}
+\centering
+
+\subfigure{[b]\label{fig:smoothtoint}\includegraphics[width=\textwidth]{figures/featured_to_smooth.pdf}}
+
+\subfigure{[b]\label{fig:smoothtoint}\includegraphics[width=\textwidth]{figures/featured_to_intermediate.pdf}}
+
+\subfigure{[b]\label{fig:smoothtoint}\includegraphics[width=\textwidth]{figures/featured_to_featured.pdf}}
+
+\caption{Galaxies whose shallow images were classified as featured and full depth images were classified as smooth, intermediate, or featured.}
+\label{fig:shallow_featured}
+\end{figure*}
+
+\subsection{FERENGI analysis of pbar}
+\label{sec:ferengi_bar}
+\begin{figure*}
+\centering
+\subfigure{[a]\label{a}\includegraphics[width=0.5\textwidth]{figures/p_vs_p_SB_redshift_bar.pdf}}
+\subfigure{[b]\label{b}\includegraphics[width=0.4\textwidth]{figures/z1_mu20_subplot1_bar.pdf}}
+\\
+\subfigure{[c]\label{c}\includegraphics[width=0.5\textwidth]{figures/orangebars_bar.pdf}}
+\subfigure{[d]\label{d}\includegraphics[width=0.4\textwidth]{figures/z1_mu20_subplot2_bar.pdf}}
+\caption{Same as Figure~\ref{fig:p_vs_p}, but with the bar question.}
+\label{fig:p_vs_p_bar}
+\end{figure*}
+
+\begin{table}ー
+\caption{Distribution of \ferengi{} images analysed in Figure~\ref{fig:p_vs_p_bar}.
+Correctable images had a single-valued relationship between their measured $p_{\rm bar}$ values at high and low redshifts (white regions in Figure~\ref{fig:p_vs_p_bar}).
+Uncorrectable images had a non single-valued relationship (blue regions).
+NEI images had undetermined relationships due to a lack of data ($N<5$) in their corresponding z-$\mu$ bins (gray regions).
+Only 17\% (maximum) of FERENGI galaxies in the sample were considered ``correctable'', which is not sufficient to compute a $\zeta$ function applicable to the Hubble data.
+\label{ferengi_bar_corrections}}
+\begin{tabular}{lrr}
+\hline \hline
+				                   & N       & \% \\
+\hline 
+Correctable                        & 664   & 17\% \\
+Uncorrectable                      & 483   & 12\% \\
+NEI                                & 2,803     & 71\%\\
+Total                              & 3,950   & 100\% \\
+\hline \hline
+\end{tabular}
+\end{table}
+
 \end{document}

### 2016-03-17 writeup/gz_hubble_data.tex
Tables for main sample, SDSS single and coadd

@@
 \usepackage{deluxetable}
+\usepackage{url}
 \bibliographystyle{mn2e}
@@
 \tablecaption{GZH redshifts by survey} 
-\label{tab:redshifts}
+\label{tbl:redshifts}
 \tabletypesize{\scriptsize}
@@
 We compiled redshifts from a variety of sources to include in the GZH catalog.
-For each galaxy, the redshift selected is in the $\tt Z\_Best$ column of the data (see Table~\ref{tab:catalog}), its type (spectroscopic: $\tt SPEC\_Z$, photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column $\tt Z\_BEST\_TYPE$, and the source catalog ($\tt Griffith$ \citep{gri12}, $\tt 3DHST$ \citep{mom15}, $\tt MUSYC$ \citep{car10}, or $\tt UltraVISTA$ \citep{ilb13}) of the redshift is in column $\tt Z\_BEST\_SOURCE$.
+For each galaxy, the redshift selected is in the $\tt Z\_Best$ column of the data (see Table~\ref{tbl:catalog}), its type (spectroscopic: $\tt SPEC\_Z$, photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column $\tt Z\_BEST\_TYPE$, and the source catalog ($\tt Griffith$ \citep{gri12}, $\tt 3DHST$ \citep{mom15}, $\tt MUSYC$ \citep{car10}, or $\tt UltraVISTA$ \citep{ilb13}) of the redshift is in column $\tt Z\_BEST\_SOURCE$.
 
@@
 If no spectroscipic redshifts are available, we compare the 1-$\sigma$ errors of the photometric (Griffith, 3DHST, MUSYC, UltraVISTA) and grism (UltraVISTA) redshifts, and use the redshift with the smallest error.
-Table~\ref{tab:redshifts} shows the results of this selection.
+Table~\ref{tbl:redshifts} shows the results of this selection.
 
@@
 
-\subsection{Results of $\zeta$ approach}
+\subsection{Results of $\zeta$ approach}\label{ssec:zeta_results}
 
@@
 We use the resulting hulls to define the correctable and uncorrectable regions for categorizing the Hubble galaxies.
-The results of this method and final categorization of the Hubble sample is displayed in Table~\ref{hubble_debiasable}.
+The results of this method and final categorization of the Hubble sample is displayed in Table~\ref{tbl:hubble_debiasable}.
 We find that of the galaxies at redshift higher than $z=z_{0}=0.3$, 17\% of these are able to be debiased using the $\zeta$ method, 27\% cannot be debiased, and 56\% cannot be determined, due to a lack of redshift or information or due to a lack of \ferengi{} data corresponding to those galaxies' redshift/surface brightness values.
@@
 \begin{itemize}
-\item talk about where the Hubble sample falls in this space, reference table \ref{hubble_debiasable} 
+\item talk about where the Hubble sample falls in this space, reference table \ref{tbl:hubble_debiasable} 
 \item justify $N>5$ and spread $< 0.2$ (or find a better way to choose criteria)
@@
 \emph{updated from 3-8-16: Switching to full depth for all GOODS data.
-Shallow depth information in appendix.}\label{hubble_debiasable}}
-\begin{tabular}{lrrrrrrrr}
+Shallow depth information in appendix.}\label{tbl:hubble_debiasable}}
+\begin{tabular}{lcrrrrrrr}
 \hline\hline
-                                  & AEGIS   & COSMOS & GEMS & GOODS-N & GOODS-S         & SDSS    & Total \\
+                                   & Correction type & AEGIS   & COSMOS & GEMS & GOODS-N & GOODS-S    & SDSS    & Total \\
 \hline
-Correctable                        & 1,654   & 15,170 & 1,837 & 993    & 835     	& 0       & 20,489\\
-Uncorrectable                      & 1,917   & 26,113 & 2,423 & 1,385  & 1,282   	& 0       & 33,120\\
-No Correction Needed ($z \le 0.3$) & 955     & 11,926 & 1,175 & 415    & 400     	& 37,545  & 52,416\\ 
-NEI                                & 2,847   & 34,511 & 3,308 & 2,535  & 2,523   	& 0       & 45,724\\
-No Redshift Information            & 1,134   & 5,088  & 561   & 687    & 102   		& 14,316  & 21,888\\
-Total                              & 8,507   & 92,808 & 9,304 & 6,015  & 5,142   	& 51,861  & 173,637\\
+Correctable                        & 0               & 1,654   & 15,170 & 1,837 & 993    & 835     	& 0       & 20,489\\
+Uncorrectable                      & 1               & 1,917   & 26,113 & 2,423 & 1,385  & 1,282   	& 0       & 33,120\\
+No Correction Needed ($z \le 0.3$) & 2               & 955     & 11,926 & 1,175 & 415    & 400     	& 37,545  & 52,416\\ 
+NEI                                & 3               & 2,847   & 34,511 & 3,308 & 2,535  & 2,523   	& 0       & 45,724\\
+No Redshift Information            & 4               & 1,134   & 5,088  & 561   & 687    & 102   		& 14,316  & 21,888\\
+Total                              &                 & 8,507   & 92,808 & 9,304 & 6,015  & 5,142   	& 51,861  & 173,637\\
 \hline\hline
@@
 \tabletypesize{\scriptsize}
-\begin{deluxetable}{lrrllcrrrrrr|c}
+\begin{deluxetable}{lllllcrllllll|c}
 \centering
 \rotate
-\tablecolumns{12}
+\tablecolumns{13}
 \tablewidth{0pc}
-\tablecaption{GZH morphological classifications} 
-\label{tab:catalog}
+\tablecaption{GZH morphological classifications for AEGIS, COSMOS, GEMS, and GOODS images} 
+\label{tbl:catalog}
 \tabletypesize{\scriptsize}
 \tablehead{
- &  &   &  &  
+ & & & RA & dec  &  
 \multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
 \multicolumn{6}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
-\colhead{$\dots$}
+\colhead{$\ldots$}
 \\
-\colhead{OBJNO} & 
-\colhead{RA} & 
-\colhead{DEC} & 
+\colhead{Project ID} & 
+\colhead{Hubble ID} & 
 \colhead{Imaging} & 
-\colhead{Correctable Category} & 
+\colhead{J2000} & 
+\colhead{J2000} & 
+\colhead{Correction$^{1}$} & 
 \colhead{$N_\mathrm{votes}$} & 
@@
 \colhead{debiased} & 
+\colhead{best} &
 \colhead{lower~limit} & 
 \colhead{upper~limit} &
+\colhead{}
+}
+\small
+\startdata
+AHZ100002g  & 10010842  & AEGIS             &          &            & 0        & 948       & 0.118    & 0.128     & 0.085    & 0.085    & 0.226     & 0.226    \\
+AHZ100002h  & 10010870  & AEGIS             &          &            & 4        & 429       & 0.567    & 0.592     & 0.927    & 0.592    & $-$       & $-$      \\
+$\ldots$    & $\ldots$  & $\ldots$          & $\ldots$ & $\ldots$   & $\ldots$ &  $\ldots$ & $\ldots$ & $\ldots$  & $\ldots$ & $\ldots$ & $\ldots$  & $\ldots$ \\
+AHZ20004kd  & 20014731  & COSMOS            &          &            & 3        & 185       & 0.682    & 0.675     & 0.147    & 0.675    & $-$       & $-$      \\
+AHZ20004ke  & 20014732  & COSMOS            &          &            & 2        & 149       & 0.689    & 0.756     & 0.893    & 0.756    & $-$       & $-$      \\
+$\ldots$    & $\ldots$  & $\ldots$          & $\ldots$ & $\ldots$   & $\ldots$ &  $\ldots$ & $\ldots$ & $\ldots$  & $\ldots$ & $\ldots$ & $\ldots$  & $\ldots$ \\
+AHZ400043g  & 90022729  & GEMS              &          &            & 1        & 400       & 0.702    & 0.733     & 0.487    & 0.734    & 0.483     & 0.800    \\
+AHZ4000416  & 90022735  & GEMS              &          &            & 1        & 463       & 0.646    & 0.698     & 0.508    & 0.698    & 0.171     & 0.727    \\
+$\ldots$    & $\ldots$  & $\ldots$          & $\ldots$ & $\ldots$   & $\ldots$ &  $\ldots$ & $\ldots$ & $\ldots$  & $\ldots$ & $\ldots$ & $\ldots$  & $\ldots$ \\
+AGZ0007z47  & 10014     & GOODS-N-FULLDEPTH &          &            & 1        & 40        & 0.475    & 0.475     & 0.197    & 0.475    & 0.011     & 0.496    \\
+AGZ0007z48  & 10017     & GOODS-N-FULLDEPTH &          &            & 3        & 40        & 0.675    & 0.675     & 0.048    & 0.675    & 0.168     & 0.669    \\
+$\ldots$    & $\ldots$  & $\ldots$          & $\ldots$ & $\ldots$   & $\ldots$ &  $\ldots$ & $\ldots$ & $\ldots$  & $\ldots$ & $\ldots$ & $\ldots$  & $\ldots$ \\
+AGZ00083jb  & 8869      & GOODS-S-FULLDEPTH &          &            & 1        & 40        & 0.425    & 0.425     & 0.109    & 0.425    & 0.070     & 0.548    \\
+AGZ00083jc  & 8878      & GOODS-S-FULLDEPTH &          &            & 0        & 40        & 0.205    & 0.205     & 0.048    & 0.048    & $-$0.005  & 0.287    \\
+\enddata
+\tablenotetext{1}{Flag indicating how the vote fractions for this galaxy were corrected through debiasing (\S\ref{ssec:zeta_results}), if possible.
+0~=~correctable, 1~=~uncorrectable ($p_{raw}$ --- $p_{adj}$ is not single-valued), 2~=~uncorrected ($z_{\rm gal} < 0.3$), 3~=~uncorrectable (insufficient FERENGI galaxies in this $z$-$\mu$ bin), 4~=~uncorrectable (no galaxy redshift available).}
+\tablecomments{The full version of this table is available in electronic form, as well as at \url{http://data.galaxyzoo.org}.
+The complete version includes data for 118,425~galaxies and morphological information for all tasks in the tree.
+A subset of the information is shown here to illustrate form and content.}
+\end{deluxetable}
+
+% Why are some values negative?
+% Why are most of the full-depth GOODS weighted fractions identical to the raw fractions?
+
+\tabletypesize{\scriptsize}
+\begin{deluxetable}{lllllcrllll|c}
+\centering
+\rotate
+\tablecolumns{13}
+\tablewidth{0pc}
+\tablecaption{GZH morphological classifications for SDSS Stripe 82 single-epoch images} 
+\label{tbl:stripe82_single}
+\tabletypesize{\scriptsize}
+\tablehead{
+ & & & RA & dec  &  
+\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
+\multicolumn{4}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
+\colhead{$\ldots$}
+\\
+\colhead{Project ID} & 
+\colhead{Hubble ID} & 
+\colhead{Imaging} & 
+\colhead{J2000} & 
+\colhead{J2000} & 
+\colhead{Correction$^{1}$} & 
+\colhead{$N_\mathrm{votes}$} & 
+\colhead{fraction} & 
+\colhead{weighted} & 
+\colhead{debiased} & 
 \colhead{best} &
@@
 \startdata
-13035128            & 214.99  & 53.02    & AEGIS   &  correctable  		&  121 &  0.46 &  0.50 & 0.12 & 0.14 & 0.73 & 0.12 \\
-13035131            & 215.01  & 53.02    & AEGIS   &  nei           		&  134 &  0.61 &  0.65 & 0.20 &      &      & 0.65 \\
-    ...             & ...     & ...      &  ...    &  ...              		&  ... & ...   &  ...  & ...  & ...  & ...  & ...  \\
-20055697            & 150.52  & 2.09     & COSMOS  &  correctable   		&  52  &  0.52 &  0.55 & 0.38 & 0.55 & 0.81 & 0.38  \\
-20055698            & 150.50  & 2.09     & COSMOS  &  uncorrectable 		&  31  &  0.61 &  0.70 & 0.47 & 0.47 & 0.80 & 0.70 \\
-    ...             & ...     & ...      &  ...    &  ...              		&  ... & ...   &  ...  & ...  & ...  & ...  & ...  \\
-90021901            & 53.29   & -27.85   & GEMS    &  correctable   		&  131 &  0.21 &  0.21 & 0.15 & 0.14 & 0.35 & 0.15 \\
-90021903            & 53.34   & -27.83   & GEMS    &  $z<0.3$         		&  142 &  0.78 &  0.80 & 1.04 &      &      & 0.80 \\
-    ...             & ...     & ...      &  ...    &  ...              		&  ... & ...   &  ...  & ...  & ...  & ...  & ...  \\
-GDS\_N\_2333        & 189.02  & 62.12    & GOODS-N & $\rm nei\_needs\_redshift$ &  40  &  0.33 &  0.33 & 0.87 &      &      & 0.33 \\
-GDS\_S\_3132        & 53.04   & -27.71   & GOODS-S & uncorrectable              &  40  &  0.83 &  0.83 & 0.45 & 0.38 & 0.85 & 0.83 \\
-    ...             & ...     & ...      &  ...    &  ...              		&  ... & ...   &  ...  & ...  & ...  & ...  & ...  \\
-587731173843665742  & 315.58  & 0.25     & SDSS    & $z<0.3$                    &  48  & 0.79  & 0.89  & 1.23 &      &      & 0.89 \\
-587731173843730515  & 315.61  & 0.30     & SDSS    & $z<0.3$                    &  53  & 0.68  & 0.75  & 1.06 &      &      & 0.75 \\
+AHZ5000001  &   587730845812064684  &   SDSS    &   &   &     2 &   41  &   0.585   &    0.595  &   0.759   &   0.594   \\
+AHZ5000002  &   587730845812065247  &   SDSS    &   &   &     2 &   46  &   0.609   &    0.651  &   0.897   &   0.651   \\
+AHZ5000003  &   587730845812196092  &   SDSS    &   &   &     2 &   51  &   0.039   &    0.044  &   0.067   &   0.043   \\
+AHZ5000004  &   587730845812196825  &   SDSS    &   &   &     2 &   35  &   0.514   &    0.605  &   0.928   &   0.605   \\
+AHZ5000005  &   587730845812524122  &   SDSS    &   &   &     2 &   47  &   0.766   &    0.812  &   1.038   &   0.810   \\
+AHZ5000006  &   587730845812654984  &   SDSS    &   &   &     2 &   42  &   0.5	    &    0.542  &   0.680   &   0.541   \\
+AHZ5000007  &   587730845812655541  &   SDSS    &   &   &     2 &   41  &   0.488   &    0.526  &   0.697   &   0.525   \\
+AHZ5000008  &   587730845812720365  &   SDSS    &   &   &     2 &   53  &   0.792   &    0.84   &   1.050   &   0.839   \\
+AHZ5000009  &   587730845812720640  &   SDSS    &   &   &     4 &   43  &   0.0	    &    0.0    &   0.0	    &   0.0	    \\
+AHZ500000a  &   587730845812720699  &   SDSS    &   &   &     2 &   40  &   0.425   &    0.478  &   0.588   &   0.477   \\
+$\ldots$    & $\ldots$  & $\ldots$  & $\ldots$  & $\ldots$   & $\ldots$ &  $\ldots$ & $\ldots$ & $\ldots$ \\
+\enddata
+\tablenotetext{1}{Flag indicating how the vote fractions for this galaxy were corrected through debiasing (\S\ref{ssec:zeta_results}), if possible.
+0~=~correctable, 1~=~uncorrectable ($p_{raw}$ --- $p_{adj}$ is not single-valued), 2~=~uncorrected ($z_{\rm gal} < 0.3$), 3~=~uncorrectable (insufficient FERENGI galaxies in this $z$-$\mu$ bin), 4~=~uncorrectable (no galaxy redshift available).}
+\tablecomments{The full version of this table is available in electronic form, as well as at \url{http://data.galaxyzoo.org}.
+The complete version includes data for 21,522~galaxies and morphological information for all tasks in the tree.
+A subset of the information is shown here to illustrate form and content.}
+\end{deluxetable}
 
+\tabletypesize{\scriptsize}
+\begin{deluxetable}{lllllcrllll|c}
+\centering
+\rotate
+\tablecolumns{13}
+\tablewidth{0pc}
+\tablecaption{GZH morphological classifications for SDSS Stripe 82 coadded images} 
+\label{tbl:stripe82_coadd}
+\tabletypesize{\scriptsize}
+\tablehead{
+ & & & RA & dec  &  
+\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
+\multicolumn{4}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
+\colhead{$\ldots$}
+\\
+\colhead{Project ID} & 
+\colhead{Hubble ID} & 
+\colhead{Imaging} & 
+\colhead{J2000} & 
+\colhead{J2000} & 
+\colhead{Correction$^{1}$} & 
+\colhead{$N_\mathrm{votes}$} & 
+\colhead{fraction} & 
+\colhead{weighted} & 
+\colhead{debiased} & 
+\colhead{best} &
+\colhead{}
+}
+\small
+\startdata
+AHZ6000001  & 8647474690312306978   &   SDSS    &   &   &    4  & 40  & 0.275   &    0.289  &   0.762   &   0.289   & \\
+AHZ6000002  & 8647474690312307154   &   SDSS    &   &   &    2  & 43  & 0.605   &    0.634  &   0.858   &   0.635   & \\
+AHZ6000003  & 8647474690312307877   &   SDSS    &   &   &    2  & 51  & 0.608   &    0.627  &   0.906   &   0.627   & \\
+AHZ6000004  & 8647474690312308301   &   SDSS    &   &   &    4  & 52  & 0.038   &    0.038  &   0.723   &   0.038   & \\
+AHZ6000005  & 8647474690312308318   &   SDSS    &   &   &    2  & 44  & 0.614   &    0.632  &   0.776   &   0.631   & \\
+AHZ6000006  & 8647474690312308880   &   SDSS    &   &   &    2  & 36  & 0.667   &    0.683  &   0.901   &   0.683   & \\
+AHZ6000007  & 8647474690312372644   &   SDSS    &   &   &    4  & 48  & 0.646   &    0.674  &   1.145   &   0.674   & \\
+AHZ6000008  & 8647474690312372789   &   SDSS    &   &   &    4  & 45  & 0.489   &    0.571  &   0.964   &   0.570   & \\
+AHZ6000009  & 8647474690312372931   &   SDSS    &   &   &    4  & 47  & 0.553   &    0.587  &   0.926   &   0.587   & \\
+AHZ600000a  & 8647474690312373190   &   SDSS    &   &   &    4  & 47  & 0.574   &    0.559  &   1.008   &   0.559   & \\
+$\ldots$    & $\ldots$  & $\ldots$  & $\ldots$  & $\ldots$   & $\ldots$ &  $\ldots$ & $\ldots$ & $\ldots$ \\
 \enddata
-\tablecomments{Full version is online at some website, here are 10 rows out of 181,101 in the full version.}
+\tablenotetext{1}{Flag indicating how the vote fractions for this galaxy were corrected through debiasing (\S\ref{ssec:zeta_results}), if possible.
+0~=~correctable, 1~=~uncorrectable ($p_{raw}$ --- $p_{adj}$ is not single-valued), 2~=~uncorrected ($z_{\rm gal} < 0.3$), 3~=~uncorrectable (insufficient FERENGI galaxies in this $z$-$\mu$ bin), 4~=~uncorrectable (no galaxy redshift available).}
+\tablecomments{The full version of this table is available in electronic form, as well as at \url{http://data.galaxyzoo.org}.
+The complete version includes data for 30,339~galaxies and morphological information for all tasks in the tree.
+A subset of the information is shown here to illustrate form and content.}
 \end{deluxetable}
@@
 Needs some test cases for extracting a given set of objects (eg, clump galaxies in a particular redshift range) and evaluation of the results. Possibly include suggested thresholds, \'a la GZ2. 
-\section{Using the Catalog}
+\section{Using the catalog}
 \label{sec:cookbook}

### 2016-03-22 writeup/gz_hubble_data.tex
Sample data tables. Still need positions (?)

@@
 We compiled redshifts from a variety of sources to include in the GZH catalog.
-For each galaxy, the redshift selected is in the $\tt Z\_Best$ column of the data (see Table~\ref{tbl:catalog}), its type (spectroscopic: $\tt SPEC\_Z$, photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column $\tt Z\_BEST\_TYPE$, and the source catalog ($\tt Griffith$ \citep{gri12}, $\tt 3DHST$ \citep{mom15}, $\tt MUSYC$ \citep{car10}, or $\tt UltraVISTA$ \citep{ilb13}) of the redshift is in column $\tt Z\_BEST\_SOURCE$.
+For each galaxy, the redshift selected is in the $\tt Z\_Best$ column of the data (see Table~\ref{tbl:catalog_hst}), its type (spectroscopic: $\tt SPEC\_Z$, photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column $\tt Z\_BEST\_TYPE$, and the source catalog ($\tt Griffith$ \citep{gri12}, $\tt 3DHST$ \citep{mom15}, $\tt MUSYC$ \citep{car10}, or $\tt UltraVISTA$ \citep{ilb13}) of the redshift is in column $\tt Z\_BEST\_SOURCE$.
 
@@
 \tablecaption{GZH morphological classifications for AEGIS, COSMOS, GEMS, and GOODS images} 
-\label{tbl:catalog}
+\label{tbl:catalog_hst}
 \tabletypesize{\scriptsize}
@@
 \tabletypesize{\scriptsize}
+\begin{deluxetable}{lllllcrllllll|c}
+\centering
+\rotate
+\tablecolumns{13}
+\tablewidth{0pc}
+\tablecaption{GZH morphological classifications for desaturated Hubble images} 
+\label{tbl:catalog_desaturated}
+\tabletypesize{\scriptsize}
+\tablehead{
+ & & & RA & dec  &  
+\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
+\multicolumn{6}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
+\colhead{$\ldots$}
+\\
+\colhead{Project ID} & 
+\colhead{Hubble ID} & 
+\colhead{Imaging} & 
+\colhead{J2000} & 
+\colhead{J2000} & 
+\colhead{Correction} & 
+\colhead{$N_\mathrm{votes}$} & 
+\colhead{fraction} & 
+\colhead{weighted} & 
+\colhead{debiased} & 
+\colhead{best} &
+\colhead{lower~limit} & 
+\colhead{upper~limit} &
+\colhead{}
+}
+\small
+\startdata
+AHZF000001  &   20000002    &   COSMOS  &   &   &   1   &   160 &  0.708   &     0.755   &   0.228    &    0.754 &   0.325 &   0.829  \\
+AHZF000003  &   20000004    &   COSMOS  &   &   &   3   &   301 &  0.367   &     0.379   &   0.100    &    0.379 &   0.198 &   0.198  \\
+AHZF000004  &   20000006    &   COSMOS  &   &   &   3   &   319 &  0.265   &     0.271   &   0.010    &    0.270 &   $-$	&   $-$    \\
+AHZF00000z  &   20000102    &   COSMOS  &   &   &   1   &   150 &  0.727   &     0.78    &   0.233    &    0.780 &   0.316 &   0.820  \\
+AHZF000010  &   20000104    &   COSMOS  &   &   &   2   &   164 &  0.811   &     0.849   &   0.904    &    0.848 &   $-$	&   $-$    \\
+\enddata
+\tablecomments{The full version of this table is available in electronic form, as well as at \url{http://data.galaxyzoo.org}.
+The complete version includes data for 3,927~galaxies and morphological information for all tasks in the tree.
+A subset of the information is shown here to illustrate form and content.}
+\end{deluxetable}
+
+\tabletypesize{\scriptsize}
+\begin{deluxetable}{lllllcrllllll|c}
+\centering
+\rotate
+\tablecolumns{13}
+\tablewidth{0pc}
+\tablecaption{GZH morphological classifications for color-inverted images} 
+\label{tbl:catalog_inverted}
+\tabletypesize{\scriptsize}
+\tablehead{
+ & & & RA & dec  &  
+\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
+\multicolumn{6}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
+\colhead{$\ldots$}
+\\
+\colhead{Project ID} & 
+\colhead{Hubble ID} & 
+\colhead{Imaging} & 
+\colhead{J2000} & 
+\colhead{J2000} & 
+\colhead{Correction} & 
+\colhead{$N_\mathrm{votes}$} & 
+\colhead{fraction} & 
+\colhead{weighted} & 
+\colhead{debiased} & 
+\colhead{best} &
+\colhead{lower~limit} & 
+\colhead{upper~limit} &
+\colhead{}
+}
+\small
+\startdata
+AHZC000001	&   20000002	&   COSMOS	&   &   &   1	&   168	&   0.615   &   0.664   &   0.160   &  0.663   &  0.271    &  0.775    \\
+AHZC000003	&   20000004	&   COSMOS	&   &   &   0	&   235	&   0.333   &   0.364   &   0.002   &  0.002   &  0.063    &  0.063    \\
+AHZC000004	&   20000006	&   COSMOS	&   &   &   3	&   316	&   0.235   &   0.252   & $-0.011$  &  0.252   &  $-$	    &  $-$      \\
+AHZC00000z	&   20000102	&   COSMOS	&   &   &   1	&   207	&   0.755   &   0.757   &   0.272   &  0.756   &  0.249    &  0.796    \\
+AHZC000010	&   20000104	&   COSMOS	&   &   &   2	&   158	&   0.843   &   0.882   &   0.936   &  0.881   &  $-$	    &  $-$      \\
+\enddata
+\tablecomments{The full version of this table is available in electronic form, as well as at \url{http://data.galaxyzoo.org}.
+The complete version includes data for 3,927~galaxies and morphological information for all tasks in the tree.
+A subset of the information is shown here to illustrate form and content.}
+\end{deluxetable}
+
+\tabletypesize{\scriptsize}
+\begin{deluxetable}{lllllcrllllll|c}
+\centering
+\rotate
+\tablecolumns{13}
+\tablewidth{0pc}
+\tablecaption{GZH morphological classifications for GOODS 2-epoch images} 
+\label{tbl:catalog_desaturated}
+\tabletypesize{\scriptsize}
+\tablehead{
+ & & & RA & dec  &  
+\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
+\multicolumn{6}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
+\colhead{$\ldots$}
+\\
+\colhead{Project ID} & 
+\colhead{Hubble ID} & 
+\colhead{Imaging} & 
+\colhead{J2000} & 
+\colhead{J2000} & 
+\colhead{Correction} & 
+\colhead{$N_\mathrm{votes}$} & 
+\colhead{fraction} & 
+\colhead{weighted} & 
+\colhead{debiased} & 
+\colhead{best} &
+\colhead{lower~limit} & 
+\colhead{upper~limit} &
+\colhead{}
+}
+\small
+\startdata
+AHZ3000001  &   50000000    &     GOODS-N   &   &   &   0   &   123	&   0.390   &   0.415	&   0.090 &   0.090 &   $-$     &   $-$      \\
+AHZ3000002  &   50000001    &     GOODS-N   &   &   &   2   &   126	&   0.341	&   0.355	&   0.356 &   0.356 &   0.220	&   0.279    \\
+AHZ3000003  &   50000005    &     GOODS-N   &   &   &   1   &   129	&   0.760   &   0.826	&   0.633 &   0.825 &   0.596	&   0.834    \\
+AHZ3000004  &   50000008    &     GOODS-N   &   &   &   1   &   120	&   0.758	&   0.787	&   0.639 &   0.787 &   0.658	&   0.834    \\
+AHZ3000005  &   50000010    &     GOODS-N   &   &   &   1   &   123	&   0.854	&   0.890   &   0.611 &   0.889 &   0.597	&   0.914    \\
+\enddata
+\tablecomments{The full version of this table is available in electronic form, as well as at \url{http://data.galaxyzoo.org}.
+The complete version includes data for 6,144~galaxies and morphological information for all tasks in the tree.
+A subset of the information is shown here to illustrate form and content.}
+\end{deluxetable}
+
+\tabletypesize{\scriptsize}
 \begin{deluxetable}{lllllcrllll|c}
@@
 \colhead{Project ID} & 
-\colhead{Hubble ID} & 
+\colhead{SDSS DR7 ObjID} & 
 \colhead{Imaging} & 
@@
 \colhead{J2000} & 
-\colhead{Correction$^{1}$} & 
+\colhead{Correction} & 
 \colhead{$N_\mathrm{votes}$} & 
@@
 \enddata
-\tablenotetext{1}{Flag indicating how the vote fractions for this galaxy were corrected through debiasing (\S\ref{ssec:zeta_results}), if possible.
-0~=~correctable, 1~=~uncorrectable ($p_{raw}$ --- $p_{adj}$ is not single-valued), 2~=~uncorrected ($z_{\rm gal} < 0.3$), 3~=~uncorrectable (insufficient FERENGI galaxies in this $z$-$\mu$ bin), 4~=~uncorrectable (no galaxy redshift available).}
 \tablecomments{The full version of this table is available in electronic form, as well as at \url{http://data.galaxyzoo.org}.

### 2016-03-23 writeup/gz_hubble_data.tex
Finished the fake AGN tables and fixed some errors.

--- 2016-03-17 writeup/gz_hubble_data.tex
@@
 \begin{table*}
-\caption{Summary of Galaxy Zoo: Hubble imaging \label{gzh_numbers}}
+\caption{Summary of Galaxy Zoo: Hubble imaging \label{tbl:gzh_numbers}}
 \begin{tabular}{lclcrr}
@@
 \begin{deluxetable}{l|rr|rrr|rr|r|rr}
-
 \centering
@@
 \tablewidth{0pc}
-\tablecaption{GZH redshifts by survey} 
-\label{tbl:redshifts}
+\tablecaption{GZH redshifts by survey\label{tbl:redshifts}} 
 \tabletypesize{\scriptsize}
@@
 
-The selection criteria for the different morphological categories is summarised in Table \ref{morphologies}.
+The selection criteria for the different morphological categories is summarised in Table \ref{tbl:morphologies}.
 The surface brightness selection ($N_\mu = 3$) was (1) low: $\mu > 21.5$~\magarc;  (2) mid: $20.5 < \mu < 21.5$~\magarc; and (3) high: $\mu < 20.5$~\magarc.
@@
 \begin{table*}
-\caption{Summary of morphological categories selected for FERENGI sample.\label{morphologies}}
+\caption{Summary of morphological categories selected for FERENGI sample.\label{tbl:morphologies}}
 \begin{tabular}{lllc}
@@
 The final number of \ferengi{} images produced for each galaxy is ultimately a function of galaxy's redshift, since the new images cannot be resampled at better angular resolution than the original SDSS data, as well as the number of $e$ values selected.
-Table~\ref{ferengivalues} summarizes the total sample of redshifted images produced for GZH.
+Table~\ref{tbl:ferengivalues} summarizes the total sample of redshifted images produced for GZH.
 
 \begin{table}
-\caption{Summary of FERENGI artificial redshifting \label{ferengivalues}}
+\caption{Summary of FERENGI artificial redshifting \label{tbl:ferengivalues}}
 \begin{tabular}{lccccr}
@@
 In Figure~\ref{fig:p_vs_p} we examine the change in $p_{\rm features}$ for the \ferengi{} galaxies relative to their lowest simulated redshift.
-In this analysis, only galaxies whose lowest simulated redshift image was ($\rm z_{sim}=0.3$) were used (see Table \ref{ferengivalues}), and only those which had detectable surface brightness measurements in \sextractor{}; this includes 3,950 of the total 6,466 images.
+In this analysis, only galaxies whose lowest simulated redshift image was ($\rm z_{sim}=0.3$) were used (see Table \ref{tbl:ferengivalues}), and only those which had detectable surface brightness measurements in \sextractor{}; this includes 3,950 of the total 6,466 images.
 For each simulated redshift value $z$, and at a fixed surface brightness $\mu$, we plot $p_{\rm features,z}$, the value measured at that simulated redshift, vs $p_{\rm features,z=0.3}$, the value measured for the same galaxy imaged at $z=0.3$.
@@
 
-\begin{table}ー
+\begin{table}
 \caption{Distribution of \ferengi{} images analysed in Figure~\ref{fig:p_vs_p}.
@@
 Uncorrectable images had a non single-valued relationship (blue regions).
-NEI images had undetermined relationships due to a lack of data ($N<5$) in their corresponding z-$\mu$ bins (gray regions).
-\label{ferengi_corrections}}
+NEI images had undetermined relationships due to a lack of data ($N<5$) in their corresponding z-$\mu$ bins (gray regions).\label{tbl:ferengi_corrections}}
 \begin{tabular}{lrr}
@@
 \begin{itemize}
-\item talk about where the Hubble sample falls in this space, reference table \ref{tbl:hubble_debiasable} 
+\item talk about where the Hubble sample falls in this space, reference Table~\ref{tbl:hubble_debiasable} 
 \item justify $N>5$ and spread $< 0.2$ (or find a better way to choose criteria)
 \item check out corrections for correctable and NEI, show some sample images of corrected galaxies
-\item show some data for $\pbar$, determine or justify why we won't debiase them  
+\item show some data for $\pbar$, determine or justify why we won't debias them  
 \end{itemize}
@@
 
-\section{The Catalog}
-
-The data release for GZH includes morphological data for 181,101 galaxies.
-The full table can be accessed at some website.
+We also classified a set of images designed to measure the effect of AGN on morphological classifications.
+This could occur since galactic nuclei can have bright, unresolved optical emission that could either mimic the effect of a strong bulge or otherwise obscure classification.
+The presence of an AGN is simulated by modeling the PSF for Hubble for a variety of images and then inserting a bright source near the center of the galaxy.
+For each galaxy, the simulated AGN can have one of three colors -- either blue, red, or flat (white) as seen in the color images -- and a range of brightnesses such that $L_\mathrm{ratio} \equiv L_\mathrm{galaxy}/L_\mathrm{AGN}$ is in $(0.2,1.0,2.0,5.0,10.0,50.0)$.
+Combining these parameters generates 15~images with different simulated AGN for each chosen host.
+
+Images with simulated AGN were classified in the main interface in an identical manner and evenly distributed with unaltered images of the galaxies.
+Classifiers were not explicitly told that the images had been altered, as the goal was to measure the effect on normal classifications in as unbiased a manner as possible.
+
+Two sets of simulated AGN were measured in GZH.
+The first set (version~1) was assembled from 95~galaxies from GEMS imaging and PSFs from \texttt{daophot}.
+The second set (version~2) was assembled from 96~galaxies with GOODS-S imaging; this version used deeper imaging and improved PSFs from \texttt{TinyTim}.
+
+\section{The catalog}
+
+The data release for GZH includes morphological data for 181,101~images (generated from a total of 150,771~unique galaxies).
+The full table can be accessed at \url{http://data.galaxyzoo.org}.
 We also include a secondary metadata table, which contains data from a variety of sources explained in Section \ref{sec:data}.
 
-For each galaxy we list its unique objid, as well as the source's RA, DEC, and survey (AEGIS, COSMOS, GEMS, GOODS North (full and shallow depth), GOODS South (full and shallow depth), SDSS.
-For each of the 40 (?) questions in the GZH decision tree, the following classification data is provided: For each question, $\tt N_{votes}$ is the number of users to answer that question.
+Each image is listed under a unique project ID (eg AHZ000001); the actual galaxy in the image is identified by the combination of the OBJNO and original survey.
+For each of the 55~responses in the GZH decision tree, the following classification data is provided: for each question, $\tt N_{votes}$ is the number of users to answer that question.
 For each unique answer, $\tt fraction$ is the fraction of users to select that answer ($\rm N_{answer}/N_{votes}$, and $\tt weighted$ is the weighted fraction, which takes into account user consistency (Section~\ref{sec:weighting}).
@@
 
-\tabletypesize{\scriptsize}
-\begin{deluxetable}{lllllcrllllll|c}
+We split the data products for GZH by the type of image being classified.
+Table~\ref{tbl:catalog_hst} contains the classifications for the Hubble images from the AEGIS, COSMOS, and GEMS surveys, as well as 5-epoch deep imaging from the GOODS-N and GOODS-S surveys.
+This contains 118,425~galaxies and is the primary output from the GZH project.
+The next two tables have data for a small subset of 3,927~COSMOS~images that were re-processed to study the effect of color balance on morphological classification.
+Table~\ref{tbl:catalog_faded} has images that are desaturated to minimize the color contrast; Table~\ref{tbl:catalog_recoloured} has images with the red and blue color channels inverted.
+Table~\ref{tbl:catalog_goods_shallow} contains data for 6,144~galaxies with 2-epoch images from GOODS.
+These have been mostly supplanted in the main table with deeper 5-epoch GOODS imaging; however, there are 1,683~galaxies in the shallower imaging that were not classified in the deeper mosaics.
+This data can also be compared to the counterparts in Table~\ref{tbl:catalog_hst} to study the effect of depth on morphological classification.
+Tables~\ref{tbl:stripe82_single} and \ref{tbl:stripe82_coadd} contain data for the SDSS Stripe~82 single-depth and co-added images, respectively, that were classified using the GZH interface and decision tree.
+Finally, Table~\ref{tbl:fake_agn} contains classifications for images with artificial point sources intended to simulate the effect of a bright AGN, as used in \citet{sim14}.
+
+\tabletypesize{\scriptsize}
+\begin{deluxetable}{lllcrllllll|c}
 \centering
@@
 \tablewidth{0pc}
-\tablecaption{GZH morphological classifications for AEGIS, COSMOS, GEMS, and GOODS images} 
-\label{tbl:catalog}
+\tablecaption{GZH morphological classifications for Hubble images from AEGIS, COSMOS, GEMS, and GOODS\label{tbl:catalog_hst}} 
 \tabletypesize{\scriptsize}
 \tablehead{
- & & & RA & dec  &  
+ & & & 
 \multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
@@
 \colhead{Imaging} & 
-\colhead{J2000} & 
-\colhead{J2000} & 
 \colhead{Correction$^{1}$} & 
@@
 \startdata
-AHZ100002g  & 10010842  & AEGIS             &          &            & 0        & 948       & 0.118    & 0.128     & 0.085    & 0.085    & 0.226     & 0.226    \\
-AHZ100002h  & 10010870  & AEGIS             &          &            & 4        & 429       & 0.567    & 0.592     & 0.927    & 0.592    & $-$       & $-$      \\
-$\ldots$    & $\ldots$  & $\ldots$          & $\ldots$ & $\ldots$   & $\ldots$ &  $\ldots$ & $\ldots$ & $\ldots$  & $\ldots$ & $\ldots$ & $\ldots$  & $\ldots$ \\
-AHZ20004kd  & 20014731  & COSMOS            &          &            & 3        & 185       & 0.682    & 0.675     & 0.147    & 0.675    & $-$       & $-$      \\
-AHZ20004ke  & 20014732  & COSMOS            &          &            & 2        & 149       & 0.689    & 0.756     & 0.893    & 0.756    & $-$       & $-$      \\
-$\ldots$    & $\ldots$  & $\ldots$          & $\ldots$ & $\ldots$   & $\ldots$ &  $\ldots$ & $\ldots$ & $\ldots$  & $\ldots$ & $\ldots$ & $\ldots$  & $\ldots$ \\
-AHZ400043g  & 90022729  & GEMS              &          &            & 1        & 400       & 0.702    & 0.733     & 0.487    & 0.734    & 0.483     & 0.800    \\
-AHZ4000416  & 90022735  & GEMS              &          &            & 1        & 463       & 0.646    & 0.698     & 0.508    & 0.698    & 0.171     & 0.727    \\
-$\ldots$    & $\ldots$  & $\ldots$          & $\ldots$ & $\ldots$   & $\ldots$ &  $\ldots$ & $\ldots$ & $\ldots$  & $\ldots$ & $\ldots$ & $\ldots$  & $\ldots$ \\
-AGZ0007z47  & 10014     & GOODS-N-FULLDEPTH &          &            & 1        & 40        & 0.475    & 0.475     & 0.197    & 0.475    & 0.011     & 0.496    \\
-AGZ0007z48  & 10017     & GOODS-N-FULLDEPTH &          &            & 3        & 40        & 0.675    & 0.675     & 0.048    & 0.675    & 0.168     & 0.669    \\
-$\ldots$    & $\ldots$  & $\ldots$          & $\ldots$ & $\ldots$   & $\ldots$ &  $\ldots$ & $\ldots$ & $\ldots$  & $\ldots$ & $\ldots$ & $\ldots$  & $\ldots$ \\
-AGZ00083jb  & 8869      & GOODS-S-FULLDEPTH &          &            & 1        & 40        & 0.425    & 0.425     & 0.109    & 0.425    & 0.070     & 0.548    \\
-AGZ00083jc  & 8878      & GOODS-S-FULLDEPTH &          &            & 0        & 40        & 0.205    & 0.205     & 0.048    & 0.048    & $-$0.005  & 0.287    \\
+AHZ100002g  & 10010842  & AEGIS             & 0        & 127       & 0.118    & 0.128     & 0.085    & 0.085    & 0.226     & 0.226    \\
+AHZ100002h  & 10010870  & AEGIS             & 4        & 127       & 0.567    & 0.592     & 0.927    & 0.592    & $-$       & $-$      \\
+$\ldots$    \\
+AHZ20004kd  & 20014731  & COSMOS            & 3        &  44       & 0.682    & 0.675     & 0.147    & 0.675    & $-$       & $-$      \\
+AHZ20004ke  & 20014732  & COSMOS            & 2        &  45       & 0.689    & 0.756     & 0.893    & 0.756    & $-$       & $-$      \\
+$\ldots$    \\
+AHZ400043g  & 90022729  & GEMS              & 1        & 121       & 0.702    & 0.733     & 0.487    & 0.734    & 0.483     & 0.800    \\
+AHZ4000416  & 90022735  & GEMS              & 1        & 127       & 0.646    & 0.698     & 0.508    & 0.698    & 0.171     & 0.727    \\
+$\ldots$    \\
+AGZ0007z47  & 10014     & GOODS-N-FULLDEPTH & 1        & 40        & 0.475    & 0.475     & 0.197    & 0.475    & 0.011     & 0.496    \\
+AGZ0007z48  & 10017     & GOODS-N-FULLDEPTH & 3        & 40        & 0.675    & 0.675     & 0.048    & 0.675    & 0.168     & 0.669    \\
+$\ldots$    \\
+AGZ00083jb  & 8869      & GOODS-S-FULLDEPTH & 1        & 40        & 0.425    & 0.425     & 0.109    & 0.425    & 0.070     & 0.548    \\
+AGZ00083jc  & 8878      & GOODS-S-FULLDEPTH & 0        & 40        & 0.205    & 0.205     & 0.048    & 0.048    & $-$0.005  & 0.287    \\
+$\ldots$    \\
 \enddata
@@
 \tabletypesize{\scriptsize}
-\begin{deluxetable}{lllllcrllll|c}
+\begin{deluxetable}{lllcrllllll|c}
 \centering
@@
 \tablewidth{0pc}
-\tablecaption{GZH morphological classifications for SDSS Stripe 82 single-epoch images} 
-\label{tbl:stripe82_single}
+\tablecaption{GZH morphological classifications for color-faded Hubble images\label{tbl:catalog_faded}} 
 \tabletypesize{\scriptsize}
 \tablehead{
- & & & RA & dec  &  
+ & & & 
+\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
+\multicolumn{6}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
+\colhead{$\ldots$}
+\\
+\colhead{Project ID} & 
+\colhead{Hubble ID} & 
+\colhead{Imaging} & 
+\colhead{Correction} & 
+\colhead{$N_\mathrm{votes}$} & 
+\colhead{fraction} & 
+\colhead{weighted} & 
+\colhead{debiased} & 
+\colhead{best} &
+\colhead{lower~limit} & 
+\colhead{upper~limit} &
+\colhead{}
+}
+\small
+\startdata
+AHZF000001  &   20000002    &   COSMOS  &   1   &   48 &  0.708   &     0.755   &   0.228    &    0.754 &   0.325   &   0.829  \\
+AHZF000003  &   20000004    &   COSMOS  &   3   &   49 &  0.367   &     0.379   &   0.100    &    0.379 &   0.198   &   0.198  \\
+AHZF000004  &   20000006    &   COSMOS  &   3   &   49 &  0.265   &     0.271   &   0.010    &    0.270 &   $-$	    &   $-$    \\
+AHZF00000z  &   20000102    &   COSMOS  &   1   &   44 &  0.727   &     0.78    &   0.233    &    0.780 &   0.316   &   0.820  \\
+AHZF000010  &   20000104    &   COSMOS  &   2   &   53 &  0.811   &     0.849   &   0.904    &    0.848 &   $-$	    &   $-$    \\
+$\ldots$    \\
+\enddata
+\tablecomments{The full version of this table is available in electronic form, as well as at \url{http://data.galaxyzoo.org}.
+The complete version includes data for 3,927~galaxies and morphological information for all tasks in the tree.
+A subset of the information is shown here to illustrate form and content.}
+\end{deluxetable}
+
+\tabletypesize{\scriptsize}
+\begin{deluxetable}{lllcrllllll|c}
+\centering
+\rotate
+\tablecolumns{13}
+\tablewidth{0pc}
+\tablecaption{GZH morphological classifications for color-inverted Hubble images\label{tbl:catalog_recoloured}} 
+\tabletypesize{\scriptsize}
+\tablehead{
+ & & & 
+\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
+\multicolumn{6}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
+\colhead{$\ldots$}
+\\
+\colhead{Project ID} & 
+\colhead{Hubble ID} & 
+\colhead{Imaging} & 
+\colhead{Correction} & 
+\colhead{$N_\mathrm{votes}$} & 
+\colhead{fraction} & 
+\colhead{weighted} & 
+\colhead{debiased} & 
+\colhead{best} &
+\colhead{lower~limit} & 
+\colhead{upper~limit} &
+\colhead{}
+}
+\small
+\startdata
+AHZC000001	&   20000002	&   COSMOS	&   1	&   168	&   0.615   &   0.664   &   0.160   &  0.663   &  0.271    &  0.775    \\
+AHZC000003	&   20000004	&   COSMOS	&   0	&   235	&   0.333   &   0.364   &   0.002   &  0.002   &  0.063    &  0.063    \\
+AHZC000004	&   20000006	&   COSMOS	&   3	&   316	&   0.235   &   0.252   & $-0.011$  &  0.252   &  $-$	    &  $-$      \\
+AHZC00000z	&   20000102	&   COSMOS	&   1	&   207	&   0.755   &   0.757   &   0.272   &  0.756   &  0.249    &  0.796    \\
+AHZC000010	&   20000104	&   COSMOS	&   2	&   158	&   0.843   &   0.882   &   0.936   &  0.881   &  $-$	    &  $-$      \\
+$\ldots$    \\
+\enddata
+\tablecomments{The full version of this table is available in electronic form, as well as at \url{http://data.galaxyzoo.org}.
+The complete version includes data for 3,927~galaxies and morphological information for all tasks in the tree.
+A subset of the information is shown here to illustrate form and content.}
+\end{deluxetable}
+
+\tabletypesize{\scriptsize}
+\begin{deluxetable}{lllcrllllll|c}
+\centering
+\rotate
+\tablecolumns{13}
+\tablewidth{0pc}
+\tablecaption{GZH morphological classifications for GOODS 2-epoch images\label{tbl:catalog_goods_shallow}} 
+\tabletypesize{\scriptsize}
+\tablehead{
+ & & &  
+\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
+\multicolumn{6}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
+\colhead{$\ldots$}
+\\
+\colhead{Project ID} & 
+\colhead{Hubble ID} & 
+\colhead{Imaging} & 
+\colhead{Correction} & 
+\colhead{$N_\mathrm{votes}$} & 
+\colhead{fraction} & 
+\colhead{weighted} & 
+\colhead{debiased} & 
+\colhead{best} &
+\colhead{lower~limit} & 
+\colhead{upper~limit} &
+\colhead{}
+}
+\small
+\startdata
+AHZ3000001  &   50000000    &     GOODS-N   &   0   &   123	&   0.390   &   0.415	&   0.090 &   0.090 &   $-$     &   $-$      \\
+AHZ3000002  &   50000001    &     GOODS-N   &   2   &   126	&   0.341	&   0.355	&   0.356 &   0.356 &   0.220	&   0.279    \\
+AHZ3000003  &   50000005    &     GOODS-N   &   1   &   129	&   0.760   &   0.826	&   0.633 &   0.825 &   0.596	&   0.834    \\
+AHZ3000004  &   50000008    &     GOODS-N   &   1   &   120	&   0.758	&   0.787	&   0.639 &   0.787 &   0.658	&   0.834    \\
+AHZ3000005  &   50000010    &     GOODS-N   &   1   &   123	&   0.854	&   0.890   &   0.611 &   0.889 &   0.597	&   0.914    \\
+$\ldots$    \\
+\enddata
+\tablecomments{The full version of this table is available in electronic form, as well as at \url{http://data.galaxyzoo.org}.
+The complete version includes data for 6,144~galaxies and morphological information for all tasks in the tree.
+A subset of the information is shown here to illustrate form and content.}
+\end{deluxetable}
+
+\tabletypesize{\scriptsize}
+\begin{deluxetable}{lllcrllll|c}
+\centering
+\rotate
+\tablecolumns{13}
+\tablewidth{0pc}
+\tablecaption{GZH morphological classifications for SDSS Stripe 82 single-epoch images\label{tbl:stripe82_single}} 
+\tabletypesize{\scriptsize}
+\tablehead{
+ & & & 
 \multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
@@
 \colhead{Project ID} & 
-\colhead{Hubble ID} & 
+\colhead{SDSS DR7 ObjID} & 
 \colhead{Imaging} & 
-\colhead{J2000} & 
-\colhead{J2000} & 
-\colhead{Correction$^{1}$} & 
+\colhead{Correction} & 
 \colhead{$N_\mathrm{votes}$} & 
@@
 \startdata
-AHZ5000001  &   587730845812064684  &   SDSS    &   &   &     2 &   41  &   0.585   &    0.595  &   0.759   &   0.594   \\
-AHZ5000002  &   587730845812065247  &   SDSS    &   &   &     2 &   46  &   0.609   &    0.651  &   0.897   &   0.651   \\
-AHZ5000003  &   587730845812196092  &   SDSS    &   &   &     2 &   51  &   0.039   &    0.044  &   0.067   &   0.043   \\
-AHZ5000004  &   587730845812196825  &   SDSS    &   &   &     2 &   35  &   0.514   &    0.605  &   0.928   &   0.605   \\
-AHZ5000005  &   587730845812524122  &   SDSS    &   &   &     2 &   47  &   0.766   &    0.812  &   1.038   &   0.810   \\
-AHZ5000006  &   587730845812654984  &   SDSS    &   &   &     2 &   42  &   0.5	    &    0.542  &   0.680   &   0.541   \\
-AHZ5000007  &   587730845812655541  &   SDSS    &   &   &     2 &   41  &   0.488   &    0.526  &   0.697   &   0.525   \\
-AHZ5000008  &   587730845812720365  &   SDSS    &   &   &     2 &   53  &   0.792   &    0.84   &   1.050   &   0.839   \\
-AHZ5000009  &   587730845812720640  &   SDSS    &   &   &     4 &   43  &   0.0	    &    0.0    &   0.0	    &   0.0	    \\
-AHZ500000a  &   587730845812720699  &   SDSS    &   &   &     2 &   40  &   0.425   &    0.478  &   0.588   &   0.477   \\
-$\ldots$    & $\ldots$  & $\ldots$  & $\ldots$  & $\ldots$   & $\ldots$ &  $\ldots$ & $\ldots$ & $\ldots$ \\
+AHZ5000001  &   587730845812064684  &   SDSS    &     2 &   41  &   0.585   &    0.595  &   0.759   &   0.594   \\
+AHZ5000002  &   587730845812065247  &   SDSS    &     2 &   46  &   0.609   &    0.651  &   0.897   &   0.651   \\
+AHZ5000003  &   587730845812196092  &   SDSS    &     2 &   51  &   0.039   &    0.044  &   0.067   &   0.043   \\
+AHZ5000004  &   587730845812196825  &   SDSS    &     2 &   35  &   0.514   &    0.605  &   0.928   &   0.605   \\
+AHZ5000005  &   587730845812524122  &   SDSS    &     2 &   47  &   0.766   &    0.812  &   1.038   &   0.810   \\
+AHZ5000006  &   587730845812654984  &   SDSS    &     2 &   42  &   0.5	    &    0.542  &   0.680   &   0.541   \\
+AHZ5000007  &   587730845812655541  &   SDSS    &     2 &   41  &   0.488   &    0.526  &   0.697   &   0.525   \\
+AHZ5000008  &   587730845812720365  &   SDSS    &     2 &   53  &   0.792   &    0.84   &   1.050   &   0.839   \\
+AHZ5000009  &   587730845812720640  &   SDSS    &     4 &   43  &   0.0	    &    0.0    &   0.0	    &   0.0	    \\
+AHZ500000a  &   587730845812720699  &   SDSS    &     2 &   40  &   0.425   &    0.478  &   0.588   &   0.477   \\
+$\ldots$    \\
 \enddata
-\tablenotetext{1}{Flag indicating how the vote fractions for this galaxy were corrected through debiasing (\S\ref{ssec:zeta_results}), if possible.
-0~=~correctable, 1~=~uncorrectable ($p_{raw}$ --- $p_{adj}$ is not single-valued), 2~=~uncorrected ($z_{\rm gal} < 0.3$), 3~=~uncorrectable (insufficient FERENGI galaxies in this $z$-$\mu$ bin), 4~=~uncorrectable (no galaxy redshift available).}
 \tablecomments{The full version of this table is available in electronic form, as well as at \url{http://data.galaxyzoo.org}.
@@
 \tabletypesize{\scriptsize}
-\begin{deluxetable}{lllllcrllll|c}
+\begin{deluxetable}{lllcrllll|c}
 \centering
@@
 \tablewidth{0pc}
-\tablecaption{GZH morphological classifications for SDSS Stripe 82 coadded images} 
-\label{tbl:stripe82_coadd}
+\tablecaption{GZH morphological classifications for SDSS Stripe 82 coadded images\label{tbl:stripe82_coadd}} 
 \tabletypesize{\scriptsize}
 \tablehead{
- & & & RA & dec  &  
+ & & & 
 \multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
@@
 \startdata
-AHZ6000001  & 8647474690312306978   &   SDSS    &   &   &    4  & 40  & 0.275   &    0.289  &   0.762   &   0.289   & \\
-AHZ6000002  & 8647474690312307154   &   SDSS    &   &   &    2  & 43  & 0.605   &    0.634  &   0.858   &   0.635   & \\
-AHZ6000003  & 8647474690312307877   &   SDSS    &   &   &    2  & 51  & 0.608   &    0.627  &   0.906   &   0.627   & \\
-AHZ6000004  & 8647474690312308301   &   SDSS    &   &   &    4  & 52  & 0.038   &    0.038  &   0.723   &   0.038   & \\
-AHZ6000005  & 8647474690312308318   &   SDSS    &   &   &    2  & 44  & 0.614   &    0.632  &   0.776   &   0.631   & \\
-AHZ6000006  & 8647474690312308880   &   SDSS    &   &   &    2  & 36  & 0.667   &    0.683  &   0.901   &   0.683   & \\
-AHZ6000007  & 8647474690312372644   &   SDSS    &   &   &    4  & 48  & 0.646   &    0.674  &   1.145   &   0.674   & \\
-AHZ6000008  & 8647474690312372789   &   SDSS    &   &   &    4  & 45  & 0.489   &    0.571  &   0.964   &   0.570   & \\
-AHZ6000009  & 8647474690312372931   &   SDSS    &   &   &    4  & 47  & 0.553   &    0.587  &   0.926   &   0.587   & \\
-AHZ600000a  & 8647474690312373190   &   SDSS    &   &   &    4  & 47  & 0.574   &    0.559  &   1.008   &   0.559   & \\
-$\ldots$    & $\ldots$  & $\ldots$  & $\ldots$  & $\ldots$   & $\ldots$ &  $\ldots$ & $\ldots$ & $\ldots$ \\
+AHZ6000001  & 8647474690312306978   &   SDSS    &    4  & 40  & 0.275   &    0.289  &   0.762   &   0.289   & \\
+AHZ6000002  & 8647474690312307154   &   SDSS    &    2  & 43  & 0.605   &    0.634  &   0.858   &   0.635   & \\
+AHZ6000003  & 8647474690312307877   &   SDSS    &    2  & 51  & 0.608   &    0.627  &   0.906   &   0.627   & \\
+AHZ6000004  & 8647474690312308301   &   SDSS    &    4  & 52  & 0.038   &    0.038  &   0.723   &   0.038   & \\
+AHZ6000005  & 8647474690312308318   &   SDSS    &    2  & 44  & 0.614   &    0.632  &   0.776   &   0.631   & \\
+AHZ6000006  & 8647474690312308880   &   SDSS    &    2  & 36  & 0.667   &    0.683  &   0.901   &   0.683   & \\
+AHZ6000007  & 8647474690312372644   &   SDSS    &    4  & 48  & 0.646   &    0.674  &   1.145   &   0.674   & \\
+AHZ6000008  & 8647474690312372789   &   SDSS    &    4  & 45  & 0.489   &    0.571  &   0.964   &   0.570   & \\
+AHZ6000009  & 8647474690312372931   &   SDSS    &    4  & 47  & 0.553   &    0.587  &   0.926   &   0.587   & \\
+AHZ600000a  & 8647474690312373190   &   SDSS    &    4  & 47  & 0.574   &    0.559  &   1.008   &   0.559   & \\
+$\ldots$    \\
 \enddata
-\tablenotetext{1}{Flag indicating how the vote fractions for this galaxy were corrected through debiasing (\S\ref{ssec:zeta_results}), if possible.
-0~=~correctable, 1~=~uncorrectable ($p_{raw}$ --- $p_{adj}$ is not single-valued), 2~=~uncorrected ($z_{\rm gal} < 0.3$), 3~=~uncorrectable (insufficient FERENGI galaxies in this $z$-$\mu$ bin), 4~=~uncorrectable (no galaxy redshift available).}
 \tablecomments{The full version of this table is available in electronic form, as well as at \url{http://data.galaxyzoo.org}.
@@
 
+\tabletypesize{\scriptsize}
+\begin{deluxetable}{lllccccrrrrrrr|c}
+\centering
+\rotate
+\tablecolumns{14}
+\tablewidth{0pc}
+\tablecaption{GZH morphological classifications for HST images with simulated AGN\label{tbl:fake_agn}} 
+\tabletypesize{\scriptsize}
+\tablehead{
+ & & & & & & & &
+\multicolumn{6}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
+\colhead{$\ldots$}
+\\
+\colhead{Project ID} & 
+\colhead{SDSS DR7 ObjID} & 
+\colhead{Imaging} & 
+\colhead{Correction} & 
+\colhead{Version} & 
+\colhead{$L_\mathrm{ratio}$} & 
+\colhead{AGN color$^{1}$} & 
+\colhead{$N_\mathrm{votes}$} & 
+\colhead{fraction} & 
+\colhead{weighted} & 
+\colhead{debiased} & 
+\colhead{best} &
+\colhead{lower limit} &
+\colhead{upper limit} &
+\colhead{}
+}
+\small
+\startdata
+AHZ7000001  &   90024700  &   GEMS    &   1   &   1   &   0.2	    &   1   &   42	&   0.238   &   0.239   &   $-$0.110  &       0.238  &  $-$0.113    &     0.287  \\
+AHZ7000002  &   90024700  &   GEMS    &   1   &   1   &   1.0	    &   1   &   51	&   0.255   &   0.265   &   $-$0.107  &       0.264  &  $-$0.128    &     0.272  \\
+AHZ7000003  &   90024700  &   GEMS    &   0   &   1   &   5.0	    &   1   &   47	&   0.170   &   0.167   &   $-$0.018  &    $-$0.018  &  $-$0.049    &     0.033  \\
+AHZ7000004  &   90024700  &   GEMS    &   0   &   1   &   10.0    &   1   &   41	&   0.195   &   0.195   &      0.045  &       0.045  &     0.044    &     0.127  \\
+AHZ7000005  &   90024700  &   GEMS    &   0   &   1   &   50.0    &   1   &   47	&   0.170   &   0.178   &      0.067  &       0.067  &     0.146    &     0.167  \\
+$\ldots$    \\
+AHZ700013m  &   90024700  &   GEMS    &   0   &   2   &   0.0	    &   0   &   35	&   0.171   &   0.136   &      0.011  &       0.011  &     0.029    &      0.112 \\
+AHZ700013n  &   90024700  &   GEMS    &   1   &   2   &   0.2	    &   1   &   20	&   0.150   &   0.158   &   $-$0.278  &       0.049  &  $-$0.351    &      0.049 \\
+AHZ700013o  &   90024700  &   GEMS    &   1   &   2   &   1.0	    &   1   &   32	&   0.281   &   0.300   &   $-$0.086  &       0.281  &  $-$0.119    &      0.281 \\
+AHZ700013p  &   90024700  &   GEMS    &   0   &   2   &   5.0	    &   1   &   29	&   0.103   &   0.115   &   $-$0.098  &    $-$0.098  &  $-$0.152    &   $-$0.069 \\
+AHZ700013q  &   90024700  &   GEMS    &   0   &   2   &   10.0    &   1   &   35	&   0.171   &   0.181   &      0.027  &       0.027  &     0.023    &      0.106 \\
+AHZ700013r  &   90024700  &   GEMS    &   0   &   2   &   50.0    &   1   &   34	&   0.206   &   0.206   &   $-$0.005  &    $-$0.005  &  $-$0.056    &      0.026 \\
+$\ldots$    \\
+\enddata
+\tablenotetext{1}{Flag indicating the color of the PSF in the simulated AGN. 0~=~no simulated AGN, 1~=~blue, 2~=~flat, 3~=~red.}
+\tablecomments{The full version of this table is available in electronic form, as well as at \url{http://data.galaxyzoo.org}.
+The complete version includes data for 2,961~galaxies and morphological information for all tasks in the tree.
+A subset of the information is shown here to illustrate form and content.}
+\end{deluxetable}
+
 To include: detailed description of each column in the machine-readable tables.
@@
 Include cookbook for selecting morphologies.
-\section{Analysis}
+
+\section{Analysis}\label{sec:analysis}
 
@@
 
-\section{Summary}
+\section{Summary}\label{sec:summary}
 
@@
 \begin{table}
-\caption{Breakdown of what we can correct out of the GOODS shallow depth data. \label{goods_shallow_categories}}
+\caption{Breakdown of what we can correct out of the GOODS shallow depth data. \label{tbl:goods_shallow_categories}}
 \begin{tabular}{lrrrrrrrr}
@@
 
-\subsection{Comparing shallow and full depth morphologies}.
+\subsection{Comparing shallow and full depth morphologies}
+
 Of the 11,157 galaxies in the GOODS-N and GOODS-S full depth sample, 4,461 of these are in the shallow-depth sample.
 In Figure~\ref{fig:shallow_vs_full} we find a strong correlation between $\rm p_{features}$ for both sets of images.
-The mean change in $\rm p_{features}$ from the shallow to full depth images  $\rm p_{features,full} - p_{features,shallow} = \Delta p = 0.00$, with a standard deviation of $\sigma = 0.17$.
+The mean change in $\rm p_{features}$ from the shallow to full depth images  $\rm p_{features,full} - p_{features,shallow} \equiv \Delta p = 0.00$, with a standard deviation of $\sigma = 0.17$.
 While there is some variance in $\Delta p$ in the whole sample, the change is usually small and not often significant enough to change a morphological classification.
@@
 Of the remaining 25\% that would change morphology, only 0.3\% (representing 10 galaxies total) drastically change morphology from smooth to featured or visa versa, while the rest would transition to or from the ``intermediate'' morphology.
-Details can be seen in Table~\ref{shallow_to_full_stats} and examples of images representing the 9 possible changes (or lack of) in morphology are shown in Figures~\ref{fig:shallow_smooth},\ref{fig:shallow_intermediate}, and \ref{fig:shallow_featured}.
+Details can be seen in Table~\ref{tbl:shallow_to_full_stats} and examples of images representing the 9 possible changes (or lack of) in morphology are shown in Figures~\ref{fig:shallow_smooth},\ref{fig:shallow_intermediate}, and \ref{fig:shallow_featured}.
 
@@
 Featured here is defined as $p_{features,best}>0.8$, intermediate = $0.2<p_{features,best}<0.8$, smooth = $p_{smooth,best}<0.2$.
-\label{shallow_to_full_stats}}
+\label{tbl:shallow_to_full_stats}}
 \begin{tabular}{lrrrrrrrr}
@@
 Only 17\% (maximum) of FERENGI galaxies in the sample were considered ``correctable'', which is not sufficient to compute a $\zeta$ function applicable to the Hubble data.
-\label{ferengi_bar_corrections}}
+\label{tbl:ferengi_bar_corrections}}
 \begin{tabular}{lrr}

### 2016-03-23 movie/papermovie.sh
Script and paths to make the paper movie.

@@ -1,0 +1,71 @@
+# !#/bin/bash
+#
+# Example:
+# > ./papermovie.sh writeup/gz_hubble_data.pdf
+
+# Inspiration: https://github.com/brownsys/paper-movies
+
+# Issues:
+#   Had to install ImageMagick (several times) with homebrew
+#   Fixed font list via http://stackoverflow.com/questions/24696433/why-font-list-is-empty-for-imagemagick
+#   Original codec (libx264) did not work on current version of ffmpeg
+
+filename=$1
+
+# Set the remote and/or branches for the git repository
+remote=origin
+branch=master
+
+# Make sure the branch is currently up to date
+git pull $remote $branch
+git checkout $branch
+
+# Find only the commits that changed this particular file
+git log -- $filename  | grep "^commit" | awk '{print $2}' > commits.txt
+
+# Download the versioned PDFs by resetting to specific commits
+rev=0
+while read p; do
+    echo "Commit $p"
+    git reset --hard $p
+    if [ -f $filename ];
+    then
+        revpad=`printf "%03d" $rev`
+        cp $filename $revpad.pdf
+        
+        # Use ImageMagick to turn the paginated PDF into a single image
+        montage $revpad.pdf -tile 7x3 -background white -geometry 213x275-15+4 frames/$revpad.png
+
+        let rev+=1
+    fi
+done < commits.txt
+
+# Modify images in ImageMagick again to make them suitable for movie frames
+# Reverse sort in this loop so that the paper goes in chronological order
+rev=0
+for f in `ls -1 frames/*.png | grep -v "movie\-1.png" | sort -nr`; do
+    n=`printf "%03d" $rev`
+    # Rename frames for ffmpeg's format style
+    convert $f -crop 1280x850+0+0 $n.png
+    let rev+=1
+done
+
+# Pick the final filename
+arr=$(echo $filename | tr ";" "\n")
+IFS='/' read -a fnameonly <<< "$filename"
+x=${fnameonly[${#fnameonly[@]}-1]}
+IFS='.' read -a stub <<< "$x"
+
+# Create the movie
+ffmpeg -r 5 -i %03d.png -vcodec mpeg4 -pix_fmt yuv420p -b:v 8000k $stub.mov
+
+# Clean up extra files in the folder
+rm -f commits.txt
+rm -f *.pdf
+rm -f *.png
+rm -f frames/*.png
+rmdir frames/
+
+# Checkout the most recent version again
+git pull $remote $branch
+git checkout $branch

### 2016-03-23 writeup/gz_hubble_data.tex
First draft of text for intro

@@
 \usepackage{natbib}
+\usepackage{amsmath,amssymb}
 \usepackage{graphicx}
@@
 \author[Lead Author \etal]{Lead Author and other Galaxy Zoo science team members\\
+%
+% List of people who have contributed (not sure if everyone will be author)
+% Definitely: Lintott, Bamford, Edmondson, Masters, Simmons, Melvin, Willett, Galloway, Fortson, Schawinski
+% Others on GZ science team: Urry, Cardamone, Nichol, Kaviraj, Keel, Skibba, Thomas, Scarlata, Beck, Smethurst
+% Tech: Smith, Parrish, Simpson, other devs?
+% External: Han, Griffith
+%
 %$^1$Institute for Cosmology and Gravitation, University of Portsmouth, Dennis Sciama Building, Burnaby Road, Portsmouth, PO1 3FX, UK \\
@@
 %$^2$Institute for Sciences of the Cosmos (ICCUB), University of Barcelona, Marti i Franques 1, Barcelona, 08024 Spain\\
-% $^{4}$Oxford Astrophysics, Department of Physics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK\\
-%$^{5}$Yale Center for Astronomy and Astrophysics, Yale University, P.O. Box 208121, New Haven, CT 06520, USA \\
+%$^4$Oxford Astrophysics, Department of Physics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK\\
+%$^5$Yale Center for Astronomy and Astrophysics, Yale University, P.O. Box 208121, New Haven, CT 06520, USA \\
 %$^6$Steward Observatory, University of Arizona, 933 N. Cherry Ave, Tuscon, AZ 85721, USA\\
 %$^4$Astronomy Department, Adler Planetarium and Astronomy Museum, 1300 Lake Shore Drive, Chicago, IL 60605, USA\\
-% $^7$Centre for Astronomy \& Particle Theory, University of Nottingham, University Park, Nottingham, NG7 2RD, UK\\
+%$^7$Centre for Astronomy \& Particle Theory, University of Nottingham, University Park, Nottingham, NG7 2RD, UK\\
 %$^6$School of Physics and Astronomy, University of Minnesota, Minneapolis, MN 55455, USA\\
 %$^7$Department of Physics \& Astronomy, 206 Gallalee Hall, 514 University Blvd., University of Alabama, Tuscaloosa, AL 35487-0234, USA\\
-% $^8$Einstein Fellow\\ 
+%$^8$Einstein Fellow\\ 
 \\
@@
 
-\begin{enumerate}
-    \item Motivation for studying morphology of galaxies
-    \item Particular scientific questions governed by galaxies at $z\sim1$
-    \item Theoretical predictions for galaxy morphology evolution
-    \item Past imaging and morphology studies at $z\sim1$
-    \item Summary of GZ/citizen science work on galaxy morphology to date
-\end{enumerate}
-
-\section{Sample and Data} 
-\label{sec:data}
+The morphology of galaxies encodes information on the orbital parameters and assembly history of the contents, including gas, dust, stars, and the central black hole.
+The morphology is also closely related to the local environment of the galaxy, as mutual interactions such as gravitational tides, shocks in cluster environments and direct mergers can all change the shape of the galaxy's potential.
+For $M^\star$~galaxies in the local Universe, this typically manifests at the most basic level as the difference between bulge-dominated, virialized systems resembling ellipticals (early-types) and disk-dominated, rotationally-supported disks (late-types) frequently exhibiting spiral arms.
+This dichotomy has been used to explore much of the astrophysics encoding galaxy formation and evolution, and has been shown to be closely linked with other galactic properties such as stellar mass, halo mass, luminosity, black hole activity, size, and the relative ages of the stellar populations.
+
+The advent of larger telescopes in an increasing range of observing wavelengths has revealed that the distribution and properties of galaxy morphology have strongly evolved over the lifetime of the Universe.
+At redshift $z\simeq1$ (roughly 6~Gyr after the Big Bang), many galaxies are still in the process of assembling the baryonic mass required to reproduce the structures seen in the present day.
+This occurs in a variety of pathways, including accretion of baryons from large-scale galactic filaments onto halos via streaming, mergers of individual dark matter halos along with their baryons, conversion of gas into stars via gravitational collapse and star formation, etc.
+The process can also be slowed or even reversed via feedback from stellar winds, supernovae, and active black holes.
+Each of these processes affects on the galaxy morphology, and so an accurate measurement of the demographics as a function of redshift provides an extremely powerful observational constraint on the physics taking place \citep[for a recent review see][]{con14}.
+
+Theoretical predictions for the morphology of galaxies as a function of redshift are primarily computed within the $\Lambda$CDM cosmological framework.
+Full treatments of this model gravitational interactions between baryons and dark matter, hydrodynamics of the gas, and baryonic physics related to star formation and evolution.
+The most advanced simulations now include volumes up to $\sim100$~Mpc$^3$ while simultaneously resolving the smaller scales necessary to reproduce the baryonic physics \citep{vog14a,sch15}.
+Such simulations predict clustering of galaxies on large scales in a hierarchical assembly model \citep{sil12}.
+The structure of individual galaxies is affected by the merger history \citep{too72,hop10}, local environment \citep[such as the morphology-density relation;][]{dre80}, initial dark halo mass, and many other factors.
+Morphologies of individial simulated high-mass galaxies at $z\sim2-3$ commonly show kpc-scale ``clumpy'' structures and few galaxies that are either smooth or well-ordered spirals; asymmetric profiles with strong density constrasts dominate down to at least $z\gtrsim$ \citep{gen14}.
+
+Observational studies of galaxies at high-redshift also display a wide range of morphological types, many of which are rare or absent at $z\sim0$.
+These include spheroids and disks (akin to the ellipticals/spirals seen in the local Universe), but also a significant population of massive, more irregular galaxies, including mergers, tadpoles, chains, double-clumps, and clump-clusters \citep{elm05,elm07,cam11a,for11a,kar15}.
+In contrast, while grand-design spirals have been observed as far back as $z=2.18$ \citep{law12}, their spatial density suggests that they are exceedingly rare, with a very low overall disk fraction \citep{mor13}.
+Current observational data thus strongly suggests that the classical Hubble sequence/tuning fork \citep{hub36} is not a suitable framework for characterizing high-redshift morphology.
+
+Space-based observatories, particularly the \textit{Hubble Space Telescope}, have been responsible for the bulk of imaging studies of high-redshift galaxies.
+Observations of fixed fields with very deep imaging \citep[eg,][]{gia04,dav07,gro11,sco07,bec06,wil96} give the photometric sensitivity necessary to detect $L^\star$ galaxies at $z>1$, while also providing the angular resolution to distinguish internal structure and characterize the morphology.
+While these measurements are helped by the fact that the angular diameter distance is relatively flat at $z>1$ in a flat $\Lambda$CDM cosmology, the scales are only of the order $\sim5-10~\mathrm{kpc}/^{\prime\prime}$ \citep{wri06}.
+\textit{HST} can thus resolve much of the structure for a Milky Way-sized galaxy (at least for distinguishing a disk from a bulge), but will be limited for more compact structures.
+Since the size of galaxies evolves as roughly $r\propto(1+z)^{-1}$ \citep{law12a}, the more compact sizes of earlier galaxies make detailed morphologies a challenge even for \textit{HST} \citet{che12}.
+The public availability of more than $10^5$~galaxies in archival imaging across various studies gives a data sample with the potential for high statistical significance.
+
+One of the major difficulties in studying the morphologies of galaxies in large samples lies in the system of measurement.
+Visual classification by experts has been used for many years \citep[eg,][]{hub26,dev59,san61,van76,nai10,bai11,kar15}.
+These methods have advantages in using the significant processing power of the human brain to identify patterns, but suffer from issues such as lack of scaling to large surveys and potential issues with replicability and calibration.
+Automated measurements, both parametric \citep{pen02a,sim11,lac12} and non-parametric \citep{con03,lot04,sca07,fre13}, scale well to arbitrary sample sizes, but do not always fully capture the relevant features, especially for asymmetric galaxies that become increasingly common at high redshifts.
+The Galaxy Zoo project \citep{lin08,lin11} utilizes crowdsourced visual classifications to measure galaxies in color-composite images.
+With $>2\times10^5$~classifiers, this allows for multiple independent classifications of each image which are combined and calibrated to give a distribution of vote fractions proportional to the probability of a feature being visible.
+While the crowdsourced data require extensive calibration \citep{bam09,wil13}, they have a proven reliability and have been used in dozens of papers \citep[eg,][]{lan08,bam09,dar10,mas11c,ski12,sim13,sch14,wil15}.
+
+This paper presents the results from the Galaxy Zoo Hubble (GZH) project.
+GZH was the third phase of Galaxy Zoo, following its initial results classifying $\sim900,000$~SDSS~images into primarily early/late~types \citep{lin11} and Galaxy~Zoo~2, which covered $\sim250,000$~SDSS~images using a more detailed classification scheme that included bars, spiral arms, and galactic bulges \citep{wil13}.
+GZH used a similarly detailed classification scheme, but focused for the first time on images of high-redshift galaxies taken with the \textit{Hubble Space Telescope}.
+
+We describe the sample selection and creation of the images used for GZH in Section~\ref{sec:data}.
+Section~\ref{sec:interface} describes the GZH interface and the collection of classifications.
+Section~\ref{sec:debiasing} outlines the process used to calibrate and ``debias'' the crowdsourced votes.
+Section~\ref{sec:results} gives the main results as a catalog, with several examples of how the data may be queried in Section~\ref{sec:cookbook}.
+Section~\ref{sec:analysis} gives a short overview of the observed morphological demographics and compares them to several other catalogs, with a summary in Section~\ref{sec:summary}.
+
+This paper uses the WMAP9 cosmology parameters of $(\Omega_m,\Omega_\Lambda,h)=(0.258,0.718,0.697)$ \citep{hin13}.
+
+%\begin{enumerate}
+%    \item Motivation for studying morphology of galaxies
+%    \item Particular scientific questions governed by galaxies at $z\sim1$
+%    \item Theoretical predictions for galaxy morphology evolution
+%    \item Past imaging and morphology studies at $z\sim1$
+%    \item Summary of GZ/citizen science work on galaxy morphology to date
+%    \item Outline of paper
+%\end{enumerate}
+
+\section{Sample and Data}\label{sec:data}
+
+The GZH project contains images drawn from a number of different dedicated surveys and sample selection criteria, which we describe below.
+The majority of the images (as implied by the project name) are taken directly from \textit{Hubble Space Telescope} Legacy Surveys,
 
@@
 FERENGI images.
+
+\subsection{Redshifts}
+
+We compiled redshifts from a variety of sources to include in the GZH catalog.
+For each galaxy, the redshift selected is in the $\tt Z\_Best$ column of the data (see Table~\ref{tbl:catalog_hst}), its type (spectroscopic: $\tt SPEC\_Z$, photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column $\tt Z\_BEST\_TYPE$, and the source catalog ($\tt Griffith$ \citep{gri12}, $\tt 3DHST$ \citep{mom15}, $\tt MUSYC$ \citep{car10}, or $\tt UltraVISTA$ \citep{ilb13}) of the redshift is in column $\tt Z\_BEST\_SOURCE$.
+
+For galaxies which have redshifts from multiple sources, we use the following algorithm to select the $\tt Z\_BEST$ redshift.
+We first prioritize spectroscopic redshifts; these are provided in the Griffith, 3DHST, and MUSYC catalogs.
+If a high quality spec-z exists in the Griffith catalog we use that, else 3DHST, else MUSYC.
+We show in Figure~\ref{fig:speczs} that over 98\% of the the spec-z's are consistent with each other, and therefore the priority order of selection makes no negligible difference.
+If no spectroscipic redshifts are available, we compare the 1-$\sigma$ errors of the photometric (Griffith, 3DHST, MUSYC, UltraVISTA) and grism (UltraVISTA) redshifts, and use the redshift with the smallest error.
+Table~\ref{tbl:redshifts} shows the results of this selection.
+
+\begin{figure*}
+\includegraphics[width=160mm]{figures/specz_comparison.pdf}
+\caption{Spectroscopic redshifts from Griffith, 3DHST, and MUSYC catalogs.
+The number in the upper left of each plot is the percentage of redshifts which agree within $\Delta z < 0.05$ between the two catalogs being compared in each panel.
+Within this range there is over 98\% agreement in redshifts between all three catalogs.}
+\label{fig:speczs}
+\end{figure*}
 
@@
 
-\subsection{Redshifts}
-
-We compiled redshifts from a variety of sources to include in the GZH catalog.
-For each galaxy, the redshift selected is in the $\tt Z\_Best$ column of the data (see Table~\ref{tbl:catalog_hst}), its type (spectroscopic: $\tt SPEC\_Z$, photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column $\tt Z\_BEST\_TYPE$, and the source catalog ($\tt Griffith$ \citep{gri12}, $\tt 3DHST$ \citep{mom15}, $\tt MUSYC$ \citep{car10}, or $\tt UltraVISTA$ \citep{ilb13}) of the redshift is in column $\tt Z\_BEST\_SOURCE$.
-
-For galaxies which have redshifts from multiple sources, we use the following algorithm to select the $\tt Z\_BEST$ redshift.
-We first prioritize spectroscopic redshifts; these are provided in the Griffith, 3DHST, and MUSYC catalogs.
-If a high quality spec-z exists in the Griffith catalog we use that, else 3DHST, else MUSYC.
-We show in Figure~\ref{fig:speczs} that over 98\% of the the spec-z's are consistent with each other, and therefore the priority order of selection makes no negligible difference.
-If no spectroscipic redshifts are available, we compare the 1-$\sigma$ errors of the photometric (Griffith, 3DHST, MUSYC, UltraVISTA) and grism (UltraVISTA) redshifts, and use the redshift with the smallest error.
-Table~\ref{tbl:redshifts} shows the results of this selection.
-
-\begin{figure*}
-\includegraphics[width=160mm]{figures/specz_comparison.pdf}
-\caption{Spectroscopic redshifts from Griffith, 3DHST, and MUSYC catalogs.
-The number in the upper left of each plot is the percentage of redshifts which agree within $\Delta z < 0.05$ between the two catalogs being compared in each panel.
-Within this range there is over 98\% agreement in redshifts between all three catalogs.}
-\label{fig:speczs}
-\end{figure*}
-
-\subsection{User weighting}
-\label{sec:weighting}
+\subsection{User weighting}\label{ssec:weighting}
 The votes of individual users who classified galaxies in GZH are combined to make a vote fraction for each question on the classification tree.
@@
 
-\section{Galaxy Zoo interface and classifications}
-\label{sec:gz_interface}
+\section{Galaxy Zoo interface and classifications}\label{sec:interface}
 
@@
 
-\section{Correcting for redshift-dependent classification bias}
-\label{sec:debiasing}
+\section{Correcting for redshift-dependent classification bias}\label{sec:debiasing}
+
 The previous versions of Galaxy Zoo morphology classifications \citep{lin08,wil13} were based on observations of galaxies in the Sloan Digital Sky Survey (SDSS) which are typically at $z<0.1$.
@@
 
-\subsection{Correcting GZH morphologies for classification bias}
-\label{sec:zeta}
+\subsection{Correcting GZH morphologies for classification bias}\label{ssec:zeta}
 
@@
 The white grid denotes the surface brightness and redshift range of the \ferengi{} images, subdivided in bins corresponding to fixed ranges used for analysis in Figure~\ref{fig:p_vs_p}.}
-
-\label{fig:features_corrections}
+\label{fig:sb_redshift}
 \end{center}
@@
 Any data in which the polynomial fit has a slope less than this value is considered \emph{not} one-to-one, and therefore ``uncorrectable.'' These regions are highlighted in blue in figure ~\ref{fig:6a}.
-Uncolored (white) regions of the plot have sufficiently high slopes for us to consider the relationship to be single-valued; galaxies in these regions are considered ``correctable'', and only these are used in measuring the parameters for the $\zeta$ function (Section \ref{sec:zeta}).
+Uncolored (white) regions of the plot have sufficiently high slopes for us to consider the relationship to be single-valued; galaxies in these regions are considered ``correctable'', and only these are used in measuring the parameters for the $\zeta$ function (Section~\ref{ssec:zeta}).
 Only surface brightness/redshift bins with at least 5 galaxies were considered; regions with fewer than 5 galaxies we consider to have ``not enough information'' to determine the  $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$ relationship, these are colored gray in Figure~\ref{fig:6a}.
@@
 \caption{Debiased $p_{features}$ corrected to $z=0.3$ vs weighted $p_{features}$ for the correctable (left), uncorrectable (middle), and NEI (right) galaxies in the GZH sample.}
-
-\label{fig:features_corrections}
+\label{fig:debiased_corrections}
 \end{center}
@@
 \subsubsection{TODO LIST}
-We need to do: 
+We need to: 
 \begin{itemize}
@@
 
-\section{The catalog}
+\section{The catalog}\label{sec:results}
 
@@
 For each of the 55~responses in the GZH decision tree, the following classification data is provided: for each question, $\tt N_{votes}$ is the number of users to answer that question.
-For each unique answer, $\tt fraction$ is the fraction of users to select that answer ($\rm N_{answer}/N_{votes}$, and $\tt weighted$ is the weighted fraction, which takes into account user consistency (Section~\ref{sec:weighting}).
+For each unique answer, $\tt fraction$ is the fraction of users to select that answer ($\rm N_{answer}/N_{votes}$, and $\tt weighted$ is the weighted fraction, which takes into account user consistency (Section~\ref{ssec:weighting}).
 
@@
 Needs some test cases for extracting a given set of objects (eg, clump galaxies in a particular redshift range) and evaluation of the results. Possibly include suggested thresholds, \'a la GZ2.
-\section{Using the catalog}
-\label{sec:cookbook}
+
+\section{Using the catalog}\label{sec:cookbook}
 Include cookbook for selecting morphologies.
@@
 
-\subfigure{[a]\label{fig:smoothtoint}\includegraphics[width=\textwidth]{figures/smooth_to_smooth.pdf}}
-
-\subfigure{[b]\label{fig:smoothtoint}\includegraphics[width=\textwidth]{figures/smooth_to_intermediate.pdf}}
-
-\subfigure{[c]\label{fig:smoothtoint}\includegraphics[width=\textwidth]{figures/smooth_to_featured.pdf}}
+\subfigure{[a]\label{fig:smooth_to_smooth}\includegraphics[width=\textwidth]{figures/smooth_to_smooth.pdf}}
+
+\subfigure{[b]\label{fig:smooth_to_int}\includegraphics[width=\textwidth]{figures/smooth_to_intermediate.pdf}}
+
+\subfigure{[c]\label{fig:smooth_to_featured}\includegraphics[width=\textwidth]{figures/smooth_to_featured.pdf}}
 
@@
 
-\subfigure{[b]\label{fig:smoothtoint}\includegraphics[width=\textwidth]{figures/intermediate_to_smooth.pdf}}
-
-\subfigure{[b]\label{fig:smoothtoint}\includegraphics[width=\textwidth]{figures/intermediate_to_intermediate.pdf}}
-
-\subfigure{[b]\label{fig:smoothtoint}\includegraphics[width=\textwidth]{figures/intermediate_to_featured.pdf}}
+\subfigure{[b]\label{fig:int_to_smooth}\includegraphics[width=\textwidth]{figures/intermediate_to_smooth.pdf}}
+
+\subfigure{[b]\label{fig:int_to_int}\includegraphics[width=\textwidth]{figures/intermediate_to_intermediate.pdf}}
+
+\subfigure{[b]\label{fig:int_to_featured}\includegraphics[width=\textwidth]{figures/intermediate_to_featured.pdf}}
 
@@
 
-\subfigure{[b]\label{fig:smoothtoint}\includegraphics[width=\textwidth]{figures/featured_to_smooth.pdf}}
-
-\subfigure{[b]\label{fig:smoothtoint}\includegraphics[width=\textwidth]{figures/featured_to_intermediate.pdf}}
-
-\subfigure{[b]\label{fig:smoothtoint}\includegraphics[width=\textwidth]{figures/featured_to_featured.pdf}}
+\subfigure{[b]\label{fig:featured_to_smooth}\includegraphics[width=\textwidth]{figures/featured_to_smooth.pdf}}
+
+\subfigure{[b]\label{fig:featured_to_int}\includegraphics[width=\textwidth]{figures/featured_to_intermediate.pdf}}
+
+\subfigure{[b]\label{fig:featured_to_featured}\includegraphics[width=\textwidth]{figures/featured_to_featured.pdf}}
 

### 2016-03-23 writeup/gz_hubble_data.tex
Bibliography small update for Bamford, Conselice

@@
 These methods have advantages in using the significant processing power of the human brain to identify patterns, but suffer from issues such as lack of scaling to large surveys and potential issues with replicability and calibration.
-Automated measurements, both parametric \citep{pen02a,sim11,lac12} and non-parametric \citep{con03,lot04,sca07,fre13}, scale well to arbitrary sample sizes, but do not always fully capture the relevant features, especially for asymmetric galaxies that become increasingly common at high redshifts.
+Automated measurements, both parametric \citep{pen02a,sim11,lac12} and non-parametric \citep{con03,lot04,sca07,bam08,fre13}, scale well to arbitrary sample sizes, but do not always fully capture the relevant features, especially for asymmetric galaxies that become increasingly common at high redshifts.
 The Galaxy Zoo project \citep{lin08,lin11} utilizes crowdsourced visual classifications to measure galaxies in color-composite images.

### 2016-03-24 writeup/gz_hubble_data.tex
Text on image creation and galaxy selection

@@
 %\documentclass[12pt,preprint]{aastex}
-
 \documentclass[usenatbib]{mn2e}
-
-\newcommand{\s}{$_{\rm s}$}
-\newcommand{\kms}{km~s$^{-1}$}
-\newcommand{\msun}{{\it M}$_{\odot}$}
-\newcommand{\lsun}{{\it L}$_{\odot}$}
-\newcommand{\mear}{{\it M}$_{\oplus}$}
-\newcommand{\etal}{{\it et al.}}
-\newcommand{\ie}{{\it i.e.}}
-\newcommand{\eg}{{\it e.g.}}
-\newcommand{\be}{\begin{equation}}
-\newcommand{\ee}{\end{equation}}
-\newcommand{\magarc}{{\rm mag\,arcsec$^{-2}$}}
-\newcommand{\MK}{{{\rm M}_{\rm ext,K}-5\log h}}
-\newcommand{\ri}{{$r_{21}$}}
-\newcommand{\ra}{$R_A$}
-\newcommand{\vobs}{{v_{\rm obs}}}
-\newcommand{\kmsMpc}{km~s$^{-1}$ Mpc$^{-1}$}
-\newcommand{\h}{$h_{70}$}
-\newcommand{\vpec}{v_{\rm pec}}
-\newcommand{\like}{{\mathcal L}}
-\newcommand{\vs}{\vspace*{5pt}}
-\newcommand{\continued}{ (Continued)}
-
-\newcommand{\ferengi}{\textsc{ferengi}}
-\newcommand{\sextractor}{\textsc{sextractor}}
-
-% Journals
-%\newcommand{\mnras}{MNRAS}
-%\newcommand{\apj}{ApJ}
-%\newcommand{\apjl}{ApJL}
-%\newcommand{\aj}{AJ}
-%\newcommand{\pasp}{PASP}
-%\newcommand{\aaps}{A\&AS}
-%\newcommand{\aap}{A\&A}
-%\newcommand{\apjs}{ApJS}
-%\newcommand{\araa}{ARA\&A}
-\newcommand{\pbar}{p_{\rm bar}}
-\newcommand{\pfeatures}{p_{\rm features}}
-\newcommand{\fHI}{f_{\rm HI}}
-
-% Bands
-
-\newcommand{\Bband}{$B_{435W}$}
-\newcommand{\Vband}{$V_{606W}$}
-\newcommand{\iband}{$I_{775W}$}
-\newcommand{\Iband}{$I_{814W}$}
-\newcommand{\zband}{$I_{850LP}$}
 
@@
 
+\input{gzh_macros.tex}
+
 \begin{document}
@@
 % List of people who have contributed (not sure if everyone will be author)
-% Definitely: Lintott, Bamford, Edmondson, Masters, Simmons, Melvin, Willett, Galloway, Fortson, Schawinski
+% Definitely: Lintott, Bamford, Edmondson, Masters, Simmons, Melvin, Willett, Galloway, Fortson, Schawinski, Cheung
 % Others on GZ science team: Urry, Cardamone, Nichol, Kaviraj, Keel, Skibba, Thomas, Scarlata, Beck, Smethurst
@@
 
-Space-based observatories, particularly the \textit{Hubble Space Telescope}, have been responsible for the bulk of imaging studies of high-redshift galaxies.
-Observations of fixed fields with very deep imaging \citep[eg,][]{gia04,dav07,gro11,sco07,bec06,wil96} give the photometric sensitivity necessary to detect $L^\star$ galaxies at $z>1$, while also providing the angular resolution to distinguish internal structure and characterize the morphology.
+Space-based observatories, particularly the \hubble, have been responsible for the bulk of imaging studies of high-redshift galaxies.
+Observations of fixed fields with very deep imaging \citep[eg,][]{wil96,gia04,bec06,dav07,sco07,gro11} give the photometric sensitivity necessary to detect $L^\star$ galaxies at $z>1$, while also providing the angular resolution to distinguish internal structure and characterize the morphology.
 While these measurements are helped by the fact that the angular diameter distance is relatively flat at $z>1$ in a flat $\Lambda$CDM cosmology, the scales are only of the order $\sim5-10~\mathrm{kpc}/^{\prime\prime}$ \citep{wri06}.
-\textit{HST} can thus resolve much of the structure for a Milky Way-sized galaxy (at least for distinguishing a disk from a bulge), but will be limited for more compact structures.
-Since the size of galaxies evolves as roughly $r\propto(1+z)^{-1}$ \citep{law12a}, the more compact sizes of earlier galaxies make detailed morphologies a challenge even for \textit{HST} \citet{che12}.
+\hst{} can thus resolve much of the structure for a Milky Way-sized galaxy (at least for distinguishing a disk from a bulge), but will be limited for more compact structures.
+Since the size of galaxies evolves as roughly $r\propto(1+z)^{-1}$ \citep{law12a}, the more compact sizes of earlier galaxies make detailed morphologies a challenge even for \hst{} \citep{che12}.
 The public availability of more than $10^5$~galaxies in archival imaging across various studies gives a data sample with the potential for high statistical significance.
@@
 GZH was the third phase of Galaxy Zoo, following its initial results classifying $\sim900,000$~SDSS~images into primarily early/late~types \citep{lin11} and Galaxy~Zoo~2, which covered $\sim250,000$~SDSS~images using a more detailed classification scheme that included bars, spiral arms, and galactic bulges \citep{wil13}.
-GZH used a similarly detailed classification scheme, but focused for the first time on images of high-redshift galaxies taken with the \textit{Hubble Space Telescope}.
+GZH used a similarly detailed classification scheme, but focused for the first time on images of high-redshift galaxies taken with the \hubble.
 
@@
 The GZH project contains images drawn from a number of different dedicated surveys and sample selection criteria, which we describe below.
-The majority of the images (as implied by the project name) are taken directly from \textit{Hubble Space Telescope} Legacy Surveys,
-
-\subsection{Summary of HST Legacy Survey Imaging}
+The majority of the images (as implied by the project name) are taken directly from \hst{} Legacy Surveys.
+
+\begin{figure*}
+\includegraphics[width=160mm]{figures/filter_curves.pdf}
+\caption{Transmission curves of the filters used by \hst{} Advanced Camera for Surveys (ACS) in wide-field channel mode for the various surveys in Galaxy Zoo: Hubble.
+The unfilled black curves show the filters for the Suprime Camera on the \textit{Subaru} telescope which were used to create color gradients in the composite images for COSMOS.\label{fig:filtercurves}}
+\end{figure*}
+
+\subsection{Summary of Hubble Legacy Survey Imaging}\label{ssec:legacy_surveys}
 
 \begin{itemize}
-\item Hubble ACS imaging for the All-Wavelength Extended Groth Strip International Survey \citep[AEGIS;][]{dav07} covers a strip centered at $\alpha=14^\textrm{h}17^\textrm{m}, \delta=+52^\circ30^\prime$.
+\item \hubble{} ACS imaging for the All-Wavelength Extended Groth Strip International Survey \citep[AEGIS;][]{dav07} covers a strip centered at $\alpha=14^\textrm{h}17^\textrm{m}, \delta=+52^\circ30^\prime$.
 The strip was originally selected due to low extinction and Galactic/zodiacal emission, making it a prime target for multi-wavelength observations by space-based observatories.
@@
 Its location near the celestial equator was designed to enable coverage by ground-based telescopes in both the Northern and Southern Hemispheres, as well as the space-based observatories.
-The Hubble ACS data from COSMOS consists of 1 orbit with 2028~seconds per pointing in \Iband, consisting of 590 total pointings.
+The \hst{} ACS data from COSMOS consists of 1 orbit with 2028~seconds per pointing in \Iband, consisting of 590 total pointings.
 The image resolution is dithered to 0.05~\arcsec/pixel.
@@
 
+\subsection{Galaxy selection}
+
+For images from the ACS-GC \citet{gri12}, galaxies are identified using a combination of SExtractor \citep{ber96} and the galaxy-profile fitting framework \textsc{Galapagos} \citep{hau07}.
+We select all galaxies with $m < 23.5$, where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS, GEMS + GOODS-S, and GOODS-N surveys, respectively.
+
+Single-epoch images from SDSS Stripe~82 were selected using the same criteria from \citet{wil13}, which required limits of \texttt{petroR90\_r}$ > 3$\arcsec~(where \texttt{petroR90\_r} is the radius containing 90\% of the $r^\prime$ Petrosian flux) and a magnitude brighter than $m_r < 17.77$.
+Coadded images from Stripe~82 were selected from the union of galaxies with coadded magnitudes brighter than $17.77$~mag and the galaxies detected in the single-depth images and matched to a coadd source.
+Of the images in the coadded sample, 5144/30339 (17 percent) are dimmer than this initial magnitude cut.
+
 \subsection{Image creation}
 
-The GOODS images in GZH use mosaics constructed from both 2-epoch and 5-epoch sets of data.
-
-The filters that \citet{gri12} uses for the colored images were F606W and F775W for GOODS-N and F606W and F850LP for GOODS-S.
-
-We use different filters for the north and south GOODS fields so that GEMS can be directly compared with GOODS-S (Figure~\ref{fig:filtercurves}).
-
-\begin{figure*}
-\includegraphics[width=160mm]{figures/filter_curves.pdf}
-\caption{Transmission curves of the filters used by \textit{HST} Advanced Camera for Surveys (ACS) in wide-field channel mode for the various surveys in Galaxy Zoo: Hubble.
-The unfilled black curves show the filters for the Suprime Camera on the \textit{Subaru} telescope which were used to create color gradients in the composite images for COSMOS.\label{fig:filtercurves}}
-\end{figure*}
-
-Fake AGN
-
-Stripe 82
-
-Different treatment of colored noise in COSMOS; creating color gradients with Subaru data and using \Iband{} for illumination map.
-
-FERENGI images.
+The images used for classification in GZH are color-composite JPGs made from multi-band data. The exact process for creating the images depends on the bands and resolutions in the surveys.
+
+For galaxies in the ACS General Catalogue \citep[AEGIS, COSMOS, GEMS, 2-epoch GOODS;][]{gri12}, the color composites are made using a fixed pixel intensity scaling with weights of $[2.4\times10^{-4},3\times10^{-4},3\times10^{-4}]$ in the red, green, and blue channels respectively.
+We also apply a nonlinear mapping to each pixel to emphasize the contrast in faint features \citep{lup04}, taking the form of:
+
+\begin{equation}
+I_\mathrm{channel,new} = I_\mathrm{channel,old} \times \frac{\arcsinh(b\times r)}{(b\times r)}
+\label{eqn:nonlinear}
+\end{equation}
+
+\noindent We adopt a value of $b=3$ for the \hst{} images in \citet{gri12}.
+
+Since the majority of the data in Legacy surveys described in \S\ref{ssec:legacy_surveys} had images in only 1 or 2~bands available when GZH was launched, making standard 3-channel RGB images in the same method used for the SDSS images in the original Galaxy Zoo was not possible.
+For surveys with images in two bands (AEGIS, GEMS, and the two-epoch GOODS-N and GOODS-S), the lower-wavelength band is mapped to the blue channel, the higher-wavelength band to the red channel, and the green channel created by taking the geometric mean of the two.
+Bands used in each of the surveys are listed in Table~\ref{tbl:gzh_numbers}.
+Note that the 2-epoch GOODS-N and GOODS-S images use different filters --- this was a deliberate choice made so that the GEMS images could be directly compared with the overlapping coverage of GOODS-S (Figure~\ref{fig:filtercurves}).
+
+By the time that the 5-epoch sets of GOODS data were put into GZH, coverage in four separate \hst{} bands had become publicly available.
+The deeper GOODS images were created using the arithmetic mean of \Bband{} and \Vband in the blue channel, \Iband{} in the red channel, and \zband in the green channel.
+These images also had the speckled noise pixels decolorized.
+
+The COSMOS images only had the \Iband{} imaging available at the time of classification in GZH.
+For these galaxies, we created ``pseudocolor'' images by using the ACS \Iband{} data as the illumination map and ground-based imaging from the \subaru{} telescope in $B_J$, $r^+$, and $i^+$ filters to provide the color gradients \citep[see][for further details]{gri12}.
+This means that the images have the angular resolution of \hst{} ($\sim0.05$~\arcsec/pixel) for the overall intensity, but the color gradients are at ground-based resolution, with seeing between 0\arcsec.95 and 1\arcsec.05 \citep{tan07}.
+
+The Stripe~82 single-epoch images were taken directly from the color composites on the DR7 SDSS Skyserver, which combines $g^{\prime}$, $r^{\prime}$, and $i^{\prime}$ exposures into the RGB channels.
+The coadded Stripe~82 images were assembled from runs (106,206) in DR7 and generated into JPGs using the method of \citet{lup04}.
+
+To address a number of images in which the sky noise was highly colored (which might have been a distraction to users), we apply a soft-edged object mask to the image that preserves the color balance for galaxies, but desaturates the speckled noise against regions of blank sky.
+This technique was applied only to the coadded Stripe~82 and the COSMOS images.
+
+\subsection{Artificial AGN}
+
+We also created a set of images designed to measure the effect of AGN on morphological classifications.
+Since galactic nuclei can have bright, unresolved optical emission, this has the potential to mimic the effect of a strong bulge.
+The presence of an AGN is simulated by modeling the PSF for \hst{} and then inserting a bright source near the center of a real galaxy.
+For each image, the simulated AGN is assigned one of three colors -- either blue, red, or flat (white) as seen in the color images -- and a range of brightnesses such that $L_\mathrm{ratio} \equiv L_\mathrm{galaxy}/L_\mathrm{AGN}$ is in $(0.2,1.0,2.0,5.0,10.0,50.0)$.
+Combining these parameters generates 15~images with different simulated AGN for each chosen host.
+
+Two sets of simulated AGN were generated in GZH.
+The first set (version~1) was assembled from 95~galaxies from GEMS imaging and PSFs from \texttt{daophot}.
+The second set (version~2) was assembled from 96~galaxies in GOODS-S; this version used deeper imaging and improved PSFs from \texttt{TinyTim}.
+
+Images with simulated AGN were classified in the main interface in an identical manner and evenly distributed with unaltered images of the galaxies.
+Classifiers were not explicitly told that the images had been altered, as the goal was to measure the effect on normal classifications in as unbiased a manner as possible.
+
+\subsection{Artifically-redshifted images}
+
+FERENGI images (ask Edmond to write this?) Should contain much of the information in \S\ref{sec:debiasing} right now.
 
@@
 We compiled redshifts from a variety of sources to include in the GZH catalog.
-For each galaxy, the redshift selected is in the $\tt Z\_Best$ column of the data (see Table~\ref{tbl:catalog_hst}), its type (spectroscopic: $\tt SPEC\_Z$, photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column $\tt Z\_BEST\_TYPE$, and the source catalog ($\tt Griffith$ \citep{gri12}, $\tt 3DHST$ \citep{mom15}, $\tt MUSYC$ \citep{car10}, or $\tt UltraVISTA$ \citep{ilb13}) of the redshift is in column $\tt Z\_BEST\_SOURCE$.
+For each galaxy, the redshift selected is in the $\tt Z\_Best$ column of the data (see Table~\ref{tbl:catalog_hst}), its type (spectroscopic: $\tt SPEC\_Z$, photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column $\tt Z\_BEST\_TYPE$, and the source catalog ($\tt ACSGC$ \citep{gri12}, $\tt 3DHST$ \citep{mom15}, $\tt MUSYC$ \citep{car10}, or $\tt UltraVISTA$ \citep{ilb13}) of the redshift is in column $\tt Z\_BEST\_SOURCE$.
 
 For galaxies which have redshifts from multiple sources, we use the following algorithm to select the $\tt Z\_BEST$ redshift.
-We first prioritize spectroscopic redshifts; these are provided in the Griffith, 3DHST, and MUSYC catalogs.
-If a high quality spec-z exists in the Griffith catalog we use that, else 3DHST, else MUSYC.
+We first prioritize spectroscopic redshifts; these are provided in the ACS-GC, 3DHST, and MUSYC catalogs.
+If a high quality spec-z exists in the ACS-GC.
+we use that, else 3DHST, else MUSYC.
 We show in Figure~\ref{fig:speczs} that over 98\% of the the spec-z's are consistent with each other, and therefore the priority order of selection makes no negligible difference.
-If no spectroscipic redshifts are available, we compare the 1-$\sigma$ errors of the photometric (Griffith, 3DHST, MUSYC, UltraVISTA) and grism (UltraVISTA) redshifts, and use the redshift with the smallest error.
+If no spectroscipic redshifts are available, we compare the 1-$\sigma$ errors of the photometric (ACS-GC, 3DHST, MUSYC, UltraVISTA) and grism (UltraVISTA) redshifts, and use the redshift with the smallest error.
 Table~\ref{tbl:redshifts} shows the results of this selection.
@@
 \includegraphics[width=160mm]{figures/specz_comparison.pdf}
-\caption{Spectroscopic redshifts from Griffith, 3DHST, and MUSYC catalogs.
+\caption{Spectroscopic redshifts from the ACS-GC, 3DHST, and MUSYC catalogs.
 The number in the upper left of each plot is the percentage of redshifts which agree within $\Delta z < 0.05$ between the two catalogs being compared in each panel.
@@
  &   
-\multicolumn{2}{c}{\underline{Griffith}} &
+\multicolumn{2}{c}{\underline{ACS-GC}} &
 \multicolumn{3}{c}{\underline{3DHST}} &
@@
 
+\section{Galaxy Zoo interface and classifications}\label{sec:interface}
+
+\begin{figure*}
+\includegraphics[width=160mm]{figures/gzh_interface.png}
+\caption{Screenshot of the Galaxy Zoo: Hubble interface showing an example COSMOS image at the first step in the decision tree.\label{fig:interface}}
+\end{figure*}
+
 \subsection{User weighting}\label{ssec:weighting}
@@
 The majority of users have weights very close to $w=1.0$ ({\bf STEVEN: Is this true for GZH - do you have a plot of the distribution of user weights or consistencies we can include here?}.
-
-\section{Galaxy Zoo interface and classifications}\label{sec:interface}
-
-\begin{figure*}
-\includegraphics[width=160mm]{figures/gzh_interface.png}
-\caption{Screenshot of the Galaxy Zoo: Hubble interface showing an example COSMOS image at the first step in the decision tree.\label{fig:interface}}
-\end{figure*}
 
@@
 
-%-----------------------------------------------------------------------------------------------------------------------------------
-%\begin{figure}
-%\begin{center}
-%\includegraphics[width=60mm]{figures/example_ferengi2.pdf}
-%\caption{Examples of an obvious spiral and obvious elliptical at $z=0$ which both look similar when redshifted to $z=0.8$.
-See below for the description of the method for redshifting.\label{fig:exampleFERENGI}}
-%\end{center}
-%\end{figure}
- %-----------------------------------------------------------------------------------------------------------------------------------
-
 In order to test and correct for the effects of redshift, we generated a set of calibration images.
 These images consist of the same galaxy as it would appear over a variety of redshifts.
-The input images are from the SDSS \citep{yor00,str02} and are processed using the \ferengi{} code \citep{bar08a} to match the observational properties of the HST surveys out to $z=1$.
-These images were classified in the Galaxy Zoo interface using the same classification scheme as the original HST images.
+The input images are from the SDSS \citep{yor00,str02} and are processed using the \ferengi{} code \citep{bar08a} to match the observational properties of the \hst{} surveys out to $z=1$.
+These images were classified in the Galaxy Zoo interface using the same classification scheme as the original \hst{} images.
 
@@
 We selected 288 unique galaxies from SDSS imaging to run through the \ferengi{} code.
-The selection spanned a variety of galaxy morphologies (as selected by GZ2 classifications) and $r^\prime$-band surface brightnesses, and also spanned the redshift range of SDSS targets (in $N_z = 4$ bins) in order to be optimised for different target minimum redshifts in HST imaging.
+The selection spanned a variety of galaxy morphologies (as selected by GZ2 classifications) and $r^\prime$-band surface brightnesses, and also spanned the redshift range of SDSS targets (in $N_z = 4$ bins) in order to be optimised for different target minimum redshifts in \hst{} imaging.
 
@@
 \includegraphics[width=160mm]{figures/example_ferengi.pdf}
-\caption{Examples of two galaxies which have been run through the FERENGI code to produce simulated HST images.
-The value of $p_{\rm features}$ for each panel is (1) Top row: $p_{\rm features}=$ 0.9, 0.625, 0.35, 0.35, 0.225 and (2) Bottom row: $p_{\rm features}=$ 1.00, 0.875, 0.875, 0.625, 0.375.
+\caption{Examples of two galaxies which have been run through the FERENGI code to produce simulated \hst{} images.
+The value of \pfeatures{} for each panel is (1) Top row: \pfeatures~= 0.9, 0.625, 0.35, 0.35, 0.225 and (2) Bottom row: \pfeatures~= 1.00, 0.875, 0.875, 0.625, 0.375.
 \label{fig:exampleFERENGI}}
@@
 \begin{equation}
-\log_{10}(\hat\zeta) = \zeta_0 + \zeta_1 \times \mu,
+\log_{10}(\hat\zeta) = \zeta_0 + (\zeta_1 \times \mu),
 \label{eqn:zetafit}
@@
 \centering
-\subfigure{[6a]\label{fig:6a}\includegraphics[width=0.5\textwidth]{figures/p_vs_p_SB_redshift.pdf}}
-\subfigure{[6b]\label{fig:6b}\includegraphics[width=0.4\textwidth]{figures/z1_mu20_subplot1.pdf}}
-\\
-\subfigure{[6c]\label{fig:6c}\includegraphics[width=0.5\textwidth]{figures/orangebars.pdf}}
-\subfigure{[6d]\label{fig:6d}\includegraphics[width=0.4\textwidth]{figures/z1_mu20_subplot2.pdf}}
+\subfigure{[a]\label{fig:6a}\includegraphics[width=0.5\textwidth]{figures/p_vs_p_SB_redshift.pdf}}
+\subfigure{[b]\label{fig:6b}\includegraphics[width=0.4\textwidth]{figures/z1_mu20_subplot1.pdf}}
+\\
+\subfigure{[c]\label{fig:6c}\includegraphics[width=0.5\textwidth]{figures/orangebars.pdf}}
+\subfigure{[d]\label{fig:6d}\includegraphics[width=0.4\textwidth]{figures/z1_mu20_subplot2.pdf}}
 \caption{Effects of redshift bias in 3,950 images in the \ferengi{} sample.
-[6a]: Each point in a given redshift and surface brightness bin represents a unique galaxy.
-On the y-axis in each bin is the $p_{\rm features}$ value of the image of that galaxy redshifted to the value corresponding to that redshift bin.
-On the x-axis is the $p_{\rm features}$ value of the image of the same galaxy redshifted to $z=0.3$.
+[a]: Each point in a given redshift and surface brightness bin represents a unique galaxy.
+On the y-axis in each bin is the \pfeatures{} value of the image of that galaxy redshifted to the value corresponding to that redshift bin.
+On the x-axis is the \pfeatures{} value of the image of the same galaxy redshifted to $z=0.3$.
 The dashed black lines represent the best-fit polynomials to the data in each square.
-The solid black line represents $p_{\rm features,z}$ = $p_{\rm features,z=0.3}$.
-Regions in which there is a single-valued relationship between $p_{\rm features}$ at high redshift and at $z=0.3$ are white; those in which there is not are blue, and those with not enough data ($N<5$) are gray.
-[6b]: A larger version of the dark-outlined square in [6a], containing \ferengi{} galaxies that have been artificially redshifted to $z=1.0$ and have surface brightnesses between $20.3 < \mu < 21.0$ $\rm (mag/arcsec^2)$.
-[6c]: The same data as [6a] is shown.
-Each $z,\mu$ bin is divided into 4 sub-bins to determine the range of intrinsic $p_{\rm features,z=0.3}$ for a given range of observed $p_{\rm features,z}$ values.
+The solid black line represents \pfeaturesz=\pfeaturesrest.
+Regions in which there is a single-valued relationship between \pfeatures{} at high redshift and at $z=0.3$ are white; those in which there is not are blue, and those with not enough data ($N<5$) are gray.
+[b]: A larger version of the dark-outlined square in [a], containing \ferengi{} galaxies that have been artificially redshifted to $z=1.0$ and have surface brightnesses between $20.3 < \mu < 21.0$ $\rm (mag/arcsec^2)$.
+[c]: The same data as [a] is shown.
+Each $z,\mu$ bin is divided into 4 sub-bins to determine the range of intrinsic \pfeaturesrest{} for a given range of observed \pfeaturesz{} values.
 In each sub-bin, the orange bars represent the inner 80th percentiles of the data, the boundaries of which are the lower and upper limits of the debiased values.
-[6d]: The same data as [6b], but highlighting the upper and lower limit regions.}
+[d]: The same data as [b], but highlighting the upper and lower limit regions.}
 \label{fig:p_vs_p}
@@
 
-In Figure~\ref{fig:p_vs_p} we examine the change in $p_{\rm features}$ for the \ferengi{} galaxies relative to their lowest simulated redshift.
+In Figure~\ref{fig:p_vs_p} we examine the change in \pfeatures{} for the \ferengi{} galaxies relative to their lowest simulated redshift.
 In this analysis, only galaxies whose lowest simulated redshift image was ($\rm z_{sim}=0.3$) were used (see Table \ref{tbl:ferengivalues}), and only those which had detectable surface brightness measurements in \sextractor{}; this includes 3,950 of the total 6,466 images.
-For each simulated redshift value $z$, and at a fixed surface brightness $\mu$, we plot $p_{\rm features,z}$, the value measured at that simulated redshift, vs $p_{\rm features,z=0.3}$, the value measured for the same galaxy imaged at $z=0.3$.
-
-Our objective is to use these data to predict, for a galaxy with a measured $p_{\rm features,z}$ value, what its $p_{\rm features}$ value \emph{would have been} if it had been viewed at $z=0.3$.
-This predicted value is defined as the debiased vote fraction $p_{\rm features,debiased}$, and is calculated by applying a correction to the measured value of $p_{\rm features}$, determined by the $\zeta$ function described in the previous section.
-A reliable predicted value can be obtained so long as the relationship between $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$ is single-valued; that is, for a given $p_{\rm features,z}$, there is exactly one corresponding value of $p_{\rm features}$ at $z=0.3$.
-
-Figure~\ref{fig:p_vs_p} shows that the relationship between $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$ is \emph{not} always single valued; hence, it is not appropriate to correct galaxies that lie in certain regions of surface brightness/redshift/$p_{\rm features}$ space.
-These regions tend to have low $p_{\rm features}$ values at high redshift, but a wide range of values at $z=0.3$.
-These regions contain two morphological types of galaxies: First are genuine ellipticals, which have low values of $p_{\rm features}$ at both high and low redshift.
-Second are disks whose features become washed out at high redshift; hence their $p_{\rm features}$ value at $z=0.3$ may be quite high, while the value observed at high redshift is very low.
+For each simulated redshift value $z$, and at a fixed surface brightness $\mu$, we plot \pfeaturesz, the value measured at that simulated redshift, vs \pfeaturesrest, the value measured for the same galaxy imaged at $z=0.3$.
+
+Our objective is to use these data to predict, for a galaxy with a measured \pfeaturesz{} value, what its \pfeatures{} value \emph{would have been} if it had been viewed at $z=0.3$.
+This predicted value is defined as the debiased vote fraction \pfeaturesdebiased, and is calculated by applying a correction to the measured value of \pfeatures, determined by the $\zeta$ function described in the previous section.
+A reliable predicted value can be obtained so long as the relationship between \pfeaturesz{} and \pfeaturesrest{} is single-valued; that is, for a given \pfeaturesz, there is exactly one corresponding value of \pfeatures{} at $z=0.3$.
+
+Figure~\ref{fig:p_vs_p} shows that the relationship between \pfeaturesz{} and \pfeaturesrest{} is \emph{not} always single valued; hence, it is not appropriate to correct galaxies that lie in certain regions of surface brightness/redshift/\pfeatures{} space.
+These regions tend to have low \pfeatures{} values at high redshift, but a wide range of values at $z=0.3$.
+These regions contain two morphological types of galaxies: First are genuine ellipticals, which have low values of \pfeatures{} at both high and low redshift.
+Second are disks whose features become washed out at high redshift; hence their \pfeatures{} value at $z=0.3$ may be quite high, while the value observed at high redshift is very low.
 This effect is strongest at high $z$ and low $\mu$, where features become nearly impossible to discern in the images.
 
-Our criteria for determining whether a region of this space is single-valued, and therefore correctable, is as follows: In each surface brightness and redshift bin, we model the relationship between $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$ by fitting the data with a polynomials of degrees 3, 2, and 1, and use the best fit out of the three.
+Our criteria for determining whether a region of this space is single-valued, and therefore correctable, is as follows: In each surface brightness and redshift bin, we model the relationship between \pfeaturesz{} and \pfeaturesrest{} by fitting the data with a polynomials of degrees 3, 2, and 1, and use the best fit out of the three.
 These fits are shown as the dashed black lines in Figure~\ref{fig:6a}.
-Any flat regions of the polynomial fits are areas in which there is not a clear single-valued relationship between $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$; we quantify this by setting a minimum slope cut of 0.4.
-Any data in which the polynomial fit has a slope less than this value is considered \emph{not} one-to-one, and therefore ``uncorrectable.'' These regions are highlighted in blue in figure ~\ref{fig:6a}.
+Any flat regions of the polynomial fits are areas in which there is not a clear single-valued relationship between \pfeaturesz{} and \pfeaturesrest; we quantify this by setting a minimum slope cut of 0.4.
+Any data in which the polynomial fit has a slope less than this value is considered \emph{not} one-to-one, and therefore ``uncorrectable.'' These regions are highlighted in blue in Figure~\ref{fig:6a}.
 Uncolored (white) regions of the plot have sufficiently high slopes for us to consider the relationship to be single-valued; galaxies in these regions are considered ``correctable'', and only these are used in measuring the parameters for the $\zeta$ function (Section~\ref{ssec:zeta}).
-Only surface brightness/redshift bins with at least 5 galaxies were considered; regions with fewer than 5 galaxies we consider to have ``not enough information'' to determine the  $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$ relationship, these are colored gray in Figure~\ref{fig:6a}.
-
-The unshaded regions in Figure~\ref{fig:6a} define discrete ranges of redshift, surface brightness, and $\pfeatures$ a galaxy must have in order for the $\zeta$ approach to be confidentely applied to a galaxy in the GZH sample.
-While the appropriate correctable regions were defined discretely, we assume the true correctable region is a smooth function of z, $\mu$, and $\pfeatures$.
-To define this smooth space, we use a convex hull method to enclose the correctable and uncorrectable \ferengi{} galaxies is z-$\mu$-$\pfeatures$ space.
+Only surface brightness/redshift bins with at least 5 galaxies were considered; regions with fewer than 5 galaxies we consider to have ``not enough information'' to determine the \pfeaturesz{} and \pfeaturesrest{} relationship, colored gray in Figure~\ref{fig:6a}.
+
+The unshaded regions in Figure~\ref{fig:6a} define discrete ranges of redshift, surface brightness, and \pfeatures{} a galaxy must have in order for the $\zeta$ approach to be confidentely applied to a galaxy in the GZH sample.
+While the appropriate correctable regions were defined discretely, we assume the true correctable region is a smooth function of z, $\mu$, and \pfeatures{}.
+To define this smooth space, we use a convex hull method to enclose the correctable and uncorrectable \ferengi{} galaxies is z-$\mu$-\pfeatures{} space.
 Due to scatter, the boundaries of the resulting hulls overlap.
 The boundaries are then adjusted until the contamination from both groups is minimized.
-We use the resulting hulls to define the correctable and uncorrectable regions for categorizing the Hubble galaxies.
-The results of this method and final categorization of the Hubble sample is displayed in Table~\ref{tbl:hubble_debiasable}.
+We use the resulting hulls to define the correctable and uncorrectable regions for categorizing the \hst{} galaxies.
+The results of this method and final categorization of the \hst{} sample is displayed in Table~\ref{tbl:hubble_debiasable}.
 We find that of the galaxies at redshift higher than $z=z_{0}=0.3$, 17\% of these are able to be debiased using the $\zeta$ method, 27\% cannot be debiased, and 56\% cannot be determined, due to a lack of redshift or information or due to a lack of \ferengi{} data corresponding to those galaxies' redshift/surface brightness values.
 
-For the ``uncorrectable'' galaxies, those for which we cannot confidentely assign a single debiased $p_{\rm features}$ value, we instead determine a likely \emph{range} of debiased values, using a method visualized in Figure~\ref{fig:6c}.
-Here we again use the \ferengi{} simulated data to analyze the range of intrinsic $p_{\rm features,z=0.3}$ values for any given observed $p_{\rm features}$ value, again as a function of surface brightness and redshift.
-In each z,$\mu$ bin, we examine the spread of intrinsic values of $p_{\rm features,z=0.3}$ for 4 ranges of observed $p_{\rm features}$.
+For the ``uncorrectable'' galaxies, those for which we cannot confidentely assign a single debiased \pfeatures{} value, we instead determine a likely \emph{range} of debiased values, using a method visualized in Figure~\ref{fig:6c}.
+Here we again use the \ferengi{} simulated data to analyze the range of intrinsic \pfeaturesrest{} values for any given observed \pfeatures{} value, again as a function of surface brightness and redshift.
+In each z,$\mu$ bin, we examine the spread of intrinsic values of \pfeaturesrest{} for 4 ranges of observed \pfeatures.
 We quantify the range of intrinsic values as the inner 80\% of the data; this range is represented by the orange bars in Figure~\ref{fig:6c}.
-For any galaxy which can't be directly debiased by the $\zeta$ method, then, we use these ranges to denote the upper and lower limits on what we expect $p_{features,z=0.3}$ to be for any observed value of $p_{\rm features}$.
+For any galaxy which can't be directly debiased by the $\zeta$ method, then, we use these ranges to denote the upper and lower limits on what we expect \pfeaturesrest{} to be for any observed value of \pfeatures.
 
@@
 \caption{Distribution of \ferengi{} images analysed in Figure~\ref{fig:p_vs_p}.
-Correctable images had a single-valued relationship between their measured $p_{\rm features}$ values at high and low redshifts (white regions in Figure~\ref{fig:p_vs_p}).
+Correctable images had a single-valued relationship between their measured \pfeatures{} values at high and low redshifts (white regions in Figure~\ref{fig:p_vs_p}).
 Uncorrectable images had a non single-valued relationship (blue regions).
@@
 \begin{itemize}
-\item talk about where the Hubble sample falls in this space, reference Table~\ref{tbl:hubble_debiasable} 
+\item talk about where the \hst{} sample falls in this space, reference Table~\ref{tbl:hubble_debiasable} 
 \item justify $N>5$ and spread $< 0.2$ (or find a better way to choose criteria)
@@
 %We show here the preliminary results of GZH classifications of images of galaxies placed at artificial redshifts.
-Figure~\ref{fig:ferengi_results_fake} shows the range of change of vote fractions for the change of $p_{\rm features}$ with redshift, for galaxies with different vote fraction levels, three ranges of surface-brightness levels and 7~evolutionary corrections (this last bit is indicated by the colour).
+Figure~\ref{fig:ferengi_results_fake} shows the range of change of vote fractions for the change of \pfeatures{} with redshift, for galaxies with different vote fraction levels, three ranges of surface-brightness levels and 7~evolutionary corrections (this last bit is indicated by the colour).
 %
@@
 
-\subsection{Effect of changing depth for GOODS}
-
-\subsection{SDSS Stripe 82 images}
-
-\subsection{Fake AGN}
-
-We also classified a set of images designed to measure the effect of AGN on morphological classifications.
-This could occur since galactic nuclei can have bright, unresolved optical emission that could either mimic the effect of a strong bulge or otherwise obscure classification.
-The presence of an AGN is simulated by modeling the PSF for Hubble for a variety of images and then inserting a bright source near the center of the galaxy.
-For each galaxy, the simulated AGN can have one of three colors -- either blue, red, or flat (white) as seen in the color images -- and a range of brightnesses such that $L_\mathrm{ratio} \equiv L_\mathrm{galaxy}/L_\mathrm{AGN}$ is in $(0.2,1.0,2.0,5.0,10.0,50.0)$.
-Combining these parameters generates 15~images with different simulated AGN for each chosen host.
-
-Images with simulated AGN were classified in the main interface in an identical manner and evenly distributed with unaltered images of the galaxies.
-Classifiers were not explicitly told that the images had been altered, as the goal was to measure the effect on normal classifications in as unbiased a manner as possible.
-
-Two sets of simulated AGN were measured in GZH.
-The first set (version~1) was assembled from 95~galaxies from GEMS imaging and PSFs from \texttt{daophot}.
-The second set (version~2) was assembled from 96~galaxies with GOODS-S imaging; this version used deeper imaging and improved PSFs from \texttt{TinyTim}.
-
 \section{The catalog}\label{sec:results}
@@
 We split the data products for GZH by the type of image being classified.
-Table~\ref{tbl:catalog_hst} contains the classifications for the Hubble images from the AEGIS, COSMOS, and GEMS surveys, as well as 5-epoch deep imaging from the GOODS-N and GOODS-S surveys.
+Table~\ref{tbl:catalog_hst} contains the classifications for the \hst{} images from the AEGIS, COSMOS, and GEMS surveys, as well as 5-epoch deep imaging from the GOODS-N and GOODS-S surveys.
 This contains 118,425~galaxies and is the primary output from the GZH project.
@@
 \tablewidth{0pc}
-\tablecaption{GZH morphological classifications for Hubble images from AEGIS, COSMOS, GEMS, and GOODS\label{tbl:catalog_hst}} 
+\tablecaption{GZH morphological classifications for \hst{} images from AEGIS, COSMOS, GEMS, and GOODS\label{tbl:catalog_hst}} 
 \tabletypesize{\scriptsize}
@@
 \tablewidth{0pc}
-\tablecaption{GZH morphological classifications for HST images with simulated AGN\label{tbl:fake_agn}} 
+\tablecaption{GZH morphological classifications for \hst{} images with simulated AGN\label{tbl:fake_agn}} 
 \tabletypesize{\scriptsize}
@@
 
+\subsection{Effect of changing depth (GOODS, Stripe 82)}
+
 \subsection{Demographics of morphology}
@@
 
-This publication has been made possible by the participation of more than 200,000 volunteers in the Galaxy Zoo project.
-Their contributions are individually acknowledged at \texttt{http://www.galaxyzoo.org/volunteers}.
-
 We thank Meg Schwamb and the ASIAA for hosting the ``Citizen Science in Astronomy'' workshop, 3-7 Mar 2014 in Taipei, Taiwan, at which some of this analysis was done.
@@
 This project made heavy use of the Astropy packages in Python \citep{ast13}, the \texttt{seaborn} plotting package \citep{was15}, and astroML \citep{van12}.
-
-HST acknowledgements.
+Modified code from Nick~Wherry and David~Schlegel was used to create the JPG images.
+
+\hubble{} acknowledgements.
 

### 2016-03-24 movie/papermovie.sh
Check for filename on running. 6x4 geometry.

@@ -10,6 +10,11 @@
 #   Fixed font list via http://stackoverflow.com/questions/24696433/why-font-list-is-empty-for-imagemagick
 #   Original codec (libx264) did not work on current version of ffmpeg
 
+if [ "$#" -ne 1 ] || ! [ -f "$1" ]; then
+  echo "Usage: $0 filename" >&2
+  exit 1
+fi
+
 filename=$1
 
 # Set the remote and/or branches for the git repository
@@ -34,7 +39,7 @@ while read p; do
         cp $filename $revpad.pdf
         
         # Use ImageMagick to turn the paginated PDF into a single image
-        montage $revpad.pdf -tile 7x3 -background white -geometry 213x275-15+4 frames/$revpad.png
+        montage $revpad.pdf -tile 6x4 -background white -geometry 213x275-15+4 frames/$revpad.png
 
         let rev+=1
     fi
@@ -64,7 +69,6 @@ rm -f commits.txt
 rm -f *.pdf
 rm -f *.png
 rm -f frames/*.png
-rmdir frames/
 
 # Checkout the most recent version again
 git pull $remote $branch

### 2016-03-24 movie/papermovie.sh
Adjusting geometry for final clip

@@ -51,7 +51,7 @@ rev=0
 for f in `ls -1 frames/*.png | grep -v "movie\-1.png" | sort -nr`; do
     n=`printf "%03d" $rev`
     # Rename frames for ffmpeg's format style
-    convert $f -crop 1280x850+0+0 $n.png
+    convert $f -crop 1280x1320+0+0 $n.png
     let rev+=1
 done
 

### 2016-03-25 writeup/gz_hubble_data.tex
added process for fixing p best to account for negative smooth values

--- 2016-03-23 writeup/gz_hubble_data.tex
@@
 \usepackage{natbib}
-\usepackage{amsmath,amssymb}
 \usepackage{graphicx}
@@
 \author[Lead Author \etal]{Lead Author and other Galaxy Zoo science team members\\
-%
-% List of people who have contributed (not sure if everyone will be author)
-% Definitely: Lintott, Bamford, Edmondson, Masters, Simmons, Melvin, Willett, Galloway, Fortson, Schawinski
-% Others on GZ science team: Urry, Cardamone, Nichol, Kaviraj, Keel, Skibba, Thomas, Scarlata, Beck, Smethurst
-% Tech: Smith, Parrish, Simpson, other devs?
-% External: Han, Griffith
-%
 %$^1$Institute for Cosmology and Gravitation, University of Portsmouth, Dennis Sciama Building, Burnaby Road, Portsmouth, PO1 3FX, UK \\
@@
 %$^2$Institute for Sciences of the Cosmos (ICCUB), University of Barcelona, Marti i Franques 1, Barcelona, 08024 Spain\\
-%$^4$Oxford Astrophysics, Department of Physics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK\\
-%$^5$Yale Center for Astronomy and Astrophysics, Yale University, P.O. Box 208121, New Haven, CT 06520, USA \\
+% $^{4}$Oxford Astrophysics, Department of Physics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK\\
+%$^{5}$Yale Center for Astronomy and Astrophysics, Yale University, P.O. Box 208121, New Haven, CT 06520, USA \\
 %$^6$Steward Observatory, University of Arizona, 933 N. Cherry Ave, Tuscon, AZ 85721, USA\\
 %$^4$Astronomy Department, Adler Planetarium and Astronomy Museum, 1300 Lake Shore Drive, Chicago, IL 60605, USA\\
-%$^7$Centre for Astronomy \& Particle Theory, University of Nottingham, University Park, Nottingham, NG7 2RD, UK\\
+% $^7$Centre for Astronomy \& Particle Theory, University of Nottingham, University Park, Nottingham, NG7 2RD, UK\\
 %$^6$School of Physics and Astronomy, University of Minnesota, Minneapolis, MN 55455, USA\\
 %$^7$Department of Physics \& Astronomy, 206 Gallalee Hall, 514 University Blvd., University of Alabama, Tuscaloosa, AL 35487-0234, USA\\
-%$^8$Einstein Fellow\\ 
+% $^8$Einstein Fellow\\ 
 \\
@@
 
-The morphology of galaxies encodes information on the orbital parameters and assembly history of the contents, including gas, dust, stars, and the central black hole.
-The morphology is also closely related to the local environment of the galaxy, as mutual interactions such as gravitational tides, shocks in cluster environments and direct mergers can all change the shape of the galaxy's potential.
-For $M^\star$~galaxies in the local Universe, this typically manifests at the most basic level as the difference between bulge-dominated, virialized systems resembling ellipticals (early-types) and disk-dominated, rotationally-supported disks (late-types) frequently exhibiting spiral arms.
-This dichotomy has been used to explore much of the astrophysics encoding galaxy formation and evolution, and has been shown to be closely linked with other galactic properties such as stellar mass, halo mass, luminosity, black hole activity, size, and the relative ages of the stellar populations.
-
-The advent of larger telescopes in an increasing range of observing wavelengths has revealed that the distribution and properties of galaxy morphology have strongly evolved over the lifetime of the Universe.
-At redshift $z\simeq1$ (roughly 6~Gyr after the Big Bang), many galaxies are still in the process of assembling the baryonic mass required to reproduce the structures seen in the present day.
-This occurs in a variety of pathways, including accretion of baryons from large-scale galactic filaments onto halos via streaming, mergers of individual dark matter halos along with their baryons, conversion of gas into stars via gravitational collapse and star formation, etc.
-The process can also be slowed or even reversed via feedback from stellar winds, supernovae, and active black holes.
-Each of these processes affects on the galaxy morphology, and so an accurate measurement of the demographics as a function of redshift provides an extremely powerful observational constraint on the physics taking place \citep[for a recent review see][]{con14}.
-
-Theoretical predictions for the morphology of galaxies as a function of redshift are primarily computed within the $\Lambda$CDM cosmological framework.
-Full treatments of this model gravitational interactions between baryons and dark matter, hydrodynamics of the gas, and baryonic physics related to star formation and evolution.
-The most advanced simulations now include volumes up to $\sim100$~Mpc$^3$ while simultaneously resolving the smaller scales necessary to reproduce the baryonic physics \citep{vog14a,sch15}.
-Such simulations predict clustering of galaxies on large scales in a hierarchical assembly model \citep{sil12}.
-The structure of individual galaxies is affected by the merger history \citep{too72,hop10}, local environment \citep[such as the morphology-density relation;][]{dre80}, initial dark halo mass, and many other factors.
-Morphologies of individial simulated high-mass galaxies at $z\sim2-3$ commonly show kpc-scale ``clumpy'' structures and few galaxies that are either smooth or well-ordered spirals; asymmetric profiles with strong density constrasts dominate down to at least $z\gtrsim$ \citep{gen14}.
-
-Observational studies of galaxies at high-redshift also display a wide range of morphological types, many of which are rare or absent at $z\sim0$.
-These include spheroids and disks (akin to the ellipticals/spirals seen in the local Universe), but also a significant population of massive, more irregular galaxies, including mergers, tadpoles, chains, double-clumps, and clump-clusters \citep{elm05,elm07,cam11a,for11a,kar15}.
-In contrast, while grand-design spirals have been observed as far back as $z=2.18$ \citep{law12}, their spatial density suggests that they are exceedingly rare, with a very low overall disk fraction \citep{mor13}.
-Current observational data thus strongly suggests that the classical Hubble sequence/tuning fork \citep{hub36} is not a suitable framework for characterizing high-redshift morphology.
-
-Space-based observatories, particularly the \textit{Hubble Space Telescope}, have been responsible for the bulk of imaging studies of high-redshift galaxies.
-Observations of fixed fields with very deep imaging \citep[eg,][]{gia04,dav07,gro11,sco07,bec06,wil96} give the photometric sensitivity necessary to detect $L^\star$ galaxies at $z>1$, while also providing the angular resolution to distinguish internal structure and characterize the morphology.
-While these measurements are helped by the fact that the angular diameter distance is relatively flat at $z>1$ in a flat $\Lambda$CDM cosmology, the scales are only of the order $\sim5-10~\mathrm{kpc}/^{\prime\prime}$ \citep{wri06}.
-\textit{HST} can thus resolve much of the structure for a Milky Way-sized galaxy (at least for distinguishing a disk from a bulge), but will be limited for more compact structures.
-Since the size of galaxies evolves as roughly $r\propto(1+z)^{-1}$ \citep{law12a}, the more compact sizes of earlier galaxies make detailed morphologies a challenge even for \textit{HST} \citet{che12}.
-The public availability of more than $10^5$~galaxies in archival imaging across various studies gives a data sample with the potential for high statistical significance.
-
-One of the major difficulties in studying the morphologies of galaxies in large samples lies in the system of measurement.
-Visual classification by experts has been used for many years \citep[eg,][]{hub26,dev59,san61,van76,nai10,bai11,kar15}.
-These methods have advantages in using the significant processing power of the human brain to identify patterns, but suffer from issues such as lack of scaling to large surveys and potential issues with replicability and calibration.
-Automated measurements, both parametric \citep{pen02a,sim11,lac12} and non-parametric \citep{con03,lot04,sca07,fre13}, scale well to arbitrary sample sizes, but do not always fully capture the relevant features, especially for asymmetric galaxies that become increasingly common at high redshifts.
-The Galaxy Zoo project \citep{lin08,lin11} utilizes crowdsourced visual classifications to measure galaxies in color-composite images.
-With $>2\times10^5$~classifiers, this allows for multiple independent classifications of each image which are combined and calibrated to give a distribution of vote fractions proportional to the probability of a feature being visible.
-While the crowdsourced data require extensive calibration \citep{bam09,wil13}, they have a proven reliability and have been used in dozens of papers \citep[eg,][]{lan08,bam09,dar10,mas11c,ski12,sim13,sch14,wil15}.
-
-This paper presents the results from the Galaxy Zoo Hubble (GZH) project.
-GZH was the third phase of Galaxy Zoo, following its initial results classifying $\sim900,000$~SDSS~images into primarily early/late~types \citep{lin11} and Galaxy~Zoo~2, which covered $\sim250,000$~SDSS~images using a more detailed classification scheme that included bars, spiral arms, and galactic bulges \citep{wil13}.
-GZH used a similarly detailed classification scheme, but focused for the first time on images of high-redshift galaxies taken with the \textit{Hubble Space Telescope}.
-
-We describe the sample selection and creation of the images used for GZH in Section~\ref{sec:data}.
-Section~\ref{sec:interface} describes the GZH interface and the collection of classifications.
-Section~\ref{sec:debiasing} outlines the process used to calibrate and ``debias'' the crowdsourced votes.
-Section~\ref{sec:results} gives the main results as a catalog, with several examples of how the data may be queried in Section~\ref{sec:cookbook}.
-Section~\ref{sec:analysis} gives a short overview of the observed morphological demographics and compares them to several other catalogs, with a summary in Section~\ref{sec:summary}.
-
-This paper uses the WMAP9 cosmology parameters of $(\Omega_m,\Omega_\Lambda,h)=(0.258,0.718,0.697)$ \citep{hin13}.
-
-%\begin{enumerate}
-%    \item Motivation for studying morphology of galaxies
-%    \item Particular scientific questions governed by galaxies at $z\sim1$
-%    \item Theoretical predictions for galaxy morphology evolution
-%    \item Past imaging and morphology studies at $z\sim1$
-%    \item Summary of GZ/citizen science work on galaxy morphology to date
-%    \item Outline of paper
-%\end{enumerate}
-
-\section{Sample and Data}\label{sec:data}
-
-The GZH project contains images drawn from a number of different dedicated surveys and sample selection criteria, which we describe below.
-The majority of the images (as implied by the project name) are taken directly from \textit{Hubble Space Telescope} Legacy Surveys,
+\begin{enumerate}
+    \item Motivation for studying morphology of galaxies
+    \item Particular scientific questions governed by galaxies at $z\sim1$
+    \item Theoretical predictions for galaxy morphology evolution
+    \item Past imaging and morphology studies at $z\sim1$
+    \item Summary of GZ/citizen science work on galaxy morphology to date
+\end{enumerate}
+
+\section{Sample and Data} 
+\label{sec:data}
 
@@
 
-\subsection{Redshifts}
-
-We compiled redshifts from a variety of sources to include in the GZH catalog.
-For each galaxy, the redshift selected is in the $\tt Z\_Best$ column of the data (see Table~\ref{tbl:catalog_hst}), its type (spectroscopic: $\tt SPEC\_Z$, photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column $\tt Z\_BEST\_TYPE$, and the source catalog ($\tt Griffith$ \citep{gri12}, $\tt 3DHST$ \citep{mom15}, $\tt MUSYC$ \citep{car10}, or $\tt UltraVISTA$ \citep{ilb13}) of the redshift is in column $\tt Z\_BEST\_SOURCE$.
-
-For galaxies which have redshifts from multiple sources, we use the following algorithm to select the $\tt Z\_BEST$ redshift.
-We first prioritize spectroscopic redshifts; these are provided in the Griffith, 3DHST, and MUSYC catalogs.
-If a high quality spec-z exists in the Griffith catalog we use that, else 3DHST, else MUSYC.
-We show in Figure~\ref{fig:speczs} that over 98\% of the the spec-z's are consistent with each other, and therefore the priority order of selection makes no negligible difference.
-If no spectroscipic redshifts are available, we compare the 1-$\sigma$ errors of the photometric (Griffith, 3DHST, MUSYC, UltraVISTA) and grism (UltraVISTA) redshifts, and use the redshift with the smallest error.
-Table~\ref{tbl:redshifts} shows the results of this selection.
-
-\begin{figure*}
-\includegraphics[width=160mm]{figures/specz_comparison.pdf}
-\caption{Spectroscopic redshifts from Griffith, 3DHST, and MUSYC catalogs.
-The number in the upper left of each plot is the percentage of redshifts which agree within $\Delta z < 0.05$ between the two catalogs being compared in each panel.
-Within this range there is over 98\% agreement in redshifts between all three catalogs.}
-\label{fig:speczs}
-\end{figure*}
-
 \tabletypesize{\scriptsize}
@@
 
-\subsection{User weighting}\label{ssec:weighting}
+\subsection{Redshifts}
+
+We compiled redshifts from a variety of sources to include in the GZH catalog.
+For each galaxy, the redshift selected is in the $\tt Z\_Best$ column of the data (see Table~\ref{tbl:catalog_hst}), its type (spectroscopic: $\tt SPEC\_Z$, photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column $\tt Z\_BEST\_TYPE$, and the source catalog ($\tt Griffith$ \citep{gri12}, $\tt 3DHST$ \citep{mom15}, $\tt MUSYC$ \citep{car10}, or $\tt UltraVISTA$ \citep{ilb13}) of the redshift is in column $\tt Z\_BEST\_SOURCE$.
+
+For galaxies which have redshifts from multiple sources, we use the following algorithm to select the $\tt Z\_BEST$ redshift.
+We first prioritize spectroscopic redshifts; these are provided in the Griffith, 3DHST, and MUSYC catalogs.
+If a high quality spec-z exists in the Griffith catalog we use that, else 3DHST, else MUSYC.
+We show in Figure~\ref{fig:speczs} that over 98\% of the the spec-z's are consistent with each other, and therefore the priority order of selection makes no negligible difference.
+If no spectroscipic redshifts are available, we compare the 1-$\sigma$ errors of the photometric (Griffith, 3DHST, MUSYC, UltraVISTA) and grism (UltraVISTA) redshifts, and use the redshift with the smallest error.
+Table~\ref{tbl:redshifts} shows the results of this selection.
+
+\begin{figure*}
+\includegraphics[width=160mm]{figures/specz_comparison.pdf}
+\caption{Spectroscopic redshifts from Griffith, 3DHST, and MUSYC catalogs.
+The number in the upper left of each plot is the percentage of redshifts which agree within $\Delta z < 0.05$ between the two catalogs being compared in each panel.
+Within this range there is over 98\% agreement in redshifts between all three catalogs.}
+\label{fig:speczs}
+\end{figure*}
+
+\subsection{User weighting}
+\label{sec:weighting}
 The votes of individual users who classified galaxies in GZH are combined to make a vote fraction for each question on the classification tree.
@@
 
-\section{Galaxy Zoo interface and classifications}\label{sec:interface}
+\section{Galaxy Zoo interface and classifications}
+\label{sec:gz_interface}
 
@@
 
-\section{Correcting for redshift-dependent classification bias}\label{sec:debiasing}
-
+\section{Correcting for redshift-dependent classification bias}
+\label{sec:debiasing}
 The previous versions of Galaxy Zoo morphology classifications \citep{lin08,wil13} were based on observations of galaxies in the Sloan Digital Sky Survey (SDSS) which are typically at $z<0.1$.
@@
 
-\subsection{Correcting GZH morphologies for classification bias}\label{ssec:zeta}
+\subsection{Correcting GZH morphologies for classification bias}
+\label{sec:zeta}
 
@@
 The white grid denotes the surface brightness and redshift range of the \ferengi{} images, subdivided in bins corresponding to fixed ranges used for analysis in Figure~\ref{fig:p_vs_p}.}
-\label{fig:sb_redshift}
+
+\label{fig:features_corrections}
 \end{center}
@@
 Any data in which the polynomial fit has a slope less than this value is considered \emph{not} one-to-one, and therefore ``uncorrectable.'' These regions are highlighted in blue in figure ~\ref{fig:6a}.
-Uncolored (white) regions of the plot have sufficiently high slopes for us to consider the relationship to be single-valued; galaxies in these regions are considered ``correctable'', and only these are used in measuring the parameters for the $\zeta$ function (Section~\ref{ssec:zeta}).
+Uncolored (white) regions of the plot have sufficiently high slopes for us to consider the relationship to be single-valued; galaxies in these regions are considered ``correctable'', and only these are used in measuring the parameters for the $\zeta$ function (Section \ref{sec:zeta}).
 Only surface brightness/redshift bins with at least 5 galaxies were considered; regions with fewer than 5 galaxies we consider to have ``not enough information'' to determine the  $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$ relationship, these are colored gray in Figure~\ref{fig:6a}.
@@
 \caption{Debiased $p_{features}$ corrected to $z=0.3$ vs weighted $p_{features}$ for the correctable (left), uncorrectable (middle), and NEI (right) galaxies in the GZH sample.}
-\label{fig:debiased_corrections}
+
+\label{fig:features_corrections}
 \end{center}
@@
 \subsubsection{TODO LIST}
-We need to: 
+We need to do: 
 \begin{itemize}
@@
 
-\section{The catalog}\label{sec:results}
+\section{The catalog}
 
@@
 For each of the 55~responses in the GZH decision tree, the following classification data is provided: for each question, $\tt N_{votes}$ is the number of users to answer that question.
-For each unique answer, $\tt fraction$ is the fraction of users to select that answer ($\rm N_{answer}/N_{votes}$, and $\tt weighted$ is the weighted fraction, which takes into account user consistency (Section~\ref{ssec:weighting}).
+For each unique answer, $\tt fraction$ is the fraction of users to select that answer ($\rm N_{answer}/N_{votes}$, and $\tt weighted$ is the weighted fraction, which takes into account user consistency (Section~\ref{sec:weighting}).
 
@@
 The $\tt best$ fraction for $p_{features}$is chosen based on the categorization of the galaxy: if it is ``correctable'', $\tt best = debiased$, if ``uncorrectable'', $\tt best = lower~limit$, and if neither, $\tt best = weighted$.
-The debiased vote fractions for $\tt p_{smooth}$ were calculated on the critera that vote fractions for all answers must sum to unity.
+
+The debiased and best vote fractions for $\tt p_{smooth}$ were calculated on the critera that vote fractions for all answers must sum to unity.
 Explicitely: $\tt p_{smooth} = 1 - p_{features} - p_{artifact}$.
+In some rare cases, representing  $<1\%$ of the sample, this requirement resulted in negative vote fractions for $\rm p_{smooth}$; these were cases in which the $\rm p_{features}$ vote fraction was boosted to a high value relative to the $\rm p_{artifact}$ vote fraction.
+In these cases, we enforce the restriction that the vote fractions must sum to 1 by raising $\rm p_{smooth}$ to a vote fraction of 0.0 and decreasing $\rm p_{features}$ accordingly.
+This correction was typically very small, with a median decrease/increase of $\rm p_{features}/p_{smooth}$ of $\Delta p = 0.04$.
 
@@
 Needs some test cases for extracting a given set of objects (eg, clump galaxies in a particular redshift range) and evaluation of the results. Possibly include suggested thresholds, \'a la GZ2. 
-
-\section{Using the catalog}\label{sec:cookbook}
+\section{Using the catalog}
+\label{sec:cookbook}
 Include cookbook for selecting morphologies.
@@
 
-\subfigure{[a]\label{fig:smooth_to_smooth}\includegraphics[width=\textwidth]{figures/smooth_to_smooth.pdf}}
-
-\subfigure{[b]\label{fig:smooth_to_int}\includegraphics[width=\textwidth]{figures/smooth_to_intermediate.pdf}}
-
-\subfigure{[c]\label{fig:smooth_to_featured}\includegraphics[width=\textwidth]{figures/smooth_to_featured.pdf}}
+\subfigure{[a]\label{fig:smoothtoint}\includegraphics[width=\textwidth]{figures/smooth_to_smooth.pdf}}
+
+\subfigure{[b]\label{fig:smoothtoint}\includegraphics[width=\textwidth]{figures/smooth_to_intermediate.pdf}}
+
+\subfigure{[c]\label{fig:smoothtoint}\includegraphics[width=\textwidth]{figures/smooth_to_featured.pdf}}
 
@@
 
-\subfigure{[b]\label{fig:int_to_smooth}\includegraphics[width=\textwidth]{figures/intermediate_to_smooth.pdf}}
-
-\subfigure{[b]\label{fig:int_to_int}\includegraphics[width=\textwidth]{figures/intermediate_to_intermediate.pdf}}
-
-\subfigure{[b]\label{fig:int_to_featured}\includegraphics[width=\textwidth]{figures/intermediate_to_featured.pdf}}
+\subfigure{[b]\label{fig:smoothtoint}\includegraphics[width=\textwidth]{figures/intermediate_to_smooth.pdf}}
+
+\subfigure{[b]\label{fig:smoothtoint}\includegraphics[width=\textwidth]{figures/intermediate_to_intermediate.pdf}}
+
+\subfigure{[b]\label{fig:smoothtoint}\includegraphics[width=\textwidth]{figures/intermediate_to_featured.pdf}}
 
@@
 
-\subfigure{[b]\label{fig:featured_to_smooth}\includegraphics[width=\textwidth]{figures/featured_to_smooth.pdf}}
-
-\subfigure{[b]\label{fig:featured_to_int}\includegraphics[width=\textwidth]{figures/featured_to_intermediate.pdf}}
-
-\subfigure{[b]\label{fig:featured_to_featured}\includegraphics[width=\textwidth]{figures/featured_to_featured.pdf}}
+\subfigure{[b]\label{fig:smoothtoint}\includegraphics[width=\textwidth]{figures/featured_to_smooth.pdf}}
+
+\subfigure{[b]\label{fig:smoothtoint}\includegraphics[width=\textwidth]{figures/featured_to_intermediate.pdf}}
+
+\subfigure{[b]\label{fig:smoothtoint}\includegraphics[width=\textwidth]{figures/featured_to_featured.pdf}}
 

### 2016-03-31 writeup/gz_hubble_data.tex
Paragraphs on metadata source

--- 2016-03-24 writeup/gz_hubble_data.tex
@@
 % Definitely: Lintott, Bamford, Edmondson, Masters, Simmons, Melvin, Willett, Galloway, Fortson, Schawinski, Cheung
-% Others on GZ science team: Urry, Cardamone, Nichol, Kaviraj, Keel, Skibba, Thomas, Scarlata, Beck, Smethurst
+% Others on GZ science team: Urry, Cardamone, Nichol, Kaviraj, Keel, Skibba, Thomas, Wong, Scarlata, Beck, Smethurst
 % Tech: Smith, Parrish, Simpson, other devs?
@@
 
-For images from the ACS-GC \citet{gri12}, galaxies are identified using a combination of SExtractor \citep{ber96} and the galaxy-profile fitting framework \textsc{Galapagos} \citep{hau07}.
-We select all galaxies with $m < 23.5$, where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS, GEMS + GOODS-S, and GOODS-N surveys, respectively.
+For images from the ACS-GC \citet{gri12}, galaxies are identified using a combination of \sextractor{} \citep{ber96} and the galaxy-profile fitting framework \textsc{Galapagos} \citep{hau07}.
+We selected all galaxies with $m < 23.5$, where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS, GEMS + GOODS-S, and GOODS-N surveys, respectively.
+This yielded a total of 113,166~images (Table~\ref{tbl:gzh_numbers}).
 
 Single-epoch images from SDSS Stripe~82 were selected using the same criteria from \citet{wil13}, which required limits of \texttt{petroR90\_r}$ > 3$\arcsec~(where \texttt{petroR90\_r} is the radius containing 90\% of the $r^\prime$ Petrosian flux) and a magnitude brighter than $m_r < 17.77$.
+21,522 galaxies in SDSS met these criteria.
 Coadded images from Stripe~82 were selected from the union of galaxies with coadded magnitudes brighter than $17.77$~mag and the galaxies detected in the single-depth images and matched to a coadd source.
-Of the images in the coadded sample, 5144/30339 (17 percent) are dimmer than this initial magnitude cut.
+This resulted in a larger set of 30,339 images.
+Of the images in the coadded sample, 5144 (17~percent) are dimmer than the initial magnitude cut of 17.77.
 
@@
 
-\subsection{Artifically-redshifted images}
-
-FERENGI images (ask Edmond to write this?) Should contain much of the information in \S\ref{sec:debiasing} right now.
-
-\subsection{Redshifts}
-
-We compiled redshifts from a variety of sources to include in the GZH catalog.
+\subsection{Galaxy metadata}
+
+Photometric data for the bulk of the GZH sample is largely drawn from the tables provided in \citet{gri12}.
+This includes photometric parameters from both \sextractor{} and \galfit, such as the fluxes, magnitudes, radii, ellipticities, position angles, and positions.
+\galfit{} also provides the parametric S\'{e}rsic index and effective half-light radius for the best-fit model.
+All parameters are measured in both bands of the ACS imaging, with the exception of the single-band COSMOS images.
+
+Redshifts for the GZH catalog are compiled from a variety of sources to include in the GZH catalog.
 For each galaxy, the redshift selected is in the $\tt Z\_Best$ column of the data (see Table~\ref{tbl:catalog_hst}), its type (spectroscopic: $\tt SPEC\_Z$, photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column $\tt Z\_BEST\_TYPE$, and the source catalog ($\tt ACSGC$ \citep{gri12}, $\tt 3DHST$ \citep{mom15}, $\tt MUSYC$ \citep{car10}, or $\tt UltraVISTA$ \citep{ilb13}) of the redshift is in column $\tt Z\_BEST\_SOURCE$.
@@
 
+Photometric and spectroscopic data for the SDSS Stripe~82 galaxies are taken from the CasJobs DR7 tables.
+This includes $ugriz$ Petrosian magnitudes and fluxes, as well as the relative de~Vaucouleurs and exponential fits from the model magnitudes.
+Redshifts used for the Sloan galaxies are all spectroscopic.
+82.6\% of galaxies in the single-depth images and 65.1\% of galaxies in the coadd images have a measured DR7 spectroscopic redshift.
+
 \section{Galaxy Zoo interface and classifications}\label{sec:interface}
@@
 In Figure~\ref{fig:p_vs_p} we examine the change in \pfeatures{} for the \ferengi{} galaxies relative to their lowest simulated redshift.
-In this analysis, only galaxies whose lowest simulated redshift image was ($\rm z_{sim}=0.3$) were used (see Table \ref{tbl:ferengivalues}), and only those which had detectable surface brightness measurements in \sextractor{}; this includes 3,950 of the total 6,466 images.
+In this analysis, only galaxies whose lowest simulated redshift image was ($\rm z_{sim}=0.3$) were used (see Table \ref{tbl:ferengivalues}), and only those which had detectable surface brightness measurements in \sextractor; this includes 3,950 of the total 6,466 images.
 For each simulated redshift value $z$, and at a fixed surface brightness $\mu$, we plot \pfeaturesz, the value measured at that simulated redshift, vs \pfeaturesrest, the value measured for the same galaxy imaged at $z=0.3$.

### 2016-04-06 writeup/gz_hubble_data.tex
added text in using catalog section

@@
 \caption{Screenshot of the Galaxy Zoo: Hubble interface showing an example COSMOS image at the first step in the decision tree.\label{fig:interface}}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\textwidth]{figures/gzh_decision_tree.pdf}
+\caption{}
+\label{fig:decisiontree}
+\end{center}
 \end{figure*}
@@
 \section{Using the catalog}\label{sec:cookbook}
-Include cookbook for selecting morphologies.
+
+The intended purpose of the GZH catalog is to provide simple, yet flexible, means of identifying samples of galaxies with a desired morphological type.
+Here we provide instructions for creating such samples using the vote fractions corresponding to the tasks shown in Figure~\ref{fig:decisiontree}.
+We stress that the selection process may vary based on the particular science case in question.
+
+To select galaxies of a morphological type identified with a Task offered in the decision tree (see Figure~\ref{fig:decisiontree}, a cut is placed on the vote fraction for that Task ($p_{\rm task}$), as well as the vote fractions for the Tasks preceding it.
+For example, to select barred galaxies, a cut may be placed on $p_{\rm bar}$ such that only galaxies where a high fraction of votes for this task voted for the $bar,yes$ answer.
+This is not the only necessary cut, however, since not all users answer this question; only those who have previously selected ``features'' in Task 01, ``not clumpy'' in Task 12, and ``not edge-on'', \emph{or} previously selected ``features'' in Task 01, ``clumpy'' in Task 12, ``$>$ 2 clumps'' in Task 16, and ``spiral arrangement'' in Task 15 will have the opportunity to vote on the bar question, Task 03.
+Therefore to ensure the value of $p_{\rm bar}$ is well-sampled, cuts on all previous tasks must be applied.
+
+The flexibility of this catalog allows the user to set their own selection criteria for vote fraction thresholds to create a morphological sample particular to their science case.
+In Table~\ref{tab:prev_tasks} we offer baseline cuts for selecting galaxies of desired morphologies.
+As an example: to select barred galaxies, one should select objects with $p_{\rm features}>0.52, p_{\rm clumpy,no} > 0.55,$ and $p_{edgeon,no}>x.xx$ \emph{or} objects with $p_{\rm features}>0.52, p_{\rm clumpy,yes} > x.xx, (p_{\rm clump~count, 3}+p_{\rm clump~count,4}+p_{\rm clump~count,>4}+p_{\rm clump~count,can't~tell})>x.xx,$ and $p_{\rm clump~arrangement,spiral}>x.xx.$ These cuts define a sample of galaxies of ``bar candidates''; ie galaxies for which answering the bar question makes physical sense and the vote fraction $p_{\rm bar}$ is well-sampled.
+In this example, such galaxies are featured, non-clumpy, non-edgeon galaxies, or featured, clumpy, spiral galaxies.
+At this point a cut can be made on $p_{\rm bar}$ to select a clean sample of only strong bars $p_{\rm bar}>0.8$, or a complete sample of weak and strong bars $p_{\rm bar}>0.3$, or the value most appropriate to the science case.
+
+\begin{itemize}
+\item explain decision tree format; vote fractions are dependent on previous task vote fractions
+\item provide example of how to select bars
+\item discuss difference between conservative/clean sample and loose/complete sample, emphasize goals differ depending on science case
+\end{itemize}
+
+\begin{table*}
+\caption{Cookbook \label{tab:prev_tasks}}
+\begin{tabular}{llll}
+\hline\hline
+Task No. &  Task 	        & Previous Task  & Vote Fraction Cut \\
+         &            	        &                & $N_{task} \ge 20$ \\
+\hline
+01       & smooth or features   &  -                  & -                 \\
+02       & edge on              & 01, 12              & $p_{\rm clumpy,no}>0.55$              \\
+03       & bar		        & 01, 12, 02          & $p_{\rm edgeon,no}>$                 \\
+         &                      & 01, 12, 16, 15      & $p_{\rm arrangement,spiral}>$         \\
+04       & spiral arms          & 01, 12, 02          & $p_{\rm edgeon,no}>$                  \\
+         &                      & 01, 12, 16, 15      & $p_{\rm arrangement,spiral}>$         \\
+05       & bulge prominence     & 01, 12, 02          & $p_{\rm edgeon,no}>$                 \\
+         &                      & 01, 12, 16, 15      & $p_{\rm arrangement,spiral}>$         \\
+06       & odd yes/no           & -                   &                   \\
+07       & rounded              & 01                  & $p_{\rm smooth}>0.45$               \\
+08       & odd feature          & 06                  & $p_{\rm odd,yes}>$                  \\
+09       & bulge shape          & 01, 12, 02          & $p_{\rm edgeon,yes}>$               \\
+10       & arms winding         & 01, 12, 02, 04      & $p_{\rm spiral,yes}>$                  \\
+         &                      & 01, 12, 16, 15, 04  & $p_{\rm spiral,yes}>$                  \\
+11       & arms number          & 01, 12, 02, 04      & $p_{\rm spiral,yes}>$                 \\
+         &                      & 01, 12, 16, 15, 04  & $p_{\rm spiral,yes}>$                  \\
+12       & clumpy               & 01                  & $p_{\rm features}>0.52$              \\
+13       & bright clump         & 01, 12, 16          & $p_{\rm one clump}<$                 \\
+14       & bright central clump & 01, 12, 16, 13      & $p_{\rm bright clump,yes}>$           \\
+15       & clump arrangement    & 01, 12, 16          & $p_{\rm one clump}<$                \\
+16       & clump count          & 01, 12              & $p_{\rm clumpy,yes}>0.55$              \\
+17       & clumps symmetrical   & 01, 12, 16          & $p_{\rm one clump}<$                \\
+18       & clumps embedded      & 01, 12, 16          &  $p_{\rm one clump}<$                 \\
+
+\hline\hline
+\end{tabular}
+\end{table*}
 

### 2016-04-06 writeup/gz_hubble_data.tex
Explicitly mark to-do as notes in red.

--- 2016-03-31 writeup/gz_hubble_data.tex
@@
 Users' votes are weighted slightly \citep[in a method identical to that described in][]{wil13} such that users who frequently disagree with all other users end up having very low weights.
-The majority of users have weights very close to $w=1.0$ ({\bf STEVEN: Is this true for GZH - do you have a plot of the distribution of user weights or consistencies we can include here?}.
+The majority of users have weights very close to $w=1.0$
+
+{\note STEVEN: Is this true for GZH - do you have a plot of the distribution of user weights or consistencies we can include here?}.
 
@@
 Without sufficient galaxies in each surface brightness/redshift bin, we cannot accurately measure a relationship between vote fractions and redshift; for this reason we only offer debiased vote fractions for question 1.
-\textbf{perhaps compute number of galaxies that can be fit to zeta for each question, show a table?
-overkill?} In Section \ref{sec:ferengi_bar} we show results of an attempt to measure $\zeta$ for $\rm p_{bar}$.
-
+
+{\note Perhaps compute number of galaxies that can be fit to zeta for each question, show a table? overkill?}
+
+In Section \ref{sec:ferengi_bar} we show results of an attempt to measure $\zeta$ for $\rm p_{bar}$.
+
+{\note
 \begin{itemize}
@@
 \end{itemize}
+}
 
@@
 
-To include: detailed description of each column in the machine-readable tables.
+{\note To include: detailed description of each column in the machine-readable tables. }
+
+\section{Using the catalog}\label{sec:cookbook}
+
+Include cookbook for selecting morphologies.
 
 Needs some test cases for extracting a given set of objects (eg, clump galaxies in a particular redshift range) and evaluation of the results. Possibly include suggested thresholds, \'a la GZ2.
-
-\section{Using the catalog}\label{sec:cookbook}
-Include cookbook for selecting morphologies.
 
@@
 
-\textit{Address trends seen in broad morphological classes, possible reasons for difference.
-Also should attempt to map between the GZH vote fractions and whatever classification systems are used in the above systems.}
+{\note \textit{Address trends seen in broad morphological classes, possible reasons for difference.
+Also should attempt to map between the GZH vote fractions and whatever classification systems are used in the above systems.}}
 

### 2016-04-07 writeup/gz_hubble_data.tex
updated threshold values

--- 2016-04-06 writeup/gz_hubble_data.tex
@@
 In Table~\ref{tab:prev_tasks} we offer baseline cuts for selecting galaxies of desired morphologies.
-As an example: to select barred galaxies, one should select objects with $p_{\rm features}>0.52, p_{\rm clumpy,no} > 0.55,$ and $p_{edgeon,no}>x.xx$ \emph{or} objects with $p_{\rm features}>0.52, p_{\rm clumpy,yes} > x.xx, (p_{\rm clump~count, 3}+p_{\rm clump~count,4}+p_{\rm clump~count,>4}+p_{\rm clump~count,can't~tell})>x.xx,$ and $p_{\rm clump~arrangement,spiral}>x.xx.$ These cuts define a sample of galaxies of ``bar candidates''; ie galaxies for which answering the bar question makes physical sense and the vote fraction $p_{\rm bar}$ is well-sampled.
+As an example: to select barred galaxies, one should select objects with $p_{\rm features}>0.52, p_{\rm clumpy,no} > 0.3,$ and $p_{edgeon,no}>0.25$ \emph{or} objects with $p_{\rm features}>0.52, p_{\rm clumpy,yes} > 0.55, (p_{\rm clump~count, 3}+p_{\rm clump~count,4}+p_{\rm clump~count,>4}+p_{\rm clump~count,can't~tell})>0.45,$ and $p_{\rm clump~arrangement,spiral}>0.85.$ These cuts define a sample of galaxies of ``bar candidates''; ie galaxies for which answering the bar question makes physical sense and the vote fraction $p_{\rm bar}$ is well-sampled.
 In this example, such galaxies are featured, non-clumpy, non-edgeon galaxies, or featured, clumpy, spiral galaxies.
@@
 01       & smooth or features   &  -                  & -                 \\
-02       & edge on              & 01, 12              & $p_{\rm clumpy,no}>0.55$              \\
-03       & bar		        & 01, 12, 02          & $p_{\rm edgeon,no}>$                 \\
-         &                      & 01, 12, 16, 15      & $p_{\rm arrangement,spiral}>$         \\
-04       & spiral arms          & 01, 12, 02          & $p_{\rm edgeon,no}>$                  \\
-         &                      & 01, 12, 16, 15      & $p_{\rm arrangement,spiral}>$         \\
-05       & bulge prominence     & 01, 12, 02          & $p_{\rm edgeon,no}>$                 \\
-         &                      & 01, 12, 16, 15      & $p_{\rm arrangement,spiral}>$         \\
+02       & edge on              & 01, 12              & $p_{\rm clumpy,no}>0.3$              \\
+03       & bar		        & 01, 12, 02          & $p_{\rm edgeon,no}>0.25$                 \\
+         &                      & 01, 12, 16, 15      & $p_{\rm arrangement,spiral}>0.85$         \\
+04       & spiral arms          & 01, 12, 02          & $p_{\rm edgeon,no}>0.25$                  \\
+         &                      & 01, 12, 16, 15      & $p_{\rm arrangement,spiral}>0.85$         \\
+05       & bulge prominence     & 01, 12, 02          & $p_{\rm edgeon,no}>0.25$                 \\
+         &                      & 01, 12, 16, 15      & $p_{\rm arrangement,spiral}>0.85$         \\
 06       & odd yes/no           & -                   &                   \\
@@
 12       & clumpy               & 01                  & $p_{\rm features}>0.52$              \\
-13       & bright clump         & 01, 12, 16          & $p_{\rm one clump}<$                 \\
-14       & bright central clump & 01, 12, 16, 13      & $p_{\rm bright clump,yes}>$           \\
-15       & clump arrangement    & 01, 12, 16          & $p_{\rm one clump}<$                \\
+13       & bright clump         & 01, 12, 16          & $p_{\rm one~clump}<$                 \\
+14       & bright central clump & 01, 12, 16, 13      & $p_{\rm bright~clump,yes}>$           \\
+15       & clump arrangement    & 01, 12, 16          & $p_{\rm multiple~clumps}>0.45$                \\
 16       & clump count          & 01, 12              & $p_{\rm clumpy,yes}>0.55$              \\
-17       & clumps symmetrical   & 01, 12, 16          & $p_{\rm one clump}<$                \\
-18       & clumps embedded      & 01, 12, 16          &  $p_{\rm one clump}<$                 \\
+17       & clumps symmetrical   & 01, 12, 16          & $p_{\rm multiple~clumps}>0.45$                \\
+18       & clumps embedded      & 01, 12, 16          &  $p_{\rm multiple~clumps}>0.45$                 \\
 

### 2016-04-14 writeup/gz_hubble_data.tex
updating threshold values in writeup

@@
 03       & bar		        & 01, 12, 02          & $p_{\rm edgeon,no}>0.25$                 \\
-         &                      & 01, 12, 16, 15      & $p_{\rm arrangement,spiral}>0.85$         \\
+         &                      & 01, 12, 16, 15      & $p_{\rm arrangement,spiral}>0.65$         \\
 04       & spiral arms          & 01, 12, 02          & $p_{\rm edgeon,no}>0.25$                  \\
-         &                      & 01, 12, 16, 15      & $p_{\rm arrangement,spiral}>0.85$         \\
+         &                      & 01, 12, 16, 15      & $p_{\rm arrangement,spiral}>0.65$         \\
 05       & bulge prominence     & 01, 12, 02          & $p_{\rm edgeon,no}>0.25$                 \\
-         &                      & 01, 12, 16, 15      & $p_{\rm arrangement,spiral}>0.85$         \\
+         &                      & 01, 12, 16, 15      & $p_{\rm arrangement,spiral}>0.65$         \\
 06       & odd yes/no           & -                   &                   \\
-07       & rounded              & 01                  & $p_{\rm smooth}>0.45$               \\
-08       & odd feature          & 06                  & $p_{\rm odd,yes}>$                  \\
-09       & bulge shape          & 01, 12, 02          & $p_{\rm edgeon,yes}>$               \\
-10       & arms winding         & 01, 12, 02, 04      & $p_{\rm spiral,yes}>$                  \\
-         &                      & 01, 12, 16, 15, 04  & $p_{\rm spiral,yes}>$                  \\
-11       & arms number          & 01, 12, 02, 04      & $p_{\rm spiral,yes}>$                 \\
-         &                      & 01, 12, 16, 15, 04  & $p_{\rm spiral,yes}>$                  \\
-12       & clumpy               & 01                  & $p_{\rm features}>0.52$              \\
-13       & bright clump         & 01, 12, 16          & $p_{\rm one~clump}<$                 \\
-14       & bright central clump & 01, 12, 16, 13      & $p_{\rm bright~clump,yes}>$           \\
+07       & rounded              & 01                  & $p_{\rm smooth}>0.7$               \\
+08       & odd feature          & 06                  & $p_{\rm odd,yes}> 0.5 $                  \\
+09       & bulge shape          & 01, 12, 02          & $p_{\rm edgeon,yes}>0.4$               \\
+10       & arms winding         & 01, 12, 02, 04      & $p_{\rm spiral,yes}>$ 0.25                 \\
+11       & arms number          & 01, 12, 02, 04      & $p_{\rm spiral,yes}>$ 0.25                \\
+12       & clumpy               & 01                  & $p_{\rm features}>0.23$              \\
+13       & bright clump         & 01, 12, 16          & $p_{\rm one~clump}< 0.4$                 \\
+14       & bright central clump & 01, 12, 16, 13      & $p_{\rm bright~clump,yes}>0.5$           \\
 15       & clump arrangement    & 01, 12, 16          & $p_{\rm multiple~clumps}>0.45$                \\
-16       & clump count          & 01, 12              & $p_{\rm clumpy,yes}>0.55$              \\
-17       & clumps symmetrical   & 01, 12, 16          & $p_{\rm multiple~clumps}>0.45$                \\
-18       & clumps embedded      & 01, 12, 16          &  $p_{\rm multiple~clumps}>0.45$                 \\
+16       & clump count          & 01, 12              & $p_{\rm clumpy,yes}>0.8$              \\
+17       & clumps symmetrical   & 01, 12              & $p_{\rm clumpy,yes}>0.8$                \\
+18       & clumps embedded      & 01, 12              & $p_{\rm clumpy,yes}>0.8$                 \\
 

### 2016-04-15 writeup/gz_hubble_data.tex
Small text changes to the higher-order branches

--- 2016-04-06 writeup/gz_hubble_data.tex
@@
 \section{Introduction}
-
-\textit{Usual due diligence for an intro science paper. Should cover:}
 
@@
 While the appropriate correctable regions were defined discretely, we assume the true correctable region is a smooth function of z, $\mu$, and \pfeatures{}.
-To define this smooth space, we use a convex hull method to enclose the correctable and uncorrectable \ferengi{} galaxies is z-$\mu$-\pfeatures{} space.
-Due to scatter, the boundaries of the resulting hulls overlap.
+To define this smooth space, we generate a convex hull that encloses the correctable and uncorrectable \ferengi{} galaxies in $z$-$\mu$-\pfeatures{} space.
 The boundaries are then adjusted until the contamination from both groups is minimized.
@@
 \subsection{Challenges of debiasing questions beyond ``smooth or features''}
-Each FERENGI image does not have the same number of users answering each question, due to the structure of the decision tree.
-Every user answers the first question, ``Is the galaxy smooth and rounded, with no sign of a disk?''; as such the vote fractions $\rm p_{smooth}, p_{features}$, and $\rm p_{artifact}$ are all computed with the minimum statistical error for any question, with roughly 40 total answers (see Section~\ref{sec:gz_interface}).
+
+As with the HST images, each FERENGI subject has a varying number of users answering the various questions in the hierarchical decision tree.
+Every user answers the first question, ``Is the galaxy smooth and rounded, with no sign of a disk?''; as such the vote fractions $\rm p_{smooth}, p_{features}$, and $\rm p_{artifact}$ are all computed with the minimum statistical error for any question, with roughly 40 total answers (see Section~\ref{sec:interface}).
 The number of users to answer any subsequent question, however, is always equal to or less than the number to answer the preceding question.
-For this reason, some galaxies may have very few (or even zero) answers to a question further down the tree (see Figure make-figure-of-count-distribution-for-each-question).
-To minimize statistical error in computing vote fractions, a cut on the number of answers to a given question is always implemented.
-
-In the FERENGI data, we find that this places large limitations on the amount of information we can extract for the higher order questions.
-We require that at least 5 users answer each question for a galaxy image at $z=0.3$ \emph{and} its image at higher $z$.
-This requirement placed on both images is not met by a significant number of galaxies for questions beyond question 1.
-Without sufficient galaxies in each surface brightness/redshift bin, we cannot accurately measure a relationship between vote fractions and redshift; for this reason we only offer debiased vote fractions for question 1.
+The average number of responses per task for fourth- or fifth-tier questions such as spiral arm structure (Tasks 12--14) is only $4\pm4$ for the FERENGI sample; while this is distribution is strongly bimodal (reflecting the true morphologies of selected galaxies), the very low absolute numbers of votes introduce very high variance when attempting to calculate a statistical correction.
+
+In the FERENGI data, these numbers severely limit the amount of information we can extract for the higher-tier questions.
+The debiasing technique used (Section~\ref{ssec:zeta}) require that at least 5~users answer each question for a galaxy image at $z=0.3$ \emph{and} its image at higher redshift.
+This requirement placed on both images is not met by a significant number of galaxies for questions beyond Task~01.
+The FERENGI images classified do not have sufficient numbers of objects in the surface brightness/redshift bins to accurately measure if the relation between vote fractions and redshift is single-valued.
+
+for this reason we only offer debiased vote fractions for Task~01 (smooth/features/artifact).
 

### 2016-04-15 writeup/gz_hubble_data.tex

@@
 
-Include cookbook for selecting morphologies.
-
-Needs some test cases for extracting a given set of objects (eg, clump galaxies in a particular redshift range) and evaluation of the results. Possibly include suggested thresholds, \'a la GZ2.
+The intended purpose of the GZH catalog is to provide a simple, yet flexible, means of identifying samples of galaxies with a desired morphological type.
+Here we provide instructions for creating such samples using the vote fractions corresponding to the tasks shown in Figure~\ref{fig:decisiontree}.
+We stress that the selection process will vary based on the particular science case.
+
+To select galaxies of a morphological type identified with a Task offered in the decision tree (see Figure~\ref{fig:decisiontree}, a cut is placed on the vote fraction for that Task ($p_{\rm task}$), as well as the vote fractions for the Tasks preceding it.
+For example, to select barred galaxies, a cut may be placed on $p_{\rm bar}$ such that only galaxies where a high fraction of votes for this task voted for the $bar,yes$ answer.
+This is not the only necessary cut, however, since not all users answer this question; only those who have previously selected ``features'' in Task~01, ``not clumpy'' in Task~12, and ``not edge-on'', \emph{or} previously selected ``features'' in Task~01, ``clumpy'' in Task~12, ``$>$ 2 clumps'' in Task~16, and ``spiral arrangement'' in Task~15 will have the opportunity to vote on the bar question, Task~03.
+To ensure that $p_{\rm bar}$ is well-sampled, cuts on all previous tasks must be applied.
+
+The flexibility of this catalog allows the user to set their own selection criteria for vote fraction thresholds to create a morphologically-pure sample.
+In Table~\ref{tab:prev_tasks} we offer baseline cuts for selecting galaxies of a variety of morphologies.
+{\note As an example: to select barred galaxies, one should select objects with $p_{\rm features}>0.52, p_{\rm clumpy,no} > 0.55,$ and $p_{edgeon,no}>x.xx$ \emph{or} objects with $p_{\rm features}>0.52, p_{\rm clumpy,yes} > x.xx, (p_{\rm clump~count, 3}+p_{\rm clump~count,4}+p_{\rm clump~count,>4}+p_{\rm clump~count,can't~tell})>x.xx,$ and $p_{\rm clump~arrangement,spiral}>x.xx.$} These cuts define a sample of galaxies of ``bar candidates''; ie galaxies for which answering the bar question makes physical sense and the vote fraction $p_{\rm bar}$ is well-sampled.
+In this example, such galaxies are featured, non-clumpy, non-edge~on galaxies, or featured, clumpy, spiral galaxies.
+At this point a cut can be made on $p_{\rm bar}$ to select a clean sample of only strong bars $p_{\rm bar}>0.8$, or a complete sample of weak and strong bars $p_{\rm bar}>0.3$, or the value most appropriate to the science case.
+
+{\note
+\begin{itemize}
+    \item explain decision tree format; vote fractions are dependent on previous task vote fractions
+    \item provide example of how to select bars
+    \item discuss difference between conservative/clean sample and loose/complete sample, emphasize goals differ depending on science case
+\end{itemize}
+}
+
+\begin{table*}
+\caption{Cookbook \label{tab:prev_tasks}}
+\begin{tabular}{llll}
+\hline\hline
+Task No. &  Task 	        & Previous Task  & Vote Fraction Cut \\
+         &            	        &                & $N_{task} \ge 20$ \\
+\hline
+01       & smooth or features   &  -                  & -                 \\
+02       & edge on              & 01, 12              & $p_{\rm clumpy,no}>0.55$              \\
+03       & bar		            & 01, 12, 02          & $p_{\rm edgeon,no}>$                 \\
+         &                      & 01, 12, 16, 15      & $p_{\rm arrangement,spiral}>$         \\
+04       & spiral arms          & 01, 12, 02          & $p_{\rm edgeon,no}>$                  \\
+         &                      & 01, 12, 16, 15      & $p_{\rm arrangement,spiral}>$         \\
+05       & bulge prominence     & 01, 12, 02          & $p_{\rm edgeon,no}>$                 \\
+         &                      & 01, 12, 16, 15      & $p_{\rm arrangement,spiral}>$         \\
+06       & odd yes/no           & -                   &                   \\
+07       & rounded              & 01                  & $p_{\rm smooth}>0.45$               \\
+08       & odd feature          & 06                  & $p_{\rm odd,yes}>$                  \\
+09       & bulge shape          & 01, 12, 02          & $p_{\rm edgeon,yes}>$               \\
+10       & arms winding         & 01, 12, 02, 04      & $p_{\rm spiral,yes}>$                  \\
+         &                      & 01, 12, 16, 15, 04  & $p_{\rm spiral,yes}>$                  \\
+11       & arms number          & 01, 12, 02, 04      & $p_{\rm spiral,yes}>$                 \\
+         &                      & 01, 12, 16, 15, 04  & $p_{\rm spiral,yes}>$                  \\
+12       & clumpy               & 01                  & $p_{\rm features}>0.52$              \\
+13       & bright clump         & 01, 12, 16          & $p_{\rm one clump}<$                 \\
+14       & bright central clump & 01, 12, 16, 13      & $p_{\rm bright clump,yes}>$           \\
+15       & clump arrangement    & 01, 12, 16          & $p_{\rm one clump}<$                \\
+16       & clump count          & 01, 12              & $p_{\rm clumpy,yes}>0.55$              \\
+17       & clumps symmetrical   & 01, 12, 16          & $p_{\rm one clump}<$                \\
+18       & clumps embedded      & 01, 12, 16          &  $p_{\rm one clump}<$                 \\
+
+\hline\hline
+\end{tabular}
+\end{table*}
 
@@
 
-Summarize the broad trends that are seen regarding the fraction of galaxies with various morphologies, how that relates to color, size, etc.
-Briefly discuss results as compared with literature and theory.
+{\note \it Summarize the broad trends that are seen regarding the fraction of galaxies with various morphologies, how that relates to color, size, etc.
+Briefly discuss results as compared with literature and theory.}
 

### 2016-04-15 writeup/gz_hubble_data.tex
Forcing in @Mel23's changes to threshold table

@@
 The flexibility of this catalog allows the user to set their own selection criteria for vote fraction thresholds to create a morphologically-pure sample.
-In Table~\ref{tab:prev_tasks} we offer baseline cuts for selecting galaxies of a variety of morphologies.
+In Table~\ref{tbl:thresholds} we offer baseline cuts for selecting galaxies of a variety of morphologies.
 {\note As an example: to select barred galaxies, one should select objects with $p_{\rm features}>0.52, p_{\rm clumpy,no} > 0.55,$ and $p_{edgeon,no}>x.xx$ \emph{or} objects with $p_{\rm features}>0.52, p_{\rm clumpy,yes} > x.xx, (p_{\rm clump~count, 3}+p_{\rm clump~count,4}+p_{\rm clump~count,>4}+p_{\rm clump~count,can't~tell})>x.xx,$ and $p_{\rm clump~arrangement,spiral}>x.xx.$} These cuts define a sample of galaxies of ``bar candidates''; ie galaxies for which answering the bar question makes physical sense and the vote fraction $p_{\rm bar}$ is well-sampled.
@@
 
-\begin{table*}
-\caption{Cookbook \label{tab:prev_tasks}}
+\begin{table}
+\caption{Suggested thresholds for selecting morphological samples from Galaxy Zoo: Hubble \label{tbl:thresholds}}
 \begin{tabular}{llll}
 \hline\hline
-Task No. &  Task 	        & Previous Task  & Vote Fraction Cut \\
-         &            	        &                & $N_{task} \ge 20$ \\
+No.      &  Task 	            & Previous              & Vote fraction threshold            \\
+         &            	        & task(s)               & $N_{\rm task} \ge 20$              \\
 \hline
-01       & smooth or features   &  -                  & -                 \\
-02       & edge on              & 01, 12              & $p_{\rm clumpy,no}>0.55$              \\
-03       & bar		            & 01, 12, 02          & $p_{\rm edgeon,no}>$                 \\
-         &                      & 01, 12, 16, 15      & $p_{\rm arrangement,spiral}>$         \\
-04       & spiral arms          & 01, 12, 02          & $p_{\rm edgeon,no}>$                  \\
-         &                      & 01, 12, 16, 15      & $p_{\rm arrangement,spiral}>$         \\
-05       & bulge prominence     & 01, 12, 02          & $p_{\rm edgeon,no}>$                 \\
-         &                      & 01, 12, 16, 15      & $p_{\rm arrangement,spiral}>$         \\
-06       & odd yes/no           & -                   &                   \\
-07       & rounded              & 01                  & $p_{\rm smooth}>0.45$               \\
-08       & odd feature          & 06                  & $p_{\rm odd,yes}>$                  \\
-09       & bulge shape          & 01, 12, 02          & $p_{\rm edgeon,yes}>$               \\
-10       & arms winding         & 01, 12, 02, 04      & $p_{\rm spiral,yes}>$                  \\
-         &                      & 01, 12, 16, 15, 04  & $p_{\rm spiral,yes}>$                  \\
-11       & arms number          & 01, 12, 02, 04      & $p_{\rm spiral,yes}>$                 \\
-         &                      & 01, 12, 16, 15, 04  & $p_{\rm spiral,yes}>$                  \\
-12       & clumpy               & 01                  & $p_{\rm features}>0.52$              \\
-13       & bright clump         & 01, 12, 16          & $p_{\rm one clump}<$                 \\
-14       & bright central clump & 01, 12, 16, 13      & $p_{\rm bright clump,yes}>$           \\
-15       & clump arrangement    & 01, 12, 16          & $p_{\rm one clump}<$                \\
-16       & clump count          & 01, 12              & $p_{\rm clumpy,yes}>0.55$              \\
-17       & clumps symmetrical   & 01, 12, 16          & $p_{\rm one clump}<$                \\
-18       & clumps embedded      & 01, 12, 16          &  $p_{\rm one clump}<$                 \\
-
+01       & smooth or features   & $-$                   & $-$                                \\
+02       & edge on              & 01, 12                & $p_{\rm clumpy,no}>0.30$            \\
+03       & bar		            & 01, 12, 02            & $p_{\rm edgeon,no}>0.25$           \\
+         &                      & 01, 12, 16, 15        & $p_{\rm clumpy~spiral}>0.65$  \\
+04       & spiral arms          & 01, 12, 02            & $p_{\rm edgeon,no}>0.25$           \\
+         &                      & 01, 12, 16, 15        & $p_{\rm clumpy~spiral}>0.65$  \\
+05       & bulge prominence     & 01, 12, 02            & $p_{\rm edgeon,no}>0.25$           \\
+         &                      & 01, 12, 16, 15        & $p_{\rm clumpy~spiral}>0.65$  \\
+06       & odd yes/no           & $-$                   & $-$                                \\
+07       & rounded              & 01                    & $p_{\rm smooth}>0.70$               \\
+08       & odd feature          & 06                    & $p_{\rm odd,yes}> 0.50$            \\
+09       & bulge shape          & 01, 12, 02            & $p_{\rm edgeon,yes}>0.40$           \\
+10       & arms winding         & 01, 12, 02, 04        & $p_{\rm spiral,yes}>0.25$          \\
+11       & arms number          & 01, 12, 02, 04        & $p_{\rm spiral,yes}>0.25$          \\
+12       & clumpy               & 01                    & $p_{\rm features}>0.23$            \\
+13       & bright clump         & 01, 12, 16            & $p_{\rm one~clump}< 0.40$           \\
+14       & bright central clump & 01, 12, 16, 13        & $p_{\rm bright~clump,yes}>0.50$     \\
+15       & clump arrangement    & 01, 12, 16            & $p_{\rm multiple~clumps}>0.45$     \\
+16       & clump count          & 01, 12                & $p_{\rm clumpy,yes}>0.80$           \\
+17       & clumps symmetrical   & 01, 12                & $p_{\rm clumpy,yes}>0.80$           \\
+18       & clumps embedded      & 01, 12                & $p_{\rm clumpy,yes}>0.80$           \\
 \hline\hline
 \end{tabular}
-\end{table*}
+\end{table}
 

### 2016-04-15 writeup/gz_hubble_data.tex
Description of user weights from @bamford. Closes #40.

@@
 Users' votes are weighted slightly \citep[in a method identical to that described in][]{wil13} such that users who frequently disagree with all other users end up having very low weights.
-The majority of users have weights very close to $w=1.0$
-
-{\note STEVEN: Is this true for GZH - do you have a plot of the distribution of user weights or consistencies we can include here?}.
+The user weighting $w$ is 1 for the top 95\% of users as ranked by consistency.
+For the bottom 5\% of users, $w$ drops smoothly and is effectively zero for only the bottom 1\% of classifiers in the CDF.
+The overall effect on the GZH dataset is relatively small, but this method is effective at filtering out contributions from random or delibrately malicious classifiers.
 

### 2016-04-18 writeup/gz_hubble_data.tex
Adding references for comparison HST catalogs

@@
 
-For images from the ACS-GC \citet{gri12}, galaxies are identified using a combination of \sextractor{} \citep{ber96} and the galaxy-profile fitting framework \textsc{Galapagos} \citep{hau07}.
+For images from the ACS-GC \citet{gri12}, galaxies are identified using a combination of \sextractor{} \citep{ber96} and the galaxy-profile fitting framework \textsc{Galapagos} \citep{bar12}.
 We selected all galaxies with $m < 23.5$, where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS, GEMS + GOODS-S, and GOODS-N surveys, respectively.
@@
 
-\subsection{Effect of changing depth (GOODS, Stripe 82)}
+%\subsection{Effect of changing depth (GOODS, Stripe 82)}
 
@@
     \item Zajmoski (COSMOS)
-    \item GEMS morphologies?
-    \item AEGIS morphologies?
-    \item GOODS N/S morphologies?
-    \item expert visual inspection?
+    \item GEMS morphologies \citep{hau07}
+    \item AEGIS morphologies \citep{lot08}
+    \item GOODS N/S morphologies \citep{bun05}
 \end{itemize}

### 2016-04-18 writeup/gz_hubble_data.tex
GEMS/GZH comparison, part 1

@@
 \usepackage{url}
+\usepackage[normalem]{ulem}
 \bibliographystyle{mn2e}
 
-\input{gzh_macros.tex}
+\input{macros.tex}
 
@@
     \item Zajmoski (COSMOS)
-    \item GEMS morphologies \citep{hau07}
+    \item \sout{GEMS morphologies} \citep{hau07}
     \item AEGIS morphologies \citep{lot08}
@@
 \end{itemize}
+
+Morphologies for galaxies in GEMS imaging have been measured by \citet{hau07}, who perform a careful comparison of single-component \sersic{} fits to the F850LP imaging using both the \galfit{} and \gimtwod{} codes.
+We compare the GZH morphological vote fractions to the \galfit{} parameters, which are evaluated by \citet{hau07} as more reliable due to \galfit's ability to fit multiple galaxies and handle crowded fields.
+
+A single \sersic{} fit is often a poor fit to the light profile of a resolved galaxy, since large numbers of classical spirals have both a de~Vaucouleurs bulge at the center and an exponential disc at larger radii.
+If a single parameter is used, however, a common division in the literature is to split on the \sersic~index $n$ into disc-dominated galaxies ($n<2.5$) and bulge-dominated galaxies ($n>2.5$), where $n$ is the exponent in the radial surface brightness profile such that $\Sigma(r)=\Sigma_e \exp{\left(-\kappa[(r/r_e)^{1/n} - 1]\right)}$.
+
+A 1\arcsec~positional match for the GEMS galaxies in Table~9 in \citet{hau07} to the GZH sample gives 8,846~galaxies found in both samples.
+We analyze galaxies for which the \galfit{} parameters are flagged as being constrained within plausible physical limits, indicating a moderately robust fit.
+There is a strong correlation between $n$ and \pbest; the average value for disk-dominated galaxies ($n<2.5$) is $\langle$\pbest$\rangle=0.44\pm0.26$, compared to $\langle$\pbest$\rangle=0.30\pm0.25$ for bulge-dominated galaxies ($n>2.5$).
+The correlation is stronger for bulge-dominated galaxies; for $n>2.5$, most galaxies have \pbest$<0.2$.
+In contrast, while $n<2.5$ do have higher \pbest~values, the spread is larger and there are significant numbers of galaxies even at the highest \pbest{} values.
+
+Inverting the comparison, we split the GZH galaxies into three samples: ``clean'' disks (\pbest$\ge0.8$), ``clean'' ellipticals (\pbest$\le0.2$), and ``intermediate'' ($0.2<$\pbest$<0.8$) galaxies \citep[eg,][]{sch14}.
+Splitting by $n<2.5/n>2.5$, clean disks are $85\%/17\%$, intermediates $84\%/16\%$, and clean ellipticals $59\%/41\%$.
+There is a strong dependence for these ratios on the brightness of the galaxy, which affects both automatic fits and visual accuracy.
+Limiting the sample to galaxies with $m_{850LP}<21$ gives fractions of: clean disks are $77\%/23\%$, intermediates $52\%/48\%$, and clean ellipticals $38\%/62\%$.
+While the clean disk fraction is largely unchanged, intermediates are more evenly balanced and there is a larger population of smooth galaxies with high $n$, as expected.
+
+Clumpy galaxies in GZH have $n$ and $R_e$ \galfit{} parameters more consistent with disky, $n<2.5$ galaxies than spheroids (Figure~\ref{fig:clumpy_gems}).
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.50\textwidth]{figures/gems_clumpy.png}
+\caption{Parameter distributions for GEMS galaxies in \citet{hau07} and GZH.
+Red and blue points indicate galaxies split by their \sersic~index into disk- and bulge-dominated galaxies.
+Galaxies identified as ``clumpy'' in GZH are labeled in green.}
+\label{fig:clumpy_gems}
+\end{center}
+\end{figure}
 

### 2016-04-19 writeup/gz_hubble_data.tex
GEMS/GZH comparison, part 2

@@
 
-Clumpy galaxies in GZH have $n$ and $R_e$ \galfit{} parameters more consistent with disky, $n<2.5$ galaxies than spheroids (Figure~\ref{fig:clumpy_gems}).
+We visually inspect galaxies for which the \galfit{} and GZH measurements indicate strong disagreement.
+Of the 84~galaxies with $n>2.5$ and \pbest$\ge0.80$, almost all are spirals with obvious disks and clearly marked spiral arms.
+These appear to be cases where \galfit{} fits the bulge at the center, but misses extended emission from the disk.
+We also examine the 35~galaxies with $n<2.5$ and \pbest$\le0.20$; these galaxies generally have smoother light profiles with no spiral arms, although several have bars and/or the sharper truncation of light near the edges that indicates an S0 galaxy.
+These galaxies are also significantly bluer $(\langle m_{606}-m_{850}\rangle=0.27\pm3.3)$ compared to the majority of galaxies classified as ``smooth'' in GZH $(\langle m_{606}-m_{850}\rangle=1.2\pm1.7)$.
+We interpret this as evidence for the fact that single-component radial fits are often inadequate to accurately characterize galaxy morphology, and that a simple cut risks significant amounts of misclassified objects.
+
+Clumpy galaxies in GZH have \galfit{} parameters more consistent with disky, $n<2.5$ galaxies than spheroids (Figure~\ref{fig:clumpy_gems}).
+Using the thresholds in Table~\ref{tbl:thresholds}, GZH clumpy galaxies have average values of $n=1.6\pm1.2$ and $R_e=32\pm16$~pix, with only 11\% of clumpy galaxies falling in the bulge-dominated region of $n>2.5$.
 
@@
 \caption{Parameter distributions for GEMS galaxies in \citet{hau07} and GZH.
-Red and blue points indicate galaxies split by their \sersic~index into disk- and bulge-dominated galaxies.
+Red and blue points indicate galaxies split by their \sersic~index (at $n=2.5$) into disk- and bulge-dominated galaxies, respectively.
 Galaxies identified as ``clumpy'' in GZH are labeled in green.}

### 2016-04-21 writeup/gz_hubble_data.tex
Comparison of AEGIS galaxies

@@
     \item \sout{GEMS morphologies} \citep{hau07}
-    \item AEGIS morphologies \citep{lot08}
+    \item \sout{AEGIS morphologies} \citep{lot08}
     \item GOODS N/S morphologies \citep{bun05}
 \end{itemize}
+
+{\note \textit{Address trends seen in broad morphological classes, possible reasons for difference.
+Also should attempt to map between the GZH vote fractions and whatever classification systems are used in the above systems.}}
+
+\subsubsection{GEMS}
 
@@
 Using the thresholds in Table~\ref{tbl:thresholds}, GZH clumpy galaxies have average values of $n=1.6\pm1.2$ and $R_e=32\pm16$~pix, with only 11\% of clumpy galaxies falling in the bulge-dominated region of $n>2.5$.
+
+\subsubsection{AEGIS}
+
+Galaxies in AEGIS were morphologically classified using non-parametric measurements by \citet{lot08}.
+They use the Gini coefficient ($G$), which measures the relative inequality in pixel brightness, and $M_{20}$, the second-order moment of the brightest 20\% of the light \citep{lot04}.
+A linear combination of $G$ and $M_{20}$ to delineate three broad categories of galaxy morphology: E/S0/Sa (bulge-dominated/spheroids), Sb/Sc/Ir (disk-dominated/irregulars), and mergers.
+
+We compare the GZH vote fractions to the morphological categories defined by their $G$-$M_{20}$ values, which are measured in both $V$- and $I$-band.
+A 1\arcsec{} positional match on AEGIS from \citet{lot08} and GZH yields 7,508~galaxies; of those, we analyze a subsample of 4,031 with reliably-measured morphologies and $S/N>3$ in both bands.
+
+The GZH morphologies are reasonably correlated with the $G$-$M_{20}$ morphological categories.
+For galaxies labeled as Sb/Sc/Ir by \citet{lot08}, 58\% of the galaxies in $I$-band (61\% in $V$-band) have \pbest{} above a nominal cut of 0.5.
+E/S0/Sa galaxies have a tighter relation, with 78\% of galaxies in $I$-band (79\% in $V$-band) having $p_\mathrm{smooth}>0.5$.
+Galaxies with high \pbest{} are largely concentrated in the E/S0/Sa region of $G$-$M_{20}$ space; the small overlaps into mergers and E/S0/Sa are close to what we expect for loosely defined boundaries.
+Galaxies with low \pbest{} have a much broader range of $G$-$M_{20}$ values, with nearly half lying well within the Sb/Sc/Ir region.
+
+Of the 47~galaxies identified by GZH as mergers in the cross-matched AEGIS sample (selected as \pmerger$>0.5$ and $N_\mathrm{merger}\ge20$), roughly two-thirds fall in the merger region of $G$-$M_{20}$ space defined in \citet{lot08}; almost all the remainder would be classified as Sb/Sc/Ir.
+Galaxies identified as mergers by $G$-$M_{20}$, in contrast, typically have lower \pmerger{} values; 66\%/50\% in $V$-band and $I$-band, respectively.
+While the total number of mergers identified in GZH is roughly $\times10$ fewer than the volume-limited $G$-$M_{20}$ sample, we do confirm the result of a non-evolving merger fraction between $0.2<z<1.2$.
+%The average bulge statistic for the GZH mergers \citep[as defined in][]{sny15} is $F=-0.3\pm0.5$ in $V$-band and $F=-0.2\pm0.5$ in $I$-band.
 
@@
 
-{\note \textit{Address trends seen in broad morphological classes, possible reasons for difference.
-Also should attempt to map between the GZH vote fractions and whatever classification systems are used in the above systems.}}
-
 \section{Summary}\label{sec:summary}
@@
 We thank Meg Schwamb and the ASIAA for hosting the ``Citizen Science in Astronomy'' workshop, 3-7 Mar 2014 in Taipei, Taiwan, at which some of this analysis was done.
+We also thank Jennifer Lotz for sharing her $G$-$M_{20}$ measurements for the AEGIS sample.
 

### 2016-04-21 writeup/gz_hubble_data.tex
Switching from mn2e to emulateapj

@@
-%\documentclass[twocolumn]{emulateapj}
-%\documentclass[12pt,preprint]{aastex}
-\documentclass[usenatbib]{mn2e}
-
-\voffset-1.25cm
+\documentclass[twocolumn]{aastex6}
+
+%% The other main article choice is a tightly typeset, two-column article
+%% that more closely resembles the final typeset pdf article.
+%%
+%% \documentclass[twocolumn]{aastex6}
+%% 
+%% There are other optional arguments one can envoke to allow other 
+%% actions. 
+%%
+% These are the available options:
+%   manuscript	: onecolumn, doublespace, 12pt fonts
+%   preprint	: onecolumn, single space, 10pt fonts
+%   preprint2	: twocolumn, single space, 10pt fonts
+%   twocolumn	: a two column article. Probably not needed, but here just in case.
+%   onecolumn	: a one column article; default option.
+%   twocolappendix: make 2 column appendix
+%   onecolappendix: make 1 column appendix is the default. 
+%   astrosymb	: Loads Astrosymb font and define \astrocommands. 
+%   tighten	: Makes baselineskip slightly smaller
+%   times	: uses times font instead of the default
+%   linenumbers	: turn on lineno package.
+%   trackchanges : required to see the revision mark up and print output
+%   numberedappendix: Labels appendix sections A, B, ... This is the default.
+%   appendixfloats: Needed. Resets figure and table counters to zero
+
+%% these can be used in any combination, e.g.
+%%
+%% \documentclass[twocolumn,twocolappendix,linenumbers,trackchanges]{aastex6}
+
+\shorttitle{Galaxy Zoo: Hubble}
+\shortauthors{Willett et al.}
+
+%% This is the end of the preamble.  Indicate the beginning of the
+%% paper itself with \begin{document}.
 
@@
 \usepackage{subfigure}
-\usepackage{deluxetable}
 \usepackage{url}
@@
 
-\title[Galaxy Zoo Hubble Data]{Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging}
-\author[Lead Author \etal]{Lead Author and other Galaxy Zoo science team members\\
+%% LaTeX will automatically break titles if they run longer than
+%% one line. However, you may use \\ to force a line break if
+%% you desire.
+
+\title{Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging}
+%% Use \author, \affil, plus the \and command to format author and affiliation 
+%% information.  If done correctly the peer review system will be able to
+%% automatically put the author and affiliation information from the manuscript
+%% and save the corresponding author the trouble of entering it by hand.
+%%
+%% The \affil should be used to document primary affiliations and the
+%% \altaffil should be used for secondary affiliations, titles, or email.
+
+%% Authors with the same affiliation can be grouped in a single
+%% \author and \affil call.
+\author{Kyle W.
+Willett\altaffilmark{1,2}, Melanie A.
+Galloway\altaffilmark{1}, Chris J.
+Lintott\altaffilmark{3}, B.D.
+Simmons\altaffilmark{3,4,5,6}, Karen L.
+Masters\altaffilmark{7,8}, Tom Melvin\altaffilmark{7}, Steven P.
+Bamford\altaffilmark{9}, Edward M.
+Edmondson\altaffilmark{7}, Lucy F.
+Fortson\altaffilmark{1}, Kevin Schawinski\altaffilmark{10}, Edmond Cheung\altaffilmark{11}, Claudia Scarlata\altaffilmark{1}, Melanie Beck\altaffilmark{1}, Arfon M.
+Smith\altaffilmark{3,12,13}, Michael Parrish\altaffilmark{12}, Roger L.
+Griffith\altaffilmark{14,15}, Anna Han\altaffilmark{16}
+}
 %
@@
 %$^8$Einstein Fellow\\
-\\
- $^*$This publication has been made possible by the participation of more than 200,000 volunteers in the Galaxy Zoo project.
-\\ Their contributions are individually acknowledged at \texttt{http://authors.galaxyzoo.org/authors.html}.
-\\
-\\
-{\tt E-mail: lead.author@university.edu}
- }
-
-%\date{Accepted for publication in MNRAS, 7th October 2010.}
-%\pagerange{1--10} \pubyear{2010}
-
-\maketitle
-
+
+%\altaffiltext{1}{School of Physics and Astronomy, University of Minnesota, USA}
+%\altaffiltext{2}{Department of Physics and Astronomy, University of Kentucky, USA}
+%\altaffiltext{3}{Oxford Astrophysics, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK}
+%\altaffiltext{4}{Center for Astrophysics and Space Sciences (CASS), Department of Physics, University of California, San Diego, CA 92093, USA}
+%\altaffiltext{5}{Balliol College}
+%\altaffiltext{6}{Einstein Fellow}
+%\altaffiltext{7}{Institute of Cosmology and Gravitation, University of Portsmouth, UK}
+%\altaffiltext{8}{SEPnet, South East Physics Network, UK}
+%\altaffiltext{9}{University of Nottingham, UK}
+%\altaffiltext{10}{ETH Z\"urich, Switzerland}
+%\altaffiltext{11}{Kavli Institute for the Physics and Mathematics of the Universe (WPI), Japan}
+%\altaffiltext{12}{Adler Planetarium, USA}
+%\altaffiltext{13}{GitHub}
+%\altaffiltext{14}{University of California, Berkeley, USA}
+%\altaffiltext{15}{Penn State University, USA}
+%\altaffiltext{16}{Yale University, USA}
+
+%% Mark off the abstract in the ``abstract'' environment. 
 \begin{abstract}
 
-This will be the data release paper for GZ:Hubble. We present the classifications, the methodology for data reduction and corrections for redshift dependent biases in the observed morphologies.
+% Note: 250-word limit
+This is the data release paper for GZ:Hubble\footnote{This publication has been made possible by the participation of more than 200,000 volunteers in the Galaxy Zoo project.
+Their contributions are individually acknowledged at \url{http://authors.galaxyzoo.org/authors.html}.}.
+We present the classifications, the methodology for data reduction and corrections for redshift dependent biases in the observed morphologies.
 
@@
 
-%\keywords{galaxies: distances and redshifts --- galaxies: clusters --- galaxies: fundamental parameters --- distance scale --- cosmological parameters}
-
-\section{Introduction}
+%% Keywords should appear after the \end{abstract} command. 
+%% See the online documentation for the full list of available subject
+%% keywords and the rules for their use.
+\keywords{galaxies --- catalogs --- surveys}
+
+\section{Introduction} \label{sec:intro}
 
@@
 \tabletypesize{\scriptsize}
-\begin{deluxetable}{l|rr|rrr|rr|r|rr}
-\centering
-\rotate
+\begin{deluxetable*}{l|rr|rrr|rr|r|rr}
 \tablecolumns{12}
@@
 \enddata
-\end{deluxetable}
+\end{deluxetable*}
 
@@
 \tabletypesize{\scriptsize}
-\begin{deluxetable}{lllcrllllll|c}
+\begin{deluxetable*}{lllcrllllll|c}
 \centering
-\rotate
 \tablecolumns{13}
@@
 A subset of the information is shown here to illustrate form and content.}
-\end{deluxetable}
+\end{deluxetable*}
 
@@
 A subset of the information is shown here to illustrate form and content.}
-\end{deluxetable}
-
-\tabletypesize{\scriptsize}
-\begin{deluxetable}{lllcrllllll|c}
+\end{deluxetable*}
+
+\tabletypesize{\scriptsize}
+\begin{deluxetable*}{lllcrllllll|c}
 \centering
-\rotate
 \tablecolumns{13}
@@
 A subset of the information is shown here to illustrate form and content.}
-\end{deluxetable}
-
-\tabletypesize{\scriptsize}
-\begin{deluxetable}{lllcrllll|c}
+\end{deluxetable*}
+
+\tabletypesize{\scriptsize}
+\begin{deluxetable*}{lllcrllll|c}
 \centering
-\rotate
 \tablecolumns{13}
@@
 A subset of the information is shown here to illustrate form and content.}
-\end{deluxetable}
-
-\tabletypesize{\scriptsize}
-\begin{deluxetable}{lllccccrrrrrrr|c}
+\end{deluxetable*}
+
+\tabletypesize{\scriptsize}
+\begin{deluxetable*}{lllccccrrrrrrr|c}
 \centering
-\rotate
 \tablecolumns{14}
@@
 Department of Energy, the National Aeronautics and Space Administration, the Japanese Monbukagakusho, the Max Planck Society, and the Higher Education Funding Council for England.
-The SDSS website is http://www.sdss.org/.
+The SDSS website is \url{http://www.sdss.org/}.
 

### 2016-04-22 writeup/gz_hubble_data.tex
GOODS comparisons to Bundy et al. (2005)

@@
 
-\subsection{Comparison to other catalogs}
+\subsection{Comparison to other catalogs}\ref{ssec:comparisons}
 
@@
     \item \sout{AEGIS morphologies} \citep{lot08}
-    \item GOODS N/S morphologies \citep{bun05}
+    \item \sout{GOODS N/S morphologies} \citep{bun05}
 \end{itemize}
@@
 Using the thresholds in Table~\ref{tbl:thresholds}, GZH clumpy galaxies have average values of $n=1.6\pm1.2$ and $R_e=32\pm16$~pix, with only 11\% of clumpy galaxies falling in the bulge-dominated region of $n>2.5$.
-
-\subsubsection{AEGIS}
-
-Galaxies in AEGIS were morphologically classified using non-parametric measurements by \citet{lot08}.
-They use the Gini coefficient ($G$), which measures the relative inequality in pixel brightness, and $M_{20}$, the second-order moment of the brightest 20\% of the light \citep{lot04}.
-A linear combination of $G$ and $M_{20}$ to delineate three broad categories of galaxy morphology: E/S0/Sa (bulge-dominated/spheroids), Sb/Sc/Ir (disk-dominated/irregulars), and mergers.
-
-We compare the GZH vote fractions to the morphological categories defined by their $G$-$M_{20}$ values, which are measured in both $V$- and $I$-band.
-A 1\arcsec{} positional match on AEGIS from \citet{lot08} and GZH yields 7,508~galaxies; of those, we analyze a subsample of 4,031 with reliably-measured morphologies and $S/N>3$ in both bands.
-
-The GZH morphologies are reasonably correlated with the $G$-$M_{20}$ morphological categories.
-For galaxies labeled as Sb/Sc/Ir by \citet{lot08}, 58\% of the galaxies in $I$-band (61\% in $V$-band) have \pbest{} above a nominal cut of 0.5.
-E/S0/Sa galaxies have a tighter relation, with 78\% of galaxies in $I$-band (79\% in $V$-band) having $p_\mathrm{smooth}>0.5$.
-Galaxies with high \pbest{} are largely concentrated in the E/S0/Sa region of $G$-$M_{20}$ space; the small overlaps into mergers and E/S0/Sa are close to what we expect for loosely defined boundaries.
-Galaxies with low \pbest{} have a much broader range of $G$-$M_{20}$ values, with nearly half lying well within the Sb/Sc/Ir region.
-
-Of the 47~galaxies identified by GZH as mergers in the cross-matched AEGIS sample (selected as \pmerger$>0.5$ and $N_\mathrm{merger}\ge20$), roughly two-thirds fall in the merger region of $G$-$M_{20}$ space defined in \citet{lot08}; almost all the remainder would be classified as Sb/Sc/Ir.
-Galaxies identified as mergers by $G$-$M_{20}$, in contrast, typically have lower \pmerger{} values; 66\%/50\% in $V$-band and $I$-band, respectively.
-While the total number of mergers identified in GZH is roughly $\times10$ fewer than the volume-limited $G$-$M_{20}$ sample, we do confirm the result of a non-evolving merger fraction between $0.2<z<1.2$.
-%The average bulge statistic for the GZH mergers \citep[as defined in][]{sny15} is $F=-0.3\pm0.5$ in $V$-band and $F=-0.2\pm0.5$ in $I$-band.
 
@@
 
+\subsubsection{AEGIS}
+
+Galaxies in AEGIS were morphologically classified using non-parametric measurements by \citet{lot08}.
+They use the Gini coefficient ($G$), which measures the relative inequality in pixel brightness, and $M_{20}$, the second-order moment of the brightest 20\% of the light \citep{lot04}.
+A linear combination of $G$ and $M_{20}$ to delineate three broad categories of galaxy morphology: E/S0/Sa (bulge-dominated/spheroids), Sb/Sc/Ir (disk-dominated/irregulars), and mergers.
+
+We compare the GZH vote fractions to the morphological categories defined by their $G$-$M_{20}$ values, which are measured in both $V$- and $I$-band.
+A 1\arcsec{} positional match on AEGIS from \citet{lot08} and GZH yields 7,508~galaxies; of those, we analyze a subsample of 4,031 with reliably-measured morphologies and $S/N>3$ in both bands.
+
+The GZH morphologies are reasonably correlated with the $G$-$M_{20}$ morphological categories.
+For galaxies labeled as Sb/Sc/Ir by \citet{lot08}, 58\% of the galaxies in $I$-band (61\% in $V$-band) have \pbest{} above a nominal cut of 0.5.
+E/S0/Sa galaxies have a tighter relation, with 78\% of galaxies in $I$-band (79\% in $V$-band) having $p_\mathrm{smooth}>0.5$.
+Galaxies with high \pbest{} are largely concentrated in the E/S0/Sa region of $G$-$M_{20}$ space; the small overlaps into mergers and E/S0/Sa are close to what we expect for loosely defined boundaries.
+Galaxies with low \pbest{} have a much broader range of $G$-$M_{20}$ values, with nearly half lying well within the Sb/Sc/Ir region.
+
+Of the 47~galaxies identified by GZH as mergers in the cross-matched AEGIS sample (selected as \pmerger$>0.5$ and $N_\mathrm{merger}\ge20$), roughly two-thirds fall in the merger region of $G$-$M_{20}$ space defined in \citet{lot08}; almost all the remainder would be classified as Sb/Sc/Ir.
+Galaxies identified as mergers by $G$-$M_{20}$, in contrast, typically have lower \pmerger{} values; 66\%/50\% in $V$-band and $I$-band, respectively.
+While the total number of mergers identified in GZH is roughly $\times10$ fewer than the volume-limited $G$-$M_{20}$ sample, we do confirm the result of a non-evolving merger fraction between $0.2<z<1.2$.
+%The average bulge statistic for the GZH mergers \citep[as defined in][]{sny15} is $F=-0.3\pm0.5$ in $V$-band and $F=-0.2\pm0.5$ in $I$-band.
+
+\subsubsection{GOODS}
+
+Galaxies in the GOODS-N and GOODS-S fields down to a limit of $z_{AB}=22.5$ have been visually classified by a single expert (R.S.~Ellis), inspecting both $z$-band and composite $Viz$ color images \citep{bun05}.
+These morphologies are assigned a numerical value based on categories in \citet{bri98a}; these are combined into broader categories of ``E/S0'' (classes 0,1,2), ``Spirals'' (classes 3,4,5), and ``Peculiar/Irregular'' (classes 6,7,8).
+\citet{bun05} use these morphologies to show that there are an increasing proportion of early-type galaxies observed at later times.
+
+Matching the \citet{bun05} catalog to GZH with a 0.5\arcsec{} radius yields 2435 galaxies (1300 in GOODS-N, 1135 in GOODS-S).
+We compare their broad morphological categories to \pbest{} in GZH; demographics of the separate GOODS-N and GOODS-S samples are highly consistent.
+``E/S0'' galaxies are dominated by high smooth fractions in GZH, with an average value of $\langle p_\mathrm{smooth,best}\rangle=0.54\pm0.20$.
+The effect is stronger when examining sub-divisions; pure E galaxies have the highest $p_\mathrm{smooth,best}$ values, while S0 have the lowest.
+Visual inspection of galaxies designated as S0 show numerous examples of both edge-on galaxies and visible substructure in the disk, including spiral arms.
+This is consistent with the design of the GZH decision tree, and likely reflects that the expert categories are using different criteria.
+
+``Spiral'' galaxies in \citet{bun05} have robustly high GZH vote fractions of features and/or disks, with $\langle p_\mathrm{features,best}\rangle=0.59\pm0.06$.
+The vote fraction increases with Hubble type, with Scd galaxies having the highest average \pbest{} values.
+``Peculiar/Irregular'' galaxies have similar ranges of \pbest{} to the ``Spiral'' galaxies, but can be sub-selected with cutoffs on $p_\mathrm{odd}$ and $p_\mathrm{irregular}$ or $p_\mathrm{merger}$.
+We note that mergers are not strongly correlated in GZH and the expert visual classifications; between 20\%--30\% have GZH merger fractions of zero, while even clear tidal tails can be as low as $p_\mathrm{merger}\sim0.1$.
+The total number of major mergers is small enough that expert visual inspection can be practically done on all candidates; a combination of methods may be the most accurate way of identifying these rarer objects, especially when the signs of interaction are relatively subtle.
+
 \section{Summary}\label{sec:summary}
@@
 
-\paragraph*{ACKNOWLEDGEMENTS.}
+\acknowledgments
 

### 2016-04-26 writeup/gz_hubble_data.tex
added text to section 6 using the catalog

@@
 We stress that the selection process will vary based on the particular science case.
-
-To select galaxies of a morphological type identified with a Task offered in the decision tree (see Figure~\ref{fig:decisiontree}, a cut is placed on the vote fraction for that Task ($p_{\rm task}$), as well as the vote fractions for the Tasks preceding it.
+More conservative cuts can be applied to create pure, but not necessarily complete, samples.
+These are useful for selecting galaxies exhibiting unique morphologies for individual case studies or observing proposals.
+Looser cuts can be applied to obtain samples with a higher level of completeness, which will increase the sample size but can potentially decrease purity.
+Population studies would make use of such large samples, in which statistical significance is a crucial factor in evaluating results.
+\citet{mas11c,mel14}, and \citet{gal15} are examples of GZ papers which select morphologies in this way.
+
+In GZH, volunteers answer questions about a galaxy's morphology in a decision tree format.
+With this structure, questions shown to a user are dependent on their answers to the previous questions.
+For example, a user is only asked Task 11, ``How many spiral arms?'' if they had answered ``yes'' to Task 10, which asks whether any spiral arms are present.
+This structure is used to reduce the workload of the users by only asking questions relevant to the particular galaxy; in this example, it would not be useful, nor would it make physical sense, to ask a user how many spiral arms in a galaxy which they had declared had no spiral arms to begin with.
+Figure~\ref{fig:decisiontree} shows the possible paths available for answering the questions offered in GZH.
+The colors represent the tier level of Tasks, which indicate the number of previous Tasks the given Task is dependent upon.
+The arm-number question, Task 11, is a 5th tier Task, meaning that whether this question is seen by a user is dependent on four Tasks preceding it.
+In this case, it is only shown to volunteers who voted the galaxy was featured/disk-shaped in Task 01, not clumpy in Task 12, not edge-on in Task 02, and had spiral structure in Task 10.
+
+To select galaxies of a morphological type identified with a particular Task, a cut is placed on the vote fraction for that Task ($p_{\rm task}$), \emph{as well as} the vote fractions for the Tasks preceding it, because of the dependency induced by the decision-tree structure.
 For example, to select barred galaxies, a cut may be placed on $p_{\rm bar}$ such that only galaxies where a high fraction of votes for this task voted for the $bar,yes$ answer.
-This is not the only necessary cut, however, since not all users answer this question; only those who have previously selected ``features'' in Task~01, ``not clumpy'' in Task~12, and ``not edge-on'', \emph{or} previously selected ``features'' in Task~01, ``clumpy'' in Task~12, ``$>$ 2 clumps'' in Task~16, and ``spiral arrangement'' in Task~15 will have the opportunity to vote on the bar question, Task~03.
+This is not the only necessary cut, however, since not all users answer this question; only those who have previously selected ``features'' in Task~01, ``not clumpy'' in Task~12, and ``not edge-on'' in Task~02 will have the opportunity to vote on the bar question, Task~03.
 To ensure that $p_{\rm bar}$ is well-sampled, cuts on all previous tasks must be applied.
@@
 In Table~\ref{tbl:thresholds} we offer baseline cuts for selecting galaxies of a variety of morphologies.
-{\note As an example: to select barred galaxies, one should select objects with $p_{\rm features}>0.52, p_{\rm clumpy,no} > 0.55,$ and $p_{edgeon,no}>x.xx$ \emph{or} objects with $p_{\rm features}>0.52, p_{\rm clumpy,yes} > x.xx, (p_{\rm clump~count, 3}+p_{\rm clump~count,4}+p_{\rm clump~count,>4}+p_{\rm clump~count,can't~tell})>x.xx,$ and $p_{\rm clump~arrangement,spiral}>x.xx.$} These cuts define a sample of galaxies of ``bar candidates''; ie galaxies for which answering the bar question makes physical sense and the vote fraction $p_{\rm bar}$ is well-sampled.
-In this example, such galaxies are featured, non-clumpy, non-edge~on galaxies, or featured, clumpy, spiral galaxies.
-At this point a cut can be made on $p_{\rm bar}$ to select a clean sample of only strong bars $p_{\rm bar}>0.8$, or a complete sample of weak and strong bars $p_{\rm bar}>0.3$, or the value most appropriate to the science case.
+We detemined these thresholds by a visual inspection of subsamples.
+For each Task, we first required that at least 20 users voted on the given question.
+We then applied a cut on the vote fraction for the previous task and analyzed a subsample of 50 galaxies meeting these criteria, as well as a control sample of galaxies which had 20 users vote on the task, but did not meet the threshold cut set for the previous task.
+The threshold cut was adjusted and new subsamples were inspected until both the original and control samples achieved $\ge 80\%$ purity.
+
+As an example of how to use Table~\ref{tbl:thresholds} to create a sample of 3-armed spirals galaxies, one should select objects with $N_{arm~number} \ge 20$, $p_{\rm features}>0.23, p_{\rm clumpy,no} > 0.30, p_{edgeon,no}>0.25$, and $p_{spiral,yes}>0.25$.
+These cuts define a sample of galaxies of ``arm number candidates''; ie galaxies for which answering the arm number question makes physical sense and the vote fraction $p_{\rm arm~number}$ is well-sampled.
+In this example, such galaxies are featured, non-clumpy, non-edge~on, spiral galaxies.
+At this point a cut can be made on $p_{\rm arm~number=3}$ to select spirals with three arms.
+
+Tasks 03, 04 and 05 have an additional possible pathway; as shown in Figure~\ref{fig:decisiontree}, a user might also be shown this question if they select ``featured/disk'' in Task 01, ``clumpy'' in Task 12, two or more clumps in Task 16, and ``spiral arrangement'' in Task 15.
+By applying the appropriate thresholds for this path, we find that $< 0.5\%$ of the galaxies which have $\ge 20$ answers to these questions used this pathway to arrive at these Tasks.
+Further, of these subjects, none were found to exhibit disk structure, although the clumps within were arranged in a spiral pattern.
+We therefore do not find this pathway necessary in examining responses to Tasks 03, 04, and 05.
+
+In this section we have described how to use the previous Task thresholds in Table~\ref{tbl:thresholds} to select well-sampled galaxies which may or may not contain the feature associated with a unique Task.
+We will now offer two examples of how to use the vote fractions for the final Task to obtain a sample of galaxies with a certain morpholgical type, by creating a sample of bars and samples of clumpy galaxies grouped by clump mulitiplicity.
+
+\subsection{Example 1: Selecting bars}
+
+We created a sample of barred galaxies by applying cuts on the previous tasks as listed in Table~\ref{tbl:thresholds}.
+11,049 ``bar candidates'', galaxies for which asking the bar question is meaningful, were selected by applying the cuts $N_{bar} \ge 20$, $p_{\rm features}>0.23, p_{\rm clumpy,no} > 0.30,$ and $p_{edgeon,no}>0.25$.
+These galaxies are featured, non-clumpy, non-edge~on galaxies.
+Of these, a pure sample of 730 barred disks was identified by applying a cut of $p_{bar}>0.7$.
+A subsample of 50 galaxies were visually inspected and 94\% were found to contain strong bars.
+A complete sample of strong and weak bars was created by applying a cut of $p_{bar}>0.3$.
+This sample contained 3,218 galaxies, 86\% of which were found to contain weak or strong bars through visual inspection in a subsample of 50.
+
+We use the complete bar sample to estimate the redshift evolution of bar fraction and find a steady decrease of $f_{bar} \sim 0.32$ at $z=0.4$ to $f_{bar} \sim 0.24$ at $z=1.0$.
+The decrease in bar fraction agrees with \ref{mel14}, however they report a lower bar fraction overall, finding a decrease from $f_{bar}=0.22$ at $z=0.4$ to $f_{bar}=0.11$ at $z=1.0$.
+The difference in total bar fraction is expected, as our analysis used a looser cut on $p_{\rm bar}$, we did not apply a luminosity cut, and we use debiased values for $p_{\rm features}$ which increases the total amount of disks in the sample.
+For a more thorough analysis of the bar fraction, a cut on $p_{\rm bar}$ that evolves with redshift may yield more accurate results, since there are no explicit debiased values of $p_{\rm bar}$ that would take redshift induced bias into account.
+
+\subsection{Example 2: Identifying clump multiplicity}
+For galaxies identified as ``clumpy'' in GZH, the number of clumps can be determined using Task 16.
+We identify samples of galaxies having one, two, three, four, and more than four clumps.
+Using Table~\ref{tbl:thresholds}, we identify 8,444 clumpy galaxies using $p_{\rm features} > 0.23$ and $p_{\rm clumpy,yes}>0.80$ to ensure the vote fractions for Task 16 are well-sampled.
+We were able to identify with reasonable confidence the clump number of 1,112 of the clumpy galaxies; in the remainder, the unique clumps were less distinguishable from each other and the exact number of clumps could not be deduced without careful visual inspection.
+In the 1,112 which did have distinguishable clumps, we identified 61 one-clump galaxies using $p_{\rm 1~clump}>0.50$ 442 two-clump galaxies using $p_{\rm 2~clumps}>0.80$, 275 three-clump galaxies using $p_{\rm 3~clumps}>0.75$, 71 four-clump galaxies using $p_{\rm 4~clumps} > 0.70$, and 263 galaxies with more than four clumps using $p_{\rm >4~clumps}>0.70$.
+Alternatively, these data may be used to create more general samples of clumpy galaxies with few clumps and many clumps.
+We define a sample of 989 ``few clumps'' galaxies using $(p_{\rm 1~clump} + p_{\rm 2~clumps}) > 0.5$ and 2,910 ``many clumps'' galaxies using $(p_{\rm 3~clumps}+p_{\rm 4~clumps}+p_{\rm >4~clumps})>0.5$.
 
@@
 \begin{itemize}
-    \item explain decision tree format; vote fractions are dependent on previous task vote fractions
-    \item provide example of how to select bars
-    \item discuss difference between conservative/clean sample and loose/complete sample, emphasize goals differ depending on science case
+    \item \sout{explain decision tree format; vote fractions are dependent on previous task vote fractions} 
+    \item \sout{provide example of how to select bars}
+    \item \sout{discuss difference between conservative/clean sample and loose/complete sample, emphasize goals differ depending on science case}
+    \item \sout{science with bar example - estimate bar fraction vs redshift}
+    \item science with clump multiplicity - not sure actually 
 \end{itemize}
 } 
-
 \begin{table}

### 2016-04-26 writeup/gz_hubble_data.tex
updating decision tree figure with correct task numbers

@@
 \includegraphics[width=\textwidth]{figures/gzh_decision_tree.pdf}
-\caption{}
+\caption{Flowchart of the questions presented to GZH users, labeled with the corresponding Task numbers.
+Tasks in the decision tree are color-coded by tier level: Gray-colored Tasks are 1st tier questions which are asked of all users.
+Tasks colored green, blue, purple, and pink (respectively) are one, two, three, or four steps below branching points in the decision tree.}
 \label{fig:decisiontree}

### 2016-04-26 writeup/gz_hubble_data.tex
updating decision tree figure with correct task numbers

--- 2016-04-26 writeup/gz_hubble_data.tex
@@
-\documentclass[twocolumn]{aastex6}
-
-%% The other main article choice is a tightly typeset, two-column article
-%% that more closely resembles the final typeset pdf article.
-%%
-%% \documentclass[twocolumn]{aastex6}
-%% 
-%% There are other optional arguments one can envoke to allow other 
-%% actions. 
-%%
-% These are the available options:
-%   manuscript	: onecolumn, doublespace, 12pt fonts
-%   preprint	: onecolumn, single space, 10pt fonts
-%   preprint2	: twocolumn, single space, 10pt fonts
-%   twocolumn	: a two column article. Probably not needed, but here just in case.
-%   onecolumn	: a one column article; default option.
-%   twocolappendix: make 2 column appendix
-%   onecolappendix: make 1 column appendix is the default. 
-%   astrosymb	: Loads Astrosymb font and define \astrocommands. 
-%   tighten	: Makes baselineskip slightly smaller
-%   times	: uses times font instead of the default
-%   linenumbers	: turn on lineno package.
-%   trackchanges : required to see the revision mark up and print output
-%   numberedappendix: Labels appendix sections A, B, ... This is the default.
-%   appendixfloats: Needed. Resets figure and table counters to zero
-
-%% these can be used in any combination, e.g.
-%%
-%% \documentclass[twocolumn,twocolappendix,linenumbers,trackchanges]{aastex6}
-
-\shorttitle{Galaxy Zoo: Hubble}
-\shortauthors{Willett et al.}
-
-%% This is the end of the preamble.  Indicate the beginning of the
-%% paper itself with \begin{document}.
+%\documentclass[twocolumn]{emulateapj}
+%\documentclass[12pt,preprint]{aastex}
+\documentclass[usenatbib]{mn2e}
+
+\voffset-1.25cm
 
@@
 \usepackage{subfigure}
+\usepackage{deluxetable}
 \usepackage{url}
-\usepackage[normalem]{ulem}
 \bibliographystyle{mn2e}
@@
 
-%% LaTeX will automatically break titles if they run longer than
-%% one line. However, you may use \\ to force a line break if
-%% you desire.
-
-\title{Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging}
-%% Use \author, \affil, plus the \and command to format author and affiliation 
-%% information.  If done correctly the peer review system will be able to
-%% automatically put the author and affiliation information from the manuscript
-%% and save the corresponding author the trouble of entering it by hand.
-%%
-%% The \affil should be used to document primary affiliations and the
-%% \altaffil should be used for secondary affiliations, titles, or email.
-
-%% Authors with the same affiliation can be grouped in a single
-%% \author and \affil call.
-\author{Kyle W.
-Willett\altaffilmark{1,2}, Melanie A.
-Galloway\altaffilmark{1}, Chris J.
-Lintott\altaffilmark{3}, B.D.
-Simmons\altaffilmark{3,4,5,6}, Karen L.
-Masters\altaffilmark{7,8}, Tom Melvin\altaffilmark{7}, Steven P.
-Bamford\altaffilmark{9}, Edward M.
-Edmondson\altaffilmark{7}, Lucy F.
-Fortson\altaffilmark{1}, Kevin Schawinski\altaffilmark{10}, Edmond Cheung\altaffilmark{11}, Claudia Scarlata\altaffilmark{1}, Melanie Beck\altaffilmark{1}, Arfon M.
-Smith\altaffilmark{3,12,13}, Michael Parrish\altaffilmark{12}, Roger L.
-Griffith\altaffilmark{14,15}, Anna Han\altaffilmark{16}
-}
+\title[Galaxy Zoo Hubble Data]{Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging}
+\author[Lead Author \etal]{Lead Author and other Galaxy Zoo science team members\\
 %
@@
 %$^8$Einstein Fellow\\ 
-
-%\altaffiltext{1}{School of Physics and Astronomy, University of Minnesota, USA}
-%\altaffiltext{2}{Department of Physics and Astronomy, University of Kentucky, USA}
-%\altaffiltext{3}{Oxford Astrophysics, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK}
-%\altaffiltext{4}{Center for Astrophysics and Space Sciences (CASS), Department of Physics, University of California, San Diego, CA 92093, USA}
-%\altaffiltext{5}{Balliol College}
-%\altaffiltext{6}{Einstein Fellow}
-%\altaffiltext{7}{Institute of Cosmology and Gravitation, University of Portsmouth, UK}
-%\altaffiltext{8}{SEPnet, South East Physics Network, UK}
-%\altaffiltext{9}{University of Nottingham, UK}
-%\altaffiltext{10}{ETH Z\"urich, Switzerland}
-%\altaffiltext{11}{Kavli Institute for the Physics and Mathematics of the Universe (WPI), Japan}
-%\altaffiltext{12}{Adler Planetarium, USA}
-%\altaffiltext{13}{GitHub}
-%\altaffiltext{14}{University of California, Berkeley, USA}
-%\altaffiltext{15}{Penn State University, USA}
-%\altaffiltext{16}{Yale University, USA}
-
-%% Mark off the abstract in the ``abstract'' environment. 
+\\
+ $^*$This publication has been made possible by the participation of more than 200,000 volunteers in the Galaxy Zoo project.
+\\ Their contributions are individually acknowledged at \texttt{http://authors.galaxyzoo.org/authors.html}.
+\\
+\\
+{\tt E-mail: lead.author@university.edu}
+ }
+
+%\date{Accepted for publication in MNRAS, 7th October 2010.}
+%\pagerange{1--10} \pubyear{2010}
+
+\maketitle
+
 \begin{abstract}
 
-% Note: 250-word limit
-This is the data release paper for GZ:Hubble\footnote{This publication has been made possible by the participation of more than 200,000 volunteers in the Galaxy Zoo project.
-Their contributions are individually acknowledged at \url{http://authors.galaxyzoo.org/authors.html}.}.
-We present the classifications, the methodology for data reduction and corrections for redshift dependent biases in the observed morphologies.
+This will be the data release paper for GZ:Hubble. We present the classifications, the methodology for data reduction and corrections for redshift dependent biases in the observed morphologies.
 
@@
 
-%% Keywords should appear after the \end{abstract} command. 
-%% See the online documentation for the full list of available subject
-%% keywords and the rules for their use.
-\keywords{galaxies --- catalogs --- surveys}
-
-\section{Introduction} \label{sec:intro}
+%\keywords{galaxies: distances and redshifts --- galaxies: clusters --- galaxies: fundamental parameters --- distance scale --- cosmological parameters}
+
+\section{Introduction}
 
@@
 \tabletypesize{\scriptsize}
-\begin{deluxetable*}{l|rr|rrr|rr|r|rr}
+\begin{deluxetable}{l|rr|rrr|rr|r|rr}
+\centering
+\rotate
 \tablecolumns{12}
@@
 \enddata
-\end{deluxetable*}
+\end{deluxetable}
 
@@
 \tabletypesize{\scriptsize}
-\begin{deluxetable*}{lllcrllllll|c}
+\begin{deluxetable}{lllcrllllll|c}
 \centering
+\rotate
 \tablecolumns{13}
@@
 A subset of the information is shown here to illustrate form and content.}
-\end{deluxetable*}
+\end{deluxetable}
 
@@
 A subset of the information is shown here to illustrate form and content.}
-\end{deluxetable*}
-
-\tabletypesize{\scriptsize}
-\begin{deluxetable*}{lllcrllllll|c}
+\end{deluxetable}
+
+\tabletypesize{\scriptsize}
+\begin{deluxetable}{lllcrllllll|c}
 \centering
+\rotate
 \tablecolumns{13}
@@
 A subset of the information is shown here to illustrate form and content.}
-\end{deluxetable*}
-
-\tabletypesize{\scriptsize}
-\begin{deluxetable*}{lllcrllll|c}
+\end{deluxetable}
+
+\tabletypesize{\scriptsize}
+\begin{deluxetable}{lllcrllll|c}
 \centering
+\rotate
 \tablecolumns{13}
@@
 A subset of the information is shown here to illustrate form and content.}
-\end{deluxetable*}
-
-\tabletypesize{\scriptsize}
-\begin{deluxetable*}{lllccccrrrrrrr|c}
+\end{deluxetable}
+
+\tabletypesize{\scriptsize}
+\begin{deluxetable}{lllccccrrrrrrr|c}
 \centering
+\rotate
 \tablecolumns{14}
@@
 In this example, such galaxies are featured, non-clumpy, non-edge~on, spiral galaxies.
-At this point a cut can be made on $p_{\rm arm~number=3}$ to select spirals with three arms.
+At this point a cut can be made on $p_{\rm arm~number=3}$ to select spirals with 3 arms.
 
@@
 This sample contained 3,218 galaxies, 86\% of which were found to contain weak or strong bars through visual inspection in a subsample of 50.
-
-We use the complete bar sample to estimate the redshift evolution of bar fraction and find a steady decrease of $f_{bar} \sim 0.32$ at $z=0.4$ to $f_{bar} \sim 0.24$ at $z=1.0$.
-The decrease in bar fraction agrees with \ref{mel14}, however they report a lower bar fraction overall, finding a decrease from $f_{bar}=0.22$ at $z=0.4$ to $f_{bar}=0.11$ at $z=1.0$.
-The difference in total bar fraction is expected, as our analysis used a looser cut on $p_{\rm bar}$, we did not apply a luminosity cut, and we use debiased values for $p_{\rm features}$ which increases the total amount of disks in the sample.
-For a more thorough analysis of the bar fraction, a cut on $p_{\rm bar}$ that evolves with redshift may yield more accurate results, since there are no explicit debiased values of $p_{\rm bar}$ that would take redshift induced bias into account.
-
-\subsection{Example 2: Identifying clump multiplicity}
-For galaxies identified as ``clumpy'' in GZH, the number of clumps can be determined using Task 16.
-We identify samples of galaxies having one, two, three, four, and more than four clumps.
-Using Table~\ref{tbl:thresholds}, we identify 8,444 clumpy galaxies using $p_{\rm features} > 0.23$ and $p_{\rm clumpy,yes}>0.80$ to ensure the vote fractions for Task 16 are well-sampled.
-We were able to identify with reasonable confidence the clump number of 1,112 of the clumpy galaxies; in the remainder, the unique clumps were less distinguishable from each other and the exact number of clumps could not be deduced without careful visual inspection.
-In the 1,112 which did have distinguishable clumps, we identified 61 one-clump galaxies using $p_{\rm 1~clump}>0.50$ 442 two-clump galaxies using $p_{\rm 2~clumps}>0.80$, 275 three-clump galaxies using $p_{\rm 3~clumps}>0.75$, 71 four-clump galaxies using $p_{\rm 4~clumps} > 0.70$, and 263 galaxies with more than four clumps using $p_{\rm >4~clumps}>0.70$.
-Alternatively, these data may be used to create more general samples of clumpy galaxies with few clumps and many clumps.
-We define a sample of 989 ``few clumps'' galaxies using $(p_{\rm 1~clump} + p_{\rm 2~clumps}) > 0.5$ and 2,910 ``many clumps'' galaxies using $(p_{\rm 3~clumps}+p_{\rm 4~clumps}+p_{\rm >4~clumps})>0.5$.
-
 {\note
 \begin{itemize}
-    \item \sout{explain decision tree format; vote fractions are dependent on previous task vote fractions} 
-    \item \sout{provide example of how to select bars}
-    \item \sout{discuss difference between conservative/clean sample and loose/complete sample, emphasize goals differ depending on science case}
-    \item \sout{science with bar example - estimate bar fraction vs redshift}
-    \item science with clump multiplicity - not sure actually 
+    \item explain decision tree format; vote fractions are dependent on previous task vote fractions 
+    \item provide example of how to select bars
+    \item discuss difference between conservative/clean sample and loose/complete sample, emphasize goals differ depending on science case
 \end{itemize}
 }
+
 \begin{table}
@@
 
-\subsection{Comparison to other catalogs}\ref{ssec:comparisons}
+\subsection{Comparison to other catalogs}
 
@@
     \item Zajmoski (COSMOS)
-    \item \sout{GEMS morphologies} \citep{hau07}
-    \item \sout{AEGIS morphologies} \citep{lot08}
-    \item \sout{GOODS N/S morphologies} \citep{bun05}
+    \item GEMS morphologies \citep{hau07}
+    \item AEGIS morphologies \citep{lot08}
+    \item GOODS N/S morphologies \citep{bun05}
 \end{itemize}
@@
 
-\subsubsection{GEMS}
-
-Morphologies for galaxies in GEMS imaging have been measured by \citet{hau07}, who perform a careful comparison of single-component \sersic{} fits to the F850LP imaging using both the \galfit{} and \gimtwod{} codes.
-We compare the GZH morphological vote fractions to the \galfit{} parameters, which are evaluated by \citet{hau07} as more reliable due to \galfit's ability to fit multiple galaxies and handle crowded fields.
-
-A single \sersic{} fit is often a poor fit to the light profile of a resolved galaxy, since large numbers of classical spirals have both a de~Vaucouleurs bulge at the center and an exponential disc at larger radii.
-If a single parameter is used, however, a common division in the literature is to split on the \sersic~index $n$ into disc-dominated galaxies ($n<2.5$) and bulge-dominated galaxies ($n>2.5$), where $n$ is the exponent in the radial surface brightness profile such that $\Sigma(r)=\Sigma_e \exp{\left(-\kappa[(r/r_e)^{1/n} - 1]\right)}$.
-
-A 1\arcsec~positional match for the GEMS galaxies in Table~9 in \citet{hau07} to the GZH sample gives 8,846~galaxies found in both samples.
-We analyze galaxies for which the \galfit{} parameters are flagged as being constrained within plausible physical limits, indicating a moderately robust fit.
-There is a strong correlation between $n$ and \pbest; the average value for disk-dominated galaxies ($n<2.5$) is $\langle$\pbest$\rangle=0.44\pm0.26$, compared to $\langle$\pbest$\rangle=0.30\pm0.25$ for bulge-dominated galaxies ($n>2.5$).
-The correlation is stronger for bulge-dominated galaxies; for $n>2.5$, most galaxies have \pbest$<0.2$.
-In contrast, while $n<2.5$ do have higher \pbest~values, the spread is larger and there are significant numbers of galaxies even at the highest \pbest{} values.
-
-Inverting the comparison, we split the GZH galaxies into three samples: ``clean'' disks (\pbest$\ge0.8$), ``clean'' ellipticals (\pbest$\le0.2$), and ``intermediate'' ($0.2<$\pbest$<0.8$) galaxies \citep[eg,][]{sch14}.
-Splitting by $n<2.5/n>2.5$, clean disks are $85\%/17\%$, intermediates $84\%/16\%$, and clean ellipticals $59\%/41\%$.
-There is a strong dependence for these ratios on the brightness of the galaxy, which affects both automatic fits and visual accuracy.
-Limiting the sample to galaxies with $m_{850LP}<21$ gives fractions of: clean disks are $77\%/23\%$, intermediates $52\%/48\%$, and clean ellipticals $38\%/62\%$.
-While the clean disk fraction is largely unchanged, intermediates are more evenly balanced and there is a larger population of smooth galaxies with high $n$, as expected.
-
-We visually inspect galaxies for which the \galfit{} and GZH measurements indicate strong disagreement.
-Of the 84~galaxies with $n>2.5$ and \pbest$\ge0.80$, almost all are spirals with obvious disks and clearly marked spiral arms.
-These appear to be cases where \galfit{} fits the bulge at the center, but misses extended emission from the disk.
-We also examine the 35~galaxies with $n<2.5$ and \pbest$\le0.20$; these galaxies generally have smoother light profiles with no spiral arms, although several have bars and/or the sharper truncation of light near the edges that indicates an S0 galaxy.
-These galaxies are also significantly bluer $(\langle m_{606}-m_{850}\rangle=0.27\pm3.3)$ compared to the majority of galaxies classified as ``smooth'' in GZH $(\langle m_{606}-m_{850}\rangle=1.2\pm1.7)$.
-We interpret this as evidence for the fact that single-component radial fits are often inadequate to accurately characterize galaxy morphology, and that a simple cut risks significant amounts of misclassified objects.
-
-Clumpy galaxies in GZH have \galfit{} parameters more consistent with disky, $n<2.5$ galaxies than spheroids (Figure~\ref{fig:clumpy_gems}).
-Using the thresholds in Table~\ref{tbl:thresholds}, GZH clumpy galaxies have average values of $n=1.6\pm1.2$ and $R_e=32\pm16$~pix, with only 11\% of clumpy galaxies falling in the bulge-dominated region of $n>2.5$.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.50\textwidth]{figures/gems_clumpy.png}
-\caption{Parameter distributions for GEMS galaxies in \citet{hau07} and GZH.
-Red and blue points indicate galaxies split by their \sersic~index (at $n=2.5$) into disk- and bulge-dominated galaxies, respectively.
-Galaxies identified as ``clumpy'' in GZH are labeled in green.}
-\label{fig:clumpy_gems}
-\end{center}
-\end{figure}
-
-\subsubsection{AEGIS}
-
-Galaxies in AEGIS were morphologically classified using non-parametric measurements by \citet{lot08}.
-They use the Gini coefficient ($G$), which measures the relative inequality in pixel brightness, and $M_{20}$, the second-order moment of the brightest 20\% of the light \citep{lot04}.
-A linear combination of $G$ and $M_{20}$ to delineate three broad categories of galaxy morphology: E/S0/Sa (bulge-dominated/spheroids), Sb/Sc/Ir (disk-dominated/irregulars), and mergers.
-
-We compare the GZH vote fractions to the morphological categories defined by their $G$-$M_{20}$ values, which are measured in both $V$- and $I$-band.
-A 1\arcsec{} positional match on AEGIS from \citet{lot08} and GZH yields 7,508~galaxies; of those, we analyze a subsample of 4,031 with reliably-measured morphologies and $S/N>3$ in both bands.
-
-The GZH morphologies are reasonably correlated with the $G$-$M_{20}$ morphological categories.
-For galaxies labeled as Sb/Sc/Ir by \citet{lot08}, 58\% of the galaxies in $I$-band (61\% in $V$-band) have \pbest{} above a nominal cut of 0.5.
-E/S0/Sa galaxies have a tighter relation, with 78\% of galaxies in $I$-band (79\% in $V$-band) having $p_\mathrm{smooth}>0.5$.
-Galaxies with high \pbest{} are largely concentrated in the E/S0/Sa region of $G$-$M_{20}$ space; the small overlaps into mergers and E/S0/Sa are close to what we expect for loosely defined boundaries.
-Galaxies with low \pbest{} have a much broader range of $G$-$M_{20}$ values, with nearly half lying well within the Sb/Sc/Ir region.
-
-Of the 47~galaxies identified by GZH as mergers in the cross-matched AEGIS sample (selected as \pmerger$>0.5$ and $N_\mathrm{merger}\ge20$), roughly two-thirds fall in the merger region of $G$-$M_{20}$ space defined in \citet{lot08}; almost all the remainder would be classified as Sb/Sc/Ir.
-Galaxies identified as mergers by $G$-$M_{20}$, in contrast, typically have lower \pmerger{} values; 66\%/50\% in $V$-band and $I$-band, respectively.
-While the total number of mergers identified in GZH is roughly $\times10$ fewer than the volume-limited $G$-$M_{20}$ sample, we do confirm the result of a non-evolving merger fraction between $0.2<z<1.2$.
-%The average bulge statistic for the GZH mergers \citep[as defined in][]{sny15} is $F=-0.3\pm0.5$ in $V$-band and $F=-0.2\pm0.5$ in $I$-band.
-
-\subsubsection{GOODS}
-
-Galaxies in the GOODS-N and GOODS-S fields down to a limit of $z_{AB}=22.5$ have been visually classified by a single expert (R.S.~Ellis), inspecting both $z$-band and composite $Viz$ color images \citep{bun05}.
-These morphologies are assigned a numerical value based on categories in \citet{bri98a}; these are combined into broader categories of ``E/S0'' (classes 0,1,2), ``Spirals'' (classes 3,4,5), and ``Peculiar/Irregular'' (classes 6,7,8).
-\citet{bun05} use these morphologies to show that there are an increasing proportion of early-type galaxies observed at later times.
-
-Matching the \citet{bun05} catalog to GZH with a 0.5\arcsec{} radius yields 2435 galaxies (1300 in GOODS-N, 1135 in GOODS-S).
-We compare their broad morphological categories to \pbest{} in GZH; demographics of the separate GOODS-N and GOODS-S samples are highly consistent.
-``E/S0'' galaxies are dominated by high smooth fractions in GZH, with an average value of $\langle p_\mathrm{smooth,best}\rangle=0.54\pm0.20$.
-The effect is stronger when examining sub-divisions; pure E galaxies have the highest $p_\mathrm{smooth,best}$ values, while S0 have the lowest.
-Visual inspection of galaxies designated as S0 show numerous examples of both edge-on galaxies and visible substructure in the disk, including spiral arms.
-This is consistent with the design of the GZH decision tree, and likely reflects that the expert categories are using different criteria.
-
-``Spiral'' galaxies in \citet{bun05} have robustly high GZH vote fractions of features and/or disks, with $\langle p_\mathrm{features,best}\rangle=0.59\pm0.06$.
-The vote fraction increases with Hubble type, with Scd galaxies having the highest average \pbest{} values.
-``Peculiar/Irregular'' galaxies have similar ranges of \pbest{} to the ``Spiral'' galaxies, but can be sub-selected with cutoffs on $p_\mathrm{odd}$ and $p_\mathrm{irregular}$ or $p_\mathrm{merger}$.
-We note that mergers are not strongly correlated in GZH and the expert visual classifications; between 20\%--30\% have GZH merger fractions of zero, while even clear tidal tails can be as low as $p_\mathrm{merger}\sim0.1$.
-The total number of major mergers is small enough that expert visual inspection can be practically done on all candidates; a combination of methods may be the most accurate way of identifying these rarer objects, especially when the signs of interaction are relatively subtle.
-
 \section{Summary}\label{sec:summary}
@@
 
-\acknowledgments
+\paragraph*{ACKNOWLEDGEMENTS.}
 
 We thank Meg Schwamb and the ASIAA for hosting the ``Citizen Science in Astronomy'' workshop, 3-7 Mar 2014 in Taipei, Taiwan, at which some of this analysis was done.
-We also thank Jennifer Lotz for sharing her $G$-$M_{20}$ measurements for the AEGIS sample.
 
@@
 Department of Energy, the National Aeronautics and Space Administration, the Japanese Monbukagakusho, the Max Planck Society, and the Higher Education Funding Council for England.
-The SDSS website is \url{http://www.sdss.org/}.
+The SDSS website is http://www.sdss.org/.
 

### 2016-04-27 writeup/gz_hubble_data.tex
adding last text to section 6 and testing bbl overwrite

--- 2016-04-26 writeup/gz_hubble_data.tex
@@
 Population studies would make use of such large samples, in which statistical significance is a crucial factor in evaluating results.
-\citet{mas11c,mel14}, and \citet{gal15} are examples of GZ papers which select morphologies in this way.
+\citet{mas11c,mel14,che15}, and \citet{gal15} are examples of GZ papers which select morphologies in this way.
 
@@
 We then applied a cut on the vote fraction for the previous task and analyzed a subsample of 50 galaxies meeting these criteria, as well as a control sample of galaxies which had 20 users vote on the task, but did not meet the threshold cut set for the previous task.
-The threshold cut was adjusted and new subsamples were inspected until both the original and control samples achieved $\ge 80\%$ purity.
+The threshold cut was adjusted and new subsamples were inspected until both the original and control samples achieved $>80\%$ purity.
 
@@
 \subsection{Example 2: Identifying clump multiplicity}
+Clumps are known to be a characteristic feature of galaxies outside the local universe, and there is evidence they play a crutial role in the evolution of modern spirals, particularly in the formation of central bulges \citep{elm05,elm14,guo15,beh16}.
+Simulations show clumps migrate from the outer disk to the galactic center on relatively short (~few orbital periods) timescales \citep{man15} and observations show increasing bulge to clump mass and density ratios as the universe evolves since $z\sim 1.5$ \citep{elm09}, suggesting that clumps coalesce over time to form the modern bulges of disk galaxies.
+GZH added a ``clumpy'' path to the decision tree for the purpose of both identifying clumps and investigating their evolution with redshift.
+Here we provide an example of how to select galaxies with particular clump multiplicities, for investigations related to the transformation of clumps as galaxies continue to form.
+
 For galaxies identified as ``clumpy'' in GZH, the number of clumps can be determined using Task 16.
@@
 We were able to identify with reasonable confidence the clump number of 1,112 of the clumpy galaxies; in the remainder, the unique clumps were less distinguishable from each other and the exact number of clumps could not be deduced without careful visual inspection.
-In the 1,112 which did have distinguishable clumps, we identified 61 one-clump galaxies using $p_{\rm 1~clump}>0.50$ 442 two-clump galaxies using $p_{\rm 2~clumps}>0.80$, 275 three-clump galaxies using $p_{\rm 3~clumps}>0.75$, 71 four-clump galaxies using $p_{\rm 4~clumps} > 0.70$, and 263 galaxies with more than four clumps using $p_{\rm >4~clumps}>0.70$.
+In the 1,112 which did have distinguishable clumps, we identified 61 one-clump galaxies using $p_{\rm 1~clump}>0.50$, 442 two-clump galaxies using $p_{\rm 2~clumps}>0.80$, 275 three-clump galaxies using $p_{\rm 3~clumps}>0.75$, 71 four-clump galaxies using $p_{\rm 4~clumps} > 0.70$, and 263 galaxies with more than four clumps using $p_{\rm >4~clumps}>0.70$.
 Alternatively, these data may be used to create more general samples of clumpy galaxies with few clumps and many clumps.
@@
     \item \sout{science with bar example - estimate bar fraction vs redshift}
-    \item science with clump multiplicity - not sure actually 
+    \item \sout{science with clump multiplicity }
 \end{itemize}

### 2016-04-27 writeup/gz_hubble_data.tex
COSMOS comparisons - Tasca and Cassata

--- 2016-04-26 writeup/gz_hubble_data.tex
@@
 These methods have advantages in using the significant processing power of the human brain to identify patterns, but suffer from issues such as lack of scaling to large surveys and potential issues with replicability and calibration.
-Automated measurements, both parametric \citep{pen02a,sim11,lac12} and non-parametric \citep{con03,lot04,sca07,bam08,fre13}, scale well to arbitrary sample sizes, but do not always fully capture the relevant features, especially for asymmetric galaxies that become increasingly common at high redshifts.
+Automated measurements, both parametric \citep{pen02a,sim11,lac12} and non-parametric \citep{abr03,con03,lot04,sca07,bam08,fre13}, scale well to arbitrary sample sizes, but do not always fully capture the relevant features, especially for asymmetric galaxies that become increasingly common at high redshifts.
 The Galaxy Zoo project \citep{lin08,lin11} utilizes crowdsourced visual classifications to measure galaxies in color-composite images.
@@
 Bands used in each of the surveys are listed in Table~\ref{tbl:gzh_numbers}.
-Note that the 2-epoch GOODS-N and GOODS-S images use different filters --- this was a deliberate choice made so that the GEMS images could be directly compared with the overlapping coverage of GOODS-S (Figure~\ref{fig:filtercurves}).
+The 2-epoch GOODS-N and GOODS-S images use different filters --- this was a deliberate choice made so that the GEMS images could be directly compared with the overlapping coverage of GOODS-S (Figure~\ref{fig:filtercurves}).
 
@@
 \begin{figure*}
+\center
 \includegraphics[width=160mm]{figures/gzh_interface.png}
@@
 \includegraphics[width=\textwidth]{figures/gzh_decision_tree.pdf}
-\caption{Flowchart of the questions presented to GZH users, labeled with the corresponding Task numbers.
-Tasks in the decision tree are color-coded by tier level: Gray-colored Tasks are 1st tier questions which are asked of all users.
-Tasks colored green, blue, purple, and pink (respectively) are one, two, three, or four steps below branching points in the decision tree.}
+\caption{}
 \label{fig:decisiontree}
@@
 \begin{figure*}
+\center
 \includegraphics[width=160mm]{figures/example_ferengi.pdf}
@@
 We stress that the selection process will vary based on the particular science case.
-More conservative cuts can be applied to create pure, but not necessarily complete, samples.
-These are useful for selecting galaxies exhibiting unique morphologies for individual case studies or observing proposals.
-Looser cuts can be applied to obtain samples with a higher level of completeness, which will increase the sample size but can potentially decrease purity.
-Population studies would make use of such large samples, in which statistical significance is a crucial factor in evaluating results.
-\citet{mas11c,mel14}, and \citet{gal15} are examples of GZ papers which select morphologies in this way.
-
-In GZH, volunteers answer questions about a galaxy's morphology in a decision tree format.
-With this structure, questions shown to a user are dependent on their answers to the previous questions.
-For example, a user is only asked Task 11, ``How many spiral arms?'' if they had answered ``yes'' to Task 10, which asks whether any spiral arms are present.
-This structure is used to reduce the workload of the users by only asking questions relevant to the particular galaxy; in this example, it would not be useful, nor would it make physical sense, to ask a user how many spiral arms in a galaxy which they had declared had no spiral arms to begin with.
-Figure~\ref{fig:decisiontree} shows the possible paths available for answering the questions offered in GZH.
-The colors represent the tier level of Tasks, which indicate the number of previous Tasks the given Task is dependent upon.
-The arm-number question, Task 11, is a 5th tier Task, meaning that whether this question is seen by a user is dependent on four Tasks preceding it.
-In this case, it is only shown to volunteers who voted the galaxy was featured/disk-shaped in Task 01, not clumpy in Task 12, not edge-on in Task 02, and had spiral structure in Task 10.
-
-To select galaxies of a morphological type identified with a particular Task, a cut is placed on the vote fraction for that Task ($p_{\rm task}$), \emph{as well as} the vote fractions for the Tasks preceding it, because of the dependency induced by the decision-tree structure.
+
+To select galaxies of a morphological type identified with a Task offered in the decision tree (see Figure~\ref{fig:decisiontree}, a cut is placed on the vote fraction for that Task ($p_{\rm task}$), as well as the vote fractions for the Tasks preceding it.
 For example, to select barred galaxies, a cut may be placed on $p_{\rm bar}$ such that only galaxies where a high fraction of votes for this task voted for the $bar,yes$ answer.
-This is not the only necessary cut, however, since not all users answer this question; only those who have previously selected ``features'' in Task~01, ``not clumpy'' in Task~12, and ``not edge-on'' in Task~02 will have the opportunity to vote on the bar question, Task~03.
+This is not the only necessary cut, however, since not all users answer this question; only those who have previously selected ``features'' in Task~01, ``not clumpy'' in Task~12, and ``not edge-on'', \emph{or} previously selected ``features'' in Task~01, ``clumpy'' in Task~12, ``$>$ 2 clumps'' in Task~16, and ``spiral arrangement'' in Task~15 will have the opportunity to vote on the bar question, Task~03.
 To ensure that $p_{\rm bar}$ is well-sampled, cuts on all previous tasks must be applied.
@@
 In Table~\ref{tbl:thresholds} we offer baseline cuts for selecting galaxies of a variety of morphologies.
-We detemined these thresholds by a visual inspection of subsamples.
-For each Task, we first required that at least 20 users voted on the given question.
-We then applied a cut on the vote fraction for the previous task and analyzed a subsample of 50 galaxies meeting these criteria, as well as a control sample of galaxies which had 20 users vote on the task, but did not meet the threshold cut set for the previous task.
-The threshold cut was adjusted and new subsamples were inspected until both the original and control samples achieved $\ge 80\%$ purity.
-
-As an example of how to use Table~\ref{tbl:thresholds} to create a sample of 3-armed spirals galaxies, one should select objects with $N_{arm~number} \ge 20$, $p_{\rm features}>0.23, p_{\rm clumpy,no} > 0.30, p_{edgeon,no}>0.25$, and $p_{spiral,yes}>0.25$.
-These cuts define a sample of galaxies of ``arm number candidates''; ie galaxies for which answering the arm number question makes physical sense and the vote fraction $p_{\rm arm~number}$ is well-sampled.
-In this example, such galaxies are featured, non-clumpy, non-edge~on, spiral galaxies.
-At this point a cut can be made on $p_{\rm arm~number=3}$ to select spirals with three arms.
-
-Tasks 03, 04 and 05 have an additional possible pathway; as shown in Figure~\ref{fig:decisiontree}, a user might also be shown this question if they select ``featured/disk'' in Task 01, ``clumpy'' in Task 12, two or more clumps in Task 16, and ``spiral arrangement'' in Task 15.
-By applying the appropriate thresholds for this path, we find that $< 0.5\%$ of the galaxies which have $\ge 20$ answers to these questions used this pathway to arrive at these Tasks.
-Further, of these subjects, none were found to exhibit disk structure, although the clumps within were arranged in a spiral pattern.
-We therefore do not find this pathway necessary in examining responses to Tasks 03, 04, and 05.
-
-In this section we have described how to use the previous Task thresholds in Table~\ref{tbl:thresholds} to select well-sampled galaxies which may or may not contain the feature associated with a unique Task.
-We will now offer two examples of how to use the vote fractions for the final Task to obtain a sample of galaxies with a certain morpholgical type, by creating a sample of bars and samples of clumpy galaxies grouped by clump mulitiplicity.
-
-\subsection{Example 1: Selecting bars}
-
-We created a sample of barred galaxies by applying cuts on the previous tasks as listed in Table~\ref{tbl:thresholds}.
-11,049 ``bar candidates'', galaxies for which asking the bar question is meaningful, were selected by applying the cuts $N_{bar} \ge 20$, $p_{\rm features}>0.23, p_{\rm clumpy,no} > 0.30,$ and $p_{edgeon,no}>0.25$.
-These galaxies are featured, non-clumpy, non-edge~on galaxies.
-Of these, a pure sample of 730 barred disks was identified by applying a cut of $p_{bar}>0.7$.
-A subsample of 50 galaxies were visually inspected and 94\% were found to contain strong bars.
-A complete sample of strong and weak bars was created by applying a cut of $p_{bar}>0.3$.
-This sample contained 3,218 galaxies, 86\% of which were found to contain weak or strong bars through visual inspection in a subsample of 50.
-
-We use the complete bar sample to estimate the redshift evolution of bar fraction and find a steady decrease of $f_{bar} \sim 0.32$ at $z=0.4$ to $f_{bar} \sim 0.24$ at $z=1.0$.
-The decrease in bar fraction agrees with \ref{mel14}, however they report a lower bar fraction overall, finding a decrease from $f_{bar}=0.22$ at $z=0.4$ to $f_{bar}=0.11$ at $z=1.0$.
-The difference in total bar fraction is expected, as our analysis used a looser cut on $p_{\rm bar}$, we did not apply a luminosity cut, and we use debiased values for $p_{\rm features}$ which increases the total amount of disks in the sample.
-For a more thorough analysis of the bar fraction, a cut on $p_{\rm bar}$ that evolves with redshift may yield more accurate results, since there are no explicit debiased values of $p_{\rm bar}$ that would take redshift induced bias into account.
-
-\subsection{Example 2: Identifying clump multiplicity}
-For galaxies identified as ``clumpy'' in GZH, the number of clumps can be determined using Task 16.
-We identify samples of galaxies having one, two, three, four, and more than four clumps.
-Using Table~\ref{tbl:thresholds}, we identify 8,444 clumpy galaxies using $p_{\rm features} > 0.23$ and $p_{\rm clumpy,yes}>0.80$ to ensure the vote fractions for Task 16 are well-sampled.
-We were able to identify with reasonable confidence the clump number of 1,112 of the clumpy galaxies; in the remainder, the unique clumps were less distinguishable from each other and the exact number of clumps could not be deduced without careful visual inspection.
-In the 1,112 which did have distinguishable clumps, we identified 61 one-clump galaxies using $p_{\rm 1~clump}>0.50$ 442 two-clump galaxies using $p_{\rm 2~clumps}>0.80$, 275 three-clump galaxies using $p_{\rm 3~clumps}>0.75$, 71 four-clump galaxies using $p_{\rm 4~clumps} > 0.70$, and 263 galaxies with more than four clumps using $p_{\rm >4~clumps}>0.70$.
-Alternatively, these data may be used to create more general samples of clumpy galaxies with few clumps and many clumps.
-We define a sample of 989 ``few clumps'' galaxies using $(p_{\rm 1~clump} + p_{\rm 2~clumps}) > 0.5$ and 2,910 ``many clumps'' galaxies using $(p_{\rm 3~clumps}+p_{\rm 4~clumps}+p_{\rm >4~clumps})>0.5$.
+{\note As an example: to select barred galaxies, one should select objects with $p_{\rm features}>0.52, p_{\rm clumpy,no} > 0.55,$ and $p_{edgeon,no}>x.xx$ \emph{or} objects with $p_{\rm features}>0.52, p_{\rm clumpy,yes} > x.xx, (p_{\rm clump~count, 3}+p_{\rm clump~count,4}+p_{\rm clump~count,>4}+p_{\rm clump~count,can't~tell})>x.xx,$ and $p_{\rm clump~arrangement,spiral}>x.xx.$} These cuts define a sample of galaxies of ``bar candidates''; ie galaxies for which answering the bar question makes physical sense and the vote fraction $p_{\rm bar}$ is well-sampled.
+In this example, such galaxies are featured, non-clumpy, non-edge~on galaxies, or featured, clumpy, spiral galaxies.
+At this point a cut can be made on $p_{\rm bar}$ to select a clean sample of only strong bars $p_{\rm bar}>0.8$, or a complete sample of weak and strong bars $p_{\rm bar}>0.3$, or the value most appropriate to the science case.
 
@@
 \begin{itemize}
-    \item \sout{explain decision tree format; vote fractions are dependent on previous task vote fractions} 
-    \item \sout{provide example of how to select bars}
-    \item \sout{discuss difference between conservative/clean sample and loose/complete sample, emphasize goals differ depending on science case}
-    \item \sout{science with bar example - estimate bar fraction vs redshift}
-    \item science with clump multiplicity - not sure actually 
+    \item explain decision tree format; vote fractions are dependent on previous task vote fractions
+    \item provide example of how to select bars
+    \item discuss difference between conservative/clean sample and loose/complete sample, emphasize goals differ depending on science case
 \end{itemize}
 }
+
 \begin{table}
@@
 
-\subsection{Comparison to other catalogs}\ref{ssec:comparisons}
+\subsection{Comparison to other catalogs}\label{ssec:comparisons}
 
@@
 The total number of major mergers is small enough that expert visual inspection can be practically done on all candidates; a combination of methods may be the most accurate way of identifying these rarer objects, especially when the signs of interaction are relatively subtle.
+
+\subsubsection{COSMOS}
+
+The COSMOS galaxies have several published datasets automatically classifying their morphologies, all using a variation of non-parametric measurements clustered with machine algorithms and trained on a visually-classified reference set of several hundred galaxies.
+\citet{cas07} use a combination of $C$, $A$, $G$, and $M_{20}$ \citep{cas05} to classify all galaxies with $m_\mathrm{I,petro}<25$.
+They divide galaxies into three broad morphological categories: early-type, spirals, and irregulars.
+A very similar method is employed by \citet{tas11}; they use the same non-parametric indices to determine galaxy morphology, but with a slightly different method of calculating the Petrosian radius.
+64\% of the galaxies have identical classifications in \citet{cas07} and \citet{tas11}; roughly two-thirds of the disagreements are galaxies originally classified as ``irregular'' in \citet{cas07} but ``spiral'' in \citet{tas11}.
+
+Using a 0.5\arcsec{} positional match, we find 76,241 galaxies with morphologies in both GZH and \citet{cas07}.
+
+% Show the fraction of galaxies in each category as a function of p_features and p_odd?
 

### 2016-04-27 writeup/gz_hubble_data.tex
Adding standalone .bib file to manage references

--- 2016-04-27 writeup/gz_hubble_data.tex
@@
 Population studies would make use of such large samples, in which statistical significance is a crucial factor in evaluating results.
-\citet{mas11c,mel14,che15}, and \citet{gal15} are examples of GZ papers which select morphologies in this way.
+\citet{mas11c,mel14}, and \citet{gal15} are examples of GZ papers which select morphologies in this way.
 
@@
 We then applied a cut on the vote fraction for the previous task and analyzed a subsample of 50 galaxies meeting these criteria, as well as a control sample of galaxies which had 20 users vote on the task, but did not meet the threshold cut set for the previous task.
-The threshold cut was adjusted and new subsamples were inspected until both the original and control samples achieved $>80\%$ purity.
+The threshold cut was adjusted and new subsamples were inspected until both the original and control samples achieved $\ge 80\%$ purity.
 
@@
 \subsection{Example 2: Identifying clump multiplicity}
-Clumps are known to be a characteristic feature of galaxies outside the local universe, and there is evidence they play a crutial role in the evolution of modern spirals, particularly in the formation of central bulges \citep{elm05,elm14,guo15,beh16}.
-Simulations show clumps migrate from the outer disk to the galactic center on relatively short (~few orbital periods) timescales \citep{man15} and observations show increasing bulge to clump mass and density ratios as the universe evolves since $z\sim 1.5$ \citep{elm09}, suggesting that clumps coalesce over time to form the modern bulges of disk galaxies.
-GZH added a ``clumpy'' path to the decision tree for the purpose of both identifying clumps and investigating their evolution with redshift.
-Here we provide an example of how to select galaxies with particular clump multiplicities, for investigations related to the transformation of clumps as galaxies continue to form.
-
 For galaxies identified as ``clumpy'' in GZH, the number of clumps can be determined using Task 16.
@@
 We were able to identify with reasonable confidence the clump number of 1,112 of the clumpy galaxies; in the remainder, the unique clumps were less distinguishable from each other and the exact number of clumps could not be deduced without careful visual inspection.
-In the 1,112 which did have distinguishable clumps, we identified 61 one-clump galaxies using $p_{\rm 1~clump}>0.50$, 442 two-clump galaxies using $p_{\rm 2~clumps}>0.80$, 275 three-clump galaxies using $p_{\rm 3~clumps}>0.75$, 71 four-clump galaxies using $p_{\rm 4~clumps} > 0.70$, and 263 galaxies with more than four clumps using $p_{\rm >4~clumps}>0.70$.
+In the 1,112 which did have distinguishable clumps, we identified 61 one-clump galaxies using $p_{\rm 1~clump}>0.50$ 442 two-clump galaxies using $p_{\rm 2~clumps}>0.80$, 275 three-clump galaxies using $p_{\rm 3~clumps}>0.75$, 71 four-clump galaxies using $p_{\rm 4~clumps} > 0.70$, and 263 galaxies with more than four clumps using $p_{\rm >4~clumps}>0.70$.
 Alternatively, these data may be used to create more general samples of clumpy galaxies with few clumps and many clumps.
@@
     \item \sout{science with bar example - estimate bar fraction vs redshift}
-    \item \sout{science with clump multiplicity }
+    \item science with clump multiplicity - not sure actually 
 \end{itemize}
@@
 
-\bibliography{kwrefs}
+\bibliography{gz_hubble_data}
 

### 2016-04-27 writeup/gz_hubble_data.tex
Finishing Cassata/Tasca

--- 2016-04-27 writeup/gz_hubble_data.tex
@@
 Using a 0.5\arcsec{} positional match, we find 76,241 galaxies with morphologies in both GZH and \citet{cas07}.
+At the lowest values of \pbest, $\sim10\%$ of the \citet{cas07} galaxies are classified as irregular, only $\sim30\%$ as early-type, and $60\%$ as spiral.
+The early-type fraction drops with increasing \pbest, with an increasing proportion of irregulars.
+The \podd{} vote fraction distinguishes sharply between spirals and irregulars at \podd$>0.2$.
+
+Despite using a similar classification method to \citet{cas07}, the \citet{tas11} classifications show significantly different trends as a function of GZH classifications.
+Spiral galaxies consistently make up $\sim60\%$ of the sample at \emph{all} \pbest, with a mild increase at \pbest$\simeq1.0$.
+Early-type and irregular galaxies make up the remainder, smoothly varying between irregulars at low \pbest{} and early-types and high \pbest.
 

### 2016-04-27 writeup/gz_hubble_data.tex

--- 2016-04-27 writeup/gz_hubble_data.tex
@@
 The total number of major mergers is small enough that expert visual inspection can be practically done on all candidates; a combination of methods may be the most accurate way of identifying these rarer objects, especially when the signs of interaction are relatively subtle.
+
+\subsubsection{COSMOS}
+
+The COSMOS galaxies have several published datasets automatically classifying their morphologies, all using a variation of non-parametric measurements clustered with machine algorithms and trained on a visually-classified reference set of several hundred galaxies.
+\citet{cas07} use a combination of $C$, $A$, $G$, and $M_{20}$ \citep{cas05} to classify all galaxies with $m_\mathrm{I,petro}<25$.
+They divide galaxies into three broad morphological categories: early-type, spirals, and irregulars.
+A very similar method is employed by \citet{tas11}; they use the same non-parametric indices to determine galaxy morphology, but with a slightly different method of calculating the Petrosian radius.
+64\% of the galaxies have identical classifications in \citet{cas07} and \citet{tas11}; roughly two-thirds of the disagreements are galaxies originally classified as ``irregular'' in \citet{cas07} but ``spiral'' in \citet{tas11}.
+
+Using a 0.5\arcsec{} positional match, we find 76,241 galaxies with morphologies in both GZH and \citet{cas07}.
+At the lowest values of \pbest, $\sim10\%$ of the \citet{cas07} galaxies are classified as irregular, only $\sim30\%$ as early-type, and $60\%$ as spiral.
+The early-type fraction drops with increasing \pbest, with an increasing proportion of irregulars.
+The \podd{} vote fraction distinguishes sharply between spirals and irregulars at \podd$>0.2$.
+
+Despite using a similar classification method to \citet{cas07}, the \citet{tas11} classifications show significantly different trends as a function of GZH classifications.
+Spiral galaxies consistently make up $\sim60\%$ of the sample at \emph{all} \pbest, with a mild increase at \pbest$\simeq1.0$.
+Early-type and irregular galaxies make up the remainder, smoothly varying between irregulars at low \pbest{} and early-types and high \pbest.
+
+% Show the fraction of galaxies in each category as a function of p_features and p_odd?
 

### 2016-04-28 writeup/gz_hubble_data.tex
Single figure for all COSMOS comparisons

@@
     \item \citet[ZEST;][]{sca07} (COSMOS)
-    \item Tasca (COSMOS)
-    \item Cassata (COSMOS)
-    \item Zajmoski (COSMOS)
+    \item \sout{Tasca (COSMOS)} \citep{tas11}
+    \item \sout{Cassata (COSMOS)} \citep{cas07}
+    \item \sout{Zamojski (COSMOS)} - \citet{zam07} measure parameters, but no assignation to discrete categories
     \item \sout{GEMS morphologies} \citep{hau07}
@@
 
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.50\textwidth]{figures/cosmos_comparisons.png}
+\caption{Distributions of morphological parameters for COSMOS galaxies matched in GZH and various machine-learning catalogs.
+The left column of plots shows the fraction of overall galaxies in discrete morphology \citep{cas07,tas11,sca07} as a function of \pbest in GZH.
+The right column shows the same split into morphological categories as a function of \podd.}
+\label{fig:cosmos_comparisons}
+\end{center}
+\end{figure}
+
 Using a 0.5\arcsec{} positional match, we find 76,241 galaxies with morphologies in both GZH and \citet{cas07}.
@@
 Early-type and irregular galaxies make up the remainder, smoothly varying between irregulars at low \pbest{} and early-types and high \pbest.
+
+\citet{sca07} provide a more extensive classification of the COSMOS galaxies using a non-parametric analysis based on $A$, $C$, $G$, $M_{20}$, ellipticity ($\epsilon$), and $n$ and use a principal component analysis to assign galaxies with $m_\mathrm{I,AB}$ to discrete morphological categories.
 

### 2016-04-28 writeup/gz_hubble_data.tex
Center all the floating images

--- 2016-04-27 writeup/gz_hubble_data.tex
@@
 These methods have advantages in using the significant processing power of the human brain to identify patterns, but suffer from issues such as lack of scaling to large surveys and potential issues with replicability and calibration.
-Automated measurements, both parametric \citep{pen02a,sim11,lac12} and non-parametric \citep{abr03,con03,lot04,sca07,bam08,fre13}, scale well to arbitrary sample sizes, but do not always fully capture the relevant features, especially for asymmetric galaxies that become increasingly common at high redshifts.
+Automated measurements, both parametric \citep{pen02a,sim11,lac12} and non-parametric \citep{con03,lot04,sca07,bam08,fre13}, scale well to arbitrary sample sizes, but do not always fully capture the relevant features, especially for asymmetric galaxies that become increasingly common at high redshifts.
 The Galaxy Zoo project \citep{lin08,lin11} utilizes crowdsourced visual classifications to measure galaxies in color-composite images.
@@
 \begin{figure*}
+\center
 \includegraphics[width=160mm]{figures/filter_curves.pdf}
@@
 Bands used in each of the surveys are listed in Table~\ref{tbl:gzh_numbers}.
-The 2-epoch GOODS-N and GOODS-S images use different filters --- this was a deliberate choice made so that the GEMS images could be directly compared with the overlapping coverage of GOODS-S (Figure~\ref{fig:filtercurves}).
+Note that the 2-epoch GOODS-N and GOODS-S images use different filters --- this was a deliberate choice made so that the GEMS images could be directly compared with the overlapping coverage of GOODS-S (Figure~\ref{fig:filtercurves}).
 
@@
 \begin{figure*}
+\center
 \includegraphics[width=160mm]{figures/specz_comparison.pdf}
@@
 \begin{figure*}
-\begin{center}
+\center
 \includegraphics[width=\textwidth]{figures/gzh_decision_tree.pdf}
@@
 \label{fig:decisiontree}
-\end{center}
 \end{figure*}
@@
 \begin{figure*}
-\begin{center}
+\center
 \includegraphics[width=\textwidth]{figures/zeta_examples.pdf}
@@
 \label{fig:zeta_examples}
-\end{center}
 \end{figure*}
@@
 \begin{figure}
-\begin{center}
+\center
 \includegraphics[width=0.50\textwidth]{figures/zeta_mu.pdf}
@@
 \label{fig:zeta_mu}
-\end{center}
 \end{figure}
@@
 \begin{figure*}
-\begin{center}
+\center
 \includegraphics[width=\textwidth]{figures/hubble_z_mu_p_distributions.pdf}
@@
 \label{fig:z_mu_p}
-\end{center}
 \end{figure*}
@@
 \begin{figure*}
-\begin{center}
+\center
 \includegraphics[width=\textwidth]{figures/debiased_corrections.pdf}
@@
 \label{fig:debiased_corrections}
-\end{center}
 \end{figure*}
@@
 
-\subsection{Comparison to other catalogs}\label{ssec:comparisons}
+\subsection{Comparison to other catalogs}\ref{ssec:comparisons}
 
@@
 The total number of major mergers is small enough that expert visual inspection can be practically done on all candidates; a combination of methods may be the most accurate way of identifying these rarer objects, especially when the signs of interaction are relatively subtle.
-
-\subsubsection{COSMOS}
-
-The COSMOS galaxies have several published datasets automatically classifying their morphologies, all using a variation of non-parametric measurements clustered with machine algorithms and trained on a visually-classified reference set of several hundred galaxies.
-\citet{cas07} use a combination of $C$, $A$, $G$, and $M_{20}$ \citep{cas05} to classify all galaxies with $m_\mathrm{I,petro}<25$.
-They divide galaxies into three broad morphological categories: early-type, spirals, and irregulars.
-A very similar method is employed by \citet{tas11}; they use the same non-parametric indices to determine galaxy morphology, but with a slightly different method of calculating the Petrosian radius.
-64\% of the galaxies have identical classifications in \citet{cas07} and \citet{tas11}; roughly two-thirds of the disagreements are galaxies originally classified as ``irregular'' in \citet{cas07} but ``spiral'' in \citet{tas11}.
-
-Using a 0.5\arcsec{} positional match, we find 76,241 galaxies with morphologies in both GZH and \citet{cas07}.
-At the lowest values of \pbest, $\sim10\%$ of the \citet{cas07} galaxies are classified as irregular, only $\sim30\%$ as early-type, and $60\%$ as spiral.
-The early-type fraction drops with increasing \pbest, with an increasing proportion of irregulars.
-The \podd{} vote fraction distinguishes sharply between spirals and irregulars at \podd$>0.2$.
-
-Despite using a similar classification method to \citet{cas07}, the \citet{tas11} classifications show significantly different trends as a function of GZH classifications.
-Spiral galaxies consistently make up $\sim60\%$ of the sample at \emph{all} \pbest, with a mild increase at \pbest$\simeq1.0$.
-Early-type and irregular galaxies make up the remainder, smoothly varying between irregulars at low \pbest{} and early-types and high \pbest.
-
-% Show the fraction of galaxies in each category as a function of p_features and p_odd?
 

### 2016-04-29 writeup/gz_hubble_data.tex
Finished first draft of external comparison section

@@
 
-\subsection{Comparison to other catalogs}\ref{ssec:comparisons}
-
-Compare GZH data to:
-
-\begin{itemize}
-    \item \citet[ZEST;][]{sca07} (COSMOS)
-    \item Tasca (COSMOS)
-    \item Cassata (COSMOS)
-    \item Zajmoski (COSMOS)
-    \item \sout{GEMS morphologies} \citep{hau07}
-    \item \sout{AEGIS morphologies} \citep{lot08}
-    \item \sout{GOODS N/S morphologies} \citep{bun05}
-\end{itemize}
-
-{\note \textit{Address trends seen in broad morphological classes, possible reasons for difference.
-Also should attempt to map between the GZH vote fractions and whatever classification systems are used in the above systems.}}
-
-\subsubsection{GEMS}
-
-Morphologies for galaxies in GEMS imaging have been measured by \citet{hau07}, who perform a careful comparison of single-component \sersic{} fits to the F850LP imaging using both the \galfit{} and \gimtwod{} codes.
-We compare the GZH morphological vote fractions to the \galfit{} parameters, which are evaluated by \citet{hau07} as more reliable due to \galfit's ability to fit multiple galaxies and handle crowded fields.
-
-A single \sersic{} fit is often a poor fit to the light profile of a resolved galaxy, since large numbers of classical spirals have both a de~Vaucouleurs bulge at the center and an exponential disc at larger radii.
-If a single parameter is used, however, a common division in the literature is to split on the \sersic~index $n$ into disc-dominated galaxies ($n<2.5$) and bulge-dominated galaxies ($n>2.5$), where $n$ is the exponent in the radial surface brightness profile such that $\Sigma(r)=\Sigma_e \exp{\left(-\kappa[(r/r_e)^{1/n} - 1]\right)}$.
-
-A 1\arcsec~positional match for the GEMS galaxies in Table~9 in \citet{hau07} to the GZH sample gives 8,846~galaxies found in both samples.
-We analyze galaxies for which the \galfit{} parameters are flagged as being constrained within plausible physical limits, indicating a moderately robust fit.
-There is a strong correlation between $n$ and \pbest; the average value for disk-dominated galaxies ($n<2.5$) is $\langle$\pbest$\rangle=0.44\pm0.26$, compared to $\langle$\pbest$\rangle=0.30\pm0.25$ for bulge-dominated galaxies ($n>2.5$).
-The correlation is stronger for bulge-dominated galaxies; for $n>2.5$, most galaxies have \pbest$<0.2$.
-In contrast, while $n<2.5$ do have higher \pbest~values, the spread is larger and there are significant numbers of galaxies even at the highest \pbest{} values.
-
-Inverting the comparison, we split the GZH galaxies into three samples: ``clean'' disks (\pbest$\ge0.8$), ``clean'' ellipticals (\pbest$\le0.2$), and ``intermediate'' ($0.2<$\pbest$<0.8$) galaxies \citep[eg,][]{sch14}.
-Splitting by $n<2.5/n>2.5$, clean disks are $85\%/17\%$, intermediates $84\%/16\%$, and clean ellipticals $59\%/41\%$.
-There is a strong dependence for these ratios on the brightness of the galaxy, which affects both automatic fits and visual accuracy.
-Limiting the sample to galaxies with $m_{850LP}<21$ gives fractions of: clean disks are $77\%/23\%$, intermediates $52\%/48\%$, and clean ellipticals $38\%/62\%$.
-While the clean disk fraction is largely unchanged, intermediates are more evenly balanced and there is a larger population of smooth galaxies with high $n$, as expected.
-
-We visually inspect galaxies for which the \galfit{} and GZH measurements indicate strong disagreement.
-Of the 84~galaxies with $n>2.5$ and \pbest$\ge0.80$, almost all are spirals with obvious disks and clearly marked spiral arms.
-These appear to be cases where \galfit{} fits the bulge at the center, but misses extended emission from the disk.
-We also examine the 35~galaxies with $n<2.5$ and \pbest$\le0.20$; these galaxies generally have smoother light profiles with no spiral arms, although several have bars and/or the sharper truncation of light near the edges that indicates an S0 galaxy.
-These galaxies are also significantly bluer $(\langle m_{606}-m_{850}\rangle=0.27\pm3.3)$ compared to the majority of galaxies classified as ``smooth'' in GZH $(\langle m_{606}-m_{850}\rangle=1.2\pm1.7)$.
-We interpret this as evidence for the fact that single-component radial fits are often inadequate to accurately characterize galaxy morphology, and that a simple cut risks significant amounts of misclassified objects.
-
-Clumpy galaxies in GZH have \galfit{} parameters more consistent with disky, $n<2.5$ galaxies than spheroids (Figure~\ref{fig:clumpy_gems}).
-Using the thresholds in Table~\ref{tbl:thresholds}, GZH clumpy galaxies have average values of $n=1.6\pm1.2$ and $R_e=32\pm16$~pix, with only 11\% of clumpy galaxies falling in the bulge-dominated region of $n>2.5$.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.50\textwidth]{figures/gems_clumpy.png}
-\caption{Parameter distributions for GEMS galaxies in \citet{hau07} and GZH.
-Red and blue points indicate galaxies split by their \sersic~index (at $n=2.5$) into disk- and bulge-dominated galaxies, respectively.
-Galaxies identified as ``clumpy'' in GZH are labeled in green.}
-\label{fig:clumpy_gems}
-\end{center}
-\end{figure}
-
-\subsubsection{AEGIS}
-
-Galaxies in AEGIS were morphologically classified using non-parametric measurements by \citet{lot08}.
-They use the Gini coefficient ($G$), which measures the relative inequality in pixel brightness, and $M_{20}$, the second-order moment of the brightest 20\% of the light \citep{lot04}.
-A linear combination of $G$ and $M_{20}$ to delineate three broad categories of galaxy morphology: E/S0/Sa (bulge-dominated/spheroids), Sb/Sc/Ir (disk-dominated/irregulars), and mergers.
-
-We compare the GZH vote fractions to the morphological categories defined by their $G$-$M_{20}$ values, which are measured in both $V$- and $I$-band.
-A 1\arcsec{} positional match on AEGIS from \citet{lot08} and GZH yields 7,508~galaxies; of those, we analyze a subsample of 4,031 with reliably-measured morphologies and $S/N>3$ in both bands.
-
-The GZH morphologies are reasonably correlated with the $G$-$M_{20}$ morphological categories.
-For galaxies labeled as Sb/Sc/Ir by \citet{lot08}, 58\% of the galaxies in $I$-band (61\% in $V$-band) have \pbest{} above a nominal cut of 0.5.
-E/S0/Sa galaxies have a tighter relation, with 78\% of galaxies in $I$-band (79\% in $V$-band) having $p_\mathrm{smooth}>0.5$.
-Galaxies with high \pbest{} are largely concentrated in the E/S0/Sa region of $G$-$M_{20}$ space; the small overlaps into mergers and E/S0/Sa are close to what we expect for loosely defined boundaries.
-Galaxies with low \pbest{} have a much broader range of $G$-$M_{20}$ values, with nearly half lying well within the Sb/Sc/Ir region.
-
-Of the 47~galaxies identified by GZH as mergers in the cross-matched AEGIS sample (selected as \pmerger$>0.5$ and $N_\mathrm{merger}\ge20$), roughly two-thirds fall in the merger region of $G$-$M_{20}$ space defined in \citet{lot08}; almost all the remainder would be classified as Sb/Sc/Ir.
-Galaxies identified as mergers by $G$-$M_{20}$, in contrast, typically have lower \pmerger{} values; 66\%/50\% in $V$-band and $I$-band, respectively.
-While the total number of mergers identified in GZH is roughly $\times10$ fewer than the volume-limited $G$-$M_{20}$ sample, we do confirm the result of a non-evolving merger fraction between $0.2<z<1.2$.
-%The average bulge statistic for the GZH mergers \citep[as defined in][]{sny15} is $F=-0.3\pm0.5$ in $V$-band and $F=-0.2\pm0.5$ in $I$-band.
-
-\subsubsection{GOODS}
-
-Galaxies in the GOODS-N and GOODS-S fields down to a limit of $z_{AB}=22.5$ have been visually classified by a single expert (R.S.~Ellis), inspecting both $z$-band and composite $Viz$ color images \citep{bun05}.
-These morphologies are assigned a numerical value based on categories in \citet{bri98a}; these are combined into broader categories of ``E/S0'' (classes 0,1,2), ``Spirals'' (classes 3,4,5), and ``Peculiar/Irregular'' (classes 6,7,8).
-\citet{bun05} use these morphologies to show that there are an increasing proportion of early-type galaxies observed at later times.
-
-Matching the \citet{bun05} catalog to GZH with a 0.5\arcsec{} radius yields 2435 galaxies (1300 in GOODS-N, 1135 in GOODS-S).
-We compare their broad morphological categories to \pbest{} in GZH; demographics of the separate GOODS-N and GOODS-S samples are highly consistent.
-``E/S0'' galaxies are dominated by high smooth fractions in GZH, with an average value of $\langle p_\mathrm{smooth,best}\rangle=0.54\pm0.20$.
-The effect is stronger when examining sub-divisions; pure E galaxies have the highest $p_\mathrm{smooth,best}$ values, while S0 have the lowest.
-Visual inspection of galaxies designated as S0 show numerous examples of both edge-on galaxies and visible substructure in the disk, including spiral arms.
-This is consistent with the design of the GZH decision tree, and likely reflects that the expert categories are using different criteria.
-
-``Spiral'' galaxies in \citet{bun05} have robustly high GZH vote fractions of features and/or disks, with $\langle p_\mathrm{features,best}\rangle=0.59\pm0.06$.
-The vote fraction increases with Hubble type, with Scd galaxies having the highest average \pbest{} values.
-``Peculiar/Irregular'' galaxies have similar ranges of \pbest{} to the ``Spiral'' galaxies, but can be sub-selected with cutoffs on $p_\mathrm{odd}$ and $p_\mathrm{irregular}$ or $p_\mathrm{merger}$.
-We note that mergers are not strongly correlated in GZH and the expert visual classifications; between 20\%--30\% have GZH merger fractions of zero, while even clear tidal tails can be as low as $p_\mathrm{merger}\sim0.1$.
-The total number of major mergers is small enough that expert visual inspection can be practically done on all candidates; a combination of methods may be the most accurate way of identifying these rarer objects, especially when the signs of interaction are relatively subtle.
+\subsection{Comparing GZH morphologies to other catalogs}\label{ssec:comparisons}
+
+All of the Legacy surveys included in the GZH imaging have had morphological catalogs previously published; these catalogs have significant differences in the number of galaxies, size and magnitude limits, classification scheme, and the methods used for measuring morphology.
+We cross-match several of these catalogs to GZH and compare the results; this is not presented as an endorsement of any particular method, but as an exploration of the strengths and weaknesses of the GZ crowdsourced catalogs as compared to products made with machine learning, automatic fits, and expert visual classification.
+
+The types and accuracies of morphological classification strongly depend on the sample and methods being used.
+In an attempt to make a consistent comparison between different techniques, we broadly group galaxies classified into three categories: bulge-dominated/elliptical/smooth, disk-dominated/spiral, and irregular/clumpy.
+These categories are compared to two parameters in GZH: \pbest, which is designed to identify smooth (elliptical) galaxies, and \podd, which is designed to identify deviations from well-formed spirals or S0s and which constitutes a ``catch-all'' for the variety of asymmetric morphologies that can constitute an irregular galaxy.
+
+Morphologies for GEMS galaxies were measured by \citet{hau07}, who use single-component \sersic{} fits to the F850LP imaging.
+We use parameters from the \galfit{} code, which \citet{hau07} evaluated as more reliable than \gimtwod{} for GEMS due to the ability to fit multiple galaxies in crowded fields.
+A 1\arcsec~positional match for the GEMS galaxies in Table~9 in \citet{hau07} to the GZH sample gives 8,846~galaxies in both \citet{hau07} and GZH.
+The main morphological parameter in the automated catalog is the \sersic{} index $n$ defining the radial surface brightness profile.
+We designate ``elliptical'' galaxies as those with $n>2.5$ and ``spirals''  with $n>2.5$.
+There is no automatic measurement of irregular or clumpy structure in this catalog.
+
+AEGIS galaxies were morphologically classified using non-parametric measurements by \citet{lot08}.
+This method uses a combination of the Gini coefficient ($G$), which measures the relative inequality in pixel brightness, and $M_{20}$, the second-order moment of the brightest 20\% of the light \citep{lot04}.
+A linear combination of $G$ and $M_{20}$ delineates their three broad categories of galaxy morphology: E/S0/Sa (``elliptical''), Sb/Sc/Ir (``spiral''), and mergers (``irregular'').
+A 1\arcsec{} positional match on AEGIS and GZH yields 4,031 galaxies with reliably-measured morphologies and $S/N>3$ in both $V$- and $I$-bands.
+
+Galaxies in both of the GOODS fields down to a limit of $z_{AB}=22.5$ were visually classified by a single expert (R.S.~Ellis), inspecting both $z$-band and composite $Viz$ color images \citep{bun05}.
+These morphologies are assigned a numerical value based on categories in \citet{bri98a}; the corresponding morphologies used are ``elliptical'' (classes 0,1,2), ``spirals'' (classes 3,4,5), and ``irregular'' (classes 6,7,8).
+A 0.5\arcsec{} matched radius yields 2,435 galaxies (1300 in GOODS-N, 1135 in GOODS-S) in both \citet{bun05} and GZH.
+
+COSMOS galaxies have multiple published datasets automatically classifying their morphologies, all using a variation of non-parametric measurements.
+\citet{cas07} use a combination of concentration ($C$), asymmetry ($A$), $G$, and $M_{20}$ \citep{cas05} to classify all galaxies with $m_\mathrm{I,petro}<25$, and use an empirical division based on several hundred training images to assign galaxies to discrete morphological categories.
+A similar method is employed by \citet{tas11}, using the same non-parametric indices but with a different method of calculating the Petrosian radius and total light profile.
+They employ a nearest-neighbors method is used to assign morphological categories for the entire sample based on a small training set.
+\citet[][ZEST]{sca07} use $C$, $A$, $G$, $M_{20}$, the galaxy ellipticity ($\epsilon$), and \sersic{} index ($n$) to quantify the galaxy shapes; a principal component analysis is used to assign galaxies to discrete morphological categories.
+The categories in all three methods are split into ellipticals, spirals, and peculiar/irregulars.
+A 0.5\arcsec{} radius search on GZH matches to 76,241 galaxies in \citet{cas07}, 76,608 in \citet{tas11}, and 77,425 in \citet{sca07}.
+
+\begin{figure*}
+\center
+\includegraphics[width=1.0\textwidth]{figures/comparisons.png}
+\caption{Distributions of morphological parameters for galaxies matched in GZH and other published catalogs, split by survey (AEGIS, COSMOS, GEMS, and GOODS).
+The first and third columns show the fraction of overall galaxies in the matched samples, split by their published morphologies as a function of the GZH \pbest.
+The corresponding second and fourth columns show data for the same galaxies as a function of \podd.
+Confidence intervals for each binned fraction in the bin are calculated for a binomial population \citep{cam11}.}
+\label{fig:comparisons}
+\end{figure*}
+
+Figure~\ref{fig:comparisons} shows the proportion of galaxies as split by their automated/expert visual morphologies for each of the six catalogs matched to GZH.
+The relation between GZH and the automated/expert morphologies is shown to vary significantly for different surveys --- this may be due to intrisic differences in the galaxies, in the techniques used to measure morphology, or both.
+The distribution of \pbest{} for AEGIS galaxies is essentially flat for spirals, showing almost no difference in proportion at the highest and lowest ends.
+Early-type galaxies are at their highest proportion at \pbest$\sim0$, but constitute only 40\% of the galaxies at most.
+In contrast, GOODS galaxies at low \pbest{} are dominated by early-types, although spiral and irregular galaxies have comparable sizes as low as \pbest$\sim0.2$.
+In GEMS galaxies, the impact of irregular or peculiar galaxies is not measured; splitting on $n=2.5$ gives an essentially flat proportion of ellipticals to spirals at \pbest$>0.3$.
+Visual inspection of images of galaxies where both \pbest{} and $n$ are high show that the majority are obvious spirals but with prominent bulges, indicating that the single-component \sersic{} fit is likely choosing too small of an effective radius and missing the extended disk structure for a large population of galaxies.
+
+Even within the same sample of galaxies in COSMOS, different techniques of measuring morphology show significant differences.
+Both \citet{cas07} and \citet{tas11} have higher proportions of early-type galaxies at \pbest$\sim0$, but constitute less than half the sample in both cases.
+The majority of all galaxies in \citet{sca07}, in contrast, are spirals; oddly, the \emph{highest} proportions of spirals are found at the lowest values of \pbest.
+The decrease in spiral galaxies at higher \pbest{} is almost entirely balanced by an increase in irregulars.
+Early-types have a small bump near \pbest$\sim0.15$, but never constitute more than 10\% of the sample.
+
+The second set of plots in Figure~\ref{fig:comparisons} indicates that \podd{} is largely an effective method for separating irregular and/or peculiar galaxies from spirals.
+Despite the somewhat vague wording of the ``anything odd?'' question in GZH, the AEGIS, COSMOS, and GOODS all show a marked increase in the irregular fraction increasing with \podd.
+Any threshold value for distinguishing between the two, however, depends strongly on survey/redshift~range.
+
+As the data shown in Figure~\ref{fig:comparisons} cover a wide range of redshifts and sizes, a volume-limited sample of galaxies (or at least binning by redshift) is likely a much more appropriate comparison.
+While we leave detailed analysis to a further paper, we note that there is no strong change in the proportion of galaxies when binning by redshift intervals of $\Delta z=0.2$ out to $z=1.0$.
 

### 2016-04-29 writeup/gz_hubble_data.tex

--- 2016-04-28 writeup/gz_hubble_data.tex
@@
 In the FERENGI data, these numbers severely limit the amount of information we can extract for the higher-tier questions.
-The debiasing technique used (Section~\ref{ssec:zeta}) require that at least 5~users answer each question for a galaxy image at $z=0.3$ \emph{and} its image at higher redshift.
-This requirement placed on both images is not met by a significant number of galaxies for questions beyond Task~01.
-The FERENGI images classified do not have sufficient numbers of objects in the surface brightness/redshift bins to accurately measure if the relation between vote fractions and redshift is single-valued.
-
-for this reason we only offer debiased vote fractions for Task~01 (smooth/features/artifact).
-
-{\note Perhaps compute number of galaxies that can be fit to zeta for each question, show a table? overkill?}
-
-In Section \ref{sec:ferengi_bar} we show results of an attempt to measure $\zeta$ for $\rm p_{bar}$.
+The debiasing technique used (Section~\ref{ssec:zeta}) require that at least 10~users answer each question for a galaxy image at $z=0.3$ \emph{and} its image at higher redshift.
+This requirement is by default met by all galaxies when analyzing the first question, since it is asked of all users.
+This requirement is often \emph{not} met for questions beyond Task~01; on average 59\% of the galaxies do not have sufficient data to measure a correction, as compared to 2\% acheived for Task~01 (see Table~\ref{tbl:ferengi_corrections}).
+Of the remaining FERENGI galaxies which did meet this requirement, the data available in each redshift-surface brightness bin were not tightly correlated between $p_{task,z=0.3}$ and $p_{task,z}$, and relationships between the two could not be fit with high confidence.
+We use these galaxies to compute $\zeta$ for each Task, and find the p-values for the resulting functions between $placeholder < p < placeholder$, which we consider insufficient for deriving a correction.
+We show an example of this in Section \ref{sec:ferengi_bar}, where we show results of measuring $\zeta$ for $p_{\rm bar}$ in Task~03.
+For this reason we only offer debiased vote fractions for Task~01 (smooth/features/artifact).
 

### 2016-04-29 writeup/gz_hubble_data.tex
Wrote a quick version of abstract and summary; removed almost all nred text.

@@
 
-\title{Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging}
+\title{Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging}
 %% Use \author, \affil, plus the \and command to format author and affiliation 
@@
 % Note: 250-word limit
-This is the data release paper for GZ:Hubble\footnote{This publication has been made possible by the participation of more than 200,000 volunteers in the Galaxy Zoo project.
-Their contributions are individually acknowledged at \url{http://authors.galaxyzoo.org/authors.html}.}.
-We present the classifications, the methodology for data reduction and corrections for redshift dependent biases in the observed morphologies.
+We present the data release paper for the Galaxy Zoo: Hubble project.\footnote{This publication has been made possible by the participation of more than 200,000 volunteers in the Galaxy Zoo project.
+Their contributions are individually acknowledged at \url{http://authors.galaxyzoo.org/authors.html}.} This is the third phase in a large effort to measure reliable morphologies of galaxies on detailed scales by using crowdsourced visual classifications of color composite image.
+Images in Galaxy Zoo: Hubble are selected from various \textit{HST} Legacy surveys taken with the Advanced Camera for Surveys, including AEGIS, COSMOS, GEMS, GOODS-N, and GOODS-S.
+Galaxies are included for GZH classifications down to magnitude limits of $m_{I}<23.5$ and have a median redshift of $\langle z\rangle=0.9\pm0.6$, with a tail extending out to sources as high as $z\simeq4$.
+The morphological data includes measurements of bulge vs.
+disk-dominated galaxies, details on spiral disk structure that relate to the Hubble type, and numerous measurements of clump identification and geometry.
+We also describe and employ a novel method for calibrating morphological bias by using artificially-redshifted galaxy images as a baseline.
+This paper presents both the raw and calibrated morphological vote fractions for $150,771$ galaxies, constituting a large data set suitable for large-scale studies of galaxy evolution.
 
@@
 \begin{table*}
+\center
 \caption{Summary of Galaxy Zoo: Hubble imaging \label{tbl:gzh_numbers}}
@@
 we use that, else 3DHST, else MUSYC.
-We show in Figure~\ref{fig:speczs} that over 98\% of the the spec-z's are consistent with each other, and therefore the priority order of selection makes no negligible difference.
+More 98\% of the matched spec-$z$'s are consistent at $\Delta z<0.001$; therefore, the priority order of selection makes no negligible difference in this sample.
 If no spectroscipic redshifts are available, we compare the 1-$\sigma$ errors of the photometric (ACS-GC, 3DHST, MUSYC, UltraVISTA) and grism (UltraVISTA) redshifts, and use the redshift with the smallest error.
@@
 
-\begin{figure*}
-\center
-\includegraphics[width=160mm]{figures/specz_comparison.pdf}
-\caption{Spectroscopic redshifts from the ACS-GC, 3DHST, and MUSYC catalogs.
+%\begin{figure*}
+%\center
+%\includegraphics[width=160mm]{figures/specz_comparison.pdf}
+%\caption{Spectroscopic redshifts from the ACS-GC, 3DHST, and MUSYC catalogs.
 The number in the upper left of each plot is the percentage of redshifts which agree within $\Delta z < 0.05$ between the two catalogs being compared in each panel.
 Within this range there is over 98\% agreement in redshifts between all three catalogs.}
-\label{fig:speczs}
-\end{figure*}
+%\label{fig:speczs}
+%\end{figure*}
 
@@
 \center
-\includegraphics[width=160mm]{figures/gzh_interface.png}
-\caption{Screenshot of the Galaxy Zoo: Hubble interface showing an example COSMOS image at the first step in the decision tree.\label{fig:interface}}
-\end{figure*}
-
-\begin{figure*}
-\center
 \includegraphics[width=\textwidth]{figures/gzh_decision_tree.pdf}
@@
 
+\subsection{Interface and decision tree}\label{ssec:interface}
+
+\begin{figure*}
+\center
+\includegraphics[width=160mm]{figures/gzh_interface.png}
+\caption{Screenshot of the Galaxy Zoo: Hubble interface at the beginning of a classification, with the user ready to select an answer for the first question in the decision tree.\label{fig:interface}}
+\end{figure*}
+
 \section{Correcting for redshift-dependent classification bias}\label{sec:debiasing}
 
-The previous versions of Galaxy Zoo morphology classifications \citep{lin08,wil13} were based on observations of galaxies in the Sloan Digital Sky Survey (SDSS) which are typically at $z<0.1$.
-In these cases it was assumed that there was no cosmological evolution of the morphologies of galaxies and therefore any observed changes in the distribution of galaxies with different consensus morphologies was due to the effects of redshift on the image quality (\ie.
+The previous versions of Galaxy Zoo morphology classifications \citep{lin08,wil13} were based on observations of galaxies in the Sloan Digital Sky Survey (SDSS) which have a median redshift of $z<0.2$.
+In these cases, it was assumed that there was no cosmological evolution of the morphologies of galaxies and therefore any observed changes in the distribution of galaxies with different consensus morphologies was due to the effects of redshift on the image quality (\ie.
 the reduction in physical resolution, surface brightness dimming, etc).
@@
 We selected 288 unique galaxies from SDSS imaging to run through the \ferengi{} code.
-The selection spanned a variety of galaxy morphologies (as selected by GZ2 classifications) and $r^\prime$-band surface brightnesses, and also spanned the redshift range of SDSS targets (in $N_z = 4$ bins) in order to be optimised for different target minimum redshifts in \hst{} imaging.
-
-The selection criteria for the different morphological categories is summarised in Table \ref{tbl:morphologies}.
-The surface brightness selection ($N_\mu = 3$) was (1) low: $\mu > 21.5$~\magarc;  (2) mid: $20.5 < \mu < 21.5$~\magarc; and (3) high: $\mu < 20.5$~\magarc.
+The selection spanned a variety of galaxy morphologies (as selected by GZ2 classifications) and $r^\prime$-band surface brightnesses, and also spanned the redshift range of SDSS targets (in $N_z = 4$ bins) in order to be optimized for different target minimum redshifts in \hst{} imaging.
+
+%The selection criteria for the different morphological categories is summarized in Table \ref{tbl:morphologies}. 
+The surface brightness selection ($N_\mu = 3$) for the FERENGI galaxies was (1) low: $\mu > 21.5$~\magarc;  (2) mid: $20.5 < \mu < 21.5$~\magarc; and (3) high: $\mu < 20.5$~\magarc.
 For each of the four ``target redshifts'' ($z = 0.3, 0.5, 0.8$ and $1.0$), the images were redshifted in $\Delta z = 0.1$ bins up to $z=1.0$.
 
-\begin{table*}
-\caption{Summary of morphological categories selected for FERENGI sample.\label{tbl:morphologies}}
-\begin{tabular}{lllc}
-\hline\hline
-Morphology          & Label &  Selection                                                                                            & $N_{\rm objects}$ \\
-                    &       &                                                                                                       & [$N_z \times N_\mu$] \\
-\hline
-Features            & Yes       & $p_{\rm features} > 0.8$, $p_{\rm odd} < 0.1$                                                         & 12 \\ 
-                    & Int.      & $0.3 < p_{\rm smooth} < 0.6$, $p_{\rm odd} < 0.1$                                                     & 12 \\ 
-                    & No        & $p_{\rm smooth} > 0.8$, $p_{\rm odd} < 0.1$                                                           & 12 \\ 
-Merger              & No        & $p_{\rm features} > 0.8$, $p_{\rm odd < 0.1}$, $p_{\rm merger} < 0.1$                                 & 12 \\
-                    & Int.      & $p_{\rm odd} > 0.5$, $0.1< p_{\rm merger} < 0.4$                                                      & 12 \\ 
-                    & Yes       & $p_{\rm odd} > 0.5$, $p_{\rm merger} > 0.4$                                                           & 12 \\
-Edge-on             & Yes       & $p_{\rm edgeon} > 0.8$, $p_{\rm features} > 0.5$                                                      & 12 \\
-                    & Int.      & $0.4 < p_{\rm edgeon} < 0.8$ , $p_{\rm features} > 0.5$                                               & 12 \\
-                    & No        & $p_{\rm edgeon} < 0.2$, $p_{\rm features} > 0.5$                                                      & 12 \\
-Bar                 & No        & $p_{\rm bar} < 0.1$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                                 & 24 \\
-                    & Int.      & $0.2 < p_{\rm bar} < 0.4$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                           & 24 \\
-                    & Yes       & $p_{\rm bar} > 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                                 & 24 \\
-Visible spiral      & No        & $p_{\rm spiral} < 0.2$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$         & 12 \\
-                    & Int.      & $0.2 < p_{\rm spiral} < 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$   & 12 \\
-                    & Yes       & $p_{\rm spiral} > 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$         & 12 \\
-Oblique bulge size  & No        & $p_{\rm nobulge>0.6}$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$          & 12 \\
-                    & Int.      & $p_{\rm justnoticeable}>0.6$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$   & 12 \\
-                    & Yes       & $p_{\rm obvious|dominant}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$ & 12 \\
-Edge-on bulge shape & Round     & $p_{\rm rounded}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.5$                               & 12 \\
-                    & Boxy      & $p_{\rm boxy}>0.4$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.2$                                  & 12 \\
-                    & No bulge  & $p_{\rm nobulge}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.5$                               & 12 \\
-\hline\hline
-\end{tabular}
-\end{table*}
+%\begin{table*}
+%\center
+%\caption{Summary of morphological categories selected for FERENGI sample.\label{tbl:morphologies}}
+%\begin{tabular}{lllc}
+%\hline\hline
+%Morphology          & Label &  Selection                                                                                            & $N_{\rm objects}$ \\
+%                    &       &                                                                                                       & [$N_z \times N_\mu$] \\
+%\hline
+%Features            & Yes       & $p_{\rm features} > 0.8$, $p_{\rm odd} < 0.1$                                                         & 12 \\ 
+%                    & Int.      & $0.3 < p_{\rm smooth} < 0.6$, $p_{\rm odd} < 0.1$                                                     & 12 \\ 
+%                    & No        & $p_{\rm smooth} > 0.8$, $p_{\rm odd} < 0.1$                                                           & 12 \\ 
+%Merger              & No        & $p_{\rm features} > 0.8$, $p_{\rm odd < 0.1}$, $p_{\rm merger} < 0.1$                                 & 12 \\
+%                    & Int.      & $p_{\rm odd} > 0.5$, $0.1< p_{\rm merger} < 0.4$                                                      & 12 \\ 
+%                    & Yes       & $p_{\rm odd} > 0.5$, $p_{\rm merger} > 0.4$                                                           & 12 \\
+%Edge-on             & Yes       & $p_{\rm edgeon} > 0.8$, $p_{\rm features} > 0.5$                                                      & 12 \\
+%                    & Int.      & $0.4 < p_{\rm edgeon} < 0.8$ , $p_{\rm features} > 0.5$                                               & 12 \\
+%                    & No        & $p_{\rm edgeon} < 0.2$, $p_{\rm features} > 0.5$                                                      & 12 \\
+%Bar                 & No        & $p_{\rm bar} < 0.1$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                                 & 24 \\
+%                    & Int.      & $0.2 < p_{\rm bar} < 0.4$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                           & 24 \\
+%                    & Yes       & $p_{\rm bar} > 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                                 & 24 \\
+%Visible spiral      & No        & $p_{\rm spiral} < 0.2$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$         & 12 \\
+%                    & Int.      & $0.2 < p_{\rm spiral} < 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$   & 12 \\
+%                    & Yes       & $p_{\rm spiral} > 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$         & 12 \\
+%Oblique bulge size  & No        & $p_{\rm nobulge>0.6}$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$          & 12 \\
+%                    & Int.      & $p_{\rm justnoticeable}>0.6$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$   & 12 \\
+%                    & Yes       & $p_{\rm obvious|dominant}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$ & 12 \\
+%Edge-on bulge shape & Round     & $p_{\rm rounded}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.5$                               & 12 \\
+%                    & Boxy      & $p_{\rm boxy}>0.4$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.2$                                  & 12 \\
+%                    & No bulge  & $p_{\rm nobulge}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.5$                               & 12 \\
+%\hline\hline
+%\end{tabular}
+%\end{table*}
 
@@
 \caption{Examples of two galaxies which have been run through the FERENGI code to produce simulated \hst{} images.
-The value of \pfeatures{} for each panel is (1) Top row: \pfeatures~= 0.9, 0.625, 0.35, 0.35, 0.225 and (2) Bottom row: \pfeatures~= 1.00, 0.875, 0.875, 0.625, 0.375.
+The measured value of \pfeatures{} from GZH for the images in each panel are (1) Top row: \pfeatures~= (0.900, 0.625, 0.350, 0.350, 0.225) and (2) Bottom row: \pfeatures~= (1.000, 0.875, 0.875, 0.625, 0.375).
 \label{fig:exampleFERENGI}}
@@
 \caption{Behavior of the normalized, weighted vote fractions of features visible in a galaxy ($f_\textrm{features}$) as a function of redshift in the artifical \ferengi{} images.
-Galaxies are a random selection of images with $e=0$ and at least three detectable images in redshift bins of $z\ge0.3$.
-The measured vote fractions (red points) are fit with an exponential function (Equation~\ref{eqn:fzeta}); the best-fit parameters are given above each plot.
+Galaxies in this plot were randomly selected from a distribution with $e=0$ and at least three detectable images in redshift bins of $z\ge0.3$.
+Measured vote fractions (red points) are fit with an exponential function (Equation~\ref{eqn:fzeta}); the best-fit parameters are given above each plot.
 Error bars are Poissonian, assuming a median of 40~votes per galaxy.}
@@
 [a]: Each point in a given redshift and surface brightness bin represents a unique galaxy.
-On the y-axis in each bin is the \pfeatures{} value of the image of that galaxy redshifted to the value corresponding to that redshift bin.
-On the x-axis is the \pfeatures{} value of the image of the same galaxy redshifted to $z=0.3$.
+On the $y$-axis in each bin is the \pfeatures{} value of the image of that galaxy redshifted to the value corresponding to that redshift bin.
+On the $x$-axis is the \pfeatures{} value of the image of the same galaxy redshifted to $z=0.3$.
 The dashed black lines represent the best-fit polynomials to the data in each square.
@@
 Each $z,\mu$ bin is divided into 4 sub-bins to determine the range of intrinsic \pfeaturesrest{} for a given range of observed \pfeaturesz{} values.
-In each sub-bin, the orange bars represent the inner 80th percentiles of the data, the boundaries of which are the lower and upper limits of the debiased values.
+In each sub-bin, the orange bars represent the inner 80$^\mathrm{th}$ percentiles of the data, the boundaries of which are the lower and upper limits of the debiased values.
 [d]: The same data as [b], but highlighting the upper and lower limit regions.}
@@
 In Figure~\ref{fig:p_vs_p} we examine the change in \pfeatures{} for the \ferengi{} galaxies relative to their lowest simulated redshift.
-In this analysis, only galaxies whose lowest simulated redshift image was ($\rm z_{sim}=0.3$) were used (see Table \ref{tbl:ferengivalues}), and only those which had detectable surface brightness measurements in \sextractor; this includes 3,950 of the total 6,466 images.
+In this analysis, only galaxies whose lowest simulated redshift image was $z_\mathrm{sim}=0.3$ were used (see Table \ref{tbl:ferengivalues}), and only those which had detectable surface brightness measurements in \sextractor; this includes 3,950 of the total 6,466 images.
 For each simulated redshift value $z$, and at a fixed surface brightness $\mu$, we plot \pfeaturesz, the value measured at that simulated redshift, vs \pfeaturesrest, the value measured for the same galaxy imaged at $z=0.3$.
@@
 
-Our criteria for determining whether a region of this space is single-valued, and therefore correctable, is as follows: In each surface brightness and redshift bin, we model the relationship between \pfeaturesz{} and \pfeaturesrest{} by fitting the data with a polynomials of degrees 3, 2, and 1, and use the best fit out of the three.
+Our criteria for determining whether a region of this space is single-valued, and therefore correctable, is as follows: In each surface brightness and redshift bin, we model the relationship between \pfeaturesz{} and \pfeaturesrest{} by fitting the data with a polynomial of degrees 3, 2, and 1, and use the best fit out of the three.
 These fits are shown as the dashed black lines in Figure~\ref{fig:6a}.
@@
 The unshaded regions in Figure~\ref{fig:6a} define discrete ranges of redshift, surface brightness, and \pfeatures{} a galaxy must have in order for the $\zeta$ approach to be confidentely applied to a galaxy in the GZH sample.
-While the appropriate correctable regions were defined discretely, we assume the true correctable region is a smooth function of z, $\mu$, and \pfeatures{}.
+While the appropriate correctable regions were defined discretely, we assume the true correctable region is a smooth function of $z$, $\mu$, and \pfeatures{}.
 To define this smooth space, we generate a convex hull that encloses the correctable and uncorrectable \ferengi{} galaxies in $z$-$\mu$-\pfeatures{} space.
@@
 The results of this method and final categorization of the \hst{} sample is displayed in Table~\ref{tbl:hubble_debiasable}.
-We find that of the galaxies at redshift higher than $z=z_{0}=0.3$, 17\% of these are able to be debiased using the $\zeta$ method, 27\% cannot be debiased, and 56\% cannot be determined, due to a lack of redshift or information or due to a lack of \ferengi{} data corresponding to those galaxies' redshift/surface brightness values.
+Of the galaxies at redshift higher than $z=z_{0}=0.3$, 17\% of these are able to be debiased using the $\zeta$ method, 27\% cannot be debiased, and 56\% cannot be determined, due to a lack of redshift or information or due to a lack of \ferengi{} data corresponding to those galaxies' redshift/surface brightness values.
 
@@
 Here we again use the \ferengi{} simulated data to analyze the range of intrinsic \pfeaturesrest{} values for any given observed \pfeatures{} value, again as a function of surface brightness and redshift.
-In each z,$\mu$ bin, we examine the spread of intrinsic values of \pfeaturesrest{} for 4 ranges of observed \pfeatures.
+In each $z$,$\mu$ bin, we examine the spread of intrinsic values of \pfeaturesrest{} for 4 ranges of observed \pfeatures.
 We quantify the range of intrinsic values as the inner 80\% of the data; this range is represented by the orange bars in Figure~\ref{fig:6c}.
@@
 \begin{table}
+\center
 \caption{Distribution of \ferengi{} images analysed in Figure~\ref{fig:p_vs_p}.
@@
 Uncorrectable images had a non single-valued relationship (blue regions).
-NEI images had undetermined relationships due to a lack of data ($N<5$) in their corresponding z-$\mu$ bins (gray regions).\label{tbl:ferengi_corrections}}
+NEI images had undetermined relationships due to a lack of data ($N<5$) in their corresponding $z$-$\mu$ bins (gray regions).\label{tbl:ferengi_corrections}}
 \begin{tabular}{lrr}
@@
 
-{\note
-\begin{itemize}
-\item talk about where the \hst{} sample falls in this space, reference Table~\ref{tbl:hubble_debiasable} 
-\item justify $N>5$ and spread $< 0.2$ (or find a better way to choose criteria)
-\item check out corrections for correctable and NEI, show some sample images of corrected galaxies
-\item show some data for $\pbar$, determine or justify why we won't debias them  
-\end{itemize}
-}
-
 \begin{table*}
-\caption{Breakdown of what we can correct out of the GZH data, by sample.
-\emph{updated from 3-8-16: Switching to full depth for all GOODS data.
-Shallow depth information in appendix.}\label{tbl:hubble_debiasable}}
+\caption{Correctable fractions for the top-level task in GZH, split by survey.}\label{tbl:hubble_debiasable}
 \begin{tabular}{lcrrrrrrr}
@@
 
-\subsubsection{TODO LIST}
-We need to: 
-\begin{itemize}
-\item Calculate the magnitudes, surface brightnesses and sizes of the galaxies in the FERENGI images....
-\item Plot of magnitude distribution of galaxies in each of the four GZH subsamples with the magnitudes of our fake galaxies over plotted. 
-\item Instructions of how to link the $z=0$ $p_X$ values for galaxies with a given size, magnitude (surface brightness) in the GZH images. 
-\end{itemize}
-
-\subsection{Morphological measurements in GZH beyond Task 1 - effects of debiasing?}
-\subsection{Duplicate images}
-
 \section{The catalog}\label{sec:results}
@@
 
-Each image is listed under a unique project ID (eg AHZ000001); the actual galaxy in the image is identified by the combination of the OBJNO and original survey.
+Each image is listed under a unique project ID (eg,~AHZ000001); the actual galaxy in the image is identified by the combination of the OBJNO and original survey.
 For each of the 55~responses in the GZH decision tree, the following classification data is provided: for each question, $\tt N_{votes}$ is the number of users to answer that question.
@@
 The debiased and best vote fractions for $\tt p_{smooth}$ were calculated on the critera that vote fractions for all answers must sum to unity.
-Explicitely: $\tt p_{smooth} = 1 - p_{features} - p_{artifact}$.
+Explicitly: $\tt p_{smooth} = 1 - p_{features} - p_{artifact}$.
 In some rare cases, representing  $<1\%$ of the sample, this requirement resulted in negative vote fractions for $\rm p_{smooth}$; these were cases in which the $\rm p_{features}$ vote fraction was boosted to a high value relative to the $\rm p_{artifact}$ vote fraction.
@@
 
-{\note To include: detailed description of each column in the machine-readable tables. }
-
 \section{Using the catalog}\label{sec:cookbook}
@@
 Tasks 03, 04 and 05 have an additional possible pathway; as shown in Figure~\ref{fig:decisiontree}, a user might also be shown this question if they select ``featured/disk'' in Task 01, ``clumpy'' in Task 12, two or more clumps in Task 16, and ``spiral arrangement'' in Task 15.
-By applying the appropriate thresholds for this path, we find that $< 0.5\%$ of the galaxies which have $\ge 20$ answers to these questions used this pathway to arrive at these Tasks.
+After applying the appropriate thresholds for this path, $< 0.5\%$ of the galaxies which have $\ge 20$ answers to these questions used this pathway to arrive at these Tasks.
 Further, of these subjects, none were found to exhibit disk structure, although the clumps within were arranged in a spiral pattern.
@@
 We use the complete bar sample to estimate the redshift evolution of bar fraction and find a steady decrease of $f_{bar} \sim 0.32$ at $z=0.4$ to $f_{bar} \sim 0.24$ at $z=1.0$.
-The decrease in bar fraction agrees with \ref{mel14}, however they report a lower bar fraction overall, finding a decrease from $f_{bar}=0.22$ at $z=0.4$ to $f_{bar}=0.11$ at $z=1.0$.
+The decrease in bar fraction agrees with \citet{mel14}, although they report a lower overall bar fraction going from $f_{bar}=0.22$ at $z=0.4$ to $f_{bar}=0.11$ at $z=1.0$.
 The difference in total bar fraction is expected, as our analysis used a looser cut on $p_{\rm bar}$, we did not apply a luminosity cut, and we use debiased values for $p_{\rm features}$ which increases the total amount of disks in the sample.
@@
 Clumps are known to be a characteristic feature of galaxies outside the local universe, and there is evidence they play a crutial role in the evolution of modern spirals, particularly in the formation of central bulges \citep{elm05,elm14,guo15,beh16}.
-Simulations show clumps migrate from the outer disk to the galactic center on relatively short (~few orbital periods) timescales \citep{man15} and observations show increasing bulge to clump mass and density ratios as the universe evolves since $z\sim 1.5$ \citep{elm09}, suggesting that clumps coalesce over time to form the modern bulges of disk galaxies.
+Simulations show clumps migrate from the outer disk to the galactic center on relatively short (a few orbital periods) timescales \citep{man15} and observations show increasing bulge to clump mass and density ratios as the universe evolves since $z\sim 1.5$ \citep{elm09}, suggesting that clumps coalesce over time to form the modern bulges of disk galaxies.
 GZH added a ``clumpy'' path to the decision tree for the purpose of both identifying clumps and investigating their evolution with redshift.
@@
 
-{\note
-\begin{itemize}
-    \item \sout{explain decision tree format; vote fractions are dependent on previous task vote fractions} 
-    \item \sout{provide example of how to select bars}
-    \item \sout{discuss difference between conservative/clean sample and loose/complete sample, emphasize goals differ depending on science case}
-    \item \sout{science with bar example - estimate bar fraction vs redshift}
-    \item \sout{science with clump multiplicity }
-\end{itemize}
-} 
 \begin{table}
-\caption{Suggested thresholds for selecting morphological samples from Galaxy Zoo: Hubble \label{tbl:thresholds}}
+\caption{Suggested thresholds for selecting morphological samples from Galaxy Zoo: Hubble. \label{tbl:thresholds}}
 \begin{tabular}{llll}
@@
 01       & smooth or features   & $-$              & $-$                                \\
-02       & edge on              & 01, 12                & $p_{\rm clumpy,no}>0.30$            \\
-03       & bar		            & 01, 12, 02            & $p_{\rm edgeon,no}>0.25$           \\
-         &                      & 01, 12, 16, 15        & $p_{\rm clumpy~spiral}>0.65$  \\
-04       & spiral arms          & 01, 12, 02            & $p_{\rm edgeon,no}>0.25$           \\
-         &                      & 01, 12, 16, 15        & $p_{\rm clumpy~spiral}>0.65$  \\
-05       & bulge prominence     & 01, 12, 02            & $p_{\rm edgeon,no}>0.25$           \\
-         &                      & 01, 12, 16, 15        & $p_{\rm clumpy~spiral}>0.65$  \\
+02       & edge on              & 01,12            & $p_{\rm clumpy,no}>0.30$           \\
+03       & bar		            & 01,12,02         & $p_{\rm edgeon,no}>0.25$           \\
+         &                      & 01,12,16,15      & $p_{\rm clumpy~spiral}>0.65$       \\
+04       & spiral arms          & 01,12,02         & $p_{\rm edgeon,no}>0.25$           \\
+         &                      & 01,12,16,15      & $p_{\rm clumpy~spiral}>0.65$       \\
+05       & bulge prominence     & 01,12,02         & $p_{\rm edgeon,no}>0.25$           \\
+         &                      & 01,12,16,15      & $p_{\rm clumpy~spiral}>0.65$       \\
 06       & odd yes/no           & $-$              & $-$                                \\
@@
 08       & odd feature          & 06               & $p_{\rm odd,yes}> 0.50$            \\
-09       & bulge shape          & 01, 12, 02            & $p_{\rm edgeon,yes}>0.40$           \\
-10       & arms winding         & 01, 12, 02, 04        & $p_{\rm spiral,yes}>0.25$          \\
-11       & arms number          & 01, 12, 02, 04        & $p_{\rm spiral,yes}>0.25$          \\
+09       & bulge shape          & 01,12,02         & $p_{\rm edgeon,yes}>0.40$          \\
+10       & arms winding         & 01,12,02,04      & $p_{\rm spiral,yes}>0.25$          \\
+11       & arms number          & 01,12,02,04      & $p_{\rm spiral,yes}>0.25$          \\
 12       & clumpy               & 01               & $p_{\rm features}>0.23$            \\
-13       & bright clump         & 01, 12, 16            & $p_{\rm one~clump}< 0.40$           \\
-14       & bright central clump & 01, 12, 16, 13        & $p_{\rm bright~clump,yes}>0.50$     \\
-15       & clump arrangement    & 01, 12, 16            & $p_{\rm multiple~clumps}>0.45$     \\
-16       & clump count          & 01, 12                & $p_{\rm clumpy,yes}>0.80$           \\
-17       & clumps symmetrical   & 01, 12                & $p_{\rm clumpy,yes}>0.80$           \\
-18       & clumps embedded      & 01, 12                & $p_{\rm clumpy,yes}>0.80$           \\
+13       & bright clump         & 01,12,16         & $p_{\rm one~clump}< 0.40$          \\
+14       & bright central clump & 01,12,16,13      & $p_{\rm bright~clump,yes}>0.50$    \\
+15       & clump arrangement    & 01,12,16         & $p_{\rm multiple~clumps}>0.45$     \\
+16       & clump count          & 01,12            & $p_{\rm clumpy,yes}>0.80$          \\
+17       & clumps symmetrical   & 01,12            & $p_{\rm clumpy,yes}>0.80$          \\
+18       & clumps embedded      & 01,12            & $p_{\rm clumpy,yes}>0.80$          \\
 \hline\hline
@@
 
-Now people go and do science with these awesome GZH classifications.
+%Now people go and do science with these awesome GZH classifications.
+
+This paper presents the catalog release for the Galaxy Zoo: Hubble project, which uses crowdsourced visual classifications to measure galaxy morphologies.
+The first two phases of Galaxy Zoo \citep{lin11,wil13} used images of low-redshift galaxies from SDSS; this is the first phase of the project with space-based images of high-redshift targets (in addition to the Galaxy Zoo: CANDELS collaboration; Simmons et al., submitted).
+The final sample includes classifications for 181,101~images generated from 150,771~unique galaxies.
+Galaxies were selected from a brightness-limited sample from multiple Legacy surveys using the Advanced Camera for Surveys on the Hubble Space Telescope, including AEGIS, GEMS, GOODS-N, GOODS-S, and COSMOS.
+We also include classifications for 51,861 Sloan Digital Sky Survey images in Stripe~82 at relatively low redshift; these serve both as a low-redshift anchor for cosmological studies and a potential comparison for the different epochs of classification between GZH and Galaxy Zoo 2 \citep{wil13}.
+
+The data for the GZH catalogs has been extensively tested and reduced.
+The dominant effect is a known bias against identifying disky and asymmetric sub-structures at either low resolution or surface brightness.
+This can be the result either of genuinely small or dim galaxies, or a perceived effect from observing galaxies at further distances (higher redshift).
+To calibrate this \emph{without} potentially overcorrecting for the genuine morphological evolution of galaxies over cosmic time, we use SDSS images of low-redshift galaxies, process them to appear as if they were at higher redshift, and pass them through the GZH interface in an identical fashion.
+The resulting change in \pfeatures{} as a function of $z$,$\mu$ is applied as a multiplicative correction to the top-level vote fractions for $\sim50\%$ of the GZH galaxies.
+
+Galaxies in GZH show significant changes in the disk/elliptical fraction as a function of redshift, along with an increasing number of galaxies dominated by smaller clumps and presumed to be in the process of building up their baryonic mass through a combination of hierarchical merging and in-situ star formation.
+While the majority of scientific interpretation is left to future papers, we confirm the decrease in observed bar fraction with increasing redshift \citep{mel14} and identify a new way for identifying clumpy galaxies as a function of clump multiplicity.
+
+The full data tables for the catalogs can be accessed in machine-readable form from both the journal and at \url{http://data.galaxyzoo.org}.
 
@@
 
-\hubble{} acknowledgements.
+This work is based on (GO-10134, GO-09822, GO-09425.01, GO-09583.01, GO-9500) program observations with the NASA/ESA Hubble Space Telescope, obtained at the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS 5-26555.
 
@@
 \clearpage
+
 \appendix
+
 \section{GOODS Shallow Depth data}
@@
 \begin{table}
-\caption{Breakdown of what we can correct out of the GOODS shallow depth data. \label{tbl:goods_shallow_categories}}
+\caption{Correctable fractions for the top-level task in GZH in the GOODS shallow-depth (2-epoch) images. \label{tbl:goods_shallow_categories}}
 \begin{tabular}{lrrrrrrrr}
@@
 Of the 11,157 galaxies in the GOODS-N and GOODS-S full depth sample, 4,461 of these are in the shallow-depth sample.
-In Figure~\ref{fig:shallow_vs_full} we find a strong correlation between $\rm p_{features}$ for both sets of images.
+Figure~\ref{fig:shallow_vs_full} shows a strong correlation between $\rm p_{features}$ for both sets of images.
 The mean change in $\rm p_{features}$ from the shallow to full depth images  $\rm p_{features,full} - p_{features,shallow} \equiv \Delta p = 0.00$, with a standard deviation of $\sigma = 0.17$.
 While there is some variance in $\Delta p$ in the whole sample, the change is usually small and not often significant enough to change a morphological classification.
-Defining a clean sample of disk galaxies as those with $p_{features,best}>0.8$, elliptical galaxies as those with  $p_{smooth,best}<0.2$, and intermediate as those in between, we find that 75\% of the sample would not change morphology.
+Defining a clean sample of disk galaxies as those with $p_{features,best}>0.8$, elliptical galaxies as those with  $p_{smooth,best}<0.2$, and intermediate as those in between, 75\% of the sample would not change morphology.
 Of the remaining 25\% that would change morphology, only 0.3\% (representing 10 galaxies total) drastically change morphology from smooth to featured or visa versa, while the rest would transition to or from the ``intermediate'' morphology.
@@
 Uncorrectable images had a non single-valued relationship (blue regions).
-NEI images had undetermined relationships due to a lack of data ($N<5$) in their corresponding z-$\mu$ bins (gray regions).
+NEI images had undetermined relationships due to a lack of data ($N<5$) in their corresponding $z$-$\mu$ bins (gray regions).
 Only 17\% (maximum) of FERENGI galaxies in the sample were considered ``correctable'', which is not sufficient to compute a $\zeta$ function applicable to the Hubble data.

### 2016-04-29 writeup/gz_hubble_data.tex
Renaming 'uncorrectable' set to 'lower limit'. Closes #48

@@
 % Note: 250-word limit
-We present the data release paper for the Galaxy Zoo: Hubble project.\footnote{This publication has been made possible by the participation of more than 200,000 volunteers in the Galaxy Zoo project.
+We present the data release paper for the Galaxy Zoo: Hubble (GZH) project.\footnote{This publication has been made possible by the participation of more than 200,000 volunteers in the Galaxy Zoo project.
 Their contributions are individually acknowledged at \url{http://authors.galaxyzoo.org/authors.html}.} This is the third phase in a large effort to measure reliable morphologies of galaxies on detailed scales by using crowdsourced visual classifications of color composite image.
-Images in Galaxy Zoo: Hubble are selected from various \textit{HST} Legacy surveys taken with the Advanced Camera for Surveys, including AEGIS, COSMOS, GEMS, GOODS-N, and GOODS-S.
-Galaxies are included for GZH classifications down to magnitude limits of $m_{I}<23.5$ and have a median redshift of $\langle z\rangle=0.9\pm0.6$, with a tail extending out to sources as high as $z\simeq4$.
-The morphological data includes measurements of bulge vs.
-disk-dominated galaxies, details on spiral disk structure that relate to the Hubble type, and numerous measurements of clump identification and geometry.
+Images in GZH are selected from various \textit{Hubble Space Telescope} Legacy programs using the Advanced Camera for Surveys (AEGIS, COSMOS, GEMS, GOODS-N, and GOODS-S), with filters selected to probe the rest-frame optical emission from galaxies out to $z\simeq1$.
+The galaxies selected for GZH classifications go down to magnitude limits of $m_{I}<23.5$ and have a median redshift of $\langle z\rangle=0.9\pm0.6$, with a tail extending out to $z\simeq4$.
+The GZH morphological data includes measurements of both bulge- and disk-dominated galaxies, details on spiral disk structure that relate to the Hubble type, and numerous measurements of clump identification and geometry.
 We also describe and employ a novel method for calibrating morphological bias by using artificially-redshifted galaxy images as a baseline.
@@
 
-This paper presents the results from the Galaxy Zoo Hubble (GZH) project.
-GZH was the third phase of Galaxy Zoo, following its initial results classifying $\sim900,000$~SDSS~images into primarily early/late~types \citep{lin11} and Galaxy~Zoo~2, which covered $\sim250,000$~SDSS~images using a more detailed classification scheme that included bars, spiral arms, and galactic bulges \citep{wil13}.
+This paper presents the results from the Galaxy Zoo Hubble (GZH) project.\footnote{\url{http://zoo3.galaxyzoo.org/}} GZH was the third phase of Galaxy Zoo, following its initial results classifying $\sim900,000$~SDSS~images into primarily early/late~types \citep{lin11} and Galaxy~Zoo~2, which covered $\sim250,000$~SDSS~images using a more detailed classification scheme that included bars, spiral arms, and galactic bulges \citep{wil13}.
 GZH used a similarly detailed classification scheme, but focused for the first time on images of high-redshift galaxies taken with the \hubble.
@@
 The Stripe~82 single-epoch images were taken directly from the color composites on the DR7 SDSS Skyserver, which combines $g^{\prime}$, $r^{\prime}$, and $i^{\prime}$ exposures into the RGB channels.
-The coadded Stripe~82 images were assembled from runs (106,206) in DR7 and generated into JPGs using the method of \citet{lup04}.
+The coadded Stripe~82 images were assembled from runs 106 and 206 in DR7 and generated as JPGs using the method of \citet{lup04}.
 
@@
 Any flat regions of the polynomial fits are areas in which there is not a clear single-valued relationship between \pfeaturesz{} and \pfeaturesrest; we quantify this by setting a minimum slope cut of 0.4.
-Any data in which the polynomial fit has a slope less than this value is considered \emph{not} one-to-one, and therefore ``uncorrectable.'' These regions are highlighted in blue in Figure~\ref{fig:6a}.
+Any data in which the polynomial fit has a slope less than this value is considered \emph{not} one-to-one, and therefore \pfeaturesz{} cannot be boosted to its \pfeaturesrest{} value.
+We refer to galaxies in this region as the \emph{lower limit} sample.
+These regions are highlighted in blue in Figure~\ref{fig:6a}.
 Uncolored (white) regions of the plot have sufficiently high slopes for us to consider the relationship to be single-valued; galaxies in these regions are considered ``correctable'', and only these are used in measuring the parameters for the $\zeta$ function (Section~\ref{ssec:zeta}).
@@
 While the appropriate correctable regions were defined discretely, we assume the true correctable region is a smooth function of $z$, $\mu$, and \pfeatures{}.
-To define this smooth space, we generate a convex hull that encloses the correctable and uncorrectable \ferengi{} galaxies in $z$-$\mu$-\pfeatures{} space.
+To define this smooth space, we generate a convex hull that encloses the correctable and lower-limit \ferengi{} galaxies in $z$-$\mu$-\pfeatures{} space.
 The boundaries are then adjusted until the contamination from both groups is minimized.
-We use the resulting hulls to define the correctable and uncorrectable regions for categorizing the \hst{} galaxies.
+We use the resulting hulls to define the correctable and lower-limit regions for categorizing the \hst{} galaxies.
 The results of this method and final categorization of the \hst{} sample is displayed in Table~\ref{tbl:hubble_debiasable}.
@@
 
-For the ``uncorrectable'' galaxies, those for which we cannot confidentely assign a single debiased \pfeatures{} value, we instead determine a likely \emph{range} of debiased values, using a method visualized in Figure~\ref{fig:6c}.
+For the ``lower-limit'' galaxies for which we cannot confidently assign a single debiased \pfeatures{} value, we instead determine a likely \emph{range} of debiased values, using a method visualized in Figure~\ref{fig:6c}.
 Here we again use the \ferengi{} simulated data to analyze the range of intrinsic \pfeaturesrest{} values for any given observed \pfeatures{} value, again as a function of surface brightness and redshift.
@@
 \caption{Distribution of \ferengi{} images analysed in Figure~\ref{fig:p_vs_p}.
-Correctable images had a single-valued relationship between their measured \pfeatures{} values at high and low redshifts (white regions in Figure~\ref{fig:p_vs_p}).
-Uncorrectable images had a non single-valued relationship (blue regions).
-NEI images had undetermined relationships due to a lack of data ($N<5$) in their corresponding $z$-$\mu$ bins (gray regions).\label{tbl:ferengi_corrections}}
+Correctable images have a single-valued relationship between their measured \pfeatures{} values at high and low redshifts (white regions in Figure~\ref{fig:p_vs_p}).
+Images with only a lower-limit on \pfeatures{} have a non single-valued relationship (blue regions).
+NEI images have undetermined relationships due to a lack of data ($N<5$) in their corresponding $z$-$\mu$ bins (gray regions).\label{tbl:ferengi_corrections}}
 \begin{tabular}{lrr}
@@
 Correctable                        & 1,884   & 48\% \\
-Uncorrectable                      & 1,986   & 50\% \\
+Lower-limit                        & 1,986   & 50\% \\
 NEI                                & 80      &  2\%\\
@@
 Correctable                        & 0               & 1,654   & 15,170 & 1,837 & 993    & 835     	& 0       & 20,489\\
-Uncorrectable                      & 1               & 1,917   & 26,113 & 2,423 & 1,385  & 1,282   	& 0       & 33,120\\
+Lower-limit                        & 1               & 1,917   & 26,113 & 2,423 & 1,385  & 1,282   	& 0       & 33,120\\
 No Correction Needed ($z \le 0.3$) & 2               & 955     & 11,926 & 1,175 & 415    & 400     	& 37,545  & 52,416\\ 
@@
 \includegraphics[width=\textwidth]{figures/hubble_z_mu_p_distributions.pdf}
-\caption{Distributions of redshift, surface brightness, and $p_{features}$ for correctable (purple), uncorrectable (green), and NEI (pink) galaxies in the full GZH sample.
-The uncorrectable galaxies tend towards higher redshift, slightly lower in surface brightness, and lower values of $p_{features}$ than the correctable galaxies.
+\caption{Distributions of redshift, surface brightness, and $p_{features}$ for correctable (purple), lower-limit (green), and NEI (pink) galaxies in the full GZH sample.
+The lower-limit galaxies have higher redshifts, slightly lower surface brightness, and lower values of $p_{features}$ on average than the correctable galaxies.
 The long tail of NEI galaxies in redshift and surface brightness demonstrates the limits of the \ferengi{} sample, for which there is no data at $z>1$ or $\mu>24$.}
@@
 \includegraphics[width=\textwidth]{figures/debiased_corrections.pdf}
-\caption{Debiased $p_{features}$ corrected to $z=0.3$ vs weighted $p_{features}$ for the correctable (left), uncorrectable (middle), and NEI (right) galaxies in the GZH sample.}
+\caption{Debiased $p_{features}$ corrected to $z=0.3$ vs weighted $p_{features}$ for the correctable (left), lower-limit (middle), and NEI (right) galaxies in the GZH sample.}
 \label{fig:debiased_corrections}
@@
 For this question, we provide the additional parameters $\tt debiased$, $\tt lower~limit$, $\tt upper~limit$, and $\tt best$ vote fractions.
-The $\tt best$ fraction for $p_{features}$is chosen based on the categorization of the galaxy: if it is ``correctable'', $\tt best = debiased$, if ``uncorrectable'', $\tt best = lower~limit$, and if neither, $\tt best = weighted$.
+The $\tt best$ fraction for $p_{features}$is chosen based on the categorization of the galaxy: if it is ``correctable'', $\tt best = debiased$, if a lower limit, $\tt best = lower~limit$, and if neither, $\tt best = weighted$.
 
@@
 \tablenotetext{1}{Flag indicating how the vote fractions for this galaxy were corrected through debiasing (\S\ref{ssec:zeta_results}), if possible.
-0~=~correctable, 1~=~uncorrectable ($p_{raw}$ --- $p_{adj}$ is not single-valued), 2~=~uncorrected ($z_{\rm gal} < 0.3$), 3~=~uncorrectable (insufficient FERENGI galaxies in this $z$-$\mu$ bin), 4~=~uncorrectable (no galaxy redshift available).}
+0~=~correctable, 1~=~lower-limit ($p_{raw}$ --- $p_{adj}$ is not single-valued), 2~=~uncorrected ($z_{\rm gal} < 0.3$), 3~=~uncorrected (insufficient FERENGI galaxies in this $z$-$\mu$ bin), 4~=~uncorrected (no galaxy redshift available).}
 \tablecomments{The full version of this table is available in electronic form, as well as at \url{http://data.galaxyzoo.org}.
@@
 Correctable                        & 748     & 514     & 1,262 \\
-Uncorrectable                      & 526     & 1,143   & 1,669 \\
+Lower limit                        & 526     & 1,143   & 1,669 \\
 No Correction Needed ($z \le 0.3$) & 267     & 267     & 534   \\ 
@@
 \caption{Distribution of \ferengi{} images analysed in Figure~\ref{fig:p_vs_p_bar}.
-Correctable images had a single-valued relationship between their measured $p_{\rm bar}$ values at high and low redshifts (white regions in Figure~\ref{fig:p_vs_p_bar}).
-Uncorrectable images had a non single-valued relationship (blue regions).
+Correctable images had a single-valued relationship between their measured \pbar{} values at high and low redshifts (white regions in Figure~\ref{fig:p_vs_p_bar}).
+Galaxies with a lower-limit on \pbar{} had a non single-valued relationship (blue regions).
 NEI images had undetermined relationships due to a lack of data ($N<5$) in their corresponding $z$-$\mu$ bins (gray regions).
@@
 Correctable                        & 664   & 17\% \\
-Uncorrectable                      & 483   & 12\% \\
+Lower-limi                         & 483   & 12\% \\
 NEI                                & 2,803     & 71\%\\

### 2016-04-30 writeup/gz_hubble_data.tex
added average goodness of fit values to high order tasks in ferengi to section 4

@@
 This requirement is by default met by all galaxies when analyzing the first question, since it is asked of all users.
-This requirement is often \emph{not} met for questions beyond Task~01; on average 59\% of the galaxies do not have sufficient data to measure a correction, as compared to 2\% acheived for Task~01 (see Table~\ref{tbl:ferengi_corrections}).
-Of the remaining FERENGI galaxies which did meet this requirement, the data available in each redshift-surface brightness bin were not tightly correlated between $p_{task,z=0.3}$ and $p_{task,z}$, and relationships between the two could not be fit with high confidence.
-We use these galaxies to compute $\zeta$ for each Task, and find the p-values for the resulting functions between $placeholder < p < placeholder$, which we consider insufficient for deriving a correction.
-We show an example of this in Section \ref{sec:ferengi_bar}, where we show results of measuring $\zeta$ for $p_{\rm bar}$ in Task~03.
-For this reason we only offer debiased vote fractions for Task~01 (smooth/features/artifact).
+This requirement is often \emph{not} met for questions beyond Task~01; on average 60.0\% of the galaxies do not have sufficient data to measure a correction, as compared to 2.0\% acheived for Task~01 (see Table~\ref{tbl:ferengi_corrections}).
+Of the remaining FERENGI galaxies which did meet this requirement, polynomials were fit to the data in each redshift-surface brightness bin, as was done for Task~01 (described above).
+The goodness-of-fit was evaluated in each bin, for each Task, using the value of the sum of the square residuals (SSR).
+The mean SSR for all Tasks was $\mu_{\rm SSR}$ = 0.46 $\pm$ 0.36, which was not considered sufficiently low in any Task for the fits to accurately model the data.
+An example of the debiasing technique applied to $p_{\rm bar}$ is shown in Section \ref{sec:ferengi_bar}; visual inspection of Figure~\ref{fig:p_vs_p_bar} confirms the available data in each bin is scattered to a degree at which no correlation may be confidentely obtained.
+For these reasons, debiased vote fractions are only offered for Task~01 (smooth/features).
 

### 2016-04-30 writeup/gz_hubble_data.tex

--- 2016-04-29 writeup/gz_hubble_data.tex
@@
 
-%% Mark off the abstract in the ``abstract'' environment. 
 \begin{abstract}
@@
 The GZH morphological data includes measurements of both bulge- and disk-dominated galaxies, details on spiral disk structure that relate to the Hubble type, and numerous measurements of clump identification and geometry.
-We also describe and employ a novel method for calibrating morphological bias by using artificially-redshifted galaxy images as a baseline.
+This paper also describes and employs a novel method for calibrating morphological bias by using artificially-redshifted galaxy images as a baseline.
 This paper presents both the raw and calibrated morphological vote fractions for $150,771$ galaxies, constituting a large data set suitable for large-scale studies of galaxy evolution.
@@
 
-%% Keywords should appear after the \end{abstract} command. 
-%% See the online documentation for the full list of available subject
-%% keywords and the rules for their use.
-\keywords{galaxies --- catalogs --- surveys}
+\keywords{galaxies:structure --- galaxies:high redshift --- galaxies:evolution --- methods:data analysis --- catalogs}
 
@@
 For $M^\star$~galaxies in the local Universe, this typically manifests at the most basic level as the difference between bulge-dominated, virialized systems resembling ellipticals (early-types) and disk-dominated, rotationally-supported disks (late-types) frequently exhibiting spiral arms.
-This dichotomy has been used to explore much of the astrophysics encoding galaxy formation and evolution, and has been shown to be closely linked with other galactic properties such as stellar mass, halo mass, luminosity, black hole activity, size, and the relative ages of the stellar populations.
-
-The advent of larger telescopes in an increasing range of observing wavelengths has revealed that the distribution and properties of galaxy morphology have strongly evolved over the lifetime of the Universe.
+This dichotomy has been used to explore much of the astrophysics encoding galaxy formation and evolution, and has been shown to be closely linked with other galactic properties such as stellar mass, halo mass, bolometric luminosity, black hole activity, effective radius, and the relative ages of the stellar populations.
+
+The advent of larger telescopes in an increasing range of observable wavelengths has revealed that the distribution and properties of galaxy morphology have strongly evolved over the lifetime of the Universe.
 At redshift $z\simeq1$ (roughly 6~Gyr after the Big Bang), many galaxies are still in the process of assembling the baryonic mass required to reproduce the structures seen in the present day.
@@
 The process can also be slowed or even reversed via feedback from stellar winds, supernovae, and active black holes.
-Each of these processes affects on the galaxy morphology, and so an accurate measurement of the demographics as a function of redshift provides an extremely powerful observational constraint on the physics taking place \citep[for a recent review see][]{con14}.
+Each of these processes affects on the galaxy morphology, and so an accurate measurement of the demographics as a function of redshift provides an extremely powerful observational constraint on the physics involved \citep[for a recent review see][]{con14}.
 
@@
 The structure of individual galaxies is affected by the merger history \citep{too72,hop10}, local environment \citep[such as the morphology-density relation;][]{dre80}, initial dark halo mass, and many other factors.
-Morphologies of individial simulated high-mass galaxies at $z\sim2-3$ commonly show kpc-scale ``clumpy'' structures and few galaxies that are either smooth or well-ordered spirals; asymmetric profiles with strong density constrasts dominate down to at least $z\gtrsim$ \citep{gen14}.
+Morphologies of individial simulated high-mass galaxies at $z\sim2-3$ commonly show kpc-scale ``clumpy'' structures and few galaxies that are either smooth or well-ordered spirals; asymmetric profiles with strong density constrasts dominate populations in the early Universe until at least $z\sim1$ \citep{gen14}.
 
@@
 
-We describe the sample selection and creation of the images used for GZH in Section~\ref{sec:data}.
+The sample selection and creation of the images used for GZH is described in Section~\ref{sec:data}.
 Section~\ref{sec:interface} describes the GZH interface and the collection of classifications.
@@
 
-The GZH project contains images drawn from a number of different dedicated surveys and sample selection criteria, which we describe below.
-The majority of the images (as implied by the project name) are taken directly from \hst{} Legacy Surveys.
+\subsection{Hubble Legacy Surveys}\label{ssec:legacy_surveys}
+
+The GZH project contains images drawn from a number of different dedicated surveys and sample selection criteria.
+The majority of the data (as implied by the project name) are taken directly from \hst{} Legacy Surveys, all of which primarily use imaging from the Advanced Camera for Surveys (ACS).
+A summary of the key parameters is given in Table~\ref{tbl:gzh_numbers}.
 
@@
 
-\subsection{Summary of Hubble Legacy Survey Imaging}\label{ssec:legacy_surveys}
-
 \begin{itemize}
-\item \hubble{} ACS imaging for the All-Wavelength Extended Groth Strip International Survey \citep[AEGIS;][]{dav07} covers a strip centered at $\alpha=14^\textrm{h}17^\textrm{m}, \delta=+52^\circ30^\prime$.
-The strip was originally selected due to low extinction and Galactic/zodiacal emission, making it a prime target for multi-wavelength observations by space-based observatories.
+\item The All-Wavelength Extended Groth Strip International Survey \citep[AEGIS;][]{dav07} covers a strip centered at $\alpha=14^\textrm{h}17^\textrm{m}, \delta=+52^\circ30^\prime$.
+This area was selected for a deep survey due to a combination of low extinction and low Galactic/zodiacal emission.
 The ACS images covered 63 separate tiles over a total area of $\sim710$~arcmin$^2$.
-Images were in two bands, with exposure times of 2300~seconds in F606W (\Vband) and 2100~seconds in F814W (\Iband).
+The two ACS bands for AEGIS had exposure times of 2300~seconds in F606W (\Vband) and 2100~seconds in F814W (\Iband).
 The final mosaic images are dithered to a resolution of 0.03~\arcsec/pixel.
@@
 
-\item The Great Observatories Origins Deep Survey \citep[GOODS;][]{gia04} covers two well-studied fields in the northern and southern hemispheres: the Hubble Deep Field-North ($\alpha=12^\textrm{h}36^\textrm{m}, \delta=+62^\circ14^\prime$) and the Chandra Deep Field-South ($\alpha=03^\textrm{h}32^\textrm{m}, \delta=-27^\circ48^\prime$).
-Data including Hubble ACS images are referred to as GOODS-N and GOODS-S, respectively.
-ACS imaged the GOODS fields in 4 filters -- F435W (\Bband), \Vband, F775W (\iband), and F850LP (\zband).
+\item The Great Observatories Origins Deep Survey \citep[GOODS;][]{gia04} covers two separate fields in the northern and southern hemispheres: the Hubble Deep Field-North ($\alpha=12^\textrm{h}36^\textrm{m}, \delta=+62^\circ14^\prime$) and the Chandra Deep Field-South ($\alpha=03^\textrm{h}32^\textrm{m}, \delta=-27^\circ48^\prime$).
+The \hst{} ACS imaging data from the two fields are referred to as GOODS-N and GOODS-S, respectively.
+ACS imaging in GOODS fields used 4 filters -- F435W (\Bband), \Vband, F775W (\iband), and F850LP (\zband).
 The mean exposure times for each epoch vary by band, from 1050--2100~seconds.
 The \Bband{} images were completed in a single epoch at the beginning of the survey, but the \Vband, \iband, and \zband{} images were taken in five separate epochs separated by 40--50~days each.
-The ACS images are dithered to a pixel scale of 0.03~\arcsec/pixel and covers a total area of $\sim320$~arcmin$^2$ (160~arcmin$^2$ per field).
+Images are dithered to a pixel scale of 0.03~\arcsec/pixel and cover a total area of $\sim320$~arcmin$^2$ (160~arcmin$^2$ per north/south field).
 The $5\sigma$ limiting magnitudes for extended sources are 25.7 for \Vband{} and 25.0 for \iband.
 
-\item The Cosmic Evolution Survey \citep[COSMOS;][]{sco07} covers an area of $\sim1.8$~deg$^2$ centered at $\alpha=10^\textrm{h}00^\textrm{m}28^\textrm{s}, \delta=+02^\circ12^\prime21^{\prime\prime}$.
-Its location near the celestial equator was designed to enable coverage by ground-based telescopes in both the Northern and Southern Hemispheres, as well as the space-based observatories.
-The \hst{} ACS data from COSMOS consists of 1 orbit with 2028~seconds per pointing in \Iband, consisting of 590 total pointings.
+\item The Cosmic Evolution Survey \citep[COSMOS;][]{sco07} covers an area of $\sim1.8$~deg$^2$ centered at $\alpha=10^\textrm{h}00^\textrm{m}, \delta=+02^\circ12^\prime$.
+Its location near the celestial equator was designed to enable coverage by ground-based telescopes in both the Northern and Southern Hemispheres, in addition to space-based observatories.
+The ACS data for COSMOS consists of 1 orbit per pointing with an exposure time of 2028~seconds in \Iband; 590 total pointings are used to cover the entire field.
 The image resolution is dithered to 0.05~\arcsec/pixel.
-The 50\% completeness magnitude for a galaxy with a half-light radius of $0^{\prime\prime}.50$ in \Iband{} is 24.7 mag.
-
-\item The Galaxy Evolution from Morphologies and SEDS \citep[GEMS;][]{rix04,cal08} survey is also centered on the Chandra Deep Field-South.
-The GEMS data covers $\sim800$~arcmin$^2$, and surrounds the area covered by GOODS-S.
+The 50\% completeness magnitude for a galaxy with a half-light radius of $0.50^{\prime\prime}$ in \Iband{} is 24.7 mag.
+
+\item The Galaxy Evolution from Morphologies and SEDs \citep[GEMS;][]{rix04,cal08} survey is also centered on the Chandra Deep Field-South.
+The GEMS data covers $\sim800$~arcmin$^2$, completely surrounding the area covered by GOODS-S.
 Images from ACS in GEMS have 1 orbit per pointing for a total of 63~pointings.
@@
 
-For images from the ACS-GC \citet{gri12}, galaxies are identified using a combination of \sextractor{} \citep{ber96} and the galaxy-profile fitting framework \textsc{Galapagos} \citep{bar12}.
-We selected all galaxies with $m < 23.5$, where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS, GEMS + GOODS-S, and GOODS-N surveys, respectively.
+In the Advanced Camera for Surveys General Catalog \citep[ACS-GC;][]{gri12}, individual galaxies are identified using a combination of \sextractor{} \citep{ber96} and the galaxy-profile fitting framework \galapagos{} \citep{bar12}.
+GZH includes all galaxies with $m < 23.5$, where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS, GEMS + GOODS-S, and GOODS-N surveys, respectively.
 This yielded a total of 113,166~images (Table~\ref{tbl:gzh_numbers}).
@@
 
-For galaxies in the ACS General Catalogue \citep[AEGIS, COSMOS, GEMS, 2-epoch GOODS;][]{gri12}, the color composites are made using a fixed pixel intensity scaling with weights of $[2.4\times10^{-4},3\times10^{-4},3\times10^{-4}]$ in the red, green, and blue channels respectively.
-We also apply a nonlinear mapping to each pixel to emphasize the contrast in faint features \citep{lup04}, taking the form of:
+For galaxies in the ACS-GC, color composites are made using a fixed pixel intensity scaling with weights of $[2.4\times10^{-4},3\times10^{-4},3\times10^{-4}]$ in the red, green, and blue channels respectively.
+A nonlinear mapping is applied to each pixel to emphasize the contrast in faint features \citep{lup04}, taking the form of:
 
@@
 
-\noindent We adopt a value of $b=3$ for the \hst{} images in \citet{gri12}.
-
-Since the majority of the data in Legacy surveys described in \S\ref{ssec:legacy_surveys} had images in only 1 or 2~bands available when GZH was launched, making standard 3-channel RGB images in the same method used for the SDSS images in the original Galaxy Zoo was not possible.
+\noindent The GZH images from \citet{gri12} use a value of $b=3$.
+
+Since the majority of the data in Legacy surveys described in \S\ref{ssec:legacy_surveys} had images in only 1 or 2~bands available when the GZH project was first launched, making standard 3-channel RGB images in the same method used for the SDSS images in the original Galaxy Zoo was not possible.
 For surveys with images in two bands (AEGIS, GEMS, and the two-epoch GOODS-N and GOODS-S), the lower-wavelength band is mapped to the blue channel, the higher-wavelength band to the red channel, and the green channel created by taking the geometric mean of the two.
@@
 
-By the time that the 5-epoch sets of GOODS data were put into GZH, coverage in four separate \hst{} bands had become publicly available.
-The deeper GOODS images were created using the arithmetic mean of \Bband{} and \Vband in the blue channel, \Iband{} in the red channel, and \zband in the green channel.
+By the time that the 5-epoch sets of GOODS data were put into GZH (in March 2015), coverage in four separate \hst{} bands were publicly available.
+The deeper GOODS images were created using the arithmetic mean of \Bband{} and \Vband{} in the blue channel, \Iband{} in the red channel, and \zband{} in the green channel.
 These images also had the speckled noise pixels decolorized.
@@
 For these galaxies, we created ``pseudocolor'' images by using the ACS \Iband{} data as the illumination map and ground-based imaging from the \subaru{} telescope in $B_J$, $r^+$, and $i^+$ filters to provide the color gradients \citep[see][for further details]{gri12}.
-This means that the images have the angular resolution of \hst{} ($\sim0.05$~\arcsec/pixel) for the overall intensity, but the color gradients are at ground-based resolution, with seeing between 0\arcsec.95 and 1\arcsec.05 \citep{tan07}.
+This means that the images have the angular resolution of \hst{} ($\sim0.05$~\arcsec/pixel) for the overall intensity, but the color gradients are at ground-based resolution, with seeing between 0.95\arcsec and 1.05\arcsec \citep{tan07}.
 
 The Stripe~82 single-epoch images were taken directly from the color composites on the DR7 SDSS Skyserver, which combines $g^{\prime}$, $r^{\prime}$, and $i^{\prime}$ exposures into the RGB channels.
-The coadded Stripe~82 images were assembled from runs 106 and 206 in DR7 and generated as JPGs using the method of \citet{lup04}.
-
-To address a number of images in which the sky noise was highly colored (which might have been a distraction to users), we apply a soft-edged object mask to the image that preserves the color balance for galaxies, but desaturates the speckled noise against regions of blank sky.
+The coadded Stripe~82 images were assembled from runs 106 and 206 in DR7 and made into color composites using the method of \citet{lup04}.
+
+To deal with images in which the sky noise was highly colored (which might have been a distraction to visual classification), a soft-edged object mask is applied to the image that preserves the color balance for galaxies, but desaturates the speckled noise against regions of blank sky.
 This technique was applied only to the coadded Stripe~82 and the COSMOS images.
 
-\subsection{Artificial AGN}
-
-We also created a set of images designed to measure the effect of AGN on morphological classifications.
-Since galactic nuclei can have bright, unresolved optical emission, this has the potential to mimic the effect of a strong bulge.
+\subsection{Images with simulated nuclear point sources}
+
+GZH also includes a set of images designed to measure the effect of active galactic nuclei (AGN) on morphological classifications.
+Since galactic nuclei can have bright, unresolved optical emission, this has the potential to mimic or distort the identification of a bulge component.
 The presence of an AGN is simulated by modeling the PSF for \hst{} and then inserting a bright source near the center of a real galaxy.
 For each image, the simulated AGN is assigned one of three colors -- either blue, red, or flat (white) as seen in the color images -- and a range of brightnesses such that $L_\mathrm{ratio} \equiv L_\mathrm{galaxy}/L_\mathrm{AGN}$ is in $(0.2,1.0,2.0,5.0,10.0,50.0)$.
-Combining these parameters generates 15~images with different simulated AGN for each chosen host.
+Combining these parameters generates 15~images with different simulated AGN for each host.
 
@@
 Photometric data for the bulk of the GZH sample is largely drawn from the tables provided in \citet{gri12}.
-This includes photometric parameters from both \sextractor{} and \galfit, such as the fluxes, magnitudes, radii, ellipticities, position angles, and positions.
+This includes photometric parameters such as the fluxes, magnitudes, radii, ellipticities, position angles, and positions drawn from both \sextractor{} and \galfit.
 \galfit{} also provides the parametric S\'{e}rsic index and effective half-light radius for the best-fit model.
@@
 
-Redshifts for the GZH catalog are compiled from a variety of sources to include in the GZH catalog.
-For each galaxy, the redshift selected is in the $\tt Z\_Best$ column of the data (see Table~\ref{tbl:catalog_hst}), its type (spectroscopic: $\tt SPEC\_Z$, photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column $\tt Z\_BEST\_TYPE$, and the source catalog ($\tt ACSGC$ \citep{gri12}, $\tt 3DHST$ \citep{mom15}, $\tt MUSYC$ \citep{car10}, or $\tt UltraVISTA$ \citep{ilb13}) of the redshift is in column $\tt Z\_BEST\_SOURCE$.
-
-For galaxies which have redshifts from multiple sources, we use the following algorithm to select the $\tt Z\_BEST$ redshift.
-We first prioritize spectroscopic redshifts; these are provided in the ACS-GC, 3DHST, and MUSYC catalogs.
-If a high quality spec-z exists in the ACS-GC.
-we use that, else 3DHST, else MUSYC.
-More 98\% of the matched spec-$z$'s are consistent at $\Delta z<0.001$; therefore, the priority order of selection makes no negligible difference in this sample.
-If no spectroscipic redshifts are available, we compare the 1-$\sigma$ errors of the photometric (ACS-GC, 3DHST, MUSYC, UltraVISTA) and grism (UltraVISTA) redshifts, and use the redshift with the smallest error.
+Redshifts for the GZH catalog are compiled from a variety of sources.
+For each galaxy, the primary redshift used for debiasing calculations (Section~\ref{sec:debiasing}) is in the $\tt Z\_Best$ column of Table~\ref{tbl:catalog_hst}.
+The redshift type (spectroscopic: $\tt SPEC\_Z$, photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column $\tt Z\_BEST\_TYPE$, and the source catalog of the redshift is included as $\tt Z\_BEST\_SOURCE$.
+
+For galaxies which have published redshifts from multiple sources, the following algorithm is used to select the $\tt Z\_BEST$ quantity.
+This first priority is spectroscopic redshifts; these are provided in the ACS-GC \citep{gri12}, 3DHST \citep{mom15}, and MUSYC \citep{car10} catalogs.
+A high quality spectroscopic redshift in the ACS-GC is the primary option; if none is available, then $\tt Z\_BEST$ uses the spectroscopic redshifts in 3DHST, and then MUSYC.
+For galaxies with multiple spectroscopic redshifts, more than 98\% are consistent at $\Delta z<0.001$; therefore, the priority order of selection makes no negligible difference for the sample.
+If no spectroscopic redshifts are available, the 1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST, MUSYC, UltraVISTA;][]{ilb13} and UltraVISTA grism data are used to select the redshift with the smallest error.
 Table~\ref{tbl:redshifts} shows the results of this selection.
@@
 the reduction in physical resolution, surface brightness dimming, etc).
-For both previous releases of GZ morphologies, we provided a correction for redshift-dependent bias based on matching the classification fractions at the highest redshfts with those at the lowest redshift.
+For both previous releases of GZ morphologies, a correction for redshift-dependent bias was applied based on matching the classification fractions at the highest redshfts with those at the lowest redshift.
 See \citet{bam09} and \citet{wil13} for the details.
 
-In the GZH samples, the redshift range is large enough that we expect to measure cosmological evolution of the types and morphologies of galaxies in the sample.
+In the GZH samples, the redshift range is large enough that cosmological evolution of the types and morphologies of galaxies is expected for galaxies in the sample.
 As a result, the previous methods of correcting for redshift dependent bias will not work.
@@
 
-In order to test and correct for the effects of redshift, we generated a set of calibration images.
+In order to test and correct for the effects of redshift, GZH includes a set of calibration images.
 These images consist of the same galaxy as it would appear over a variety of redshifts.
@@
 
-We selected 288 unique galaxies from SDSS imaging to run through the \ferengi{} code.
+The GZH classifications include 288 unique galaxies originally generated from SDSS imaging and processed with the \ferengi{} code.
 The selection spanned a variety of galaxy morphologies (as selected by GZ2 classifications) and $r^\prime$-band surface brightnesses, and also spanned the redshift range of SDSS targets (in $N_z = 4$ bins) in order to be optimized for different target minimum redshifts in \hst{} imaging.
@@
 The effect on the redshifted images is simply an empirical addition to the magnitude of a galaxy of the form $M' = e\times z + M$, where $M'$ is the corrected magnitude, and $e$ is the evolutionary correction in magnitudes (i.e., $e=-1$ essentially brightens the galaxy by 1~magnitude by $z=1$).
-We ran \ferengi{} for values of $e$ starting from $e=0$ and decreasing to $e=-3.5$ in increments of $\Delta e = 0.5$.
+\ferengi{} was run on the images for values of $e$ starting from $e=0$ and decreasing to $e=-3.5$ in increments of $\Delta e = 0.5$.
 Figure~\ref{fig:exampleFERENGI} shows several examples of the effects of ``losing`` spiral/disc features with increasing redshift for two galaxies with $e=0$.
@@
 There are likely other parameters that affect user accuracy, such as the proximity of close companions \citep[``distraction bias''; see][]{joh15} or bias as a function of the individual user.
-The combination of all such parameters forms a high-dimensional space, and we have insufficient data to measure their individual effects.
-Instead, we use just two parameters that are intended to capture the bulk of the change in bias (based on GZ1/GZ2): a galaxy's $r^\prime$-band surface brightness ($\mu_r$; intrinsic) and redshift ($z$; extrinsic).
+The combination of all such parameters forms a high-dimensional space, and there are insufficient data to measure their individual effects.
+Instead, this method uses only two parameters intended to capture the bulk of the change in bias (based on GZ1/GZ2): the $r^\prime$-band surface brightness ($\mu_r$; intrinsic) and redshift ($z$; extrinsic).
 
 The change in bias as a function of $\mu_r$ and $z$ is measured using the \ferengi{} images over all the evolutionary correction factors.
-We assume that the ``true'' (ie, debiased) vote fraction $f_{\mu,z}$ for a galaxy can be expressed as:
+It is assumed that the ``true'' (ie, debiased) vote fraction $f_{\mu,z}$ for a galaxy can be expressed as:
 
@@
 
-We use the values of $\zeta$ for \emph{all} sets of artifically redshifted galaxies to fit the overall distribution as a function of surface brightness, since we expect the correction being applied to vary as a function of the intrinsic galaxy properties.
-We restrict the galaxies that can be used to measure the calibration to those with data at the pivot redshift of $z=0.3$, non-zero $f_\textrm{features}$ at $z=0.3$, and with a reasonable fit to the exponential model ($\Delta \chi^2 > 3.0$).
+GZH uses the values of $\zeta$ for \emph{all} sets of artifically redshifted galaxies to fit the overall distribution as a function of surface brightness, since the correction being applied is expected to vary as a function of the intrinsic galaxy properties.
+The galaxies that can be used to measure the calibration are restricted to those with data at the pivot redshift of $z=0.3$, non-zero $f_\textrm{features}$ at $z=0.3$, and with a reasonable fit to the exponential model ($\Delta \chi^2 > 3.0$).
 
@@
 
-We fit the data in Figure~\ref{fig:zeta_mu} with a linear function such that:
+The data in Figure~\ref{fig:zeta_mu} are fit with a linear function such that:
 
@@
 The best-fit parameters to the linear fit (from least-squares optimization) are $\zeta_0=0.1$, $\zeta_1=1.4$.
-To make the final debiased correction, we modify the simple exponential form of Equation~\ref{eqn:fzeta} to bound the debiased vote fractions between $f$ and 1:
+To make the final debiased correction, the simple exponential form of Equation~\ref{eqn:fzeta} is modified to bound the debiased vote fractions between $f$ and 1:
 
@@
 
-In Figure~\ref{fig:p_vs_p} we examine the change in \pfeatures{} for the \ferengi{} galaxies relative to their lowest simulated redshift.
+Figure~\ref{fig:p_vs_p} shows the change in \pfeatures{} for the \ferengi{} galaxies relative to their lowest simulated redshift.
 In this analysis, only galaxies whose lowest simulated redshift image was $z_\mathrm{sim}=0.3$ were used (see Table \ref{tbl:ferengivalues}), and only those which had detectable surface brightness measurements in \sextractor; this includes 3,950 of the total 6,466 images.
-For each simulated redshift value $z$, and at a fixed surface brightness $\mu$, we plot \pfeaturesz, the value measured at that simulated redshift, vs \pfeaturesrest, the value measured for the same galaxy imaged at $z=0.3$.
-
-Our objective is to use these data to predict, for a galaxy with a measured \pfeaturesz{} value, what its \pfeatures{} value \emph{would have been} if it had been viewed at $z=0.3$.
+For each simulated redshift value $z$, and at a fixed surface brightness $\mu$, \pfeaturesz, the value measured at that simulated redshift, is plotted against \pfeaturesrest, the value measured for the same galaxy imaged at $z=0.3$.
+
+The objective is to use these data to predict, for a galaxy with a measured \pfeaturesz{} value, what its \pfeatures{} value \emph{would have been} if it had been viewed at $z=0.3$.
 This predicted value is defined as the debiased vote fraction \pfeaturesdebiased, and is calculated by applying a correction to the measured value of \pfeatures, determined by the $\zeta$ function described in the previous section.
@@
 
-Our criteria for determining whether a region of this space is single-valued, and therefore correctable, is as follows: In each surface brightness and redshift bin, we model the relationship between \pfeaturesz{} and \pfeaturesrest{} by fitting the data with a polynomial of degrees 3, 2, and 1, and use the best fit out of the three.
+The criteria for determining whether a region of this space is single-valued, and therefore correctable, is as follows: In each surface brightness and redshift bin, the relationship between \pfeaturesz{} and \pfeaturesrest{} is modeled by fitting the data with a polynomial of degrees 3, 2, and 1, and use the best fit out of the three.
 These fits are shown as the dashed black lines in Figure~\ref{fig:6a}.
-Any flat regions of the polynomial fits are areas in which there is not a clear single-valued relationship between \pfeaturesz{} and \pfeaturesrest; we quantify this by setting a minimum slope cut of 0.4.
+Any flat regions of the polynomial fits are areas in which there is not a clear single-valued relationship between \pfeaturesz{} and \pfeaturesrest; this is quantified by setting a minimum slope cut of 0.4.
 Any data in which the polynomial fit has a slope less than this value is considered \emph{not} one-to-one, and therefore \pfeaturesz{} cannot be boosted to its \pfeaturesrest{} value.
-We refer to galaxies in this region as the \emph{lower limit} sample.
+Galaxies in this region are referred to as the \emph{lower limit} sample.
 These regions are highlighted in blue in Figure~\ref{fig:6a}.
-Uncolored (white) regions of the plot have sufficiently high slopes for us to consider the relationship to be single-valued; galaxies in these regions are considered ``correctable'', and only these are used in measuring the parameters for the $\zeta$ function (Section~\ref{ssec:zeta}).
-Only surface brightness/redshift bins with at least 5 galaxies were considered; regions with fewer than 5 galaxies we consider to have ``not enough information'' to determine the \pfeaturesz{} and \pfeaturesrest{} relationship, colored gray in Figure~\ref{fig:6a}.
+Uncolored (white) regions of the plot have sufficiently high slopes to consider the relationship as single-valued; galaxies in these regions are considered ``correctable'', and only these are used in measuring the parameters for the $\zeta$ function (Section~\ref{ssec:zeta}).
+Only surface brightness/redshift bins with at least 5 galaxies were considered; regions with fewer than 5 galaxies are considered to have ``not enough information'' to determine the \pfeaturesz{} and \pfeaturesrest{} relationship, colored gray in Figure~\ref{fig:6a}.
 
 The unshaded regions in Figure~\ref{fig:6a} define discrete ranges of redshift, surface brightness, and \pfeatures{} a galaxy must have in order for the $\zeta$ approach to be confidentely applied to a galaxy in the GZH sample.
-While the appropriate correctable regions were defined discretely, we assume the true correctable region is a smooth function of $z$, $\mu$, and \pfeatures{}.
-To define this smooth space, we generate a convex hull that encloses the correctable and lower-limit \ferengi{} galaxies in $z$-$\mu$-\pfeatures{} space.
+While the appropriate correctable regions were defined discretely, the true correctable region is assumed to be a smooth function of $z$, $\mu$, and \pfeatures{}.
+To define this smooth space, a convex hull is generated that encloses the correctable and lower-limit \ferengi{} galaxies in $z$-$\mu$-\pfeatures{} space.
 The boundaries are then adjusted until the contamination from both groups is minimized.
-We use the resulting hulls to define the correctable and lower-limit regions for categorizing the \hst{} galaxies.
+The resulting hulls define the correctable and lower-limit regions for categorizing the \hst{} galaxies.
 The results of this method and final categorization of the \hst{} sample is displayed in Table~\ref{tbl:hubble_debiasable}.
@@
 
-For the ``lower-limit'' galaxies for which we cannot confidently assign a single debiased \pfeatures{} value, we instead determine a likely \emph{range} of debiased values, using a method visualized in Figure~\ref{fig:6c}.
-Here we again use the \ferengi{} simulated data to analyze the range of intrinsic \pfeaturesrest{} values for any given observed \pfeatures{} value, again as a function of surface brightness and redshift.
-In each $z$,$\mu$ bin, we examine the spread of intrinsic values of \pfeaturesrest{} for 4 ranges of observed \pfeatures.
-We quantify the range of intrinsic values as the inner 80\% of the data; this range is represented by the orange bars in Figure~\ref{fig:6c}.
-For any galaxy which can't be directly debiased by the $\zeta$ method, then, we use these ranges to denote the upper and lower limits on what we expect \pfeaturesrest{} to be for any observed value of \pfeatures.
+For the ``lower-limit'' galaxies for which a single debiased \pfeatures{} value cannot be confidently assigned, the \emph{range} of debiased values is estimated using a method visualized in Figure~\ref{fig:6c}.
+This uses the \ferengi{} simulated data to analyze the range of intrinsic \pfeaturesrest{} values for any given observed \pfeatures{} value, again as a function of surface brightness and redshift.
+Each $z$,$\mu$ bin, shows the spread of intrinsic values of \pfeaturesrest{} for four ranges of observed \pfeatures.
+The range of intrinsic values is defined as the inner 80\% of the data, represented by the orange bars in Figure~\ref{fig:6c}.
+For any galaxy which cannot be directly debiased by the $\zeta$ method, these ranges are used to denote the upper and lower limits on the expected values \pfeaturesrest{} as a function of the observed \pfeatures.
 
@@
 
-In the FERENGI data, these numbers severely limit the amount of information we can extract for the higher-tier questions.
+In the FERENGI data, these numbers severely limit the amount of information that can be extracted for the higher-tier questions.
 The debiasing technique used (Section~\ref{ssec:zeta}) require that at least 10~users answer each question for a galaxy image at $z=0.3$ \emph{and} its image at higher redshift.
@@
 Of the remaining FERENGI galaxies which did meet this requirement, the data available in each redshift-surface brightness bin were not tightly correlated between $p_{task,z=0.3}$ and $p_{task,z}$, and relationships between the two could not be fit with high confidence.
-We use these galaxies to compute $\zeta$ for each Task, and find the p-values for the resulting functions between $placeholder < p < placeholder$, which we consider insufficient for deriving a correction.
-We show an example of this in Section \ref{sec:ferengi_bar}, where we show results of measuring $\zeta$ for $p_{\rm bar}$ in Task~03.
-For this reason we only offer debiased vote fractions for Task~01 (smooth/features/artifact).
+These galaxies are used to compute $\zeta$ for each Task, and find the p-values for the resulting functions between $placeholder < p < placeholder$, which are insufficient for deriving a correction.
+An example of this is given in Section \ref{sec:ferengi_bar}, based on attempting to compute $\zeta$ for $p_{\rm bar}$ in Task~03.
+For this reason, GZH only provides debiased vote fractions for Task~01 (smooth/features/artifact).
 
@@
 The full table can be accessed at \url{http://data.galaxyzoo.org}.
-We also include a secondary metadata table, which contains data from a variety of sources explained in Section \ref{sec:data}.
+This also includes a secondary metadata table, which contains data from a variety of sources explained in Section \ref{sec:data}.
 
@@
 Two otherwise morphologically identical galaxies which differ significantly in redshift, brightness, or size may result in very different vote fractions for any given question, given that many features of a galaxy are difficult to discern in less-resolved images (bars, spiral arms, disk structure, etc).
-For this reason, it is necessary to take caution utilizing vote fractions as cut-offs to determine morphological structure; we offer guidelines for careful classification in Section~\ref{sec:cookbook}.
-
-We corrected for the biases described for the first question of the GZH decision tree, which asks ``Is the galaxy smooth and round, with no sign of a disk?'' The method is described in Section~\ref{sec:debiasing}.
-For this question, we provide the additional parameters $\tt debiased$, $\tt lower~limit$, $\tt upper~limit$, and $\tt best$ vote fractions.
+For this reason, it is necessary to take caution utilizing vote fractions as cut-offs to determine morphological structure; guidelines for careful classification are given in Section~\ref{sec:cookbook}.
+
+The GZH catalog is corrected for classification bias in the first question of the GZH decision tree, which asks ``Is the galaxy smooth and round, with no sign of a disk?'' The method is described in Section~\ref{sec:debiasing}.
+For this question, the catalog provides the additional parameters $\tt debiased$, $\tt lower~limit$, $\tt upper~limit$, and $\tt best$ vote fractions.
 The $\tt best$ fraction for $p_{features}$is chosen based on the categorization of the galaxy: if it is ``correctable'', $\tt best = debiased$, if a lower limit, $\tt best = lower~limit$, and if neither, $\tt best = weighted$.
@@
 In some rare cases, representing  $<1\%$ of the sample, this requirement resulted in negative vote fractions for $\rm p_{smooth}$; these were cases in which the $\rm p_{features}$ vote fraction was boosted to a high value relative to the $\rm p_{artifact}$ vote fraction.
-In these cases, we enforce the restriction that the vote fractions must sum to 1 by raising $\rm p_{smooth}$ to a vote fraction of 0.0 and decreasing $\rm p_{features}$ accordingly.
-This correction was typically very small, with a median decrease/increase of $\rm p_{features}/p_{smooth}$ of $\Delta p = 0.04$.
-
-We split the data products for GZH by the type of image being classified.
+In these cases, the constraint that the vote fractions must sum to 1 is met by raising $\rm p_{smooth}$ to a vote fraction of 0.0 and decreasing $\rm p_{features}$ accordingly.
+This correction is typically small, with a median decrease/increase of $\rm p_{features}/p_{smooth}$ of $\Delta p = 0.04$.
+
+Data products for GZH are split by the type of image being classified.
 Table~\ref{tbl:catalog_hst} contains the classifications for the \hst{} images from the AEGIS, COSMOS, and GEMS surveys, as well as 5-epoch deep imaging from the GOODS-N and GOODS-S surveys.
@@
 The intended purpose of the GZH catalog is to provide a simple, yet flexible, means of identifying samples of galaxies with a desired morphological type.
-Here we provide instructions for creating such samples using the vote fractions corresponding to the tasks shown in Figure~\ref{fig:decisiontree}.
+This section provides instructions for creating such samples using the vote fractions corresponding to the tasks shown in Figure~\ref{fig:decisiontree}.
 We stress that the selection process will vary based on the particular science case.
@@
 The flexibility of this catalog allows the user to set their own selection criteria for vote fraction thresholds to create a morphologically-pure sample.
-In Table~\ref{tbl:thresholds} we offer baseline cuts for selecting galaxies of a variety of morphologies.
-We detemined these thresholds by a visual inspection of subsamples.
-For each Task, we first required that at least 20 users voted on the given question.
-We then applied a cut on the vote fraction for the previous task and analyzed a subsample of 50 galaxies meeting these criteria, as well as a control sample of galaxies which had 20 users vote on the task, but did not meet the threshold cut set for the previous task.
+Table~\ref{tbl:thresholds} provides baseline cuts for selecting galaxies of a variety of morphologies.
+These thresholds are determined by a visual inspection of subsamples.
+For each Task, at least 20 users are required to have voted on the given question along with a cut on the vote fraction is applied to the previous task.
+We visually analyzed subsamples of 50~galaxies meeting both criteria, as well as a control sample of galaxies which had 20~users vote on the task, but did not meet the threshold cut set for the previous task.
 The threshold cut was adjusted and new subsamples were inspected until both the original and control samples achieved $>80\%$ purity.
@@
 Further, of these subjects, none were found to exhibit disk structure, although the clumps within were arranged in a spiral pattern.
-We therefore do not find this pathway necessary in examining responses to Tasks 03, 04, and 05.
-
-In this section we have described how to use the previous Task thresholds in Table~\ref{tbl:thresholds} to select well-sampled galaxies which may or may not contain the feature associated with a unique Task.
-We will now offer two examples of how to use the vote fractions for the final Task to obtain a sample of galaxies with a certain morpholgical type, by creating a sample of bars and samples of clumpy galaxies grouped by clump mulitiplicity.
+
+This section described how to use the previous Task thresholds in Table~\ref{tbl:thresholds} to select well-sampled galaxies which may or may not contain the feature associated with a unique Task.
+The following two examples show to use the vote fractions for a particular Task to obtain a sample of galaxies with a certain morpholgical type.
 
@@
 
-We created a sample of barred galaxies by applying cuts on the previous tasks as listed in Table~\ref{tbl:thresholds}.
+A sample of barred disk galaxies is created by applying cuts on the previous tasks as listed in Table~\ref{tbl:thresholds}.
 11,049 ``bar candidates'', galaxies for which asking the bar question is meaningful, were selected by applying the cuts $N_{bar} \ge 20$, $p_{\rm features}>0.23, p_{\rm clumpy,no} > 0.30,$ and $p_{edgeon,no}>0.25$.
@@
 
-We use the complete bar sample to estimate the redshift evolution of bar fraction and find a steady decrease of $f_{bar} \sim 0.32$ at $z=0.4$ to $f_{bar} \sim 0.24$ at $z=1.0$.
+The resulting bar sample can be used to estimate the redshift evolution of bar fraction and find a steady decrease of $f_{bar} \sim 0.32$ at $z=0.4$ to $f_{bar} \sim 0.24$ at $z=1.0$.
 The decrease in bar fraction agrees with \citet{mel14}, although they report a lower overall bar fraction going from $f_{bar}=0.22$ at $z=0.4$ to $f_{bar}=0.11$ at $z=1.0$.
-The difference in total bar fraction is expected, as our analysis used a looser cut on $p_{\rm bar}$, we did not apply a luminosity cut, and we use debiased values for $p_{\rm features}$ which increases the total amount of disks in the sample.
+The difference in total bar fraction is expected, as this analysis used a looser cut on $p_{\rm bar}$, there is no luminosity cut, and the use of debiased values for $p_{\rm features}$ increases the total amount of disks in the sample compared to \citet{mel14}.
 For a more thorough analysis of the bar fraction, a cut on $p_{\rm bar}$ that evolves with redshift may yield more accurate results, since there are no explicit debiased values of $p_{\rm bar}$ that would take redshift induced bias into account.
@@
 GZH added a ``clumpy'' path to the decision tree for the purpose of both identifying clumps and investigating their evolution with redshift.
-Here we provide an example of how to select galaxies with particular clump multiplicities, for investigations related to the transformation of clumps as galaxies continue to form.
 
 For galaxies identified as ``clumpy'' in GZH, the number of clumps can be determined using Task 16.
-We identify samples of galaxies having one, two, three, four, and more than four clumps.
-Using Table~\ref{tbl:thresholds}, we identify 8,444 clumpy galaxies using $p_{\rm features} > 0.23$ and $p_{\rm clumpy,yes}>0.80$ to ensure the vote fractions for Task 16 are well-sampled.
-We were able to identify with reasonable confidence the clump number of 1,112 of the clumpy galaxies; in the remainder, the unique clumps were less distinguishable from each other and the exact number of clumps could not be deduced without careful visual inspection.
-In the 1,112 which did have distinguishable clumps, we identified 61 one-clump galaxies using $p_{\rm 1~clump}>0.50$, 442 two-clump galaxies using $p_{\rm 2~clumps}>0.80$, 275 three-clump galaxies using $p_{\rm 3~clumps}>0.75$, 71 four-clump galaxies using $p_{\rm 4~clumps} > 0.70$, and 263 galaxies with more than four clumps using $p_{\rm >4~clumps}>0.70$.
+Table~\ref{tbl:thresholds} can be used to select 8,444 galaxies measured as ``clumpy'' using $p_{\rm features} > 0.23$ and $p_{\rm clumpy,yes}>0.80$ to ensure the vote fractions for Task 16 are well-sampled.
+The clump number can be reasonably identified for 1,112 of the clumpy galaxies; for the remainder, the unique clumps were less distinguishable from each other and the exact number of clumps could not be deduced without careful visual inspection.
+In the 1,112 which did have distinguishable clumps, there are 61 one-clump galaxies using $p_{\rm 1~clump}>0.50$, 442 two-clump galaxies using $p_{\rm 2~clumps}>0.80$, 275 three-clump galaxies using $p_{\rm 3~clumps}>0.75$, 71 four-clump galaxies using $p_{\rm 4~clumps} > 0.70$, and 263 galaxies with more than four clumps using $p_{\rm >4~clumps}>0.70$.
 Alternatively, these data may be used to create more general samples of clumpy galaxies with few clumps and many clumps.
-We define a sample of 989 ``few clumps'' galaxies using $(p_{\rm 1~clump} + p_{\rm 2~clumps}) > 0.5$ and 2,910 ``many clumps'' galaxies using $(p_{\rm 3~clumps}+p_{\rm 4~clumps}+p_{\rm >4~clumps})>0.5$.
+A sample of 989 ``few clumps'' galaxies can be made using $(p_{\rm 1~clump} + p_{\rm 2~clumps}) > 0.5$ and 2,910 ``many clumps'' galaxies using $(p_{\rm 3~clumps}+p_{\rm 4~clumps}+p_{\rm >4~clumps})>0.5$.
 
@@
 All of the Legacy surveys included in the GZH imaging have had morphological catalogs previously published; these catalogs have significant differences in the number of galaxies, size and magnitude limits, classification scheme, and the methods used for measuring morphology.
-We cross-match several of these catalogs to GZH and compare the results; this is not presented as an endorsement of any particular method, but as an exploration of the strengths and weaknesses of the GZ crowdsourced catalogs as compared to products made with machine learning, automatic fits, and expert visual classification.
+These catalogs have been cross-matched to GZH to compare the results; this is not presented as an endorsement of any particular method, but as an exploration of the strengths and weaknesses of the GZ crowdsourced catalogs as compared to products made with machine learning, automatic fits, and expert visual classification.
 
 The types and accuracies of morphological classification strongly depend on the sample and methods being used.
-In an attempt to make a consistent comparison between different techniques, we broadly group galaxies classified into three categories: bulge-dominated/elliptical/smooth, disk-dominated/spiral, and irregular/clumpy.
+In an attempt to make a consistent comparison between different techniques, galaxies are broadly grouped into three categories: bulge-dominated/elliptical/smooth, disk-dominated/spiral, and irregular/clumpy.
 These categories are compared to two parameters in GZH: \pbest, which is designed to identify smooth (elliptical) galaxies, and \podd, which is designed to identify deviations from well-formed spirals or S0s and which constitutes a ``catch-all'' for the variety of asymmetric morphologies that can constitute an irregular galaxy.
@@
 Morphologies for GEMS galaxies were measured by \citet{hau07}, who use single-component \sersic{} fits to the F850LP imaging.
-We use parameters from the \galfit{} code, which \citet{hau07} evaluated as more reliable than \gimtwod{} for GEMS due to the ability to fit multiple galaxies in crowded fields.
+This analysis uses parameters from the \galfit{} code, which \citet{hau07} evaluated as more reliable than \gimtwod{} for GEMS due to the ability to fit multiple galaxies in crowded fields.
 A 1\arcsec~positional match for the GEMS galaxies in Table~9 in \citet{hau07} to the GZH sample gives 8,846~galaxies in both \citet{hau07} and GZH.
 The main morphological parameter in the automated catalog is the \sersic{} index $n$ defining the radial surface brightness profile.
-We designate ``elliptical'' galaxies as those with $n>2.5$ and ``spirals''  with $n>2.5$.
+``Elliptical'' galaxies are selected by $n>2.5$ and ``spirals''  by $n>2.5$.
 There is no automatic measurement of irregular or clumpy structure in this catalog.
@@
 As the data shown in Figure~\ref{fig:comparisons} cover a wide range of redshifts and sizes, a volume-limited sample of galaxies (or at least binning by redshift) is likely a much more appropriate comparison.
-While we leave detailed analysis to a further paper, we note that there is no strong change in the proportion of galaxies when binning by redshift intervals of $\Delta z=0.2$ out to $z=1.0$.
+While detailed analysis is left to a further paper, we note that there is no strong change in the proportion of galaxies when binning by redshift intervals of $\Delta z=0.2$ out to $z=1.0$.
 
@@
 Galaxies were selected from a brightness-limited sample from multiple Legacy surveys using the Advanced Camera for Surveys on the Hubble Space Telescope, including AEGIS, GEMS, GOODS-N, GOODS-S, and COSMOS.
-We also include classifications for 51,861 Sloan Digital Sky Survey images in Stripe~82 at relatively low redshift; these serve both as a low-redshift anchor for cosmological studies and a potential comparison for the different epochs of classification between GZH and Galaxy Zoo 2 \citep{wil13}.
+The catalog also includes classifications for 51,861 Sloan Digital Sky Survey images in Stripe~82 at relatively low redshift; these serve both as a low-redshift anchor for cosmological studies and a potential comparison for the different epochs of classification between GZH and Galaxy Zoo 2 \citep{wil13}.
 
@@
 This can be the result either of genuinely small or dim galaxies, or a perceived effect from observing galaxies at further distances (higher redshift).
-To calibrate this \emph{without} potentially overcorrecting for the genuine morphological evolution of galaxies over cosmic time, we use SDSS images of low-redshift galaxies, process them to appear as if they were at higher redshift, and pass them through the GZH interface in an identical fashion.
+To calibrate this \emph{without} potentially overcorrecting for the genuine morphological evolution of galaxies over cosmic time, the GZH project uses SDSS images of low-redshift galaxies, processes them to appear as if they were at higher redshift, and classifies them through the GZH interface in an identical fashion.
 The resulting change in \pfeatures{} as a function of $z$,$\mu$ is applied as a multiplicative correction to the top-level vote fractions for $\sim50\%$ of the GZH galaxies.
@@
 Galaxies in GZH show significant changes in the disk/elliptical fraction as a function of redshift, along with an increasing number of galaxies dominated by smaller clumps and presumed to be in the process of building up their baryonic mass through a combination of hierarchical merging and in-situ star formation.
-While the majority of scientific interpretation is left to future papers, we confirm the decrease in observed bar fraction with increasing redshift \citep{mel14} and identify a new way for identifying clumpy galaxies as a function of clump multiplicity.
+While the majority of scientific interpretation is left to future work, this paper confirms the decrease in observed bar fraction with increasing redshift \citep{mel14} and identify a new way for identifying clumpy galaxies as a function of clump multiplicity.
 
@@
 The 11,157 full depth 5-epoch images are used in the main catalog; the classifications for the 7,464 shallow depth 2-epoch images are offered as a supplementary table.
-Here we briefly analyze the effect of image depth on the ability of the GZ users to identify features or disk structure in the images.
+This section analyzes the effect of image depth on the ability of the GZ users to identify features or disk structure in the images.
 

### 2016-05-01 python/gzh_gzc.py
Code for comparing GZH and GZC

@@ -1,0 +1,91 @@
+# Import any necessary packages
+
+from matplotlib import pyplot as plt
+from matplotlib.colors import LogNorm
+from astropy.io import fits
+import numpy as np
+
+import warnings
+
+warnings.filterwarnings('ignore', category=RuntimeWarning, append=True)
+
+data = fits.getdata('/Users/willettk/Dropbox/gzhubble/gzh_gzcandels.fits',1)
+
+pd = [
+      {'gzc_col':'t00_smooth_or_featured_a1_features_frac',
+       'gzh_col':'t01_smooth_or_features_a02_features_or_disk_fraction',
+       'label':'features (raw)'},
+      {'gzc_col':'t00_smooth_or_featured_a1_features_weighted_frac',
+       'gzh_col':'t01_smooth_or_features_a02_features_or_disk_weighted_fraction',
+       'label':'features (weighted)'},
+      {'gzc_col':'t00_smooth_or_featured_a1_features_weighted_frac',
+       'gzh_col':'t01_smooth_or_features_a02_features_or_disk_best_fraction',
+       'label':'features (best)'},
+      {'gzc_col':'t09_disk_edge_on_a0_yes_weighted_frac',
+       'gzh_col':'t02_edgeon_a01_yes_weighted_fraction',
+       'label':'edge-on',
+       'constraints':{'t02_edgeon_total_weight':20,'t12_clumpy_a02_no_weighted_fraction':0.3}},
+      {'gzc_col':'t12_spiral_pattern_a0_yes_weighted_frac',
+       'gzh_col':'t04_spiral_a01_spiral_weighted_fraction',
+       'label':'spiral',
+       'constraints':{'t04_spiral_total_weight':20,'t02_edgeon_a02_no_weighted_fraction':0.25}},
+      {'gzc_col':'t16_merging_tidal_debris_a0_merging_frac',
+       'gzh_col':'t08_odd_feature_a06_merger_weighted_fraction',
+       'label':'merger',
+       'constraints':{'t01_smooth_or_features_a03_star_or_artifact_weighted_fraction':0.10,'t06_odd_total_weight':20}},
+       ]
+
+
[…]

### 2016-05-02 writeup/gz_hubble_data.tex

@@
 
-In the FERENGI data, these numbers severely limit the amount of information that can be extracted for the higher-tier questions.
+In the FERENGI data, these numbers severely limit the amount of information we can extract for the higher-tier questions.
 The debiasing technique used (Section~\ref{ssec:zeta}) require that at least 10~users answer each question for a galaxy image at $z=0.3$ \emph{and} its image at higher redshift.
 This requirement is by default met by all galaxies when analyzing the first question, since it is asked of all users.
-This requirement is often \emph{not} met for questions beyond Task~01; on average 59\% of the galaxies do not have sufficient data to measure a correction, as compared to 2\% acheived for Task~01 (see Table~\ref{tbl:ferengi_corrections}).
-Of the remaining FERENGI galaxies which did meet this requirement, the data available in each redshift-surface brightness bin were not tightly correlated between $p_{task,z=0.3}$ and $p_{task,z}$, and relationships between the two could not be fit with high confidence.
-These galaxies are used to compute $\zeta$ for each Task, and find the p-values for the resulting functions between $placeholder < p < placeholder$, which are insufficient for deriving a correction.
-An example of this is given in Section \ref{sec:ferengi_bar}, based on attempting to compute $\zeta$ for $p_{\rm bar}$ in Task~03.
-For this reason, GZH only provides debiased vote fractions for Task~01 (smooth/features/artifact).
-
+This requirement is often \emph{not} met for questions beyond Task~01; on average 60.0\% of the galaxies do not have sufficient data to measure a correction, as compared to 2.0\% acheived for Task~01 (see Table~\ref{tbl:ferengi_corrections}).
+Of the remaining FERENGI galaxies which did meet this requirement, polynomials were fit to the data in each redshift-surface brightness bin, as was done for Task~01 (described above).
+The goodness-of-fit was evaluated in each bin, for each Task, using the value of the sum of the square residuals (SSR).
+The mean SSR for all Tasks was $\mu_{\rm SSR}$ = 0.46, $\sigma$ = 0.36, which was not considered sufficiently low in any Task for the fits to accurately model the data.
+An example of the debiasing technique applied to $p_{\rm bar}$ is shown in Section \ref{sec:ferengi_bar}; visual inspection of Figure~\ref{fig:p_vs_p_bar} confirms the available data in each bin is scattered to a degree at which no correlation may be confidently obtained.
+For these reasons, debiased vote fractions are only offered for Task~01 (smooth/features).
 \begin{table*}

### 2016-05-04 writeup/gz_hubble_data.tex
added ferengi stats and updated figures in appendices

@@
 \subsection{Challenges of debiasing questions beyond ``smooth or features''}
-
+\label{ssec:higher_order_tasks}
 As with the HST images, each FERENGI subject has a varying number of users answering the various questions in the hierarchical decision tree.
@@
 This requirement is by default met by all galaxies when analyzing the first question, since it is asked of all users.
-This requirement is often \emph{not} met for questions beyond Task~01; on average 60.0\% of the galaxies do not have sufficient data to measure a correction, as compared to 2.0\% acheived for Task~01 (see Table~\ref{tbl:ferengi_corrections}).
+This requirement is often \emph{not} met for questions beyond Task~01; on average 60.0\% $\pm$ 24.0\% of the galaxies do not have sufficient data to measure a correction, as compared to 2.0\% acheived for Task~01 (see Table~\ref{tbl:ferengi_corrections}).
 Of the remaining FERENGI galaxies which did meet this requirement, polynomials were fit to the data in each redshift-surface brightness bin, as was done for Task~01 (described above).
-The goodness-of-fit was evaluated in each bin, for each Task, using the value of the sum of the square residuals (SSR).
-The mean SSR for all Tasks was $\mu_{\rm SSR}$ = 0.46, $\sigma$ = 0.36, which was not considered sufficiently low in any Task for the fits to accurately model the data.
+The goodness-of-fit was evaluated in each bin, for each Task, using a normalized $\chi^2$ metric.
+The mean $\chi^2$ for all higher-order tasks was $\mu_{\chi^2} = 0.10 \pm 0.04$, which were significantly greater than that achieved for Task 01, $\chi^2 = 0.04$.
+From this statistic it was determined that the data could not be modeled with sufficient confidence for the higher order tasks.
 An example of the debiasing technique applied to $p_{\rm bar}$ is shown in Section \ref{sec:ferengi_bar}; visual inspection of Figure~\ref{fig:p_vs_p_bar} confirms the available data in each bin is scattered to a degree at which no correlation may be confidently obtained.
 For these reasons, debiased vote fractions are only offered for Task~01 (smooth/features).
+
 \begin{table*}
@@
 
-\begin{figure}
+\begin{figure*}
 \begin{center}
 \includegraphics[width=0.50\textwidth]{figures/full_shallow_p_plot.pdf}
-\caption{shallowfull}
+\caption{Distribution of $p_{\rm features}$ for the 4,461 GOODS galaxies which had both shallow and full depth images morphologically classified in GZH.
+For most galaxies, the value of $p_{\rm features}$ is in strong agreement between both types of images.
+Examples of galaxies with both sharp changes in $p_{\rm features}$, and little to no change, are shown in Figures~\ref{fig:shallow_smooth}-\ref{fig:shallow_featured}.}
 \label{fig:shallow_vs_full}
 \end{center}
-\end{figure}
+\end{figure*}
 
@@
 \label{sec:ferengi_bar}
+
+To determine the rate at which the vote fraction for any Task decreases with redshift or surface brightness, data from simluated FERENGI images were modeled with functions in discrete redshift / surface brightness bins, described in detail in Section~\ref{ssec:zeta_results}.
+A cut of $N>10$ was placed on the number of votes to reduce the error in the vote fractions and ensure they were well-sampled before applying a fit to the data.
+This requirement was not met for sufficient data in Tasks higher than Task~01, which significantly reduced the goodness-of-fit for the model functions as compared with the features Task.
+Here we show an example of results obtained for the bar Task.
+In Figure~\ref{fig:p_vs_p_bar}, it is apparent that both the lack of points and the degree of scatter in each bin prevent proper functions to be fit to the data.
+Table~\ref{tbl:ferengi_bar} summarizes the correction-type classification of the FERENGI data for this Task; 71\% of the galaxies simulated did not meet requirements for well-sampled vote fractions, as compared with 2\% acheived for Task~01.
+These results were similar for all higher-order Tasks, as described in Section~\ref{ssec:higher_order_tasks}, and therefore corrections were not derived for these Tasks.
+
 \begin{figure*}
@@
 \subfigure{[d]\label{d}\includegraphics[width=0.4\textwidth]{figures/z1_mu20_subplot2_bar.pdf}}
-\caption{Same as Figure~\ref{fig:p_vs_p}, but with the bar question.}
+\caption{Refer to Figure~\ref{fig:p_vs_p} for a comparison to the features question.
+Effects of redshift bias in 3,950 images in the \ferengi{} sample.
+[a]: Each point in a given redshift and surface brightness bin represents a unique galaxy.
+On the $y$-axis in each bin is the \pfeatures{} value of the image of that galaxy redshifted to the value corresponding to that redshift bin.
+On the $x$-axis is the \pfeatures{} value of the image of the same galaxy redshifted to $z=0.3$.
+The dashed black lines represent the best-fit polynomials to the data in each square.
+The solid black line represents \pfeaturesz=\pfeaturesrest.
+Regions in which there is a single-valued relationship between \pfeatures{} at high redshift and at $z=0.3$ are white; those in which there is not are blue, and those with not enough data ($N<5$) are gray.
+\textbf{The mean normalized $\chi^2$, $\mu_{\chi^2}=0.08$ over all bins confirmed the polynomials were not good fits to the data, and no correction was derived from these.} [b]: A larger version of the dark-outlined square in [a], containing \ferengi{} galaxies that have been artificially redshifted to $z=1.0$ and have surface brightnesses between $20.3 < \mu < 21.0$ $\rm (mag/arcsec^2)$.
+[c]: The same data as [a] is shown.
+Each $z,\mu$ bin is divided into 4 sub-bins to determine the range of intrinsic \pfeaturesrest{} for a given range of observed \pfeaturesz{} values.
+In each sub-bin, the orange bars represent the inner 80$^\mathrm{th}$ percentiles of the data, the boundaries of which are the lower and upper limits of the debiased values.
+[d]: The same data as [b], but highlighting the upper and lower limit regions.}
 \label{fig:p_vs_p_bar}
@@
 \begin{table}ー
+\label{tbl:ferengi_bar}
 \caption{Distribution of \ferengi{} images analysed in Figure~\ref{fig:p_vs_p_bar}.
@@
 Correctable                        & 664   & 17\% \\
-Lower-limi                         & 483   & 12\% \\
+Lower-limit                        & 483   & 12\% \\
 NEI                                & 2,803     & 71\%\\

### 2016-05-05 writeup/gz_hubble_data.tex

--- 2016-04-30 writeup/gz_hubble_data.tex
@@
 In the FERENGI data, these numbers severely limit the amount of information that can be extracted for the higher-tier questions.
-The debiasing technique used (Section~\ref{ssec:zeta}) require that at least 10~users answer each question for a galaxy image at $z=0.3$ \emph{and} its image at higher redshift.
-This requirement is by default met by all galaxies when analyzing the first question, since it is asked of all users.
-This requirement is often \emph{not} met for questions beyond Task~01; on average 59\% of the galaxies do not have sufficient data to measure a correction, as compared to 2\% acheived for Task~01 (see Table~\ref{tbl:ferengi_corrections}).
-Of the remaining FERENGI galaxies which did meet this requirement, the data available in each redshift-surface brightness bin were not tightly correlated between $p_{task,z=0.3}$ and $p_{task,z}$, and relationships between the two could not be fit with high confidence.
-These galaxies are used to compute $\zeta$ for each Task, and find the p-values for the resulting functions between $placeholder < p < placeholder$, which are insufficient for deriving a correction.
-An example of this is given in Section \ref{sec:ferengi_bar}, based on attempting to compute $\zeta$ for $p_{\rm bar}$ in Task~03.
-For this reason, GZH only provides debiased vote fractions for Task~01 (smooth/features/artifact).
+The debiasing technique used (Section~\ref{ssec:zeta}) requires that at least 10~users answer each question for a galaxy with $z_\mathrm{sim}=0.3$ \emph{and} the corresponding image at higher redshift.
+This requirement is (by default) met by all galaxies for the smooth/features question.
+However, this is often \emph{not} met for questions beyond Task~01; on average.
+$60\%\pm24\%$ of the galaxies do not have sufficient data to measure a correction, as compared to 2.0\% achieved for Task~01 (Table~\ref{tbl:ferengi_corrections}).
+Of the remaining FERENGI galaxies which did meet this requirement, polynomials were fit to the data in each redshift-surface brightness bin, as was done for Task~01.
+The goodness-of-fit was evaluated in each bin, for each Task, using a normalized $\chi^2$ metric.
+The mean $\chi^2$ for all higher-order tasks was $0.10\pm0.04$, significantly larger than the Task 01 value of $0.04$.
+Based on this statistic, the data cannot not be modeled with sufficient confidence for the higher order tasks.
+An example of the debiasing technique applied to $p_{\rm bar}$ is shown in Section~\ref{sec:ferengi_bar}; visual inspection of Figure~\ref{fig:p_vs_p_bar} confirms that the points in each bin are scattered to a degree at which no strong correlation is present.
+For these reasons, debiased vote fractions are only offered in the GZH catalog for Task~01 (smooth/features).
 
@@
 
-\begin{figure}
+\begin{figure*}
 \begin{center}
 \includegraphics[width=0.50\textwidth]{figures/full_shallow_p_plot.pdf}
-\caption{shallowfull}
+\caption{Distribution of $p_{\rm features}$ for the 4,461 GOODS galaxies with both shallow (2-epoch) and full-depth (5-epoch) images morphologically classified in GZH.
+For most galaxies, the value of $p_{\rm features}$ is consistent ($\Delta p_\mathrm{features}<0.2$) between depths.
+Examples of galaxies with sharp changes in $p_{\rm features}$, as well as those with little to no change are shown in Figures~\ref{fig:shallow_smooth}-\ref{fig:shallow_featured}.}
 \label{fig:shallow_vs_full}
 \end{center}
-\end{figure}
+\end{figure*}
 
@@
 \label{sec:ferengi_bar}
+
+To determine the rate at which the vote fraction for any Task decreases with redshift or surface brightness, data from simluated FERENGI images were modeled with functions in discrete redshift and surface brightness bins (Section~\ref{ssec:zeta_results}).
+A cut of $N>10$ was placed on the number of votes to reduce the error in the vote fractions and ensure they were well-sampled before applying a fit to the data.
+This requirement was only met for Task~01, which significantly reduced the goodness-of-fit for the model functions as compared with to the smooth/features task.
+Here we show an example of results obtained for the bar Task.
+Figure~\ref{fig:p_vs_p_bar} shows that both the low sample rate and the degree of scatter in each bin inhibit fitting a reliable function that predicts $p_\mathrm{bar,z=0.3}$.
+Table~\ref{tbl:ferengi_bar} summarizes the correction types for the FERENGI data ; 71\% of the galaxies simulated did not meet the GZH requirements for well-sampled vote fractions for $p_\mathrm{bar}$, as compared to 2\% for $p_\mathrm{features}$.
+Similar results were obtained for all higher-order Tasks in GZH, as described in Section~\ref{ssec:higher_order_tasks}.
+
 \begin{figure*}
@@
 \subfigure{[d]\label{d}\includegraphics[width=0.4\textwidth]{figures/z1_mu20_subplot2_bar.pdf}}
-\caption{Same as Figure~\ref{fig:p_vs_p}, but with the bar question.}
+\caption{Similar to Figure~\ref{fig:p_vs_p}, showing effects of redshift bias for 3,950~images in the \ferengi{} sample.
+[a]: Each point in a given redshift and surface brightness bin represents a unique galaxy.
+The $y$-axis in each bin is the \pfeatures{} value of the image of that galaxy redshifted to the value corresponding to that redshift bin.
+The $x$-axis is the \pfeatures{} value of the image of the same galaxy redshifted to $z=0.3$.
+The dashed black lines represent the best-fit polynomials to the data in each square.
+The solid black line represents \pfeaturesz=\pfeaturesrest.
+Regions in which there is a single-valued relationship between \pfeatures{} at high redshift and at $z=0.3$ are marked in white; those in which there is not are blue, and those with not enough data ($N<5$) are gray.
+\textbf{The mean normalized $\chi^2$ of 0.08 confirms that these polynomials are not good fits to the data, with no correction derived.} [b]: A larger version of the dark-outlined square in [a], containing \ferengi{} galaxies artificially redshifted to $z=1.0$ and have surface brightnesses between $20.3 < \mu < 21.0$ $\rm (mag/arcsec^2)$.
+[c]: The same data as [a].
+Each $z,\mu$ bin is divided into 4~sub-bins to determine the range of intrinsic \pfeaturesrest{} for a given range of observed \pfeaturesz{} values.
+In each sub-bin, the orange bars represent the inner 80$^\mathrm{th}$ percentiles of the data, the boundaries of which are the lower and upper limits of the debiased values.
+[d]: The same data as [b], but highlighting the upper and lower limit regions.}
 \label{fig:p_vs_p_bar}

### 2016-05-05 writeup/gz_hubble_data.tex

@@
 \caption{Surface brightness vs.
-redshift of 118,083 galaxies in the ACS sample.
-The white grid denotes the surface brightness and redshift range of the \ferengi{} images, subdivided in bins corresponding to fixed ranges used for analysis in Figure~\ref{fig:p_vs_p}.}
+redshift of 3,950 \ferengi{} images and the 102,548 galaxies in the ACS sample which had measured values of $\mu$ and $z$.
+The color histogram counts the number of \ferengi{} images as a function of $\mu$ and $z_{\rm simulated}$.
+The white contours show counts for the ACS sample as a function of $\mu$ and $z$, with contours starting at N = 1000 and separated by 1000 up to 7000.}
 \label{fig:sb_redshift}

### 2016-05-05 writeup/gz_hubble_data.tex
Text changes and tightening of language.

--- 2016-05-05 writeup/gz_hubble_data.tex
@@
 The majority of the data (as implied by the project name) are taken directly from \hst{} Legacy Surveys, all of which primarily use imaging from the Advanced Camera for Surveys (ACS).
+Results from the individual surveys have been combined into a single photometric and morphological database, the Advanced Camera for Surveys General Catalog \citep[ACS-GC;][]{gri12}.
 A summary of the key parameters is given in Table~\ref{tbl:gzh_numbers}.
@@
 
-In the Advanced Camera for Surveys General Catalog \citep[ACS-GC;][]{gri12}, individual galaxies are identified using a combination of \sextractor{} \citep{ber96} and the galaxy-profile fitting framework \galapagos{} \citep{bar12}.
+In the ACS-GC \citep{gri12}, individual galaxies are identified using a combination of \sextractor{} \citep{ber96} and the galaxy-profile fitting framework \galapagos{} \citep{bar12}.
 GZH includes all galaxies with $m < 23.5$, where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS, GEMS + GOODS-S, and GOODS-N surveys, respectively.
@@
 
-Since the majority of the data in Legacy surveys described in \S\ref{ssec:legacy_surveys} had images in only 1 or 2~bands available when the GZH project was first launched, making standard 3-channel RGB images in the same method used for the SDSS images in the original Galaxy Zoo was not possible.
-For surveys with images in two bands (AEGIS, GEMS, and the two-epoch GOODS-N and GOODS-S), the lower-wavelength band is mapped to the blue channel, the higher-wavelength band to the red channel, and the green channel created by taking the geometric mean of the two.
+The majority of the data in Legacy surveys described in \S\ref{ssec:legacy_surveys} had images in only one or two filters available when the GZH project was first launched, making standard 3-channel RGB images in the same method used for the SDSS images in the original Galaxy Zoo impossible.
+For surveys with images in two bands (AEGIS, GEMS, and the two-epoch GOODS-N and GOODS-S), the lower-wavelength band was mapped to the blue channel, the higher-wavelength band to the red channel, and the green channel created by taking the geometric mean of the two.
 Bands used in each of the surveys are listed in Table~\ref{tbl:gzh_numbers}.
@@
 
-To deal with images in which the sky noise was highly colored (which might have been a distraction to visual classification), a soft-edged object mask is applied to the image that preserves the color balance for galaxies, but desaturates the speckled noise against regions of blank sky.
+To deal with images in which the sky noise was highly colored (which might have been a distraction to visual classification), a soft-edged object mask was applied that preserves the color balance for galaxies, but desaturates the speckled noise against regions of blank sky.
 This technique was applied only to the coadded Stripe~82 and the COSMOS images.
@@
 Since galactic nuclei can have bright, unresolved optical emission, this has the potential to mimic or distort the identification of a bulge component.
-The presence of an AGN is simulated by modeling the PSF for \hst{} and then inserting a bright source near the center of a real galaxy.
+The presence of an AGN is simulated by modeling the point spread function (PSF) of the telescope and then inserting a bright source near the center of a real galaxy.
 For each image, the simulated AGN is assigned one of three colors -- either blue, red, or flat (white) as seen in the color images -- and a range of brightnesses such that $L_\mathrm{ratio} \equiv L_\mathrm{galaxy}/L_\mathrm{AGN}$ is in $(0.2,1.0,2.0,5.0,10.0,50.0)$.
@@
 A high quality spectroscopic redshift in the ACS-GC is the primary option; if none is available, then $\tt Z\_BEST$ uses the spectroscopic redshifts in 3DHST, and then MUSYC.
-For galaxies with multiple spectroscopic redshifts, more than 98\% are consistent at $\Delta z<0.001$; therefore, the priority order of selection makes no negligible difference for the sample.
+For galaxies with multiple spectroscopic redshifts, more than 98\% are consistent at $\Delta z<0.001$, and so the order of selection makes no practical difference.
 If no spectroscopic redshifts are available, the 1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST, MUSYC, UltraVISTA;][]{ilb13} and UltraVISTA grism data are used to select the redshift with the smallest error.
@@
 This includes $ugriz$ Petrosian magnitudes and fluxes, as well as the relative de~Vaucouleurs and exponential fits from the model magnitudes.
-Redshifts used for the Sloan galaxies are all spectroscopic.
+Redshifts used for the SDSS galaxies are all spectroscopic.
 82.6\% of galaxies in the single-depth images and 65.1\% of galaxies in the coadd images have a measured DR7 spectroscopic redshift.
@@
 
+{\note Describe the GZ interface and the hierarchical decision tree.}
+
 \begin{figure*}
@@
 For both previous releases of GZ morphologies, a correction for redshift-dependent bias was applied based on matching the classification fractions at the highest redshfts with those at the lowest redshift.
-See \citet{bam09} and \citet{wil13} for the details.
+\citet{bam09} and \citet{wil13} provide complete descriptions of the process for GZ1 and GZ2, respectively.
 
@@
 The surface brightness selection ($N_\mu = 3$) for the FERENGI galaxies was (1) low: $\mu > 21.5$~\magarc;  (2) mid: $20.5 < \mu < 21.5$~\magarc; and (3) high: $\mu < 20.5$~\magarc.
-For each of the four ``target redshifts'' ($z = 0.3, 0.5, 0.8$ and $1.0$), the images were redshifted in $\Delta z = 0.1$ bins up to $z=1.0$.
+For each of the four ``target redshifts'' ($z_\mathrm{sim} = 0.3, 0.5, 0.8$ and $1.0$), the images were redshifted in $\Delta z = 0.1$ bins up to $z_\mathrm{sim}=1.0$.
 
@@
 \hline\hline
-$z_{\rm target}$ & $N_{z {\rm bins}}$ & $N_{\rm evolution}$ & $e_{\rm max}$ & $N_{\rm galaxies}$ & $N_{\rm images}$\\
+$z_{\rm sim}$ & $N_{z {\rm bins}}$ & $N_{\rm evolution}$ & $e_{\rm max}$ & $N_{\rm galaxies}$ & $N_{\rm images}$\\
 \hline
@@
 
-The change in bias as a function of $\mu_r$ and $z$ is measured using the \ferengi{} images over all the evolutionary correction factors.
+The change in bias as a function of $\mu_r$ and \zsim{} is measured using the \ferengi{} images over all the evolutionary correction factors.
 It is assumed that the ``true'' (ie, debiased) vote fraction $f_{\mu,z}$ for a galaxy can be expressed as:
@@
 GZH uses the values of $\zeta$ for \emph{all} sets of artifically redshifted galaxies to fit the overall distribution as a function of surface brightness, since the correction being applied is expected to vary as a function of the intrinsic galaxy properties.
-The galaxies that can be used to measure the calibration are restricted to those with data at the pivot redshift of $z=0.3$, non-zero $f_\textrm{features}$ at $z=0.3$, and with a reasonable fit to the exponential model ($\Delta \chi^2 > 3.0$).
+The galaxies that can be used to measure the calibration are restricted to those with a non-zero $f_\textrm{features}$ at $z_\mathrm{sim}=0.3$ and with a reasonable fit ($\Delta \chi^2 > 3.0$) to the exponential model for the measured change in \ffeatures.
 
@@
 \includegraphics[width=0.5\textwidth]{figures/eye_of_sauron.pdf}
-\caption{Surface brightness vs.
-redshift of 118,083 galaxies in the ACS sample.
-The white grid denotes the surface brightness and redshift range of the \ferengi{} images, subdivided in bins corresponding to fixed ranges used for analysis in Figure~\ref{fig:p_vs_p}.}
+\caption{Surface brightness as a function of redshift for 3,950~\ferengi{} images and the 102,548~galaxies in the ACS sample ith measured $\mu$ and $z$ values.
+The color histogram shows the number of \ferengi{} images as a function of $\mu$ and $z_{\rm sim}$.
+White contours show counts for the full ACS sample, with contours starting at $N=1000$ and separated by intervals of 1000 up to 7000.}
 \label{fig:sb_redshift}
@@
 These regions tend to have low \pfeatures{} values at high redshift, but a wide range of values at $z=0.3$.
-These regions contain two morphological types of galaxies: First are genuine ellipticals, which have low values of \pfeatures{} at both high and low redshift.
-Second are disks whose features become washed out at high redshift; hence their \pfeatures{} value at $z=0.3$ may be quite high, while the value observed at high redshift is very low.
+These regions contain two morphological types of galaxies: the first set are genuine ellipticals, which have low values of \pfeatures{} at both high and low redshift.
+The second group are disks whose features become indistinct at high redshift; hence their \pfeatures{} value at $z=0.3$ may be quite high, while the value observed at high redshift is very low.
 This effect is strongest at high $z$ and low $\mu$, where features become nearly impossible to discern in the images.
 
-The criteria for determining whether a region of this space is single-valued, and therefore correctable, is as follows: In each surface brightness and redshift bin, the relationship between \pfeaturesz{} and \pfeaturesrest{} is modeled by fitting the data with a polynomial of degrees 3, 2, and 1, and use the best fit out of the three.
+The criteria for determining whether a region of this space is single-valued, and therefore correctable, is as follows: In each surface brightness and redshift bin, the relationship between \pfeaturesz{} and \pfeaturesrest{} is modeled by fitting the data with a polynomial of degrees $n=3$, 2, and 1, and using the best fit out of the three.
 These fits are shown as the dashed black lines in Figure~\ref{fig:6a}.
@@
 
-The unshaded regions in Figure~\ref{fig:6a} define discrete ranges of redshift, surface brightness, and \pfeatures{} a galaxy must have in order for the $\zeta$ approach to be confidentely applied to a galaxy in the GZH sample.
+The unshaded regions in Figure~\ref{fig:6a} define discrete ranges of redshift, surface brightness, and \pfeatures{} a galaxy must have in order for the debiased correction to be confidentely applied to a galaxy in the GZH sample.
 While the appropriate correctable regions were defined discretely, the true correctable region is assumed to be a smooth function of $z$, $\mu$, and \pfeatures{}.
@@
 The results of this method and final categorization of the \hst{} sample is displayed in Table~\ref{tbl:hubble_debiasable}.
-Of the galaxies at redshift higher than $z=z_{0}=0.3$, 17\% of these are able to be debiased using the $\zeta$ method, 27\% cannot be debiased, and 56\% cannot be determined, due to a lack of redshift or information or due to a lack of \ferengi{} data corresponding to those galaxies' redshift/surface brightness values.
+Of the galaxies at redshift higher than $z=0.3$, 17\% can be debiased using the $\zeta$ method, 27\% cannot be debiased, and 56\% cannot have the potential for a correction determined, due either a lack of redshift for the host galaxy or insufficient \ferengi{} images corresponding to the relevant $z$-$\mu$ values.
 
@@
 
+\begin{figure*}
+\center
+\includegraphics[width=\textwidth]{figures/debiased_corrections.pdf}
+\caption{Debiased $p_{features}$ corrected to $z=0.3$ vs weighted $p_{features}$ for the correctable (left), lower-limit (middle), and NEI (right) galaxies in the GZH sample.}
+\label{fig:debiased_corrections}
+\end{figure*}
+
 \subsection{Challenges of debiasing questions beyond ``smooth or features''}
@@
 As with the HST images, each FERENGI subject has a varying number of users answering the various questions in the hierarchical decision tree.
-Every user answers the first question, ``Is the galaxy smooth and rounded, with no sign of a disk?''; as such the vote fractions $\rm p_{smooth}, p_{features}$, and $\rm p_{artifact}$ are all computed with the minimum statistical error for any question, with roughly 40 total answers (see Section~\ref{sec:interface}).
+Every user answers the first question, {\it ``Is the galaxy smooth and rounded, with no sign of a disk?''}; as such the vote fractions $p_\mathrm{smooth}, p_{features}$, and $p_\mathrm{artifact}$ are all computed with the minimum statistical error for any question, with roughly 40 total answers (see Section~\ref{sec:interface}).
 The number of users to answer any subsequent question, however, is always equal to or less than the number to answer the preceding question.
@@
 
-\begin{figure*}
-\center
-\includegraphics[width=\textwidth]{figures/hubble_z_mu_p_distributions.pdf}
-\caption{Distributions of redshift, surface brightness, and $p_{features}$ for correctable (purple), lower-limit (green), and NEI (pink) galaxies in the full GZH sample.
+%\begin{figure*}
+%\center
+%\includegraphics[width=\textwidth]{figures/hubble_z_mu_p_distributions.pdf}
+%\caption{Distributions of redshift, surface brightness, and $p_{features}$ for correctable (purple), lower-limit (green), and NEI (pink) galaxies in the full GZH sample.
 The lower-limit galaxies have higher redshifts, slightly lower surface brightness, and lower values of $p_{features}$ on average than the correctable galaxies.
 The long tail of NEI galaxies in redshift and surface brightness demonstrates the limits of the \ferengi{} sample, for which there is no data at $z>1$ or $\mu>24$.}
-\label{fig:z_mu_p}
-\end{figure*}
-
-\begin{figure*}
-\center
-\includegraphics[width=\textwidth]{figures/debiased_corrections.pdf}
-\caption{Debiased $p_{features}$ corrected to $z=0.3$ vs weighted $p_{features}$ for the correctable (left), lower-limit (middle), and NEI (right) galaxies in the GZH sample.}
-\label{fig:debiased_corrections}
-\end{figure*}
+%\label{fig:z_mu_p}
+%\end{figure*}
 
@@
 
-\section{The catalog}\label{sec:results}
+\section{The GZH catalog}\label{sec:results}
 
@@
 The full table can be accessed at \url{http://data.galaxyzoo.org}.
-This also includes a secondary metadata table, which contains data from a variety of sources explained in Section \ref{sec:data}.
+The online data also includes a secondary metadata table, which is drawn from a variety of sources detailed in Section \ref{sec:data}.
 
@@
 
-The GZH catalog is corrected for classification bias in the first question of the GZH decision tree, which asks ``Is the galaxy smooth and round, with no sign of a disk?'' The method is described in Section~\ref{sec:debiasing}.
-For this question, the catalog provides the additional parameters $\tt debiased$, $\tt lower~limit$, $\tt upper~limit$, and $\tt best$ vote fractions.
+The GZH catalog is corrected for classification bias only for the first question of the GZH decision tree (Section~\ref{sec:debiasing}), which asks {\it ``Is the galaxy smooth and round, with no sign of a disk?''} For this question, the catalog provides the additional parameters $\tt debiased$, $\tt lower~limit$, $\tt upper~limit$, and $\tt best$ vote fractions.
 The $\tt best$ fraction for $p_{features}$is chosen based on the categorization of the galaxy: if it is ``correctable'', $\tt best = debiased$, if a lower limit, $\tt best = lower~limit$, and if neither, $\tt best = weighted$.
 
-The debiased and best vote fractions for $\tt p_{smooth}$ were calculated on the critera that vote fractions for all answers must sum to unity.
-Explicitly: $\tt p_{smooth} = 1 - p_{features} - p_{artifact}$.
-In some rare cases, representing  $<1\%$ of the sample, this requirement resulted in negative vote fractions for $\rm p_{smooth}$; these were cases in which the $\rm p_{features}$ vote fraction was boosted to a high value relative to the $\rm p_{artifact}$ vote fraction.
-In these cases, the constraint that the vote fractions must sum to 1 is met by raising $\rm p_{smooth}$ to a vote fraction of 0.0 and decreasing $\rm p_{features}$ accordingly.
-This correction is typically small, with a median decrease/increase of $\rm p_{features}/p_{smooth}$ of $\Delta p = 0.04$.
+The debiased and best vote fractions for $\tt p_{smooth}$ were calculated on the critera that vote fractions for all answers must sum to unity, such that:
+
+\begin{equation}
+p_\mathrm{smooth} \equiv 1 - p_\mathrm{features,best} - p_\mathrm{artifact}.
+\label{eqn:nonlinear}
+\end{equation}
+
+\noindent In rare cases ($<1\%$ of the sample), this requirement resulted in negative vote fractions for $p_\mathrm{smooth}$; these were cases in which the $p_\mathrm{features}$ vote fraction was boosted to a high value relative to the $p_\mathrm{artifact}$ vote fraction.
+In these cases, the constraint that the vote fractions must sum to 1 is met by setting $p_\mathrm{smooth}=0.0$ and decreasing $p_\mathrm{features}$ accordingly.
+This correction is typically small, with a median decrease/increase of $p_\mathrm{features}/p_{smooth}$ of $\Delta p = 0.04$.
 
@@
 With this structure, questions shown to a user are dependent on their answers to the previous questions.
-For example, a user is only asked Task 11, ``How many spiral arms?'' if they had answered ``yes'' to Task 10, which asks whether any spiral arms are present.
+For example, a user is only asked Task 11, {\it ``How many spiral arms?''} if they had answered ``yes'' to Task 10, which asks whether any spiral arms are present.
 This structure is used to reduce the workload of the users by only asking questions relevant to the particular galaxy; in this example, it would not be useful, nor would it make physical sense, to ask a user how many spiral arms in a galaxy which they had declared had no spiral arms to begin with.
@@
 
-{\note \it Summarize the broad trends that are seen regarding the fraction of galaxies with various morphologies, how that relates to color, size, etc.
+{\note Summarize the broad trends that are seen regarding the fraction of galaxies with various morphologies, how that relates to color, size, etc.
 Briefly discuss results as compared with literature and theory.}
@@
 The second set of plots in Figure~\ref{fig:comparisons} indicates that \podd{} is largely an effective method for separating irregular and/or peculiar galaxies from spirals.
-Despite the somewhat vague wording of the ``anything odd?'' question in GZH, the AEGIS, COSMOS, and GOODS all show a marked increase in the irregular fraction increasing with \podd.
+Despite the somewhat vague wording of the {\it ``anything odd?''} question in GZH, the AEGIS, COSMOS, and GOODS all show a marked increase in the irregular fraction increasing with \podd.
 Any threshold value for distinguishing between the two, however, depends strongly on survey/redshift~range.
@@
 Of the 11,157 galaxies in the GOODS-N and GOODS-S full depth sample, 4,461 of these are in the shallow-depth sample.
-Figure~\ref{fig:shallow_vs_full} shows a strong correlation between $\rm p_{features}$ for both sets of images.
-The mean change in $\rm p_{features}$ from the shallow to full depth images  $\rm p_{features,full} - p_{features,shallow} \equiv \Delta p = 0.00$, with a standard deviation of $\sigma = 0.17$.
+Figure~\ref{fig:shallow_vs_full} shows a strong correlation between $p_\mathrm{features}$ for both sets of images.
+The mean change in $p_\mathrm{features}$ from the shallow to full depth images  $p_\mathrm{features,full} - p_{features,shallow} \equiv \Delta p = 0.00$, with a standard deviation of $\sigma = 0.17$.
 While there is some variance in $\Delta p$ in the whole sample, the change is usually small and not often significant enough to change a morphological classification.

### 2016-05-05 writeup/gz_hubble_data.tex

@@
 \end{figure*}
+
+Few galaxies in the sample have sufficiently high corrections to completely change them from being confidently smooth to featured following the bias correction (Figure~\ref{:debiased_corrections}).
+As a check, highly boosted galaxies are compared to the expert classifications in the CANDELS catalog \citep{kar15}.
+There are only eight galaxies that were strongly boosted ($p_\mathrm{features,raw}<0.2$ and $p_\mathrm{features,best} > 0.5$) in GZH and also appears in the CANDELS expert sample.
+Of those eight galaxies, \citet{kar15} classifies 5 as spheroids, 2 as disks, and 1 as irregular/disky.
+The \pbest{} values for GZH are all between 0.5 and 0.6, making them intermediate disk candidates.
+One of the spheroids has hints of an interaction or minor merger to the south that may have been missed by the CANDELS experts, but almost all images are dim and with very low surface brightnesses in the ACS imaging, making positive identification challenging.
+Since the surveys use different rest-frame filters and the overlap sample is tiny, though, detailed comparisons between the overall morphologies are highly difficult.
 

### 2016-05-05 writeup/gz_hubble_data.tex
Typo in boosted figure reference

@@
 
-Few galaxies in the sample have sufficiently high corrections to completely change them from being confidently smooth to featured following the bias correction (Figure~\ref{:debiased_corrections}).
+Few galaxies in the sample have sufficiently high corrections to completely change them from being confidently smooth to featured following the bias correction (Figure~\ref{fig:debiased_corrections}).
 As a check, highly boosted galaxies are compared to the expert classifications in the CANDELS catalog \citep{kar15}.

### 2016-05-06 writeup/gz_hubble_data.tex

@@
 GEMS                          & 2160$-$2286 & \Vband{} and \zband{}            & 0.03 & 800   & 9143  \\
-GOODS                         & 1000$-$2100 & \Bband, \Vband, \iband, \zband{} & 0.03 & 320   & 7336  \\
-\hspace{10pt} \emph{GOODS-N}  & $-$         & $-$                              & $-$  & $-$   & \emph{2551}  \\
-\hspace{10pt} \emph{GOODS-S}  & $-$         & $-$                              & $-$  & $-$   & \emph{4785}  \\
+GOODS                         & 1000$-$2100 & \Bband, \Vband, \iband, \zband{} & 0.03 & 320   &   \\
+\hspace{10pt} \emph{GOODS-N~2~epoch}  & $-$         & $-$                              & $-$  & $-$   & \emph{2551}  \\
+\hspace{10pt} \emph{GOODS-S~2~epoch}  & $-$         & $-$                              & $-$  & $-$   & \emph{3593}  \\
+\hspace{10pt} \emph{GOODS-N~5~epoch}  & $-$         & $-$                              & $-$  & $-$   & \emph{6015}  \\
+\hspace{10pt} \emph{GOODS-S~5~epoch}  & $-$         & $-$                              & $-$  & $-$   & \emph{5142}  \\
+
 \hline
-total                         & $-$         & $-$                              & $-$  & 8310  & 113166  \\
+total                         & $-$         & $-$                              & $-$  & 8310  & 130467  \\
 \hline\hline

### 2016-05-06 writeup/gz_hubble_data.tex
Sankey diagrams of sample

@@
 
+\begin{figure*}
+\center
+\includegraphics[width=0.90\textwidth]{figures/sankey_both.png}
+\caption{Demographics of the galaxy morphologies in GZH.
+Each node in each diagram (dark blue horizontal bars of uniform height) represents a task in the tree.
+The left diagram shows the full decision tree; the right diagram zooms in on the features/clumpy tasks, which are otherwise difficult to see.
+The paths between tasks represent each possible answer to the task; these flow from top to bottom between their origin question and the subsequent task in the tree.
+Labels are assigned to each galaxy based on the plurality answer for each task.
+A galaxy is assigned only one label at each node.
+Widths of the paths are proportional to the number of galaxies assigned to that path; the widths of the nodes are proportional to the number of galaxies for which the question was reliably answered.}
+\label{fig:sankey}
+\end{figure*}
+
 \subsection{Comparing GZH morphologies to other catalogs}\label{ssec:comparisons}

### 2016-05-06 python/gzh_gzc.py
Fixed label, bin order

@@ -79,13 +79,18 @@ for p,ax in zip(pd,axarr.ravel()):
     #cb.set_label(r'$N$',fontsize=16)
 
     plotbins = bins[:-1] + db/2.
-    ax.errorbar(plotbins,gzc_avg,xerr=gzh_std,color=blue,marker='o',ls='-',markersize=10)
-    ax.errorbar(plotbins,gzh_avg,yerr=gzc_std,color=red,marker='o',ls='-',markersize=10)
+    ax.errorbar(gzc_avg,plotbins,xerr=gzc_std,color=blue,marker='o',ls='-',markersize=10)
+    ax.errorbar(plotbins,gzh_avg,yerr=gzh_std,color=red,marker='o',ls='-',markersize=10)
 
     ax.set_xlim(-0.05,1.05)
     ax.set_ylim(-0.05,1.05)
     ax.set_xlabel(r'GZC {0} vote fraction'.format(p['label']),fontsize=16)
     ax.set_ylabel(r'GZH {0} vote fraction'.format(p['label']),fontsize=16)
+
+    # Super kluge
+    if ax == axarr.ravel()[2]:
+        ax.set_xlabel(r'GZC features (weighted) vote fraction',fontsize=16)
+
 
 fig.tight_layout()
 plt.show()

### 2016-05-07 writeup/gz_hubble_data.tex
Fixed error in task labeling. Closes #65.
Initial stab at ordering author list.

@@
 Willett\altaffilmark{1,2}, Melanie A.
-Galloway\altaffilmark{1}, Chris J.
-Lintott\altaffilmark{3}, B.D.
-Simmons\altaffilmark{3,4,5,6}, Karen L.
-Masters\altaffilmark{7,8}, Tom Melvin\altaffilmark{7}, Steven P.
-Bamford\altaffilmark{9}, Edward M.
-Edmondson\altaffilmark{7}, Lucy F.
-Fortson\altaffilmark{1}, Kevin Schawinski\altaffilmark{10}, Edmond Cheung\altaffilmark{11}, Claudia Scarlata\altaffilmark{1}, Melanie Beck\altaffilmark{1}, Arfon M.
-Smith\altaffilmark{3,12,13}, Michael Parrish\altaffilmark{12}, Roger L.
-Griffith\altaffilmark{14,15}, Anna Han\altaffilmark{16}
+Galloway\altaffilmark{1}, Karen L.
+Masters\altaffilmark{3,4}, B.D.
+Simmons\altaffilmark{5,6,7}, Chris J.
+Lintott\altaffilmark{5}, Steven P.
+Bamford\altaffilmark{8}, Edmond Cheung\altaffilmark{9}, Tom Melvin\altaffilmark{3}, Lucy F.
+Fortson\altaffilmark{1}, Melanie Beck\altaffilmark{1}, Claudia Scarlata\altaffilmark{1}, Roger L.
+Griffith\altaffilmark{10,11}, Kevin Schawinski\altaffilmark{12}, Edward M.
+Edmondson\altaffilmark{3}, Arfon M.
+Smith\altaffilmark{5,13,14}, Michael Parrish\altaffilmark{13}, Anna Han\altaffilmark{15}
 }
 %
-% List of people who have contributed (not sure if everyone will be author)
-% Definitely: Lintott, Bamford, Edmondson, Masters, Simmons, Melvin, Willett, Galloway, Fortson, Schawinski, Cheung
-% Others on GZ science team: Urry, Cardamone, Nichol, Kaviraj, Keel, Skibba, Thomas, Wong, Scarlata, Beck, Smethurst
-% Tech: Smith, Parrish, Simpson, other devs?
-% External: Han, Griffith
-%
-%$^1$Institute for Cosmology and Gravitation, University of Portsmouth, Dennis Sciama Building, Burnaby Road, Portsmouth, PO1 3FX, UK \\
-%$^2$South East Physics Network, www.sepnet.ac.uk\\
-%$^3$Dept. of Astronomy, Cornell University, Space Sciences Building, Ithaca, NY 14850, USA\\
-%$^2$Institute for Sciences of the Cosmos (ICCUB), University of Barcelona, Marti i Franques 1, Barcelona, 08024 Spain\\
-%$^4$Oxford Astrophysics, Department of Physics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK\\
-%$^5$Yale Center for Astronomy and Astrophysics, Yale University, P.O. Box 208121, New Haven, CT 06520, USA \\
-%$^6$Steward Observatory, University of Arizona, 933 N. Cherry Ave, Tuscon, AZ 85721, USA\\
-%$^4$Astronomy Department, Adler Planetarium and Astronomy Museum, 1300 Lake Shore Drive, Chicago, IL 60605, USA\\
-%$^7$Centre for Astronomy \& Particle Theory, University of Nottingham, University Park, Nottingham, NG7 2RD, UK\\
-%$^6$School of Physics and Astronomy, University of Minnesota, Minneapolis, MN 55455, USA\\
-%$^7$Department of Physics \& Astronomy, 206 Gallalee Hall, 514 University Blvd., University of Alabama, Tuscaloosa, AL 35487-0234, USA\\
-%$^8$Einstein Fellow\\
+%$^N$Institute for Cosmology and Gravitation, University of Portsmouth, Dennis Sciama Building, Burnaby Road, Portsmouth, PO1 3FX, UK \\
+%$^N$South East Physics Network, www.sepnet.ac.uk\\
+%$^N$Dept. of Astronomy, Cornell University, Space Sciences Building, Ithaca, NY 14850, USA\\
+%$^N$Institute for Sciences of the Cosmos (ICCUB), University of Barcelona, Marti i Franques 1, Barcelona, 08024 Spain\\
+%$^N$Oxford Astrophysics, Department of Physics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK\\
+%$^N$Yale Center for Astronomy and Astrophysics, Yale University, P.O. Box 208121, New Haven, CT 06520, USA \\
+%$^N$Steward Observatory, University of Arizona, 933 N. Cherry Ave, Tuscon, AZ 85721, USA\\
+%$^N$Astronomy Department, Adler Planetarium and Astronomy Museum, 1300 Lake Shore Drive, Chicago, IL 60605, USA\\
+%$^N$Centre for Astronomy \& Particle Theory, University of Nottingham, University Park, Nottingham, NG7 2RD, UK\\
+%$^N$School of Physics and Astronomy, University of Minnesota, Minneapolis, MN 55455, USA\\
+%$^N$Department of Physics \& Astronomy, 206 Gallalee Hall, 514 University Blvd., University of Alabama, Tuscaloosa, AL 35487-0234, USA\\
+%$^N$Einstein Fellow\\
 
@@
 Images in GZH are selected from various \textit{Hubble Space Telescope} Legacy programs using the Advanced Camera for Surveys (AEGIS, COSMOS, GEMS, GOODS-N, and GOODS-S), with filters selected to probe the rest-frame optical emission from galaxies out to $z\simeq1$.
-The galaxies selected for GZH classifications go down to magnitude limits of $m_{I}<23.5$ and have a median redshift of $\langle z\rangle=0.9\pm0.6$, with a tail extending out to $z\simeq4$.
+The galaxies selected for GZH classifications go down to magnitude limits of $m_{I814W}<23.5$ and have a median redshift of $\langle z\rangle=0.9\pm0.6$, with a tail extending out to $z\simeq4$.
 The GZH morphological data includes measurements of both bulge- and disk-dominated galaxies, details on spiral disk structure that relate to the Hubble type, and numerous measurements of clump identification and geometry.
 This paper also describes and employs a novel method for calibrating morphological bias by using artificially-redshifted galaxy images as a baseline.
-This paper presents both the raw and calibrated morphological vote fractions for $150,771$ galaxies, constituting a large data set suitable for large-scale studies of galaxy evolution.
+The GZH catalog includes both the raw and calibrated morphological vote fractions for $150,771$ galaxies, constituting a large data set suitable for large-scale studies of galaxy evolution.
 
@@
 The process can also be slowed or even reversed via feedback from stellar winds, supernovae, and active black holes.
-Each of these processes affects on the galaxy morphology, and so an accurate measurement of the demographics as a function of redshift provides an extremely powerful observational constraint on the physics involved \citep[for a recent review see][]{con14}.
+Each of these processes affects the galaxy morphology in different ways, and so an accurate measurement of the demographics as a function of redshift provides an extremely powerful observational constraint on the physics involved \citep[for a recent review see][]{con14}.
 
@@
 The Galaxy Zoo project \citep{lin08,lin11} utilizes crowdsourced visual classifications to measure galaxies in color-composite images.
-With $>2\times10^5$~classifiers, this allows for multiple independent classifications of each image which are combined and calibrated to give a distribution of vote fractions proportional to the probability of a feature being visible.
+The efforts of more than $2\times10^5$~classifiers allow for multiple independent classifications of each image which are combined and calibrated to give a distribution of vote fractions proportional to the probability of a feature being visible.
 While the crowdsourced data require extensive calibration \citep{bam09,wil13}, they have a proven reliability and have been used in dozens of papers \citep[eg,][]{lan08,bam09,dar10,mas11c,ski12,sim13,sch14,wil15}.
@@
 GZH used a similarly detailed classification scheme, but focused for the first time on images of high-redshift galaxies taken with the \hubble.
+The Galaxy Zoo: CANDELS project also classified morphologies of galaxies at high redshift using ACS and WFC3 imaging (Simmons et~al., submitted).
 
@@
 Section~\ref{sec:interface} describes the GZH interface and the collection of classifications.
-Section~\ref{sec:debiasing} outlines the process used to calibrate and ``debias'' the crowdsourced votes.
-Section~\ref{sec:results} gives the main results as a catalog, with several examples of how the data may be queried in Section~\ref{sec:cookbook}.
+Section~\ref{sec:debiasing} outlines the process used to calibrate and correct the crowdsourced vote fractions for redshift-dependent bias.
+Section~\ref{sec:results} gives the main catalog of results, with several examples of how the data may be queried in Section~\ref{sec:cookbook}.
 Section~\ref{sec:analysis} gives a short overview of the observed morphological demographics and compares them to several other catalogs, with a summary in Section~\ref{sec:summary}.
@@
 \includegraphics[width=160mm]{figures/filter_curves.pdf}
-\caption{Transmission curves of the filters used by \hst{} Advanced Camera for Surveys (ACS) in wide-field channel mode for the various surveys in Galaxy Zoo: Hubble.
-The unfilled black curves show the filters for the Suprime Camera on the \textit{Subaru} telescope which were used to create color gradients in the composite images for COSMOS.\label{fig:filtercurves}}
+\caption{Transmission curves of the filters used by \hst{} Advanced Camera for Surveys (ACS) in wide-field channel mode for the various surveys in GZH.
+The unfilled black curves show the filters for the Suprime Camera on the \textit{Subaru} telescope, which was used to create color gradients in the GZH images for COSMOS.\label{fig:filtercurves}}
 \end{figure*}
@@
 Single-epoch images from SDSS Stripe~82 were selected using the same criteria from \citet{wil13}, which required limits of \texttt{petroR90\_r}$ > 3$\arcsec~(where \texttt{petroR90\_r} is the radius containing 90\% of the $r^\prime$ Petrosian flux) and a magnitude brighter than $m_r < 17.77$.
+The images used are three-color composites using the $g^\prime$, $r^\prime$, and $i^\prime$ filters \citep{nie04}.
 21,522 galaxies in SDSS met these criteria.
@@
 
-The majority of the data in Legacy surveys described in \S\ref{ssec:legacy_surveys} had images in only one or two filters available when the GZH project was first launched, making standard 3-channel RGB images in the same method used for the SDSS images in the original Galaxy Zoo impossible.
+The majority of the data in Legacy surveys described in Section~\ref{ssec:legacy_surveys} had images in only one or two filters available when the GZH project was first launched, making standard 3-channel RGB images in the same method used for the SDSS images in the original Galaxy Zoo impossible.
 For surveys with images in two bands (AEGIS, GEMS, and the two-epoch GOODS-N and GOODS-S), the lower-wavelength band was mapped to the blue channel, the higher-wavelength band to the red channel, and the green channel created by taking the geometric mean of the two.
@@
 Redshifts for the GZH catalog are compiled from a variety of sources.
-For each galaxy, the primary redshift used for debiasing calculations (Section~\ref{sec:debiasing}) is in the $\tt Z\_Best$ column of Table~\ref{tbl:catalog_hst}.
+For each galaxy, the primary redshift used for debiasing calculations (Section~\ref{sec:debiasing}) is in the $\tt Z\_BEST$ column of Table~\ref{tbl:catalog_hst}.
 The redshift type (spectroscopic: $\tt SPEC\_Z$, photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column $\tt Z\_BEST\_TYPE$, and the source catalog of the redshift is included as $\tt Z\_BEST\_SOURCE$.
@@
 If no spectroscopic redshifts are available, the 1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST, MUSYC, UltraVISTA;][]{ilb13} and UltraVISTA grism data are used to select the redshift with the smallest error.
-Table~\ref{tbl:redshifts} shows the results of this selection.
+%Table~\ref{tbl:redshifts} shows the results of this selection.
 
@@
 
-\tabletypesize{\scriptsize}
-\begin{deluxetable*}{l|rr|rrr|rr|r|rr}
-\tablecolumns{12}
-\tablewidth{0pc}
-\tablecaption{GZH redshifts by survey\label{tbl:redshifts}} 
-\tabletypesize{\scriptsize}
-\tablehead{
- &   
-\multicolumn{2}{c}{\underline{ACS-GC}} &
-\multicolumn{3}{c}{\underline{3DHST}} &
-\multicolumn{2}{c}{\underline{MUSYC}} &
-\multicolumn{1}{c}{\underline{UltraVISTA}}&
-\multicolumn{2}{c}{\underline{Total}} 
-\\
-\colhead{Survey} & 
-\colhead{spec-z} & 
-\colhead{photo-z} & 
-\colhead{spec-z} & 
-\colhead{grism-z} & 
-\colhead{photo-z} & 
-\colhead{spec-z} & 
-\colhead{photo-z} & 
-\colhead{photo-z} & 
-\colhead{with redshift} &
-\colhead{in survey}
-}
-\small
-\startdata
-%Survey     Gs        Gp    3ds    3dg     3dp       Ms      Mp       UVp       total
-AEGIS    & 3,656  & 2,941  & 12  &  515  &  249    & 0     & 0     &  0      & 7,373  & 8,507\\
-COSMOS   & 7,201  & 77,435 & 35  &  358  &  26     & 0     & 0     &  2,665  & 85,020 & 92,808 \\
-GEMS     & 387    & 628    & 6   &  99   &  40     & 279   & 7,304 & 0       & 8,743  & 9,304\\
-GOODS-N  & 1,947  & 37     & 418 & 1,545 &  1,381  & 0     & 0     & 0       & 5,328  & 12,030 \\
-GOODS-S  & 1,080  & 4      & 327 & 1,348 &  281    & 816   & 1,184 & 0       & 5,040  & 10,284 \\
-SDSS     & 0      & 0      & 0   &  0    &  0      & 0     & 0     & 0       & 37,545 & 51,861  \\
-\hline
-Total    & 14,271 & 81,045 & 798 & 3,865 & 1,977   & 1,095 & 8,488 & 2,665   & 114,204 & 184,794\\
-\enddata
-\end{deluxetable*}
+%\tabletypesize{\scriptsize}
+%\begin{deluxetable*}{l|rr|rrr|rr|r|rr}
+%\tablecolumns{12}
+%\tablewidth{0pc}
+%\tablecaption{GZH redshifts by survey\label{tbl:redshifts}} 
+%\tabletypesize{\scriptsize}
+%\tablehead{
+% &   
+%\multicolumn{2}{c}{\underline{ACS-GC}} &
+%\multicolumn{3}{c}{\underline{3DHST}} &
+%\multicolumn{2}{c}{\underline{MUSYC}} &
+%\multicolumn{1}{c}{\underline{UltraVISTA}}&
+%\multicolumn{2}{c}{\underline{Total}} 
+%\\
+%\colhead{Survey} & 
+%\colhead{spec-z} & 
+%\colhead{photo-z} & 
+%\colhead{spec-z} & 
+%\colhead{grism-z} & 
+%\colhead{photo-z} & 
+%\colhead{spec-z} & 
+%\colhead{photo-z} & 
+%\colhead{photo-z} & 
+%\colhead{with redshift} &
+%\colhead{in survey}
+%}
+%\small
+%\startdata
+%%Survey     Gs        Gp    3ds    3dg     3dp       Ms      Mp       UVp       total
+%AEGIS    & 3,656  & 2,941  & 12  &  515  &  249    & 0     & 0     &  0      & 7,373  & 8,507\\
+%COSMOS   & 7,201  & 77,435 & 35  &  358  &  26     & 0     & 0     &  2,665  & 85,020 & 92,808 \\
+%GEMS     & 387    & 628    & 6   &  99   &  40     & 279   & 7,304 & 0       & 8,743  & 9,304\\
+%GOODS-N  & 1,947  & 37     & 418 & 1,545 &  1,381  & 0     & 0     & 0       & 5,328  & 12,030 \\
+%GOODS-S  & 1,080  & 4      & 327 & 1,348 &  281    & 816   & 1,184 & 0       & 5,040  & 10,284 \\
+%SDSS     & 0      & 0      & 0   &  0    &  0      & 0     & 0     & 0       & 37,545 & 51,861  \\
+%\hline
+%Total    & 14,271 & 81,045 & 798 & 3,865 & 1,977   & 1,095 & 8,488 & 2,665   & 114,204 & 184,794\\
+%\enddata
+%\end{deluxetable*}
 
@@
 \caption{Flowchart of the questions presented to GZH users, labeled with the corresponding Task numbers.
-Tasks in the decision tree are color-coded by tier level: Gray-colored Tasks are 1st tier questions which are asked of all users.
+Tasks in the decision tree are color-coded by tier level: Gray-colored Tasks are 1$^\mathrm{st}$-tier questions which are asked of all users.
 Tasks colored green, blue, purple, and pink (respectively) are one, two, three, or four steps below branching points in the decision tree.}
@@
 Users' votes are weighted slightly \citep[in a method identical to that described in][]{wil13} such that users who frequently disagree with all other users end up having very low weights.
-The user weighting $w$ is 1 for the top 95\% of users as ranked by consistency.
+The user weighting $(w)$ is 1 for the top 95\% of users as ranked by consistency.
 For the bottom 5\% of users, $w$ drops smoothly and is effectively zero for only the bottom 1\% of classifiers in the CDF.
-The overall effect on the GZH dataset is relatively small, but this method is effective at filtering out contributions from random or delibrately malicious classifiers.
+Since this only affects a tiny percentage of the users (and an even smaller percentage of the classifications) the overall effect on the GZH dataset is minimal.
+This method is primarily effective, however, at filtering out contributions from random or delibrately malicious classifiers.
 
@@
 
-\subsection{Selection of FERENGI input galaxies}
+\subsection{Selection of \ferengi{} input galaxies}
 
@@
 %The selection criteria for the different morphological categories is summarized in Table \ref{tbl:morphologies}. 
-The surface brightness selection ($N_\mu = 3$) for the FERENGI galaxies was (1) low: $\mu > 21.5$~\magarc;  (2) mid: $20.5 < \mu < 21.5$~\magarc; and (3) high: $\mu < 20.5$~\magarc.
+The surface brightness selection ($N_\mu = 3$) for the \ferengi{} galaxies was (1) low: $\mu > 21.5$~\magarc;  (2) mid: $20.5 < \mu < 21.5$~\magarc; and (3) high: $\mu < 20.5$~\magarc.
 For each of the four ``target redshifts'' ($z_\mathrm{sim} = 0.3, 0.5, 0.8$ and $1.0$), the images were redshifted in $\Delta z = 0.1$ bins up to $z_\mathrm{sim}=1.0$.
@@
 %\center
-%\caption{Summary of morphological categories selected for FERENGI sample.\label{tbl:morphologies}}
+%\caption{Summary of morphological categories selected for \ferengi{} sample.\label{tbl:morphologies}}
 %\begin{tabular}{lllc}
@@
 \begin{table}
-\caption{Summary of FERENGI artificial redshifting \label{tbl:ferengivalues}}
+\caption{Summary of \ferengi{} artificial redshifting \label{tbl:ferengivalues}}
 \begin{tabular}{lccccr}
@@
 \includegraphics[width=160mm]{figures/example_ferengi.pdf}
-\caption{Examples of two galaxies which have been run through the FERENGI code to produce simulated \hst{} images.
+\caption{Examples of two galaxies which have been run through the \ferengi{} code to produce simulated \hst{} images.
 The measured value of \pfeatures{} from GZH for the images in each panel are (1) Top row: \pfeatures~= (0.900, 0.625, 0.350, 0.350, 0.225) and (2) Bottom row: \pfeatures~= (1.000, 0.875, 0.875, 0.625, 0.375).
@@
 \includegraphics[width=\textwidth]{figures/zeta_examples.pdf}
-\caption{Behavior of the normalized, weighted vote fractions of features visible in a galaxy ($f_\textrm{features}$) as a function of redshift in the artifical \ferengi{} images.
+\caption{Behavior of the normalized, weighted vote fractions of features visible in a galaxy ($f_\textrm{features}$) as a function of redshift in the artificial \ferengi{} images.
 Galaxies in this plot were randomly selected from a distribution with $e=0$ and at least three detectable images in redshift bins of $z\ge0.3$.
@@
 
-GZH uses the values of $\zeta$ for \emph{all} sets of artifically redshifted galaxies to fit the overall distribution as a function of surface brightness, since the correction being applied is expected to vary as a function of the intrinsic galaxy properties.
+GZH uses the values of $\zeta$ for \emph{all} sets of artificially redshifted galaxies to fit the overall distribution as a function of surface brightness, since the correction being applied is expected to vary as a function of the intrinsic galaxy properties.
 The galaxies that can be used to measure the calibration are restricted to those with a non-zero $f_\textrm{features}$ at $z_\mathrm{sim}=0.3$ and with a reasonable fit ($\Delta \chi^2 > 3.0$) to the exponential model for the measured change in \ffeatures.
@@
 \includegraphics[width=0.5\textwidth]{figures/eye_of_sauron.pdf}
-\caption{Surface brightness as a function of redshift for 3,950~\ferengi{} images and the 102,548~galaxies in the ACS sample ith measured $\mu$ and $z$ values.
+\caption{Surface brightness as a function of redshift for 3,950~\ferengi{} images and the 102,548~galaxies in the ACS sample with measured $\mu$ and $z$ values.
 The color histogram shows the number of \ferengi{} images as a function of $\mu$ and $z_{\rm sim}$.
@@
 Images with only a lower-limit on \pfeatures{} have a non single-valued relationship (blue regions).
-NEI images have undetermined relationships due to a lack of data ($N<5$) in their corresponding $z$-$\mu$ bins (gray regions).\label{tbl:ferengi_corrections}}
+NEI (``not enough information'') images have undetermined relationships due to a lack of data ($N<5$) in their corresponding $z$-$\mu$ bins (gray regions).\label{tbl:ferengi_corrections}}
 \begin{tabular}{lrr}
@@
 \label{ssec:higher_order_tasks}
-As with the HST images, each FERENGI subject has a varying number of users answering the various questions in the hierarchical decision tree.
+As with the HST images, each \ferengi{} subject has a varying number of users answering the various questions in the hierarchical decision tree.
 Every user answers the first question, {\it ``Is the galaxy smooth and rounded, with no sign of a disk?''}; as such the vote fractions $p_\mathrm{smooth}, p_{features}$, and $p_\mathrm{artifact}$ are all computed with the minimum statistical error for any question, with roughly 40 total answers (see Section~\ref{sec:interface}).
 The number of users to answer any subsequent question, however, is always equal to or less than the number to answer the preceding question.
-The average number of responses per task for fourth- or fifth-tier questions such as spiral arm structure (Tasks 12--14) is only $4\pm4$ for the FERENGI sample; while this is distribution is strongly bimodal (reflecting the true morphologies of selected galaxies), the very low absolute numbers of votes introduce very high variance when attempting to calculate a statistical correction.
-
-In the FERENGI data, these numbers severely limit the amount of information that can be extracted for the higher-tier questions.
+The average number of responses per task for fourth- or fifth-tier questions such as spiral arm structure (Tasks 12--14) is only $4\pm4$ for the \ferengi{} sample; while this is distribution is strongly bimodal (reflecting the true morphologies of selected galaxies), the very low absolute numbers of votes introduce very high variance when attempting to calculate a statistical correction.
+
+In the \ferengi{} data, these numbers severely limit the amount of information that can be extracted for the higher-tier questions.
 The debiasing technique used (Section~\ref{ssec:zeta}) requires that at least 10~users answer each question for a galaxy with $z_\mathrm{sim}=0.3$ \emph{and} the corresponding image at higher redshift.
@@
 $60\%\pm24\%$ of the galaxies do not have sufficient data to measure a correction, as compared to 2.0\% achieved for Task~01 (Table~\ref{tbl:ferengi_corrections}).
-Of the remaining FERENGI galaxies which did meet this requirement, polynomials were fit to the data in each redshift-surface brightness bin, as was done for Task~01.
+Of the remaining \ferengi{} galaxies which did meet this requirement, polynomials were fit to the data in each redshift-surface brightness bin, as was done for Task~01.
 The goodness-of-fit was evaluated in each bin, for each Task, using a normalized $\chi^2$ metric.
@@
 No Redshift Information            & 4               & 1,134   & 5,088  & 561   & 687    & 102   		& 14,316  & 21,888\\
+\hline
 Total                              &                 & 8,507   & 92,808 & 9,304 & 6,015  & 5,142   	& 51,861  & 173,637\\
@@
 
-%\subsection{Results of FERENGI analysis}
+%\subsection{Results of \ferengi{} analysis}
 %
@@
 %We show here the preliminary results of GZH classifications of images of galaxies placed at artificial redshifts.
-Figure~\ref{fig:ferengi_results_fake} shows the range of change of vote fractions for the change of \pfeatures{} with redshift, for galaxies with different vote fraction levels, three ranges of surface-brightness levels and 7~evolutionary corrections (this last bit is indicated by the colour).
+Figure~\ref{fig:ferengi_results_fake} shows the range of change of vote fractions for the change of \pfeatures{} with redshift, for galaxies with different vote fraction levels, three ranges of surface-brightness levels and 7~evolutionary corrections (this last bit is indicated by the color).
 %
@@
 WARNING NO USER WEIGHTING....
-For a range of vote fraction levels with three surface-brightness levels and 7 evolutionary corrections each (the colours indicate evolutionary correction value with green being $e=0$, we show the range of evolution of the vote fractions for featured vs.
+For a range of vote fraction levels with three surface-brightness levels and 7 evolutionary corrections each (the colors indicate evolutionary correction value with green being $e=0$, we show the range of evolution of the vote fractions for featured vs.
 smooth with redshift.}
@@
 The next two tables have data for a small subset of 3,927~COSMOS~images that were re-processed to study the effect of color balance on morphological classification.
-Table~\ref{tbl:catalog_faded} has images that are desaturated to minimize the color contrast; Table~\ref{tbl:catalog_recoloured} has images with the red and blue color channels inverted.
+Table~\ref{tbl:catalog_faded} has images that are desaturated to minimize the color contrast; Table~\ref{tbl:catalog_recolored} has images with the red and blue color channels inverted.
 Table~\ref{tbl:catalog_goods_shallow} contains data for 6,144~galaxies with 2-epoch images from GOODS.
@@
 \enddata
-\tablenotetext{1}{Flag indicating how the vote fractions for this galaxy were corrected through debiasing (\S\ref{ssec:zeta_results}), if possible.
-0~=~correctable, 1~=~lower-limit ($p_{raw}$ --- $p_{adj}$ is not single-valued), 2~=~uncorrected ($z_{\rm gal} < 0.3$), 3~=~uncorrected (insufficient FERENGI galaxies in this $z$-$\mu$ bin), 4~=~uncorrected (no galaxy redshift available).}
+\tablenotetext{1}{Flag indicating how the vote fractions for this galaxy were corrected through debiasing (Section~\ref{ssec:zeta_results}), if possible.
+0~=~correctable, 1~=~lower-limit ($p_{raw}$ --- $p_{adj}$ is not single-valued), 2~=~uncorrected ($z_{\rm gal} < 0.3$), 3~=~uncorrected (insufficient \ferengi{} galaxies in this $z$-$\mu$ bin), 4~=~uncorrected (no galaxy redshift available).}
 \tablecomments{The full version of this table is available in electronic form, as well as at \url{http://data.galaxyzoo.org}.
@@
 \tablewidth{0pc}
-\tablecaption{GZH morphological classifications for color-inverted Hubble images\label{tbl:catalog_recoloured}} 
+\tablecaption{GZH morphological classifications for color-inverted Hubble images\label{tbl:catalog_recolored}} 
 \tabletypesize{\scriptsize}
@@
 \includegraphics[width=0.90\textwidth]{figures/sankey_both.png}
-\caption{Demographics of the galaxy morphologies in GZH.
+\caption{Demographics of the morphologies for all galaxies in GZH (including both \hst{} and SDSS imaging).
 Each node in each diagram (dark blue horizontal bars of uniform height) represents a task in the tree.
@@
 The full data tables for the catalogs can be accessed in machine-readable form from both the journal and at \url{http://data.galaxyzoo.org}.
+All the code and data tables used to generate this manuscript can be found at \url{https://github.com/willettk/gzhubble}.
 
@@
 
-This project made heavy use of the Astropy packages in Python \citep{ast13}, the \texttt{seaborn} plotting package \citep{was15}, and astroML \citep{van12}.
+This project made heavy use of the Astropy packages in Python \citep{ast13}, the \texttt{seaborn} plotting package \citep{was15}, astroML \citep{van12}, and TOPCAT \citep{tay05,tay11}.
 Modified code from Nick~Wherry and David~Schlegel was used to create the JPG images.
@@
 
-To determine the rate at which the vote fraction for any Task decreases with redshift or surface brightness, data from simluated FERENGI images were modeled with functions in discrete redshift and surface brightness bins (Section~\ref{ssec:zeta_results}).
+To determine the rate at which the vote fraction for any Task decreases with redshift or surface brightness, data from simluated \ferengi{} images were modeled with functions in discrete redshift and surface brightness bins (Section~\ref{ssec:zeta_results}).
 A cut of $N>10$ was placed on the number of votes to reduce the error in the vote fractions and ensure they were well-sampled before applying a fit to the data.
@@
 Figure~\ref{fig:p_vs_p_bar} shows that both the low sample rate and the degree of scatter in each bin inhibit fitting a reliable function that predicts $p_\mathrm{bar,z=0.3}$.
-Table~\ref{tbl:ferengi_bar} summarizes the correction types for the FERENGI data ; 71\% of the galaxies simulated did not meet the GZH requirements for well-sampled vote fractions for $p_\mathrm{bar}$, as compared to 2\% for $p_\mathrm{features}$.
+Table~\ref{tbl:ferengi_bar} summarizes the correction types for the \ferengi{} data; 71\% of the galaxies simulated did not meet the GZH requirements for well-sampled vote fractions for $p_\mathrm{bar}$, as compared to 2\% for $p_\mathrm{features}$.
 Similar results were obtained for all higher-order Tasks in GZH, as described in Section~\ref{ssec:higher_order_tasks}.
@@
 Regions in which there is a single-valued relationship between \pfeatures{} at high redshift and at $z=0.3$ are marked in white; those in which there is not are blue, and those with not enough data ($N<5$) are gray.
-\textbf{The mean normalized $\chi^2$ of 0.08 confirms that these polynomials are not good fits to the data, with no correction derived.} [b]: A larger version of the dark-outlined square in [a], containing \ferengi{} galaxies artificially redshifted to $z=1.0$ and have surface brightnesses between $20.3 < \mu < 21.0$ $\rm (mag/arcsec^2)$.
+The mean normalized $\chi^2$ of the change in vote fraction is 0.08.
+None of the correlations for higher-order tasks (including bars) were applied to galaxies in the GZH catalog.
+[b]: A larger version of the dark-outlined square in [a], containing \ferengi{} galaxies artificially redshifted to $z=1.0$ and have surface brightnesses between $20.3 < \mu < 21.0$ $\rm (mag/arcsec^2)$.
 [c]: The same data as [a].
@@
 NEI images had undetermined relationships due to a lack of data ($N<5$) in their corresponding $z$-$\mu$ bins (gray regions).
-Only 17\% (maximum) of FERENGI galaxies in the sample were considered ``correctable'', which is not sufficient to compute a $\zeta$ function applicable to the Hubble data.
+Only 17\% (maximum) of \ferengi{} galaxies in the sample were considered ``correctable'', which is not sufficient to compute a $\zeta$ function applicable to the Hubble data.
 \label{tbl:ferengi_bar_corrections}}

### 2016-05-07 writeup/gz_hubble_data.tex
Text on interface and classification stats

@@
 
+\subsection{User weighting}\label{ssec:weighting}
+The votes of individual users who classified galaxies in GZH are combined to make a vote fraction for each question on the classification tree.
+Users' votes are weighted slightly \citep[in a method identical to that described in][]{wil13} such that users who frequently disagree with all other users end up having very low weights.
+The user weighting $(w)$ is 1 for the top 95\% of users as ranked by consistency.
+For the bottom 5\% of users, $w$ drops smoothly and is effectively zero for only the bottom 1\% of classifiers in the CDF.
+Since this only affects a tiny percentage of the users (and an even smaller percentage of the classifications) the overall effect on the GZH dataset is minimal.
+This method is primarily effective, however, at filtering out contributions from random or delibrately malicious classifiers.
+
+Classifications for a particular user are aggregated and weighted only if they were logged into GZH under their username (which is encouraged by not required for participation).
+Classifications by users not logged in are marked as ``Anonymous''; no weighting is applied to these classifications, but they are otherwise treated identically in the data processing.
+
+\subsection{Interface and decision tree}\label{ssec:interface}
+
+\begin{figure*}
+\center
+\includegraphics[width=160mm]{figures/gzh_interface.png}
+\caption{Screenshot of the Galaxy Zoo: Hubble interface (\url{http:/zoo3.galaxyzoo.org}) at the beginning of a classification, with the user ready to select an answer for the first question in the decision tree.\label{fig:interface}}
+\end{figure*}
+
+Classifications for GZH are made using a web-based interface (Figure~\ref{fig:interface}), similar in design to Galaxy~Zoo and Galaxy~Zoo~2.
+The front-end runs on a Ruby~on~Rails framework with classifications stored in a MySQL backend.
+Users are shown a randomly-selected color composite image from the GZH sample; the default shows the image with a black sky background, although users have the options to invert the color palette if desired.
+The questions and responses for morphology appear on the right side of the image as a panel, including both text and icons.
+There is no tutorial required for participation, although users can access an extensive ``Help'' section containing example images and descriptive text for all the morphological labels.
+
 \begin{figure*}
@@
 
-\subsection{User weighting}\label{ssec:weighting}
-The votes of individual users who classified galaxies in GZH are combined to make a vote fraction for each question on the classification tree.
-Users' votes are weighted slightly \citep[in a method identical to that described in][]{wil13} such that users who frequently disagree with all other users end up having very low weights.
-The user weighting $(w)$ is 1 for the top 95\% of users as ranked by consistency.
-For the bottom 5\% of users, $w$ drops smoothly and is effectively zero for only the bottom 1\% of classifiers in the CDF.
-Since this only affects a tiny percentage of the users (and an even smaller percentage of the classifications) the overall effect on the GZH dataset is minimal.
-This method is primarily effective, however, at filtering out contributions from random or delibrately malicious classifiers.
-
-\subsection{Interface and decision tree}\label{ssec:interface}
-
-{\note Describe the GZ interface and the hierarchical decision tree.}
-
-\begin{figure*}
+The procedure for classifying an image in GZH follows a hierarchical decision tree (Figure~\ref{fig:decisiontree}).
+Every classification begins with the user identifying whether the object at the center of the image is a smooth galaxy, a galaxy with a disk or other features, or a star/artifact.
+Subsequent questions in the tree depend on the previous answer(s) given by the user; the structure of the decision tree is designed so that the user will answer every question relevant to the morphology that they have identified.
+Questions that are not answered are implicitly assumed to be absent in the image --- for example, if the user identifies a galaxy as being smooth, they are not asked to count the number of spiral arms.
+For every task, the user chooses a single answer before continuing to the next question; they have also the option to restart a classification in-progress if a mistake has been made.
+
+The GZH decision tree has four broad sets of morphologies classified by the users.
+The first option is designating the object as a star or artifact (the result of either bad data or incorrect classification by the ACS pipeline as a galaxy); in this case, the classification ends and no further questions are asked.
+The second set are smooth galaxies, intended to identify ellipticals/early-types; users also measure the relative axial ratio (roundness) for these galaxies.
+The third set is for disk/late-type galaxies, which measures the features necessary to place a galaxy on the standard Hubble tuning fork (bars, spiral arm, strength of the central bulge).
+The final set, which is new to the high-redshift targets in GZH, asks users to identify objects dominated by clumpy morphologies.
+Further annotation for these galaxies includes assessing the number, arrangement, relative brightness, and location of the clumps within the galaxy.
+Finally, every classification of a galaxy gives users the option of annotating ``odd'' features within the image; these labels are typically rare in large surveys, including dust lanes, gravitational lenses, and major mergers.
+
+The number of independent classifications per subject collected by GZH is on average higher than GZ1 or GZ2, due to both the increased complexity of the decision tree and the relative difficulty of classifying images of small and distant galaxies.
+Images from the main AEGIS, GEMS, and GOODS data sets have a median of 122~independent classifications per image.
+The remainder of the images were set slightly lower, either from having a later activation date (COSMOS, simulated AGN) or by setting a lower retirement rate (the low-redshift SDSS Stripe~82 galaxies).
+Images from these samples have a median of 46-48~classifications per image (Figure~\ref{fig:classification_hist}).
+
+\begin{figure}
 \center
-\includegraphics[width=160mm]{figures/gzh_interface.png}
-\caption{Screenshot of the Galaxy Zoo: Hubble interface at the beginning of a classification, with the user ready to select an answer for the first question in the decision tree.\label{fig:interface}}
-\end{figure*}
+\includegraphics[width=0.5\textwidth]{figures/classification_hist.pdf}
+\caption{Distribution of the total number of classifications per image for GZH, split by the survey types.}
+\label{fig:classification_hist}
+\end{figure}
+
+The GZH project was launched on 23~Apr~2010 with the inclusion of the AEGIS, GEMS, GOODS 2-epoch, and SDSS Stripe~82 images.
+Images from COSMOS and the simulated AGN were activated in Dec 2010, as well as a small sample of AEGIS/GEMS/GOODS images mistakenly excluded from the original sample based on an overly restrictive cut on blended and/or saturated objects.
+The main site operated until the launch of the Galaxy~Zoo:~CANDELS project on 10~Sep~2012.
+Classifications for the GOODS 5-epoch images were obtained with the fourth version of the site\footnote{\url{http://www.galaxyzoo.org}} from Mar-Jun 2015.
+The GZH project had a total of 10,349,357~classifications from 93,898 registered participants.
+% Sum is the total of the GZH SQL table plus the GOODS full-depth imaging in GZ4.
 
@@
 The goodness-of-fit was evaluated in each bin, for each Task, using a normalized $\chi^2$ metric.
-The mean $\chi^2$ for all higher-order tasks was $0.10\pm0.04$, significantly larger than the Task 01 value of $0.04$.
+The mean $\chi^2$ for all higher-order tasks was $0.10\pm0.04$, significantly larger than the Task~01 value of $0.04$.
 Based on this statistic, the data cannot not be modeled with sufficient confidence for the higher order tasks.
@@
 With this structure, questions shown to a user are dependent on their answers to the previous questions.
-For example, a user is only asked Task 11, {\it ``How many spiral arms?''} if they had answered ``yes'' to Task 10, which asks whether any spiral arms are present.
+For example, a user is only asked Task~11, {\it ``How many spiral arms?''} if they had answered ``yes'' to Task~10, which asks whether any spiral arms are present.
 This structure is used to reduce the workload of the users by only asking questions relevant to the particular galaxy; in this example, it would not be useful, nor would it make physical sense, to ask a user how many spiral arms in a galaxy which they had declared had no spiral arms to begin with.
@@
 The colors represent the tier level of Tasks, which indicate the number of previous Tasks the given Task is dependent upon.
-The arm-number question, Task 11, is a 5th tier Task, meaning that whether this question is seen by a user is dependent on four Tasks preceding it.
-In this case, it is only shown to volunteers who voted the galaxy was featured/disk-shaped in Task 01, not clumpy in Task 12, not edge-on in Task 02, and had spiral structure in Task 10.
+The arm-number question, Task~11, is a 5$^\mathrm{th}$-tier Task, meaning that whether this question is seen by a user is dependent on four Tasks preceding it.
+In this case, it is only shown to volunteers who voted the galaxy was featured/disk-shaped in Task~01, not clumpy in Task~12, not edge-on in Task~02, and had spiral structure in Task~10.
 
@@
 
-Tasks 03, 04 and 05 have an additional possible pathway; as shown in Figure~\ref{fig:decisiontree}, a user might also be shown this question if they select ``featured/disk'' in Task 01, ``clumpy'' in Task 12, two or more clumps in Task 16, and ``spiral arrangement'' in Task 15.
+Tasks 03, 04 and 05 have an additional possible pathway; as shown in Figure~\ref{fig:decisiontree}, a user might also be shown this question if they select ``featured/disk'' in Task~01, ``clumpy'' in Task~12, two or more clumps in Task~16, and ``spiral arrangement'' in Task~15.
 After applying the appropriate thresholds for this path, $< 0.5\%$ of the galaxies which have $\ge 20$ answers to these questions used this pathway to arrive at these Tasks.
@@
 
-For galaxies identified as ``clumpy'' in GZH, the number of clumps can be determined using Task 16.
-Table~\ref{tbl:thresholds} can be used to select 8,444 galaxies measured as ``clumpy'' using $p_{\rm features} > 0.23$ and $p_{\rm clumpy,yes}>0.80$ to ensure the vote fractions for Task 16 are well-sampled.
+For galaxies identified as ``clumpy'' in GZH, the number of clumps can be determined using Task~16.
+Table~\ref{tbl:thresholds} can be used to select 8,444 galaxies measured as ``clumpy'' using $p_{\rm features} > 0.23$ and $p_{\rm clumpy,yes}>0.80$ to ensure the vote fractions for Task~16 are well-sampled.
 The clump number can be reasonably identified for 1,112 of the clumpy galaxies; for the remainder, the unique clumps were less distinguishable from each other and the exact number of clumps could not be deduced without careful visual inspection.

### 2016-05-07 writeup/gz_hubble_data.tex
Acknowledge SankeyMatic

@@
 
-\subsection{Selection of \ferengi{} input galaxies}
+\subsection{Generating images of artifically-redshifted galaxies}
 
@@
 
-\subsection{Results of $\zeta$ approach}\label{ssec:zeta_results}
+\subsection{Effects of morphological debiasing}\label{ssec:zeta_results}
 
@@
 
-\section{The GZH catalog}\label{sec:results}
+\section{The Galaxy Zoo: Hubble catalog}\label{sec:results}
 
@@
 
-\subsection{Example 1: Selecting bars}
+\subsection{Example 1: Selecting barred galaxies}
 
@@
 This paper presents the catalog release for the Galaxy Zoo: Hubble project, which uses crowdsourced visual classifications to measure galaxy morphologies.
-The first two phases of Galaxy Zoo \citep{lin11,wil13} used images of low-redshift galaxies from SDSS; this is the first phase of the project with space-based images of high-redshift targets (in addition to the Galaxy Zoo: CANDELS collaboration; Simmons et al., submitted).
+The first two phases of Galaxy Zoo \citep{lin11,wil13} used images of low-redshift galaxies from SDSS; this is the first result of the project with space-based images of high-redshift targets (in addition to the Galaxy Zoo: CANDELS collaboration; Simmons et al., submitted).
 The final sample includes classifications for 181,101~images generated from 150,771~unique galaxies.
@@
 To calibrate this \emph{without} potentially overcorrecting for the genuine morphological evolution of galaxies over cosmic time, the GZH project uses SDSS images of low-redshift galaxies, processes them to appear as if they were at higher redshift, and classifies them through the GZH interface in an identical fashion.
-The resulting change in \pfeatures{} as a function of $z$,$\mu$ is applied as a multiplicative correction to the top-level vote fractions for $\sim50\%$ of the GZH galaxies.
+The resulting change in \pfeatures{} as a function of $z$ and $\mu$ is applied as a multiplicative correction to the top-level vote fractions for $\sim50\%$ of the GZH galaxies.
 
@@
 Modified code from Nick~Wherry and David~Schlegel was used to create the JPG images.
+Figure~\ref{fig:sankey} was generated with \url{http://sankeymatic.com/}.
 

### 2016-05-08 writeup/gz_hubble_data.tex
Overall demographic distribution

@@
 %% 
-%% There are other optional arguments one can envoke to allow other 
+%% There are other optional arguments one can invoke to allow other 
 %% actions. 
@@
 
-{\note Summarize the broad trends that are seen regarding the fraction of galaxies with various morphologies, how that relates to color, size, etc.
-Briefly discuss results as compared with literature and theory.}
+Any analysis of the morphological distribution of galaxies must properly consider morphology with respect to other physical properties of the sample, such as color, mass, size, environment, and redshift.
+We defer such analyses to later papers, and comment here only on a few broad characteristics of the overall GZH sample.
+
+Figure~\ref{fig:sankey} shows the breakdown of morphologies for the combined surveys in GZH as a Sankey~diagram, where each node represents a task and the flows between the nodes represent the possible responses.
+The width of the flows is proportional to the number of galaxies associated with that response; Figure~\ref{fig:sankey} uses a simple plurality vote to assign the combined set of labels for each galaxy.
+This method is likely to undersample some of the categories; visual inspection of images suggests that $p_\mathrm{features}\gtrsim0.3$ identifies disk-dominated or irregular galaxies reliably, for example.
+This method also does not use the suggested thresholds in Table~\ref{tbl:thresholds}.
 
@@
 
+Given these caveats, the overall distribution of galaxy types is significantly different than the low-redshift sample classified in SDSS imaging from GZ1 and GZ2.
+\citet{lin11} found that elliptical galaxies exceeded spiral galaxies by a factor of $\sim2:1$ in the main spectroscopic sample if using a plurality vote criterion (although \citealt{bam09} show that this strongly depends on the selection method; spirals are the dominant population in a volume-limited sample at $z<0.088$, for example).
+The weighted votes for GZH have smooth galaxies outnumbering disks and clumpy galaxies by a factor of $\sim3:1$, however.
+The fraction of objects identified as stars or artifact is also much higher in the Hubble imaging; by plurality votes, these encompass only $\sim0.1\%$ of images in SDSS \citep{wil13}, but 6\% of images in GZH.
+
+Within the sample of galaxies identified as ``not smooth'', it is clear that the addition of the clumpy branch is necessary to describe a large fraction of the sample; disk-dominated galaxies outnumber clumpy morphologies by less than a factor of 2.
+Disk galaxies are primarily unbarred \citet{mel14} and possessing two visible spiral arms over a flat distribution of pitch angles and bulge prominences.
+Clumpy galaxies are identified across the full range of clump multiplicities, with the exception of 1-clump galaxies (which would be difficult to differentiate from compact spheroids).
+Roughly half of the galaxies have at least 1~clump identified as the brightest; the clumps are most commonly asymmetrically arranged in clusters and are not often seen embedded in larger structures.
+
 \subsection{Comparing GZH morphologies to other catalogs}\label{ssec:comparisons}
@@
 While detailed analysis is left to a further paper, we note that there is no strong change in the proportion of galaxies when binning by redshift intervals of $\Delta z=0.2$ out to $z=1.0$.
+
+Finally, we note that there are 7,681~galaxies in the GOODS-S field with morphological classifications in both GZH and the Galaxy~Zoo:~CANDELS project (Simmons et~al., submitted).
+Since both the sensitivity and filters for the two sets of images differ (and there is no debiased correction applied to GZC), there is no prior reason to expect a perfect correlation between the separate vote fractions for the projects.
+Briefly, we note that the \pfeatures{} value for GZH is on average higher than GZC; the effect is strongest at $p_\mathrm{features,GZC}<0.3$, for which roughly half the galaxies have $p_\mathrm{features,GZH}>0.5$.
+However, the correlation between vote fractions is single-valued (although not linear, with a Pearson correlation coefficient of $r=0.6$), and should be possible to calibrate using a similar approach to that described in Section~\ref{sec:debiasing}; the correlation between other tasks, such as edge-on galaxies is significantly stronger ($r=0.9$).
+So while the raw vote fractions are not directly comparable, the initial analysis indicates that the broad morphologies are at least consistent.
 

### 2016-05-08 writeup/gz_hubble_data.tex
Text and Fig 10 fixes for #66.

@@
 \subsection{User weighting}\label{ssec:weighting}
-The votes of individual users who classified galaxies in GZH are combined to make a vote fraction for each question on the classification tree.
+The votes of individual users who classified galaxies in GZH are combined to make a vote fraction for each response to a question ($f_{response}$) on the classification tree.
 Users' votes are weighted slightly \citep[in a method identical to that described in][]{wil13} such that users who frequently disagree with all other users end up having very low weights.
@@
 Since this only affects a tiny percentage of the users (and an even smaller percentage of the classifications) the overall effect on the GZH dataset is minimal.
-This method is primarily effective, however, at filtering out contributions from random or delibrately malicious classifiers.
+This method is effective, however, at filtering out contributions from random or delibrately malicious classifiers.
 
@@
 Further annotation for these galaxies includes assessing the number, arrangement, relative brightness, and location of the clumps within the galaxy.
-Finally, every classification of a galaxy gives users the option of annotating ``odd'' features within the image; these labels are typically rare in large surveys, including dust lanes, gravitational lenses, and major mergers.
+Finally, every classification of a galaxy gives users the option of annotating ``odd'' features within the image; these labels are for relatively rare $(\lesssim1\%)$ phenomena, including dust lanes, gravitational lenses, and major mergers.
 
@@
 Images from the main AEGIS, GEMS, and GOODS data sets have a median of 122~independent classifications per image.
-The remainder of the images were set slightly lower, either from having a later activation date (COSMOS, simulated AGN) or by setting a lower retirement rate (the low-redshift SDSS Stripe~82 galaxies).
+The remainder of the images either had a later activation date (COSMOS, simulated AGN) or by a lower retirement limit (the low-redshift SDSS Stripe~82 galaxies).
 Images from these samples have a median of 46-48~classifications per image (Figure~\ref{fig:classification_hist}).
@@
 %\hline
-%Features            & Yes       & $p_{\rm features} > 0.8$, $p_{\rm odd} < 0.1$                                                         & 12 \\ 
-%                    & Int.      & $0.3 < p_{\rm smooth} < 0.6$, $p_{\rm odd} < 0.1$                                                     & 12 \\ 
-%                    & No        & $p_{\rm smooth} > 0.8$, $p_{\rm odd} < 0.1$                                                           & 12 \\ 
-%Merger              & No        & $p_{\rm features} > 0.8$, $p_{\rm odd < 0.1}$, $p_{\rm merger} < 0.1$                                 & 12 \\
-%                    & Int.      & $p_{\rm odd} > 0.5$, $0.1< p_{\rm merger} < 0.4$                                                      & 12 \\ 
-%                    & Yes       & $p_{\rm odd} > 0.5$, $p_{\rm merger} > 0.4$                                                           & 12 \\
-%Edge-on             & Yes       & $p_{\rm edgeon} > 0.8$, $p_{\rm features} > 0.5$                                                      & 12 \\
-%                    & Int.      & $0.4 < p_{\rm edgeon} < 0.8$ , $p_{\rm features} > 0.5$                                               & 12 \\
-%                    & No        & $p_{\rm edgeon} < 0.2$, $p_{\rm features} > 0.5$                                                      & 12 \\
-%Bar                 & No        & $p_{\rm bar} < 0.1$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                                 & 24 \\
-%                    & Int.      & $0.2 < p_{\rm bar} < 0.4$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                           & 24 \\
-%                    & Yes       & $p_{\rm bar} > 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                                 & 24 \\
-%Visible spiral      & No        & $p_{\rm spiral} < 0.2$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$         & 12 \\
-%                    & Int.      & $0.2 < p_{\rm spiral} < 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$   & 12 \\
-%                    & Yes       & $p_{\rm spiral} > 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$         & 12 \\
-%Oblique bulge size  & No        & $p_{\rm nobulge>0.6}$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$          & 12 \\
-%                    & Int.      & $p_{\rm justnoticeable}>0.6$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$   & 12 \\
-%                    & Yes       & $p_{\rm obvious|dominant}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$ & 12 \\
-%Edge-on bulge shape & Round     & $p_{\rm rounded}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.5$                               & 12 \\
-%                    & Boxy      & $p_{\rm boxy}>0.4$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.2$                                  & 12 \\
-%                    & No bulge  & $p_{\rm nobulge}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.5$                               & 12 \\
+%Features            & Yes       & $f_{\rm features} > 0.8$, $f_{\rm odd} < 0.1$                                                         & 12 \\ 
+%                    & Int.      & $0.3 < f_{\rm smooth} < 0.6$, $f_{\rm odd} < 0.1$                                                     & 12 \\ 
+%                    & No        & $f_{\rm smooth} > 0.8$, $f_{\rm odd} < 0.1$                                                           & 12 \\ 
+%Merger              & No        & $f_{\rm features} > 0.8$, $f_{\rm odd < 0.1}$, $f_{\rm merger} < 0.1$                                 & 12 \\
+%                    & Int.      & $f_{\rm odd} > 0.5$, $0.1< f_{\rm merger} < 0.4$                                                      & 12 \\ 
+%                    & Yes       & $f_{\rm odd} > 0.5$, $f_{\rm merger} > 0.4$                                                           & 12 \\
+%Edge-on             & Yes       & $f_{\rm edgeon} > 0.8$, $f_{\rm features} > 0.5$                                                      & 12 \\
+%                    & Int.      & $0.4 < f_{\rm edgeon} < 0.8$ , $f_{\rm features} > 0.5$                                               & 12 \\
+%                    & No        & $f_{\rm edgeon} < 0.2$, $f_{\rm features} > 0.5$                                                      & 12 \\
+%Bar                 & No        & $f_{\rm bar} < 0.1$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$                                 & 24 \\
+%                    & Int.      & $0.2 < f_{\rm bar} < 0.4$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$                           & 24 \\
+%                    & Yes       & $f_{\rm bar} > 0.8$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$                                 & 24 \\
+%Visible spiral      & No        & $f_{\rm spiral} < 0.2$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$, $f_{\rm bar} < 0.1$         & 12 \\
+%                    & Int.      & $0.2 < f_{\rm spiral} < 0.8$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$, $f_{\rm bar} < 0.1$   & 12 \\
+%                    & Yes       & $f_{\rm spiral} > 0.8$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$, $f_{\rm bar} < 0.1$         & 12 \\
+%Oblique bulge size  & No        & $f_{\rm nobulge>0.6}$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.5$, $f_{\rm bar} < 0.2$          & 12 \\
+%                    & Int.      & $f_{\rm justnoticeable}>0.6$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.5$, $f_{\rm bar} < 0.2$   & 12 \\
+%                    & Yes       & $f_{\rm obvious|dominant}>0.5$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.5$, $f_{\rm bar} < 0.2$ & 12 \\
+%Edge-on bulge shape & Round     & $f_{\rm rounded}>0.5$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} > 0.5$                               & 12 \\
+%                    & Boxy      & $f_{\rm boxy}>0.4$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} > 0.2$                                  & 12 \\
+%                    & No bulge  & $f_{\rm nobulge}>0.5$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} > 0.5$                               & 12 \\
 %\hline\hline
@@
 \caption{Examples of two galaxies which have been run through the \ferengi{} code to produce simulated \hst{} images.
-The measured value of \pfeatures{} from GZH for the images in each panel are (1) Top row: \pfeatures~= (0.900, 0.625, 0.350, 0.350, 0.225) and (2) Bottom row: \pfeatures~= (1.000, 0.875, 0.875, 0.625, 0.375).
+The measured value of \ffeatures{} from GZH for the images in each panel are (1) Top row: \ffeatures~= (0.900, 0.625, 0.350, 0.350, 0.225) and (2) Bottom row: \ffeatures~= (1.000, 0.875, 0.875, 0.625, 0.375).
 \label{fig:exampleFERENGI}}
@@
 [a]: Each point in a given redshift and surface brightness bin represents a unique galaxy.
-On the $y$-axis in each bin is the \pfeatures{} value of the image of that galaxy redshifted to the value corresponding to that redshift bin.
-On the $x$-axis is the \pfeatures{} value of the image of the same galaxy redshifted to $z=0.3$.
+On the $y$-axis in each bin is the \ffeatures{} value of the image of that galaxy redshifted to the value corresponding to that redshift bin.
+On the $x$-axis is the \ffeatures{} value of the image of the same galaxy redshifted to $z=0.3$.
 The dashed black lines represent the best-fit polynomials to the data in each square.
-The solid black line represents \pfeaturesz=\pfeaturesrest.
-Regions in which there is a single-valued relationship between \pfeatures{} at high redshift and at $z=0.3$ are white; those in which there is not are blue, and those with not enough data ($N<5$) are gray.
+The solid black line represents \ffeaturesz=\ffeaturesrest.
+Regions in which there is a single-valued relationship between \ffeatures{} at high redshift and at $z=0.3$ are white; those in which there is not are blue, and those with not enough data ($N<5$) are gray.
 [b]: A larger version of the dark-outlined square in [a], containing \ferengi{} galaxies that have been artificially redshifted to $z=1.0$ and have surface brightnesses between $20.3 < \mu < 21.0$ $\rm (mag/arcsec^2)$.
 [c]: The same data as [a] is shown.
-Each $z,\mu$ bin is divided into 4 sub-bins to determine the range of intrinsic \pfeaturesrest{} for a given range of observed \pfeaturesz{} values.
+Each $z,\mu$ bin is divided into 4 sub-bins to determine the range of intrinsic \ffeaturesrest{} for a given range of observed \ffeaturesz{} values.
 In each sub-bin, the orange bars represent the inner 80$^\mathrm{th}$ percentiles of the data, the boundaries of which are the lower and upper limits of the debiased values.
 [d]: The same data as [b], but highlighting the upper and lower limit regions.}
-\label{fig:p_vs_p}
+\label{fig:f_vs_f}
 \end{figure*}
 
-Figure~\ref{fig:p_vs_p} shows the change in \pfeatures{} for the \ferengi{} galaxies relative to their lowest simulated redshift.
+Figure~\ref{fig:f_vs_f} shows the change in \ffeatures{} for the \ferengi{} galaxies relative to their lowest simulated redshift.
 In this analysis, only galaxies whose lowest simulated redshift image was $z_\mathrm{sim}=0.3$ were used (see Table \ref{tbl:ferengivalues}), and only those which had detectable surface brightness measurements in \sextractor; this includes 3,950 of the total 6,466 images.
-For each simulated redshift value $z$, and at a fixed surface brightness $\mu$, \pfeaturesz, the value measured at that simulated redshift, is plotted against \pfeaturesrest, the value measured for the same galaxy imaged at $z=0.3$.
-
-The objective is to use these data to predict, for a galaxy with a measured \pfeaturesz{} value, what its \pfeatures{} value \emph{would have been} if it had been viewed at $z=0.3$.
-This predicted value is defined as the debiased vote fraction \pfeaturesdebiased, and is calculated by applying a correction to the measured value of \pfeatures, determined by the $\zeta$ function described in the previous section.
-A reliable predicted value can be obtained so long as the relationship between \pfeaturesz{} and \pfeaturesrest{} is single-valued; that is, for a given \pfeaturesz, there is exactly one corresponding value of \pfeatures{} at $z=0.3$.
-
-Figure~\ref{fig:p_vs_p} shows that the relationship between \pfeaturesz{} and \pfeaturesrest{} is \emph{not} always single valued; hence, it is not appropriate to correct galaxies that lie in certain regions of surface brightness/redshift/\pfeatures{} space.
-These regions tend to have low \pfeatures{} values at high redshift, but a wide range of values at $z=0.3$.
-These regions contain two morphological types of galaxies: the first set are genuine ellipticals, which have low values of \pfeatures{} at both high and low redshift.
-The second group are disks whose features become indistinct at high redshift; hence their \pfeatures{} value at $z=0.3$ may be quite high, while the value observed at high redshift is very low.
+For each simulated redshift value $z$, and at a fixed surface brightness $\mu$, \ffeaturesz, the value measured at that simulated redshift, is plotted against \ffeaturesrest, the value measured for the same galaxy imaged at $z=0.3$.
+
+The objective is to use these data to predict, for a galaxy with a measured \ffeaturesz{} value, what its \ffeatures{} value \emph{would have been} if it had been viewed at $z=0.3$.
+This predicted value is defined as the debiased vote fraction \ffeaturesdebiased, and is calculated by applying a correction to the measured value of \ffeatures, determined by the $\zeta$ function described in the previous section.
+A reliable predicted value can be obtained so long as the relationship between \ffeaturesz{} and \ffeaturesrest{} is single-valued; that is, for a given \ffeaturesz, there is exactly one corresponding value of \ffeatures{} at $z=0.3$.
+
+Figure~\ref{fig:f_vs_f} shows that the relationship between \ffeaturesz{} and \ffeaturesrest{} is \emph{not} always single valued; hence, it is not appropriate to correct galaxies that lie in certain regions of surface brightness/redshift/\ffeatures{} space.
+These regions tend to have low \ffeatures{} values at high redshift, but a wide range of values at $z=0.3$.
+These regions contain two morphological types of galaxies: the first set are genuine ellipticals, which have low values of \ffeatures{} at both high and low redshift.
+The second group are disks whose features become indistinct at high redshift; hence their \ffeatures{} value at $z=0.3$ may be quite high, while the value observed at high redshift is very low.
 This effect is strongest at high $z$ and low $\mu$, where features become nearly impossible to discern in the images.
 
-The criteria for determining whether a region of this space is single-valued, and therefore correctable, is as follows: In each surface brightness and redshift bin, the relationship between \pfeaturesz{} and \pfeaturesrest{} is modeled by fitting the data with a polynomial of degrees $n=3$, 2, and 1, and using the best fit out of the three.
+The criteria for determining whether a region of this space is single-valued, and therefore correctable, is as follows: In each surface brightness and redshift bin, the relationship between \ffeaturesz{} and \ffeaturesrest{} is modeled by fitting the data with a polynomial of degrees $n=3$, 2, and 1, and using the best fit out of the three.
 These fits are shown as the dashed black lines in Figure~\ref{fig:6a}.
-Any flat regions of the polynomial fits are areas in which there is not a clear single-valued relationship between \pfeaturesz{} and \pfeaturesrest; this is quantified by setting a minimum slope cut of 0.4.
-Any data in which the polynomial fit has a slope less than this value is considered \emph{not} one-to-one, and therefore \pfeaturesz{} cannot be boosted to its \pfeaturesrest{} value.
+Any flat regions of the polynomial fits are areas in which there is not a clear single-valued relationship between \ffeaturesz{} and \ffeaturesrest; this is quantified by setting a minimum slope cut of 0.4.
+Any data in which the polynomial fit has a slope less than this value is considered \emph{not} one-to-one, and therefore \ffeaturesz{} cannot be boosted to its \ffeaturesrest{} value.
 Galaxies in this region are referred to as the \emph{lower limit} sample.
@@
 Uncolored (white) regions of the plot have sufficiently high slopes to consider the relationship as single-valued; galaxies in these regions are considered ``correctable'', and only these are used in measuring the parameters for the $\zeta$ function (Section~\ref{ssec:zeta}).
-Only surface brightness/redshift bins with at least 5 galaxies were considered; regions with fewer than 5 galaxies are considered to have ``not enough information'' to determine the \pfeaturesz{} and \pfeaturesrest{} relationship, colored gray in Figure~\ref{fig:6a}.
-
-The unshaded regions in Figure~\ref{fig:6a} define discrete ranges of redshift, surface brightness, and \pfeatures{} a galaxy must have in order for the debiased correction to be confidentely applied to a galaxy in the GZH sample.
-While the appropriate correctable regions were defined discretely, the true correctable region is assumed to be a smooth function of $z$, $\mu$, and \pfeatures{}.
-To define this smooth space, a convex hull is generated that encloses the correctable and lower-limit \ferengi{} galaxies in $z$-$\mu$-\pfeatures{} space.
+Only surface brightness/redshift bins with at least 5 galaxies were considered; regions with fewer than 5 galaxies are considered to have ``not enough information'' to determine the \ffeaturesz{} and \ffeaturesrest{} relationship, colored gray in Figure~\ref{fig:6a}.
+
+The unshaded regions in Figure~\ref{fig:6a} define discrete ranges of redshift, surface brightness, and \ffeatures{} a galaxy must have in order for the debiased correction to be confidentely applied to a galaxy in the GZH sample.
+While the appropriate correctable regions were defined discretely, the true correctable region is assumed to be a smooth function of $z$, $\mu$, and \ffeatures{}.
+To define this smooth space, a convex hull is generated that encloses the correctable and lower-limit \ferengi{} galaxies in $z$-$\mu$-\ffeatures{} space.
 The boundaries are then adjusted until the contamination from both groups is minimized.
@@
 
-For the ``lower-limit'' galaxies for which a single debiased \pfeatures{} value cannot be confidently assigned, the \emph{range} of debiased values is estimated using a method visualized in Figure~\ref{fig:6c}.
-This uses the \ferengi{} simulated data to analyze the range of intrinsic \pfeaturesrest{} values for any given observed \pfeatures{} value, again as a function of surface brightness and redshift.
-Each $z$,$\mu$ bin, shows the spread of intrinsic values of \pfeaturesrest{} for four ranges of observed \pfeatures.
+For the ``lower-limit'' galaxies for which a single debiased \ffeatures{} value cannot be confidently assigned, the \emph{range} of debiased values is estimated using a method visualized in Figure~\ref{fig:6c}.
+This uses the \ferengi{} simulated data to analyze the range of intrinsic \ffeaturesrest{} values for any given observed \ffeatures{} value, again as a function of surface brightness and redshift.
+Each $z$,$\mu$ bin, shows the spread of intrinsic values of \ffeaturesrest{} for four ranges of observed \ffeatures.
 The range of intrinsic values is defined as the inner 80\% of the data, represented by the orange bars in Figure~\ref{fig:6c}.
-For any galaxy which cannot be directly debiased by the $\zeta$ method, these ranges are used to denote the upper and lower limits on the expected values \pfeaturesrest{} as a function of the observed \pfeatures.
+For any galaxy which cannot be directly debiased by the $\zeta$ method, these ranges are used to denote the upper and lower limits on the expected values \ffeaturesrest{} as a function of the observed \ffeatures.
 
@@
 \center
-\caption{Distribution of \ferengi{} images analysed in Figure~\ref{fig:p_vs_p}.
-Correctable images have a single-valued relationship between their measured \pfeatures{} values at high and low redshifts (white regions in Figure~\ref{fig:p_vs_p}).
-Images with only a lower-limit on \pfeatures{} have a non single-valued relationship (blue regions).
+\caption{Distribution of \ferengi{} images analysed in Figure~\ref{fig:f_vs_f}.
+Correctable images have a single-valued relationship between their measured \ffeatures{} values at high and low redshifts (white regions in Figure~\ref{fig:f_vs_f}).
+Images with only a lower-limit on \ffeatures{} have a non single-valued relationship (blue regions).
 NEI (``not enough information'') images have undetermined relationships due to a lack of data ($N<5$) in their corresponding $z$-$\mu$ bins (gray regions).\label{tbl:ferengi_corrections}}
@@
 \includegraphics[width=\textwidth]{figures/debiased_corrections.pdf}
-\caption{Debiased $p_{features}$ corrected to $z=0.3$ vs weighted $p_{features}$ for the correctable (left), lower-limit (middle), and NEI (right) galaxies in the GZH sample.}
+\caption{Debiased \ffeatures{} corrected to $z=0.3$ vs weighted \ffeatures{} for the correctable (left), lower-limit (middle), and NEI (right) galaxies in the GZH sample.}
 \label{fig:debiased_corrections}
@@
 As a check, highly boosted galaxies are compared to the expert classifications in the CANDELS catalog \citep{kar15}.
-There are only eight galaxies that were strongly boosted ($p_\mathrm{features,raw}<0.2$ and $p_\mathrm{features,best} > 0.5$) in GZH and also appears in the CANDELS expert sample.
+There are only eight galaxies that were strongly boosted (\ffeatures$<0.2$ and \fbest$>0.5$) in GZH and also appears in the CANDELS expert sample.
 Of those eight galaxies, \citet{kar15} classifies 5 as spheroids, 2 as disks, and 1 as irregular/disky.
-The \pbest{} values for GZH are all between 0.5 and 0.6, making them intermediate disk candidates.
+The \fbest{} values for GZH are all between 0.5 and 0.6, making them intermediate disk candidates.
 One of the spheroids has hints of an interaction or minor merger to the south that may have been missed by the CANDELS experts, but almost all images are dim and with very low surface brightnesses in the ACS imaging, making positive identification challenging.
@@
 As with the HST images, each \ferengi{} subject has a varying number of users answering the various questions in the hierarchical decision tree.
-Every user answers the first question, {\it ``Is the galaxy smooth and rounded, with no sign of a disk?''}; as such the vote fractions $p_\mathrm{smooth}, p_{features}$, and $p_\mathrm{artifact}$ are all computed with the minimum statistical error for any question, with roughly 40 total answers (see Section~\ref{sec:interface}).
+Every user answers the first question, {\it ``Is the galaxy smooth and rounded, with no sign of a disk?''}; as such the vote fractions \fsmooth, \ffeatures, and \fartifact{} are all computed with the minimum statistical error for any question, with roughly 40 total answers (see Section~\ref{sec:interface}).
 The number of users to answer any subsequent question, however, is always equal to or less than the number to answer the preceding question.
@@
 Based on this statistic, the data cannot not be modeled with sufficient confidence for the higher order tasks.
-An example of the debiasing technique applied to $p_{\rm bar}$ is shown in Section~\ref{sec:ferengi_bar}; visual inspection of Figure~\ref{fig:p_vs_p_bar} confirms that the points in each bin are scattered to a degree at which no strong correlation is present.
+An example of the debiasing technique applied to \fbar{} is shown in Section~\ref{sec:ferengi_bar}; visual inspection of Figure~\ref{fig:f_vs_fbar} confirms that the points in each bin are scattered to a degree at which no strong correlation is present.
 For these reasons, debiased vote fractions are only offered in the GZH catalog for Task~01 (smooth/features).
@@
 %\includegraphics[width=\textwidth]{figures/hubble_z_mu_p_distributions.pdf}
-%\caption{Distributions of redshift, surface brightness, and $p_{features}$ for correctable (purple), lower-limit (green), and NEI (pink) galaxies in the full GZH sample.
-The lower-limit galaxies have higher redshifts, slightly lower surface brightness, and lower values of $p_{features}$ on average than the correctable galaxies.
+%\caption{Distributions of redshift, surface brightness, and \ffeatures{} for correctable (purple), lower-limit (green), and NEI (pink) galaxies in the full GZH sample.
+The lower-limit galaxies have higher redshifts, slightly lower surface brightness, and lower values of \ffeatures{} on average than the correctable galaxies.
 The long tail of NEI galaxies in redshift and surface brightness demonstrates the limits of the \ferengi{} sample, for which there is no data at $z>1$ or $\mu>24$.}
@@
 %We show here the preliminary results of GZH classifications of images of galaxies placed at artificial redshifts.
-Figure~\ref{fig:ferengi_results_fake} shows the range of change of vote fractions for the change of \pfeatures{} with redshift, for galaxies with different vote fraction levels, three ranges of surface-brightness levels and 7~evolutionary corrections (this last bit is indicated by the color).
+Figure~\ref{fig:ferengi_results_fake} shows the range of change of vote fractions for the change of \ffeatures{} with redshift, for galaxies with different vote fraction levels, three ranges of surface-brightness levels and 7~evolutionary corrections (this last bit is indicated by the color).
 %
@@
 The GZH catalog is corrected for classification bias only for the first question of the GZH decision tree (Section~\ref{sec:debiasing}), which asks {\it ``Is the galaxy smooth and round, with no sign of a disk?''} For this question, the catalog provides the additional parameters $\tt debiased$, $\tt lower~limit$, $\tt upper~limit$, and $\tt best$ vote fractions.
-The $\tt best$ fraction for $p_{features}$is chosen based on the categorization of the galaxy: if it is ``correctable'', $\tt best = debiased$, if a lower limit, $\tt best = lower~limit$, and if neither, $\tt best = weighted$.
-
-The debiased and best vote fractions for $\tt p_{smooth}$ were calculated on the critera that vote fractions for all answers must sum to unity, such that:
+The $\tt best$ fraction for \ffeatures{} is chosen based on the categorization of the galaxy: if it is ``correctable'', $\tt best = debiased$, if a lower limit, $\tt best = lower~limit$, and if neither, $\tt best = weighted$.
+
+The debiased and best vote fractions for \fsmooth{} were calculated on the criteria that vote fractions for all answers must sum to unity, such that:
 
 \begin{equation}
-p_\mathrm{smooth} \equiv 1 - p_\mathrm{features,best} - p_\mathrm{artifact}.
+f_\mathrm{smooth} \equiv 1 - f_\mathrm{features,best} - f_\mathrm{artifact}.
 \label{eqn:nonlinear}
@@
 
-\noindent In rare cases ($<1\%$ of the sample), this requirement resulted in negative vote fractions for $p_\mathrm{smooth}$; these were cases in which the $p_\mathrm{features}$ vote fraction was boosted to a high value relative to the $p_\mathrm{artifact}$ vote fraction.
-In these cases, the constraint that the vote fractions must sum to 1 is met by setting $p_\mathrm{smooth}=0.0$ and decreasing $p_\mathrm{features}$ accordingly.
-This correction is typically small, with a median decrease/increase of $p_\mathrm{features}/p_{smooth}$ of $\Delta p = 0.04$.
+\noindent In rare cases ($<1\%$ of the sample), this requirement resulted in negative vote fractions for \fsmooth; these were cases in which the \ffeatures{} vote fraction was boosted to a high value relative to the \fartifact{} vote fraction.
+In these cases, the constraint that the vote fractions must sum to 1 is met by setting \fsmooth$=0.0$ and decreasing \fbest{} accordingly.
+This correction is typically small, with a median decrease/increase of $f_\mathrm{features}/f_\mathrm{smooth}$ of $\Delta f = 0.04$.
 
@@
 Tables~\ref{tbl:stripe82_single} and \ref{tbl:stripe82_coadd} contain data for the SDSS Stripe~82 single-depth and co-added images, respectively, that were classified using the GZH interface and decision tree.
-Finally, Table~\ref{tbl:fake_agn} contains classifications for images with artificial point sources intended to simulate the effect of a bright AGN, as used in \citet{sim14}.
+Finally, Table~\ref{tbl:simulated_agn} contains classifications for images with artificial point sources intended to simulate the effect of a bright AGN, as used in \citet{sim14}.
 
@@
 \tablenotetext{1}{Flag indicating how the vote fractions for this galaxy were corrected through debiasing (Section~\ref{ssec:zeta_results}), if possible.
-0~=~correctable, 1~=~lower-limit ($p_{raw}$ --- $p_{adj}$ is not single-valued), 2~=~uncorrected ($z_{\rm gal} < 0.3$), 3~=~uncorrected (insufficient \ferengi{} galaxies in this $z$-$\mu$ bin), 4~=~uncorrected (no galaxy redshift available).}
+0~=~correctable, 1~=~lower-limit ($f_{raw}$ --- $f_{adj}$ is not single-valued), 2~=~uncorrected ($z_{\rm gal} < 0.3$), 3~=~uncorrected (insufficient \ferengi{} galaxies in this $z$-$\mu$ bin), 4~=~uncorrected (no galaxy redshift available).}
 \tablecomments{The full version of this table is available in electronic form, as well as at \url{http://data.galaxyzoo.org}.
@@
 \tablewidth{0pc}
-\tablecaption{GZH morphological classifications for \hst{} images with simulated AGN\label{tbl:fake_agn}} 
+\tablecaption{GZH morphological classifications for \hst{} images with simulated AGN\label{tbl:simulated_agn}} 
 \tabletypesize{\scriptsize}
@@
 
-To select galaxies of a morphological type identified with a particular Task, a cut is placed on the vote fraction for that Task ($p_{\rm task}$), \emph{as well as} the vote fractions for the Tasks preceding it, because of the dependency induced by the decision-tree structure.
-For example, to select barred galaxies, a cut may be placed on $p_{\rm bar}$ such that only galaxies where a high fraction of votes for this task voted for the $bar,yes$ answer.
+To select galaxies of a morphological type identified with a particular Task, a cut is placed on the vote fraction for that Task ($f_{\rm task}$), \emph{as well as} the vote fractions for the Tasks preceding it, because of the dependency induced by the decision-tree structure.
+For example, to select barred galaxies, a cut may be placed on \fbar{} such that only galaxies where a high fraction of votes for this task voted for the $bar,yes$ answer.
 This is not the only necessary cut, however, since not all users answer this question; only those who have previously selected ``features'' in Task~01, ``not clumpy'' in Task~12, and ``not edge-on'' in Task~02 will have the opportunity to vote on the bar question, Task~03.
-To ensure that $p_{\rm bar}$ is well-sampled, cuts on all previous tasks must be applied.
+To ensure that \fbar{} is well-sampled, cuts on all previous tasks must be applied.
 
@@
 
-As an example of how to use Table~\ref{tbl:thresholds} to create a sample of 3-armed spirals galaxies, one should select objects with $N_{arm~number} \ge 20$, $p_{\rm features}>0.23, p_{\rm clumpy,no} > 0.30, p_{edgeon,no}>0.25$, and $p_{spiral,yes}>0.25$.
-These cuts define a sample of galaxies of ``arm number candidates''; ie galaxies for which answering the arm number question makes physical sense and the vote fraction $p_{\rm arm~number}$ is well-sampled.
+As an example of how to use Table~\ref{tbl:thresholds} to create a sample of 3-armed spirals galaxies, one should select objects with $N_{arm~number} \ge 20$, \ffeatures$>0.23, f_{\rm clumpy,no} > 0.30, f_{edgeon,no}>0.25$, and $f_{spiral,yes}>0.25$.
+These cuts define a sample of galaxies of ``arm number candidates''; ie galaxies for which answering the arm number question makes physical sense and the vote fraction $f_{\rm arm~number}$ is well-sampled.
 In this example, such galaxies are featured, non-clumpy, non-edge~on, spiral galaxies.
-At this point a cut can be made on $p_{\rm arm~number=3}$ to select spirals with three arms.
+At this point a cut can be made on $f_{\rm arm~number=3}$ to select spirals with three arms.
 
@@
 A sample of barred disk galaxies is created by applying cuts on the previous tasks as listed in Table~\ref{tbl:thresholds}.
-11,049 ``bar candidates'', galaxies for which asking the bar question is meaningful, were selected by applying the cuts $N_{bar} \ge 20$, $p_{\rm features}>0.23, p_{\rm clumpy,no} > 0.30,$ and $p_{edgeon,no}>0.25$.
+11,049 ``bar candidates'', galaxies for which asking the bar question is meaningful, were selected by applying the cuts $N_{bar} \ge 20$, $f_{\rm features}>0.23, f_{\rm clumpy,no} > 0.30,$ and $f_{edgeon,no}>0.25$.
 These galaxies are featured, non-clumpy, non-edge~on galaxies.
-Of these, a pure sample of 730 barred disks was identified by applying a cut of $p_{bar}>0.7$.
+Of these, a pure sample of 730 barred disks was identified by applying a cut of \fbar$>0.7$.
 A subsample of 50 galaxies were visually inspected and 94\% were found to contain strong bars.
-A complete sample of strong and weak bars was created by applying a cut of $p_{bar}>0.3$.
+A complete sample of strong and weak bars was created by applying a cut of \fbar$>0.3$.
 This sample contained 3,218 galaxies, 86\% of which were found to contain weak or strong bars through visual inspection in a subsample of 50.
 
-The resulting bar sample can be used to estimate the redshift evolution of bar fraction and find a steady decrease of $f_{bar} \sim 0.32$ at $z=0.4$ to $f_{bar} \sim 0.24$ at $z=1.0$.
-The decrease in bar fraction agrees with \citet{mel14}, although they report a lower overall bar fraction going from $f_{bar}=0.22$ at $z=0.4$ to $f_{bar}=0.11$ at $z=1.0$.
-The difference in total bar fraction is expected, as this analysis used a looser cut on $p_{\rm bar}$, there is no luminosity cut, and the use of debiased values for $p_{\rm features}$ increases the total amount of disks in the sample compared to \citet{mel14}.
-For a more thorough analysis of the bar fraction, a cut on $p_{\rm bar}$ that evolves with redshift may yield more accurate results, since there are no explicit debiased values of $p_{\rm bar}$ that would take redshift induced bias into account.
+The resulting bar sample can be used to estimate the redshift evolution of bar fraction and find a steady decrease of \fbar$\sim 0.32$ at $z=0.4$ to \fbar$\sim 0.24$ at $z=1.0$.
+The decrease in bar fraction agrees with \citet{mel14}, although they report a lower overall bar fraction going from \fbar$=0.22$ at $z=0.4$ to \fbar$=0.11$ at $z=1.0$.
+The difference in total bar fraction is expected, as this analysis used a looser cut on \fbar, there is no luminosity cut, and the use of debiased values for \ffeatures{} increases the total amount of disks in the sample compared to \citet{mel14}.
+For a more thorough analysis of the bar fraction, a cut on \fbar{} that evolves with redshift may yield more accurate results, since there are no explicit debiased values of \fbar{} that would take redshift induced bias into account.
 
@@
 For galaxies identified as ``clumpy'' in GZH, the number of clumps can be determined using Task~16.
-Table~\ref{tbl:thresholds} can be used to select 8,444 galaxies measured as ``clumpy'' using $p_{\rm features} > 0.23$ and $p_{\rm clumpy,yes}>0.80$ to ensure the vote fractions for Task~16 are well-sampled.
+Table~\ref{tbl:thresholds} can be used to select 8,444 galaxies measured as ``clumpy'' using \ffeatures$> 0.23$ and $f_{\rm clumpy,yes}>0.80$ to ensure the vote fractions for Task~16 are well-sampled.
 The clump number can be reasonably identified for 1,112 of the clumpy galaxies; for the remainder, the unique clumps were less distinguishable from each other and the exact number of clumps could not be deduced without careful visual inspection.
-In the 1,112 which did have distinguishable clumps, there are 61 one-clump galaxies using $p_{\rm 1~clump}>0.50$, 442 two-clump galaxies using $p_{\rm 2~clumps}>0.80$, 275 three-clump galaxies using $p_{\rm 3~clumps}>0.75$, 71 four-clump galaxies using $p_{\rm 4~clumps} > 0.70$, and 263 galaxies with more than four clumps using $p_{\rm >4~clumps}>0.70$.
+In the 1,112 which did have distinguishable clumps, there are 61 one-clump galaxies using $f_{\rm 1~clump}>0.50$, 442 two-clump galaxies using $f_{\rm 2~clumps}>0.80$, 275 three-clump galaxies using $f_{\rm 3~clumps}>0.75$, 71 four-clump galaxies using $f_{\rm 4~clumps} > 0.70$, and 263 galaxies with more than four clumps using $f_{\rm >4~clumps}>0.70$.
 Alternatively, these data may be used to create more general samples of clumpy galaxies with few clumps and many clumps.
-A sample of 989 ``few clumps'' galaxies can be made using $(p_{\rm 1~clump} + p_{\rm 2~clumps}) > 0.5$ and 2,910 ``many clumps'' galaxies using $(p_{\rm 3~clumps}+p_{\rm 4~clumps}+p_{\rm >4~clumps})>0.5$.
+A sample of 989 ``few clumps'' galaxies can be made using $(f_{\rm 1~clump} + f_{\rm 2~clumps}) > 0.5$ and 2,910 ``many clumps'' galaxies using $(f_{\rm 3~clumps}+f_{\rm 4~clumps}+f_{\rm >4~clumps})>0.5$.
 
@@
 01       & smooth or features   & $-$              & $-$                                \\
-02       & edge on              & 01,12            & $p_{\rm clumpy,no}>0.30$           \\
-03       & bar		            & 01,12,02         & $p_{\rm edgeon,no}>0.25$           \\
-         &                      & 01,12,16,15      & $p_{\rm clumpy~spiral}>0.65$       \\
-04       & spiral arms          & 01,12,02         & $p_{\rm edgeon,no}>0.25$           \\
-         &                      & 01,12,16,15      & $p_{\rm clumpy~spiral}>0.65$       \\
-05       & bulge prominence     & 01,12,02         & $p_{\rm edgeon,no}>0.25$           \\
-         &                      & 01,12,16,15      & $p_{\rm clumpy~spiral}>0.65$       \\
+02       & edge on              & 01,12            & $f_{\rm clumpy,no}>0.30$           \\
+03       & bar		            & 01,12,02         & $f_{\rm edgeon,no}>0.25$           \\
+         &                      & 01,12,16,15      & $f_{\rm clumpy~spiral}>0.65$       \\
+04       & spiral arms          & 01,12,02         & $f_{\rm edgeon,no}>0.25$           \\
+         &                      & 01,12,16,15      & $f_{\rm clumpy~spiral}>0.65$       \\
+05       & bulge prominence     & 01,12,02         & $f_{\rm edgeon,no}>0.25$           \\
+         &                      & 01,12,16,15      & $f_{\rm clumpy~spiral}>0.65$       \\
 06       & odd yes/no           & $-$              & $-$                                \\
-07       & rounded              & 01               & $p_{\rm smooth}>0.70$              \\
-08       & odd feature          & 06               & $p_{\rm odd,yes}> 0.50$            \\
-09       & bulge shape          & 01,12,02         & $p_{\rm edgeon,yes}>0.40$          \\
-10       & arms winding         & 01,12,02,04      & $p_{\rm spiral,yes}>0.25$          \\
-11       & arms number          & 01,12,02,04      & $p_{\rm spiral,yes}>0.25$          \\
-12       & clumpy               & 01               & $p_{\rm features}>0.23$            \\
-13       & bright clump         & 01,12,16         & $p_{\rm one~clump}< 0.40$          \\
-14       & bright central clump & 01,12,16,13      & $p_{\rm bright~clump,yes}>0.50$    \\
-15       & clump arrangement    & 01,12,16         & $p_{\rm multiple~clumps}>0.45$     \\
-16       & clump count          & 01,12            & $p_{\rm clumpy,yes}>0.80$          \\
-17       & clumps symmetrical   & 01,12            & $p_{\rm clumpy,yes}>0.80$          \\
-18       & clumps embedded      & 01,12            & $p_{\rm clumpy,yes}>0.80$          \\
+07       & rounded              & 01               & $f_{\rm smooth}>0.70$              \\
+08       & odd feature          & 06               & $f_{\rm odd,yes}> 0.50$            \\
+09       & bulge shape          & 01,12,02         & $f_{\rm edgeon,yes}>0.40$          \\
+10       & arms winding         & 01,12,02,04      & $f_{\rm spiral,yes}>0.25$          \\
+11       & arms number          & 01,12,02,04      & $f_{\rm spiral,yes}>0.25$          \\
+12       & clumpy               & 01               & $f_{\rm features}>0.23$            \\
+13       & bright clump         & 01,12,16         & $f_{\rm one~clump}< 0.40$          \\
+14       & bright central clump & 01,12,16,13      & $f_{\rm bright~clump,yes}>0.50$    \\
+15       & clump arrangement    & 01,12,16         & $f_{\rm multiple~clumps}>0.45$     \\
+16       & clump count          & 01,12            & $f_{\rm clumpy,yes}>0.80$          \\
+17       & clumps symmetrical   & 01,12            & $f_{\rm clumpy,yes}>0.80$          \\
+18       & clumps embedded      & 01,12            & $f_{\rm clumpy,yes}>0.80$          \\
 \hline\hline
@@
 The width of the flows is proportional to the number of galaxies associated with that response; Figure~\ref{fig:sankey} uses a simple plurality vote to assign the combined set of labels for each galaxy.
-This method is likely to undersample some of the categories; visual inspection of images suggests that $p_\mathrm{features}\gtrsim0.3$ identifies disk-dominated or irregular galaxies reliably, for example.
+This method is likely to undersample some of the categories; visual inspection of images suggests that \ffeatures$\gtrsim0.3$ identifies disk-dominated or irregular galaxies reliably, for example.
 This method also does not use the suggested thresholds in Table~\ref{tbl:thresholds}.
@@
 In an attempt to make a consistent comparison between different techniques, galaxies are broadly grouped into three categories: bulge-dominated/elliptical/smooth, disk-dominated/spiral, and irregular/clumpy.
-These categories are compared to two parameters in GZH: \pbest, which is designed to identify smooth (elliptical) galaxies, and \podd, which is designed to identify deviations from well-formed spirals or S0s and which constitutes a ``catch-all'' for the variety of asymmetric morphologies that can constitute an irregular galaxy.
+These categories are compared to two parameters in GZH: \fbest, which is designed to identify smooth (elliptical) galaxies, and \fodd, which is designed to identify deviations from well-formed spirals or S0s and which constitutes a ``catch-all'' for the variety of asymmetric morphologies that can constitute an irregular galaxy.
 
@@
 \caption{Distributions of morphological parameters for galaxies matched in GZH and other published catalogs, split by survey (AEGIS, COSMOS, GEMS, and GOODS).
-The first and third columns show the fraction of overall galaxies in the matched samples, split by their published morphologies as a function of the GZH \pbest.
-The corresponding second and fourth columns show data for the same galaxies as a function of \podd.
+The first and third columns show the fraction of overall galaxies in the matched samples, split by their published morphologies as a function of the GZH \fbest.
+The corresponding second and fourth columns show data for the same galaxies as a function of \fodd.
 Confidence intervals for each binned fraction in the bin are calculated for a binomial population \citep{cam11}.}
@@
 The relation between GZH and the automated/expert morphologies is shown to vary significantly for different surveys --- this may be due to intrisic differences in the galaxies, in the techniques used to measure morphology, or both.
-The distribution of \pbest{} for AEGIS galaxies is essentially flat for spirals, showing almost no difference in proportion at the highest and lowest ends.
-Early-type galaxies are at their highest proportion at \pbest$\sim0$, but constitute only 40\% of the galaxies at most.
-In contrast, GOODS galaxies at low \pbest{} are dominated by early-types, although spiral and irregular galaxies have comparable sizes as low as \pbest$\sim0.2$.
-In GEMS galaxies, the impact of irregular or peculiar galaxies is not measured; splitting on $n=2.5$ gives an essentially flat proportion of ellipticals to spirals at \pbest$>0.3$.
-Visual inspection of images of galaxies where both \pbest{} and $n$ are high show that the majority are obvious spirals but with prominent bulges, indicating that the single-component \sersic{} fit is likely choosing too small of an effective radius and missing the extended disk structure for a large population of galaxies.
+The distribution of \fbest{} for AEGIS galaxies is essentially flat for spirals, showing almost no difference in proportion at the highest and lowest ends.
+Early-type galaxies are at their highest proportion at \fbest$\sim0$, but constitute only 40\% of the galaxies at most.
+In contrast, GOODS galaxies at low \fbest{} are dominated by early-types, although spiral and irregular galaxies have comparable sizes as low as \fbest$\sim0.2$.
+In GEMS galaxies, the impact of irregular or peculiar galaxies is not measured; splitting on $n=2.5$ gives an essentially flat proportion of ellipticals to spirals at \fbest$>0.3$.
+Visual inspection of images of galaxies where both \fbest{} and $n$ are high show that the majority are obvious spirals but with prominent bulges, indicating that the single-component \sersic{} fit is likely choosing too small of an effective radius and missing the extended disk structure for a large population of galaxies.
 
 Even within the same sample of galaxies in COSMOS, different techniques of measuring morphology show significant differences.
-Both \citet{cas07} and \citet{tas11} have higher proportions of early-type galaxies at \pbest$\sim0$, but constitute less than half the sample in both cases.
-The majority of all galaxies in \citet{sca07}, in contrast, are spirals; oddly, the \emph{highest} proportions of spirals are found at the lowest values of \pbest.
-The decrease in spiral galaxies at higher \pbest{} is almost entirely balanced by an increase in irregulars.
-Early-types have a small bump near \pbest$\sim0.15$, but never constitute more than 10\% of the sample.
-
-The second set of plots in Figure~\ref{fig:comparisons} indicates that \podd{} is largely an effective method for separating irregular and/or peculiar galaxies from spirals.
-Despite the somewhat vague wording of the {\it ``anything odd?''} question in GZH, the AEGIS, COSMOS, and GOODS all show a marked increase in the irregular fraction increasing with \podd.
+Both \citet{cas07} and \citet{tas11} have higher proportions of early-type galaxies at \fbest$\sim0$, but constitute less than half the sample in both cases.
+The majority of all galaxies in \citet{sca07}, in contrast, are spirals; oddly, the \emph{highest} proportions of spirals are found at the lowest values of \fbest.
+The decrease in spiral galaxies at higher \fbest{} is almost entirely balanced by an increase in irregulars.
+Early-types have a small bump near \fbest$\sim0.15$, but never constitute more than 10\% of the sample.
+
+The second set of plots in Figure~\ref{fig:comparisons} indicates that \fodd{} is largely an effective method for separating irregular and/or peculiar galaxies from spirals.
+Despite the somewhat vague wording of the {\it ``anything odd?''} question in GZH, the AEGIS, COSMOS, and GOODS all show a marked increase in the irregular fraction increasing with \fodd.
 Any threshold value for distinguishing between the two, however, depends strongly on survey/redshift~range.
@@
 Since both the sensitivity and filters for the two sets of images differ (and there is no debiased correction applied to GZC), there is no prior reason to expect a perfect correlation between the separate vote fractions for the projects.
-Briefly, we note that the \pfeatures{} value for GZH is on average higher than GZC; the effect is strongest at $p_\mathrm{features,GZC}<0.3$, for which roughly half the galaxies have $p_\mathrm{features,GZH}>0.5$.
+Briefly, we note that the \ffeatures{} value for GZH is on average higher than GZC; the effect is strongest at $f_\mathrm{features,GZC}<0.3$, for which roughly half the galaxies have $f_\mathrm{features,GZH}>0.5$.
 However, the correlation between vote fractions is single-valued (although not linear, with a Pearson correlation coefficient of $r=0.6$), and should be possible to calibrate using a similar approach to that described in Section~\ref{sec:debiasing}; the correlation between other tasks, such as edge-on galaxies is significantly stronger ($r=0.9$).
@@
 To calibrate this \emph{without} potentially overcorrecting for the genuine morphological evolution of galaxies over cosmic time, the GZH project uses SDSS images of low-redshift galaxies, processes them to appear as if they were at higher redshift, and classifies them through the GZH interface in an identical fashion.
-The resulting change in \pfeatures{} as a function of $z$ and $\mu$ is applied as a multiplicative correction to the top-level vote fractions for $\sim50\%$ of the GZH galaxies.
+The resulting change in \ffeatures{} as a function of $z$ and $\mu$ is applied as a multiplicative correction to the top-level vote fractions for $\sim50\%$ of the GZH galaxies.
 
@@
 Of the 11,157 galaxies in the GOODS-N and GOODS-S full depth sample, 4,461 of these are in the shallow-depth sample.
-Figure~\ref{fig:shallow_vs_full} shows a strong correlation between $p_\mathrm{features}$ for both sets of images.
-The mean change in $p_\mathrm{features}$ from the shallow to full depth images  $p_\mathrm{features,full} - p_{features,shallow} \equiv \Delta p = 0.00$, with a standard deviation of $\sigma = 0.17$.
+Figure~\ref{fig:shallow_vs_full} shows a strong correlation between \ffeatures{} for both sets of images.
+The mean change in \ffeatures{} from the shallow to full depth images  $f_\mathrm{features,full} - f_{features,shallow} \equiv \Delta p = 0.00$, with a standard deviation of $\sigma = 0.17$.
 While there is some variance in $\Delta p$ in the whole sample, the change is usually small and not often significant enough to change a morphological classification.
-Defining a clean sample of disk galaxies as those with $p_{features,best}>0.8$, elliptical galaxies as those with  $p_{smooth,best}<0.2$, and intermediate as those in between, 75\% of the sample would not change morphology.
+Defining a clean sample of disk galaxies as those with \fbest$>0.8$, elliptical galaxies as those with $f_\mathrm{smooth,best}<0.2$, and intermediate as those in between, 75\% of the sample would not change morphology.
 Of the remaining 25\% that would change morphology, only 0.3\% (representing 10 galaxies total) drastically change morphology from smooth to featured or visa versa, while the rest would transition to or from the ``intermediate'' morphology.
@@
 \includegraphics[width=0.50\textwidth]{figures/full_shallow_p_plot.pdf}
-\caption{Distribution of $p_{\rm features}$ for the 4,461 GOODS galaxies with both shallow (2-epoch) and full-depth (5-epoch) images morphologically classified in GZH.
-For most galaxies, the value of $p_{\rm features}$ is consistent ($\Delta p_\mathrm{features}<0.2$) between depths.
-Examples of galaxies with sharp changes in $p_{\rm features}$, as well as those with little to no change are shown in Figures~\ref{fig:shallow_smooth}-\ref{fig:shallow_featured}.}
+\caption{Distribution of \ffeatures{} for the 4,461 GOODS galaxies with both shallow (2-epoch) and full-depth (5-epoch) images morphologically classified in GZH.
+For most galaxies, the value of \ffeatures{} is consistent ($\Delta f_\mathrm{features}<0.2$) between depths.
+Examples of galaxies with sharp changes in \ffeatures, as well as those with little to no change are shown in Figures~\ref{fig:shallow_smooth}-\ref{fig:shallow_featured}.}
 \label{fig:shallow_vs_full}
@@
 \caption{Properties of galaxies whose morphologies changed or stayed the same in the shallow vs full images.
-Featured here is defined as $p_{features,best}>0.8$, intermediate = $0.2<p_{features,best}<0.8$, smooth = $p_{smooth,best}<0.2$.
+Featured here is defined as \fbest$>0.8$, intermediate = $0.2<$\fbest$<0.8$, smooth = $f_\mathrm{smooth,best}<0.2$.
 \label{tbl:shallow_to_full_stats}}
@@
 
-\subsection{FERENGI analysis of pbar}
+\subsection{Debiasing higher-order tasks: \fbar}
 \label{sec:ferengi_bar}
@@
 Here we show an example of results obtained for the bar Task.
-Figure~\ref{fig:p_vs_p_bar} shows that both the low sample rate and the degree of scatter in each bin inhibit fitting a reliable function that predicts $p_\mathrm{bar,z=0.3}$.
-Table~\ref{tbl:ferengi_bar} summarizes the correction types for the \ferengi{} data; 71\% of the galaxies simulated did not meet the GZH requirements for well-sampled vote fractions for $p_\mathrm{bar}$, as compared to 2\% for $p_\mathrm{features}$.
+Figure~\ref{fig:f_vs_fbar} shows that both the low sample rate and the degree of scatter in each bin inhibit fitting a reliable function that predicts $f_\mathrm{bar,z=0.3}$.
+Table~\ref{tbl:ferengi_bar} summarizes the correction types for the \ferengi{} data; 71\% of the galaxies simulated did not meet the GZH requirements for well-sampled vote fractions for $f_\mathrm{bar}$, as compared to 2\% for $f_\mathrm{features}$.
 Similar results were obtained for all higher-order Tasks in GZH, as described in Section~\ref{ssec:higher_order_tasks}.
@@
 \subfigure{[d]\label{d}\includegraphics[width=0.4\textwidth]{figures/z1_mu20_subplot2_bar.pdf}}
-\caption{Similar to Figure~\ref{fig:p_vs_p}, showing effects of redshift bias for 3,950~images in the \ferengi{} sample.
+\caption{Similar to Figure~\ref{fig:f_vs_f}, showing effects of redshift bias for 3,950~images in the \ferengi{} sample.
 [a]: Each point in a given redshift and surface brightness bin represents a unique galaxy.
-The $y$-axis in each bin is the \pfeatures{} value of the image of that galaxy redshifted to the value corresponding to that redshift bin.
-The $x$-axis is the \pfeatures{} value of the image of the same galaxy redshifted to $z=0.3$.
+The $y$-axis in each bin is the \ffeatures{} value of the image of that galaxy redshifted to the value corresponding to that redshift bin.
+The $x$-axis is the \ffeatures{} value of the image of the same galaxy redshifted to $z=0.3$.
 The dashed black lines represent the best-fit polynomials to the data in each square.
-The solid black line represents \pfeaturesz=\pfeaturesrest.
-Regions in which there is a single-valued relationship between \pfeatures{} at high redshift and at $z=0.3$ are marked in white; those in which there is not are blue, and those with not enough data ($N<5$) are gray.
+The solid black line represents \ffeaturesz=\ffeaturesrest.
+Regions in which there is a single-valued relationship between \ffeatures{} at high redshift and at $z=0.3$ are marked in white; those in which there is not are blue, and those with not enough data ($N<5$) are gray.
 The mean normalized $\chi^2$ of the change in vote fraction is 0.08.
@@
 [c]: The same data as [a].
-Each $z,\mu$ bin is divided into 4~sub-bins to determine the range of intrinsic \pfeaturesrest{} for a given range of observed \pfeaturesz{} values.
+Each $z,\mu$ bin is divided into 4~sub-bins to determine the range of intrinsic \ffeaturesrest{} for a given range of observed \ffeaturesz{} values.
 In each sub-bin, the orange bars represent the inner 80$^\mathrm{th}$ percentiles of the data, the boundaries of which are the lower and upper limits of the debiased values.
 [d]: The same data as [b], but highlighting the upper and lower limit regions.}
-\label{fig:p_vs_p_bar}
+\label{fig:f_vs_fbar}
 \end{figure*}
@@
 \label{tbl:ferengi_bar}
-\caption{Distribution of \ferengi{} images analysed in Figure~\ref{fig:p_vs_p_bar}.
-Correctable images had a single-valued relationship between their measured \pbar{} values at high and low redshifts (white regions in Figure~\ref{fig:p_vs_p_bar}).
-Galaxies with a lower-limit on \pbar{} had a non single-valued relationship (blue regions).
+\caption{Distribution of \ferengi{} images analysed in Figure~\ref{fig:f_vs_fbar}.
+Correctable images had a single-valued relationship between their measured \fbar{} values at high and low redshifts (white regions in Figure~\ref{fig:f_vs_fbar}).
+Galaxies with a lower-limit on \fbar{} had a non single-valued relationship (blue regions).
 NEI images had undetermined relationships due to a lack of data ($N<5$) in their corresponding $z$-$\mu$ bins (gray regions).

### 2016-05-09 writeup/gz_hubble_data.tex
Figure 10 fixed for #66.
Spell-checked with aspell

@@
 The structure of individual galaxies is affected by the merger history \citep{too72,hop10}, local environment \citep[such as the morphology-density relation;][]{dre80}, initial dark halo mass, and many other factors.
-Morphologies of individial simulated high-mass galaxies at $z\sim2-3$ commonly show kpc-scale ``clumpy'' structures and few galaxies that are either smooth or well-ordered spirals; asymmetric profiles with strong density constrasts dominate populations in the early Universe until at least $z\sim1$ \citep{gen14}.
+Morphologies of individual simulated high-mass galaxies at $z\sim2-3$ commonly show kpc-scale ``clumpy'' structures and few galaxies that are either smooth or well-ordered spirals; asymmetric profiles with strong density contrasts dominate populations in the early Universe until at least $z\sim1$ \citep{gen14}.
 
@@
 21,522 galaxies in SDSS met these criteria.
-Coadded images from Stripe~82 were selected from the union of galaxies with coadded magnitudes brighter than $17.77$~mag and the galaxies detected in the single-depth images and matched to a coadd source.
+Co-added images from Stripe~82 were selected from the union of galaxies with co-added magnitudes brighter than $17.77$~mag and the galaxies detected in the single-depth images and matched to a co-add source.
 This resulted in a larger set of 30,339 images.
-Of the images in the coadded sample, 5144 (17~percent) are dimmer than the initial magnitude cut of 17.77.
+Of the images in the co-added sample, 5144 (17~percent) are dimmer than the initial magnitude cut of 17.77.
 
@@
 The Stripe~82 single-epoch images were taken directly from the color composites on the DR7 SDSS Skyserver, which combines $g^{\prime}$, $r^{\prime}$, and $i^{\prime}$ exposures into the RGB channels.
-The coadded Stripe~82 images were assembled from runs 106 and 206 in DR7 and made into color composites using the method of \citet{lup04}.
+The co-added Stripe~82 images were assembled from runs 106 and 206 in DR7 and made into color composites using the method of \citet{lup04}.
 
@@
 Since this only affects a tiny percentage of the users (and an even smaller percentage of the classifications) the overall effect on the GZH dataset is minimal.
-This method is effective, however, at filtering out contributions from random or delibrately malicious classifiers.
+This method is effective, however, at filtering out contributions from random or deliberately malicious classifiers.
 
@@
 the reduction in physical resolution, surface brightness dimming, etc).
-For both previous releases of GZ morphologies, a correction for redshift-dependent bias was applied based on matching the classification fractions at the highest redshfts with those at the lowest redshift.
+For both previous releases of GZ morphologies, a correction for redshift-dependent bias was applied based on matching the classification fractions at the highest redshifts with those at the lowest redshift.
 \citet{bam09} and \citet{wil13} provide complete descriptions of the process for GZ1 and GZ2, respectively.
@@
 
-\subsection{Generating images of artifically-redshifted galaxies}
+\subsection{Generating images of artificially-redshifted galaxies}
 
@@
 \center
-\includegraphics[width=0.50\textwidth]{figures/zeta_mu.pdf}
+\includegraphics[width=0.50\textwidth]{figures/zeta_mu.png}
 \caption{All fits for the vote fraction dropoff parameter $\zeta$ for $f_\textrm{features}$ in the \ferengi{} galaxies as a function of surface brightness.
@@
 
-The unshaded regions in Figure~\ref{fig:6a} define discrete ranges of redshift, surface brightness, and \ffeatures{} a galaxy must have in order for the debiased correction to be confidentely applied to a galaxy in the GZH sample.
+The unshaded regions in Figure~\ref{fig:6a} define discrete ranges of redshift, surface brightness, and \ffeatures{} a galaxy must have in order for the debiased correction to be confidently applied to a galaxy in the GZH sample.
 While the appropriate correctable regions were defined discretely, the true correctable region is assumed to be a smooth function of $z$, $\mu$, and \ffeatures{}.
@@
 \center
-\caption{Distribution of \ferengi{} images analysed in Figure~\ref{fig:f_vs_f}.
+\caption{Distribution of \ferengi{} images analyzed in Figure~\ref{fig:f_vs_f}.
 Correctable images have a single-valued relationship between their measured \ffeatures{} values at high and low redshifts (white regions in Figure~\ref{fig:f_vs_f}).
@@
 
-\begin{figure*}
-\center
-\includegraphics[width=\textwidth]{figures/debiased_corrections.pdf}
-\caption{Debiased \ffeatures{} corrected to $z=0.3$ vs weighted \ffeatures{} for the correctable (left), lower-limit (middle), and NEI (right) galaxies in the GZH sample.}
-\label{fig:debiased_corrections}
-\end{figure*}
-
 Few galaxies in the sample have sufficiently high corrections to completely change them from being confidently smooth to featured following the bias correction (Figure~\ref{fig:debiased_corrections}).
@@
 Since the surveys use different rest-frame filters and the overlap sample is tiny, though, detailed comparisons between the overall morphologies are highly difficult.
+
+\begin{figure*}
+\center
+\includegraphics[width=\textwidth]{figures/debiased_corrections.pdf}
+\caption{Debiased \ffeatures{} corrected to $z=0.3$ vs weighted \ffeatures{} for the correctable (left), lower-limit (middle), and NEI (right) galaxies in the GZH sample.}
+\label{fig:debiased_corrections}
+\end{figure*}
 
@@
 This section described how to use the previous Task thresholds in Table~\ref{tbl:thresholds} to select well-sampled galaxies which may or may not contain the feature associated with a unique Task.
-The following two examples show to use the vote fractions for a particular Task to obtain a sample of galaxies with a certain morpholgical type.
+The following two examples show to use the vote fractions for a particular Task to obtain a sample of galaxies with a certain morphological type.
 
@@
 \subsection{Example 2: Identifying clump multiplicity}
-Clumps are known to be a characteristic feature of galaxies outside the local universe, and there is evidence they play a crutial role in the evolution of modern spirals, particularly in the formation of central bulges \citep{elm05,elm14,guo15,beh16}.
+Clumps are known to be a characteristic feature of galaxies outside the local universe, and there is evidence they play a crucial role in the evolution of modern spirals, particularly in the formation of central bulges \citep{elm05,elm14,guo15,beh16}.
 Simulations show clumps migrate from the outer disk to the galactic center on relatively short (a few orbital periods) timescales \citep{man15} and observations show increasing bulge to clump mass and density ratios as the universe evolves since $z\sim 1.5$ \citep{elm09}, suggesting that clumps coalesce over time to form the modern bulges of disk galaxies.
@@
 Within the sample of galaxies identified as ``not smooth'', it is clear that the addition of the clumpy branch is necessary to describe a large fraction of the sample; disk-dominated galaxies outnumber clumpy morphologies by less than a factor of 2.
-Disk galaxies are primarily unbarred \citet{mel14} and possessing two visible spiral arms over a flat distribution of pitch angles and bulge prominences.
+Disk galaxies are primarily unbarred \citet{mel14} and possessing two visible spiral arms over a flat distribution of pitch angles and bulge prominence.
 Clumpy galaxies are identified across the full range of clump multiplicities, with the exception of 1-clump galaxies (which would be difficult to differentiate from compact spheroids).
@@
 
-The types and accuracies of morphological classification strongly depend on the sample and methods being used.
+The types and accuracy of morphological classification strongly depend on the sample and methods being used.
 In an attempt to make a consistent comparison between different techniques, galaxies are broadly grouped into three categories: bulge-dominated/elliptical/smooth, disk-dominated/spiral, and irregular/clumpy.
@@
 Figure~\ref{fig:comparisons} shows the proportion of galaxies as split by their automated/expert visual morphologies for each of the six catalogs matched to GZH.
-The relation between GZH and the automated/expert morphologies is shown to vary significantly for different surveys --- this may be due to intrisic differences in the galaxies, in the techniques used to measure morphology, or both.
+The relation between GZH and the automated/expert morphologies is shown to vary significantly for different surveys --- this may be due to intrinsic differences in the galaxies, in the techniques used to measure morphology, or both.
 The distribution of \fbest{} for AEGIS galaxies is essentially flat for spirals, showing almost no difference in proportion at the highest and lowest ends.
@@
 Defining a clean sample of disk galaxies as those with \fbest$>0.8$, elliptical galaxies as those with $f_\mathrm{smooth,best}<0.2$, and intermediate as those in between, 75\% of the sample would not change morphology.
-Of the remaining 25\% that would change morphology, only 0.3\% (representing 10 galaxies total) drastically change morphology from smooth to featured or visa versa, while the rest would transition to or from the ``intermediate'' morphology.
+Of the remaining 25\% that would change morphology, only 0.3\% (representing 10 galaxies total) drastically change morphology from smooth to featured or vice versa, while the rest would transition to or from the ``intermediate'' morphology.
 Details can be seen in Table~\ref{tbl:shallow_to_full_stats} and examples of images representing the 9 possible changes (or lack of) in morphology are shown in Figures~\ref{fig:shallow_smooth},\ref{fig:shallow_intermediate}, and \ref{fig:shallow_featured}.
@@
 
-To determine the rate at which the vote fraction for any Task decreases with redshift or surface brightness, data from simluated \ferengi{} images were modeled with functions in discrete redshift and surface brightness bins (Section~\ref{ssec:zeta_results}).
+To determine the rate at which the vote fraction for any Task decreases with redshift or surface brightness, data from simulated \ferengi{} images were modeled with functions in discrete redshift and surface brightness bins (Section~\ref{ssec:zeta_results}).
 A cut of $N>10$ was placed on the number of votes to reduce the error in the vote fractions and ensure they were well-sampled before applying a fit to the data.
@@
 \label{tbl:ferengi_bar}
-\caption{Distribution of \ferengi{} images analysed in Figure~\ref{fig:f_vs_fbar}.
+\caption{Distribution of \ferengi{} images analyzed in Figure~\ref{fig:f_vs_fbar}.
 Correctable images had a single-valued relationship between their measured \fbar{} values at high and low redshifts (white regions in Figure~\ref{fig:f_vs_fbar}).

### 2016-05-09 writeup/gz_hubble_data.tex
Final proofreading for now, I swear.

@@
 This paper also describes and employs a novel method for calibrating morphological bias by using artificially-redshifted galaxy images as a baseline.
-The GZH catalog includes both the raw and calibrated morphological vote fractions for $150,771$ galaxies, constituting a large data set suitable for large-scale studies of galaxy evolution.
+The GZH catalog includes both the raw and calibrated morphological vote fractions for $150,771$ galaxies, providing a comprehensive data set suitable for large-scale studies of galaxy evolution.
 
@@
 The morphology of galaxies encodes information on the orbital parameters and assembly history of the contents, including gas, dust, stars, and the central black hole.
-The morphology is also closely related to the local environment of the galaxy, as mutual interactions such as gravitational tides, shocks in cluster environments and direct mergers can all change the shape of the galaxy's potential.
+The morphology is also closely related to the local environment of the galaxy, as mutual interactions such as tides, shocks in cluster environments and direct mergers can all change the shape of the galaxy's gravitational potential.
 For $M^\star$~galaxies in the local Universe, this typically manifests at the most basic level as the difference between bulge-dominated, virialized systems resembling ellipticals (early-types) and disk-dominated, rotationally-supported disks (late-types) frequently exhibiting spiral arms.
-This dichotomy has been used to explore much of the astrophysics encoding galaxy formation and evolution, and has been shown to be closely linked with other galactic properties such as stellar mass, halo mass, bolometric luminosity, black hole activity, effective radius, and the relative ages of the stellar populations.
-
-The advent of larger telescopes in an increasing range of observable wavelengths has revealed that the distribution and properties of galaxy morphology have strongly evolved over the lifetime of the Universe.
+This dichotomy has been used to explore much of the astrophysics governing galaxy formation and evolution, and has been shown to be closely linked with other galactic properties such as stellar mass, halo mass, bolometric luminosity, black hole activity, effective radius, and the relative ages of the stellar populations.
+
+The advent of larger telescopes in an increasing range of observing wavelengths has revealed that the distribution and properties of galaxy morphology have strongly evolved over the lifetime of the Universe.
 At redshift $z\simeq1$ (roughly 6~Gyr after the Big Bang), many galaxies are still in the process of assembling the baryonic mass required to reproduce the structures seen in the present day.
@@
 Observational studies of galaxies at high-redshift also display a wide range of morphological types, many of which are rare or absent at $z\sim0$.
-These include spheroids and disks (akin to the ellipticals/spirals seen in the local Universe), but also a significant population of massive, more irregular galaxies, including mergers, tadpoles, chains, double-clumps, and clump-clusters \citep{elm05,elm07,cam11a,for11a,kar15}.
+These include spheroids and disks (akin to the ellipticals and spirals seen in the local Universe), but also a significant population of massive, more irregular galaxies, including mergers, tadpoles, chains, double-clumps, and clump-clusters \citep{elm05,elm07,cam11a,for11a,kar15}.
 In contrast, while grand-design spirals have been observed as far back as $z=2.18$ \citep{law12}, their spatial density suggests that they are exceedingly rare, with a very low overall disk fraction \citep{mor13}.
@@
 Observations of fixed fields with very deep imaging \citep[eg,][]{wil96,gia04,bec06,dav07,sco07,gro11} give the photometric sensitivity necessary to detect $L^\star$ galaxies at $z>1$, while also providing the angular resolution to distinguish internal structure and characterize the morphology.
-While these measurements are helped by the fact that the angular diameter distance is relatively flat at $z>1$ in a flat $\Lambda$CDM cosmology, the scales are only of the order $\sim5-10~\mathrm{kpc}/^{\prime\prime}$ \citep{wri06}.
+While these measurements are helped by the fact that the angular diameter distance is relatively flat beyond $z>1$ in a flat $\Lambda$CDM cosmology, the relevant angular scales are only of the order $\sim5-10~\mathrm{kpc}/^{\prime\prime}$ \citep{wri06}.
 \hst{} can thus resolve much of the structure for a Milky Way-sized galaxy (at least for distinguishing a disk from a bulge), but will be limited for more compact structures.
-Since the size of galaxies evolves as roughly $r\propto(1+z)^{-1}$ \citep{law12a}, the more compact sizes of earlier galaxies make detailed morphologies a challenge even for \hst{} \citep{che12}.
+Since the size of galaxies evolves as roughly $r\propto(1+z)^{-1}$ \citep{law12a}, the compact sizes of high-redshift galaxies make detailed morphologies a challenge even for \hst{} \citep{che12}.
 The public availability of more than $10^5$~galaxies in archival imaging across various studies gives a data sample with the potential for high statistical significance.
 
-One of the major difficulties in studying the morphologies of galaxies in large samples lies in the system of measurement.
+One of the major difficulties in studying the morphologies of galaxies lies in the techniques used for measurement.
 Visual classification by experts has been used for many years \citep[eg,][]{hub26,dev59,san61,van76,nai10,bai11,kar15}.
-These methods have advantages in using the significant processing power of the human brain to identify patterns, but suffer from issues such as lack of scaling to large surveys and potential issues with replicability and calibration.
-Automated measurements, both parametric \citep{pen02a,sim11,lac12} and non-parametric \citep{abr03,con03,lot04,sca07,bam08,fre13}, scale well to arbitrary sample sizes, but do not always fully capture the relevant features, especially for asymmetric galaxies that become increasingly common at high redshifts.
+These methods have the advantage of using the significant processing power of the human brain to identify patterns, but suffer from issues such as lack of scaling to large surveys and potential issues with replicability and calibration.
+Automated measurements, both parametric \citep{pen02a,sim11,lac12} and non-parametric \citep{abr03,con03,lot04,sca07,bam08,fre13}, scale well to very large sample sizes, but do not always fully capture the relevant features, especially for asymmetric galaxies that become increasingly common at high redshifts.
 The Galaxy Zoo project \citep{lin08,lin11} utilizes crowdsourced visual classifications to measure galaxies in color-composite images.
 The efforts of more than $2\times10^5$~classifiers allow for multiple independent classifications of each image which are combined and calibrated to give a distribution of vote fractions proportional to the probability of a feature being visible.
-While the crowdsourced data require extensive calibration \citep{bam09,wil13}, they have a proven reliability and have been used in dozens of papers \citep[eg,][]{lan08,bam09,dar10,mas11c,ski12,sim13,sch14,wil15}.
+While crowdsourced data require extensive calibration \citep{bam09,wil13}, they have a proven reliability and have been used in dozens of papers \citep[eg,][]{lan08,bam09,dar10,mas11c,ski12,sim13,sch14,wil15}.
 
@@
 GZH used a similarly detailed classification scheme, but focused for the first time on images of high-redshift galaxies taken with the \hubble.
-The Galaxy Zoo: CANDELS project also classified morphologies of galaxies at high redshift using ACS and WFC3 imaging (Simmons et~al., submitted).
+The Galaxy Zoo: CANDELS project has also classified morphologies of galaxies at high redshift using ACS and WFC3 imaging (Simmons et~al., submitted).
 
@@
 \center
-\caption{Summary of Galaxy Zoo: Hubble imaging \label{tbl:gzh_numbers}}
+\caption{Summary of GZH imaging \label{tbl:gzh_numbers}}
 \begin{tabular}{lclcrr}
@@
 The deeper GOODS images were created using the arithmetic mean of \Bband{} and \Vband{} in the blue channel, \Iband{} in the red channel, and \zband{} in the green channel.
-These images also had the speckled noise pixels decolorized.
+These images also had their speckled noise pixels decolorized.
 
@@
 For these galaxies, we created ``pseudocolor'' images by using the ACS \Iband{} data as the illumination map and ground-based imaging from the \subaru{} telescope in $B_J$, $r^+$, and $i^+$ filters to provide the color gradients \citep[see][for further details]{gri12}.
-This means that the images have the angular resolution of \hst{} ($\sim0.05$~\arcsec/pixel) for the overall intensity, but the color gradients are at ground-based resolution, with seeing between 0.95\arcsec and 1.05\arcsec \citep{tan07}.
-
-The Stripe~82 single-epoch images were taken directly from the color composites on the DR7 SDSS Skyserver, which combines $g^{\prime}$, $r^{\prime}$, and $i^{\prime}$ exposures into the RGB channels.
+This means that the images have the angular resolution of \hst{} ($\sim0.05$~\arcsec/pixel) for the overall intensity, but the color gradients are at ground-based resolution, with seeing between 0.95\arcsec{} and 1.05\arcsec{} \citep{tan07}.
+
+Stripe~82 single-epoch images were taken directly from the color composites on the DR7 SDSS Skyserver, which combines $g^{\prime}$, $r^{\prime}$, and $i^{\prime}$ exposures into the RGB channels.
 The co-added Stripe~82 images were assembled from runs 106 and 206 in DR7 and made into color composites using the method of \citet{lup04}.
 
-To deal with images in which the sky noise was highly colored (which might have been a distraction to visual classification), a soft-edged object mask was applied that preserves the color balance for galaxies, but desaturates the speckled noise against regions of blank sky.
-This technique was applied only to the coadded Stripe~82 and the COSMOS images.
+To deal with images in which the sky noise was highly colored (which might have been a distraction to visual classification), a soft-edged object mask was applied that preserves the color balance for galaxies, but desaturates speckled noise against regions of blank sky.
+This technique was applied only to the co-added Stripe~82 and the COSMOS images.
 
@@
 This includes photometric parameters such as the fluxes, magnitudes, radii, ellipticities, position angles, and positions drawn from both \sextractor{} and \galfit.
-\galfit{} also provides the parametric S\'{e}rsic index and effective half-light radius for the best-fit model.
+\galfit{} also provides the parametric \sersic{} index and effective half-light radius for the best-fit model.
 All parameters are measured in both bands of the ACS imaging, with the exception of the single-band COSMOS images.
@@
 Redshifts used for the SDSS galaxies are all spectroscopic.
-82.6\% of galaxies in the single-depth images and 65.1\% of galaxies in the coadd images have a measured DR7 spectroscopic redshift.
-
-\section{Galaxy Zoo interface and classifications}\label{sec:interface}
+82.6\% of galaxies in the single-depth images and 65.1\% of galaxies in the co-add images have a measured DR7 spectroscopic redshift.
+
+\section{GZH interface and classifications}\label{sec:interface}
 
@@
 
-Classifications for a particular user are aggregated and weighted only if they were logged into GZH under their username (which is encouraged by not required for participation).
+Classifications for a particular user are aggregated and weighted only if they were logged into GZH under their username (which is encouraged, but not required for participation).
 Classifications by users not logged in are marked as ``Anonymous''; no weighting is applied to these classifications, but they are otherwise treated identically in the data processing.
@@
 \includegraphics[width=160mm]{figures/gzh_interface.png}
-\caption{Screenshot of the Galaxy Zoo: Hubble interface (\url{http:/zoo3.galaxyzoo.org}) at the beginning of a classification, with the user ready to select an answer for the first question in the decision tree.\label{fig:interface}}
+\caption{Screenshot of the GZH interface (\url{http:/zoo3.galaxyzoo.org}) at the beginning of a classification, with the user ready to select an answer for the first question in the decision tree.\label{fig:interface}}
 \end{figure*}
@@
 The GZH decision tree has four broad sets of morphologies classified by the users.
-The first option is designating the object as a star or artifact (the result of either bad data or incorrect classification by the ACS pipeline as a galaxy); in this case, the classification ends and no further questions are asked.
-The second set are smooth galaxies, intended to identify ellipticals/early-types; users also measure the relative axial ratio (roundness) for these galaxies.
+The first option is designating the object as a star or image artifact (the result of either bad data or incorrect classification by the ACS pipeline as a galaxy); in this case, the classification ends and no further questions are asked.
+The second set are smooth galaxies, intended to select ellipticals/early-types; users also measure the relative axial ratio (roundness) for these galaxies.
 The third set is for disk/late-type galaxies, which measures the features necessary to place a galaxy on the standard Hubble tuning fork (bars, spiral arm, strength of the central bulge).
 The final set, which is new to the high-redshift targets in GZH, asks users to identify objects dominated by clumpy morphologies.
-Further annotation for these galaxies includes assessing the number, arrangement, relative brightness, and location of the clumps within the galaxy.
-Finally, every classification of a galaxy gives users the option of annotating ``odd'' features within the image; these labels are for relatively rare $(\lesssim1\%)$ phenomena, including dust lanes, gravitational lenses, and major mergers.
+Further annotations for these galaxies includes assessing the number, arrangement, relative brightness, and location of the clumps within the galaxy.
+Finally, every classification of a galaxy gives users the option of identifying ``odd'' features within the image; these labels are for relatively rare $(\lesssim1\%)$ phenomena, including dust lanes, gravitational lenses, and mergers.
 
@@
 The remainder of the images either had a later activation date (COSMOS, simulated AGN) or by a lower retirement limit (the low-redshift SDSS Stripe~82 galaxies).
-Images from these samples have a median of 46-48~classifications per image (Figure~\ref{fig:classification_hist}).
+Images from these samples have a median of 46--48~classifications per image (Figure~\ref{fig:classification_hist}).
 
@@
 \includegraphics[width=0.5\textwidth]{figures/classification_hist.pdf}
-\caption{Distribution of the total number of classifications per image for GZH, split by the survey types.}
+\caption{Distribution of the total number of classifications per image for GZH, split by survey.}
 \label{fig:classification_hist}
@@
 Images from COSMOS and the simulated AGN were activated in Dec 2010, as well as a small sample of AEGIS/GEMS/GOODS images mistakenly excluded from the original sample based on an overly restrictive cut on blended and/or saturated objects.
-The main site operated until the launch of the Galaxy~Zoo:~CANDELS project on 10~Sep~2012.
-Classifications for the GOODS 5-epoch images were obtained with the fourth version of the site\footnote{\url{http://www.galaxyzoo.org}} from Mar-Jun 2015.
+The main GZH site collected data until its replacement, the Galaxy~Zoo:~CANDELS project, began on 10~Sep~2012.
+Classifications for the GOODS 5-epoch images were separately obtained with the fourth version of the site\footnote{\url{http://www.galaxyzoo.org}} from Mar-Jun 2015.
 The GZH project had a total of 10,349,357~classifications from 93,898 registered participants.
@@
 The previous versions of Galaxy Zoo morphology classifications \citep{lin08,wil13} were based on observations of galaxies in the Sloan Digital Sky Survey (SDSS) which have a median redshift of $z<0.2$.
-In these cases, it was assumed that there was no cosmological evolution of the morphologies of galaxies and therefore any observed changes in the distribution of galaxies with different consensus morphologies was due to the effects of redshift on the image quality (\ie.
-the reduction in physical resolution, surface brightness dimming, etc).
+In these cases, it was assumed that there was no cosmological evolution of the morphologies of galaxies and therefore any observed changes in the distribution of galaxies with different consensus morphologies was due to the effects of redshift on the image quality (\ie, the reduction in physical resolution, surface brightness dimming, etc).
 For both previous releases of GZ morphologies, a correction for redshift-dependent bias was applied based on matching the classification fractions at the highest redshifts with those at the lowest redshift.
@@
 In the GZH samples, the redshift range is large enough that cosmological evolution of the types and morphologies of galaxies is expected for galaxies in the sample.
-As a result, the previous methods of correcting for redshift dependent bias will not work.
+As a result, the previous methods of correcting for redshift dependent bias do not work.
 In addition, the effects of band shifting will change the images even more across these redshift ranges.
@@
 The input images are from the SDSS \citep{yor00,str02} and are processed using the \ferengi{} code \citep{bar08a} to match the observational properties of the \hst{} surveys out to $z=1$.
-These images were classified in the Galaxy Zoo interface using the same classification scheme as the original \hst{} images.
+These images were classified in the GZH interface using the same classification scheme as the original \hst{} images.
 
@@
 \ferengi{} was run on the images for values of $e$ starting from $e=0$ and decreasing to $e=-3.5$ in increments of $\Delta e = 0.5$.
-Figure~\ref{fig:exampleFERENGI} shows several examples of the effects of ``losing`` spiral/disc features with increasing redshift for two galaxies with $e=0$.
-
-The final number of \ferengi{} images produced for each galaxy is ultimately a function of galaxy's redshift, since the new images cannot be resampled at better angular resolution than the original SDSS data, as well as the number of $e$ values selected.
-Table~\ref{tbl:ferengivalues} summarizes the total sample of redshifted images produced for GZH.
+Figure~\ref{fig:exampleFERENGI} shows several examples of the effects of ``losing'' spiral/disc features with increasing redshift for two galaxies with $e=0$.
+
+The final number of \ferengi{} images produced for each galaxy is ultimately a function of galaxy's redshift (since the new images cannot be resampled at better angular resolution than the original SDSS data), as well as the number of $e$ values selected.
+Table~\ref{tbl:ferengivalues} summarizes the redshifted images produced for GZH.
 
@@
 
-\subsection{Correcting GZH morphologies for classification bias}\label{ssec:zeta}
+\subsection{Correcting morphologies for classification bias}\label{ssec:zeta}
 
@@
 This is controlled by two types of parameters: \textbf{intrinsic} properties of the galaxy itself, such as its physical diameter and luminosity, and \textbf{extrinsic} properties, such as the distance (redshift) of the galaxy and its relative orientation.
-There are likely other parameters that affect user accuracy, such as the proximity of close companions \citep[``distraction bias''; see][]{joh15} or bias as a function of the individual user.
-The combination of all such parameters forms a high-dimensional space, and there are insufficient data to measure their individual effects.
-Instead, this method uses only two parameters intended to capture the bulk of the change in bias (based on GZ1/GZ2): the $r^\prime$-band surface brightness ($\mu_r$; intrinsic) and redshift ($z$; extrinsic).
+There are likely other parameters that affect user accuracy, such as the proximity of close companions \citep[``distraction bias''; see][]{joh15} or bias as a function of individual user ability and skill.
+The combination of all such parameters forms a high-dimensional space, and it is not clear how to separate this into individual effects.
+Instead, the method used here employs only two parameters intended to capture the bulk of the change in bias: the $r^\prime$-band surface brightness ($\mu_r$; intrinsic) and redshift ($z$; extrinsic).
 
@@
 \noindent where $f_{\mu,z=0.3}$ is the ``calibrated'' vote fraction at the lowest redshift in the \ferengi{} bins ($z=0.3$) and $\zeta$ is a positive parameter that controls the rate at which $f$ decreases with increasing redshift.
-This formula fits the data relatively well (with almost no exceptions, the vote fractions for featured galaxies decrease monotonically with increasing redshift), and the exponential function bounds the observed vote fractions between $f_{\mu,z=0.3}$ and zero.
-Figure~\ref{fig:zeta_examples} show examples of the change in vote fraction and their fits to Equation~\ref{eqn:fzeta} for a random selection of galaxies in the \ferengi{} images.
+This formula fits the data relatively well (with very few exceptions, the vote fractions for featured galaxies decrease monotonically with increasing redshift), and the exponential function bounds the observed vote fractions between $f_{\mu,z=0.3}$ and zero.
+Figure~\ref{fig:zeta_examples} shows the change in vote fraction and the fit to Equation~\ref{eqn:fzeta} for a random selection of galaxies in the \ferengi{} images.
 
@@
 
-Figure~\ref{fig:zeta_mu} shows the results of fitting the \ferengi{} images with Equation~\ref{eqn:fzeta}; the correction is a weak function of galaxy surface brightness.
+Figure~\ref{fig:zeta_mu} shows the results of fitting the \ferengi{} images with Equation~\ref{eqn:fzeta}; the correction is only a weak function of surface brightness ($\mu$).
 Higher-surface brightness galaxies have stronger average corrections, likely because these galaxies are more likely to have larger $f_\textrm{features}$ values at high redshifts.
-Low surface brightness galaxies are more likely to begin low and remain low; the bounded nature of the dropoff (and Poissonian-like variance among the individual voters) means that the average magnitude of $\zeta$ will be less.
+Low surface brightness galaxies are more likely to begin low and remain low; the bounded nature of the dropoff (and variance among the individual voters) means that the average magnitude of $\zeta$ will be lower.
 
@@
 \begin{equation}
-f_\textrm{features,debiased} = 1 - (1 - f)e^{\frac{z-z_0}{\hat\zeta}}.
+f_\textrm{features,debiased} = 1 - (1 - f_\mathrm{features,weighted})e^{\frac{z-z_0}{\hat\zeta}}.
 \label{eqn:fzeta_mod}
@@
 In this analysis, only galaxies whose lowest simulated redshift image was $z_\mathrm{sim}=0.3$ were used (see Table \ref{tbl:ferengivalues}), and only those which had detectable surface brightness measurements in \sextractor; this includes 3,950 of the total 6,466 images.
-For each simulated redshift value $z$, and at a fixed surface brightness $\mu$, \ffeaturesz, the value measured at that simulated redshift, is plotted against \ffeaturesrest, the value measured for the same galaxy imaged at $z=0.3$.
+For each simulated redshift value \zsim{} at a fixed surface brightness $\mu$, \ffeaturesz, the value measured at that simulated redshift, is plotted against \ffeaturesrest, the value measured for the same galaxy at \zsim$=0.3$.
 
@@
 
-The criteria for determining whether a region of this space is single-valued, and therefore correctable, is as follows: In each surface brightness and redshift bin, the relationship between \ffeaturesz{} and \ffeaturesrest{} is modeled by fitting the data with a polynomial of degrees $n=3$, 2, and 1, and using the best fit out of the three.
+The criteria for determining whether a region of this space is single-valued, and therefore correctable, is as follows: In each surface brightness and redshift bin, the relationship between \ffeaturesz{} and \ffeaturesrest{} is modeled by fitting the data with a polynomial of degrees $n=3$, 2, and 1, and using the best formal fit out of the three as measured by the sum of the residuals.
 These fits are shown as the dashed black lines in Figure~\ref{fig:6a}.
@@
 While the appropriate correctable regions were defined discretely, the true correctable region is assumed to be a smooth function of $z$, $\mu$, and \ffeatures{}.
-To define this smooth space, a convex hull is generated that encloses the correctable and lower-limit \ferengi{} galaxies in $z$-$\mu$-\ffeatures{} space.
+To define this smooth space, we calculate the shape of the convex hull that encloses the correctable and lower-limit \ferengi{} galaxies in $z$-$\mu$-\ffeatures{} space.
 The boundaries are then adjusted until the contamination from both groups is minimized.
 The resulting hulls define the correctable and lower-limit regions for categorizing the \hst{} galaxies.
-The results of this method and final categorization of the \hst{} sample is displayed in Table~\ref{tbl:hubble_debiasable}.
-Of the galaxies at redshift higher than $z=0.3$, 17\% can be debiased using the $\zeta$ method, 27\% cannot be debiased, and 56\% cannot have the potential for a correction determined, due either a lack of redshift for the host galaxy or insufficient \ferengi{} images corresponding to the relevant $z$-$\mu$ values.
+The results of this method and final categorization of the \hst{} sample are in Table~\ref{tbl:hubble_debiasable}.
+Of the galaxies at redshift higher than $z=0.3$, 17\% can be debiased using the $\zeta$ method, 27\% cannot be debiased, and 56\% cannot have the potential for a correction determined, due either to an unknown redshift or insufficient \ferengi{} images corresponding to the relevant $z$-$\mu$ values.
 
@@
 Few galaxies in the sample have sufficiently high corrections to completely change them from being confidently smooth to featured following the bias correction (Figure~\ref{fig:debiased_corrections}).
-As a check, highly boosted galaxies are compared to the expert classifications in the CANDELS catalog \citep{kar15}.
+As a check, highly boosted galaxies are compared to the expert classifications in CANDELS \citep{kar15}.
 There are only eight galaxies that were strongly boosted (\ffeatures$<0.2$ and \fbest$>0.5$) in GZH and also appears in the CANDELS expert sample.
-Of those eight galaxies, \citet{kar15} classifies 5 as spheroids, 2 as disks, and 1 as irregular/disky.
+Of those eight galaxies, \citet{kar15} classify 5 as spheroids, 2 as disks, and 1 as irregular/disky.
 The \fbest{} values for GZH are all between 0.5 and 0.6, making them intermediate disk candidates.
-One of the spheroids has hints of an interaction or minor merger to the south that may have been missed by the CANDELS experts, but almost all images are dim and with very low surface brightnesses in the ACS imaging, making positive identification challenging.
+One of the spheroids has a hint of extended emission to the south that may have been missed by the CANDELS experts, but almost all images are dim and with very low surface brightnesses in the ACS imaging, making positive identification challenging.
 Since the surveys use different rest-frame filters and the overlap sample is tiny, though, detailed comparisons between the overall morphologies are highly difficult.
@@
 As with the HST images, each \ferengi{} subject has a varying number of users answering the various questions in the hierarchical decision tree.
-Every user answers the first question, {\it ``Is the galaxy smooth and rounded, with no sign of a disk?''}; as such the vote fractions \fsmooth, \ffeatures, and \fartifact{} are all computed with the minimum statistical error for any question, with roughly 40 total answers (see Section~\ref{sec:interface}).
+Every user answers the first question, {\it ``Is the galaxy smooth and rounded, with no sign of a disk?''}; as such the vote fractions \fsmooth, \ffeatures, and \fartifact{} are all computed with the minimum statistical error for any question, with between 40 and 140~responses (see Section~\ref{sec:interface}).
 The number of users to answer any subsequent question, however, is always equal to or less than the number to answer the preceding question.
@@
 Two otherwise morphologically identical galaxies which differ significantly in redshift, brightness, or size may result in very different vote fractions for any given question, given that many features of a galaxy are difficult to discern in less-resolved images (bars, spiral arms, disk structure, etc).
-For this reason, it is necessary to take caution utilizing vote fractions as cut-offs to determine morphological structure; guidelines for careful classification are given in Section~\ref{sec:cookbook}.
+For this reason, caution must be used when taking vote fractions as cut-offs to determine morphological structure; guidelines for careful classification are given in Section~\ref{sec:cookbook}.
 
 The GZH catalog is corrected for classification bias only for the first question of the GZH decision tree (Section~\ref{sec:debiasing}), which asks {\it ``Is the galaxy smooth and round, with no sign of a disk?''} For this question, the catalog provides the additional parameters $\tt debiased$, $\tt lower~limit$, $\tt upper~limit$, and $\tt best$ vote fractions.
-The $\tt best$ fraction for \ffeatures{} is chosen based on the categorization of the galaxy: if it is ``correctable'', $\tt best = debiased$, if a lower limit, $\tt best = lower~limit$, and if neither, $\tt best = weighted$.
-
-The debiased and best vote fractions for \fsmooth{} were calculated on the criteria that vote fractions for all answers must sum to unity, such that:
+The $\tt best$ fraction for \ffeatures{} is chosen based on the categorization of the galaxy: if it is ``correctable'', $\tt best = debiased$; if it is a lower limit, $\tt best = lower~limit$; if neither condition applies, then $\tt best = weighted$.
+
+The debiased and best vote fractions for \fsmooth{} are calculated on the criteria that vote fractions for all answers must sum to unity:
 
@@
 f_\mathrm{smooth} \equiv 1 - f_\mathrm{features,best} - f_\mathrm{artifact}.
-\label{eqn:nonlinear}
+\label{eqn:constraint}
 \end{equation}
 
-\noindent In rare cases ($<1\%$ of the sample), this requirement resulted in negative vote fractions for \fsmooth; these were cases in which the \ffeatures{} vote fraction was boosted to a high value relative to the \fartifact{} vote fraction.
-In these cases, the constraint that the vote fractions must sum to 1 is met by setting \fsmooth$=0.0$ and decreasing \fbest{} accordingly.
+\noindent In rare cases ($<1\%$ of the sample), this requirement resulted in negative vote fractions for \fsmooth; these were cases in which the \ffeatures{} vote fraction was boosted to a high value relative to \fartifact.
+In these cases, the constraint of Equation~\ref{eqn:constraint} is met by setting \fsmooth$=0.0$ and decreasing \fbest{} accordingly.
 This correction is typically small, with a median decrease/increase of $f_\mathrm{features}/f_\mathrm{smooth}$ of $\Delta f = 0.04$.
@@
 Tables~\ref{tbl:stripe82_single} and \ref{tbl:stripe82_coadd} contain data for the SDSS Stripe~82 single-depth and co-added images, respectively, that were classified using the GZH interface and decision tree.
-Finally, Table~\ref{tbl:simulated_agn} contains classifications for images with artificial point sources intended to simulate the effect of a bright AGN, as used in \citet{sim14}.
+Finally, Table~\ref{tbl:simulated_agn} contains classifications for images with artificial point sources intended to simulate the effect of a bright AGN (see \citealt{sim14} for an example).
 
@@
 \tablewidth{0pc}
-\tablecaption{GZH morphological classifications for SDSS Stripe 82 coadded images\label{tbl:stripe82_coadd}} 
+\tablecaption{GZH morphological classifications for SDSS Stripe 82 co-added images\label{tbl:stripe82_coadd}} 
 \tabletypesize{\scriptsize}
@@
 In GZH, volunteers answer questions about a galaxy's morphology in a decision tree format.
-With this structure, questions shown to a user are dependent on their answers to the previous questions.
-For example, a user is only asked Task~11, {\it ``How many spiral arms?''} if they had answered ``yes'' to Task~10, which asks whether any spiral arms are present.
-This structure is used to reduce the workload of the users by only asking questions relevant to the particular galaxy; in this example, it would not be useful, nor would it make physical sense, to ask a user how many spiral arms in a galaxy which they had declared had no spiral arms to begin with.
+With this structure, questions shown to a user are dependent on their answers to the previous questions (Section~\ref{ssec:interface}).
 Figure~\ref{fig:decisiontree} shows the possible paths available for answering the questions offered in GZH.
@@
 
-The flexibility of this catalog allows the user to set their own selection criteria for vote fraction thresholds to create a morphologically-pure sample.
+The flexibility of this catalog allows the user to set their own selection criteria for vote fraction thresholds to create a morphologically pure sample.
 Table~\ref{tbl:thresholds} provides baseline cuts for selecting galaxies of a variety of morphologies.
@@
 
-As an example of how to use Table~\ref{tbl:thresholds} to create a sample of 3-armed spirals galaxies, one should select objects with $N_{arm~number} \ge 20$, \ffeatures$>0.23, f_{\rm clumpy,no} > 0.30, f_{edgeon,no}>0.25$, and $f_{spiral,yes}>0.25$.
-These cuts define a sample of galaxies of ``arm number candidates''; ie galaxies for which answering the arm number question makes physical sense and the vote fraction $f_{\rm arm~number}$ is well-sampled.
-In this example, such galaxies are featured, non-clumpy, non-edge~on, spiral galaxies.
+As an example of how to use Table~\ref{tbl:thresholds} to create a sample of 3-armed spirals galaxies, we suggest selecting objects with $N_{arm~number} \ge 20$, \ffeatures$>0.23, f_{\rm clumpy,no} > 0.30, f_{edgeon,no}>0.25$, and $f_{spiral,yes}>0.25$.
+These cuts define a sample of galaxies of ``arm number candidates''; \ie, galaxies for which answering the arm number question makes physical sense and the vote fraction $f_{\rm arm~number}$ is well-sampled.
+In this example, such galaxies are featured, non-clumpy, non-edge~on spirals.
 At this point a cut can be made on $f_{\rm arm~number=3}$ to select spirals with three arms.
@@
 Clumps are known to be a characteristic feature of galaxies outside the local universe, and there is evidence they play a crucial role in the evolution of modern spirals, particularly in the formation of central bulges \citep{elm05,elm14,guo15,beh16}.
-Simulations show clumps migrate from the outer disk to the galactic center on relatively short (a few orbital periods) timescales \citep{man15} and observations show increasing bulge to clump mass and density ratios as the universe evolves since $z\sim 1.5$ \citep{elm09}, suggesting that clumps coalesce over time to form the modern bulges of disk galaxies.
+Simulations show clumps migrate from the outer disk to the galactic center in only a few orbital periods \citep{man15} and observations show increasing bulge to clump mass and density ratios as the universe evolves since $z\sim 1.5$ \citep{elm09}, suggesting that clumps coalesce over time to form the modern bulges of disk galaxies.
 GZH added a ``clumpy'' path to the decision tree for the purpose of both identifying clumps and investigating their evolution with redshift.
@@
 \begin{table}
-\caption{Suggested thresholds for selecting morphological samples from Galaxy Zoo: Hubble. \label{tbl:thresholds}}
+\caption{Suggested thresholds for selecting morphological samples from GZH. \label{tbl:thresholds}}
 \begin{tabular}{llll}
@@
 
-Figure~\ref{fig:sankey} shows the breakdown of morphologies for the combined surveys in GZH as a Sankey~diagram, where each node represents a task and the flows between the nodes represent the possible responses.
+Figure~\ref{fig:sankey} shows the breakdown of morphologies for the combined surveys in GZH as a flow~diagram, where each node represents a task and the flows between the nodes represent the possible responses.
 The width of the flows is proportional to the number of galaxies associated with that response; Figure~\ref{fig:sankey} uses a simple plurality vote to assign the combined set of labels for each galaxy.
@@
 
-Morphologies for GEMS galaxies were measured by \citet{hau07}, who use single-component \sersic{} fits to the F850LP imaging.
-This analysis uses parameters from the \galfit{} code, which \citet{hau07} evaluated as more reliable than \gimtwod{} for GEMS due to the ability to fit multiple galaxies in crowded fields.
+Morphologies for GEMS galaxies were measured by \citet{hau07}, who used single-component \sersic{} fits to the F850LP imaging.
+This analysis used parameters from the \galfit{} code, which \citet{hau07} evaluated as more reliable than \gimtwod{} for GEMS due to the ability to fit multiple galaxies in crowded fields.
 A 1\arcsec~positional match for the GEMS galaxies in Table~9 in \citet{hau07} to the GZH sample gives 8,846~galaxies in both \citet{hau07} and GZH.
@@
 AEGIS galaxies were morphologically classified using non-parametric measurements by \citet{lot08}.
-This method uses a combination of the Gini coefficient ($G$), which measures the relative inequality in pixel brightness, and $M_{20}$, the second-order moment of the brightest 20\% of the light \citep{lot04}.
-A linear combination of $G$ and $M_{20}$ delineates their three broad categories of galaxy morphology: E/S0/Sa (``elliptical''), Sb/Sc/Ir (``spiral''), and mergers (``irregular'').
+This method used a combination of the Gini coefficient ($G$), which measures the relative inequality in pixel brightness, and $M_{20}$, the second-order moment of the brightest 20\% of the light \citep{lot04}.
+A linear combination of $G$ and $M_{20}$ delineates three broad categories of galaxy morphology: E/S0/Sa (``elliptical''), Sb/Sc/Ir (``spiral''), and mergers (``irregular'').
 A 1\arcsec{} positional match on AEGIS and GZH yields 4,031 galaxies with reliably-measured morphologies and $S/N>3$ in both $V$- and $I$-bands.
@@
 
-COSMOS galaxies have multiple published datasets automatically classifying their morphologies, all using a variation of non-parametric measurements.
-\citet{cas07} use a combination of concentration ($C$), asymmetry ($A$), $G$, and $M_{20}$ \citep{cas05} to classify all galaxies with $m_\mathrm{I,petro}<25$, and use an empirical division based on several hundred training images to assign galaxies to discrete morphological categories.
+COSMOS galaxies have multiple published datasets automatically classifying morphology, all using a variation of non-parametric measurements.
+\citet{cas07} used a combination of concentration ($C$), asymmetry ($A$), $G$, and $M_{20}$ \citep{cas05} to classify all galaxies with $m_\mathrm{I,petro}<25$, and used an empirical division based on several hundred training images to assign galaxies to discrete morphological categories.
 A similar method is employed by \citet{tas11}, using the same non-parametric indices but with a different method of calculating the Petrosian radius and total light profile.
 They employ a nearest-neighbors method is used to assign morphological categories for the entire sample based on a small training set.
-\citet[][ZEST]{sca07} use $C$, $A$, $G$, $M_{20}$, the galaxy ellipticity ($\epsilon$), and \sersic{} index ($n$) to quantify the galaxy shapes; a principal component analysis is used to assign galaxies to discrete morphological categories.
+\citet[][ZEST]{sca07} used $C$, $A$, $G$, $M_{20}$, the galaxy ellipticity ($\epsilon$), and \sersic{} index ($n$) to quantify the galaxy shapes; a principal component analysis is used to assign galaxies to discrete morphological categories.
 The categories in all three methods are split into ellipticals, spirals, and peculiar/irregulars.
@@
 Figure~\ref{fig:comparisons} shows the proportion of galaxies as split by their automated/expert visual morphologies for each of the six catalogs matched to GZH.
-The relation between GZH and the automated/expert morphologies is shown to vary significantly for different surveys --- this may be due to intrinsic differences in the galaxies, in the techniques used to measure morphology, or both.
+The relation between GZH and the automated/expert morphologies is shown to vary significantly for different surveys --- this could be due to intrinsic differences in the galaxies, in the techniques used to measure morphology, or both.
 The distribution of \fbest{} for AEGIS galaxies is essentially flat for spirals, showing almost no difference in proportion at the highest and lowest ends.
-Early-type galaxies are at their highest proportion at \fbest$\sim0$, but constitute only 40\% of the galaxies at most.
+Early-type galaxies are at their highest proportion at \fbest$\sim0$, but constitute at most only 40\% of galaxies.
 In contrast, GOODS galaxies at low \fbest{} are dominated by early-types, although spiral and irregular galaxies have comparable sizes as low as \fbest$\sim0.2$.
@@
 
-Finally, we note that there are 7,681~galaxies in the GOODS-S field with morphological classifications in both GZH and the Galaxy~Zoo:~CANDELS project (Simmons et~al., submitted).
+Finally, there are 7,681~galaxies in the GOODS-S field with morphological classifications in both GZH and the Galaxy~Zoo:~CANDELS project (Simmons et~al., submitted).
 Since both the sensitivity and filters for the two sets of images differ (and there is no debiased correction applied to GZC), there is no prior reason to expect a perfect correlation between the separate vote fractions for the projects.
@@
 Galaxies in GZH show significant changes in the disk/elliptical fraction as a function of redshift, along with an increasing number of galaxies dominated by smaller clumps and presumed to be in the process of building up their baryonic mass through a combination of hierarchical merging and in-situ star formation.
-While the majority of scientific interpretation is left to future work, this paper confirms the decrease in observed bar fraction with increasing redshift \citep{mel14} and identify a new way for identifying clumpy galaxies as a function of clump multiplicity.
+While the majority of scientific interpretation is left to future work, this paper confirms the decrease in observed bar fraction with increasing redshift \citep{mel14} and identifies a new way for selecting clumpy galaxies as a function of clump multiplicity.
 
@@
 GZH used both 5-epoch and 2-epoch sets of data to construct the GOODS set of images.
-The 11,157 full depth 5-epoch images are used in the main catalog; the classifications for the 7,464 shallow depth 2-epoch images are offered as a supplementary table.
+The 11,157 full depth 5-epoch images are used in the main catalog; the classifications for the 7,464 shallow depth 2-epoch images are provided as a supplementary table.
 This section analyzes the effect of image depth on the ability of the GZ users to identify features or disk structure in the images.
@@
 Figure~\ref{fig:shallow_vs_full} shows a strong correlation between \ffeatures{} for both sets of images.
-The mean change in \ffeatures{} from the shallow to full depth images  $f_\mathrm{features,full} - f_{features,shallow} \equiv \Delta p = 0.00$, with a standard deviation of $\sigma = 0.17$.
-While there is some variance in $\Delta p$ in the whole sample, the change is usually small and not often significant enough to change a morphological classification.
+The mean change in \ffeatures{} from the shallow to full depth images  $f_\mathrm{features,full} - f_{features,shallow} \equiv \Delta f = 0.00$, with a standard deviation of $\sigma = 0.17$.
+While there is some variance in $\Delta f$ in the whole sample, the change is usually small and not often significant enough to change a morphological classification.
 Defining a clean sample of disk galaxies as those with \fbest$>0.8$, elliptical galaxies as those with $f_\mathrm{smooth,best}<0.2$, and intermediate as those in between, 75\% of the sample would not change morphology.
@@
 \hline\hline
-shallow to full morphology    & N       & \%       & $<\Delta p>$ & $<z>$ \\
+shallow to full morphology    & N       & \%       & $<\Delta f>$ & $<z>$ \\
 \hline
@@
 Here we show an example of results obtained for the bar Task.
-Figure~\ref{fig:f_vs_fbar} shows that both the low sample rate and the degree of scatter in each bin inhibit fitting a reliable function that predicts $f_\mathrm{bar,z=0.3}$.
+Figure~\ref{fig:f_vs_fbar} shows that both the low sample rate and the degree of scatter in each bin inhibit fitting a reliable function that predicts $f_{{\rm bar},z=0.3}$.
 Table~\ref{tbl:ferengi_bar} summarizes the correction types for the \ferengi{} data; 71\% of the galaxies simulated did not meet the GZH requirements for well-sampled vote fractions for $f_\mathrm{bar}$, as compared to 2\% for $f_\mathrm{features}$.
-Similar results were obtained for all higher-order Tasks in GZH, as described in Section~\ref{ssec:higher_order_tasks}.
+Similar results were obtained for all higher-order Tasks in GZH (Section~\ref{ssec:higher_order_tasks}).
 

### 2016-05-11 writeup/gz_hubble_data.tex
abstract edits & comments

@@
 We present the data release paper for the Galaxy Zoo: Hubble (GZH) project.\footnote{This publication has been made possible by the participation of more than 200,000 volunteers in the Galaxy Zoo project.
-Their contributions are individually acknowledged at \url{http://authors.galaxyzoo.org/authors.html}.} This is the third phase in a large effort to measure reliable morphologies of galaxies on detailed scales by using crowdsourced visual classifications of color composite image.
+Their contributions are individually acknowledged at \url{http://authors.galaxyzoo.org/authors.html}.} This is the third phase in a large effort to measure reliable, detailed morphologies of galaxies by using crowdsourced visual classifications of color composite images.
 Images in GZH are selected from various \textit{Hubble Space Telescope} Legacy programs using the Advanced Camera for Surveys (AEGIS, COSMOS, GEMS, GOODS-N, and GOODS-S), with filters selected to probe the rest-frame optical emission from galaxies out to $z\simeq1$.
@@
 The GZH catalog includes both the raw and calibrated morphological vote fractions for $150,771$ galaxies, providing a comprehensive data set suitable for large-scale studies of galaxy evolution.
+% didn't the GOODS-N and GOODS-S second phases go deeper than 23.5 mag? am I misremembering? --BDS
 

### 2016-05-12 writeup/gz_hubble_data.tex
Steven's suggested edits for section 1

--- 2016-05-09 writeup/gz_hubble_data.tex
@@
 The galaxies selected for GZH classifications go down to magnitude limits of $m_{I814W}<23.5$ and have a median redshift of $\langle z\rangle=0.9\pm0.6$, with a tail extending out to $z\simeq4$.
-The GZH morphological data includes measurements of both bulge- and disk-dominated galaxies, details on spiral disk structure that relate to the Hubble type, and numerous measurements of clump identification and geometry.
+The GZH morphological data includes measurements of both bulge- and disk-dominated galaxies, details on spiral disk structure that relate to the Hubble type, as well as clump identification and geometry.
 This paper also describes and employs a novel method for calibrating morphological bias by using artificially-redshifted galaxy images as a baseline.
@@
 
-The morphology of galaxies encodes information on the orbital parameters and assembly history of the contents, including gas, dust, stars, and the central black hole.
-The morphology is also closely related to the local environment of the galaxy, as mutual interactions such as tides, shocks in cluster environments and direct mergers can all change the shape of the galaxy's gravitational potential.
-For $M^\star$~galaxies in the local Universe, this typically manifests at the most basic level as the difference between bulge-dominated, virialized systems resembling ellipticals (early-types) and disk-dominated, rotationally-supported disks (late-types) frequently exhibiting spiral arms.
+The morphology of galaxies encodes information on the orbital parameters and assembly history of their contents, including gas, dust, stars, and the central black hole.
+The morphology is also closely related to the local environment of a galaxy, as interactions such as tides, shocks in cluster environments and direct mergers can all influence a galaxy's internal structure.
+For $M^\star$~galaxies in the local Universe, this interplay between the physical development of a galaxy and its external appearance typically manifests at the most basic level as the difference between bulge-dominated, virialized systems resembling ellipticals (early-types) and disk-dominated, rotationally-supported systems (late-types) frequently exhibiting spiral arms.
 This dichotomy has been used to explore much of the astrophysics governing galaxy formation and evolution, and has been shown to be closely linked with other galactic properties such as stellar mass, halo mass, bolometric luminosity, black hole activity, effective radius, and the relative ages of the stellar populations.
@@
 The advent of larger telescopes in an increasing range of observing wavelengths has revealed that the distribution and properties of galaxy morphology have strongly evolved over the lifetime of the Universe.
-At redshift $z\simeq1$ (roughly 6~Gyr after the Big Bang), many galaxies are still in the process of assembling the baryonic mass required to reproduce the structures seen in the present day.
-This occurs in a variety of pathways, including accretion of baryons from large-scale galactic filaments onto halos via streaming, mergers of individual dark matter halos along with their baryons, conversion of gas into stars via gravitational collapse and star formation, etc.
-The process can also be slowed or even reversed via feedback from stellar winds, supernovae, and active black holes.
-Each of these processes affects the galaxy morphology in different ways, and so an accurate measurement of the demographics as a function of redshift provides an extremely powerful observational constraint on the physics involved \citep[for a recent review see][]{con14}.
+At redshift $z\simeq1$ (roughly 6~Gyr after the Big Bang), many galaxies are still in the process of assembling the baryonic and stellar mass required to reproduce the mature, coherent structures seen at the present day.
+This growth occurs via a variety of pathways, including accretion from large-scale galactic filaments onto halos via streaming, mergers of individual halos, conversion of gas into stars via gravitational collapse, etc.
+The accrual of baryons can be slowed or even reversed via feedback from stellar winds, supernovae, and active black holes.
+Each of these processes affects galaxy morphology in different ways, and so an accurate measurement of morphological demographics as a function of redshift provides an extremely powerful observational constraint on the physics involved \citep[for a recent review see][]{con14}.
 
 Theoretical predictions for the morphology of galaxies as a function of redshift are primarily computed within the $\Lambda$CDM cosmological framework.
-Full treatments of this model gravitational interactions between baryons and dark matter, hydrodynamics of the gas, and baryonic physics related to star formation and evolution.
-The most advanced simulations now include volumes up to $\sim100$~Mpc$^3$ while simultaneously resolving the smaller scales necessary to reproduce the baryonic physics \citep{vog14a,sch15}.
+Full treatments model gravitational interactions between baryons and dark matter, hydrodynamics of the gas, and baryonic physics related to star formation and evolution.
+The most advanced simulations now span volumes up to $\sim100$~Mpc$^3$ while simultaneously resolving the smaller ($<1$ kpc) scales necessary to reproduce the influence of baryonic physics \citep{vog14a,sch15}.
 Such simulations predict clustering of galaxies on large scales in a hierarchical assembly model \citep{sil12}.
-The structure of individual galaxies is affected by the merger history \citep{too72,hop10}, local environment \citep[such as the morphology-density relation;][]{dre80}, initial dark halo mass, and many other factors.
-Morphologies of individual simulated high-mass galaxies at $z\sim2-3$ commonly show kpc-scale ``clumpy'' structures and few galaxies that are either smooth or well-ordered spirals; asymmetric profiles with strong density contrasts dominate populations in the early Universe until at least $z\sim1$ \citep{gen14}.
+The structure of individual galaxies is affected by their merger history \citep{too72,hop10}, local environment \citep[such as the morphology-density relation;][]{dre80}, initial dark halo mass, and many other factors.
+Morphologies of individual simulated high-mass galaxies at $z\sim2-3$ commonly show kpc-scale ``clumpy'' structures, with few galaxies that are either smooth or well-ordered spirals; asymmetric profiles with strong density contrasts dominate simulated populations in the early Universe until at least $z\sim1$ \citep{gen14}.
 
 Observational studies of galaxies at high-redshift also display a wide range of morphological types, many of which are rare or absent at $z\sim0$.
-These include spheroids and disks (akin to the ellipticals and spirals seen in the local Universe), but also a significant population of massive, more irregular galaxies, including mergers, tadpoles, chains, double-clumps, and clump-clusters \citep{elm05,elm07,cam11a,for11a,kar15}.
-In contrast, while grand-design spirals have been observed as far back as $z=2.18$ \citep{law12}, their spatial density suggests that they are exceedingly rare, with a very low overall disk fraction \citep{mor13}.
+Although spheroids and disks are present, they are typically much more compact than those in the local Universe.
+There is also a significant population of more irregular, massive galaxies, including mergers, tadpoles, chains, double-clumps, and clump-clusters \citep{elm05,elm07,cam11a,for11a,kar15}.
+In contrast, while grand-design spirals have been observed as far back as $z=2.18$ \citep{law12}, their spatial density suggests that they are exceedingly rare, with a very low fraction of undisturbed disks \citep{mor13}.
 Current observational data thus strongly suggests that the classical Hubble sequence/tuning fork \citep{hub36} is not a suitable framework for characterizing high-redshift morphology.
 
-Space-based observatories, particularly the \hubble, have been responsible for the bulk of imaging studies of high-redshift galaxies.
+Space-based observatories, particularly the \hubble (\hst), have been responsible for the bulk of imaging studies of high-redshift galaxies.
 Observations of fixed fields with very deep imaging \citep[eg,][]{wil96,gia04,bec06,dav07,sco07,gro11} give the photometric sensitivity necessary to detect $L^\star$ galaxies at $z>1$, while also providing the angular resolution to distinguish internal structure and characterize the morphology.
@@
 One of the major difficulties in studying the morphologies of galaxies lies in the techniques used for measurement.
-Visual classification by experts has been used for many years \citep[eg,][]{hub26,dev59,san61,van76,nai10,bai11,kar15}.
+Visual classification by experts has been used for many decades \citep[eg,][]{hub26,dev59,san61,van76,nai10,bai11,kar15}.
 These methods have the advantage of using the significant processing power of the human brain to identify patterns, but suffer from issues such as lack of scaling to large surveys and potential issues with replicability and calibration.
@@
 This paper presents the results from the Galaxy Zoo Hubble (GZH) project.\footnote{\url{http://zoo3.galaxyzoo.org/}} GZH was the third phase of Galaxy Zoo, following its initial results classifying $\sim900,000$~SDSS~images into primarily early/late~types \citep{lin11} and Galaxy~Zoo~2, which covered $\sim250,000$~SDSS~images using a more detailed classification scheme that included bars, spiral arms, and galactic bulges \citep{wil13}.
-GZH used a similarly detailed classification scheme, but focused for the first time on images of high-redshift galaxies taken with the \hubble.
+GZH used a similarly detailed classification scheme, but focused for the first time on images of high-redshift galaxies taken with \hst.
 The Galaxy Zoo: CANDELS project has also classified morphologies of galaxies at high redshift using ACS and WFC3 imaging (Simmons et~al., submitted).
@@
 
-This paper uses the WMAP9 cosmology parameters of $(\Omega_m,\Omega_\Lambda,h)=(0.258,0.718,0.697)$ \citep{hin13}.
+This paper assumes the WMAP9 cosmological parameters of $(\Omega_m,\Omega_\Lambda,h)=(0.282,0.718,0.697)$ \citep{hin13}.
 
@@
 
+KS gratefully acknowledges support from Swiss National Science Foundation Grant PP00P2\_138979/1.
+
 This work is based on (GO-10134, GO-09822, GO-09425.01, GO-09583.01, GO-9500) program observations with the NASA/ESA Hubble Space Telescope, obtained at the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS 5-26555.

### 2016-05-15 python/classification_hist.py
Miscellaneous Python scripts

@@ -1,0 +1,30 @@
+from astropy.io import fits
+from matplotlib import pyplot as plt
+
+data = fits.getdata('/Users/willettk/Astronomy/Research/GalaxyZoo/fits/gz_hst_table.fits',1)
+
+sample = data['sample']
+
+original = (sample == 'original_initial') | (sample == 'original_flagmissed')
+cosmos = (sample == 'cosmos_initial') | (sample == 'cosmos_flagmissed')
+fake_agn = (sample == 'fake_agn_v1') | (sample == 'fake_agn_v1')
+stripe82 =  (sample == 'stripe82') | (sample == 'stripe82_coadd')
+
+fig,ax = plt.subplots(1,1,figsize=(8,8))
+ax.hist(data[original]['t01_smooth_or_features_total_count'],bins=range(170),histtype='step',lw=2,label='AEGIS,GEMS,GOODS')
+ax.hist(data[cosmos]['t01_smooth_or_features_total_count'],bins=range(170),histtype='step',lw=2,label='COSMOS')
+ax.hist(data[fake_agn]['t01_smooth_or_features_total_count'],bins=range(170),histtype='step',lw=2,label='simulated AGN')
+ax.hist(data[stripe82]['t01_smooth_or_features_total_count'],bins=range(170),histtype='step',lw=2,label='SDSS Stripe 82')
+
+ax.set_xlabel('classification count',fontsize=16)
+ax.set_ylabel('count',fontsize=16)
+
+import numpy as np
+print 'original',np.median(data[original]['t01_smooth_or_features_total_count'])
+print 'cosmos',np.median(data[cosmos]['t01_smooth_or_features_total_count'])
+print 'fake_agn',np.median(data[fake_agn]['t01_smooth_or_features_total_count'])
+print 'stripe82',np.median(data[stripe82]['t01_smooth_or_features_total_count'])
+
+ax.legend(fontsize=16)
+
+plt.show()

### 2016-05-15 python/comparisons.py

@@ -1,0 +1,891 @@
+from PIL import Image
+from astropy.io import fits
+from matplotlib import cm
+from matplotlib import pyplot as plt
+from matplotlib.colors import LogNorm
+from numpy import ma
+from scipy.ndimage.filters import gaussian_filter
+import matplotlib.gridspec as gridspec
+import numpy as np
+import random
+import scipy.stats.distributions as dist
+import warnings
+
+warnings.filterwarnings('ignore', category=RuntimeWarning, append=True)
+
+gzh_path = '/Users/willettk/Astronomy/Research/GalaxyZoo/gzhubble'
+
+# Abbreviate some of the GZH morphology categories
+pfeat = 't01_smooth_or_features_a02_features_or_disk_best_fraction'
+psmooth = 't01_smooth_or_features_a01_smooth_best_fraction'
+pclumpy = 't12_clumpy_a01_yes_weighted_fraction'
+podd = 't06_odd_a01_yes_weighted_fraction'
+pstar = 't01_smooth_or_features_a03_star_or_artifact_weighted_fraction'
+pspiral = 't04_spiral_a01_spiral_weighted_fraction'
+pirr = 't08_odd_feature_a04_irregular_fraction'
+pmerger = 't08_odd_feature_a06_merger_fraction'
+
+# Colors
+blue = '#377EB8'
+red = '#E41A1C'
+green = '#4DAF4A'
+
+def get_image(survey_id,goods=False,ns='n'):
+
+    if goods:
+        filename = "/Volumes/3TB/gz4/GOODS_full/jpg/standard/goods_full_{0}_g{1}_standard.jpg".format(ns,survey_id)
+    else:
+        filename = "/Volumes/3TB/gzh/jpg/{0}.jpg".format(survey_id)
+    img = Image.open(filename)
+    return img
+
+def cameron_err(c,k,n):
+    f_lower = dist.beta.ppf((1-c)/2., k+1,n-k+1)
+    f_upper = dist.beta.ppf(1-(1-c)/2., k+1,n-k+1)
+
+    return f_lower,f_upper
+
+def gems():
+
+    do_all = False
+
+    data = fits.getdata('{0}/comparisons/GEMS/gems_gzh.fits'.format(gzh_path),1)
+
+    # Only consider data that didn't run up against the GALFIT constraints?
+
+    discs = (data['n'] < 2.5)
+    bulges   = (data['n'] > 2.5)
+
[…]

### 2016-05-15 python/p_features_thresholds.py

@@ -1,0 +1,392 @@
+import numpy as np
+import time
+import warnings
+from astropy.io import fits
+from astropy.io.fits import Column
+
+warnings.filterwarnings('ignore', category=RuntimeWarning, append=True)
+
+'''
+Trim the plotting functions to output only the new classification categories.
+'''
+
+def bins():
+
+    data=fits.getdata('../data/ferengi_debiasable_data.fits',1)
+
+    #surface brightness bins
+    yedges=np.linspace(np.min(data['mu_max_i']),np.max(data['mu_max_i']),10)
+
+    #simulated redshifts of FERENGI data:
+    redshifts=[.3,.4,.5,.6,.7,.8,.9,1.]
+
+    return yedges,redshifts
+    
+def polyfit_with_fixed_points(n, xs, ys, xf, yf) :
+    
+    mat = np.empty((n + 1 + len(xf),) * 2)
+    vec = np.empty((n + 1 + len(xf),))
+    x_n = xs**np.arange(2 * n + 1)[:, None]
+    yx_n = np.sum(x_n[:n + 1] * ys, axis=1)
+    x_n = np.sum(x_n, axis=1)
+    idx = np.arange(n + 1) + np.arange(n + 1)[:, None]
+    mat[:n + 1, :n + 1] = np.take(x_n, idx)
+    xf_n = xf**np.arange(n + 1)[:, None]
+    mat[:n + 1, n + 1:] = xf_n / 2
+    mat[n + 1:, :n + 1] = xf_n.T
+    mat[n + 1:, n + 1:] = 0
+    vec[:n + 1] = yx_n
+    vec[n + 1:] = yf
+    params = np.linalg.solve(mat, vec)
+    
+    return params[:n + 1]
+    
+def calculate_hbins(deg,xs,ys):
+    
+    eps = 1e-3
+    xf = (0+eps,1) # offset by small amount so matrix is non-singular
+    yf = (0,1)
+    p = polyfit_with_fixed_points(deg,xs,ys,xf,yf)
+    poly = np.polynomial.Polynomial(p)
+    
+    return poly
+    
+def categorize_ferengi_data():
+
+    '''
+    Run zeta method on FERENGI data to determine which galaxies are correctable as function of SB, z, p_features
+    '''
+    
+    data=fits.getdata('../data/ferengi_debiasable_data.fits',1)
+    
+    #Pick out unique galaxies
+    galaxies = set(data['sdss_id'])
+    
+    yedges, redshifts = bins()
+
[…]

### 2016-05-15 python/signal_to_noise_comparison.py

@@ -1,0 +1,107 @@
+# Compare the measured SNR in the original Hubble images to those in FERENGI
+#
+# Naively: plot the SNR as a function of galaxy (apparent) magnitude for both GZH and FERENGI
+
+from astropy.stats import signal_to_noise_oir_ccd
+from astropy.io import fits
+import numpy as np
+from matplotlib import pyplot as plt
+import pandas as pd
+
+def load_gzh_image():
+
+    # Load a single GZH FITS image
+
+    # First problem - don't have the original GZH FITS images anywhere
+    
+    img = fits.getdata(filename,0)
+
+    return img
+
+def load_ferengi_image():
+
+    # Load a single FERENGI FITS image
+
+    filename = "../588848899357999327_imout_acsf814_ugriz_z0.800_evo0.0.fits"
+    img = fits.getdata(filename,0)
+
+    return img
+
+def example_snr():
+
+    img = load_ferengi_image()
+
+    snr = signal_to_noise_oir_ccd(t, source_eps, sky_eps, dark_eps, rd, npix, gain=1.0)
+
+    return None
+
+# Super naively. What if I just look at the rms of the background for all of the FERENGI
+# images, both as a histogram and function of galaxy magnitude?
+#
+# Pick 25x25 patch in one corner of the image
+#
+def scrape_rms():
+
+    path = '/Users/willettk/Astronomy/Research/GalaxyZoo/gzhubble'
+
+    import glob
+
+    files = glob.glob("{0}/ferengi_fits/*.fits".format(path))
+
+    f606 = open("{0}/ferengi_rms_f606.csv".format(path),"w")
+    f814 = open("{0}/ferengi_rms_f814.csv".format(path),"w")
+
+    for filename in files:
+        img = fits.getdata(filename,0)
+        corner_patch = img[:25,:25]
+        mean = np.mean(corner_patch)
+        rms = np.std(corner_patch)
+
+        fname = filename.split("/")[-1]
+        objid = fname.split("_")[0]
+        band = fname.split("_")[2]
+
+        if band == 'acsf606':
+            print >> f606,"{0},{2},{3}".format(objid,band,mean,rms)
+        elif band == 'acsf814':
+            print >> f814,"{0},{2},{3}".format(objid,band,mean,rms)
+
+    return None
[…]

### 2016-05-15 writeup/gz_hubble_data.tex

@@
 We present the data release paper for the Galaxy Zoo: Hubble (GZH) project.\footnote{This publication has been made possible by the participation of more than 200,000 volunteers in the Galaxy Zoo project.
-Their contributions are individually acknowledged at \url{http://authors.galaxyzoo.org/authors.html}.} This is the third phase in a large effort to measure reliable morphologies of galaxies on detailed scales by using crowdsourced visual classifications of color composite image.
-Images in GZH are selected from various \textit{Hubble Space Telescope} Legacy programs using the Advanced Camera for Surveys (AEGIS, COSMOS, GEMS, GOODS-N, and GOODS-S), with filters selected to probe the rest-frame optical emission from galaxies out to $z\simeq1$.
+Their contributions are individually acknowledged at \url{http://authors.galaxyzoo.org/authors.html}.} This is the third phase in a large effort to measure reliable, detailed morphologies of galaxies by using crowdsourced visual classifications of color composite images.
+Images in GZH are selected from various \textit{Hubble Space Telescope} Legacy programs that used the Advanced Camera for Surveys (AEGIS, COSMOS, GEMS, GOODS-N, and GOODS-S), with filters selected to probe the rest-frame optical emission from galaxies out to $z\simeq1$.
 The galaxies selected for GZH classifications go down to magnitude limits of $m_{I814W}<23.5$ and have a median redshift of $\langle z\rangle=0.9\pm0.6$, with a tail extending out to $z\simeq4$.
-The GZH morphological data includes measurements of both bulge- and disk-dominated galaxies, details on spiral disk structure that relate to the Hubble type, as well as clump identification and geometry.
+The GZH morphological data include measurements of both bulge- and disk-dominated galaxies, details on spiral disk structure that relate to the Hubble type, as well as clump identification and geometry.
 This paper also describes and employs a novel method for calibrating morphological bias by using artificially-redshifted galaxy images as a baseline.
-The GZH catalog includes both the raw and calibrated morphological vote fractions for $150,771$ galaxies, providing a comprehensive data set suitable for large-scale studies of galaxy evolution.
+The GZH catalog contains both raw and calibrated morphological vote fractions for $150,771$ galaxies, providing a comprehensive data set suitable for large-scale studies of galaxy evolution.
+% didn't the GOODS-N and GOODS-S second phases go deeper than 23.5 mag? am I misremembering? --BDS
 

### 2016-05-15 writeup/gz_hubble_data.tex
Linebreak the prose text at 80 chars

@@
 % Note: 250-word limit
-We present the data release paper for the Galaxy Zoo: Hubble (GZH) project.\footnote{This publication has been made possible by the participation of more than 200,000 volunteers in the Galaxy Zoo project.
-Their contributions are individually acknowledged at \url{http://authors.galaxyzoo.org/authors.html}.} This is the third phase in a large effort to measure reliable, detailed morphologies of galaxies by using crowdsourced visual classifications of color composite images.
-Images in GZH are selected from various \textit{Hubble Space Telescope} Legacy programs that used the Advanced Camera for Surveys (AEGIS, COSMOS, GEMS, GOODS-N, and GOODS-S), with filters selected to probe the rest-frame optical emission from galaxies out to $z\simeq1$.
-The galaxies selected for GZH classifications go down to magnitude limits of $m_{I814W}<23.5$ and have a median redshift of $\langle z\rangle=0.9\pm0.6$, with a tail extending out to $z\simeq4$.
-The GZH morphological data include measurements of both bulge- and disk-dominated galaxies, details on spiral disk structure that relate to the Hubble type, as well as clump identification and geometry.
-This paper also describes and employs a novel method for calibrating morphological bias by using artificially-redshifted galaxy images as a baseline.
-The GZH catalog contains both raw and calibrated morphological vote fractions for $150,771$ galaxies, providing a comprehensive data set suitable for large-scale studies of galaxy evolution.
+We present the data release paper for the Galaxy Zoo: Hubble (GZH)
+project.\footnote{This publication has been made possible by the participation
+of more than 200,000 volunteers in the Galaxy Zoo project. Their contributions
+are individually acknowledged at
+\url{http://authors.galaxyzoo.org/authors.html}.} This is the third phase in a
+large effort to measure reliable, detailed morphologies of galaxies by using
+crowdsourced visual classifications of color composite images. Images in GZH
+are selected from various \textit{Hubble Space Telescope} Legacy programs that
+used the Advanced Camera for Surveys (AEGIS, COSMOS, GEMS, GOODS-N, and
+GOODS-S), with filters selected to probe the rest-frame optical emission from
+galaxies out to $z\simeq1$. The galaxies selected for GZH classifications go
+down to magnitude limits of $m_{I814W}<23.5$ and have a median redshift of
+$\langle z\rangle=0.9\pm0.6$, with a tail extending out to $z\simeq4$. The GZH
+morphological data include measurements of both bulge- and disk-dominated
+galaxies, details on spiral disk structure that relate to the Hubble type, as
+well as clump identification and geometry. This paper also describes and
+employs a novel method for calibrating morphological bias by using
+artificially-redshifted galaxy images as a baseline. The GZH catalog contains
+both raw and calibrated morphological vote fractions for $150,771$ galaxies,
+providing a comprehensive data set suitable for large-scale studies of galaxy
+evolution. 
 % didn't the GOODS-N and GOODS-S second phases go deeper than 23.5 mag? am I misremembering? --BDS
@@
 
-The morphology of galaxies encodes information on the orbital parameters and assembly history of their contents, including gas, dust, stars, and the central black hole.
-The morphology is also closely related to the local environment of a galaxy, as interactions such as tides, shocks in cluster environments and direct mergers can all influence a galaxy's internal structure.
-For $M^\star$~galaxies in the local Universe, this interplay between the physical development of a galaxy and its external appearance typically manifests at the most basic level as the difference between bulge-dominated, virialized systems resembling ellipticals (early-types) and disk-dominated, rotationally-supported systems (late-types) frequently exhibiting spiral arms.
-This dichotomy has been used to explore much of the astrophysics governing galaxy formation and evolution, and has been shown to be closely linked with other galactic properties such as stellar mass, halo mass, bolometric luminosity, black hole activity, effective radius, and the relative ages of the stellar populations.
-
-The advent of larger telescopes in an increasing range of observing wavelengths has revealed that the distribution and properties of galaxy morphology have strongly evolved over the lifetime of the Universe.
-At redshift $z\simeq1$ (roughly 6~Gyr after the Big Bang), many galaxies are still in the process of assembling the baryonic and stellar mass required to reproduce the mature, coherent structures seen at the present day.
-This growth occurs via a variety of pathways, including accretion from large-scale galactic filaments onto halos via streaming, mergers of individual halos, conversion of gas into stars via gravitational collapse, etc.
-The accrual of baryons can be slowed or even reversed via feedback from stellar winds, supernovae, and active black holes.
-Each of these processes affects galaxy morphology in different ways, and so an accurate measurement of morphological demographics as a function of redshift provides an extremely powerful observational constraint on the physics involved \citep[for a recent review see][]{con14}.
-
-Theoretical predictions for the morphology of galaxies as a function of redshift are primarily computed within the $\Lambda$CDM cosmological framework.
-Full treatments model gravitational interactions between baryons and dark matter, hydrodynamics of the gas, and baryonic physics related to star formation and evolution.
-The most advanced simulations now span volumes up to $\sim100$~Mpc$^3$ while simultaneously resolving the smaller ($<1$ kpc) scales necessary to reproduce the influence of baryonic physics \citep{vog14a,sch15}.
-Such simulations predict clustering of galaxies on large scales in a hierarchical assembly model \citep{sil12}.
-The structure of individual galaxies is affected by their merger history \citep{too72,hop10}, local environment \citep[such as the morphology-density relation;][]{dre80}, initial dark halo mass, and many other factors.
-Morphologies of individual simulated high-mass galaxies at $z\sim2-3$ commonly show kpc-scale ``clumpy'' structures, with few galaxies that are either smooth or well-ordered spirals; asymmetric profiles with strong density contrasts dominate simulated populations in the early Universe until at least $z\sim1$ \citep{gen14}.
-
-Observational studies of galaxies at high-redshift also display a wide range of morphological types, many of which are rare or absent at $z\sim0$.
-Although spheroids and disks are present, they are typically much more compact than those in the local Universe.
-There is also a significant population of more irregular, massive galaxies, including mergers, tadpoles, chains, double-clumps, and clump-clusters \citep{elm05,elm07,cam11a,for11a,kar15}.
-In contrast, while grand-design spirals have been observed as far back as $z=2.18$ \citep{law12}, their spatial density suggests that they are exceedingly rare, with a very low fraction of undisturbed disks \citep{mor13}.
-Current observational data thus strongly suggests that the classical Hubble sequence/tuning fork \citep{hub36} is not a suitable framework for characterizing high-redshift morphology.
-
-Space-based observatories, particularly the \hubble (\hst), have been responsible for the bulk of imaging studies of high-redshift galaxies.
-Observations of fixed fields with very deep imaging \citep[eg,][]{wil96,gia04,bec06,dav07,sco07,gro11} give the photometric sensitivity necessary to detect $L^\star$ galaxies at $z>1$, while also providing the angular resolution to distinguish internal structure and characterize the morphology.
-While these measurements are helped by the fact that the angular diameter distance is relatively flat beyond $z>1$ in a flat $\Lambda$CDM cosmology, the relevant angular scales are only of the order $\sim5-10~\mathrm{kpc}/^{\prime\prime}$ \citep{wri06}.
-\hst{} can thus resolve much of the structure for a Milky Way-sized galaxy (at least for distinguishing a disk from a bulge), but will be limited for more compact structures.
-Since the size of galaxies evolves as roughly $r\propto(1+z)^{-1}$ \citep{law12a}, the compact sizes of high-redshift galaxies make detailed morphologies a challenge even for \hst{} \citep{che12}.
-The public availability of more than $10^5$~galaxies in archival imaging across various studies gives a data sample with the potential for high statistical significance.
-
-One of the major difficulties in studying the morphologies of galaxies lies in the techniques used for measurement.
-Visual classification by experts has been used for many decades \citep[eg,][]{hub26,dev59,san61,van76,nai10,bai11,kar15}.
-These methods have the advantage of using the significant processing power of the human brain to identify patterns, but suffer from issues such as lack of scaling to large surveys and potential issues with replicability and calibration.
-Automated measurements, both parametric \citep{pen02a,sim11,lac12} and non-parametric \citep{abr03,con03,lot04,sca07,bam08,fre13}, scale well to very large sample sizes, but do not always fully capture the relevant features, especially for asymmetric galaxies that become increasingly common at high redshifts.
-The Galaxy Zoo project \citep{lin08,lin11} utilizes crowdsourced visual classifications to measure galaxies in color-composite images.
-The efforts of more than $2\times10^5$~classifiers allow for multiple independent classifications of each image which are combined and calibrated to give a distribution of vote fractions proportional to the probability of a feature being visible.
-While crowdsourced data require extensive calibration \citep{bam09,wil13}, they have a proven reliability and have been used in dozens of papers \citep[eg,][]{lan08,bam09,dar10,mas11c,ski12,sim13,sch14,wil15}.
-
-This paper presents the results from the Galaxy Zoo Hubble (GZH) project.\footnote{\url{http://zoo3.galaxyzoo.org/}} GZH was the third phase of Galaxy Zoo, following its initial results classifying $\sim900,000$~SDSS~images into primarily early/late~types \citep{lin11} and Galaxy~Zoo~2, which covered $\sim250,000$~SDSS~images using a more detailed classification scheme that included bars, spiral arms, and galactic bulges \citep{wil13}.
-GZH used a similarly detailed classification scheme, but focused for the first time on images of high-redshift galaxies taken with \hst.
-The Galaxy Zoo: CANDELS project has also classified morphologies of galaxies at high redshift using ACS and WFC3 imaging (Simmons et~al., submitted).
-
-The sample selection and creation of the images used for GZH is described in Section~\ref{sec:data}.
-Section~\ref{sec:interface} describes the GZH interface and the collection of classifications.
-Section~\ref{sec:debiasing} outlines the process used to calibrate and correct the crowdsourced vote fractions for redshift-dependent bias.
-Section~\ref{sec:results} gives the main catalog of results, with several examples of how the data may be queried in Section~\ref{sec:cookbook}.
-Section~\ref{sec:analysis} gives a short overview of the observed morphological demographics and compares them to several other catalogs, with a summary in Section~\ref{sec:summary}.
-
-This paper assumes the WMAP9 cosmological parameters of $(\Omega_m,\Omega_\Lambda,h)=(0.282,0.718,0.697)$ \citep{hin13}.
-
-%\begin{enumerate}
-%    \item Motivation for studying morphology of galaxies
-%    \item Particular scientific questions governed by galaxies at $z\sim1$
-%    \item Theoretical predictions for galaxy morphology evolution
-%    \item Past imaging and morphology studies at $z\sim1$
-%    \item Summary of GZ/citizen science work on galaxy morphology to date
-%    \item Outline of paper
-%\end{enumerate}
+The morphology of galaxies encodes information on the orbital parameters and
+assembly history of their contents, including gas, dust, stars, and the central
+black hole. The morphology is also closely related to the local environment of
+a galaxy, as interactions such as tides, shocks in cluster environments and
+direct mergers can all influence a galaxy's internal structure.  For
+$M^\star$~galaxies in the local Universe, this interplay between the physical
+development of a galaxy and its external appearance typically manifests at the
+most basic level as the difference between bulge-dominated, virialized systems
+resembling ellipticals (early-types) and disk-dominated, rotationally-supported
+systems (late-types) frequently exhibiting spiral arms. This dichotomy has been
+used to explore much of the astrophysics governing galaxy formation and
+evolution, and has been shown to be closely linked with other galactic
+properties such as stellar mass, halo mass, bolometric luminosity, black hole
+activity, effective radius, and the relative ages of the stellar populations.
+
+The advent of larger telescopes in an increasing range of observing wavelengths
+has revealed that the distribution and properties of galaxy morphology have
+strongly evolved over the lifetime of the Universe. At redshift $z\simeq1$
+(roughly 6~Gyr after the Big Bang), many galaxies are still in the process of
+assembling the baryonic and stellar mass required to reproduce the mature,
+coherent structures seen at the present day. This growth occurs via a variety
+of pathways, including accretion from large-scale galactic filaments onto halos
+via streaming, mergers of individual halos, conversion of gas into stars via
+gravitational collapse, etc. The accrual of baryons can be slowed or even
+reversed via feedback from stellar winds, supernovae, and active black holes.
+Each of these processes affects galaxy morphology in different ways, and so an
+accurate measurement of morphological demographics as a function of redshift
+provides an extremely powerful observational constraint on the physics involved
+\citep[for a recent review see][]{con14}.
+
+Theoretical predictions for the morphology of galaxies as a function of
+redshift are primarily computed within the $\Lambda$CDM cosmological framework.
+Full treatments model gravitational interactions between baryons and dark
+matter, hydrodynamics of the gas, and baryonic physics related to star
+formation and evolution. The most advanced simulations now span volumes up to
+$\sim100$~Mpc$^3$ while simultaneously resolving the smaller ($<1$ kpc) scales
+necessary to reproduce the influence of baryonic physics \citep{vog14a,sch15}.
+Such simulations predict clustering of galaxies on large scales in a
+hierarchical assembly model \citep{sil12}. The structure of individual galaxies
+is affected by their merger history \citep{too72,hop10}, local environment
+\citep[such as the morphology-density relation;][]{dre80}, initial dark halo
+mass, and many other factors. Morphologies of individual simulated high-mass
+galaxies at $z\sim2-3$ commonly show kpc-scale ``clumpy'' structures, with few
+galaxies that are either smooth or well-ordered spirals; asymmetric profiles
+with strong density contrasts dominate simulated populations in the early
+Universe until at least $z\sim1$ \citep{gen14}.
+
+Observational studies of galaxies at high-redshift also display a wide range of
+morphological types, many of which are rare or absent at $z\sim0$. Although
+spheroids and disks are present, they are typically much more compact than
+those in the local Universe. There is also a significant population of more
+irregular, massive galaxies, including mergers, tadpoles, chains,
+double-clumps, and clump-clusters \citep{elm05,elm07,cam11a,for11a,kar15}. In
+contrast, while grand-design spirals have been observed as far back as $z=2.18$
+\citep{law12}, their spatial density suggests that they are exceedingly rare,
+with a very low fraction of undisturbed disks \citep{mor13}. Current
+observational data thus strongly suggests that the classical Hubble
+sequence/tuning fork \citep{hub36} is not a suitable framework for
+characterizing high-redshift morphology.
+
+Space-based observatories, particularly the \hubble{} (\hst), have been
+responsible for the bulk of imaging studies of high-redshift galaxies.
+Observations of fixed fields with very deep imaging
+\citep[eg,][]{wil96,gia04,bec06,dav07,sco07,gro11} give the photometric
+sensitivity necessary to detect $L^\star$ galaxies at $z>1$, while also
+providing the angular resolution to distinguish internal structure and
+characterize the morphology. While these measurements are helped by the fact
+that the angular diameter distance is relatively flat beyond $z>1$ in a flat
+$\Lambda$CDM cosmology, the relevant angular scales are only of the order
+$\sim5-10~\mathrm{kpc}/^{\prime\prime}$ \citep{wri06}. \hst{} can thus resolve
+much of the structure for a Milky Way-sized galaxy (at least for distinguishing
+a disk from a bulge), but will be limited for more compact structures. Since
+the size of galaxies evolves as roughly $r\propto(1+z)^{-1}$ \citep{law12a},
+the compact sizes of high-redshift galaxies make detailed morphologies a
+challenge even for \hst{} \citep{che12}. The public availability of more than
+$10^5$~galaxies in archival imaging across various studies gives a data sample
+with the potential for high statistical significance.
+
+One of the major difficulties in studying the morphologies of galaxies lies in
+the techniques used for measurement. Visual classification by experts has been
+used for many decades \citep[eg,][]{hub26,dev59,san61,van76,nai10,bai11,kar15}.
+These methods have the advantage of using the significant processing power of
+the human brain to identify patterns, but suffer from issues such as lack of
+scaling to large surveys and potential issues with replicability and
+calibration. Automated measurements, both parametric \citep{pen02a,sim11,lac12}
+and non-parametric \citep{abr03,con03,lot04,sca07,bam08,fre13}, scale well to
+very large sample sizes, but do not always fully capture the relevant features,
+especially for asymmetric galaxies that become increasingly common at high
+redshifts. The Galaxy Zoo project \citep{lin08,lin11} utilizes crowdsourced
+visual classifications to measure galaxies in color-composite images. The
+efforts of more than $2\times10^5$~classifiers allow for multiple independent
+classifications of each image which are combined and calibrated to give a
+distribution of vote fractions proportional to the probability of a feature
+being visible. While crowdsourced data require extensive calibration
+\citep{bam09,wil13}, they have a proven reliability and have been used in
+dozens of papers
+\citep[eg,][]{lan08,bam09,dar10,mas11c,ski12,sim13,sch14,wil15}.
+
+This paper presents the results from the Galaxy Zoo Hubble (GZH)
+project.\footnote{\url{http://zoo3.galaxyzoo.org/}} GZH was the third phase of
+Galaxy Zoo, following its initial results classifying $\sim900,000$~SDSS~images
+into primarily early/late~types \citep{lin11} and Galaxy~Zoo~2, which covered
+$\sim250,000$~SDSS~images using a more detailed classification scheme that
+included bars, spiral arms, and galactic bulges \citep{wil13}. GZH used a
+similarly detailed classification scheme, but focused for the first time on
+images of high-redshift galaxies taken with \hst. The Galaxy Zoo: CANDELS
+project has also classified morphologies of galaxies at high redshift using ACS
+and WFC3 imaging (Simmons et~al., submitted).
+
+The sample selection and creation of the images used for GZH is described in
+Section~\ref{sec:data}. Section~\ref{sec:interface} describes the GZH interface
+and the collection of classifications. Section~\ref{sec:debiasing} outlines the
+process used to calibrate and correct the crowdsourced vote fractions for
+redshift-dependent bias. Section~\ref{sec:results} gives the main catalog of
+results, with several examples of how the data may be queried in
+Section~\ref{sec:cookbook}. Section~\ref{sec:analysis} gives a short overview
+of the observed morphological demographics and compares them to several other
+catalogs, with a summary in Section~\ref{sec:summary}.
+
+This paper assumes the WMAP9 cosmological parameters of
+$(\Omega_m,\Omega_\Lambda,h)=(0.282,0.718,0.697)$ \citep{hin13}.
 
@@
 
-The GZH project contains images drawn from a number of different dedicated surveys and sample selection criteria.
-The majority of the data (as implied by the project name) are taken directly from \hst{} Legacy Surveys, all of which primarily use imaging from the Advanced Camera for Surveys (ACS).
-Results from the individual surveys have been combined into a single photometric and morphological database, the Advanced Camera for Surveys General Catalog \citep[ACS-GC;][]{gri12}.
-A summary of the key parameters is given in Table~\ref{tbl:gzh_numbers}.
+The GZH project contains images drawn from a number of different dedicated
+surveys and sample selection criteria. The majority of the data (as implied by
+the project name) are taken directly from \hst{} Legacy Surveys, all of which
+primarily use imaging from the Advanced Camera for Surveys (ACS). Results from
+the individual surveys have been combined into a single photometric and
+morphological database, the Advanced Camera for Surveys General Catalog
+\citep[ACS-GC;][]{gri12}. A summary of the key parameters is given in
+Table~\ref{tbl:gzh_numbers}.
 
@@
 \includegraphics[width=160mm]{figures/filter_curves.pdf}
-\caption{Transmission curves of the filters used by \hst{} Advanced Camera for Surveys (ACS) in wide-field channel mode for the various surveys in GZH.
-The unfilled black curves show the filters for the Suprime Camera on the \textit{Subaru} telescope, which was used to create color gradients in the GZH images for COSMOS.\label{fig:filtercurves}}
+\caption{Transmission curves of the filters used by \hst{} Advanced Camera for
+Surveys (ACS) in wide-field channel mode for the various surveys in GZH. The
+unfilled black curves show the filters for the Suprime Camera on the
+\textit{Subaru} telescope, which was used to create color gradients in the GZH
+images for COSMOS.\label{fig:filtercurves}}
 \end{figure*}
@@
 \begin{itemize}
-\item The All-Wavelength Extended Groth Strip International Survey \citep[AEGIS;][]{dav07} covers a strip centered at $\alpha=14^\textrm{h}17^\textrm{m}, \delta=+52^\circ30^\prime$.
-This area was selected for a deep survey due to a combination of low extinction and low Galactic/zodiacal emission.
-The ACS images covered 63 separate tiles over a total area of $\sim710$~arcmin$^2$.
-The two ACS bands for AEGIS had exposure times of 2300~seconds in F606W (\Vband) and 2100~seconds in F814W (\Iband).
-The final mosaic images are dithered to a resolution of 0.03~\arcsec/pixel.
-For extended objects, the limiting magnitudes of sources in AEGIS are 26.23~(AB) in \Vband{} and 25.61 (AB) in \Iband.
-
-\item The Great Observatories Origins Deep Survey \citep[GOODS;][]{gia04} covers two separate fields in the northern and southern hemispheres: the Hubble Deep Field-North ($\alpha=12^\textrm{h}36^\textrm{m}, \delta=+62^\circ14^\prime$) and the Chandra Deep Field-South ($\alpha=03^\textrm{h}32^\textrm{m}, \delta=-27^\circ48^\prime$).
-The \hst{} ACS imaging data from the two fields are referred to as GOODS-N and GOODS-S, respectively.
-ACS imaging in GOODS fields used 4 filters -- F435W (\Bband), \Vband, F775W (\iband), and F850LP (\zband).
-The mean exposure times for each epoch vary by band, from 1050--2100~seconds.
-The \Bband{} images were completed in a single epoch at the beginning of the survey, but the \Vband, \iband, and \zband{} images were taken in five separate epochs separated by 40--50~days each.
-Images are dithered to a pixel scale of 0.03~\arcsec/pixel and cover a total area of $\sim320$~arcmin$^2$ (160~arcmin$^2$ per north/south field).
-The $5\sigma$ limiting magnitudes for extended sources are 25.7 for \Vband{} and 25.0 for \iband.
-
-\item The Cosmic Evolution Survey \citep[COSMOS;][]{sco07} covers an area of $\sim1.8$~deg$^2$ centered at $\alpha=10^\textrm{h}00^\textrm{m}, \delta=+02^\circ12^\prime$.
-Its location near the celestial equator was designed to enable coverage by ground-based telescopes in both the Northern and Southern Hemispheres, in addition to space-based observatories.
-The ACS data for COSMOS consists of 1 orbit per pointing with an exposure time of 2028~seconds in \Iband; 590 total pointings are used to cover the entire field.
-The image resolution is dithered to 0.05~\arcsec/pixel.
-The 50\% completeness magnitude for a galaxy with a half-light radius of $0.50^{\prime\prime}$ in \Iband{} is 24.7 mag.
-
-\item The Galaxy Evolution from Morphologies and SEDs \citep[GEMS;][]{rix04,cal08} survey is also centered on the Chandra Deep Field-South.
-The GEMS data covers $\sim800$~arcmin$^2$, completely surrounding the area covered by GOODS-S.
-Images from ACS in GEMS have 1 orbit per pointing for a total of 63~pointings.
-The exposure times are 2160 and 2286~seconds in \Vband{} and \zband{}, respectively.
-The image resolution has a pixel scale of 0.03~\arcsec/pixel.
-The $5\sigma$ limiting magnitudes for source detection are 25.7 AB in \Vband{} and 24.2~AB in \zband.
+
+\item The All-Wavelength Extended Groth Strip International Survey
+    \citep[AEGIS;][]{dav07} covers a strip centered at
+    $\alpha=14^\textrm{h}17^\textrm{m}, \delta=+52^\circ30^\prime$. This area was
+    selected for a deep survey due to a combination of low extinction and low
+    Galactic/zodiacal emission. The ACS images covered 63 separate tiles over a
+    total area of $\sim710$~arcmin$^2$. The two ACS bands for AEGIS had exposure
+    times of 2300~seconds in F606W (\Vband) and 2100~seconds in F814W (\Iband). The
+    final mosaic images are dithered to a resolution of 0.03~\arcsec/pixel. For
+    extended objects, the limiting magnitudes of sources in AEGIS are 26.23~(AB) in
+    \Vband{} and 25.61 (AB) in \Iband.
+
+\item The Great Observatories Origins Deep Survey \citep[GOODS;][]{gia04}
+    covers two separate fields in the northern and southern hemispheres: the Hubble
+    Deep Field-North ($\alpha=12^\textrm{h}36^\textrm{m},
+    \delta=+62^\circ14^\prime$) and the Chandra Deep Field-South
+    ($\alpha=03^\textrm{h}32^\textrm{m}, \delta=-27^\circ48^\prime$). The \hst{}
+    ACS imaging data from the two fields are referred to as GOODS-N and GOODS-S,
+    respectively. ACS imaging in GOODS fields used 4 filters -- F435W (\Bband),
+    \Vband, F775W (\iband), and F850LP (\zband). The mean exposure times for each
+    epoch vary by band, from 1050--2100~seconds. The \Bband{} images were completed
+    in a single epoch at the beginning of the survey, but the \Vband, \iband, and
+    \zband{} images were taken in five separate epochs separated by 40--50~days
+    each. Images are dithered to a pixel scale of 0.03~\arcsec/pixel and cover a
+    total area of $\sim320$~arcmin$^2$ (160~arcmin$^2$ per north/south field). The
+    $5\sigma$ limiting magnitudes for extended sources are 25.7 for \Vband{} and
+    25.0 for \iband.
+
+\item The Cosmic Evolution Survey \citep[COSMOS;][]{sco07} covers an area of
+    $\sim1.8$~deg$^2$ centered at $\alpha=10^\textrm{h}00^\textrm{m},
+    \delta=+02^\circ12^\prime$. Its location near the celestial equator was
+    designed to enable coverage by ground-based telescopes in both the Northern and
+    Southern Hemispheres, in addition to space-based observatories. The ACS data
+    for COSMOS consists of 1 orbit per pointing with an exposure time of
+    2028~seconds in \Iband; 590 total pointings are used to cover the entire
+    field. The image resolution is dithered to 0.05~\arcsec/pixel. The 50\%
+    completeness magnitude for a galaxy with a half-light radius of
+    $0.50^{\prime\prime}$ in \Iband{} is 24.7 mag.
+
+\item The Galaxy Evolution from Morphologies and SEDs
+    \citep[GEMS;][]{rix04,cal08} survey is also centered on the Chandra Deep
+    Field-South. The GEMS data covers $\sim800$~arcmin$^2$, completely surrounding
+    the area covered by GOODS-S. Images from ACS in GEMS have 1 orbit per pointing
+    for a total of 63~pointings. The exposure times are 2160 and 2286~seconds in
+    \Vband{} and \zband{}, respectively. The image resolution has a pixel scale
+    of 0.03~\arcsec/pixel. The $5\sigma$ limiting magnitudes for source
+    detection are 25.7 AB in \Vband{} and 24.2~AB in \zband.
+
 \end{itemize}
@@
 
-In the ACS-GC \citep{gri12}, individual galaxies are identified using a combination of \sextractor{} \citep{ber96} and the galaxy-profile fitting framework \galapagos{} \citep{bar12}.
-GZH includes all galaxies with $m < 23.5$, where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS, GEMS + GOODS-S, and GOODS-N surveys, respectively.
-This yielded a total of 113,166~images (Table~\ref{tbl:gzh_numbers}).
-
-Single-epoch images from SDSS Stripe~82 were selected using the same criteria from \citet{wil13}, which required limits of \texttt{petroR90\_r}$ > 3$\arcsec~(where \texttt{petroR90\_r} is the radius containing 90\% of the $r^\prime$ Petrosian flux) and a magnitude brighter than $m_r < 17.77$.
-The images used are three-color composites using the $g^\prime$, $r^\prime$, and $i^\prime$ filters \citep{nie04}.
-21,522 galaxies in SDSS met these criteria.
-Co-added images from Stripe~82 were selected from the union of galaxies with co-added magnitudes brighter than $17.77$~mag and the galaxies detected in the single-depth images and matched to a co-add source.
-This resulted in a larger set of 30,339 images.
-Of the images in the co-added sample, 5144 (17~percent) are dimmer than the initial magnitude cut of 17.77.
+In the ACS-GC \citep{gri12}, individual galaxies are identified using a
+combination of \sextractor{} \citep{ber96} and the galaxy-profile fitting
+framework \galapagos{} \citep{bar12}. GZH includes all galaxies with $m <
+23.5$, where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS,
+GEMS + GOODS-S, and GOODS-N surveys, respectively. This yielded a total of
+113,166~images (Table~\ref{tbl:gzh_numbers}).
+
+Single-epoch images from SDSS Stripe~82 were selected using the same criteria
+from \citet{wil13}, which required limits of \texttt{petroR90\_r}$ >
+3$\arcsec~(where \texttt{petroR90\_r} is the radius containing 90\% of the
+$r^\prime$ Petrosian flux) and a magnitude brighter than $m_r < 17.77$. The
+images used are three-color composites using the $g^\prime$, $r^\prime$, and
+$i^\prime$ filters \citep{nie04}. 21,522 galaxies in SDSS met these criteria.
+Co-added images from Stripe~82 were selected from the union of galaxies with
+co-added magnitudes brighter than $17.77$~mag and the galaxies detected in the
+single-depth images and matched to a co-add source. This resulted in a larger
+set of 30,339 images. Of the images in the co-added sample, 5144 (17~percent)
+are dimmer than the initial magnitude cut of 17.77.
 
@@
 
-The images used for classification in GZH are color-composite JPGs made from multi-band data. The exact process for creating the images depends on the bands and resolutions in the surveys.
-
-For galaxies in the ACS-GC, color composites are made using a fixed pixel intensity scaling with weights of $[2.4\times10^{-4},3\times10^{-4},3\times10^{-4}]$ in the red, green, and blue channels respectively.
-A nonlinear mapping is applied to each pixel to emphasize the contrast in faint features \citep{lup04}, taking the form of:
+The images used for classification in GZH are color-composite JPGs made from
+multi-band data. The exact process for creating the images depends on the bands
+and resolutions in the surveys.
+
+For galaxies in the ACS-GC, color composites are made using a fixed pixel
+intensity scaling with weights of
+$[2.4\times10^{-4},3\times10^{-4},3\times10^{-4}]$ in the red, green, and blue
+channels respectively. A nonlinear mapping is applied to each pixel to
+emphasize the contrast in faint features \citep{lup04}, taking the form of:
 
@@
 
-The majority of the data in Legacy surveys described in Section~\ref{ssec:legacy_surveys} had images in only one or two filters available when the GZH project was first launched, making standard 3-channel RGB images in the same method used for the SDSS images in the original Galaxy Zoo impossible.
-For surveys with images in two bands (AEGIS, GEMS, and the two-epoch GOODS-N and GOODS-S), the lower-wavelength band was mapped to the blue channel, the higher-wavelength band to the red channel, and the green channel created by taking the geometric mean of the two.
-Bands used in each of the surveys are listed in Table~\ref{tbl:gzh_numbers}.
-The 2-epoch GOODS-N and GOODS-S images use different filters --- this was a deliberate choice made so that the GEMS images could be directly compared with the overlapping coverage of GOODS-S (Figure~\ref{fig:filtercurves}).
-
-By the time that the 5-epoch sets of GOODS data were put into GZH (in March 2015), coverage in four separate \hst{} bands were publicly available.
-The deeper GOODS images were created using the arithmetic mean of \Bband{} and \Vband{} in the blue channel, \Iband{} in the red channel, and \zband{} in the green channel.
-These images also had their speckled noise pixels decolorized.
-
-The COSMOS images only had the \Iband{} imaging available at the time of classification in GZH.
-For these galaxies, we created ``pseudocolor'' images by using the ACS \Iband{} data as the illumination map and ground-based imaging from the \subaru{} telescope in $B_J$, $r^+$, and $i^+$ filters to provide the color gradients \citep[see][for further details]{gri12}.
-This means that the images have the angular resolution of \hst{} ($\sim0.05$~\arcsec/pixel) for the overall intensity, but the color gradients are at ground-based resolution, with seeing between 0.95\arcsec{} and 1.05\arcsec{} \citep{tan07}.
-
-Stripe~82 single-epoch images were taken directly from the color composites on the DR7 SDSS Skyserver, which combines $g^{\prime}$, $r^{\prime}$, and $i^{\prime}$ exposures into the RGB channels.
-The co-added Stripe~82 images were assembled from runs 106 and 206 in DR7 and made into color composites using the method of \citet{lup04}.
-
-To deal with images in which the sky noise was highly colored (which might have been a distraction to visual classification), a soft-edged object mask was applied that preserves the color balance for galaxies, but desaturates speckled noise against regions of blank sky.
-This technique was applied only to the co-added Stripe~82 and the COSMOS images.
+The majority of the data in Legacy surveys described in
+Section~\ref{ssec:legacy_surveys} had images in only one or two filters
+available when the GZH project was first launched, making standard 3-channel
+RGB images in the same method used for the SDSS images in the original Galaxy
+Zoo impossible. For surveys with images in two bands (AEGIS, GEMS, and the
+two-epoch GOODS-N and GOODS-S), the lower-wavelength band was mapped to the
+blue channel, the higher-wavelength band to the red channel, and the green
+channel created by taking the geometric mean of the two. Bands used in each of
+the surveys are listed in Table~\ref{tbl:gzh_numbers}. The 2-epoch GOODS-N and
+GOODS-S images use different filters --- this was a deliberate choice made so
+that the GEMS images could be directly compared with the overlapping coverage
+of GOODS-S (Figure~\ref{fig:filtercurves}).
+
+By the time that the 5-epoch sets of GOODS data were put into GZH (in March
+2015), coverage in four separate \hst{} bands were publicly available. The
+deeper GOODS images were created using the arithmetic mean of \Bband{} and
+\Vband{} in the blue channel, \Iband{} in the red channel, and \zband{} in the
+green channel. These images also had their speckled noise pixels decolorized.
+
+The COSMOS images only had the \Iband{} imaging available at the time of
+classification in GZH. For these galaxies, we created ``pseudocolor'' images by
+using the ACS \Iband{} data as the illumination map and ground-based imaging
+from the \subaru{} telescope in $B_J$, $r^+$, and $i^+$ filters to provide the
+color gradients \citep[see][for further details]{gri12}. This means that the
+images have the angular resolution of \hst{} ($\sim0.05$~\arcsec/pixel) for the
+overall intensity, but the color gradients are at ground-based resolution, with
+seeing between 0.95\arcsec{} and 1.05\arcsec{} \citep{tan07}.
+
+Stripe~82 single-epoch images were taken directly from the color composites on
+the DR7 SDSS Skyserver, which combines $g^{\prime}$, $r^{\prime}$, and
+$i^{\prime}$ exposures into the RGB channels. The co-added Stripe~82 images
+were assembled from runs 106 and 206 in DR7 and made into color composites
+using the method of \citet{lup04}.
+
+To deal with images in which the sky noise was highly colored (which might have
+been a distraction to visual classification), a soft-edged object mask was
+applied that preserves the color balance for galaxies, but desaturates speckled
+noise against regions of blank sky. This technique was applied only to the
+co-added Stripe~82 and the COSMOS images.
 
@@
 
-GZH also includes a set of images designed to measure the effect of active galactic nuclei (AGN) on morphological classifications.
-Since galactic nuclei can have bright, unresolved optical emission, this has the potential to mimic or distort the identification of a bulge component.
-The presence of an AGN is simulated by modeling the point spread function (PSF) of the telescope and then inserting a bright source near the center of a real galaxy.
-For each image, the simulated AGN is assigned one of three colors -- either blue, red, or flat (white) as seen in the color images -- and a range of brightnesses such that $L_\mathrm{ratio} \equiv L_\mathrm{galaxy}/L_\mathrm{AGN}$ is in $(0.2,1.0,2.0,5.0,10.0,50.0)$.
-Combining these parameters generates 15~images with different simulated AGN for each host.
-
-Two sets of simulated AGN were generated in GZH.
-The first set (version~1) was assembled from 95~galaxies from GEMS imaging and PSFs from \texttt{daophot}.
-The second set (version~2) was assembled from 96~galaxies in GOODS-S; this version used deeper imaging and improved PSFs from \texttt{TinyTim}.
-
-Images with simulated AGN were classified in the main interface in an identical manner and evenly distributed with unaltered images of the galaxies.
-Classifiers were not explicitly told that the images had been altered, as the goal was to measure the effect on normal classifications in as unbiased a manner as possible.
+GZH also includes a set of images designed to measure the effect of active
+galactic nuclei (AGN) on morphological classifications. Since galactic nuclei
+can have bright, unresolved optical emission, this has the potential to mimic
+or distort the identification of a bulge component. The presence of an AGN is
+simulated by modeling the point spread function (PSF) of the telescope and then
+inserting a bright source near the center of a real galaxy. For each image, the
+simulated AGN is assigned one of three colors -- either blue, red, or flat
+(white) as seen in the color images -- and a range of brightnesses such that
+$L_\mathrm{ratio} \equiv L_\mathrm{galaxy}/L_\mathrm{AGN}$ is in
+$(0.2,1.0,2.0,5.0,10.0,50.0)$. Combining these parameters generates 15~images
+with different simulated AGN for each host.
+
+Two sets of simulated AGN were generated in GZH. The first set (version~1) was
+assembled from 95~galaxies from GEMS imaging and PSFs from \texttt{daophot}.
+The second set (version~2) was assembled from 96~galaxies in GOODS-S; this
+version used deeper imaging and improved PSFs from \texttt{TinyTim}.
+
+Images with simulated AGN were classified in the main interface in an identical
+manner and evenly distributed with unaltered images of the galaxies.
+Classifiers were not explicitly told that the images had been altered, as the
+goal was to measure the effect on normal classifications in as unbiased a
+manner as possible.
 
@@
 
-Photometric data for the bulk of the GZH sample is largely drawn from the tables provided in \citet{gri12}.
-This includes photometric parameters such as the fluxes, magnitudes, radii, ellipticities, position angles, and positions drawn from both \sextractor{} and \galfit.
-\galfit{} also provides the parametric \sersic{} index and effective half-light radius for the best-fit model.
-All parameters are measured in both bands of the ACS imaging, with the exception of the single-band COSMOS images.
-
-Redshifts for the GZH catalog are compiled from a variety of sources.
-For each galaxy, the primary redshift used for debiasing calculations (Section~\ref{sec:debiasing}) is in the $\tt Z\_BEST$ column of Table~\ref{tbl:catalog_hst}.
-The redshift type (spectroscopic: $\tt SPEC\_Z$, photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column $\tt Z\_BEST\_TYPE$, and the source catalog of the redshift is included as $\tt Z\_BEST\_SOURCE$.
-
-For galaxies which have published redshifts from multiple sources, the following algorithm is used to select the $\tt Z\_BEST$ quantity.
-This first priority is spectroscopic redshifts; these are provided in the ACS-GC \citep{gri12}, 3DHST \citep{mom15}, and MUSYC \citep{car10} catalogs.
-A high quality spectroscopic redshift in the ACS-GC is the primary option; if none is available, then $\tt Z\_BEST$ uses the spectroscopic redshifts in 3DHST, and then MUSYC.
-For galaxies with multiple spectroscopic redshifts, more than 98\% are consistent at $\Delta z<0.001$, and so the order of selection makes no practical difference.
-If no spectroscopic redshifts are available, the 1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST, MUSYC, UltraVISTA;][]{ilb13} and UltraVISTA grism data are used to select the redshift with the smallest error.
+Photometric data for the bulk of the GZH sample is largely drawn from the
+tables provided in \citet{gri12}. This includes photometric parameters such as
+the fluxes, magnitudes, radii, ellipticities, position angles, and positions
+drawn from both \sextractor{} and \galfit. \galfit{} also provides the
+parametric \sersic{} index and effective half-light radius for the best-fit
+model. All parameters are measured in both bands of the ACS imaging, with the
+exception of the single-band COSMOS images.
+
+Redshifts for the GZH catalog are compiled from a variety of sources. For each
+galaxy, the primary redshift used for debiasing calculations
+(Section~\ref{sec:debiasing}) is in the $\tt Z\_BEST$ column of
+Table~\ref{tbl:catalog_hst}. The redshift type (spectroscopic: $\tt SPEC\_Z$,
+photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column
+$\tt Z\_BEST\_TYPE$, and the source catalog of the redshift is included as $\tt
+Z\_BEST\_SOURCE$.
+
+For galaxies which have published redshifts from multiple sources, the
+following algorithm is used to select the $\tt Z\_BEST$ quantity. This first
+priority is spectroscopic redshifts; these are provided in the ACS-GC
+\citep{gri12}, 3DHST \citep{mom15}, and MUSYC \citep{car10} catalogs. A high
+quality spectroscopic redshift in the ACS-GC is the primary option; if none is
+available, then $\tt Z\_BEST$ uses the spectroscopic redshifts in 3DHST, and
+then MUSYC. For galaxies with multiple spectroscopic redshifts, more than 98\%
+are consistent at $\Delta z<0.001$, and so the order of selection makes no
+practical difference. If no spectroscopic redshifts are available, the
+1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST, MUSYC,
+UltraVISTA;][]{ilb13} and UltraVISTA grism data are used to select the redshift
+with the smallest error. 
 %Table~\ref{tbl:redshifts} shows the results of this selection.
@@
 %\caption{Spectroscopic redshifts from the ACS-GC, 3DHST, and MUSYC catalogs.
-The number in the upper left of each plot is the percentage of redshifts which agree within $\Delta z < 0.05$ between the two catalogs being compared in each panel.
-Within this range there is over 98\% agreement in redshifts between all three catalogs.}
+%The number in the upper left of each plot is the percentage of redshifts which
+%agree within $\Delta z < 0.05$ between the two catalogs being compared in each
+%panel. Within this range there is over 98\% agreement in redshifts between all
+%three catalogs.}
 %\label{fig:speczs}
@@
 %%Survey     Gs        Gp    3ds    3dg     3dp       Ms      Mp       UVp       total
-%AEGIS    & 3,656  & 2,941  & 12  &  515  &  249    & 0     & 0     &  0      & 7,373  & 8,507\\
+%AEGIS    & 3,656  & 2,941  & 12  &  515  &  249    & 0     & 0     &  0      & 7,373   & 8,507   \\
 %COSMOS   & 7,201  & 77,435 & 35  &  358  &  26     & 0     & 0     &  2,665  & 85,020  & 92,808  \\
-%GEMS     & 387    & 628    & 6   &  99   &  40     & 279   & 7,304 & 0       & 8,743  & 9,304\\
+%GEMS     & 387    & 628    & 6   &  99   &  40     & 279   & 7,304 & 0       & 8,743   & 9,304   \\
 %GOODS-N  & 1,947  & 37     & 418 & 1,545 &  1,381  & 0     & 0     & 0       & 5,328   & 12,030  \\
@@
 %\hline
-%Total    & 14,271 & 81,045 & 798 & 3,865 & 1,977   & 1,095 & 8,488 & 2,665   & 114,204 & 184,794\\
+%Total    & 14,271 & 81,045 & 798 & 3,865 & 1,977   & 1,095 & 8,488 & 2,665   & 114,204 & 184,794 \\
 %\enddata
@@
 
-Photometric and spectroscopic data for the SDSS Stripe~82 galaxies are taken from the CasJobs DR7 tables.
-This includes $ugriz$ Petrosian magnitudes and fluxes, as well as the relative de~Vaucouleurs and exponential fits from the model magnitudes.
-Redshifts used for the SDSS galaxies are all spectroscopic.
-82.6\% of galaxies in the single-depth images and 65.1\% of galaxies in the co-add images have a measured DR7 spectroscopic redshift.
+Photometric and spectroscopic data for the SDSS Stripe~82 galaxies are taken
+from the CasJobs DR7 tables. This includes $ugriz$ Petrosian magnitudes and
+fluxes, as well as the relative de~Vaucouleurs and exponential fits from the
+model magnitudes. Redshifts used for the SDSS galaxies are all spectroscopic.
+82.6\% of galaxies in the single-depth images and 65.1\% of galaxies in the
+co-add images have a measured DR7 spectroscopic redshift.
 
@@
 
-\subsection{User weighting}\label{ssec:weighting}
-The votes of individual users who classified galaxies in GZH are combined to make a vote fraction for each response to a question ($f_{response}$) on the classification tree.
-Users' votes are weighted slightly \citep[in a method identical to that described in][]{wil13} such that users who frequently disagree with all other users end up having very low weights.
-The user weighting $(w)$ is 1 for the top 95\% of users as ranked by consistency.
-For the bottom 5\% of users, $w$ drops smoothly and is effectively zero for only the bottom 1\% of classifiers in the CDF.
-Since this only affects a tiny percentage of the users (and an even smaller percentage of the classifications) the overall effect on the GZH dataset is minimal.
-This method is effective, however, at filtering out contributions from random or deliberately malicious classifiers.
-
-Classifications for a particular user are aggregated and weighted only if they were logged into GZH under their username (which is encouraged, but not required for participation).
-Classifications by users not logged in are marked as ``Anonymous''; no weighting is applied to these classifications, but they are otherwise treated identically in the data processing.
+\subsection{User weighting}\label{ssec:weighting} The votes of individual users
+who classified galaxies in GZH are combined to make a vote fraction for each
+response to a question ($f_{response}$) on the classification tree. Users'
+votes are weighted slightly \citep[in a method identical to that described
+in][]{wil13} such that users who frequently disagree with all other users end
+up having very low weights. The user weighting $(w)$ is 1 for the top 95\% of
+users as ranked by consistency. For the bottom 5\% of users, $w$ drops smoothly
+and is effectively zero for only the bottom 1\% of classifiers in the CDF.
+Since this only affects a tiny percentage of the users (and an even smaller
+percentage of the classifications) the overall effect on the GZH dataset is
+minimal. This method is effective, however, at filtering out contributions from
+random or deliberately malicious classifiers.
+
+Classifications for a particular user are aggregated and weighted only if they
+were logged into GZH under their username (which is encouraged, but not
+required for participation). Classifications by users not logged in are marked
+as ``Anonymous''; no weighting is applied to these classifications, but they
+are otherwise treated identically in the data processing.
 
@@
 \includegraphics[width=160mm]{figures/gzh_interface.png}
-\caption{Screenshot of the GZH interface (\url{http:/zoo3.galaxyzoo.org}) at the beginning of a classification, with the user ready to select an answer for the first question in the decision tree.\label{fig:interface}}
+\caption{Screenshot of the GZH interface (\url{http:/zoo3.galaxyzoo.org}) at
+the beginning of a classification, with the user ready to select an answer for
+the first question in the decision tree.\label{fig:interface}}
 \end{figure*}
 
-Classifications for GZH are made using a web-based interface (Figure~\ref{fig:interface}), similar in design to Galaxy~Zoo and Galaxy~Zoo~2.
-The front-end runs on a Ruby~on~Rails framework with classifications stored in a MySQL backend.
-Users are shown a randomly-selected color composite image from the GZH sample; the default shows the image with a black sky background, although users have the options to invert the color palette if desired.
-The questions and responses for morphology appear on the right side of the image as a panel, including both text and icons.
-There is no tutorial required for participation, although users can access an extensive ``Help'' section containing example images and descriptive text for all the morphological labels.
+Classifications for GZH are made using a web-based interface
+(Figure~\ref{fig:interface}), similar in design to Galaxy~Zoo and Galaxy~Zoo~2.
+The front-end runs on a Ruby~on~Rails framework with classifications stored in
+a MySQL backend. Users are shown a randomly-selected color composite image from
+the GZH sample; the default shows the image with a black sky background,
+although users have the options to invert the color palette if desired. The
+questions and responses for morphology appear on the right side of the image as
+a panel, including both text and icons. There is no tutorial required for
+participation, although users can access an extensive ``Help'' section
+containing example images and descriptive text for all the morphological
+labels.
 
@@
 \includegraphics[width=\textwidth]{figures/gzh_decision_tree.pdf}
-\caption{Flowchart of the questions presented to GZH users, labeled with the corresponding Task numbers.
-Tasks in the decision tree are color-coded by tier level: Gray-colored Tasks are 1$^\mathrm{st}$-tier questions which are asked of all users.
-Tasks colored green, blue, purple, and pink (respectively) are one, two, three, or four steps below branching points in the decision tree.}
+\caption{Flowchart of the questions presented to GZH users, labeled with the
+corresponding Task numbers. Tasks in the decision tree are color-coded by tier
+level: Gray-colored Tasks are 1$^\mathrm{st}$-tier questions which are asked of
+all users. Tasks colored green, blue, purple, and pink (respectively) are one,
+two, three, or four steps below branching points in the decision tree.}
 \label{fig:decisiontree}
@@
 
-The procedure for classifying an image in GZH follows a hierarchical decision tree (Figure~\ref{fig:decisiontree}).
-Every classification begins with the user identifying whether the object at the center of the image is a smooth galaxy, a galaxy with a disk or other features, or a star/artifact.
-Subsequent questions in the tree depend on the previous answer(s) given by the user; the structure of the decision tree is designed so that the user will answer every question relevant to the morphology that they have identified.
-Questions that are not answered are implicitly assumed to be absent in the image --- for example, if the user identifies a galaxy as being smooth, they are not asked to count the number of spiral arms.
-For every task, the user chooses a single answer before continuing to the next question; they have also the option to restart a classification in-progress if a mistake has been made.
-
-The GZH decision tree has four broad sets of morphologies classified by the users.
-The first option is designating the object as a star or image artifact (the result of either bad data or incorrect classification by the ACS pipeline as a galaxy); in this case, the classification ends and no further questions are asked.
-The second set are smooth galaxies, intended to select ellipticals/early-types; users also measure the relative axial ratio (roundness) for these galaxies.
-The third set is for disk/late-type galaxies, which measures the features necessary to place a galaxy on the standard Hubble tuning fork (bars, spiral arm, strength of the central bulge).
-The final set, which is new to the high-redshift targets in GZH, asks users to identify objects dominated by clumpy morphologies.
-Further annotations for these galaxies includes assessing the number, arrangement, relative brightness, and location of the clumps within the galaxy.
-Finally, every classification of a galaxy gives users the option of identifying ``odd'' features within the image; these labels are for relatively rare $(\lesssim1\%)$ phenomena, including dust lanes, gravitational lenses, and mergers.
-
-The number of independent classifications per subject collected by GZH is on average higher than GZ1 or GZ2, due to both the increased complexity of the decision tree and the relative difficulty of classifying images of small and distant galaxies.
-Images from the main AEGIS, GEMS, and GOODS data sets have a median of 122~independent classifications per image.
-The remainder of the images either had a later activation date (COSMOS, simulated AGN) or by a lower retirement limit (the low-redshift SDSS Stripe~82 galaxies).
-Images from these samples have a median of 46--48~classifications per image (Figure~\ref{fig:classification_hist}).
+The procedure for classifying an image in GZH follows a hierarchical decision
+tree (Figure~\ref{fig:decisiontree}). Every classification begins with the user
+identifying whether the object at the center of the image is a smooth galaxy, a
+galaxy with a disk or other features, or a star/artifact. Subsequent questions
+in the tree depend on the previous answer(s) given by the user; the structure
+of the decision tree is designed so that the user will answer every question
+relevant to the morphology that they have identified. Questions that are not
+answered are implicitly assumed to be absent in the image --- for example, if
+the user identifies a galaxy as being smooth, they are not asked to count the
+number of spiral arms. For every task, the user chooses a single answer before
+continuing to the next question; they have also the option to restart a
+classification in-progress if a mistake has been made.
+
+The GZH decision tree has four broad sets of morphologies classified by the
+users. The first option is designating the object as a star or image artifact
+(the result of either bad data or incorrect classification by the ACS pipeline
+as a galaxy); in this case, the classification ends and no further questions
+are asked. The second set are smooth galaxies, intended to select
+ellipticals/early-types; users also measure the relative axial ratio
+(roundness) for these galaxies. The third set is for disk/late-type galaxies,
+which measures the features necessary to place a galaxy on the standard Hubble
+tuning fork (bars, spiral arm, strength of the central bulge). The final set,
+which is new to the high-redshift targets in GZH, asks users to identify
+objects dominated by clumpy morphologies. Further annotations for these
+galaxies includes assessing the number, arrangement, relative brightness, and
+location of the clumps within the galaxy. Finally, every classification of a
+galaxy gives users the option of identifying ``odd'' features within the image;
+these labels are for relatively rare $(\lesssim1\%)$ phenomena, including dust
+lanes, gravitational lenses, and mergers.
+
+The number of independent classifications per subject collected by GZH is on
+average higher than GZ1 or GZ2, due to both the increased complexity of the
+decision tree and the relative difficulty of classifying images of small and
+distant galaxies. Images from the main AEGIS, GEMS, and GOODS data sets have a
+median of 122~independent classifications per image. The remainder of the
+images either had a later activation date (COSMOS, simulated AGN) or by a lower
+retirement limit (the low-redshift SDSS Stripe~82 galaxies). Images from these
+samples have a median of 46--48~classifications per image
+(Figure~\ref{fig:classification_hist}).
 
@@
 \includegraphics[width=0.5\textwidth]{figures/classification_hist.pdf}
-\caption{Distribution of the total number of classifications per image for GZH, split by survey.}
+\caption{Distribution of the total number of classifications per image for GZH,
+split by survey.}
 \label{fig:classification_hist}
@@
 
-The GZH project was launched on 23~Apr~2010 with the inclusion of the AEGIS, GEMS, GOODS 2-epoch, and SDSS Stripe~82 images.
-Images from COSMOS and the simulated AGN were activated in Dec 2010, as well as a small sample of AEGIS/GEMS/GOODS images mistakenly excluded from the original sample based on an overly restrictive cut on blended and/or saturated objects.
-The main GZH site collected data until its replacement, the Galaxy~Zoo:~CANDELS project, began on 10~Sep~2012.
-Classifications for the GOODS 5-epoch images were separately obtained with the fourth version of the site\footnote{\url{http://www.galaxyzoo.org}} from Mar-Jun 2015.
-The GZH project had a total of 10,349,357~classifications from 93,898 registered participants.
+The GZH project was launched on 23~Apr~2010 with the inclusion of the AEGIS,
+GEMS, GOODS 2-epoch, and SDSS Stripe~82 images. Images from COSMOS and the
+simulated AGN were activated in Dec 2010, as well as a small sample of
+AEGIS/GEMS/GOODS images mistakenly excluded from the original sample based on
+an overly restrictive cut on blended and/or saturated objects. The main GZH
+site collected data until its replacement, the Galaxy~Zoo:~CANDELS project,
+began on 10~Sep~2012. Classifications for the GOODS 5-epoch images were
+separately obtained with the fourth version of the
+site\footnote{\url{http://www.galaxyzoo.org}} from Mar-Jun 2015. The GZH
+project had a total of 10,349,357~classifications from 93,898 registered
+participants. 
 % Sum is the total of the GZH SQL table plus the GOODS full-depth imaging in GZ4.
@@
 
-The previous versions of Galaxy Zoo morphology classifications \citep{lin08,wil13} were based on observations of galaxies in the Sloan Digital Sky Survey (SDSS) which have a median redshift of $z<0.2$.
-In these cases, it was assumed that there was no cosmological evolution of the morphologies of galaxies and therefore any observed changes in the distribution of galaxies with different consensus morphologies was due to the effects of redshift on the image quality (\ie, the reduction in physical resolution, surface brightness dimming, etc).
-For both previous releases of GZ morphologies, a correction for redshift-dependent bias was applied based on matching the classification fractions at the highest redshifts with those at the lowest redshift.
-\citet{bam09} and \citet{wil13} provide complete descriptions of the process for GZ1 and GZ2, respectively.
-
-In the GZH samples, the redshift range is large enough that cosmological evolution of the types and morphologies of galaxies is expected for galaxies in the sample.
-As a result, the previous methods of correcting for redshift dependent bias do not work.
-In addition, the effects of band shifting will change the images even more across these redshift ranges.
-%Figure~\ref{fig:exampleFERENGI} illustrates some of the possible effects of losing features in spiral galaxies at high redshift.
-
-In order to test and correct for the effects of redshift, GZH includes a set of calibration images.
-These images consist of the same galaxy as it would appear over a variety of redshifts.
-The input images are from the SDSS \citep{yor00,str02} and are processed using the \ferengi{} code \citep{bar08a} to match the observational properties of the \hst{} surveys out to $z=1$.
-These images were classified in the GZH interface using the same classification scheme as the original \hst{} images.
+The previous versions of Galaxy Zoo morphology classifications
+\citep{lin08,wil13} were based on observations of galaxies in the Sloan Digital
+Sky Survey (SDSS) which have a median redshift of $z<0.2$. In these cases, it
+was assumed that there was no cosmological evolution of the morphologies of
+galaxies and therefore any observed changes in the distribution of galaxies
+with different consensus morphologies was due to the effects of redshift on the
+image quality (\ie, the reduction in physical resolution, surface brightness
+dimming, etc). For both previous releases of GZ morphologies, a correction for
+redshift-dependent bias was applied based on matching the classification
+fractions at the highest redshifts with those at the lowest redshift.
+\citet{bam09} and \citet{wil13} provide complete descriptions of the process
+for GZ1 and GZ2, respectively.
+
+In the GZH samples, the redshift range is large enough that cosmological
+evolution of the types and morphologies of galaxies is expected for galaxies in
+the sample. As a result, the previous methods of correcting for redshift
+dependent bias do not work. In addition, the effects of band shifting will
+change the images even more across these redshift ranges. 
+%Figure~\ref{fig:exampleFERENGI} illustrates some of the possible effects of
+%losing features in spiral galaxies at high redshift.
+
+In order to test and correct for the effects of redshift, GZH includes a set of
+calibration images. These images consist of the same galaxy as it would appear
+over a variety of redshifts. The input images are from the SDSS
+\citep{yor00,str02} and are processed using the \ferengi{} code \citep{bar08a}
+to match the observational properties of the \hst{} surveys out to $z=1$. These
+images were classified in the GZH interface using the same classification
+scheme as the original \hst{} images.
 
@@
 
-The GZH classifications include 288 unique galaxies originally generated from SDSS imaging and processed with the \ferengi{} code.
-The selection spanned a variety of galaxy morphologies (as selected by GZ2 classifications) and $r^\prime$-band surface brightnesses, and also spanned the redshift range of SDSS targets (in $N_z = 4$ bins) in order to be optimized for different target minimum redshifts in \hst{} imaging.
+The GZH classifications include 288 unique galaxies originally generated from
+SDSS imaging and processed with the \ferengi{} code. The selection spanned a
+variety of galaxy morphologies (as selected by GZ2 classifications) and
+$r^\prime$-band surface brightnesses, and also spanned the redshift range of
+SDSS targets (in $N_z = 4$ bins) in order to be optimized for different target
+minimum redshifts in \hst{} imaging.
 
 %The selection criteria for the different morphological categories is summarized in Table \ref{tbl:morphologies}. 
-The surface brightness selection ($N_\mu = 3$) for the \ferengi{} galaxies was (1) low: $\mu > 21.5$~\magarc;  (2) mid: $20.5 < \mu < 21.5$~\magarc; and (3) high: $\mu < 20.5$~\magarc.
-For each of the four ``target redshifts'' ($z_\mathrm{sim} = 0.3, 0.5, 0.8$ and $1.0$), the images were redshifted in $\Delta z = 0.1$ bins up to $z_\mathrm{sim}=1.0$.
+The surface brightness selection ($N_\mu = 3$) for the \ferengi{} galaxies was
+(1) low: $\mu > 21.5$~\magarc;  (2) mid: $20.5 < \mu < 21.5$~\magarc; and (3)
+high: $\mu < 20.5$~\magarc. For each of the four ``target redshifts''
+($z_\mathrm{sim} = 0.3, 0.5, 0.8$ and $1.0$), the images were redshifted in
+$\Delta z = 0.1$ bins up to $z_\mathrm{sim}=1.0$.
 
@@
 
-In addition to the physical parameters of the input images, the \ferengi{} output depends on assumptions of the global galaxy evolution model.
-This evolution is a crude mechanism that mimics the brightness increase of galaxies with increasing redshift (out to at least $z\sim1-2$).
-The effect on the redshifted images is simply an empirical addition to the magnitude of a galaxy of the form $M' = e\times z + M$, where $M'$ is the corrected magnitude, and $e$ is the evolutionary correction in magnitudes (i.e., $e=-1$ essentially brightens the galaxy by 1~magnitude by $z=1$).
-\ferengi{} was run on the images for values of $e$ starting from $e=0$ and decreasing to $e=-3.5$ in increments of $\Delta e = 0.5$.
-Figure~\ref{fig:exampleFERENGI} shows several examples of the effects of ``losing'' spiral/disc features with increasing redshift for two galaxies with $e=0$.
-
-The final number of \ferengi{} images produced for each galaxy is ultimately a function of galaxy's redshift (since the new images cannot be resampled at better angular resolution than the original SDSS data), as well as the number of $e$ values selected.
-Table~\ref{tbl:ferengivalues} summarizes the redshifted images produced for GZH.
+In addition to the physical parameters of the input images, the \ferengi{}
+output depends on assumptions of the global galaxy evolution model. This
+evolution is a crude mechanism that mimics the brightness increase of galaxies
+with increasing redshift (out to at least $z\sim1-2$). The effect on the
+redshifted images is simply an empirical addition to the magnitude of a galaxy
+of the form $M' = e\times z + M$, where $M'$ is the corrected magnitude, and
+$e$ is the evolutionary correction in magnitudes (i.e., $e=-1$ essentially
+brightens the galaxy by 1~magnitude by $z=1$). \ferengi{} was run on the images
+for values of $e$ starting from $e=0$ and decreasing to $e=-3.5$ in increments
+of $\Delta e = 0.5$. Figure~\ref{fig:exampleFERENGI} shows several examples
+of the effects of ``losing'' spiral/disc features with increasing redshift
+for two galaxies with $e=0$.
+
+The final number of \ferengi{} images produced for each galaxy is ultimately a
+function of galaxy's redshift (since the new images cannot be resampled at
+better angular resolution than the original SDSS data), as well as the number
+of $e$ values selected. Table~\ref{tbl:ferengivalues} summarizes the redshifted
+images produced for GZH.
 
@@
 \includegraphics[width=160mm]{figures/example_ferengi.pdf}
-\caption{Examples of two galaxies which have been run through the \ferengi{} code to produce simulated \hst{} images.
-The measured value of \ffeatures{} from GZH for the images in each panel are (1) Top row: \ffeatures~= (0.900, 0.625, 0.350, 0.350, 0.225) and (2) Bottom row: \ffeatures~= (1.000, 0.875, 0.875, 0.625, 0.375).
-\label{fig:exampleFERENGI}}
+\caption{Examples of two galaxies which have been run through the \ferengi{}
+code to produce simulated \hst{} images. The measured value of \ffeatures{}
+from GZH for the images in each panel are (1) Top row: \ffeatures~= (0.900,
+0.625, 0.350, 0.350, 0.225) and (2) Bottom row: \ffeatures~= (1.000, 0.875,
+0.875, 0.625, 0.375). \label{fig:exampleFERENGI}}
 \end{figure*}
@@
 
-The approach used in GZH for correcting the weighted classifications for user bias rests on the assumption that the \emph{amount} of bias is a function of the apparent size and brightness of the image as seen on screen.
-This is controlled by two types of parameters: \textbf{intrinsic} properties of the galaxy itself, such as its physical diameter and luminosity, and \textbf{extrinsic} properties, such as the distance (redshift) of the galaxy and its relative orientation.
-There are likely other parameters that affect user accuracy, such as the proximity of close companions \citep[``distraction bias''; see][]{joh15} or bias as a function of individual user ability and skill.
-The combination of all such parameters forms a high-dimensional space, and it is not clear how to separate this into individual effects.
-Instead, the method used here employs only two parameters intended to capture the bulk of the change in bias: the $r^\prime$-band surface brightness ($\mu_r$; intrinsic) and redshift ($z$; extrinsic).
-
-The change in bias as a function of $\mu_r$ and \zsim{} is measured using the \ferengi{} images over all the evolutionary correction factors.
-It is assumed that the ``true'' (ie, debiased) vote fraction $f_{\mu,z}$ for a galaxy can be expressed as:
+The approach used in GZH for correcting the weighted classifications for user
+bias rests on the assumption that the \emph{amount} of bias is a function of
+the apparent size and brightness of the image as seen on screen. This is
+controlled by two types of parameters: \textbf{intrinsic} properties of the
+galaxy itself, such as its physical diameter and luminosity, and
+\textbf{extrinsic} properties, such as the distance (redshift) of the galaxy
+and its relative orientation. There are likely other parameters that affect
+user accuracy, such as the proximity of close companions \citep[``distraction
+bias''; see][]{joh15} or bias as a function of individual user ability and
+skill. The combination of all such parameters forms a high-dimensional space,
+and it is not clear how to separate this into individual effects. Instead, the
+method used here employs only two parameters intended to capture the bulk of
+the change in bias: the $r^\prime$-band surface brightness ($\mu_r$; intrinsic)
+and redshift ($z$; extrinsic).
+
+The change in bias as a function of $\mu_r$ and \zsim{} is measured using the
+\ferengi{} images over all the evolutionary correction factors. It is assumed
+that the ``true'' (ie, debiased) vote fraction $f_{\mu,z}$ for a galaxy can be
+expressed as:
 
@@
 
-\noindent where $f_{\mu,z=0.3}$ is the ``calibrated'' vote fraction at the lowest redshift in the \ferengi{} bins ($z=0.3$) and $\zeta$ is a positive parameter that controls the rate at which $f$ decreases with increasing redshift.
-This formula fits the data relatively well (with very few exceptions, the vote fractions for featured galaxies decrease monotonically with increasing redshift), and the exponential function bounds the observed vote fractions between $f_{\mu,z=0.3}$ and zero.
-Figure~\ref{fig:zeta_examples} shows the change in vote fraction and the fit to Equation~\ref{eqn:fzeta} for a random selection of galaxies in the \ferengi{} images.
+\noindent where $f_{\mu,z=0.3}$ is the ``calibrated'' vote fraction at the
+lowest redshift in the \ferengi{} bins ($z=0.3$) and $\zeta$ is a positive
+parameter that controls the rate at which $f$ decreases with increasing
+redshift. This formula fits the data relatively well (with very few exceptions,
+the vote fractions for featured galaxies decrease monotonically with increasing
+redshift), and the exponential function bounds the observed vote fractions
+between $f_{\mu,z=0.3}$ and zero. Figure~\ref{fig:zeta_examples} shows the
+change in vote fraction and the fit to Equation~\ref{eqn:fzeta} for a random
+selection of galaxies in the \ferengi{} images.
 
@@
 \includegraphics[width=\textwidth]{figures/zeta_examples.pdf}
-\caption{Behavior of the normalized, weighted vote fractions of features visible in a galaxy ($f_\textrm{features}$) as a function of redshift in the artificial \ferengi{} images.
-Galaxies in this plot were randomly selected from a distribution with $e=0$ and at least three detectable images in redshift bins of $z\ge0.3$.
-Measured vote fractions (red points) are fit with an exponential function (Equation~\ref{eqn:fzeta}); the best-fit parameters are given above each plot.
-Error bars are Poissonian, assuming a median of 40~votes per galaxy.}
+\caption{Behavior of the normalized, weighted vote fractions of features
+visible in a galaxy ($f_\textrm{features}$) as a function of redshift in the
+artificial \ferengi{} images. Galaxies in this plot were randomly selected from
+a distribution with $e=0$ and at least three detectable images in redshift bins
+of $z\ge0.3$. Measured vote fractions (red points) are fit with an exponential
+function (Equation~\ref{eqn:fzeta}); the best-fit parameters are given above
+each plot. Error bars are Poissonian, assuming a median of 40~votes per
+galaxy.}
 \label{fig:zeta_examples}
@@
 
-GZH uses the values of $\zeta$ for \emph{all} sets of artificially redshifted galaxies to fit the overall distribution as a function of surface brightness, since the correction being applied is expected to vary as a function of the intrinsic galaxy properties.
-The galaxies that can be used to measure the calibration are restricted to those with a non-zero $f_\textrm{features}$ at $z_\mathrm{sim}=0.3$ and with a reasonable fit ($\Delta \chi^2 > 3.0$) to the exponential model for the measured change in \ffeatures.
-
-Figure~\ref{fig:zeta_mu} shows the results of fitting the \ferengi{} images with Equation~\ref{eqn:fzeta}; the correction is only a weak function of surface brightness ($\mu$).
-Higher-surface brightness galaxies have stronger average corrections, likely because these galaxies are more likely to have larger $f_\textrm{features}$ values at high redshifts.
-Low surface brightness galaxies are more likely to begin low and remain low; the bounded nature of the dropoff (and variance among the individual voters) means that the average magnitude of $\zeta$ will be lower.
+GZH uses the values of $\zeta$ for \emph{all} sets of artificially redshifted
+galaxies to fit the overall distribution as a function of surface brightness,
+since the correction being applied is expected to vary as a function of the
+intrinsic galaxy properties. The galaxies that can be used to measure the
+calibration are restricted to those with a non-zero $f_\textrm{features}$ at
+$z_\mathrm{sim}=0.3$ and with a reasonable fit ($\Delta \chi^2 > 3.0$) to the
+exponential model for the measured change in \ffeatures.
+
+Figure~\ref{fig:zeta_mu} shows the results of fitting the \ferengi{} images
+with Equation~\ref{eqn:fzeta}; the correction is only a weak function of
+surface brightness ($\mu$). Higher-surface brightness galaxies have stronger
+average corrections, likely because these galaxies are more likely to have
+larger $f_\textrm{features}$ values at high redshifts. Low surface brightness
+galaxies are more likely to begin low and remain low; the bounded nature of the
+dropoff (and variance among the individual voters) means that the average
+magnitude of $\zeta$ will be lower.
 
@@
 \includegraphics[width=0.50\textwidth]{figures/zeta_mu.png}
-\caption{All fits for the vote fraction dropoff parameter $\zeta$ for $f_\textrm{features}$ in the \ferengi{} galaxies as a function of surface brightness.
-This includes only the 37~galaxies with a reasonably bounded range on the dropoff ($-10<\log(\zeta)<10$) and sufficient points to fit the function.}
+\caption{All fits for the vote fraction dropoff parameter $\zeta$ for
+$f_\textrm{features}$ in the \ferengi{} galaxies as a function of surface
+brightness. This includes only the 37~galaxies with a reasonably bounded range
+on the dropoff ($-10<\log(\zeta)<10$) and sufficient points to fit the
+function.}
 \label{fig:zeta_mu}
@@
 
-\noindent where $\hat\zeta$ is the correction factor applied to each galaxy as a function of surface brightness.
-The best-fit parameters to the linear fit (from least-squares optimization) are $\zeta_0=0.1$, $\zeta_1=1.4$.
-To make the final debiased correction, the simple exponential form of Equation~\ref{eqn:fzeta} is modified to bound the debiased vote fractions between $f$ and 1:
+\noindent where $\hat\zeta$ is the correction factor applied to each galaxy as
+a function of surface brightness. The best-fit parameters to the linear fit
+(from least-squares optimization) are $\zeta_0=0.1$, $\zeta_1=1.4$. To make the
+final debiased correction, the simple exponential form of
+Equation~\ref{eqn:fzeta} is modified to bound the debiased vote fractions
+between $f$ and 1:
 
@@
 \includegraphics[width=0.5\textwidth]{figures/eye_of_sauron.pdf}
-\caption{Surface brightness as a function of redshift for 3,950~\ferengi{} images and the 102,548~galaxies in the ACS sample with measured $\mu$ and $z$ values.
-The color histogram shows the number of \ferengi{} images as a function of $\mu$ and $z_{\rm sim}$.
-White contours show counts for the full ACS sample, with contours starting at $N=1000$ and separated by intervals of 1000 up to 7000.}
+\caption{Surface brightness as a function of redshift for 3,950~\ferengi{}
+images and the 102,548~galaxies in the ACS sample with measured $\mu$ and $z$
+values. The color histogram shows the number of \ferengi{} images as a function
+of $\mu$ and $z_{\rm sim}$. White contours show counts for the full ACS sample,
+with contours starting at $N=1000$ and separated by intervals of 1000 up to
+7000.} 
 \label{fig:sb_redshift}
@@
 \caption{Effects of redshift bias in 3,950 images in the \ferengi{} sample.
-[a]: Each point in a given redshift and surface brightness bin represents a unique galaxy.
-On the $y$-axis in each bin is the \ffeatures{} value of the image of that galaxy redshifted to the value corresponding to that redshift bin.
-On the $x$-axis is the \ffeatures{} value of the image of the same galaxy redshifted to $z=0.3$.
-The dashed black lines represent the best-fit polynomials to the data in each square.
-The solid black line represents \ffeaturesz=\ffeaturesrest.
-Regions in which there is a single-valued relationship between \ffeatures{} at high redshift and at $z=0.3$ are white; those in which there is not are blue, and those with not enough data ($N<5$) are gray.
-[b]: A larger version of the dark-outlined square in [a], containing \ferengi{} galaxies that have been artificially redshifted to $z=1.0$ and have surface brightnesses between $20.3 < \mu < 21.0$ $\rm (mag/arcsec^2)$.
-[c]: The same data as [a] is shown.
-Each $z,\mu$ bin is divided into 4 sub-bins to determine the range of intrinsic \ffeaturesrest{} for a given range of observed \ffeaturesz{} values.
-In each sub-bin, the orange bars represent the inner 80$^\mathrm{th}$ percentiles of the data, the boundaries of which are the lower and upper limits of the debiased values.
-[d]: The same data as [b], but highlighting the upper and lower limit regions.}
+[a]: Each point in a given redshift and surface brightness bin represents a
+unique galaxy. On the $y$-axis in each bin is the \ffeatures{} value of the
+image of that galaxy redshifted to the value corresponding to that redshift
+bin. On the $x$-axis is the \ffeatures{} value of the image of the same galaxy
+redshifted to $z=0.3$. The dashed black lines represent the best-fit
+polynomials to the data in each square. The solid black line represents
+\ffeaturesz=\ffeaturesrest. Regions in which there is a single-valued
+relationship between \ffeatures{} at high redshift and at $z=0.3$ are white;
+those in which there is not are blue, and those with not enough data ($N<5$)
+are gray. [b]: A larger version of the dark-outlined square in [a], containing
+\ferengi{} galaxies that have been artificially redshifted to $z=1.0$ and have
+surface brightnesses between $20.3 < \mu < 21.0$ $\rm (mag/arcsec^2)$. [c]: The
+same data as [a] is shown. Each $z,\mu$ bin is divided into 4 sub-bins to
+determine the range of intrinsic \ffeaturesrest{} for a given range of observed
+\ffeaturesz{} values. In each sub-bin, the orange bars represent the inner
+80$^\mathrm{th}$ percentiles of the data, the boundaries of which are the lower
+and upper limits of the debiased values. [d]: The same data as [b], but
+highlighting the upper and lower limit regions.}
 \label{fig:f_vs_f}
@@
 
-Figure~\ref{fig:f_vs_f} shows the change in \ffeatures{} for the \ferengi{} galaxies relative to their lowest simulated redshift.
-In this analysis, only galaxies whose lowest simulated redshift image was $z_\mathrm{sim}=0.3$ were used (see Table \ref{tbl:ferengivalues}), and only those which had detectable surface brightness measurements in \sextractor; this includes 3,950 of the total 6,466 images.
-For each simulated redshift value \zsim{} at a fixed surface brightness $\mu$, \ffeaturesz, the value measured at that simulated redshift, is plotted against \ffeaturesrest, the value measured for the same galaxy at \zsim$=0.3$.
-
-The objective is to use these data to predict, for a galaxy with a measured \ffeaturesz{} value, what its \ffeatures{} value \emph{would have been} if it had been viewed at $z=0.3$.
-This predicted value is defined as the debiased vote fraction \ffeaturesdebiased, and is calculated by applying a correction to the measured value of \ffeatures, determined by the $\zeta$ function described in the previous section.
-A reliable predicted value can be obtained so long as the relationship between \ffeaturesz{} and \ffeaturesrest{} is single-valued; that is, for a given \ffeaturesz, there is exactly one corresponding value of \ffeatures{} at $z=0.3$.
-
-Figure~\ref{fig:f_vs_f} shows that the relationship between \ffeaturesz{} and \ffeaturesrest{} is \emph{not} always single valued; hence, it is not appropriate to correct galaxies that lie in certain regions of surface brightness/redshift/\ffeatures{} space.
-These regions tend to have low \ffeatures{} values at high redshift, but a wide range of values at $z=0.3$.
-These regions contain two morphological types of galaxies: the first set are genuine ellipticals, which have low values of \ffeatures{} at both high and low redshift.
-The second group are disks whose features become indistinct at high redshift; hence their \ffeatures{} value at $z=0.3$ may be quite high, while the value observed at high redshift is very low.
-This effect is strongest at high $z$ and low $\mu$, where features become nearly impossible to discern in the images.
-
-The criteria for determining whether a region of this space is single-valued, and therefore correctable, is as follows: In each surface brightness and redshift bin, the relationship between \ffeaturesz{} and \ffeaturesrest{} is modeled by fitting the data with a polynomial of degrees $n=3$, 2, and 1, and using the best formal fit out of the three as measured by the sum of the residuals.
-These fits are shown as the dashed black lines in Figure~\ref{fig:6a}.
-Any flat regions of the polynomial fits are areas in which there is not a clear single-valued relationship between \ffeaturesz{} and \ffeaturesrest; this is quantified by setting a minimum slope cut of 0.4.
-Any data in which the polynomial fit has a slope less than this value is considered \emph{not} one-to-one, and therefore \ffeaturesz{} cannot be boosted to its \ffeaturesrest{} value.
-Galaxies in this region are referred to as the \emph{lower limit} sample.
-These regions are highlighted in blue in Figure~\ref{fig:6a}.
-Uncolored (white) regions of the plot have sufficiently high slopes to consider the relationship as single-valued; galaxies in these regions are considered ``correctable'', and only these are used in measuring the parameters for the $\zeta$ function (Section~\ref{ssec:zeta}).
-Only surface brightness/redshift bins with at least 5 galaxies were considered; regions with fewer than 5 galaxies are considered to have ``not enough information'' to determine the \ffeaturesz{} and \ffeaturesrest{} relationship, colored gray in Figure~\ref{fig:6a}.
-
-The unshaded regions in Figure~\ref{fig:6a} define discrete ranges of redshift, surface brightness, and \ffeatures{} a galaxy must have in order for the debiased correction to be confidently applied to a galaxy in the GZH sample.
-While the appropriate correctable regions were defined discretely, the true correctable region is assumed to be a smooth function of $z$, $\mu$, and \ffeatures{}.
-To define this smooth space, we calculate the shape of the convex hull that encloses the correctable and lower-limit \ferengi{} galaxies in $z$-$\mu$-\ffeatures{} space.
-The boundaries are then adjusted until the contamination from both groups is minimized.
-The resulting hulls define the correctable and lower-limit regions for categorizing the \hst{} galaxies.
-The results of this method and final categorization of the \hst{} sample are in Table~\ref{tbl:hubble_debiasable}.
-Of the galaxies at redshift higher than $z=0.3$, 17\% can be debiased using the $\zeta$ method, 27\% cannot be debiased, and 56\% cannot have the potential for a correction determined, due either to an unknown redshift or insufficient \ferengi{} images corresponding to the relevant $z$-$\mu$ values.
-
-For the ``lower-limit'' galaxies for which a single debiased \ffeatures{} value cannot be confidently assigned, the \emph{range} of debiased values is estimated using a method visualized in Figure~\ref{fig:6c}.
-This uses the \ferengi{} simulated data to analyze the range of intrinsic \ffeaturesrest{} values for any given observed \ffeatures{} value, again as a function of surface brightness and redshift.
-Each $z$,$\mu$ bin, shows the spread of intrinsic values of \ffeaturesrest{} for four ranges of observed \ffeatures.
-The range of intrinsic values is defined as the inner 80\% of the data, represented by the orange bars in Figure~\ref{fig:6c}.
-For any galaxy which cannot be directly debiased by the $\zeta$ method, these ranges are used to denote the upper and lower limits on the expected values \ffeaturesrest{} as a function of the observed \ffeatures.
+Figure~\ref{fig:f_vs_f} shows the change in \ffeatures{} for the \ferengi{}
+galaxies relative to their lowest simulated redshift. In this analysis, only
+galaxies whose lowest simulated redshift image was $z_\mathrm{sim}=0.3$ were
+used (see Table \ref{tbl:ferengivalues}), and only those which had detectable
+surface brightness measurements in \sextractor; this includes 3,950 of the
+total 6,466 images. For each simulated redshift value \zsim{} at a fixed
+surface brightness $\mu$, \ffeaturesz, the value measured at that simulated
+redshift, is plotted against \ffeaturesrest, the value measured for the same
+galaxy at \zsim$=0.3$.
+
+The objective is to use these data to predict, for a galaxy with a measured
+\ffeaturesz{} value, what its \ffeatures{} value \emph{would have been} if it
+had been viewed at $z=0.3$. This predicted value is defined as the debiased
+vote fraction \ffeaturesdebiased, and is calculated by applying a correction to
+the measured value of \ffeatures, determined by the $\zeta$ function described
+in the previous section. A reliable predicted value can be obtained so long as
+the relationship between \ffeaturesz{} and \ffeaturesrest{} is single-valued;
+that is, for a given \ffeaturesz, there is exactly one corresponding value of
+\ffeatures{} at $z=0.3$.
+
+Figure~\ref{fig:f_vs_f} shows that the relationship between \ffeaturesz{} and
+\ffeaturesrest{} is \emph{not} always single valued; hence, it is not
+appropriate to correct galaxies that lie in certain regions of surface
+brightness/redshift/\ffeatures{} space. These regions tend to have low
+\ffeatures{} values at high redshift, but a wide range of values at $z=0.3$.
+These regions contain two morphological types of galaxies: the first set are
+genuine ellipticals, which have low values of \ffeatures{} at both high and low
+redshift. The second group are disks whose features become indistinct at high
+redshift; hence their \ffeatures{} value at $z=0.3$ may be quite high, while
+the value observed at high redshift is very low. This effect is strongest at
+high $z$ and low $\mu$, where features become nearly impossible to discern in
+the images.
+
+The criteria for determining whether a region of this space is single-valued,
+and therefore correctable, is as follows: In each surface brightness and
+redshift bin, the relationship between \ffeaturesz{} and \ffeaturesrest{} is
+modeled by fitting the data with a polynomial of degrees $n=3$, 2, and 1, and
+using the best formal fit out of the three as measured by the sum of the
+residuals. These fits are shown as the dashed black lines in
+Figure~\ref{fig:6a}. Any flat regions of the polynomial fits are areas in which
+there is not a clear single-valued relationship between \ffeaturesz{} and
+\ffeaturesrest; this is quantified by setting a minimum slope cut of 0.4. Any
+data in which the polynomial fit has a slope less than this value is considered
+\emph{not} one-to-one, and therefore \ffeaturesz{} cannot be boosted to its
+\ffeaturesrest{} value. Galaxies in this region are referred to as the
+\emph{lower limit} sample. These regions are highlighted in blue in
+Figure~\ref{fig:6a}. Uncolored (white) regions of the plot have sufficiently
+high slopes to consider the relationship as single-valued; galaxies in these
+regions are considered ``correctable'', and only these are used in measuring
+the parameters for the $\zeta$ function (Section~\ref{ssec:zeta}). Only surface
+brightness/redshift bins with at least 5 galaxies were considered; regions with
+fewer than 5 galaxies are considered to have ``not enough information'' to
+determine the \ffeaturesz{} and \ffeaturesrest{} relationship, colored gray in
+Figure~\ref{fig:6a}.
+
+The unshaded regions in Figure~\ref{fig:6a} define discrete ranges of redshift,
+surface brightness, and \ffeatures{} a galaxy must have in order for the
+debiased correction to be confidently applied to a galaxy in the GZH sample.
+While the appropriate correctable regions were defined discretely, the true
+correctable region is assumed to be a smooth function of $z$, $\mu$, and
+\ffeatures{}. To define this smooth space, we calculate the shape of the convex
+hull that encloses the correctable and lower-limit \ferengi{} galaxies in
+$z$-$\mu$-\ffeatures{} space. The boundaries are then adjusted until the
+contamination from both groups is minimized. The resulting hulls define the
+correctable and lower-limit regions for categorizing the \hst{} galaxies. The
+results of this method and final categorization of the \hst{} sample are in
+Table~\ref{tbl:hubble_debiasable}. Of the galaxies at redshift higher than
+$z=0.3$, 17\% can be debiased using the $\zeta$ method, 27\% cannot be
+debiased, and 56\% cannot have the potential for a correction determined, due
+either to an unknown redshift or insufficient \ferengi{} images corresponding
+to the relevant $z$-$\mu$ values.
+
+For the ``lower-limit'' galaxies for which a single debiased \ffeatures{} value
+cannot be confidently assigned, the \emph{range} of debiased values is
+estimated using a method visualized in Figure~\ref{fig:6c}. This uses the
+\ferengi{} simulated data to analyze the range of intrinsic \ffeaturesrest{}
+values for any given observed \ffeatures{} value, again as a function of
+surface brightness and redshift. Each $z$,$\mu$ bin, shows the spread of
+intrinsic values of \ffeaturesrest{} for four ranges of observed \ffeatures.
+The range of intrinsic values is defined as the inner 80\% of the data,
+represented by the orange bars in Figure~\ref{fig:6c}. For any galaxy which
+cannot be directly debiased by the $\zeta$ method, these ranges are used to
+denote the upper and lower limits on the expected values \ffeaturesrest{} as a
+function of the observed \ffeatures.
 
@@
 \caption{Distribution of \ferengi{} images analyzed in Figure~\ref{fig:f_vs_f}.
-Correctable images have a single-valued relationship between their measured \ffeatures{} values at high and low redshifts (white regions in Figure~\ref{fig:f_vs_f}).
-Images with only a lower-limit on \ffeatures{} have a non single-valued relationship (blue regions).
-NEI (``not enough information'') images have undetermined relationships due to a lack of data ($N<5$) in their corresponding $z$-$\mu$ bins (gray regions).\label{tbl:ferengi_corrections}}
+Correctable images have a single-valued relationship between their measured
+\ffeatures{} values at high and low redshifts (white regions in
+Figure~\ref{fig:f_vs_f}). Images with only a lower-limit on \ffeatures{} have a
+non single-valued relationship (blue regions). NEI (``not enough information'')
+images have undetermined relationships due to a lack of data ($N<5$) in their
+corresponding $z$-$\mu$ bins (gray regions).\label{tbl:ferengi_corrections}}
 \begin{tabular}{lrr}
@@
 
-Few galaxies in the sample have sufficiently high corrections to completely change them from being confidently smooth to featured following the bias correction (Figure~\ref{fig:debiased_corrections}).
-As a check, highly boosted galaxies are compared to the expert classifications in CANDELS \citep{kar15}.
-There are only eight galaxies that were strongly boosted (\ffeatures$<0.2$ and \fbest$>0.5$) in GZH and also appears in the CANDELS expert sample.
-Of those eight galaxies, \citet{kar15} classify 5 as spheroids, 2 as disks, and 1 as irregular/disky.
-The \fbest{} values for GZH are all between 0.5 and 0.6, making them intermediate disk candidates.
-One of the spheroids has a hint of extended emission to the south that may have been missed by the CANDELS experts, but almost all images are dim and with very low surface brightnesses in the ACS imaging, making positive identification challenging.
-Since the surveys use different rest-frame filters and the overlap sample is tiny, though, detailed comparisons between the overall morphologies are highly difficult.
+Few galaxies in the sample have sufficiently high corrections to completely
+change them from being confidently smooth to featured following the bias
+correction (Figure~\ref{fig:debiased_corrections}). As a check, highly boosted
+galaxies are compared to the expert classifications in CANDELS \citep{kar15}.
+There are only eight galaxies that were strongly boosted (\ffeatures$<0.2$ and
+\fbest$>0.5$) in GZH and also appears in the CANDELS expert sample. Of those
+eight galaxies, \citet{kar15} classify 5 as spheroids, 2 as disks, and 1 as
+irregular/disky. The \fbest{} values for GZH are all between 0.5 and 0.6,
+making them intermediate disk candidates. One of the spheroids has a hint of
+extended emission to the south that may have been missed by the CANDELS
+experts, but almost all images are dim and with very low surface brightnesses
+in the ACS imaging, making positive identification challenging. Since the
+surveys use different rest-frame filters and the overlap sample is tiny,
+though, detailed comparisons between the overall morphologies are highly
+difficult.
 
@@
 \includegraphics[width=\textwidth]{figures/debiased_corrections.pdf}
-\caption{Debiased \ffeatures{} corrected to $z=0.3$ vs weighted \ffeatures{} for the correctable (left), lower-limit (middle), and NEI (right) galaxies in the GZH sample.}
+\caption{Debiased \ffeatures{} corrected to $z=0.3$ vs weighted \ffeatures{}
+for the correctable (left), lower-limit (middle), and NEI (right) galaxies in
+    the GZH sample.}
 \label{fig:debiased_corrections}
@@
 
-\subsection{Challenges of debiasing questions beyond ``smooth or features''}
-\label{ssec:higher_order_tasks}
-As with the HST images, each \ferengi{} subject has a varying number of users answering the various questions in the hierarchical decision tree.
-Every user answers the first question, {\it ``Is the galaxy smooth and rounded, with no sign of a disk?''}; as such the vote fractions \fsmooth, \ffeatures, and \fartifact{} are all computed with the minimum statistical error for any question, with between 40 and 140~responses (see Section~\ref{sec:interface}).
-The number of users to answer any subsequent question, however, is always equal to or less than the number to answer the preceding question.
-The average number of responses per task for fourth- or fifth-tier questions such as spiral arm structure (Tasks 12--14) is only $4\pm4$ for the \ferengi{} sample; while this is distribution is strongly bimodal (reflecting the true morphologies of selected galaxies), the very low absolute numbers of votes introduce very high variance when attempting to calculate a statistical correction.
-
-In the \ferengi{} data, these numbers severely limit the amount of information that can be extracted for the higher-tier questions.
-The debiasing technique used (Section~\ref{ssec:zeta}) requires that at least 10~users answer each question for a galaxy with $z_\mathrm{sim}=0.3$ \emph{and} the corresponding image at higher redshift.
-This requirement is (by default) met by all galaxies for the smooth/features question.
-However, this is often \emph{not} met for questions beyond Task~01; on average.
-$60\%\pm24\%$ of the galaxies do not have sufficient data to measure a correction, as compared to 2.0\% achieved for Task~01 (Table~\ref{tbl:ferengi_corrections}).
-Of the remaining \ferengi{} galaxies which did meet this requirement, polynomials were fit to the data in each redshift-surface brightness bin, as was done for Task~01.
-The goodness-of-fit was evaluated in each bin, for each Task, using a normalized $\chi^2$ metric.
-The mean $\chi^2$ for all higher-order tasks was $0.10\pm0.04$, significantly larger than the Task~01 value of $0.04$.
-Based on this statistic, the data cannot not be modeled with sufficient confidence for the higher order tasks.
-An example of the debiasing technique applied to \fbar{} is shown in Section~\ref{sec:ferengi_bar}; visual inspection of Figure~\ref{fig:f_vs_fbar} confirms that the points in each bin are scattered to a degree at which no strong correlation is present.
-For these reasons, debiased vote fractions are only offered in the GZH catalog for Task~01 (smooth/features).
+\subsection{Challenges of debiasing questions beyond ``smooth or features''}\label{ssec:higher_order_tasks}
+
+As with the HST images, each \ferengi{} subject has a varying number of users
+answering the various questions in the hierarchical decision tree. Every user
+answers the first question, {\it ``Is the galaxy smooth and rounded, with no
+sign of a disk?''}; as such the vote fractions \fsmooth, \ffeatures, and
+\fartifact{} are all computed with the minimum statistical error for any
+question, with between 40 and 140~responses (see Section~\ref{sec:interface}).
+The number of users to answer any subsequent question, however, is always equal
+to or less than the number to answer the preceding question. The average number
+of responses per task for fourth- or fifth-tier questions such as spiral arm
+structure (Tasks 12--14) is only $4\pm4$ for the \ferengi{} sample; while this
+is distribution is strongly bimodal (reflecting the true morphologies of
+selected galaxies), the very low absolute numbers of votes introduce very high
+variance when attempting to calculate a statistical correction.
+
+In the \ferengi{} data, these numbers severely limit the amount of information
+that can be extracted for the higher-tier questions. The debiasing technique
+used (Section~\ref{ssec:zeta}) requires that at least 10~users answer each
+question for a galaxy with $z_\mathrm{sim}=0.3$ \emph{and} the corresponding
+image at higher redshift. This requirement is (by default) met by all galaxies
+for the smooth/features question. However, this is often \emph{not} met for
+questions beyond Task~01; on average. $60\%\pm24\%$ of the galaxies do not have
+sufficient data to measure a correction, as compared to 2.0\% achieved for
+Task~01 (Table~\ref{tbl:ferengi_corrections}). Of the remaining
+\ferengi{} galaxies which did meet this requirement, polynomials were fit to
+the data in each redshift-surface brightness bin, as was done for Task~01. The
+goodness-of-fit was evaluated in each bin, for each Task, using a normalized
+$\chi^2$ metric. The mean $\chi^2$ for all higher-order tasks was
+$0.10\pm0.04$, significantly larger than the Task~01 value of $0.04$. Based on
+this statistic, the data cannot not be modeled with sufficient confidence for
+the higher order tasks. An example of the debiasing technique applied to
+\fbar{} is shown in Section~\ref{sec:ferengi_bar}; visual inspection of
+Figure~\ref{fig:f_vs_fbar} confirms that the points in each bin are scattered
+to a degree at which no strong correlation is present.  For these reasons,
+debiased vote fractions are only offered in the GZH catalog for Task~01
+(smooth/features).
 
@@
 %\includegraphics[width=\textwidth]{figures/hubble_z_mu_p_distributions.pdf}
-%\caption{Distributions of redshift, surface brightness, and \ffeatures{} for correctable (purple), lower-limit (green), and NEI (pink) galaxies in the full GZH sample.
-The lower-limit galaxies have higher redshifts, slightly lower surface brightness, and lower values of \ffeatures{} on average than the correctable galaxies.
-The long tail of NEI galaxies in redshift and surface brightness demonstrates the limits of the \ferengi{} sample, for which there is no data at $z>1$ or $\mu>24$.}
+%\caption{Distributions of redshift, surface brightness, and \ffeatures{} for
+%correctable (purple), lower-limit (green), and NEI (pink) galaxies in the full
+%GZH sample. The lower-limit galaxies have higher redshifts, slightly lower
+%surface brightness, and lower values of \ffeatures{} on average than the
+%correctable galaxies. The long tail of NEI galaxies in redshift and surface
+%brightness demonstrates the limits of the \ferengi{} sample, for which there
+%is no data at $z>1$ or $\mu>24$.}
 %\label{fig:z_mu_p}
@@
 %
-%We show here the preliminary results of GZH classifications of images of galaxies placed at artificial redshifts.
-Figure~\ref{fig:ferengi_results_fake} shows the range of change of vote fractions for the change of \ffeatures{} with redshift, for galaxies with different vote fraction levels, three ranges of surface-brightness levels and 7~evolutionary corrections (this last bit is indicated by the color).
+%We show here the preliminary results of GZH classifications of images of
+%galaxies placed at artificial redshifts. Figure~\ref{fig:ferengi_results_fake}
+%shows the range of change of vote fractions for the change of \ffeatures{}
+%with redshift, for galaxies with different vote fraction levels, three ranges
+%of surface-brightness levels and 7~evolutionary corrections (this last bit is
+%indicated by the color). 
 %
-%%-----------------------------------------------------------------------------------------------------------------------------------
+%%---------------------------------------------------------------------------
 %\begin{figure}
@@
 %
-%\caption{Preliminary results of the \ferengi{} redshifting exercise.
-WARNING NO USER WEIGHTING....
-For a range of vote fraction levels with three surface-brightness levels and 7 evolutionary corrections each (the colors indicate evolutionary correction value with green being $e=0$, we show the range of evolution of the vote fractions for featured vs.
-smooth with redshift.}
+%\caption{Preliminary results of the \ferengi{} redshifting exercise. WARNING
+%NO USER WEIGHTING.... For a range of vote fraction levels with three
+%surface-brightness levels and 7 evolutionary corrections each (the colors
+%indicate evolutionary correction value with green being $e=0$, we show the
+%range of evolution of the vote fractions for featured vs. smooth with
+%redshift.}
 %
@@
 %\end{figure}
-%%-----------------------------------------------------------------------------------------------------------------------------------
+%%--------------------------------------------------------------------------
 
@@
 
-The data release for GZH includes morphological data for 181,101~images (generated from a total of 150,771~unique galaxies).
-The full table can be accessed at \url{http://data.galaxyzoo.org}.
-The online data also includes a secondary metadata table, which is drawn from a variety of sources detailed in Section \ref{sec:data}.
-
-Each image is listed under a unique project ID (eg,~AHZ000001); the actual galaxy in the image is identified by the combination of the OBJNO and original survey.
-For each of the 55~responses in the GZH decision tree, the following classification data is provided: for each question, $\tt N_{votes}$ is the number of users to answer that question.
-For each unique answer, $\tt fraction$ is the fraction of users to select that answer ($\rm N_{answer}/N_{votes}$, and $\tt weighted$ is the weighted fraction, which takes into account user consistency (Section~\ref{ssec:weighting}).
+The data release for GZH includes morphological data for 181,101~images
+(generated from a total of 150,771~unique galaxies). The full table can be
+accessed at \url{http://data.galaxyzoo.org}. The online data also includes a
+secondary metadata table, which is drawn from a variety of sources detailed in
+Section \ref{sec:data}.
+
+Each image is listed under a unique project ID (eg,~AHZ000001); the actual
+galaxy in the image is identified by the combination of the OBJNO and original
+survey. For each of the 55~responses in the GZH decision tree, the following
+classification data is provided: for each question, $\tt N_{votes}$ is the
+number of users to answer that question. For each unique answer, $\tt fraction$
+is the fraction of users to select that answer ($\rm N_{answer}/N_{votes}$, and
+$\tt weighted$ is the weighted fraction, which takes into account user
+consistency (Section~\ref{ssec:weighting}).
 
 The GZH vote fractions can be largely dependent on the resolution of the image.
-Two otherwise morphologically identical galaxies which differ significantly in redshift, brightness, or size may result in very different vote fractions for any given question, given that many features of a galaxy are difficult to discern in less-resolved images (bars, spiral arms, disk structure, etc).
-For this reason, caution must be used when taking vote fractions as cut-offs to determine morphological structure; guidelines for careful classification are given in Section~\ref{sec:cookbook}.
-
-The GZH catalog is corrected for classification bias only for the first question of the GZH decision tree (Section~\ref{sec:debiasing}), which asks {\it ``Is the galaxy smooth and round, with no sign of a disk?''} For this question, the catalog provides the additional parameters $\tt debiased$, $\tt lower~limit$, $\tt upper~limit$, and $\tt best$ vote fractions.
-The $\tt best$ fraction for \ffeatures{} is chosen based on the categorization of the galaxy: if it is ``correctable'', $\tt best = debiased$; if it is a lower limit, $\tt best = lower~limit$; if neither condition applies, then $\tt best = weighted$.
-
-The debiased and best vote fractions for \fsmooth{} are calculated on the criteria that vote fractions for all answers must sum to unity:
+Two otherwise morphologically identical galaxies which differ significantly in
+redshift, brightness, or size may result in very different vote fractions for
+any given question, given that many features of a galaxy are difficult to
+discern in less-resolved images (bars, spiral arms, disk structure, etc). For
+this reason, caution must be used when taking vote fractions as cut-offs to
+determine morphological structure; guidelines for careful classification are
+given in Section~\ref{sec:cookbook}.
+
+The GZH catalog is corrected for classification bias only for the first
+question of the GZH decision tree (Section~\ref{sec:debiasing}), which asks
+{\it ``Is the galaxy smooth and round, with no sign of a disk?''} For this
+question, the catalog provides the additional parameters $\tt debiased$, $\tt
+lower~limit$, $\tt upper~limit$, and $\tt best$ vote fractions. The $\tt best$
+fraction for \ffeatures{} is chosen based on the categorization of the galaxy:
+if it is ``correctable'', $\tt best = debiased$; if it is a lower limit, 
+$\tt best = lower~limit$; if neither condition applies, then 
+$\tt best = weighted$.
+
+The debiased and best vote fractions for \fsmooth{} are calculated on the
+criteria that vote fractions for all answers must sum to unity:
 
@@
 
-\noindent In rare cases ($<1\%$ of the sample), this requirement resulted in negative vote fractions for \fsmooth; these were cases in which the \ffeatures{} vote fraction was boosted to a high value relative to \fartifact.
-In these cases, the constraint of Equation~\ref{eqn:constraint} is met by setting \fsmooth$=0.0$ and decreasing \fbest{} accordingly.
-This correction is typically small, with a median decrease/increase of $f_\mathrm{features}/f_\mathrm{smooth}$ of $\Delta f = 0.04$.
+\noindent In rare cases ($<1\%$ of the sample), this requirement resulted in
+negative vote fractions for \fsmooth; these were cases in which the
+\ffeatures{} vote fraction was boosted to a high value relative to \fartifact.
+In these cases, the constraint of Equation~\ref{eqn:constraint} is met by
+setting \fsmooth$=0.0$ and decreasing \fbest{} accordingly. This correction is
+typically small, with a median decrease/increase of
+$f_\mathrm{features}/f_\mathrm{smooth}$ of $\Delta f = 0.04$.
 
 Data products for GZH are split by the type of image being classified.
-Table~\ref{tbl:catalog_hst} contains the classifications for the \hst{} images from the AEGIS, COSMOS, and GEMS surveys, as well as 5-epoch deep imaging from the GOODS-N and GOODS-S surveys.
-This contains 118,425~galaxies and is the primary output from the GZH project.
-The next two tables have data for a small subset of 3,927~COSMOS~images that were re-processed to study the effect of color balance on morphological classification.
-Table~\ref{tbl:catalog_faded} has images that are desaturated to minimize the color contrast; Table~\ref{tbl:catalog_recolored} has images with the red and blue color channels inverted.
-Table~\ref{tbl:catalog_goods_shallow} contains data for 6,144~galaxies with 2-epoch images from GOODS.
-These have been mostly supplanted in the main table with deeper 5-epoch GOODS imaging; however, there are 1,683~galaxies in the shallower imaging that were not classified in the deeper mosaics.
-This data can also be compared to the counterparts in Table~\ref{tbl:catalog_hst} to study the effect of depth on morphological classification.
-Tables~\ref{tbl:stripe82_single} and \ref{tbl:stripe82_coadd} contain data for the SDSS Stripe~82 single-depth and co-added images, respectively, that were classified using the GZH interface and decision tree.
-Finally, Table~\ref{tbl:simulated_agn} contains classifications for images with artificial point sources intended to simulate the effect of a bright AGN (see \citealt{sim14} for an example).
+Table~\ref{tbl:catalog_hst} contains the classifications for the \hst{} images
+from the AEGIS, COSMOS, and GEMS surveys, as well as 5-epoch deep imaging from
+the GOODS-N and GOODS-S surveys. This contains 118,425~galaxies and is the
+primary output from the GZH project. The next two tables have data for a small
+subset of 3,927~COSMOS~images that were re-processed to study the effect of
+color balance on morphological classification. Table~\ref{tbl:catalog_faded}
+has images that are desaturated to minimize the color contrast;
+Table~\ref{tbl:catalog_recolored} has images with the red and blue color
+channels inverted. Table~\ref{tbl:catalog_goods_shallow} contains data for
+6,144~galaxies with 2-epoch images from GOODS. These have been mostly
+supplanted in the main table with deeper 5-epoch GOODS imaging; however, there
+are 1,683~galaxies in the shallower imaging that were not classified in the
+deeper mosaics. This data can also be compared to the counterparts in
+Table~\ref{tbl:catalog_hst} to study the effect of depth on morphological
+classification. Tables~\ref{tbl:stripe82_single} and \ref{tbl:stripe82_coadd}
+contain data for the SDSS Stripe~82 single-depth and co-added images,
+respectively, that were classified using the GZH interface and decision tree.
+Finally, Table~\ref{tbl:simulated_agn} contains classifications for images with
+artificial point sources intended to simulate the effect of a bright AGN (see
+\citealt{sim14} for an example).
 
@@
 \enddata
-\tablenotetext{1}{Flag indicating how the vote fractions for this galaxy were corrected through debiasing (Section~\ref{ssec:zeta_results}), if possible.
-0~=~correctable, 1~=~lower-limit ($f_{raw}$ --- $f_{adj}$ is not single-valued), 2~=~uncorrected ($z_{\rm gal} < 0.3$), 3~=~uncorrected (insufficient \ferengi{} galaxies in this $z$-$\mu$ bin), 4~=~uncorrected (no galaxy redshift available).}
-\tablecomments{The full version of this table is available in electronic form, as well as at \url{http://data.galaxyzoo.org}.
-The complete version includes data for 118,425~galaxies and morphological information for all tasks in the tree.
-A subset of the information is shown here to illustrate form and content.}
+\tablenotetext{1}{Flag indicating how the vote fractions for this galaxy were
+corrected through debiasing (Section~\ref{ssec:zeta_results}), if possible.
+0~=~correctable, 1~=~lower-limit ($f_{raw}$ --- $f_{adj}$ is not
+single-valued), 2~=~uncorrected ($z_{\rm gal} < 0.3$), 3~=~uncorrected
+(insufficient \ferengi{} galaxies in this $z$-$\mu$ bin), 4~=~uncorrected (no
+galaxy redshift available).}
+\tablecomments{The full version of this table is available in electronic form,
+as well as at \url{http://data.galaxyzoo.org}. The complete version includes
+data for 118,425~galaxies and morphological information for all tasks in the
+tree. A subset of the information is shown here to illustrate form and
+content.}
 \end{deluxetable*}
@@
 \enddata
-\tablecomments{The full version of this table is available in electronic form, as well as at \url{http://data.galaxyzoo.org}.
-The complete version includes data for 3,927~galaxies and morphological information for all tasks in the tree.
-A subset of the information is shown here to illustrate form and content.}
+\tablecomments{The full version of this table is available in electronic form,
+as well as at \url{http://data.galaxyzoo.org}. The complete version includes
+data for 3,927~galaxies and morphological information for all tasks in the
+tree. A subset of the information is shown here to illustrate form and
+content.}
 \end{deluxetable*}
@@
 \enddata
-\tablecomments{The full version of this table is available in electronic form, as well as at \url{http://data.galaxyzoo.org}.
-The complete version includes data for 6,144~galaxies and morphological information for all tasks in the tree.
-A subset of the information is shown here to illustrate form and content.}
+\tablecomments{The full version of this table is available in electronic form,
+as well as at \url{http://data.galaxyzoo.org}. The complete version includes
+data for 6,144~galaxies and morphological information for all tasks in the
+tree. A subset of the information is shown here to illustrate form and
+content.}
 \end{deluxetable*}
@@
 \enddata
-\tablecomments{The full version of this table is available in electronic form, as well as at \url{http://data.galaxyzoo.org}.
-The complete version includes data for 21,522~galaxies and morphological information for all tasks in the tree.
-A subset of the information is shown here to illustrate form and content.}
+\tablecomments{The full version of this table is available in electronic form,
+as well as at \url{http://data.galaxyzoo.org}. The complete version includes
+data for 21,522~galaxies and morphological information for all tasks in the
+tree. A subset of the information is shown here to illustrate form and
+content.}
 \end{deluxetable*}
@@
 \enddata
-\tablecomments{The full version of this table is available in electronic form, as well as at \url{http://data.galaxyzoo.org}.
-The complete version includes data for 30,339~galaxies and morphological information for all tasks in the tree.
-A subset of the information is shown here to illustrate form and content.}
+\tablecomments{The full version of this table is available in electronic form,
+as well as at \url{http://data.galaxyzoo.org}. The complete version includes
+data for 30,339~galaxies and morphological information for all tasks in the
+tree. A subset of the information is shown here to illustrate form and
+content.}
 \end{deluxetable*}
@@
 \tablenotetext{1}{Flag indicating the color of the PSF in the simulated AGN. 0~=~no simulated AGN, 1~=~blue, 2~=~flat, 3~=~red.}
-\tablecomments{The full version of this table is available in electronic form, as well as at \url{http://data.galaxyzoo.org}.
-The complete version includes data for 2,961~galaxies and morphological information for all tasks in the tree.
-A subset of the information is shown here to illustrate form and content.}
+\tablecomments{The full version of this table is available in electronic form,
+as well as at \url{http://data.galaxyzoo.org}. The complete version includes
+data for 2,961~galaxies and morphological information for all tasks in the
+tree. A subset of the information is shown here to illustrate form and
+content.}
 \end{deluxetable*}
@@
 
-The intended purpose of the GZH catalog is to provide a simple, yet flexible, means of identifying samples of galaxies with a desired morphological type.
-This section provides instructions for creating such samples using the vote fractions corresponding to the tasks shown in Figure~\ref{fig:decisiontree}.
-We stress that the selection process will vary based on the particular science case.
-More conservative cuts can be applied to create pure, but not necessarily complete, samples.
-These are useful for selecting galaxies exhibiting unique morphologies for individual case studies or observing proposals.
-Looser cuts can be applied to obtain samples with a higher level of completeness, which will increase the sample size but can potentially decrease purity.
-Population studies would make use of such large samples, in which statistical significance is a crucial factor in evaluating results.
-\citet{mas11c,mel14,che15}, and \citet{gal15} are examples of GZ papers which select morphologies in this way.
-
-In GZH, volunteers answer questions about a galaxy's morphology in a decision tree format.
-With this structure, questions shown to a user are dependent on their answers to the previous questions (Section~\ref{ssec:interface}).
-Figure~\ref{fig:decisiontree} shows the possible paths available for answering the questions offered in GZH.
-The colors represent the tier level of Tasks, which indicate the number of previous Tasks the given Task is dependent upon.
-The arm-number question, Task~11, is a 5$^\mathrm{th}$-tier Task, meaning that whether this question is seen by a user is dependent on four Tasks preceding it.
-In this case, it is only shown to volunteers who voted the galaxy was featured/disk-shaped in Task~01, not clumpy in Task~12, not edge-on in Task~02, and had spiral structure in Task~10.
-
-To select galaxies of a morphological type identified with a particular Task, a cut is placed on the vote fraction for that Task ($f_{\rm task}$), \emph{as well as} the vote fractions for the Tasks preceding it, because of the dependency induced by the decision-tree structure.
-For example, to select barred galaxies, a cut may be placed on \fbar{} such that only galaxies where a high fraction of votes for this task voted for the $bar,yes$ answer.
-This is not the only necessary cut, however, since not all users answer this question; only those who have previously selected ``features'' in Task~01, ``not clumpy'' in Task~12, and ``not edge-on'' in Task~02 will have the opportunity to vote on the bar question, Task~03.
-To ensure that \fbar{} is well-sampled, cuts on all previous tasks must be applied.
-
-The flexibility of this catalog allows the user to set their own selection criteria for vote fraction thresholds to create a morphologically pure sample.
-Table~\ref{tbl:thresholds} provides baseline cuts for selecting galaxies of a variety of morphologies.
-These thresholds are determined by a visual inspection of subsamples.
-For each Task, at least 20 users are required to have voted on the given question along with a cut on the vote fraction is applied to the previous task.
-We visually analyzed subsamples of 50~galaxies meeting both criteria, as well as a control sample of galaxies which had 20~users vote on the task, but did not meet the threshold cut set for the previous task.
-The threshold cut was adjusted and new subsamples were inspected until both the original and control samples achieved $>80\%$ purity.
-
-As an example of how to use Table~\ref{tbl:thresholds} to create a sample of 3-armed spirals galaxies, we suggest selecting objects with $N_{arm~number} \ge 20$, \ffeatures$>0.23, f_{\rm clumpy,no} > 0.30, f_{edgeon,no}>0.25$, and $f_{spiral,yes}>0.25$.
-These cuts define a sample of galaxies of ``arm number candidates''; \ie, galaxies for which answering the arm number question makes physical sense and the vote fraction $f_{\rm arm~number}$ is well-sampled.
-In this example, such galaxies are featured, non-clumpy, non-edge~on spirals.
-At this point a cut can be made on $f_{\rm arm~number=3}$ to select spirals with three arms.
-
-Tasks 03, 04 and 05 have an additional possible pathway; as shown in Figure~\ref{fig:decisiontree}, a user might also be shown this question if they select ``featured/disk'' in Task~01, ``clumpy'' in Task~12, two or more clumps in Task~16, and ``spiral arrangement'' in Task~15.
-After applying the appropriate thresholds for this path, $< 0.5\%$ of the galaxies which have $\ge 20$ answers to these questions used this pathway to arrive at these Tasks.
-Further, of these subjects, none were found to exhibit disk structure, although the clumps within were arranged in a spiral pattern.
-
-This section described how to use the previous Task thresholds in Table~\ref{tbl:thresholds} to select well-sampled galaxies which may or may not contain the feature associated with a unique Task.
-The following two examples show to use the vote fractions for a particular Task to obtain a sample of galaxies with a certain morphological type.
+The intended purpose of the GZH catalog is to provide a simple, yet flexible,
+means of identifying samples of galaxies with a desired morphological type.
+This section provides instructions for creating such samples using the vote
+fractions corresponding to the tasks shown in Figure~\ref{fig:decisiontree}. We
+stress that the selection process will vary based on the particular science
+case. More conservative cuts can be applied to create pure, but not necessarily
+complete, samples. These are useful for selecting galaxies exhibiting unique
+morphologies for individual case studies or observing proposals. Looser cuts
+can be applied to obtain samples with a higher level of completeness, which
+will increase the sample size but can potentially decrease purity. Population
+studies would make use of such large samples, in which statistical significance
+is a crucial factor in evaluating results. \citet{mas11c,mel14,che15}, and
+\citet{gal15} are examples of GZ papers which select morphologies in this way.
+
+In GZH, volunteers answer questions about a galaxy's morphology in a decision
+tree format. With this structure, questions shown to a user are dependent on
+their answers to the previous questions (Section~\ref{ssec:interface}).
+Figure~\ref{fig:decisiontree} shows the possible paths available for answering
+the questions offered in GZH. The colors represent the tier level of Tasks,
+which indicate the number of previous Tasks the given Task is dependent upon.
+The arm-number question, Task~11, is a 5$^\mathrm{th}$-tier Task, meaning that
+whether this question is seen by a user is dependent on four Tasks preceding
+it. In this case, it is only shown to volunteers who voted the galaxy was
+featured/disk-shaped in Task~01, not clumpy in Task~12, not edge-on in Task~02,
+and had spiral structure in Task~10.
+
+To select galaxies of a morphological type identified with a particular Task, a
+cut is placed on the vote fraction for that Task ($f_{\rm task}$), \emph{as
+well as} the vote fractions for the Tasks preceding it, because of the
+dependency induced by the decision-tree structure. For example, to select
+barred galaxies, a cut may be placed on \fbar{} such that only galaxies where a
+high fraction of votes for this task voted for the $bar,yes$ answer. This is
+not the only necessary cut, however, since not all users answer this question;
+only those who have previously selected ``features'' in Task~01, ``not clumpy''
+in Task~12, and ``not edge-on'' in Task~02 will have the opportunity to vote on
+the bar question, Task~03. To ensure that \fbar{} is well-sampled, cuts on all
+previous tasks must be applied.
+
+The flexibility of this catalog allows the user to set their own selection
+criteria for vote fraction thresholds to create a morphologically pure sample.
+Table~\ref{tbl:thresholds} provides baseline cuts for selecting galaxies of a
+variety of morphologies. These thresholds are determined by a visual inspection
+of subsamples. For each Task, at least 20 users are required to have voted on
+the given question along with a cut on the vote fraction is applied to the
+previous task. We visually analyzed subsamples of 50~galaxies meeting both
+criteria, as well as a control sample of galaxies which had 20~users vote on
+the task, but did not meet the threshold cut set for the previous task. The
+threshold cut was adjusted and new subsamples were inspected until both the
+original and control samples achieved $>80\%$ purity.
+
+As an example of how to use Table~\ref{tbl:thresholds} to create a sample of
+3-armed spirals galaxies, we suggest selecting objects with $N_{arm~number} \ge
+20$, \ffeatures$>0.23, f_{\rm clumpy,no} > 0.30, f_{edgeon,no}>0.25$, and
+$f_{spiral,yes}>0.25$. These cuts define a sample of galaxies of ``arm number
+candidates''; \ie, galaxies for which answering the arm number question makes
+physical sense and the vote fraction $f_{\rm arm~number}$ is well-sampled. In
+this example, such galaxies are featured, non-clumpy, non-edge~on spirals. At
+this point a cut can be made on $f_{\rm arm~number=3}$ to select spirals with
+three arms.
+
+Tasks 03, 04 and 05 have an additional possible pathway; as shown in
+Figure~\ref{fig:decisiontree}, a user might also be shown this question if they
+select ``featured/disk'' in Task~01, ``clumpy'' in Task~12, two or more clumps
+in Task~16, and ``spiral arrangement'' in Task~15. After applying the
+appropriate thresholds for this path, $< 0.5\%$ of the galaxies which have $\ge
+20$ answers to these questions used this pathway to arrive at these Tasks.
+Further, of these subjects, none were found to exhibit disk structure, although
+the clumps within were arranged in a spiral pattern.
+
+This section described how to use the previous Task thresholds in
+Table~\ref{tbl:thresholds} to select well-sampled galaxies which may or may not
+contain the feature associated with a unique Task. The following two examples
+show to use the vote fractions for a particular Task to obtain a sample of
+galaxies with a certain morphological type.
 
@@
 
-A sample of barred disk galaxies is created by applying cuts on the previous tasks as listed in Table~\ref{tbl:thresholds}.
-11,049 ``bar candidates'', galaxies for which asking the bar question is meaningful, were selected by applying the cuts $N_{bar} \ge 20$, $f_{\rm features}>0.23, f_{\rm clumpy,no} > 0.30,$ and $f_{edgeon,no}>0.25$.
-These galaxies are featured, non-clumpy, non-edge~on galaxies.
-Of these, a pure sample of 730 barred disks was identified by applying a cut of \fbar$>0.7$.
-A subsample of 50 galaxies were visually inspected and 94\% were found to contain strong bars.
-A complete sample of strong and weak bars was created by applying a cut of \fbar$>0.3$.
-This sample contained 3,218 galaxies, 86\% of which were found to contain weak or strong bars through visual inspection in a subsample of 50.
-
-The resulting bar sample can be used to estimate the redshift evolution of bar fraction and find a steady decrease of \fbar$\sim 0.32$ at $z=0.4$ to \fbar$\sim 0.24$ at $z=1.0$.
-The decrease in bar fraction agrees with \citet{mel14}, although they report a lower overall bar fraction going from \fbar$=0.22$ at $z=0.4$ to \fbar$=0.11$ at $z=1.0$.
-The difference in total bar fraction is expected, as this analysis used a looser cut on \fbar, there is no luminosity cut, and the use of debiased values for \ffeatures{} increases the total amount of disks in the sample compared to \citet{mel14}.
-For a more thorough analysis of the bar fraction, a cut on \fbar{} that evolves with redshift may yield more accurate results, since there are no explicit debiased values of \fbar{} that would take redshift induced bias into account.
-
-\subsection{Example 2: Identifying clump multiplicity}
-Clumps are known to be a characteristic feature of galaxies outside the local universe, and there is evidence they play a crucial role in the evolution of modern spirals, particularly in the formation of central bulges \citep{elm05,elm14,guo15,beh16}.
-Simulations show clumps migrate from the outer disk to the galactic center in only a few orbital periods \citep{man15} and observations show increasing bulge to clump mass and density ratios as the universe evolves since $z\sim 1.5$ \citep{elm09}, suggesting that clumps coalesce over time to form the modern bulges of disk galaxies.
-GZH added a ``clumpy'' path to the decision tree for the purpose of both identifying clumps and investigating their evolution with redshift.
-
-For galaxies identified as ``clumpy'' in GZH, the number of clumps can be determined using Task~16.
-Table~\ref{tbl:thresholds} can be used to select 8,444 galaxies measured as ``clumpy'' using \ffeatures$> 0.23$ and $f_{\rm clumpy,yes}>0.80$ to ensure the vote fractions for Task~16 are well-sampled.
-The clump number can be reasonably identified for 1,112 of the clumpy galaxies; for the remainder, the unique clumps were less distinguishable from each other and the exact number of clumps could not be deduced without careful visual inspection.
-In the 1,112 which did have distinguishable clumps, there are 61 one-clump galaxies using $f_{\rm 1~clump}>0.50$, 442 two-clump galaxies using $f_{\rm 2~clumps}>0.80$, 275 three-clump galaxies using $f_{\rm 3~clumps}>0.75$, 71 four-clump galaxies using $f_{\rm 4~clumps} > 0.70$, and 263 galaxies with more than four clumps using $f_{\rm >4~clumps}>0.70$.
-Alternatively, these data may be used to create more general samples of clumpy galaxies with few clumps and many clumps.
-A sample of 989 ``few clumps'' galaxies can be made using $(f_{\rm 1~clump} + f_{\rm 2~clumps}) > 0.5$ and 2,910 ``many clumps'' galaxies using $(f_{\rm 3~clumps}+f_{\rm 4~clumps}+f_{\rm >4~clumps})>0.5$.
+A sample of barred disk galaxies is created by applying cuts on the previous
+tasks as listed in Table~\ref{tbl:thresholds}. 11,049 ``bar candidates'',
+galaxies for which asking the bar question is meaningful, were selected by
+applying the cuts $N_{bar} \ge 20$, $f_{\rm features}>0.23, f_{\rm clumpy,no} >
+0.30,$ and $f_{edgeon,no}>0.25$. These galaxies are featured, non-clumpy,
+non-edge~on galaxies. Of these, a pure sample of 730 barred disks was
+identified by applying a cut of \fbar$>0.7$. A subsample of 50 galaxies were
+visually inspected and 94\% were found to contain strong bars. A complete
+sample of strong and weak bars was created by applying a cut of \fbar$>0.3$.
+This sample contained 3,218 galaxies, 86\% of which were found to contain weak
+or strong bars through visual inspection in a subsample of 50.
+
+The resulting bar sample can be used to estimate the redshift evolution of bar
+fraction and find a steady decrease of \fbar$\sim 0.32$ at $z=0.4$ to
+\fbar$\sim 0.24$ at $z=1.0$. The decrease in bar fraction agrees with
+\citet{mel14}, although they report a lower overall bar fraction going from
+\fbar$=0.22$ at $z=0.4$ to \fbar$=0.11$ at $z=1.0$. The difference in total bar
+fraction is expected, as this analysis used a looser cut on \fbar, there is no
+luminosity cut, and the use of debiased values for \ffeatures{} increases the
+total amount of disks in the sample compared to \citet{mel14}. For a more
+thorough analysis of the bar fraction, a cut on \fbar{} that evolves with
+redshift may yield more accurate results, since there are no explicit debiased
+values of \fbar{} that would take redshift induced bias into account.
+
+\subsection{Example 2: Identifying clump multiplicity} Clumps are known to be a
+characteristic feature of galaxies outside the local universe, and there is
+evidence they play a crucial role in the evolution of modern spirals,
+particularly in the formation of central bulges
+\citep{elm05,elm14,guo15,beh16}. Simulations show clumps migrate from the outer
+disk to the galactic center in only a few orbital periods \citep{man15} and
+observations show increasing bulge to clump mass and density ratios as the
+universe evolves since $z\sim 1.5$ \citep{elm09}, suggesting that clumps
+coalesce over time to form the modern bulges of disk galaxies. GZH added a
+``clumpy'' path to the decision tree for the purpose of both identifying clumps
+and investigating their evolution with redshift.
+
+For galaxies identified as ``clumpy'' in GZH, the number of clumps can be
+determined using Task~16. Table~\ref{tbl:thresholds} can be used to select
+8,444 galaxies measured as ``clumpy'' using \ffeatures$> 0.23$ and $f_{\rm
+clumpy,yes}>0.80$ to ensure the vote fractions for Task~16 are well-sampled.
+The clump number can be reasonably identified for 1,112 of the clumpy galaxies;
+for the remainder, the unique clumps were less distinguishable from each other
+and the exact number of clumps could not be deduced without careful visual
+inspection. In the 1,112 which did have distinguishable clumps, there are
+61 one-clump galaxies using $f_{\rm 1~clump}>0.50$, 442 two-clump galaxies
+using $f_{\rm 2~clumps}>0.80$, 275 three-clump galaxies using $f_{\rm
+3~clumps}>0.75$, 71 four-clump galaxies using $f_{\rm 4~clumps} > 0.70$,
+and 263 galaxies with more than four clumps using $f_{\rm >4~clumps}>0.70$.
+Alternatively, these data may be used to create more general samples of
+clumpy galaxies with few clumps and many clumps. A sample of 989 ``few
+clumps'' galaxies can be made using $(f_{\rm 1~clump} + f_{\rm 2~clumps}) >
+0.5$ and 2,910 ``many clumps'' galaxies using $(f_{\rm 3~clumps}+f_{\rm
+4~clumps}+f_{\rm >4~clumps})>0.5$.
 
@@
 
-Any analysis of the morphological distribution of galaxies must properly consider morphology with respect to other physical properties of the sample, such as color, mass, size, environment, and redshift.
-We defer such analyses to later papers, and comment here only on a few broad characteristics of the overall GZH sample.
-
-Figure~\ref{fig:sankey} shows the breakdown of morphologies for the combined surveys in GZH as a flow~diagram, where each node represents a task and the flows between the nodes represent the possible responses.
-The width of the flows is proportional to the number of galaxies associated with that response; Figure~\ref{fig:sankey} uses a simple plurality vote to assign the combined set of labels for each galaxy.
-This method is likely to undersample some of the categories; visual inspection of images suggests that \ffeatures$\gtrsim0.3$ identifies disk-dominated or irregular galaxies reliably, for example.
-This method also does not use the suggested thresholds in Table~\ref{tbl:thresholds}.
+Any analysis of the morphological distribution of galaxies must properly
+consider morphology with respect to other physical properties of the sample,
+such as color, mass, size, environment, and redshift. We defer such analyses to
+later papers, and comment here only on a few broad characteristics of the
+overall GZH sample.
+
+Figure~\ref{fig:sankey} shows the breakdown of morphologies for the combined
+surveys in GZH as a flow~diagram, where each node represents a task and the
+flows between the nodes represent the possible responses. The width of the
+flows is proportional to the number of galaxies associated with that response;
+Figure~\ref{fig:sankey} uses a simple plurality vote to assign the combined set
+of labels for each galaxy. This method is likely to undersample some of the
+categories; visual inspection of images suggests that \ffeatures$\gtrsim0.3$
+identifies disk-dominated or irregular galaxies reliably, for example. This
+method also does not use the suggested thresholds in
+Table~\ref{tbl:thresholds}.
 
@@
 \includegraphics[width=0.90\textwidth]{figures/sankey_both.png}
-\caption{Demographics of the morphologies for all galaxies in GZH (including both \hst{} and SDSS imaging).
-Each node in each diagram (dark blue horizontal bars of uniform height) represents a task in the tree.
-The left diagram shows the full decision tree; the right diagram zooms in on the features/clumpy tasks, which are otherwise difficult to see.
-The paths between tasks represent each possible answer to the task; these flow from top to bottom between their origin question and the subsequent task in the tree.
-Labels are assigned to each galaxy based on the plurality answer for each task.
-A galaxy is assigned only one label at each node.
-Widths of the paths are proportional to the number of galaxies assigned to that path; the widths of the nodes are proportional to the number of galaxies for which the question was reliably answered.}
+\caption{Demographics of the morphologies for all galaxies in GZH (including
+both \hst{} and SDSS imaging). Each node in each diagram (dark blue horizontal
+bars of uniform height) represents a task in the tree. The left diagram shows
+the full decision tree; the right diagram zooms in on the features/clumpy
+tasks, which are otherwise difficult to see. The paths between tasks represent
+each possible answer to the task; these flow from top to bottom between their
+origin question and the subsequent task in the tree. Labels are assigned to
+each galaxy based on the plurality answer for each task. A galaxy is assigned
+only one label at each node. Widths of the paths are proportional to the number
+of galaxies assigned to that path; the widths of the nodes are proportional to
+the number of galaxies for which the question was reliably answered.}
 \label{fig:sankey}
@@
 
-Given these caveats, the overall distribution of galaxy types is significantly different than the low-redshift sample classified in SDSS imaging from GZ1 and GZ2.
-\citet{lin11} found that elliptical galaxies exceeded spiral galaxies by a factor of $\sim2:1$ in the main spectroscopic sample if using a plurality vote criterion (although \citealt{bam09} show that this strongly depends on the selection method; spirals are the dominant population in a volume-limited sample at $z<0.088$, for example).
-The weighted votes for GZH have smooth galaxies outnumbering disks and clumpy galaxies by a factor of $\sim3:1$, however.
-The fraction of objects identified as stars or artifact is also much higher in the Hubble imaging; by plurality votes, these encompass only $\sim0.1\%$ of images in SDSS \citep{wil13}, but 6\% of images in GZH.
-
-Within the sample of galaxies identified as ``not smooth'', it is clear that the addition of the clumpy branch is necessary to describe a large fraction of the sample; disk-dominated galaxies outnumber clumpy morphologies by less than a factor of 2.
-Disk galaxies are primarily unbarred \citet{mel14} and possessing two visible spiral arms over a flat distribution of pitch angles and bulge prominence.
-Clumpy galaxies are identified across the full range of clump multiplicities, with the exception of 1-clump galaxies (which would be difficult to differentiate from compact spheroids).
-Roughly half of the galaxies have at least 1~clump identified as the brightest; the clumps are most commonly asymmetrically arranged in clusters and are not often seen embedded in larger structures.
+Given these caveats, the overall distribution of galaxy types is significantly
+different than the low-redshift sample classified in SDSS imaging from GZ1 and
+GZ2. \citet{lin11} found that elliptical galaxies exceeded spiral galaxies by a
+factor of $\sim2:1$ in the main spectroscopic sample if using a plurality vote
+criterion (although \citealt{bam09} show that this strongly depends on the
+selection method; spirals are the dominant population in a volume-limited
+sample at $z<0.088$, for example). The weighted votes for GZH have smooth
+galaxies outnumbering disks and clumpy galaxies by a factor of $\sim3:1$,
+however. The fraction of objects identified as stars or artifact is also much
+higher in the Hubble imaging; by plurality votes, these encompass only
+$\sim0.1\%$ of images in SDSS \citep{wil13}, but 6\% of images in GZH.
+
+Within the sample of galaxies identified as ``not smooth'', it is clear that
+the addition of the clumpy branch is necessary to describe a large fraction of
+the sample; disk-dominated galaxies outnumber clumpy morphologies by less than
+a factor of 2. Disk galaxies are primarily unbarred \citet{mel14} and
+possessing two visible spiral arms over a flat distribution of pitch angles and
+bulge prominence. Clumpy galaxies are identified across the full range of clump
+multiplicities, with the exception of 1-clump galaxies (which would be
+difficult to differentiate from compact spheroids). Roughly half of the
+galaxies have at least 1~clump identified as the brightest; the clumps are most
+commonly asymmetrically arranged in clusters and are not often seen embedded in
+larger structures.
 
@@
 
-All of the Legacy surveys included in the GZH imaging have had morphological catalogs previously published; these catalogs have significant differences in the number of galaxies, size and magnitude limits, classification scheme, and the methods used for measuring morphology.
-These catalogs have been cross-matched to GZH to compare the results; this is not presented as an endorsement of any particular method, but as an exploration of the strengths and weaknesses of the GZ crowdsourced catalogs as compared to products made with machine learning, automatic fits, and expert visual classification.
-
-The types and accuracy of morphological classification strongly depend on the sample and methods being used.
-In an attempt to make a consistent comparison between different techniques, galaxies are broadly grouped into three categories: bulge-dominated/elliptical/smooth, disk-dominated/spiral, and irregular/clumpy.
-These categories are compared to two parameters in GZH: \fbest, which is designed to identify smooth (elliptical) galaxies, and \fodd, which is designed to identify deviations from well-formed spirals or S0s and which constitutes a ``catch-all'' for the variety of asymmetric morphologies that can constitute an irregular galaxy.
-
-Morphologies for GEMS galaxies were measured by \citet{hau07}, who used single-component \sersic{} fits to the F850LP imaging.
-This analysis used parameters from the \galfit{} code, which \citet{hau07} evaluated as more reliable than \gimtwod{} for GEMS due to the ability to fit multiple galaxies in crowded fields.
-A 1\arcsec~positional match for the GEMS galaxies in Table~9 in \citet{hau07} to the GZH sample gives 8,846~galaxies in both \citet{hau07} and GZH.
-The main morphological parameter in the automated catalog is the \sersic{} index $n$ defining the radial surface brightness profile.
+All of the Legacy surveys included in the GZH imaging have had morphological
+catalogs previously published; these catalogs have significant differences in
+the number of galaxies, size and magnitude limits, classification scheme, and
+the methods used for measuring morphology. These catalogs have been
+cross-matched to GZH to compare the results; this is not presented as an
+endorsement of any particular method, but as an exploration of the strengths
+and weaknesses of the GZ crowdsourced catalogs as compared to products made
+with machine learning, automatic fits, and expert visual classification.
+
+The types and accuracy of morphological classification strongly depend on the
+sample and methods being used. In an attempt to make a consistent comparison
+between different techniques, galaxies are broadly grouped into three
+categories: bulge-dominated/elliptical/smooth, disk-dominated/spiral, and
+irregular/clumpy. These categories are compared to two parameters in GZH:
+\fbest, which is designed to identify smooth (elliptical) galaxies, and \fodd,
+which is designed to identify deviations from well-formed spirals or S0s and
+which constitutes a ``catch-all'' for the variety of asymmetric morphologies
+that can constitute an irregular galaxy.
+
+Morphologies for GEMS galaxies were measured by \citet{hau07}, who used
+single-component \sersic{} fits to the F850LP imaging. This analysis used
+parameters from the \galfit{} code, which \citet{hau07} evaluated as more
+reliable than \gimtwod{} for GEMS due to the ability to fit multiple galaxies
+in crowded fields. A 1\arcsec~positional match for the GEMS galaxies in Table~9
+in \citet{hau07} to the GZH sample gives 8,846~galaxies in both \citet{hau07}
+and GZH. The main morphological parameter in the automated catalog is the
+\sersic{} index $n$ defining the radial surface brightness profile.
 ``Elliptical'' galaxies are selected by $n>2.5$ and ``spirals''  by $n>2.5$.
-There is no automatic measurement of irregular or clumpy structure in this catalog.
-
-AEGIS galaxies were morphologically classified using non-parametric measurements by \citet{lot08}.
-This method used a combination of the Gini coefficient ($G$), which measures the relative inequality in pixel brightness, and $M_{20}$, the second-order moment of the brightest 20\% of the light \citep{lot04}.
-A linear combination of $G$ and $M_{20}$ delineates three broad categories of galaxy morphology: E/S0/Sa (``elliptical''), Sb/Sc/Ir (``spiral''), and mergers (``irregular'').
-A 1\arcsec{} positional match on AEGIS and GZH yields 4,031 galaxies with reliably-measured morphologies and $S/N>3$ in both $V$- and $I$-bands.
-
-Galaxies in both of the GOODS fields down to a limit of $z_{AB}=22.5$ were visually classified by a single expert (R.S.~Ellis), inspecting both $z$-band and composite $Viz$ color images \citep{bun05}.
-These morphologies are assigned a numerical value based on categories in \citet{bri98a}; the corresponding morphologies used are ``elliptical'' (classes 0,1,2), ``spirals'' (classes 3,4,5), and ``irregular'' (classes 6,7,8).
-A 0.5\arcsec{} matched radius yields 2,435 galaxies (1300 in GOODS-N, 1135 in GOODS-S) in both \citet{bun05} and GZH.
-
-COSMOS galaxies have multiple published datasets automatically classifying morphology, all using a variation of non-parametric measurements.
-\citet{cas07} used a combination of concentration ($C$), asymmetry ($A$), $G$, and $M_{20}$ \citep{cas05} to classify all galaxies with $m_\mathrm{I,petro}<25$, and used an empirical division based on several hundred training images to assign galaxies to discrete morphological categories.
-A similar method is employed by \citet{tas11}, using the same non-parametric indices but with a different method of calculating the Petrosian radius and total light profile.
-They employ a nearest-neighbors method is used to assign morphological categories for the entire sample based on a small training set.
-\citet[][ZEST]{sca07} used $C$, $A$, $G$, $M_{20}$, the galaxy ellipticity ($\epsilon$), and \sersic{} index ($n$) to quantify the galaxy shapes; a principal component analysis is used to assign galaxies to discrete morphological categories.
-The categories in all three methods are split into ellipticals, spirals, and peculiar/irregulars.
-A 0.5\arcsec{} radius search on GZH matches to 76,241 galaxies in \citet{cas07}, 76,608 in \citet{tas11}, and 77,425 in \citet{sca07}.
+There is no automatic measurement of irregular or clumpy structure in this
+catalog.
+
+AEGIS galaxies were morphologically classified using non-parametric
+measurements by \citet{lot08}. This method used a combination of the Gini
+coefficient ($G$), which measures the relative inequality in pixel brightness,
+and $M_{20}$, the second-order moment of the brightest 20\% of the light
+\citep{lot04}. A linear combination of $G$ and $M_{20}$ delineates three broad
+categories of galaxy morphology: E/S0/Sa (``elliptical''), Sb/Sc/Ir
+(``spiral''), and mergers (``irregular''). A 1\arcsec{} positional match on
+AEGIS and GZH yields 4,031 galaxies with reliably-measured morphologies and
+$S/N>3$ in both $V$- and $I$-bands.
+
+Galaxies in both of the GOODS fields down to a limit of $z_{AB}=22.5$ were
+visually classified by a single expert (R.S.~Ellis), inspecting both $z$-band
+and composite $Viz$ color images \citep{bun05}. These morphologies are assigned
+a numerical value based on categories in \citet{bri98a}; the corresponding
+morphologies used are ``elliptical'' (classes 0,1,2), ``spirals'' (classes
+3,4,5), and ``irregular'' (classes 6,7,8). A 0.5\arcsec{} matched radius yields
+2,435 galaxies (1300 in GOODS-N, 1135 in GOODS-S) in both \citet{bun05} and
+GZH.
+
+COSMOS galaxies have multiple published datasets automatically classifying
+morphology, all using a variation of non-parametric measurements. \citet{cas07}
+used a combination of concentration ($C$), asymmetry ($A$), $G$, and $M_{20}$
+\citep{cas05} to classify all galaxies with $m_\mathrm{I,petro}<25$, and used
+an empirical division based on several hundred training images to assign
+galaxies to discrete morphological categories. A similar method is employed by
+\citet{tas11}, using the same non-parametric indices but with a different
+method of calculating the Petrosian radius and total light profile. They employ
+a nearest-neighbors method is used to assign morphological categories for the
+entire sample based on a small training set. \citet[][ZEST]{sca07} used $C$,
+$A$, $G$, $M_{20}$, the galaxy ellipticity ($\epsilon$), and \sersic{} index
+($n$) to quantify the galaxy shapes; a principal component analysis is used to
+assign galaxies to discrete morphological categories. The categories in all
+three methods are split into ellipticals, spirals, and peculiar/irregulars. A
+0.5\arcsec{} radius search on GZH matches to 76,241 galaxies in \citet{cas07},
+76,608 in \citet{tas11}, and 77,425 in \citet{sca07}.
 
@@
 \includegraphics[width=1.0\textwidth]{figures/comparisons.png}
-\caption{Distributions of morphological parameters for galaxies matched in GZH and other published catalogs, split by survey (AEGIS, COSMOS, GEMS, and GOODS).
-The first and third columns show the fraction of overall galaxies in the matched samples, split by their published morphologies as a function of the GZH \fbest.
-The corresponding second and fourth columns show data for the same galaxies as a function of \fodd.
-Confidence intervals for each binned fraction in the bin are calculated for a binomial population \citep{cam11}.}
+\caption{Distributions of morphological parameters for galaxies matched in GZH
+and other published catalogs, split by survey (AEGIS, COSMOS, GEMS, and GOODS).
+The first and third columns show the fraction of overall galaxies in the
+matched samples, split by their published morphologies as a function of the GZH
+\fbest. The corresponding second and fourth columns show data for the same
+galaxies as a function of \fodd. Confidence intervals for each binned fraction
+in the bin are calculated for a binomial population \citep{cam11}.}
 \label{fig:comparisons}
@@
 
-Figure~\ref{fig:comparisons} shows the proportion of galaxies as split by their automated/expert visual morphologies for each of the six catalogs matched to GZH.
-The relation between GZH and the automated/expert morphologies is shown to vary significantly for different surveys --- this could be due to intrinsic differences in the galaxies, in the techniques used to measure morphology, or both.
-The distribution of \fbest{} for AEGIS galaxies is essentially flat for spirals, showing almost no difference in proportion at the highest and lowest ends.
-Early-type galaxies are at their highest proportion at \fbest$\sim0$, but constitute at most only 40\% of galaxies.
-In contrast, GOODS galaxies at low \fbest{} are dominated by early-types, although spiral and irregular galaxies have comparable sizes as low as \fbest$\sim0.2$.
-In GEMS galaxies, the impact of irregular or peculiar galaxies is not measured; splitting on $n=2.5$ gives an essentially flat proportion of ellipticals to spirals at \fbest$>0.3$.
-Visual inspection of images of galaxies where both \fbest{} and $n$ are high show that the majority are obvious spirals but with prominent bulges, indicating that the single-component \sersic{} fit is likely choosing too small of an effective radius and missing the extended disk structure for a large population of galaxies.
-
-Even within the same sample of galaxies in COSMOS, different techniques of measuring morphology show significant differences.
-Both \citet{cas07} and \citet{tas11} have higher proportions of early-type galaxies at \fbest$\sim0$, but constitute less than half the sample in both cases.
-The majority of all galaxies in \citet{sca07}, in contrast, are spirals; oddly, the \emph{highest} proportions of spirals are found at the lowest values of \fbest.
-The decrease in spiral galaxies at higher \fbest{} is almost entirely balanced by an increase in irregulars.
-Early-types have a small bump near \fbest$\sim0.15$, but never constitute more than 10\% of the sample.
-
-The second set of plots in Figure~\ref{fig:comparisons} indicates that \fodd{} is largely an effective method for separating irregular and/or peculiar galaxies from spirals.
-Despite the somewhat vague wording of the {\it ``anything odd?''} question in GZH, the AEGIS, COSMOS, and GOODS all show a marked increase in the irregular fraction increasing with \fodd.
-Any threshold value for distinguishing between the two, however, depends strongly on survey/redshift~range.
-
-As the data shown in Figure~\ref{fig:comparisons} cover a wide range of redshifts and sizes, a volume-limited sample of galaxies (or at least binning by redshift) is likely a much more appropriate comparison.
-While detailed analysis is left to a further paper, we note that there is no strong change in the proportion of galaxies when binning by redshift intervals of $\Delta z=0.2$ out to $z=1.0$.
-
-Finally, there are 7,681~galaxies in the GOODS-S field with morphological classifications in both GZH and the Galaxy~Zoo:~CANDELS project (Simmons et~al., submitted).
-Since both the sensitivity and filters for the two sets of images differ (and there is no debiased correction applied to GZC), there is no prior reason to expect a perfect correlation between the separate vote fractions for the projects.
-Briefly, we note that the \ffeatures{} value for GZH is on average higher than GZC; the effect is strongest at $f_\mathrm{features,GZC}<0.3$, for which roughly half the galaxies have $f_\mathrm{features,GZH}>0.5$.
-However, the correlation between vote fractions is single-valued (although not linear, with a Pearson correlation coefficient of $r=0.6$), and should be possible to calibrate using a similar approach to that described in Section~\ref{sec:debiasing}; the correlation between other tasks, such as edge-on galaxies is significantly stronger ($r=0.9$).
-So while the raw vote fractions are not directly comparable, the initial analysis indicates that the broad morphologies are at least consistent.
+Figure~\ref{fig:comparisons} shows the proportion of galaxies as split by their
+automated/expert visual morphologies for each of the six catalogs matched to
+GZH. The relation between GZH and the automated/expert morphologies is shown to
+vary significantly for different surveys --- this could be due to intrinsic
+differences in the galaxies, in the techniques used to measure morphology, or
+both. The distribution of \fbest{} for AEGIS galaxies is essentially flat for
+spirals, showing almost no difference in proportion at the highest and lowest
+ends. Early-type galaxies are at their highest proportion at \fbest$\sim0$, but
+constitute at most only 40\% of galaxies. In contrast, GOODS galaxies at low
+\fbest{} are dominated by early-types, although spiral and irregular galaxies
+have comparable sizes as low as \fbest$\sim0.2$. In GEMS galaxies, the impact
+of irregular or peculiar galaxies is not measured; splitting on $n=2.5$ gives
+an essentially flat proportion of ellipticals to spirals at \fbest$>0.3$.
+Visual inspection of images of galaxies where both \fbest{} and $n$ are high
+show that the majority are obvious spirals but with prominent bulges,
+indicating that the single-component \sersic{} fit is likely choosing too small
+of an effective radius and missing the extended disk structure for a large
+population of galaxies.
+
+Even within the same sample of galaxies in COSMOS, different techniques of
+measuring morphology show significant differences. Both \citet{cas07} and
+\citet{tas11} have higher proportions of early-type galaxies at \fbest$\sim0$,
+but constitute less than half the sample in both cases. The majority of all
+galaxies in \citet{sca07}, in contrast, are spirals; oddly, the \emph{highest}
+proportions of spirals are found at the lowest values of \fbest. The decrease
+in spiral galaxies at higher \fbest{} is almost entirely balanced by an
+increase in irregulars. Early-types have a small bump near \fbest$\sim0.15$,
+but never constitute more than 10\% of the sample.
+
+The second set of plots in Figure~\ref{fig:comparisons} indicates that \fodd{}
+is largely an effective method for separating irregular and/or peculiar
+galaxies from spirals. Despite the somewhat vague wording of the {\it
+``anything odd?''} question in GZH, the AEGIS, COSMOS, and GOODS all show a
+marked increase in the irregular fraction increasing with \fodd. Any threshold
+value for distinguishing between the two, however, depends strongly on
+survey/redshift~range.
+
+As the data shown in Figure~\ref{fig:comparisons} cover a wide range of
+redshifts and sizes, a volume-limited sample of galaxies (or at least binning
+by redshift) is likely a much more appropriate comparison. While detailed
+analysis is left to a further paper, we note that there is no strong change in
+the proportion of galaxies when binning by redshift intervals of $\Delta z=0.2$
+out to $z=1.0$.
+
+Finally, there are 7,681~galaxies in the GOODS-S field with morphological
+classifications in both GZH and the Galaxy~Zoo:~CANDELS project (Simmons
+et~al., submitted). Since both the sensitivity and filters for the two sets of
+images differ (and there is no debiased correction applied to GZC), there is no
+prior reason to expect a perfect correlation between the separate vote
+fractions for the projects. Briefly, we note that the \ffeatures{} value for
+GZH is on average higher than GZC; the effect is strongest at
+$f_\mathrm{features,GZC}<0.3$, for which roughly half the galaxies have
+$f_\mathrm{features,GZH}>0.5$. However, the correlation between vote fractions
+is single-valued (although not linear, with a Pearson correlation coefficient
+of $r=0.6$), and should be possible to calibrate using a similar approach to
+that described in Section~\ref{sec:debiasing}; the correlation between other
+tasks, such as edge-on galaxies is significantly stronger ($r=0.9$). So while
+the raw vote fractions are not directly comparable, the initial analysis
+indicates that the broad morphologies are at least consistent.
 
@@
 
-This paper presents the catalog release for the Galaxy Zoo: Hubble project, which uses crowdsourced visual classifications to measure galaxy morphologies.
-The first two phases of Galaxy Zoo \citep{lin11,wil13} used images of low-redshift galaxies from SDSS; this is the first result of the project with space-based images of high-redshift targets (in addition to the Galaxy Zoo: CANDELS collaboration; Simmons et al., submitted).
-The final sample includes classifications for 181,101~images generated from 150,771~unique galaxies.
-Galaxies were selected from a brightness-limited sample from multiple Legacy surveys using the Advanced Camera for Surveys on the Hubble Space Telescope, including AEGIS, GEMS, GOODS-N, GOODS-S, and COSMOS.
-The catalog also includes classifications for 51,861 Sloan Digital Sky Survey images in Stripe~82 at relatively low redshift; these serve both as a low-redshift anchor for cosmological studies and a potential comparison for the different epochs of classification between GZH and Galaxy Zoo 2 \citep{wil13}.
-
-The data for the GZH catalogs has been extensively tested and reduced.
-The dominant effect is a known bias against identifying disky and asymmetric sub-structures at either low resolution or surface brightness.
-This can be the result either of genuinely small or dim galaxies, or a perceived effect from observing galaxies at further distances (higher redshift).
-To calibrate this \emph{without} potentially overcorrecting for the genuine morphological evolution of galaxies over cosmic time, the GZH project uses SDSS images of low-redshift galaxies, processes them to appear as if they were at higher redshift, and classifies them through the GZH interface in an identical fashion.
-The resulting change in \ffeatures{} as a function of $z$ and $\mu$ is applied as a multiplicative correction to the top-level vote fractions for $\sim50\%$ of the GZH galaxies.
-
-Galaxies in GZH show significant changes in the disk/elliptical fraction as a function of redshift, along with an increasing number of galaxies dominated by smaller clumps and presumed to be in the process of building up their baryonic mass through a combination of hierarchical merging and in-situ star formation.
-While the majority of scientific interpretation is left to future work, this paper confirms the decrease in observed bar fraction with increasing redshift \citep{mel14} and identifies a new way for selecting clumpy galaxies as a function of clump multiplicity.
-
-The full data tables for the catalogs can be accessed in machine-readable form from both the journal and at \url{http://data.galaxyzoo.org}.
-All the code and data tables used to generate this manuscript can be found at \url{https://github.com/willettk/gzhubble}.
+This paper presents the catalog release for the Galaxy Zoo: Hubble project,
+which uses crowdsourced visual classifications to measure galaxy morphologies.
+The first two phases of Galaxy Zoo \citep{lin11,wil13} used images of
+low-redshift galaxies from SDSS; this is the first result of the project with
+space-based images of high-redshift targets (in addition to the Galaxy Zoo:
+CANDELS collaboration; Simmons et al., submitted). The final sample includes
+classifications for 181,101~images generated from 150,771~unique galaxies.
+Galaxies were selected from a brightness-limited sample from multiple Legacy
+surveys using the Advanced Camera for Surveys on the Hubble Space Telescope,
+including AEGIS, GEMS, GOODS-N, GOODS-S, and COSMOS. The catalog also includes
+classifications for 51,861 Sloan Digital Sky Survey images in Stripe~82 at
+relatively low redshift; these serve both as a low-redshift anchor for
+cosmological studies and a potential comparison for the different epochs of
+classification between GZH and Galaxy Zoo 2 \citep{wil13}.
+
+The data for the GZH catalogs has been extensively tested and reduced. The
+dominant effect is a known bias against identifying disky and asymmetric
+sub-structures at either low resolution or surface brightness. This can be the
+result either of genuinely small or dim galaxies, or a perceived effect from
+observing galaxies at further distances (higher redshift). To calibrate this
+\emph{without} potentially overcorrecting for the genuine morphological
+evolution of galaxies over cosmic time, the GZH project uses SDSS images of
+low-redshift galaxies, processes them to appear as if they were at higher
+redshift, and classifies them through the GZH interface in an identical
+fashion. The resulting change in \ffeatures{} as a function of $z$ and $\mu$ is
+applied as a multiplicative correction to the top-level vote fractions for
+$\sim50\%$ of the GZH galaxies.
+
+Galaxies in GZH show significant changes in the disk/elliptical fraction as a
+function of redshift, along with an increasing number of galaxies dominated by
+smaller clumps and presumed to be in the process of building up their baryonic
+mass through a combination of hierarchical merging and in-situ star formation.
+While the majority of scientific interpretation is left to future work, this
+paper confirms the decrease in observed bar fraction with increasing redshift
+\citep{mel14} and identifies a new way for selecting clumpy galaxies as a
+function of clump multiplicity.
+
+The full data tables for the catalogs can be accessed in machine-readable form
+from both the journal and at \url{http://data.galaxyzoo.org}. All the code and
+data tables used to generate this manuscript can be found at
+\url{https://github.com/willettk/gzhubble}.
 
@@
 
-We thank Meg Schwamb and the ASIAA for hosting the ``Citizen Science in Astronomy'' workshop, 3-7 Mar 2014 in Taipei, Taiwan, at which some of this analysis was done.
-We also thank Jennifer Lotz for sharing her $G$-$M_{20}$ measurements for the AEGIS sample.
-
-This project made heavy use of the Astropy packages in Python \citep{ast13}, the \texttt{seaborn} plotting package \citep{was15}, astroML \citep{van12}, and TOPCAT \citep{tay05,tay11}.
-Modified code from Nick~Wherry and David~Schlegel was used to create the JPG images.
-Figure~\ref{fig:sankey} was generated with \url{http://sankeymatic.com/}.
-
-KS gratefully acknowledges support from Swiss National Science Foundation Grant PP00P2\_138979/1.
-
-This work is based on (GO-10134, GO-09822, GO-09425.01, GO-09583.01, GO-9500) program observations with the NASA/ESA Hubble Space Telescope, obtained at the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS 5-26555.
-
-Funding for the SDSS and SDSS-II has been provided by the Alfred P.
-Sloan Foundation, the Participating Institutions, the National Science Foundation, the U.S.
-Department of Energy, the National Aeronautics and Space Administration, the Japanese Monbukagakusho, the Max Planck Society, and the Higher Education Funding Council for England.
-The SDSS website is \url{http://www.sdss.org/}.
-
-The SDSS is managed by the Astrophysical Research Consortium for the Participating Institutions.
-The Participating Institutions are the American Museum of Natural History, Astrophysical Institute Potsdam, University of Basel, University of Cambridge, Case Western Reserve University, University of Chicago, Drexel University, Fermilab, the Institute for Advanced Study, the Japan Participation Group, Johns Hopkins University, the Joint Institute for Nuclear Astrophysics, the Kavli Institute for Particle Astrophysics and Cosmology, the Korean Scientist Group, the Chinese Academy of Sciences (LAMOST), Los Alamos National Laboratory, the Max-Planck-Institute for Astronomy (MPIA), the Max-Planck-Institute for Astrophysics (MPA), New Mexico State University, Ohio State University, University of Pittsburgh, University of Portsmouth, Princeton University, the United States Naval Observatory and the University of Washington.
+We thank Meg Schwamb and the ASIAA for hosting the ``Citizen Science in
+Astronomy'' workshop, 3-7 Mar 2014 in Taipei, Taiwan, at which some of this
+analysis was done. We also thank Jennifer Lotz for sharing her $G$-$M_{20}$
+measurements for the AEGIS sample.
+
+This project made heavy use of the Astropy packages in Python \citep{ast13},
+the \texttt{seaborn} plotting package \citep{was15}, astroML \citep{van12}, and
+TOPCAT \citep{tay05,tay11}. Modified code from Nick~Wherry and David~Schlegel
+was used to create the JPG images. Figure~\ref{fig:sankey} was generated with
+\url{http://sankeymatic.com/}.
+
+KS gratefully acknowledges support from Swiss National Science Foundation Grant
+PP00P2\_138979/1.
+
+This work is based on (GO-10134, GO-09822, GO-09425.01, GO-09583.01, GO-9500)
+program observations with the NASA/ESA Hubble Space Telescope, obtained at the
+Space Telescope Science Institute, which is operated by the Association of
+Universities for Research in Astronomy, Inc., under NASA contract NAS 5-26555.
+
+Funding for the SDSS and SDSS-II has been provided by the Alfred P. Sloan
+Foundation, the Participating Institutions, the National Science Foundation,
+the U.S. Department of Energy, the National Aeronautics and Space
+Administration, the Japanese Monbukagakusho, the Max Planck Society, and the
+Higher Education Funding Council for England. The SDSS website is
+\url{http://www.sdss.org/}.
+
+The SDSS is managed by the Astrophysical Research Consortium for the
+Participating Institutions. The Participating Institutions are the American
+Museum of Natural History, Astrophysical Institute Potsdam, University of
+Basel, University of Cambridge, Case Western Reserve University, University of
+Chicago, Drexel University, Fermilab, the Institute for Advanced Study, the
+Japan Participation Group, Johns Hopkins University, the Joint Institute for
+Nuclear Astrophysics, the Kavli Institute for Particle Astrophysics and
+Cosmology, the Korean Scientist Group, the Chinese Academy of Sciences
+(LAMOST), Los Alamos National Laboratory, the Max-Planck-Institute for
+Astronomy (MPIA), the Max-Planck-Institute for Astrophysics (MPA), New Mexico
+State University, Ohio State University, University of Pittsburgh, University
+of Portsmouth, Princeton University, the United States Naval Observatory and
+the University of Washington.
 
@@
 
-GZH used both 5-epoch and 2-epoch sets of data to construct the GOODS set of images.
-The 11,157 full depth 5-epoch images are used in the main catalog; the classifications for the 7,464 shallow depth 2-epoch images are provided as a supplementary table.
-This section analyzes the effect of image depth on the ability of the GZ users to identify features or disk structure in the images.
+GZH used both 5-epoch and 2-epoch sets of data to construct the GOODS set of
+images. The 11,157 full depth 5-epoch images are used in the main catalog; the
+classifications for the 7,464 shallow depth 2-epoch images are provided as a
+supplementary table. This section analyzes the effect of image depth on the
+ability of the GZ users to identify features or disk structure in the images.
 
@@
 
-Of the 11,157 galaxies in the GOODS-N and GOODS-S full depth sample, 4,461 of these are in the shallow-depth sample.
-Figure~\ref{fig:shallow_vs_full} shows a strong correlation between \ffeatures{} for both sets of images.
-The mean change in \ffeatures{} from the shallow to full depth images  $f_\mathrm{features,full} - f_{features,shallow} \equiv \Delta f = 0.00$, with a standard deviation of $\sigma = 0.17$.
-While there is some variance in $\Delta f$ in the whole sample, the change is usually small and not often significant enough to change a morphological classification.
-Defining a clean sample of disk galaxies as those with \fbest$>0.8$, elliptical galaxies as those with $f_\mathrm{smooth,best}<0.2$, and intermediate as those in between, 75\% of the sample would not change morphology.
-Of the remaining 25\% that would change morphology, only 0.3\% (representing 10 galaxies total) drastically change morphology from smooth to featured or vice versa, while the rest would transition to or from the ``intermediate'' morphology.
-Details can be seen in Table~\ref{tbl:shallow_to_full_stats} and examples of images representing the 9 possible changes (or lack of) in morphology are shown in Figures~\ref{fig:shallow_smooth},\ref{fig:shallow_intermediate}, and \ref{fig:shallow_featured}.
+Of the 11,157 galaxies in the GOODS-N and GOODS-S full depth sample, 4,461 of
+these are in the shallow-depth sample. Figure~\ref{fig:shallow_vs_full} shows a
+strong correlation between \ffeatures{} for both sets of images. The mean
+change in \ffeatures{} from the shallow to full depth images
+$f_\mathrm{features,full} - f_{features,shallow} \equiv \Delta f = 0.00$, with
+a standard deviation of $\sigma = 0.17$. While there is some variance in
+$\Delta f$ in the whole sample, the change is usually small and not often
+significant enough to change a morphological classification. Defining a clean
+sample of disk galaxies as those with \fbest$>0.8$, elliptical galaxies as
+those with $f_\mathrm{smooth,best}<0.2$, and intermediate as those in between,
+75\% of the sample would not change morphology. Of the remaining 25\% that
+would change morphology, only 0.3\% (representing 10 galaxies total)
+drastically change morphology from smooth to featured or vice versa, while the
+rest would transition to or from the ``intermediate'' morphology. Details can
+be seen in Table~\ref{tbl:shallow_to_full_stats} and examples of images
+representing the 9 possible changes (or lack of) in morphology are shown in
+Figures~\ref{fig:shallow_smooth},\ref{fig:shallow_intermediate}, and
+\ref{fig:shallow_featured}.
 
@@
 \includegraphics[width=0.50\textwidth]{figures/full_shallow_p_plot.pdf}
-\caption{Distribution of \ffeatures{} for the 4,461 GOODS galaxies with both shallow (2-epoch) and full-depth (5-epoch) images morphologically classified in GZH.
-For most galaxies, the value of \ffeatures{} is consistent ($\Delta f_\mathrm{features}<0.2$) between depths.
-Examples of galaxies with sharp changes in \ffeatures, as well as those with little to no change are shown in Figures~\ref{fig:shallow_smooth}-\ref{fig:shallow_featured}.}
+\caption{Distribution of \ffeatures{} for the 4,461 GOODS galaxies with both
+shallow (2-epoch) and full-depth (5-epoch) images morphologically classified in
+GZH. For most galaxies, the value of \ffeatures{} is consistent ($\Delta
+f_\mathrm{features}<0.2$) between depths. Examples of galaxies with sharp
+changes in \ffeatures, as well as those with little to no change are shown in
+Figures~\ref{fig:shallow_smooth}-\ref{fig:shallow_featured}.}
 \label{fig:shallow_vs_full}
@@
 \begin{table}
-\caption{Properties of galaxies whose morphologies changed or stayed the same in the shallow vs full images.
-Featured here is defined as \fbest$>0.8$, intermediate = $0.2<$\fbest$<0.8$, smooth = $f_\mathrm{smooth,best}<0.2$.
+\caption{Properties of galaxies whose morphologies changed or stayed the same
+in the shallow vs full images. Featured here is defined as \fbest$>0.8$,
+intermediate = $0.2<$\fbest$<0.8$, smooth = $f_\mathrm{smooth,best}<0.2$.
 \label{tbl:shallow_to_full_stats}}
@@
 
-\caption{Galaxies whose shallow images were classified as featured and full depth images were classified as smooth, intermediate, or featured.}
+\caption{Galaxies whose shallow images were classified as featured and full
+depth images were classified as smooth, intermediate, or featured.}
 \label{fig:shallow_featured}
@@
 
-To determine the rate at which the vote fraction for any Task decreases with redshift or surface brightness, data from simulated \ferengi{} images were modeled with functions in discrete redshift and surface brightness bins (Section~\ref{ssec:zeta_results}).
-A cut of $N>10$ was placed on the number of votes to reduce the error in the vote fractions and ensure they were well-sampled before applying a fit to the data.
-This requirement was only met for Task~01, which significantly reduced the goodness-of-fit for the model functions as compared with to the smooth/features task.
-Here we show an example of results obtained for the bar Task.
-Figure~\ref{fig:f_vs_fbar} shows that both the low sample rate and the degree of scatter in each bin inhibit fitting a reliable function that predicts $f_{{\rm bar},z=0.3}$.
-Table~\ref{tbl:ferengi_bar} summarizes the correction types for the \ferengi{} data; 71\% of the galaxies simulated did not meet the GZH requirements for well-sampled vote fractions for $f_\mathrm{bar}$, as compared to 2\% for $f_\mathrm{features}$.
-Similar results were obtained for all higher-order Tasks in GZH (Section~\ref{ssec:higher_order_tasks}).
+To determine the rate at which the vote fraction for any Task decreases with
+redshift or surface brightness, data from simulated \ferengi{} images were
+modeled with functions in discrete redshift and surface brightness bins
+(Section~\ref{ssec:zeta_results}). A cut of $N>10$ was placed on the number of
+votes to reduce the error in the vote fractions and ensure they were
+well-sampled before applying a fit to the data. This requirement was only met
+for Task~01, which significantly reduced the goodness-of-fit for the model
+functions as compared with to the smooth/features task. Here we show an
+example of results obtained for the bar Task. Figure~\ref{fig:f_vs_fbar}
+shows that both the low sample rate and the degree of scatter in each bin
+inhibit fitting a reliable function that predicts $f_{{\rm bar},z=0.3}$.
+Table~\ref{tbl:ferengi_bar} summarizes the correction types for the
+\ferengi{} data; 71\% of the galaxies simulated did not meet the GZH
+requirements for well-sampled vote fractions for $f_\mathrm{bar}$, as
+compared to 2\% for $f_\mathrm{features}$. Similar results were obtained
+for all higher-order Tasks in GZH (Section~\ref{ssec:higher_order_tasks}).
 
@@
 \subfigure{[d]\label{d}\includegraphics[width=0.4\textwidth]{figures/z1_mu20_subplot2_bar.pdf}}
-\caption{Similar to Figure~\ref{fig:f_vs_f}, showing effects of redshift bias for 3,950~images in the \ferengi{} sample.
-[a]: Each point in a given redshift and surface brightness bin represents a unique galaxy.
-The $y$-axis in each bin is the \ffeatures{} value of the image of that galaxy redshifted to the value corresponding to that redshift bin.
-The $x$-axis is the \ffeatures{} value of the image of the same galaxy redshifted to $z=0.3$.
-The dashed black lines represent the best-fit polynomials to the data in each square.
-The solid black line represents \ffeaturesz=\ffeaturesrest.
-Regions in which there is a single-valued relationship between \ffeatures{} at high redshift and at $z=0.3$ are marked in white; those in which there is not are blue, and those with not enough data ($N<5$) are gray.
-The mean normalized $\chi^2$ of the change in vote fraction is 0.08.
-None of the correlations for higher-order tasks (including bars) were applied to galaxies in the GZH catalog.
-[b]: A larger version of the dark-outlined square in [a], containing \ferengi{} galaxies artificially redshifted to $z=1.0$ and have surface brightnesses between $20.3 < \mu < 21.0$ $\rm (mag/arcsec^2)$.
-[c]: The same data as [a].
-Each $z,\mu$ bin is divided into 4~sub-bins to determine the range of intrinsic \ffeaturesrest{} for a given range of observed \ffeaturesz{} values.
-In each sub-bin, the orange bars represent the inner 80$^\mathrm{th}$ percentiles of the data, the boundaries of which are the lower and upper limits of the debiased values.
-[d]: The same data as [b], but highlighting the upper and lower limit regions.}
+\caption{Similar to Figure~\ref{fig:f_vs_f}, showing effects of redshift bias
+for 3,950~images in the \ferengi{} sample. [a]: Each point in a given redshift
+and surface brightness bin represents a unique galaxy. The $y$-axis in each
+bin is the \ffeatures{} value of the image of that galaxy redshifted to the
+value corresponding to that redshift bin. The $x$-axis is the \ffeatures{}
+value of the image of the same galaxy redshifted to $z=0.3$. The dashed
+black lines represent the best-fit polynomials to the data in each square.
+The solid black line represents \ffeaturesz=\ffeaturesrest. Regions in
+which there is a single-valued relationship between \ffeatures{} at high
+redshift and at $z=0.3$ are marked in white; those in which there is not
+are blue, and those with not enough data ($N<5$) are gray. The mean
+normalized $\chi^2$ of the change in vote fraction is 0.08. None of the
+correlations for higher-order tasks (including bars) were applied to
+galaxies in the GZH catalog. [b]: A larger version of the dark-outlined
+square in [a], containing \ferengi{} galaxies artificially redshifted to
+$z=1.0$ and have surface brightnesses between $20.3 < \mu < 21.0$ $\rm
+(mag/arcsec^2)$. [c]: The same data as [a]. Each $z,\mu$ bin is divided
+into 4~sub-bins to determine the range of intrinsic \ffeaturesrest{} for a
+given range of observed \ffeaturesz{} values. In each sub-bin, the orange
+bars represent the inner 80$^\mathrm{th}$ percentiles of the data, the
+boundaries of which are the lower and upper limits of the debiased values.
+[d]: The same data as [b], but highlighting the upper and lower limit
+regions.}
 \label{fig:f_vs_fbar}
@@
 \label{tbl:ferengi_bar}
-\caption{Distribution of \ferengi{} images analyzed in Figure~\ref{fig:f_vs_fbar}.
-Correctable images had a single-valued relationship between their measured \fbar{} values at high and low redshifts (white regions in Figure~\ref{fig:f_vs_fbar}).
-Galaxies with a lower-limit on \fbar{} had a non single-valued relationship (blue regions).
-NEI images had undetermined relationships due to a lack of data ($N<5$) in their corresponding $z$-$\mu$ bins (gray regions).
-Only 17\% (maximum) of \ferengi{} galaxies in the sample were considered ``correctable'', which is not sufficient to compute a $\zeta$ function applicable to the Hubble data.
-\label{tbl:ferengi_bar_corrections}}
+\caption{Distribution of \ferengi{} images analyzed in
+Figure~\ref{fig:f_vs_fbar}. Correctable images had a single-valued relationship
+between their measured \fbar{} values at high and low redshifts (white regions
+in Figure~\ref{fig:f_vs_fbar}). Galaxies with a lower-limit on \fbar{} had a
+non single-valued relationship (blue regions). NEI images had undetermined
+relationships due to a lack of data ($N<5$) in their corresponding $z$-$\mu$
+bins (gray regions). Only 17\% (maximum) of \ferengi{} galaxies in the sample
+were considered ``correctable'', which is not sufficient to compute a $\zeta$
+function applicable to the Hubble data.   \label{tbl:ferengi_bar_corrections}}
 \begin{tabular}{lrr}

### 2016-05-15 writeup/gz_hubble_data.tex
Caption of Figure 7. Closes #103.

@@
 \caption{All fits for the vote fraction dropoff parameter $\zeta$ for
-$f_\textrm{features}$ in the \ferengi{} galaxies as a function of surface
-brightness. This includes only the 37~galaxies with a reasonably bounded range
-on the dropoff ($-10<\log(\zeta)<10$) and sufficient points to fit the
-function.}
+\ffeatures{} in the \ferengi{} galaxies as a function of surface
+brightness. This includes only those galaxies with a reasonably bounded range
+on the dropoff ($-10<\log(\zeta)<10$) and sufficient points to fit each
+function (37 original galaxies, each artificially redshifted to create a total
+of 296~images}
 \label{fig:zeta_mu}

### 2016-05-15 writeup/gz_hubble_data.tex
Re-iterate definition of lower-limit. Closes #102.

@@
 \ffeaturesrest{} value.  Galaxies in this region are referred to as the
-\emph{lower limit} sample. These regions are highlighted in blue in
-Figure~\ref{fig:6a}. Uncolored (white) regions of the plot have sufficiently
-high slopes to consider the relationship as single-valued; galaxies in these
-regions are considered ``correctable'', and only these are used in measuring
-the parameters for the $\zeta$ function (Section~\ref{ssec:zeta}). Only surface
-brightness/redshift bins with at least 5 galaxies were considered; regions with
-fewer than 5 galaxies are considered to have ``not enough information'' to
-determine the \ffeaturesz{} and \ffeaturesrest{} relationship, colored gray in
-Figure~\ref{fig:6a}.
+\emph{lower limit} sample, because the most stringent correction available is
+that the weighted \ffeatures{} is a lower limit to the true value.  These
+regions are highlighted in blue in Figure~\ref{fig:6a}. Uncolored (white)
+regions of the plot have sufficiently high slopes to consider the relationship
+as single-valued; galaxies in these regions are considered ``correctable'', and
+only these are used in measuring the parameters for the $\zeta$ function
+(Section~\ref{ssec:zeta}). Only surface brightness/redshift bins with at least
+5 galaxies were considered; regions with fewer than 5 galaxies are considered
+to have ``not enough information'' to determine the \ffeaturesz{} and
+\ffeaturesrest{} relationship, colored gray in Figure~\ref{fig:6a}.
 

### 2016-05-15 writeup/gz_hubble_data.tex
Amend description of GZ4. Closes #101.

@@
 an overly restrictive cut on blended and/or saturated objects. The main GZH
-site collected data until its replacement, the Galaxy~Zoo:~CANDELS project,
-began on 10~Sep~2012. Classifications for the GOODS 5-epoch images were
-separately obtained with the fourth version of the
-site\footnote{\url{http://www.galaxyzoo.org}} from Mar-Jun 2015. The GZH
-project had a total of 10,349,357~classifications from 93,898 registered
-participants. 
+site collected data until its replacement, the fourth phase of
+Galaxy~Zoo\footnote{\url{http://zoo4.galaxyzoo.org}} (including data from both
+the \hst{} CANDELS survey and SDSS DR8) began on 10~Sep~2012. Classifications
+for the GOODS 5-epoch images were separately obtained from Mar-Jun 2015 on
+the fourth version of the Galaxy~Zoo site. The GZH project had a total of
+10,349,357~classifications from 93,898 registered participants. 
 % Sum is the total of the GZH SQL table plus the GOODS full-depth imaging in GZ4.

### 2016-05-15 writeup/gz_hubble_data.tex
Moving to past tense for Sections 2 and 3. Closes #97.

@@
 crowdsourced visual classifications of color composite images. Images in GZH
-are selected from various \textit{Hubble Space Telescope} Legacy programs that
+were selected from various \textit{Hubble Space Telescope} Legacy programs that
 used the Advanced Camera for Surveys (AEGIS, COSMOS, GEMS, GOODS-N, and
@@
 surveys and sample selection criteria. The majority of the data (as implied by
-the project name) are taken directly from \hst{} Legacy Surveys, all of which
-primarily use imaging from the Advanced Camera for Surveys (ACS). Results from
+the project name) were taken directly from \hst{} Legacy Surveys, all of which
+primarily used imaging from the Advanced Camera for Surveys (ACS). Results from
 the individual surveys have been combined into a single photometric and
@@
     \citep[AEGIS;][]{dav07} covers a strip centered at
-    $\alpha=14^\textrm{h}17^\textrm{m}, \delta=+52^\circ30^\prime$. This area was
-    selected for a deep survey due to a combination of low extinction and low
-    Galactic/zodiacal emission. The ACS images covered 63 separate tiles over a
-    total area of $\sim710$~arcmin$^2$. The two ACS bands for AEGIS had exposure
-    times of 2300~seconds in F606W (\Vband) and 2100~seconds in F814W (\Iband). The
-    final mosaic images are dithered to a resolution of 0.03~\arcsec/pixel. For
-    extended objects, the limiting magnitudes of sources in AEGIS are 26.23~(AB) in
-    \Vband{} and 25.61 (AB) in \Iband.
+    $\alpha=14^\textrm{h}17^\textrm{m}, \delta=+52^\circ30^\prime$. This area
+    of the sky was selected for a deep survey due to a combination of low
+    extinction and low Galactic/zodiacal emission. The ACS images covered 63
+    separate tiles over a total area of $\sim710$~arcmin$^2$. The two ACS bands
+    for AEGIS had exposure times of 2300~seconds in F606W (\Vband) and
+    2100~seconds in F814W (\Iband). The final mosaic images were dithered
+    to a resolution of 0.03~\arcsec/pixel. For extended objects, the
+    limiting magnitude of sources was 26.23~(AB) in \Vband{} and 25.61 (AB) in
+    \Iband.
 
 \item The Great Observatories Origins Deep Survey \citep[GOODS;][]{gia04}
-    covers two separate fields in the northern and southern hemispheres: the Hubble
+    covered two separate fields in the northern and southern hemispheres: the Hubble
     Deep Field-North ($\alpha=12^\textrm{h}36^\textrm{m},
@@
     \Vband, F775W (\iband), and F850LP (\zband). The mean exposure times for each
-    epoch vary by band, from 1050--2100~seconds. The \Bband{} images were completed
+    epoch varied by band, from 1050--2100~seconds. The \Bband{} images were completed
     in a single epoch at the beginning of the survey, but the \Vband, \iband, and
     \zband{} images were taken in five separate epochs separated by 40--50~days
-    each. Images are dithered to a pixel scale of 0.03~\arcsec/pixel and cover a
+    each. Images were dithered to a pixel scale of 0.03~\arcsec/pixel and covered a
     total area of $\sim320$~arcmin$^2$ (160~arcmin$^2$ per north/south field). The
-    $5\sigma$ limiting magnitudes for extended sources are 25.7 for \Vband{} and
+    $5\sigma$ limiting magnitude for extended sources was 25.7 for \Vband{} and
     25.0 for \iband.
 
-\item The Cosmic Evolution Survey \citep[COSMOS;][]{sco07} covers an area of
+\item The Cosmic Evolution Survey \citep[COSMOS;][]{sco07} covered an area of
     $\sim1.8$~deg$^2$ centered at $\alpha=10^\textrm{h}00^\textrm{m},
@@
     Southern Hemispheres, in addition to space-based observatories. The ACS data
-    for COSMOS consists of 1 orbit per pointing with an exposure time of
-    2028~seconds in \Iband; 590 total pointings are used to cover the entire
-    field. The image resolution is dithered to 0.05~\arcsec/pixel. The 50\%
+    for COSMOS consisted of 1~orbit per pointing with an exposure time of
+    2028~seconds in \Iband; 590 total pointings were used to cover the entire
+    field. The image resolution was dithered to 0.05~\arcsec/pixel. The 50\%
     completeness magnitude for a galaxy with a half-light radius of
-    $0.50^{\prime\prime}$ in \Iband{} is 24.7 mag.
+    $0.50^{\prime\prime}$ in \Iband{} was 24.7 mag.
 
 \item The Galaxy Evolution from Morphologies and SEDs
-    \citep[GEMS;][]{rix04,cal08} survey is also centered on the Chandra Deep
-    Field-South. The GEMS data covers $\sim800$~arcmin$^2$, completely surrounding
-    the area covered by GOODS-S. Images from ACS in GEMS have 1 orbit per pointing
-    for a total of 63~pointings. The exposure times are 2160 and 2286~seconds in
-    \Vband{} and \zband{}, respectively. The image resolution has a pixel scale
-    of 0.03~\arcsec/pixel. The $5\sigma$ limiting magnitudes for source
-    detection are 25.7 AB in \Vband{} and 24.2~AB in \zband.
+    \citep[GEMS;][]{rix04,cal08} survey was also centered on the Chandra Deep
+    Field-South. The GEMS data covered $\sim800$~arcmin$^2$, completely surrounding
+    the area covered by GOODS-S. Images from ACS in GEMS had 1 orbit per pointing
+    for a total of 63~pointings. The exposure times were 2160 and 2286~seconds in
+    \Vband{} and \zband{}, respectively. The image resolution had a pixel scale
+    of 0.03~\arcsec/pixel. The $5\sigma$ limiting magnitude for source
+    detection was 25.7 AB in \Vband{} and 24.2~AB in \zband.
 
@@
 
-In the ACS-GC \citep{gri12}, individual galaxies are identified using a
+In the ACS-GC \citep{gri12}, individual galaxies were identified using a
 combination of \sextractor{} \citep{ber96} and the galaxy-profile fitting
-framework \galapagos{} \citep{bar12}. GZH includes all galaxies with $m <
-23.5$, where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS,
-GEMS + GOODS-S, and GOODS-N surveys, respectively. This yielded a total of
+framework \galapagos{} \citep{bar12}. GZH included all galaxies with $m<23.5$,
+where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS, GEMS +
+GOODS-S, and GOODS-N surveys, respectively. This yielded a total of
 113,166~images (Table~\ref{tbl:gzh_numbers}).
@@
 $r^\prime$ Petrosian flux) and a magnitude brighter than $m_r < 17.77$. The
-images used are three-color composites using the $g^\prime$, $r^\prime$, and
+images used were three-color composites using the $g^\prime$, $r^\prime$, and
 $i^\prime$ filters \citep{nie04}. 21,522 galaxies in SDSS met these criteria.
 Co-added images from Stripe~82 were selected from the union of galaxies with
-co-added magnitudes brighter than $17.77$~mag and the galaxies detected in the
-single-depth images and matched to a co-add source. This resulted in a larger
+co-added magnitudes brighter than $17.77$~mag, and the galaxies detected in the
+single-depth images and matched to a co-add source. This resulted in a total
 set of 30,339 images. Of the images in the co-added sample, 5144 (17~percent)
-are dimmer than the initial magnitude cut of 17.77.
+were dimmer than the initial magnitude cut of 17.77.
 
@@
 
-The images used for classification in GZH are color-composite JPGs made from
-multi-band data. The exact process for creating the images depends on the bands
+The images used for classification in GZH were color-composite JPGs made from
+multi-band data. The exact process for creating the images depended on the bands
 and resolutions in the surveys.
 
-For galaxies in the ACS-GC, color composites are made using a fixed pixel
+For galaxies in the ACS-GC, color composites were made using a fixed pixel
 intensity scaling with weights of
 $[2.4\times10^{-4},3\times10^{-4},3\times10^{-4}]$ in the red, green, and blue
-channels respectively. A nonlinear mapping is applied to each pixel to
+channels respectively. A nonlinear mapping was applied to each pixel to
 emphasize the contrast in faint features \citep{lup04}, taking the form of:
@@
 
-\noindent The GZH images from \citet{gri12} use a value of $b=3$.
+\noindent GZH images from \citet{gri12} used a value of $b=3$.
 
@@
 the surveys are listed in Table~\ref{tbl:gzh_numbers}. The 2-epoch GOODS-N and
-GOODS-S images use different filters --- this was a deliberate choice made so
+GOODS-S images used different filters --- this was a deliberate choice made so
 that the GEMS images could be directly compared with the overlapping coverage
@@
 The COSMOS images only had the \Iband{} imaging available at the time of
-classification in GZH. For these galaxies, we created ``pseudocolor'' images by
-using the ACS \Iband{} data as the illumination map and ground-based imaging
-from the \subaru{} telescope in $B_J$, $r^+$, and $i^+$ filters to provide the
-color gradients \citep[see][for further details]{gri12}. This means that the
-images have the angular resolution of \hst{} ($\sim0.05$~\arcsec/pixel) for the
-overall intensity, but the color gradients are at ground-based resolution, with
-seeing between 0.95\arcsec{} and 1.05\arcsec{} \citep{tan07}.
-
-Stripe~82 single-epoch images were taken directly from the color composites on
-the DR7 SDSS Skyserver, which combines $g^{\prime}$, $r^{\prime}$, and
-$i^{\prime}$ exposures into the RGB channels. The co-added Stripe~82 images
-were assembled from runs 106 and 206 in DR7 and made into color composites
-using the method of \citet{lup04}.
-
-To deal with images in which the sky noise was highly colored (which might have
-been a distraction to visual classification), a soft-edged object mask was
-applied that preserves the color balance for galaxies, but desaturates speckled
-noise against regions of blank sky. This technique was applied only to the
-co-added Stripe~82 and the COSMOS images.
+classification in GZH. For these galaxies, GZH used ``pseudocolor'' images
+created by using the ACS \Iband{} data as an illumination map and ground-based
+imaging from the \subaru{} telescope in $B_J$, $r^+$, and $i^+$ filters to
+provide the color gradients \citep[see][for further details]{gri12}. This
+resulted in images with the angular resolution of \hst{}
+($\sim0.05$~\arcsec/pixel) for the overall intensity, but color gradients at
+ground-based resolution, with seeing between 0.95\arcsec{} and 1.05\arcsec{}
+\citep{tan07}.
+
+Stripe~82 single-epoch images were taken directly from the DR7 SDSS Skyserver,
+which combined $g^{\prime}$, $r^{\prime}$, and $i^{\prime}$ exposures into the
+RGB channels. The co-added Stripe~82 images were assembled from runs 106 and
+206 in DR7 and made into color composites using the method of \citet{lup04}.
+
+To deal with situations in which the sky noise was highly colored (which might
+have been a distraction to visual classification), a soft-edged object mask was
+applied to the coadded Stripe~82 and the COSMOS images. This mask preserved the
+color balance for galaxies, but desaturated speckled noise against regions of
+blank sky.
 
@@
 
-GZH also includes a set of images designed to measure the effect of active
+GZH also included a set of images designed to measure the effect of active
 galactic nuclei (AGN) on morphological classifications. Since galactic nuclei
-can have bright, unresolved optical emission, this has the potential to mimic
-or distort the identification of a bulge component. The presence of an AGN is
+can have bright, unresolved optical emission, AGN have the potential to mimic
+or distort the identification of a bulge component. The presence of an AGN was
 simulated by modeling the point spread function (PSF) of the telescope and then
 inserting a bright source near the center of a real galaxy. For each image, the
-simulated AGN is assigned one of three colors -- either blue, red, or flat
+simulated AGN was assigned one of three colors -- either blue, red, or flat
 (white) as seen in the color images -- and a range of brightnesses such that
 $L_\mathrm{ratio} \equiv L_\mathrm{galaxy}/L_\mathrm{AGN}$ is in
-$(0.2,1.0,2.0,5.0,10.0,50.0)$. Combining these parameters generates 15~images
+$(0.2,1.0,2.0,5.0,10.0,50.0)$. Combining these parameters generated 15~images
 with different simulated AGN for each host.
@@
 
-Photometric data for the bulk of the GZH sample is largely drawn from the
-tables provided in \citet{gri12}. This includes photometric parameters such as
+Photometric data for the bulk of the GZH sample were largely drawn from the
+tables in \citet{gri12}. This included photometric parameters such as
 the fluxes, magnitudes, radii, ellipticities, position angles, and positions
-drawn from both \sextractor{} and \galfit. \galfit{} also provides the
+drawn from both \sextractor{} and \galfit. \galfit{} also provided the
 parametric \sersic{} index and effective half-light radius for the best-fit
-model. All parameters are measured in both bands of the ACS imaging, with the
+model. All parameters were measured in both bands of the ACS imaging, with the
 exception of the single-band COSMOS images.
 
-Redshifts for the GZH catalog are compiled from a variety of sources. For each
+Redshifts for the GZH catalog were compiled from a variety of sources. For each
 galaxy, the primary redshift used for debiasing calculations
@@
 For galaxies which have published redshifts from multiple sources, the
-following algorithm is used to select the $\tt Z\_BEST$ quantity. This first
-priority is spectroscopic redshifts; these are provided in the ACS-GC
-\citep{gri12}, 3DHST \citep{mom15}, and MUSYC \citep{car10} catalogs. A high
-quality spectroscopic redshift in the ACS-GC is the primary option; if none is
-available, then $\tt Z\_BEST$ uses the spectroscopic redshifts in 3DHST, and
-then MUSYC. For galaxies with multiple spectroscopic redshifts, more than 98\%
-are consistent at $\Delta z<0.001$, and so the order of selection makes no
-practical difference. If no spectroscopic redshifts are available, the
-1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST, MUSYC,
-UltraVISTA;][]{ilb13} and UltraVISTA grism data are used to select the redshift
-with the smallest error. 
+following algorithm was used to select the $\tt Z\_BEST$ quantity. The first
+priority is spectroscopic redshifts; these were taken from the ACS-GC
+\citep{gri12}, 3DHST \citep{mom15}, and MUSYC \citep{car10} catalogs. A
+high-quality spectroscopic redshift in the ACS-GC is the primary option; if
+none is available, then $\tt Z\_BEST$ uses the spectroscopic redshifts in
+3DHST, and then MUSYC. For galaxies with multiple spectroscopic redshifts, more
+than 98\% are consistent at $\Delta z<0.001$, and so the order of selection
+made no practical difference. If no spectroscopic redshifts were available,
+the 1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST, MUSYC,
+UltraVISTA;][]{ilb13} and UltraVISTA grism data were used to select the
+redshift with the smallest error. 
 %Table~\ref{tbl:redshifts} shows the results of this selection.
@@
 
-Photometric and spectroscopic data for the SDSS Stripe~82 galaxies are taken
-from the CasJobs DR7 tables. This includes $ugriz$ Petrosian magnitudes and
+Photometric and spectroscopic data for the SDSS Stripe~82 galaxies were taken
+from the CasJobs DR7 tables. This included $ugriz$ Petrosian magnitudes and
 fluxes, as well as the relative de~Vaucouleurs and exponential fits from the
-model magnitudes. Redshifts used for the SDSS galaxies are all spectroscopic.
+model magnitudes. All redshifts used for SDSS galaxies were spectroscopic.
 82.6\% of galaxies in the single-depth images and 65.1\% of galaxies in the
-co-add images have a measured DR7 spectroscopic redshift.
+co-add images had a measured DR7 spectroscopic redshift.
 
@@
 
-\subsection{User weighting}\label{ssec:weighting} The votes of individual users
-who classified galaxies in GZH are combined to make a vote fraction for each
-response to a question ($f_{response}$) on the classification tree. Users'
-votes are weighted slightly \citep[in a method identical to that described
-in][]{wil13} such that users who frequently disagree with all other users end
-up having very low weights. The user weighting $(w)$ is 1 for the top 95\% of
-users as ranked by consistency. For the bottom 5\% of users, $w$ drops smoothly
-and is effectively zero for only the bottom 1\% of classifiers in the CDF.
-Since this only affects a tiny percentage of the users (and an even smaller
-percentage of the classifications) the overall effect on the GZH dataset is
-minimal. This method is effective, however, at filtering out contributions from
-random or deliberately malicious classifiers.
-
-Classifications for a particular user are aggregated and weighted only if they
-were logged into GZH under their username (which is encouraged, but not
-required for participation). Classifications by users not logged in are marked
-as ``Anonymous''; no weighting is applied to these classifications, but they
-are otherwise treated identically in the data processing.
+\subsection{User weighting}\label{ssec:weighting}
+
+The votes of individual users who classified galaxies in GZH were combined to
+make a vote fraction for each response ($f_{response}$) to a question in the
+classification tree. Users' votes were weighted \citep[in a method identical to
+that described in][]{wil13} such that users who frequently disagreed with all
+other users ended up having very low weights. The user weighting $(w)$ was 1
+for the top 95\% of users, as ranked by consistency. For the bottom 5\% of
+users, $w$ was designed to drop smoothly and was effectively zero for the
+bottom 1\% of classifiers.  Since this only affected a tiny percentage of
+the users (and an even smaller percentage of the classifications) the
+overall effect on the GZH dataset was minimal. The method was effective,
+however, at filtering out contributions from random or deliberately
+malicious classifiers.
+
+Classifications each user were aggregated and weighted only if they
+were logged into GZH under their username (which was encouraged, but not
+required for participation). Classifications by users not logged in were marked
+as ``Anonymous''; no weighting was applied to these classifications, but they
+were otherwise treated identically in the data processing.
 
@@
 
-Classifications for GZH are made using a web-based interface
+Classifications for GZH were made using a web-based interface
 (Figure~\ref{fig:interface}), similar in design to Galaxy~Zoo and Galaxy~Zoo~2.
 The front-end runs on a Ruby~on~Rails framework with classifications stored in
-a MySQL backend. Users are shown a randomly-selected color composite image from
-the GZH sample; the default shows the image with a black sky background,
-although users have the options to invert the color palette if desired. The
-questions and responses for morphology appear on the right side of the image as
-a panel, including both text and icons. There is no tutorial required for
-participation, although users can access an extensive ``Help'' section
+a MySQL backend. Users were shown a randomly-selected color composite image from
+the GZH sample; the default showed the image with a black sky background,
+although users had the option to invert the color palette if desired. The
+questions and responses for morphology appeared on the right side of the image as
+a panel, including both text and icons. There was no tutorial required for
+participation, although users could access an extensive ``Help'' section
 containing example images and descriptive text for all the morphological
@@
 
-The procedure for classifying an image in GZH follows a hierarchical decision
-tree (Figure~\ref{fig:decisiontree}). Every classification begins with the user
-identifying whether the object at the center of the image is a smooth galaxy, a
-galaxy with a disk or other features, or a star/artifact. Subsequent questions
-in the tree depend on the previous answer(s) given by the user; the structure
-of the decision tree is designed so that the user will answer every question
-relevant to the morphology that they have identified. Questions that are not
-answered are implicitly assumed to be absent in the image --- for example, if
-the user identifies a galaxy as being smooth, they are not asked to count the
-number of spiral arms. For every task, the user chooses a single answer before
-continuing to the next question; they have also the option to restart a
-classification in-progress if a mistake has been made.
-
-The GZH decision tree has four broad sets of morphologies classified by the
-users. The first option is designating the object as a star or image artifact
+The procedure for classifying an image in GZH followed a hierarchical decision
+tree (Figure~\ref{fig:decisiontree}). Every classification began with the user
+identifying whether the object at the center of the image was a smooth galaxy,
+a galaxy with a disk or other features, or a star/artifact. Subsequent
+questions in the tree depended on the previous answer(s) given by the user; the
+decision tree as designed so that the user answered every question relevant to
+the morphology in the process of being identified. Questions that were not
+answered were implicitly assumed to be absent in the image --- for example, if
+the user identified a galaxy as being smooth, they were not asked to count the
+number of spiral arms. For every task, the user chose a single answer before
+continuing to the next question; they also had the option to restart any
+classification in-progress.
+
+The GZH decision tree had four broad sets of morphologies classified by the
+users. The first option designated stars or image artifacts
 (the result of either bad data or incorrect classification by the ACS pipeline
-as a galaxy); in this case, the classification ends and no further questions
-are asked. The second set are smooth galaxies, intended to select
+as a galaxy); in this case, the classification process ended and no further questions
+were asked of the user. The second set were smooth galaxies, intended to select
 ellipticals/early-types; users also measure the relative axial ratio
-(roundness) for these galaxies. The third set is for disk/late-type galaxies,
-which measures the features necessary to place a galaxy on the standard Hubble
+(roundness) for these galaxies. The third set was for disk/late-type galaxies,
+which measured the features necessary to place a galaxy on the standard Hubble
 tuning fork (bars, spiral arm, strength of the central bulge). The final set,
-which is new to the high-redshift targets in GZH, asks users to identify
-objects dominated by clumpy morphologies. Further annotations for these
-galaxies includes assessing the number, arrangement, relative brightness, and
+which was new in this phase of Galaxy~Zoo and designed for high-redshift targets, asked users to identify
+objects dominated by clumpy morphologies. Further annotations for clumpy
+galaxies included assessing the number, arrangement, relative brightness, and
 location of the clumps within the galaxy. Finally, every classification of a
-galaxy gives users the option of identifying ``odd'' features within the image;
-these labels are for relatively rare $(\lesssim1\%)$ phenomena, including dust
+galaxy gave users the option of identifying ``odd'' features within the image;
+these labels were for relatively rare $(\lesssim1\%)$ phenomena, including dust
 lanes, gravitational lenses, and mergers.
 
-The number of independent classifications per subject collected by GZH is on
+The number of independent classifications per subject collected by GZH was on
 average higher than GZ1 or GZ2, due to both the increased complexity of the
 decision tree and the relative difficulty of classifying images of small and
-distant galaxies. Images from the main AEGIS, GEMS, and GOODS data sets have a
+distant galaxies. Images from the main AEGIS, GEMS, and GOODS data sets had a
 median of 122~independent classifications per image. The remainder of the
-images either had a later activation date (COSMOS, simulated AGN) or by a lower
+images either had a later activation date (COSMOS, simulated AGN) or a lower
 retirement limit (the low-redshift SDSS Stripe~82 galaxies). Images from these
-samples have a median of 46--48~classifications per image
+samples had a median of 46--48~classifications per image
 (Figure~\ref{fig:classification_hist}).

### 2016-05-15 writeup/gz_hubble_data.tex
User -> classifier. Closes #93.

@@
 project.\footnote{This publication has been made possible by the participation
-of more than 200,000 volunteers in the Galaxy Zoo project. Their contributions
+of more than 200,000~volunteers in the Galaxy Zoo project. Their contributions
 are individually acknowledged at
@@
 
-\subsection{User weighting}\label{ssec:weighting}
-
-The votes of individual users who classified galaxies in GZH were combined to
+\subsection{Classifier weighting}\label{ssec:weighting}
+
+The votes of individual classifiers in GZH were combined to
 make a vote fraction for each response ($f_{response}$) to a question in the
-classification tree. Users' votes were weighted \citep[in a method identical to
-that described in][]{wil13} such that users who frequently disagreed with all
-other users ended up having very low weights. The user weighting $(w)$ was 1
-for the top 95\% of users, as ranked by consistency. For the bottom 5\% of
-users, $w$ was designed to drop smoothly and was effectively zero for the
-bottom 1\% of classifiers.  Since this only affected a tiny percentage of
-the users (and an even smaller percentage of the classifications) the
+classification tree. Votes were weighted \citep[in a method identical to
+that described in][]{wil13} such that classifiers who frequently disagreed with
+others ended up having very low weights. The weighting $(w)$ was 1
+for the top 95\% of classifiers, as ranked by consistency. For the bottom 5\% of
+classifiers, $w$ was designed to drop smoothly and was effectively zero for the
+bottom 1\%.  Since this only affected a tiny percentage of
+the classifiers (and an even smaller percentage of the classifications) the
 overall effect on the GZH dataset was minimal. The method was effective,
@@
 
-Classifications each user were aggregated and weighted only if they
-were logged into GZH under their username (which was encouraged, but not
-required for participation). Classifications by users not logged in were marked
-as ``Anonymous''; no weighting was applied to these classifications, but they
-were otherwise treated identically in the data processing.
+Classifications were aggregated and weighted only if the classifier was logged
+into GZH under their username (which was encouraged, but not required for
+participation). Classifications by participants who were not logged in were marked as
+``Anonymous''; no weighting was applied, but the data were otherwise treated
+identically in the data processing.
 
@@
 \caption{Screenshot of the GZH interface (\url{http:/zoo3.galaxyzoo.org}) at
-the beginning of a classification, with the user ready to select an answer for
+the beginning of a classification, with the classifier ready to select an answer for
 the first question in the decision tree.\label{fig:interface}}
@@
 The front-end runs on a Ruby~on~Rails framework with classifications stored in
-a MySQL backend. Users were shown a randomly-selected color composite image from
+a MySQL backend. Classifiers were shown a randomly-selected color composite image from
 the GZH sample; the default showed the image with a black sky background,
-although users had the option to invert the color palette if desired. The
+although they had the option to invert the color palette if desired. The
 questions and responses for morphology appeared on the right side of the image as
 a panel, including both text and icons. There was no tutorial required for
-participation, although users could access an extensive ``Help'' section
+participation, although classifiers could access an extensive ``Help'' section
 containing example images and descriptive text for all the morphological
@@
 \includegraphics[width=\textwidth]{figures/gzh_decision_tree.pdf}
-\caption{Flowchart of the questions presented to GZH users, labeled with the
-corresponding Task numbers. Tasks in the decision tree are color-coded by tier
-level: Gray-colored Tasks are 1$^\mathrm{st}$-tier questions which are asked of
-all users. Tasks colored green, blue, purple, and pink (respectively) are one,
-two, three, or four steps below branching points in the decision tree.}
+\caption{Flowchart of the questions presented to GZH classifiers, labeled with
+the corresponding Task numbers. Tasks in the decision tree are color-coded by
+tier level: Gray-colored Tasks are 1$^\mathrm{st}$-tier questions which are
+asked in every classification. Tasks colored green, blue, purple, and pink
+(respectively) are one, two, three, or four steps below branching points in the
+decision tree.}
 \label{fig:decisiontree}
@@
 The procedure for classifying an image in GZH followed a hierarchical decision
-tree (Figure~\ref{fig:decisiontree}). Every classification began with the user
+tree (Figure~\ref{fig:decisiontree}). Every classification began with the step of
 identifying whether the object at the center of the image was a smooth galaxy,
 a galaxy with a disk or other features, or a star/artifact. Subsequent
-questions in the tree depended on the previous answer(s) given by the user; the
-decision tree as designed so that the user answered every question relevant to
-the morphology in the process of being identified. Questions that were not
+questions in the tree depended on the previous answer(s) given by the classifier; the
+decision tree was designed so that every question relevant to
+the morphology in the process of being identified was answered. Questions that were not
 answered were implicitly assumed to be absent in the image --- for example, if
-the user identified a galaxy as being smooth, they were not asked to count the
-number of spiral arms. For every task, the user chose a single answer before
+the classifier identified a galaxy as being smooth, they were not asked to count the
+number of spiral arms. For every task, the classifier chose a single answer before
 continuing to the next question; they also had the option to restart any
@@
 
-The GZH decision tree had four broad sets of morphologies classified by the
-users. The first option designated stars or image artifacts
-(the result of either bad data or incorrect classification by the ACS pipeline
-as a galaxy); in this case, the classification process ended and no further questions
-were asked of the user. The second set were smooth galaxies, intended to select
-ellipticals/early-types; users also measure the relative axial ratio
-(roundness) for these galaxies. The third set was for disk/late-type galaxies,
-which measured the features necessary to place a galaxy on the standard Hubble
-tuning fork (bars, spiral arm, strength of the central bulge). The final set,
-which was new in this phase of Galaxy~Zoo and designed for high-redshift targets, asked users to identify
+The GZH decision tree had four broad sets of morphologies. The first option
+designated stars or image artifacts (the result of either bad data or incorrect
+classification by the ACS pipeline as a galaxy); in this case, the
+classification process ended and no further questions were asked. The second
+set were smooth galaxies, intended to select ellipticals/early-types;
+classifiers also measured the relative axial ratio (roundness) for these
+galaxies. The third set was for disk/late-type galaxies, which measured the
+features necessary to place a galaxy on the standard Hubble tuning fork (bars,
+spiral arm, strength of the central bulge). The final set, which was new in
+this phase of Galaxy~Zoo and designed for high-redshift targets, identified
 objects dominated by clumpy morphologies. Further annotations for clumpy
@@
 location of the clumps within the galaxy. Finally, every classification of a
-galaxy gave users the option of identifying ``odd'' features within the image;
-these labels were for relatively rare $(\lesssim1\%)$ phenomena, including dust
+galaxy gave the option of identifying ``odd'' features within the image; these
+labels were for relatively rare $(\lesssim1\%)$ phenomena, including dust
 lanes, gravitational lenses, and mergers.
@@
 
-The approach used in GZH for correcting the weighted classifications for user
+The approach used in GZH for correcting the weighted classifications for redshift
 bias rests on the assumption that the \emph{amount} of bias is a function of
@@
 \textbf{extrinsic} properties, such as the distance (redshift) of the galaxy
-and its relative orientation. There are likely other parameters that affect
-user accuracy, such as the proximity of close companions \citep[``distraction
-bias''; see][]{joh15} or bias as a function of individual user ability and
+and its relative orientation. There may also be other parameters that affect
+classifier accuracy, such as the proximity of close companions \citep[``distraction
+bias''; see][]{joh15} or bias as a function of individual classifier ability and
 skill. The combination of all such parameters forms a high-dimensional space,
@@
 
-As with the HST images, each \ferengi{} subject has a varying number of users
-answering the various questions in the hierarchical decision tree. Every user
+As with the HST images, each \ferengi{} subject had a varying number of classifiers
+answering the various questions in the hierarchical decision tree. Every classifier
 answers the first question, {\it ``Is the galaxy smooth and rounded, with no
@@
 question, with between 40 and 140~responses (see Section~\ref{sec:interface}).
-The number of users to answer any subsequent question, however, is always equal
-to or less than the number to answer the preceding question. The average number
+The number of participants answering subsequent questions, however, is always equal
+to or less than the number who answered the preceding question. The average number
 of responses per task for fourth- or fifth-tier questions such as spiral arm
@@
 that can be extracted for the higher-tier questions. The debiasing technique
-used (Section~\ref{ssec:zeta}) requires that at least 10~users answer each
+used (Section~\ref{ssec:zeta}) requires that at least 10~classifiers answer each
 question for a galaxy with $z_\mathrm{sim}=0.3$ \emph{and} the corresponding
@@
 classification data is provided: for each question, $\tt N_{votes}$ is the
-number of users to answer that question. For each unique answer, $\tt fraction$
-is the fraction of users to select that answer ($\rm N_{answer}/N_{votes}$, and
-$\tt weighted$ is the weighted fraction, which takes into account user
+number of classifiers who answered that question. For each unique answer, $\tt fraction$
+is the fraction of classifiers who selected that answer ($\rm N_{answer}/N_{votes}$, and
+$\tt weighted$ is the weighted fraction, which takes into account overall
 consistency (Section~\ref{ssec:weighting}).
@@
 
-In GZH, volunteers answer questions about a galaxy's morphology in a decision
-tree format. With this structure, questions shown to a user are dependent on
+In GZH, participants answered questions about a galaxy's morphology in a decision
+tree format. With this structure, questions shown to a classifier were dependent on
 their answers to the previous questions (Section~\ref{ssec:interface}).
@@
 The arm-number question, Task~11, is a 5$^\mathrm{th}$-tier Task, meaning that
-whether this question is seen by a user is dependent on four Tasks preceding
-it. In this case, it is only shown to volunteers who voted the galaxy was
+whether this question is seen by a classifier was dependent on four Tasks preceding
+it. In this case, it as only shown to classifiers who identified the galaxy as
 featured/disk-shaped in Task~01, not clumpy in Task~12, not edge-on in Task~02,
-and had spiral structure in Task~10.
+and having spiral structure in Task~10.
 
@@
 high fraction of votes for this task voted for the $bar,yes$ answer. This is
-not the only necessary cut, however, since not all users answer this question;
+not the only necessary cut, however, since not all classifiers answer this question;
 only those who have previously selected ``features'' in Task~01, ``not clumpy''
@@
 
-The flexibility of this catalog allows the user to set their own selection
+The flexibility of this catalog allows users to set their own selection
 criteria for vote fraction thresholds to create a morphologically pure sample.
@@
 variety of morphologies. These thresholds are determined by a visual inspection
-of subsamples. For each Task, at least 20 users are required to have voted on
+of subsamples. For each Task, at least 20 classifiers are required to have voted on
 the given question along with a cut on the vote fraction is applied to the
 previous task. We visually analyzed subsamples of 50~galaxies meeting both
-criteria, as well as a control sample of galaxies which had 20~users vote on
+criteria, as well as a control sample of galaxies which had 20~classifiers vote on
 the task, but did not meet the threshold cut set for the previous task. The
@@
 Tasks 03, 04 and 05 have an additional possible pathway; as shown in
-Figure~\ref{fig:decisiontree}, a user might also be shown this question if they
+Figure~\ref{fig:decisiontree}, a classifier might also be shown this question if they
 select ``featured/disk'' in Task~01, ``clumpy'' in Task~12, two or more clumps
@@
 supplementary table. This section analyzes the effect of image depth on the
-ability of the GZ users to identify features or disk structure in the images.
+ability of the GZ classifiers to identify features or disk structure in the images.
 

### 2016-05-15 writeup/gz_hubble_data.tex
Credit @ckrawczyk for Figure 3. Closes #85.
Cite Land+08 for weighting. Closes #80.

@@
 
-The votes of individual classifiers in GZH were combined to
-make a vote fraction for each response ($f_{response}$) to a question in the
-classification tree. Votes were weighted \citep[in a method identical to
-that described in][]{wil13} such that classifiers who frequently disagreed with
-others ended up having very low weights. The weighting $(w)$ was 1
-for the top 95\% of classifiers, as ranked by consistency. For the bottom 5\% of
+The votes of individual classifiers in GZH were combined to make a vote
+fraction for each response ($f_{response}$) to a question in the classification
+tree. Votes were weighted in a method similar that in previous versions of
+Galaxy~Zoo \citep{lan08,wil13}, such that classifiers who frequently disagreed
+with others ended up having very low weights. The weighting $(w)$ was 1 for the
+top 95\% of classifiers, as ranked by consistency. For the bottom 5\% of
 classifiers, $w$ was designed to drop smoothly and was effectively zero for the
-bottom 1\%.  Since this only affected a tiny percentage of
-the classifiers (and an even smaller percentage of the classifications) the
-overall effect on the GZH dataset was minimal. The method was effective,
-however, at filtering out contributions from random or deliberately
-malicious classifiers.
+bottom 1\%.  Since this only affected a tiny percentage of the classifiers (and
+an even smaller percentage of the classifications) the overall effect on the
+GZH dataset was minimal. The method was effective, however, at filtering out
+contributions from random or deliberately malicious classifiers.
 
@@
 Astronomy'' workshop, 3-7 Mar 2014 in Taipei, Taiwan, at which some of this
-analysis was done. We also thank Jennifer Lotz for sharing her $G$-$M_{20}$
-measurements for the AEGIS sample.
+analysis was done. We thank Jennifer Lotz for sharing her $G$-$M_{20}$
+measurements for the AEGIS sample. We thank Coleman Krawczyk for his assistance
+in producing Figure~\ref{fig:decisiontree}.
 

### 2016-05-16 writeup/gz_hubble_data.tex
added specz flag to dropbox metadata tables and explanation text in sec 2.5
Edits from @bamford on image creation.

@@
 
-The images used for classification in GZH were color-composite JPGs made from
-multi-band data. The exact process for creating the images depended on the bands
-and resolutions in the surveys.
-
-For galaxies in the ACS-GC, color composites were made using a fixed pixel
-intensity scaling with weights of
-$[2.4\times10^{-4},3\times10^{-4},3\times10^{-4}]$ in the red, green, and blue
-channels respectively. A nonlinear mapping was applied to each pixel to
-emphasize the contrast in faint features \citep{lup04}, taking the form of:
-
-\begin{equation}
-I_\mathrm{channel,new} = I_\mathrm{channel,old} \times \frac{\arcsinh(b\times r)}{(b\times r)}
-\label{eqn:nonlinear}
-\end{equation}
-
-\noindent GZH images from \citet{gri12} used a value of $b=3$.
-
-The majority of the data in Legacy surveys described in
-Section~\ref{ssec:legacy_surveys} had images in only one or two filters
-available when the GZH project was first launched, making standard 3-channel
-RGB images in the same method used for the SDSS images in the original Galaxy
-Zoo impossible. For surveys with images in two bands (AEGIS, GEMS, and the
-two-epoch GOODS-N and GOODS-S), the lower-wavelength band was mapped to the
-blue channel, the higher-wavelength band to the red channel, and the green
-channel created by taking the geometric mean of the two. Bands used in each of
-the surveys are listed in Table~\ref{tbl:gzh_numbers}. The 2-epoch GOODS-N and
-GOODS-S images used different filters --- this was a deliberate choice made so
-that the GEMS images could be directly compared with the overlapping coverage
-of GOODS-S (Figure~\ref{fig:filtercurves}).
-
-By the time that the 5-epoch sets of GOODS data were put into GZH (in March
-2015), coverage in four separate \hst{} bands were publicly available. The
-deeper GOODS images were created using the arithmetic mean of \Bband{} and
-\Vband{} in the blue channel, \Iband{} in the red channel, and \zband{} in the
-green channel. These images also had their speckled noise pixels decolorized.
-
-The COSMOS images only had the \Iband{} imaging available at the time of
-classification in GZH. For these galaxies, GZH used ``pseudocolor'' images
-created by using the ACS \Iband{} data as an illumination map and ground-based
-imaging from the \subaru{} telescope in $B_J$, $r^+$, and $i^+$ filters to
-provide the color gradients \citep[see][for further details]{gri12}. This
-resulted in images with the angular resolution of \hst{}
-($\sim0.05$~\arcsec/pixel) for the overall intensity, but color gradients at
-ground-based resolution, with seeing between 0.95\arcsec{} and 1.05\arcsec{}
-\citep{tan07}.
+The images used for classification in GZH were color-composite JPEGs made from
+multi-band data. These were created followed the method of \citet{lup04}, which
+preserves colour information irrespective of intensity.  An asinh intensity
+mapping was applied to enhance the appearance of faint features while avoiding
+saturating galaxy centers. The relative scalings of the filter bands were
+chosen while trying to reproduce the color appearance of the SDSS images in
+previous iterations of Galaxy Zoo.
+
+Many of the Legacy surveys described in Section~\ref{ssec:legacy_surveys}
+provided images in only two filters. For these, the shorter-wavelength band was
+mapped to the blue channel, the longer-wavelength band to the red channel, and
+the green channel created by taking the arithmetic mean of the two. The bands
+used in each of the surveys are listed in Table~\ref{tbl:gzh_numbers}.
+Although four bands were available for the GOODS survey, only two bands were
+used to create the original 2-epoch images, for consistency with AEGIS and
+GEMS. The 2-epoch GOODS-N and GOODS-S images were created using different
+filters --- this was a deliberate choice made so that the GEMS images could be
+directly compared with the overlapping coverage of GOODS-S
+(Figure~\ref{fig:filtercurves}).
+
+Only 2-epoch GOODS images were included at the launch of GZH.  Deeper, 5-epoch 
+GOODS images were added into GZH later (in March 2015). These images made
+use of the full four-band data by using the arithmetic mean of \Bband{} and
+\Vband{} in the blue channel, \Iband{} in the green channel, and \zband{} in
+the red channel.
+
+The COSMOS survey provided only \Iband{} HST imaging at the time of the GZH
+launch.  These galaxies used ``pseudocolor'' images created by using
+the ACS \Iband{} data as an illumination map and ground-based imaging from the
+\subaru{} telescope in $B_J$, $r^+$, and $i^+$ filters to provide color
+information (see \citealt{gri12} for further details). This resulted in images
+with the angular resolution of \hst{} ($\sim0.05$~\arcsec/pixel) for the
+overall intensity, but color gradients at ground-based resolution, with seeing
+between 0.95\arcsec{} and 1.05\arcsec{} \citep{tan07}.
 
@@
 RGB channels. The co-added Stripe~82 images were assembled from runs 106 and
-206 in DR7 and made into color composites using the method of \citet{lup04}.
-
-To deal with situations in which the sky noise was highly colored (which might
-have been a distraction to visual classification), a soft-edged object mask was
-applied to the coadded Stripe~82 and the COSMOS images. This mask preserved the
-color balance for galaxies, but desaturated speckled noise against regions of
-blank sky.
+206 in DR7 and processed into color composites in a corresponding manner.
+
+In some cases, we found that attempting to emphasize faint features in the
+images resulted in the sky noise taking the appearance of brightly colored
+speckles. This impaired the aesthetics of the images and might have been a
+distraction to visual classification.  To counteract this, a soft-edged object
+mask was applied to the color images and a desaturation operation performed.
+This masked procedure was effective in preserving the color balance for
+galaxies, retaining the visibility of faint features, but reduced the color
+contrast in the sky noise and greatly improved the appearance of the images.
+This solution was applied to the coadded Stripe~82, COSMOS and 5-epoch GOODS
+images.
 

### 2016-05-16 writeup/gz_hubble_data.tex
Fixing filter curves for GOODS 5-epoch. See #91.

--- 2016-05-15 writeup/gz_hubble_data.tex
@@
 3DHST, and then MUSYC. For galaxies with multiple spectroscopic redshifts, more
-than 98\% are consistent at $\Delta z<0.001$, and so the order of selection
-made no practical difference. If no spectroscopic redshifts were available,
-the 1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST, MUSYC,
+than 98\% are consistent ($\Delta z<0.001$), and so the order of selection
+made no practical difference. Galaxies with inconsistent spectroscopic
+redshifts between any pair of catalogs are marked with a flag in
+Table~\ref{tbl:catalog_hst}. If no spectroscopic redshifts were available, the
+1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST, MUSYC,
 UltraVISTA;][]{ilb13} and UltraVISTA grism data were used to select the

### 2016-05-16 python/filter_curves.py

@@ -68,7 +68,7 @@ suprime_filters = {'B':{'label':r'$B_J$','labelpos':(3500,0.50)},
                     'g':{'label':r'$g^+$','labelpos':(5100,0.80)},
                     'r':{'label':r'$r^+$','labelpos':(6300,0.70)}}
 
-gzh = {'AEGIS':('F606W','F814W'),'COSMOS':('F814W',),'GEMS, GOODS-S':('F606W','F850LP'),'GOODS-N':('F606W','F775W'),'deep GOODS-N,-S':('F435W','F606W','F775W','F814W')}
+gzh = {'AEGIS':('F606W','F814W'),'COSMOS':('F814W',),'GEMS, GOODS-S':('F606W','F850LP'),'GOODS-N':('F606W','F775W'),'deep GOODS-N,-S':('F435W','F606W','F775W','F850LP')}
 kwargs = dict(fontsize=14, ha='center', va='center')
 
 for survey,ax in zip(gzh,axarr.ravel()):

### 2016-05-16 writeup/gz_hubble_data.tex
clarifying daophot vs tinytim
plus references; closes #99

--- 2016-05-15 writeup/gz_hubble_data.tex
@@
 Two sets of simulated AGN were generated in GZH. The first set (version~1) was
-assembled from 95~galaxies from GEMS imaging and PSFs from \texttt{daophot}.
+assembled from 95~galaxies from GOODS-S imaging and empirical PSFs made by combining stars in the GOODS fields using the PSF creation tools in \texttt{daophot}. 
 The second set (version~2) was assembled from 96~galaxies in GOODS-S; this
-version used deeper imaging and improved PSFs from \texttt{TinyTim}.
+version used simulated PSFs from \texttt{TinyTim} \citep{kri93}, drizzled using the same procedures as those used in reduction of the GOODS-S images \citep{koe02,koe03,gia04}.
+The use of these 2 versions facilitates comparisons between these different PSF creation methods, which are widely used in AGN host galaxy morphology studies \citep[e.g.,][]{san04,sim08,pie10a,simm11}.
+% okay so I'm a cheeky self-citing biyotch
+Each PSF creation method has advantages and disadvantages: the empirical PSFs better represent the nuances of the PSF in the specific data being used and look more realistic at lower luminosities, but the extended features of the noiseless \texttt{TinyTim} PSFs are visually more realistic at higher luminosities.
 
@@
 manner and evenly distributed with unaltered images of the galaxies.
-Classifiers were not explicitly told that the images had been altered, as the
+Classifiers were not explicitly told that the images had been altered during classification, as the
 goal was to measure the effect on normal classifications in as unbiased a
 manner as possible.
+Following classification, a classifier could view a page with additional details about each galaxy they had classified; where applicable these pages contained further information regarding image modifications.
 

### 2016-05-16 writeup/gz_hubble_data.tex
Fixes several points in #89

@@
 
+The properties of the individual surveys are as follows:
+
 \begin{itemize}
@@
 \caption{Summary of GZH imaging \label{tbl:gzh_numbers}}
-\begin{tabular}{lclcrr}
+\begin{tabular}{lllcrr}
 \hline\hline
-Survey &  $t_{\rm exp}$ & Filters & Resolution & Area & $N_{\rm galaxies}$ \\
+Survey &  Total $t_{\rm exp}$ & Filters & Resolution & Area & $N_{\rm galaxies}$ \\
  & [sec] & & [\arcsec/pix] & [arcmin$^2$] & \\
 \hline
-AEGIS                                   & 2100$-$2300 & \Vband{} and \Iband{}            & 0.03 & 710   & 8157  \\
+AEGIS                                   & 2100$-$2300  & \Vband, \Iband{}                 & 0.03 & 710                & 8157    \\
 COSMOS                                  & 2028         & \Iband{}                         & 0.05 & 6480               & 88530   \\
-GEMS                                    & 2160$-$2286 & \Vband{} and \zband{}            & 0.03 & 800   & 9143  \\
-GOODS                                   & 1000$-$2100 & \Bband, \Vband, \iband, \zband{} & 0.03 & 320   &   \\
-\hspace{10pt} \emph{GOODS-N~2~epoch}    & $-$         & $-$                              & $-$  & $-$   & \emph{2551}  \\
-\hspace{10pt} \emph{GOODS-S~2~epoch}    & $-$         & $-$                              & $-$  & $-$   & \emph{3593}  \\
-\hspace{10pt} \emph{GOODS-N~5~epoch}    & $-$         & $-$                              & $-$  & $-$   & \emph{6015}  \\
-\hspace{10pt} \emph{GOODS-S~5~epoch}    & $-$         & $-$                              & $-$  & $-$   & \emph{5142}  \\
-
+GEMS                                    & 2160$-$2286  & \Vband, \zband{}                 & 0.03 & 800                & 9143    \\
+GOODS                                   & $-$          & $-$                              & $-$  & $-$                & $-$     \\
+\hspace{10pt} \emph{GOODS-N~2~epoch}    & 2100$-$4200  & \Vband, \iband                   & 0.03 & 320                & 2551    \\
+\hspace{10pt} \emph{GOODS-S~2~epoch}    & 2100$-$4200  & \Vband, \zband                   & 0.03 & 320                & 3593    \\
+\hspace{10pt} \emph{GOODS-N~5~epoch}    & 5100$-$10500 & \Bband, \Vband, \iband, \zband{} & 0.03 & $^{\prime\prime}$  & 6015    \\
+\hspace{10pt} \emph{GOODS-S~5~epoch}    & 5100$-$10500 & \Bband, \Vband, \iband, \zband{} & 0.03 & $^{\prime\prime}$  & 5142    \\
 \hline
-total                                   & $-$         & $-$                              & $-$  & 8310  & 130467  \\
+total                                   & $-$          & $-$                              & $-$  & 8630 & 123131  \\
 \hline\hline
@@
 than 98\% are consistent at $\Delta z<0.001$, and so the order of selection
-made no practical difference. If no spectroscopic redshifts were available,
+made no practical difference.
+Those which are inconsistent ($\Delta z>0.001$) between any of the three catalogs are marked with a Boolean flag in the column $\tt z\_spec\_conflict\_flag$ in Table~\ref{tbl:catalog_hst}.
+If no spectroscopic redshifts were available,
 the 1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST, MUSYC,

### 2016-05-16 writeup/gz_hubble_data.tex
swap S3.1 and 3.2; add S3 intro
closes #96; also addresses one of the points on Carie's list in #109

@@
-\documentclass[twocolumn]{aastex6}
+\documentclass[twocolumn]{aastex}
 
@@
 
-\subsection{Classifier weighting}\label{ssec:weighting}
-
-The votes of individual classifiers in GZH were combined to make a vote
-fraction for each response ($f_{response}$) to a question in the classification
-tree. Votes were weighted in a method similar that in previous versions of
-Galaxy~Zoo \citep{lan08,wil13}, such that classifiers who frequently disagreed
-with others ended up having very low weights. The weighting $(w)$ was 1 for the
-top 95\% of classifiers, as ranked by consistency. For the bottom 5\% of
-classifiers, $w$ was designed to drop smoothly and was effectively zero for the
-bottom 1\%.  Since this only affected a tiny percentage of the classifiers (and
-an even smaller percentage of the classifications) the overall effect on the
-GZH dataset was minimal. The method was effective, however, at filtering out
-contributions from random or deliberately malicious classifiers.
-
-Classifications were aggregated and weighted only if the classifier was logged
-into GZH under their username (which was encouraged, but not required for
-participation). Classifications by participants who were not logged in were marked as
-``Anonymous''; no weighting was applied, but the data were otherwise treated
-identically in the data processing.
+Below we describe the classification structure of GZH, including the software 
+interface and the hierarchical structure of a classification. Section \ref{ssec:weighting}
+describes the process of combining individual classifications into vote fractions for each
+galaxy.
 
@@
 simulated AGN were activated in Dec 2010, as well as a small sample of
-AEGIS/GEMS/GOODS images mistakenly excluded from the original sample based on
-an overly restrictive cut on blended and/or saturated objects. The main GZH
+images from AEGIS, GEMS, and GOODS that were previously excluded from the original sample
+due to cuts on blended and/or saturated objects and subsequently confirmed as classifiable galaxies. The main GZH
 site collected data until its replacement, the fourth phase of
@@
 % Sum is the total of the GZH SQL table plus the GOODS full-depth imaging in GZ4.
+
+\subsection{Classifier weighting}\label{ssec:weighting}
+
+As a first step to producing consensus classifications of each galaxy, 
+the votes of individual classifiers in GZH were combined to make a vote
+fraction for each response ($f_{response}$) to a question in the classification
+tree. Votes were subsequently weighted and re-combined in an iterative method similar that in 
+previous versions of Galaxy~Zoo \citep{lan08,wil13}, using a method chosen 
+to be as egalitarian as possible while also identifying and downweighting classifiers 
+who frequently disagreed with others. The weighting factor $(w)$ was 1 for the
+top 95\% of classifiers, as ranked by consistency. For the bottom 5\% of
+classifiers, $w$ was designed to drop smoothly and was effectively zero for the
+bottom 1\%.  Since this only affected a tiny percentage of the classifiers (and
+% would be good to quantify "tiny" and "even smaller [than tiny]"
+an even smaller percentage of the classifications) the overall effect on the
+GZH dataset was minimal. The method was effective, however, at filtering out
+contributions from random or deliberately malicious classifiers.
+
+Classifications were aggregated and weighted only if the classifier was logged
+into GZH under their username (which was encouraged, but not required for
+participation). Classifications by participants who were not logged in were marked as
+``Anonymous'' and assumed to have $w = 1$. 
+% We should also try to estimate how many anonymous classifiers there were, if possible.
 

### 2016-05-17 writeup/gz_hubble_data.tex
Changed all HST curves to system throughput

--- 2016-05-16 writeup/gz_hubble_data.tex
@@
-\documentclass[twocolumn]{aastex}
+\documentclass[twocolumn]{aastex6}
 
@@
 \includegraphics[width=160mm]{figures/filter_curves.pdf}
-\caption{Transmission curves of the filters used by \hst{} Advanced Camera for
-Surveys (ACS) in wide-field channel mode for the various surveys in GZH. The
-unfilled black curves show the filters for the Suprime Camera on the
-\textit{Subaru} telescope, which was used to create color gradients in the GZH
-images for COSMOS.\label{fig:filtercurves}}
+\caption{System throughput (fractional photon detection efficiency) of the
+filters used by \hst{} Advanced Camera for Surveys (ACS) in wide-field channel
+mode for the various surveys in GZH. The unfilled black curves show the filters
+for the Suprime Camera on the \textit{Subaru} telescope, which was used to
+create color gradients in the GZH images for COSMOS.\label{fig:filtercurves}}
 \end{figure*}
-
-The properties of the individual surveys are as follows:
 
@@
 \caption{Summary of GZH imaging \label{tbl:gzh_numbers}}
-\begin{tabular}{lllcrr}
+\begin{tabular}{lclcrr}
 \hline\hline
-Survey &  Total $t_{\rm exp}$ & Filters & Resolution & Area & $N_{\rm galaxies}$ \\
+Survey &  $t_{\rm exp}$ & Filters & Resolution & Area & $N_{\rm galaxies}$ \\
  & [sec] & & [\arcsec/pix] & [arcmin$^2$] & \\
 \hline
-AEGIS                                   & 2100$-$2300  & \Vband, \Iband{}                 & 0.03 & 710                & 8157    \\
+AEGIS                                   & 2100$-$2300 & \Vband{} and \Iband{}            & 0.03 & 710   & 8157  \\
 COSMOS                                  & 2028        & \Iband{}                         & 0.05 & 6480  & 88530 \\
-GEMS                                    & 2160$-$2286  & \Vband, \zband{}                 & 0.03 & 800                & 9143    \\
-GOODS                                   & $-$          & $-$                              & $-$  & $-$                & $-$     \\
-\hspace{10pt} \emph{GOODS-N~2~epoch}    & 2100$-$4200  & \Vband, \iband                   & 0.03 & 320                & 2551    \\
-\hspace{10pt} \emph{GOODS-S~2~epoch}    & 2100$-$4200  & \Vband, \zband                   & 0.03 & 320                & 3593    \\
-\hspace{10pt} \emph{GOODS-N~5~epoch}    & 5100$-$10500 & \Bband, \Vband, \iband, \zband{} & 0.03 & $^{\prime\prime}$  & 6015    \\
-\hspace{10pt} \emph{GOODS-S~5~epoch}    & 5100$-$10500 & \Bband, \Vband, \iband, \zband{} & 0.03 & $^{\prime\prime}$  & 5142    \\
+GEMS                                    & 2160$-$2286 & \Vband{} and \zband{}            & 0.03 & 800   & 9143  \\
+GOODS                                   & 1000$-$2100 & \Bband, \Vband, \iband, \zband{} & 0.03 & 320   &   \\
+\hspace{10pt} \emph{GOODS-N~2~epoch}    & $-$         & $-$                              & $-$  & $-$   & \emph{2551}  \\
+\hspace{10pt} \emph{GOODS-S~2~epoch}    & $-$         & $-$                              & $-$  & $-$   & \emph{3593}  \\
+\hspace{10pt} \emph{GOODS-N~5~epoch}    & $-$         & $-$                              & $-$  & $-$   & \emph{6015}  \\
+\hspace{10pt} \emph{GOODS-S~5~epoch}    & $-$         & $-$                              & $-$  & $-$   & \emph{5142}  \\
+
 \hline
-total                                   & $-$          & $-$                              & $-$  & 8630 & 123131  \\
+total                                   & $-$         & $-$                              & $-$  & 8310  & 130467  \\
 \hline\hline
@@
 Two sets of simulated AGN were generated in GZH. The first set (version~1) was
-assembled from 95~galaxies from GOODS-S imaging and empirical PSFs made by combining stars in the GOODS fields using the PSF creation tools in \texttt{daophot}. 
+assembled from 95~galaxies from GEMS imaging and PSFs from \texttt{daophot}.
 The second set (version~2) was assembled from 96~galaxies in GOODS-S; this
-version used simulated PSFs from \texttt{TinyTim} \citep{kri93}, drizzled using the same procedures as those used in reduction of the GOODS-S images \citep{koe02,koe03,gia04}.
-The use of these 2 versions facilitates comparisons between these different PSF creation methods, which are widely used in AGN host galaxy morphology studies \citep[e.g.,][]{san04,sim08,pie10a,simm11}.
-% okay so I'm a cheeky self-citing biyotch
-Each PSF creation method has advantages and disadvantages: the empirical PSFs better represent the nuances of the PSF in the specific data being used and look more realistic at lower luminosities, but the extended features of the noiseless \texttt{TinyTim} PSFs are visually more realistic at higher luminosities.
+version used deeper imaging and improved PSFs from \texttt{TinyTim}.
 
@@
 manner and evenly distributed with unaltered images of the galaxies.
-Classifiers were not explicitly told that the images had been altered during classification, as the
+Classifiers were not explicitly told that the images had been altered, as the
 goal was to measure the effect on normal classifications in as unbiased a
 manner as possible.
-Following classification, a classifier could view a page with additional details about each galaxy they had classified; where applicable these pages contained further information regarding image modifications.
 
@@
 3DHST, and then MUSYC. For galaxies with multiple spectroscopic redshifts, more
-than 98\% are consistent at $\Delta z<0.001$, and so the order of selection
-made no practical difference.
-Those which are inconsistent ($\Delta z>0.001$) between any of the three catalogs are marked with a Boolean flag in the column $\tt z\_spec\_conflict\_flag$ in Table~\ref{tbl:catalog_hst}.
-If no spectroscopic redshifts were available,
-the 1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST, MUSYC,
+than 98\% are consistent ($\Delta z<0.001$), and so the order of selection
+made no practical difference. Galaxies with inconsistent spectroscopic
+redshifts between any pair of catalogs are marked with a flag in
+Table~\ref{tbl:catalog_hst}. If no spectroscopic redshifts were available, the
+1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST, MUSYC,
 UltraVISTA;][]{ilb13} and UltraVISTA grism data were used to select the
@@
 
-Below we describe the classification structure of GZH, including the software 
-interface and the hierarchical structure of a classification. Section \ref{ssec:weighting}
-describes the process of combining individual classifications into vote fractions for each
-galaxy.
+\subsection{Classifier weighting}\label{ssec:weighting}
+
+The votes of individual classifiers in GZH were combined to make a vote
+fraction for each response ($f_{response}$) to a question in the classification
+tree. Votes were weighted in a method similar that in previous versions of
+Galaxy~Zoo \citep{lan08,wil13}, such that classifiers who frequently disagreed
+with others ended up having very low weights. The weighting $(w)$ was 1 for the
+top 95\% of classifiers, as ranked by consistency. For the bottom 5\% of
+classifiers, $w$ was designed to drop smoothly and was effectively zero for the
+bottom 1\%.  Since this only affected a tiny percentage of the classifiers (and
+an even smaller percentage of the classifications) the overall effect on the
+GZH dataset was minimal. The method was effective, however, at filtering out
+contributions from random or deliberately malicious classifiers.
+
+Classifications were aggregated and weighted only if the classifier was logged
+into GZH under their username (which was encouraged, but not required for
+participation). Classifications by participants who were not logged in were marked as
+``Anonymous''; no weighting was applied, but the data were otherwise treated
+identically in the data processing.
 
@@
 simulated AGN were activated in Dec 2010, as well as a small sample of
-images from AEGIS, GEMS, and GOODS that were previously excluded from the original sample
-due to cuts on blended and/or saturated objects and subsequently confirmed as classifiable galaxies. The main GZH
+AEGIS/GEMS/GOODS images mistakenly excluded from the original sample based on
+an overly restrictive cut on blended and/or saturated objects. The main GZH
 site collected data until its replacement, the fourth phase of
@@
 % Sum is the total of the GZH SQL table plus the GOODS full-depth imaging in GZ4.
-
-\subsection{Classifier weighting}\label{ssec:weighting}
-
-As a first step to producing consensus classifications of each galaxy, 
-the votes of individual classifiers in GZH were combined to make a vote
-fraction for each response ($f_{response}$) to a question in the classification
-tree. Votes were subsequently weighted and re-combined in an iterative method similar that in 
-previous versions of Galaxy~Zoo \citep{lan08,wil13}, using a method chosen 
-to be as egalitarian as possible while also identifying and downweighting classifiers 
-who frequently disagreed with others. The weighting factor $(w)$ was 1 for the
-top 95\% of classifiers, as ranked by consistency. For the bottom 5\% of
-classifiers, $w$ was designed to drop smoothly and was effectively zero for the
-bottom 1\%.  Since this only affected a tiny percentage of the classifiers (and
-% would be good to quantify "tiny" and "even smaller [than tiny]"
-an even smaller percentage of the classifications) the overall effect on the
-GZH dataset was minimal. The method was effective, however, at filtering out
-contributions from random or deliberately malicious classifiers.
-
-Classifications were aggregated and weighted only if the classifier was logged
-into GZH under their username (which was encouraged, but not required for
-participation). Classifications by participants who were not logged in were marked as
-``Anonymous'' and assumed to have $w = 1$. 
-% We should also try to estimate how many anonymous classifiers there were, if possible.
 

### 2016-05-17 python/filter_curves.py

@@ -7,32 +7,43 @@ from matplotlib.patches import Arrow
 from astropy.io import fits
 import glob
 
-def fetch_acs_filter(filt):
+def fetch_acs_filter(filt,efficiency=True,synphot=False):
 
-    url = 'http://www.stsci.edu/hst/acs/analysis/throughputs/tables/wfc_{0}.dat'.format(filt)
-    
-    if not os.path.exists('downloads'):
-        os.makedirs('downloads')
+    # Can't select both
 
-    '''
-    loc = os.path.join('downloads', '%s.dat' % filt)
-    if not os.path.exists(loc):
-        print "downloading from %s" % url
-        F = urllib2.urlopen(url)
-        open(loc, 'w').write(F.read())
+    if synphot + efficiency == 1:
 
-    F = open(loc)
-        
-    data = np.loadtxt(F)
-    '''
+        if efficiency:
 
-    # Picked filter curves instead from http://www.stsci.edu/hst/observatory/crds/SIfileInfo/pysynphottables/current_acs_throughput_html
+            url = 'http://www.stsci.edu/hst/acs/analysis/throughputs/tables/wfc_{0}.dat'.format(filt)
+            
+            if not os.path.exists('downloads'):
+                os.makedirs('downloads')
 
-    filenames = glob.glob("downloads/acs*{0}*wfc*.fits".format(filt))
-    if len(filenames) > 0:
-        data = fits.getdata(filenames[0],1)
+            loc = os.path.join('downloads', '%s.dat' % filt)
+            if not os.path.exists(loc):
+                print "downloading from %s" % url
+                F = urllib2.urlopen(url)
+                open(loc, 'w').write(F.read())
 
-    return data
+            F = open(loc)
+                
+            data = np.loadtxt(F)
+
+        # Deprecated by suggestion of B. Simmons and S. Bamford
+        # Alternate method of showing throughput
+        # from http://www.stsci.edu/hst/observatory/crds/SIfileInfo/pysynphottables/current_acs_throughput_html
+
+        if synphot:
+            filenames = glob.glob("downloads/acs*{0}*wfc*.fits".format(filt))
+            if len(filenames) > 0:
[…]

### 2016-05-17 writeup/gz_hubble_data.tex
All filter transmission curves from SVO.

@@
 \includegraphics[width=160mm]{figures/filter_curves.pdf}
-\caption{System throughput (fractional photon detection efficiency) of the
-filters used by \hst{} Advanced Camera for Surveys (ACS) in wide-field channel
-mode for the various surveys in GZH. The unfilled black curves show the filters
-for the Suprime Camera on the \textit{Subaru} telescope, which was used to
-create color gradients in the GZH images for COSMOS.\label{fig:filtercurves}}
+\caption{Transmission curves of the filters used by \hst{} Advanced Camera for
+Surveys (ACS) in wide-field channel mode for the various surveys in GZH. The
+unfilled black curves show the filters for the Suprime Camera on \subaru, which
+was used to create color gradients in the GZH COSMOS
+images.\label{fig:filtercurves}}
 \end{figure*}

### 2016-05-17 python/filter_curves.py

@@ -1,69 +1,44 @@
 import os
 import urllib2
-
-import numpy as np
+from astropy.io.votable import parse_single_table
 from matplotlib import pyplot as plt
-from matplotlib.patches import Arrow
-from astropy.io import fits
-import glob
 
-def fetch_acs_filter(filt,efficiency=True,synphot=False):
+'''
+Deprecated locations for filter curves:
 
-    # Can't select both
+ACS:
+    http://www.stsci.edu/hst/acs/analysis/throughputs/tables/wfc_{0}.dat'.format(filt)
+    http://www.stsci.edu/hst/observatory/crds/SIfileInfo/pysynphottables/current_acs_throughput_html
 
-    if synphot + efficiency == 1:
+Suprime:
 
-        if efficiency:
+    http://www.astro.caltech.edu/~capak/filters/{0}.res'.format(filename)
 
-            url = 'http://www.stsci.edu/hst/acs/analysis/throughputs/tables/wfc_{0}.dat'.format(filt)
-            
-            if not os.path.exists('downloads'):
-                os.makedirs('downloads')
-
-            loc = os.path.join('downloads', '%s.dat' % filt)
-            if not os.path.exists(loc):
-                print "downloading from %s" % url
-                F = urllib2.urlopen(url)
-                open(loc, 'w').write(F.read())
-
-            F = open(loc)
-                
-            data = np.loadtxt(F)
-
-        # Deprecated by suggestion of B. Simmons and S. Bamford
-        # Alternate method of showing throughput
-        # from http://www.stsci.edu/hst/observatory/crds/SIfileInfo/pysynphottables/current_acs_throughput_html
-
-        if synphot:
-            filenames = glob.glob("downloads/acs*{0}*wfc*.fits".format(filt))
-            if len(filenames) > 0:
-                data = fits.getdata(filenames[0],1)
-
-        return data
-
-    else:
-        print "efficiency = {0}, synphot = {1} - must choose only one option".format(efficiency,synphot)
-        return None
-
-def fetch_subaru_filter(filt):
-
-    filename = '{0}_subaru'.format(filt)
-    url = 'http://www.astro.caltech.edu/~capak/filters/{0}.res'.format(filename)
+'''
     
[…]

### 2016-05-17 writeup/gz_hubble_data.tex
Incorporated abstract changes by KLM. Closes #83.

@@
 crowdsourced visual classifications of color composite images. Images in GZH
-were selected from various \textit{Hubble Space Telescope} Legacy programs that
-used the Advanced Camera for Surveys (AEGIS, COSMOS, GEMS, GOODS-N, and
-GOODS-S), with filters selected to probe the rest-frame optical emission from
-galaxies out to $z\simeq1$. The galaxies selected for GZH classifications go
-down to magnitude limits of $m_{I814W}<23.5$ and have a median redshift of
-$\langle z\rangle=0.9\pm0.6$, with a tail extending out to $z\simeq4$. The GZH
+were selected from various \textit{Hubble Space Telescope} Legacy programs
+using the Advanced Camera for Surveys (AEGIS, COSMOS, GEMS, GOODS-N, and
+GOODS-S), with filters that probe the rest-frame optical emission from galaxies
+out to $z\sim1$. The galaxies selected for GZH classifications go down to
+magnitude limits of $m_{I814W}<23.5$ and have a median redshift of $\langle
+z\rangle=0.9\pm0.6$, with a tail extending out to $z\simeq4$. The GZH
 morphological data include measurements of both bulge- and disk-dominated
-galaxies, details on spiral disk structure that relate to the Hubble type, as
-well as clump identification and geometry. This paper also describes and
-employs a novel method for calibrating morphological bias by using
-artificially-redshifted galaxy images as a baseline. The GZH catalog contains
-both raw and calibrated morphological vote fractions for $150,771$ galaxies,
-providing a comprehensive data set suitable for large-scale studies of galaxy
-evolution. 
-% didn't the GOODS-N and GOODS-S second phases go deeper than 23.5 mag? am I misremembering? --BDS
-
+galaxies, details on spiral disk structure that relate to the Hubble type, bar
+identification, and numerous measuremenst of clump identification and geometry.
+This paper also describes a new method for calibrating morphological bias by
+using artificially-redshifted galaxy images as a baseline. The GZH catalog
+contains both raw and calibrated morphological vote fractions for
+$150,771$~galaxies, providing the largest data set to date suitable for
+large-scale studies of galaxy evolution out to $z\sim1$. 
 \end{abstract}

### 2016-05-17 writeup/gz_hubble_data.tex

@@
 development of a galaxy and its external appearance typically manifests at the
-most basic level as the difference between bulge-dominated, virialized systems
-resembling ellipticals (early-types) and disk-dominated, rotationally-supported
-systems (late-types) frequently exhibiting spiral arms. This dichotomy has been
-used to explore much of the astrophysics governing galaxy formation and
-evolution, and has been shown to be closely linked with other galactic
-properties such as stellar mass, halo mass, bolometric luminosity, black hole
-activity, effective radius, and the relative ages of the stellar populations.
+most basic level as the difference between bulge-dominated systems with
+no/little spiral structure (early-types) and disk-dominated,
+rotationally-supported galaxies (late-types) frequently exhibiting spiral arms.
+This dichotomy has been used to explore much of the astrophysics governing
+galaxy formation and evolution, and has been shown to be closely linked with
+other galactic properties such as stellar mass, halo mass, bolometric
+luminosity, black hole activity, effective radius, and the relative ages of the
+stellar populations.
 
@@
 provides an extremely powerful observational constraint on the physics involved
-\citep[for a recent review see][]{con14}.
+\citep[for recent reviews see][]{but13,con14}.
 
@@
 hierarchical assembly model \citep{sil12}. The structure of individual galaxies
-is affected by their merger history \citep{too72,hop10}, local environment
-\citep[such as the morphology-density relation;][]{dre80}, initial dark halo
-mass, and many other factors. Morphologies of individual simulated high-mass
-galaxies at $z\sim2-3$ commonly show kpc-scale ``clumpy'' structures, with few
-galaxies that are either smooth or well-ordered spirals; asymmetric profiles
-with strong density contrasts dominate simulated populations in the early
-Universe until at least $z\sim1$ \citep{gen14}.
+is affected by their merger history \citep{too72,ste02,hop10}, local
+environment \citep[such as the morphology-density relation;][]{dre80}, initial
+dark halo mass, secular evolution rate, and many other factors. Morphologies of
+individual simulated high-mass galaxies at $z\sim2-3$ commonly show kpc-scale
+``clumpy'' structures, with few galaxies that are either smooth or well-ordered
+spirals; asymmetric profiles with strong density contrasts dominate simulated
+populations in the early Universe until at least $z\sim1$ \citep{bel12,gen14}.
 
@@
 a disk from a bulge), but will be limited for more compact structures. Since
-the size of galaxies evolves as roughly $r\propto(1+z)^{-1}$ \citep{law12a},
-the compact sizes of high-redshift galaxies make detailed morphologies a
-challenge even for \hst{} \citep{che12}. The public availability of more than
-$10^5$~galaxies in archival imaging across various studies gives a data sample
-with the potential for high statistical significance.
+the size of galaxies evolves as roughly $r\propto(1+z)^{-1}$
+\citep{mao98,law12a}, the compact sizes of high-redshift galaxies make detailed
+morphologies a challenge even for \hst{} \citep{che12}. The public availability
+of more than $10^5$~galaxies in archival imaging across various studies gives a
+data sample with the potential for high statistical significance.
 
@@
 especially for asymmetric galaxies that become increasingly common at high
-redshifts. The Galaxy Zoo project \citep{lin08,lin11} utilizes crowdsourced
-visual classifications to measure galaxies in color-composite images. The
-efforts of more than $2\times10^5$~classifiers allow for multiple independent
+redshifts. The Galaxy Zoo project \citep{lin08} utilizes crowdsourced visual
+classifications to measure galaxies in color-composite images. The efforts of
+more than $2\times10^5$~classifiers allow for multiple independent
 classifications of each image which are combined and calibrated to give a
@@
 being visible. While crowdsourced data require extensive calibration
-\citep{bam09,wil13}, they have a proven reliability and have been used in
-dozens of papers
+\citep{bam09,wil13}, they have a proven reliability and have been used for a
+wide variety of scientific studies
 \citep[eg,][]{lan08,bam09,dar10,mas11c,ski12,sim13,sch14,wil15}.
 
-This paper presents the results from the Galaxy Zoo Hubble (GZH)
-project.\footnote{\url{http://zoo3.galaxyzoo.org/}} GZH was the third phase of
-Galaxy Zoo, following its initial results classifying $\sim900,000$~SDSS~images
-into primarily early/late~types \citep{lin11} and Galaxy~Zoo~2, which covered
-$\sim250,000$~SDSS~images using a more detailed classification scheme that
-included bars, spiral arms, and galactic bulges \citep{wil13}. GZH used a
-similarly detailed classification scheme, but focused for the first time on
-images of high-redshift galaxies taken with \hst. The Galaxy Zoo: CANDELS
-project has also classified morphologies of galaxies at high redshift using ACS
-and WFC3 imaging (Simmons et~al., submitted).
+This paper presents the classifications collected from the Galaxy Zoo Hubble
+(GZH) project.\footnote{\url{http://zoo3.galaxyzoo.org/}} GZH was the third
+phase of Galaxy Zoo, following its initial results classifying
+$\sim900,000$~SDSS~images into primarily early/late~types \citep{lin11} and
+Galaxy~Zoo~2, which covered $\sim250,000$~SDSS~images using a more detailed
+classification scheme that included bars, spiral arms, and galactic bulges
+\citep{wil13}. GZH used a similarly detailed classification scheme, but focused
+for the first time on images of high-redshift galaxies taken with \hst. The
+Galaxy Zoo: CANDELS project has also classified morphologies of galaxies at
+high redshift using ACS and WFC3 imaging (Simmons et~al., submitted).
 

### 2016-05-17 writeup/gz_hubble_data.tex
Correct magnitude limits in abstract

@@
 were selected from various \textit{Hubble Space Telescope} Legacy programs
-using the Advanced Camera for Surveys (AEGIS, COSMOS, GEMS, GOODS-N, and
-GOODS-S), with filters that probe the rest-frame optical emission from galaxies
-out to $z\sim1$. The galaxies selected for GZH classifications go down to
-magnitude limits of $m_{I814W}<23.5$ and have a median redshift of $\langle
-z\rangle=0.9\pm0.6$, with a tail extending out to $z\simeq4$. The GZH
-morphological data include measurements of both bulge- and disk-dominated
-galaxies, details on spiral disk structure that relate to the Hubble type, bar
-identification, and numerous measuremenst of clump identification and geometry.
-This paper also describes a new method for calibrating morphological bias by
-using artificially-redshifted galaxy images as a baseline. The GZH catalog
-contains both raw and calibrated morphological vote fractions for
-$150,771$~galaxies, providing the largest data set to date suitable for
-large-scale studies of galaxy evolution out to $z\sim1$. 
+using the Advanced Camera for Surveys, with filters that probe the rest-frame
+optical emission from galaxies out to $z\sim1$.  The bulk of the sample is
+selected to have $m_{I814W}<23.5$ across AEGIS, COSMOS, GEMS, and 2-epoch
+exposures in GOODS-N and GOODS-S. Full-depth 5-epoch images from the GOODS
+fields are also included and have $m_{I814W}<26.8$. The median redshift of the
+combined samples is $\langle z\rangle=0.9\pm0.6$, with a tail extending out to
+$z\simeq4$. The GZH morphological data include measurements of both bulge- and
+disk-dominated galaxies, details on spiral disk structure that relate to the
+Hubble type, bar identification, and numerous measuremenst of clump
+identification and geometry.  This paper also describes a new method for
+calibrating morphological bias by using artificially-redshifted galaxy images
+as a baseline. The GZH catalog contains both raw and calibrated morphological
+vote fractions for $150,771$~galaxies, providing the largest dataset to date
+suitable for large-scale studies of galaxy evolution out to $z\sim1$. 
 \end{abstract}

### 2016-05-17 writeup/comments/gz_hubble_data_cjl.tex
Smaller changes (via email) from CJL.

--- 2016-05-17 writeup/gz_hubble_data.tex
@@
 % Note: 250-word limit
-We present the data release paper for the Galaxy Zoo: Hubble (GZH)
-project.\footnote{This publication has been made possible by the participation
-of more than 200,000~volunteers in the Galaxy Zoo project. Their contributions
-are individually acknowledged at
-\url{http://authors.galaxyzoo.org/authors.html}.} This is the third phase in a
-large effort to measure reliable, detailed morphologies of galaxies by using
-crowdsourced visual classifications of color composite images. Images in GZH
-were selected from various \textit{Hubble Space Telescope} Legacy programs
-using the Advanced Camera for Surveys (AEGIS, COSMOS, GEMS, GOODS-N, and
-GOODS-S), with filters that probe the rest-frame optical emission from galaxies
-out to $z\sim1$. The galaxies selected for GZH classifications go down to
-magnitude limits of $m_{I814W}<23.5$ and have a median redshift of $\langle
-z\rangle=0.9\pm0.6$, with a tail extending out to $z\simeq4$. The GZH
-morphological data include measurements of both bulge- and disk-dominated
-galaxies, details on spiral disk structure that relate to the Hubble type, bar
-identification, and numerous measuremenst of clump identification and geometry.
-This paper also describes a new method for calibrating morphological bias by
-using artificially-redshifted galaxy images as a baseline. The GZH catalog
-contains both raw and calibrated morphological vote fractions for
-$150,771$~galaxies, providing the largest data set to date suitable for
-large-scale studies of galaxy evolution out to $z\sim1$. 
+We present the data release paper for the Galaxy Zoo: Hubble (GZH) project.\footnote{This publication has been made possible by the participation of more than 200,000 volunteers in the Galaxy Zoo project.
+Their contributions are individually acknowledged at \url{http://authors.galaxyzoo.org/authors.html}.} This is the third phase in a large effort to measure reliable morphologies of galaxies on detailed scales by using crowdsourced visual classifications of color composite image.
+Images in GZH are selected from various \textit{Hubble Space Telescope} Legacy programs using the Advanced Camera for Surveys (AEGIS, COSMOS, GEMS, GOODS-N, and GOODS-S), with filters selected to probe the rest-frame optical emission from galaxies out to $z\simeq1$.
+The galaxies selected for GZH classifications go down to magnitude limits of $m_{I814W}<23.5$ and have a median redshift of $\langle z\rangle=0.9\pm0.6$, with a tail extending out to $z\simeq4$.
+The GZH morphological data includes measurements of both bulge- and disk-dominated galaxies, details on spiral disk structure that relate to the Hubble type, and numerous measurements of clump identification and geometry.
+This paper also describes and employs a novel method for calibrating morphologies for galaxies of different luminosities and at different redshifts by using artificially-redshifted galaxy images as a baseline.
+The GZH catalog includes both the raw and calibrated morphological vote fractions for $150,771$ galaxies, providing a comprehensive data set suitable for large-scale studies of galaxy evolution.
+
 \end{abstract}
@@
 
-The morphology of galaxies encodes information on the orbital parameters and
-assembly history of their contents, including gas, dust, stars, and the central
-black hole. The morphology is also closely related to the local environment of
-a galaxy, as interactions such as tides, shocks in cluster environments and
-direct mergers can all influence a galaxy's internal structure.  For
-$M^\star$~galaxies in the local Universe, this interplay between the physical
-development of a galaxy and its external appearance typically manifests at the
-most basic level as the difference between bulge-dominated, virialized systems
-resembling ellipticals (early-types) and disk-dominated, rotationally-supported
-systems (late-types) frequently exhibiting spiral arms. This dichotomy has been
-used to explore much of the astrophysics governing galaxy formation and
-evolution, and has been shown to be closely linked with other galactic
-properties such as stellar mass, halo mass, bolometric luminosity, black hole
-activity, effective radius, and the relative ages of the stellar populations.
-
-The advent of larger telescopes in an increasing range of observing wavelengths
-has revealed that the distribution and properties of galaxy morphology have
-strongly evolved over the lifetime of the Universe. At redshift $z\simeq1$
-(roughly 6~Gyr after the Big Bang), many galaxies are still in the process of
-assembling the baryonic and stellar mass required to reproduce the mature,
-coherent structures seen at the present day. This growth occurs via a variety
-of pathways, including accretion from large-scale galactic filaments onto halos
-via streaming, mergers of individual halos, conversion of gas into stars via
-gravitational collapse, etc. The accrual of baryons can be slowed or even
-reversed via feedback from stellar winds, supernovae, and active black holes.
-Each of these processes affects galaxy morphology in different ways, and so an
-accurate measurement of morphological demographics as a function of redshift
-provides an extremely powerful observational constraint on the physics involved
-\citep[for a recent review see][]{con14}.
-
-Theoretical predictions for the morphology of galaxies as a function of
-redshift are primarily computed within the $\Lambda$CDM cosmological framework.
-Full treatments model gravitational interactions between baryons and dark
-matter, hydrodynamics of the gas, and baryonic physics related to star
-formation and evolution. The most advanced simulations now span volumes up to
-$\sim100$~Mpc$^3$ while simultaneously resolving the smaller ($<1$ kpc) scales
-necessary to reproduce the influence of baryonic physics \citep{vog14a,sch15}.
-Such simulations predict clustering of galaxies on large scales in a
-hierarchical assembly model \citep{sil12}. The structure of individual galaxies
-is affected by their merger history \citep{too72,hop10}, local environment
-\citep[such as the morphology-density relation;][]{dre80}, initial dark halo
-mass, and many other factors. Morphologies of individual simulated high-mass
-galaxies at $z\sim2-3$ commonly show kpc-scale ``clumpy'' structures, with few
-galaxies that are either smooth or well-ordered spirals; asymmetric profiles
-with strong density contrasts dominate simulated populations in the early
-Universe until at least $z\sim1$ \citep{gen14}.
-
-Observational studies of galaxies at high-redshift also display a wide range of
-morphological types, many of which are rare or absent at $z\sim0$. Although
-spheroids and disks are present, they are typically much more compact than
-those in the local Universe. There is also a significant population of more
-irregular, massive galaxies, including mergers, tadpoles, chains,
-double-clumps, and clump-clusters \citep{elm05,elm07,cam11a,for11a,kar15}. In
-contrast, while grand-design spirals have been observed as far back as $z=2.18$
-\citep{law12}, their spatial density suggests that they are exceedingly rare,
-with a very low fraction of undisturbed disks \citep{mor13}. Current
-observational data thus strongly suggests that the classical Hubble
-sequence/tuning fork \citep{hub36} is not a suitable framework for
-characterizing high-redshift morphology.
-
-Space-based observatories, particularly the \hubble{} (\hst), have been
-responsible for the bulk of imaging studies of high-redshift galaxies.
-Observations of fixed fields with very deep imaging
-\citep[eg,][]{wil96,gia04,bec06,dav07,sco07,gro11} give the photometric
-sensitivity necessary to detect $L^\star$ galaxies at $z>1$, while also
-providing the angular resolution to distinguish internal structure and
-characterize the morphology. While these measurements are helped by the fact
-that the angular diameter distance is relatively flat beyond $z>1$ in a flat
-$\Lambda$CDM cosmology, the relevant angular scales are only of the order
-$\sim5-10~\mathrm{kpc}/^{\prime\prime}$ \citep{wri06}. \hst{} can thus resolve
-much of the structure for a Milky Way-sized galaxy (at least for distinguishing
-a disk from a bulge), but will be limited for more compact structures. Since
-the size of galaxies evolves as roughly $r\propto(1+z)^{-1}$ \citep{law12a},
-the compact sizes of high-redshift galaxies make detailed morphologies a
-challenge even for \hst{} \citep{che12}. The public availability of more than
-$10^5$~galaxies in archival imaging across various studies gives a data sample
-with the potential for high statistical significance.
-
-One of the major difficulties in studying the morphologies of galaxies lies in
-the techniques used for measurement. Visual classification by experts has been
-used for many decades \citep[eg,][]{hub26,dev59,san61,van76,nai10,bai11,kar15}.
-These methods have the advantage of using the significant processing power of
-the human brain to identify patterns, but suffer from issues such as lack of
-scaling to large surveys and potential issues with replicability and
-calibration. Automated measurements, both parametric \citep{pen02a,sim11,lac12}
-and non-parametric \citep{abr03,con03,lot04,sca07,bam08,fre13}, scale well to
-very large sample sizes, but do not always fully capture the relevant features,
-especially for asymmetric galaxies that become increasingly common at high
-redshifts. The Galaxy Zoo project \citep{lin08,lin11} utilizes crowdsourced
-visual classifications to measure galaxies in color-composite images. The
-efforts of more than $2\times10^5$~classifiers allow for multiple independent
-classifications of each image which are combined and calibrated to give a
-distribution of vote fractions proportional to the probability of a feature
-being visible. While crowdsourced data require extensive calibration
-\citep{bam09,wil13}, they have a proven reliability and have been used in
-dozens of papers
-\citep[eg,][]{lan08,bam09,dar10,mas11c,ski12,sim13,sch14,wil15}.
-
-This paper presents the results from the Galaxy Zoo Hubble (GZH)
-project.\footnote{\url{http://zoo3.galaxyzoo.org/}} GZH was the third phase of
-Galaxy Zoo, following its initial results classifying $\sim900,000$~SDSS~images
-into primarily early/late~types \citep{lin11} and Galaxy~Zoo~2, which covered
-$\sim250,000$~SDSS~images using a more detailed classification scheme that
-included bars, spiral arms, and galactic bulges \citep{wil13}. GZH used a
-similarly detailed classification scheme, but focused for the first time on
-images of high-redshift galaxies taken with \hst. The Galaxy Zoo: CANDELS
-project has also classified morphologies of galaxies at high redshift using ACS
-and WFC3 imaging (Simmons et~al., submitted).
-
-The sample selection and creation of the images used for GZH is described in
-Section~\ref{sec:data}. Section~\ref{sec:interface} describes the GZH interface
-and the collection of classifications. Section~\ref{sec:debiasing} outlines the
-process used to calibrate and correct the crowdsourced vote fractions for
-redshift-dependent bias. Section~\ref{sec:results} gives the main catalog of
-results, with several examples of how the data may be queried in
-Section~\ref{sec:cookbook}. Section~\ref{sec:analysis} gives a short overview
-of the observed morphological demographics and compares them to several other
-catalogs, with a summary in Section~\ref{sec:summary}.
-
-This paper assumes the WMAP9 cosmological parameters of
-$(\Omega_m,\Omega_\Lambda,h)=(0.282,0.718,0.697)$ \citep{hin13}.
+The morphology of galaxies encodes information on the orbital parameters and assembly history of the contents, including gas, dust, stars, and the central black hole.
+The morphology is also closely related to the local environment of the galaxy, as mutual interactions such as tides, shocks in cluster environments and direct mergers can all change the shape of the galaxy's gravitational potential.
+For $M^\star$~galaxies in the local Universe, this typically manifests at the most basic level as the difference between bulge-dominated, virialized systems resembling ellipticals (early-types) and disk-dominated, rotationally-supported disks (late-types) frequently exhibiting spiral arms.
+This dichotomy has been used to explore much of the astrophysics governing galaxy formation and evolution, and has been shown to be closely linked with other galactic properties such as stellar mass, halo mass, bolometric luminosity, black hole activity, effective radius, and the relative ages of the stellar populations.
+
+The advent of larger telescopes in an increasing range of observing wavelengths has revealed that the distribution and properties of galaxy morphology have strongly evolved over the lifetime of the Universe.
+At redshift $z\simeq1$ (roughly 6~Gyr after the Big Bang), many galaxies are still in the process of assembling the baryonic mass required to reproduce the structures seen in the present day.
+This occurs in a variety of pathways, including accretion of baryons from large-scale galactic filaments onto halos via streaming, mergers of individual dark matter halos along with their baryons, conversion of gas into stars via gravitational collapse and star formation, etc.
+The process can also be slowed or even reversed via feedback from stellar winds, supernovae, and active black holes.
+Each of these processes affects the galaxy morphology in different ways, and so an accurate measurement of the demographics as a function of redshift provides an extremely powerful observational constraint on the physics involved \citep[for a recent review see][]{con14}.
+
+Theoretical predictions for the morphology of galaxies as a function of redshift are primarily computed within the $\Lambda$CDM cosmological framework.
+Full treatments of this model gravitational interactions between baryons and dark matter, hydrodynamics of the gas, and baryonic physics related to star formation and evolution.
+The most advanced simulations now include volumes up to $\sim100$~Mpc$^3$ while simultaneously resolving the smaller scales necessary to reproduce the baryonic physics \citep{vog14a,sch15}.
+Such simulations predict clustering of galaxies on large scales in a hierarchical assembly model \citep{sil12}.
+The structure of individual galaxies is affected by the merger history \citep{too72,hop10}, local environment \citep[such as the morphology-density relation;][]{dre80}, initial dark halo mass, and many other factors.
+Morphologies of individual simulated high-mass galaxies at $z\sim2-3$ commonly show kpc-scale ``clumpy'' structures and few galaxies that are either smooth or well-ordered spirals; asymmetric profiles with strong density contrasts dominate populations in the early Universe until at least $z\sim1$ \citep{gen14}.
+
+Observational studies of galaxies at high-redshift also display a wide range of morphological types, many of which are rare or absent at $z\sim0$.
+These include spheroids and disks (akin to the ellipticals and spirals seen in the local Universe), but also a significant population of massive, more irregular galaxies, including mergers, tadpoles, chains, double-clumps, and clump-clusters \citep{elm05,elm07,cam11a,for11a,kar15}.
+In contrast, while grand-design spirals have been observed as far back as $z=2.18$ \citep{law12}, their spatial density suggests that they are exceedingly rare at these higher redshifts, with a very low overall disk fraction \citep{mor13}.
+Current observational data thus strongly suggests that the classical Hubble sequence/tuning fork \citep{hub36} is not a suitable framework for characterizing high-redshift morphology.
+
+Space-based observatories, particularly the \hubble, have been responsible for the bulk of imaging studies of high-redshift galaxies.
+Observations of fixed fields with very deep imaging \citep[eg,][]{wil96,gia04,bec06,dav07,sco07,gro11} give the photometric sensitivity necessary to detect $L^\star$ galaxies at $z>1$, while also providing the angular resolution to distinguish internal structure and characterize the morphology.
+While these measurements are helped by the fact that the angular diameter distance is relatively flat beyond $z>1$ in a flat $\Lambda$CDM cosmology, the relevant angular scales are only of the order $\sim5-10~\mathrm{kpc}/^{\prime\prime}$ \citep{wri06}.
+\hst{} can thus resolve much of the structure for a Milky Way-sized galaxy out to moderately high redshifts (at least distinguishing a disk from a bulge), but will be limited for more compact structures.
+Since the size of galaxies evolves as roughly $r\propto(1+z)^{-1}$ \citep{law12a}, the compact sizes of high-redshift galaxies make detailed morphologies a challenge even for \hst{} \citep{che12}.
+The public availability of more than $10^5$~galaxies in archival imaging across various studies gives a data sample with the potential for high statistical significance.
+
+One of the major difficulties in studying the morphologies of galaxies lies in the techniques used for measurement.
+Visual classification by experts has been used for many years \citep[eg,][]{hub26,dev59,san61,van76,nai10,bai11,kar15}.
+These methods have the advantage of using the significant processing power of the human brain to identify patterns, but suffer from issues such as lack of scaling to large surveys and potential issues with replicability and calibration.
+Automated measurements, both parametric \citep{pen02a,sim11,lac12} and non-parametric \citep{abr03,con03,lot04,sca07,bam08,fre13}, scale well to very large sample sizes, but do not always fully capture the relevant features, especially for asymmetric galaxies that become increasingly common at high redshifts.
+The Galaxy Zoo project \citep{lin08,lin11} utilizes crowdsourced visual classifications to measure galaxies in color-composite images.
+The efforts of more than $2\times10^5$~classifiers allow for multiple independent classifications of each image which are combined and calibrated to give a distribution of vote fractions proportional to the probability of a feature being visible.
+While crowdsourced data require extensive calibration \citep{bam09,wil13}, they have a proven reliability and have been used in dozens of papers \citep[eg,][]{lan08,bam09,dar10,mas11c,ski12,sim13,sch14,wil15}.
+
+This paper presents the results from the Galaxy Zoo Hubble (GZH) project.\footnote{\url{http://zoo3.galaxyzoo.org/}} GZH was the third phase of Galaxy Zoo, following its initial results classifying $\sim900,000$~SDSS~images into primarily early/late~types \citep{lin11} and Galaxy~Zoo~2, which covered $\sim250,000$~SDSS~images using a more detailed classification scheme that included bars, spiral arms, and galactic bulges \citep{wil13}.
+GZH used a similarly detailed classification scheme, but focused for the first time on images of high-redshift galaxies taken with the \hubble.
+The Galaxy Zoo: CANDELS project has also classified morphologies of galaxies at high redshift using ACS and WFC3 imaging (Simmons et~al., submitted).
+
+The sample selection and creation of the images used for GZH is described in Section~\ref{sec:data}.
+Section~\ref{sec:interface} describes the GZH interface and the collection of classifications.
+Section~\ref{sec:debiasing} outlines the process used to calibrate and correct the crowdsourced vote fractions for redshift-dependent bias.
+Section~\ref{sec:results} gives the main catalog of results, with several examples of how the data may be queried in Section~\ref{sec:cookbook}.
+Section~\ref{sec:analysis} gives a short overview of the observed morphological demographics and compares them to several other catalogs, with a summary in Section~\ref{sec:summary}.
+
+This paper uses the WMAP9 cosmology parameters of $(\Omega_m,\Omega_\Lambda,h)=(0.258,0.718,0.697)$ \citep{hin13}.
+
+%\begin{enumerate}
+%    \item Motivation for studying morphology of galaxies
+%    \item Particular scientific questions governed by galaxies at $z\sim1$
+%    \item Theoretical predictions for galaxy morphology evolution
+%    \item Past imaging and morphology studies at $z\sim1$
+%    \item Summary of GZ/citizen science work on galaxy morphology to date
+%    \item Outline of paper
+%\end{enumerate}
 
@@
 
-The GZH project contains images drawn from a number of different dedicated
-surveys and sample selection criteria. The majority of the data (as implied by
-the project name) were taken directly from \hst{} Legacy Surveys, all of which
-primarily used imaging from the Advanced Camera for Surveys (ACS). Results from
-the individual surveys have been combined into a single photometric and
-morphological database, the Advanced Camera for Surveys General Catalog
-\citep[ACS-GC;][]{gri12}. A summary of the key parameters is given in
-Table~\ref{tbl:gzh_numbers}.
+The GZH project contains images drawn from a number of different dedicated surveys and sample selection criteria.
+The majority of the data (as implied by the project name) are taken directly from \hst{} Legacy Surveys, all of which primarily use imaging from the Advanced Camera for Surveys (ACS).
+Results from the individual surveys have been combined into a single photometric and morphological database, the Advanced Camera for Surveys General Catalog \citep[ACS-GC;][]{gri12}.
+A summary of the key parameters is given in Table~\ref{tbl:gzh_numbers}.
 
@@
 \includegraphics[width=160mm]{figures/filter_curves.pdf}
-\caption{Transmission curves of the filters used by \hst{} Advanced Camera for
-Surveys (ACS) in wide-field channel mode for the various surveys in GZH. The
-unfilled black curves show the filters for the Suprime Camera on \subaru, which
-was used to create color gradients in the GZH COSMOS
-images.\label{fig:filtercurves}}
+\caption{Transmission curves of the filters used by \hst{} Advanced Camera for Surveys (ACS) in wide-field channel mode for the various surveys in GZH.
+The unfilled black curves show the filters for the Suprime Camera on the \textit{Subaru} telescope, which was used to create color gradients in the GZH images for COSMOS.\label{fig:filtercurves}}
 \end{figure*}
 
-The properties of the individual surveys are as follows:
-
 \begin{itemize}
-
-\item The All-Wavelength Extended Groth Strip International Survey
-    \citep[AEGIS;][]{dav07} covers a strip centered at
-    $\alpha=14^\textrm{h}17^\textrm{m}, \delta=+52^\circ30^\prime$. This area
-    of the sky was selected for a deep survey due to a combination of low
-    extinction and low Galactic/zodiacal emission. The ACS images covered 63
-    separate tiles over a total area of $\sim710$~arcmin$^2$. The two ACS bands
-    for AEGIS had exposure times of 2300~seconds in F606W (\Vband) and
-    2100~seconds in F814W (\Iband). The final mosaic images were dithered
-    to a resolution of 0.03~\arcsec/pixel. For extended objects, the
-    limiting magnitude of sources was 26.23~(AB) in \Vband{} and 25.61 (AB) in
-    \Iband.
-
-\item The Great Observatories Origins Deep Survey \citep[GOODS;][]{gia04}
-    covered two separate fields in the northern and southern hemispheres: the Hubble
-    Deep Field-North ($\alpha=12^\textrm{h}36^\textrm{m},
-    \delta=+62^\circ14^\prime$) and the Chandra Deep Field-South
-    ($\alpha=03^\textrm{h}32^\textrm{m}, \delta=-27^\circ48^\prime$). The \hst{}
-    ACS imaging data from the two fields are referred to as GOODS-N and GOODS-S,
-    respectively. ACS imaging in GOODS fields used 4 filters -- F435W (\Bband),
-    \Vband, F775W (\iband), and F850LP (\zband). The mean exposure times for each
-    epoch varied by band, from 1050--2100~seconds. The \Bband{} images were completed
-    in a single epoch at the beginning of the survey, but the \Vband, \iband, and
-    \zband{} images were taken in five separate epochs separated by 40--50~days
-    each. Images were dithered to a pixel scale of 0.03~\arcsec/pixel and covered a
-    total area of $\sim320$~arcmin$^2$ (160~arcmin$^2$ per north/south field). The
-    $5\sigma$ limiting magnitude for extended sources was 25.7 for \Vband{} and
-    25.0 for \iband.
-
-\item The Cosmic Evolution Survey \citep[COSMOS;][]{sco07} covered an area of
-    $\sim1.8$~deg$^2$ centered at $\alpha=10^\textrm{h}00^\textrm{m},
-    \delta=+02^\circ12^\prime$. Its location near the celestial equator was
-    designed to enable coverage by ground-based telescopes in both the Northern and
-    Southern Hemispheres, in addition to space-based observatories. The ACS data
-    for COSMOS consisted of 1~orbit per pointing with an exposure time of
-    2028~seconds in \Iband; 590 total pointings were used to cover the entire
-    field. The image resolution was dithered to 0.05~\arcsec/pixel. The 50\%
-    completeness magnitude for a galaxy with a half-light radius of
-    $0.50^{\prime\prime}$ in \Iband{} was 24.7 mag.
-
-\item The Galaxy Evolution from Morphologies and SEDs
-    \citep[GEMS;][]{rix04,cal08} survey was also centered on the Chandra Deep
-    Field-South. The GEMS data covered $\sim800$~arcmin$^2$, completely surrounding
-    the area covered by GOODS-S. Images from ACS in GEMS had 1 orbit per pointing
-    for a total of 63~pointings. The exposure times were 2160 and 2286~seconds in
-    \Vband{} and \zband{}, respectively. The image resolution had a pixel scale
-    of 0.03~\arcsec/pixel. The $5\sigma$ limiting magnitude for source
-    detection was 25.7 AB in \Vband{} and 24.2~AB in \zband.
-
+\item The All-Wavelength Extended Groth Strip International Survey \citep[AEGIS;][]{dav07} covers a strip centered at $\alpha=14^\textrm{h}17^\textrm{m}, \delta=+52^\circ30^\prime$.
+This area was selected for a deep survey due to a combination of low extinction and low Galactic/zodiacal emission.
+The ACS images covered 63 separate tiles over a total area of $\sim710$~arcmin$^2$.
+The two ACS bands for AEGIS had exposure times of 2300~seconds in F606W (\Vband) and 2100~seconds in F814W (\Iband).
+The final mosaic images are dithered to a resolution of 0.03~\arcsec/pixel.
+For extended objects, the limiting magnitudes of sources in AEGIS are 26.23~(AB) in \Vband{} and 25.61 (AB) in \Iband.
+
+\item The Great Observatories Origins Deep Survey \citep[GOODS;][]{gia04} covers two separate fields in the northern and southern hemispheres: the Hubble Deep Field-North ($\alpha=12^\textrm{h}36^\textrm{m}, \delta=+62^\circ14^\prime$) and the Chandra Deep Field-South ($\alpha=03^\textrm{h}32^\textrm{m}, \delta=-27^\circ48^\prime$).
+The \hst{} ACS imaging data from the two fields are referred to as GOODS-N and GOODS-S, respectively.
+ACS imaging in GOODS fields used 4 filters -- F435W (\Bband), \Vband, F775W (\iband), and F850LP (\zband).
+The mean exposure times for each epoch vary by band, from 1050--2100~seconds.
+The \Bband{} images were completed in a single epoch at the beginning of the survey, but the \Vband, \iband, and \zband{} images were taken in five separate epochs separated by 40--50~days each.
+Images are dithered to a pixel scale of 0.03~\arcsec/pixel and cover a total area of $\sim320$~arcmin$^2$ (160~arcmin$^2$ per north/south field).
+The $5\sigma$ limiting magnitudes for extended sources are 25.7 for \Vband{} and 25.0 for \iband.
+
+\item The Cosmic Evolution Survey \citep[COSMOS;][]{sco07} covers an area of $\sim1.8$~deg$^2$ centered at $\alpha=10^\textrm{h}00^\textrm{m}, \delta=+02^\circ12^\prime$.
+Its location near the celestial equator was designed to enable coverage by ground-based telescopes in both the Northern and Southern Hemispheres, in addition to space-based observatories.
+The ACS data for COSMOS consists of 1 orbit per pointing with an exposure time of 2028~seconds in \Iband; 590 total pointings are used to cover the entire field.
+The image resolution is dithered to 0.05~\arcsec/pixel.
+The 50\% completeness magnitude for a galaxy with a half-light radius of $0.50^{\prime\prime}$ in \Iband{} is 24.7 mag.
+
+\item The Galaxy Evolution from Morphologies and SEDs \citep[GEMS;][]{rix04,cal08} survey is also centered on the Chandra Deep Field-South.
+The GEMS data covers $\sim800$~arcmin$^2$, completely surrounding the area covered by GOODS-S.
+Images from ACS in GEMS have 1 orbit per pointing for a total of 63~pointings.
+The exposure times are 2160 and 2286~seconds in \Vband{} and \zband{}, respectively.
+The image resolution has a pixel scale of 0.03~\arcsec/pixel.
+The $5\sigma$ limiting magnitudes for source detection are 25.7 AB in \Vband{} and 24.2~AB in \zband.
 \end{itemize}
@@
 \caption{Summary of GZH imaging \label{tbl:gzh_numbers}}
-\begin{tabular}{lllcrr}
+\begin{tabular}{lclcrr}
 \hline\hline
-Survey &  Total $t_{\rm exp}$ & Filters & Resolution & Area & $N_{\rm galaxies}$ \\
+Survey &  $t_{\rm exp}$ & Filters & Resolution & Area & $N_{\rm galaxies}$ \\
  & [sec] & & [\arcsec/pix] & [arcmin$^2$] & \\
 \hline
-AEGIS                                   & 2100$-$2300  & \Vband, \Iband{}                 & 0.03 & 710                & 8157    \\
+AEGIS                         & 2100$-$2300 & \Vband{} and \Iband{}            & 0.03 & 710   & 8157  \\
 COSMOS                        & 2028        & \Iband{}                         & 0.05 & 6480  & 88530 \\
-GEMS                                    & 2160$-$2286  & \Vband, \zband{}                 & 0.03 & 800                & 9143    \\
-GOODS                                   & $-$          & $-$                              & $-$  & $-$                & $-$     \\
-\hspace{10pt} \emph{GOODS-N~2~epoch}    & 2100$-$4200  & \Vband, \iband                   & 0.03 & 320                & 2551    \\
-\hspace{10pt} \emph{GOODS-S~2~epoch}    & 2100$-$4200  & \Vband, \zband                   & 0.03 & 320                & 3593    \\
-\hspace{10pt} \emph{GOODS-N~5~epoch}    & 5100$-$10500 & \Bband, \Vband, \iband, \zband{} & 0.03 & $^{\prime\prime}$  & 6015    \\
-\hspace{10pt} \emph{GOODS-S~5~epoch}    & 5100$-$10500 & \Bband, \Vband, \iband, \zband{} & 0.03 & $^{\prime\prime}$  & 5142    \\
+GEMS                          & 2160$-$2286 & \Vband{} and \zband{}            & 0.03 & 800   & 9143  \\
+GOODS                         & 1000$-$2100 & \Bband, \Vband, \iband, \zband{} & 0.03 & 320   &   \\
+\hspace{10pt} \emph{GOODS-N~2~epoch}  & $-$         & $-$                              & $-$  & $-$   & \emph{2551}  \\
+\hspace{10pt} \emph{GOODS-S~2~epoch}  & $-$         & $-$                              & $-$  & $-$   & \emph{3593}  \\
+\hspace{10pt} \emph{GOODS-N~5~epoch}  & $-$         & $-$                              & $-$  & $-$   & \emph{6015}  \\
+\hspace{10pt} \emph{GOODS-S~5~epoch}  & $-$         & $-$                              & $-$  & $-$   & \emph{5142}  \\
+
 \hline
-total                                   & $-$          & $-$                              & $-$  & 8630 & 123131  \\
+total                         & $-$         & $-$                              & $-$  & 8310  & 130467  \\
 \hline\hline
@@
 
-In the ACS-GC \citep{gri12}, individual galaxies were identified using a
-combination of \sextractor{} \citep{ber96} and the galaxy-profile fitting
-framework \galapagos{} \citep{bar12}. GZH included all galaxies with $m<23.5$,
-where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS, GEMS +
-GOODS-S, and GOODS-N surveys, respectively. This yielded a total of
-113,166~images (Table~\ref{tbl:gzh_numbers}).
-
-Single-epoch images from SDSS Stripe~82 were selected using the same criteria
-from \citet{wil13}, which required limits of \texttt{petroR90\_r}$ >
-3$\arcsec~(where \texttt{petroR90\_r} is the radius containing 90\% of the
-$r^\prime$ Petrosian flux) and a magnitude brighter than $m_r < 17.77$. The
-images used were three-color composites using the $g^\prime$, $r^\prime$, and
-$i^\prime$ filters \citep{nie04}. 21,522 galaxies in SDSS met these criteria.
-Co-added images from Stripe~82 were selected from the union of galaxies with
-co-added magnitudes brighter than $17.77$~mag, and the galaxies detected in the
-single-depth images and matched to a co-add source. This resulted in a total
-set of 30,339 images. Of the images in the co-added sample, 5144 (17~percent)
-were dimmer than the initial magnitude cut of 17.77.
+In the ACS-GC \citep{gri12}, individual galaxies are identified using a combination of \sextractor{} \citep{ber96} and the \sersic{}-profile fitting framework \galapagos{} \citep{bar12}.
+GZH includes all galaxies with $m < 23.5$, where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS, GEMS + GOODS-S, and GOODS-N surveys, respectively.
+This yielded a total of 113,166~images (Table~\ref{tbl:gzh_numbers}).
+
+Single-epoch images from SDSS Stripe~82 were selected using the same criteria from \citet{wil13}, which required limits of \texttt{petroR90\_r}$ > 3$\arcsec~(where \texttt{petroR90\_r} is the radius containing 90\% of the $r^\prime$ Petrosian flux) and a magnitude brighter than $m_r < 17.77$.
+The images used are three-color composites using the $g^\prime$, $r^\prime$, and $i^\prime$ filters \citep{nie04}.
+21,522 galaxies in SDSS met these criteria.
+Co-added images from Stripe~82 were selected from the union of galaxies with co-added magnitudes brighter than $17.77$~mag and the galaxies detected in the single-depth images and matched to a co-add source.
+This resulted in a larger set of 30,339 images.
+Of the images in the co-added sample, 5144 (17~percent) are dimmer than the initial magnitude cut of 17.77.
 
@@
 
-The images used for classification in GZH were color-composite JPEGs made from
-multi-band data. These were created followed the method of \citet{lup04}, which
-preserves colour information irrespective of intensity.  An asinh intensity
-mapping was applied to enhance the appearance of faint features while avoiding
-saturating galaxy centers. The relative scalings of the filter bands were
-chosen while trying to reproduce the color appearance of the SDSS images in
-previous iterations of Galaxy Zoo.
-
-Many of the Legacy surveys described in Section~\ref{ssec:legacy_surveys}
-provided images in only two filters. For these, the shorter-wavelength band was
-mapped to the blue channel, the longer-wavelength band to the red channel, and
-the green channel created by taking the arithmetic mean of the two. The bands
-used in each of the surveys are listed in Table~\ref{tbl:gzh_numbers}.
-Although four bands were available for the GOODS survey, only two bands were
-used to create the original 2-epoch images, for consistency with AEGIS and
-GEMS. The 2-epoch GOODS-N and GOODS-S images were created using different
-filters --- this was a deliberate choice made so that the GEMS images could be
-directly compared with the overlapping coverage of GOODS-S
-(Figure~\ref{fig:filtercurves}).
-
-Only 2-epoch GOODS images were included at the launch of GZH.  Deeper, 5-epoch 
-GOODS images were added into GZH later (in March 2015). These images made
-use of the full four-band data by using the arithmetic mean of \Bband{} and
-\Vband{} in the blue channel, \Iband{} in the green channel, and \zband{} in
-the red channel.
-
-The COSMOS survey provided only \Iband{} HST imaging at the time of the GZH
-launch.  These galaxies used ``pseudocolor'' images created by using
-the ACS \Iband{} data as an illumination map and ground-based imaging from the
-\subaru{} telescope in $B_J$, $r^+$, and $i^+$ filters to provide color
-information (see \citealt{gri12} for further details). This resulted in images
-with the angular resolution of \hst{} ($\sim0.05$~\arcsec/pixel) for the
-overall intensity, but color gradients at ground-based resolution, with seeing
-between 0.95\arcsec{} and 1.05\arcsec{} \citep{tan07}.
-
-Stripe~82 single-epoch images were taken directly from the DR7 SDSS Skyserver,
-which combined $g^{\prime}$, $r^{\prime}$, and $i^{\prime}$ exposures into the
-RGB channels. The co-added Stripe~82 images were assembled from runs 106 and
-206 in DR7 and processed into color composites in a corresponding manner.
-
-In some cases, we found that attempting to emphasize faint features in the
-images resulted in the sky noise taking the appearance of brightly colored
-speckles. This impaired the aesthetics of the images and might have been a
-distraction to visual classification.  To counteract this, a soft-edged object
-mask was applied to the color images and a desaturation operation performed.
-This masked procedure was effective in preserving the color balance for
-galaxies, retaining the visibility of faint features, but reduced the color
-contrast in the sky noise and greatly improved the appearance of the images.
-This solution was applied to the coadded Stripe~82, COSMOS and 5-epoch GOODS
-images.
+The images used for classification in GZH are color-composite JPGs made from multi-band data. The exact process for creating the images depends on the bands and resolutions in the surveys.
+
+For galaxies in the ACS-GC, color composites are made using a fixed pixel intensity scaling with weights of $[2.4\times10^{-4},3\times10^{-4},3\times10^{-4}]$ in the red, green, and blue channels respectively.
+A nonlinear mapping is applied to each pixel to emphasize the contrast in faint features \citep{lup04}, taking the form of:
+
+\begin{equation}
+I_\mathrm{channel,new} = I_\mathrm{channel,old} \times \frac{\arcsinh(b\times r)}{(b\times r)}
+\label{eqn:nonlinear}
+\end{equation}
+
+\noindent The GZH images from \citet{gri12} use a value of $b=3$.
+
+The majority of the data in Legacy surveys described in Section~\ref{ssec:legacy_surveys} had images in only one or two filters available when the GZH project was first launched, making standard 3-channel RGB images in the same method used for the SDSS images in the original Galaxy Zoo impossible.
+For surveys with images in two bands (AEGIS, GEMS, and the two-epoch GOODS-N and GOODS-S), the lower-wavelength band was mapped to the blue channel, the higher-wavelength band to the red channel, and the green channel created by taking the geometric mean of the two.
+Bands used in each of the surveys are listed in Table~\ref{tbl:gzh_numbers}.
+The 2-epoch GOODS-N and GOODS-S images use different filters --- this was a deliberate choice made so that the GEMS images could be directly compared with the overlapping coverage of GOODS-S (Figure~\ref{fig:filtercurves}).
+
+By the time that the 5-epoch sets of GOODS data were put into GZH (in March 2015), coverage in four separate \hst{} bands were publicly available.
+The deeper GOODS images were created using the arithmetic mean of \Bband{} and \Vband{} in the blue channel, \Iband{} in the red channel, and \zband{} in the green channel.
+These images also had their speckled noise pixels decolorized.
+
+The COSMOS images only had the \Iband{} imaging available at the time of classification in GZH.
+For these galaxies, we created ``pseudocolor'' images by using the ACS \Iband{} data as the illumination map and ground-based imaging from the \subaru{} telescope in $B_J$, $r^+$, and $i^+$ filters to provide the color gradients \citep[see][for further details]{gri12}.
+This means that the images have the angular resolution of \hst{} ($\sim0.05$~\arcsec/pixel) for the overall intensity, but the color gradients are at ground-based resolution, with seeing between 0.95\arcsec{} and 1.05\arcsec{} \citep{tan07}.
+
+Stripe~82 single-epoch images were taken directly from the color composites on the DR7 SDSS Skyserver, which combines $g^{\prime}$, $r^{\prime}$, and $i^{\prime}$ exposures into the RGB channels.
+The co-added Stripe~82 images were assembled from runs 106 and 206 in DR7 and made into color composites using the method of \citet{lup04}, as in previous iterations of Galaxy Zoo.
+
+To deal with images in which the sky noise was highly colored (which might have been a distraction to visual classification), a soft-edged object mask was applied that preserves the color balance for galaxies, but desaturates speckled noise against regions of blank sky.
+This technique was applied only to the co-added Stripe~82 and the COSMOS images.
 
@@
 
-GZH also included a set of images designed to measure the effect of active
-galactic nuclei (AGN) on morphological classifications. Since galactic nuclei
-can have bright, unresolved optical emission, AGN have the potential to mimic
-or distort the identification of a bulge component. The presence of an AGN was
-simulated by modeling the point spread function (PSF) of the telescope and then
-inserting a bright source near the center of a real galaxy. For each image, the
-simulated AGN was assigned one of three colors -- either blue, red, or flat
-(white) as seen in the color images -- and a range of brightnesses such that
-$L_\mathrm{ratio} \equiv L_\mathrm{galaxy}/L_\mathrm{AGN}$ is in
-$(0.2,1.0,2.0,5.0,10.0,50.0)$. Combining these parameters generated 15~images
-with different simulated AGN for each host.
-
-Two sets of simulated AGN were generated in GZH. The first set (version~1) was
-assembled from 95~galaxies from GOODS-S imaging and empirical PSFs made by combining stars in the GOODS fields using the PSF creation tools in \texttt{daophot}. 
-The second set (version~2) was assembled from 96~galaxies in GOODS-S; this
-version used simulated PSFs from \texttt{TinyTim} \citep{kri93}, drizzled using the same procedures as those used in reduction of the GOODS-S images \citep{koe02,koe03,gia04}.
-The use of these 2 versions facilitates comparisons between these different PSF creation methods, which are widely used in AGN host galaxy morphology studies \citep[e.g.,][]{san04,sim08,pie10a,simm11}.
-% okay so I'm a cheeky self-citing biyotch
-Each PSF creation method has advantages and disadvantages: the empirical PSFs better represent the nuances of the PSF in the specific data being used and look more realistic at lower luminosities, but the extended features of the noiseless \texttt{TinyTim} PSFs are visually more realistic at higher luminosities.
-
-Images with simulated AGN were classified in the main interface in an identical
-manner and evenly distributed with unaltered images of the galaxies.
-Classifiers were not explicitly told that the images had been altered during classification, as the
-goal was to measure the effect on normal classifications in as unbiased a
-manner as possible.
-Following classification, a classifier could view a page with additional details about each galaxy they had classified; where applicable these pages contained further information regarding image modifications.
+GZH also includes a set of images designed to measure the effect of active galactic nuclei (AGN) on morphological classifications.
+Since galactic nuclei can have bright, unresolved optical emission, this has the potential to mimic or distort the identification of a bulge component.
+The presence of an AGN is simulated by modeling the point spread function (PSF) of the telescope and then inserting a bright source near the center of a real galaxy.
+For each image, the simulated AGN is assigned one of three colors -- either blue, red, or flat (white) as seen in the color images -- and a range of brightnesses such that $L_\mathrm{ratio} \equiv L_\mathrm{galaxy}/L_\mathrm{AGN}$ is in $(0.2,1.0,2.0,5.0,10.0,50.0)$.
+This range was selected to run from AGN which were all but undetectable through to those which dominate the galaxy, providing coverage of all plausible effects.
+Combining these parameters generates 15~images with different simulated AGN for each host.
+
+Two sets of simulated AGN were generated in GZH.
+The first set (version~1) was assembled from 95~galaxies from GEMS imaging and PSFs from \texttt{daophot}.
+The second set (version~2) was assembled from 96~galaxies in GOODS-S; this version used deeper imaging and improved PSFs from \texttt{TinyTim}.
+
+Images with simulated AGN were classified in the main interface in an identical manner and evenly distributed with unaltered images of the galaxies.
+Classifiers were not explicitly told that the images had been altered, as the goal was to measure the effect on normal classifications in as unbiased a manner as possible.
 
@@
 
-Photometric data for the bulk of the GZH sample were largely drawn from the
-tables in \citet{gri12}. This included photometric parameters such as
-the fluxes, magnitudes, radii, ellipticities, position angles, and positions
-drawn from both \sextractor{} and \galfit. \galfit{} also provided the
-parametric \sersic{} index and effective half-light radius for the best-fit
-model. All parameters were measured in both bands of the ACS imaging, with the
-exception of the single-band COSMOS images.
-
-Redshifts for the GZH catalog were compiled from a variety of sources. For each
-galaxy, the primary redshift used for debiasing calculations
-(Section~\ref{sec:debiasing}) is in the $\tt Z\_BEST$ column of
-Table~\ref{tbl:catalog_hst}. The redshift type (spectroscopic: $\tt SPEC\_Z$,
-photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column
-$\tt Z\_BEST\_TYPE$, and the source catalog of the redshift is included as $\tt
-Z\_BEST\_SOURCE$.
-
-For galaxies which have published redshifts from multiple sources, the
-following algorithm was used to select the $\tt Z\_BEST$ quantity. The first
-priority is spectroscopic redshifts; these were taken from the ACS-GC
-\citep{gri12}, 3DHST \citep{mom15}, and MUSYC \citep{car10} catalogs. A
-high-quality spectroscopic redshift in the ACS-GC is the primary option; if
-none is available, then $\tt Z\_BEST$ uses the spectroscopic redshifts in
-3DHST, and then MUSYC. For galaxies with multiple spectroscopic redshifts, more
-than 98\% are consistent ($\Delta z<0.001$), and so the order of selection
-made no practical difference. Galaxies with inconsistent spectroscopic
-redshifts between any pair of catalogs are marked with a flag in
-Table~\ref{tbl:catalog_hst}. If no spectroscopic redshifts were available, the
-1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST, MUSYC,
-UltraVISTA;][]{ilb13} and UltraVISTA grism data were used to select the
-redshift with the smallest error. 
+Photometric data for the bulk of the GZH sample is largely drawn from the tables provided in \citet{gri12}.
+This includes photometric parameters such as the fluxes, magnitudes, radii, ellipticities, position angles, and positions drawn from both \sextractor{} and \galfit.
+\galfit{} also provides the parametric \sersic{} index and effective half-light radius for the best-fit model.
+All parameters are measured in both bands of the ACS imaging, with the exception of the single-band COSMOS images.
+
+Redshifts for the GZH catalog are compiled from a variety of sources.
+For each galaxy, the primary redshift used for debiasing calculations (Section~\ref{sec:debiasing}) is in the $\tt Z\_BEST$ column of Table~\ref{tbl:catalog_hst}.
+The redshift type (spectroscopic: $\tt SPEC\_Z$, photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column $\tt Z\_BEST\_TYPE$, and the source catalog of the redshift is included as $\tt Z\_BEST\_SOURCE$.
+
+For galaxies which have published redshifts from multiple sources, the following algorithm is used to select the $\tt Z\_BEST$ quantity.
+A high quality spectroscopic redshift in the ACS-GC is the primary option, provided in the ACS-GC \citep{gri12}, 3DHST \citep{mom15}, and MUSYC \citep{car10} catalogs and used in that order.
+For galaxies with multiple spectroscopic redshifts, more than 98\% are consistent at $\Delta z<0.001$, and so the order of selection makes no practical difference.
+If no spectroscopic redshifts are available, the 1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST, MUSYC, UltraVISTA;][]{ilb13} and UltraVISTA grism data are used to select the estimated redshift with the smallest error.
 %Table~\ref{tbl:redshifts} shows the results of this selection.
@@
 %\caption{Spectroscopic redshifts from the ACS-GC, 3DHST, and MUSYC catalogs.
-%The number in the upper left of each plot is the percentage of redshifts which
-%agree within $\Delta z < 0.05$ between the two catalogs being compared in each
-%panel. Within this range there is over 98\% agreement in redshifts between all
-%three catalogs.}
+The number in the upper left of each plot is the percentage of redshifts which agree within $\Delta z < 0.05$ between the two catalogs being compared in each panel.
+Within this range there is over 98\% agreement in redshifts between all three catalogs.}
 %\label{fig:speczs}
@@
 %%Survey     Gs        Gp    3ds    3dg     3dp       Ms      Mp       UVp       total
-%AEGIS    & 3,656  & 2,941  & 12  &  515  &  249    & 0     & 0     &  0      & 7,373   & 8,507   \\
+%AEGIS    & 3,656  & 2,941  & 12  &  515  &  249    & 0     & 0     &  0      & 7,373  & 8,507\\
 %COSMOS   & 7,201  & 77,435 & 35  &  358  &  26     & 0     & 0     &  2,665  & 85,020 & 92,808 \\
-%GEMS     & 387    & 628    & 6   &  99   &  40     & 279   & 7,304 & 0       & 8,743   & 9,304   \\
+%GEMS     & 387    & 628    & 6   &  99   &  40     & 279   & 7,304 & 0       & 8,743  & 9,304\\
 %GOODS-N  & 1,947  & 37     & 418 & 1,545 &  1,381  & 0     & 0     & 0       & 5,328  & 12,030 \\
@@
 %\hline
-%Total    & 14,271 & 81,045 & 798 & 3,865 & 1,977   & 1,095 & 8,488 & 2,665   & 114,204 & 184,794 \\
+%Total    & 14,271 & 81,045 & 798 & 3,865 & 1,977   & 1,095 & 8,488 & 2,665   & 114,204 & 184,794\\
 %\enddata
@@
 
-Photometric and spectroscopic data for the SDSS Stripe~82 galaxies were taken
-from the CasJobs DR7 tables. This included $ugriz$ Petrosian magnitudes and
-fluxes, as well as the relative de~Vaucouleurs and exponential fits from the
-model magnitudes. All redshifts used for SDSS galaxies were spectroscopic.
-82.6\% of galaxies in the single-depth images and 65.1\% of galaxies in the
-co-add images had a measured DR7 spectroscopic redshift.
+Photometric and spectroscopic data for the SDSS Stripe~82 galaxies are taken from the CasJobs DR7 tables.
+This includes $ugriz$ Petrosian magnitudes and fluxes, as well as the relative de~Vaucouleurs and exponential fits from the model magnitudes.
+Redshifts used for the SDSS galaxies are all spectroscopic.
+82.6\% of galaxies in the single-depth images and 65.1\% of galaxies in the co-add images have a measured DR7 spectroscopic redshift.
 
@@
 
-Below we describe the classification structure of GZH, including the software 
-interface and the hierarchical structure of a classification. Section \ref{ssec:weighting}
-describes the process of combining individual classifications into vote fractions for each
-galaxy.
+\subsection{User weighting}\label{ssec:weighting}
+The votes of individual volunteers who classified galaxies in GZH are combined to make a vote fraction for each response to a question ($f_{response}$) on the classification tree.
+Votes are weighted slightly \citep[in a method identical to that described in][]{wil13} such that users who frequently disagree with all other users end up having very low weights.
+The user weighting $(w)$ is 1 for the top 95\% of users as ranked by consistency.
+For the bottom 5\% of users, $w$ drops smoothly and is effectively zero for only the bottom 1\% of classifiers in the distribution function.
+Since this only affects a tiny percentage of the users (and an even smaller percentage of the classifications) the overall effect on the GZH dataset is minimal.
+This method is effective, however, at filtering out contributions from randomly classifying or malicious users.
+
+Classifications for a particular user are aggregated and weighted only if they were logged into GZH under their username (which is encouraged, but not required for participation).
+Classifications by users not logged in are marked as ``Anonymous''; no weighting is applied to these classifications, but they are otherwise treated identically in the data processing.
 
@@
 \includegraphics[width=160mm]{figures/gzh_interface.png}
-\caption{Screenshot of the GZH interface (\url{http:/zoo3.galaxyzoo.org}) at
-the beginning of a classification, with the classifier ready to select an answer for
-the first question in the decision tree.\label{fig:interface}}
+\caption{Screenshot of the GZH interface (\url{http:/zoo3.galaxyzoo.org}) at the beginning of a classification, with the user ready to select an answer for the first question in the decision tree.\label{fig:interface}}
 \end{figure*}
 
-Classifications for GZH were made using a web-based interface
-(Figure~\ref{fig:interface}), similar in design to Galaxy~Zoo and Galaxy~Zoo~2.
-The front-end runs on a Ruby~on~Rails framework with classifications stored in
-a MySQL backend. Classifiers were shown a randomly-selected color composite image from
-the GZH sample; the default showed the image with a black sky background,
-although they had the option to invert the color palette if desired. The
-questions and responses for morphology appeared on the right side of the image as
-a panel, including both text and icons. There was no tutorial required for
-participation, although classifiers could access an extensive ``Help'' section
-containing example images and descriptive text for all the morphological
-labels.
+Classifications for GZH are made using a web-based interface (Figure~\ref{fig:interface}), similar in design to Galaxy~Zoo and Galaxy~Zoo~2.
+The front-end runs on a Ruby~on~Rails framework with classifications stored in a MySQL backend.
+Users are shown a randomly-selected color composite image from the GZH sample; the default shows the image with a black sky background, although users have the options to invert the color palette if desired.
+The questions and responses for morphology appear on the right side of the image as a panel, including both text and icons.
+There is no tutorial required for participation, although users can access an extensive ``Help'' section containing example images and descriptive text for all the morphological labels.
 
@@
 \includegraphics[width=\textwidth]{figures/gzh_decision_tree.pdf}
-\caption{Flowchart of the questions presented to GZH classifiers, labeled with
-the corresponding Task numbers. Tasks in the decision tree are color-coded by
-tier level: Gray-colored Tasks are 1$^\mathrm{st}$-tier questions which are
-asked in every classification. Tasks colored green, blue, purple, and pink
-(respectively) are one, two, three, or four steps below branching points in the
-decision tree.}
+\caption{Flowchart of the questions presented to GZH users, labeled with the corresponding Task numbers.
+Tasks in the decision tree are color-coded by tier level: Gray-colored Tasks are 1$^\mathrm{st}$-tier questions which are asked of all users.
+Tasks colored green, blue, purple, and pink (respectively) are one, two, three, or four steps below branching points in the decision tree.}
 \label{fig:decisiontree}
@@
 
-The procedure for classifying an image in GZH followed a hierarchical decision
-tree (Figure~\ref{fig:decisiontree}). Every classification began with the step of
-identifying whether the object at the center of the image was a smooth galaxy,
-a galaxy with a disk or other features, or a star/artifact. Subsequent
-questions in the tree depended on the previous answer(s) given by the classifier; the
-decision tree was designed so that every question relevant to
-the morphology in the process of being identified was answered. Questions that were not
-answered were implicitly assumed to be absent in the image --- for example, if
-the classifier identified a galaxy as being smooth, they were not asked to count the
-number of spiral arms. For every task, the classifier chose a single answer before
-continuing to the next question; they also had the option to restart any
-classification in-progress.
-
-The GZH decision tree had four broad sets of morphologies. The first option
-designated stars or image artifacts (the result of either bad data or incorrect
-classification by the ACS pipeline as a galaxy); in this case, the
-classification process ended and no further questions were asked. The second
-set were smooth galaxies, intended to select ellipticals/early-types;
-classifiers also measured the relative axial ratio (roundness) for these
-galaxies. The third set was for disk/late-type galaxies, which measured the
-features necessary to place a galaxy on the standard Hubble tuning fork (bars,
-spiral arm, strength of the central bulge). The final set, which was new in
-this phase of Galaxy~Zoo and designed for high-redshift targets, identified
-objects dominated by clumpy morphologies. Further annotations for clumpy
-galaxies included assessing the number, arrangement, relative brightness, and
-location of the clumps within the galaxy. Finally, every classification of a
-galaxy gave the option of identifying ``odd'' features within the image; these
-labels were for relatively rare $(\lesssim1\%)$ phenomena, including dust
-lanes, gravitational lenses, and mergers.
-
-The number of independent classifications per subject collected by GZH was on
-average higher than GZ1 or GZ2, due to both the increased complexity of the
-decision tree and the relative difficulty of classifying images of small and
-distant galaxies. Images from the main AEGIS, GEMS, and GOODS data sets had a
-median of 122~independent classifications per image. The remainder of the
-images either had a later activation date (COSMOS, simulated AGN) or a lower
-retirement limit (the low-redshift SDSS Stripe~82 galaxies). Images from these
-samples had a median of 46--48~classifications per image
-(Figure~\ref{fig:classification_hist}).
+The procedure for classifying an image in GZH follows a hierarchical decision tree (Figure~\ref{fig:decisiontree}).
+Every classification begins with the user identifying whether the object at the center of the image is a smooth galaxy, a galaxy with a disk or other features, or a star/artifact.
+Subsequent questions in the tree depend on the previous answer(s) given by the user; the structure of the decision tree is designed so that the user will answer every question relevant to the morphology that they have identified.
+Questions that are not answered are implicitly assumed to be absent in the image --- for example, if the user identifies a galaxy as being smooth, they are not asked to count the number of spiral arms.
+For every task, the user chooses a single answer before continuing to the next question; they have also the option to restart a classification in-progress if a mistake has been made.
+
+The GZH decision tree was designed to remain close to that used by GZ2 while taking account of the likely differences in high redshift systems, and has four broad sets of morphologies classified by the users.
+The first option is designating the object as a star or image artifact (the result of either bad data or incorrect classification by the ACS pipeline as a galaxy); in this case, the classification ends and no further questions are asked.
+The second set are smooth galaxies, intended to select ellipticals/early-types; volunteers also indicate the relative axial ratio (roundness) for these galaxies.
+The third set is for disk/late-type galaxies, which measures the features necessary to place a galaxy on the standard Hubble tuning fork (bars, spiral arm, strength of the central bulge).
+The final set, which is new to the high-redshift targets in GZH, asks users to identify objects dominated by clumpy morphologies.
+Further annotations for these galaxies includes assessing the number, arrangement, relative brightness, and location of the clumps within the galaxy.
+Finally, every classification of a galaxy gives users the option of identifying ``odd'' features within the image; these labels are for relatively rare $(\lesssim1\%)$ phenomena, including dust lanes, gravitational lenses, and mergers.
+
+The number of independent classifications per subject collected by GZH is on average higher than GZ1 or GZ2, due to both the increased complexity of the decision tree and the relative difficulty of classifying images of small and distant galaxies.
+Images from the main AEGIS, GEMS, and GOODS data sets have a median of 122~independent classifications per image.
+The remainder of the images either had a later activation date (COSMOS, simulated AGN) or by a lower retirement limit (the low-redshift SDSS Stripe~82 galaxies).
+Images from these samples have a median of 46--48~classifications per image (Figure~\ref{fig:classification_hist}).
 
@@
 \includegraphics[width=0.5\textwidth]{figures/classification_hist.pdf}
-\caption{Distribution of the total number of classifications per image for GZH,
-split by survey.}
+\caption{Distribution of the total number of classifications per image for GZH, split by survey.}
 \label{fig:classification_hist}
@@
 
-The GZH project was launched on 23~Apr~2010 with the inclusion of the AEGIS,
-GEMS, GOODS 2-epoch, and SDSS Stripe~82 images. Images from COSMOS and the
-simulated AGN were activated in Dec 2010, as well as a small sample of
-images from AEGIS, GEMS, and GOODS that were previously excluded from the original sample
-due to cuts on blended and/or saturated objects and subsequently confirmed as classifiable galaxies. The main GZH
-site collected data until its replacement, the fourth phase of
-Galaxy~Zoo\footnote{\url{http://zoo4.galaxyzoo.org}} (including data from both
-the \hst{} CANDELS survey and SDSS DR8) began on 10~Sep~2012. Classifications
-for the GOODS 5-epoch images were separately obtained from Mar-Jun 2015 on
-the fourth version of the Galaxy~Zoo site. The GZH project had a total of
-10,349,357~classifications from 93,898 registered participants. 
+The GZH project was launched on 23~Apr~2010 with the inclusion of the AEGIS, GEMS, GOODS 2-epoch, and SDSS Stripe~82 images.
+Images from COSMOS and the simulated AGN were activated in Dec 2010, as well as a small sample of AEGIS/GEMS/GOODS images mistakenly excluded from the original sample based on an overly restrictive cut on blended and/or saturated objects.
+The main GZH site collected data until its replacement, the Galaxy~Zoo:~CANDELS project, began on 10~Sep~2012.
+Classifications for the GOODS 5-epoch images were separately obtained with the fourth version of the site\footnote{\url{http://www.galaxyzoo.org}} from Mar-Jun 2015.
+The GZH project had a total of 10,349,357~classifications from 93,898 registered participants.
 % Sum is the total of the GZH SQL table plus the GOODS full-depth imaging in GZ4.
 
-\subsection{Classifier weighting}\label{ssec:weighting}
-
-As a first step to producing consensus classifications of each galaxy, 
-the votes of individual classifiers in GZH were combined to make a vote
-fraction for each response ($f_{response}$) to a question in the classification
-tree. Votes were subsequently weighted and re-combined in an iterative method similar that in 
-previous versions of Galaxy~Zoo \citep{lan08,wil13}, using a method chosen 
-to be as egalitarian as possible while also identifying and downweighting classifiers 
-who frequently disagreed with others. The weighting factor $(w)$ was 1 for the
-top 95\% of classifiers, as ranked by consistency. For the bottom 5\% of
-classifiers, $w$ was designed to drop smoothly and was effectively zero for the
-bottom 1\%.  Since this only affected a tiny percentage of the classifiers (and
-% would be good to quantify "tiny" and "even smaller [than tiny]"
-an even smaller percentage of the classifications) the overall effect on the
-GZH dataset was minimal. The method was effective, however, at filtering out
-contributions from random or deliberately malicious classifiers.
-
-Classifications were aggregated and weighted only if the classifier was logged
-into GZH under their username (which was encouraged, but not required for
-participation). Classifications by participants who were not logged in were marked as
-``Anonymous'' and assumed to have $w = 1$. 
-% We should also try to estimate how many anonymous classifiers there were, if possible.
-
 \section{Correcting for redshift-dependent classification bias}\label{sec:debiasing}
 
-The previous versions of Galaxy Zoo morphology classifications
-\citep{lin08,wil13} were based on observations of galaxies in the Sloan Digital
-Sky Survey (SDSS) which have a median redshift of $z<0.2$. In these cases, it
-was assumed that there was no cosmological evolution of the morphologies of
-galaxies and therefore any observed changes in the distribution of galaxies
-with different consensus morphologies was due to the effects of redshift on the
-image quality (\ie, the reduction in physical resolution, surface brightness
-dimming, etc). For both previous releases of GZ morphologies, a correction for
-redshift-dependent bias was applied based on matching the classification
-fractions at the highest redshifts with those at the lowest redshift.
-\citet{bam09} and \citet{wil13} provide complete descriptions of the process
-for GZ1 and GZ2, respectively.
-
-In the GZH samples, the redshift range is large enough that cosmological
-evolution of the types and morphologies of galaxies is expected for galaxies in
-the sample. As a result, the previous methods of correcting for redshift
-dependent bias do not work. In addition, the effects of band shifting will
-change the images even more across these redshift ranges. 
-%Figure~\ref{fig:exampleFERENGI} illustrates some of the possible effects of
-%losing features in spiral galaxies at high redshift.
-
-In order to test and correct for the effects of redshift, GZH includes a set of
-calibration images. These images consist of the same galaxy as it would appear
-over a variety of redshifts. The input images are from the SDSS
-\citep{yor00,str02} and are processed using the \ferengi{} code \citep{bar08a}
-to match the observational properties of the \hst{} surveys out to $z=1$. These
-images were classified in the GZH interface using the same classification
-scheme as the original \hst{} images.
+The previous versions of Galaxy Zoo morphology classifications \citep{lin08,wil13} were based on observations of galaxies in the Sloan Digital Sky Survey (SDSS) which have a median redshift of $z<0.2$.
+In these cases, it was assumed that there was no cosmological evolution of the morphologies of galaxies and therefore any observed changes in the distribution of galaxies with different consensus morphologies was due to the effects of redshift on the image quality (\ie, the reduction in physical resolution, surface brightness dimming, etc).
+For both previous releases of GZ morphologies, a correction for redshift-dependent bias was applied based on matching the classification fractions at the highest redshifts with those at the lowest redshift.
+\citet{bam09} and \citet{wil13} provide complete descriptions of the process for GZ1 and GZ2, respectively.
+
+In the GZH samples, the redshift range is large enough that cosmological evolution of the types and morphologies of galaxies is expected for galaxies in the sample.
+As a result, the previous methods of correcting for redshift dependent bias do not work.
+In addition, the effects of band shifting will change the images even more across these redshift ranges.
+%Figure~\ref{fig:exampleFERENGI} illustrates some of the possible effects of losing features in spiral galaxies at high redshift.
+
+In order to test and correct for the effects of redshift, GZH includes a set of calibration images.
+These images consist of the same galaxy as it would appear over a variety of redshifts.
+The input images are from the SDSS \citep{yor00,str02} and are processed using the \ferengi{} code \citep{bar08a} to match the observational properties of the \hst{} surveys out to $z=1$.
+These images were classified in the GZH interface using the same classification scheme as the original \hst{} images.
 
@@
 
-The GZH classifications include 288 unique galaxies originally generated from
-SDSS imaging and processed with the \ferengi{} code. The selection spanned a
-variety of galaxy morphologies (as selected by GZ2 classifications) and
-$r^\prime$-band surface brightnesses, and also spanned the redshift range of
-SDSS targets (in $N_z = 4$ bins) in order to be optimized for different target
-minimum redshifts in \hst{} imaging.
+The GZH classifications include 288 unique galaxies originally generated from SDSS imaging and processed with the \ferengi{} code.
+The selection spanned a variety of galaxy morphologies (as selected by GZ2 classifications) and $r^\prime$-band surface brightnesses, and also spanned the redshift range of SDSS targets (in $N_z = 4$ bins) in order to be optimized for different target minimum redshifts in \hst{} imaging.
 
 %The selection criteria for the different morphological categories is summarized in Table \ref{tbl:morphologies}. 
-The surface brightness selection ($N_\mu = 3$) for the \ferengi{} galaxies was
-(1) low: $\mu > 21.5$~\magarc;  (2) mid: $20.5 < \mu < 21.5$~\magarc; and (3)
-high: $\mu < 20.5$~\magarc. For each of the four ``target redshifts''
-($z_\mathrm{sim} = 0.3, 0.5, 0.8$ and $1.0$), the images were redshifted in
-$\Delta z = 0.1$ bins up to $z_\mathrm{sim}=1.0$.
+The surface brightness selection ($N_\mu = 3$) for the \ferengi{} galaxies was (1) low: $\mu > 21.5$~\magarc;  (2) mid: $20.5 < \mu < 21.5$~\magarc; and (3) high: $\mu < 20.5$~\magarc.
+For each of the four ``target redshifts'' ($z_\mathrm{sim} = 0.3, 0.5, 0.8$ and $1.0$), the images were redshifted in $\Delta z = 0.1$ bins up to $z_\mathrm{sim}=1.0$.
 
@@
 
-In addition to the physical parameters of the input images, the \ferengi{}
-output depends on assumptions of the global galaxy evolution model. This
-evolution is a crude mechanism that mimics the brightness increase of galaxies
-with increasing redshift (out to at least $z\sim1-2$). The effect on the
-redshifted images is simply an empirical addition to the magnitude of a galaxy
-of the form $M' = e\times z + M$, where $M'$ is the corrected magnitude, and
-$e$ is the evolutionary correction in magnitudes (i.e., $e=-1$ essentially
-brightens the galaxy by 1~magnitude by $z=1$). \ferengi{} was run on the images
-for values of $e$ starting from $e=0$ and decreasing to $e=-3.5$ in increments
-of $\Delta e = 0.5$. Figure~\ref{fig:exampleFERENGI} shows several examples
-of the effects of ``losing'' spiral/disc features with increasing redshift
-for two galaxies with $e=0$.
-
-The final number of \ferengi{} images produced for each galaxy is ultimately a
-function of galaxy's redshift (since the new images cannot be resampled at
-better angular resolution than the original SDSS data), as well as the number
-of $e$ values selected. Table~\ref{tbl:ferengivalues} summarizes the redshifted
-images produced for GZH.
+In addition to the physical parameters of the input images, the \ferengi{} output depends on assumptions of the global galaxy evolution model.
+This evolution is a crude mechanism that mimics the brightness increase of galaxies with increasing redshift (out to at least $z\sim1-2$).
+The effect on the redshifted images is simply an empirical addition to the magnitude of a galaxy of the form $M' = e\times z + M$, where $M'$ is the corrected magnitude, and $e$ is the evolutionary correction in magnitudes (i.e., $e=-1$ essentially brightens the galaxy by 1~magnitude by $z=1$).
+\ferengi{} was run on the images for values of $e$ starting from $e=0$ and decreasing to $e=-3.5$ in increments of $\Delta e = 0.5$.
+Figure~\ref{fig:exampleFERENGI} shows several examples of the effects of ``losing'' spiral/disc features with increasing redshift for two galaxies with $e=0$.
+
+The final number of \ferengi{} images produced for each galaxy is ultimately a function of galaxy's redshift (since the new images cannot be resampled at better angular resolution than the original SDSS data), as well as the number of $e$ values selected.
+Table~\ref{tbl:ferengivalues} summarizes the redshifted images produced for GZH.
 
@@
 \includegraphics[width=160mm]{figures/example_ferengi.pdf}
-\caption{Examples of two galaxies which have been run through the \ferengi{}
-code to produce simulated \hst{} images. The measured value of \ffeatures{}
-from GZH for the images in each panel are (1) Top row: \ffeatures~= (0.900,
-0.625, 0.350, 0.350, 0.225) and (2) Bottom row: \ffeatures~= (1.000, 0.875,
-0.875, 0.625, 0.375). \label{fig:exampleFERENGI}}
+\caption{Examples of two galaxies which have been run through the \ferengi{} code to produce simulated \hst{} images.
+The measured value of \ffeatures{} from GZH for the images in each panel are (1) Top row: \ffeatures~= (0.900, 0.625, 0.350, 0.350, 0.225) and (2) Bottom row: \ffeatures~= (1.000, 0.875, 0.875, 0.625, 0.375).
+\label{fig:exampleFERENGI}}
 \end{figure*}
@@
 
-The approach used in GZH for correcting the weighted classifications for redshift
-bias rests on the assumption that the \emph{amount} of bias is a function of
-the apparent size and brightness of the image as seen on screen. This is
-controlled by two types of parameters: \textbf{intrinsic} properties of the
-galaxy itself, such as its physical diameter and luminosity, and
-\textbf{extrinsic} properties, such as the distance (redshift) of the galaxy
-and its relative orientation. There may also be other parameters that affect
-classifier accuracy, such as the proximity of close companions \citep[``distraction
-bias''; see][]{joh15} or bias as a function of individual classifier ability and
-skill. The combination of all such parameters forms a high-dimensional space,
-and it is not clear how to separate this into individual effects. Instead, the
-method used here employs only two parameters intended to capture the bulk of
-the change in bias: the $r^\prime$-band surface brightness ($\mu_r$; intrinsic)
-and redshift ($z$; extrinsic).
-
-The change in bias as a function of $\mu_r$ and \zsim{} is measured using the
-\ferengi{} images over all the evolutionary correction factors. It is assumed
-that the ``true'' (ie, debiased) vote fraction $f_{\mu,z}$ for a galaxy can be
-expressed as:
+The approach used in GZH for correcting the weighted classifications for user bias rests on the assumption that the \emph{degree} of bias is a function of the apparent size and brightness of the image as seen on screen.
+This is controlled by two types of parameters: \textbf{intrinsic} properties of the galaxy itself, such as its physical diameter and luminosity, and \textbf{extrinsic} properties, such as the distance (redshift) of the galaxy and its relative orientation.
+There are likely other parameters that affect user accuracy, such as the proximity of close companions \citep[``distraction bias''; see][]{joh15} or bias as a function of individual user ability and skill.
+The combination of all such parameters forms a high-dimensional space, and it is not clear how to separate this into individual effects.
+Instead, the method used here employs only two parameters intended to capture the bulk of the change in bias: the $r^\prime$-band surface brightness ($\mu_r$; intrinsic) and redshift ($z$; extrinsic).
+
+The change in bias as a function of $\mu_r$ and \zsim{} is measured using the \ferengi{} images over all the evolutionary correction factors.
+It is assumed that the ``true'' (ie, debiased) vote fraction $f_{\mu,z}$ for an artificially-redshifted galaxy can be expressed as:
 
@@
 
-\noindent where $f_{\mu,z=0.3}$ is the ``calibrated'' vote fraction at the
-lowest redshift in the \ferengi{} bins ($z=0.3$) and $\zeta$ is a positive
-parameter that controls the rate at which $f$ decreases with increasing
-redshift. This formula fits the data relatively well (with very few exceptions,
-the vote fractions for featured galaxies decrease monotonically with increasing
-redshift), and the exponential function bounds the observed vote fractions
-between $f_{\mu,z=0.3}$ and zero. Figure~\ref{fig:zeta_examples} shows the
-change in vote fraction and the fit to Equation~\ref{eqn:fzeta} for a random
-selection of galaxies in the \ferengi{} images.
+\noindent where $f_{\mu,z=0.3}$ is the ``calibrated'' vote fraction at the lowest redshift in the \ferengi{} bins ($z=0.3$) and $\zeta$ is a positive parameter that controls the rate at which $f$ decreases with increasing redshift.
+This formula fits the data relatively well (with very few exceptions, the vote fractions for featured galaxies decrease monotonically with increasing redshift), and the exponential function bounds the observed vote fractions between $f_{\mu,z=0.3}$ and zero.
+Figure~\ref{fig:zeta_examples} shows the change in vote fraction and the fit to Equation~\ref{eqn:fzeta} for a random selection of galaxies in the \ferengi{} images.
 
@@
 \includegraphics[width=\textwidth]{figures/zeta_examples.pdf}
-\caption{Behavior of the normalized, weighted vote fractions of features
-visible in a galaxy ($f_\textrm{features}$) as a function of redshift in the
-artificial \ferengi{} images. Galaxies in this plot were randomly selected from
-a distribution with $e=0$ and at least three detectable images in redshift bins
-of $z\ge0.3$. Measured vote fractions (red points) are fit with an exponential
-function (Equation~\ref{eqn:fzeta}); the best-fit parameters are given above
-each plot. Error bars are Poissonian, assuming a median of 40~votes per
-galaxy.}
+\caption{Behavior of the normalized, weighted vote fractions of features visible in a galaxy ($f_\textrm{features}$) as a function of redshift in the artificial \ferengi{} images.
+Galaxies in this plot were randomly selected from a distribution with $e=0$ and at least three detectable images in redshift bins of $z\ge0.3$.
+Measured vote fractions (red points) are fit with an exponential function (Equation~\ref{eqn:fzeta}); the best-fit parameters are given above each plot.
+Error bars are Poissonian, assuming a median of 40~votes per galaxy.}
 \label{fig:zeta_examples}
@@
 
-GZH uses the values of $\zeta$ for \emph{all} sets of artificially redshifted
-galaxies to fit the overall distribution as a function of surface brightness,
-since the correction being applied is expected to vary as a function of the
-intrinsic galaxy properties. The galaxies that can be used to measure the
-calibration are restricted to those with a non-zero $f_\textrm{features}$ at
-$z_\mathrm{sim}=0.3$ and with a reasonable fit ($\Delta \chi^2 > 3.0$) to the
-exponential model for the measured change in \ffeatures.
-
-Figure~\ref{fig:zeta_mu} shows the results of fitting the \ferengi{} images
-with Equation~\ref{eqn:fzeta}; the correction is only a weak function of
-surface brightness ($\mu$). Higher-surface brightness galaxies have stronger
-average corrections, likely because these galaxies are more likely to have
-larger $f_\textrm{features}$ values at high redshifts. Low surface brightness
-galaxies are more likely to begin low and remain low; the bounded nature of the
-dropoff (and variance among the individual voters) means that the average
-magnitude of $\zeta$ will be lower.
+GZH uses the values of $\zeta$ for \emph{all} sets of artificially redshifted galaxies to fit the overall distribution as a function of surface brightness, since the correction being applied is expected to vary as a function of the intrinsic galaxy properties.
+The galaxies that can be used to measure the calibration are restricted to those with a non-zero $f_\textrm{features}$ at $z_\mathrm{sim}=0.3$ and with a reasonable fit ($\Delta \chi^2 > 3.0$) to the exponential model for the measured change in \ffeatures.
+
+Figure~\ref{fig:zeta_mu} shows the results of fitting the \ferengi{} images with Equation~\ref{eqn:fzeta}; the correction is only a weak function of surface brightness ($\mu$).
+Higher-surface brightness galaxies have stronger average corrections, likely because these galaxies are more likely to have larger $f_\textrm{features}$ values at high redshifts.
+Low surface brightness galaxies are more likely to begin low and remain low; the bounded nature of the dropoff (and variance among the individual voters) means that the average magnitude of $\zeta$ will be lower.
 
@@
 \includegraphics[width=0.50\textwidth]{figures/zeta_mu.png}
-\caption{All fits for the vote fraction dropoff parameter $\zeta$ for
-\ffeatures{} in the \ferengi{} galaxies as a function of surface
-brightness. This includes only those galaxies with a reasonably bounded range
-on the dropoff ($-10<\log(\zeta)<10$) and sufficient points to fit each
-function (37 original galaxies, each artificially redshifted to create a total
-of 296~images}
+\caption{All fits for the vote fraction dropoff parameter $\zeta$ for $f_\textrm{features}$ in the \ferengi{} galaxies as a function of surface brightness.
+This includes only the 37~galaxies with a reasonably bounded range on the dropoff ($-10<\log(\zeta)<10$) and sufficient points to fit the function.}
 \label{fig:zeta_mu}
@@
 
-\noindent where $\hat\zeta$ is the correction factor applied to each galaxy as
-a function of surface brightness. The best-fit parameters to the linear fit
-(from least-squares optimization) are $\zeta_0=0.1$, $\zeta_1=1.4$. To make the
-final debiased correction, the simple exponential form of
-Equation~\ref{eqn:fzeta} is modified to bound the debiased vote fractions
-between $f$ and 1:
+\noindent where $\hat\zeta$ is the correction factor applied to each galaxy as a function of surface brightness.
+The best-fit parameters to the linear fit (from least-squares optimization) are $\zeta_0=0.1$, $\zeta_1=1.4$.
+To make the final debiased correction, the simple exponential form of Equation~\ref{eqn:fzeta} is modified to bound the debiased vote fractions between $f$ and 1:
 
@@
 \includegraphics[width=0.5\textwidth]{figures/eye_of_sauron.pdf}
-\caption{Surface brightness as a function of redshift for 3,950~\ferengi{}
-images and the 102,548~galaxies in the ACS sample with measured $\mu$ and $z$
-values. The color histogram shows the number of \ferengi{} images as a function
-of $\mu$ and $z_{\rm sim}$. White contours show counts for the full ACS sample,
-with contours starting at $N=1000$ and separated by intervals of 1000 up to
-7000.} 
+\caption{Surface brightness as a function of redshift for 3,950~\ferengi{} images and the 102,548~galaxies in the ACS sample with measured $\mu$ and $z$ values.
+The color histogram shows the number of \ferengi{} images as a function of $\mu$ and $z_{\rm sim}$.
+White contours show counts for the full ACS sample, with contours starting at $N=1000$ and separated by intervals of 1000 up to 7000.}
 \label{fig:sb_redshift}
@@
 \caption{Effects of redshift bias in 3,950 images in the \ferengi{} sample.
-[a]: Each point in a given redshift and surface brightness bin represents a
-unique galaxy. On the $y$-axis in each bin is the \ffeatures{} value of the
-image of that galaxy redshifted to the value corresponding to that redshift
-bin. On the $x$-axis is the \ffeatures{} value of the image of the same galaxy
-redshifted to $z=0.3$. The dashed black lines represent the best-fit
-polynomials to the data in each square. The solid black line represents
-\ffeaturesz=\ffeaturesrest. Regions in which there is a single-valued
-relationship between \ffeatures{} at high redshift and at $z=0.3$ are white;
-those in which there is not are blue, and those with not enough data ($N<5$)
-are gray. [b]: A larger version of the dark-outlined square in [a], containing
-\ferengi{} galaxies that have been artificially redshifted to $z=1.0$ and have
-surface brightnesses between $20.3 < \mu < 21.0$ $\rm (mag/arcsec^2)$. [c]: The
-same data as [a] is shown. Each $z,\mu$ bin is divided into 4 sub-bins to
-determine the range of intrinsic \ffeaturesrest{} for a given range of observed
-\ffeaturesz{} values. In each sub-bin, the orange bars represent the inner
-80$^\mathrm{th}$ percentiles of the data, the boundaries of which are the lower
-and upper limits of the debiased values. [d]: The same data as [b], but
-highlighting the upper and lower limit regions.}
+[a]: Each point in a given redshift and surface brightness bin represents a unique galaxy.
+On the $y$-axis in each bin is the \ffeatures{} value of the image of that galaxy redshifted to the value corresponding to that redshift bin.
+On the $x$-axis is the \ffeatures{} value of the image of the same galaxy redshifted to $z=0.3$.
+The dashed black lines represent the best-fit polynomials to the data in each square.
+The solid black line represents \ffeaturesz=\ffeaturesrest.
+Regions in which there is a single-valued relationship between \ffeatures{} at high redshift and at $z=0.3$ are white; those in which there is not are blue, and those with not enough data ($N<5$) are gray.
+[b]: A larger version of the dark-outlined square in [a], containing \ferengi{} galaxies that have been artificially redshifted to $z=1.0$ and have surface brightnesses between $20.3 < \mu < 21.0$ $\rm (mag/arcsec^2)$.
+[c]: The same data as [a] is shown.
+Each $z,\mu$ bin is divided into 4 sub-bins to determine the range of intrinsic \ffeaturesrest{} for a given range of observed \ffeaturesz{} values.
+In each sub-bin, the orange bars represent the inner 80$^\mathrm{th}$ percentiles of the data, the boundaries of which are the lower and upper limits of the debiased values.
+[d]: The same data as [b], but highlighting the upper and lower limit regions.}
 \label{fig:f_vs_f}
@@
 
-Figure~\ref{fig:f_vs_f} shows the change in \ffeatures{} for the \ferengi{}
-galaxies relative to their lowest simulated redshift. In this analysis, only
-galaxies whose lowest simulated redshift image was $z_\mathrm{sim}=0.3$ were
-used (see Table \ref{tbl:ferengivalues}), and only those which had detectable
-surface brightness measurements in \sextractor; this includes 3,950 of the
-total 6,466 images. For each simulated redshift value \zsim{} at a fixed
-surface brightness $\mu$, \ffeaturesz, the value measured at that simulated
-redshift, is plotted against \ffeaturesrest, the value measured for the same
-galaxy at \zsim$=0.3$.
-
-The objective is to use these data to predict, for a galaxy with a measured
-\ffeaturesz{} value, what its \ffeatures{} value \emph{would have been} if it
-had been viewed at $z=0.3$. This predicted value is defined as the debiased
-vote fraction \ffeaturesdebiased, and is calculated by applying a correction to
-the measured value of \ffeatures, determined by the $\zeta$ function described
-in the previous section. A reliable predicted value can be obtained so long as
-the relationship between \ffeaturesz{} and \ffeaturesrest{} is single-valued;
-that is, for a given \ffeaturesz, there is exactly one corresponding value of
-\ffeatures{} at $z=0.3$.
-
-Figure~\ref{fig:f_vs_f} shows that the relationship between \ffeaturesz{} and
-\ffeaturesrest{} is \emph{not} always single valued; hence, it is not
-appropriate to correct galaxies that lie in certain regions of surface
-brightness/redshift/\ffeatures{} space. These regions tend to have low
-\ffeatures{} values at high redshift, but a wide range of values at $z=0.3$.
-These regions contain two morphological types of galaxies: the first set are
-genuine ellipticals, which have low values of \ffeatures{} at both high and low
-redshift. The second group are disks whose features become indistinct at high
-redshift; hence their \ffeatures{} value at $z=0.3$ may be quite high, while
-the value observed at high redshift is very low. This effect is strongest at
-high $z$ and low $\mu$, where features become nearly impossible to discern in
-the images.
-
-The criteria for determining whether a region of this space is single-valued,
-and therefore correctable, is as follows: In each surface brightness and
-redshift bin, the relationship between \ffeaturesz{} and \ffeaturesrest{} is
-modeled by fitting the data with a polynomial of degrees $n=3$, 2, and 1, and
-using the best formal fit out of the three as measured by the sum of the
-residuals. These fits are shown as the dashed black lines in
-Figure~\ref{fig:6a}. Any flat regions of the polynomial fits are areas in which
-there is not a clear single-valued relationship between \ffeaturesz{} and
-\ffeaturesrest; this is quantified by setting a minimum slope cut of 0.4. Any
-data in which the polynomial fit has a slope less than this value is considered
-\emph{not} one-to-one, and therefore \ffeaturesz{} cannot be boosted to its
-\ffeaturesrest{} value.  Galaxies in this region are referred to as the
-\emph{lower limit} sample, because the most stringent correction available is
-that the weighted \ffeatures{} is a lower limit to the true value.  These
-regions are highlighted in blue in Figure~\ref{fig:6a}. Uncolored (white)
-regions of the plot have sufficiently high slopes to consider the relationship
-as single-valued; galaxies in these regions are considered ``correctable'', and
-only these are used in measuring the parameters for the $\zeta$ function
-(Section~\ref{ssec:zeta}). Only surface brightness/redshift bins with at least
-5 galaxies were considered; regions with fewer than 5 galaxies are considered
-to have ``not enough information'' to determine the \ffeaturesz{} and
-\ffeaturesrest{} relationship, colored gray in Figure~\ref{fig:6a}.
-
-The unshaded regions in Figure~\ref{fig:6a} define discrete ranges of redshift,
-surface brightness, and \ffeatures{} a galaxy must have in order for the
-debiased correction to be confidently applied to a galaxy in the GZH sample.
-While the appropriate correctable regions were defined discretely, the true
-correctable region is assumed to be a smooth function of $z$, $\mu$, and
-\ffeatures{}. To define this smooth space, we calculate the shape of the convex
-hull that encloses the correctable and lower-limit \ferengi{} galaxies in
-$z$-$\mu$-\ffeatures{} space. The boundaries are then adjusted until the
-contamination from both groups is minimized. The resulting hulls define the
-correctable and lower-limit regions for categorizing the \hst{} galaxies. The
-results of this method and final categorization of the \hst{} sample are in
-Table~\ref{tbl:hubble_debiasable}. Of the galaxies at redshift higher than
-$z=0.3$, 17\% can be debiased using the $\zeta$ method, 27\% cannot be
-debiased, and 56\% cannot have the potential for a correction determined, due
-either to an unknown redshift or insufficient \ferengi{} images corresponding
-to the relevant $z$-$\mu$ values.
-
-For the ``lower-limit'' galaxies for which a single debiased \ffeatures{} value
-cannot be confidently assigned, the \emph{range} of debiased values is
-estimated using a method visualized in Figure~\ref{fig:6c}. This uses the
-\ferengi{} simulated data to analyze the range of intrinsic \ffeaturesrest{}
-values for any given observed \ffeatures{} value, again as a function of
-surface brightness and redshift. Each $z$,$\mu$ bin, shows the spread of
-intrinsic values of \ffeaturesrest{} for four ranges of observed \ffeatures.
-The range of intrinsic values is defined as the inner 80\% of the data,
-represented by the orange bars in Figure~\ref{fig:6c}. For any galaxy which
-cannot be directly debiased by the $\zeta$ method, these ranges are used to
-denote the upper and lower limits on the expected values \ffeaturesrest{} as a
-function of the observed \ffeatures.
+Figure~\ref{fig:f_vs_f} shows the change in \ffeatures{} for the \ferengi{} galaxies relative to their lowest simulated redshift.
+In this analysis, only galaxies whose lowest simulated redshift image was $z_\mathrm{sim}=0.3$ were used (see Table \ref{tbl:ferengivalues}), and only those which had detectable surface brightness measurements in \sextractor; this includes 3,950 of the total 6,466 images.
+For each simulated redshift value \zsim{} at a fixed surface brightness $\mu$, \ffeaturesz, the value measured at that simulated redshift, is plotted against \ffeaturesrest, the value measured for the same galaxy at \zsim$=0.3$.
+
+The objective is to use these data to predict, for a galaxy with a measured \ffeaturesz{} value, what its \ffeatures{} value \emph{would have been} if it had been viewed at $z=0.3$.
+This predicted value is defined as the debiased vote fraction \ffeaturesdebiased, and is calculated by applying a correction to the measured value of \ffeatures, determined by the $\zeta$ function described in the previous section.
+A reliable predicted value can be obtained so long as the relationship between \ffeaturesz{} and \ffeaturesrest{} is single-valued; that is, for a given \ffeaturesz, there is exactly one corresponding value of \ffeatures{} at $z=0.3$.
+
+Figure~\ref{fig:f_vs_f} shows that the relationship between \ffeaturesz{} and \ffeaturesrest{} is \emph{not} always single valued; hence, it is not appropriate to correct galaxies that lie in certain regions of surface brightness/redshift/\ffeatures{} space.
+These regions tend to have low \ffeatures{} values at high redshift, but a wide range of values at $z=0.3$.
+These regions contain two morphological types of galaxies: the first set are genuine ellipticals, which have low values of \ffeatures{} at both high and low redshift.
+The second group are disks whose features become indistinct at high redshift; hence their \ffeatures{} value at $z=0.3$ may be quite high, while the value observed at high redshift is very low.
+This effect is strongest at high $z$ and low $\mu$, where features become nearly impossible to discern in the images.
+
+The criteria for determining whether a region of this space is single-valued, and therefore correctable, is as follows: In each surface brightness and redshift bin, the relationship between \ffeaturesz{} and \ffeaturesrest{} is modeled by fitting the data with a polynomial of degrees $n=3$, 2, and 1, and using the best formal fit out of the three as measured by the sum of the residuals.
+These fits are shown as the dashed black lines in Figure~\ref{fig:6a}.
+Any flat regions of the polynomial fits are areas in which there is not a clear single-valued relationship between \ffeaturesz{} and \ffeaturesrest; this is quantified by setting a minimum slope cut of 0.4.
+Any data in which the polynomial fit has a slope less than this value is considered \emph{not} one-to-one, and therefore \ffeaturesz{} cannot be boosted to its \ffeaturesrest{} value.
+Galaxies in this region are referred to as the \emph{lower limit} sample.
+These regions are highlighted in blue in Figure~\ref{fig:6a}.
+Uncolored (white) regions of the plot have sufficiently high slopes to consider the relationship as single-valued; galaxies in these regions are considered ``correctable'', and only these are used in measuring the parameters for the $\zeta$ function (Section~\ref{ssec:zeta}).
+Only surface brightness/redshift bins with at least 5 galaxies were considered; regions with fewer than 5 galaxies are considered to have ``not enough information'' to determine the \ffeaturesz{} and \ffeaturesrest{} relationship, colored gray in Figure~\ref{fig:6a}.
+
+The unshaded regions in Figure~\ref{fig:6a} define discrete ranges of redshift, surface brightness, and \ffeatures{} a galaxy must have in order for the debiased correction to be confidently applied to a galaxy in the GZH sample.
+While the appropriate correctable regions were defined discretely, the true correctable region is assumed to be a smooth function of $z$, $\mu$, and \ffeatures{}.
+To define this smooth space, we calculate the shape of the convex hull that encloses the correctable and lower-limit \ferengi{} galaxies in $z$-$\mu$-\ffeatures{} space.
+The boundaries are then adjusted until the contamination from both groups is minimized.
+The resulting hulls define the correctable and lower-limit regions for categorizing the \hst{} galaxies.
+The results of this method and final categorization of the \hst{} sample are in Table~\ref{tbl:hubble_debiasable}.
+Of the galaxies at redshift higher than $z=0.3$, 17\% can be debiased using the $\zeta$ method, 27\% cannot be debiased, and 56\% cannot have the potential for a correction determined, due either to an unknown redshift or insufficient \ferengi{} images corresponding to the relevant $z$-$\mu$ values.
+
+For the ``lower-limit'' galaxies for which a single debiased \ffeatures{} value cannot be confidently assigned, the \emph{range} of debiased values is estimated using a method visualized in Figure~\ref{fig:6c}.
+This uses the \ferengi{} simulated data to analyze the range of intrinsic \ffeaturesrest{} values for any given observed \ffeatures{} value, again as a function of surface brightness and redshift.
+Each $z$,$\mu$ bin, shows the spread of intrinsic values of \ffeaturesrest{} for four ranges of observed \ffeatures.
+The range of intrinsic values is defined as the inner 80\% of the data, represented by the orange bars in Figure~\ref{fig:6c}.
+For any galaxy which cannot be directly debiased by the $\zeta$ method, these ranges are used to denote the upper and lower limits on the expected values \ffeaturesrest{} as a function of the observed \ffeatures.
 
@@
 \caption{Distribution of \ferengi{} images analyzed in Figure~\ref{fig:f_vs_f}.
-Correctable images have a single-valued relationship between their measured
-\ffeatures{} values at high and low redshifts (white regions in
-Figure~\ref{fig:f_vs_f}). Images with only a lower-limit on \ffeatures{} have a
-non single-valued relationship (blue regions). NEI (``not enough information'')
-images have undetermined relationships due to a lack of data ($N<5$) in their
-corresponding $z$-$\mu$ bins (gray regions).\label{tbl:ferengi_corrections}}
+Correctable images have a single-valued relationship between their measured \ffeatures{} values at high and low redshifts (white regions in Figure~\ref{fig:f_vs_f}).
+Images with only a lower-limit on \ffeatures{} have a non single-valued relationship (blue regions).
+NEI (``not enough information'') images have undetermined relationships due to a lack of data ($N<5$) in their corresponding $z$-$\mu$ bins (gray regions).\label{tbl:ferengi_corrections}}
 \begin{tabular}{lrr}
@@
 
-Few galaxies in the sample have sufficiently high corrections to completely
-change them from being confidently smooth to featured following the bias
-correction (Figure~\ref{fig:debiased_corrections}). As a check, highly boosted
-galaxies are compared to the expert classifications in CANDELS \citep{kar15}.
-There are only eight galaxies that were strongly boosted (\ffeatures$<0.2$ and
-\fbest$>0.5$) in GZH and also appears in the CANDELS expert sample. Of those
-eight galaxies, \citet{kar15} classify 5 as spheroids, 2 as disks, and 1 as
-irregular/disky. The \fbest{} values for GZH are all between 0.5 and 0.6,
-making them intermediate disk candidates. One of the spheroids has a hint of
-extended emission to the south that may have been missed by the CANDELS
-experts, but almost all images are dim and with very low surface brightnesses
-in the ACS imaging, making positive identification challenging. Since the
-surveys use different rest-frame filters and the overlap sample is tiny,
-though, detailed comparisons between the overall morphologies are highly
-difficult.
+Few galaxies in the sample have sufficiently high corrections to completely change them from being confidently smooth to featured following the bias correction (Figure~\ref{fig:debiased_corrections}).
+As a check, highly boosted galaxies are compared to the expert classifications in CANDELS \citep{kar15}.
+There are only eight galaxies that were strongly boosted (\ffeatures$<0.2$ and \fbest$>0.5$) in GZH and also appears in the CANDELS expert sample.
+Of those eight galaxies, \citet{kar15} classify 5 as spheroids, 2 as disks, and 1 as irregular/disky.
+The \fbest{} values for GZH are all between 0.5 and 0.6, making them intermediate disk candidates.
+One of the spheroids has a hint of extended emission to the south that may have been missed by the CANDELS experts, but almost all images are dim and with very low surface brightnesses in the ACS imaging, making positive identification challenging.
+Since the surveys use different rest-frame filters and the overlap sample is tiny, though, detailed comparisons between the overall morphologies are highly difficult.
 
@@
 \includegraphics[width=\textwidth]{figures/debiased_corrections.pdf}
-\caption{Debiased \ffeatures{} corrected to $z=0.3$ vs weighted \ffeatures{}
-for the correctable (left), lower-limit (middle), and NEI (right) galaxies in
-    the GZH sample.}
+\caption{Debiased \ffeatures{} corrected to $z=0.3$ vs weighted \ffeatures{} for the correctable (left), lower-limit (middle), and NEI (right) galaxies in the GZH sample.}
 \label{fig:debiased_corrections}
@@
 
-\subsection{Challenges of debiasing questions beyond ``smooth or features''}\label{ssec:higher_order_tasks}
-
-As with the HST images, each \ferengi{} subject had a varying number of classifiers
-answering the various questions in the hierarchical decision tree. Every classifier
-answers the first question, {\it ``Is the galaxy smooth and rounded, with no
-sign of a disk?''}; as such the vote fractions \fsmooth, \ffeatures, and
-\fartifact{} are all computed with the minimum statistical error for any
-question, with between 40 and 140~responses (see Section~\ref{sec:interface}).
-The number of participants answering subsequent questions, however, is always equal
-to or less than the number who answered the preceding question. The average number
-of responses per task for fourth- or fifth-tier questions such as spiral arm
-structure (Tasks 12--14) is only $4\pm4$ for the \ferengi{} sample; while this
-is distribution is strongly bimodal (reflecting the true morphologies of
-selected galaxies), the very low absolute numbers of votes introduce very high
-variance when attempting to calculate a statistical correction.
-
-In the \ferengi{} data, these numbers severely limit the amount of information
-that can be extracted for the higher-tier questions. The debiasing technique
-used (Section~\ref{ssec:zeta}) requires that at least 10~classifiers answer each
-question for a galaxy with $z_\mathrm{sim}=0.3$ \emph{and} the corresponding
-image at higher redshift. This requirement is (by default) met by all galaxies
-for the smooth/features question. However, this is often \emph{not} met for
-questions beyond Task~01; on average. $60\%\pm24\%$ of the galaxies do not have
-sufficient data to measure a correction, as compared to 2.0\% achieved for
-Task~01 (Table~\ref{tbl:ferengi_corrections}). Of the remaining
-\ferengi{} galaxies which did meet this requirement, polynomials were fit to
-the data in each redshift-surface brightness bin, as was done for Task~01. The
-goodness-of-fit was evaluated in each bin, for each Task, using a normalized
-$\chi^2$ metric. The mean $\chi^2$ for all higher-order tasks was
-$0.10\pm0.04$, significantly larger than the Task~01 value of $0.04$. Based on
-this statistic, the data cannot not be modeled with sufficient confidence for
-the higher order tasks. An example of the debiasing technique applied to
-\fbar{} is shown in Section~\ref{sec:ferengi_bar}; visual inspection of
-Figure~\ref{fig:f_vs_fbar} confirms that the points in each bin are scattered
-to a degree at which no strong correlation is present.  For these reasons,
-debiased vote fractions are only offered in the GZH catalog for Task~01
-(smooth/features).
+\subsection{Challenges of debiasing questions beyond ``smooth or features''}
+\label{ssec:higher_order_tasks}
+As with the HST images, each \ferengi{} subject has a varying number of users answering the various questions in the hierarchical decision tree.
+Every user answers the first question, {\it ``Is the galaxy smooth and rounded, with no sign of a disk?''}; as such the vote fractions \fsmooth, \ffeatures, and \fartifact{} are all computed with the minimum statistical error for any question, with between 40 and 140~responses (see Section~\ref{sec:interface}).
+The number of users to answer any subsequent question, however, is always equal to or less than the number to answer the preceding question.
+The average number of responses per task for fourth- or fifth-tier questions such as spiral arm structure (Tasks 12--14) is only $4\pm4$ for the \ferengi{} sample; while this distribution is strongly bimodal (reflecting the true morphologies of selected galaxies), the very low absolute numbers of votes introduce very high variance when attempting to calculate a statistical correction.
+
+In the \ferengi{} data, these numbers severely limit the amount of information that can be extracted for the higher-tier questions.
+The debiasing technique used (Section~\ref{ssec:zeta}) requires that at least 10~users answer each question for a galaxy with $z_\mathrm{sim}=0.3$ \emph{and} the corresponding image at higher redshift.
+This requirement is (by default) met by all galaxies for the smooth/features question.
+However, this is often \emph{not} met for questions beyond Task~01; on average.
+$60\%\pm24\%$ of the galaxies do not have sufficient data to measure a correction, as compared to 2.0\% achieved for Task~01 (Table~\ref{tbl:ferengi_corrections}).
+Of the remaining \ferengi{} galaxies which did meet this requirement, polynomials were fit to the data in each redshift-surface brightness bin, as was done for Task~01.
+The goodness-of-fit was evaluated in each bin, for each Task, using a normalized $\chi^2$ metric.
+The mean $\chi^2$ for all higher-order tasks was $0.10\pm0.04$, significantly larger than the Task~01 value of $0.04$.
+Based on this statistic, the data cannot not be modeled with sufficient confidence for the higher order tasks.
+An example of the debiasing technique applied to \fbar{} is shown in Section~\ref{sec:ferengi_bar}; visual inspection of Figure~\ref{fig:f_vs_fbar} confirms that the points in each bin are scattered to a degree at which no strong correlation is present.
+For these reasons, debiased vote fractions are only offered in the GZH catalog for Task~01 (smooth/features).
 
@@
 %\includegraphics[width=\textwidth]{figures/hubble_z_mu_p_distributions.pdf}
-%\caption{Distributions of redshift, surface brightness, and \ffeatures{} for
-%correctable (purple), lower-limit (green), and NEI (pink) galaxies in the full
-%GZH sample. The lower-limit galaxies have higher redshifts, slightly lower
-%surface brightness, and lower values of \ffeatures{} on average than the
-%correctable galaxies. The long tail of NEI galaxies in redshift and surface
-%brightness demonstrates the limits of the \ferengi{} sample, for which there
-%is no data at $z>1$ or $\mu>24$.}
+%\caption{Distributions of redshift, surface brightness, and \ffeatures{} for correctable (purple), lower-limit (green), and NEI (pink) galaxies in the full GZH sample.
+The lower-limit galaxies have higher redshifts, slightly lower surface brightness, and lower values of \ffeatures{} on average than the correctable galaxies.
+The long tail of NEI galaxies in redshift and surface brightness demonstrates the limits of the \ferengi{} sample, for which there is no data at $z>1$ or $\mu>24$.}
 %\label{fig:z_mu_p}
@@
 %
-%We show here the preliminary results of GZH classifications of images of
-%galaxies placed at artificial redshifts. Figure~\ref{fig:ferengi_results_fake}
-%shows the range of change of vote fractions for the change of \ffeatures{}
-%with redshift, for galaxies with different vote fraction levels, three ranges
-%of surface-brightness levels and 7~evolutionary corrections (this last bit is
-%indicated by the color). 
+%We show here the preliminary results of GZH classifications of images of galaxies placed at artificial redshifts.
+Figure~\ref{fig:ferengi_results_fake} shows the range of change of vote fractions for the change of \ffeatures{} with redshift, for galaxies with different vote fraction levels, three ranges of surface-brightness levels and 7~evolutionary corrections (this last bit is indicated by the color).
 %
-%%---------------------------------------------------------------------------
+%%-----------------------------------------------------------------------------------------------------------------------------------
 %\begin{figure}
@@
 %
-%\caption{Preliminary results of the \ferengi{} redshifting exercise. WARNING
-%NO USER WEIGHTING.... For a range of vote fraction levels with three
-%surface-brightness levels and 7 evolutionary corrections each (the colors
-%indicate evolutionary correction value with green being $e=0$, we show the
-%range of evolution of the vote fractions for featured vs. smooth with
-%redshift.}
+%\caption{Preliminary results of the \ferengi{} redshifting exercise.
+WARNING NO USER WEIGHTING....
+For a range of vote fraction levels with three surface-brightness levels and 7 evolutionary corrections each (the colors indicate evolutionary correction value with green being $e=0$, we show the range of evolution of the vote fractions for featured vs.
+smooth with redshift.}
 %
@@
 %\end{figure}
-%%--------------------------------------------------------------------------
+%%-----------------------------------------------------------------------------------------------------------------------------------
 
@@
 
-The data release for GZH includes morphological data for 181,101~images
-(generated from a total of 150,771~unique galaxies). The full table can be
-accessed at \url{http://data.galaxyzoo.org}. The online data also includes a
-secondary metadata table, which is drawn from a variety of sources detailed in
-Section \ref{sec:data}.
-
-Each image is listed under a unique project ID (eg,~AHZ000001); the actual
-galaxy in the image is identified by the combination of the OBJNO and original
-survey. For each of the 55~responses in the GZH decision tree, the following
-classification data is provided: for each question, $\tt N_{votes}$ is the
-number of classifiers who answered that question. For each unique answer, $\tt fraction$
-is the fraction of classifiers who selected that answer ($\rm N_{answer}/N_{votes}$, and
-$\tt weighted$ is the weighted fraction, which takes into account overall
-consistency (Section~\ref{ssec:weighting}).
+The data release for GZH includes morphological data for 181,101~images (generated from a total of 150,771~unique galaxies).
+The full table can be accessed at \url{http://data.galaxyzoo.org}.
+The online data also includes a secondary metadata table, which is drawn from a variety of sources detailed in Section \ref{sec:data}.
+
+Each image is listed under a unique project ID (eg,~AHZ000001); the actual galaxy in the image is identified by the combination of the OBJNO and original survey.
+For each of the 55~responses in the GZH decision tree, the following classification data is provided: for each question, $\tt N_{votes}$ is the number of users to answer that question.
+For each unique answer, $\tt fraction$ is the fraction of users to select that answer ($\rm N_{answer}/N_{votes}$, and $\tt weighted$ is the weighted fraction, which takes into account user consistency (Section~\ref{ssec:weighting}).
 
 The GZH vote fractions can be largely dependent on the resolution of the image.
-Two otherwise morphologically identical galaxies which differ significantly in
-redshift, brightness, or size may result in very different vote fractions for
-any given question, given that many features of a galaxy are difficult to
-discern in less-resolved images (bars, spiral arms, disk structure, etc). For
-this reason, caution must be used when taking vote fractions as cut-offs to
-determine morphological structure; guidelines for careful classification are
-given in Section~\ref{sec:cookbook}.
-
-The GZH catalog is corrected for classification bias only for the first
-question of the GZH decision tree (Section~\ref{sec:debiasing}), which asks
-{\it ``Is the galaxy smooth and round, with no sign of a disk?''} For this
-question, the catalog provides the additional parameters $\tt debiased$, $\tt
-lower~limit$, $\tt upper~limit$, and $\tt best$ vote fractions. The $\tt best$
-fraction for \ffeatures{} is chosen based on the categorization of the galaxy:
-if it is ``correctable'', $\tt best = debiased$; if it is a lower limit, 
-$\tt best = lower~limit$; if neither condition applies, then 
-$\tt best = weighted$.
-
-The debiased and best vote fractions for \fsmooth{} are calculated on the
-criteria that vote fractions for all answers must sum to unity:
+Two otherwise morphologically identical galaxies which differ significantly in redshift, brightness, or size may result in very different vote fractions for any given question, given that many features of a galaxy are difficult to discern in less-resolved images (bars, spiral arms, disk structure, etc).
+For this reason, caution must be used when taking vote fractions as cut-offs to determine morphological structure; guidelines for careful classification are given in Section~\ref{sec:cookbook}.
+
+The GZH catalog is corrected for classification bias only for the first question of the GZH decision tree (Section~\ref{sec:debiasing}), which asks {\it ``Is the galaxy smooth and round, with no sign of a disk?''} For this question, the catalog provides the additional parameters $\tt debiased$, $\tt lower~limit$, $\tt upper~limit$, and $\tt best$ vote fractions.
+The $\tt best$ fraction for \ffeatures{} is chosen based on the categorization of the galaxy: if it is ``correctable'', $\tt best = debiased$; if it is a lower limit, $\tt best = lower~limit$; if neither condition applies, then $\tt best = weighted$.
+
+The debiased and best vote fractions for \fsmooth{} are calculated on the criteria that vote fractions for all answers must sum to unity:
 
@@
 
-\noindent In rare cases ($<1\%$ of the sample), this requirement resulted in
-negative vote fractions for \fsmooth; these were cases in which the
-\ffeatures{} vote fraction was boosted to a high value relative to \fartifact.
-In these cases, the constraint of Equation~\ref{eqn:constraint} is met by
-setting \fsmooth$=0.0$ and decreasing \fbest{} accordingly. This correction is
-typically small, with a median decrease/increase of
-$f_\mathrm{features}/f_\mathrm{smooth}$ of $\Delta f = 0.04$.
+\noindent In rare cases ($<1\%$ of the sample), this requirement resulted in negative vote fractions for \fsmooth; these were cases in which the \ffeatures{} vote fraction was boosted to a high value relative to \fartifact.
+In these cases, the constraint of Equation~\ref{eqn:constraint} is met by setting \fsmooth$=0.0$ and decreasing \fbest{} accordingly.
+This correction is typically small, with a median decrease/increase of $f_\mathrm{features}/f_\mathrm{smooth}$ of $\Delta f = 0.04$.
 
 Data products for GZH are split by the type of image being classified.
-Table~\ref{tbl:catalog_hst} contains the classifications for the \hst{} images
-from the AEGIS, COSMOS, and GEMS surveys, as well as 5-epoch deep imaging from
-the GOODS-N and GOODS-S surveys. This contains 118,425~galaxies and is the
-primary output from the GZH project. The next two tables have data for a small
-subset of 3,927~COSMOS~images that were re-processed to study the effect of
-color balance on morphological classification. Table~\ref{tbl:catalog_faded}
-has images that are desaturated to minimize the color contrast;
-Table~\ref{tbl:catalog_recolored} has images with the red and blue color
-channels inverted. Table~\ref{tbl:catalog_goods_shallow} contains data for
-6,144~galaxies with 2-epoch images from GOODS. These have been mostly
-supplanted in the main table with deeper 5-epoch GOODS imaging; however, there
-are 1,683~galaxies in the shallower imaging that were not classified in the
-deeper mosaics. This data can also be compared to the counterparts in
-Table~\ref{tbl:catalog_hst} to study the effect of depth on morphological
-classification. Tables~\ref{tbl:stripe82_single} and \ref{tbl:stripe82_coadd}
-contain data for the SDSS Stripe~82 single-depth and co-added images,
-respectively, that were classified using the GZH interface and decision tree.
-Finally, Table~\ref{tbl:simulated_agn} contains classifications for images with
-artificial point sources intended to simulate the effect of a bright AGN (see
-\citealt{sim14} for an example).
+Table~\ref{tbl:catalog_hst} contains the classifications for the \hst{} images from the AEGIS, COSMOS, and GEMS surveys, as well as 5-epoch deep imaging from the GOODS-N and GOODS-S surveys.
+This contains 118,425~galaxies and is the primary output from the GZH project.
+The next two tables have data for a small subset of 3,927~COSMOS~images that were re-processed to study the effect of color balance on morphological classification.
+Table~\ref{tbl:catalog_faded} has images that are desaturated to minimize the color contrast; Table~\ref{tbl:catalog_recolored} has images with the red and blue color channels inverted.
+Table~\ref{tbl:catalog_goods_shallow} contains data for 6,144~galaxies with 2-epoch images from GOODS.
+These have been mostly supplanted in the main table with deeper 5-epoch GOODS imaging; however, there are 1,683~galaxies in the shallower imaging that were not classified in the deeper mosaics.
+This data can also be compared to the counterparts in Table~\ref{tbl:catalog_hst} to study the effect of depth on morphological classification.
+Tables~\ref{tbl:stripe82_single} and \ref{tbl:stripe82_coadd} contain data for the SDSS Stripe~82 single-depth and co-added images, respectively, that were classified using the GZH interface and decision tree.
+Finally, Table~\ref{tbl:simulated_agn} contains classifications for images with artificial point sources intended to simulate the effect of a bright AGN (see \citealt{sim14} for an example).
 
@@
 \enddata
-\tablenotetext{1}{Flag indicating how the vote fractions for this galaxy were
-corrected through debiasing (Section~\ref{ssec:zeta_results}), if possible.
-0~=~correctable, 1~=~lower-limit ($f_{raw}$ --- $f_{adj}$ is not
-single-valued), 2~=~uncorrected ($z_{\rm gal} < 0.3$), 3~=~uncorrected
-(insufficient \ferengi{} galaxies in this $z$-$\mu$ bin), 4~=~uncorrected (no
-galaxy redshift available).}
-\tablecomments{The full version of this table is available in electronic form,
-as well as at \url{http://data.galaxyzoo.org}. The complete version includes
-data for 118,425~galaxies and morphological information for all tasks in the
-tree. A subset of the information is shown here to illustrate form and
-content.}
+\tablenotetext{1}{Flag indicating how the vote fractions for this galaxy were corrected through debiasing (Section~\ref{ssec:zeta_results}), if possible.
+0~=~correctable, 1~=~lower-limit ($f_{raw}$ --- $f_{adj}$ is not single-valued), 2~=~uncorrected ($z_{\rm gal} < 0.3$), 3~=~uncorrected (insufficient \ferengi{} galaxies in this $z$-$\mu$ bin), 4~=~uncorrected (no galaxy redshift available).}
+\tablecomments{The full version of this table is available in electronic form, as well as at \url{http://data.galaxyzoo.org}.
+The complete version includes data for 118,425~galaxies and morphological information for all tasks in the tree.
+A subset of the information is shown here to illustrate form and content.}
 \end{deluxetable*}
@@
 \enddata
-\tablecomments{The full version of this table is available in electronic form,
-as well as at \url{http://data.galaxyzoo.org}. The complete version includes
-data for 3,927~galaxies and morphological information for all tasks in the
-tree. A subset of the information is shown here to illustrate form and
-content.}
+\tablecomments{The full version of this table is available in electronic form, as well as at \url{http://data.galaxyzoo.org}.
+The complete version includes data for 3,927~galaxies and morphological information for all tasks in the tree.
+A subset of the information is shown here to illustrate form and content.}
 \end{deluxetable*}
@@
 \enddata
-\tablecomments{The full version of this table is available in electronic form,
-as well as at \url{http://data.galaxyzoo.org}. The complete version includes
-data for 6,144~galaxies and morphological information for all tasks in the
-tree. A subset of the information is shown here to illustrate form and
-content.}
+\tablecomments{The full version of this table is available in electronic form, as well as at \url{http://data.galaxyzoo.org}.
+The complete version includes data for 6,144~galaxies and morphological information for all tasks in the tree.
+A subset of the information is shown here to illustrate form and content.}
 \end{deluxetable*}
@@
 \enddata
-\tablecomments{The full version of this table is available in electronic form,
-as well as at \url{http://data.galaxyzoo.org}. The complete version includes
-data for 21,522~galaxies and morphological information for all tasks in the
-tree. A subset of the information is shown here to illustrate form and
-content.}
+\tablecomments{The full version of this table is available in electronic form, as well as at \url{http://data.galaxyzoo.org}.
+The complete version includes data for 21,522~galaxies and morphological information for all tasks in the tree.
+A subset of the information is shown here to illustrate form and content.}
 \end{deluxetable*}
@@
 \enddata
-\tablecomments{The full version of this table is available in electronic form,
-as well as at \url{http://data.galaxyzoo.org}. The complete version includes
-data for 30,339~galaxies and morphological information for all tasks in the
-tree. A subset of the information is shown here to illustrate form and
-content.}
+\tablecomments{The full version of this table is available in electronic form, as well as at \url{http://data.galaxyzoo.org}.
+The complete version includes data for 30,339~galaxies and morphological information for all tasks in the tree.
+A subset of the information is shown here to illustrate form and content.}
 \end{deluxetable*}
@@
 \tablenotetext{1}{Flag indicating the color of the PSF in the simulated AGN. 0~=~no simulated AGN, 1~=~blue, 2~=~flat, 3~=~red.}
-\tablecomments{The full version of this table is available in electronic form,
-as well as at \url{http://data.galaxyzoo.org}. The complete version includes
-data for 2,961~galaxies and morphological information for all tasks in the
-tree. A subset of the information is shown here to illustrate form and
-content.}
+\tablecomments{The full version of this table is available in electronic form, as well as at \url{http://data.galaxyzoo.org}.
+The complete version includes data for 2,961~galaxies and morphological information for all tasks in the tree.
+A subset of the information is shown here to illustrate form and content.}
 \end{deluxetable*}
@@
 
-The intended purpose of the GZH catalog is to provide a simple, yet flexible,
-means of identifying samples of galaxies with a desired morphological type.
-This section provides instructions for creating such samples using the vote
-fractions corresponding to the tasks shown in Figure~\ref{fig:decisiontree}. We
-stress that the selection process will vary based on the particular science
-case. More conservative cuts can be applied to create pure, but not necessarily
-complete, samples. These are useful for selecting galaxies exhibiting unique
-morphologies for individual case studies or observing proposals. Looser cuts
-can be applied to obtain samples with a higher level of completeness, which
-will increase the sample size but can potentially decrease purity. Population
-studies would make use of such large samples, in which statistical significance
-is a crucial factor in evaluating results. \citet{mas11c,mel14,che15}, and
-\citet{gal15} are examples of GZ papers which select morphologies in this way.
-
-In GZH, participants answered questions about a galaxy's morphology in a decision
-tree format. With this structure, questions shown to a classifier were dependent on
-their answers to the previous questions (Section~\ref{ssec:interface}).
-Figure~\ref{fig:decisiontree} shows the possible paths available for answering
-the questions offered in GZH. The colors represent the tier level of Tasks,
-which indicate the number of previous Tasks the given Task is dependent upon.
-The arm-number question, Task~11, is a 5$^\mathrm{th}$-tier Task, meaning that
-whether this question is seen by a classifier was dependent on four Tasks preceding
-it. In this case, it as only shown to classifiers who identified the galaxy as
-featured/disk-shaped in Task~01, not clumpy in Task~12, not edge-on in Task~02,
-and having spiral structure in Task~10.
-
-To select galaxies of a morphological type identified with a particular Task, a
-cut is placed on the vote fraction for that Task ($f_{\rm task}$), \emph{as
-well as} the vote fractions for the Tasks preceding it, because of the
-dependency induced by the decision-tree structure. For example, to select
-barred galaxies, a cut may be placed on \fbar{} such that only galaxies where a
-high fraction of votes for this task voted for the $bar,yes$ answer. This is
-not the only necessary cut, however, since not all classifiers answer this question;
-only those who have previously selected ``features'' in Task~01, ``not clumpy''
-in Task~12, and ``not edge-on'' in Task~02 will have the opportunity to vote on
-the bar question, Task~03. To ensure that \fbar{} is well-sampled, cuts on all
-previous tasks must be applied.
-
-The flexibility of this catalog allows users to set their own selection
-criteria for vote fraction thresholds to create a morphologically pure sample.
-Table~\ref{tbl:thresholds} provides baseline cuts for selecting galaxies of a
-variety of morphologies. These thresholds are determined by a visual inspection
-of subsamples. For each Task, at least 20 classifiers are required to have voted on
-the given question along with a cut on the vote fraction is applied to the
-previous task. We visually analyzed subsamples of 50~galaxies meeting both
-criteria, as well as a control sample of galaxies which had 20~classifiers vote on
-the task, but did not meet the threshold cut set for the previous task. The
-threshold cut was adjusted and new subsamples were inspected until both the
-original and control samples achieved $>80\%$ purity.
-
-As an example of how to use Table~\ref{tbl:thresholds} to create a sample of
-3-armed spirals galaxies, we suggest selecting objects with $N_{arm~number} \ge
-20$, \ffeatures$>0.23, f_{\rm clumpy,no} > 0.30, f_{edgeon,no}>0.25$, and
-$f_{spiral,yes}>0.25$. These cuts define a sample of galaxies of ``arm number
-candidates''; \ie, galaxies for which answering the arm number question makes
-physical sense and the vote fraction $f_{\rm arm~number}$ is well-sampled. In
-this example, such galaxies are featured, non-clumpy, non-edge~on spirals. At
-this point a cut can be made on $f_{\rm arm~number=3}$ to select spirals with
-three arms.
-
-Tasks 03, 04 and 05 have an additional possible pathway; as shown in
-Figure~\ref{fig:decisiontree}, a classifier might also be shown this question if they
-select ``featured/disk'' in Task~01, ``clumpy'' in Task~12, two or more clumps
-in Task~16, and ``spiral arrangement'' in Task~15. After applying the
-appropriate thresholds for this path, $< 0.5\%$ of the galaxies which have $\ge
-20$ answers to these questions used this pathway to arrive at these Tasks.
-Further, of these subjects, none were found to exhibit disk structure, although
-the clumps within were arranged in a spiral pattern.
-
-This section described how to use the previous Task thresholds in
-Table~\ref{tbl:thresholds} to select well-sampled galaxies which may or may not
-contain the feature associated with a unique Task. The following two examples
-show to use the vote fractions for a particular Task to obtain a sample of
-galaxies with a certain morphological type.
+The intended purpose of the GZH catalog is to provide a simple, yet flexible, means of identifying samples of galaxies with a desired morphological type.
+This section provides instructions for creating such samples using the vote fractions corresponding to the tasks shown in Figure~\ref{fig:decisiontree}.
+We stress that the selection process will vary based on the particular science case.
+More conservative cuts can be applied to create pure, but not necessarily complete, samples.
+These are useful for selecting galaxies exhibiting unique morphologies for individual case studies or observing proposals.
+Looser cuts can be applied to obtain samples with a higher level of completeness, which will increase the sample size but can potentially decrease purity.
+Population studies would make use of such large samples, in which statistical significance is a crucial factor in evaluating results.
+\citet{mas11c,mel14,che15}, and \citet{gal15} are examples of papers which select Galaxy Zoo morphologies in this way.
+
+In GZH, volunteers answer questions about a galaxy's morphology in a decision tree format.
+With this structure, questions shown to a user are dependent on their answers to the previous questions (Section~\ref{ssec:interface}).
+Figure~\ref{fig:decisiontree} shows the possible paths available for answering the questions offered in GZH.
+The colors represent the tier level of Tasks, which indicate the number of previous Tasks the given Task is dependent upon.
+The arm-number question, Task~11, is a 5$^\mathrm{th}$-tier Task, meaning that whether this question is seen by a user is dependent on four Tasks preceding it.
+In this case, it is only shown to volunteers who voted the galaxy was featured/disk-shaped in Task~01, not clumpy in Task~12, not edge-on in Task~02, and had spiral structure in Task~10.
+
+To select galaxies of a morphological type identified with a particular Task, a cut is placed on the vote fraction for that Task ($f_{\rm task}$), \emph{as well as} the vote fractions for the Tasks preceding it, because of the dependency induced by the decision-tree structure.
+For example, to select barred galaxies, a cut may be placed on \fbar{} such that only galaxies where a high fraction of votes for this task voted for the $bar,yes$ answer.
+This is not the only necessary cut, however, since not all users answer this question; only those who have previously selected ``features'' in Task~01, ``not clumpy'' in Task~12, and ``not edge-on'' in Task~02 will have the opportunity to vote on the bar question, Task~03.
+To ensure that \fbar{} is well-sampled, cuts on all previous tasks must be applied.
+
+The flexibility of this catalog allows the user to set their own selection criteria for vote fraction thresholds to create a morphologically pure sample.
+Table~\ref{tbl:thresholds} provides baseline cuts for selecting galaxies of a variety of morphologies.
+These thresholds are determined by a visual inspection of subsamples.
+For each Task, at least 20 users are required to have voted on the given question along with a cut on the vote fraction is applied to the previous task.
+We visually analyzed subsamples of 50~galaxies meeting both criteria, as well as a control sample of galaxies which had 20~users vote on the task, but did not meet the threshold cut set for the previous task.
+The threshold cut was adjusted and new subsamples were inspected until both the original and control samples achieved $>80\%$ purity.
+
+As an example of how to use Table~\ref{tbl:thresholds} to create a sample of 3-armed spirals galaxies, we suggest selecting objects with $N_{arm~number} \ge 20$, \ffeatures$>0.23, f_{\rm clumpy,no} > 0.30, f_{edgeon,no}>0.25$, and $f_{spiral,yes}>0.25$.
+These cuts define a sample of galaxies of ``arm number candidates''; \ie, galaxies for which answering the arm number question makes physical sense and the vote fraction $f_{\rm arm~number}$ is well-sampled.
+In this example, such galaxies are featured, non-clumpy, non-edge~on spirals.
+At this point a cut can be made on $f_{\rm arm~number=3}$ to select spirals with three arms.
+
+Tasks 03, 04 and 05 have an additional possible pathway; as shown in Figure~\ref{fig:decisiontree}, a user might also be shown this question if they select ``featured/disk'' in Task~01, ``clumpy'' in Task~12, two or more clumps in Task~16, and ``spiral arrangement'' in Task~15.
+After applying the appropriate thresholds for this path, $< 0.5\%$ of the galaxies which have $\ge 20$ answers to these questions used this pathway to arrive at these Tasks.
+Further, of these subjects, none were found to exhibit disk structure, although the clumps within were arranged in a spiral pattern.
+
+This section described how to use the previous Task thresholds in Table~\ref{tbl:thresholds} to select well-sampled galaxies which may or may not contain the feature associated with a unique Task.
+The following two examples show to use the vote fractions for a particular Task to obtain a sample of galaxies with a certain morphological type.
 
@@
 
-A sample of barred disk galaxies is created by applying cuts on the previous
-tasks as listed in Table~\ref{tbl:thresholds}. 11,049 ``bar candidates'',
-galaxies for which asking the bar question is meaningful, were selected by
-applying the cuts $N_{bar} \ge 20$, $f_{\rm features}>0.23, f_{\rm clumpy,no} >
-0.30,$ and $f_{edgeon,no}>0.25$. These galaxies are featured, non-clumpy,
-non-edge~on galaxies. Of these, a pure sample of 730 barred disks was
-identified by applying a cut of \fbar$>0.7$. A subsample of 50 galaxies were
-visually inspected and 94\% were found to contain strong bars. A complete
-sample of strong and weak bars was created by applying a cut of \fbar$>0.3$.
-This sample contained 3,218 galaxies, 86\% of which were found to contain weak
-or strong bars through visual inspection in a subsample of 50.
-
-The resulting bar sample can be used to estimate the redshift evolution of bar
-fraction and find a steady decrease of \fbar$\sim 0.32$ at $z=0.4$ to
-\fbar$\sim 0.24$ at $z=1.0$. The decrease in bar fraction agrees with
-\citet{mel14}, although they report a lower overall bar fraction going from
-\fbar$=0.22$ at $z=0.4$ to \fbar$=0.11$ at $z=1.0$. The difference in total bar
-fraction is expected, as this analysis used a looser cut on \fbar, there is no
-luminosity cut, and the use of debiased values for \ffeatures{} increases the
-total amount of disks in the sample compared to \citet{mel14}. For a more
-thorough analysis of the bar fraction, a cut on \fbar{} that evolves with
-redshift may yield more accurate results, since there are no explicit debiased
-values of \fbar{} that would take redshift induced bias into account.
-
-\subsection{Example 2: Identifying clump multiplicity} Clumps are known to be a
-characteristic feature of galaxies outside the local universe, and there is
-evidence they play a crucial role in the evolution of modern spirals,
-particularly in the formation of central bulges
-\citep{elm05,elm14,guo15,beh16}. Simulations show clumps migrate from the outer
-disk to the galactic center in only a few orbital periods \citep{man15} and
-observations show increasing bulge to clump mass and density ratios as the
-universe evolves since $z\sim 1.5$ \citep{elm09}, suggesting that clumps
-coalesce over time to form the modern bulges of disk galaxies. GZH added a
-``clumpy'' path to the decision tree for the purpose of both identifying clumps
-and investigating their evolution with redshift.
-
-For galaxies identified as ``clumpy'' in GZH, the number of clumps can be
-determined using Task~16. Table~\ref{tbl:thresholds} can be used to select
-8,444 galaxies measured as ``clumpy'' using \ffeatures$> 0.23$ and $f_{\rm
-clumpy,yes}>0.80$ to ensure the vote fractions for Task~16 are well-sampled.
-The clump number can be reasonably identified for 1,112 of the clumpy galaxies;
-for the remainder, the unique clumps were less distinguishable from each other
-and the exact number of clumps could not be deduced without careful visual
-inspection. In the 1,112 which did have distinguishable clumps, there are
-61 one-clump galaxies using $f_{\rm 1~clump}>0.50$, 442 two-clump galaxies
-using $f_{\rm 2~clumps}>0.80$, 275 three-clump galaxies using $f_{\rm
-3~clumps}>0.75$, 71 four-clump galaxies using $f_{\rm 4~clumps} > 0.70$,
-and 263 galaxies with more than four clumps using $f_{\rm >4~clumps}>0.70$.
-Alternatively, these data may be used to create more general samples of
-clumpy galaxies with few clumps and many clumps. A sample of 989 ``few
-clumps'' galaxies can be made using $(f_{\rm 1~clump} + f_{\rm 2~clumps}) >
-0.5$ and 2,910 ``many clumps'' galaxies using $(f_{\rm 3~clumps}+f_{\rm
-4~clumps}+f_{\rm >4~clumps})>0.5$.
+A sample of barred disk galaxies is created by applying cuts on the previous tasks as listed in Table~\ref{tbl:thresholds}.
+11,049 ``bar candidates'', galaxies for which asking the bar question is meaningful, were selected by applying the cuts $N_{bar} \ge 20$, $f_{\rm features}>0.23, f_{\rm clumpy,no} > 0.30,$ and $f_{edgeon,no}>0.25$.
+These galaxies are featured, non-clumpy, non-edge~on galaxies.
+Of these, a pure sample of 730 barred disks was identified by applying a cut of \fbar$>0.7$.
+A subsample of 50 galaxies were visually inspected and 94\% were found to contain strong bars.
+A complete sample of strong and weak bars was created by applying a cut of \fbar$>0.3$.
+This sample contained 3,218 galaxies, 86\% of which were found to contain weak or strong bars through visual inspection in a subsample of 50.
+
+The resulting bar sample can be used to estimate the redshift evolution of bar fraction and find a steady decrease of \fbar$\sim 0.32$ at $z=0.4$ to \fbar$\sim 0.24$ at $z=1.0$.
+The decrease in bar fraction agrees with \citet{mel14}, although they report a lower overall bar fraction going from \fbar$=0.22$ at $z=0.4$ to \fbar$=0.11$ at $z=1.0$.
+The difference in total bar fraction is expected, as this analysis used a looser cut on \fbar, there is no luminosity cut, and the use of debiased values for \ffeatures{} increases the total amount of disks in the sample compared to \citet{mel14}.
+For a more thorough analysis of the bar fraction, a cut on \fbar{} that evolves with redshift may yield more accurate results, since there are no explicit debiased values of \fbar{} that would take redshift induced bias into account.
+
+\subsection{Example 2: Identifying clump multiplicity}
+Clumps are known to be a characteristic feature of galaxies outside the local universe, and there is evidence they play a crucial role in the evolution of modern spirals, particularly in the formation of central bulges \citep{elm05,elm14,guo15,beh16}.
+Simulations show clumps migrate from the outer disk to the galactic center in only a few orbital periods \citep{man15} and observations show increasing bulge to clump mass and density ratios as the universe evolves since $z\sim 1.5$ \citep{elm09}, suggesting that clumps coalesce over time to form the modern bulges of disk galaxies.
+GZH added a ``clumpy'' path to the decision tree for the purpose of both identifying clumps and investigating their evolution with redshift.
+
+For galaxies identified as ``clumpy'' in GZH, the number of clumps can be determined using Task~16.
+Table~\ref{tbl:thresholds} can be used to select 8,444 galaxies measured as ``clumpy'' using \ffeatures$> 0.23$ and $f_{\rm clumpy,yes}>0.80$ to ensure the vote fractions for Task~16 are well-sampled.
+The clump number can be reasonably identified for 1,112 of the clumpy galaxies; for the remainder, the unique clumps were less distinguishable from each other and the exact number of clumps could not be deduced without careful visual inspection.
+In the 1,112 which did have distinguishable clumps, there are 61 one-clump galaxies using $f_{\rm 1~clump}>0.50$, 442 two-clump galaxies using $f_{\rm 2~clumps}>0.80$, 275 three-clump galaxies using $f_{\rm 3~clumps}>0.75$, 71 four-clump galaxies using $f_{\rm 4~clumps} > 0.70$, and 263 galaxies with more than four clumps using $f_{\rm >4~clumps}>0.70$.
+Alternatively, these data may be used to create more general samples of clumpy galaxies with few clumps and many clumps.
+A sample of 989 ``few clumps'' galaxies can be made using $(f_{\rm 1~clump} + f_{\rm 2~clumps}) > 0.5$ and 2,910 ``many clumps'' galaxies using $(f_{\rm 3~clumps}+f_{\rm 4~clumps}+f_{\rm >4~clumps})>0.5$.
 
@@
 
-Any analysis of the morphological distribution of galaxies must properly
-consider morphology with respect to other physical properties of the sample,
-such as color, mass, size, environment, and redshift. We defer such analyses to
-later papers, and comment here only on a few broad characteristics of the
-overall GZH sample.
-
-Figure~\ref{fig:sankey} shows the breakdown of morphologies for the combined
-surveys in GZH as a flow~diagram, where each node represents a task and the
-flows between the nodes represent the possible responses. The width of the
-flows is proportional to the number of galaxies associated with that response;
-Figure~\ref{fig:sankey} uses a simple plurality vote to assign the combined set
-of labels for each galaxy. This method is likely to undersample some of the
-categories; visual inspection of images suggests that \ffeatures$\gtrsim0.3$
-identifies disk-dominated or irregular galaxies reliably, for example. This
-method also does not use the suggested thresholds in
-Table~\ref{tbl:thresholds}.
+Any analysis of the morphological distribution of galaxies must properly consider morphology with respect to other physical properties of the sample, such as color, mass, size, environment, and redshift.
+We defer such analyses to later papers, and comment here only on a few broad characteristics of the overall GZH sample.
+
+Figure~\ref{fig:sankey} shows the breakdown of morphologies for the combined surveys in GZH as a flow~diagram, where each node represents a task and the flows between the nodes represent the possible responses.
+The width of the flows is proportional to the number of galaxies associated with that response; Figure~\ref{fig:sankey} uses a simple plurality vote to assign the combined set of labels for each galaxy.
+This method is likely to undersample some of the categories; visual inspection of images suggests that \ffeatures$\gtrsim0.3$ identifies disk-dominated or irregular galaxies reliably, for example.
+This method also does not use the suggested thresholds in Table~\ref{tbl:thresholds}.
 
@@
 \includegraphics[width=0.90\textwidth]{figures/sankey_both.png}
-\caption{Demographics of the morphologies for all galaxies in GZH (including
-both \hst{} and SDSS imaging). Each node in each diagram (dark blue horizontal
-bars of uniform height) represents a task in the tree. The left diagram shows
-the full decision tree; the right diagram zooms in on the features/clumpy
-tasks, which are otherwise difficult to see. The paths between tasks represent
-each possible answer to the task; these flow from top to bottom between their
-origin question and the subsequent task in the tree. Labels are assigned to
-each galaxy based on the plurality answer for each task. A galaxy is assigned
-only one label at each node. Widths of the paths are proportional to the number
-of galaxies assigned to that path; the widths of the nodes are proportional to
-the number of galaxies for which the question was reliably answered.}
+\caption{Demographics of the morphologies for all galaxies in GZH (including both \hst{} and SDSS imaging).
+Each node in each diagram (dark blue horizontal bars of uniform height) represents a task in the tree.
+The left diagram shows the full decision tree; the right diagram zooms in on the features/clumpy tasks, which are otherwise difficult to see.
+The paths between tasks represent each possible answer to the task; these flow from top to bottom between their origin question and the subsequent task in the tree.
+Labels are assigned to each galaxy based on the plurality answer for each task.
+A galaxy is assigned only one label at each node.
+Widths of the paths are proportional to the number of galaxies assigned to that path; the widths of the nodes are proportional to the number of galaxies for which the question was reliably answered.}
 \label{fig:sankey}
@@
 
-Given these caveats, the overall distribution of galaxy types is significantly
-different than the low-redshift sample classified in SDSS imaging from GZ1 and
-GZ2. \citet{lin11} found that elliptical galaxies exceeded spiral galaxies by a
-factor of $\sim2:1$ in the main spectroscopic sample if using a plurality vote
-criterion (although \citealt{bam09} show that this strongly depends on the
-selection method; spirals are the dominant population in a volume-limited
-sample at $z<0.088$, for example). The weighted votes for GZH have smooth
-galaxies outnumbering disks and clumpy galaxies by a factor of $\sim3:1$,
-however. The fraction of objects identified as stars or artifact is also much
-higher in the Hubble imaging; by plurality votes, these encompass only
-$\sim0.1\%$ of images in SDSS \citep{wil13}, but 6\% of images in GZH.
-
-Within the sample of galaxies identified as ``not smooth'', it is clear that
-the addition of the clumpy branch is necessary to describe a large fraction of
-the sample; disk-dominated galaxies outnumber clumpy morphologies by less than
-a factor of 2. Disk galaxies are primarily unbarred \citet{mel14} and
-possessing two visible spiral arms over a flat distribution of pitch angles and
-bulge prominence. Clumpy galaxies are identified across the full range of clump
-multiplicities, with the exception of 1-clump galaxies (which would be
-difficult to differentiate from compact spheroids). Roughly half of the
-galaxies have at least 1~clump identified as the brightest; the clumps are most
-commonly asymmetrically arranged in clusters and are not often seen embedded in
-larger structures.
+Given these caveats, the overall distribution of galaxy types is significantly different than the low-redshift sample classified in SDSS imaging from GZ1 and GZ2.
+\citet{lin11} found that elliptical galaxies exceeded spiral galaxies by a factor of $\sim2:1$ in the main spectroscopic sample if using a plurality vote criterion (although \citealt{bam09} show that this strongly depends on the selection method; spirals are the dominant population in a volume-limited sample at $z<0.088$, for example).
+The weighted votes for GZH have smooth galaxies outnumbering disks and clumpy galaxies by a factor of $\sim3:1$, however.
+The fraction of objects identified as stars or artifact is also much higher in the Hubble imaging; by plurality votes, these encompass only $\sim0.1\%$ of images in SDSS \citep{wil13}, but 6\% of images in GZH.
+
+Within the sample of galaxies identified as ``not smooth'', it is clear that the addition of the clumpy branch is necessary to describe a large fraction of the sample; disk-dominated galaxies outnumber clumpy morphologies by less than a factor of 2.
+Disk galaxies are primarily unbarred \citet{mel14} and possessing two visible spiral arms over a flat distribution of pitch angles and bulge prominence.
+Clumpy galaxies are identified across the full range of clump multiplicities, with the exception of 1-clump galaxies (which would be difficult to differentiate from compact spheroids).
+Roughly half of the galaxies have at least 1~clump identified as the brightest; the clumps are most commonly asymmetrically arranged in clusters and are not often seen embedded in larger structures.
 
@@
 
-All of the Legacy surveys included in the GZH imaging have had morphological
-catalogs previously published; these catalogs have significant differences in
-the number of galaxies, size and magnitude limits, classification scheme, and
-the methods used for measuring morphology. These catalogs have been
-cross-matched to GZH to compare the results; this is not presented as an
-endorsement of any particular method, but as an exploration of the strengths
-and weaknesses of the GZ crowdsourced catalogs as compared to products made
-with machine learning, automatic fits, and expert visual classification.
-
-The types and accuracy of morphological classification strongly depend on the
-sample and methods being used. In an attempt to make a consistent comparison
-between different techniques, galaxies are broadly grouped into three
-categories: bulge-dominated/elliptical/smooth, disk-dominated/spiral, and
-irregular/clumpy. These categories are compared to two parameters in GZH:
-\fbest, which is designed to identify smooth (elliptical) galaxies, and \fodd,
-which is designed to identify deviations from well-formed spirals or S0s and
-which constitutes a ``catch-all'' for the variety of asymmetric morphologies
-that can constitute an irregular galaxy.
-
-Morphologies for GEMS galaxies were measured by \citet{hau07}, who used
-single-component \sersic{} fits to the F850LP imaging. This analysis used
-parameters from the \galfit{} code, which \citet{hau07} evaluated as more
-reliable than \gimtwod{} for GEMS due to the ability to fit multiple galaxies
-in crowded fields. A 1\arcsec~positional match for the GEMS galaxies in Table~9
-in \citet{hau07} to the GZH sample gives 8,846~galaxies in both \citet{hau07}
-and GZH. The main morphological parameter in the automated catalog is the
-\sersic{} index $n$ defining the radial surface brightness profile.
+All of the Legacy surveys included in the GZH imaging have had morphological catalogs previously published; these catalogs have significant differences in the number of galaxies, size and magnitude limits, classification scheme, and the methods used for measuring morphology.
+These catalogs have been cross-matched to GZH to compare the results; this is not presented as an endorsement of any particular method, but as an exploration of the strengths and weaknesses of the GZ crowdsourced catalogs as compared to products made with machine learning, automatic fits, and expert visual classification.
+
+The types and accuracy of morphological classification strongly depend on the sample and methods being used.
+In an attempt to make a consistent comparison between different techniques, galaxies are broadly grouped into three categories: bulge-dominated/elliptical/smooth, disk-dominated/spiral, and irregular/clumpy.
+These categories are compared to two parameters in GZH: \fbest, which is designed to identify smooth (elliptical) galaxies, and \fodd, which is designed to identify deviations from well-formed spirals or S0s and which constitutes a ``catch-all'' for the variety of asymmetric morphologies that can constitute an irregular galaxy.
+
+Morphologies for GEMS galaxies were measured by \citet{hau07}, who used single-component \sersic{} fits to the F850LP imaging.
+This analysis used parameters from the \galfit{} code, which \citet{hau07} evaluated as more reliable than \gimtwod{} for GEMS due to the ability to fit multiple galaxies in crowded fields.
+A 1\arcsec~positional match for the GEMS galaxies in Table~9 in \citet{hau07} to the GZH sample gives 8,846~galaxies in both \citet{hau07} and GZH.
+The main morphological parameter in the automated catalog is the \sersic{} index $n$ defining the radial surface brightness profile.
 ``Elliptical'' galaxies are selected by $n>2.5$ and ``spirals''  by $n>2.5$.
-There is no automatic measurement of irregular or clumpy structure in this
-catalog.
-
-AEGIS galaxies were morphologically classified using non-parametric
-measurements by \citet{lot08}. This method used a combination of the Gini
-coefficient ($G$), which measures the relative inequality in pixel brightness,
-and $M_{20}$, the second-order moment of the brightest 20\% of the light
-\citep{lot04}. A linear combination of $G$ and $M_{20}$ delineates three broad
-categories of galaxy morphology: E/S0/Sa (``elliptical''), Sb/Sc/Ir
-(``spiral''), and mergers (``irregular''). A 1\arcsec{} positional match on
-AEGIS and GZH yields 4,031 galaxies with reliably-measured morphologies and
-$S/N>3$ in both $V$- and $I$-bands.
-
-Galaxies in both of the GOODS fields down to a limit of $z_{AB}=22.5$ were
-visually classified by a single expert (R.S.~Ellis), inspecting both $z$-band
-and composite $Viz$ color images \citep{bun05}. These morphologies are assigned
-a numerical value based on categories in \citet{bri98a}; the corresponding
-morphologies used are ``elliptical'' (classes 0,1,2), ``spirals'' (classes
-3,4,5), and ``irregular'' (classes 6,7,8). A 0.5\arcsec{} matched radius yields
-2,435 galaxies (1300 in GOODS-N, 1135 in GOODS-S) in both \citet{bun05} and
-GZH.
-
-COSMOS galaxies have multiple published datasets automatically classifying
-morphology, all using a variation of non-parametric measurements. \citet{cas07}
-used a combination of concentration ($C$), asymmetry ($A$), $G$, and $M_{20}$
-\citep{cas05} to classify all galaxies with $m_\mathrm{I,petro}<25$, and used
-an empirical division based on several hundred training images to assign
-galaxies to discrete morphological categories. A similar method is employed by
-\citet{tas11}, using the same non-parametric indices but with a different
-method of calculating the Petrosian radius and total light profile. They employ
-a nearest-neighbors method is used to assign morphological categories for the
-entire sample based on a small training set. \citet[][ZEST]{sca07} used $C$,
-$A$, $G$, $M_{20}$, the galaxy ellipticity ($\epsilon$), and \sersic{} index
-($n$) to quantify the galaxy shapes; a principal component analysis is used to
-assign galaxies to discrete morphological categories. The categories in all
-three methods are split into ellipticals, spirals, and peculiar/irregulars. A
-0.5\arcsec{} radius search on GZH matches to 76,241 galaxies in \citet{cas07},
-76,608 in \citet{tas11}, and 77,425 in \citet{sca07}.
+There is no automatic measurement of irregular or clumpy structure in this catalog.
+
+AEGIS galaxies were morphologically classified using non-parametric measurements by \citet{lot08}.
+This method used a combination of the Gini coefficient ($G$), which measures the relative inequality in pixel brightness, and $M_{20}$, the second-order moment of the brightest 20\% of the light \citep{lot04}.
+A linear combination of $G$ and $M_{20}$ delineates three broad categories of galaxy morphology: E/S0/Sa (``elliptical''), Sb/Sc/Ir (``spiral''), and mergers (``irregular'').
+A 1\arcsec{} positional match on AEGIS and GZH yields 4,031 galaxies with reliably-measured morphologies and $S/N>3$ in both $V$- and $I$-bands.
+
+Galaxies in both of the GOODS fields down to a limit of $z_{AB}=22.5$ were visually classified by a single expert (R.S.~Ellis), inspecting both $z$-band and composite $Viz$ color images \citep{bun05}.
+These morphologies are assigned a numerical value based on categories in \citet{bri98a}; the corresponding morphologies used are ``elliptical'' (classes 0,1,2), ``spirals'' (classes 3,4,5), and ``irregular'' (classes 6,7,8).
+A 0.5\arcsec{} matched radius yields 2,435 galaxies (1300 in GOODS-N, 1135 in GOODS-S) in both \citet{bun05} and GZH.
+
+COSMOS galaxies have multiple published datasets automatically classifying morphology, all using a variation of non-parametric measurements.
+\citet{cas07} used a combination of concentration ($C$), asymmetry ($A$), $G$, and $M_{20}$ \citep{cas05} to classify all galaxies with $m_\mathrm{I,petro}<25$, and used an empirical division based on several hundred training images to assign galaxies to discrete morphological categories.
+A similar method is employed by \citet{tas11}, using the same non-parametric indices but with a different method of calculating the Petrosian radius and total light profile.
+They employ a nearest-neighbors method is used to assign morphological categories for the entire sample based on a small training set.
+\citet[][ZEST]{sca07} used $C$, $A$, $G$, $M_{20}$, the galaxy ellipticity ($\epsilon$), and \sersic{} index ($n$) to quantify the galaxy shapes; a principal component analysis is used to assign galaxies to discrete morphological categories.
+The categories in all three methods are split into ellipticals, spirals, and peculiar/irregulars.
+A 0.5\arcsec{} radius search on GZH matches to 76,241 galaxies in \citet{cas07}, 76,608 in \citet{tas11}, and 77,425 in \citet{sca07}.
 
@@
 \includegraphics[width=1.0\textwidth]{figures/comparisons.png}
-\caption{Distributions of morphological parameters for galaxies matched in GZH
-and other published catalogs, split by survey (AEGIS, COSMOS, GEMS, and GOODS).
-The first and third columns show the fraction of overall galaxies in the
-matched samples, split by their published morphologies as a function of the GZH
-\fbest. The corresponding second and fourth columns show data for the same
-galaxies as a function of \fodd. Confidence intervals for each binned fraction
-in the bin are calculated for a binomial population \citep{cam11}.}
+\caption{Distributions of morphological parameters for galaxies matched in GZH and other published catalogs, split by survey (AEGIS, COSMOS, GEMS, and GOODS).
+The first and third columns show the fraction of overall galaxies in the matched samples, split by their published morphologies as a function of the GZH \fbest.
+The corresponding second and fourth columns show data for the same galaxies as a function of \fodd.
+Confidence intervals for each binned fraction in the bin are calculated for a binomial population \citep{cam11}.}
 \label{fig:comparisons}
@@
 
-Figure~\ref{fig:comparisons} shows the proportion of galaxies as split by their
-automated/expert visual morphologies for each of the six catalogs matched to
-GZH. The relation between GZH and the automated/expert morphologies is shown to
-vary significantly for different surveys --- this could be due to intrinsic
-differences in the galaxies, in the techniques used to measure morphology, or
-both. The distribution of \fbest{} for AEGIS galaxies is essentially flat for
-spirals, showing almost no difference in proportion at the highest and lowest
-ends. Early-type galaxies are at their highest proportion at \fbest$\sim0$, but
-constitute at most only 40\% of galaxies. In contrast, GOODS galaxies at low
-\fbest{} are dominated by early-types, although spiral and irregular galaxies
-have comparable sizes as low as \fbest$\sim0.2$. In GEMS galaxies, the impact
-of irregular or peculiar galaxies is not measured; splitting on $n=2.5$ gives
-an essentially flat proportion of ellipticals to spirals at \fbest$>0.3$.
-Visual inspection of images of galaxies where both \fbest{} and $n$ are high
-show that the majority are obvious spirals but with prominent bulges,
-indicating that the single-component \sersic{} fit is likely choosing too small
-of an effective radius and missing the extended disk structure for a large
-population of galaxies.
-
-Even within the same sample of galaxies in COSMOS, different techniques of
-measuring morphology show significant differences. Both \citet{cas07} and
-\citet{tas11} have higher proportions of early-type galaxies at \fbest$\sim0$,
-but constitute less than half the sample in both cases. The majority of all
-galaxies in \citet{sca07}, in contrast, are spirals; oddly, the \emph{highest}
-proportions of spirals are found at the lowest values of \fbest. The decrease
-in spiral galaxies at higher \fbest{} is almost entirely balanced by an
-increase in irregulars. Early-types have a small bump near \fbest$\sim0.15$,
-but never constitute more than 10\% of the sample.
-
-The second set of plots in Figure~\ref{fig:comparisons} indicates that \fodd{}
-is largely an effective method for separating irregular and/or peculiar
-galaxies from spirals. Despite the somewhat vague wording of the {\it
-``anything odd?''} question in GZH, the AEGIS, COSMOS, and GOODS all show a
-marked increase in the irregular fraction increasing with \fodd. Any threshold
-value for distinguishing between the two, however, depends strongly on
-survey/redshift~range.
-
-As the data shown in Figure~\ref{fig:comparisons} cover a wide range of
-redshifts and sizes, a volume-limited sample of galaxies (or at least binning
-by redshift) is likely a much more appropriate comparison. While detailed
-analysis is left to a further paper, we note that there is no strong change in
-the proportion of galaxies when binning by redshift intervals of $\Delta z=0.2$
-out to $z=1.0$.
-
-Finally, there are 7,681~galaxies in the GOODS-S field with morphological
-classifications in both GZH and the Galaxy~Zoo:~CANDELS project (Simmons
-et~al., submitted). Since both the sensitivity and filters for the two sets of
-images differ (and there is no debiased correction applied to GZC), there is no
-prior reason to expect a perfect correlation between the separate vote
-fractions for the projects. Briefly, we note that the \ffeatures{} value for
-GZH is on average higher than GZC; the effect is strongest at
-$f_\mathrm{features,GZC}<0.3$, for which roughly half the galaxies have
-$f_\mathrm{features,GZH}>0.5$. However, the correlation between vote fractions
-is single-valued (although not linear, with a Pearson correlation coefficient
-of $r=0.6$), and should be possible to calibrate using a similar approach to
-that described in Section~\ref{sec:debiasing}; the correlation between other
-tasks, such as edge-on galaxies is significantly stronger ($r=0.9$). So while
-the raw vote fractions are not directly comparable, the initial analysis
-indicates that the broad morphologies are at least consistent.
+Figure~\ref{fig:comparisons} shows the proportion of galaxies as split by their automated/expert visual morphologies for each of the six catalogs matched to GZH.
+The relation between GZH and the automated/expert morphologies is shown to vary significantly for different surveys --- this could be due to intrinsic differences in the galaxies, in the techniques used to measure morphology, or both.
+The distribution of \fbest{} for AEGIS galaxies is essentially flat for spirals, showing almost no difference in proportion at the highest and lowest ends.
+Early-type galaxies are at their highest proportion at \fbest$\sim0$, but constitute at most only 40\% of galaxies.
+In contrast, GOODS galaxies at low \fbest{} are dominated by early-types, although spiral and irregular galaxies have comparable sizes as low as \fbest$\sim0.2$.
+In GEMS galaxies, the impact of irregular or peculiar galaxies is not measured; splitting on $n=2.5$ gives an essentially flat proportion of ellipticals to spirals at \fbest$>0.3$.
+Visual inspection of images of galaxies where both \fbest{} and $n$ are high show that the majority are obvious spirals but with prominent bulges, indicating that the single-component \sersic{} fit is likely choosing too small of an effective radius and missing the extended disk structure for a large population of galaxies.
+
+Even within the same sample of galaxies in COSMOS, different techniques of measuring morphology show significant differences.
+Both \citet{cas07} and \citet{tas11} have higher proportions of early-type galaxies at \fbest$\sim0$, but constitute less than half the sample in both cases.
+The majority of all galaxies in \citet{sca07}, in contrast, are spirals; oddly, the \emph{highest} proportions of spirals are found at the lowest values of \fbest.
+The decrease in spiral galaxies at higher \fbest{} is almost entirely balanced by an increase in irregulars.
+Early-types have a small bump near \fbest$\sim0.15$, but never constitute more than 10\% of the sample.
+
+The second set of plots in Figure~\ref{fig:comparisons} indicates that \fodd{} is largely an effective method for separating irregular and/or peculiar galaxies from spirals.
+Despite the somewhat vague wording of the {\it ``anything odd?''} question in GZH, the AEGIS, COSMOS, and GOODS all show a marked increase in the irregular fraction increasing with \fodd.
+Any threshold value for distinguishing between the two, however, depends strongly on survey/redshift~range.
+
+As the data shown in Figure~\ref{fig:comparisons} cover a wide range of redshifts and sizes, a volume-limited sample of galaxies (or at least binning by redshift) is likely a much more appropriate comparison.
+While detailed analysis is left to a further paper, we note that there is no strong change in the proportion of galaxies when binning by redshift intervals of $\Delta z=0.2$ out to $z=1.0$.
+
+Finally, there are 7,681~galaxies in the GOODS-S field with morphological classifications in both GZH and the Galaxy~Zoo:~CANDELS project (Simmons et~al., submitted).
+Since both the sensitivity and filters for the two sets of images differ (and there is no debiased correction applied to GZC), there is no prior reason to expect a perfect correlation between the separate vote fractions for the projects.
+Briefly, we note that the \ffeatures{} value for GZH is on average higher than GZC; the effect is strongest at $f_\mathrm{features,GZC}<0.3$, for which roughly half the galaxies have $f_\mathrm{features,GZH}>0.5$.
+However, the correlation between vote fractions is single-valued (although not linear, with a Pearson correlation coefficient of $r=0.6$), and should be possible to calibrate using a similar approach to that described in Section~\ref{sec:debiasing}; the correlation between other tasks, such as edge-on galaxies is significantly stronger ($r=0.9$).
+So while the raw vote fractions are not directly comparable, the initial analysis indicates that the broad morphologies are at least consistent.
 
@@
 
-This paper presents the catalog release for the Galaxy Zoo: Hubble project,
-which uses crowdsourced visual classifications to measure galaxy morphologies.
-The first two phases of Galaxy Zoo \citep{lin11,wil13} used images of
-low-redshift galaxies from SDSS; this is the first result of the project with
-space-based images of high-redshift targets (in addition to the Galaxy Zoo:
-CANDELS collaboration; Simmons et al., submitted). The final sample includes
-classifications for 181,101~images generated from 150,771~unique galaxies.
-Galaxies were selected from a brightness-limited sample from multiple Legacy
-surveys using the Advanced Camera for Surveys on the Hubble Space Telescope,
-including AEGIS, GEMS, GOODS-N, GOODS-S, and COSMOS. The catalog also includes
-classifications for 51,861 Sloan Digital Sky Survey images in Stripe~82 at
-relatively low redshift; these serve both as a low-redshift anchor for
-cosmological studies and a potential comparison for the different epochs of
-classification between GZH and Galaxy Zoo 2 \citep{wil13}.
-
-The data for the GZH catalogs has been extensively tested and reduced. The
-dominant effect is a known bias against identifying disky and asymmetric
-sub-structures at either low resolution or surface brightness. This can be the
-result either of genuinely small or dim galaxies, or a perceived effect from
-observing galaxies at further distances (higher redshift). To calibrate this
-\emph{without} potentially overcorrecting for the genuine morphological
-evolution of galaxies over cosmic time, the GZH project uses SDSS images of
-low-redshift galaxies, processes them to appear as if they were at higher
-redshift, and classifies them through the GZH interface in an identical
-fashion. The resulting change in \ffeatures{} as a function of $z$ and $\mu$ is
-applied as a multiplicative correction to the top-level vote fractions for
-$\sim50\%$ of the GZH galaxies.
-
-Galaxies in GZH show significant changes in the disk/elliptical fraction as a
-function of redshift, along with an increasing number of galaxies dominated by
-smaller clumps and presumed to be in the process of building up their baryonic
-mass through a combination of hierarchical merging and in-situ star formation.
-While the majority of scientific interpretation is left to future work, this
-paper confirms the decrease in observed bar fraction with increasing redshift
-\citep{mel14} and identifies a new way for selecting clumpy galaxies as a
-function of clump multiplicity.
-
-The full data tables for the catalogs can be accessed in machine-readable form
-from both the journal and at \url{http://data.galaxyzoo.org}. All the code and
-data tables used to generate this manuscript can be found at
-\url{https://github.com/willettk/gzhubble}.
+This paper presents the catalog release for the Galaxy Zoo: Hubble project, which uses crowdsourced visual classifications to measure galaxy morphologies.
+The first two phases of Galaxy Zoo \citep{lin11,wil13} used images of low-redshift galaxies from SDSS; this is the first result of the project with space-based images of high-redshift targets (in addition to the Galaxy Zoo: CANDELS collaboration; Simmons et al., submitted).
+The final sample includes classifications for 181,101~images generated from 150,771~unique galaxies.
+Galaxies were selected from a brightness-limited sample from multiple Legacy surveys using the Advanced Camera for Surveys on the Hubble Space Telescope, including AEGIS, GEMS, GOODS-N, GOODS-S, and COSMOS.
+The catalog also includes classifications for 51,861 Sloan Digital Sky Survey images in Stripe~82 at relatively low redshift; these serve both as a low-redshift anchor for cosmological studies and a potential comparison for the different epochs of classification between GZH and Galaxy Zoo 2 \citep{wil13}.
+
+The data for the GZH catalogs has been extensively tested and reduced.
+The dominant effect is a known bias against identifying disky and asymmetric sub-structures at either low resolution or surface brightness.
+This can be the result either of genuinely small or dim galaxies, or a perceived effect from observing galaxies at further distances (higher redshift).
+To calibrate this \emph{without} potentially overcorrecting for the genuine morphological evolution of galaxies over cosmic time, the GZH project uses SDSS images of low-redshift galaxies, processes them to appear as if they were at higher redshift, and classifies them through the GZH interface in an identical fashion.
+The resulting change in \ffeatures{} as a function of $z$ and $\mu$ is applied as a multiplicative correction to the top-level vote fractions for $\sim50\%$ of the GZH galaxies.
+
+Galaxies in GZH show significant changes in the disk/elliptical fraction as a function of redshift, along with an increasing number of galaxies dominated by smaller clumps and presumed to be in the process of building up their baryonic mass through a combination of hierarchical merging and in-situ star formation.
+While the majority of scientific interpretation is left to future work, this paper confirms the decrease in observed bar fraction with increasing redshift \citep{mel14} and identifies a new way for selecting clumpy galaxies as a function of clump multiplicity.
+
+The full data tables for the catalogs can be accessed in machine-readable form from both the journal and at \url{http://data.galaxyzoo.org}.
+All the code and data tables used to generate this manuscript can be found at \url{https://github.com/willettk/gzhubble}.
 
@@
 
-We thank Meg Schwamb and the ASIAA for hosting the ``Citizen Science in
-Astronomy'' workshop, 3-7 Mar 2014 in Taipei, Taiwan, at which some of this
-analysis was done. We thank Jennifer Lotz for sharing her $G$-$M_{20}$
-measurements for the AEGIS sample. We thank Coleman Krawczyk for his assistance
-in producing Figure~\ref{fig:decisiontree}.
-
-This project made heavy use of the Astropy packages in Python \citep{ast13},
-the \texttt{seaborn} plotting package \citep{was15}, astroML \citep{van12}, and
-TOPCAT \citep{tay05,tay11}. Modified code from Nick~Wherry and David~Schlegel
-was used to create the JPG images. Figure~\ref{fig:sankey} was generated with
-\url{http://sankeymatic.com/}.
-
-KS gratefully acknowledges support from Swiss National Science Foundation Grant
-PP00P2\_138979/1.
-
-This work is based on (GO-10134, GO-09822, GO-09425.01, GO-09583.01, GO-9500)
-program observations with the NASA/ESA Hubble Space Telescope, obtained at the
-Space Telescope Science Institute, which is operated by the Association of
-Universities for Research in Astronomy, Inc., under NASA contract NAS 5-26555.
-
-Funding for the SDSS and SDSS-II has been provided by the Alfred P. Sloan
-Foundation, the Participating Institutions, the National Science Foundation,
-the U.S. Department of Energy, the National Aeronautics and Space
-Administration, the Japanese Monbukagakusho, the Max Planck Society, and the
-Higher Education Funding Council for England. The SDSS website is
-\url{http://www.sdss.org/}.
-
-The SDSS is managed by the Astrophysical Research Consortium for the
-Participating Institutions. The Participating Institutions are the American
-Museum of Natural History, Astrophysical Institute Potsdam, University of
-Basel, University of Cambridge, Case Western Reserve University, University of
-Chicago, Drexel University, Fermilab, the Institute for Advanced Study, the
-Japan Participation Group, Johns Hopkins University, the Joint Institute for
-Nuclear Astrophysics, the Kavli Institute for Particle Astrophysics and
-Cosmology, the Korean Scientist Group, the Chinese Academy of Sciences
-(LAMOST), Los Alamos National Laboratory, the Max-Planck-Institute for
-Astronomy (MPIA), the Max-Planck-Institute for Astrophysics (MPA), New Mexico
-State University, Ohio State University, University of Pittsburgh, University
-of Portsmouth, Princeton University, the United States Naval Observatory and
-the University of Washington.
+We thank Meg Schwamb and the ASIAA for hosting the ``Citizen Science in Astronomy'' workshop, 3-7 Mar 2014 in Taipei, Taiwan, at which some of this analysis was done.
+We also thank Jennifer Lotz for sharing her $G$-$M_{20}$ measurements for the AEGIS sample.
+
+This project made heavy use of the Astropy packages in Python \citep{ast13}, the \texttt{seaborn} plotting package \citep{was15}, astroML \citep{van12}, and TOPCAT \citep{tay05,tay11}.
+Modified code from Nick~Wherry and David~Schlegel was used to create the JPG images.
+Figure~\ref{fig:sankey} was generated with \url{http://sankeymatic.com/}.
+
+The development and hosting of Galaxy Zoo Hubble was supported by a grant from the Alfred P. Sloan Foundation. The Zooniverse acknowledges support from a Google Global Impact Award.
+
+KS gratefully acknowledges support from Swiss National Science Foundation Grant PP00P2\_138979/1.
+
+This work is based on (GO-10134, GO-09822, GO-09425.01, GO-09583.01, GO-9500) program observations with the NASA/ESA Hubble Space Telescope, obtained at the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS 5-26555.
+
+Funding for the SDSS and SDSS-II has been provided by the Alfred P.
+Sloan Foundation, the Participating Institutions, the National Science Foundation, the U.S.
+Department of Energy, the National Aeronautics and Space Administration, the Japanese Monbukagakusho, the Max Planck Society, and the Higher Education Funding Council for England.
+The SDSS website is \url{http://www.sdss.org/}.
+
+The SDSS is managed by the Astrophysical Research Consortium for the Participating Institutions.
+The Participating Institutions are the American Museum of Natural History, Astrophysical Institute Potsdam, University of Basel, University of Cambridge, Case Western Reserve University, University of Chicago, Drexel University, Fermilab, the Institute for Advanced Study, the Japan Participation Group, Johns Hopkins University, the Joint Institute for Nuclear Astrophysics, the Kavli Institute for Particle Astrophysics and Cosmology, the Korean Scientist Group, the Chinese Academy of Sciences (LAMOST), Los Alamos National Laboratory, the Max-Planck-Institute for Astronomy (MPIA), the Max-Planck-Institute for Astrophysics (MPA), New Mexico State University, Ohio State University, University of Pittsburgh, University of Portsmouth, Princeton University, the United States Naval Observatory and the University of Washington.
 
@@
 
-GZH used both 5-epoch and 2-epoch sets of data to construct the GOODS set of
-images. The 11,157 full depth 5-epoch images are used in the main catalog; the
-classifications for the 7,464 shallow depth 2-epoch images are provided as a
-supplementary table. This section analyzes the effect of image depth on the
-ability of the GZ classifiers to identify features or disk structure in the images.
+GZH used both 5-epoch and 2-epoch sets of data to construct the GOODS set of images.
+The 11,157 full depth 5-epoch images are used in the main catalog; the classifications for the 7,464 shallow depth 2-epoch images are provided as a supplementary table.
+This section analyzes the effect of image depth on the ability of the GZ users to identify features or disk structure in the images.
 
@@
 
-Of the 11,157 galaxies in the GOODS-N and GOODS-S full depth sample, 4,461 of
-these are in the shallow-depth sample. Figure~\ref{fig:shallow_vs_full} shows a
-strong correlation between \ffeatures{} for both sets of images. The mean
-change in \ffeatures{} from the shallow to full depth images
-$f_\mathrm{features,full} - f_{features,shallow} \equiv \Delta f = 0.00$, with
-a standard deviation of $\sigma = 0.17$. While there is some variance in
-$\Delta f$ in the whole sample, the change is usually small and not often
-significant enough to change a morphological classification. Defining a clean
-sample of disk galaxies as those with \fbest$>0.8$, elliptical galaxies as
-those with $f_\mathrm{smooth,best}<0.2$, and intermediate as those in between,
-75\% of the sample would not change morphology. Of the remaining 25\% that
-would change morphology, only 0.3\% (representing 10 galaxies total)
-drastically change morphology from smooth to featured or vice versa, while the
-rest would transition to or from the ``intermediate'' morphology. Details can
-be seen in Table~\ref{tbl:shallow_to_full_stats} and examples of images
-representing the 9 possible changes (or lack of) in morphology are shown in
-Figures~\ref{fig:shallow_smooth},\ref{fig:shallow_intermediate}, and
-\ref{fig:shallow_featured}.
+Of the 11,157 galaxies in the GOODS-N and GOODS-S full depth sample, 4,461 of these are in the shallow-depth sample.
+Figure~\ref{fig:shallow_vs_full} shows a strong correlation between \ffeatures{} for both sets of images.
+The mean change in \ffeatures{} from the shallow to full depth images  $f_\mathrm{features,full} - f_{features,shallow} \equiv \Delta f = 0.00$, with a standard deviation of $\sigma = 0.17$.
+While there is some variance in $\Delta f$ in the whole sample, the change is usually small and not often significant enough to change a morphological classification.
+Defining a clean sample of disk galaxies as those with \fbest$>0.8$, elliptical galaxies as those with $f_\mathrm{smooth,best}<0.2$, and intermediate as those in between, 75\% of the sample would not change morphology.
+Of the remaining 25\% that would change morphology, only 0.3\% (representing 10 galaxies total) drastically change morphology from smooth to featured or vice versa, while the rest would transition to or from the ``intermediate'' morphology.
+Details can be seen in Table~\ref{tbl:shallow_to_full_stats} and examples of images representing the 9 possible changes (or lack of) in morphology are shown in Figures~\ref{fig:shallow_smooth},\ref{fig:shallow_intermediate}, and \ref{fig:shallow_featured}.
 
@@
 \includegraphics[width=0.50\textwidth]{figures/full_shallow_p_plot.pdf}
-\caption{Distribution of \ffeatures{} for the 4,461 GOODS galaxies with both
-shallow (2-epoch) and full-depth (5-epoch) images morphologically classified in
-GZH. For most galaxies, the value of \ffeatures{} is consistent ($\Delta
-f_\mathrm{features}<0.2$) between depths. Examples of galaxies with sharp
-changes in \ffeatures, as well as those with little to no change are shown in
-Figures~\ref{fig:shallow_smooth}-\ref{fig:shallow_featured}.}
+\caption{Distribution of \ffeatures{} for the 4,461 GOODS galaxies with both shallow (2-epoch) and full-depth (5-epoch) images morphologically classified in GZH.
+For most galaxies, the value of \ffeatures{} is consistent ($\Delta f_\mathrm{features}<0.2$) between depths.
+Examples of galaxies with sharp changes in \ffeatures, as well as those with little to no change are shown in Figures~\ref{fig:shallow_smooth}-\ref{fig:shallow_featured}.}
 \label{fig:shallow_vs_full}
@@
 \begin{table}
-\caption{Properties of galaxies whose morphologies changed or stayed the same
-in the shallow vs full images. Featured here is defined as \fbest$>0.8$,
-intermediate = $0.2<$\fbest$<0.8$, smooth = $f_\mathrm{smooth,best}<0.2$.
+\caption{Properties of galaxies whose morphologies changed or stayed the same in the shallow vs full images.
+Featured here is defined as \fbest$>0.8$, intermediate = $0.2<$\fbest$<0.8$, smooth = $f_\mathrm{smooth,best}<0.2$.
 \label{tbl:shallow_to_full_stats}}
@@
 
-\caption{Galaxies whose shallow images were classified as featured and full
-depth images were classified as smooth, intermediate, or featured.}
+\caption{Galaxies whose shallow images were classified as featured and full depth images were classified as smooth, intermediate, or featured.}
 \label{fig:shallow_featured}
@@
 
-To determine the rate at which the vote fraction for any Task decreases with
-redshift or surface brightness, data from simulated \ferengi{} images were
-modeled with functions in discrete redshift and surface brightness bins
-(Section~\ref{ssec:zeta_results}). A cut of $N>10$ was placed on the number of
-votes to reduce the error in the vote fractions and ensure they were
-well-sampled before applying a fit to the data. This requirement was only met
-for Task~01, which significantly reduced the goodness-of-fit for the model
-functions as compared with to the smooth/features task. Here we show an
-example of results obtained for the bar Task. Figure~\ref{fig:f_vs_fbar}
-shows that both the low sample rate and the degree of scatter in each bin
-inhibit fitting a reliable function that predicts $f_{{\rm bar},z=0.3}$.
-Table~\ref{tbl:ferengi_bar} summarizes the correction types for the
-\ferengi{} data; 71\% of the galaxies simulated did not meet the GZH
-requirements for well-sampled vote fractions for $f_\mathrm{bar}$, as
-compared to 2\% for $f_\mathrm{features}$. Similar results were obtained
-for all higher-order Tasks in GZH (Section~\ref{ssec:higher_order_tasks}).
+To determine the rate at which the vote fraction for any Task decreases with redshift or surface brightness, data from simulated \ferengi{} images were modeled with functions in discrete redshift and surface brightness bins (Section~\ref{ssec:zeta_results}).
+A cut of $N>10$ was placed on the number of votes to reduce the error in the vote fractions and ensure they were well-sampled before applying a fit to the data.
+This requirement was only met for Task~01, which significantly reduced the goodness-of-fit for the model functions as compared with to the smooth/features task.
+Here we show an example of results obtained for the bar Task.
+Figure~\ref{fig:f_vs_fbar} shows that both the low sample rate and the degree of scatter in each bin inhibit fitting a reliable function that predicts $f_{{\rm bar},z=0.3}$.
+Table~\ref{tbl:ferengi_bar} summarizes the correction types for the \ferengi{} data; 71\% of the galaxies simulated did not meet the GZH requirements for well-sampled vote fractions for $f_\mathrm{bar}$, as compared to 2\% for $f_\mathrm{features}$.
+Similar results were obtained for all higher-order Tasks in GZH (Section~\ref{ssec:higher_order_tasks}).
 
@@
 \subfigure{[d]\label{d}\includegraphics[width=0.4\textwidth]{figures/z1_mu20_subplot2_bar.pdf}}
-\caption{Similar to Figure~\ref{fig:f_vs_f}, showing effects of redshift bias
-for 3,950~images in the \ferengi{} sample. [a]: Each point in a given redshift
-and surface brightness bin represents a unique galaxy. The $y$-axis in each
-bin is the \ffeatures{} value of the image of that galaxy redshifted to the
-value corresponding to that redshift bin. The $x$-axis is the \ffeatures{}
-value of the image of the same galaxy redshifted to $z=0.3$. The dashed
-black lines represent the best-fit polynomials to the data in each square.
-The solid black line represents \ffeaturesz=\ffeaturesrest. Regions in
-which there is a single-valued relationship between \ffeatures{} at high
-redshift and at $z=0.3$ are marked in white; those in which there is not
-are blue, and those with not enough data ($N<5$) are gray. The mean
-normalized $\chi^2$ of the change in vote fraction is 0.08. None of the
-correlations for higher-order tasks (including bars) were applied to
-galaxies in the GZH catalog. [b]: A larger version of the dark-outlined
-square in [a], containing \ferengi{} galaxies artificially redshifted to
-$z=1.0$ and have surface brightnesses between $20.3 < \mu < 21.0$ $\rm
-(mag/arcsec^2)$. [c]: The same data as [a]. Each $z,\mu$ bin is divided
-into 4~sub-bins to determine the range of intrinsic \ffeaturesrest{} for a
-given range of observed \ffeaturesz{} values. In each sub-bin, the orange
-bars represent the inner 80$^\mathrm{th}$ percentiles of the data, the
-boundaries of which are the lower and upper limits of the debiased values.
-[d]: The same data as [b], but highlighting the upper and lower limit
-regions.}
+\caption{Similar to Figure~\ref{fig:f_vs_f}, showing effects of redshift bias for 3,950~images in the \ferengi{} sample.
+[a]: Each point in a given redshift and surface brightness bin represents a unique galaxy.
+The $y$-axis in each bin is the \ffeatures{} value of the image of that galaxy redshifted to the value corresponding to that redshift bin.
+The $x$-axis is the \ffeatures{} value of the image of the same galaxy redshifted to $z=0.3$.
+The dashed black lines represent the best-fit polynomials to the data in each square.
+The solid black line represents \ffeaturesz=\ffeaturesrest.
+Regions in which there is a single-valued relationship between \ffeatures{} at high redshift and at $z=0.3$ are marked in white; those in which there is not are blue, and those with not enough data ($N<5$) are gray.
+The mean normalized $\chi^2$ of the change in vote fraction is 0.08.
+None of the correlations for higher-order tasks (including bars) were applied to galaxies in the GZH catalog.
+[b]: A larger version of the dark-outlined square in [a], containing \ferengi{} galaxies artificially redshifted to $z=1.0$ and have surface brightnesses between $20.3 < \mu < 21.0$ $\rm (mag/arcsec^2)$.
+[c]: The same data as [a].
+Each $z,\mu$ bin is divided into 4~sub-bins to determine the range of intrinsic \ffeaturesrest{} for a given range of observed \ffeaturesz{} values.
+In each sub-bin, the orange bars represent the inner 80$^\mathrm{th}$ percentiles of the data, the boundaries of which are the lower and upper limits of the debiased values.
+[d]: The same data as [b], but highlighting the upper and lower limit regions.}
 \label{fig:f_vs_fbar}
@@
 \label{tbl:ferengi_bar}
-\caption{Distribution of \ferengi{} images analyzed in
-Figure~\ref{fig:f_vs_fbar}. Correctable images had a single-valued relationship
-between their measured \fbar{} values at high and low redshifts (white regions
-in Figure~\ref{fig:f_vs_fbar}). Galaxies with a lower-limit on \fbar{} had a
-non single-valued relationship (blue regions). NEI images had undetermined
-relationships due to a lack of data ($N<5$) in their corresponding $z$-$\mu$
-bins (gray regions). Only 17\% (maximum) of \ferengi{} galaxies in the sample
-were considered ``correctable'', which is not sufficient to compute a $\zeta$
-function applicable to the Hubble data.   \label{tbl:ferengi_bar_corrections}}
+\caption{Distribution of \ferengi{} images analyzed in Figure~\ref{fig:f_vs_fbar}.
+Correctable images had a single-valued relationship between their measured \fbar{} values at high and low redshifts (white regions in Figure~\ref{fig:f_vs_fbar}).
+Galaxies with a lower-limit on \fbar{} had a non single-valued relationship (blue regions).
+NEI images had undetermined relationships due to a lack of data ($N<5$) in their corresponding $z$-$\mu$ bins (gray regions).
+Only 17\% (maximum) of \ferengi{} galaxies in the sample were considered ``correctable'', which is not sufficient to compute a $\zeta$ function applicable to the Hubble data.
+\label{tbl:ferengi_bar_corrections}}
 \begin{tabular}{lrr}

### 2016-05-17 writeup/gz_hubble_data.tex
Smaller changes (via email) from CJL.

@@
 identification and geometry.  This paper also describes a new method for
-calibrating morphological bias by using artificially-redshifted galaxy images
-as a baseline. The GZH catalog contains both raw and calibrated morphological
-vote fractions for $150,771$~galaxies, providing the largest dataset to date
+calibrating morphologies for galaxies of different luminosities and at
+different redshifts by using artificially-redshifted galaxy images as a
+baseline. The GZH catalog contains both raw and calibrated morphological vote
+fractions for $150,771$~galaxies, providing the largest dataset to date
 suitable for large-scale studies of galaxy evolution out to $z\sim1$. 
@@
 black hole. The morphology is also closely related to the local environment of
-a galaxy, as interactions such as tides, shocks in cluster environments and
-direct mergers can all influence a galaxy's internal structure.  For
-$M^\star$~galaxies in the local Universe, this interplay between the physical
-development of a galaxy and its external appearance typically manifests at the
-most basic level as the difference between bulge-dominated systems with
-no/little spiral structure (early-types) and disk-dominated,
-rotationally-supported galaxies (late-types) frequently exhibiting spiral arms.
-This dichotomy has been used to explore much of the astrophysics governing
-galaxy formation and evolution, and has been shown to be closely linked with
-other galactic properties such as stellar mass, halo mass, bolometric
-luminosity, black hole activity, effective radius, and the relative ages of the
-stellar populations.
+the galaxy, as mutual interactions such as tides, shocks in cluster
+environments, and direct mergers can all change the shape of the galaxy's
+gravitational potential. For $M^\star$~galaxies in the local Universe, this
+interplay between the physical development of a galaxy and its external
+appearance typically manifests at the most basic level as the difference
+between bulge-dominated systems with no/little spiral structure (early-types)
+and disk-dominated, rotationally-supported galaxies (late-types) frequently
+exhibiting spiral arms.  This dichotomy has been used to explore much of the
+astrophysics governing galaxy formation and evolution, and has been shown to be
+closely linked with other galactic properties such as stellar mass, halo mass,
+bolometric luminosity, black hole activity, effective radius, and the relative
+ages of the stellar populations.
 
@@
 (roughly 6~Gyr after the Big Bang), many galaxies are still in the process of
-assembling the baryonic and stellar mass required to reproduce the mature,
-coherent structures seen at the present day. This growth occurs via a variety
-of pathways, including accretion from large-scale galactic filaments onto halos
-via streaming, mergers of individual halos, conversion of gas into stars via
-gravitational collapse, etc. The accrual of baryons can be slowed or even
-reversed via feedback from stellar winds, supernovae, and active black holes.
-Each of these processes affects galaxy morphology in different ways, and so an
-accurate measurement of morphological demographics as a function of redshift
-provides an extremely powerful observational constraint on the physics involved
-\citep[for recent reviews see][]{but13,con14}.
+assembling the baryonic mass required to reproduce the mature, coherent
+structures seen in the present day. This growth occurs in a variety of
+pathways, including accretion of baryons from large-scale galactic filaments
+onto halos via streaming, mergers of individual dark matter halos along with
+their baryons, conversion of gas into stars through gravitational collapse and
+star formation, etc. The process can also be slowed or even reversed via
+feedback from stellar winds, supernovae, and active black holes.  Each of these
+processes affects the galaxy morphology in different ways, and so an accurate
+measurement of the demographics as a function of redshift provides an extremely
+powerful observational constraint on the physics involved \citep[for recent
+reviews see][]{but13,con14}.
 
@@
 Observational studies of galaxies at high-redshift also display a wide range of
-morphological types, many of which are rare or absent at $z\sim0$. Although
-spheroids and disks are present, they are typically much more compact than
-those in the local Universe. There is also a significant population of more
-irregular, massive galaxies, including mergers, tadpoles, chains,
-double-clumps, and clump-clusters \citep{elm05,elm07,cam11a,for11a,kar15}. In
-contrast, while grand-design spirals have been observed as far back as $z=2.18$
-\citep{law12}, their spatial density suggests that they are exceedingly rare,
-with a very low fraction of undisturbed disks \citep{mor13}. Current
+morphological types, many of which are rare or absent at $z\sim0$.  These
+include spheroids and disks (akin to the ellipticals and spirals seen in the
+local Universe), but also a significant population of massive, more irregular
+galaxies, including mergers, tadpoles, chains, double-clumps, and
+clump-clusters \citep{elm05,elm07,cam11a,for11a,kar15}.  In contrast, while
+grand-design spirals have been observed as far back as $z=2.18$ \citep{law12},
+their spatial density suggests that they are exceedingly rare at these high
+redshifts, with a very low overall disk fraction \citep{mor13}. Current
 observational data thus strongly suggests that the classical Hubble
@@
 $\sim5-10~\mathrm{kpc}/^{\prime\prime}$ \citep{wri06}. \hst{} can thus resolve
-much of the structure for a Milky Way-sized galaxy (at least for distinguishing
-a disk from a bulge), but will be limited for more compact structures. Since
-the size of galaxies evolves as roughly $r\propto(1+z)^{-1}$
-\citep{mao98,law12a}, the compact sizes of high-redshift galaxies make detailed
-morphologies a challenge even for \hst{} \citep{che12}. The public availability
-of more than $10^5$~galaxies in archival imaging across various studies gives a
-data sample with the potential for high statistical significance.
+much of the structure for a Milky Way-sized galaxy out to moderately high
+redshifts (at least distinguishing a disk from a bulge), but is limited for
+more compact structures. Since the size of galaxies evolves as roughly
+$r\propto(1+z)^{-1}$ \citep{mao98,law12a}, the compact sizes of high-redshift
+galaxies make detailed morphologies a challenge even for \hst{} \citep{che12}.
+The public availability of more than $10^5$~galaxies in archival imaging across
+various studies gives a data sample with the potential for high statistical
+significance.
 
@@
 In the ACS-GC \citep{gri12}, individual galaxies were identified using a
-combination of \sextractor{} \citep{ber96} and the galaxy-profile fitting
+combination of \sextractor{} \citep{ber96} and the \sersic-profile fitting
 framework \galapagos{} \citep{bar12}. GZH included all galaxies with $m<23.5$,
@@
 RGB channels. The co-added Stripe~82 images were assembled from runs 106 and
-206 in DR7 and processed into color composites in a corresponding manner.
+206 in DR7 and processed into color composites in the same manner as previous
+iterations of Galaxy~Zoo.
 
@@
 $L_\mathrm{ratio} \equiv L_\mathrm{galaxy}/L_\mathrm{AGN}$ is in
-$(0.2,1.0,2.0,5.0,10.0,50.0)$. Combining these parameters generated 15~images
-with different simulated AGN for each host.
+$(0.2,1.0,2.0,5.0,10.0,50.0)$. This range was selected to run from AGN which
+were all but undetectable through to those which dominate the galaxy, providing
+coverage of all plausible effects. Combining these parameters generated
+15~images with different simulated AGN for each host.
 
 Two sets of simulated AGN were generated in GZH. The first set (version~1) was
-assembled from 95~galaxies from GOODS-S imaging and empirical PSFs made by combining stars in the GOODS fields using the PSF creation tools in \texttt{daophot}. 
-The second set (version~2) was assembled from 96~galaxies in GOODS-S; this
-version used simulated PSFs from \texttt{TinyTim} \citep{kri93}, drizzled using the same procedures as those used in reduction of the GOODS-S images \citep{koe02,koe03,gia04}.
-The use of these 2 versions facilitates comparisons between these different PSF creation methods, which are widely used in AGN host galaxy morphology studies \citep[e.g.,][]{san04,sim08,pie10a,simm11}.
+assembled from 95~galaxies from GOODS-S imaging and empirical PSFs made by
+combining stars in the GOODS fields using the PSF creation tools in
+\texttt{daophot}.  The second set (version~2) was assembled from 96~galaxies in
+GOODS-S; this version used simulated PSFs from \texttt{TinyTim} \citep{kri93},
+drizzled using the same procedures as those used in reduction of the GOODS-S
+images \citep{koe02,koe03,gia04}. The use of these 2 versions facilitates
+comparisons between these different PSF creation methods, which are widely used
+in AGN host galaxy morphology studies
+\citep[e.g.,][]{san04,sim08,pie10a,simm11}.  Each PSF creation method has
+advantages and disadvantages: the empirical PSFs better represent the nuances
+of the PSF in the specific data being used and look more realistic at lower
+luminosities, but the extended features of the noiseless \texttt{TinyTim} PSFs
+are visually more realistic at higher luminosities.
 % okay so I'm a cheeky self-citing biyotch
-Each PSF creation method has advantages and disadvantages: the empirical PSFs better represent the nuances of the PSF in the specific data being used and look more realistic at lower luminosities, but the extended features of the noiseless \texttt{TinyTim} PSFs are visually more realistic at higher luminosities.
 
@@
 manner and evenly distributed with unaltered images of the galaxies.
-Classifiers were not explicitly told that the images had been altered during classification, as the
-goal was to measure the effect on normal classifications in as unbiased a
-manner as possible.
-Following classification, a classifier could view a page with additional details about each galaxy they had classified; where applicable these pages contained further information regarding image modifications.
+Classifiers were not explicitly told that the images had been altered during
+classification, as the goal was to measure the effect on normal classifications
+in as unbiased a manner as possible. Following classification, a classifier
+could view a page with additional details about each galaxy they had
+classified; where applicable these pages contained further information
+regarding image modifications.
 
@@
 For galaxies which have published redshifts from multiple sources, the
-following algorithm was used to select the $\tt Z\_BEST$ quantity. The first
-priority is spectroscopic redshifts; these were taken from the ACS-GC
-\citep{gri12}, 3DHST \citep{mom15}, and MUSYC \citep{car10} catalogs. A
-high-quality spectroscopic redshift in the ACS-GC is the primary option; if
-none is available, then $\tt Z\_BEST$ uses the spectroscopic redshifts in
-3DHST, and then MUSYC. For galaxies with multiple spectroscopic redshifts, more
-than 98\% are consistent ($\Delta z<0.001$), and so the order of selection
-made no practical difference. Galaxies with inconsistent spectroscopic
-redshifts between any pair of catalogs are marked with a flag in
-Table~\ref{tbl:catalog_hst}. If no spectroscopic redshifts were available, the
-1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST, MUSYC,
-UltraVISTA;][]{ilb13} and UltraVISTA grism data were used to select the
-redshift with the smallest error. 
+following algorithm was used to select the $\tt Z\_BEST$ quantity. A
+high-quality spectroscopic redshift in the ACS-GC is the primary option,
+provided in the ACS-GC \citep{gri12}, 3DHST \citep{mom15}, and MUSYC
+\citep{car10} catalogs and used in that order. For galaxies with multiple
+spectroscopic redshifts, more than 98\% are consistent ($\Delta z<0.001$), and
+so the order of selection made no practical difference. Galaxies with
+inconsistent spectroscopic redshifts between any pair of catalogs are marked
+with a flag in Table~\ref{tbl:catalog_hst}. If no spectroscopic redshifts were
+available, the 1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST,
+MUSYC, UltraVISTA;][]{ilb13} and UltraVISTA grism data were used to select the
+estimated redshift with the smallest error. 
 %Table~\ref{tbl:redshifts} shows the results of this selection.
@@
 
-The GZH decision tree had four broad sets of morphologies. The first option
+The GZH decision tree was designed to remain close to that used by GZ2 while
+taking account of the likely differences in high redshift systems, and has four
+broad sets of morphologies classified by the users.  The first option
 designated stars or image artifacts (the result of either bad data or incorrect
-classification by the ACS pipeline as a galaxy); in this case, the
+identification as a galaxy by the ACS pipeline); in this case, the
 classification process ended and no further questions were asked. The second
-set were smooth galaxies, intended to select ellipticals/early-types;
-classifiers also measured the relative axial ratio (roundness) for these
+set was smooth galaxies, intended to select ellipticals/early-types;
+volunteers also indicate the relative axial ratio (roundness) for these
 galaxies. The third set was for disk/late-type galaxies, which measured the
@@
 
-As a first step to producing consensus classifications of each galaxy, 
-the votes of individual classifiers in GZH were combined to make a vote
-fraction for each response ($f_{response}$) to a question in the classification
-tree. Votes were subsequently weighted and re-combined in an iterative method similar that in 
-previous versions of Galaxy~Zoo \citep{lan08,wil13}, using a method chosen 
-to be as egalitarian as possible while also identifying and downweighting classifiers 
-who frequently disagreed with others. The weighting factor $(w)$ was 1 for the
-top 95\% of classifiers, as ranked by consistency. For the bottom 5\% of
-classifiers, $w$ was designed to drop smoothly and was effectively zero for the
-bottom 1\%.  Since this only affected a tiny percentage of the classifiers (and
+As a first step to producing a consensus measurement of each galaxy, the votes
+of individual volunteers who classified galaxies in GZH were combined to make a
+vote fraction for each response ($f_{response}$) to a question in the decision
+tree. Votes were subsequently weighted and re-combined in an iterative method
+similar that in previous versions of Galaxy~Zoo \citep{lan08,wil13}, using a
+method chosen to be as egalitarian as possible while also identifying and
+downweighting classifiers who frequently disagreed with others. The weighting
+factor $(w)$ was 1 for the top 95\% of classifiers, as ranked by consistency.
+For the bottom 5\% of classifiers, $w$ was designed to drop smoothly and was
+effectively zero for the bottom 1\% in the distribution function. Since this
+only affected a tiny percentage of the classifiers (and an even smaller
+percentage of the classifications) the overall effect on the GZH dataset was
+minimal. The method was effective, however, at filtering out contributions from
+randomly classifying or malicious participants.
 % would be good to quantify "tiny" and "even smaller [than tiny]"
-an even smaller percentage of the classifications) the overall effect on the
-GZH dataset was minimal. The method was effective, however, at filtering out
-contributions from random or deliberately malicious classifiers.
 
@@
 image quality (\ie, the reduction in physical resolution, surface brightness
-dimming, etc). For both previous releases of GZ morphologies, a correction for
+dimming, etc). For both previous releases of Galaxy~Zoo morphologies, a correction for
 redshift-dependent bias was applied based on matching the classification
@@
 The approach used in GZH for correcting the weighted classifications for redshift
-bias rests on the assumption that the \emph{amount} of bias is a function of
+bias rests on the assumption that the \emph{degree} of bias is a function of
 the apparent size and brightness of the image as seen on screen. This is
@@
 \ferengi{} images over all the evolutionary correction factors. It is assumed
-that the ``true'' (ie, debiased) vote fraction $f_{\mu,z}$ for a galaxy can be
-expressed as:
+that the ``true'' (ie, debiased) vote fraction $f_{\mu,z}$ for an
+artificially-redshifted galaxy can be expressed as:
 
@@
 structure (Tasks 12--14) is only $4\pm4$ for the \ferengi{} sample; while this
-is distribution is strongly bimodal (reflecting the true morphologies of
+distribution is strongly bimodal (reflecting the true morphologies of
 selected galaxies), the very low absolute numbers of votes introduce very high
@@
 is a crucial factor in evaluating results. \citet{mas11c,mel14,che15}, and
-\citet{gal15} are examples of GZ papers which select morphologies in this way.
+\citet{gal15} are examples of Galaxy~Zoo papers which select morphologies in this way.
 
@@
 endorsement of any particular method, but as an exploration of the strengths
-and weaknesses of the GZ crowdsourced catalogs as compared to products made
+and weaknesses of the Galaxy~Zoo crowdsourced catalogs as compared to products made
 with machine learning, automatic fits, and expert visual classification.
@@
 
-KS gratefully acknowledges support from Swiss National Science Foundation Grant
-PP00P2\_138979/1.
+The development and hosting of Galaxy Zoo Hubble was supported by a grant from
+the Alfred P. Sloan Foundation. The Zooniverse acknowledges support from a
+Google Global Impact Award. KS gratefully acknowledges support from Swiss
+National Science Foundation Grant PP00P2\_138979/1.
 
@@
 supplementary table. This section analyzes the effect of image depth on the
-ability of the GZ classifiers to identify features or disk structure in the images.
+ability of the Galaxy~Zoo classifiers to identify features or disk structure in the images.
 

### 2016-05-17 writeup/gz_hubble_data.tex
adding flags to Task 01 in datatables and description of such in text

--- 2016-05-17 writeup/gz_hubble_data.tex
@@
 $\tt best = weighted$.
+Flags are also given for the three responses of Task 01 to identify clean samples of galaxies with high likelihoods of being smooth, featured, or an artifact.
+These are set as $\tt smooth/featured/artifact\_flag=1$ if $\rm f_{smooth/features/artifact\_best}>0.8$.
+For a galaxy to be flagged as ``smooth'', an additional criterion of $\tt correction\_type =~$0, 1, or 2 is applied.
+This is to account for the uncertainty in distinguishing between genuine ellipticals and disks whose features have been washed out due to surface brightness and redshift effects, as described in Section~\ref{sec:debiasing}.
 
@@
 \tabletypesize{\scriptsize}
-\begin{deluxetable*}{lllcrllllll|c}
+\begin{deluxetable*}{lllcrlllllll|c}
 \centering
@@
 \multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
-\multicolumn{6}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
+\multicolumn{7}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
 \colhead{$\ldots$}
 \\
-\colhead{Project ID} & 
-\colhead{Hubble ID} & 
+\colhead{Zooniverse ID} & 
+\colhead{Survey ID} & 
 \colhead{Imaging} & 
@@
 \colhead{upper~limit} &
+\colhead{flag} &
 \colhead{}
@@
 \startdata
-AHZ100002g  & 10010842  & AEGIS             & 0        & 127       & 0.118    & 0.128     & 0.085    & 0.085    & 0.226     & 0.226    \\
-AHZ100002h  & 10010870  & AEGIS             & 4        & 127       & 0.567    & 0.592     & 0.927    & 0.592    & $-$       & $-$      \\
+AHZ100002g  & 10010842  & AEGIS             & 0        & 127       & 0.118    & 0.128     & 0.085    & 0.085    & 0.226     & 0.226 & 0   \\
+AHZ100002h  & 10010870  & AEGIS             & 4        & 127       & 0.567    & 0.592     & 0.927    & 0.592    & $-$       & $-$   &0   \\
 $\ldots$    \\
-AHZ20004kd  & 20014731  & COSMOS            & 3        &  44       & 0.682    & 0.675     & 0.147    & 0.675    & $-$       & $-$      \\
-AHZ20004ke  & 20014732  & COSMOS            & 2        &  45       & 0.689    & 0.756     & 0.893    & 0.756    & $-$       & $-$      \\
+AHZ20004kd  & 20014731  & COSMOS            & 3        &  44       & 0.682    & 0.675     & 0.147    & 0.675    & $-$       & $-$   &0   \\
+AHZ20004ke  & 20014732  & COSMOS            & 2        &  45       & 0.689    & 0.756     & 0.893    & 0.756    & $-$       & $-$   &0   \\
 $\ldots$    \\
-AHZ400043g  & 90022729  & GEMS              & 1        & 121       & 0.702    & 0.733     & 0.487    & 0.734    & 0.483     & 0.800    \\
-AHZ4000416  & 90022735  & GEMS              & 1        & 127       & 0.646    & 0.698     & 0.508    & 0.698    & 0.171     & 0.727    \\
+AHZ400043g  & 90022729  & GEMS              & 1        & 121       & 0.702    & 0.733     & 0.487    & 0.734    & 0.483     & 0.800 &0   \\
+AHZ4000416  & 90022735  & GEMS              & 1        & 127       & 0.646    & 0.698     & 0.508    & 0.698    & 0.171     & 0.727 &0   \\
 $\ldots$    \\
-AGZ0007z47  & 10014     & GOODS-N-FULLDEPTH & 1        & 40        & 0.475    & 0.475     & 0.197    & 0.475    & 0.011     & 0.496    \\
-AGZ0007z48  & 10017     & GOODS-N-FULLDEPTH & 3        & 40        & 0.675    & 0.675     & 0.048    & 0.675    & 0.168     & 0.669    \\
+AGZ0007z47  & 10014     & GOODS-N-FULLDEPTH & 1        & 40        & 0.475    & 0.475     & 0.197    & 0.475    & 0.011     & 0.496 &0   \\
+AGZ0007z48  & 10017     & GOODS-N-FULLDEPTH & 3        & 40        & 0.675    & 0.675     & 0.048    & 0.675    & 0.168     & 0.669 &0  \\
 $\ldots$    \\
-AGZ00083jb  & 8869      & GOODS-S-FULLDEPTH & 1        & 40        & 0.425    & 0.425     & 0.109    & 0.425    & 0.070     & 0.548    \\
-AGZ00083jc  & 8878      & GOODS-S-FULLDEPTH & 0        & 40        & 0.205    & 0.205     & 0.048    & 0.048    & $-$0.005  & 0.287    \\
+AGZ00083jb  & 8869      & GOODS-S-FULLDEPTH & 1        & 40        & 0.425    & 0.425     & 0.109    & 0.425    & 0.070     & 0.548 &0   \\
+AGZ00083jc  & 8878      & GOODS-S-FULLDEPTH & 0        & 40        & 0.205    & 0.205     & 0.048    & 0.048    & $-$0.005  & 0.287 &0   \\
 $\ldots$    \\
@@
 \startdata
-AHZF000001  &   20000002    &   COSMOS  &   1   &   48 &  0.708   &     0.755   &   0.228    &    0.754 &   0.325   &   0.829  \\
-AHZF000003  &   20000004    &   COSMOS  &   3   &   49 &  0.367   &     0.379   &   0.100    &    0.379 &   0.198   &   0.198  \\
-AHZF000004  &   20000006    &   COSMOS  &   3   &   49 &  0.265   &     0.271   &   0.010    &    0.270 &   $-$	    &   $-$    \\
-AHZF00000z  &   20000102    &   COSMOS  &   1   &   44 &  0.727   &     0.78    &   0.233    &    0.780 &   0.316   &   0.820  \\
-AHZF000010  &   20000104    &   COSMOS  &   2   &   53 &  0.811   &     0.849   &   0.904    &    0.848 &   $-$	    &   $-$    \\
+AHZF000001  &   20000002    &   COSMOS  &   1   &   48 &  0.708   &     0.755   &   0.228    &    0.754 &   0.325   &   0.829 &0 \\
+AHZF000003  &   20000004    &   COSMOS  &   3   &   49 &  0.367   &     0.379   &   0.100    &    0.379 &   0.198   &   0.198 &0 \\
+AHZF000004  &   20000006    &   COSMOS  &   3   &   49 &  0.265   &     0.271   &   0.010    &    0.270 &   $-$	    &   $-$   &0 \\
+AHZF00000z  &   20000102    &   COSMOS  &   1   &   44 &  0.727   &     0.78    &   0.233    &    0.780 &   0.316   &   0.820 &0 \\
+AHZF000010  &   20000104    &   COSMOS  &   2   &   53 &  0.811   &     0.849   &   0.904    &    0.848 &   $-$	    &   $-$   &0 \\
 $\ldots$    \\
@@
 \tabletypesize{\scriptsize}
-\begin{deluxetable*}{lllcrllllll|c}
+\begin{deluxetable*}{lllcrllllllll|c}
 \centering
@@
 \startdata
-AHZC000001	&   20000002	&   COSMOS	&   1	&   168	&   0.615   &   0.664   &   0.160   &  0.663   &  0.271    &  0.775    \\
-AHZC000003	&   20000004	&   COSMOS	&   0	&   235	&   0.333   &   0.364   &   0.002   &  0.002   &  0.063    &  0.063    \\
-AHZC000004	&   20000006	&   COSMOS	&   3	&   316	&   0.235   &   0.252   & $-0.011$  &  0.252   &  $-$	    &  $-$      \\
-AHZC00000z	&   20000102	&   COSMOS	&   1	&   207	&   0.755   &   0.757   &   0.272   &  0.756   &  0.249    &  0.796    \\
-AHZC000010	&   20000104	&   COSMOS	&   2	&   158	&   0.843   &   0.882   &   0.936   &  0.881   &  $-$	    &  $-$      \\
+AHZC000001	&   20000002	&   COSMOS	&   1	&   168	&   0.615   &   0.664   &   0.160   &  0.663   &  0.271    &  0.775 &0   \\
+AHZC000003	&   20000004	&   COSMOS	&   0	&   235	&   0.333   &   0.364   &   0.002   &  0.002   &  0.063    &  0.063 &0   \\
+AHZC000004	&   20000006	&   COSMOS	&   3	&   316	&   0.235   &   0.252   & $-0.011$  &  0.252   &  $-$	    &  $-$  &1    \\
+AHZC00000z	&   20000102	&   COSMOS	&   1	&   207	&   0.755   &   0.757   &   0.272   &  0.756   &  0.249    &  0.796 &0   \\
+AHZC000010	&   20000104	&   COSMOS	&   2	&   158	&   0.843   &   0.882   &   0.936   &  0.881   &  $-$	    &  $-$  &1    \\
 $\ldots$    \\
@@
 \startdata
-AHZ3000001  &   50000000    &     GOODS-N   &   0   &   123	&   0.390   &   0.415	&   0.090 &   0.090 &   $-$     &   $-$      \\
-AHZ3000002  &   50000001    &     GOODS-N   &   2   &   126	&   0.341	&   0.355	&   0.356 &   0.356 &   0.220	&   0.279    \\
-AHZ3000003  &   50000005    &     GOODS-N   &   1   &   129	&   0.760   &   0.826	&   0.633 &   0.825 &   0.596	&   0.834    \\
-AHZ3000004  &   50000008    &     GOODS-N   &   1   &   120	&   0.758	&   0.787	&   0.639 &   0.787 &   0.658	&   0.834    \\
-AHZ3000005  &   50000010    &     GOODS-N   &   1   &   123	&   0.854	&   0.890   &   0.611 &   0.889 &   0.597	&   0.914    \\
+AHZ3000001  &   50000000    &     GOODS-N   &   0   &   123	&   0.390   &   0.415	&   0.090 &   0.090 &   $-$     &   $-$ &0     \\
+AHZ3000002  &   50000001    &     GOODS-N   &   2   &   126	&   0.341	&   0.355	&   0.356 &   0.356 &   0.220	&   0.279 &0   \\
+AHZ3000003  &   50000005    &     GOODS-N   &   1   &   129	&   0.760   &   0.826	&   0.633 &   0.825 &   0.596	&   0.834 &0   \\
+AHZ3000004  &   50000008    &     GOODS-N   &   1   &   120	&   0.758	&   0.787	&   0.639 &   0.787 &   0.658	&   0.834 &0   \\
+AHZ3000005  &   50000010    &     GOODS-N   &   1   &   123	&   0.854	&   0.890   &   0.611 &   0.889 &   0.597	&   0.914 &0  \\
 $\ldots$    \\
@@
 \tabletypesize{\scriptsize}
-\begin{deluxetable*}{lllcrllll|c}
+\begin{deluxetable*}{lllcrlllll|c}
 \centering
@@
 \multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
-\multicolumn{4}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
+\multicolumn{5}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
 \colhead{$\ldots$}
 \\
-\colhead{Project ID} & 
-\colhead{SDSS DR7 ObjID} & 
+\colhead{Zooniverse ID} & 
+\colhead{Survey ID} & 
 \colhead{Imaging} & 
@@
 \colhead{best} &
+\colhead{flag} &
 \colhead{}
@@
 \startdata
-AHZ5000001  &   587730845812064684  &   SDSS    &     2 &   41  &   0.585   &    0.595  &   0.759   &   0.594   \\
-AHZ5000002  &   587730845812065247  &   SDSS    &     2 &   46  &   0.609   &    0.651  &   0.897   &   0.651   \\
-AHZ5000003  &   587730845812196092  &   SDSS    &     2 &   51  &   0.039   &    0.044  &   0.067   &   0.043   \\
-AHZ5000004  &   587730845812196825  &   SDSS    &     2 &   35  &   0.514   &    0.605  &   0.928   &   0.605   \\
-AHZ5000005  &   587730845812524122  &   SDSS    &     2 &   47  &   0.766   &    0.812  &   1.038   &   0.810   \\
-AHZ5000006  &   587730845812654984  &   SDSS    &     2 &   42  &   0.5	    &    0.542  &   0.680   &   0.541   \\
-AHZ5000007  &   587730845812655541  &   SDSS    &     2 &   41  &   0.488   &    0.526  &   0.697   &   0.525   \\
-AHZ5000008  &   587730845812720365  &   SDSS    &     2 &   53  &   0.792   &    0.84   &   1.050   &   0.839   \\
-AHZ5000009  &   587730845812720640  &   SDSS    &     4 &   43  &   0.0	    &    0.0    &   0.0	    &   0.0	    \\
-AHZ500000a  &   587730845812720699  &   SDSS    &     2 &   40  &   0.425   &    0.478  &   0.588   &   0.477   \\
+AHZ5000001  &   587730845812064684  &   SDSS    &     2 &   41  &   0.585   &    0.595  &   0.759   &   0.594 &0  \\
+AHZ5000002  &   587730845812065247  &   SDSS    &     2 &   46  &   0.609   &    0.651  &   0.897   &   0.651 &0  \\
+AHZ5000003  &   587730845812196092  &   SDSS    &     2 &   51  &   0.039   &    0.044  &   0.067   &   0.043 &0  \\
+AHZ5000004  &   587730845812196825  &   SDSS    &     2 &   35  &   0.514   &    0.605  &   0.928   &   0.605 &0  \\
+AHZ5000005  &   587730845812524122  &   SDSS    &     2 &   47  &   0.766   &    0.812  &   1.038   &   0.810 &1  \\
+AHZ5000006  &   587730845812654984  &   SDSS    &     2 &   42  &   0.5	    &    0.542  &   0.680   &   0.541 &0  \\
+AHZ5000007  &   587730845812655541  &   SDSS    &     2 &   41  &   0.488   &    0.526  &   0.697   &   0.525 &0  \\
+AHZ5000008  &   587730845812720365  &   SDSS    &     2 &   53  &   0.792   &    0.84   &   1.050   &   0.839 &1  \\
+AHZ5000009  &   587730845812720640  &   SDSS    &     4 &   43  &   0.0	    &    0.0    &   0.0	    &   0.0   &0    \\
+AHZ500000a  &   587730845812720699  &   SDSS    &     2 &   40  &   0.425   &    0.478  &   0.588   &   0.477 &0  \\
 $\ldots$    \\
@@
 \startdata
-AHZ6000001  & 8647474690312306978   &   SDSS    &    4  & 40  & 0.275   &    0.289  &   0.762   &   0.289   & \\
-AHZ6000002  & 8647474690312307154   &   SDSS    &    2  & 43  & 0.605   &    0.634  &   0.858   &   0.635   & \\
-AHZ6000003  & 8647474690312307877   &   SDSS    &    2  & 51  & 0.608   &    0.627  &   0.906   &   0.627   & \\
-AHZ6000004  & 8647474690312308301   &   SDSS    &    4  & 52  & 0.038   &    0.038  &   0.723   &   0.038   & \\
-AHZ6000005  & 8647474690312308318   &   SDSS    &    2  & 44  & 0.614   &    0.632  &   0.776   &   0.631   & \\
-AHZ6000006  & 8647474690312308880   &   SDSS    &    2  & 36  & 0.667   &    0.683  &   0.901   &   0.683   & \\
-AHZ6000007  & 8647474690312372644   &   SDSS    &    4  & 48  & 0.646   &    0.674  &   1.145   &   0.674   & \\
-AHZ6000008  & 8647474690312372789   &   SDSS    &    4  & 45  & 0.489   &    0.571  &   0.964   &   0.570   & \\
-AHZ6000009  & 8647474690312372931   &   SDSS    &    4  & 47  & 0.553   &    0.587  &   0.926   &   0.587   & \\
-AHZ600000a  & 8647474690312373190   &   SDSS    &    4  & 47  & 0.574   &    0.559  &   1.008   &   0.559   & \\
+AHZ6000001  & 8647474690312306978   &   SDSS    &    4  & 40  & 0.275   &    0.289  &   0.762   &   0.289   & 0&\\
+AHZ6000002  & 8647474690312307154   &   SDSS    &    2  & 43  & 0.605   &    0.634  &   0.858   &   0.635   & 0&\\
+AHZ6000003  & 8647474690312307877   &   SDSS    &    2  & 51  & 0.608   &    0.627  &   0.906   &   0.627   & 0&\\
+AHZ6000004  & 8647474690312308301   &   SDSS    &    4  & 52  & 0.038   &    0.038  &   0.723   &   0.038   & 0&\\
+AHZ6000005  & 8647474690312308318   &   SDSS    &    2  & 44  & 0.614   &    0.632  &   0.776   &   0.631   & 0&\\
+AHZ6000006  & 8647474690312308880   &   SDSS    &    2  & 36  & 0.667   &    0.683  &   0.901   &   0.683   & 0&\\
+AHZ6000007  & 8647474690312372644   &   SDSS    &    4  & 48  & 0.646   &    0.674  &   1.145   &   0.674   & 0&\\
+AHZ6000008  & 8647474690312372789   &   SDSS    &    4  & 45  & 0.489   &    0.571  &   0.964   &   0.570   & 0&\\
+AHZ6000009  & 8647474690312372931   &   SDSS    &    4  & 47  & 0.553   &    0.587  &   0.926   &   0.587   & 0&\\
+AHZ600000a  & 8647474690312373190   &   SDSS    &    4  & 47  & 0.574   &    0.559  &   1.008   &   0.559   & 0&\\
 $\ldots$    \\
@@
 \tabletypesize{\scriptsize}
-\begin{deluxetable*}{lllccccrrrrrrr|c}
+\begin{deluxetable*}{lllccccrrrrrrrr|c}
 \centering
@@
  & & & & & & & &
-\multicolumn{6}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
+\multicolumn{7}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
 \colhead{$\ldots$}
 \\
-\colhead{Project ID} & 
-\colhead{SDSS DR7 ObjID} & 
+\colhead{Zooniverse ID} & 
+\colhead{Survey ID} & 
 \colhead{Imaging} & 
@@
 \colhead{upper limit} &
+\colhead{flag} &
 \colhead{}
@@
 \startdata
-AHZ7000001  &   90024700  &   GEMS    &   1   &   1   &   0.2	    &   1   &   42	&   0.238   &   0.239   &   $-$0.110  &       0.238  &  $-$0.113    &     0.287  \\
-AHZ7000002  &   90024700  &   GEMS    &   1   &   1   &   1.0	    &   1   &   51	&   0.255   &   0.265   &   $-$0.107  &       0.264  &  $-$0.128    &     0.272  \\
-AHZ7000003  &   90024700  &   GEMS    &   0   &   1   &   5.0	    &   1   &   47	&   0.170   &   0.167   &   $-$0.018  &    $-$0.018  &  $-$0.049    &     0.033  \\
-AHZ7000004  &   90024700  &   GEMS    &   0   &   1   &   10.0    &   1   &   41	&   0.195   &   0.195   &      0.045  &       0.045  &     0.044    &     0.127  \\
-AHZ7000005  &   90024700  &   GEMS    &   0   &   1   &   50.0    &   1   &   47	&   0.170   &   0.178   &      0.067  &       0.067  &     0.146    &     0.167  \\
+AHZ7000001  &   90024700  &   GEMS    &   1   &   1   &   0.2	    &   1   &   42	&   0.238   &   0.239   &   $-$0.110  &       0.238  &  $-$0.113    &     0.287  &0\\
+AHZ7000002  &   90024700  &   GEMS    &   1   &   1   &   1.0	    &   1   &   51	&   0.255   &   0.265   &   $-$0.107  &       0.264  &  $-$0.128    &     0.272  &0\\
+AHZ7000003  &   90024700  &   GEMS    &   0   &   1   &   5.0	    &   1   &   47	&   0.170   &   0.167   &   $-$0.018  &    $-$0.018  &  $-$0.049    &     0.033  &0\\
+AHZ7000004  &   90024700  &   GEMS    &   0   &   1   &   10.0    &   1   &   41	&   0.195   &   0.195   &      0.045  &       0.045  &     0.044    &     0.127  &0\\
+AHZ7000005  &   90024700  &   GEMS    &   0   &   1   &   50.0    &   1   &   47	&   0.170   &   0.178   &      0.067  &       0.067  &     0.146    &     0.167  &0\\
 $\ldots$    \\
-AHZ700013m  &   90024700  &   GEMS    &   0   &   2   &   0.0	    &   0   &   35	&   0.171   &   0.136   &      0.011  &       0.011  &     0.029    &      0.112 \\
-AHZ700013n  &   90024700  &   GEMS    &   1   &   2   &   0.2	    &   1   &   20	&   0.150   &   0.158   &   $-$0.278  &       0.049  &  $-$0.351    &      0.049 \\
-AHZ700013o  &   90024700  &   GEMS    &   1   &   2   &   1.0	    &   1   &   32	&   0.281   &   0.300   &   $-$0.086  &       0.281  &  $-$0.119    &      0.281 \\
-AHZ700013p  &   90024700  &   GEMS    &   0   &   2   &   5.0	    &   1   &   29	&   0.103   &   0.115   &   $-$0.098  &    $-$0.098  &  $-$0.152    &   $-$0.069 \\
-AHZ700013q  &   90024700  &   GEMS    &   0   &   2   &   10.0    &   1   &   35	&   0.171   &   0.181   &      0.027  &       0.027  &     0.023    &      0.106 \\
-AHZ700013r  &   90024700  &   GEMS    &   0   &   2   &   50.0    &   1   &   34	&   0.206   &   0.206   &   $-$0.005  &    $-$0.005  &  $-$0.056    &      0.026 \\
+AHZ700013m  &   90024700  &   GEMS    &   0   &   2   &   0.0	    &   0   &   35	&   0.171   &   0.136   &      0.011  &       0.011  &     0.029    &      0.112 &0\\
+AHZ700013n  &   90024700  &   GEMS    &   1   &   2   &   0.2	    &   1   &   20	&   0.150   &   0.158   &   $-$0.278  &       0.049  &  $-$0.351    &      0.049 &0\\
+AHZ700013o  &   90024700  &   GEMS    &   1   &   2   &   1.0	    &   1   &   32	&   0.281   &   0.300   &   $-$0.086  &       0.281  &  $-$0.119    &      0.281 &0\\
+AHZ700013p  &   90024700  &   GEMS    &   0   &   2   &   5.0	    &   1   &   29	&   0.103   &   0.115   &   $-$0.098  &    $-$0.098  &  $-$0.152    &   $-$0.069 &0\\
+AHZ700013q  &   90024700  &   GEMS    &   0   &   2   &   10.0    &   1   &   35	&   0.171   &   0.181   &      0.027  &       0.027  &     0.023    &      0.106 &0\\
+AHZ700013r  &   90024700  &   GEMS    &   0   &   2   &   50.0    &   1   &   34	&   0.206   &   0.206   &   $-$0.005  &    $-$0.005  &  $-$0.056    &      0.026 &0\\
 $\ldots$    \\

### 2016-05-17 writeup/gz_hubble_data.tex

--- 2016-05-17 writeup/gz_hubble_data.tex
@@
 $r^\prime$-band surface brightnesses, and also spanned the redshift range of
-SDSS targets (in $N_z = 4$ bins) in order to be optimized for different target
-minimum redshifts in \hst{} imaging.
+SDSS targets that maximuze the coverage of parameter space.
 
@@
 brightens the galaxy by 1~magnitude by $z=1$). \ferengi{} was run on the images
-for values of $e$ starting from $e=0$ and decreasing to $e=-3.5$ in increments
-of $\Delta e = 0.5$. Figure~\ref{fig:exampleFERENGI} shows several examples
-of the effects of ``losing'' spiral/disc features with increasing redshift
-for two galaxies with $e=0$.
+for values of $e$ starting from $e=0$ and increasing the effect to $e=-3.5$ in
+increments of $\Delta e = 0.5$. Figure~\ref{fig:exampleFERENGI} shows
+several examples of the effects of ``losing'' spiral/disc features with
+increasing redshift for two galaxies with $e=0$.
 
@@
 
+Another existing study using GZH to select barred galaxies was presented in
+\citet{che15}. This study used a slightly different bar selection method to
+demonstrate that AGN hosts show no statistically significant enhancement in bar
+fraction or average bar likelihood compared to closely-matched inactive
+galaxies.
+
 \subsection{Example 2: Identifying clump multiplicity} Clumps are known to be a

### 2016-05-17 writeup/gz_hubble_data.tex

@@
 fraction for \ffeatures{} is chosen based on the categorization of the galaxy:
-if it is ``correctable'', $\tt best = debiased$; if it is a lower limit, 
-$\tt best = lower~limit$; if neither condition applies, then 
-$\tt best = weighted$.
+if it is ``correctable'', $\tt best = debiased$; if it is a lower limit, $\tt
+best = lower~limit$; if neither condition applies, then $\tt best = weighted$.
 
@@
 $f_\mathrm{features}/f_\mathrm{smooth}$ of $\Delta f = 0.04$.
+
+Tables~\ref{tbl:catalog_hst}-\ref{tbl:simulated_agn} also contain flags for
+Task 01 that identify clean (but not complete) samples of galaxies with high
+likelihoods of being either smooth, featured, or a star/artifact.  These are
+set as $\tt smooth/featured/artifact\_flag=1$ if $\rm
+f_{smooth/features/artifact\_best}>0.8$. For a galaxy to be flagged as
+``smooth'', an additional criterion of $\tt correction\_type =~$0, 1, or 2 is
+applied. This accounts for the uncertainty in distinguishing between genuine
+ellipticals and disks whose features have been washed out due to surface
+brightness and redshift effects (Section~\ref{sec:debiasing}).
 
@@
 \startdata
-AHZ100002g  & 10010842  & AEGIS             & 0        & 127       & 0.118    & 0.128     & 0.085    & 0.085    & 0.226     & 0.226    \\
-AHZ100002h  & 10010870  & AEGIS             & 4        & 127       & 0.567    & 0.592     & 0.927    & 0.592    & $-$       & $-$      \\
+AHZ100002g  & 10010842  & AEGIS             & 0        & 127       & 0.118    & 0.128     & 0.085    & 0.085    & 0.226     & 0.226 & 0  \\
+AHZ100002h  & 10010870  & AEGIS             & 4        & 127       & 0.567    & 0.592     & 0.927    & 0.592    & $-$       & $-$   & 0  \\
 $\ldots$    \\
-AHZ20004kd  & 20014731  & COSMOS            & 3        &  44       & 0.682    & 0.675     & 0.147    & 0.675    & $-$       & $-$      \\
-AHZ20004ke  & 20014732  & COSMOS            & 2        &  45       & 0.689    & 0.756     & 0.893    & 0.756    & $-$       & $-$      \\
+AHZ20004kd  & 20014731  & COSMOS            & 3        &  44       & 0.682    & 0.675     & 0.147    & 0.675    & $-$       & $-$   & 0  \\
+AHZ20004ke  & 20014732  & COSMOS            & 2        &  45       & 0.689    & 0.756     & 0.893    & 0.756    & $-$       & $-$   & 0  \\
 $\ldots$    \\
-AHZ400043g  & 90022729  & GEMS              & 1        & 121       & 0.702    & 0.733     & 0.487    & 0.734    & 0.483     & 0.800    \\
-AHZ4000416  & 90022735  & GEMS              & 1        & 127       & 0.646    & 0.698     & 0.508    & 0.698    & 0.171     & 0.727    \\
+AHZ400043g  & 90022729  & GEMS              & 1        & 121       & 0.702    & 0.733     & 0.487    & 0.734    & 0.483     & 0.800 & 0  \\
+AHZ4000416  & 90022735  & GEMS              & 1        & 127       & 0.646    & 0.698     & 0.508    & 0.698    & 0.171     & 0.727 & 0  \\
 $\ldots$    \\
-AGZ0007z47  & 10014     & GOODS-N-FULLDEPTH & 1        & 40        & 0.475    & 0.475     & 0.197    & 0.475    & 0.011     & 0.496    \\
-AGZ0007z48  & 10017     & GOODS-N-FULLDEPTH & 3        & 40        & 0.675    & 0.675     & 0.048    & 0.675    & 0.168     & 0.669    \\
+AGZ0007z47  & 10014     & GOODS-N-FULLDEPTH & 1        & 40        & 0.475    & 0.475     & 0.197    & 0.475    & 0.011     & 0.496 & 0  \\
+AGZ0007z48  & 10017     & GOODS-N-FULLDEPTH & 3        & 40        & 0.675    & 0.675     & 0.048    & 0.675    & 0.168     & 0.669 & 0  \\
 $\ldots$    \\
-AGZ00083jb  & 8869      & GOODS-S-FULLDEPTH & 1        & 40        & 0.425    & 0.425     & 0.109    & 0.425    & 0.070     & 0.548    \\
-AGZ00083jc  & 8878      & GOODS-S-FULLDEPTH & 0        & 40        & 0.205    & 0.205     & 0.048    & 0.048    & $-$0.005  & 0.287    \\
+AGZ00083jb  & 8869      & GOODS-S-FULLDEPTH & 1        & 40        & 0.425    & 0.425     & 0.109    & 0.425    & 0.070     & 0.548 & 0  \\
+AGZ00083jc  & 8878      & GOODS-S-FULLDEPTH & 0        & 40        & 0.205    & 0.205     & 0.048    & 0.048    & $-$0.005  & 0.287 & 0  \\
 $\ldots$    \\
@@
 \startdata
-AHZF000001  &   20000002    &   COSMOS  &   1   &   48 &  0.708   &     0.755   &   0.228    &    0.754 &   0.325   &   0.829  \\
-AHZF000003  &   20000004    &   COSMOS  &   3   &   49 &  0.367   &     0.379   &   0.100    &    0.379 &   0.198   &   0.198  \\
-AHZF000004  &   20000006    &   COSMOS  &   3   &   49 &  0.265   &     0.271   &   0.010    &    0.270 &   $-$	    &   $-$    \\
-AHZF00000z  &   20000102    &   COSMOS  &   1   &   44 &  0.727   &     0.78    &   0.233    &    0.780 &   0.316   &   0.820  \\
-AHZF000010  &   20000104    &   COSMOS  &   2   &   53 &  0.811   &     0.849   &   0.904    &    0.848 &   $-$	    &   $-$    \\
+AHZF000001  &   20000002    &   COSMOS  &   1   &   48 &  0.708   &     0.755   &   0.228    &    0.754 &   0.325   &   0.829 & 0 \\
+AHZF000003  &   20000004    &   COSMOS  &   3   &   49 &  0.367   &     0.379   &   0.100    &    0.379 &   0.198   &   0.198 & 0 \\
+AHZF000004  &   20000006    &   COSMOS  &   3   &   49 &  0.265   &     0.271   &   0.010    &    0.270 &   $-$	    &   $-$   & 0 \\
+AHZF00000z  &   20000102    &   COSMOS  &   1   &   44 &  0.727   &     0.78    &   0.233    &    0.780 &   0.316   &   0.820 & 0 \\
+AHZF000010  &   20000104    &   COSMOS  &   2   &   53 &  0.811   &     0.849   &   0.904    &    0.848 &   $-$	    &   $-$   & 0 \\
 $\ldots$    \\
@@
 \startdata
-AHZC000001	&   20000002	&   COSMOS	&   1	&   168	&   0.615   &   0.664   &   0.160   &  0.663   &  0.271    &  0.775    \\
-AHZC000003	&   20000004	&   COSMOS	&   0	&   235	&   0.333   &   0.364   &   0.002   &  0.002   &  0.063    &  0.063    \\
-AHZC000004	&   20000006	&   COSMOS	&   3	&   316	&   0.235   &   0.252   & $-0.011$  &  0.252   &  $-$	    &  $-$      \\
-AHZC00000z	&   20000102	&   COSMOS	&   1	&   207	&   0.755   &   0.757   &   0.272   &  0.756   &  0.249    &  0.796    \\
-AHZC000010	&   20000104	&   COSMOS	&   2	&   158	&   0.843   &   0.882   &   0.936   &  0.881   &  $-$	    &  $-$      \\
+AHZC000001	&   20000002	&   COSMOS	&   1	&   168	&   0.615   &   0.664   &   0.160   &  0.663   &  0.271   &  0.775  & 0  \\
+AHZC000003	&   20000004	&   COSMOS	&   0	&   235	&   0.333   &   0.364   &   0.002   &  0.002   &  0.063   &  0.063  & 0  \\
+AHZC000004	&   20000006	&   COSMOS	&   3	&   316	&   0.235   &   0.252   & $-0.011$  &  0.252   &  $-$	  &  $-$    & 1  \\
+AHZC00000z	&   20000102	&   COSMOS	&   1	&   207	&   0.755   &   0.757   &   0.272   &  0.756   &  0.249   &  0.796  & 0  \\
+AHZC000010	&   20000104	&   COSMOS	&   2	&   158	&   0.843   &   0.882   &   0.936   &  0.881   &  $-$	  &  $-$    & 1  \\
 $\ldots$    \\
@@
 \startdata
-AHZ3000001  &   50000000    &     GOODS-N   &   0   &   123	&   0.390   &   0.415	&   0.090 &   0.090 &   $-$     &   $-$      \\
-AHZ3000002  &   50000001    &     GOODS-N   &   2   &   126	&   0.341	&   0.355	&   0.356 &   0.356 &   0.220	&   0.279    \\
-AHZ3000003  &   50000005    &     GOODS-N   &   1   &   129	&   0.760   &   0.826	&   0.633 &   0.825 &   0.596	&   0.834    \\
-AHZ3000004  &   50000008    &     GOODS-N   &   1   &   120	&   0.758	&   0.787	&   0.639 &   0.787 &   0.658	&   0.834    \\
-AHZ3000005  &   50000010    &     GOODS-N   &   1   &   123	&   0.854	&   0.890   &   0.611 &   0.889 &   0.597	&   0.914    \\
+AHZ3000001  &   50000000    &     GOODS-N   &   0   &   123	&   0.390   &   0.415	&   0.090 &   0.090 &   $-$     &   $-$   & 0 \\
+AHZ3000002  &   50000001    &     GOODS-N   &   2   &   126	&   0.341	&   0.355	&   0.356 &   0.356 &   0.220	&   0.279 & 0 \\
+AHZ3000003  &   50000005    &     GOODS-N   &   1   &   129	&   0.760   &   0.826	&   0.633 &   0.825 &   0.596	&   0.834 & 0 \\
+AHZ3000004  &   50000008    &     GOODS-N   &   1   &   120	&   0.758	&   0.787	&   0.639 &   0.787 &   0.658	&   0.834 & 0 \\
+AHZ3000005  &   50000010    &     GOODS-N   &   1   &   123	&   0.854	&   0.890   &   0.611 &   0.889 &   0.597	&   0.914 & 0 \\
 $\ldots$    \\
@@
 \startdata
-AHZ5000001  &   587730845812064684  &   SDSS    &     2 &   41  &   0.585   &    0.595  &   0.759   &   0.594   \\
-AHZ5000002  &   587730845812065247  &   SDSS    &     2 &   46  &   0.609   &    0.651  &   0.897   &   0.651   \\
-AHZ5000003  &   587730845812196092  &   SDSS    &     2 &   51  &   0.039   &    0.044  &   0.067   &   0.043   \\
-AHZ5000004  &   587730845812196825  &   SDSS    &     2 &   35  &   0.514   &    0.605  &   0.928   &   0.605   \\
-AHZ5000005  &   587730845812524122  &   SDSS    &     2 &   47  &   0.766   &    0.812  &   1.038   &   0.810   \\
-AHZ5000006  &   587730845812654984  &   SDSS    &     2 &   42  &   0.5	    &    0.542  &   0.680   &   0.541   \\
-AHZ5000007  &   587730845812655541  &   SDSS    &     2 &   41  &   0.488   &    0.526  &   0.697   &   0.525   \\
-AHZ5000008  &   587730845812720365  &   SDSS    &     2 &   53  &   0.792   &    0.84   &   1.050   &   0.839   \\
-AHZ5000009  &   587730845812720640  &   SDSS    &     4 &   43  &   0.0	    &    0.0    &   0.0	    &   0.0	    \\
-AHZ500000a  &   587730845812720699  &   SDSS    &     2 &   40  &   0.425   &    0.478  &   0.588   &   0.477   \\
+AHZ5000001  &   587730845812064684  &   SDSS    &     2 &   41  &   0.585   &    0.595  &   0.759   &   0.594 &  0  \\
+AHZ5000002  &   587730845812065247  &   SDSS    &     2 &   46  &   0.609   &    0.651  &   0.897   &   0.651 &  0  \\
+AHZ5000003  &   587730845812196092  &   SDSS    &     2 &   51  &   0.039   &    0.044  &   0.067   &   0.043 &  0  \\
+AHZ5000004  &   587730845812196825  &   SDSS    &     2 &   35  &   0.514   &    0.605  &   0.928   &   0.605 &  0  \\
+AHZ5000005  &   587730845812524122  &   SDSS    &     2 &   47  &   0.766   &    0.812  &   1.038   &   0.810 &  1  \\
+AHZ5000006  &   587730845812654984  &   SDSS    &     2 &   42  &   0.5	    &    0.542  &   0.680   &   0.541 &  0  \\
+AHZ5000007  &   587730845812655541  &   SDSS    &     2 &   41  &   0.488   &    0.526  &   0.697   &   0.525 &  0  \\
+AHZ5000008  &   587730845812720365  &   SDSS    &     2 &   53  &   0.792   &    0.84   &   1.050   &   0.839 &  1  \\
+AHZ5000009  &   587730845812720640  &   SDSS    &     4 &   43  &   0.0	    &    0.0    &   0.0	    &   0.0   &  0  \\
+AHZ500000a  &   587730845812720699  &   SDSS    &     2 &   40  &   0.425   &    0.478  &   0.588   &   0.477 &  0  \\
 $\ldots$    \\
@@
 \startdata
-AHZ6000001  & 8647474690312306978   &   SDSS    &    4  & 40  & 0.275   &    0.289  &   0.762   &   0.289   & \\
-AHZ6000002  & 8647474690312307154   &   SDSS    &    2  & 43  & 0.605   &    0.634  &   0.858   &   0.635   & \\
-AHZ6000003  & 8647474690312307877   &   SDSS    &    2  & 51  & 0.608   &    0.627  &   0.906   &   0.627   & \\
-AHZ6000004  & 8647474690312308301   &   SDSS    &    4  & 52  & 0.038   &    0.038  &   0.723   &   0.038   & \\
-AHZ6000005  & 8647474690312308318   &   SDSS    &    2  & 44  & 0.614   &    0.632  &   0.776   &   0.631   & \\
-AHZ6000006  & 8647474690312308880   &   SDSS    &    2  & 36  & 0.667   &    0.683  &   0.901   &   0.683   & \\
-AHZ6000007  & 8647474690312372644   &   SDSS    &    4  & 48  & 0.646   &    0.674  &   1.145   &   0.674   & \\
-AHZ6000008  & 8647474690312372789   &   SDSS    &    4  & 45  & 0.489   &    0.571  &   0.964   &   0.570   & \\
-AHZ6000009  & 8647474690312372931   &   SDSS    &    4  & 47  & 0.553   &    0.587  &   0.926   &   0.587   & \\
-AHZ600000a  & 8647474690312373190   &   SDSS    &    4  & 47  & 0.574   &    0.559  &   1.008   &   0.559   & \\
+AHZ6000001  & 8647474690312306978   &   SDSS    &    4  & 40  & 0.275   &    0.289  &   0.762   &   0.289   & 0 \\
+AHZ6000002  & 8647474690312307154   &   SDSS    &    2  & 43  & 0.605   &    0.634  &   0.858   &   0.635   & 0 \\
+AHZ6000003  & 8647474690312307877   &   SDSS    &    2  & 51  & 0.608   &    0.627  &   0.906   &   0.627   & 0 \\
+AHZ6000004  & 8647474690312308301   &   SDSS    &    4  & 52  & 0.038   &    0.038  &   0.723   &   0.038   & 0 \\
+AHZ6000005  & 8647474690312308318   &   SDSS    &    2  & 44  & 0.614   &    0.632  &   0.776   &   0.631   & 0 \\
+AHZ6000006  & 8647474690312308880   &   SDSS    &    2  & 36  & 0.667   &    0.683  &   0.901   &   0.683   & 0 \\
+AHZ6000007  & 8647474690312372644   &   SDSS    &    4  & 48  & 0.646   &    0.674  &   1.145   &   0.674   & 0 \\
+AHZ6000008  & 8647474690312372789   &   SDSS    &    4  & 45  & 0.489   &    0.571  &   0.964   &   0.570   & 0 \\
+AHZ6000009  & 8647474690312372931   &   SDSS    &    4  & 47  & 0.553   &    0.587  &   0.926   &   0.587   & 0 \\
+AHZ600000a  & 8647474690312373190   &   SDSS    &    4  & 47  & 0.574   &    0.559  &   1.008   &   0.559   & 0 \\
 $\ldots$    \\
@@
 \startdata
-AHZ7000001  &   90024700  &   GEMS    &   1   &   1   &   0.2	    &   1   &   42	&   0.238   &   0.239   &   $-$0.110  &       0.238  &  $-$0.113    &     0.287  \\
-AHZ7000002  &   90024700  &   GEMS    &   1   &   1   &   1.0	    &   1   &   51	&   0.255   &   0.265   &   $-$0.107  &       0.264  &  $-$0.128    &     0.272  \\
-AHZ7000003  &   90024700  &   GEMS    &   0   &   1   &   5.0	    &   1   &   47	&   0.170   &   0.167   &   $-$0.018  &    $-$0.018  &  $-$0.049    &     0.033  \\
-AHZ7000004  &   90024700  &   GEMS    &   0   &   1   &   10.0    &   1   &   41	&   0.195   &   0.195   &      0.045  &       0.045  &     0.044    &     0.127  \\
-AHZ7000005  &   90024700  &   GEMS    &   0   &   1   &   50.0    &   1   &   47	&   0.170   &   0.178   &      0.067  &       0.067  &     0.146    &     0.167  \\
+AHZ7000001  &   90024700  &   GEMS    &   1   &   1   &   0.2	    &   1   &   42	&   0.238   &   0.239   &   $-$0.110  &       0.238  &  $-$0.113    &     0.287  & 0 \\
+AHZ7000002  &   90024700  &   GEMS    &   1   &   1   &   1.0	    &   1   &   51	&   0.255   &   0.265   &   $-$0.107  &       0.264  &  $-$0.128    &     0.272  & 0 \\
+AHZ7000003  &   90024700  &   GEMS    &   0   &   1   &   5.0	    &   1   &   47	&   0.170   &   0.167   &   $-$0.018  &    $-$0.018  &  $-$0.049    &     0.033  & 0 \\
+AHZ7000004  &   90024700  &   GEMS    &   0   &   1   &   10.0    &   1   &   41	&   0.195   &   0.195   &      0.045  &       0.045  &     0.044    &     0.127  & 0 \\
+AHZ7000005  &   90024700  &   GEMS    &   0   &   1   &   50.0    &   1   &   47	&   0.170   &   0.178   &      0.067  &       0.067  &     0.146    &     0.167  & 0 \\
 $\ldots$    \\
-AHZ700013m  &   90024700  &   GEMS    &   0   &   2   &   0.0	    &   0   &   35	&   0.171   &   0.136   &      0.011  &       0.011  &     0.029    &      0.112 \\
-AHZ700013n  &   90024700  &   GEMS    &   1   &   2   &   0.2	    &   1   &   20	&   0.150   &   0.158   &   $-$0.278  &       0.049  &  $-$0.351    &      0.049 \\
-AHZ700013o  &   90024700  &   GEMS    &   1   &   2   &   1.0	    &   1   &   32	&   0.281   &   0.300   &   $-$0.086  &       0.281  &  $-$0.119    &      0.281 \\
-AHZ700013p  &   90024700  &   GEMS    &   0   &   2   &   5.0	    &   1   &   29	&   0.103   &   0.115   &   $-$0.098  &    $-$0.098  &  $-$0.152    &   $-$0.069 \\
-AHZ700013q  &   90024700  &   GEMS    &   0   &   2   &   10.0    &   1   &   35	&   0.171   &   0.181   &      0.027  &       0.027  &     0.023    &      0.106 \\
-AHZ700013r  &   90024700  &   GEMS    &   0   &   2   &   50.0    &   1   &   34	&   0.206   &   0.206   &   $-$0.005  &    $-$0.005  &  $-$0.056    &      0.026 \\
+AHZ700013m  &   90024700  &   GEMS    &   0   &   2   &   0.0	    &   0   &   35	&   0.171   &   0.136   &      0.011  &       0.011  &     0.029    &      0.112 & 0 \\
+AHZ700013n  &   90024700  &   GEMS    &   1   &   2   &   0.2	    &   1   &   20	&   0.150   &   0.158   &   $-$0.278  &       0.049  &  $-$0.351    &      0.049 & 0 \\
+AHZ700013o  &   90024700  &   GEMS    &   1   &   2   &   1.0	    &   1   &   32	&   0.281   &   0.300   &   $-$0.086  &       0.281  &  $-$0.119    &      0.281 & 0 \\
+AHZ700013p  &   90024700  &   GEMS    &   0   &   2   &   5.0	    &   1   &   29	&   0.103   &   0.115   &   $-$0.098  &    $-$0.098  &  $-$0.152    &   $-$0.069 & 0 \\
+AHZ700013q  &   90024700  &   GEMS    &   0   &   2   &   10.0    &   1   &   35	&   0.171   &   0.181   &      0.027  &       0.027  &     0.023    &      0.106 & 0 \\
+AHZ700013r  &   90024700  &   GEMS    &   0   &   2   &   50.0    &   1   &   34	&   0.206   &   0.206   &   $-$0.005  &    $-$0.005  &  $-$0.056    &      0.026 & 0 \\
 $\ldots$    \\
@@
 Tasks 03, 04 and 05 have an additional possible pathway; as shown in
-Figure~\ref{fig:decisiontree}, a classifier might also be shown this question if they
-select ``featured/disk'' in Task~01, ``clumpy'' in Task~12, two or more clumps
-in Task~16, and ``spiral arrangement'' in Task~15. After applying the
-appropriate thresholds for this path, $< 0.5\%$ of the galaxies which have $\ge
-20$ answers to these questions used this pathway to arrive at these Tasks.
-Further, of these subjects, none were found to exhibit disk structure, although
-the clumps within were arranged in a spiral pattern.
-
-This section described how to use the previous Task thresholds in
-Table~\ref{tbl:thresholds} to select well-sampled galaxies which may or may not
-contain the feature associated with a unique Task. The following two examples
-show to use the vote fractions for a particular Task to obtain a sample of
-galaxies with a certain morphological type.
+Figure~\ref{fig:decisiontree}, a classifier might also be shown this question
+if they select ``featured/disk'' in Task~01, ``clumpy'' in Task~12, two or more
+clumps in Task~16, and ``spiral arrangement'' in Task~15. After applying
+the appropriate thresholds for this path, $< 0.5\%$ of the galaxies which
+have $\ge 20$ answers to these questions used this pathway to arrive at
+these Tasks.  Further, of these subjects, none were found to exhibit disk
+structure, although the clumps within were arranged in a spiral pattern.
+
+This section described how to use Table~\ref{tbl:thresholds} to select
+well-sampled galaxies for which a particular task is reliably sampled. The
+following two examples extend this and show how to use the vote fractions to
+obtain samples of galaxies with a specific morphological type.
 

### 2016-05-17 writeup/gz_hubble_data.tex
rearranged S2
closes #95

--- 2016-05-17 writeup/gz_hubble_data.tex
@@
 
-\subsection{Hubble Legacy Surveys}\label{ssec:legacy_surveys}
-
 The GZH project contains images drawn from a number of different dedicated
 surveys and sample selection criteria. The majority of the data (as implied by
-the project name) were taken directly from \hst{} Legacy Surveys, all of which
-primarily used imaging from the Advanced Camera for Surveys (ACS). Results from
+the project name) were sourced directly from \hst{} Legacy Surveys, all of which
+primarily used imaging from the Advanced Camera for Surveys (ACS). In addition
+to \hst{} images, the project uses images from SDSS Stripe~82, as well as
+simulated \hst{} images from multiple sources. Below we provide details on each
+source of imaging and describe the creation process for images shown to classifiers. 
+We also detail the sources of metadata for galaxies in the sample, such as 
+photometry and redshifts.
+
+\subsection{Hubble Legacy Surveys}\label{ssec:legacy_surveys}
+
+Image information from
 the individual surveys have been combined into a single photometric and
@@
 \end{itemize}
+
+%Selection of galaxies from these samples is described in Section \ref{ssec:galselect} below. 
+In the ACS-GC \citep{gri12}, individual galaxies were identified using a
+combination of \sextractor{} \citep{ber96} and the galaxy-profile fitting
+framework \galapagos{} \citep{bar12}. GZH included all galaxies with $m<23.5$,
+where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS, GEMS +
+GOODS-S (2-epoch), and GOODS-N (2-epoch) surveys, respectively. The full-depth 
+GOODS images from both fields included galaxies with $m<26.8$. This yielded a total of
+113,166~images (Table~\ref{tbl:gzh_numbers}).
+
+Images from \hst{} legacy surveys were used to create multiple different color and grayscale 
+images using different depths and filter combinations; these are described further in Section 
+\ref{ssec:images}. Additionally, the use of a small set of \hst{} images to create simulated 
+images of active galactic nucleus (AGN) host galaxies is described in Section \ref{ssec:sim_agn}.
 
@@
 
-\subsection{Galaxy selection}
-
-In the ACS-GC \citep{gri12}, individual galaxies were identified using a
-combination of \sextractor{} \citep{ber96} and the galaxy-profile fitting
-framework \galapagos{} \citep{bar12}. GZH included all galaxies with $m<23.5$,
-where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS, GEMS +
-GOODS-S, and GOODS-N surveys, respectively. This yielded a total of
-113,166~images (Table~\ref{tbl:gzh_numbers}).
-
+\subsection{The Sloan Digital Sky Survey}\label{ssec:sdss}
+
+The project includes images from the Sloan Digital Sky Survey \citep[SDSS;][]{yor00,str02}, 
+in particular those from Data Release 7 \citep{aba09}. A small number of images 
+were used in the creation of simulated \hst{} images, described in Sections 
+\ref{ssec:ferengi} and \ref{sec:debiasing} below; the majority of SDSS images used 
+in GZH were from Stripe~82. The Stripe~82 samples in GZH include single-epoch 
+and co-added images, intended to facilitate comparison of morphological 
+classification with image depth.
+
+%The creation of 51,861 images from these sources is described in Section \ref{ssec:galselect} below.
 Single-epoch images from SDSS Stripe~82 were selected using the same criteria
@@
 
-\subsection{Image creation}
+\subsection{Simulated \hst{} images}\label{ssec:simulatedimages}
+
+To facilitate correction of classifications in the presence of known biasing effects, 
+GZH includes two different samples of simulated \hst{} images: real \hst{} galaxy images 
+(Section \ref{ssec:legacy_surveys}) with nuclear emission added to simulate AGN 
+host galaxies, and lower-redshift galaxy images from SDSS (Section \ref{ssec:sdss}), 
+artificially redshifted from $0.3 \leq z \leq 1$. Each is described separately below.
+
+\subsubsection{Images with simulated nuclear point sources}\label{ssec:sim_agn}
+
+As active galactic nuclei often have bright, unresolved optical emission, AGN have the 
+potential to mimic or distort the identification of a bulge component. GZH thus includes 
+a set of images designed to measure the effect of AGN on morphological classifications. 
+The presence of an AGN was
+simulated by modeling the point spread function (PSF) of the telescope and then
+inserting a bright source near the center of a real galaxy. For each image, the
+simulated AGN was assigned one of three colors -- either blue, red, or flat
+(white) as seen in the color images -- and a range of brightnesses such that
+$L_\mathrm{ratio} \equiv L_\mathrm{galaxy}/L_\mathrm{AGN}$ is in
+$(0.2,1.0,2.0,5.0,10.0,50.0)$. Combining these parameters generated 15~images
+with different simulated AGN for each host, in addition to the original galaxy image.
+
+Two sets of simulated AGN were generated in GZH. The first set (version~1) was
+assembled from 95~galaxies from GOODS-S imaging and empirical PSFs made 
+by combining stars in the GOODS fields using the PSF creation tools in \texttt{daophot}. 
+The second set (version~2) was assembled from 96~galaxies in GOODS-S; this
+version used simulated PSFs from \texttt{TinyTim} \citep{kri93}, drizzled using the 
+same procedures as those used in reduction of the GOODS-S images 
+\citep{koe02,koe03,gia04}. The use of these 2 versions facilitates comparisons 
+between these different PSF creation methods, which are widely used in AGN host 
+galaxy morphology studies \citep[e.g.,][]{san04,sim08,pie10a,simm11}. 
+% okay so I'm a cheeky self-citing biyotch
+Each PSF creation method has advantages and disadvantages: the empirical 
+PSFs better represent the nuances of the PSF in the specific data being used and 
+look more realistic at lower luminosities, but the extended features of the noiseless 
+\texttt{TinyTim} PSFs are visually more realistic at higher luminosities.
+
+Images with simulated AGN were classified in the main interface in an identical
+manner and evenly distributed with unaltered images of the galaxies.
+Classifiers were not explicitly told that the images had been altered during classification, as the
+goal was to measure the effect on normal classifications in as unbiased a
+manner as possible. Following classification, a classifier could view a page with 
+additional details about each galaxy they had classified; where applicable these pages 
+contained further information regarding image modifications.
+
+\subsubsection{Generating images of artificially-redshifted galaxies}\label{ssec:ferengi}
+
+The dimming and resolution effects of redshift can significantly affect galaxy classifications 
+derived from any method. To facilitate corrections due to redshift, we include a sample 
+of 288 galaxies with at redshifts such that available SDSS imaging can be transformed 
+to simulate \hst{} imaging out to $z = 1$. The selection spanned a
+variety of galaxy morphologies (as selected by GZ2 classifications) and
+$r^\prime$-band surface brightnesses, and also spanned the redshift range of
+SDSS targets (in $N_z = 4$ bins) in order to optimize for different target
+minimum redshifts in \hst{} imaging. We redshifted the galaxies and produced simulated
+\hst{} imaging using the \ferengi{} code \citep{bar08a}.
+
+%The selection criteria for the different morphological categories is summarized in Table \ref{tbl:morphologies}. 
+The surface brightness selection ($N_\mu = 3$) for the \ferengi{} galaxies was
+(1) low: $\mu > 21.5$~\magarc;  (2) mid: $20.5 < \mu < 21.5$~\magarc; and (3)
+high: $\mu < 20.5$~\magarc. For each of the four ``target redshifts''
+($z_\mathrm{sim} = 0.3, 0.5, 0.8$ and $1.0$), the images were redshifted in
+$\Delta z = 0.1$ bins up to $z_\mathrm{sim}=1.0$.
+
+%\begin{table*}
+%\center
+%\caption{Summary of morphological categories selected for \ferengi{} sample.\label{tbl:morphologies}}
+%\begin{tabular}{lllc}
+%\hline\hline
+%Morphology          & Label &  Selection                                                                                            & $N_{\rm objects}$ \\
+%                    &       &                                                                                                       & [$N_z \times N_\mu$] \\
+%\hline
+%Features            & Yes       & $f_{\rm features} > 0.8$, $f_{\rm odd} < 0.1$                                                         & 12 \\ 
+%                    & Int.      & $0.3 < f_{\rm smooth} < 0.6$, $f_{\rm odd} < 0.1$                                                     & 12 \\ 
+%                    & No        & $f_{\rm smooth} > 0.8$, $f_{\rm odd} < 0.1$                                                           & 12 \\ 
+%Merger              & No        & $f_{\rm features} > 0.8$, $f_{\rm odd < 0.1}$, $f_{\rm merger} < 0.1$                                 & 12 \\
+%                    & Int.      & $f_{\rm odd} > 0.5$, $0.1< f_{\rm merger} < 0.4$                                                      & 12 \\ 
+%                    & Yes       & $f_{\rm odd} > 0.5$, $f_{\rm merger} > 0.4$                                                           & 12 \\
+%Edge-on             & Yes       & $f_{\rm edgeon} > 0.8$, $f_{\rm features} > 0.5$                                                      & 12 \\
+%                    & Int.      & $0.4 < f_{\rm edgeon} < 0.8$ , $f_{\rm features} > 0.5$                                               & 12 \\
+%                    & No        & $f_{\rm edgeon} < 0.2$, $f_{\rm features} > 0.5$                                                      & 12 \\
+%Bar                 & No        & $f_{\rm bar} < 0.1$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$                                 & 24 \\
+%                    & Int.      & $0.2 < f_{\rm bar} < 0.4$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$                           & 24 \\
+%                    & Yes       & $f_{\rm bar} > 0.8$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$                                 & 24 \\
+%Visible spiral      & No        & $f_{\rm spiral} < 0.2$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$, $f_{\rm bar} < 0.1$         & 12 \\
+%                    & Int.      & $0.2 < f_{\rm spiral} < 0.8$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$, $f_{\rm bar} < 0.1$   & 12 \\
+%                    & Yes       & $f_{\rm spiral} > 0.8$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$, $f_{\rm bar} < 0.1$         & 12 \\
+%Oblique bulge size  & No        & $f_{\rm nobulge>0.6}$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.5$, $f_{\rm bar} < 0.2$          & 12 \\
+%                    & Int.      & $f_{\rm justnoticeable}>0.6$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.5$, $f_{\rm bar} < 0.2$   & 12 \\
+%                    & Yes       & $f_{\rm obvious|dominant}>0.5$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.5$, $f_{\rm bar} < 0.2$ & 12 \\
+%Edge-on bulge shape & Round     & $f_{\rm rounded}>0.5$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} > 0.5$                               & 12 \\
+%                    & Boxy      & $f_{\rm boxy}>0.4$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} > 0.2$                                  & 12 \\
+%                    & No bulge  & $f_{\rm nobulge}>0.5$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} > 0.5$                               & 12 \\
+%\hline\hline
+%\end{tabular}
+%\end{table*}
+
+In addition to the physical parameters of the input images, the \ferengi{}
+output depends on assumptions of the global galaxy evolution model. This
+evolution is a crude mechanism that mimics the brightness increase of galaxies
+with increasing redshift (out to at least $z\sim1-2$). The effect on the
+redshifted images is simply an empirical addition to the magnitude of a galaxy
+of the form $M' = e\times z + M$, where $M'$ is the corrected magnitude, and
+$e$ is the evolutionary correction in magnitudes (i.e., $e=-1$ essentially
+brightens the galaxy by 1~magnitude by $z=1$). \ferengi{} was run on the images
+for values of $e$ starting from $e=0$ and decreasing to $e=-3.5$ in increments
+of $\Delta e = 0.5$. Figure~\ref{fig:exampleFERENGI} shows several examples
+of the effects of ``losing'' spiral/disc features with increasing redshift
+for two galaxies with $e=0$.
+
+The final number of \ferengi{} images produced for each galaxy is ultimately a
+function of galaxy's redshift (since the new images cannot be resampled at
+better angular resolution than the original SDSS data), as well as the number
+of $e$ values selected. Table~\ref{tbl:ferengivalues} summarizes the redshifted
+images produced for GZH. The use of these images to correct for redshift-dependent
+classification bias is described in Section \ref{sec:debiasing}.
+
+\begin{table}
+\caption{Summary of \ferengi{} artificial redshifting \label{tbl:ferengivalues}}
+\begin{tabular}{lccccr}
+\hline\hline
+$z_{\rm sim}$ & $N_{z {\rm bins}}$ & $N_{\rm evolution}$ & $e_{\rm max}$ & $N_{\rm galaxies}$ & $N_{\rm images}$\\
+\hline
+0.3              & 8                  & 7                   & $-3.0$        & 72             & 4032 \\
+0.5              & 6                  & 4                   & $-1.5$        & 72             & 1728 \\
+0.8              & 3                  & 3                   & $-1.0$        & 72             &  648 \\
+1.0              & 1                  & 3                   & $-1.0$        & 72             &  216 \\
+\hline\hline
+\end{tabular}
+\end{table}
+
+\begin{figure*}
+\center
+\includegraphics[width=160mm]{figures/example_ferengi.pdf}
+\caption{Examples of two galaxies which have been run through the \ferengi{}
+code to produce simulated \hst{} images. The measured value of \ffeatures{}
+from GZH for the images in each panel are (1) Top row: \ffeatures~= (0.900,
+0.625, 0.350, 0.350, 0.225) and (2) Bottom row: \ffeatures~= (1.000, 0.875,
+0.875, 0.625, 0.375). \label{fig:exampleFERENGI}}
+\end{figure*}
+
+%\subsection{Galaxy selection}\label{ssec:galselect}
+%
+%In the ACS-GC \citep{gri12}, individual galaxies were identified using a
+%combination of \sextractor{} \citep{ber96} and the galaxy-profile fitting
+%framework \galapagos{} \citep{bar12}. GZH included all galaxies with $m<23.5$,
+%where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS, GEMS +
+%GOODS-S, and GOODS-N surveys, respectively. This yielded a total of
+%113,166~images (Table~\ref{tbl:gzh_numbers}).
+%
+%Single-epoch images from SDSS Stripe~82 were selected using the same criteria
+%from \citet{wil13}, which required limits of \texttt{petroR90\_r}$ >
+%3$\arcsec~(where \texttt{petroR90\_r} is the radius containing 90\% of the
+%$r^\prime$ Petrosian flux) and a magnitude brighter than $m_r < 17.77$. The
+%images used were three-color composites using the $g^\prime$, $r^\prime$, and
+%$i^\prime$ filters \citep{nie04}. 21,522 galaxies in SDSS met these criteria.
+%Co-added images from Stripe~82 were selected from the union of galaxies with
+%co-added magnitudes brighter than $17.77$~mag, and the galaxies detected in the
+%single-depth images and matched to a co-add source. This resulted in a total
+%set of 30,339 images. Of the images in the co-added sample, 5144 (17~percent)
+%were dimmer than the initial magnitude cut of 17.77.
+
+\subsection{Image creation}\label{ssec:images}
 
@@
 This masked procedure was effective in preserving the color balance for
-galaxies, retaining the visibility of faint features, but reduced the color
-contrast in the sky noise and greatly improved the appearance of the images.
+galaxies, retaining the visibility of faint features while reducing the color
+contrast in the sky noise and greatly improving the appearance of the images.
 This solution was applied to the coadded Stripe~82, COSMOS and 5-epoch GOODS
@@
 
-\subsection{Images with simulated nuclear point sources}
-
-GZH also included a set of images designed to measure the effect of active
-galactic nuclei (AGN) on morphological classifications. Since galactic nuclei
-can have bright, unresolved optical emission, AGN have the potential to mimic
-or distort the identification of a bulge component. The presence of an AGN was
-simulated by modeling the point spread function (PSF) of the telescope and then
-inserting a bright source near the center of a real galaxy. For each image, the
-simulated AGN was assigned one of three colors -- either blue, red, or flat
-(white) as seen in the color images -- and a range of brightnesses such that
-$L_\mathrm{ratio} \equiv L_\mathrm{galaxy}/L_\mathrm{AGN}$ is in
-$(0.2,1.0,2.0,5.0,10.0,50.0)$. Combining these parameters generated 15~images
-with different simulated AGN for each host.
-
-Two sets of simulated AGN were generated in GZH. The first set (version~1) was
-assembled from 95~galaxies from GOODS-S imaging and empirical PSFs made by combining stars in the GOODS fields using the PSF creation tools in \texttt{daophot}. 
-The second set (version~2) was assembled from 96~galaxies in GOODS-S; this
-version used simulated PSFs from \texttt{TinyTim} \citep{kri93}, drizzled using the same procedures as those used in reduction of the GOODS-S images \citep{koe02,koe03,gia04}.
-The use of these 2 versions facilitates comparisons between these different PSF creation methods, which are widely used in AGN host galaxy morphology studies \citep[e.g.,][]{san04,sim08,pie10a,simm11}.
-% okay so I'm a cheeky self-citing biyotch
-Each PSF creation method has advantages and disadvantages: the empirical PSFs better represent the nuances of the PSF in the specific data being used and look more realistic at lower luminosities, but the extended features of the noiseless \texttt{TinyTim} PSFs are visually more realistic at higher luminosities.
-
-Images with simulated AGN were classified in the main interface in an identical
-manner and evenly distributed with unaltered images of the galaxies.
-Classifiers were not explicitly told that the images had been altered during classification, as the
-goal was to measure the effect on normal classifications in as unbiased a
-manner as possible.
-Following classification, a classifier could view a page with additional details about each galaxy they had classified; where applicable these pages contained further information regarding image modifications.
+In addition to the main \hst{} legacy imaging sample with colored images described
+as above, GZH also includes samples of \hst{} galaxy images with different color
+prescriptions. In particular, there are 2 sets of 3,927 images each, drawn from the
+COSMOS sample; the first has a dramatically reduced color saturation, and the second
+has reversed the colors so that the blue and red filters have exchanged places in the
+RGB image. The `faded' galaxy set facilitates measuring of possible variations in
+classification due to the presence or absence of color features. The reversed-color set
+enables an alternative test of potential color biases in classifications.
+% I guess this means we need to say somewhere later that we don't see an effect (we don't, right?).
+% Would also be good to cite here where we have done similar things in the past...
+
+The simulated AGN host galaxy color images (described in Section \ref{ssec:sim_agn})
+were created using the same prescription as for the GOODS 2-epoch imaging. The
+artificially redshifted color images (Section \ref{ssec:ferengi}) were created using the
+same prescription as for the AEGIS images.
+% Edmond should verify the AEGIS bit above.
+
+\subsection{Galaxy sample labels}\label{ssec:sample_labels}
+
+The full GZH sample is composed of 7 different galaxy sub-samples. Throughout this
+paper and in the published catalogs they are referred to with the following labels:
+
+\begin{itemize}
+
+%\ref{tbl:catalog_hst}
+\item \texttt{main}: \hst{} imaging with RGB colors making use of all available filters with typical saturation and in correct order, as described in Section \ref{ssec:images}.
+This sample includes AEGIS, COSMOS, GEMS, and full-depth GOODS (North and South) images.
+(118,425 galaxies)
+
+%\ref{tbl:catalog_faded}
+\item \texttt{faded}: a subset of COSMOS images with very low color saturation. (3,927 galaxies)
+
+%\ref{tbl:catalog_recolored}
+\item \texttt{recolored}: a subset of COSMOS images with red and blue channels reversed. Note: this sub-sample uses the same galaxies as the \texttt{faded} sub-sample. (3,927 galaxies)
+
+%\ref{tbl:catalog_goods_shallow}
+\item \texttt{goods-shallow}: Images from GOODS-North and GOODS-South, with color from 2 filters and imaged at 2-epoch depth. (6,144 galaxies)
+
+%\ref{tbl:stripe82_single}
+\item \texttt{stripe-82-single}: Single-epoch images from SDSS Stripe~82. (21,522 galaxies)
+
+%\ref{tbl:stripe82_coadd}
+\item \texttt{stripe-82-coadd}: Co-added images from SDSS Stripe~82.
+Note: this sub-sample includes all galaxies in the \texttt{stripe-82-single} sub-sample, with additional sources detected in the deeper imaging.
+(30,339 galaxies)
+
+%ferengi <-- no table?
+\item \texttt{redshifted}: Simulated \hst{} images constructed using SDSS images and artificially redshifted to between $0.3 \leq z \leq 1$. (288 original galaxies; 3,950 redshifted galaxies)
+
+%\ref{tbl:simulated_agn}
+\item \texttt{simulated-agn}: Simulated AGN host galaxies constructed using \hst{} images and PSFs. (96 original galaxies; 2,961 simulated AGN host galaxies)
+
+\end{itemize}
 
@@
 over a variety of redshifts. The input images are from the SDSS
-\citep{yor00,str02} and are processed using the \ferengi{} code \citep{bar08a}
-to match the observational properties of the \hst{} surveys out to $z=1$. These
+\citep{yor00,str02} and are processed to match the observational properties of 
+the \hst{} surveys out to $z=1$. These
 images were classified in the GZH interface using the same classification
-scheme as the original \hst{} images.
-
-\subsection{Generating images of artificially-redshifted galaxies}
-
-The GZH classifications include 288 unique galaxies originally generated from
-SDSS imaging and processed with the \ferengi{} code. The selection spanned a
-variety of galaxy morphologies (as selected by GZ2 classifications) and
-$r^\prime$-band surface brightnesses, and also spanned the redshift range of
-SDSS targets (in $N_z = 4$ bins) in order to be optimized for different target
-minimum redshifts in \hst{} imaging.
-
-%The selection criteria for the different morphological categories is summarized in Table \ref{tbl:morphologies}. 
-The surface brightness selection ($N_\mu = 3$) for the \ferengi{} galaxies was
-(1) low: $\mu > 21.5$~\magarc;  (2) mid: $20.5 < \mu < 21.5$~\magarc; and (3)
-high: $\mu < 20.5$~\magarc. For each of the four ``target redshifts''
-($z_\mathrm{sim} = 0.3, 0.5, 0.8$ and $1.0$), the images were redshifted in
-$\Delta z = 0.1$ bins up to $z_\mathrm{sim}=1.0$.
-
-%\begin{table*}
-%\center
-%\caption{Summary of morphological categories selected for \ferengi{} sample.\label{tbl:morphologies}}
-%\begin{tabular}{lllc}
-%\hline\hline
-%Morphology          & Label &  Selection                                                                                            & $N_{\rm objects}$ \\
-%                    &       &                                                                                                       & [$N_z \times N_\mu$] \\
-%\hline
-%Features            & Yes       & $f_{\rm features} > 0.8$, $f_{\rm odd} < 0.1$                                                         & 12 \\ 
-%                    & Int.      & $0.3 < f_{\rm smooth} < 0.6$, $f_{\rm odd} < 0.1$                                                     & 12 \\ 
-%                    & No        & $f_{\rm smooth} > 0.8$, $f_{\rm odd} < 0.1$                                                           & 12 \\ 
-%Merger              & No        & $f_{\rm features} > 0.8$, $f_{\rm odd < 0.1}$, $f_{\rm merger} < 0.1$                                 & 12 \\
-%                    & Int.      & $f_{\rm odd} > 0.5$, $0.1< f_{\rm merger} < 0.4$                                                      & 12 \\ 
-%                    & Yes       & $f_{\rm odd} > 0.5$, $f_{\rm merger} > 0.4$                                                           & 12 \\
-%Edge-on             & Yes       & $f_{\rm edgeon} > 0.8$, $f_{\rm features} > 0.5$                                                      & 12 \\
-%                    & Int.      & $0.4 < f_{\rm edgeon} < 0.8$ , $f_{\rm features} > 0.5$                                               & 12 \\
-%                    & No        & $f_{\rm edgeon} < 0.2$, $f_{\rm features} > 0.5$                                                      & 12 \\
-%Bar                 & No        & $f_{\rm bar} < 0.1$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$                                 & 24 \\
-%                    & Int.      & $0.2 < f_{\rm bar} < 0.4$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$                           & 24 \\
-%                    & Yes       & $f_{\rm bar} > 0.8$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$                                 & 24 \\
-%Visible spiral      & No        & $f_{\rm spiral} < 0.2$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$, $f_{\rm bar} < 0.1$         & 12 \\
-%                    & Int.      & $0.2 < f_{\rm spiral} < 0.8$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$, $f_{\rm bar} < 0.1$   & 12 \\
-%                    & Yes       & $f_{\rm spiral} > 0.8$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$, $f_{\rm bar} < 0.1$         & 12 \\
-%Oblique bulge size  & No        & $f_{\rm nobulge>0.6}$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.5$, $f_{\rm bar} < 0.2$          & 12 \\
-%                    & Int.      & $f_{\rm justnoticeable}>0.6$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.5$, $f_{\rm bar} < 0.2$   & 12 \\
-%                    & Yes       & $f_{\rm obvious|dominant}>0.5$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.5$, $f_{\rm bar} < 0.2$ & 12 \\
-%Edge-on bulge shape & Round     & $f_{\rm rounded}>0.5$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} > 0.5$                               & 12 \\
-%                    & Boxy      & $f_{\rm boxy}>0.4$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} > 0.2$                                  & 12 \\
-%                    & No bulge  & $f_{\rm nobulge}>0.5$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} > 0.5$                               & 12 \\
-%\hline\hline
-%\end{tabular}
-%\end{table*}
-
-In addition to the physical parameters of the input images, the \ferengi{}
-output depends on assumptions of the global galaxy evolution model. This
-evolution is a crude mechanism that mimics the brightness increase of galaxies
-with increasing redshift (out to at least $z\sim1-2$). The effect on the
-redshifted images is simply an empirical addition to the magnitude of a galaxy
-of the form $M' = e\times z + M$, where $M'$ is the corrected magnitude, and
-$e$ is the evolutionary correction in magnitudes (i.e., $e=-1$ essentially
-brightens the galaxy by 1~magnitude by $z=1$). \ferengi{} was run on the images
-for values of $e$ starting from $e=0$ and decreasing to $e=-3.5$ in increments
-of $\Delta e = 0.5$. Figure~\ref{fig:exampleFERENGI} shows several examples
-of the effects of ``losing'' spiral/disc features with increasing redshift
-for two galaxies with $e=0$.
-
-The final number of \ferengi{} images produced for each galaxy is ultimately a
-function of galaxy's redshift (since the new images cannot be resampled at
-better angular resolution than the original SDSS data), as well as the number
-of $e$ values selected. Table~\ref{tbl:ferengivalues} summarizes the redshifted
-images produced for GZH.
-
-\begin{table}
-\caption{Summary of \ferengi{} artificial redshifting \label{tbl:ferengivalues}}
-\begin{tabular}{lccccr}
-\hline\hline
-$z_{\rm sim}$ & $N_{z {\rm bins}}$ & $N_{\rm evolution}$ & $e_{\rm max}$ & $N_{\rm galaxies}$ & $N_{\rm images}$\\
-\hline
-0.3              & 8                  & 7                   & $-3.0$        & 72             & 4032 \\
-0.5              & 6                  & 4                   & $-1.5$        & 72             & 1728 \\
-0.8              & 3                  & 3                   & $-1.0$        & 72             &  648 \\
-1.0              & 1                  & 3                   & $-1.0$        & 72             &  216 \\
-\hline\hline
-\end{tabular}
-\end{table}
-
-\begin{figure*}
-\center
-\includegraphics[width=160mm]{figures/example_ferengi.pdf}
-\caption{Examples of two galaxies which have been run through the \ferengi{}
-code to produce simulated \hst{} images. The measured value of \ffeatures{}
-from GZH for the images in each panel are (1) Top row: \ffeatures~= (0.900,
-0.625, 0.350, 0.350, 0.225) and (2) Bottom row: \ffeatures~= (1.000, 0.875,
-0.875, 0.625, 0.375). \label{fig:exampleFERENGI}}
-\end{figure*}
+scheme as the original \hst{} images. Further details on the creation of these images
+is given in Section \ref{ssec:ferengi}.
 
@@
 $\tt best = weighted$.
-Flags are also given for the three responses of Task 01 to identify clean samples of galaxies with high likelihoods of being smooth, featured, or an artifact.
-These are set as $\tt smooth/featured/artifact\_flag=1$ if $\rm f_{smooth/features/artifact\_best}>0.8$.
-For a galaxy to be flagged as ``smooth'', an additional criterion of $\tt correction\_type =~$0, 1, or 2 is applied.
-This is to account for the uncertainty in distinguishing between genuine ellipticals and disks whose features have been washed out due to surface brightness and redshift effects, as described in Section~\ref{sec:debiasing}.
 
@@
 \tabletypesize{\scriptsize}
-\begin{deluxetable*}{lllcrlllllll|c}
+\begin{deluxetable*}{lllcrllllll|c}
 \centering
@@
 \multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
-\multicolumn{7}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
+\multicolumn{6}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
 \colhead{$\ldots$}
 \\
-\colhead{Zooniverse ID} & 
-\colhead{Survey ID} & 
+\colhead{Project ID} & 
+\colhead{Hubble ID} & 
 \colhead{Imaging} & 
@@
 \colhead{upper~limit} &
-\colhead{flag} &
 \colhead{}
@@
 \startdata
-AHZ100002g  & 10010842  & AEGIS             & 0        & 127       & 0.118    & 0.128     & 0.085    & 0.085    & 0.226     & 0.226 & 0   \\
-AHZ100002h  & 10010870  & AEGIS             & 4        & 127       & 0.567    & 0.592     & 0.927    & 0.592    & $-$       & $-$   &0   \\
+AHZ100002g  & 10010842  & AEGIS             & 0        & 127       & 0.118    & 0.128     & 0.085    & 0.085    & 0.226     & 0.226    \\
+AHZ100002h  & 10010870  & AEGIS             & 4        & 127       & 0.567    & 0.592     & 0.927    & 0.592    & $-$       & $-$      \\
 $\ldots$    \\
-AHZ20004kd  & 20014731  & COSMOS            & 3        &  44       & 0.682    & 0.675     & 0.147    & 0.675    & $-$       & $-$   &0   \\
-AHZ20004ke  & 20014732  & COSMOS            & 2        &  45       & 0.689    & 0.756     & 0.893    & 0.756    & $-$       & $-$   &0   \\
+AHZ20004kd  & 20014731  & COSMOS            & 3        &  44       & 0.682    & 0.675     & 0.147    & 0.675    & $-$       & $-$      \\
+AHZ20004ke  & 20014732  & COSMOS            & 2        &  45       & 0.689    & 0.756     & 0.893    & 0.756    & $-$       & $-$      \\
 $\ldots$    \\
-AHZ400043g  & 90022729  & GEMS              & 1        & 121       & 0.702    & 0.733     & 0.487    & 0.734    & 0.483     & 0.800 &0   \\
-AHZ4000416  & 90022735  & GEMS              & 1        & 127       & 0.646    & 0.698     & 0.508    & 0.698    & 0.171     & 0.727 &0   \\
+AHZ400043g  & 90022729  & GEMS              & 1        & 121       & 0.702    & 0.733     & 0.487    & 0.734    & 0.483     & 0.800    \\
+AHZ4000416  & 90022735  & GEMS              & 1        & 127       & 0.646    & 0.698     & 0.508    & 0.698    & 0.171     & 0.727    \\
 $\ldots$    \\
-AGZ0007z47  & 10014     & GOODS-N-FULLDEPTH & 1        & 40        & 0.475    & 0.475     & 0.197    & 0.475    & 0.011     & 0.496 &0   \\
-AGZ0007z48  & 10017     & GOODS-N-FULLDEPTH & 3        & 40        & 0.675    & 0.675     & 0.048    & 0.675    & 0.168     & 0.669 &0  \\
+AGZ0007z47  & 10014     & GOODS-N-FULLDEPTH & 1        & 40        & 0.475    & 0.475     & 0.197    & 0.475    & 0.011     & 0.496    \\
+AGZ0007z48  & 10017     & GOODS-N-FULLDEPTH & 3        & 40        & 0.675    & 0.675     & 0.048    & 0.675    & 0.168     & 0.669    \\
 $\ldots$    \\
-AGZ00083jb  & 8869      & GOODS-S-FULLDEPTH & 1        & 40        & 0.425    & 0.425     & 0.109    & 0.425    & 0.070     & 0.548 &0   \\
-AGZ00083jc  & 8878      & GOODS-S-FULLDEPTH & 0        & 40        & 0.205    & 0.205     & 0.048    & 0.048    & $-$0.005  & 0.287 &0   \\
+AGZ00083jb  & 8869      & GOODS-S-FULLDEPTH & 1        & 40        & 0.425    & 0.425     & 0.109    & 0.425    & 0.070     & 0.548    \\
+AGZ00083jc  & 8878      & GOODS-S-FULLDEPTH & 0        & 40        & 0.205    & 0.205     & 0.048    & 0.048    & $-$0.005  & 0.287    \\
 $\ldots$    \\
@@
 \startdata
-AHZF000001  &   20000002    &   COSMOS  &   1   &   48 &  0.708   &     0.755   &   0.228    &    0.754 &   0.325   &   0.829 &0 \\
-AHZF000003  &   20000004    &   COSMOS  &   3   &   49 &  0.367   &     0.379   &   0.100    &    0.379 &   0.198   &   0.198 &0 \\
-AHZF000004  &   20000006    &   COSMOS  &   3   &   49 &  0.265   &     0.271   &   0.010    &    0.270 &   $-$	    &   $-$   &0 \\
-AHZF00000z  &   20000102    &   COSMOS  &   1   &   44 &  0.727   &     0.78    &   0.233    &    0.780 &   0.316   &   0.820 &0 \\
-AHZF000010  &   20000104    &   COSMOS  &   2   &   53 &  0.811   &     0.849   &   0.904    &    0.848 &   $-$	    &   $-$   &0 \\
+AHZF000001  &   20000002    &   COSMOS  &   1   &   48 &  0.708   &     0.755   &   0.228    &    0.754 &   0.325   &   0.829  \\
+AHZF000003  &   20000004    &   COSMOS  &   3   &   49 &  0.367   &     0.379   &   0.100    &    0.379 &   0.198   &   0.198  \\
+AHZF000004  &   20000006    &   COSMOS  &   3   &   49 &  0.265   &     0.271   &   0.010    &    0.270 &   $-$	    &   $-$    \\
+AHZF00000z  &   20000102    &   COSMOS  &   1   &   44 &  0.727   &     0.78    &   0.233    &    0.780 &   0.316   &   0.820  \\
+AHZF000010  &   20000104    &   COSMOS  &   2   &   53 &  0.811   &     0.849   &   0.904    &    0.848 &   $-$	    &   $-$    \\
 $\ldots$    \\
@@
 \tabletypesize{\scriptsize}
-\begin{deluxetable*}{lllcrllllllll|c}
+\begin{deluxetable*}{lllcrllllll|c}
 \centering
@@
 \startdata
-AHZC000001	&   20000002	&   COSMOS	&   1	&   168	&   0.615   &   0.664   &   0.160   &  0.663   &  0.271    &  0.775 &0   \\
-AHZC000003	&   20000004	&   COSMOS	&   0	&   235	&   0.333   &   0.364   &   0.002   &  0.002   &  0.063    &  0.063 &0   \\
-AHZC000004	&   20000006	&   COSMOS	&   3	&   316	&   0.235   &   0.252   & $-0.011$  &  0.252   &  $-$	    &  $-$  &1    \\
-AHZC00000z	&   20000102	&   COSMOS	&   1	&   207	&   0.755   &   0.757   &   0.272   &  0.756   &  0.249    &  0.796 &0   \\
-AHZC000010	&   20000104	&   COSMOS	&   2	&   158	&   0.843   &   0.882   &   0.936   &  0.881   &  $-$	    &  $-$  &1    \\
+AHZC000001	&   20000002	&   COSMOS	&   1	&   168	&   0.615   &   0.664   &   0.160   &  0.663   &  0.271    &  0.775    \\
+AHZC000003	&   20000004	&   COSMOS	&   0	&   235	&   0.333   &   0.364   &   0.002   &  0.002   &  0.063    &  0.063    \\
+AHZC000004	&   20000006	&   COSMOS	&   3	&   316	&   0.235   &   0.252   & $-0.011$  &  0.252   &  $-$	    &  $-$      \\
+AHZC00000z	&   20000102	&   COSMOS	&   1	&   207	&   0.755   &   0.757   &   0.272   &  0.756   &  0.249    &  0.796    \\
+AHZC000010	&   20000104	&   COSMOS	&   2	&   158	&   0.843   &   0.882   &   0.936   &  0.881   &  $-$	    &  $-$      \\
 $\ldots$    \\
@@
 \startdata
-AHZ3000001  &   50000000    &     GOODS-N   &   0   &   123	&   0.390   &   0.415	&   0.090 &   0.090 &   $-$     &   $-$ &0     \\
-AHZ3000002  &   50000001    &     GOODS-N   &   2   &   126	&   0.341	&   0.355	&   0.356 &   0.356 &   0.220	&   0.279 &0   \\
-AHZ3000003  &   50000005    &     GOODS-N   &   1   &   129	&   0.760   &   0.826	&   0.633 &   0.825 &   0.596	&   0.834 &0   \\
-AHZ3000004  &   50000008    &     GOODS-N   &   1   &   120	&   0.758	&   0.787	&   0.639 &   0.787 &   0.658	&   0.834 &0   \\
-AHZ3000005  &   50000010    &     GOODS-N   &   1   &   123	&   0.854	&   0.890   &   0.611 &   0.889 &   0.597	&   0.914 &0  \\
+AHZ3000001  &   50000000    &     GOODS-N   &   0   &   123	&   0.390   &   0.415	&   0.090 &   0.090 &   $-$     &   $-$      \\
+AHZ3000002  &   50000001    &     GOODS-N   &   2   &   126	&   0.341	&   0.355	&   0.356 &   0.356 &   0.220	&   0.279    \\
+AHZ3000003  &   50000005    &     GOODS-N   &   1   &   129	&   0.760   &   0.826	&   0.633 &   0.825 &   0.596	&   0.834    \\
+AHZ3000004  &   50000008    &     GOODS-N   &   1   &   120	&   0.758	&   0.787	&   0.639 &   0.787 &   0.658	&   0.834    \\
+AHZ3000005  &   50000010    &     GOODS-N   &   1   &   123	&   0.854	&   0.890   &   0.611 &   0.889 &   0.597	&   0.914    \\
 $\ldots$    \\
@@
 \tabletypesize{\scriptsize}
-\begin{deluxetable*}{lllcrlllll|c}
+\begin{deluxetable*}{lllcrllll|c}
 \centering
@@
 \multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
-\multicolumn{5}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
+\multicolumn{4}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
 \colhead{$\ldots$}
 \\
-\colhead{Zooniverse ID} & 
-\colhead{Survey ID} & 
+\colhead{Project ID} & 
+\colhead{SDSS DR7 ObjID} & 
 \colhead{Imaging} & 
@@
 \colhead{best} &
-\colhead{flag} &
 \colhead{}
@@
 \startdata
-AHZ5000001  &   587730845812064684  &   SDSS    &     2 &   41  &   0.585   &    0.595  &   0.759   &   0.594 &0  \\
-AHZ5000002  &   587730845812065247  &   SDSS    &     2 &   46  &   0.609   &    0.651  &   0.897   &   0.651 &0  \\
-AHZ5000003  &   587730845812196092  &   SDSS    &     2 &   51  &   0.039   &    0.044  &   0.067   &   0.043 &0  \\
-AHZ5000004  &   587730845812196825  &   SDSS    &     2 &   35  &   0.514   &    0.605  &   0.928   &   0.605 &0  \\
-AHZ5000005  &   587730845812524122  &   SDSS    &     2 &   47  &   0.766   &    0.812  &   1.038   &   0.810 &1  \\
-AHZ5000006  &   587730845812654984  &   SDSS    &     2 &   42  &   0.5	    &    0.542  &   0.680   &   0.541 &0  \\
-AHZ5000007  &   587730845812655541  &   SDSS    &     2 &   41  &   0.488   &    0.526  &   0.697   &   0.525 &0  \\
-AHZ5000008  &   587730845812720365  &   SDSS    &     2 &   53  &   0.792   &    0.84   &   1.050   &   0.839 &1  \\
-AHZ5000009  &   587730845812720640  &   SDSS    &     4 &   43  &   0.0	    &    0.0    &   0.0	    &   0.0   &0    \\
-AHZ500000a  &   587730845812720699  &   SDSS    &     2 &   40  &   0.425   &    0.478  &   0.588   &   0.477 &0  \\
+AHZ5000001  &   587730845812064684  &   SDSS    &     2 &   41  &   0.585   &    0.595  &   0.759   &   0.594   \\
+AHZ5000002  &   587730845812065247  &   SDSS    &     2 &   46  &   0.609   &    0.651  &   0.897   &   0.651   \\
+AHZ5000003  &   587730845812196092  &   SDSS    &     2 &   51  &   0.039   &    0.044  &   0.067   &   0.043   \\
+AHZ5000004  &   587730845812196825  &   SDSS    &     2 &   35  &   0.514   &    0.605  &   0.928   &   0.605   \\
+AHZ5000005  &   587730845812524122  &   SDSS    &     2 &   47  &   0.766   &    0.812  &   1.038   &   0.810   \\
+AHZ5000006  &   587730845812654984  &   SDSS    &     2 &   42  &   0.5	    &    0.542  &   0.680   &   0.541   \\
+AHZ5000007  &   587730845812655541  &   SDSS    &     2 &   41  &   0.488   &    0.526  &   0.697   &   0.525   \\
+AHZ5000008  &   587730845812720365  &   SDSS    &     2 &   53  &   0.792   &    0.84   &   1.050   &   0.839   \\
+AHZ5000009  &   587730845812720640  &   SDSS    &     4 &   43  &   0.0	    &    0.0    &   0.0	    &   0.0	    \\
+AHZ500000a  &   587730845812720699  &   SDSS    &     2 &   40  &   0.425   &    0.478  &   0.588   &   0.477   \\
 $\ldots$    \\
@@
 \startdata
-AHZ6000001  & 8647474690312306978   &   SDSS    &    4  & 40  & 0.275   &    0.289  &   0.762   &   0.289   & 0&\\
-AHZ6000002  & 8647474690312307154   &   SDSS    &    2  & 43  & 0.605   &    0.634  &   0.858   &   0.635   & 0&\\
-AHZ6000003  & 8647474690312307877   &   SDSS    &    2  & 51  & 0.608   &    0.627  &   0.906   &   0.627   & 0&\\
-AHZ6000004  & 8647474690312308301   &   SDSS    &    4  & 52  & 0.038   &    0.038  &   0.723   &   0.038   & 0&\\
-AHZ6000005  & 8647474690312308318   &   SDSS    &    2  & 44  & 0.614   &    0.632  &   0.776   &   0.631   & 0&\\
-AHZ6000006  & 8647474690312308880   &   SDSS    &    2  & 36  & 0.667   &    0.683  &   0.901   &   0.683   & 0&\\
-AHZ6000007  & 8647474690312372644   &   SDSS    &    4  & 48  & 0.646   &    0.674  &   1.145   &   0.674   & 0&\\
-AHZ6000008  & 8647474690312372789   &   SDSS    &    4  & 45  & 0.489   &    0.571  &   0.964   &   0.570   & 0&\\
-AHZ6000009  & 8647474690312372931   &   SDSS    &    4  & 47  & 0.553   &    0.587  &   0.926   &   0.587   & 0&\\
-AHZ600000a  & 8647474690312373190   &   SDSS    &    4  & 47  & 0.574   &    0.559  &   1.008   &   0.559   & 0&\\
+AHZ6000001  & 8647474690312306978   &   SDSS    &    4  & 40  & 0.275   &    0.289  &   0.762   &   0.289   & \\
+AHZ6000002  & 8647474690312307154   &   SDSS    &    2  & 43  & 0.605   &    0.634  &   0.858   &   0.635   & \\
+AHZ6000003  & 8647474690312307877   &   SDSS    &    2  & 51  & 0.608   &    0.627  &   0.906   &   0.627   & \\
+AHZ6000004  & 8647474690312308301   &   SDSS    &    4  & 52  & 0.038   &    0.038  &   0.723   &   0.038   & \\
+AHZ6000005  & 8647474690312308318   &   SDSS    &    2  & 44  & 0.614   &    0.632  &   0.776   &   0.631   & \\
+AHZ6000006  & 8647474690312308880   &   SDSS    &    2  & 36  & 0.667   &    0.683  &   0.901   &   0.683   & \\
+AHZ6000007  & 8647474690312372644   &   SDSS    &    4  & 48  & 0.646   &    0.674  &   1.145   &   0.674   & \\
+AHZ6000008  & 8647474690312372789   &   SDSS    &    4  & 45  & 0.489   &    0.571  &   0.964   &   0.570   & \\
+AHZ6000009  & 8647474690312372931   &   SDSS    &    4  & 47  & 0.553   &    0.587  &   0.926   &   0.587   & \\
+AHZ600000a  & 8647474690312373190   &   SDSS    &    4  & 47  & 0.574   &    0.559  &   1.008   &   0.559   & \\
 $\ldots$    \\
@@
 \tabletypesize{\scriptsize}
-\begin{deluxetable*}{lllccccrrrrrrrr|c}
+\begin{deluxetable*}{lllccccrrrrrrr|c}
 \centering
@@
  & & & & & & & &
-\multicolumn{7}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
+\multicolumn{6}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
 \colhead{$\ldots$}
 \\
-\colhead{Zooniverse ID} & 
-\colhead{Survey ID} & 
+\colhead{Project ID} & 
+\colhead{SDSS DR7 ObjID} & 
 \colhead{Imaging} & 
@@
 \colhead{upper limit} &
-\colhead{flag} &
 \colhead{}
@@
 \startdata
-AHZ7000001  &   90024700  &   GEMS    &   1   &   1   &   0.2	    &   1   &   42	&   0.238   &   0.239   &   $-$0.110  &       0.238  &  $-$0.113    &     0.287  &0\\
-AHZ7000002  &   90024700  &   GEMS    &   1   &   1   &   1.0	    &   1   &   51	&   0.255   &   0.265   &   $-$0.107  &       0.264  &  $-$0.128    &     0.272  &0\\
-AHZ7000003  &   90024700  &   GEMS    &   0   &   1   &   5.0	    &   1   &   47	&   0.170   &   0.167   &   $-$0.018  &    $-$0.018  &  $-$0.049    &     0.033  &0\\
-AHZ7000004  &   90024700  &   GEMS    &   0   &   1   &   10.0    &   1   &   41	&   0.195   &   0.195   &      0.045  &       0.045  &     0.044    &     0.127  &0\\
-AHZ7000005  &   90024700  &   GEMS    &   0   &   1   &   50.0    &   1   &   47	&   0.170   &   0.178   &      0.067  &       0.067  &     0.146    &     0.167  &0\\
+AHZ7000001  &   90024700  &   GEMS    &   1   &   1   &   0.2	    &   1   &   42	&   0.238   &   0.239   &   $-$0.110  &       0.238  &  $-$0.113    &     0.287  \\
+AHZ7000002  &   90024700  &   GEMS    &   1   &   1   &   1.0	    &   1   &   51	&   0.255   &   0.265   &   $-$0.107  &       0.264  &  $-$0.128    &     0.272  \\
+AHZ7000003  &   90024700  &   GEMS    &   0   &   1   &   5.0	    &   1   &   47	&   0.170   &   0.167   &   $-$0.018  &    $-$0.018  &  $-$0.049    &     0.033  \\
+AHZ7000004  &   90024700  &   GEMS    &   0   &   1   &   10.0    &   1   &   41	&   0.195   &   0.195   &      0.045  &       0.045  &     0.044    &     0.127  \\
+AHZ7000005  &   90024700  &   GEMS    &   0   &   1   &   50.0    &   1   &   47	&   0.170   &   0.178   &      0.067  &       0.067  &     0.146    &     0.167  \\
 $\ldots$    \\
-AHZ700013m  &   90024700  &   GEMS    &   0   &   2   &   0.0	    &   0   &   35	&   0.171   &   0.136   &      0.011  &       0.011  &     0.029    &      0.112 &0\\
-AHZ700013n  &   90024700  &   GEMS    &   1   &   2   &   0.2	    &   1   &   20	&   0.150   &   0.158   &   $-$0.278  &       0.049  &  $-$0.351    &      0.049 &0\\
-AHZ700013o  &   90024700  &   GEMS    &   1   &   2   &   1.0	    &   1   &   32	&   0.281   &   0.300   &   $-$0.086  &       0.281  &  $-$0.119    &      0.281 &0\\
-AHZ700013p  &   90024700  &   GEMS    &   0   &   2   &   5.0	    &   1   &   29	&   0.103   &   0.115   &   $-$0.098  &    $-$0.098  &  $-$0.152    &   $-$0.069 &0\\
-AHZ700013q  &   90024700  &   GEMS    &   0   &   2   &   10.0    &   1   &   35	&   0.171   &   0.181   &      0.027  &       0.027  &     0.023    &      0.106 &0\\
-AHZ700013r  &   90024700  &   GEMS    &   0   &   2   &   50.0    &   1   &   34	&   0.206   &   0.206   &   $-$0.005  &    $-$0.005  &  $-$0.056    &      0.026 &0\\
+AHZ700013m  &   90024700  &   GEMS    &   0   &   2   &   0.0	    &   0   &   35	&   0.171   &   0.136   &      0.011  &       0.011  &     0.029    &      0.112 \\
+AHZ700013n  &   90024700  &   GEMS    &   1   &   2   &   0.2	    &   1   &   20	&   0.150   &   0.158   &   $-$0.278  &       0.049  &  $-$0.351    &      0.049 \\
+AHZ700013o  &   90024700  &   GEMS    &   1   &   2   &   1.0	    &   1   &   32	&   0.281   &   0.300   &   $-$0.086  &       0.281  &  $-$0.119    &      0.281 \\
+AHZ700013p  &   90024700  &   GEMS    &   0   &   2   &   5.0	    &   1   &   29	&   0.103   &   0.115   &   $-$0.098  &    $-$0.098  &  $-$0.152    &   $-$0.069 \\
+AHZ700013q  &   90024700  &   GEMS    &   0   &   2   &   10.0    &   1   &   35	&   0.171   &   0.181   &      0.027  &       0.027  &     0.023    &      0.106 \\
+AHZ700013r  &   90024700  &   GEMS    &   0   &   2   &   50.0    &   1   &   34	&   0.206   &   0.206   &   $-$0.005  &    $-$0.005  &  $-$0.056    &      0.026 \\
 $\ldots$    \\

### 2016-05-18 writeup/gz_hubble_data.tex
consistent 'recolored' label in S2

--- 2016-05-17 writeup/gz_hubble_data.tex
@@
 
-\keywords{galaxies:structure --- galaxies:high redshift --- galaxies:evolution --- methods:data analysis --- catalogs}
+\keywords{galaxies:structure --- galaxies:high redshift --- galaxies:evolution
+--- methods:data analysis --- catalogs}
 
@@
 \end{itemize}
+
+%Selection of galaxies from these samples is described in Section \ref{ssec:galselect} below. 
+In the ACS-GC \citep{gri12}, individual galaxies were identified using a
+combination of \sextractor{} \citep{ber96} and the galaxy-profile fitting
+framework \galapagos{} \citep{bar12}. GZH included all galaxies with $m<23.5$,
+where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS, GEMS +
+GOODS-S (2-epoch), and GOODS-N (2-epoch) surveys, respectively. The full-depth
+GOODS images from both fields included galaxies with $m<26.8$. This yielded a
+total of 113,166~images (Table~\ref{tbl:gzh_numbers}).
+
+Images from \hst{} legacy surveys were used to create multiple different color
+and grayscale images using different depths and filter combinations; these are
+described further in Section \ref{ssec:images}. Additionally, the use of a
+small set of \hst{} images to create simulated images of active galactic
+nucleus (AGN) host galaxies is described in Section \ref{ssec:sim_agn}.
 
@@
 
-\subsection{Galaxy selection}
-
-In the ACS-GC \citep{gri12}, individual galaxies were identified using a
-combination of \sextractor{} \citep{ber96} and the \sersic-profile fitting
-framework \galapagos{} \citep{bar12}. GZH included all galaxies with $m<23.5$,
-where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS, GEMS +
-GOODS-S, and GOODS-N surveys, respectively. This yielded a total of
-113,166~images (Table~\ref{tbl:gzh_numbers}).
-
+\subsection{The Sloan Digital Sky Survey}\label{ssec:sdss}
+
+The project includes images from the Sloan Digital Sky Survey
+\citep[SDSS;][]{yor00,str02}, in particular those from Data~Release~7
+\citep{aba09}. A small number of images were used in the creation of simulated
+\hst{} images, described in Sections \ref{ssec:ferengi} and \ref{sec:debiasing}
+below; the majority of SDSS images used in GZH were from Stripe~82. The
+Stripe~82 samples in GZH include single-epoch and co-added images, intended to
+facilitate comparison of morphological classification with image depth.
+
+%The creation of 51,861 images from these sources is described in Section
+%\ref{ssec:galselect} below.
 Single-epoch images from SDSS Stripe~82 were selected using the same criteria
@@
 
-\subsection{Image creation}
-
-The images used for classification in GZH were color-composite JPEGs made from
-multi-band data. These were created followed the method of \citet{lup04}, which
-preserves colour information irrespective of intensity.  An asinh intensity
-mapping was applied to enhance the appearance of faint features while avoiding
-saturating galaxy centers. The relative scalings of the filter bands were
-chosen while trying to reproduce the color appearance of the SDSS images in
-previous iterations of Galaxy Zoo.
-
-Many of the Legacy surveys described in Section~\ref{ssec:legacy_surveys}
-provided images in only two filters. For these, the shorter-wavelength band was
-mapped to the blue channel, the longer-wavelength band to the red channel, and
-the green channel created by taking the arithmetic mean of the two. The bands
-used in each of the surveys are listed in Table~\ref{tbl:gzh_numbers}.
-Although four bands were available for the GOODS survey, only two bands were
-used to create the original 2-epoch images, for consistency with AEGIS and
-GEMS. The 2-epoch GOODS-N and GOODS-S images were created using different
-filters --- this was a deliberate choice made so that the GEMS images could be
-directly compared with the overlapping coverage of GOODS-S
-(Figure~\ref{fig:filtercurves}).
-
-Only 2-epoch GOODS images were included at the launch of GZH.  Deeper, 5-epoch 
-GOODS images were added into GZH later (in March 2015). These images made
-use of the full four-band data by using the arithmetic mean of \Bband{} and
-\Vband{} in the blue channel, \Iband{} in the green channel, and \zband{} in
-the red channel.
-
-The COSMOS survey provided only \Iband{} HST imaging at the time of the GZH
-launch.  These galaxies used ``pseudocolor'' images created by using
-the ACS \Iband{} data as an illumination map and ground-based imaging from the
-\subaru{} telescope in $B_J$, $r^+$, and $i^+$ filters to provide color
-information (see \citealt{gri12} for further details). This resulted in images
-with the angular resolution of \hst{} ($\sim0.05$~\arcsec/pixel) for the
-overall intensity, but color gradients at ground-based resolution, with seeing
-between 0.95\arcsec{} and 1.05\arcsec{} \citep{tan07}.
-
-Stripe~82 single-epoch images were taken directly from the DR7 SDSS Skyserver,
-which combined $g^{\prime}$, $r^{\prime}$, and $i^{\prime}$ exposures into the
-RGB channels. The co-added Stripe~82 images were assembled from runs 106 and
-206 in DR7 and processed into color composites in the same manner as previous
-iterations of Galaxy~Zoo.
-
-In some cases, we found that attempting to emphasize faint features in the
-images resulted in the sky noise taking the appearance of brightly colored
-speckles. This impaired the aesthetics of the images and might have been a
-distraction to visual classification.  To counteract this, a soft-edged object
-mask was applied to the color images and a desaturation operation performed.
-This masked procedure was effective in preserving the color balance for
-galaxies, retaining the visibility of faint features, but reduced the color
-contrast in the sky noise and greatly improved the appearance of the images.
-This solution was applied to the coadded Stripe~82, COSMOS and 5-epoch GOODS
-images.
-
-\subsection{Images with simulated nuclear point sources}
-
-GZH also included a set of images designed to measure the effect of active
-galactic nuclei (AGN) on morphological classifications. Since galactic nuclei
-can have bright, unresolved optical emission, AGN have the potential to mimic
-or distort the identification of a bulge component. The presence of an AGN was
-simulated by modeling the point spread function (PSF) of the telescope and then
-inserting a bright source near the center of a real galaxy. For each image, the
-simulated AGN was assigned one of three colors -- either blue, red, or flat
-(white) as seen in the color images -- and a range of brightnesses such that
+\subsection{Simulated \hst{} images}\label{ssec:simulatedimages}
+
+To facilitate correction of classifications in the presence of known biasing
+effects, GZH includes two different samples of simulated \hst{} images: real
+\hst{} galaxy images (Section \ref{ssec:legacy_surveys}) with nuclear emission
+added to simulate AGN host galaxies, and lower-redshift galaxy images from SDSS
+(Section \ref{ssec:sdss}), artificially redshifted from $0.3 \leq z \leq 1$.
+Each is described separately below.
+
+\subsubsection{Images with simulated nuclear point sources}\label{ssec:sim_agn}
+
+As active galactic nuclei often have bright, unresolved optical emission, AGN
+have the potential to mimic or distort the identification of a bulge component.
+GZH thus includes a set of images designed to measure the effect of AGN on
+morphological classifications.  The presence of an AGN was simulated by
+modeling the point spread function (PSF) of the telescope and then inserting a
+bright source near the center of a real galaxy. For each image, the simulated
+AGN was assigned one of three colors -- either blue, red, or flat (white) as
+seen in the color images -- and a range of brightnesses such that
 $L_\mathrm{ratio} \equiv L_\mathrm{galaxy}/L_\mathrm{AGN}$ is in
-$(0.2,1.0,2.0,5.0,10.0,50.0)$. This range was selected to run from AGN which
-were all but undetectable through to those which dominate the galaxy, providing
-coverage of all plausible effects. Combining these parameters generated
-15~images with different simulated AGN for each host.
+$(0.2,1.0,2.0,5.0,10.0,50.0)$. Combining these parameters generated 15~images
+with different simulated AGN for each host, in addition to the original galaxy
+image.
 
@@
 regarding image modifications.
+
+\subsubsection{Generating images of artificially-redshifted galaxies}\label{ssec:ferengi}
+
+The dimming and resolution effects of redshift can significantly affect galaxy
+classifications derived from any method. To facilitate corrections due to
+redshift, we include a sample of 288 galaxies with at redshifts such that
+available SDSS imaging can be transformed to simulate \hst{} imaging out to $z
+= 1$. The selection spanned a variety of galaxy morphologies (as selected by
+GZ2 classifications) and $r^\prime$-band surface brightnesses, and also spanned
+the redshift range of SDSS targets (in $N_z = 4$ bins) in order to optimize for
+different target minimum redshifts in \hst{} imaging. We redshifted the
+galaxies and produced simulated \hst{} imaging using the \ferengi{} code
+\citep{bar08a}.
+
+%The selection criteria for the different morphological categories is
+%summarized in Table \ref{tbl:morphologies}. 
+The surface brightness selection ($N_\mu = 3$) for the \ferengi{} galaxies was
+(1) low: $\mu > 21.5$~\magarc;  (2) mid: $20.5 < \mu < 21.5$~\magarc; and (3)
+high: $\mu < 20.5$~\magarc. For each of the four ``target redshifts''
+($z_\mathrm{sim} = 0.3, 0.5, 0.8$ and $1.0$), the images were redshifted in
+$\Delta z = 0.1$ bins up to $z_\mathrm{sim}=1.0$.
+
+%\begin{table*}
+%\center
+%\caption{Summary of morphological categories selected for \ferengi{} sample.\label{tbl:morphologies}}
+%\begin{tabular}{lllc}
+%\hline\hline
+%Morphology          & Label &  Selection                                                                                            & $N_{\rm objects}$ \\
+%                    &       &                                                                                                       & [$N_z \times N_\mu$] \\
+%\hline
+%Features            & Yes       & $f_{\rm features} > 0.8$, $f_{\rm odd} < 0.1$                                                         & 12 \\ 
+%                    & Int.      & $0.3 < f_{\rm smooth} < 0.6$, $f_{\rm odd} < 0.1$                                                     & 12 \\ 
+%                    & No        & $f_{\rm smooth} > 0.8$, $f_{\rm odd} < 0.1$                                                           & 12 \\ 
+%Merger              & No        & $f_{\rm features} > 0.8$, $f_{\rm odd < 0.1}$, $f_{\rm merger} < 0.1$                                 & 12 \\
+%                    & Int.      & $f_{\rm odd} > 0.5$, $0.1< f_{\rm merger} < 0.4$                                                      & 12 \\ 
+%                    & Yes       & $f_{\rm odd} > 0.5$, $f_{\rm merger} > 0.4$                                                           & 12 \\
+%Edge-on             & Yes       & $f_{\rm edgeon} > 0.8$, $f_{\rm features} > 0.5$                                                      & 12 \\
+%                    & Int.      & $0.4 < f_{\rm edgeon} < 0.8$ , $f_{\rm features} > 0.5$                                               & 12 \\
+%                    & No        & $f_{\rm edgeon} < 0.2$, $f_{\rm features} > 0.5$                                                      & 12 \\
+%Bar                 & No        & $f_{\rm bar} < 0.1$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$                                 & 24 \\
+%                    & Int.      & $0.2 < f_{\rm bar} < 0.4$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$                           & 24 \\
+%                    & Yes       & $f_{\rm bar} > 0.8$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$                                 & 24 \\
+%Visible spiral      & No        & $f_{\rm spiral} < 0.2$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$, $f_{\rm bar} < 0.1$         & 12 \\
+%                    & Int.      & $0.2 < f_{\rm spiral} < 0.8$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$, $f_{\rm bar} < 0.1$   & 12 \\
+%                    & Yes       & $f_{\rm spiral} > 0.8$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$, $f_{\rm bar} < 0.1$         & 12 \\
+%Oblique bulge size  & No        & $f_{\rm nobulge>0.6}$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.5$, $f_{\rm bar} < 0.2$          & 12 \\
+%                    & Int.      & $f_{\rm justnoticeable}>0.6$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.5$, $f_{\rm bar} < 0.2$   & 12 \\
+%                    & Yes       & $f_{\rm obvious|dominant}>0.5$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.5$, $f_{\rm bar} < 0.2$ & 12 \\
+%Edge-on bulge shape & Round     & $f_{\rm rounded}>0.5$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} > 0.5$                               & 12 \\
+%                    & Boxy      & $f_{\rm boxy}>0.4$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} > 0.2$                                  & 12 \\
+%                    & No bulge  & $f_{\rm nobulge}>0.5$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} > 0.5$                               & 12 \\
+%\hline\hline
+%\end{tabular}
+%\end{table*}
+
+In addition to the physical parameters of the input images, the \ferengi{}
+output depends on assumptions of the global galaxy evolution model. This
+evolution is a crude mechanism that mimics the brightness increase of galaxies
+with increasing redshift (out to at least $z\sim1-2$). The effect on the
+redshifted images is simply an empirical addition to the magnitude of a galaxy
+of the form $M' = e\times z + M$, where $M'$ is the corrected magnitude, and
+$e$ is the evolutionary correction in magnitudes (i.e., $e=-1$ essentially
+brightens the galaxy by 1~magnitude by $z=1$). \ferengi{} was run on the images
+for values of $e$ starting from $e=0$ and decreasing to $e=-3.5$ in increments
+of $\Delta e = 0.5$. Figure~\ref{fig:exampleFERENGI} shows several examples
+of the effects of ``losing'' spiral/disc features with increasing redshift
+for two galaxies with $e=0$.
+
+The final number of \ferengi{} images produced for each galaxy is ultimately a
+function of galaxy's redshift (since the new images cannot be resampled at
+better angular resolution than the original SDSS data), as well as the number
+of $e$ values selected. Table~\ref{tbl:ferengivalues} summarizes the redshifted
+images produced for GZH. The use of these images to correct for redshift-dependent
+classification bias is described in Section \ref{sec:debiasing}.
+
+\begin{table}
+\caption{Summary of \ferengi{} artificial redshifting \label{tbl:ferengivalues}}
+\begin{tabular}{lccccr}
+\hline\hline
+$z_{\rm sim}$ & $N_{z {\rm bins}}$ & $N_{\rm evolution}$ & $e_{\rm max}$ & $N_{\rm galaxies}$ & $N_{\rm images}$\\
+\hline
+0.3              & 8                  & 7                   & $-3.0$        & 72             & 4032 \\
+0.5              & 6                  & 4                   & $-1.5$        & 72             & 1728 \\
+0.8              & 3                  & 3                   & $-1.0$        & 72             &  648 \\
+1.0              & 1                  & 3                   & $-1.0$        & 72             &  216 \\
+\hline\hline
+\end{tabular}
+\end{table}
+
+\begin{figure*}
+\center
+\includegraphics[width=160mm]{figures/example_ferengi.pdf}
+\caption{Examples of two galaxies which have been run through the \ferengi{}
+code to produce simulated \hst{} images. The measured value of \ffeatures{}
+from GZH for the images in each panel are (1) Top row: \ffeatures~= (0.900,
+0.625, 0.350, 0.350, 0.225) and (2) Bottom row: \ffeatures~= (1.000, 0.875,
+0.875, 0.625, 0.375). \label{fig:exampleFERENGI}}
+\end{figure*}
+
+\subsection{Image creation}\label{ssec:images}
+
+The images used for classification in GZH were color-composite JPEGs made from
+multi-band data. These were created followed the method of \citet{lup04}, which
+preserves colour information irrespective of intensity.  An asinh intensity
+mapping was applied to enhance the appearance of faint features while avoiding
+saturating galaxy centers. The relative scalings of the filter bands were
+chosen while trying to reproduce the color appearance of the SDSS images in
+previous iterations of Galaxy Zoo.
+
+Many of the Legacy surveys described in Section~\ref{ssec:legacy_surveys}
+provided images in only two filters. For these, the shorter-wavelength band was
+mapped to the blue channel, the longer-wavelength band to the red channel, and
+the green channel created by taking the arithmetic mean of the two. The bands
+used in each of the surveys are listed in Table~\ref{tbl:gzh_numbers}.
+Although four bands were available for the GOODS survey, only two bands were
+used to create the original 2-epoch images, for consistency with AEGIS and
+GEMS. The 2-epoch GOODS-N and GOODS-S images were created using different
+filters --- this was a deliberate choice made so that the GEMS images could be
+directly compared with the overlapping coverage of GOODS-S
+(Figure~\ref{fig:filtercurves}).
+
+Only 2-epoch GOODS images were included at the launch of GZH.  Deeper, 5-epoch 
+GOODS images were added into GZH later (in March 2015). These images made
+use of the full four-band data by using the arithmetic mean of \Bband{} and
+\Vband{} in the blue channel, \Iband{} in the green channel, and \zband{} in
+the red channel.
+
+The COSMOS survey provided only \Iband{} HST imaging at the time of the GZH
+launch.  These galaxies used ``pseudocolor'' images created by using
+the ACS \Iband{} data as an illumination map and ground-based imaging from the
+\subaru{} telescope in $B_J$, $r^+$, and $i^+$ filters to provide color
+information (see \citealt{gri12} for further details). This resulted in images
+with the angular resolution of \hst{} ($\sim0.05$~\arcsec/pixel) for the
+overall intensity, but color gradients at ground-based resolution, with seeing
+between 0.95\arcsec{} and 1.05\arcsec{} \citep{tan07}.
+
+Stripe~82 single-epoch images were taken directly from the DR7 SDSS Skyserver,
+which combined $g^{\prime}$, $r^{\prime}$, and $i^{\prime}$ exposures into the
+RGB channels. The co-added Stripe~82 images were assembled from runs 106 and
+206 in DR7 and processed into color composites in the same manner as previous
+iterations of Galaxy~Zoo.
+
+In some cases, we found that attempting to emphasize faint features in the
+images resulted in the sky noise taking the appearance of brightly colored
+speckles. This impaired the aesthetics of the images and might have been a
+distraction to visual classification.  To counteract this, a soft-edged object
+mask was applied to the color images and a desaturation operation performed.
+This masked procedure was effective in preserving the color balance for
+galaxies, retaining the visibility of faint features while reducing the color
+contrast in the sky noise and greatly improving the appearance of the images.
+This solution was applied to the coadded Stripe~82, COSMOS and 5-epoch GOODS
+images.
+
+In addition to the main \hst{} legacy imaging sample with colored images
+described as above, GZH also includes samples of \hst{} galaxy images with
+different color prescriptions. In particular, there are 2 sets of 3,927 images
+each, drawn from the COSMOS sample; the first has a dramatically reduced color
+saturation, and the second has reversed the colors so that the blue and red
+filters have exchanged places in the RGB image. The `faded' galaxy set
+facilitates measuring of possible variations in classification due to the
+presence or absence of color features. The `recolored' set enables an
+alternative test of potential color biases in classifications.
+% I guess this means we need to say somewhere later that we don't see an effect
+% (we don't, right?).  Would also be good to cite here where we have done
+% similar things in the past...
+
+The simulated AGN host galaxy color images (described in Section \ref{ssec:sim_agn})
+were created using the same prescription as for the GOODS 2-epoch imaging. The
+artificially redshifted color images (Section \ref{ssec:ferengi}) were created using the
+same prescription as for the AEGIS images.
+% Edmond should verify the AEGIS bit above.
+
+\subsection{Galaxy sample labels}\label{ssec:sample_labels}
+
+The full GZH sample is composed of 7~different galaxy sub-samples. Throughout
+this paper and in the published catalogs they are referred to with the
+following labels:
+
+\begin{itemize}
+
+%\ref{tbl:catalog_hst}
+\item \texttt{main}: \hst{} imaging with RGB colors making use of all available
+filters with typical saturation and in correct order, as described in
+Section~\ref{ssec:images}. This sample includes AEGIS, COSMOS, GEMS, and
+full-depth GOODS (North and South) images. (118,425 galaxies)
+
+%\ref{tbl:catalog_faded}
+\item \texttt{faded}: a subset of COSMOS images with very low color saturation.
+(3,927 galaxies)
+
+%\ref{tbl:catalog_recolored}
+\item \texttt{recolored}: a subset of COSMOS images with red and blue channels
+reversed. Note: this sub-sample uses the same galaxies as the \texttt{faded}
+sub-sample. (3,927 galaxies)
+
+%\ref{tbl:catalog_goods_shallow}
+\item \texttt{goods-shallow}: Images from GOODS-North and GOODS-South, with
+color from 2 filters and imaged at 2-epoch depth. (6,144 galaxies)
+
+%\ref{tbl:stripe82_single}
+\item \texttt{stripe-82-single}: Single-epoch images from SDSS Stripe~82.
+(21,522 galaxies)
+
+%\ref{tbl:stripe82_coadd}
+\item \texttt{stripe-82-coadd}: Co-added images from SDSS Stripe~82. Note: this
+sub-sample includes all galaxies in the \texttt{stripe-82-single} sub-sample,
+with additional sources detected in the deeper imaging. (30,339 galaxies)
+
+%ferengi <-- no table?
+\item \texttt{redshifted}: Simulated \hst{} images constructed using SDSS
+images and artificially redshifted to between $0.3 \leq z \leq 1$. (288
+original galaxies; 3,950 redshifted galaxies)
+
+%\ref{tbl:simulated_agn}
+\item \texttt{simulated-agn}: Simulated AGN host galaxies constructed using
+\hst{} images and PSFs. (96 original galaxies; 2,961 simulated AGN host
+galaxies)
+
+\end{itemize}
 
@@
 GEMS, GOODS 2-epoch, and SDSS Stripe~82 images. Images from COSMOS and the
-simulated AGN were activated in Dec 2010, as well as a small sample of
-images from AEGIS, GEMS, and GOODS that were previously excluded from the original sample
-due to cuts on blended and/or saturated objects and subsequently confirmed as classifiable galaxies. The main GZH
-site collected data until its replacement, the fourth phase of
+simulated AGN were activated in Dec 2010, as well as a small sample of images
+from AEGIS, GEMS, and GOODS that were previously excluded from the original
+sample due to cuts on blended and/or saturated objects and subsequently
+confirmed as classifiable galaxies. The main GZH site collected data until its
+replacement, the fourth phase of
 Galaxy~Zoo\footnote{\url{http://zoo4.galaxyzoo.org}} (including data from both
 the \hst{} CANDELS survey and SDSS DR8) began on 10~Sep~2012. Classifications
-for the GOODS 5-epoch images were separately obtained from Mar-Jun 2015 on
-the fourth version of the Galaxy~Zoo site. The GZH project had a total of
+for the GOODS 5-epoch images were separately obtained from Mar-Jun 2015 on the
+fourth version of the Galaxy~Zoo site. The GZH project had a total of
 10,349,357~classifications from 93,898 registered participants. 
@@
 The previous versions of Galaxy Zoo morphology classifications
-\citep{lin08,wil13} were based on observations of galaxies in the Sloan Digital
+\citep{lin11,wil13} were based on observations of galaxies in the Sloan Digital
 Sky Survey (SDSS) which have a median redshift of $z<0.2$. In these cases, it
@@
 over a variety of redshifts. The input images are from the SDSS
-\citep{yor00,str02} and are processed using the \ferengi{} code \citep{bar08a}
-to match the observational properties of the \hst{} surveys out to $z=1$. These
+\citep{yor00,str02} and are processed to match the observational properties of 
+the \hst{} surveys out to $z=1$. These
 images were classified in the GZH interface using the same classification
-scheme as the original \hst{} images.
-
-\subsection{Generating images of artificially-redshifted galaxies}
+scheme as the original \hst{} images. Further details on the creation of these images
+is given in Section \ref{ssec:ferengi}.
 
@@
 $r^\prime$-band surface brightnesses, and also spanned the redshift range of
-SDSS targets that maximuze the coverage of parameter space.
-
-%The selection criteria for the different morphological categories is summarized in Table \ref{tbl:morphologies}. 
+SDSS targets that maximize the coverage of parameter space.
+
+%The selection criteria for the different morphological categories is
+%summarized in Table \ref{tbl:morphologies}. 
 The surface brightness selection ($N_\mu = 3$) for the \ferengi{} galaxies was
@@
 \end{figure*}
+>>>>>>> master
 

### 2016-05-18 writeup/gz_hubble_data.tex
Use sample labels from Section 2.5 onward

@@
 co-added magnitudes brighter than $17.77$~mag, and the galaxies detected in the
-single-depth images and matched to a co-add source. This resulted in a total
+\stripe{} images and matched to a co-add source. This resulted in a total
 set of 30,339 images. Of the images in the co-added sample, 5144 (17~percent)
@@
 
-Images with simulated AGN were classified in the main interface in an identical
+Images with simulated AGN were classified in the interface in an identical
 manner and evenly distributed with unaltered images of the galaxies.
@@
 classified; where applicable these pages contained further information
-regarding image modifications.
+regarding image modifications. \citet{sim14} uses similarly-processed
+images for reliable identification of bulgeless galaxies using SDSS data.
 
@@
 
-In addition to the main \hst{} legacy imaging sample with colored images
+In addition to the primary \hst{} legacy imaging sample with colored images
 described as above, GZH also includes samples of \hst{} galaxy images with
@@
 %\ref{tbl:catalog_hst}
-\item \texttt{main}: \hst{} imaging with RGB colors making use of all available
+\item \main: \hst{} imaging with RGB colors making use of all available
 filters with typical saturation and in correct order, as described in
@@
 %\ref{tbl:catalog_faded}
-\item \texttt{faded}: a subset of COSMOS images with very low color saturation.
+\item \faded: a subset of COSMOS images with very low color saturation.
 (3,927 galaxies)
@@
 %\ref{tbl:catalog_recolored}
-\item \texttt{recolored}: a subset of COSMOS images with red and blue channels
+\item \recolored: a subset of COSMOS images with red and blue channels
 reversed. Note: this sub-sample uses the same galaxies as the \texttt{faded}
@@
 %\ref{tbl:catalog_goods_shallow}
-\item \texttt{goods-shallow}: Images from GOODS-North and GOODS-South, with
+\item \goods: Images from GOODS-North and GOODS-South, with
 color from 2 filters and imaged at 2-epoch depth. (6,144 galaxies)
@@
 %\ref{tbl:stripe82_single}
-\item \texttt{stripe-82-single}: Single-epoch images from SDSS Stripe~82.
+\item \stripe: Single-epoch images from SDSS Stripe~82.
 (21,522 galaxies)
@@
 %\ref{tbl:stripe82_coadd}
-\item \texttt{stripe-82-coadd}: Co-added images from SDSS Stripe~82. Note: this
+\item \coadd: Co-added images from SDSS Stripe~82. Note: this
 sub-sample includes all galaxies in the \texttt{stripe-82-single} sub-sample,
@@
 %ferengi <-- no table?
-\item \texttt{redshifted}: Simulated \hst{} images constructed using SDSS
+\item \redshifted: Simulated \hst{} images constructed using SDSS
 images and artificially redshifted to between $0.3 \leq z \leq 1$. (288
@@
 %\ref{tbl:simulated_agn}
-\item \texttt{simulated-agn}: Simulated AGN host galaxies constructed using
+\item \simagn: Simulated AGN host galaxies constructed using
 \hst{} images and PSFs. (96 original galaxies; 2,961 simulated AGN host
@@
 
-Photometric data for the bulk of the GZH sample were largely drawn from the
-tables in \citet{gri12}. This included photometric parameters such as
-the fluxes, magnitudes, radii, ellipticities, position angles, and positions
-drawn from both \sextractor{} and \galfit. \galfit{} also provided the
-parametric \sersic{} index and effective half-light radius for the best-fit
-model. All parameters were measured in both bands of the ACS imaging, with the
-exception of the single-band COSMOS images.
+Photometric data for the bulk of the GZH \main, \faded, \recolored, and \goods{}
+samples were largely drawn from the tables in \citet{gri12}. This included
+photometric parameters such as the fluxes, magnitudes, radii, ellipticities,
+position angles, and positions drawn from both \sextractor{} and \galfit.
+\galfit{} also provided the parametric \sersic{} index and effective half-light
+radius for the best-fit model. All parameters were measured in both bands of
+the ACS imaging, with the exception of the single-band COSMOS images.
 
@@
 
-Photometric and spectroscopic data for the SDSS Stripe~82 galaxies were taken
+Photometric and spectroscopic data for the \stripe{} and \coadd{} galaxies were taken
 from the CasJobs DR7 tables. This included $ugriz$ Petrosian magnitudes and
@@
 model magnitudes. All redshifts used for SDSS galaxies were spectroscopic.
-82.6\% of galaxies in the single-depth images and 65.1\% of galaxies in the
-co-add images had a measured DR7 spectroscopic redshift.
+82.6\% of galaxies in the \stripe{} images and 65.1\% of galaxies in the
+\coadd{} images had a measured DR7 spectroscopic redshift.
 
@@
 decision tree and the relative difficulty of classifying images of small and
-distant galaxies. Images from the main AEGIS, GEMS, and GOODS data sets had a
-median of 122~independent classifications per image. The remainder of the
-images either had a later activation date (COSMOS, simulated AGN) or a lower
-retirement limit (the low-redshift SDSS Stripe~82 galaxies). Images from these
-samples had a median of 46--48~classifications per image
-(Figure~\ref{fig:classification_hist}).
+distant galaxies. Images from the \main{} AEGIS, GEMS, and GOODS data sets had
+a median of 122~independent classifications per image. The remainder of the
+images either had a later activation date (\main{} COSMOS, \simagn) or a lower
+retirement limit (\stripe{} and \coadd). Images from these samples had a median
+of 46--48~classifications per image (Figure~\ref{fig:classification_hist}).
 
@@
 sample due to cuts on blended and/or saturated objects and subsequently
-confirmed as classifiable galaxies. The main GZH site collected data until its
+confirmed as classifiable galaxies. The GZH site collected data until its
 replacement, the fourth phase of
@@
 
-Data products for GZH are split by the type of image being classified.
-Table~\ref{tbl:catalog_hst} contains the classifications for the \hst{} images
-from the AEGIS, COSMOS, and GEMS surveys, as well as 5-epoch deep imaging from
-the GOODS-N and GOODS-S surveys. This contains 118,425~galaxies and is the
-primary output from the GZH project. The next two tables have data for a small
-subset of 3,927~COSMOS~images that were re-processed to study the effect of
-color balance on morphological classification. Table~\ref{tbl:catalog_faded}
-has images that are desaturated to minimize the color contrast;
-Table~\ref{tbl:catalog_recolored} has images with the red and blue color
-channels inverted. Table~\ref{tbl:catalog_goods_shallow} contains data for
-6,144~galaxies with 2-epoch images from GOODS. These have been mostly
-supplanted in the main table with deeper 5-epoch GOODS imaging; however, there
-are 1,683~galaxies in the shallower imaging that were not classified in the
-deeper mosaics. This data can also be compared to the counterparts in
-Table~\ref{tbl:catalog_hst} to study the effect of depth on morphological
-classification. Tables~\ref{tbl:stripe82_single} and \ref{tbl:stripe82_coadd}
-contain data for the SDSS Stripe~82 single-depth and co-added images,
-respectively, that were classified using the GZH interface and decision tree.
-Finally, Table~\ref{tbl:simulated_agn} contains classifications for images with
-artificial point sources intended to simulate the effect of a bright AGN (see
-\citealt{sim14} for an example).
+Data products for GZH are split by the type of image being classified. Each
+sample in Section~\ref{ssec:sample_labels} corresponds to the data in
+Tables~\ref{tbl:Catalog_hst}-\ref{tbl:simulated_agn}.
 
@@
 GZ2. \citet{lin11} found that elliptical galaxies exceeded spiral galaxies by a
-factor of $\sim2:1$ in the main spectroscopic sample if using a plurality vote
+factor of $\sim2:1$ in their spectroscopic sample if using a plurality vote
 criterion (although \citealt{bam09} show that this strongly depends on the
@@
 in \citet{hau07} to the GZH sample gives 8,846~galaxies in both \citet{hau07}
-and GZH. The main morphological parameter in the automated catalog is the
+and GZH. The primary morphological parameter in the automated catalog is the
 \sersic{} index $n$ defining the radial surface brightness profile.
@@
 GZH used both 5-epoch and 2-epoch sets of data to construct the GOODS set of
-images. The 11,157 full depth 5-epoch images are used in the main catalog; the
-classifications for the 7,464 shallow depth 2-epoch images are provided as a
+images. The 11,157 full depth 5-epoch images are used in the \main{} catalog; the
+classifications for the 7,464 \goods{} images are provided as a
 supplementary table. This section analyzes the effect of image depth on the
@@
 \caption{Distribution of \ffeatures{} for the 4,461 GOODS galaxies with both
-shallow (2-epoch) and full-depth (5-epoch) images morphologically classified in
-GZH. For most galaxies, the value of \ffeatures{} is consistent ($\Delta
-f_\mathrm{features}<0.2$) between depths. Examples of galaxies with sharp
-changes in \ffeatures, as well as those with little to no change are shown in
+shallow (2-epoch; \goods) and full-depth (5-epoch; \main) images
+morphologically classified in GZH. For most galaxies, the value of \ffeatures{}
+is consistent ($\Delta f_\mathrm{features}<0.2$) between depths. Examples of
+galaxies with sharp changes in \ffeatures, as well as those with little to no
+change are shown in
 Figures~\ref{fig:shallow_smooth}-\ref{fig:shallow_featured}.}

### 2016-05-18 writeup/gz_hubble_data.tex
Remove reference to Johnson+15 on distraction bias

--- 2016-05-18 writeup/gz_hubble_data.tex
@@
 
-The approach used in GZH for correcting the weighted classifications for redshift
-bias rests on the assumption that the \emph{degree} of bias is a function of
-the apparent size and brightness of the image as seen on screen. This is
-controlled by two types of parameters: \textbf{intrinsic} properties of the
-galaxy itself, such as its physical diameter and luminosity, and
+The approach used in GZH for correcting the weighted classifications for
+redshift bias rests on the assumption that the \emph{degree} of bias is a
+function of the apparent size and brightness of the image as seen on screen.
+This is controlled by two types of parameters: \textbf{intrinsic} properties of
+the galaxy itself, such as its physical diameter and luminosity, and
 \textbf{extrinsic} properties, such as the distance (redshift) of the galaxy
 and its relative orientation. There may also be other parameters that affect
-classifier accuracy, such as the proximity of close companions \citep[``distraction
-bias''; see][]{joh15} or bias as a function of individual classifier ability and
-skill. The combination of all such parameters forms a high-dimensional space,
-and it is not clear how to separate this into individual effects. Instead, the
-method used here employs only two parameters intended to capture the bulk of
-the change in bias: the $r^\prime$-band surface brightness ($\mu_r$; intrinsic)
-and redshift ($z$; extrinsic).
+classifier accuracy, such as the proximity of close companions or bias as a
+function of individual classifier ability and skill. The combination of all
+such parameters forms a high-dimensional space, and it is not clear how to
+separate this into individual effects. Instead, the method used here employs
+only two parameters intended to capture the bulk of the change in bias: the
+$r^\prime$-band surface brightness ($\mu_r$; intrinsic) and redshift ($z$;
+extrinsic).
 

### 2016-05-18 python/comparisons.py
Spelling is Haeussler, not Hauessler

@@ -221,7 +221,7 @@ def gems():
     print "Clumpy galaxies  n: {0:.2f}+-{1:.2f}".format(np.mean(data[clumpy_sample]['n']),np.std(data[clumpy_sample]['n']))
     print "Clumpy galaxies Re: {0:.0f}+-{1:.0f}".format(np.mean(data[clumpy_sample]['Re']),np.std(data[clumpy_sample]['Re']))
 
-    # Plot Figure 16 from Haussler+07
+    # Plot Figure 16 from Haeussler+07
 
 
     fig = plt.figure(figsize=(10,6))
@@ -792,7 +792,7 @@ def frac_all(zint=0.0,zlow=0.0):
               'classcol':'AUTOCLASS'},
              {'data':gems,
               'survey':'GEMS',
-              'citation':'Hauessler+07',
+              'citation':'Haeussler+07',
               'classcol':'TYPE'},
              {'data':zest,
               'survey':'COSMOS',

### 2016-05-19 writeup/gz_hubble_data.tex
Reference Tom's findings of flat f_bar[z]

@@
 luminosity cut, and the use of debiased values for \ffeatures{} increases the
-total amount of disks in the sample compared to \citet{mel14}. For a more
-thorough analysis of the bar fraction, a cut on \fbar{} that evolves with
-redshift may yield more accurate results, since there are no explicit debiased
-values of \fbar{} that would take redshift induced bias into account.
+total amount of disks in the sample compared to \citet{mel14}. However, the
+results from GZH indicate that if features are reliably identified, the bar is
+always visible; for galaxies at increasing redshifts, the discs fade first but
+the galactic bar remains visible \citep{mel16}. As a result, we do \emph{not}
+recommend using an evolving cut on \fbar{} as a function of redshift for the
+selection of barred discs.
 

### 2016-05-19 writeup/gz_hubble_data.tex
Doubled text leftover from merge
KLM comments on intro. Closes #129.

--- 2016-05-18 writeup/gz_hubble_data.tex
@@
 scaling to large surveys and potential issues with replicability and
-calibration. Automated measurements, both parametric \citep{pen02a,sim11,lac12}
-and non-parametric \citep{abr03,con03,lot04,sca07,bam08,fre13}, scale well to
-very large sample sizes, but do not always fully capture the relevant features,
-especially for asymmetric galaxies that become increasingly common at high
-redshifts. The Galaxy Zoo project \citep{lin08} utilizes crowdsourced visual
-classifications to measure galaxies in color-composite images. The efforts of
-more than $2\times10^5$~classifiers allow for multiple independent
-classifications of each image which are combined and calibrated to give a
-distribution of vote fractions proportional to the probability of a feature
-being visible. While crowdsourced data require extensive calibration
-\citep{bam09,wil13}, they have a proven reliability and have been used for a
-wide variety of scientific studies
-\citep[eg,][]{lan08,bam09,dar10,mas11c,ski12,sim13,sch14,wil15}.
+calibration (e.g., see \citealt{lah95} for a discussion on the extent to which
+eight expert classifiers agree with each other). Automated measurements, both
+parametric \citep{pen02a,sim11,lac12} and non-parametric
+\citep{abr03,con03,lot04,sca07,bam08,fre13}, scale well to very large sample
+sizes, but do not always fully capture the relevant features, especially for
+asymmetric galaxies that become increasingly common at high redshifts. The
+Galaxy Zoo project \citep{lin08} utilizes crowdsourced visual classifications
+to measure galaxies in color-composite images. The efforts of more than
+$2\times10^5$~classifiers allow for multiple independent classifications of
+each image which are combined and calibrated to give a distribution of vote
+fractions proportional to the probability of a feature being visible. While
+crowdsourced data require extensive calibration \citep{bam09,wil13}, they have
+a proven reliability and have been used for a wide variety of scientific
+studies \citep[eg,][]{lan08,bam09,dar10,mas11c,ski12,sim13,sch14,wil15}.
 
@@
 Galaxy Zoo: CANDELS project has also classified morphologies of galaxies at
-high redshift using ACS and WFC3 imaging (Simmons et~al., submitted).
+high redshift, but using ACS and WFC3 rest-frame infrared imaging (Simmons
+et~al., submitted).
 
@@
 SDSS targets that maximize the coverage of parameter space.
-
-%The selection criteria for the different morphological categories is
-%summarized in Table \ref{tbl:morphologies}. 
-The surface brightness selection ($N_\mu = 3$) for the \ferengi{} galaxies was
-(1) low: $\mu > 21.5$~\magarc;  (2) mid: $20.5 < \mu < 21.5$~\magarc; and (3)
-high: $\mu < 20.5$~\magarc. For each of the four ``target redshifts''
-($z_\mathrm{sim} = 0.3, 0.5, 0.8$ and $1.0$), the images were redshifted in
-$\Delta z = 0.1$ bins up to $z_\mathrm{sim}=1.0$.
-
-%\begin{table*}
-%\center
-%\caption{Summary of morphological categories selected for \ferengi{} sample.\label{tbl:morphologies}}
-%\begin{tabular}{lllc}
-%\hline\hline
-%Morphology          & Label &  Selection                                                                                            & $N_{\rm objects}$ \\
-%                    &       &                                                                                                       & [$N_z \times N_\mu$] \\
-%\hline
-%Features            & Yes       & $f_{\rm features} > 0.8$, $f_{\rm odd} < 0.1$                                                         & 12 \\ 
-%                    & Int.      & $0.3 < f_{\rm smooth} < 0.6$, $f_{\rm odd} < 0.1$                                                     & 12 \\ 
-%                    & No        & $f_{\rm smooth} > 0.8$, $f_{\rm odd} < 0.1$                                                           & 12 \\ 
-%Merger              & No        & $f_{\rm features} > 0.8$, $f_{\rm odd < 0.1}$, $f_{\rm merger} < 0.1$                                 & 12 \\
-%                    & Int.      & $f_{\rm odd} > 0.5$, $0.1< f_{\rm merger} < 0.4$                                                      & 12 \\ 
-%                    & Yes       & $f_{\rm odd} > 0.5$, $f_{\rm merger} > 0.4$                                                           & 12 \\
-%Edge-on             & Yes       & $f_{\rm edgeon} > 0.8$, $f_{\rm features} > 0.5$                                                      & 12 \\
-%                    & Int.      & $0.4 < f_{\rm edgeon} < 0.8$ , $f_{\rm features} > 0.5$                                               & 12 \\
-%                    & No        & $f_{\rm edgeon} < 0.2$, $f_{\rm features} > 0.5$                                                      & 12 \\
-%Bar                 & No        & $f_{\rm bar} < 0.1$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$                                 & 24 \\
-%                    & Int.      & $0.2 < f_{\rm bar} < 0.4$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$                           & 24 \\
-%                    & Yes       & $f_{\rm bar} > 0.8$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$                                 & 24 \\
-%Visible spiral      & No        & $f_{\rm spiral} < 0.2$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$, $f_{\rm bar} < 0.1$         & 12 \\
-%                    & Int.      & $0.2 < f_{\rm spiral} < 0.8$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$, $f_{\rm bar} < 0.1$   & 12 \\
-%                    & Yes       & $f_{\rm spiral} > 0.8$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$, $f_{\rm bar} < 0.1$         & 12 \\
-%Oblique bulge size  & No        & $f_{\rm nobulge>0.6}$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.5$, $f_{\rm bar} < 0.2$          & 12 \\
-%                    & Int.      & $f_{\rm justnoticeable}>0.6$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.5$, $f_{\rm bar} < 0.2$   & 12 \\
-%                    & Yes       & $f_{\rm obvious|dominant}>0.5$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.5$, $f_{\rm bar} < 0.2$ & 12 \\
-%Edge-on bulge shape & Round     & $f_{\rm rounded}>0.5$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} > 0.5$                               & 12 \\
-%                    & Boxy      & $f_{\rm boxy}>0.4$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} > 0.2$                                  & 12 \\
-%                    & No bulge  & $f_{\rm nobulge}>0.5$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} > 0.5$                               & 12 \\
-%\hline\hline
-%\end{tabular}
-%\end{table*}
-
-In addition to the physical parameters of the input images, the \ferengi{}
-output depends on assumptions of the global galaxy evolution model. This
-evolution is a crude mechanism that mimics the brightness increase of galaxies
-with increasing redshift (out to at least $z\sim1-2$). The effect on the
-redshifted images is simply an empirical addition to the magnitude of a galaxy
-of the form $M' = e\times z + M$, where $M'$ is the corrected magnitude, and
-$e$ is the evolutionary correction in magnitudes (i.e., $e=-1$ essentially
-brightens the galaxy by 1~magnitude by $z=1$). \ferengi{} was run on the images
-for values of $e$ starting from $e=0$ and increasing the effect to $e=-3.5$ in
-increments of $\Delta e = 0.5$. Figure~\ref{fig:exampleFERENGI} shows
-several examples of the effects of ``losing'' spiral/disc features with
-increasing redshift for two galaxies with $e=0$.
-
-The final number of \ferengi{} images produced for each galaxy is ultimately a
-function of galaxy's redshift (since the new images cannot be resampled at
-better angular resolution than the original SDSS data), as well as the number
-of $e$ values selected. Table~\ref{tbl:ferengivalues} summarizes the redshifted
-images produced for GZH.
-
-\begin{table}
-\caption{Summary of \ferengi{} artificial redshifting \label{tbl:ferengivalues}}
-\begin{tabular}{lccccr}
-\hline\hline
-$z_{\rm sim}$ & $N_{z {\rm bins}}$ & $N_{\rm evolution}$ & $e_{\rm max}$ & $N_{\rm galaxies}$ & $N_{\rm images}$\\
-\hline
-0.3              & 8                  & 7                   & $-3.0$        & 72             & 4032 \\
-0.5              & 6                  & 4                   & $-1.5$        & 72             & 1728 \\
-0.8              & 3                  & 3                   & $-1.0$        & 72             &  648 \\
-1.0              & 1                  & 3                   & $-1.0$        & 72             &  216 \\
-\hline\hline
-\end{tabular}
-\end{table}
-
-\begin{figure*}
-\center
-\includegraphics[width=160mm]{figures/example_ferengi.pdf}
-\caption{Examples of two galaxies which have been run through the \ferengi{}
-code to produce simulated \hst{} images. The measured value of \ffeatures{}
-from GZH for the images in each panel are (1) Top row: \ffeatures~= (0.900,
-0.625, 0.350, 0.350, 0.225) and (2) Bottom row: \ffeatures~= (1.000, 0.875,
-0.875, 0.625, 0.375). \label{fig:exampleFERENGI}}
-\end{figure*}
->>>>>>> master
 

### 2016-05-19 writeup/gz_hubble_data.tex
Streamline Section 6 intro. Closes #130.

@@
 
-The intended purpose of the GZH catalog is to provide a simple, yet flexible,
-means of identifying samples of galaxies with a desired morphological type.
-This section provides instructions for creating such samples using the vote
-fractions corresponding to the tasks shown in Figure~\ref{fig:decisiontree}. We
-stress that the selection process will vary based on the particular science
-case. More conservative cuts can be applied to create pure, but not necessarily
-complete, samples. These are useful for selecting galaxies exhibiting unique
-morphologies for individual case studies or observing proposals. Looser cuts
-can be applied to obtain samples with a higher level of completeness, which
-will increase the sample size but can potentially decrease purity. Population
-studies would make use of such large samples, in which statistical significance
-is a crucial factor in evaluating results. \citet{mas11c,mel14,che15}, and
-\citet{gal15} are examples of Galaxy~Zoo papers which select morphologies in this way.
-
-In GZH, participants answered questions about a galaxy's morphology in a decision
-tree format. With this structure, questions shown to a classifier were dependent on
-their answers to the previous questions (Section~\ref{ssec:interface}).
-Figure~\ref{fig:decisiontree} shows the possible paths available for answering
-the questions offered in GZH. The colors represent the tier level of Tasks,
-which indicate the number of previous Tasks the given Task is dependent upon.
-The arm-number question, Task~11, is a 5$^\mathrm{th}$-tier Task, meaning that
-whether this question is seen by a classifier was dependent on four Tasks preceding
-it. In this case, it as only shown to classifiers who identified the galaxy as
-featured/disk-shaped in Task~01, not clumpy in Task~12, not edge-on in Task~02,
-and having spiral structure in Task~10.
+The primary purpose of the GZH catalog is to provide a reliable method of
+selecting galaxies of a desired morphological type.  This section provides
+instructions for creating such samples using the vote fractions corresponding
+to the tasks shown in Figure~\ref{fig:decisiontree}. More conservative cuts can
+be applied to create pure, but not necessarily complete, samples. These are
+useful for selecting galaxies exhibiting unique morphologies for individual
+case studies.  Looser cuts can be applied to obtain samples with a higher level
+of completeness, (but with a potential decrease on the overall purity). We
+stress that the details of any selection process will vary based on the
+particular science case.
 

### 2016-05-19 writeup/gz_hubble_data.tex
General feedback from RJS. Addresses #126.

@@
 $r^\prime$-band surface brightnesses, and also spanned the redshift range of
-SDSS targets that maximize the coverage of parameter space.
+SDSS targets that maximize the coverage of parameter space
+(Figure~\ref{fig:sb_redshift}).
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.5\textwidth]{figures/eye_of_sauron.pdf}
+\caption{Surface brightness as a function of redshift for 3,950~\ferengi{}
+images and the 102,548~galaxies in the ACS sample with measured $\mu$ and $z$
+values. The color histogram shows the number of \ferengi{} images as a function
+of $\mu$ and $z_{\rm sim}$. White contours show counts for the full ACS sample,
+with contours starting at $N=1000$ and separated by intervals of 1000 up to
+7000.} 
+\label{fig:sb_redshift}
+\end{center}
+\end{figure}
 
@@
 \subsection{Effects of morphological debiasing}\label{ssec:zeta_results}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.5\textwidth]{figures/eye_of_sauron.pdf}
-\caption{Surface brightness as a function of redshift for 3,950~\ferengi{}
-images and the 102,548~galaxies in the ACS sample with measured $\mu$ and $z$
-values. The color histogram shows the number of \ferengi{} images as a function
-of $\mu$ and $z_{\rm sim}$. White contours show counts for the full ACS sample,
-with contours starting at $N=1000$ and separated by intervals of 1000 up to
-7000.} 
-\label{fig:sb_redshift}
-\end{center}
-\end{figure}
 
@@
 selecting galaxies of a desired morphological type.  This section provides
-instructions for creating such samples using the vote fractions corresponding
-to the tasks shown in Figure~\ref{fig:decisiontree}. More conservative cuts can
-be applied to create pure, but not necessarily complete, samples. These are
-useful for selecting galaxies exhibiting unique morphologies for individual
-case studies.  Looser cuts can be applied to obtain samples with a higher level
-of completeness, (but with a potential decrease on the overall purity). We
-stress that the details of any selection process will vary based on the
-particular science case.
+instructions for creating such pure samples using the vote fractions
+corresponding to the tasks shown in Figure~\ref{fig:decisiontree}
+\citep[eg,][]{mas11c,che15,gal15}. Increasing the levels of the thresholds can
+create purer, but not necessarily complete, morphologically-selected samples.
+These are useful for selecting galaxies of rare or unique types that merit
+individual study.  Looser cuts can be applied to obtain samples with a higher
+level of completeness, although the rate of false positives must be closely
+monitored.  We stress that the details of any selection process will vary based
+on the particular science case; for example, \citet{bam09,ski09,sme15} demonstrate
+the advantages of using the vote fractions directly as weights rather than
+applying discrete thresholds.
 

### 2016-05-19 python/classification_hist.py
figure 4 histogram plot updated for dashed lines and legend

@@ -1,7 +1,7 @@
 from astropy.io import fits
 from matplotlib import pyplot as plt
 
-data = fits.getdata('/Users/willettk/Astronomy/Research/GalaxyZoo/fits/gz_hst_table.fits',1)
+data = fits.getdata('/Users/becky/Downloads/gz_hst_table.fits',1)
 
 sample = data['sample']
 
@@ -10,14 +10,23 @@ cosmos = (sample == 'cosmos_initial') | (sample == 'cosmos_flagmissed')
 fake_agn = (sample == 'fake_agn_v1') | (sample == 'fake_agn_v1')
 stripe82 =  (sample == 'stripe82') | (sample == 'stripe82_coadd')
 
+samps = [original, cosmos, fake_agn, stripe82]
+labels = ['AEGIS,GEMS,GOODS', 'COSMOS', 'simulated AGN', 'SDSS Stripe 82']
+linetypes = ['dashdot', 'solid', 'dotted', 'dashed']
+
+
 fig,ax = plt.subplots(1,1,figsize=(8,8))
-ax.hist(data[original]['t01_smooth_or_features_total_count'],bins=range(170),histtype='step',lw=2,label='AEGIS,GEMS,GOODS')
-ax.hist(data[cosmos]['t01_smooth_or_features_total_count'],bins=range(170),histtype='step',lw=2,label='COSMOS')
-ax.hist(data[fake_agn]['t01_smooth_or_features_total_count'],bins=range(170),histtype='step',lw=2,label='simulated AGN')
-ax.hist(data[stripe82]['t01_smooth_or_features_total_count'],bins=range(170),histtype='step',lw=2,label='SDSS Stripe 82')
+for n in range(4):
+	ax.hist(data[samps[n]]['t01_smooth_or_features_total_count'],bins=range(170),histtype='step',lw=2, color='k', linestyle=linetypes[n])
+	ax.axhline((0.725+(0.2*(4-float(n))/4))*8000, 0.5, 0.55, linestyle=linetypes[n],color='k', lw=2)
+	ax.text(0.6, 0.725+(0.2*(4-n)/4), labels[n], transform=ax.transAxes, fontsize=16)
+# ax.hist(data[cosmos]['t01_smooth_or_features_total_count'],bins=range(170),histtype='step',lw=2,label='COSMOS')
+# ax.hist(data[fake_agn]['t01_smooth_or_features_total_count'],bins=range(170),histtype='step',lw=2,label='simulated AGN')
[…]

### 2016-05-19 writeup/gz_hubble_data.tex
Reference panel for high-z/low-mu. Closes #126.

@@
 \centering
-\subfigure{[a]\label{fig:6a}\includegraphics[width=0.5\textwidth]{figures/p_vs_p_SB_redshift.pdf}}
-\subfigure{[b]\label{fig:6b}\includegraphics[width=0.4\textwidth]{figures/z1_mu20_subplot1.pdf}}
+\subfigure{[a]\label{fig:bias_a}\includegraphics[width=0.5\textwidth]{figures/p_vs_p_SB_redshift.pdf}}
+\subfigure{[b]\label{fig:bias_b}\includegraphics[width=0.4\textwidth]{figures/z1_mu20_subplot1.pdf}}
 \\
-\subfigure{[c]\label{fig:6c}\includegraphics[width=0.5\textwidth]{figures/orangebars.pdf}}
-\subfigure{[d]\label{fig:6d}\includegraphics[width=0.4\textwidth]{figures/z1_mu20_subplot2.pdf}}
+\subfigure{[c]\label{fig:bias_c}\includegraphics[width=0.5\textwidth]{figures/orangebars.pdf}}
+\subfigure{[d]\label{fig:bias_d}\includegraphics[width=0.4\textwidth]{figures/z1_mu20_subplot2.pdf}}
 \caption{Effects of redshift bias in 3,950 images in the \ferengi{} sample.
@@
 high $z$ and low $\mu$, where features become nearly impossible to discern in
-the images.
+the images (see top right panel of Figure~\ref{fig:bias_a}).
 
@@
 residuals. These fits are shown as the dashed black lines in
-Figure~\ref{fig:6a}. Any flat regions of the polynomial fits are areas in which
+Figure~\ref{fig:bias_a}. Any flat regions of the polynomial fits are areas in which
 there is not a clear single-valued relationship between \ffeaturesz{} and
@@
 that the weighted \ffeatures{} is a lower limit to the true value.  These
-regions are highlighted in blue in Figure~\ref{fig:6a}. Uncolored (white)
+regions are highlighted in blue in Figure~\ref{fig:bias_a}. Uncolored (white)
 regions of the plot have sufficiently high slopes to consider the relationship
@@
 to have ``not enough information'' to determine the \ffeaturesz{} and
-\ffeaturesrest{} relationship, colored gray in Figure~\ref{fig:6a}.
-
-The unshaded regions in Figure~\ref{fig:6a} define discrete ranges of redshift,
+\ffeaturesrest{} relationship, colored gray in Figure~\ref{fig:bias_a}.
+
+The unshaded regions in Figure~\ref{fig:bias_a} define discrete ranges of redshift,
 surface brightness, and \ffeatures{} a galaxy must have in order for the
@@
 cannot be confidently assigned, the \emph{range} of debiased values is
-estimated using a method visualized in Figure~\ref{fig:6c}. This uses the
+estimated using a method visualized in Figure~\ref{fig:bias_c}. This uses the
 \ferengi{} simulated data to analyze the range of intrinsic \ffeaturesrest{}
@@
 The range of intrinsic values is defined as the inner 80\% of the data,
-represented by the orange bars in Figure~\ref{fig:6c}. For any galaxy which
+represented by the orange bars in Figure~\ref{fig:bias_c}. For any galaxy which
 cannot be directly debiased by the $\zeta$ method, these ranges are used to

### 2016-05-19 writeup/gz_hubble_data.tex
Small fixes to text; closes #89.

@@
 $L_\mathrm{ratio} \equiv L_\mathrm{galaxy}/L_\mathrm{AGN}$ is in
-$(0.2,1.0,2.0,5.0,10.0,50.0)$. Combining these parameters generated 15~images
+$(0.2,1.0,5.0,10.0,50.0)$. Combining these parameters generated 15~images
 with different simulated AGN for each host, in addition to the original galaxy
@@
 classifications derived from any method. To facilitate corrections due to
-redshift, we include a sample of 288 galaxies with at redshifts such that
-available SDSS imaging can be transformed to simulate \hst{} imaging out to $z
-= 1$. The selection spanned a variety of galaxy morphologies (as selected by
-GZ2 classifications) and $r^\prime$-band surface brightnesses, and also spanned
-the redshift range of SDSS targets (in $N_z = 4$ bins) in order to optimize for
-different target minimum redshifts in \hst{} imaging. We redshifted the
-galaxies and produced simulated \hst{} imaging using the \ferengi{} code
-\citep{bar08a}.
+redshift, we include a sample of 288 galaxies with SDSS imaging that can be
+transformed to simulate \hst{} imaging out to $z = 1$. The selection spanned a
+variety of galaxy morphologies (as selected by GZ2 classifications) and
+$r^\prime$-band surface brightnesses, and also spanned the redshift range of
+SDSS targets (in $N_z = 4$ bins) in order to optimize for different target
+minimum redshifts in \hst{} imaging. We redshifted the galaxies and produced
+simulated \hst{} imaging using the \ferengi{} code \citep{bar08a}.
 

### 2016-05-19 writeup/gz_hubble_data.tex
Better use and definition of 'bias'. Closes #71.

@@
 
-To facilitate correction of classifications in the presence of known biasing
-effects, GZH includes two different samples of simulated \hst{} images: real
-\hst{} galaxy images (Section \ref{ssec:legacy_surveys}) with nuclear emission
-added to simulate AGN host galaxies, and lower-redshift galaxy images from SDSS
-(Section \ref{ssec:sdss}), artificially redshifted from $0.3 \leq z \leq 1$.
-Each is described separately below.
+To facilitate correction of classifications in the presence of known redshift
+bias (Section~\ref{sec:debiasing}), GZH includes two different samples of
+simulated \hst{} images: real \hst{} galaxy images (Section
+\ref{ssec:legacy_surveys}) with nuclear emission added to simulate AGN host
+galaxies, and lower-redshift galaxy images from SDSS (Section \ref{ssec:sdss}),
+artificially redshifted from $0.3 \leq z \leq 1$.  Each is described separately
+below.
 
@@
 manner and evenly distributed with unaltered images of the galaxies.
-Classifiers were not explicitly told that the images had been altered during
+Volunteers were not explicitly told that the images had been altered during
 classification, as the goal was to measure the effect on normal classifications
-in as unbiased a manner as possible. Following classification, a classifier
-could view a page with additional details about each galaxy they had
-classified; where applicable these pages contained further information
-regarding image modifications. \citet{sim14} uses similarly-processed
-images for reliable identification of bulgeless galaxies using SDSS data.
+usng the same technique as closely as possible. Following classification, a
+classifier could view a page with additional details about each galaxy; where
+applicable, these pages contained further information regarding image
+modifications. \citet{sim14} uses similarly-processed images for reliable
+identification of bulgeless galaxies using SDSS data.
 
@@
 images produced for GZH. The use of these images to correct for redshift-dependent
-classification bias is described in Section \ref{sec:debiasing}.
+bias is described in Section \ref{sec:debiasing}.
 
@@
 Redshifts for the GZH catalog were compiled from a variety of sources. For each
-galaxy, the primary redshift used for debiasing calculations
-(Section~\ref{sec:debiasing}) is in the $\tt Z\_BEST$ column of
+galaxy, the primary redshift is in the $\tt Z\_BEST$ column of
 Table~\ref{tbl:catalog_hst}. The redshift type (spectroscopic: $\tt SPEC\_Z$,
@@
 was assumed that there was no cosmological evolution of the morphologies of
-galaxies and therefore any observed changes in the distribution of galaxies
-with different consensus morphologies was due to the effects of redshift on the
-image quality (\ie, the reduction in physical resolution, surface brightness
-dimming, etc). For both previous releases of Galaxy~Zoo morphologies, a correction for
+galaxies and therefore any observed changes in the morphological distribution
+were due to a redshift-dependent bias that affects image quality and
+classification accuracy (ie, galaxies of a given mass/size will appear smaller
+and dimmer at higher redshifts).  This bias is not unique to the crowdsourcing
+technique; its dependence in data quality is a potential problem for
+\emph{both} automated and visual classifications, and must be addressed in
+order to accurately measure demographics over any significant redshift range.
+
+For both previous releases of Galaxy~Zoo morphologies, a correction for
 redshift-dependent bias was applied based on matching the classification
@@
 evolution of the types and morphologies of galaxies is expected for galaxies in
-the sample. As a result, the previous methods of correcting for redshift
-dependent bias do not work. In addition, the effects of band shifting will
-change the images even more across these redshift ranges. 
+the sample. As a result, the previous methods of correcting for
+redshift-dependent bias do not work. In addition, the effects of band shifting
+will change the images even more across these redshift ranges. 
 %Figure~\ref{fig:exampleFERENGI} illustrates some of the possible effects of
@@
 \citep{yor00,str02} and are processed to match the observational properties of
-the \hst{} surveys out to $z=1$. These
-images were classified in the GZH interface using the same classification
-scheme as the original \hst{} images. Further details on the creation of these images
-is given in Section \ref{ssec:ferengi}.
+the \hst{} surveys out to $z=1$. These images were classified in the GZH
+interface using the same classification scheme as the original \hst{} images.
+Further details on the creation of these images is given in Section
+\ref{ssec:ferengi}.
 
@@
 and its relative orientation. There may also be other parameters that affect
-classifier accuracy, such as the proximity of close companions or bias as a
-function of individual classifier ability and skill. The combination of all
+classifier accuracy, such as the proximity of close companions or 
+individual classifier ability and skill. The combination of all
 such parameters forms a high-dimensional space, and it is not clear how to
@@
 
-The change in bias as a function of $\mu_r$ and \zsim{} is measured using the
+This dependence of the vote fraction on $\mu_r$ and \zsim{} is measured using the
 \ferengi{} images over all the evolutionary correction factors. It is assumed
@@
 \ffeaturesz{} value, what its \ffeatures{} value \emph{would have been} if it
-had been viewed at $z=0.3$. This predicted value is defined as the debiased
+had been viewed at $z=0.3$. This predicted value is defined as the ``debiased''
 vote fraction \ffeaturesdebiased, and is calculated by applying a correction to
@@
 Few galaxies in the sample have sufficiently high corrections to completely
-change them from being confidently smooth to featured following the bias
-correction (Figure~\ref{fig:debiased_corrections}). As a check, highly boosted
-galaxies are compared to the expert classifications in CANDELS \citep{kar15}.
-There are only eight galaxies that were strongly boosted (\ffeatures$<0.2$ and
-\fbest$>0.5$) in GZH and also appears in the CANDELS expert sample. Of those
-eight galaxies, \citet{kar15} classify 5 as spheroids, 2 as disks, and 1 as
-irregular/disky. The \fbest{} values for GZH are all between 0.5 and 0.6,
-making them intermediate disk candidates. One of the spheroids has a hint of
-extended emission to the south that may have been missed by the CANDELS
-experts, but almost all images are dim and with very low surface brightnesses
-in the ACS imaging, making positive identification challenging. Since the
-surveys use different rest-frame filters and the overlap sample is tiny,
-though, detailed comparisons between the overall morphologies are highly
-difficult.
+change them from being confidently ``smooth'' to ``featured'' following the
+correction for redshift bias (Figure~\ref{fig:debiased_corrections}). As a
+check, highly boosted galaxies are compared to the expert classifications in
+CANDELS \citep{kar15}.  There are only eight galaxies that were strongly
+boosted (\ffeatures$<0.2$ and \fbest$>0.5$) in GZH and also appears in the
+CANDELS expert sample. Of those eight galaxies, \citet{kar15} classify 5 as
+spheroids, 2 as disks, and 1 as irregular/disky. The \fbest{} values for GZH
+are all between 0.5 and 0.6, making them intermediate disk candidates. One of
+the spheroids has a hint of extended emission to the south that may have been
+missed by the CANDELS experts, but almost all images are dim and with very low
+surface brightnesses in the ACS imaging, making positive identification
+challenging. Since the surveys use different rest-frame filters and the overlap
+sample is tiny, though, detailed comparisons between the overall morphologies
+are highly difficult.
 
@@
 
-The GZH catalog is corrected for classification bias only for the first
+The GZH catalog is corrected for redshift bias only for the first
 question of the GZH decision tree (Section~\ref{sec:debiasing}), which asks
@@
 et~al., submitted). Since both the sensitivity and filters for the two sets of
-images differ (and there is no debiased correction applied to GZC), there is no
+images differ (and there is no correction for redshift bias applied to GZC), there is no
 prior reason to expect a perfect correlation between the separate vote

### 2016-05-19 writeup/gz_hubble_data.tex
splitting figure 9 into 2 figures

--- 2016-05-19 writeup/gz_hubble_data.tex
@@
 \centering
-\subfigure{[a]\label{fig:bias_a}\includegraphics[width=0.5\textwidth]{figures/p_vs_p_SB_redshift.pdf}}
-\subfigure{[b]\label{fig:bias_b}\includegraphics[width=0.4\textwidth]{figures/z1_mu20_subplot1.pdf}}
-\\
-\subfigure{[c]\label{fig:bias_c}\includegraphics[width=0.5\textwidth]{figures/orangebars.pdf}}
-\subfigure{[d]\label{fig:bias_d}\includegraphics[width=0.4\textwidth]{figures/z1_mu20_subplot2.pdf}}
+\includegraphics[width=\textwidth]{figures/p_vs_p_sb_redshift.pdf}
 \caption{Effects of redshift bias in 3,950 images in the \ferengi{} sample.
-[a]: Each point in a given redshift and surface brightness bin represents a
+Each point in a given redshift and surface brightness bin represents a
 unique galaxy. On the $y$-axis in each bin is the \ffeatures{} value of the
@@
 those in which there is not are blue, and those with not enough data ($N<5$)
-are gray. [b]: A larger version of the dark-outlined square in [a], containing
-\ferengi{} galaxies that have been artificially redshifted to $z=1.0$ and have
-surface brightnesses between $20.3 < \mu < 21.0$ $\rm (mag/arcsec^2)$. [c]: The
-same data as [a] is shown. Each $z,\mu$ bin is divided into 4 sub-bins to
-determine the range of intrinsic \ffeaturesrest{} for a given range of observed
-\ffeaturesz{} values. In each sub-bin, the orange bars represent the inner
-80$^\mathrm{th}$ percentiles of the data, the boundaries of which are the lower
-and upper limits of the debiased values. [d]: The same data as [b], but
-highlighting the upper and lower limit regions.}
+are gray. A larger version of the bin outlined at $z=1.0$ and $20.3 < \mu < 21.0$ $\rm (mag/arcsec^2)$ is shown in Figure~\ref{fig:f_vs_f_zoom}.}
 \label{fig:f_vs_f}
 \end{figure*}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{figures/z1_mu20_subplot2.pdf}
+\caption{A larger version of the dark-outlined square in Figure~\ref{fig:f_vs_f}, containing
+\ferengi{} galaxies that have been artificially redshifted to $z=1.0$ and have
+surface brightnesses between $20.3 < \mu < 21.0$ $\rm (mag/arcsec^2)$. The orange bars represent the inner
+80$^\mathrm{th}$ percentiles of the data, the boundaries of which are the lower
+and upper limits of the debiased values.}
+\label{fig:f_vs_f_zoom}
+\end{figure}
 
@@
 high $z$ and low $\mu$, where features become nearly impossible to discern in
-the images (see top right panel of Figure~\ref{fig:bias_a}).
+the images (see top right panel of Figure~\ref{fig:f_vs_f}).
 
@@
 residuals. These fits are shown as the dashed black lines in
-Figure~\ref{fig:bias_a}. Any flat regions of the polynomial fits are areas in which
+Figure~\ref{fig:f_vs_f}. Any flat regions of the polynomial fits are areas in which
 there is not a clear single-valued relationship between \ffeaturesz{} and
@@
 that the weighted \ffeatures{} is a lower limit to the true value.  These
-regions are highlighted in blue in Figure~\ref{fig:bias_a}. Uncolored (white)
+regions are highlighted in blue in Figure~\ref{fig:f_vs_f}. Uncolored (white)
 regions of the plot have sufficiently high slopes to consider the relationship
@@
 to have ``not enough information'' to determine the \ffeaturesz{} and
-\ffeaturesrest{} relationship, colored gray in Figure~\ref{fig:bias_a}.
-
-The unshaded regions in Figure~\ref{fig:bias_a} define discrete ranges of redshift,
+\ffeaturesrest{} relationship, colored gray in Figure~\ref{fig:f_vs_f}.
+
+The unshaded regions in Figure~\ref{fig:f_vs_f} define discrete ranges of redshift,
 surface brightness, and \ffeatures{} a galaxy must have in order for the
@@
 cannot be confidently assigned, the \emph{range} of debiased values is
-estimated using a method visualized in Figure~\ref{fig:bias_c}. This uses the
+estimated using a method visualized in Figure~\ref{fig:f_vs_f_zoom}. This uses the
 \ferengi{} simulated data to analyze the range of intrinsic \ffeaturesrest{}
 values for any given observed \ffeatures{} value, again as a function of
-surface brightness and redshift. Each $z$,$\mu$ bin, shows the spread of
-intrinsic values of \ffeaturesrest{} for four ranges of observed \ffeatures.
+surface brightness and redshift. In each unclassifiable (shaded blue) $z$,$\mu$ bin, the spread of
+intrinsic values of \ffeaturesrest{} for four ranges of observed \ffeatures is computed.
 The range of intrinsic values is defined as the inner 80\% of the data,
-represented by the orange bars in Figure~\ref{fig:bias_c}. For any galaxy which
+represented by the orange bars in Figure~\ref{fig:f_vs_f_zoom}. For any galaxy which
 cannot be directly debiased by the $\zeta$ method, these ranges are used to
@@
 \centering
-\subfigure{[a]\label{a}\includegraphics[width=0.5\textwidth]{figures/p_vs_p_SB_redshift_bar.pdf}}
-\subfigure{[b]\label{b}\includegraphics[width=0.4\textwidth]{figures/z1_mu20_subplot1_bar.pdf}}
-\\
-\subfigure{[c]\label{c}\includegraphics[width=0.5\textwidth]{figures/orangebars_bar.pdf}}
-\subfigure{[d]\label{d}\includegraphics[width=0.4\textwidth]{figures/z1_mu20_subplot2_bar.pdf}}
+\includegraphics[width=\textwidth]{figures/p_vs_p_SB_redshift_bar.pdf}
 \caption{Similar to Figure~\ref{fig:f_vs_f}, showing effects of redshift bias
-for 3,950~images in the \ferengi{} sample. [a]: Each point in a given redshift
+for 3,950~images in the \ferengi{} sample. Each point in a given redshift
 and surface brightness bin represents a unique galaxy. The $y$-axis in each
@@
 redshift and at $z=0.3$ are marked in white; those in which there is not
-are blue, and those with not enough data ($N<5$) are gray. The mean
+are blue, and those with not enough data ($N<5$) are gray.
+A larger version of the bin outlined at $z=1.0$ and $20.3 < \mu < 21.0$ $\rm (mag/arcsec^2)$ is shown in Figure~\ref{fig:f_vs_fbar_zoom}.
+The mean
 normalized $\chi^2$ of the change in vote fraction is 0.08. None of the
 correlations for higher-order tasks (including bars) were applied to
-galaxies in the GZH catalog. [b]: A larger version of the dark-outlined
-square in [a], containing \ferengi{} galaxies artificially redshifted to
-$z=1.0$ and have surface brightnesses between $20.3 < \mu < 21.0$ $\rm
-(mag/arcsec^2)$. [c]: The same data as [a]. Each $z,\mu$ bin is divided
-into 4~sub-bins to determine the range of intrinsic \ffeaturesrest{} for a
-given range of observed \ffeaturesz{} values. In each sub-bin, the orange
-bars represent the inner 80$^\mathrm{th}$ percentiles of the data, the
-boundaries of which are the lower and upper limits of the debiased values.
-[d]: The same data as [b], but highlighting the upper and lower limit
-regions.}
+galaxies in the GZH catalog.}
 \label{fig:f_vs_fbar}
 \end{figure*}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{figures/z1_mu20_subplot2_bar.pdf}
+\caption{A larger version of the dark-outlined square in Figure~\ref{fig:f_vs_fbar}, containing
+\ferengi{} galaxies that have been artificially redshifted to $z=1.0$ and have
+surface brightnesses between $20.3 < \mu < 21.0$ $\rm (mag/arcsec^2)$. The orange bars represent the inner
+80$^\mathrm{th}$ percentiles of the data, the boundaries of which are the lower
+and upper limits of the debiased values.}
+\label{fig:f_vs_fbar_zoom}
+\end{figure}
 

### 2016-05-20 writeup/gz_hubble_data.tex
splitting figure 9 into 2, SB not sb filenames

@@
 \centering
-\includegraphics[width=\textwidth]{figures/p_vs_p_sb_redshift.pdf}
+\includegraphics[width=\textwidth]{figures/p_vs_p_SB_redshift.pdf}
 \caption{Effects of redshift bias in 3,950 images in the \ferengi{} sample.

### 2016-05-20 writeup/gz_hubble_data.tex
Sort individual FERENGI curves by f_z=0.3 and add more

@@
 \center
-\includegraphics[width=\textwidth]{figures/zeta_examples.pdf}
+\includegraphics[width=\textwidth]{figures/zeta_examples_sorted.pdf}
 \caption{Behavior of the normalized, weighted vote fractions of features
@@
 a distribution with $e=0$ and at least three detectable images in redshift bins
-of $z\ge0.3$. Measured vote fractions (red points) are fit with an exponential
-function (Equation~\ref{eqn:fzeta}); the best-fit parameters are given above
-each plot. Error bars are Poissonian, assuming a median of 40~votes per
-galaxy.}
+of $z\ge0.3$, and are sorted by \ffeaturesrest. Measured vote fractions (blue
+solid line) are fit with an exponential function (red dashed line;
+Equation~\ref{eqn:fzeta}); the best-fit parameter for $\zeta$ is given above
+each plot.}
+% Error bars are binomial for each f, symmetrised, then added in quadrature.
 \label{fig:zeta_examples}

### 2016-05-20 writeup/gz_hubble_data.tex
Feedback from Boris, espec. on Figure 12

@@
 \fbest{} are dominated by early-types, although spiral and irregular galaxies
-have comparable sizes as low as \fbest$\sim0.2$. In GEMS galaxies, the impact
-of irregular or peculiar galaxies is not measured; splitting on $n=2.5$ gives
-an essentially flat proportion of ellipticals to spirals at \fbest$>0.3$.
-Visual inspection of images of galaxies where both \fbest{} and $n$ are high
-show that the majority are obvious spirals but with prominent bulges,
-indicating that the single-component \sersic{} fit is likely choosing too small
-of an effective radius and missing the extended disk structure for a large
-population of galaxies.
+have comparable sizes as low as \fbest$\sim0.2$.
+
+In GEMS galaxies, the impact of irregular or peculiar galaxies is not measured;
+splitting on $n=2.5$ gives an essentially flat proportion of ellipticals to
+spirals at \fbest$>0.3$.  Visual inspection of images of galaxies where both
+\fbest{} and $n$ are high show that the majority are obvious spirals but with
+prominent bulges, indicating that the single-component \sersic{} fit is likely
+choosing too small of an effective radius and missing the extended disk
+structure for a large population of galaxies. This is a known issue with using
+$n$ as a standalone measure of galaxy morphology -- it is relatively common,
+for example, to measure high $n$ for an object with an exponential disk but a
+central cusp in the light profile (eg, due to an AGN, cluster, foreground
+star, noise, etc).
 

### 2016-05-20 python/comparisons.py

@@ -852,8 +852,8 @@ def frac_all(zint=0.0,zlow=0.0):
             for morph,color,label,ls in zip((early,spiral,irr),colors,mlabels,('-','--','-.')):
 
                 if morph.sum() > 0:
-                    h,edges = np.histogram(data[morph][frac],bins=bnum)
-                    h2,edges2 = np.histogram(data[np.any([early,spiral,irr],axis=0)][frac],bins=bnum)
+                    h,edges = np.histogram(data[morph][frac],bins=bnum,range=(0,1))
+                    h2,edges2 = np.histogram(data[np.any([early,spiral,irr],axis=0)][frac],bins=bnum,range=(0,1))
 
                     e_frac = h * 1./h2
                     e_frac_err = cameron_err(0.90,h,h2)
@@ -878,6 +878,7 @@ def frac_all(zint=0.0,zlow=0.0):
             ax1.legend(loc='upper left',fontsize=12)
 
     fig.tight_layout()
+
     if zint > 0.:
         plt.savefig("{0}/comparisons/all_z{1:.1f}.png".format(gzh_path,zlow),dpi=100)
     else:

### 2016-05-20 writeup/gz_hubble_data.tex
Remove lenses and dust lanes from odd comparison. Closes #77.

@@
 disk-dominated galaxies, details on spiral disk structure that relate to the
-Hubble type, bar identification, and numerous measuremenst of clump
+Hubble type, bar identification, and numerous measurements of clump
 identification and geometry.  This paper also describes a new method for
@@
 method of calculating the Petrosian radius and total light profile. They employ
-a nearest-neighbors method is used to assign morphological categories for the
+a nearest-neighbors method to assign morphological categories for the
 entire sample based on a small training set. \citet[][ZEST]{sca07} used $C$,
@@
 \fbest. The corresponding second and fourth columns show data for the same
-galaxies as a function of \fodd. Confidence intervals for each binned fraction
-in the bin are calculated for a binomial population \citep{cam11}.}
+galaxies as a function of \fodd. The ``odd'' samples exclude galaxies dominated
+by lenses or dust lanes ($<1\%$ of the total), which are GZH categories not
+expected to correlate to larger-scale structural parameters. Confidence
+intervals for each binned fraction in the bin are calculated for a binomial
+population \citep{cam11}.}
 \label{fig:comparisons}

### 2016-05-20 python/comparisons.py

@@ -24,6 +24,8 @@ pstar = 't01_smooth_or_features_a03_star_or_artifact_weighted_fraction'
 pspiral = 't04_spiral_a01_spiral_weighted_fraction'
 pirr = 't08_odd_feature_a04_irregular_fraction'
 pmerger = 't08_odd_feature_a06_merger_fraction'
+pdustlane = 't08_odd_feature_a07_dust_lane_fraction'
+plens = 't08_odd_feature_a02_lens_or_arc_fraction'
 
 # Colors
 blue = '#377EB8'
@@ -851,9 +853,17 @@ def frac_all(zint=0.0,zlow=0.0):
         for ax,frac in zip((ax1,ax2),(pfeat,podd)):
             for morph,color,label,ls in zip((early,spiral,irr),colors,mlabels,('-','--','-.')):
 
+                # Don't look at p_odd for galaxies dominated by dust lanes or lenses
+                if frac == podd:
+                    odd_ind = np.logical_not((data[podd] >= 0.5) & (data[pdustlane] + data[plens] > 0.5))
+                    if ls == '-':
+                        print d['survey'],d['citation'],len(data),odd_ind.sum(),len(data)-odd_ind.sum(),(len(data)-odd_ind.sum()) * 100./len(data)
+                else:
+                    odd_ind = np.ones(len(data),dtype=bool)
+
                 if morph.sum() > 0:
-                    h,edges = np.histogram(data[morph][frac],bins=bnum,range=(0,1))
-                    h2,edges2 = np.histogram(data[np.any([early,spiral,irr],axis=0)][frac],bins=bnum,range=(0,1))
+                    h,edges = np.histogram(data[morph & odd_ind][frac],bins=bnum,range=(0,1))
+                    h2,edges2 = np.histogram(data[np.any([early,spiral,irr],axis=0) & odd_ind][frac],bins=bnum,range=(0,1))
 
                     e_frac = h * 1./h2
                     e_frac_err = cameron_err(0.90,h,h2)
@@ -879,6 +889,9 @@ def frac_all(zint=0.0,zlow=0.0):
 
     fig.tight_layout()
 
+    '''
+    plt.show()
+    '''
     if zint > 0.:
         plt.savefig("{0}/comparisons/all_z{1:.1f}.png".format(gzh_path,zlow),dpi=100)
     else:

### 2016-05-20 writeup/gz_hubble_data.tex
edits to text in response to comments in issue 140

--- 2016-05-20 writeup/gz_hubble_data.tex
@@
 only two parameters intended to capture the bulk of the change in bias: the
-$r^\prime$-band surface brightness ($\mu_r$; intrinsic) and redshift ($z$;
+$i$-band surface brightness ($\mu_i$; intrinsic) and redshift ($z$;
 extrinsic).
 
-This dependence of the vote fraction on $\mu_r$ and \zsim{} is measured using the
+This dependence of the vote fraction on $\mu_i$ and \zsim{} is measured using the
 \ferengi{} images over all the evolutionary correction factors. It is assumed
@@
 parameter that controls the rate at which $f$ decreases with increasing
-redshift. This formula fits the data relatively well (with very few exceptions,
-the vote fractions for featured galaxies decrease monotonically with increasing
-redshift), and the exponential function bounds the observed vote fractions
-between $f_{\mu,z=0.3}$ and zero. Figure~\ref{fig:zeta_examples} shows the
+redshift. The exponential function bounds the observed vote fractions
+between $f_{\mu,z=0.3}$ and zero based on two assumptions: 1) the vote fractions for featured galaxies decrease monotonically with increasing redshift, therefore restricting vote fractions for a given galaxy to be less than $f_{\mu,z=0.3}$  (which is true of the data with very few exceptions), and 2) the vote fractions cannot be less than zero (which is always true).
+Figure~\ref{fig:zeta_examples} shows the
 change in vote fraction and the fit to Equation~\ref{eqn:fzeta} for a random
@@
 a function of surface brightness. The best-fit parameters to the linear fit
-(from least-squares optimization) are $\zeta_0=0.1$, $\zeta_1=1.4$. To make the
+(from least-squares optimization) are $\zeta_0=0.75$, $\zeta_1=-.04$. To make the
 final debiased correction, the simple exponential form of
@@
 to have ``not enough information'' to determine the \ffeaturesz{} and
-\ffeaturesrest{} relationship, colored gray in Figure~\ref{fig:f_vs_f}.
+\ffeaturesrest{} relationship, colored gray in Figure~\ref{fig:f_vs_f}. These galaxies are hereafter referred to as the ``NEI'' sample.
 

### 2016-05-20 writeup/gz_hubble_data.tex
Comment on weighting for anonymous users. Closes #81.
added reference to toms thesis

@@
 redshift bias rests on the assumption that the \emph{degree} of bias is a
-function of the apparent size and brightness of the image as seen on screen.
+function of the apparent size and brightness of the galaxy.
 This is controlled by two types of parameters: \textbf{intrinsic} properties of
@@
 used (see Table \ref{tbl:ferengivalues}), and only those which had detectable
-surface brightness measurements in \sextractor; this includes 3,950 of the
+surface brightness measurements in \sextractor~\citep{mel16}; this includes 3,950 of the
 total 6,466 images. For each simulated redshift value \zsim{} at a fixed

### 2016-05-23 writeup/gz_hubble_data.tex

--- 2016-05-20 writeup/gz_hubble_data.tex
@@
 redshift, we include a sample of 288 galaxies with SDSS imaging that can be
-transformed to simulate \hst{} imaging out to $z = 1$. The selection spanned a
-variety of galaxy morphologies (as selected by GZ2 classifications) and
-$r^\prime$-band surface brightnesses, and also spanned the redshift range of
-SDSS targets (in $N_z = 4$ bins) in order to optimize for different target
-minimum redshifts in \hst{} imaging. We redshifted the galaxies and produced
-simulated \hst{} imaging using the \ferengi{} code \citep{bar08a}.
+transformed to simulate \hst{} imaging out to $z = 1$. 
+The SDSS images were redshifted and processed to mimic simulated \hst{} imaging 
+parameters using the \ferengi{} code \citep{bar08a}.
 
@@
 %summarized in Table \ref{tbl:morphologies}.
-The surface brightness selection ($N_\mu = 3$) for the \ferengi{} galaxies was
-(1) low: $\mu > 21.5$~\magarc;  (2) mid: $20.5 < \mu < 21.5$~\magarc; and (3)
-high: $\mu < 20.5$~\magarc. For each of the four ``target redshifts''
-($z_\mathrm{sim} = 0.3, 0.5, 0.8$ and $1.0$), the images were redshifted in
-$\Delta z = 0.1$ bins up to $z_\mathrm{sim}=1.0$.
 
@@
 $e$ is the evolutionary correction in magnitudes (i.e., $e=-1$ essentially
-brightens the galaxy by 1~magnitude by $z=1$). \ferengi{} was run on the images
+brightens the entire galaxy by 1~magnitude by $z=1$). \ferengi{} was run on the images
 for values of $e$ starting from $e=0$ and decreasing to $e=-3.5$ in increments
@@
 better angular resolution than the original SDSS data), as well as the number
-of $e$ values selected. Table~\ref{tbl:ferengivalues} summarizes the redshifted
-images produced for GZH. The use of these images to correct for redshift-dependent
+of $e$ values selected. The use of these images to correct for redshift-dependent
 bias is described in Section \ref{sec:debiasing}.
 
-\begin{table}
-\caption{Summary of \ferengi{} artificial redshifting \label{tbl:ferengivalues}}
-\begin{tabular}{lccccr}
-\hline\hline
-$z_{\rm sim}$ & $N_{z {\rm bins}}$ & $N_{\rm evolution}$ & $e_{\rm max}$ & $N_{\rm galaxies}$ & $N_{\rm images}$\\
-\hline
-0.3              & 8                  & 7                   & $-3.0$        & 72             & 4032 \\
-0.5              & 6                  & 4                   & $-1.5$        & 72             & 1728 \\
-0.8              & 3                  & 3                   & $-1.0$        & 72             &  648 \\
-1.0              & 1                  & 3                   & $-1.0$        & 72             &  216 \\
-\hline\hline
-\end{tabular}
-\end{table}
+%\begin{table}
+%\caption{Summary of \ferengi{} artificial redshifting \label{tbl:ferengivalues}}
+%\begin{tabular}{lccccr}
+%\hline\hline
+%$z_{\rm sim}$ & $N_{z {\rm bins}}$ & $N_{\rm evolution}$ & $e_{\rm max}$ & $N_{\rm galaxies}$ & $N_{\rm images}$\\
+%\hline
+%0.3              & 8                  & 7                   & $-3.0$        & 72             & 4032 \\
+%0.5              & 6                  & 4                   & $-1.5$        & 72             & 1728 \\
+%0.8              & 3                  & 3                   & $-1.0$        & 72             &  648 \\
+%1.0              & 1                  & 3                   & $-1.0$        & 72             &  216 \\
+%\hline\hline
+%\end{tabular}
+%\end{table}
 
@@
 participation). Classifications by participants who were not logged in were marked as
-``Anonymous'' and assumed to have $w = 1$. 
+``Anonymous'' and receive the same $w=1$ weighting as the vast majority
+of logged-in classifiers.
 % We should also try to estimate how many anonymous classifiers there were, if possible. 
+% Not clear that I can do that given the SQL data
 
@@
 \citep{lin11,wil13} were based on observations of galaxies in the Sloan Digital
-Sky Survey (SDSS) which have a median redshift of $z<0.2$. In these cases, it
+Sky Survey (SDSS), which have a median redshift of $z<0.2$. In these cases, it
 was assumed that there was no cosmological evolution of the morphologies of
@@
 were due to a redshift-dependent bias that affects image quality and
-classification accuracy (ie, galaxies of a given mass/size will appear smaller
+classification accuracy (\ie, galaxies of a given mass/size will appear smaller
 and dimmer at higher redshifts).  This bias is not unique to the crowdsourcing
@@
 
-In the GZH samples, the redshift range is large enough that cosmological
-evolution of the types and morphologies of galaxies is expected for galaxies in
-the sample. As a result, the previous methods of correcting for
+In GZH, the redshift range is large enough that cosmological
+evolution of the types and morphologies of galaxies is expected for the \hst{}
+sample. As a result, the previous methods of correcting for
 redshift-dependent bias do not work. In addition, the effects of band shifting
 will change the images even more across these redshift ranges.
-%Figure~\ref{fig:exampleFERENGI} illustrates some of the possible effects of
-%losing features in spiral galaxies at high redshift.
 
 In order to test and correct for the effects of redshift, GZH includes a set of
-calibration images. These images consist of the same galaxy as it would appear
-over a variety of redshifts. The input images are from the SDSS
-\citep{yor00,str02} and are processed to match the observational properties of
-the \hst{} surveys out to $z=1$. These images were classified in the GZH
-interface using the same classification scheme as the original \hst{} images.
-Further details on the creation of these images is given in Section
-\ref{ssec:ferengi}.
-
-The GZH classifications include 288 unique galaxies originally generated from
-SDSS imaging and processed with the \ferengi{} code. The selection spanned a
-variety of galaxy morphologies (as selected by GZ2 classifications) and
-$r^\prime$-band surface brightnesses, and also spanned the redshift range of
-SDSS targets that maximize the coverage of parameter space
-(Figure~\ref{fig:sb_redshift}).
+calibration images.  These are simulated images of a set of nearby galaxies as
+they would appear observed at a variety of redshifts.  The input images are
+from the SDSS \citep{yor00,str02}.  The sample consists of 288~nearby galaxies
+at $z<0.013$. The galaxies spanned a variety of morphologies (as selected by
+GZ2 classifications, including identifications of spiral structure,
+ellipticals, mergers, edge-on disks, bulge prominence/shape, and bars) and
+$r^\prime$-band surface brightnesses.  The overall selection spanned the
+redshift range of SDSS targets and maximized the number of \hst{} galaxies at
+the same surface brightness and redshift (Figure~\ref{fig:sb_redshift}).  The
+\ferengi{} code was used to produce sets of images corresponding to
+observations of these galaxies out to $z_\mathrm{sim}=1.0$ (see
+Section~\ref{ssec:ferengi}).  The resulting images were classified in the GZH
+interface using the standard classification scheme.
 
@@
 \textbf{extrinsic} properties, such as the distance (redshift) of the galaxy
-and its relative orientation. There may also be other parameters that affect
-classifier accuracy, such as the proximity of close companions or 
-individual classifier ability and skill. The combination of all
+and its relative orientation. The combination of all
 such parameters forms a high-dimensional space, and it is not clear how to
 separate this into individual effects. Instead, the method used here employs
-only two parameters intended to capture the bulk of the change in bias: the
+only two parameters as a simple model of the effect of redshift brightness on classification: the
 $r^\prime$-band surface brightness ($\mu_r$; intrinsic) and redshift ($z$;
@@
 
-This dependence of the vote fraction on $\mu_r$ and \zsim{} is measured using the
-\ferengi{} images over all the evolutionary correction factors. It is assumed
-that the ``true'' (ie, debiased) vote fraction $f_{\mu,z}$ for an
-artificially-redshifted galaxy can be expressed as:
+%This dependence of the vote fraction on $\mu_r$ and \zsim{} is measured using the \ferengi{} images over all the evolutionary correction factors. 
+We model the debiased vote fraction $f_{\mu,z}$ for an
+artificially-redshifted galaxy as:
 
@@
 
-\noindent where $f_{\mu,z=0.3}$ is the ``calibrated'' vote fraction at the
-lowest redshift in the \ferengi{} bins ($z=0.3$) and $\zeta$ is a positive
-parameter that controls the rate at which $f$ decreases with increasing
-redshift. This formula fits the data relatively well (with very few exceptions,
-the vote fractions for featured galaxies decrease monotonically with increasing
-redshift), and the exponential function bounds the observed vote fractions
-between $f_{\mu,z=0.3}$ and zero. Figure~\ref{fig:zeta_examples} shows the
-change in vote fraction and the fit to Equation~\ref{eqn:fzeta} for a random
-selection of galaxies in the \ferengi{} images.
+\noindent where $f_{\mu,z=0.3}$ is the vote fraction at the
+lowest redshift in the \ferengi{} bins ($z=0.3$). Here, $\zeta$ is a model
+parameter that controls the rate at which \ffeatures{} decreases with increasing
+redshift (and that may depend on other galaxy properties). This formula fits
+the data relatively well (with very few exceptions, the vote fractions for
+featured galaxies decrease monotonically with increasing redshift), and the
+exponential function bounds the observed vote fractions between $f_{\mu,z=0.3}$
+and zero. Figure~\ref{fig:zeta_examples} shows the change in vote fraction and
+the best-fit model for a random sample of galaxies.
 
@@
 
-GZH uses the values of $\zeta$ for \emph{all} sets of artificially redshifted
-galaxies to fit the overall distribution as a function of surface brightness,
-since the correction being applied is expected to vary as a function of the
-intrinsic galaxy properties. The galaxies that can be used to measure the
-calibration are restricted to those with a non-zero $f_\textrm{features}$ at
-$z_\mathrm{sim}=0.3$ and with a reasonable fit ($\Delta \chi^2 > 3.0$) to the
-exponential model for the measured change in \ffeatures.
-
-Figure~\ref{fig:zeta_mu} shows the results of fitting the \ferengi{} images
-with Equation~\ref{eqn:fzeta}; the correction is only a weak function of
-surface brightness ($\mu$). Higher-surface brightness galaxies have stronger
-average corrections, likely because these galaxies are more likely to have
-larger $f_\textrm{features}$ values at high redshifts. Low surface brightness
-galaxies are more likely to begin low and remain low; the bounded nature of the
-dropoff (and variance among the individual voters) means that the average
-magnitude of $\zeta$ will be lower.
+The data from Figure~\ref{fig:zeta_examples} show that there is a clear
+dependence on redshift for the observed changes in \ffeatures. To examine
+whether a better fit should involve different parameters, we examine the global
+dependence of $\zeta$ on the galaxy surface brightness. This is motivated by
+the fact that brighter galaxies would presumably be easier to identify;
+\citet{bam09} and \citet{wil13} found changes in \ffeatures{} depending on a
+combination of physical size and absolute magnitude. To simplify our model, we
+subsume these into a single parameter $\mu$.
+
+Figure~\ref{fig:zeta_mu} examines the results of fitting the \ferengi{} images
+with Equation~\ref{eqn:fzeta}. Interestingly, the correction is only a weak
+function of surface brightness. Higher-surface brightness galaxies have
+slightly stronger average corrections, possibly because these galaxies are more
+likely to have larger $f_\textrm{features}$ values at high redshifts. Low
+surface brightness galaxies are more likely to begin low and remain low; the
+bounded nature of the dropoff (and variance among the individual voters) means
+that the average magnitude of $\zeta$ will be lower.
 
@@
 \includegraphics[width=0.50\textwidth]{figures/zeta_mu.png}
-\caption{All fits for the vote fraction dropoff parameter $\zeta$ for
-\ffeatures{} in the \ferengi{} galaxies as a function of surface
-brightness. This includes only those galaxies with a reasonably bounded range
-on the dropoff ($-10<\log(\zeta)<10$) and sufficient points to fit each
-function (37 original galaxies, each artificially redshifted to create a total
-of 296~images}
+\caption{All fits for the \ferengi{} galaxies of the vote fraction dropoff
+parameter $\zeta$ for \ffeatures{} as a function of surface brightness. This
+includes only galaxies with a bounded range on the dropoff
+($-10<\log(\zeta)<10$) and sufficient points to fit each function (37~original
+galaxies, each artificially redshifted to create a total of 296~images).}
 \label{fig:zeta_mu}
@@
 
-The data in Figure~\ref{fig:zeta_mu} are fit with a linear function such that:
+Since there is little evidence for any strong systematic dependence of $\zeta$
+on $\mu$, we do not include any additional parameters in fitting to our
+calibration model.  We fit the data in Figure~\ref{fig:zeta_mu} with a linear
+function:
 
@@
 \caption{Effects of redshift bias in 3,950 images in the \ferengi{} sample.
-Each point in a given redshift and surface brightness bin represents a
+Each point \emph{in a given redshift and surface brightness bin} represents a
 unique galaxy. On the $y$-axis in each bin is the \ffeatures{} value of the
@@
 those in which there is not are blue, and those with not enough data ($N<5$)
-are gray. A larger version of the bin outlined at $z=1.0$ and $20.3 < \mu < 21.0$ $\rm (mag/arcsec^2)$ is shown in Figure~\ref{fig:f_vs_f_zoom}.}
+are gray. A larger version of the bin outlined at $z=1.0$ and $20.3 < \mu <
+21.0$ $\rm (mag/arcsec^2)$ is shown in Figure~\ref{fig:f_vs_f_zoom}.}
 \label{fig:f_vs_f}
@@
 Figure~\ref{fig:f_vs_f} shows the change in \ffeatures{} for the \ferengi{}
-galaxies relative to their lowest simulated redshift. In this analysis, only
-galaxies whose lowest simulated redshift image was $z_\mathrm{sim}=0.3$ were
-used (see Table \ref{tbl:ferengivalues}), and only those which had detectable
-surface brightness measurements in \sextractor; this includes 3,950 of the
-total 6,466 images. For each simulated redshift value \zsim{} at a fixed
-surface brightness $\mu$, \ffeaturesz, the value measured at that simulated
-redshift, is plotted against \ffeaturesrest, the value measured for the same
-galaxy at \zsim$=0.3$.
+galaxies relative to their lowest simulated redshift. This analysis only uses
+galaxies whose lowest simulated redshift image was $z_\mathrm{sim}=0.3$ and
+with detectable surface brightness measurements from \sextractor; this includes
+3,950 of the total 6,466~images originally processed. For each simulated
+redshift value \zsim{} at a fixed surface brightness $\mu$, \ffeaturesz, the
+value measured at that simulated redshift, is plotted against \ffeaturesrest,
+the value measured for the same galaxy at \zsim$=0.3$.
 

### 2016-05-23 python/fzeta_examples.py
Create zeta_examples plot sorted by vote fraction
Addresses #124, corresponding plot added in 943b134.

@@ -10,7 +10,8 @@ data = Table.read("../data/ferengi_debiasable_data.fits")
 
 # Use only galaxies with surface brightness/redshift ranges that are considered "debiasable"
 
-data = data[data['Debiasable']]
+
+data = data#[data['Correctable_Category']!=uncorrectable]
 
 # Limit to galaxies that have data at z_sim = 0.3, since that's what we're normalizing to.
 unique_galaxies = set(data['sdss_id'])
@@ -19,19 +20,19 @@ for ug in unique_galaxies:
     ind = (data['sdss_id'] == ug)
     if data[ind]['sim_redshift'].min() < 0.301:
         z0ind[ind] = True
-        
+
 data_z0 = data[z0ind]
 
 def fzeta_exp(p,x):
-    
+
     #y = p[0] * np.exp(-1 * (x-p[1])/p[2])
-    
+
     y = np.exp(-1 * (x-0.3)/p[0])
 
     return y
-    
+
 def fzeta_lin(p,x):
-    
+
     y = p[0] + p[1] * x
 
     return y
@@ -41,13 +42,13 @@ def fzeta(p,x):
     return fzeta_exp(p,x)
 
 def errfunc(p,x,y,s):
-    
+
     err = (y - fzeta(p,x))/s
 
     return err
 
 def errfunc_lin(p,x,y,s):
-    
+
     err = (y - fzeta_lin(p,x))/s
 
     return err
@@ -57,10 +58,11 @@ def error_bars(k,n=40,c=0.683):
     f_gal_lower = dist.beta.ppf((1-c)/2.,k+1,n-k+1)
     f_gal_upper = dist.beta.ppf(1-(1-c)/2.,k+1,n-k+1)
     f_gal_err = (f_gal_upper - f_gal_lower) / 2.0
-    
+
     return f_gal_err
 
-def common_labels(fig,xlabel=None,ylabel=None,xfontsize=16,yfontsize=40):
+def common_labels(fig,xlabel=None,ylabel=None,xfontsize=16,yfontsize=40,
+                  xlabelpad=None, ylabelpad=None):
 
     # Set common labels
     cax = fig.add_subplot(111)    # The big subplot
@@ -70,36 +72,59 @@ def common_labels(fig,xlabel=None,ylabel=None,xfontsize=16,yfontsize=40):
     cax.spines['left'].set_color('none')
     cax.spines['right'].set_color('none')
[…]

### 2016-05-23 writeup/gz_hubble_data.tex
Cheung+15 compared over matched redshift ranges. See #128.
Changes from all annotated PDFs. Closes #108.

@@
 is affected by their merger history \citep{too72,ste02,hop10}, local
-environment \citep[such as the morphology-density relation;][]{dre80}, initial
+environment \citep[\eg, the morphology-density relation;][]{dre80}, initial
 dark halo mass, secular evolution rate, and many other factors. Morphologies of
@@
 ``clumpy'' structures, with few galaxies that are either smooth or well-ordered
-spirals; asymmetric profiles with strong density contrasts dominate simulated
+spirals; asymmetric galaxies with strong density contrasts dominate simulated
 populations in the early Universe until at least $z\sim1$ \citep{bel12,gen14}.
@@
 responsible for the bulk of imaging studies of high-redshift galaxies.
-Observations of fixed fields with very deep imaging
+Observations of fields with very deep imaging
 \citep[eg,][]{wil96,gia04,bec06,dav07,sco07,gro11} give the photometric
@@
 galaxies make detailed morphologies a challenge even for \hst{} \citep{che12}.
-The public availability of more than $10^5$~galaxies in archival imaging across
-various studies gives a data sample with the potential for high statistical
-significance.
+However, the public availability of more than $10^5$~galaxies in archival
+imaging has generated a data sample with the potential
+for statistically-robust studies of galaxy demographics and evolution.
 
@@
 asymmetric galaxies that become increasingly common at high redshifts. The
-Galaxy Zoo project \citep{lin08} utilizes crowdsourced visual classifications
+Galaxy Zoo project \citep{lin08,for12} utilizes crowdsourced visual classifications
 to measure galaxies in color-composite images. The efforts of more than
@@
 phase of Galaxy Zoo, following its initial results classifying
-$\sim900,000$~SDSS~images into primarily early/late~types \citep{lin11} and
-Galaxy~Zoo~2, which covered $\sim250,000$~SDSS~images using a more detailed
+$\sim900,000$ Sloan Digital Sky Survey (SDSS)~images into primarily early/late~types \citep{lin11} and
+Galaxy~Zoo~2, which covered a subset of $\sim250,000$~images using a more detailed
 classification scheme that included bars, spiral arms, and galactic bulges
@@
 
-The project includes images from the Sloan Digital Sky Survey
-\citep[SDSS;][]{yor00,str02}, in particular those from Data~Release~7
-\citep{aba09}. A small number of images were used in the creation of simulated
-\hst{} images, described in Sections \ref{ssec:ferengi} and \ref{sec:debiasing}
-below; the majority of SDSS images used in GZH were from Stripe~82. The
-Stripe~82 samples in GZH include single-epoch and co-added images, intended to
-facilitate comparison of morphological classification with image depth.
+The project includes images from the SDSS \citep{yor00,str02}, in particular
+those from Data~Release~7 \citep{aba09}. A small number of images were used in
+the creation of simulated \hst{} images, described in Sections
+\ref{ssec:ferengi} and \ref{sec:debiasing} below; the majority of SDSS images
+used in GZH were from Stripe~82. The Stripe~82 samples in GZH include
+single-epoch and co-added images. The single-epoch images provide a local
+sample for comparison to higher-redshift galaxies (including the new
+measurments of clumpy structure), while the co-added images allow for analysis
+of morphological properties as a function of image depth.
 
@@
 %\ref{ssec:galselect} below.
-Single-epoch images from SDSS Stripe~82 were selected using the same criteria
+Single-epoch images from SDSS Stripe~82 were selected using the criteria
 from \citet{wil13}, which required limits of \texttt{petroR90\_r}$ >
@@
 $r^\prime$ Petrosian flux) and a magnitude brighter than $m_r < 17.77$. The
-images used were three-color composites using the $g^\prime$, $r^\prime$, and
+images used were three-color composites created using the $g^\prime$, $r^\prime$, and
 $i^\prime$ filters \citep{nie04}. 21,522 galaxies in SDSS met these criteria.
@@
 GOODS-S; this version used simulated PSFs from \texttt{TinyTim} \citep{kri93},
-drizzled using the same procedures as those used in reduction of the GOODS-S
+drizzled using the same procedures as those used in the reduction of the GOODS-S
 images \citep{koe02,koe03,gia04}. The use of these 2 versions facilitates
@@
 evolution is a crude mechanism that mimics the brightness increase of galaxies
-with increasing redshift (out to at least $z\sim1-2$). The effect on the
+with increasing redshift \citep[\eg,][]{lil98,lov12}. The effect on the
 redshifted images is simply an empirical addition to the magnitude of a galaxy
 of the form $M' = e\times z + M$, where $M'$ is the corrected magnitude, and
-$e$ is the evolutionary correction in magnitudes (i.e., $e=-1$ essentially
+$e$ is the evolutionary correction in magnitudes ($e=-1$ essentially
 brightens the entire galaxy by 1~magnitude by $z=1$). \ferengi{} was run on the images
@@
 of the effects of ``losing'' spiral/disc features with increasing redshift
-for two galaxies with $e=0$.
+for two galaxies with no evolution corrections ($e=0$); as the signal-to-noise ratio in the images
+decreases and the galaxies become fainter, the contrast between features
+like spiral arms goes down and \ffeatures{} drops to the point where both
+galaxies would have been classified as likely ellipticals.
 
 The final number of \ferengi{} images produced for each galaxy is ultimately a
-function of galaxy's redshift (since the new images cannot be resampled at
+function of the galaxy's redshift (since the new images cannot be resampled at
 better angular resolution than the original SDSS data), as well as the number
@@
 
-\subsection{Image creation}\label{ssec:images}
+\subsection{Creating color images}\label{ssec:images}
 
 The images used for classification in GZH were color-composite JPEGs made from
-multi-band data. These were created followed the method of \citet{lup04}, which
-preserves colour information irrespective of intensity.  An asinh intensity
+multi-band data. These were created following the method of \citet{lup04}, which
+preserves color information irrespective of intensity.  An asinh intensity
 mapping was applied to enhance the appearance of faint features while avoiding
@@
 Many of the Legacy surveys described in Section~\ref{ssec:legacy_surveys}
-provided images in only two filters. For these, the shorter-wavelength band was
+provided \hst{} images in only two filters. For these, the shorter-wavelength band was
 mapped to the blue channel, the longer-wavelength band to the red channel, and
@@
 
-The COSMOS survey provided only \Iband{} HST imaging at the time of the GZH
-launch.  These galaxies used ``pseudocolor'' images created by using
-the ACS \Iband{} data as an illumination map and ground-based imaging from the
-\subaru{} telescope in $B_J$, $r^+$, and $i^+$ filters to provide color
-information (see \citealt{gri12} for further details). This resulted in images
-with the angular resolution of \hst{} ($\sim0.05$~\arcsec/pixel) for the
-overall intensity, but color gradients at ground-based resolution, with seeing
-between 0.95\arcsec{} and 1.05\arcsec{} \citep{tan07}.
+The COSMOS survey provides only \Iband{} HST imaging. For these galaxies, GZH
+used ``pseudocolor'' images created by using the ACS \Iband{} data as an
+illumination map and ground-based imaging from the \subaru{} telescope in
+$B_J$, $r^+$, and $i^+$ filters to provide color information (see
+\citealt{gri12} for further details). This resulted in images with the angular
+resolution of \hst{} ($\sim0.05$~\arcsec/pixel) for the overall intensity, but
+color gradients at ground-based resolution, with seeing between 0.95\arcsec{}
+and 1.05\arcsec{} \citep{tan07}.
 
@@
 mask was applied to the color images and a desaturation operation performed.
-This masked procedure was effective in preserving the color balance for
-galaxies, retaining the visibility of faint features while reducing the color
+This masking procedure was effective in preserving the color balance for
+galaxies and retained the visibility of faint features, while reducing the color
 contrast in the sky noise and greatly improving the appearance of the images.
@@
 (respectively) are one, two, three, or four steps below branching points in the
-decision tree.}
+decision tree. The dashed line between T15 and T03 indicates the unique case
+where volunteers could label both clumpy and disk-like morphologies for
+galaxies with clumps arranged in a spiral pattern.}
 \label{fig:decisiontree}
@@
 taking account of the likely differences in high redshift systems, and has four
-broad sets of morphologies classified by the users.  The first option
-designated stars or image artifacts (the result of either bad data or incorrect
+broad sets of morphologies classified by the users.  The first set
+identified stars or image artifacts (the result of either bad data or incorrect
 identification as a galaxy by the ACS pipeline); in this case, the
@@
 volunteers also indicate the relative axial ratio (roundness) for these
-galaxies. The third set was for disk/late-type galaxies, which measured the
+galaxies. The third set was for disk/late-type galaxies, which labeled the
 features necessary to place a galaxy on the standard Hubble tuning fork (bars,
@@
 the \hst{} CANDELS survey and SDSS DR8) began on 10~Sep~2012. Classifications
-for the GOODS 5-epoch images were separately obtained from Mar-Jun 2015 on the
-fourth version of the Galaxy~Zoo site. The GZH project had a total of
-10,349,357~classifications from 93,898 registered participants. 
+for the GOODS 5-epoch images were separately obtained from Mar-Jun 2015 using
+the fourth version of the Galaxy~Zoo site and the same GZH decision tree.
+The GZH project had a total of 10,349,357~classifications from
+93,898~registered participants. 
 % Sum is the total of the GZH SQL table plus the GOODS full-depth imaging in GZ4.
@@
 tree. Votes were subsequently weighted and re-combined in an iterative method
-similar that in previous versions of Galaxy~Zoo \citep{lan08,wil13}, using a
+similar to that in previous versions of Galaxy~Zoo \citep{lan08,wil13}, using a
 method chosen to be as egalitarian as possible while also identifying and
 downweighting classifiers who frequently disagreed with others. The weighting
-factor $(w)$ was 1 for the top 95\% of classifiers, as ranked by consistency.
+factor $w$ was 1 for the top 95\% of classifiers, as ranked by consistency.
 For the bottom 5\% of classifiers, $w$ was designed to drop smoothly and was
-effectively zero for the bottom 1\% in the distribution function. Since this
-only affected a tiny percentage of the classifiers (and an even smaller
-percentage of the classifications) the overall effect on the GZH dataset was
+effectively zero for the bottom 1\% in the distribution function. Since
+downweighting only occurs for the bottom few percent of classifiers (and an even smaller
+percentage of the classifications), the overall effect on the GZH dataset was
 minimal. The method was effective, however, at filtering out contributions from
 randomly classifying or malicious participants.
-% would be good to quantify "tiny" and "even smaller [than tiny]"
 
@@
 The previous versions of Galaxy Zoo morphology classifications
-\citep{lin11,wil13} were based on observations of galaxies in the Sloan Digital
-Sky Survey (SDSS), which have a median redshift of $z<0.2$. In these cases, it
+\citep{lin11,wil13} were based on observations of galaxies in the SDSS,
+which have a median redshift of $z<0.2$. In these cases, it
 was assumed that there was no cosmological evolution of the morphologies of
@@
 For both previous releases of Galaxy~Zoo morphologies, a correction for
-redshift-dependent bias was applied based on matching the classification
+redshift-dependent bias was applied based on matching the mean classification
 fractions at the highest redshifts with those at the lowest redshift.
@@
 \begin{center}
-\includegraphics[width=0.5\textwidth]{figures/eye_of_sauron.pdf}
+\includegraphics[width=0.5\textwidth]{figures/sb_redshift.pdf}
 \caption{Surface brightness as a function of redshift for 3,950~\ferengi{}
@@
 \noindent where $f_{\mu,z=0.3}$ is the vote fraction at the
-lowest redshift in the \ferengi{} bins ($z=0.3$). Here, $\zeta$ is a model
+lowest redshift in the \ferengi{} bins ($z_0=0.3$). Here, $\zeta$ is a model
 parameter that controls the rate at which \ffeatures{} decreases with increasing
@@
 with Equation~\ref{eqn:fzeta}. Interestingly, the correction is only a weak
-function of surface brightness. Higher-surface brightness galaxies have
-slightly stronger average corrections, possibly because these galaxies are more
-likely to have larger $f_\textrm{features}$ values at high redshifts. Low
-surface brightness galaxies are more likely to begin low and remain low; the
-bounded nature of the dropoff (and variance among the individual voters) means
-that the average magnitude of $\zeta$ will be lower.
+function of surface brightness. Higher-surface brightness galaxies have on
+average slightly stronger corrections, possibly because these galaxies have
+larger $f_\textrm{features}$ values at high redshifts. Low surface brightness
+galaxies are more likely to begin low and remain low; the bounded nature of the
+dropoff (and variance among the individual voters) means that the average
+magnitude of $\zeta$ will be lower.
 
@@
 \begin{equation}
-f_\textrm{features,debiased} = 1 - (1 - f_\mathrm{features,weighted})e^{\frac{z-z_0}{\hat\zeta}}.
+f_\textrm{features,debiased} = 1 - (1 - f_\mathrm{features,weighted})e^{\frac{z-z_0}{\hat\zeta}}
 \label{eqn:fzeta_mod}
 \end{equation}
+
+\noindent where $f_\mathrm{features,weighted}$ is the weighted vote fraction
+described in Section~\ref{ssec:weighting}.
 
@@
 Figure~\ref{fig:f_vs_f} shows that the relationship between \ffeaturesz{} and
-\ffeaturesrest{} is \emph{not} always single valued; hence, it is not
+\ffeaturesrest{} is \emph{not} always single-valued; hence, it is not
 appropriate to correct galaxies that lie in certain regions of surface
@@
 redshift bin, the relationship between \ffeaturesz{} and \ffeaturesrest{} is
-modeled by fitting the data with a polynomial of degrees $n=3$, 2, and 1, and
+modeled by fitting the data with polynomials of degrees $n=3$, 2, and 1, and
 using the best formal fit out of the three as measured by the sum of the
 residuals. These fits are shown as the dashed black lines in
-Figure~\ref{fig:f_vs_f}. Any flat regions of the polynomial fits are areas in which
-there is not a clear single-valued relationship between \ffeaturesz{} and
-\ffeaturesrest; this is quantified by setting a minimum slope cut of 0.4. Any
-data in which the polynomial fit has a slope less than this value is considered
-\emph{not} one-to-one, and therefore \ffeaturesz{} cannot be boosted to its
-\ffeaturesrest{} value.  Galaxies in this region are referred to as the
+Figure~\ref{fig:f_vs_f}. Flat regions of the bins are areas in which there is
+not a clear single-valued relationship between \ffeaturesz{} and
+\ffeaturesrest. We quantify this by measuring the slope of the best-fit
+polynomical; regions of the bins with a slope less than 0.4 value are
+considered \emph{not} one-to-one, and therefore \ffeaturesz{} cannot be boosted
+to its \ffeaturesrest{} value.  Galaxies in this region are referred to as the
 \emph{lower limit} sample, because the most stringent correction available is
@@
 Table~\ref{tbl:hubble_debiasable}. Of the galaxies at redshift higher than
-$z=0.3$, 17\% can be debiased using the $\zeta$ method, 27\% cannot be
-debiased, and 56\% cannot have the potential for a correction determined, due
-either to an unknown redshift or insufficient \ferengi{} images corresponding
-to the relevant $z$-$\mu$ values.
+$z=0.3$, 17\% can be debiased using the $\zeta$ method, 27\% cannot be debiased
+since the relationship between \ffeaturesz{} and \ffeaturesrest{} is not
+monotonic, and 56\% cannot be debiased since they either have an unknown
+redshift or insufficient numbers of \ferengi{} images in their $z$-$\mu$ value
+to determine a reliable value of $\zeta$.
 
@@
 \caption{Debiased \ffeatures{} corrected to $z=0.3$ vs weighted \ffeatures{}
-for the correctable (left), lower-limit (middle), and NEI (right) galaxies in
-    the GZH sample.}
+for the correctable (left), lower-limit (middle), and ``not enough
+information'' (NEI; right) galaxies in the GZH sample.}
 \label{fig:debiased_corrections}
@@
 to or less than the number who answered the preceding question. The average number
-of responses per task for fourth- or fifth-tier questions such as spiral arm
-structure (Tasks 12--14) is only $4\pm4$ for the \ferengi{} sample; while this
+of responses per task for fourth- or fifth-tier questions (such as spiral arm
+structure; Tasks 12--14) is only $4\pm4$ for the \ferengi{} sample. While this
 distribution is strongly bimodal (reflecting the true morphologies of
@@
 for the smooth/features question. However, this is often \emph{not} met for
-questions beyond Task~01; on average. $60\%\pm24\%$ of the galaxies do not have
+questions beyond Task~01. On average, $60\%\pm24\%$ of the galaxies do not have
 sufficient data to measure a correction, as compared to 2.0\% achieved for
@@
 \hline
-Correctable                        & 0               & 1,654   & 15,170 & 1,837 & 993    & 835     	& 0       & 20,489\\
-Lower-limit                        & 1               & 1,917   & 26,113 & 2,423 & 1,385  & 1,282   	& 0       & 33,120\\
-No Correction Needed ($z \le 0.3$) & 2               & 955     & 11,926 & 1,175 & 415    & 400     	& 37,545  & 52,416\\ 
-NEI                                & 3               & 2,847   & 34,511 & 3,308 & 2,535  & 2,523   	& 0       & 45,724\\
-No Redshift Information            & 4               & 1,134   & 5,088  & 561   & 687    & 102   		& 14,316  & 21,888\\
+correctable                        & 0               & 1,654   & 15,170 & 1,837 & 993    & 835     	& 0       & 20,489\\
+lower-limit                        & 1               & 1,917   & 26,113 & 2,423 & 1,385  & 1,282   	& 0       & 33,120\\
+no correction needed ($z \le 0.3$) & 2               & 955     & 11,926 & 1,175 & 415    & 400     	& 37,545  & 52,416\\ 
+not enough information (NEI)       & 3               & 2,847   & 34,511 & 3,308 & 2,535  & 2,523   	& 0       & 45,724\\
+no redshift information            & 4               & 1,134   & 5,088  & 561   & 687    & 102   		& 14,316  & 21,888\\
 \hline
-Total                              &                 & 8,507   & 92,808 & 9,304 & 6,015  & 5,142   	& 51,861  & 173,637\\
+total                              &                 & 8,507   & 92,808 & 9,304 & 6,015  & 5,142   	& 51,861  & 173,637\\
 \hline\hline
@@
 
-The data release for GZH includes morphological data for 181,101~images
+The catalog for GZH includes morphological data for 181,101~images
 (generated from a total of 150,771~unique galaxies). The full table can be
@@
 setting \fsmooth$=0.0$ and decreasing \fbest{} accordingly. This correction is
-typically small, with a median decrease/increase of
-$f_\mathrm{features}/f_\mathrm{smooth}$ of $\Delta f = 0.04$.
+typically small, with a median change of
+\ffeatures{} or \fsmooth{} of $\Delta f = 0.04$.
 
@@
 sample in Section~\ref{ssec:sample_labels} corresponds to the data in
-Tables~\ref{tbl:Catalog_hst}-\ref{tbl:simulated_agn}.
+Tables~\ref{tbl:catalog_hst}-\ref{tbl:simulated_agn}.
 
@@
 variety of morphologies. These thresholds are determined by a visual inspection
-of subsamples. For each Task, at least 20 classifiers are required to have voted on
-the given question along with a cut on the vote fraction is applied to the
-previous task. We visually analyzed subsamples of 50~galaxies meeting both
+of subsamples. The thresholds used are a combination of 20~votes for the
+task being considered, as well as limits on the vote fractions for previous
+response(s) in the decision tree.
+
+We visually analyzed subsamples of 50~galaxies meeting both
 criteria, as well as a control sample of galaxies which had 20~classifiers vote on
@@
 As an example of how to use Table~\ref{tbl:thresholds} to create a sample of
-3-armed spirals galaxies, we suggest selecting objects with $N_{arm~number} \ge
+3-armed spiral galaxies, we suggest selecting objects with $N_{arm~number} \ge
 20$, \ffeatures$>0.23, f_{\rm clumpy,no} > 0.30, f_{edgeon,no}>0.25$, and
@@
 have $\ge 20$ answers to these questions used this pathway to arrive at
-these Tasks.  Further, of these subjects, none were found to exhibit disk
-structure, although the clumps within were arranged in a spiral pattern.
+these Tasks. None of these images show obvious disk
+structure, although the clumps within are arranged in a spiral pattern.
 
 This section described how to use Table~\ref{tbl:thresholds} to select
-well-sampled galaxies for which a particular task is reliably sampled. The
+galaxies for which a particular task is reliably sampled. The
 following two examples extend this and show how to use the vote fractions to
@@
 A sample of barred disk galaxies is created by applying cuts on the previous
-tasks as listed in Table~\ref{tbl:thresholds}. 11,049 ``bar candidates'',
-galaxies for which asking the bar question is meaningful, were selected by
+tasks as listed in Table~\ref{tbl:thresholds}. 11,049 ``bar candidates'' are
+galaxies for which asking the bar question is meaningful, and were selected by
 applying the cuts $N_{bar} \ge 20$, $f_{\rm features}>0.23, f_{\rm clumpy,no} >
 0.30,$ and $f_{edgeon,no}>0.25$. These galaxies are featured, non-clumpy,
-non-edge~on galaxies. Of these, a pure sample of 730 barred disks was
-identified by applying a cut of \fbar$>0.7$. A subsample of 50 galaxies were
+non-edge~on galaxies. Of these, a pure sample of 730~barred disks was
+identified by applying a cut of \fbar$>0.7$. A subsample of 50~galaxies were
 visually inspected and 94\% were found to contain strong bars. A complete
 sample of strong and weak bars was created by applying a cut of \fbar$>0.3$.
-This sample contained 3,218 galaxies, 86\% of which were found to contain weak
+This sample contained 3,218~galaxies, 86\% of which were found to contain weak
 or strong bars through visual inspection in a subsample of 50.
@@
 The resulting bar sample can be used to estimate the redshift evolution of bar
-fraction and find a steady decrease of \fbar$\sim 0.32$ at $z=0.4$ to
-\fbar$\sim 0.24$ at $z=1.0$. The decrease in bar fraction agrees with
+fraction; we find a steady decrease of \fbar$\sim 0.32$ at $z=0.4$ to
+\fbar$\sim 0.24$ at $z=1.0$. This decrease agrees with
 \citet{mel14}, although they report a lower overall bar fraction going from
@@
 fraction or average bar likelihood compared to closely-matched inactive
-galaxies.
+galaxies. We note that their technique matched test and control galaxies over
+the same redshift ranges, which minimizes the possible impact of redshift bias.
 
 \subsection{Example 2: Identifying clump multiplicity} Clumps are known to be a
-characteristic feature of galaxies outside the local universe, and there is
+characteristic feature of galaxies at high redshift, and there is
 evidence they play a crucial role in the evolution of modern spirals,
@@
 observations show increasing bulge to clump mass and density ratios as the
-universe evolves since $z\sim 1.5$ \citep{elm09}, suggesting that clumps
+Universe evolves since $z\sim 1.5$ \citep{elm09}, suggesting that clumps
 coalesce over time to form the modern bulges of disk galaxies. GZH added a
@@
 flows between the nodes represent the possible responses. The width of the
-flows is proportional to the number of galaxies associated with that response;
+flows is proportional to the number of galaxies associated with that response.
 Figure~\ref{fig:sankey} uses a simple plurality vote to assign the combined set
@@
 bars of uniform height) represents a task in the tree. The left diagram shows
-the full decision tree; the right diagram zooms in on the features/clumpy
+the full decision tree. The right diagram zooms in on the features/clumpy
 tasks, which are otherwise difficult to see. The paths between tasks represent
-each possible answer to the task; these flow from top to bottom between their
-origin question and the subsequent task in the tree. Labels are assigned to
+each possible answer to the task, flowing from top to bottom between their
+origin and the subsequent task in the tree. Labels are assigned to
 each galaxy based on the plurality answer for each task. A galaxy is assigned
 only one label at each node. Widths of the paths are proportional to the number
-of galaxies assigned to that path; the widths of the nodes are proportional to
+of galaxies assigned to that path. The widths of the nodes are proportional to
 the number of galaxies for which the question was reliably answered.}
@@
 however. The fraction of objects identified as stars or artifact is also much
-higher in the Hubble imaging; by plurality votes, these encompass only
+higher in the Hubble imaging. By plurality votes, these encompass only
 $\sim0.1\%$ of images in SDSS \citep{wil13}, but 6\% of images in GZH.
@@
 the addition of the clumpy branch is necessary to describe a large fraction of
-the sample; disk-dominated galaxies outnumber clumpy morphologies by less than
+the sample, since disk-dominated galaxies outnumber clumpy morphologies by less than
 a factor of 2. Disk galaxies are primarily unbarred \citet{mel14} and
@@
 difficult to differentiate from compact spheroids). Roughly half of the
-galaxies have at least 1~clump identified as the brightest; the clumps are most
+galaxies have at least 1~clump identified as the brightest. Clumps are most
 commonly asymmetrically arranged in clusters and are not often seen embedded in
@@
 the methods used for measuring morphology. These catalogs have been
-cross-matched to GZH to compare the results; this is not presented as an
+cross-matched to GZH to compare the results. This is not presented as an
 endorsement of any particular method, but as an exploration of the strengths
-and weaknesses of the Galaxy~Zoo crowdsourced catalogs as compared to products made
+and weaknesses of the Galaxy~Zoo crowdsourced catalogs compared to products made
 with machine learning, automatic fits, and expert visual classification.
@@
 Morphologies for GEMS galaxies were measured by \citet{hau07}, who used
-single-component \sersic{} fits to the F850LP imaging. This analysis used
-parameters from the \galfit{} code, which \citet{hau07} evaluated as more
-reliable than \gimtwod{} for GEMS due to the ability to fit multiple galaxies
-in crowded fields. A 1\arcsec~positional match for the GEMS galaxies in Table~9
-in \citet{hau07} to the GZH sample gives 8,846~galaxies in both \citet{hau07}
-and GZH. The primary morphological parameter in the automated catalog is the
-\sersic{} index $n$ defining the radial surface brightness profile.
-``Elliptical'' galaxies are selected by $n>2.5$ and ``spirals''  by $n>2.5$.
-There is no automatic measurement of irregular or clumpy structure in this
-catalog.
+single-component \sersic{} fits to the F850LP imaging. A 1\arcsec~positional
+match for the GEMS galaxies in Table~9 in \citet{hau07} to the GZH sample gives
+8,846~galaxies in both \citet{hau07} and GZH. The primary morphological
+parameter in the automated catalog is the \sersic{} index $n$ defining the
+radial surface brightness profile.  ``Elliptical'' galaxies are selected by
+$n>2.5$ and ``spirals''  by $n>2.5$.  There is no automatic measurement of
+irregular or clumpy structure in this catalog.
 
@@
 and composite $Viz$ color images \citep{bun05}. These morphologies are assigned
-a numerical value based on categories in \citet{bri98a}; the corresponding
+a numerical value based on categories in \citet{bri98a}: the corresponding
 morphologies used are ``elliptical'' (classes 0,1,2), ``spirals'' (classes
@@
 automated/expert visual morphologies for each of the six catalogs matched to
-GZH. The relation between GZH and the automated/expert morphologies is shown to
-vary significantly for different surveys --- this could be due to intrinsic
+GZH. The relation between GZH and the automated/expert morphologies varies
+significantly, depending on the survey --- this could be due to intrinsic
 differences in the galaxies, in the techniques used to measure morphology, or
@@
 The second set of plots in Figure~\ref{fig:comparisons} indicates that \fodd{}
-is largely an effective method for separating irregular and/or peculiar
+is an effective method for separating irregular and/or peculiar
 galaxies from spirals. Despite the somewhat vague wording of the {\it
@@
 marked increase in the irregular fraction increasing with \fodd. Any threshold
-value for distinguishing between the two, however, depends strongly on
-survey/redshift~range.
+value for distinguishing between the two, however, depends on
+both the survey and redshift~range covered.
 
@@
 including AEGIS, GEMS, GOODS-N, GOODS-S, and COSMOS. The catalog also includes
-classifications for 51,861 Sloan Digital Sky Survey images in Stripe~82 at
+classifications for 51,861 SDSS images from Stripe~82 at
 relatively low redshift; these serve both as a low-redshift anchor for
@@
 
-\caption{Galaxies whose shallow images were classified as smooth and full depth images were classified as smooth, intermediate, or featured.}
+\caption{Galaxies whose shallow images were classified as smooth and full depth
+images were classified as smooth, intermediate, or featured.}
 \label{fig:shallow_smooth}
@@
 
-\caption{Galaxies whose shallow images were classified as intermediate and full depth images were classified as smooth, intermediate, or featured.}
+\caption{Galaxies whose shallow images were classified as intermediate and full
+depth images were classified as smooth, intermediate, or featured.}
 \label{fig:shallow_intermediate}
@@
 redshift and at $z=0.3$ are marked in white; those in which there is not
-are blue, and those with not enough data ($N<5$) are gray.
-A larger version of the bin outlined at $z=1.0$ and $20.3 < \mu < 21.0$ $\rm (mag/arcsec^2)$ is shown in Figure~\ref{fig:f_vs_fbar_zoom}.
-The mean
-normalized $\chi^2$ of the change in vote fraction is 0.08. None of the
-correlations for higher-order tasks (including bars) were applied to
-galaxies in the GZH catalog.}
+are blue, and those with not enough data ($N<5$) are gray. A larger version of
+the bin outlined at $z=1.0$ and $20.3 < \mu < 21.0$ $\rm (mag/arcsec^2)$ is
+shown in Figure~\ref{fig:f_vs_fbar_zoom}. The mean normalized $\chi^2$ of the
+change in vote fraction is 0.08. None of the correlations for higher-order
+tasks (including bars) were applied to galaxies in the GZH catalog.}
 \label{fig:f_vs_fbar}

### 2016-05-24 writeup/gz_hubble_data.tex
Legends on all subfigures of comparisons
PNG -> PDF for comparisons

Comparisons tweak
non-breaking spaces in text

@@
     ACS imaging data from the two fields are referred to as GOODS-N and GOODS-S,
-    respectively. ACS imaging in GOODS fields used 4 filters -- F435W (\Bband),
+    respectively. ACS imaging in GOODS fields used 4~filters -- F435W (\Bband),
     \Vband, F775W (\iband), and F850LP (\zband). The mean exposure times for each
@@
     for COSMOS consisted of 1~orbit per pointing with an exposure time of
-    2028~seconds in \Iband; 590 total pointings were used to cover the entire
+    2028~seconds in \Iband; 590~total pointings were used to cover the entire
     field. The image resolution was dithered to 0.05~\arcsec/pixel. The 50\%
     completeness magnitude for a galaxy with a half-light radius of
-    $0.50^{\prime\prime}$ in \Iband{} was 24.7 mag.
+    $0.50^{\prime\prime}$ in \Iband{} was 24.7~mag.
 
@@
     Field-South. The GEMS data covered $\sim800$~arcmin$^2$, completely surrounding
-    the area covered by GOODS-S. Images from ACS in GEMS had 1 orbit per pointing
+    the area covered by GOODS-S. Images from ACS in GEMS had 1~orbit per pointing
     for a total of 63~pointings. The exposure times were 2160 and 2286~seconds in
@@
     of 0.03~\arcsec/pixel. The $5\sigma$ limiting magnitude for source
-    detection was 25.7 AB in \Vband{} and 24.2~AB in \zband.
+    detection was 25.7~AB in \Vband{} and 24.2~AB in \zband.
 
@@
 images used were three-color composites created using the $g^\prime$, $r^\prime$, and
-$i^\prime$ filters \citep{nie04}. 21,522 galaxies in SDSS met these criteria.
+$i^\prime$ filters \citep{nie04}. 21,522~galaxies in SDSS met these criteria.
 Co-added images from Stripe~82 were selected from the union of galaxies with
@@
 \stripe{} images and matched to a co-add source. This resulted in a total
-set of 30,339 images. Of the images in the co-added sample, 5144 (17~percent)
+set of 30,339~images. Of the images in the co-added sample, 5144 (17~percent)
 were dimmer than the initial magnitude cut of 17.77.
@@
 drizzled using the same procedures as those used in the reduction of the GOODS-S
-images \citep{koe02,koe03,gia04}. The use of these 2 versions facilitates
+images \citep{koe02,koe03,gia04}. The use of these two versions facilitates
 comparisons between these different PSF creation methods, which are widely used
@@
 classifications derived from any method. To facilitate corrections due to
-redshift, we include a sample of 288 galaxies with SDSS imaging that can be
+redshift, we include a sample of 288~galaxies with SDSS imaging that can be
 transformed to simulate \hst{} imaging out to $z = 1$. 
@@
 described as above, GZH also includes samples of \hst{} galaxy images with
-different color prescriptions. In particular, there are 2 sets of 3,927 images
+different color prescriptions. In particular, there are two sets of 3,927~images
 each, drawn from the COSMOS sample; the first has a dramatically reduced color
@@
 Section~\ref{ssec:images}. This sample includes AEGIS, COSMOS, GEMS, and
-full-depth GOODS (North and South) images. (118,425 galaxies)
+full-depth GOODS (North and South) images. (118,425~galaxies)
 
@@
 \item \faded: a subset of COSMOS images with very low color saturation.
-(3,927 galaxies)
+(3,927~galaxies)
 
@@
 reversed. Note: this sub-sample uses the same galaxies as the \texttt{faded}
-sub-sample. (3,927 galaxies)
+sub-sample. (3,927~galaxies)
 
@@
 \item \goods: Images from GOODS-North and GOODS-South, with
-color from 2 filters and imaged at 2-epoch depth. (6,144 galaxies)
+color from 2~filters and imaged at 2-epoch depth. (6,144~galaxies)
 
@@
 \item \stripe: Single-epoch images from SDSS Stripe~82.
-(21,522 galaxies)
+(21,522~galaxies)
 
@@
 sub-sample includes all galaxies in the \texttt{stripe-82-single} sub-sample,
-with additional sources detected in the deeper imaging. (30,339 galaxies)
+with additional sources detected in the deeper imaging. (30,339~galaxies)
 
@@
 images and artificially redshifted to between $0.3 \leq z \leq 1$. (288
-original galaxies; 3,950 redshifted galaxies)
+original galaxies; 3,950~redshifted galaxies)
 
@@
 \item \simagn: Simulated AGN host galaxies constructed using
-\hst{} images and PSFs. (96 original galaxies; 2,961 simulated AGN host
+\hst{} images and PSFs. (96~original galaxies; 2,961~simulated AGN host
 galaxies)
@@
 
-Photometric data for the bulk of the GZH \main, \faded, \recolored, and \goods{}
-samples were largely drawn from the tables in \citet{gri12}. This included
-photometric parameters such as the fluxes, magnitudes, radii, ellipticities,
-position angles, and positions drawn from both \sextractor{} and \galfit.
-\galfit{} also provided the parametric \sersic{} index and effective half-light
-radius for the best-fit model. All parameters were measured in both bands of
-the ACS imaging, with the exception of the single-band COSMOS images.
+Photometric data for the bulk of the GZH \main, \faded, \recolored, and
+\goods{} samples were largely drawn from the tables in \citet{gri12}. This
+included photometric parameters such as the fluxes, magnitudes, radii,
+ellipticities, position angles, and positions drawn from both \sextractor{} and
+\galfit.  All photometric parameters were measured in both bands of the ACS
+imaging, with the exception of the single-band COSMOS images. Photometric data
+for the GOODS 5-epoch imaging, including \sextractor{} parameters, is from
+\citet{gia12}.
+%\galfit{} also provided the parametric \sersic{} index and effective
+%half-light radius for the best-fit model.
 
@@
 \includegraphics[width=\textwidth]{figures/p_vs_p_SB_redshift.pdf}
-\caption{Effects of redshift bias in 3,950 images in the \ferengi{} sample.
+\caption{Effects of redshift bias in 3,950~images in the \ferengi{} sample.
 Each point \emph{in a given redshift and surface brightness bin} represents a
@@
 \ffeaturesrest. We quantify this by measuring the slope of the best-fit
-polynomical; regions of the bins with a slope less than 0.4 value are
+polynomical; regions of the bins with a slope less than 0.4 are
 considered \emph{not} one-to-one, and therefore \ffeaturesz{} cannot be boosted
@@
 (Section~\ref{ssec:zeta}). Only surface brightness/redshift bins with at least
-5 galaxies were considered; regions with fewer than 5 galaxies are considered
+5~galaxies were considered; regions with fewer than 5~galaxies are considered
 to have ``not enough information'' to determine the \ffeaturesz{} and
@@
 determined using Task~16. Table~\ref{tbl:thresholds} can be used to select
-8,444 galaxies measured as ``clumpy'' using \ffeatures$> 0.23$ and $f_{\rm
+8,444~galaxies measured as ``clumpy'' using \ffeatures$> 0.23$ and $f_{\rm
 clumpy,yes}>0.80$ to ensure the vote fractions for Task~16 are well-sampled.
@@
 3~clumps}>0.75$, 71 four-clump galaxies using $f_{\rm 4~clumps} > 0.70$,
-and 263 galaxies with more than four clumps using $f_{\rm >4~clumps}>0.70$.
+and 263~galaxies with more than four clumps using $f_{\rm >4~clumps}>0.70$.
 Alternatively, these data may be used to create more general samples of
@@
 irregular/clumpy. These categories are compared to two parameters in GZH:
-\fbest, which is designed to identify smooth (elliptical) galaxies, and \fodd,
-which is designed to identify deviations from well-formed spirals or S0s and
+\fbest, which identifies disk-dominated and clumpy galaxies, and \fodd,
+which identifies deviations from well-formed spirals or S0s and
 which constitutes a ``catch-all'' for the variety of asymmetric morphologies
@@
 (``spiral''), and mergers (``irregular''). A 1\arcsec{} positional match on
-AEGIS and GZH yields 4,031 galaxies with reliably-measured morphologies and
+AEGIS and GZH yields 4,031~galaxies with reliably-measured morphologies and
 $S/N>3$ in both $V$- and $I$-bands.
@@
 3,4,5), and ``irregular'' (classes 6,7,8). A 0.5\arcsec{} matched radius yields
-2,435 galaxies (1300 in GOODS-N, 1135 in GOODS-S) in both \citet{bun05} and
+2,435~galaxies (1300 in GOODS-N, 1135 in GOODS-S) in both \citet{bun05} and
 GZH.
@@
 three methods are split into ellipticals, spirals, and peculiar/irregulars. A
-0.5\arcsec{} radius search on GZH matches to 76,241 galaxies in \citet{cas07},
+0.5\arcsec{} radius search on GZH matches to 76,241~galaxies in \citet{cas07},
 76,608 in \citet{tas11}, and 77,425 in \citet{sca07}.
@@
 \center
-\includegraphics[width=1.0\textwidth]{figures/comparisons.png}
+\includegraphics[width=1.0\textwidth]{figures/comparisons.pdf}
 \caption{Distributions of morphological parameters for galaxies matched in GZH
@@
 including AEGIS, GEMS, GOODS-N, GOODS-S, and COSMOS. The catalog also includes
-classifications for 51,861 SDSS images from Stripe~82 at
+classifications for 51,861~SDSS images from Stripe~82 at
 relatively low redshift; these serve both as a low-redshift anchor for

### 2016-05-26 writeup/gz_hubble_data.tex
Significant rewrite of comparisons with volume-limited sample. Closes #133.

@@
 endorsement of any particular method, but as an exploration of the strengths
-and weaknesses of the Galaxy~Zoo crowdsourced catalogs compared to products made
-with machine learning, automatic fits, and expert visual classification.
+and weaknesses of the Galaxy~Zoo crowdsourced catalogs compared to products
+made with machine learning, automatic fits, and expert visual classification.
 
@@
 irregular/clumpy. These categories are compared to two parameters in GZH:
-\fbest, which identifies disk-dominated and clumpy galaxies, and \fodd,
-which identifies deviations from well-formed spirals or S0s and
-which constitutes a ``catch-all'' for the variety of asymmetric morphologies
-that can constitute an irregular galaxy.
+\fbest, which identifies disk-dominated and clumpy galaxies, and \fodd, which
+identifies deviations from well-formed spirals or S0s and which constitutes a
+``catch-all'' for the variety of asymmetric morphologies that can constitute an
+irregular galaxy.
+
+The comparison and analysis of the GZH morphologies is done a set of matched,
+volume-limited samples at $z<1.0$ and $m_{I|i|z} < 22.5$~mag.  The redshift and
+magnitude limits for the sample are chosen to match the shared constraints for
+the shallowest depths \citep[GEMS;][]{bun05} and the limits on morphological
+reliability \citep[COSMOS/ZEST;][]{sca07} in the comparison catalogs. We match
+all catalogs against GZH using a positional radius of 0.5\arcsec.
 
@@
 radial surface brightness profile.  ``Elliptical'' galaxies are selected by
-$n>2.5$ and ``spirals''  by $n>2.5$.  There is no automatic measurement of
-irregular or clumpy structure in this catalog.
+$n>2.5$ and ``spirals''  by $n<2.5$.  There is no automatic measurement of
+irregular or clumpy structure.
 
 AEGIS galaxies were morphologically classified using non-parametric
-measurements by \citet{lot08}. This method used a combination of the Gini
+measurements by \citet{lot08}. Their method used a combination of the Gini
 coefficient ($G$), which measures the relative inequality in pixel brightness,
@@
 categories of galaxy morphology: E/S0/Sa (``elliptical''), Sb/Sc/Ir
-(``spiral''), and mergers (``irregular''). A 1\arcsec{} positional match on
-AEGIS and GZH yields 4,031~galaxies with reliably-measured morphologies and
-$S/N>3$ in both $V$- and $I$-bands.
+(``spiral''), and mergers (``irregular''). We limit the AEGIS galaxies to those
+with reliably-measured morphologies and $S/N>3$ in both $V$- and $I$-bands in
+\citet{lot08}.
 
@@
 morphologies used are ``elliptical'' (classes 0,1,2), ``spirals'' (classes
-3,4,5), and ``irregular'' (classes 6,7,8). A 0.5\arcsec{} matched radius yields
-2,435~galaxies (1300 in GOODS-N, 1135 in GOODS-S) in both \citet{bun05} and
-GZH.
+3,4,5), and ``irregular'' (classes 6,7,8).
 
@@
 used a combination of concentration ($C$), asymmetry ($A$), $G$, and $M_{20}$
-\citep{cas05} to classify all galaxies with $m_\mathrm{I,petro}<25$, and used
-an empirical division based on several hundred training images to assign
-galaxies to discrete morphological categories. A similar method is employed by
-\citet{tas11}, using the same non-parametric indices but with a different
-method of calculating the Petrosian radius and total light profile. They employ
-a nearest-neighbors method to assign morphological categories for the
-entire sample based on a small training set. \citet[][ZEST]{sca07} used $C$,
+\citep{cas05} make empirical divisions based on several hundred training images
+to assign galaxy morphology. A similar method was employed by \citet{tas11},
+using the same non-parametric indices but with a different method of
+calculating the Petrosian radius and total light profile, and using a
+nearest-neighbors method to label morphologies. \citet[][ZEST]{sca07} used $C$,
 $A$, $G$, $M_{20}$, the galaxy ellipticity ($\epsilon$), and \sersic{} index
-($n$) to quantify the galaxy shapes; a principal component analysis is used to
-assign galaxies to discrete morphological categories. The categories in all
-three methods are split into ellipticals, spirals, and peculiar/irregulars. A
-0.5\arcsec{} radius search on GZH matches to 76,241~galaxies in \citet{cas07},
-76,608 in \citet{tas11}, and 77,425 in \citet{sca07}.
+($n$) to quantify morphology; a principal component analysis is used to assign
+galaxies to categories. All three methods use discrete morphological categories
+of ellipticals, spirals, and peculiar/irregulars. We use the same categories
+with the exception of assigning S0/bulge-dominated disks (type~2.0) from ZEST
+into the elliptical category.
 
@@
 \center
-\includegraphics[width=1.0\textwidth]{figures/comparisons.pdf}
-\caption{Distributions of morphological parameters for galaxies matched in GZH
-and other published catalogs, split by survey (AEGIS, COSMOS, GEMS, and GOODS).
-The first and third columns show the fraction of overall galaxies in the
-matched samples, split by their published morphologies as a function of the GZH
-\fbest. The corresponding second and fourth columns show data for the same
-galaxies as a function of \fodd. The ``odd'' samples exclude galaxies dominated
-by lenses or dust lanes ($<1\%$ of the total), which are GZH categories not
-expected to correlate to larger-scale structural parameters. Confidence
-intervals for each binned fraction in the bin are calculated for a binomial
+\includegraphics[width=1.0\textwidth]{figures/comparisons_features.pdf}
+\caption{Distributions of morphological parameters for a volume-limited sample
+($z<1.0$, $m<22.5$) of galaxies matched between GZH and six published
+morphological catalogs, split by survey (AEGIS, COSMOS, GEMS, and GOODS). This
+plot shows the fraction of overall galaxies for each of the external
+morphological categories as a function of \fbest{} in GZH. The shaded regions
+around the binned fractions are confidence intervals calculated for a binomial
 population \citep{cam11}.}
-\label{fig:comparisons}
+\label{fig:comparisons_features}
 \end{figure*}
 
-Figure~\ref{fig:comparisons} shows the proportion of galaxies as split by their
-automated/expert visual morphologies for each of the six catalogs matched to
-GZH. The relation between GZH and the automated/expert morphologies varies
-significantly, depending on the survey --- this could be due to intrinsic
-differences in the galaxies, in the techniques used to measure morphology, or
-both. The distribution of \fbest{} for AEGIS galaxies is essentially flat for
-spirals, showing almost no difference in proportion at the highest and lowest
-ends. Early-type galaxies are at their highest proportion at \fbest$\sim0$, but
-constitute at most only 40\% of galaxies. In contrast, GOODS galaxies at low
-\fbest{} are dominated by early-types, although spiral and irregular galaxies
-have comparable sizes as low as \fbest$\sim0.2$.
-
-In GEMS galaxies, the impact of irregular or peculiar galaxies is not measured;
-splitting on $n=2.5$ gives an essentially flat proportion of ellipticals to
-spirals at \fbest$>0.3$.  Visual inspection of images of galaxies where both
-\fbest{} and $n$ are high show that the majority are obvious spirals but with
-prominent bulges, indicating that the single-component \sersic{} fit is likely
-choosing too small of an effective radius and missing the extended disk
-structure for a large population of galaxies. This is a known issue with using
-$n$ as a standalone measure of galaxy morphology -- it is relatively common,
-for example, to measure high $n$ for an object with an exponential disk but a
-central cusp in the light profile (eg, due to an AGN, cluster, foreground
-star, noise, etc).
-
-Even within the same sample of galaxies in COSMOS, different techniques of
-measuring morphology show significant differences. Both \citet{cas07} and
-\citet{tas11} have higher proportions of early-type galaxies at \fbest$\sim0$,
-but constitute less than half the sample in both cases. The majority of all
-galaxies in \citet{sca07}, in contrast, are spirals; oddly, the \emph{highest}
-proportions of spirals are found at the lowest values of \fbest. The decrease
-in spiral galaxies at higher \fbest{} is almost entirely balanced by an
-increase in irregulars. Early-types have a small bump near \fbest$\sim0.15$,
-but never constitute more than 10\% of the sample.
-
-The second set of plots in Figure~\ref{fig:comparisons} indicates that \fodd{}
-is an effective method for separating irregular and/or peculiar
-galaxies from spirals. Despite the somewhat vague wording of the {\it
-``anything odd?''} question in GZH, the AEGIS, COSMOS, and GOODS all show a
-marked increase in the irregular fraction increasing with \fodd. Any threshold
-value for distinguishing between the two, however, depends on
-both the survey and redshift~range covered.
-
-As the data shown in Figure~\ref{fig:comparisons} cover a wide range of
-redshifts and sizes, a volume-limited sample of galaxies (or at least binning
-by redshift) is likely a much more appropriate comparison. While detailed
-analysis is left to a further paper, we note that there is no strong change in
-the proportion of galaxies when binning by redshift intervals of $\Delta z=0.2$
-out to $z=1.0$.
+Figure~\ref{fig:comparisons_features} shows the proportion of galaxies as split
+by their automated/expert visual morphologies for each of the six catalogs
+matched to GZH. Galaxies from every catalog show a strong correlation between
+\fbest{} and the fraction of galaxies identified as spirals, with a
+corresponding anti-correlation between \fbest{} and the fraction of
+ellipticals.
+
+The AEGIS sample had the fewest number of matched galaxies (485) with GZH;
+while the statistical uncertainties are as a result higher, the strongest
+difference between spirals and early-types is seen at \fbest$>0.8$. GOODS
+galaxies, which are the only comparison sample that also uses visual
+morphology, shows a very similar trend, with nearly 100\% pure samples at
+the lowest and highest values of \fbest.  Galaxies from GEMS (which are
+only split into two types) also have a strong correlation with \fbest,
+which is somewhat surprising (but encouraging) considering the known limits
+of assigning galaxy morphology based only on a single \sersic{} fit.
+
+Visual inspection of images of the exceptions --- where both \fbest{} and $n$
+are high --- show that most are obvious spirals but with prominent bulges. This
+means that the single-component \sersic{} fit is likely choosing too small of
+an effective radius and missing the extended disk structure for a large
+population of galaxies. This is a known issue with using $n$ as a standalone
+measure of galaxy morphology -- it is relatively common, for example, to
+measure high $n$ for an object with an exponential disk but a central cusp in
+the light profile (eg, due to an AGN, cluster, foreground star, noise, etc).
+
+Galaxies from the three COSMOS surveys all have morphologies that are
+reasonably well-predicted by the GZH based on \fbest. The relation is strongest
+for early-type galaxies, since the comparable fractions of irregulars and
+spirals shows that clumpy/asymmetric morphologies are clearly also being
+captured by the \fbest{} parameter. The small dropoff in the fraction of
+early-types for the Cassata and ZEST samples at \fbest$<0.1$ is somewhat
+puzzling, but could potentially be due to the presence of a small
+population of extremely compact objects (stars or quasars) that would be
+classified as artifacts in GZH, explaining the dip in \fbest.
+
+We also emphasize that the various COSMOS catalogs are not consistent; for
+example, only 64\% of the galaxies in \citet{tas11} have the same morphological
+class as \citet{cas07}. The bulk of these are galaxies classified as ``spiral''
+using one technique and ``irregular'' using another (\citealt{cas07} is more
+likely to classify galaxies as irregular).  A detailed comparison of the
+external catalogs is outside the scope of this paper, but we emphasize only
+that it is \emph{impossible} for any catalog to be consistent with all three.
+We interpret the broad agreements between early-types, spirals, and irregulars
+for all three samples as a validation of the crowdsourced visual
+classifications provided by GZH.
+
+\begin{figure*}
+\center
+\includegraphics[width=1.0\textwidth]{figures/comparisons_odd.pdf}
+\caption{Same as Figure~\ref{fig:comparisons_features}, but comparing external
+morphologies to \fodd{} in GZH. Measurement of \fodd{} excludes galaxies
+dominated by lenses or dust lanes ($<1\%$ of the total), which are GZH
+categories not expected to correlate with larger-scale structural parameters.}
+\label{fig:comparisons_odd}
+\end{figure*}
+
+Figure~\ref{fig:comparisons_odd} analyzes the same sets of matched galaxies, but
+compares the data the \fodd{} parameter in GZH to examine its correlation with
+irregular morphologies. The relationship in this case is less clear; for the
+COSMOS catalogs, in particular, early-types, spirals, and irregulars are
+roughly equally probable at \fodd$>0.5$. In both AEGIS and GOODS (there is no
+measurment of irregular structure for GEMS in \citealt{hau07}), the proportion
+of irregular galaxies does increase with \fodd. However, the actual number of
+galaxies at \fodd$>0.5$ is quite small ($N\lesssim100$) in both samples, and so
+estimating an accurate fraction is less precise.  We also note that this
+particular question ({\it ``anything odd?''}) has somewhat uncertain phrasing
+in GZH, and that the design of the tree explicitly separates clumpy from
+irregular or merging morphologies, which would have similar properties in
+automatic techniques. A more accurate selection of irregular morphologies in
+GZH should likely use some combination of \fbest, \fclumpy, and \fodd.
+
+We repeated all of the analysis comparing morphologies between GZH and external
+catalogs on the entire catalog, rather than the volume-limited sample
+($z<1.0,m<22.5$) discussed above. If all redshifts and the original magnitude
+limit of $m<23.5$ are used, the correlations between all of the automatic
+morphological populations and GZH decrease significantly.  The only exception
+are the GEMS galaxies, which are the only sample visually classified (similar
+to GZH) and had a shallower magnitude cut on their catalog. Based on these
+comparisons, we suggest that use of the GZH catalog be limited to galaxies with
+$m<22.5$; fainter targets at the sensitivity of the \hst{} Legacy surveys have
+been demonstrated to be less reliable, regardless of the method of
+morphological classification being used.
+
+\subsection{Galaxy Zoo: Hubble and Galaxy Zoo: CANDELS}\label{ssec:gzh_gzc}
 
@@
 et~al., submitted). Since both the sensitivity and filters for the two sets of
-images differ (and there is no correction for redshift bias applied to GZC), there is no
-prior reason to expect a perfect correlation between the separate vote
-fractions for the projects. Briefly, we note that the \ffeatures{} value for
-GZH is on average higher than GZC; the effect is strongest at
-$f_\mathrm{features,GZC}<0.3$, for which roughly half the galaxies have
-$f_\mathrm{features,GZH}>0.5$. However, the correlation between vote fractions
-is single-valued (although not linear, with a Pearson correlation coefficient
-of $r=0.6$), and should be possible to calibrate using a similar approach to
-that described in Section~\ref{sec:debiasing}; the correlation between other
-tasks, such as edge-on galaxies is significantly stronger ($r=0.9$). So while
-the raw vote fractions are not directly comparable, the initial analysis
-indicates that the broad morphologies are at least consistent.
+images are significantly different (and there is no correction for redshift
+bias applied to GZC), there is no prior reason to expect a perfect correlation
+between the separate vote fractions for the projects. Briefly, we note that the
+\ffeatures{} value for GZH is on average higher than GZC; the effect is
+strongest at $f_\mathrm{features,GZC}<0.3$, for which roughly half the galaxies
+have $f_\mathrm{features,GZH}>0.5$. However, the correlation between vote
+fractions is single-valued (although not linear, with a Pearson correlation
+coefficient of $r=0.6$), and should be possible to calibrate using a similar
+approach to that described in Section~\ref{sec:debiasing}; the correlation
+between other tasks, such as edge-on galaxies is significantly stronger
+($r=0.9$). So while the raw vote fractions are not directly comparable, the
+initial analysis indicates that the broad morphologies are at least consistent.
 

### 2016-05-26 python/comparisons.py

@@ -1,5 +1,6 @@
 from PIL import Image
 from astropy.io import fits
+from astropy import units as u
 from matplotlib import cm
 from matplotlib import pyplot as plt
 from matplotlib.colors import LogNorm
@@ -10,6 +11,8 @@ import numpy as np
 import random
 import scipy.stats.distributions as dist
 import warnings
+from astropy.cosmology import WMAP9
+    
 
 warnings.filterwarnings('ignore', category=RuntimeWarning, append=True)
 
@@ -41,11 +44,97 @@ def get_image(survey_id,goods=False,ns='n'):
     img = Image.open(filename)
     return img
 
+def get_dlist(aegis,gems,goods,cassata,tasca,zest):
+
+    dlist = [
+             {'data':aegis,
+              'survey':'AEGIS',
+              'citation':'Lotz+08',
+              'magcol':'MAG_BEST_HI',
+              'maglim':23.5,
+              'classcol':'TYPE'},
+             {'data':gems,
+              'survey':'GEMS',
+              'citation':'Haeussler+07',
+              'magcol':'MAG_BEST_HI',
+              'maglim':23.5,
+              'classcol':'TYPE'},
+             {'data':goods,
+              'survey':'GOODS',
+              'citation':'Bundy+05',
+              'magcol':'ZMAG',
+              'maglim':22.5,
+              'classcol':'TYPE'},
+             {'data':cassata,
+              'survey':'COSMOS',
+              'citation':'Cassata+07',
+              'magcol':'MAG_BEST_HI',
+              'maglim':23.5,
+              'classcol':'AUTOCLASS'},
+             {'data':tasca,
+              'survey':'COSMOS',
+              'citation':'Tasca+11',
+              'magcol':'MAG_BEST_HI',
+              'maglim':23.5,
+              'classcol':'CLASS_INT'},
+             {'data':zest,
+              'survey':'COSMOS',
+              'citation':'Scarlata+07',
+              'magcol':'MAG_BEST_HI',
+              'maglim':23.5,
+              'classcol':'TYPE'},
+              ]
+
+    return dlist
+
 def cameron_err(c,k,n):
[…]

### 2016-05-26 writeup/gz_hubble_data.tex

@@
 only two parameters as a simple model of the effect of redshift brightness on classification: the
-$r^\prime$-band surface brightness ($\mu_r$; intrinsic) and redshift ($z$;
+$i^\prime$-band surface brightness ($\mu_\mathrm{i}$; intrinsic) and redshift ($z$;
 extrinsic).
 
-%This dependence of the vote fraction on $\mu_r$ and \zsim{} is measured using the \ferengi{} images over all the evolutionary correction factors. 
 We model the debiased vote fraction $f_{\mu,z}$ for an
@@
 
-\noindent where $f_{\mu,z=0.3}$ is the vote fraction at the
-lowest redshift in the \ferengi{} bins ($z_0=0.3$). Here, $\zeta$ is a model
-parameter that controls the rate at which \ffeatures{} decreases with increasing
-redshift (and that may depend on other galaxy properties). This formula fits
-the data relatively well (with very few exceptions, the vote fractions for
-featured galaxies decrease monotonically with increasing redshift), and the
-exponential function bounds the observed vote fractions between $f_{\mu,z=0.3}$
-and zero. Figure~\ref{fig:zeta_examples} shows the change in vote fraction and
-the best-fit model for a random sample of galaxies.
+\noindent where $f_{\mu,z=0.3}$ is the vote fraction at the lowest redshift in
+the artificially-redshifted sample ($z_0=0.3$). Here, $\zeta$ is a parameter that
+controls the rate at which \ffeatures{} decreases with increasing redshift (and
+that may depend on other galaxy properties). This function bounds the observed
+vote fractions between $f_{\mu,z=0.3}$ and zero based on two assumptions: 1)
+the vote fractions for featured galaxies decrease monotonically with increasing
+redshift, therefore restricting vote fractions for a given galaxy to be less
+than $f_{\mu,z=0.3}$ (which is almost always true of the data), and 2) the
+vote fractions cannot be less than zero (which is always true).
 
@@
 
-The data from Figure~\ref{fig:zeta_examples} show that there is a clear
-dependence on redshift for the observed changes in \ffeatures. To examine
-whether a better fit should involve different parameters, we examine the global
-dependence of $\zeta$ on the galaxy surface brightness. This is motivated by
-the fact that brighter galaxies would presumably be easier to identify;
-\citet{bam09} and \citet{wil13} found changes in \ffeatures{} depending on a
-combination of physical size and absolute magnitude. To simplify our model, we
-subsume these into a single parameter $\mu$.
+Figure~\ref{fig:zeta_examples} shows the change in vote fraction and the
+best-fit model for a random set of galaxies in the \ferengi{} sample. The
+results show that there is a clear dependence on redshift for the observed
+changes in \ffeatures. To examine whether a better fit should involve
+additional parameters, we examine the global dependence of $\zeta$ on the
+galaxy surface brightness. This is motivated by the fact that brighter galaxies
+would presumably be easier to identify; \citet{bam09} and \citet{wil13} found
+changes in \ffeatures{} depending on a combination of physical size and
+absolute magnitude. To simplify our model, we subsume these into a single
+parameter $\mu$.
 
@@
 galaxies whose lowest simulated redshift image was $z_\mathrm{sim}=0.3$ and
-with detectable surface brightness measurements from \sextractor; this includes
+with detectable surface brightness measurements from \sextractor{} \citep{mel16}; this includes
 3,950 of the total 6,466~images originally processed. For each simulated

### 2016-05-26 writeup/gz_hubble_data.tex
Updating PDF and almost all figures for new SB technique

@@
 \center
-\includegraphics[width=0.50\textwidth]{figures/zeta_mu.png}
+\includegraphics[width=0.50\textwidth]{figures/zeta_mu.pdf}
 \caption{All fits for the \ferengi{} galaxies of the vote fraction dropoff
@@
 \centering
-\includegraphics[width=0.5\textwidth]{figures/z1_mu20_subplot2.pdf}
+\includegraphics[width=0.45\textwidth]{figures/z1_mu20_subplot2.pdf}
 \caption{A larger version of the dark-outlined square in Figure~\ref{fig:f_vs_f}, containing
@@
 \ffeaturesrest. We quantify this by measuring the slope of the best-fit
-polynomical; regions of the bins with a slope less than 0.4 are
-considered \emph{not} one-to-one, and therefore \ffeaturesz{} cannot be boosted
-to its \ffeaturesrest{} value.  Galaxies in this region are referred to as the
+polynomical; regions of the bins with a slope less than 0.4 are considered
+\emph{not} one-to-one, and therefore \ffeaturesz{} cannot be boosted to its
+\ffeaturesrest{} value.  Galaxies in this region are referred to as the
 \emph{lower limit} sample, because the most stringent correction available is
@@
 to have ``not enough information'' to determine the \ffeaturesz{} and
-\ffeaturesrest{} relationship, colored gray in Figure~\ref{fig:f_vs_f}. These galaxies are hereafter referred to as the ``NEI'' sample.
+\ffeaturesrest{} relationship, colored gray in Figure~\ref{fig:f_vs_f}. These
+galaxies are hereafter referred to as the ``NEI'' sample.
 

### 2016-05-27 writeup/gz_hubble_data.tex
Bands in SDSS 2.5 are not primed; that's the old USNO.

@@
 3$\arcsec~(where \texttt{petroR90\_r} is the radius containing 90\% of the
-$r^\prime$ Petrosian flux) and a magnitude brighter than $m_r < 17.77$. The
-images used were three-color composites created using the $g^\prime$, $r^\prime$, and
-$i^\prime$ filters \citep{nie04}. 21,522~galaxies in SDSS met these criteria.
+$r$-band Petrosian flux) and a magnitude brighter than $m_r < 17.77$.
+21,522~galaxies in SDSS met these criteria.
 Co-added images from Stripe~82 were selected from the union of galaxies with
@@
 which combined $g^{\prime}$, $r^{\prime}$, and $i^{\prime}$ exposures into the
-RGB channels. The co-added Stripe~82 images were assembled from runs 106 and
+RGB channels \citep{nie04}. The co-added Stripe~82 images were assembled from runs 106 and
 206 in DR7 and processed into color composites in the same manner as previous
@@
 ellipticals, mergers, edge-on disks, bulge prominence/shape, and bars) and
-$r^\prime$-band surface brightnesses.  The overall selection spanned the
+$r$-band surface brightnesses.  The overall selection spanned the
 redshift range of SDSS targets and maximized the number of \hst{} galaxies at
@@
 only two parameters as a simple model of the effect of redshift brightness on classification: the
-$i^\prime$-band surface brightness ($\mu_\mathrm{i}$; intrinsic) and redshift ($z$;
+$i$-band surface brightness ($\mu_\mathrm{i}$; intrinsic) and redshift ($z$;
 extrinsic).

### 2016-05-27 writeup/gz_hubble_data.tex
Re-ordering authors and adding affiliations.

@@
 %% \author and \affil call.
-\author{Kyle W.
-Willett\altaffilmark{1,2}, Melanie A.
-Galloway\altaffilmark{1}, Karen L.
-Masters\altaffilmark{3,4}, B.D.
-Simmons\altaffilmark{5,6,7}, Chris J.
-Lintott\altaffilmark{5}, Steven P.
-Bamford\altaffilmark{8}, Edmond Cheung\altaffilmark{9}, Tom Melvin\altaffilmark{3}, Lucy F.
-Fortson\altaffilmark{1}, Melanie Beck\altaffilmark{1}, Claudia Scarlata\altaffilmark{1}, Roger L.
-Griffith\altaffilmark{10,11}, Kevin Schawinski\altaffilmark{12}, Edward M.
-Edmondson\altaffilmark{3}, Arfon M.
-Smith\altaffilmark{5,13,14}, Michael Parrish\altaffilmark{13}, Anna Han\altaffilmark{15}
+\author{
+    Kyle W. Willett\altaffilmark{1,2}, 
+    Melanie A. Galloway\altaffilmark{1}, 
+    Steven P. Bamford\altaffilmark{3}, 
+    Chris J. Lintott\altaffilmark{4}, 
+    Karen L. Masters\altaffilmark{5,6}, 
+    Claudia Scarlata\altaffilmark{1}, 
+    B.D. Simmons\altaffilmark{4,7}, 
+    Melanie Beck\altaffilmark{1}, 
+    Carolin N. Cardamone\altaffilmark{8}, 
+    Edmond Cheung\altaffilmark{9}, 
+    Edward M. Edmondson\altaffilmark{5}, 
+    Lucy F. Fortson\altaffilmark{1},
+    Roger L. Griffith\altaffilmark{10,11}, 
+    Boris H\"au{\ss}ler\altaffilmark{4,12,13},
+    Anna Han\altaffilmark{14}, 
+    Ross Hart\altaffilmark{3}, 
+    Tom Melvin\altaffilmark{5}, 
+    Michael Parrish\altaffilmark{15}, 
+    Kevin Schawinski\altaffilmark{16}, 
+    R.J. Smethurst\altaffilmark{4}, 
+    Arfon M. Smith\altaffilmark{5,15,17}
 }
@@
 %$^N$Yale Center for Astronomy and Astrophysics, Yale University, P.O. Box 208121, New Haven, CT 06520, USA \\
-%$^N$Steward Observatory, University of Arizona, 933 N. Cherry Ave, Tuscon, AZ 85721, USA\\
+%$^N$Steward Observatory, University of Arizona, 933 N. Cherry Ave, Tucson, AZ 85721, USA\\
 %$^N$Astronomy Department, Adler Planetarium and Astronomy Museum, 1300 Lake Shore Drive, Chicago, IL 60605, USA\\
@@
 
-%\altaffiltext{1}{School of Physics and Astronomy, University of Minnesota, USA}
-%\altaffiltext{2}{Department of Physics and Astronomy, University of Kentucky, USA}
-%\altaffiltext{3}{Oxford Astrophysics, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK}
-%\altaffiltext{4}{Center for Astrophysics and Space Sciences (CASS), Department of Physics, University of California, San Diego, CA 92093, USA}
-%\altaffiltext{5}{Balliol College}
-%\altaffiltext{6}{Einstein Fellow}
-%\altaffiltext{7}{Institute of Cosmology and Gravitation, University of Portsmouth, UK}
-%\altaffiltext{8}{SEPnet, South East Physics Network, UK}
-%\altaffiltext{9}{University of Nottingham, UK}
-%\altaffiltext{10}{ETH Z\"urich, Switzerland}
-%\altaffiltext{11}{Kavli Institute for the Physics and Mathematics of the Universe (WPI), Japan}
-%\altaffiltext{12}{Adler Planetarium, USA}
-%\altaffiltext{13}{GitHub}
-%\altaffiltext{14}{University of California, Berkeley, USA}
-%\altaffiltext{15}{Penn State University, USA}
-%\altaffiltext{16}{Yale University, USA}
+\altaffiltext{1}{School of Physics and Astronomy, University of Minnesota, USA}
+\altaffiltext{2}{Department of Physics and Astronomy, University of Kentucky, USA}
+\altaffiltext{3}{School of Physics and Astronomy, University of Nottingham, UK}
+\altaffiltext{4}{Oxford Astrophysics, University of Oxford, UK}
+\altaffiltext{5}{Institute of Cosmology and Gravitation, University of Portsmouth, UK}
+\altaffiltext{6}{SEPnet, South East Physics Network, UK}
+\altaffiltext{7}{Center for Astrophysics and Space Sciences, UC San Diego, USA}
+\altaffiltext{8}{Department of Mathematics and Science, Wheelock College, USA}
+\altaffiltext{9}{Kavli Institute for the Physics and Mathematics of the Universe (WPI), Japan}
+\altaffiltext{10}{Infrared Processing and Analysis Center, California Institute of Technology, USA}
+\altaffiltext{11}{Department of Astronomy and Astrophysics, Pennsylvania State University, USA}
+\altaffiltext{12}{Centre for Astrophysics, University of Hertfordshire, UK}
+\altaffiltext{13}{European Southern Observatory, Santiago, Chile}
+\altaffiltext{14}{Department of Astronomy, Yale University, USA}
+\altaffiltext{15}{Adler Planetarium, USA}
+\altaffiltext{16}{Institute for Astronomy, ETH Z\"urich, Switzerland}
+\altaffiltext{17}{GitHub}
 

### 2016-05-27 writeup/gz_hubble_data.tex

@@
 
-\title{Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging}
+\title{Galaxy Zoo: Morphological Classifications for 120,000 Galaxies in HST Legacy Imaging}
 %% Use \author, \affil, plus the \and command to format author and affiliation 
@@
 baseline. The GZH catalog contains both raw and calibrated morphological vote
-fractions for $150,771$~galaxies, providing the largest dataset to date
+fractions for $119,849$~galaxies, providing the largest dataset to date
 suitable for large-scale studies of galaxy evolution out to $z\sim1$. 
+% Number = hubble + goods_shallow + stripe82_coadd
 \end{abstract}
@@
 GOODS images from both fields included galaxies with $m<26.8$. This yielded a
-total of 113,166~images (Table~\ref{tbl:gzh_numbers}).
+total of $119,849$~images (Table~\ref{tbl:gzh_numbers}).
 
@@
 \center
-\caption{Summary of GZH imaging \label{tbl:gzh_numbers}}
+\caption{Summary of GZH \hubble{} imaging \label{tbl:gzh_numbers}}
 \begin{tabular}{lllcrr}
@@
 \hline
-AEGIS                                   & 2100$-$2300  & \Vband, \Iband{}                 & 0.03 & 710                & 8157    \\
-COSMOS                                  & 2028         & \Iband{}                         & 0.05 & 6480               & 88530   \\
-GEMS                                    & 2160$-$2286  & \Vband, \zband{}                 & 0.03 & 800                & 9143    \\
+AEGIS                                   & 2100$-$2300  & \Vband, \Iband{}                 & 0.03 & 710                & 8507    \\
+COSMOS                                  & 2028         & \Iband{}                         & 0.05 & 6480               & 84954   \\
+GEMS                                    & 2160$-$2286  & \Vband, \zband{}                 & 0.03 & 800                & 9087    \\
 GOODS                                   & $-$          & $-$                              & $-$  & $-$                & $-$     \\
@@
 \hline
-total                                   & $-$          & $-$                              & $-$  & 8630 & 123131  \\
+all \hst{} surveys                      & $-$          & $-$                              & $-$  & 8630               & 119849  \\
 \hline\hline
@@
 
-The full GZH sample is composed of 7~different galaxy sub-samples. Throughout
+The full GZH sample is composed of 8~different galaxy sub-samples. Throughout
 this paper and in the published catalogs they are referred to with the
@@
 Section~\ref{ssec:images}. This sample includes AEGIS, COSMOS, GEMS, and
-full-depth GOODS (North and South) images. (118,425~galaxies)
+full-depth GOODS (North and South) images. (113,705~galaxies)
 
@@
 \item \redshifted: Simulated \hst{} images constructed using SDSS
-images and artificially redshifted to between $0.3 \leq z \leq 1$. (288
-original galaxies; 3,950~redshifted galaxies)
+images and artificially processed to redshifts between $0.3 \leq z \leq 1$.
+(288~original galaxies; 6,624~redshifted images)
 
 %\ref{tbl:simulated_agn}
-\item \simagn: Simulated AGN host galaxies constructed using
-\hst{} images and PSFs. (96~original galaxies; 2,961~simulated AGN host
-galaxies)
+\item \simagn: Simulated AGN host galaxies constructed using \hst{} images and
+PSFs. (96~original galaxies; 2,961~images of simulated AGN hosts)
 
@@
 
+The technique for redshift debiasing (Section~\ref{sec:debiasing}) requires
+consistent measurements of the galaxy surface brightness. For both the
+\redshifted{} calibration images and the \hst{} images which have their
+morphologies corrected, we calculate the mean surface brightness $\mu$ within the
+:w
+effective radius ($R_e$) as:
+
+\begin{equation}
+\mu = m + 2.5*\log_{10}{(2 \times (b/a) \times \pi R_e^2 )}.
+\label{eqn:surface_brightness}
+\end{equation}
+
+All photometric parameters are taken from \sextractor. For the \ferengi{}
+galaxies, $m$ is {\tt MAG\_AUTO} in the \Iband{} band, $(b/a)$ is the galaxy
+ellipticity (the profile RMS along the semi-major and -minor axes), and $R_e$
+is the 50\% {\tt FLUX\_RADIUS} converted into arcsec \citep{mel16}. For the \hst{} galaxies in the \main{} sample,
+the parameters are identical except that we use {\tt MAG\_BEST} instead of
+{\tt MAG\_AUTO} \citep{gri12} in either the \Iband, \iband, or \zband{} bands, depending 
+on the available imaging (Table~\ref{tbl:gzh_numbers}).
+
 \section{GZH interface and classifications}\label{sec:interface}
@@
 \caption{Flowchart of the questions presented to GZH classifiers, labeled with
-the corresponding Task numbers. Tasks in the decision tree are color-coded by
-tier level: Gray-colored Tasks are 1$^\mathrm{st}$-tier questions which are
+the corresponding task numbers. Tasks in the decision tree are color-coded by
+tier level: Gray-colored tasks are 1$^\mathrm{st}$-tier questions which are
 asked in every classification. Tasks colored green, blue, purple, and pink
@@
 
-In GZH, the redshift range is large enough that cosmological
-evolution of the types and morphologies of galaxies is expected for the \hst{}
-sample. As a result, the previous methods of correcting for
-redshift-dependent bias do not work. In addition, the effects of band shifting
-will change the images even more across these redshift ranges.
+In GZH, the redshift range is large enough that cosmological evolution of the
+types and morphologies of galaxies is expected for the \hst{} sample. In
+addition, the effects of band shifting will change the images even more across
+these redshift ranges. As a result, the previous methods of correcting for
+redshift-dependent bias do not work.
 
@@
 they would appear observed at a variety of redshifts.  The input images are
-from the SDSS \citep{yor00,str02}.  The sample consists of 288~nearby galaxies
+from the SDSS \citep{yor00,str02}.  The sample consists of 288~well-resolved galaxies
 at $z<0.013$. The galaxies spanned a variety of morphologies (as selected by
@@
 \includegraphics[width=0.5\textwidth]{figures/sb_redshift.pdf}
-\caption{Surface brightness as a function of redshift for 3,950~\ferengi{}
-images and the 102,548~galaxies in the ACS sample with measured $\mu$ and $z$
-values. The color histogram shows the number of \ferengi{} images as a function
-of $\mu$ and $z_{\rm sim}$. White contours show counts for the full ACS sample,
-with contours starting at $N=1000$ and separated by intervals of 1000 up to
-7000.} 
+\caption{Surface brightness as a function of redshift for 3,449~\ferengi{}
+images and the 102,548~\main{} galaxies with measured $\mu$ and $z$ values. The
+color histogram shows the number of \ferengi{} images as a function of $\mu$
+and $z_{\rm sim}$. White contours show counts for the galaxies in the \main{}
+sample, with the outermost contour starting at $N=1500$ and separated by
+intervals of 1500.} 
 \label{fig:sb_redshift}
@@
 only two parameters as a simple model of the effect of redshift brightness on classification: the
-$i$-band surface brightness ($\mu_\mathrm{i}$; intrinsic) and redshift ($z$;
+surface brightness ($\mu$; intrinsic) and redshift ($z$;
 extrinsic).
@@
 Figure~\ref{fig:zeta_mu} examines the results of fitting the \ferengi{} images
-with Equation~\ref{eqn:fzeta}. Interestingly, the correction is only a weak
-function of surface brightness. Higher-surface brightness galaxies have on
-average slightly stronger corrections, possibly because these galaxies have
-larger $f_\textrm{features}$ values at high redshifts. Low surface brightness
-galaxies are more likely to begin low and remain low; the bounded nature of the
-dropoff (and variance among the individual voters) means that the average
-magnitude of $\zeta$ will be lower.
+with Equation~\ref{eqn:fzeta}. This fit only includes galaxies where
+\sextractor{} robustly measured the photometry in all images between
+$0.3<z_\mathrm{sim}<1.0$ (such that $\sigma_{M_I}<1.0$~mag; \citealt{mel16}). Interestingly, the
+derived correction is only a very weak function of surface brightness.
+Higher-surface brightness galaxies have on average slightly stronger
+corrections, possibly because these galaxies have larger $f_\textrm{features}$
+values at high redshifts. Low surface brightness galaxies are more likely to
+begin low and remain low; the bounded nature of the dropoff (and variance among
+the individual voters) means that the average magnitude of $\zeta$ will be
+lower.
 
@@
 ($-10<\log(\zeta)<10$) and sufficient points to fit each function (37~original
-galaxies, each artificially redshifted to create a total of 296~images).}
+galaxies, each artificially redshifted in eight bins over a range from $0.3\lesssim z_\mathrm{sim}\lesssim1.0$).}
 \label{fig:zeta_mu}
@@
 a function of surface brightness. The best-fit parameters to the linear fit
-(from least-squares optimization) are $\zeta_0=0.75$, $\zeta_1=-.04$. To make the
+(from least-squares optimization) are $\zeta_0=0.50$, $\zeta_1=-0.03$. To make the
 final debiased correction, the simple exponential form of
@@
 \includegraphics[width=\textwidth]{figures/p_vs_p_SB_redshift.pdf}
-\caption{Effects of redshift bias in 3,950~images in the \ferengi{} sample.
+\caption{Effects of redshift bias in 3,449~images in the \ferengi{} sample.
 Each point \emph{in a given redshift and surface brightness bin} represents a
@@
 
-Figure~\ref{fig:f_vs_f} shows the change in \ffeatures{} for the \ferengi{}
-galaxies relative to their lowest simulated redshift. This analysis only uses
-galaxies whose lowest simulated redshift image was $z_\mathrm{sim}=0.3$ and
-with detectable surface brightness measurements from \sextractor{} \citep{mel16}; this includes
-3,950 of the total 6,466~images originally processed. For each simulated
-redshift value \zsim{} at a fixed surface brightness $\mu$, \ffeaturesz, the
-value measured at that simulated redshift, is plotted against \ffeaturesrest,
-the value measured for the same galaxy at \zsim$=0.3$.
+Figure~\ref{fig:f_vs_f} shows the change in \ffeatures{} as a function of their
+lowest simulated redshift for the 3,449~\ferengi{} images with robust photometric
+measurements across the full range of redshifts.  For each simulated redshift
+value \zsim{} at a fixed surface brightness, \ffeaturesz{} is the value
+measured at that simulated redshift. We plot \ffeaturesz{} against \ffeaturesrest, the
+value measured for the same galaxy at \zsim$=0.3$.
 
@@
 \hline 
-Correctable                        & 1,884   & 48\% \\
-Lower-limit                        & 1,986   & 50\% \\
-NEI                                & 80      &  2\%\\
-Total                              & 3,950   & 100\% \\
+Correctable                        & 1,690   &  49\% \\
+Lower-limit                        & 1,678   &  49\% \\
+NEI                                & 81      &   2\%\\
+Total                              & 3,449   & 100\% \\
 \hline \hline
@@
 \caption{Correctable fractions for the top-level task in GZH, split by survey.}\label{tbl:hubble_debiasable}
-\begin{tabular}{lcrrrrrrr}
+\begin{tabular}{lcrrrrr|r}
 \hline\hline
-                                   & Correction type & AEGIS   & COSMOS & GEMS & GOODS-N & GOODS-S    & SDSS    & Total \\
+                                   & Correction type & AEGIS   & COSMOS & GEMS  & GOODS-N & GOODS-S  &  Total  \\
+                                   &                 &         &        &       & 5-epoch & 5-epoch  &         \\
 \hline
-correctable                        & 0               & 1,654   & 15,170 & 1,837 & 993    & 835     	& 0       & 20,489\\
-lower-limit                        & 1               & 1,917   & 26,113 & 2,423 & 1,385  & 1,282   	& 0       & 33,120\\
-no correction needed ($z \le 0.3$) & 2               & 955     & 11,926 & 1,175 & 415    & 400     	& 37,545  & 52,416\\ 
-not enough information (NEI)       & 3               & 2,847   & 34,511 & 3,308 & 2,535  & 2,523   	& 0       & 45,724\\
-no redshift information            & 4               & 1,134   & 5,088  & 561   & 687    & 102   		& 14,316  & 21,888\\
+correctable                        & 0               & 2,908   & 21,169 & 2,802 & 1,459   & 1,189    &  29,527 \\
+lower-limit                        & 1               &   833   &  5,169 & 1,021 & 1,377   & 1,267    &   9,667 \\
+no correction needed ($z \le 0.3$) & 2               &   955   & 10,870 & 1,175 &   415   &   400    &  13,815 \\ 
+not enough information (NEI)       & 3               & 2,677   & 43,058 & 3,559 & 2,077   & 2,184    &  53,555 \\
+no redshift information            & 4               & 1,134   &  4,688 &   530 &   687   &   102    &   7,141 \\
 \hline
-total                              &                 & 8,507   & 92,808 & 9,304 & 6,015  & 5,142   	& 51,861  & 173,637\\
+total                              &                 & 8,507   & 84,954 & 9,087 & 6,015   & 5,142    & 113,705 \\
 \hline\hline
@@
 
-The catalog for GZH includes morphological data for 181,101~images
-(generated from a total of 150,771~unique galaxies). The full table can be
+The catalog for GZH includes morphological data for 189,149~images
+(generated from a total of 145,741~unique galaxies). The full table can be
 accessed at \url{http://data.galaxyzoo.org}. The online data also includes a
@@
 Section \ref{sec:data}. 
+% 113705+6144+30339-4447 = 145,741
+% main + goods_shallow + stripe82_coadd - goods_union
 
@@
 
-\noindent In rare cases ($<1\%$ of the sample), this requirement resulted in
+\noindent In rare cases ($1.2\%$ of the \main{} sample), this requirement resulted in
 negative vote fractions for \fsmooth; these were cases in which the
@@
 corrected through debiasing (Section~\ref{ssec:zeta_results}), if possible.
-0~=~correctable, 1~=~lower-limit ($f_{raw}$ --- $f_{adj}$ is not
-single-valued), 2~=~uncorrected ($z_{\rm gal} < 0.3$), 3~=~uncorrected
+0~=~correctable, 1~=~lower-limit ($f_\mathrm{raw}$ --- $f_\mathrm{adj}$ is not
+single-valued), 2~=~uncorrected ($z < 0.3$), 3~=~uncorrected
 (insufficient \ferengi{} galaxies in this $z$-$\mu$ bin), 4~=~uncorrected (no
@@
 as well as at \url{http://data.galaxyzoo.org}. The complete version includes
-data for 118,425~galaxies and morphological information for all tasks in the
+data for 113,705~galaxies and morphological information for all tasks in the
 tree. A subset of the information is shown here to illustrate form and
@@
 \end{deluxetable*}
-
-% Why are some values negative?
-% Why are most of the full-depth GOODS weighted fractions identical to the raw fractions?
 
@@
 \tablewidth{0pc}
-\tablecaption{GZH morphological classifications for color-faded Hubble images\label{tbl:catalog_faded}} 
+\tablecaption{GZH morphological classifications for color-faded \hst{} images\label{tbl:catalog_faded}} 
 \tabletypesize{\scriptsize}
@@
 \tablewidth{0pc}
-\tablecaption{GZH morphological classifications for color-inverted Hubble images\label{tbl:catalog_recolored}} 
+\tablecaption{GZH morphological classifications for color-inverted \hst{} images\label{tbl:catalog_recolored}} 
 \tabletypesize{\scriptsize}
@@
 \startdata
-AHZC000001	&   20000002	&   COSMOS	&   1	&   168	&   0.615   &   0.664   &   0.160   &  0.663   &  0.271   &  0.775  & 0  \\
-AHZC000003	&   20000004	&   COSMOS	&   0	&   235	&   0.333   &   0.364   &   0.002   &  0.002   &  0.063   &  0.063  & 0  \\
-AHZC000004	&   20000006	&   COSMOS	&   3	&   316	&   0.235   &   0.252   & $-0.011$  &  0.252   &  $-$	  &  $-$    & 1  \\
-AHZC00000z	&   20000102	&   COSMOS	&   1	&   207	&   0.755   &   0.757   &   0.272   &  0.756   &  0.249   &  0.796  & 0  \\
-AHZC000010	&   20000104	&   COSMOS	&   2	&   158	&   0.843   &   0.882   &   0.936   &  0.881   &  $-$	  &  $-$    & 1  \\
+AHZC000001  &   20000002      &   COSMOS      &   1    168  &   0.615   &   0.664   &   0.160   &  0.663   &  0.271   &  0.775  & 0  \\
+AHZC000003  &   20000004      &   COSMOS      &   0    235  &   0.333   &   0.364   &   0.002   &  0.002   &  0.063   &  0.063  & 0  \\
+AHZC000004  &   20000006      &   COSMOS      &   3    316  &   0.235   &   0.252   & $-0.011$  &  0.252   &  $-$     &  $-$    & 1  \\
+AHZC00000z  &   20000102      &   COSMOS      &   1    207  &   0.755   &   0.757   &   0.272   &  0.756   &  0.249   &  0.796  & 0  \\
+AHZC000010  &   20000104      &   COSMOS      &   2    158  &   0.843   &   0.882   &   0.936   &  0.881   &  $-$     &  $-$    & 1  \\
 $\ldots$    \\
@@
 AHZ5000005  &   587730845812524122  &   SDSS    &     2 &   47  &   0.766   &    0.812  &   1.038   &   0.810 &  1  \\
-AHZ5000006  &   587730845812654984  &   SDSS    &     2 &   42  &   0.5	    &    0.542  &   0.680   &   0.541 &  0  \\
+AHZ5000006  &   587730845812654984  &   SDSS    &     2 &   42  &   0.500   &    0.542  &   0.680   &   0.541 &  0  \\
 AHZ5000007  &   587730845812655541  &   SDSS    &     2 &   41  &   0.488   &    0.526  &   0.697   &   0.525 &  0  \\
 AHZ5000008  &   587730845812720365  &   SDSS    &     2 &   53  &   0.792   &    0.84   &   1.050   &   0.839 &  1  \\
-AHZ5000009  &   587730845812720640  &   SDSS    &     4 &   43  &   0.0	    &    0.0    &   0.0	    &   0.0   &  0  \\
+AHZ5000009  &   587730845812720640  &   SDSS    &     4 &   43  &   0.000   &    0.0    &   0.000   &   0.0   &  0  \\
 AHZ500000a  &   587730845812720699  &   SDSS    &     2 &   40  &   0.425   &    0.478  &   0.588   &   0.477 &  0  \\
@@
 monitored.  We stress that the details of any selection process will vary based
-on the particular science case; for example, \citet{bam09,ski09,sme15} demonstrate
-the advantages of using the vote fractions directly as weights rather than
-applying discrete thresholds.
-
-To select galaxies of a morphological type identified with a particular Task, a
-cut is placed on the vote fraction for that Task ($f_{\rm task}$), \emph{as
-well as} the vote fractions for the Tasks preceding it, because of the
+on the particular science case; for example, \citet{bam09,ski09,sme15} all
+demonstrate the advantages of using the vote fractions directly as weights
+rather than applying discrete thresholds.
+
+To select galaxies of a morphological type identified with a particular task, a
+cut is placed on the vote fraction for that task ($f_{\rm task}$), \emph{as
+well as} the vote fractions for the tasks preceding it, because of the
 dependency induced by the decision-tree structure. For example, to select
@@
 A sample of barred disk galaxies is created by applying cuts on the previous
-tasks as listed in Table~\ref{tbl:thresholds}. 11,049 ``bar candidates'' are
-galaxies for which asking the bar question is meaningful, and were selected by
-applying the cuts $N_{bar} \ge 20$, $f_{\rm features}>0.23, f_{\rm clumpy,no} >
-0.30,$ and $f_{edgeon,no}>0.25$. These galaxies are featured, non-clumpy,
-non-edge~on galaxies. Of these, a pure sample of 730~barred disks was
-identified by applying a cut of \fbar$>0.7$. A subsample of 50~galaxies were
-visually inspected and 94\% were found to contain strong bars. A complete
-sample of strong and weak bars was created by applying a cut of \fbar$>0.3$.
-This sample contained 3,218~galaxies, 86\% of which were found to contain weak
-or strong bars through visual inspection in a subsample of 50.
+tasks as listed in Table~\ref{tbl:thresholds}. We identify 11,049 ``bar
+candidates'' as disk galaxies for which bar identification can be attempted in
+GZH. These galaxies were selected by applying the cuts $N_{bar} \ge 20$,
+$f_{\rm features}>0.23, f_{\rm clumpy,no} > 0.30,$ and $f_{edgeon,no}>0.25$.
+These galaxies are featured, non-clumpy, non-edge~on galaxies. Of these, a pure
+sample of 730~barred disks was identified by applying a cut of \fbar$>0.7$. A
+subsample of 50~galaxies were visually inspected and 94\% were found to contain
+strong bars. A complete sample of strong and weak bars was created by applying
+a cut of \fbar$>0.3$.  This sample contained 3,218~galaxies, 86\% of which were
+found to contain weak or strong bars through visual inspection.
 
@@
 Universe evolves since $z\sim 1.5$ \citep{elm09}, suggesting that clumps
-coalesce over time to form the modern bulges of disk galaxies. GZH added a
-``clumpy'' path to the decision tree for the purpose of both identifying clumps
+coalesce over time to form the modern bulges of disk galaxies. GZH includes a
+``clumpy'' path in the decision tree for the purposes of identifying clumps
 and investigating their evolution with redshift.
@@
 however. The fraction of objects identified as stars or artifact is also much
-higher in the Hubble imaging. By plurality votes, these encompass only
+higher in the \hst{} imaging. By plurality votes, these encompass only
 $\sim0.1\%$ of images in SDSS \citep{wil13}, but 6\% of images in GZH.
@@
 which is somewhat surprising (but encouraging) considering the known limits
-of assigning galaxy morphology based only on a single \sersic{} fit.
+of assigning galaxy morphology based only on a single \sersic{} parameter.
 
@@
 morphologies to \fodd{} in GZH. Measurement of \fodd{} excludes galaxies
-dominated by lenses or dust lanes ($<1\%$ of the total), which are GZH
+labeled as ``odd'' due to lenses or dust lanes ($<1\%$ of the total), which are GZH
 categories not expected to correlate with larger-scale structural parameters.}
@@
 automatic techniques. A more accurate selection of irregular morphologies in
-GZH should likely use some combination of \fbest, \fclumpy, and \fodd.
+GZH should use a weighted combination of \fbest, \fclumpy, and \fodd.
 
@@
 
-This paper presents the catalog release for the Galaxy Zoo: Hubble project,
+This paper presents the catalog release for the Galaxy Zoo Hubble project,
 which uses crowdsourced visual classifications to measure galaxy morphologies.
@@
 CANDELS collaboration; Simmons et al., submitted). The final sample includes
-classifications for 181,101~images generated from 150,771~unique galaxies.
+classifications for 189,149~images generated from 145,741~unique galaxies
+(of which 115,402 are in \hst{} Legacy imaging).
+
 Galaxies were selected from a brightness-limited sample from multiple Legacy
-surveys using the Advanced Camera for Surveys on the Hubble Space Telescope,
+surveys using the Advanced Camera for Surveys on the \hubble,
 including AEGIS, GEMS, GOODS-N, GOODS-S, and COSMOS. The catalog also includes
-classifications for 51,861~SDSS images from Stripe~82 at
-relatively low redshift; these serve both as a low-redshift anchor for
+classifications for SDSS images from Stripe~82 at $z<0.25$; these images
+serve both as a low-redshift anchor for
 cosmological studies and a potential comparison for the different epochs of
@@
 paper confirms the decrease in observed bar fraction with increasing redshift
-\citep{mel14} and identifies a new way for selecting clumpy galaxies as a
+and identifies a new way of selecting clumpy galaxies as a
 function of clump multiplicity.
@@
 \acknowledgments
+KW, MG, CS, MB, and LF gratefully acknowledge support from the US National Science
+Foundation Grant AST1413610. KS gratefully acknowledges support from Swiss
+National Science Foundation Grant PP00P2\_138979/1. The development and hosting of 
+Galaxy Zoo Hubble was supported by a grant from the Alfred P. Sloan Foundation. 
+The Zooniverse acknowledges support from a Google Global Impact Award.
 
@@
 was used to create the JPG images. Figure~\ref{fig:sankey} was generated with
-\url{http://sankeymatic.com/}.
-
-The development and hosting of Galaxy Zoo Hubble was supported by a grant from
-the Alfred P. Sloan Foundation. The Zooniverse acknowledges support from a
-Google Global Impact Award. KS gratefully acknowledges support from Swiss
-National Science Foundation Grant PP00P2\_138979/1.
+\url{http://sankeymatic.com/}. \citet{hol05} provided invaluable assistance
+in intepreting \sextractor{} output.
 
@@
 \begin{table}
-\caption{Correctable fractions for the top-level task in GZH in the GOODS shallow-depth (2-epoch) images. \label{tbl:goods_shallow_categories}}
-\begin{tabular}{lrrrrrrrr}
+\caption{Correctable fractions for the top-level task in GZH in the GOODS
+shallow-depth (2-epoch) images. \label{tbl:goods_shallow_categories}}
+\begin{tabular}{lrr|r}
 \hline\hline
@@
 \hline
-Correctable                        & 748     & 514     & 1,262 \\
-Lower limit                        & 526     & 1,143   & 1,669 \\
-No Correction Needed ($z \le 0.3$) & 267     & 267     & 534   \\ 
-NEI                                & 851     & 2,670   & 3,521 \\
-No Redshift Information            & 159     & 319     & 478   \\
-Total                              & 2,551   & 4,913   & 7,464 \\
+correctable                        & 1,051   &   730   & 1,781 \\
+lower-limit                        &   131   &   334   &   465 \\
+no correction needed ($z \le 0.3$) &   267   &   267   &   534 \\ 
+NEI                                &   943   & 2,078   & 3,021 \\
+no redshift information            &   159   &   184   &   343 \\
+\hline
+total                              & 2,551   & 3,593   & 6,144 \\
 \hline\hline
@@
 images. The 11,157 full depth 5-epoch images are used in the \main{} catalog; the
-classifications for the 7,464 \goods{} images are provided as a
+classifications for the 6,144 \goods{} images are provided as a
 supplementary table. This section analyzes the effect of image depth on the
@@
 
-Of the 11,157 galaxies in the GOODS-N and GOODS-S full depth sample, 4,461 of
-these are in the shallow-depth sample. Figure~\ref{fig:shallow_vs_full} shows a
+Of the 11,157 galaxies in the GOODS-N and GOODS-S full depth sample, 4,461
+are also in the shallow-depth sample. Figure~\ref{fig:shallow_vs_full} shows a
 strong correlation between \ffeatures{} for both sets of images. The mean
@@
 75\% of the sample would not change morphology. Of the remaining 25\% that
-would change morphology, only 0.3\% (representing 10 galaxies total)
-drastically change morphology from smooth to featured or vice versa, while the
-rest would transition to or from the ``intermediate'' morphology. Details can
+would change morphology, only 0.3\% (10~galaxies)
+drastically change morphology either from smooth to featured or vice versa, while the
+rest transition to or from the ``intermediate'' morphology. Details can
 be seen in Table~\ref{tbl:shallow_to_full_stats} and examples of images
@@
 \hline\hline
-shallow to full morphology    & N       & \%       & $<\Delta f>$ & $<z>$ \\
+                              & $N$     & \%       & $<\Delta f>$ & $<z>$   \\
 \hline
-smooth to smooth              & 758     & 17.0     & -0.00        &  0.69\\
-smooth to intermediate        & 367     & 8.2      & 0.18         &  0.69\\
-smooth to featured            & 7       & 0.2      & 0.76         &  0.57\\ 
-intermediate to smooth        & 214     & 4.8      & -0.18        &  0.65\\
+smooth to smooth              & 758     & 17.0     & $-$0.00      &  0.69   \\
+smooth to intermediate        & 367     & 8.2      &    0.18      &  0.69   \\
+smooth to featured            & 7       & 0.2      &    0.76      &  0.57   \\ 
+intermediate to smooth        & 214     & 4.8      & $-$0.18      &  0.65   \\
 intermediate to intermediate  & 2,303   & 51.6     &    0.01      &  0.78   \\
-intermediate to featured      & 168     & 3.8      & 0.19         &  0.83\\
-featured to smooth            & 3       & 0.1      & -0.74        &  0.71\\
-featured to intermediate      & 337     & 7.6      & -0.18        &  0.68\\
-featured to featured          & 301     & 6.8      & -0.05        &  0.71\\
-
+intermediate to featured      & 168     & 3.8      &    0.19      &  0.83   \\
+featured to smooth            & 3       & 0.1      & $-$0.74      &  0.71   \\
+featured to intermediate      & 337     & 7.6      & $-$0.18      &  0.68   \\
+featured to featured          & 301     & 6.8      & $-$0.05      &  0.71   \\
+\hline
 Total                         & 4,461   & 100      &              &         \\
@@
 \caption{Similar to Figure~\ref{fig:f_vs_f}, showing effects of redshift bias
-for 3,950~images in the \ferengi{} sample. Each point in a given redshift
+for 3,449~images in the \ferengi{} sample. Each point in a given redshift
 and surface brightness bin represents a unique galaxy. The $y$-axis in each
@@
 were considered ``correctable'', which is not sufficient to compute a $\zeta$
-function applicable to the Hubble data.   \label{tbl:ferengi_bar_corrections}}
+function applicable to the \hst{} data.   \label{tbl:ferengi_bar_corrections}}
 \begin{tabular}{lrr}
 \hline \hline
-				                   & N       & \% \\
+                                   & $N$    & \%        \\
 \hline 
@@
 Lower-limit                        & 483    & 12\%      \\
-NEI                                & 2,803     & 71\%\\
+NEI                                & 2,803  & 71\%      \\
+\hline
 Total                              & 3,950  & 100\%     \\

### 2016-05-28 writeup/gz_hubble_data.tex
Fix last sig fig on WMAP9 parameters. Closes #162.

@@
 This paper assumes the WMAP9 cosmological parameters of
-$(\Omega_m,\Omega_\Lambda,h)=(0.282,0.718,0.697)$ \citep{hin13}.
+$(\Omega_m,\Omega_\Lambda,h)=(0.286,0.714,0.693)$ \citep{hin13}.
 
@@
 applicable, these pages contained further information regarding image
-modifications. \citet{sim14} uses similarly-processed images for reliable
-identification of bulgeless galaxies using SDSS data.
+modifications. \citet{sim13} uses the simulated AGN host galaxy images for
+more reliable identification of bulgeless galaxies hosting AGN in SDSS data.
 

### 2016-05-28 writeup/gz_hubble_data.tex
Science motivation for studying bars. Closes #128.

@@
 of $\Delta e = 0.5$. Figure~\ref{fig:exampleFERENGI} shows several examples
-of the effects of ``losing'' spiral/disc features with increasing redshift
+of the effects of ``losing'' spiral/disk features with increasing redshift
 for two galaxies with no evolution corrections ($e=0$); as the signal-to-noise ratio in the images
@@
 
-A sample of barred disk galaxies is created by applying cuts on the previous
-tasks as listed in Table~\ref{tbl:thresholds}. We identify 11,049 ``bar
-candidates'' as disk galaxies for which bar identification can be attempted in
-GZH. These galaxies were selected by applying the cuts $N_{bar} \ge 20$,
+Bars in galaxies are a trace of the dynamical state of the disk
+\citep[\eg,][]{com09a,ath12}. Disks which have significant vertical motions
+typically do not form bars (with the exception of tidally triggered bars;
+\citealt{bar91}), but once a disk settles to a thin, dynamically cool state,
+the formation of bars proceeds quickly. Most theoretical predictions show that
+bars are long-lasting in the absence of significant galaxy interactions
+\citep{ath05}, so the fraction of bars in disk galaxies can measure the
+dynamical maturity of that population. For this reason, tracking the fraction
+of bars in disk galaxies as a function of redshift has attracted significant
+interest since the first resolved images of high redshift galaxies were
+obtained \citep[\eg,][]{abr99,elm04,jog04,she08a, mel14,sim14}.
+
+We create a sample of barred disk galaxies in GZH by applying cuts on the previous
+tasks in Table~\ref{tbl:thresholds}. We first identify 11,049 ``bar
+candidates,'' which are disk galaxies that are sufficiently face-on to attempt
+visual identification of a bar. These galaxies were selected by applying the cuts $N_{bar} \ge 20$,
 $f_{\rm features}>0.23, f_{\rm clumpy,no} > 0.30,$ and $f_{edgeon,no}>0.25$.
@@
 results from GZH indicate that if features are reliably identified, the bar is
-always visible; for galaxies at increasing redshifts, the discs fade first but
+always visible; for galaxies at increasing redshifts, the disks fade first but
 the galactic bar remains visible \citep{mel16}. As a result, we do \emph{not}
 recommend using an evolving cut on \fbar{} as a function of redshift for the
-selection of barred discs.
+selection of barred disks.
 

### 2016-05-29 writeup/gz_hubble_data.tex
Funding source for TM, re #69.
various typos corrected; changed bounding box for figure 8

--- 2016-05-27 writeup/gz_hubble_data.tex
@@
 morphologies corrected, we calculate the mean surface brightness $\mu$ within the
-:w
 effective radius ($R_e$) as:
@@
 would presumably be easier to identify; \citet{bam09} and \citet{wil13} found
-changes in \ffeatures{} depending on a combination of physical size and
+changes in \ffeatures{} depend on a combination of physical size and
 absolute magnitude. To simplify our model, we subsume these into a single
@@
 \center
-\includegraphics[width=0.50\textwidth]{figures/zeta_mu.pdf}
+\includegraphics[width=0.5\textwidth]{figures/zeta_mu.pdf}
 \caption{All fits for the \ferengi{} galaxies of the vote fraction dropoff
@@
 \ffeaturesrest. We quantify this by measuring the slope of the best-fit
-polynomical; regions of the bins with a slope less than 0.4 are considered
+polynomial; regions of the bins with a slope less than 0.4 are considered
 \emph{not} one-to-one, and therefore \ffeaturesz{} cannot be boosted to its
@@
 surface brightness and redshift. In each unclassifiable (shaded blue) $z$,$\mu$ bin, the spread of
-intrinsic values of \ffeaturesrest{} for four ranges of observed \ffeatures is computed.
+intrinsic values of \ffeaturesrest{} for four ranges of observed \ffeatures{} is computed.
 The range of intrinsic values is defined as the inner 80\% of the data,
@@
 CANDELS \citep{kar15}.  There are only eight galaxies that were strongly
-boosted (\ffeatures$<0.2$ and \fbest$>0.5$) in GZH and also appears in the
+boosted (\ffeatures$<0.2$ and \fbest$>0.5$) in GZH and also appear in the
 CANDELS expert sample. Of those eight galaxies, \citet{kar15} classify 5 as
@@
 number of classifiers who answered that question. For each unique answer, $\tt fraction$
-is the fraction of classifiers who selected that answer ($\rm N_{answer}/N_{votes}$, and
+is the fraction of classifiers who selected that answer ($\rm N_{answer}/N_{votes}$), and
 $\tt weighted$ is the weighted fraction, which takes into account overall
@@
 
-The comparison and analysis of the GZH morphologies is done a set of matched,
+The comparison and analysis of the GZH morphologies is done on a set of matched,
 volume-limited samples at $z<1.0$ and $m_{I|i|z} < 22.5$~mag.  The redshift and
@@
 Figure~\ref{fig:comparisons_odd} analyzes the same sets of matched galaxies, but
-compares the data the \fodd{} parameter in GZH to examine its correlation with
+compares the data to the \fodd{} parameter in GZH to examine its correlation with
 irregular morphologies. The relationship in this case is less clear; for the
@@
 for Task~01, which significantly reduced the goodness-of-fit for the model
-functions as compared with to the smooth/features task. Here we show an
+functions as compared to the smooth/features task. Here we show an
 example of results obtained for the bar Task. Figure~\ref{fig:f_vs_fbar}

### 2016-05-29 writeup/gz_hubble_data.tex

--- 2016-05-28 writeup/gz_hubble_data.tex
@@
 \acknowledgments
-KW, MG, CS, MB, and LF gratefully acknowledge support from the US National Science
-Foundation Grant AST1413610. KS gratefully acknowledges support from Swiss
-National Science Foundation Grant PP00P2\_138979/1. The development and hosting of 
-Galaxy Zoo Hubble was supported by a grant from the Alfred P. Sloan Foundation. 
-The Zooniverse acknowledges support from a Google Global Impact Award.
+KW, MG, CS, MB, and LF gratefully acknowledge support from the US National
+Science Foundation Grant AST1413610. KS gratefully acknowledges support from
+Swiss National Science Foundation Grant PP00P2\_138979/1. TM acknowledges
+funding from the Science and Technology Facilities Council ST/J500665/1. The
+development and hosting of Galaxy Zoo Hubble was supported by a grant from the
+Alfred P. Sloan Foundation. The Zooniverse acknowledges support from a Google
+Global Impact Award.
 
@@
 was used to create the JPG images. Figure~\ref{fig:sankey} was generated with
-\url{http://sankeymatic.com/}. \citet{hol05} provided invaluable assistance
+\url{http://sankeymatic.com/}. \citet{hol05} provided valuable assistance
 in intepreting \sextractor{} output.

### 2016-05-29 writeup/gz_hubble_data.tex
Fix affiliation for Arfon.

@@
     Ross Hart\altaffilmark{3}, 
-    Tom Melvin\altaffilmark{5}, 
+    Thomas Melvin\altaffilmark{5}, 
     Michael Parrish\altaffilmark{15}, 
@@
     R.J. Smethurst\altaffilmark{4}, 
-    Arfon M. Smith\altaffilmark{5,15,17}
+    Arfon M. Smith\altaffilmark{4,15,17}
 }

### 2016-05-29 writeup/gz_hubble_data.tex
Expand captions on Figures A2-A4. Closes #167.

@@
 
-\subsection{Comparing shallow and full depth morphologies}
+\subsection{Comparing shallow and full depth morphologies}\label{ssec:depth_comparison}
 
@@
 
-\caption{Galaxies whose shallow images were classified as smooth and full depth
-images were classified as smooth, intermediate, or featured.}
+\caption{Example images of GOODS galaxies that compare GZH morphological
+classifications between their 2-epoch and 5-epoch imaging.  The top set (a)
+were classified as ``smooth'' in both the 2- and 5-epoch imaging. The
+middle set (b) was classified as ``smooth'' in the 2-epoch imaging and as
+intermediate between ``smooth'' and ``featured'' in the 5-epoch imaging. The
+bottom set (c) was classified as ``smooth'' in the 2-epoch imaging and
+``featured'' in the 5-epoch imaging.}
 \label{fig:shallow_smooth}
@@
 
-\caption{Galaxies whose shallow images were classified as intermediate and full
-depth images were classified as smooth, intermediate, or featured.}
+\caption{Similar to Figure~\ref{fig:shallow_smooth}. The top set (a) were
+classified as ``intermediate'' in the 2-epoch imaging and ``smooth'' in the
+5-epoch imaging. The middle set (b) was classified as intermediate in both the
+2- and 5-epoch imaging. The bottom set (c) was classified as ``intermediate''
+in the 2-epoch imaging and ``featured'' in the 5-epoch imaging.}
 \label{fig:shallow_intermediate}
@@
 
-\caption{Galaxies whose shallow images were classified as featured and full
-depth images were classified as smooth, intermediate, or featured.}
+\caption{Similar to Figure~\ref{fig:shallow_smooth}. The top set (a) were
+classified as ``featured'' in the 2-epoch imaging and ``smooth'' in the 5-epoch
+imaging (there were only six such images in the sample). The middle set (b) was
+classified as ``featured'' in the 2-epoch imaging and ``intermediate'' in the
+5-epoch imaging. The bottom set (c) was classified as ``featured'' in both the
+2- and 5-epoch imaging.}
 \label{fig:shallow_featured}

### 2016-05-29 writeup/gz_hubble_data.tex
Fixed caption on Table 3. Closes #164.
References to Kaviraj+14a,b

@@
 hierarchical assembly model \citep{sil12}. The structure of individual galaxies
-is affected by their merger history \citep{too72,ste02,hop10}, local
+is affected by their merger history \citep{too72,ste02,hop10,kav14,kav14a}, local
 environment \citep[\eg, the morphology-density relation;][]{dre80}, initial
@@
 \begin{table*}
-\caption{Correctable fractions for the top-level task in GZH, split by survey.}\label{tbl:hubble_debiasable}
+\caption{Number of correctable galaxies for the top-level task in GZH, split by \hst{} survey.}\label{tbl:hubble_debiasable}
 \begin{tabular}{lcrrrrr|r}

### 2016-05-29 writeup/gz_hubble_data.tex
Adding full address to all affiliations.

@@
 
-\altaffiltext{1}{School of Physics and Astronomy, University of Minnesota, USA}
-\altaffiltext{2}{Department of Physics and Astronomy, University of Kentucky, USA}
-\altaffiltext{3}{School of Physics and Astronomy, University of Nottingham, UK}
-\altaffiltext{4}{Oxford Astrophysics, University of Oxford, UK}
-\altaffiltext{5}{Institute of Cosmology and Gravitation, University of Portsmouth, UK}
+\altaffiltext{1}{School of Physics and Astronomy, University of Minnesota, 116 Church St. SE, Minneapolis, MN 55455, USA}
+\altaffiltext{2}{Department of Physics and Astronomy, University of Kentucky, 505 Rose St., Lexington, KY 40506, USA}
+\altaffiltext{3}{School of Physics and Astronomy, The University of Nottingham, University Park, Nottingham, NG7 2RD, UK}
+\altaffiltext{4}{Oxford Astrophysics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK}
+\altaffiltext{5}{Institute for Cosmology and Gravitation, University of Portsmouth, Dennis Sciama Building, Burnaby Road, Portsmouth, PO1 3FX, UK}
 \altaffiltext{6}{SEPnet, South East Physics Network, UK}
-\altaffiltext{7}{Center for Astrophysics and Space Sciences, UC San Diego, USA}
-\altaffiltext{8}{Department of Mathematics and Science, Wheelock College, USA}
-\altaffiltext{9}{Kavli Institute for the Physics and Mathematics of the Universe (WPI), Japan}
-\altaffiltext{10}{Infrared Processing and Analysis Center, California Institute of Technology, USA}
-\altaffiltext{11}{Department of Astronomy and Astrophysics, Pennsylvania State University, USA}
-\altaffiltext{12}{Centre for Astrophysics, University of Hertfordshire, UK}
-\altaffiltext{13}{European Southern Observatory, Santiago, Chile}
-\altaffiltext{14}{Department of Astronomy, Yale University, USA}
-\altaffiltext{15}{Adler Planetarium, USA}
-\altaffiltext{16}{Institute for Astronomy, ETH Z\"urich, Switzerland}
+\altaffiltext{7}{Center for Astrophysics and Space Sciences, Department of Physics, University of California, San Diego, CA 92093, USA}
+\altaffiltext{8}{Department of Mathematics and Science, Wheelock College, Boston, MA 02215, USA}
+\altaffiltext{9}{Kavli Institute for the Physics and Mathematics of the Universe (WPI), Todai Institutes for Advanced Study, The University of Tokyo, Kashiwa 277-8583, Japan}
+\altaffiltext{10}{Infrared Processing and Analysis Center, California Institute of Technology, Pasadena, CA 91125, USA}
+\altaffiltext{11}{Department of Astronomy \& Astrophysics, 525 Davey Lab, The Pennsylvania State University, University Park, PA 16802, USA}
+\altaffiltext{12}{Centre for Astrophysics, Science \& Technology Research Institute, University of Hertfordshire, Hatfield, AL10 9AB, UK}
+\altaffiltext{13}{European Southern Observatory, Alonso de C\'ordova 3107, Vitacura, Casilla 19001, Santiago, Chile}
+\altaffiltext{14}{Department of Astronomy, Yale University, New Haven, CT 06520, USA}
+\altaffiltext{15}{Adler Planetarium, 1300 S. Lake Shore Drive, Chicago, IL 60605, USA}
+\altaffiltext{16}{Institute for Astronomy, Department of Physics, ETH Z\"urich, Wolfgang-Pauli-Strasse 27, CH-8093 Z\"urich, Switzerland}
 \altaffiltext{17}{GitHub}

### 2016-05-29 writeup/gz_hubble_data.tex
Text changes from KLM. Closes #169.

@@
 crowdsourced visual classifications of color composite images. Images in GZH
-were selected from various \textit{Hubble Space Telescope} Legacy programs
-using the Advanced Camera for Surveys, with filters that probe the rest-frame
-optical emission from galaxies out to $z\sim1$.  The bulk of the sample is
-selected to have $m_{I814W}<23.5$ across AEGIS, COSMOS, GEMS, and 2-epoch
-exposures in GOODS-N and GOODS-S. Full-depth 5-epoch images from the GOODS
-fields are also included and have $m_{I814W}<26.8$. The median redshift of the
-combined samples is $\langle z\rangle=0.9\pm0.6$, with a tail extending out to
-$z\simeq4$. The GZH morphological data include measurements of both bulge- and
-disk-dominated galaxies, details on spiral disk structure that relate to the
-Hubble type, bar identification, and numerous measurements of clump
+were selected from various publicly-released \textit{Hubble Space Telescope}
+Legacy programs using the Advanced Camera for Surveys, with filters that probe
+the rest-frame optical emission from galaxies out to $z\sim1$.  The bulk of the
+sample is selected to have $m_{I814W}<23.5$, but goes as faint as
+$m_{I814W}<26.8$ for deep images combined over 5~epochs. The median redshift of
+the combined samples is $\langle z\rangle=0.9\pm0.6$, with a tail extending out
+to $z\simeq4$. The GZH morphological data include measurements of both bulge-
+and disk-dominated galaxies, details on spiral disk structure that relate to
+the Hubble type, bar identification, and numerous measurements of clump
 identification and geometry.  This paper also describes a new method for
@@
 
+\item The Galaxy Evolution from Morphologies and SEDs
+    \citep[GEMS;][]{rix04,cal08} survey was centered on the Chandra Deep
+    Field-South. The GEMS data covered $\sim800$~arcmin$^2$, completely surrounding
+    the area covered by GOODS-S. Images from ACS in GEMS had 1~orbit per pointing
+    for a total of 63~pointings. The exposure times were 2160 and 2286~seconds in
+    \Vband{} and \zband{}, respectively. The image resolution had a pixel scale
+    of 0.03~\arcsec/pixel. The $5\sigma$ limiting magnitude for source
+    detection was 25.7~AB in \Vband{} and 24.2~AB in \zband.
+
 \item The Cosmic Evolution Survey \citep[COSMOS;][]{sco07} covered an area of
@@
     $0.50^{\prime\prime}$ in \Iband{} was 24.7~mag.
-
-\item The Galaxy Evolution from Morphologies and SEDs
-    \citep[GEMS;][]{rix04,cal08} survey was also centered on the Chandra Deep
-    Field-South. The GEMS data covered $\sim800$~arcmin$^2$, completely surrounding
-    the area covered by GOODS-S. Images from ACS in GEMS had 1~orbit per pointing
-    for a total of 63~pointings. The exposure times were 2160 and 2286~seconds in
-    \Vband{} and \zband{}, respectively. The image resolution had a pixel scale
-    of 0.03~\arcsec/pixel. The $5\sigma$ limiting magnitude for source
-    detection was 25.7~AB in \Vband{} and 24.2~AB in \zband.
 
@@
 sample for comparison to higher-redshift galaxies (including the new
-measurments of clumpy structure), while the co-added images allow for analysis
+measurements of clumpy structure), while the co-added images allow for analysis
 of morphological properties as a function of image depth.
@@
 \caption{Screenshot of the GZH interface (\url{http:/zoo3.galaxyzoo.org}) at
-the beginning of a classification, with the classifier ready to select an answer for
-the first question in the decision tree.\label{fig:interface}}
+the beginning of classifying a random galaxy, with the classifier ready
+to select an answer for the first question in the decision
+tree.\label{fig:interface}}
 \end{figure*}
@@
 correction for redshift bias (Figure~\ref{fig:debiased_corrections}). As a
-check, highly boosted galaxies are compared to the expert classifications in
-CANDELS \citep{kar15}.  There are only eight galaxies that were strongly
-boosted (\ffeatures$<0.2$ and \fbest$>0.5$) in GZH and also appear in the
-CANDELS expert sample. Of those eight galaxies, \citet{kar15} classify 5 as
-spheroids, 2 as disks, and 1 as irregular/disky. The \fbest{} values for GZH
-are all between 0.5 and 0.6, making them intermediate disk candidates. One of
-the spheroids has a hint of extended emission to the south that may have been
-missed by the CANDELS experts, but almost all images are dim and with very low
-surface brightnesses in the ACS imaging, making positive identification
-challenging. Since the surveys use different rest-frame filters and the overlap
-sample is tiny, though, detailed comparisons between the overall morphologies
-are highly difficult.
+check, we compare morphologies of highly boosted galaxies to the expert visual
+classifications in CANDELS \citep{kar15}.  Only nine galaxies that
+were strongly boosted (\ffeatures$<0.25$ and \fbest$>0.50$) in GZH also
+appear in the CANDELS expert sample. Of those, \citet{kar15}
+classify 4 as spheroids/disky, 2 as disks, 1 as a spheroid, 1 as
+irregular/disky and 1 as unclassifiable. The \fbest{} values for GZH are all
+between 0.5 and 0.7, making them all intermediate disk candidates. Visual
+inspection of the GZH images shows extended disk structure in at least
+5~images; the remaining 4 are either extremely faint or have imaging artifacts
+in the ACS data.  Since the surveys use different rest-frame filters and the
+overlap sample is tiny, though, detailed comparisons between the overall
+morphologies are highly difficult.
 
@@
 
-As with the HST images, each \ferengi{} subject had a varying number of classifiers
-answering the various questions in the hierarchical decision tree. Every classifier
-answers the first question, {\it ``Is the galaxy smooth and rounded, with no
-sign of a disk?''}; as such the vote fractions \fsmooth, \ffeatures, and
-\fartifact{} are all computed with the minimum statistical error for any
-question, with between 40 and 140~responses (see Section~\ref{sec:interface}).
-The number of participants answering subsequent questions, however, is always equal
-to or less than the number who answered the preceding question. The average number
-of responses per task for fourth- or fifth-tier questions (such as spiral arm
-structure; Tasks 12--14) is only $4\pm4$ for the \ferengi{} sample. While this
-distribution is strongly bimodal (reflecting the true morphologies of
-selected galaxies), the very low absolute numbers of votes introduce very high
-variance when attempting to calculate a statistical correction.
+As with the HST images, each \ferengi{} subject had a varying number of
+classifiers answering the various questions in the hierarchical decision tree.
+Every classifier answers the first question, {\it ``Is the galaxy smooth and
+rounded, with no sign of a disk?''}; as such, the vote fractions \fsmooth,
+\ffeatures, and \fartifact{} all have the lowest statistical error for any
+question in the tree, based only on the total number of responses (between
+40 and 120; see Section~\ref{sec:interface}).  The number of participants
+answering subsequent questions, however, is always equal to or less than the
+number who answered the preceding question. The average number of responses per
+task for fourth- or fifth-tier questions (such as spiral arm structure; Tasks
+12--14) is only $4\pm4$ for the \ferengi{} sample. While this distribution is
+strongly bimodal (reflecting the true morphologies of selected galaxies), the
+very low absolute numbers of votes introduce very high variance when attempting
+to calculate a statistical correction.
 
@@
 Another existing study using GZH to select barred galaxies was presented in
-\citet{che15}. This study used a slightly different bar selection method to
+\citet{che15}. This study used a slightly different bar sample selection to
 demonstrate that AGN hosts show no statistically significant enhancement in bar
@@
 with the exception of assigning S0/bulge-dominated disks (type~2.0) from ZEST
-into the elliptical category.
+into the early-type category.
 
@@
 
-Galaxies from the three COSMOS surveys all have morphologies that are
+Galaxies from the three COSMOS morphology catalogs all have morphologies that are
 reasonably well-predicted by the GZH based on \fbest. The relation is strongest
@@
 
-We also emphasize that the various COSMOS catalogs are not consistent; for
-example, only 64\% of the galaxies in \citet{tas11} have the same morphological
-class as \citet{cas07}. The bulk of these are galaxies classified as ``spiral''
-using one technique and ``irregular'' using another (\citealt{cas07} is more
-likely to classify galaxies as irregular).  A detailed comparison of the
-external catalogs is outside the scope of this paper, but we emphasize only
-that it is \emph{impossible} for any catalog to be consistent with all three.
-We interpret the broad agreements between early-types, spirals, and irregulars
-for all three samples as a validation of the crowdsourced visual
-classifications provided by GZH.
-
-\begin{figure*}
-\center
-\includegraphics[width=1.0\textwidth]{figures/comparisons_odd.pdf}
-\caption{Same as Figure~\ref{fig:comparisons_features}, but comparing external
-morphologies to \fodd{} in GZH. Measurement of \fodd{} excludes galaxies
-labeled as ``odd'' due to lenses or dust lanes ($<1\%$ of the total), which are GZH
-categories not expected to correlate with larger-scale structural parameters.}
-\label{fig:comparisons_odd}
-\end{figure*}
-
-Figure~\ref{fig:comparisons_odd} analyzes the same sets of matched galaxies, but
-compares the data to the \fodd{} parameter in GZH to examine its correlation with
-irregular morphologies. The relationship in this case is less clear; for the
-COSMOS catalogs, in particular, early-types, spirals, and irregulars are
-roughly equally probable at \fodd$>0.5$. In both AEGIS and GOODS (there is no
-measurment of irregular structure for GEMS in \citealt{hau07}), the proportion
-of irregular galaxies does increase with \fodd. However, the actual number of
-galaxies at \fodd$>0.5$ is quite small ($N\lesssim100$) in both samples, and so
-estimating an accurate fraction is less precise.  We also note that this
-particular question ({\it ``anything odd?''}) has somewhat uncertain phrasing
-in GZH, and that the design of the tree explicitly separates clumpy from
-irregular or merging morphologies, which would have similar properties in
-automatic techniques. A more accurate selection of irregular morphologies in
-GZH should use a weighted combination of \fbest, \fclumpy, and \fodd.
-
-We repeated all of the analysis comparing morphologies between GZH and external
+%We also emphasize that the previously published COSMOS catalogs are not
+%internally consistent; for example, only 64\% of the galaxies in \citet{tas11}
+%have the same morphological class as \citet{cas07}. The bulk of these are
+%galaxies classified as ``spiral'' using one technique and ``irregular'' using
+%another (\citealt{cas07} is more likely to classify galaxies as irregular).  A
+%detailed comparison of the external catalogs is outside the scope of this
+%paper, but we emphasize only that it is \emph{impossible} for any catalog to be
+%consistent with all three.  We interpret the broad agreements between
+%early-types, spirals, and irregulars for all three samples as a validation of
+%the crowdsourced visual classifications provided by GZH.
+
+%\begin{figure*}
+%\center
+%\includegraphics[width=1.0\textwidth]{figures/comparisons_odd.pdf}
+%\caption{Same as Figure~\ref{fig:comparisons_features}, but comparing external
+%morphologies to \fodd{} in GZH. Measurement of \fodd{} excludes galaxies
+%labeled as ``odd'' due to lenses or dust lanes ($<1\%$ of the total), which are GZH
+%categories not expected to correlate with larger-scale structural parameters.}
+%\label{fig:comparisons_odd}
+%\end{figure*}
+%
+%Figure~\ref{fig:comparisons_odd} analyzes the same sets of matched galaxies, but
+%compares the data to the \fodd{} parameter in GZH to examine its correlation with
+%irregular morphologies. The relationship in this case is less clear; for the
+%COSMOS catalogs, in particular, early-types, spirals, and irregulars are
+%roughly equally probable at \fodd$>0.5$. In both AEGIS and GOODS (there is no
+%measurement of irregular structure for GEMS in \citealt{hau07}), the proportion
+%of irregular galaxies does increase with \fodd. However, the actual number of
+%galaxies at \fodd$>0.5$ is quite small ($N\lesssim100$) in both samples, and so
+%estimating an accurate fraction is less precise.  We also note that this
+%particular question ({\it ``anything odd?''}) has somewhat uncertain phrasing
+%in GZH, and that the design of the tree explicitly separates clumpy from
+%irregular or merging morphologies, which would have similar properties in
+%automatic techniques. A more accurate selection of irregular morphologies in
+%GZH should use a weighted combination of \fbest, \fclumpy, and \fodd.
+
+A detailed comparison of the external catalogs is outside the scope of this
+paper, but we emphasize only that it is impossible for any catalog to be fully
+consistent with all of the previously published datasets (for example, only
+64\% of the galaxies in \citealt{tas11} have the same morphological class as
+the same galaxies in \citealt{cas07}). We interpret the broad agreements
+between early-types, spirals, and irregulars between GZH and all three methods
+of automated classification as a validation of both the crowdsourced visual
+classifications provided by GZH and those automated methods.
+
+It has been argued that automated methods are preferable to visual
+classification due to being quantified and more easily reproducible
+\citep[\eg,][]{con14,paw16}. We argue that this distinction applies only to
+visual classification done by individual and/or small numbers of experts. The
+technique of crowdsourcing using a large number of independent classifiers
+provides visual classification which is both quantified, and reproducible, and
+(as demonstrated in this section), broadly agrees with all the automated
+methods and expert visual classifications.
+
+We repeated all analyses comparing morphologies between GZH and external
 catalogs on the entire catalog, rather than the volume-limited sample
-($z<1.0,m<22.5$) discussed above. If all redshifts and the original magnitude
-limit of $m<23.5$ are used, the correlations between all of the automatic
-morphological populations and GZH decrease significantly.  The only exception
-are the GEMS galaxies, which are the only sample visually classified (similar
-to GZH) and had a shallower magnitude cut on their catalog. Based on these
-comparisons, we suggest that use of the GZH catalog be limited to galaxies with
-$m<22.5$; fainter targets at the sensitivity of the \hst{} Legacy surveys have
-been demonstrated to be less reliable, regardless of the method of
-morphological classification being used.
+($z<1.0,m<22.5$) discussed above. If galaxies at all redshifts and at the
+original magnitude limit of $m<23.5$ are used, the correlations between all of
+the automatic morphological populations and GZH decrease significantly.  The
+exceptions are the GEMS galaxies, which are the only sample that was visually
+classified and had a shallower magnitude cut on their catalog.
+Based on these comparisons, we suggest that use of the GZH catalog be limited
+to galaxies with $m_\mathrm{I|i|z}<22.5$; fainter targets at the sensitivity of the \hst{}
+Legacy surveys have been demonstrated to be less reliable, regardless of the
+method of morphological classification being used.
 
@@
 Astronomy'' workshop, 3-7 Mar 2014 in Taipei, Taiwan, at which some of this
-analysis was done. We thank Jennifer Lotz for sharing her $G$-$M_{20}$
+analysis was initiated. We thank Jennifer Lotz for sharing her $G$-$M_{20}$
 measurements for the AEGIS sample. We thank Coleman Krawczyk for his assistance

### 2016-05-30 writeup/gz_hubble_data.tex
Spell-checked. Closes #171.

@@
 classification, as the goal was to measure the effect on normal classifications
-usng the same technique as closely as possible. Following classification, a
+using the same technique as closely as possible. Following classification, a
 classifier could view a page with additional details about each galaxy; where
@@
 
-Stripe~82 single-epoch images were taken directly from the DR7 SDSS Skyserver,
+Stripe~82 single-epoch images were taken directly from the DR7 SDSS SkyServer,
 which combined $g^{\prime}$, $r^{\prime}$, and $i^{\prime}$ exposures into the
@@
 smaller clumps and presumed to be in the process of building up their baryonic
-mass through a combination of hierarchical merging and in-situ star formation.
+mass through a combination of hierarchical merging and {\it in-situ} star formation.
 While the majority of scientific interpretation is left to future work, this
@@
 \url{http://sankeymatic.com/}. \citet{hol05} provided valuable assistance
-in intepreting \sextractor{} output.
+in interpreting \sextractor{} output.
 

### 2016-05-30 writeup/gz_hubble_data.tex
ApJ bst file
Funding for @rjsmethurst.
Moved tables to separate files.

@@
-\documentclass[twocolumn]{aastex6}
-
-%% The other main article choice is a tightly typeset, two-column article
-%% that more closely resembles the final typeset pdf article.
-%%
-%% \documentclass[twocolumn]{aastex6}
-%% 
-%% There are other optional arguments one can invoke to allow other 
-%% actions. 
-%%
-% These are the available options:
-%   manuscript  : onecolumn, doublespace, 12pt fonts
-%   preprint    : onecolumn, single space, 10pt fonts
-%   preprint2   : twocolumn, single space, 10pt fonts
-%   twocolumn   : a two column article. Probably not needed, but here just in case.
-%   onecolumn   : a one column article; default option.
-%   twocolappendix: make 2 column appendix
-%   onecolappendix: make 1 column appendix is the default. 
-%   astrosymb   : Loads Astrosymb font and define \astrocommands. 
-%   tighten : Makes baselineskip slightly smaller
-%   times   : uses times font instead of the default
-%   linenumbers : turn on lineno package.
-%   trackchanges : required to see the revision mark up and print output
-%   numberedappendix: Labels appendix sections A, B, ... This is the default.
-%   appendixfloats: Needed. Resets figure and table counters to zero
-
-%% these can be used in any combination, e.g.
-%%
-%% \documentclass[twocolumn,twocolappendix,linenumbers,trackchanges]{aastex6}
-
-\shorttitle{Galaxy Zoo: Hubble}
-\shortauthors{Willett et al.}
-
-%% This is the end of the preamble.  Indicate the beginning of the
-%% paper itself with \begin{document}.
-
-\usepackage{epsfig}
+\documentclass[a4paper,fleqn,usenatbib]{mnras}
+
+%\usepackage{epsfig}
 \usepackage{color,soul}
-\usepackage{natbib}
+%\usepackage{natbib}
+\usepackage{deluxetable}
 \usepackage{amsmath,amssymb}
@@
 \usepackage{url}
-\usepackage[normalem]{ulem}
-\bibliographystyle{mn2e}
+%\usepackage[normalem]{ulem}
+\usepackage[T1]{fontenc}
+\usepackage{ae,aecompl}
 
@@
 
+\title[Galaxy Zoo: Hubble]{Galaxy Zoo: Morphological Classifications for 120,000 Galaxies in HST Legacy Imaging}
+
+\author[Willett et al.]{
+Kyle W. Willett$^{1,2}$,
+Melanie A. Galloway$^{1}$,
+Steven P. Bamford$^{3}$,
+Chris J. Lintott$^{4}$,
+\newauthor
+Karen L. Masters$^{5,6}$,
+Claudia Scarlata$^{1}$,
+B.D. Simmons$^{4,7}$\footnote{Einstein Fellow},
+Melanie Beck$^{1}$,
+\newauthor
+Carolin N. Cardamone$^{8}$,
+Edmond Cheung$^{9}$,
+Edward M. Edmondson$^{5}$,
+Lucy F. Fortson$^{1}$,
+\newauthor
+Roger L. Griffith$^{10,11}$,
+Boris H\"au{\ss}ler$^{4,12,13}$,
+Anna Han$^{14}$,
+Ross Hart$^{3}$,
+\newauthor
+Thomas Melvin$^{5}$,
+Michael Parrish$^{15}$,
+Kevin Schawinski$^{16}$,
+R.J. Smethurst$^{4}$,
+\newauthor
+Arfon M. Smith$^{4,15,17}$
+\\
+%
+$^{1}$School of Physics and Astronomy, University of Minnesota, 116 Church St. SE, Minneapolis, MN 55455, USA \\
+$^{2}$Department of Physics and Astronomy, University of Kentucky, 505 Rose St., Lexington, KY 40506, USA \\
+$^{3}$School of Physics and Astronomy, The University of Nottingham, University Park, Nottingham, NG7 2RD, UK \\
+$^{4}$Oxford Astrophysics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK \\
+$^{5}$Institute for Cosmology and Gravitation, University of Portsmouth, Dennis Sciama Building, Burnaby Road, Portsmouth, PO1 3FX, UK \\
+$^{6}$SEPnet, South East Physics Network, UK \\
+$^{7}$Center for Astrophysics and Space Sciences, Department of Physics, University of California, San Diego, CA 92093, USA \\
+$^{8}$Department of Mathematics and Science, Wheelock College, Boston, MA 02215, USA \\
+$^{9}$Kavli Institute for the Physics and Mathematics of the Universe (WPI), \\ Todai Institutes for Advanced Study, The University of Tokyo, Kashiwa 277-8583, Japan \\
+$^{10}$Infrared Processing and Analysis Center, California Institute of Technology, Pasadena, CA 91125, USA \\
+$^{11}$Department of Astronomy \& Astrophysics, 525 Davey Lab, The Pennsylvania State University, University Park, PA 16802, USA \\
+$^{12}$Centre for Astrophysics, Science \& Technology Research Institute, University of Hertfordshire, Hatfield, AL10 9AB, UK \\
+$^{13}$European Southern Observatory, Alonso de C\'ordova 3107, Vitacura, Casilla 19001, Santiago, Chile \\
+$^{14}$Department of Astronomy, Yale University, New Haven, CT 06520, USA \\
+$^{15}$Adler Planetarium, 1300 S. Lake Shore Drive, Chicago, IL 60605, USA \\
+$^{16}$Institute for Astronomy, Department of Physics, ETH Z\"urich, Wolfgang-Pauli-Strasse 27, CH-8093 Z\"urich, Switzerland \\
+$^{17}$GitHub
+}
+
+\date{Accepted XXX. Received YYY; in original form ZZZ}
+\pubyear{2016}
+
 \begin{document}
-
-%% LaTeX will automatically break titles if they run longer than
-%% one line. However, you may use \\ to force a line break if
-%% you desire.
-
-\title{Galaxy Zoo: Morphological Classifications for 120,000 Galaxies in HST Legacy Imaging}
-%% Use \author, \affil, plus the \and command to format author and affiliation 
-%% information.  If done correctly the peer review system will be able to
-%% automatically put the author and affiliation information from the manuscript
-%% and save the corresponding author the trouble of entering it by hand.
-%%
-%% The \affil should be used to document primary affiliations and the
-%% \altaffil should be used for secondary affiliations, titles, or email.
-
-%% Authors with the same affiliation can be grouped in a single
-%% \author and \affil call.
-\author{
-    Kyle W. Willett\altaffilmark{1,2}, 
-    Melanie A. Galloway\altaffilmark{1}, 
-    Steven P. Bamford\altaffilmark{3}, 
-    Chris J. Lintott\altaffilmark{4}, 
-    Karen L. Masters\altaffilmark{5,6}, 
-    Claudia Scarlata\altaffilmark{1}, 
-    B.D. Simmons\altaffilmark{4,7}, 
-    Melanie Beck\altaffilmark{1}, 
-    Carolin N. Cardamone\altaffilmark{8}, 
-    Edmond Cheung\altaffilmark{9}, 
-    Edward M. Edmondson\altaffilmark{5}, 
-    Lucy F. Fortson\altaffilmark{1},
-    Roger L. Griffith\altaffilmark{10,11}, 
-    Boris H\"au{\ss}ler\altaffilmark{4,12,13},
-    Anna Han\altaffilmark{14}, 
-    Ross Hart\altaffilmark{3}, 
-    Thomas Melvin\altaffilmark{5}, 
-    Michael Parrish\altaffilmark{15}, 
-    Kevin Schawinski\altaffilmark{16}, 
-    R.J. Smethurst\altaffilmark{4}, 
-    Arfon M. Smith\altaffilmark{4,15,17}
-}
-%
-%$^N$Institute for Cosmology and Gravitation, University of Portsmouth, Dennis Sciama Building, Burnaby Road, Portsmouth, PO1 3FX, UK \\
-%$^N$South East Physics Network, www.sepnet.ac.uk\\
-%$^N$Dept. of Astronomy, Cornell University, Space Sciences Building, Ithaca, NY 14850, USA\\
-%$^N$Institute for Sciences of the Cosmos (ICCUB), University of Barcelona, Marti i Franques 1, Barcelona, 08024 Spain\\
-%$^N$Oxford Astrophysics, Department of Physics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK\\
-%$^N$Yale Center for Astronomy and Astrophysics, Yale University, P.O. Box 208121, New Haven, CT 06520, USA \\
-%$^N$Steward Observatory, University of Arizona, 933 N. Cherry Ave, Tucson, AZ 85721, USA\\
-%$^N$Astronomy Department, Adler Planetarium and Astronomy Museum, 1300 Lake Shore Drive, Chicago, IL 60605, USA\\
-%$^N$Centre for Astronomy \& Particle Theory, University of Nottingham, University Park, Nottingham, NG7 2RD, UK\\
-%$^N$School of Physics and Astronomy, University of Minnesota, Minneapolis, MN 55455, USA\\
-%$^N$Department of Physics \& Astronomy, 206 Gallalee Hall, 514 University Blvd., University of Alabama, Tuscaloosa, AL 35487-0234, USA\\
-%$^N$Einstein Fellow\\
-
-\altaffiltext{1}{School of Physics and Astronomy, University of Minnesota, 116 Church St. SE, Minneapolis, MN 55455, USA}
-\altaffiltext{2}{Department of Physics and Astronomy, University of Kentucky, 505 Rose St., Lexington, KY 40506, USA}
-\altaffiltext{3}{School of Physics and Astronomy, The University of Nottingham, University Park, Nottingham, NG7 2RD, UK}
-\altaffiltext{4}{Oxford Astrophysics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK}
-\altaffiltext{5}{Institute for Cosmology and Gravitation, University of Portsmouth, Dennis Sciama Building, Burnaby Road, Portsmouth, PO1 3FX, UK}
-\altaffiltext{6}{SEPnet, South East Physics Network, UK}
-\altaffiltext{7}{Center for Astrophysics and Space Sciences, Department of Physics, University of California, San Diego, CA 92093, USA}
-\altaffiltext{8}{Department of Mathematics and Science, Wheelock College, Boston, MA 02215, USA}
-\altaffiltext{9}{Kavli Institute for the Physics and Mathematics of the Universe (WPI), Todai Institutes for Advanced Study, The University of Tokyo, Kashiwa 277-8583, Japan}
-\altaffiltext{10}{Infrared Processing and Analysis Center, California Institute of Technology, Pasadena, CA 91125, USA}
-\altaffiltext{11}{Department of Astronomy \& Astrophysics, 525 Davey Lab, The Pennsylvania State University, University Park, PA 16802, USA}
-\altaffiltext{12}{Centre for Astrophysics, Science \& Technology Research Institute, University of Hertfordshire, Hatfield, AL10 9AB, UK}
-\altaffiltext{13}{European Southern Observatory, Alonso de C\'ordova 3107, Vitacura, Casilla 19001, Santiago, Chile}
-\altaffiltext{14}{Department of Astronomy, Yale University, New Haven, CT 06520, USA}
-\altaffiltext{15}{Adler Planetarium, 1300 S. Lake Shore Drive, Chicago, IL 60605, USA}
-\altaffiltext{16}{Institute for Astronomy, Department of Physics, ETH Z\"urich, Wolfgang-Pauli-Strasse 27, CH-8093 Z\"urich, Switzerland}
-\altaffiltext{17}{GitHub}
+\label{firstpage}
+\pagerange{\pageref{firstpage}--\pageref{lastpage}}
+\maketitle
 
 \begin{abstract}
-
-% Note: 250-word limit
 We present the data release paper for the Galaxy Zoo: Hubble (GZH)
@@
 
-\keywords{galaxies:structure --- galaxies:high redshift --- galaxies:evolution
---- methods:data analysis --- catalogs}
-
-\section{Introduction} \label{sec:intro}
+\begin{keywords}
+galaxies:structure --- galaxies:high redshift --- galaxies:evolution
+--- methods:data analysis --- catalogs
+\end{keywords}
+
+\section{Introduction}\label{sec:intro}
 
@@
 \begin{figure*}
-\center
 \includegraphics[width=160mm]{figures/filter_curves.pdf}
@@
 was used to create color gradients in the GZH COSMOS
-images.\label{fig:filtercurves}}
+images.}
+\label{fig:filtercurves}
 \end{figure*}
@@
 are visually more realistic at higher luminosities.
-% okay so I'm a cheeky self-citing biyotch
+% okay so I'm a cheeky self-citing biyotch - BDS
 
@@
 
-%\begin{table*}
-%\center
-%\caption{Summary of morphological categories selected for \ferengi{} sample.\label{tbl:morphologies}}
-%\begin{tabular}{lllc}
-%\hline\hline
-%Morphology          & Label &  Selection                                                                                            & $N_{\rm objects}$ \\
-%                    &       &                                                                                                       & [$N_z \times N_\mu$] \\
-%\hline
-%Features            & Yes       & $f_{\rm features} > 0.8$, $f_{\rm odd} < 0.1$                                                         & 12 \\ 
-%                    & Int.      & $0.3 < f_{\rm smooth} < 0.6$, $f_{\rm odd} < 0.1$                                                     & 12 \\ 
-%                    & No        & $f_{\rm smooth} > 0.8$, $f_{\rm odd} < 0.1$                                                           & 12 \\ 
-%Merger              & No        & $f_{\rm features} > 0.8$, $f_{\rm odd < 0.1}$, $f_{\rm merger} < 0.1$                                 & 12 \\
-%                    & Int.      & $f_{\rm odd} > 0.5$, $0.1< f_{\rm merger} < 0.4$                                                      & 12 \\ 
-%                    & Yes       & $f_{\rm odd} > 0.5$, $f_{\rm merger} > 0.4$                                                           & 12 \\
-%Edge-on             & Yes       & $f_{\rm edgeon} > 0.8$, $f_{\rm features} > 0.5$                                                      & 12 \\
-%                    & Int.      & $0.4 < f_{\rm edgeon} < 0.8$ , $f_{\rm features} > 0.5$                                               & 12 \\
-%                    & No        & $f_{\rm edgeon} < 0.2$, $f_{\rm features} > 0.5$                                                      & 12 \\
-%Bar                 & No        & $f_{\rm bar} < 0.1$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$                                 & 24 \\
-%                    & Int.      & $0.2 < f_{\rm bar} < 0.4$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$                           & 24 \\
-%                    & Yes       & $f_{\rm bar} > 0.8$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$                                 & 24 \\
-%Visible spiral      & No        & $f_{\rm spiral} < 0.2$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$, $f_{\rm bar} < 0.1$         & 12 \\
-%                    & Int.      & $0.2 < f_{\rm spiral} < 0.8$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$, $f_{\rm bar} < 0.1$   & 12 \\
-%                    & Yes       & $f_{\rm spiral} > 0.8$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$, $f_{\rm bar} < 0.1$         & 12 \\
-%Oblique bulge size  & No        & $f_{\rm nobulge>0.6}$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.5$, $f_{\rm bar} < 0.2$          & 12 \\
-%                    & Int.      & $f_{\rm justnoticeable}>0.6$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.5$, $f_{\rm bar} < 0.2$   & 12 \\
-%                    & Yes       & $f_{\rm obvious|dominant}>0.5$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.5$, $f_{\rm bar} < 0.2$ & 12 \\
-%Edge-on bulge shape & Round     & $f_{\rm rounded}>0.5$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} > 0.5$                               & 12 \\
-%                    & Boxy      & $f_{\rm boxy}>0.4$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} > 0.2$                                  & 12 \\
-%                    & No bulge  & $f_{\rm nobulge}>0.5$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} > 0.5$                               & 12 \\
-%\hline\hline
-%\end{tabular}
-%\end{table*}
+%\input{tables/morphologies.tex}
 
@@
 
-%\begin{table}
-%\caption{Summary of \ferengi{} artificial redshifting \label{tbl:ferengivalues}}
-%\begin{tabular}{lccccr}
-%\hline\hline
-%$z_{\rm sim}$ & $N_{z {\rm bins}}$ & $N_{\rm evolution}$ & $e_{\rm max}$ & $N_{\rm galaxies}$ & $N_{\rm images}$\\
-%\hline
-%0.3              & 8                  & 7                   & $-3.0$        & 72             & 4032 \\
-%0.5              & 6                  & 4                   & $-1.5$        & 72             & 1728 \\
-%0.8              & 3                  & 3                   & $-1.0$        & 72             &  648 \\
-%1.0              & 1                  & 3                   & $-1.0$        & 72             &  216 \\
-%\hline\hline
-%\end{tabular}
-%\end{table}
+%\input{tables/ferengi.tex}
 
@@
 % (we don't, right?).  Would also be good to cite here where we have done
-% similar things in the past...
+% similar things in the past... - BDS
 
@@
 same prescription as for the AEGIS images.
-% Edmond should verify the AEGIS bit above.
+% Edmond should verify the AEGIS bit above. - BDS
 
@@
 
-%\tabletypesize{\scriptsize}
-%\begin{deluxetable*}{l|rr|rrr|rr|r|rr}
-%\tablecolumns{12}
-%\tablewidth{0pc}
-%\tablecaption{GZH redshifts by survey\label{tbl:redshifts}} 
-%\tabletypesize{\scriptsize}
-%\tablehead{
-% &   
-%\multicolumn{2}{c}{\underline{ACS-GC}} &
-%\multicolumn{3}{c}{\underline{3DHST}} &
-%\multicolumn{2}{c}{\underline{MUSYC}} &
-%\multicolumn{1}{c}{\underline{UltraVISTA}}&
-%\multicolumn{2}{c}{\underline{Total}} 
-%\\
-%\colhead{Survey} & 
-%\colhead{spec-z} & 
-%\colhead{photo-z} & 
-%\colhead{spec-z} & 
-%\colhead{grism-z} & 
-%\colhead{photo-z} & 
-%\colhead{spec-z} & 
-%\colhead{photo-z} & 
-%\colhead{photo-z} & 
-%\colhead{with redshift} &
-%\colhead{in survey}
-%}
-%\small
-%\startdata
-%%Survey     Gs        Gp    3ds    3dg     3dp       Ms      Mp       UVp       total
-%AEGIS    & 3,656  & 2,941  & 12  &  515  &  249    & 0     & 0     &  0      & 7,373   & 8,507   \\
-%COSMOS   & 7,201  & 77,435 & 35  &  358  &  26     & 0     & 0     &  2,665  & 85,020  & 92,808  \\
-%GEMS     & 387    & 628    & 6   &  99   &  40     & 279   & 7,304 & 0       & 8,743   & 9,304   \\
-%GOODS-N  & 1,947  & 37     & 418 & 1,545 &  1,381  & 0     & 0     & 0       & 5,328   & 12,030  \\
-%GOODS-S  & 1,080  & 4      & 327 & 1,348 &  281    & 816   & 1,184 & 0       & 5,040   & 10,284  \\
-%SDSS     & 0      & 0      & 0   &  0    &  0      & 0     & 0     & 0       & 37,545  & 51,861  \\
-%\hline
-%Total    & 14,271 & 81,045 & 798 & 3,865 & 1,977   & 1,095 & 8,488 & 2,665   & 114,204 & 184,794 \\
-%\enddata
-%\end{deluxetable*}
+%\input{tables/redshifts.tex}
 
@@
 \includegraphics[width=160mm]{figures/gzh_interface.png}
-\caption{Screenshot of the GZH interface (\url{http:/zoo3.galaxyzoo.org}) at
+\caption{Screenshot of the GZH interface at
 the beginning of classifying a random galaxy, with the classifier ready
@@
 \center
-\caption{Distribution of \ferengi{} images analyzed in Figure~\ref{fig:f_vs_f}.
-Correctable images have a single-valued relationship between their measured
-\ffeatures{} values at high and low redshifts (white regions in
-Figure~\ref{fig:f_vs_f}). Images with only a lower-limit on \ffeatures{} have a
-non single-valued relationship (blue regions). NEI (``not enough information'')
-images have undetermined relationships due to a lack of data ($N<5$) in their
-corresponding $z$-$\mu$ bins (gray regions).\label{tbl:ferengi_corrections}}
+\caption{Distribution of the ability of images to measure
+morphological bias for
+the \ferengi{} data (see Figure~\ref{fig:f_vs_f}).}
+\label{tbl:ferengi_corrections}
 \begin{tabular}{lrr}
@@
 
-\tabletypesize{\scriptsize}
-\begin{deluxetable*}{lllcrlllllll|c}
-\centering
-\tablecolumns{13}
-\tablewidth{0pc}
-\tablecaption{GZH morphological classifications for \hst{} images from AEGIS, COSMOS, GEMS, and GOODS\label{tbl:catalog_hst}} 
-\tabletypesize{\scriptsize}
-\tablehead{
- & & & 
-\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
-\multicolumn{7}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
-\colhead{$\ldots$}
-\\
-\colhead{Zooniverse ID} & 
-\colhead{Survey ID} & 
-\colhead{Imaging} & 
-\colhead{Correction$^{1}$} & 
-\colhead{$N_\mathrm{votes}$} & 
-\colhead{fraction} & 
-\colhead{weighted} & 
-\colhead{debiased} & 
-\colhead{best} &
-\colhead{lower~limit} & 
-\colhead{upper~limit} &
-\colhead{flag} &
-\colhead{}
-}
-\small
-\startdata
-AHZ100002g  & 10010842  & AEGIS             & 0        & 127       & 0.118    & 0.128     & 0.085    & 0.085    & 0.226     & 0.226 & 0  \\
-AHZ100002h  & 10010870  & AEGIS             & 4        & 127       & 0.567    & 0.592     & 0.927    & 0.592    & $-$       & $-$   & 0  \\
-$\ldots$    \\
-AHZ20004kd  & 20014731  & COSMOS            & 3        &  44       & 0.682    & 0.675     & 0.147    & 0.675    & $-$       & $-$   & 0  \\
-AHZ20004ke  & 20014732  & COSMOS            & 2        &  45       & 0.689    & 0.756     & 0.893    & 0.756    & $-$       & $-$   & 0  \\
-$\ldots$    \\
-AHZ400043g  & 90022729  & GEMS              & 1        & 121       & 0.702    & 0.733     & 0.487    & 0.734    & 0.483     & 0.800 & 0  \\
-AHZ4000416  & 90022735  & GEMS              & 1        & 127       & 0.646    & 0.698     & 0.508    & 0.698    & 0.171     & 0.727 & 0  \\
-$\ldots$    \\
-AGZ0007z47  & 10014     & GOODS-N-FULLDEPTH & 1        & 40        & 0.475    & 0.475     & 0.197    & 0.475    & 0.011     & 0.496 & 0  \\
-AGZ0007z48  & 10017     & GOODS-N-FULLDEPTH & 3        & 40        & 0.675    & 0.675     & 0.048    & 0.675    & 0.168     & 0.669 & 0  \\
-$\ldots$    \\
-AGZ00083jb  & 8869      & GOODS-S-FULLDEPTH & 1        & 40        & 0.425    & 0.425     & 0.109    & 0.425    & 0.070     & 0.548 & 0  \\
-AGZ00083jc  & 8878      & GOODS-S-FULLDEPTH & 0        & 40        & 0.205    & 0.205     & 0.048    & 0.048    & $-$0.005  & 0.287 & 0  \\
-$\ldots$    \\
-\enddata
-\tablenotetext{1}{Flag indicating how the vote fractions for this galaxy were
-corrected through debiasing (Section~\ref{ssec:zeta_results}), if possible.
-0~=~correctable, 1~=~lower-limit ($f_\mathrm{raw}$ --- $f_\mathrm{adj}$ is not
-single-valued), 2~=~uncorrected ($z < 0.3$), 3~=~uncorrected
-(insufficient \ferengi{} galaxies in this $z$-$\mu$ bin), 4~=~uncorrected (no
-galaxy redshift available).}
-\tablecomments{The full version of this table is available in electronic form,
-as well as at \url{http://data.galaxyzoo.org}. The complete version includes
-data for 113,705~galaxies and morphological information for all tasks in the
-tree. A subset of the information is shown here to illustrate form and
-content.}
-\end{deluxetable*}
-
-\tabletypesize{\scriptsize}
-\begin{deluxetable*}{lllcrlllllll|c}
-\centering
-\tablecolumns{13}
-\tablewidth{0pc}
-\tablecaption{GZH morphological classifications for color-faded \hst{} images\label{tbl:catalog_faded}} 
-\tabletypesize{\scriptsize}
-\tablehead{
- & & & 
-\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
-\multicolumn{7}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
-\colhead{$\ldots$}
-\\
-\colhead{Zooniverse ID} & 
-\colhead{Survey ID} & 
-\colhead{Imaging} & 
-\colhead{Correction} & 
-\colhead{$N_\mathrm{votes}$} & 
-\colhead{fraction} & 
-\colhead{weighted} & 
-\colhead{debiased} & 
-\colhead{best} &
-\colhead{lower~limit} & 
-\colhead{upper~limit} &
-\colhead{flag} &
-\colhead{}
-}
-\small
-\startdata
-AHZF000001  &   20000002    &   COSMOS  &   1   &   48 &  0.708   &     0.755   &   0.228    &    0.754 &   0.325   &   0.829 & 0 \\
-AHZF000003  &   20000004    &   COSMOS  &   3   &   49 &  0.367   &     0.379   &   0.100    &    0.379 &   0.198   &   0.198 & 0 \\
-AHZF000004  &   20000006    &   COSMOS  &   3   &   49 &  0.265   &     0.271   &   0.010    &    0.270 &   $-$     &   $-$   & 0 \\
-AHZF00000z  &   20000102    &   COSMOS  &   1   &   44 &  0.727   &     0.78    &   0.233    &    0.780 &   0.316   &   0.820 & 0 \\
-AHZF000010  &   20000104    &   COSMOS  &   2   &   53 &  0.811   &     0.849   &   0.904    &    0.848 &   $-$     &   $-$   & 0 \\
-$\ldots$    \\
-\enddata
-\tablecomments{The full version of this table is available in electronic form,
-as well as at \url{http://data.galaxyzoo.org}. The complete version includes
-data for 3,927~galaxies and morphological information for all tasks in the
-tree. A subset of the information is shown here to illustrate form and
-content.}
-\end{deluxetable*}
-
-\tabletypesize{\scriptsize}
-\begin{deluxetable*}{lllcrllllllll|c}
-\centering
-\tablecolumns{13}
-\tablewidth{0pc}
-\tablecaption{GZH morphological classifications for color-inverted \hst{} images\label{tbl:catalog_recolored}} 
-\tabletypesize{\scriptsize}
-\tablehead{
- & & & 
-\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
-\multicolumn{7}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
-\colhead{$\ldots$}
-\\
-\colhead{Zooniverse ID} & 
-\colhead{Survey ID} & 
-\colhead{Imaging} & 
-\colhead{Correction} & 
-\colhead{$N_\mathrm{votes}$} & 
-\colhead{fraction} & 
-\colhead{weighted} & 
-\colhead{debiased} & 
-\colhead{best} &
-\colhead{lower~limit} & 
-\colhead{upper~limit} &
-\colhead{flag} &
-\colhead{}
-}
-\small
-\startdata
-AHZC000001  &   20000002      &   COSMOS      &   1    168  &   0.615   &   0.664   &   0.160   &  0.663   &  0.271   &  0.775  & 0  \\
-AHZC000003  &   20000004      &   COSMOS      &   0    235  &   0.333   &   0.364   &   0.002   &  0.002   &  0.063   &  0.063  & 0  \\
-AHZC000004  &   20000006      &   COSMOS      &   3    316  &   0.235   &   0.252   & $-0.011$  &  0.252   &  $-$     &  $-$    & 1  \\
-AHZC00000z  &   20000102      &   COSMOS      &   1    207  &   0.755   &   0.757   &   0.272   &  0.756   &  0.249   &  0.796  & 0  \\
-AHZC000010  &   20000104      &   COSMOS      &   2    158  &   0.843   &   0.882   &   0.936   &  0.881   &  $-$     &  $-$    & 1  \\
-$\ldots$    \\
-\enddata
-\tablecomments{The full version of this table is available in electronic form,
-as well as at \url{http://data.galaxyzoo.org}. The complete version includes
-data for 3,927~galaxies and morphological information for all tasks in the
-tree. A subset of the information is shown here to illustrate form and
-content.}
-\end{deluxetable*}
-
-\tabletypesize{\scriptsize}
-\begin{deluxetable*}{lllcrlllllll|c}
-\centering
-\tablecolumns{13}
-\tablewidth{0pc}
-\tablecaption{GZH morphological classifications for GOODS 2-epoch images\label{tbl:catalog_goods_shallow}} 
-\tabletypesize{\scriptsize}
-\tablehead{
- & & &  
-\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
-\multicolumn{7}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
-\colhead{$\ldots$}
-\\
-\colhead{Zooniverse ID} & 
-\colhead{Survey ID} & 
-\colhead{Imaging} & 
-\colhead{Correction} & 
-\colhead{$N_\mathrm{votes}$} & 
-\colhead{fraction} & 
-\colhead{weighted} & 
-\colhead{debiased} & 
-\colhead{best} &
-\colhead{lower~limit} & 
-\colhead{upper~limit} &
-\colhead{flag} &
-\colhead{}
-}
-\small
-\startdata
-AHZ3000001  &   50000000    &     GOODS-N   &   0   &   123 &   0.390   &   0.415   &   0.090 &   0.090 &   $-$     &   $-$   & 0 \\
-AHZ3000002  &   50000001    &     GOODS-N   &   2   &   126 &   0.341   &   0.355   &   0.356 &   0.356 &   0.220   &   0.279 & 0 \\
-AHZ3000003  &   50000005    &     GOODS-N   &   1   &   129 &   0.760   &   0.826   &   0.633 &   0.825 &   0.596   &   0.834 & 0 \\
-AHZ3000004  &   50000008    &     GOODS-N   &   1   &   120 &   0.758   &   0.787   &   0.639 &   0.787 &   0.658   &   0.834 & 0 \\
-AHZ3000005  &   50000010    &     GOODS-N   &   1   &   123 &   0.854   &   0.890   &   0.611 &   0.889 &   0.597   &   0.914 & 0 \\
-$\ldots$    \\
-\enddata
-\tablecomments{The full version of this table is available in electronic form,
-as well as at \url{http://data.galaxyzoo.org}. The complete version includes
-data for 6,144~galaxies and morphological information for all tasks in the
-tree. A subset of the information is shown here to illustrate form and
-content.}
-\end{deluxetable*}
-
-\tabletypesize{\scriptsize}
-\begin{deluxetable*}{lllcrlllll|c}
-\centering
-\tablecolumns{13}
-\tablewidth{0pc}
-\tablecaption{GZH morphological classifications for SDSS Stripe 82 single-epoch images\label{tbl:stripe82_single}} 
-\tabletypesize{\scriptsize}
-\tablehead{
- & & & 
-\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
-\multicolumn{5}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
-\colhead{$\ldots$}
-\\
-\colhead{Zooniverse ID} & 
-\colhead{Survey ID} & 
-\colhead{Imaging} & 
-\colhead{Correction} & 
-\colhead{$N_\mathrm{votes}$} & 
-\colhead{fraction} & 
-\colhead{weighted} & 
-\colhead{debiased} & 
-\colhead{best} &
-\colhead{flag} &
-\colhead{}
-}
-\small
-\startdata
-AHZ5000001  &   587730845812064684  &   SDSS    &     2 &   41  &   0.585   &    0.595  &   0.759   &   0.594 &  0  \\
-AHZ5000002  &   587730845812065247  &   SDSS    &     2 &   46  &   0.609   &    0.651  &   0.897   &   0.651 &  0  \\
-AHZ5000003  &   587730845812196092  &   SDSS    &     2 &   51  &   0.039   &    0.044  &   0.067   &   0.043 &  0  \\
-AHZ5000004  &   587730845812196825  &   SDSS    &     2 &   35  &   0.514   &    0.605  &   0.928   &   0.605 &  0  \\
-AHZ5000005  &   587730845812524122  &   SDSS    &     2 &   47  &   0.766   &    0.812  &   1.038   &   0.810 &  1  \\
-AHZ5000006  &   587730845812654984  &   SDSS    &     2 &   42  &   0.500   &    0.542  &   0.680   &   0.541 &  0  \\
-AHZ5000007  &   587730845812655541  &   SDSS    &     2 &   41  &   0.488   &    0.526  &   0.697   &   0.525 &  0  \\
-AHZ5000008  &   587730845812720365  &   SDSS    &     2 &   53  &   0.792   &    0.84   &   1.050   &   0.839 &  1  \\
-AHZ5000009  &   587730845812720640  &   SDSS    &     4 &   43  &   0.000   &    0.0    &   0.000   &   0.0   &  0  \\
-AHZ500000a  &   587730845812720699  &   SDSS    &     2 &   40  &   0.425   &    0.478  &   0.588   &   0.477 &  0  \\
-$\ldots$    \\
-\enddata
-\tablecomments{The full version of this table is available in electronic form,
-as well as at \url{http://data.galaxyzoo.org}. The complete version includes
-data for 21,522~galaxies and morphological information for all tasks in the
-tree. A subset of the information is shown here to illustrate form and
-content.}
-\end{deluxetable*}
-
-\tabletypesize{\scriptsize}
-\begin{deluxetable*}{lllcrlllll|c}
-\centering
-\tablecolumns{13}
-\tablewidth{0pc}
-\tablecaption{GZH morphological classifications for SDSS Stripe 82 co-added images\label{tbl:stripe82_coadd}} 
-\tabletypesize{\scriptsize}
-\tablehead{
- & & & 
-\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
-\multicolumn{5}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
-\colhead{$\ldots$}
-\\
-\colhead{Zooniverse ID} & 
-\colhead{Survey ID} & 
-\colhead{Imaging} & 
-\colhead{Correction} & 
-\colhead{$N_\mathrm{votes}$} & 
-\colhead{fraction} & 
-\colhead{weighted} & 
-\colhead{debiased} & 
-\colhead{best} &
-\colhead{flag} &
-\colhead{}
-}
-\small
-\startdata
-AHZ6000001  & 8647474690312306978   &   SDSS    &    4  & 40  & 0.275   &    0.289  &   0.762   &   0.289   & 0 \\
-AHZ6000002  & 8647474690312307154   &   SDSS    &    2  & 43  & 0.605   &    0.634  &   0.858   &   0.635   & 0 \\
-AHZ6000003  & 8647474690312307877   &   SDSS    &    2  & 51  & 0.608   &    0.627  &   0.906   &   0.627   & 0 \\
-AHZ6000004  & 8647474690312308301   &   SDSS    &    4  & 52  & 0.038   &    0.038  &   0.723   &   0.038   & 0 \\
-AHZ6000005  & 8647474690312308318   &   SDSS    &    2  & 44  & 0.614   &    0.632  &   0.776   &   0.631   & 0 \\
-AHZ6000006  & 8647474690312308880   &   SDSS    &    2  & 36  & 0.667   &    0.683  &   0.901   &   0.683   & 0 \\
-AHZ6000007  & 8647474690312372644   &   SDSS    &    4  & 48  & 0.646   &    0.674  &   1.145   &   0.674   & 0 \\
-AHZ6000008  & 8647474690312372789   &   SDSS    &    4  & 45  & 0.489   &    0.571  &   0.964   &   0.570   & 0 \\
-AHZ6000009  & 8647474690312372931   &   SDSS    &    4  & 47  & 0.553   &    0.587  &   0.926   &   0.587   & 0 \\
-AHZ600000a  & 8647474690312373190   &   SDSS    &    4  & 47  & 0.574   &    0.559  &   1.008   &   0.559   & 0 \\
-$\ldots$    \\
-\enddata
-\tablecomments{The full version of this table is available in electronic form,
-as well as at \url{http://data.galaxyzoo.org}. The complete version includes
-data for 30,339~galaxies and morphological information for all tasks in the
-tree. A subset of the information is shown here to illustrate form and
-content.}
-\end{deluxetable*}
-
-\tabletypesize{\scriptsize}
-\begin{deluxetable*}{lllccccrrrrrrrr|c}
-\centering
-\tablecolumns{14}
-\tablewidth{0pc}
-\tablecaption{GZH morphological classifications for \hst{} images with simulated AGN\label{tbl:simulated_agn}} 
-\tabletypesize{\scriptsize}
-\tablehead{
- & & & & & & & &
-\multicolumn{7}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
-\colhead{$\ldots$}
-\\
-\colhead{Zooniverse ID} & 
-\colhead{Survey ID} & 
-\colhead{Imaging} & 
-\colhead{Correction} & 
-\colhead{Version} & 
-\colhead{$L_\mathrm{ratio}$} & 
-\colhead{AGN color$^{1}$} & 
-\colhead{$N_\mathrm{votes}$} & 
-\colhead{fraction} & 
-\colhead{weighted} & 
-\colhead{debiased} & 
-\colhead{best} &
-\colhead{lower limit} &
-\colhead{upper limit} &
-\colhead{flag} &
-\colhead{}
-}
-\small
-\startdata
-AHZ7000001  &   90024700  &   GEMS    &   1   &   1   &   0.2   &   1   &   42  &   0.238   &   0.239   &   $-$0.110  &       0.238  &  $-$0.113    &     0.287  & 0 \\
-AHZ7000002  &   90024700  &   GEMS    &   1   &   1   &   1.0   &   1   &   51  &   0.255   &   0.265   &   $-$0.107  &       0.264  &  $-$0.128    &     0.272  & 0 \\
-AHZ7000003  &   90024700  &   GEMS    &   0   &   1   &   5.0   &   1   &   47  &   0.170   &   0.167   &   $-$0.018  &    $-$0.018  &  $-$0.049    &     0.033  & 0 \\
-AHZ7000004  &   90024700  &   GEMS    &   0   &   1   &   10.0  &   1   &   41  &   0.195   &   0.195   &      0.045  &       0.045  &     0.044    &     0.127  & 0 \\
-AHZ7000005  &   90024700  &   GEMS    &   0   &   1   &   50.0  &   1   &   47  &   0.170   &   0.178   &      0.067  &       0.067  &     0.146    &     0.167  & 0 \\
-$\ldots$    \\
-AHZ700013m  &   90024700  &   GEMS    &   0   &   2   &   0.0   &   0   &   35  &   0.171   &   0.136   &      0.011  &       0.011  &     0.029    &      0.112 & 0 \\
-AHZ700013n  &   90024700  &   GEMS    &   1   &   2   &   0.2   &   1   &   20  &   0.150   &   0.158   &   $-$0.278  &       0.049  &  $-$0.351    &      0.049 & 0 \\
-AHZ700013o  &   90024700  &   GEMS    &   1   &   2   &   1.0   &   1   &   32  &   0.281   &   0.300   &   $-$0.086  &       0.281  &  $-$0.119    &      0.281 & 0 \\
-AHZ700013p  &   90024700  &   GEMS    &   0   &   2   &   5.0   &   1   &   29  &   0.103   &   0.115   &   $-$0.098  &    $-$0.098  &  $-$0.152    &   $-$0.069 & 0 \\
-AHZ700013q  &   90024700  &   GEMS    &   0   &   2   &   10.0  &   1   &   35  &   0.171   &   0.181   &      0.027  &       0.027  &     0.023    &      0.106 & 0 \\
-AHZ700013r  &   90024700  &   GEMS    &   0   &   2   &   50.0  &   1   &   34  &   0.206   &   0.206   &   $-$0.005  &    $-$0.005  &  $-$0.056    &      0.026 & 0 \\
-$\ldots$    \\
-\enddata
-\tablenotetext{1}{Flag indicating the color of the PSF in the simulated AGN. 0~=~no simulated AGN, 1~=~blue, 2~=~flat, 3~=~red.}
-\tablecomments{The full version of this table is available in electronic form,
-as well as at \url{http://data.galaxyzoo.org}. The complete version includes
-data for 2,961~galaxies and morphological information for all tasks in the
-tree. A subset of the information is shown here to illustrate form and
-content.}
-\end{deluxetable*}
+\clearpage
+\input{tables/main.tex}
+\input{tables/faded.tex}
+\input{tables/recolored.tex}
+\input{tables/goods-shallow.tex}
+\clearpage
+\input{tables/stripe82-single.tex}
+\input{tables/stripe82-coadded.tex}
+\input{tables/simulated-agn.tex}
+\clearpage
 
@@
 
-\acknowledgments
+\section*{Acknowledgements}
 KW, MG, CS, MB, and LF gratefully acknowledge support from the US National
@@
 
+\bibliographystyle{mnras}
 \bibliography{gz_hubble_data}
@@
 
+\bsp	% typesetting comment
+\label{lastpage}
 \end{document}

### 2016-05-30 writeup/gz_hubble_data.tex
Subfigure package does not work with mnras

@@
 \usepackage{graphicx}
-\usepackage{subfigure}
 \usepackage{url}
@@
 \centering
-
-\subfigure{[a]\label{fig:smooth_to_smooth}\includegraphics[width=\textwidth]{figures/smooth_to_smooth.pdf}}
-
-\subfigure{[b]\label{fig:smooth_to_int}\includegraphics[width=\textwidth]{figures/smooth_to_intermediate.pdf}}
-
-\subfigure{[c]\label{fig:smooth_to_featured}\includegraphics[width=\textwidth]{figures/smooth_to_featured.pdf}}
-
+\includegraphics[width=\textwidth]{figures/shallow_smooth.pdf}
 \caption{Example images of GOODS galaxies that compare GZH morphological
-classifications between their 2-epoch and 5-epoch imaging.  The top set (a)
+classifications between their 2-epoch and 5-epoch imaging.  The top set
 were classified as ``smooth'' in both the 2- and 5-epoch imaging. The
-middle set (b) was classified as ``smooth'' in the 2-epoch imaging and as
+middle set was classified as ``smooth'' in the 2-epoch imaging and as
 intermediate between ``smooth'' and ``featured'' in the 5-epoch imaging. The
-bottom set (c) was classified as ``smooth'' in the 2-epoch imaging and
-``featured'' in the 5-epoch imaging.}
+bottom set was classified as ``smooth'' in the 2-epoch imaging and
+``featured'' in the 5-epoch imaging (there are only seven such images
+in the sample).}
 \label{fig:shallow_smooth}
@@
 \centering
-
-\subfigure{[b]\label{fig:int_to_smooth}\includegraphics[width=\textwidth]{figures/intermediate_to_smooth.pdf}}
-
-\subfigure{[b]\label{fig:int_to_int}\includegraphics[width=\textwidth]{figures/intermediate_to_intermediate.pdf}}
-
-\subfigure{[b]\label{fig:int_to_featured}\includegraphics[width=\textwidth]{figures/intermediate_to_featured.pdf}}
-
+\includegraphics[width=\textwidth]{figures/shallow_intermediate.pdf}
 \caption{Similar to Figure~\ref{fig:shallow_smooth}. The top set (a) were
@@
 \centering
-
-\subfigure{[b]\label{fig:featured_to_smooth}\includegraphics[width=\textwidth]{figures/featured_to_smooth.pdf}}
-
-\subfigure{[b]\label{fig:featured_to_int}\includegraphics[width=\textwidth]{figures/featured_to_intermediate.pdf}}
-
-\subfigure{[b]\label{fig:featured_to_featured}\includegraphics[width=\textwidth]{figures/featured_to_featured.pdf}}
-
+\includegraphics[width=\textwidth]{figures/shallow_featured.pdf}
 \caption{Similar to Figure~\ref{fig:shallow_smooth}. The top set (a) were

### 2016-05-31 writeup/gz_hubble_data.tex
CJL last small edits

@@
 
-%\usepackage{epsfig}
 \usepackage{color,soul}
-%\usepackage{natbib}
 \usepackage{deluxetable}
@@
 \usepackage{url}
-%\usepackage[normalem]{ulem}
 \usepackage[T1]{fontenc}
@@
 \\
-%
 $^{1}$School of Physics and Astronomy, University of Minnesota, 116 Church St. SE, Minneapolis, MN 55455, USA \\
@@
 were selected from various publicly-released \textit{Hubble Space Telescope}
-Legacy programs using the Advanced Camera for Surveys, with filters that probe
+Legacy programs conducted with the Advanced Camera for Surveys, with filters that probe
 the rest-frame optical emission from galaxies out to $z\sim1$.  The bulk of the
@@
 
-The advent of larger telescopes in an increasing range of observing wavelengths
+The advent of larger telescopes sensitive to a full range of observing wavelengths
 has revealed that the distribution and properties of galaxy morphology have
@@
 structures seen in the present day. This growth occurs in a variety of
-pathways, including accretion of baryons from large-scale galactic filaments
+ways, including accretion of baryons from large-scale galactic filaments
 onto halos via streaming, mergers of individual dark matter halos along with
@@
 However, the public availability of more than $10^5$~galaxies in archival
-imaging has generated a data sample with the potential
+imaging has generated a sample with the potential
 for statistically-robust studies of galaxy demographics and evolution.
@@
     \zband{} images were taken in five separate epochs separated by 40--50~days
-    each. Images were dithered to a pixel scale of 0.03~\arcsec/pixel and covered a
+    each. GZH includes co-added images from GOODS at both 2-epoch and 5-epoch
+    depths. Images were dithered to a pixel scale of 0.03~\arcsec/pixel and covered a
     total area of $\sim320$~arcmin$^2$ (160~arcmin$^2$ per north/south field). The
@@
 framework \galapagos{} \citep{bar12}. GZH included all galaxies with $m<23.5$,
-where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS, GEMS +
+where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS \& COSMOS, GEMS \&
 GOODS-S (2-epoch), and GOODS-N (2-epoch) surveys, respectively. The full-depth
@@
 
-The project includes images from the SDSS \citep{yor00,str02}, in particular
+The GZH project also includes images from the SDSS \citep{yor00,str02}, in particular
 those from Data~Release~7 \citep{aba09}. A small number of images were used in
 the creation of simulated \hst{} images, described in Sections
-\ref{ssec:ferengi} and \ref{sec:debiasing} below; the majority of SDSS images
-used in GZH were from Stripe~82. The Stripe~82 samples in GZH include
+\ref{ssec:ferengi} and \ref{sec:debiasing} below. The majority of SDSS images
+used in GZH were from Stripe~82, including both
 single-epoch and co-added images. The single-epoch images provide a local
@@
 Images with simulated AGN were classified in the interface in an identical
-manner and evenly distributed with unaltered images of the galaxies.
+manner and were evenly distributed with unaltered images of the galaxies.
 Volunteers were not explicitly told that the images had been altered during
@@
 In addition to the physical parameters of the input images, the \ferengi{}
-output depends on assumptions of the global galaxy evolution model. This
-evolution is a crude mechanism that mimics the brightness increase of galaxies
+output depends on assumptions of the global galaxy evolution model.
+This evolution is parameterized by a crude model that mimics the brightness increase of galaxies
 with increasing redshift \citep[\eg,][]{lil98,lov12}. The effect on the
@@
 available, the 1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST,
-MUSYC, UltraVISTA;][]{ilb13} and UltraVISTA grism data were used to select the
-estimated redshift with the smallest error. 
+MUSYC, UltraVISTA;][]{ilb13} and UltraVISTA grism data were used. The
+measurement with the smallest reported 1-$\sigma$ error was selected in each
+case.
 %Table~\ref{tbl:redshifts} shows the results of this selection.
@@
 
-Classifications were aggregated and weighted only if the classifier was logged
-into GZH under their username (which was encouraged, but not required for
+Classifications for GZH were weighted only if the classifier was logged
+into the site under their username (this was encouraged, but not required for
 participation). Classifications by participants who were not logged in were marked as
@@
 
-In GZH, the redshift range is large enough that cosmological evolution of the
+Instead, in GZH the redshift range is large enough that cosmological evolution of the
 types and morphologies of galaxies is expected for the \hst{} sample. In
@@
 The unshaded regions in Figure~\ref{fig:f_vs_f} define discrete ranges of redshift,
-surface brightness, and \ffeatures{} a galaxy must have in order for the
-debiased correction to be confidently applied to a galaxy in the GZH sample.
-While the appropriate correctable regions were defined discretely, the true
+surface brightness, and \ffeatures{} within which a galaxy must lie in order for the
+debiased correction to be confidently applied.
+While the appropriate correctable regions were defined as discrete bins, the true
 correctable region is assumed to be a smooth function of $z$, $\mu$, and
@@
 monotonic, and 56\% cannot be debiased since they either have an unknown
-redshift or insufficient numbers of \ferengi{} images in their $z$-$\mu$ value
+redshift or insufficient numbers of \ferengi{} images in their $z$-$\mu$ bin
 to determine a reliable value of $\zeta$.
@@
 overlap sample is tiny, though, detailed comparisons between the overall
-morphologies are highly difficult.
+morphologies are highly difficult (see
+Sections~\ref{ssec:comparisons}--\ref{ssec:gzh_gzc}).
 
@@
 criteria for vote fraction thresholds to create a morphologically pure sample.
-Table~\ref{tbl:thresholds} provides baseline cuts for selecting galaxies of a
-variety of morphologies. These thresholds are determined by a visual inspection
-of subsamples. The thresholds used are a combination of 20~votes for the
+Table~\ref{tbl:thresholds} provides suggested cuts for selecting galaxies with a
+variety of morphologies. These thresholds were determined by visual inspection
+of various subsamples of GZH data. The thresholds employ a combination of 20~votes for the
 task being considered, as well as limits on the vote fractions for previous

### 2016-05-31 writeup/gz_hubble_data.tex
Text is now Britishised.

@@
 large effort to measure reliable, detailed morphologies of galaxies by using
-crowdsourced visual classifications of color composite images. Images in GZH
+crowdsourced visual classifications of colour composite images. Images in GZH
 were selected from various publicly-released \textit{Hubble Space Telescope}
@@
 different redshifts by using artificially-redshifted galaxy images as a
-baseline. The GZH catalog contains both raw and calibrated morphological vote
+baseline. The GZH catalogue contains both raw and calibrated morphological vote
 fractions for $119,849$~galaxies, providing the largest dataset to date
@@
 galaxies:structure --- galaxies:high redshift --- galaxies:evolution
---- methods:data analysis --- catalogs
+--- methods:data analysis --- catalogues
 \end{keywords}
@@
 sequence/tuning fork \citep{hub36} is not a suitable framework for
-characterizing high-redshift morphology.
+characterising high-redshift morphology.
 
@@
 providing the angular resolution to distinguish internal structure and
-characterize the morphology. While these measurements are helped by the fact
+characterise the morphology. While these measurements are helped by the fact
 that the angular diameter distance is relatively flat beyond $z>1$ in a flat
@@
 asymmetric galaxies that become increasingly common at high redshifts. The
-Galaxy Zoo project \citep{lin08,for12} utilizes crowdsourced visual classifications
-to measure galaxies in color-composite images. The efforts of more than
+Galaxy Zoo project \citep{lin08,for12} utilises crowdsourced visual classifications
+to measure galaxies in colour-composite images. The efforts of more than
 $2\times10^5$~classifiers allow for multiple independent classifications of
@@
 process used to calibrate and correct the crowdsourced vote fractions for
-redshift-dependent bias. Section~\ref{sec:results} gives the main catalog of
+redshift-dependent bias. Section~\ref{sec:results} gives the main catalogue of
 results, with several examples of how the data may be queried in
@@
 of the observed morphological demographics and compares them to several other
-catalogs, with a summary in Section~\ref{sec:summary}.
+catalogues, with a summary in Section~\ref{sec:summary}.
 
@@
 unfilled black curves show the filters for the Suprime Camera on \subaru, which
-was used to create color gradients in the GZH COSMOS
+was used to create colour gradients in the GZH COSMOS
 images.}
@@
 \item The All-Wavelength Extended Groth Strip International Survey
-    \citep[AEGIS;][]{dav07} covers a strip centered at
+    \citep[AEGIS;][]{dav07} covers a strip centred at
     $\alpha=14^\textrm{h}17^\textrm{m}, \delta=+52^\circ30^\prime$. This area
@@
 \item The Galaxy Evolution from Morphologies and SEDs
-    \citep[GEMS;][]{rix04,cal08} survey was centered on the Chandra Deep
+    \citep[GEMS;][]{rix04,cal08} survey was centred on the Chandra Deep
     Field-South. The GEMS data covered $\sim800$~arcmin$^2$, completely surrounding
@@
 \item The Cosmic Evolution Survey \citep[COSMOS;][]{sco07} covered an area of
-    $\sim1.8$~deg$^2$ centered at $\alpha=10^\textrm{h}00^\textrm{m},
+    $\sim1.8$~deg$^2$ centred at $\alpha=10^\textrm{h}00^\textrm{m},
     \delta=+02^\circ12^\prime$. Its location near the celestial equator was
@@
 
-Images from \hst{} legacy surveys were used to create multiple different color
-and grayscale images using different depths and filter combinations; these are
+Images from \hst{} legacy surveys were used to create multiple different colour
+and greyscale images using different depths and filter combinations; these are
 described further in Section \ref{ssec:images}. Additionally, the use of a
@@
 morphological classifications.  The presence of an AGN was simulated by
-modeling the point spread function (PSF) of the telescope and then inserting a
-bright source near the center of a real galaxy. For each image, the simulated
-AGN was assigned one of three colors -- either blue, red, or flat (white) as
-seen in the color images -- and a range of brightnesses such that
+modelling the point spread function (PSF) of the telescope and then inserting a
+bright source near the centre of a real galaxy. For each image, the simulated
+AGN was assigned one of three colours -- either blue, red, or flat (white) as
+seen in the colour images -- and a range of brightnesses such that
 $L_\mathrm{ratio} \equiv L_\mathrm{galaxy}/L_\mathrm{AGN}$ is in
@@
 %The selection criteria for the different morphological categories is
-%summarized in Table \ref{tbl:morphologies}.
+%summarised in Table \ref{tbl:morphologies}.
 
@@
 output depends on assumptions of the global galaxy evolution model.
-This evolution is parameterized by a crude model that mimics the brightness increase of galaxies
+This evolution is parameterised by a crude model that mimics the brightness increase of galaxies
 with increasing redshift \citep[\eg,][]{lil98,lov12}. The effect on the
@@
 
-\subsection{Creating color images}\label{ssec:images}
-
-The images used for classification in GZH were color-composite JPEGs made from
+\subsection{Creating colour images}\label{ssec:images}
+
+The images used for classification in GZH were colour-composite JPEGs made from
 multi-band data. These were created following the method of \citet{lup04}, which
-preserves color information irrespective of intensity.  An asinh intensity
+preserves colour information irrespective of intensity.  An asinh intensity
 mapping was applied to enhance the appearance of faint features while avoiding
-saturating galaxy centers. The relative scalings of the filter bands were
-chosen while trying to reproduce the color appearance of the SDSS images in
+saturating galaxy centres. The relative scalings of the filter bands were
+chosen while trying to reproduce the colour appearance of the SDSS images in
 previous iterations of Galaxy Zoo.
@@
 The COSMOS survey provides only \Iband{} HST imaging. For these galaxies, GZH
-used ``pseudocolor'' images created by using the ACS \Iband{} data as an
+used ``pseudocolour'' images created by using the ACS \Iband{} data as an
 illumination map and ground-based imaging from the \subaru{} telescope in
-$B_J$, $r^+$, and $i^+$ filters to provide color information (see
+$B_J$, $r^+$, and $i^+$ filters to provide colour information (see
 \citealt{gri12} for further details). This resulted in images with the angular
 resolution of \hst{} ($\sim0.05$~\arcsec/pixel) for the overall intensity, but
-color gradients at ground-based resolution, with seeing between 0.95\arcsec{}
+colour gradients at ground-based resolution, with seeing between 0.95\arcsec{}
 and 1.05\arcsec{} \citep{tan07}.
@@
 RGB channels \citep{nie04}. The co-added Stripe~82 images were assembled from runs 106 and
-206 in DR7 and processed into color composites in the same manner as previous
+206 in DR7 and processed into colour composites in the same manner as previous
 iterations of Galaxy~Zoo.
 
-In some cases, we found that attempting to emphasize faint features in the
-images resulted in the sky noise taking the appearance of brightly colored
+In some cases, we found that attempting to emphasise faint features in the
+images resulted in the sky noise taking the appearance of brightly-coloured
 speckles. This impaired the aesthetics of the images and might have been a
 distraction to visual classification.  To counteract this, a soft-edged object
-mask was applied to the color images and a desaturation operation performed.
-This masking procedure was effective in preserving the color balance for
-galaxies and retained the visibility of faint features, while reducing the color
+mask was applied to the colour images and a desaturation operation performed.
+This masking procedure was effective in preserving the colour balance for
+galaxies and retained the visibility of faint features, while reducing the colour
 contrast in the sky noise and greatly improving the appearance of the images.
@@
 
-In addition to the primary \hst{} legacy imaging sample with colored images
+In addition to the primary \hst{} legacy imaging sample with coloured images
 described as above, GZH also includes samples of \hst{} galaxy images with
-different color prescriptions. In particular, there are two sets of 3,927~images
-each, drawn from the COSMOS sample; the first has a dramatically reduced color
-saturation, and the second has reversed the colors so that the blue and red
+different colour prescriptions. In particular, there are two sets of 3,927~images
+each, drawn from the COSMOS sample; the first has a dramatically reduced colour
+saturation, and the second has reversed the colours so that the blue and red
 filters have exchanged places in the RGB image. The `faded' galaxy set
 facilitates measuring of possible variations in classification due to the
-presence or absence of color features. The `recolored' set enables an
-alternative test of potential color biases in classifications.
+presence or absence of colour features. The `recoloured' set enables an
+alternative test of potential colour biases in classifications.
 % I guess this means we need to say somewhere later that we don't see an effect
@@
 
-The simulated AGN host galaxy color images (described in Section \ref{ssec:sim_agn})
+The simulated AGN host galaxy colour images (described in Section \ref{ssec:sim_agn})
 were created using the same prescription as for the GOODS 2-epoch imaging. The
-artificially redshifted color images (Section \ref{ssec:ferengi}) were created using the
+artificially redshifted colour images (Section \ref{ssec:ferengi}) were created using the
 same prescription as for the AEGIS images.
@@
 The full GZH sample is composed of 8~different galaxy sub-samples. Throughout
-this paper and in the published catalogs they are referred to with the
+this paper and in the published catalogues they are referred to with the
 following labels:
@@
 %\ref{tbl:catalog_hst}
-\item \main: \hst{} imaging with RGB colors making use of all available
+\item \main: \hst{} imaging with RGB colours making use of all available
 filters with typical saturation and in correct order, as described in
@@
 %\ref{tbl:catalog_faded}
-\item \faded: a subset of COSMOS images with very low color saturation.
+\item \faded: a subset of COSMOS images with very low colour saturation.
 (3,927~galaxies)
@@
 \item \goods: Images from GOODS-North and GOODS-South, with
-color from 2~filters and imaged at 2-epoch depth. (6,144~galaxies)
+colour from 2~filters and imaged at 2-epoch depth. (6,144~galaxies)
 
@@
 
-Redshifts for the GZH catalog were compiled from a variety of sources. For each
+Redshifts for the GZH catalogue were compiled from a variety of sources. For each
 galaxy, the primary redshift is in the $\tt Z\_BEST$ column of
-Table~\ref{tbl:catalog_hst}. The redshift type (spectroscopic: $\tt SPEC\_Z$,
+Table~\ref{tbl:catalogue_hst}. The redshift type (spectroscopic: $\tt SPEC\_Z$,
 photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column
-$\tt Z\_BEST\_TYPE$, and the source catalog of the redshift is included as $\tt
+$\tt Z\_BEST\_TYPE$, and the source catalogue of the redshift is included as $\tt
 Z\_BEST\_SOURCE$.
@@
 provided in the ACS-GC \citep{gri12}, 3DHST \citep{mom15}, and MUSYC
-\citep{car10} catalogs and used in that order. For galaxies with multiple
+\citep{car10} catalogues and used in that order. For galaxies with multiple
 spectroscopic redshifts, more than 98\% are consistent ($\Delta z<0.001$), and
 so the order of selection made no practical difference. Galaxies with
-inconsistent spectroscopic redshifts between any pair of catalogs are marked
-with a flag in Table~\ref{tbl:catalog_hst}.  If no spectroscopic redshifts were
+inconsistent spectroscopic redshifts between any pair of catalogues are marked
+with a flag in Table~\ref{tbl:catalogue_hst}.  If no spectroscopic redshifts were
 available, the 1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST,
@@
 %\includegraphics[width=160mm]{figures/specz_comparison.pdf}
-%\caption{Spectroscopic redshifts from the ACS-GC, 3DHST, and MUSYC catalogs.
+%\caption{Spectroscopic redshifts from the ACS-GC, 3DHST, and MUSYC catalogues.
 %The number in the upper left of each plot is the percentage of redshifts which
-%agree within $\Delta z < 0.05$ between the two catalogs being compared in each
+%agree within $\Delta z < 0.05$ between the two catalogues being compared in each
 %panel. Within this range there is over 98\% agreement in redshifts between all
-%three catalogs.}
+%three catalogues.}
 %\label{fig:speczs}
@@
 The front-end runs on a Ruby~on~Rails framework with classifications stored in
-a MySQL backend. Classifiers were shown a randomly-selected color composite image from
+a MySQL backend. Classifiers were shown a randomly-selected colour composite image from
 the GZH sample; the default showed the image with a black sky background,
-although they had the option to invert the color palette if desired. The
+although they had the option to invert the colour palette if desired. The
 questions and responses for morphology appeared on the right side of the image as
@@
 \caption{Flowchart of the questions presented to GZH classifiers, labeled with
-the corresponding task numbers. Tasks in the decision tree are color-coded by
-tier level: Gray-colored tasks are 1$^\mathrm{st}$-tier questions which are
-asked in every classification. Tasks colored green, blue, purple, and pink
+the corresponding task numbers. Tasks in the decision tree are colour-coded by
+tier level: Grey-coloured tasks are 1$^\mathrm{st}$-tier questions which are
+asked in every classification. Tasks coloured green, blue, purple, and pink
 (respectively) are one, two, three, or four steps below branching points in the
@@
 tree (Figure~\ref{fig:decisiontree}). Every classification began with the step of
-identifying whether the object at the center of the image was a smooth galaxy,
+identifying whether the object at the centre of the image was a smooth galaxy,
 a galaxy with a disk or other features, or a star/artifact. Subsequent
@@
 $r$-band surface brightnesses.  The overall selection spanned the
-redshift range of SDSS targets and maximized the number of \hst{} galaxies at
+redshift range of SDSS targets and maximised the number of \hst{} galaxies at
 the same surface brightness and redshift (Figure~\ref{fig:sb_redshift}).  The
@@
 images and the 102,548~\main{} galaxies with measured $\mu$ and $z$ values. The
-color histogram shows the number of \ferengi{} images as a function of $\mu$
+colour histogram shows the number of \ferengi{} images as a function of $\mu$
 and $z_{\rm sim}$. White contours show counts for the galaxies in the \main{}
@@
 \includegraphics[width=\textwidth]{figures/zeta_examples_sorted.pdf}
-\caption{Behavior of the normalized, weighted vote fractions of features
+\caption{Behaviour of the normalised, weighted vote fractions of features
 visible in a galaxy ($f_\textrm{features}$) as a function of redshift in the
@@
 those in which there is not are blue, and those with not enough data ($N<5$)
-are gray. A larger version of the bin outlined at $z=1.0$ and $20.3 < \mu <
+are grey. A larger version of the bin outlined at $z=1.0$ and $20.3 < \mu <
 21.0$ $\rm (mag/arcsec^2)$ is shown in Figure~\ref{fig:f_vs_f_zoom}.}
@@
 redshift bin, the relationship between \ffeaturesz{} and \ffeaturesrest{} is
-modeled by fitting the data with polynomials of degrees $n=3$, 2, and 1, and
+modelled by fitting the data with polynomials of degrees $n=3$, 2, and 1, and
 using the best formal fit out of the three as measured by the sum of the
@@
 that the weighted \ffeatures{} is a lower limit to the true value.  These
-regions are highlighted in blue in Figure~\ref{fig:f_vs_f}. Uncolored (white)
+regions are highlighted in blue in Figure~\ref{fig:f_vs_f}. Uncoloured (white)
 regions of the plot have sufficiently high slopes to consider the relationship
@@
 to have ``not enough information'' to determine the \ffeaturesz{} and
-\ffeaturesrest{} relationship, colored gray in Figure~\ref{fig:f_vs_f}. These
+\ffeaturesrest{} relationship, coloured grey in Figure~\ref{fig:f_vs_f}. These
 galaxies are hereafter referred to as the ``NEI'' sample.
@@
 $z$-$\mu$-\ffeatures{} space. The boundaries are then adjusted until the
-contamination from both groups is minimized. The resulting hulls define the
-correctable and lower-limit regions for categorizing the \hst{} galaxies. The
-results of this method and final categorization of the \hst{} sample are in
+contamination from both groups is minimised. The resulting hulls define the
+correctable and lower-limit regions for categorising the \hst{} galaxies. The
+results of this method and final categorisation of the \hst{} sample are in
 Table~\ref{tbl:hubble_debiasable}. Of the galaxies at redshift higher than
@@
 cannot be confidently assigned, the \emph{range} of debiased values is
-estimated using a method visualized in Figure~\ref{fig:f_vs_f_zoom}. This uses the
-\ferengi{} simulated data to analyze the range of intrinsic \ffeaturesrest{}
+estimated using a method visualised in Figure~\ref{fig:f_vs_f_zoom}. This uses the
+\ferengi{} simulated data to analyse the range of intrinsic \ffeaturesrest{}
 values for any given observed \ffeatures{} value, again as a function of
@@
 the data in each redshift-surface brightness bin, as was done for Task~01. The
-goodness-of-fit was evaluated in each bin, for each Task, using a normalized
+goodness-of-fit was evaluated in each bin, for each Task, using a normalised
 $\chi^2$ metric. The mean $\chi^2$ for all higher-order tasks was
 $0.10\pm0.04$, significantly larger than the Task~01 value of $0.04$. Based on
-this statistic, the data cannot not be modeled with sufficient confidence for
+this statistic, the data cannot not be modelled with sufficient confidence for
 the higher order tasks. An example of the debiasing technique applied to
@@
 to a degree at which no strong correlation is present.  For these reasons,
-debiased vote fractions are only offered in the GZH catalog for Task~01
+debiased vote fractions are only offered in the GZH catalogue for Task~01
 (smooth/features).
@@
 %of surface-brightness levels and 7~evolutionary corrections (this last bit is
-%indicated by the color). 
+%indicated by the colour). 
 %
@@
 %NO USER WEIGHTING.... For a range of vote fraction levels with three
-%surface-brightness levels and 7 evolutionary corrections each (the colors
+%surface-brightness levels and 7 evolutionary corrections each (the colours
 %indicate evolutionary correction value with green being $e=0$, we show the
@@
 
-\section{The Galaxy Zoo: Hubble catalog}\label{sec:results}
-
-The catalog for GZH includes morphological data for 189,149~images
+\section{The Galaxy Zoo: Hubble catalogue}\label{sec:results}
+
+The catalogue for GZH includes morphological data for 189,149~images
 (generated from a total of 145,741~unique galaxies). The full table can be
@@
 
-The GZH catalog is corrected for redshift bias only for the first
+The GZH catalogue is corrected for redshift bias only for the first
 question of the GZH decision tree (Section~\ref{sec:debiasing}), which asks
 {\it ``Is the galaxy smooth and round, with no sign of a disk?''} For this
-question, the catalog provides the additional parameters $\tt debiased$, $\tt
+question, the catalogue provides the additional parameters $\tt debiased$, $\tt
 lower~limit$, $\tt upper~limit$, and $\tt best$ vote fractions. The $\tt best$
@@
 
-Tables~\ref{tbl:catalog_hst}-\ref{tbl:simulated_agn} also contain flags for
+Tables~\ref{tbl:catalogue_hst}-\ref{tbl:simulated_agn} also contain flags for
 Task 01 that identify clean (but not complete) samples of galaxies with high
@@
 sample in Section~\ref{ssec:sample_labels} corresponds to the data in
-Tables~\ref{tbl:catalog_hst}-\ref{tbl:simulated_agn}.
+Tables~\ref{tbl:catalogue_hst}-\ref{tbl:simulated_agn}.
 
@@
 
-\section{Using the catalog}\label{sec:cookbook}
-
-The primary purpose of the GZH catalog is to provide a reliable method of
+\section{Using the catalogue}\label{sec:cookbook}
+
+The primary purpose of the GZH catalogue is to provide a reliable method of
 selecting galaxies of a desired morphological type.  This section provides
@@
 
-The flexibility of this catalog allows users to set their own selection
+The flexibility of this catalogue allows users to set their own selection
 criteria for vote fraction thresholds to create a morphologically pure sample.
@@
 
-We visually analyzed subsamples of 50~galaxies meeting both
+We visually analysed subsamples of 50~galaxies meeting both
 criteria, as well as a control sample of galaxies which had 20~classifiers vote on
@@
 galaxies. We note that their technique matched test and control galaxies over
-the same redshift ranges, which minimizes the possible impact of redshift bias.
+the same redshift ranges, which minimises the possible impact of redshift bias.
 
@@
 \citep{elm05,elm14,guo15,beh16}. Simulations show clumps migrate from the outer
-disk to the galactic center in only a few orbital periods \citep{man15} and
+disk to the galactic centre in only a few orbital periods \citep{man15} and
 observations show increasing bulge to clump mass and density ratios as the
@@
 consider morphology with respect to other physical properties of the sample,
-such as color, mass, size, environment, and redshift. We defer such analyses to
+such as colour, mass, size, environment, and redshift. We defer such analyses to
 later papers, and comment here only on a few broad characteristics of the
@@
 galaxies outnumbering disks and clumpy galaxies by a factor of $\sim3:1$,
-however. The fraction of objects identified as stars or artifact is also much
+however. The fraction of objects identified as stars or artifacts is also much
 higher in the \hst{} imaging. By plurality votes, these encompass only
@@
 
-\subsection{Comparing GZH morphologies to other catalogs}\label{ssec:comparisons}
+\subsection{Comparing GZH morphologies to other catalogues}\label{ssec:comparisons}
 
 All of the Legacy surveys included in the GZH imaging have had morphological
-catalogs previously published; these catalogs have significant differences in
+catalogues previously published; these have significant differences in
 the number of galaxies, size and magnitude limits, classification scheme, and
-the methods used for measuring morphology. These catalogs have been
+the methods used for measuring morphology. These catalogues have been
 cross-matched to GZH to compare the results. This is not presented as an
 endorsement of any particular method, but as an exploration of the strengths
-and weaknesses of the Galaxy~Zoo crowdsourced catalogs compared to products
+and weaknesses of the Galaxy~Zoo crowdsourced catalogues compared to products
 made with machine learning, automatic fits, and expert visual classification.
@@
 the shallowest depths \citep[GEMS;][]{bun05} and the limits on morphological
-reliability \citep[COSMOS/ZEST;][]{sca07} in the comparison catalogs. We match
-all catalogs against GZH using a positional radius of 0.5\arcsec.
+reliability \citep[COSMOS/ZEST;][]{sca07} in the comparison catalogues. We match
+all catalogues against GZH using a positional radius of 0.5\arcsec.
 
@@
 8,846~galaxies in both \citet{hau07} and GZH. The primary morphological
-parameter in the automated catalog is the \sersic{} index $n$ defining the
+parameter in the automated catalogue is the \sersic{} index $n$ defining the
 radial surface brightness profile.  ``Elliptical'' galaxies are selected by
@@
 visually classified by a single expert (R.S.~Ellis), inspecting both $z$-band
-and composite $Viz$ color images \citep{bun05}. These morphologies are assigned
+and composite $Viz$ colour images \citep{bun05}. These morphologies are assigned
 a numerical value based on categories in \citet{bri98a}: the corresponding
@@
 ($z<1.0$, $m<22.5$) of galaxies matched between GZH and six published
-morphological catalogs, split by survey (AEGIS, COSMOS, GEMS, and GOODS). This
+morphological catalogues, split by survey (AEGIS, COSMOS, GEMS, and GOODS). This
 plot shows the fraction of overall galaxies for each of the external
@@
 Figure~\ref{fig:comparisons_features} shows the proportion of galaxies as split
-by their automated/expert visual morphologies for each of the six catalogs
-matched to GZH. Galaxies from every catalog show a strong correlation between
+by their automated/expert visual morphologies for each of the six catalogues
+matched to GZH. Galaxies from every catalogue show a strong correlation between
 \fbest{} and the fraction of galaxies identified as spirals, with a
@@
 
-Galaxies from the three COSMOS morphology catalogs all have morphologies that are
+Galaxies from the three COSMOS morphology catalogues all have morphologies that are
 reasonably well-predicted by the GZH based on \fbest. The relation is strongest
@@
 
-%We also emphasize that the previously published COSMOS catalogs are not
+%We also emphasise that the previously published COSMOS catalogues are not
 %internally consistent; for example, only 64\% of the galaxies in \citet{tas11}
@@
 %another (\citealt{cas07} is more likely to classify galaxies as irregular).  A
-%detailed comparison of the external catalogs is outside the scope of this
-%paper, but we emphasize only that it is \emph{impossible} for any catalog to be
+%detailed comparison of the external catalogues is outside the scope of this
+%paper, but we emphasise only that it is \emph{impossible} for any catalogue to be
 %consistent with all three.  We interpret the broad agreements between
@@
 %
-%Figure~\ref{fig:comparisons_odd} analyzes the same sets of matched galaxies, but
+%Figure~\ref{fig:comparisons_odd} analyses the same sets of matched galaxies, but
 %compares the data to the \fodd{} parameter in GZH to examine its correlation with
 %irregular morphologies. The relationship in this case is less clear; for the
-%COSMOS catalogs, in particular, early-types, spirals, and irregulars are
+%COSMOS catalogues, in particular, early-types, spirals, and irregulars are
 %roughly equally probable at \fodd$>0.5$. In both AEGIS and GOODS (there is no
@@
 
-A detailed comparison of the external catalogs is outside the scope of this
-paper, but we emphasize only that it is impossible for any catalog to be fully
+A detailed comparison of the external catalogues is outside the scope of this
+paper, but we emphasise only that it is impossible for any catalogue to be fully
 consistent with all of the previously published datasets (for example, only
@@
 We repeated all analyses comparing morphologies between GZH and external
-catalogs on the entire catalog, rather than the volume-limited sample
+pulblications on the entire GZH dataset, rather than the volume-limited sample
 ($z<1.0,m<22.5$) discussed above. If galaxies at all redshifts and at the
@@
 exceptions are the GEMS galaxies, which are the only sample that was visually
-classified and had a shallower magnitude cut on their catalog.
-Based on these comparisons, we suggest that use of the GZH catalog be limited
+classified and had a shallower magnitude cut on their catalogue.
+Based on these comparisons, we suggest that use of the GZH catalogue be limited
 to galaxies with $m_\mathrm{I|i|z}<22.5$; fainter targets at the sensitivity of the \hst{}
@@
 
-This paper presents the catalog release for the Galaxy Zoo Hubble project,
+This paper presents the catalogue release for the Galaxy Zoo Hubble project,
 which uses crowdsourced visual classifications to measure galaxy morphologies.
@@
 surveys using the Advanced Camera for Surveys on the \hubble,
-including AEGIS, GEMS, GOODS-N, GOODS-S, and COSMOS. The catalog also includes
+including AEGIS, GEMS, GOODS-N, GOODS-S, and COSMOS. The catalogue also includes
 classifications for SDSS images from Stripe~82 at $z<0.25$; these images
@@
 
-The data for the GZH catalogs has been extensively tested and reduced. The
+The data for the GZH catalogues has been extensively tested and reduced. The
 dominant effect is a known bias against identifying disky and asymmetric
@@
 
-The full data tables for the catalogs can be accessed in machine-readable form
+The full data tables for the catalogues can be accessed in machine-readable form
 from both the journal and at \url{http://data.galaxyzoo.org}. All the code and
@@
 GZH used both 5-epoch and 2-epoch sets of data to construct the GOODS set of
-images. The 11,157 full depth 5-epoch images are used in the \main{} catalog; the
+images. The 11,157 full depth 5-epoch images are used in the \main{} catalogue; the
 classifications for the 6,144 \goods{} images are provided as a
-supplementary table. This section analyzes the effect of image depth on the
+supplementary table. This section analyses the effect of image depth on the
 ability of the Galaxy~Zoo classifiers to identify features or disk structure in the images.
@@
 redshift or surface brightness, data from simulated \ferengi{} images were
-modeled with functions in discrete redshift and surface brightness bins
+modelled with functions in discrete redshift and surface brightness bins
 (Section~\ref{ssec:zeta_results}). A cut of $N>10$ was placed on the number of
@@
 inhibit fitting a reliable function that predicts $f_{{\rm bar},z=0.3}$.
-Table~\ref{tbl:ferengi_bar} summarizes the correction types for the
+Table~\ref{tbl:ferengi_bar} summarises the correction types for the
 \ferengi{} data; 71\% of the galaxies simulated did not meet the GZH
@@
 redshift and at $z=0.3$ are marked in white; those in which there is not
-are blue, and those with not enough data ($N<5$) are gray. A larger version of
+are blue, and those with not enough data ($N<5$) are grey. A larger version of
 the bin outlined at $z=1.0$ and $20.3 < \mu < 21.0$ $\rm (mag/arcsec^2)$ is
-shown in Figure~\ref{fig:f_vs_fbar_zoom}. The mean normalized $\chi^2$ of the
+shown in Figure~\ref{fig:f_vs_fbar_zoom}. The mean normalised $\chi^2$ of the
 change in vote fraction is 0.08. None of the correlations for higher-order
-tasks (including bars) were applied to galaxies in the GZH catalog.}
+tasks (including bars) were applied to galaxies in the GZH catalogue.}
 \label{fig:f_vs_fbar}
@@
 \label{tbl:ferengi_bar}
-\caption{Distribution of \ferengi{} images analyzed in
+\caption{Morphological correction categories for the \ferengi{} images summarised in
 Figure~\ref{fig:f_vs_fbar}. Correctable images had a single-valued relationship
@@
 relationships due to a lack of data ($N<5$) in their corresponding $z$-$\mu$
-bins (gray regions). Only 17\% (maximum) of \ferengi{} galaxies in the sample
+bins (grey regions). Only 17\% (maximum) of \ferengi{} galaxies in the sample
 were considered ``correctable'', which is not sufficient to compute a $\zeta$

### 2016-05-31 writeup/gz_hubble_data.tex
Switching order of 7.2 and 7.3

@@
 
+\subsection{Galaxy Zoo: Hubble and Galaxy Zoo: CANDELS}\label{ssec:gzh_gzc}
+
+There are 7,681~galaxies in the GOODS-S field with morphological
+classifications in both GZH and the Galaxy~Zoo:~CANDELS project (Simmons
+et~al., submitted). Since both the sensitivity and filters for the two sets of
+images are significantly different (and there is no correction for redshift
+bias applied to GZC), there is no prior reason to expect a perfect correlation
+between the separate vote fractions for the projects. Briefly, we note that the
+\ffeatures{} value for GZH is on average higher than GZC; the effect is
+strongest at $f_\mathrm{features,GZC}<0.3$, for which roughly half the galaxies
+have $f_\mathrm{features,GZH}>0.5$. However, the correlation between vote
+fractions is single-valued (although not linear, with a Pearson correlation
+coefficient of $r=0.6$), and should be possible to calibrate using a similar
+approach to that described in Section~\ref{sec:debiasing}; the correlation
+between other tasks, such as edge-on galaxies is significantly stronger
+($r=0.9$). So while the raw vote fractions are not directly comparable, the
+initial analysis indicates that the broad morphologies are at least consistent.
+
 \subsection{Comparing GZH morphologies to other catalogues}\label{ssec:comparisons}
@@
 the methods used for measuring morphology. These catalogues have been
-cross-matched to GZH to compare the results. This is not presented as an
-endorsement of any particular method, but as an exploration of the strengths
-and weaknesses of the Galaxy~Zoo crowdsourced catalogues compared to products
-made with machine learning, automatic fits, and expert visual classification.
+cross-matched to GZH to compare the results. 
+%This is not presented as an
+%endorsement of any particular method, but as an exploration of the strengths
+%and weaknesses of the Galaxy~Zoo crowdsourced catalogues compared to products
+%made with machine learning, automatic fits, and expert visual classification.
 
@@
 Morphologies for GEMS galaxies were measured by \citet{hau07}, who used
-single-component \sersic{} fits to the F850LP imaging. A 1\arcsec~positional
-match for the GEMS galaxies in Table~9 in \citet{hau07} to the GZH sample gives
-8,846~galaxies in both \citet{hau07} and GZH. The primary morphological
+single-component \sersic{} fits to the F850LP imaging. There are 8,846~galaxies
+with measurements in both \citet{hau07} and GZH. The primary morphological
 parameter in the automated catalogue is the \sersic{} index $n$ defining the
@@
 with the exception of assigning S0/bulge-dominated disks (type~2.0) from ZEST
-into the early-type category.
+into the unfeatured category.
 
@@
 
-The AEGIS sample had the fewest number of matched galaxies (485) with GZH;
-while the statistical uncertainties are as a result higher, the strongest
-difference between spirals and early-types is seen at \fbest$>0.8$. GOODS
-galaxies, which are the only comparison sample that also uses visual
-morphology, shows a very similar trend, with nearly 100\% pure samples at
-the lowest and highest values of \fbest.  Galaxies from GEMS (which are
-only split into two types) also have a strong correlation with \fbest,
-which is somewhat surprising (but encouraging) considering the known limits
-of assigning galaxy morphology based only on a single \sersic{} parameter.
-
+The AEGIS sample had only 485~galaxies matched with GZH, and so the statistical
+uncertainties in the analysis are higher. However, at \fbest$>0.8$ there is a
+clear separation of featured and unfeatured galaxies, though this is not seen
+at lower \fbest.  GOODS galaxies, which are the only comparison sample that
+also uses visual morphology, shows a very similar trend, with nearly 100\% pure
+samples at the lowest and highest values of \fbest.
+
+Galaxies from GEMS (which
+are only split into two types) also have a strong correlation with \fbest,
+which is somewhat surprising (but encouraging) considering the known limits of
+assigning galaxy morphology based only on a single \sersic{} parameter. 
 Visual inspection of images of the exceptions --- where both \fbest{} and $n$
@@
 exceptions are the GEMS galaxies, which are the only sample that was visually
-classified and had a shallower magnitude cut on their catalogue.
-Based on these comparisons, we suggest that use of the GZH catalogue be limited
-to galaxies with $m_\mathrm{I|i|z}<22.5$; fainter targets at the sensitivity of the \hst{}
-Legacy surveys have been demonstrated to be less reliable, regardless of the
-method of morphological classification being used.
-
-\subsection{Galaxy Zoo: Hubble and Galaxy Zoo: CANDELS}\label{ssec:gzh_gzc}
-
-Finally, there are 7,681~galaxies in the GOODS-S field with morphological
-classifications in both GZH and the Galaxy~Zoo:~CANDELS project (Simmons
-et~al., submitted). Since both the sensitivity and filters for the two sets of
-images are significantly different (and there is no correction for redshift
-bias applied to GZC), there is no prior reason to expect a perfect correlation
-between the separate vote fractions for the projects. Briefly, we note that the
-\ffeatures{} value for GZH is on average higher than GZC; the effect is
-strongest at $f_\mathrm{features,GZC}<0.3$, for which roughly half the galaxies
-have $f_\mathrm{features,GZH}>0.5$. However, the correlation between vote
-fractions is single-valued (although not linear, with a Pearson correlation
-coefficient of $r=0.6$), and should be possible to calibrate using a similar
-approach to that described in Section~\ref{sec:debiasing}; the correlation
-between other tasks, such as edge-on galaxies is significantly stronger
-($r=0.9$). So while the raw vote fractions are not directly comparable, the
-initial analysis indicates that the broad morphologies are at least consistent.
+classified and had a shallower magnitude cut on their catalogue.  Based on
+these comparisons, we suggest that use of morphological catalogues with these
+\hst{} images be limited to galaxies with $m_\mathrm{I|i|z}<22.5$; fainter
+targets have been demonstrated to be less reliable, regardless of the method of
+morphological classification being used.
 

### 2016-05-31 writeup/gz_hubble_data.tex
7.3 is now organized by survey

@@
 
-Morphologies for GEMS galaxies were measured by \citet{hau07}, who used
-single-component \sersic{} fits to the F850LP imaging. There are 8,846~galaxies
-with measurements in both \citet{hau07} and GZH. The primary morphological
-parameter in the automated catalogue is the \sersic{} index $n$ defining the
-radial surface brightness profile.  ``Elliptical'' galaxies are selected by
-$n>2.5$ and ``spirals''  by $n<2.5$.  There is no automatic measurement of
-irregular or clumpy structure.
+Figure~\ref{fig:comparisons_features} shows the proportion of galaxies as split
+by their automated/expert visual morphologies for each of the six catalogues
+matched to GZH. Galaxies from every catalogue show a strong correlation between
+\fbest{} and the fraction of galaxies identified as spirals, with a
+corresponding anti-correlation between \fbest{} and the fraction of
+ellipticals.
+
+\begin{figure*}
+\center
+\includegraphics[width=1.0\textwidth]{figures/comparisons_features.pdf}
+\caption{Distributions of morphological parameters for a volume-limited sample
+($z<1.0$, $m<22.5$) of galaxies matched between GZH and six published
+morphological catalogues, split by survey (AEGIS, COSMOS, GEMS, and GOODS). This
+plot shows the fraction of overall galaxies for each of the external
+morphological categories as a function of \fbest{} in GZH. The shaded regions
+around the binned fractions are confidence intervals calculated for a binomial
+population \citep{cam11}.}
+\label{fig:comparisons_features}
+\end{figure*}
 
@@
 
+The AEGIS sample had only 485~total galaxies matched with GZH, and so the
+statistical uncertainties in the analysis are higher. However, at \fbest$>0.8$
+there is a clear separation of featured and unfeatured galaxies in
+Figure~\ref{fig:comparisons_features}, though this is not seen at lower \fbest.
+
+Morphologies for GEMS galaxies were measured by \citet{hau07}, who used
+single-component \sersic{} fits to the F850LP imaging. There are 8,846~galaxies
+with measurements in both \citet{hau07} and GZH. The primary morphological
+parameter in the automated catalogue is the \sersic{} index $n$ defining the
+radial surface brightness profile.  ``Elliptical'' galaxies are selected by
+$n>2.5$ and ``spirals''  by $n<2.5$.  There is no automatic measurement of
+irregular or clumpy structure.
+
+Galaxies from GEMS also have a strong correlation with \fbest{}
+(Figure~\ref{fig:comparisons_features}), which is somewhat surprising (but
+encouraging) considering the known limits of assigning galaxy morphology based
+only on a single \sersic{} parameter.  Visual inspection of images of the
+exceptions --- where both \fbest{} and $n$ are high --- show that most are
+obvious spirals but with prominent bulges. This means that the single-component
+\sersic{} fit is likely choosing too small of an effective radius and missing
+the extended disk structure for a large population of galaxies. This is a known
+issue with using $n$ as a standalone measure of galaxy morphology -- it is
+relatively common, for example, to measure high $n$ for an object with an
+exponential disk but a central cusp in the light profile (eg, due to an AGN,
+cluster, foreground star, noise, etc).
+
 Galaxies in both of the GOODS fields down to a limit of $z_{AB}=22.5$ were
@@
 3,4,5), and ``irregular'' (classes 6,7,8).
+
+The GOODS galaxies show a very similar trend to the AEGIS images in
+Figure~\ref{fig:comparisons_features}, with nearly 100\% pure samples at the
+lowest and highest values of \fbest. We conjecture that the strong agreement
+is at least partially due to the shared method of visual classification,
+and reinforces the findings from several phases of Galaxy~Zoo that crowdsourced
+classifications can be competitive with dedicated experts.
 
@@
 
-\begin{figure*}
-\center
-\includegraphics[width=1.0\textwidth]{figures/comparisons_features.pdf}
-\caption{Distributions of morphological parameters for a volume-limited sample
-($z<1.0$, $m<22.5$) of galaxies matched between GZH and six published
-morphological catalogues, split by survey (AEGIS, COSMOS, GEMS, and GOODS). This
-plot shows the fraction of overall galaxies for each of the external
-morphological categories as a function of \fbest{} in GZH. The shaded regions
-around the binned fractions are confidence intervals calculated for a binomial
-population \citep{cam11}.}
-\label{fig:comparisons_features}
-\end{figure*}
-
-Figure~\ref{fig:comparisons_features} shows the proportion of galaxies as split
-by their automated/expert visual morphologies for each of the six catalogues
-matched to GZH. Galaxies from every catalogue show a strong correlation between
-\fbest{} and the fraction of galaxies identified as spirals, with a
-corresponding anti-correlation between \fbest{} and the fraction of
-ellipticals.
-
-The AEGIS sample had only 485~galaxies matched with GZH, and so the statistical
-uncertainties in the analysis are higher. However, at \fbest$>0.8$ there is a
-clear separation of featured and unfeatured galaxies, though this is not seen
-at lower \fbest.  GOODS galaxies, which are the only comparison sample that
-also uses visual morphology, shows a very similar trend, with nearly 100\% pure
-samples at the lowest and highest values of \fbest.
-
-Galaxies from GEMS (which
-are only split into two types) also have a strong correlation with \fbest,
-which is somewhat surprising (but encouraging) considering the known limits of
-assigning galaxy morphology based only on a single \sersic{} parameter. 
-Visual inspection of images of the exceptions --- where both \fbest{} and $n$
-are high --- show that most are obvious spirals but with prominent bulges. This
-means that the single-component \sersic{} fit is likely choosing too small of
-an effective radius and missing the extended disk structure for a large
-population of galaxies. This is a known issue with using $n$ as a standalone
-measure of galaxy morphology -- it is relatively common, for example, to
-measure high $n$ for an object with an exponential disk but a central cusp in
-the light profile (eg, due to an AGN, cluster, foreground star, noise, etc).
-
-Galaxies from the three COSMOS morphology catalogues all have morphologies that are
+Galaxies from the COSMOS morphology catalogues all have morphologies that are
 reasonably well-predicted by the GZH based on \fbest. The relation is strongest
@@
 captured by the \fbest{} parameter. The small dropoff in the fraction of
-early-types for the Cassata and ZEST samples at \fbest$<0.1$ is somewhat
-puzzling, but could potentially be due to the presence of a small
-population of extremely compact objects (stars or quasars) that would be
-classified as artifacts in GZH, explaining the dip in \fbest.
-
-%We also emphasise that the previously published COSMOS catalogues are not
-%internally consistent; for example, only 64\% of the galaxies in \citet{tas11}
-%have the same morphological class as \citet{cas07}. The bulk of these are
-%galaxies classified as ``spiral'' using one technique and ``irregular'' using
-%another (\citealt{cas07} is more likely to classify galaxies as irregular).  A
-%detailed comparison of the external catalogues is outside the scope of this
-%paper, but we emphasise only that it is \emph{impossible} for any catalogue to be
-%consistent with all three.  We interpret the broad agreements between
-%early-types, spirals, and irregulars for all three samples as a validation of
-%the crowdsourced visual classifications provided by GZH.
-
-%\begin{figure*}
-%\center
-%\includegraphics[width=1.0\textwidth]{figures/comparisons_odd.pdf}
-%\caption{Same as Figure~\ref{fig:comparisons_features}, but comparing external
-%morphologies to \fodd{} in GZH. Measurement of \fodd{} excludes galaxies
-%labeled as ``odd'' due to lenses or dust lanes ($<1\%$ of the total), which are GZH
-%categories not expected to correlate with larger-scale structural parameters.}
-%\label{fig:comparisons_odd}
-%\end{figure*}
-%
-%Figure~\ref{fig:comparisons_odd} analyses the same sets of matched galaxies, but
-%compares the data to the \fodd{} parameter in GZH to examine its correlation with
-%irregular morphologies. The relationship in this case is less clear; for the
-%COSMOS catalogues, in particular, early-types, spirals, and irregulars are
-%roughly equally probable at \fodd$>0.5$. In both AEGIS and GOODS (there is no
-%measurement of irregular structure for GEMS in \citealt{hau07}), the proportion
-%of irregular galaxies does increase with \fodd. However, the actual number of
-%galaxies at \fodd$>0.5$ is quite small ($N\lesssim100$) in both samples, and so
-%estimating an accurate fraction is less precise.  We also note that this
-%particular question ({\it ``anything odd?''}) has somewhat uncertain phrasing
-%in GZH, and that the design of the tree explicitly separates clumpy from
-%irregular or merging morphologies, which would have similar properties in
-%automatic techniques. A more accurate selection of irregular morphologies in
-%GZH should use a weighted combination of \fbest, \fclumpy, and \fodd.
-
-A detailed comparison of the external catalogues is outside the scope of this
+early-types for the Cassata and ZEST samples at \fbest$<0.1$ in
+Figure~\ref{fig:comparisons_features} is somewhat puzzling, but could
+potentially be due to the presence of a small population of extremely
+compact objects (stars or quasars) that would be classified as artifacts in
+GZH, explaining the dip in \fbest.
+
+A detailed comparison of all external catalogues is outside the scope of this
 paper, but we emphasise only that it is impossible for any catalogue to be fully

### 2016-05-31 writeup/gz_hubble_data.tex
New version of Figure 12. Closes #158.

@@
 
-Figure~\ref{fig:sankey} shows the breakdown of morphologies for the combined
-surveys in GZH as a flow~diagram, where each node represents a task and the
-flows between the nodes represent the possible responses. The width of the
-flows is proportional to the number of galaxies associated with that response.
-Figure~\ref{fig:sankey} uses a simple plurality vote to assign the combined set
-of labels for each galaxy. This method is likely to undersample some of the
-categories; visual inspection of images suggests that \ffeatures$\gtrsim0.3$
-identifies disk-dominated or irregular galaxies reliably, for example. This
-method also does not use the suggested thresholds in
-Table~\ref{tbl:thresholds}.
+As an example of visualising the overall morphological distribution,
+Figure~\ref{fig:sankey} shows the breakdown of GZH morphologies as a flow
+diagram. In order to show a physically meaningful sample,
+Figure~\ref{fig:sankey} only includes images from a volume-limited sample
+($z<1.0, m_\mathrm{I}<22.5$) in a single \hst{} survey (COSMOS, which has the
+largest number of total galaxies).  We use a simple plurality vote for the
+responses to each task to characterise the morphologies.  This emphasises one
+of the basic results of the GZH project; namely, that there are comparable
+numbers of spheroid and disk galaxies in the Universe at $z\sim1$, with
+significant diversity in the arrangement of spiral arms and internal clumps.
 
@@
 \center
-\includegraphics[width=0.90\textwidth]{figures/sankey_both.png}
-\caption{Demographics of the morphologies for all galaxies in GZH (including
-both \hst{} and SDSS imaging). Each node in each diagram (dark blue horizontal
-bars of uniform height) represents a task in the tree. The left diagram shows
+\includegraphics[width=0.90\textwidth]{figures/sankey_cosmos.pdf}
+\caption{Demographics of the morphologies for GZH from a volume-limited
+sample ($z<1.0, m_\mathrm{I}<22.5$) of the COSMOS galaxies. Each node in the diagram (dark blue horizontal
+bars of uniform height) represents a task in the tree (Figure~\ref{fig:decisiontree}). The left diagram shows
 the full decision tree. The right diagram zooms in on the features/clumpy
-tasks, which are otherwise difficult to see. The paths between tasks represent
+tasks, which are otherwise difficult to see. Paths between tasks represent
 each possible answer to the task, flowing from top to bottom between their
@@
 
-Given these caveats, the overall distribution of galaxy types is significantly
-different than the low-redshift sample classified in SDSS imaging from GZ1 and
-GZ2. \citet{lin11} found that elliptical galaxies exceeded spiral galaxies by a
-factor of $\sim2:1$ in their spectroscopic sample if using a plurality vote
-criterion (although \citealt{bam09} show that this strongly depends on the
-selection method; spirals are the dominant population in a volume-limited
-sample at $z<0.088$, for example). The weighted votes for GZH have smooth
-galaxies outnumbering disks and clumpy galaxies by a factor of $\sim3:1$,
-however. The fraction of objects identified as stars or artifacts is also much
-higher in the \hst{} imaging. By plurality votes, these encompass only
-$\sim0.1\%$ of images in SDSS \citep{wil13}, but 6\% of images in GZH.
+The overall distribution of galaxy types is significantly different than the
+low-redshift sample classified in SDSS imaging from GZ1 and GZ2. \citet{lin11}
+found that elliptical galaxies exceeded spiral galaxies by a factor of
+$\sim2:1$ in their spectroscopic sample when using a plurality vote criterion
+(although \citealt{bam09} show that this strongly depends on the selection
+method; spirals are the dominant population in a volume-limited sample at
+$z<0.088$). The data for GZH show that smooth galaxies have a comparable total
+population to ``featured'' galaxies of which roughly 20\% are dominated by
+clumps rather than well-organized disks.  The fraction of objects identified as
+stars or artifacts is also much higher in the \hst{} imaging. By plurality
+votes, these encompass only $\sim0.1\%$ of images in SDSS \citep{wil13}, but
+6\% of images in GZH.
 
@@
 the sample, since disk-dominated galaxies outnumber clumpy morphologies by less than
-a factor of 2. Disk galaxies are primarily unbarred \citet{mel14} and
-possessing two visible spiral arms over a flat distribution of pitch angles and
+a factor of 2. Disk galaxies are mostly unbarred \citep{mel14} and
+possess two visible spiral arms over a flat distribution of pitch angles and
 bulge prominence. Clumpy galaxies are identified across the full range of clump
@@
 galaxies have at least 1~clump identified as the brightest. Clumps are most
-commonly asymmetrically arranged in clusters and are not often seen embedded in
-larger structures.
+commonly asymmetrically arranged in clusters and usually embedded within
+larger objects.
 

### 2016-08-10 writeup/gz_hubble_data.tex
Necessary to get Manuscript Central's stupid system to accept PDF.
Reducing figure size for submitted MNRAS version
Fix typo in caption of Fig 8. Closes #181

@@
 \input{macros.tex}
+
+\pdfminorversion 4
 
@@
 
-%\begin{figure*}
-%\center
-%\includegraphics[width=160mm]{figures/specz_comparison.pdf}
-%\caption{Spectroscopic redshifts from the ACS-GC, 3DHST, and MUSYC catalogues.
-%The number in the upper left of each plot is the percentage of redshifts which
-%agree within $\Delta z < 0.05$ between the two catalogues being compared in each
-%panel. Within this range there is over 98\% agreement in redshifts between all
-%three catalogues.}
-%\label{fig:speczs}
-%\end{figure*}
-
 %\input{tables/redshifts.tex}
@@
 \center
-\includegraphics[width=160mm]{figures/gzh_interface.png}
+\includegraphics[width=160mm]{figures/gzh_interface.pdf}
 \caption{Screenshot of the GZH interface at
@@
 includes only galaxies with a bounded range on the dropoff
-($-10<\log(\zeta)<10$) and sufficient points to fit each function (37~original
+($-10<\zeta<10$) and sufficient points to fit each function (37~original
 galaxies, each artificially redshifted in eight bins over a range from $0.3\lesssim z_\mathrm{sim}\lesssim1.0$).}
@@
 \end{table*}
-
-%\begin{figure*}
-%\center
-%\includegraphics[width=\textwidth]{figures/hubble_z_mu_p_distributions.pdf}
-%\caption{Distributions of redshift, surface brightness, and \ffeatures{} for
-%correctable (purple), lower-limit (green), and NEI (pink) galaxies in the full
-%GZH sample. The lower-limit galaxies have higher redshifts, slightly lower
-%surface brightness, and lower values of \ffeatures{} on average than the
-%correctable galaxies. The long tail of NEI galaxies in redshift and surface
-%brightness demonstrates the limits of the \ferengi{} sample, for which there
-%is no data at $z>1$ or $\mu>24$.}
-%\label{fig:z_mu_p}
-%\end{figure*}
-
-%\subsection{Results of \ferengi{} analysis}
-%
-%{\bf Old text from Taiwan workshop}
-%
-%We show here the preliminary results of GZH classifications of images of
-%galaxies placed at artificial redshifts. Figure~\ref{fig:ferengi_results_fake}
-%shows the range of change of vote fractions for the change of \ffeatures{}
-%with redshift, for galaxies with different vote fraction levels, three ranges
-%of surface-brightness levels and 7~evolutionary corrections (this last bit is
-%indicated by the colour). 
-%
-%%---------------------------------------------------------------------------
-%\begin{figure}
-%\begin{center}
-%
-%\includegraphics[width=0.45\textwidth]{figures/somewhat_fake_results.pdf}
-%
-%\caption{Preliminary results of the \ferengi{} redshifting exercise. WARNING
-%NO USER WEIGHTING.... For a range of vote fraction levels with three
-%surface-brightness levels and 7 evolutionary corrections each (the colours
-%indicate evolutionary correction value with green being $e=0$, we show the
-%range of evolution of the vote fractions for featured vs. smooth with
-%redshift.}
-%
-%\label{fig:ferengi_results_fake}
-%
-%\end{center}
-%\end{figure}
-%%--------------------------------------------------------------------------
 
@@
 Swiss National Science Foundation Grant PP00P2\_138979/1. TM acknowledges
-funding from the Science and Technology Facilities Council ST/J500665/1. The
-development and hosting of Galaxy Zoo Hubble was supported by a grant from the
-Alfred P. Sloan Foundation. The Zooniverse acknowledges support from a Google
-Global Impact Award.
+funding from the Science and Technology Facilities Council ST/J500665/1. 
+RJS is supported by the STFC grant code ST/K502236/1.
+The development and hosting of Galaxy Zoo Hubble was supported by a grant from
+the Alfred P. Sloan Foundation. The Zooniverse acknowledges support from a
+Google Global Impact Award.
 

### 2016-08-10 writeup/gz_hubble_data.tex
Figure 10 has five quantiles, not four. Closes #184.

@@
 values for any given observed \ffeatures{} value, again as a function of
-surface brightness and redshift. In each unclassifiable (shaded blue) $z$,$\mu$ bin, the spread of
-intrinsic values of \ffeaturesrest{} for four ranges of observed \ffeatures{} is computed.
-The range of intrinsic values is defined as the inner 80\% of the data,
+surface brightness and redshift. In each unclassifiable (shaded blue) $z$,$\mu$ bin, 
+we compute the spread of
+intrinsic values of \ffeaturesrest{} for five quantiles of observed \ffeatures{}
+(corresponding to the ``clean'' thresholds used in prior GZ publications).
+The range of intrinsic values for GZH is defined as the inner 80\% of the data,
 represented by the orange bars in Figure~\ref{fig:f_vs_f_zoom}. For any galaxy which

### 2016-08-12 writeup/gz_hubble_data.tex
first draft of reorganizing section 4

@@
 
-\subsection{Correcting morphologies for classification bias}\label{ssec:zeta}
-
+\subsection{Effects of morphological debiasing}\label{ssec:zeta_results}
 The approach used in GZH for correcting the weighted classifications for
@@
 extrinsic).
-
-We model the debiased vote fraction $f_{\mu,z}$ for an
-artificially-redshifted galaxy as:
-
-\begin{equation}
-f_{\mu,z} = \left(f_{\mu,z=0.3}\right) \times e^{{\frac{z-z_0}{\zeta}}},
-\label{eqn:fzeta}
-\end{equation}
-
-\noindent where $f_{\mu,z=0.3}$ is the vote fraction at the lowest redshift in
-the artificially-redshifted sample ($z_0=0.3$). Here, $\zeta$ is a parameter that
-controls the rate at which \ffeatures{} decreases with increasing redshift (and
-that may depend on other galaxy properties). This function bounds the observed
-vote fractions between $f_{\mu,z=0.3}$ and zero based on two assumptions: 1)
-the vote fractions for featured galaxies decrease monotonically with increasing
-redshift, therefore restricting vote fractions for a given galaxy to be less
-than $f_{\mu,z=0.3}$ (which is almost always true of the data), and 2) the
-vote fractions cannot be less than zero (which is always true).
-
-\begin{figure*}
-\center
-\includegraphics[width=\textwidth]{figures/zeta_examples_sorted.pdf}
-\caption{Behaviour of the normalised, weighted vote fractions of features
-visible in a galaxy ($f_\textrm{features}$) as a function of redshift in the
-artificial \ferengi{} images. Galaxies in this plot were randomly selected from
-a distribution with $e=0$ and at least three detectable images in redshift bins
-of $z\ge0.3$, and are sorted by \ffeaturesrest. Measured vote fractions (blue
-solid line) are fit with an exponential function (red dashed line;
-Equation~\ref{eqn:fzeta}); the best-fit parameter for $\zeta$ is given above
-each plot.}
-% Error bars are binomial for each f, symmetrised, then added in quadrature.
-\label{fig:zeta_examples}
-\end{figure*}
-
-Figure~\ref{fig:zeta_examples} shows the change in vote fraction and the
-best-fit model for a random set of galaxies in the \ferengi{} sample. The
-results show that there is a clear dependence on redshift for the observed
-changes in \ffeatures. To examine whether a better fit should involve
-additional parameters, we examine the global dependence of $\zeta$ on the
-galaxy surface brightness. This is motivated by the fact that brighter galaxies
-would presumably be easier to identify; \citet{bam09} and \citet{wil13} found
-changes in \ffeatures{} depend on a combination of physical size and
-absolute magnitude. To simplify our model, we subsume these into a single
-parameter $\mu$.
-
-Figure~\ref{fig:zeta_mu} examines the results of fitting the \ferengi{} images
-with Equation~\ref{eqn:fzeta}. This fit only includes galaxies where
-\sextractor{} robustly measured the photometry in all images between
-$0.3<z_\mathrm{sim}<1.0$ (such that $\sigma_{M_I}<1.0$~mag; \citealt{mel16}). Interestingly, the
-derived correction is only a very weak function of surface brightness.
-Higher-surface brightness galaxies have on average slightly stronger
-corrections, possibly because these galaxies have larger $f_\textrm{features}$
-values at high redshifts. Low surface brightness galaxies are more likely to
-begin low and remain low; the bounded nature of the dropoff (and variance among
-the individual voters) means that the average magnitude of $\zeta$ will be
-lower.
-
-\begin{figure}
-\center
-\includegraphics[width=0.5\textwidth]{figures/zeta_mu.pdf}
-\caption{All fits for the \ferengi{} galaxies of the vote fraction dropoff
-parameter $\zeta$ for \ffeatures{} as a function of surface brightness. This
-includes only galaxies with a bounded range on the dropoff
-($-10<\zeta<10$) and sufficient points to fit each function (37~original
-galaxies, each artificially redshifted in eight bins over a range from $0.3\lesssim z_\mathrm{sim}\lesssim1.0$).}
-\label{fig:zeta_mu}
-\end{figure}
-
-Since there is little evidence for any strong systematic dependence of $\zeta$
-on $\mu$, we do not include any additional parameters in fitting to our
-calibration model.  We fit the data in Figure~\ref{fig:zeta_mu} with a linear
-function:
-
-\begin{equation}
-\log_{10}(\hat\zeta) = \zeta_0 + (\zeta_1 \times \mu),
-\label{eqn:zetafit}
-\end{equation}
-
-\noindent where $\hat\zeta$ is the correction factor applied to each galaxy as
-a function of surface brightness. The best-fit parameters to the linear fit
-(from least-squares optimization) are $\zeta_0=0.50$, $\zeta_1=-0.03$. To make the
-final debiased correction, the simple exponential form of
-Equation~\ref{eqn:fzeta} is modified to bound the debiased vote fractions
-between $f$ and 1:
-
-\begin{equation}
-f_\textrm{features,debiased} = 1 - (1 - f_\mathrm{features,weighted})e^{\frac{z-z_0}{\hat\zeta}}
-\label{eqn:fzeta_mod}
-\end{equation}
-
-\noindent where $f_\mathrm{features,weighted}$ is the weighted vote fraction
-described in Section~\ref{ssec:weighting}.
-
-\subsection{Effects of morphological debiasing}\label{ssec:zeta_results}
 
@@
 the measured value of \ffeatures, determined by the $\zeta$ function described
-in the previous section. A reliable predicted value can be obtained so long as
+in the following section. A reliable predicted value can be obtained so long as
 the relationship between \ffeaturesz{} and \ffeaturesrest{} is single-valued;
@@
 redshift or insufficient numbers of \ferengi{} images in their $z$-$\mu$ bin
-to determine a reliable value of $\zeta$.
+to determine a reliable correction term ($\zeta$, described in section ~\ref{ssec:zeta}).
 
@@
 
+\begin{figure*}
+\center
+\includegraphics[width=\textwidth]{figures/debiased_corrections.pdf}
+\caption{Debiased \ffeatures{} corrected to $z=0.3$ vs weighted \ffeatures{}
+for the correctable (left), lower-limit (middle), and ``not enough
+information'' (NEI; right) galaxies in the GZH sample.}
+\label{fig:debiased_corrections}
+\end{figure*}
+
+\subsection{Correcting morphologies for classification bias}\label{ssec:zeta}
+
+For the ``correctable'' sample of galaxies, we observe a decline in the vote fraction
+\ffeatures{} with increasing simulated redshift for each unique galaxy. 
+We model this relationship with a simple exponential
+function which bounds $f_{\mu, z>0.3}$  between $f_{\mu, z=0.3}$ and 0:
+
+\begin{equation}
+f_{\mu,z} = 1 - (1 - f_{\mu,z=0.3})e^{\frac{z-z_0}{\hat\zeta}}
+\label{eqn:fzeta}
+\end{equation}
+
+%old equation
+%We model the debiased vote fraction $f_{\mu,z}$ for an
+%artificially-redshifted galaxy as:
+
+%\begin{equation}
+%f_{\mu,z} = \left(f_{\mu,z=0.3}\right) \times e^{{\frac{z-z_0}{\zeta}}},
+%\label{eqn:fzeta}
+%\end{equation}
+
+\noindent where $f_{\mu,z=0.3}$ is the vote fraction at the lowest redshift in
+the artificially-redshifted sample ($z_0=0.3$). Here, $\zeta$ is a parameter that
+controls the rate at which \ffeatures{} decreases with increasing redshift (and
+that may depend on other galaxy properties). This function bounds the observed
+vote fractions between $f_{\mu,z=0.3}$ and zero based on two assumptions: 1)
+the vote fractions for featured galaxies decrease monotonically with increasing
+redshift, therefore restricting vote fractions for a given galaxy to be less
+than $f_{\mu,z=0.3}$ (which is almost always true of the data), and 2) the
+vote fractions cannot be less than zero (which is always true).
+
+\begin{figure*}
+\center
+\includegraphics[width=\textwidth]{figures/zeta_examples_sorted.pdf}
+\caption{Behaviour of the normalised, weighted vote fractions of features
+visible in a galaxy ($f_\textrm{features}$) as a function of redshift in the
+artificial \ferengi{} images. Galaxies in this plot were randomly selected from
+a distribution with $e=0$ and at least three detectable images in redshift bins
+of $z\ge0.3$, and are sorted by \ffeaturesrest. Measured vote fractions (blue
+solid line) are fit with an exponential function (red dashed line;
+Equation~\ref{eqn:fzeta}); the best-fit parameter for $\zeta$ is given above
+each plot.}
+% Error bars are binomial for each f, symmetrised, then added in quadrature.
+\label{fig:zeta_examples}
+\end{figure*}
+
+Figure~\ref{fig:zeta_examples} shows the change in vote fraction and the
+best-fit model for a random set of galaxies in the \ferengi{} sample. The
+results show that there is a clear dependence on redshift for the observed
+changes in \ffeatures. To examine whether a better fit should involve
+additional parameters, we examine the global dependence of $\zeta$ on the
+galaxy surface brightness. This is motivated by the fact that brighter galaxies
+would presumably be easier to identify; \citet{bam09} and \citet{wil13} found
+changes in \ffeatures{} depend on a combination of physical size and
+absolute magnitude. To simplify our model, we subsume these into a single
+parameter $\mu$.
+
+Figure~\ref{fig:zeta_mu} examines the results of fitting the \ferengi{} images
+with Equation~\ref{eqn:fzeta}. This fit only includes galaxies where
+\sextractor{} robustly measured the photometry in all images between
+$0.3<z_\mathrm{sim}<1.0$ (such that $\sigma_{M_I}<1.0$~mag; \citealt{mel16}). Interestingly, the
+derived correction is only a very weak function of surface brightness.
+Higher-surface brightness galaxies have on average slightly stronger
+corrections, possibly because these galaxies have larger $f_\textrm{features}$
+values at high redshifts. Low surface brightness galaxies are more likely to
+begin low and remain low; the bounded nature of the dropoff (and variance among
+the individual voters) means that the average magnitude of $\zeta$ will be
+lower.
+
+\begin{figure}
+\center
+\includegraphics[width=0.5\textwidth]{figures/zeta_mu.pdf}
+\caption{All fits for the \ferengi{} galaxies of the vote fraction dropoff
+parameter $\zeta$ for \ffeatures{} as a function of surface brightness. This
+includes only galaxies with a bounded range on the dropoff
+($-10<\zeta<10$) and sufficient points to fit each function (37~original
+galaxies, each artificially redshifted in eight bins over a range from $0.3\lesssim z_\mathrm{sim}\lesssim1.0$).}
+\label{fig:zeta_mu}
+\end{figure}
+
+Since there is little evidence for any strong systematic dependence of $\zeta$
+on $\mu$, we do not include any additional parameters in fitting to our
+calibration model.  We fit the data in Figure~\ref{fig:zeta_mu} with a linear
+function:
+
+\begin{equation}
+\log_{10}(\hat\zeta) = \zeta_0 + (\zeta_1 \times \mu),
+\label{eqn:zetafit}
+\end{equation}
+
+\noindent where $\hat\zeta$ is the correction factor applied to each galaxy as
+a function of surface brightness. The best-fit parameters to the linear fit
+(from least-squares optimization) are $\zeta_0=0.50$, $\zeta_1=-0.03$. To make the
+final debiased correction, we use Equation~\ref{eqn:fzeta}, rearranged for clarity:
+
+\begin{equation}
+f_\textrm{features,debiased} = 1 - (1 - f_\mathrm{features,weighted})e^{\frac{-(z-z_0)}{\hat\zeta}}
+\label{eqn:fzeta_mod}
+\end{equation}
+
+\noindent where $f_\mathrm{features,weighted}$ is the weighted vote fraction
+described in Section~\ref{ssec:weighting}, and here $f_{\rm features,debiased}$ is bounded 
+between $f_{\rm features,weighted}$ and 1.
+
 Few galaxies in the sample have sufficiently high corrections to completely
@@
 Sections~\ref{ssec:comparisons}--\ref{ssec:gzh_gzc}).
-
-\begin{figure*}
-\center
-\includegraphics[width=\textwidth]{figures/debiased_corrections.pdf}
-\caption{Debiased \ffeatures{} corrected to $z=0.3$ vs weighted \ffeatures{}
-for the correctable (left), lower-limit (middle), and ``not enough
-information'' (NEI; right) galaxies in the GZH sample.}
-\label{fig:debiased_corrections}
-\end{figure*}
 

### 2016-08-26 response.md
Create response.md

referee response
==========
Major Issue I: Reorganization of Section 4
------------------------------------------
Section 4 has been reorganized in the manner suggested by the reviewer. The authors agree this structure will be more clear to the reader.

### 2016-08-26 response.md
Update response.md

@@
 ------------------------------------------
-Section 4 has been reorganized in the manner suggested by the reviewer. The authors agree this structure will be more clear to the reader.
+Section 4 has been reorganized in the manner suggested by the reviewer. The authors agree this structure will be more clear to the readers.
+
+------------------------------------------
+Major Issue II: Statistical Model
+------------------------------------------
+We tested a variety of models for fitting f/f_o, including linear, exponential, polynomial, and power, each testing a constant zeta parameter and a linear with surface brightness dependence.
+We compared the relative quality of fits using the AIC parameter, and found no great difference in the choice of model ***should quantify this if we can***, the details and code can be viewed in this python notebook (link eventually).
+Of these, we believe the best model is an exponential fit for f_features vs z with a linear (maybe??) zeta, based on the following:
+
+1)

### 2016-08-26 response.md
Update response.md

--- 2016-08-26 response.md
@@
 ------------------------------------------
-Section 4 has been reorganized in the manner suggested by the reviewer. The authors agree this structure will be more clear to the reader.
+Section 4 has been reorganized in the manner suggested by the reviewer. The authors agree this structure will be more clear to the readers.
+
+------------------------------------------
+Major Issue II: Statistical Model
+------------------------------------------
+
+We thank the referee for the very thorough analysis of this method and for the detailed suggestions.
+We used this input to review and revise the fitting of the ferengi data and construction of the debiasing equation for the Hubble data, as follows:
+
+We tested a variety of models for fitting f/f_o, including linear, exponential, polynomial, and power, each testing a constant zeta parameter and a linear with surface brightness dependence.
+We compared the relative quality of fits using the AIC parameter, and found no great difference in the choice of model (***should quantify this if we can***), the details and code can be viewed in this python notebook (***link eventually***).
+Of these, we believe the best model is an exponential fit for f_features vs z with a linear/constant (***need to choose***) zeta, based on the following:
+
+1) While the ferengi data could be fit relatively well using any of the models tested, the exponential is ideal because it is the only form which allows f_features to be simply and continuously bound between 0 and 1, which is a requirement of the debiased vote fractions.
+
+***Zeta: need to choose which.***
+
+2a) We choose a linear equation to represent zeta as a function of surface brightness because (***I can't think of a great reason other than it doesn't hurt since the slope is ~0 anyway, but that feels like such a weak argument...***)
+
+2b) We choose to remove the surface brightness dependence from zeta and use a constant parameter.
+Between the exponential fit with a constant and linear model for zeta, the constant model was shown to be a slightly better fit via the AIC parameter.
+We note that this does not change the effect of the debiasing equation strongly, as the original slope was approximately zero.
+This change is mostly implemented to remove the possible implication that there is any strong surface brightness dependence in the paper.
+
+Additionally, we chose to modify equation 2 to match the normalization of equation 4 (as suggested in minor comment 4).
+
+-----------------------------------
+Minor Comment 1
+-----------------------------------
+
+-----------------------------------
+Minor Comment 2
+-----------------------------------
+
+The FERENGI sample is biased to lower surface brightness than the real data, simply because the local Universe does not include galaxies which are as high surface brightness as are found at high redshift.
+We get around this partially by applying the evolutionary correction described in Section 2.3.2, but this still results in a sample which only spans, not reproduces the surface brightness-redshift distribution of the real data.
+This is fine as we are not correcting the population as a whole, but only galaxies at a given surface brightness and redshift.
+
+-----------------------------------
+Minor Comment 3
+-----------------------------------
+
+(*** will continue to be taken care of as section 4 continues to be finalized (pending choice of zeta in Major Comment II), but probable response will be:***)
+
+We have implemented changes in the text that we believe removes the confusion.
+
+-----------------------------------
+Minor Comment 4
+-----------------------------------
+
+We originally left equation 2 un-bounded because the data being fit was inherently bounded between 0 and 1, while the correction equation 4 would produce vote fractions greater than 1 if left in the same form as 2.
+We recognize now that the difference in normalization, while being only a small effect on the fitting of the data, is inconsistent and confusing to the reader.
+Therfore we changed equation 2 to match equation 4 (see response to Major Comment II).
+
+----------------------------------
+Minor Comment 5
+----------------------------------
+
+This mistake is edited in the text.
+
+---------------------------------
+Minor Comment 6
+----------------------------------
+
+***response pending final fit / choice of zeta***
+
+----------------------------------
+Minor Comment 7
+----------------------------------
+
+The regions can be perfectly separated if we keep the discrete binning as in Figure 9 - however we assumed that a true/physical separation would be a smooth function of z-mu-f.
+Implementing a convex hull in this space created a small amount of contamination around the edges, which was minimized by adjusting the hull as described.
+
+***does this sound efficient?***
+
+----------------------------------
+Minor Comment 8
+----------------------------------

### 2016-08-29 response.md
Update response.md

@@
 ----------------------------------
+
+We chose to evaluate the distribution of f_features in 5 (not 4, this was a typo) bins to match the common ranges of vote fractions used in GZ morphological studies: 0-0.2 indicating a weak/no detection of the feature in question, 0.2-0.4, 0.4-0.6, and 0.6-0.8 representing different ranges of intermediate detection, and 0.8-1.0 representing a very strong detection.
+This explanation has been added to the text.
+
+----------------------------------
+Minor Comment 9
+----------------------------------
+80% was a mostly arbitrary choice to represent the distribution of f_features in a given bin; we discussed and agree with the referee that a more typical statistical range would be more appropriate.
+We therefore chose to represent the range as the upper and lower 1 sigma limits, or the inner 68% of the data.
+
+----------------------------------
+Minor Comment 10
+----------------------------------

### 2016-08-30 response.md
Update response.md

@@
 
-(*** will continue to be taken care of as section 4 continues to be finalized (pending choice of zeta in Major Comment II), but probable response will be:***)
+( ***will continue to be taken care of as section 4 continues to be finalized (pending choice of zeta in Major Comment II), but probable response will be:*** )
 
@@
 
-***does this sound efficient?***
+***does this sound sufficient?***
 
@@
 ----------------------------------
+We have switched to a reduced chi squared metric on the grounds that is a more commonly used and typical values are well-known, as suggested by the referee.
+We believe this metric will make it more evident to the reader that the ferengi data was not well-fit for questions beyond Task 01.
+
+----------------------------------
+Minor Comment 11
+----------------------------------
+Typo has been fixed in the text.

### 2016-09-01 response.md
Update response.md

@@
 We tested a variety of models for fitting f/f_o, including linear, exponential, polynomial, and power, each testing a constant zeta parameter and a linear with surface brightness dependence.
-We compared the relative quality of fits using the AIC parameter, and found no great difference in the choice of model (***should quantify this if we can***), the details and code can be viewed in this python notebook (***link eventually***).
-Of these, we believe the best model is an exponential fit for f_features vs z with a linear/constant (***need to choose***) zeta, based on the following:
+We compared the relative quality of fits using the AIC parameter, and found no great difference in the choice of model.
+The details and code can be viewed in this python notebook https://github.com/willettk/gzhubble/blob/master/python/notebooks/zeta_models_compared.ipynb.
+Of these, we believe the best model is an exponential fit for f_features vs z with a linear zeta, based on the following:
 
 1) While the ferengi data could be fit relatively well using any of the models tested, the exponential is ideal because it is the only form which allows f_features to be simply and continuously bound between 0 and 1, which is a requirement of the debiased vote fractions.
+Further, the AIC test showed the exponential fit was either better than, or had similar support to the other models tested.
 
-***Zeta: need to choose which.***
-
-2a) We choose a linear equation to represent zeta as a function of surface brightness because (***I can't think of a great reason other than it doesn't hurt since the slope is ~0 anyway, but that feels like such a weak argument...***)
-
-2b) We choose to remove the surface brightness dependence from zeta and use a constant parameter.
-Between the exponential fit with a constant and linear model for zeta, the constant model was shown to be a slightly better fit via the AIC parameter.
-We note that this does not change the effect of the debiasing equation strongly, as the original slope was approximately zero.
-This change is mostly implemented to remove the possible implication that there is any strong surface brightness dependence in the paper.
+2) We choose a linear equation to represent zeta as a function of surface brightness.
+In terms of goodness of fit, the AIC test showed both models were of equal quality.
+While this and the small slope in zeta shows we were not able to detect a surface brightness dependence, we still opt to keep the more general, linear form.
+As similar debiasing methods are planned for future GZ projects with a greater quantity of ferengi data, in which a possible surface brightness dependence could be better detected, keeping the general form for this project will allow for a closer comparison of the two iterations of the method.
+We added an emphasis on this reasoning in the paper so as not to lead the readers to the conclusion that we are claiming a strong surface brightness depedence detection in this run.
 
@@
 -----------------------------------
-
-( ***will continue to be taken care of as section 4 continues to be finalized (pending choice of zeta in Major Comment II), but probable response will be:*** )
 
@@
 
-***response pending final fit / choice of zeta***
+***response pending final fit ***
 

### 2016-09-01 response.md
Update response.md

@@
 
-We tested a variety of models for fitting f/f_o, including linear, exponential, polynomial, and power, each testing a constant zeta parameter and a linear with surface brightness dependence.
+We tested a variety of models for fitting f/f_o, including linear, exponential, quadratic, and cubic, each using both a constant zeta parameter and a linear with surface brightness dependence.
 We compared the relative quality of fits using the AIC parameter, and found no great difference in the choice of model.

### 2016-09-02 response.md
Update response.md

@@
 ----------------------------------
-We have switched to a reduced chi squared metric on the grounds that is a more commonly used and typical values are well-known, as suggested by the referee.
-We believe this metric will make it more evident to the reader that the ferengi data was not well-fit for questions beyond Task 01.
+We agree that the normalized chi squared is not the ideal metric for evaluating the goodness of fit here.
+Rather than comparing the fits of the polynomials for Task 1 vs the rest, we chose to compare the available data per bin.
+For Task 1, an average of 59 points were fit in each z-mu bin (Figure 9).
+For the other tasks, an average of 9 points remained in each bin, due to these questions often not being asked of at least 10 users per galaxy, as is required by default in Task 1.
+We believe this simpler evaluation will make it more evident to the reader that the ferengi data was not well-fit for questions beyond Task 01.
+Last, we felt that stating these numbers was sufficient and opted to remove the example visual from the appendix.
 

### 2016-09-06 response.md
Some language cleanup, added text to Minor Comment 1; see #177)

--- 2016-09-01 response.md
@@
 ------------------------------------------
-Section 4 has been reorganized in the manner suggested by the reviewer. The authors agree this structure will be more clear to the readers.
+Section 4 has been re-organized in the manner suggested by the reviewer. The authors agree this structure will be more clear to the readers.
 
@@
 We thank the referee for the very thorough analysis of this method and for the detailed suggestions.
-We used this input to review and revise the fitting of the ferengi data and construction of the debiasing equation for the Hubble data, as follows:
+We used this input to review and revise the fitting of the artificially-redshifted images (from FERENGI) and construction of the debiasing equation for the Hubble data, as follows:
 
-We tested a variety of models for fitting f/f_o, including linear, exponential, polynomial, and power, each testing a constant zeta parameter and a linear with surface brightness dependence.
-We compared the relative quality of fits using the AIC parameter, and found no great difference in the choice of model.
-The details and code can be viewed in this python notebook https://github.com/willettk/gzhubble/blob/master/python/notebooks/zeta_models_compared.ipynb.
-Of these, we believe the best model is an exponential fit for f_features vs z with a linear zeta, based on the following:
+We tested a variety of models for fitting f/f_o, including linear, quadratic, cubic, and exponential dependences on redshift; for each of these functional forms, we also tested combinations using either a constant zeta parameter or a zeta function that linearly depends on surface brightness.
+We compared the relative quality of fits using the Akaike information criteria (AIC); for each case, we found no significant differences in the results based on the choice of model.
+Full details and code for these tests can be viewed in this Python notebook: https://github.com/willettk/gzhubble/blob/master/python/notebooks/zeta_models_compared.ipynb.
 
-1) While the ferengi data could be fit relatively well using any of the models tested, the exponential is ideal because it is the only form which allows f_features to be simply and continuously bound between 0 and 1, which is a requirement of the debiased vote fractions.
-Further, the AIC test showed the exponential fit was either better than, or had similar support to the other models tested.
+Of all the models tested, we believe the best model is an exponential fit for f_features vs redshift using a linear dependence on zeta. This decision is based on the following points:
+
+1) While the FERENGI data can be fit relatively well using any of the above models, the exponential is ideal because it is the only form which allows f_features to be simply and continuously bound between 0 and 1.
+This is a key requirement for the debiased votes so that they can be interpreted as normalized fractions.
+Furthermore, the results of the AIC test show that the exponential fit is either better than, or had similar support to the other models tested.
 
 2) We choose a linear equation to represent zeta as a function of surface brightness.
-In terms of goodness of fit, the AIC test showed both models were of equal quality.
-While this and the small slope in zeta shows we were not able to detect a surface brightness dependence, we still opt to keep the more general, linear form.
-As similar debiasing methods are planned for future GZ projects with a greater quantity of ferengi data, in which a possible surface brightness dependence could be better detected, keeping the general form for this project will allow for a closer comparison of the two iterations of the method.
-We added an emphasis on this reasoning in the paper so as not to lead the readers to the conclusion that we are claiming a strong surface brightness depedence detection in this run.
+In terms of goodness-of-fit, the AIC test showed both models were of equal quality.
+While this and the small slope in zeta shows that there is no significant surface brightness dependence in the GZH data, we still opt to keep the more general, linear form.
+As similar debiasing methods are planned for future GZ projects with a greater quantity of calibration images (and for which there may exist stronger dependencies on surface brightness), keeping the general form for this project will allow for a closer comparison of the two iterations of the method.
+We have added an emphasis on this reasoning in the manuscript so as not to lead the readers to the conclusion that we are claiming a strong surface brightness depedence detection in this run.
 
-Additionally, we chose to modify equation 2 to match the normalization of equation 4 (as suggested in minor comment 4).
+Finally, we have modified Equation 2 to match the normalization of Equation 4 (as suggested in minor comment 4).
 
@@
 
+From a strict sense, it is impossible to tell a priori if giving the anonymous classifiers a weight of 1 is valid (since the grouping within the anonymous data is unknown).
+However, there are large amounts of data from similar projects that support this approach.
+For the Galaxy Zoo: CANDELS project (Simmons et al.
+2016, submitted), which is nearly identical in design to Galaxy Zoo: Hubble and shares a large fraction of the same user base, the distribution of the classifier consistency for both the logged-in and non-logged-in populations peak at the same value (kappa = 0.7).
+The anonymous users have slightly broader wings, with slightly more addresses at the lowest and highest levels of consistency, but the overall behavior is similar.
+The roughly 50-50 split between logged-in users and non-logged-in IP addresses is typical of the ratio for Zooniverse crowdsourced projects as a group.
+
 -----------------------------------
@@
 
-The FERENGI sample is biased to lower surface brightness than the real data, simply because the local Universe does not include galaxies which are as high surface brightness as are found at high redshift.
-We get around this partially by applying the evolutionary correction described in Section 2.3.2, but this still results in a sample which only spans, not reproduces the surface brightness-redshift distribution of the real data.
-This is fine as we are not correcting the population as a whole, but only galaxies at a given surface brightness and redshift.
+The FERENGI sample is biased in including examples of galaxies that have lower surface brightnesses than any images found in the real Hubble data, simply because the local Universe has no examples of galaxies at the high surface brightness end.
+This is a combination of both a finite-volume sample at low redshift in addition to some evolution in the stellar populations and size-magnitude relation over cosmic time.
+We deal with this issue partially by applying the evolutionary correction described in Section 2.3.2, but this still results in a sample spans (but does not reproduce) the surface brightness-redshift distribution of the real data.
+The mismatch does not affect the overall calibration accuracy as we are not correcting the population as a whole, but only galaxies at particular bins of surface brightness and redshift.
 
@@
 
-We originally left equation 2 un-bounded because the data being fit was inherently bounded between 0 and 1, while the correction equation 4 would produce vote fractions greater than 1 if left in the same form as 2.
-We recognize now that the difference in normalization, while being only a small effect on the fitting of the data, is inconsistent and confusing to the reader.
-Therfore we changed equation 2 to match equation 4 (see response to Major Comment II).
+We originally left Equation 2 unbounded because the data being fit was inherently bounded between vote fractions of 0 and 1, while the corrected Equation 4 would produce vote fractions greater than 1 if left in the same form as Equation 2.
+We have realized that the difference in normalization, while having only a small effect on the fitting of the data, is inconsistent and may be confusing to a reader.
+Therefore, we have changed Equation 2 to match Equation 4 (see response to Major Comment II).
 
@@
 
-The regions can be perfectly separated if we keep the discrete binning as in Figure 9 - however we assumed that a true/physical separation would be a smooth function of z-mu-f.
+The regions in Figure 9 can be perfectly separated in f_features-redshift space if we keep the same discrete binning shown in the figure.
+However, our analysis makes the assumption that a true/physical separation should be a smooth function of z-mu-f.
 Implementing a convex hull in this space created a small amount of contamination around the edges, which was minimized by adjusting the hull as described.
@@
 
-We chose to evaluate the distribution of f_features in 5 (not 4, this was a typo) bins to match the common ranges of vote fractions used in GZ morphological studies: 0-0.2 indicating a weak/no detection of the feature in question, 0.2-0.4, 0.4-0.6, and 0.6-0.8 representing different ranges of intermediate detection, and 0.8-1.0 representing a very strong detection.
-This explanation has been added to the text.
+We chose to evaluate the distribution of f_features in 5 (not 4; a typo in the earlier manuscript has been corrected) bins to match the common ranges of vote fractions used in previous GZ morphological studies: 0.0-0.2 is typically used to indicate weak/no detection of the feature in question, 0.2-0.4, 0.4-0.6, and 0.6-0.8 represent ranges of increasing likelihood of detection, and 0.8-1.0 represents a very strong detection.
+This explanation and references to other papers using a similar system has been added to the text.
 
@@
 ----------------------------------
-80% was a mostly arbitrary choice to represent the distribution of f_features in a given bin; we discussed and agree with the referee that a more typical statistical range would be more appropriate.
-We therefore chose to represent the range as the upper and lower 1 sigma limits, or the inner 68% of the data.
+The threshold of 80% was a mostly arbitrary choice to represent the distribution of f_features in a given bin; the authors have discussed it and agree with the referee that a more typical statistical range would be more appropriate.
+We therefore have changed the range to upper and lower 1 sigma limits, or the inner 68% of the data.
 
@@
 ----------------------------------
-We have switched to a reduced chi squared metric on the grounds that is a more commonly used and typical values are well-known, as suggested by the referee.
-We believe this metric will make it more evident to the reader that the ferengi data was not well-fit for questions beyond Task 01.
+We agree that the normalized chi-squared is not the ideal metric for evaluating the goodness-of-fit here.
+Rather than comparing the fits of the polynomials for Task 1 vs the rest of the tasks, we compare the available data per bin.
+For Task 1, an average of 59 points were fit in each z-mu bin (Figure 9).
+For the other tasks, an average of 9 points remained in each bin, due to these questions often not being asked of at least 10 users per galaxy (as required by default in Task 1).
+This simpler evaluation should make it more evident to the reader that the FERENGI data was not well-fit for questions beyond Task 01.
+
+The authors feel that quoting the numbers is sufficient for the manuscript; we have removed the example visual from the Appendix for streamlining.
 

### 2016-09-06 writeup/gz_hubble_data.tex

--- 2016-08-10 writeup/gz_hubble_data.tex
@@
 We repeated all analyses comparing morphologies between GZH and external
-pulblications on the entire GZH dataset, rather than the volume-limited sample
+publications on the entire GZH dataset, rather than the volume-limited sample
 ($z<1.0,m<22.5$) discussed above. If galaxies at all redshifts and at the

### 2016-09-06 writeup/gz_hubble_data_draft_2.tex
adding 2nd draft file of writeup

--- 2016-08-12 writeup/gz_hubble_data.tex
@@
 (corresponding to the ``clean'' thresholds used in prior GZ publications).
-The range of intrinsic values for GZH is defined as the inner 80\% of the data,
-represented by the orange bars in Figure~\ref{fig:f_vs_f_zoom}. For any galaxy which
+\hl{The range of intrinsic values for GZH is defined as the inner 68\% of the data, corresponding to
+where the upper and lower limits of this range correspond to} $\pm{1~\sigma}$ \hl{ above and 
+below the mean. This range is represented by the orange bars in Figure}~\ref{fig:f_vs_f_zoom}. For any galaxy which
 cannot be directly debiased by the $\zeta$ method, these ranges are used to
@@
 sufficient data to measure a correction, as compared to 2.0\% achieved for
-Task~01 (Table~\ref{tbl:ferengi_corrections}). Of the remaining
-\ferengi{} galaxies which did meet this requirement, polynomials were fit to
-the data in each redshift-surface brightness bin, as was done for Task~01. The
-goodness-of-fit was evaluated in each bin, for each Task, using a normalised
-$\chi^2$ metric. The mean $\chi^2$ for all higher-order tasks was
-$0.10\pm0.04$, significantly larger than the Task~01 value of $0.04$. Based on
-this statistic, the data cannot not be modelled with sufficient confidence for
-the higher order tasks. An example of the debiasing technique applied to
-\fbar{} is shown in Section~\ref{sec:ferengi_bar}; visual inspection of
-Figure~\ref{fig:f_vs_fbar} confirms that the points in each bin are scattered
-to a degree at which no strong correlation is present.  For these reasons,
+Task~01 (Table~\ref{tbl:ferengi_corrections}).\hl{This left each surface brightness/redshift bin 
+with insufficient data points to fit a function with confidence; on average only 9 points
+remained in each bin (as compared to an average of 59 points per bin for Task~01). For these reasons,
 debiased vote fractions are only offered in the GZH catalogue for Task~01
-(smooth/features).
+(smooth/features).  }
 
@@
 We repeated all analyses comparing morphologies between GZH and external
-pulblications on the entire GZH dataset, rather than the volume-limited sample
+\hl{publications} on the entire GZH dataset, rather than the volume-limited sample
 ($z<1.0,m<22.5$) discussed above. If galaxies at all redshifts and at the
@@
 
-\subsection{Debiasing higher-order tasks: \fbar}
-\label{sec:ferengi_bar}
-
-To determine the rate at which the vote fraction for any Task decreases with
-redshift or surface brightness, data from simulated \ferengi{} images were
-modelled with functions in discrete redshift and surface brightness bins
-(Section~\ref{ssec:zeta_results}). A cut of $N>10$ was placed on the number of
-votes to reduce the error in the vote fractions and ensure they were
-well-sampled before applying a fit to the data. This requirement was only met
-for Task~01, which significantly reduced the goodness-of-fit for the model
-functions as compared to the smooth/features task. Here we show an
-example of results obtained for the bar Task. Figure~\ref{fig:f_vs_fbar}
-shows that both the low sample rate and the degree of scatter in each bin
-inhibit fitting a reliable function that predicts $f_{{\rm bar},z=0.3}$.
-Table~\ref{tbl:ferengi_bar} summarises the correction types for the
-\ferengi{} data; 71\% of the galaxies simulated did not meet the GZH
-requirements for well-sampled vote fractions for $f_\mathrm{bar}$, as
-compared to 2\% for $f_\mathrm{features}$. Similar results were obtained
-for all higher-order Tasks in GZH (Section~\ref{ssec:higher_order_tasks}).
-
-\begin{figure*}
-\centering
-\includegraphics[width=\textwidth]{figures/p_vs_p_SB_redshift_bar.pdf}
-\caption{Similar to Figure~\ref{fig:f_vs_f}, showing effects of redshift bias
-for 3,449~images in the \ferengi{} sample. Each point in a given redshift
-and surface brightness bin represents a unique galaxy. The $y$-axis in each
-bin is the \ffeatures{} value of the image of that galaxy redshifted to the
-value corresponding to that redshift bin. The $x$-axis is the \ffeatures{}
-value of the image of the same galaxy redshifted to $z=0.3$. The dashed
-black lines represent the best-fit polynomials to the data in each square.
-The solid black line represents \ffeaturesz=\ffeaturesrest. Regions in
-which there is a single-valued relationship between \ffeatures{} at high
-redshift and at $z=0.3$ are marked in white; those in which there is not
-are blue, and those with not enough data ($N<5$) are grey. A larger version of
-the bin outlined at $z=1.0$ and $20.3 < \mu < 21.0$ $\rm (mag/arcsec^2)$ is
-shown in Figure~\ref{fig:f_vs_fbar_zoom}. The mean normalised $\chi^2$ of the
-change in vote fraction is 0.08. None of the correlations for higher-order
-tasks (including bars) were applied to galaxies in the GZH catalogue.}
-\label{fig:f_vs_fbar}
-\end{figure*}
-
-\begin{figure}
-\centering
-\includegraphics[width=0.5\textwidth]{figures/z1_mu20_subplot2_bar.pdf}
-\caption{A larger version of the dark-outlined square in Figure~\ref{fig:f_vs_fbar}, containing
-\ferengi{} galaxies that have been artificially redshifted to $z=1.0$ and have
-surface brightnesses between $20.3 < \mu < 21.0$ $\rm (mag/arcsec^2)$. The orange bars represent the inner
-80$^\mathrm{th}$ percentiles of the data, the boundaries of which are the lower
-and upper limits of the debiased values.}
-\label{fig:f_vs_fbar_zoom}
-\end{figure}
-
-\begin{table}ー
-\label{tbl:ferengi_bar}
-\caption{Morphological correction categories for the \ferengi{} images summarised in
-Figure~\ref{fig:f_vs_fbar}. Correctable images had a single-valued relationship
-between their measured \fbar{} values at high and low redshifts (white regions
-in Figure~\ref{fig:f_vs_fbar}). Galaxies with a lower-limit on \fbar{} had a
-non single-valued relationship (blue regions). NEI images had undetermined
-relationships due to a lack of data ($N<5$) in their corresponding $z$-$\mu$
-bins (grey regions). Only 17\% (maximum) of \ferengi{} galaxies in the sample
-were considered ``correctable'', which is not sufficient to compute a $\zeta$
-function applicable to the \hst{} data.   \label{tbl:ferengi_bar_corrections}}
-\begin{tabular}{lrr}
-\hline \hline
-                                   & $N$    & \%        \\
-\hline 
-Correctable                        & 664    & 17\%      \\
-Lower-limit                        & 483    & 12\%      \\
-NEI                                & 2,803  & 71\%      \\
-\hline
-Total                              & 3,950  & 100\%     \\
-\hline \hline
-\end{tabular}
-\end{table}
-
 \bsp	% typesetting comment

### 2016-09-06 response.md
Update response.md

@@
 
+***1) Section 3.2: what checking did the authors do to indicate that giving all anonymous classifications a weight of 1 is valid?***
+
 From a strict sense, it is impossible to tell a priori if giving the anonymous classifiers a weight of 1 is valid (since the grouping within the anonymous data is unknown).
@@
 
+***2) Figure 6: the authors should comment (unless I missed the comment) on why the bivariate distribution of the FERENGI galaxies in (mu,z) does not match the bivariate distribution for the main sample.***
+
 The FERENGI sample is biased in including examples of galaxies that have lower surface brightnesses than any images found in the real Hubble data, simply because the local Universe has no examples of galaxies at the high surface brightness end.
@@
 
+***3) In parts of Section 4.1, there is a confusing mix of f_mu,z and f_features, which appear to represent the same thing.
+Some clean-up (or additional explanation as to why they are different quantities) would be useful here.***
+
 We have implemented changes in the text that we believe removes the confusion.
@@
 -----------------------------------
+
+***4) I probably should have mentioned this above, but why are the authors not working with equation (4) as the basis of their regression model?***
 
@@
 
+***5) Figure 8: "-10 < log(xi) < 10" should be "-10 < xi < 10"***
+
 This mistake is edited in the text.
@@
 
+***6) How many data points are there in Figure 8? Obviously more than 37, but fewer than 37 x 8.***
+
 ***response pending final fit ***
@@
 ----------------------------------
+
+***7) Section 4.2: "The boundaries [of the convex hull] are then adjusted until the contamination from both groups is minimized." If I look at Figure 9, it would appear that the correctable and lower-limit regions can be perfectly separated (using a tree, for instance).
+Am I wrong about this?***
 
@@
 
+***8) Section 4.2: "In each unclassifiable (shaded blue) z,mu bin, the spread of intrinsic values for f_features,z=0.3 for four ranges of observed f_features is computed." Where did the "four" come from?
+More explanation needed.***
+
 We chose to evaluate the distribution of f_features in 5 (not 4; a typo in the earlier manuscript has been corrected) bins to match the common ranges of vote fractions used in previous GZ morphological studies: 0.0-0.2 is typically used to indicate weak/no detection of the feature in question, 0.2-0.4, 0.4-0.6, and 0.6-0.8 represent ranges of increasing likelihood of detection, and 0.8-1.0 represents a very strong detection.
@@
 ----------------------------------
+
+***9) Why 80% of the data (orange bars, Figure 10)?
+This is an ad hoc choice that doesn't correspond to any typical statistical practice (except perhaps a 10% trimmed mean, but the authors are not computing means here).
+And how is this information applied in Figure 11, middle panel?
+This is not clear.***
+
 The threshold of 80% was a mostly arbitrary choice to represent the distribution of f_features in a given bin; the authors have discussed it and agree with the referee that a more typical statistical range would be more appropriate.
@@
 ----------------------------------
+
+***10) Section 4.3: "The goodness-of-fit was evaluated in each bin, for each Task, using a normalized chi^2 metric." The authors need to provide the formula for this; the numbers don't make sense, if one assumes "normalized" is the same
+as "reduced chi^2" (where the typical value for a good fit is approximately1).***
+
 We agree that the normalized chi-squared is not the ideal metric for evaluating the goodness-of-fit here.
@@
 ----------------------------------
+
+***11) Section 7.3: "external pulblications" -> "external publications"***
+
 Typo has been fixed in the text.

### 2016-09-06 writeup/gz_hubble_data_draft_2.tex
fixing typo

@@
 (corresponding to the ``clean'' thresholds used in prior GZ publications).
-\hl{The range of intrinsic values for GZH is defined as the inner 68\% of the data, corresponding to
-where the upper and lower limits of this range correspond to} $\pm{1~\sigma}$ \hl{ above and 
-below the mean. This range is represented by the orange bars in Figure}~\ref{fig:f_vs_f_zoom}. For any galaxy which
+\hl{The range of intrinsic values for GZH is defined by the upper and lower 1~$\sigma$ limits,
+enclosing the inner 68\% of the data. This range is represented by the orange bars in 
+Figure}~\ref{fig:f_vs_f_zoom}. For any galaxy which
 cannot be directly debiased by the $\zeta$ method, these ranges are used to

### 2016-09-06 response.md
Update response.md

@@
-referee response
+We thank the referee for the very thorough analysis and for the detailed suggestions that helped to improve the analysis and the paper overall.
+In the following, we report the original comment by the referee, followed by our response.
+In the manuscript, we highlighted our changes in boldface.
+
 ==========
@@
 
-We thank the referee for the very thorough analysis of this method and for the detailed suggestions.
 We used this input to review and revise the fitting of the artificially-redshifted images (from FERENGI) and construction of the debiasing equation for the Hubble data, as follows:

### 2016-09-06 response.md
Changed the opening.

@@
 
-We used this input to review and revise the fitting of the artificially-redshifted images (from FERENGI) and construction of the debiasing equation for the Hubble data, as follows:
+We used the referee's input to review and revise the fitting of the artificially-redshifted images (from FERENGI) and construction of the debiasing equation for the Hubble data, as follows:
 

### 2016-09-06 response.md
Consistency for anonymous users; closes #177

--- 2016-09-06 response.md
@@
 
-We tested a variety of models for fitting f/f_o, including linear, quadratic, cubic, and exponential dependences on redshift; for each of these functional forms, we also tested combinations using either a constant zeta parameter or a zeta function that linearly depends on surface brightness.
+We tested a variety of models for fitting f/f_0, including linear, quadratic, cubic, and exponential dependences on redshift; for each of these functional forms, we also tested combinations using either a constant zeta parameter or a zeta function that linearly depends on surface brightness.
 We compared the relative quality of fits using the Akaike information criteria (AIC); for each case, we found no significant differences in the results based on the choice of model.
@@
 The roughly 50-50 split between logged-in users and non-logged-in IP addresses is typical of the ratio for Zooniverse crowdsourced projects as a group.
+
+ATTACH: Figure from https://cloud.githubusercontent.com/assets/2357126/17576650/cfc59fbe-5f29-11e6-99b7-c39a43c013b6.png
 

### 2016-09-07 writeup/gz_hubble_data_draft_2.tex
Consistency for anonymous users; closes #177
Explain bivariate distributions (MiC 2); closes #178.

@@
 participation). Classifications by participants who were not logged in were marked as
-``Anonymous'' and receive the same $w=1$ weighting as the vast majority
-of logged-in classifiers.
+``Anonymous'' and receive the same $w=1$ weighting as the vast majority of
+logged-in classifiers. Results from the Galaxy Zoo: CANDELS project (Simmons et~al., submitted)
+show that the distributions of weights for anonymous and
+logged-in users are similar, supporting the default technique of GZH. 
 % We should also try to estimate how many anonymous classifiers there were, if possible. 
@@
 they would appear observed at a variety of redshifts.  The input images are
-from the SDSS \citep{yor00,str02}.  The sample consists of 288~well-resolved galaxies
-at $z<0.013$. The galaxies spanned a variety of morphologies (as selected by
-GZ2 classifications, including identifications of spiral structure,
+from the SDSS \citep{yor00,str02}.  The sample consists of 288~well-resolved
+galaxies at $z<0.013$. The galaxies spanned a variety of morphologies (as
+selected by GZ2 classifications, including identifications of spiral structure,
 ellipticals, mergers, edge-on disks, bulge prominence/shape, and bars) and
-$r$-band surface brightnesses.  The overall selection spanned the
-redshift range of SDSS targets and maximised the number of \hst{} galaxies at
-the same surface brightness and redshift (Figure~\ref{fig:sb_redshift}).  The
-\ferengi{} code was used to produce sets of images corresponding to
-observations of these galaxies out to $z_\mathrm{sim}=1.0$ (see
-Section~\ref{ssec:ferengi}).  The resulting images were classified in the GZH
-interface using the standard classification scheme.
+$r$-band surface brightnesses.  The selection of galaxies spanned the redshift
+range of SDSS targets and maximised the number of \hst{} galaxies at the same
+surface brightness and redshift. The \ferengi{} code was used to produce sets
+of images corresponding to observations of these galaxies out to
+$z_\mathrm{sim}=1.0$ (see Section~\ref{ssec:ferengi}). The resulting images
+were classified in the GZH interface using the standard classification scheme.
+
+\changes{Figure~\ref{fig:sb_redshift} shows the distribution in $\mu$ and $z$ of
+the artificially-redshifted \textsc{FERENGI} images compared to the genuine
+\hst{} images. The full bivariate distributions differ due to a combination of
+the detection limits of the \hst{} surveys, intrinsic rareness of bright $\mu$
+galaxies in the SDSS volume, and evolution of the stellar populations. Since
+the dependence of the debiasing correction is evaluated in separate bins, the
+main concern is the existence of an overlap between the two sets of images;
+this is the case for almost all of the \hst{} images, which have $\mu >
+19$~mag~arcsec$^{-2}$.  The brightest end of the distribution, which has fewer
+examples of comparable \textsc{FERENGI} images, correspond to galaxies for
+which the debiased correction is expected to be minor.}
 

### 2016-09-07 writeup/gz_hubble_data_draft_2.tex
Highlight changes for MiC 1.

@@
 ``Anonymous'' and receive the same $w=1$ weighting as the vast majority of
-logged-in classifiers. Results from the Galaxy Zoo: CANDELS project (Simmons et~al., submitted)
+logged-in classifiers. \changes{Results from the Galaxy Zoo: CANDELS project (Simmons et~al., submitted)
 show that the distributions of weights for anonymous and
-logged-in users are similar, supporting the default technique of GZH. 
+logged-in users are similar, supporting the default technique of GZH.}
 % We should also try to estimate how many anonymous classifiers there were, if possible. 

### 2016-09-07 response.md
Explain bivariate distributions (MiC 2); closes #178.
Confusing nomenclature (MiC 3); closes #179.

@@
 
+We have added a paragraph in Section 4 for clarification.
+
 -----------------------------------
@@
 
-We have implemented changes in the text that we believe removes the confusion.
+The main difference between Equations 2 and 4 is that the former is applied to the FERENGI calibration images and used to fit the normalization and zeta parameters.
+The latter uses the parameters to apply corrections to individual galaxies from the true data, and is the form implemented throughout the text.
+
+We have added text to explicitly mark the difference between the two equations in what is now Section 4.2.
 

### 2016-09-07 writeup/gz_hubble_data_draft_2.tex
Confusing nomenclature (MiC 3); closes #179.

@@
 \ffeatures{} with increasing simulated redshift for each unique galaxy. 
-We model this relationship with a simple exponential
+We model this relationship \changes{for artificially-redshifted images} with a simple exponential
 function which bounds $f_{\mu, z>0.3}$  between $f_{\mu, z=0.3}$ and 0:
@@
 (from least-squares optimization) are $\zeta_0=0.50$, $\zeta_1=-0.03$. To make the
-final debiased correction, we use Equation~\ref{eqn:fzeta}, rearranged for clarity:
+final debiased correction \changes{for the genuine \hst{} data, we apply Equation~\ref{eqn:fzeta}:}
 

### 2016-09-07 response.md
Add some detail on MiC 4. Closes #180.

@@
 
-We originally left Equation 2 unbounded because the data being fit was inherently bounded between vote fractions of 0 and 1, while the corrected Equation 4 would produce vote fractions greater than 1 if left in the same form as Equation 2.
+Equation 2 was originally left unbounded because the raw data being fit was inherently bounded between vote fractions of 0 and 1.
+However, the original verseion of Equation 4 could produce vote fractions greater than 1 if left in the same form as Equation 2.
 We have realized that the difference in normalization, while having only a small effect on the fitting of the data, is inconsistent and may be confusing to a reader.
-Therefore, we have changed Equation 2 to match Equation 4 (see response to Major Comment II).
+Therefore, we have changed Equation 2 to match Equation 4 (see response to Major Comment II, as well as Minor Comment 3).
+All data in the tables and catalog have been updated to account for these small changes.
 

### 2016-09-07 writeup/gz_hubble_data_draft_2.tex
Mark the change in Fig 11 caption (MiC 5). See #181.

@@
 includes only galaxies with a bounded range on the dropoff
-($-10<\zeta<10$) and sufficient points to fit each function (37~original
+\changes{($-10<\zeta<10$)} and sufficient points to fit each function (37~original
 galaxies, each artificially redshifted in eight bins over a range from $0.3\lesssim z_\mathrm{sim}\lesssim1.0$).}

### 2016-09-07 response.md
Mark the change in Fig 11 caption (MiC 5). See #181.
Explain the convex hull results, link to notebook (MiC 7). Closes #183.

@@
 
-This mistake is edited in the text.
+Correct, thank you. This typo has been edited in the figure caption.
 
@@
 
-The regions in Figure 9 can be perfectly separated in f_features-redshift space if we keep the same discrete binning shown in the figure.
+The regions in Figure 9 (now Figure 7) can be nearly perfectly separated in f_features-redshift space, but there are a few regions near the edges in which there is overlap between the two populations.
+This is affected slightly in Figure 9 by the choice of bin size and location.
 However, our analysis makes the assumption that a true/physical separation should be a smooth function of z-mu-f.
-Implementing a convex hull in this space created a small amount of contamination around the edges, which was minimized by adjusting the hull as described.
+Implementing a convex hull in this space created a very small volume near the edge of the inner convex hull that had overlapping positive and negative data points; we optimize the overall accuracy of the hull by adjusting the outer boundaries as described in what is now Section 4.1.
 
-***does this sound sufficient?***
+Use of a different method such as a tree could potentially prove to be a superior separator.
+However, the new normalization technique used in this draft results in very clean separation based on the convex hull, with only a single adjustment (see https://github.com/willettk/gzhubble/blob/master/python/creating_debiased_catalog/STEP_3_ferengi_smooth_function.ipynb).
+Further optimization would have an extremely minimal effect on the overall results.
 

### 2016-09-07 writeup/gz_hubble_data_draft_2.tex
Choice of five quintiles (MiC 8). See #184.

@@
 values for any given observed \ffeatures{} value, again as a function of
-surface brightness and redshift. In each unclassifiable (shaded blue) $z$,$\mu$ bin, 
+surface brightness and redshift. \changes{In each unclassifiable (shaded blue) $z$,$\mu$ bin, 
 we compute the spread of
@@
 (corresponding to the ``clean'' thresholds used in prior GZ publications).
-\hl{The range of intrinsic values for GZH is defined by the upper and lower 1~$\sigma$ limits,
+The range of intrinsic values for GZH is defined by the upper and lower 1~$\sigma$ limits,
 enclosing the inner 68\% of the data. This range is represented by the orange bars in 

### 2016-09-07 response.md
Choice of five quintiles (MiC 8). See #184.
Explanation of the += 1 sigma (MiC 9). Figure still needs to be changed. See #185.
Removal of reduced chi^2, discussion of higher-order tasks (MiC 10).

@@
 We chose to evaluate the distribution of f_features in 5 (not 4; a typo in the earlier manuscript has been corrected) bins to match the common ranges of vote fractions used in previous GZ morphological studies: 0.0-0.2 is typically used to indicate weak/no detection of the feature in question, 0.2-0.4, 0.4-0.6, and 0.6-0.8 represent ranges of increasing likelihood of detection, and 0.8-1.0 represents a very strong detection.
-This explanation and references to other papers using a similar system has been added to the text.
+This explanation has been added to the text at the end of Section 4.1.
 
@@
 
-The threshold of 80% was a mostly arbitrary choice to represent the distribution of f_features in a given bin; the authors have discussed it and agree with the referee that a more typical statistical range would be more appropriate.
-We therefore have changed the range to upper and lower 1 sigma limits, or the inner 68% of the data.
+The threshold of 80% was initially a somewhat arbitrary choice to represent the distribution of f_features in a given bin; the authors agree with the referee that a more typical statistical range would be more appropriate.
+We have changed the range to upper and lower 1 sigma limits, or the inner 68% of the data.
+The figure (now Figure 8) has been modified and text added to the end of Section 4.1.
 
@@
 ***10) Section 4.3: "The goodness-of-fit was evaluated in each bin, for each Task, using a normalized chi^2 metric." The authors need to provide the formula for this; the numbers don't make sense, if one assumes "normalized" is the same
-as "reduced chi^2" (where the typical value for a good fit is approximately1).***
+as "reduced chi^2" (where the typical value for a good fit is approximately 1).***
 
@@
 For Task 1, an average of 59 points were fit in each z-mu bin (Figure 9).
-For the other tasks, an average of 9 points remained in each bin, due to these questions often not being asked of at least 10 users per galaxy (as required by default in Task 1).
+Fitting parameters for any other task is significantly limited by the number of galaxies in each z-mu bin; the higher-order tasks have an average of only 9 galaxies per bin.
+This is driven by the fact that the tasks do not meet the minimum threshold of 10 individual classifications (this threshold is exceeded for every galaxy in Task 1, however).
 This simpler evaluation should make it more evident to the reader that the FERENGI data was not well-fit for questions beyond Task 01.
 
-The authors feel that quoting the numbers is sufficient for the manuscript; we have removed the example visual from the Appendix for streamlining.
+As this is not a key product of the paper, we have removed Figures A5 and A6 from the manuscript to avoid confusion and extraneous discussion. Additional text has been added at the end of Section 4.3.
 

### 2016-09-07 writeup/gz_hubble_data_draft_2.tex
Removal of reduced chi^2, discussion of higher-order tasks (MiC 10).

@@
 sufficient data to measure a correction, as compared to 2.0\% achieved for
-Task~01 (Table~\ref{tbl:ferengi_corrections}).\hl{This left each surface brightness/redshift bin 
-with insufficient data points to fit a function with confidence; on average only 9 points
-remained in each bin (as compared to an average of 59 points per bin for Task~01). For these reasons,
-debiased vote fractions are only offered in the GZH catalogue for Task~01
-(smooth/features).  }
+Task~01 (Table~\ref{tbl:ferengi_corrections}). \changes{This leaves the average
+surface brightness/redshift bin 
+with insufficient data points to confidently measure the change in vote fraction ($\lesssim10$~galaxies per bin). 
+For these reasons, debiased vote fractions are only provided in the GZH catalogue for Task~01
+(smooth/features). We suggest that use of morphological data for higher order tasks should instead use
+the weighted vote fractions (see Section~\ref{sec:cookbook}).}
 
@@
 We repeated all analyses comparing morphologies between GZH and external
-\hl{publications} on the entire GZH dataset, rather than the volume-limited sample
+\changes{publications} on the entire GZH dataset, rather than the volume-limited sample
 ($z<1.0,m<22.5$) discussed above. If galaxies at all redshifts and at the

### 2016-09-07 writeup/gz_hubble_data_draft_2.tex
Full readthrough and small changes.

@@
 hierarchical assembly model \citep{sil12}. The structure of individual galaxies
-is affected by their merger history \citep{too72,ste02,hop10,kav14,kav14a}, local
+is affected by their merger history \citep{too72,ste02,hop10,kav14a,kav14}, local
 environment \citep[\eg, the morphology-density relation;][]{dre80}, initial
@@
 to measure galaxies in colour-composite images. The efforts of more than
-$2\times10^5$~classifiers allow for multiple independent classifications of
+200,000~classifiers allow for multiple independent classifications of
 each image which are combined and calibrated to give a distribution of vote
@@
 a proven reliability and have been used for a wide variety of scientific
-studies \citep[eg,][]{lan08,bam09,dar10,mas11c,ski12,sim13,sch14,wil15}.
+studies \citep[eg,][]{lan08,bam09,dar10,mas11c,ski12,sim13,sch14,wil15,sme16}.
 
@@
 Image information from
-the individual surveys have been combined into a single photometric and
-morphological database, the Advanced Camera for Surveys General Catalog
-\citep[ACS-GC;][]{gri12}. A summary of the key parameters is given in
+multiple \hst{} surveys were combined into a single photometric and
+morphological database, the Advanced Camera for Surveys General Catalog (ACS-GC) by 
+\citet{gri12}. A summary of the key parameters of the ACS-GC is given in
 Table~\ref{tbl:gzh_numbers}.
@@
 \item The Great Observatories Origins Deep Survey \citep[GOODS;][]{gia04}
-    covered two separate fields in the northern and southern hemispheres: the Hubble
+    covered two separate fields in the Northern and Southern Hemispheres: the Hubble
     Deep Field-North ($\alpha=12^\textrm{h}36^\textrm{m},
@@
     depths. Images were dithered to a pixel scale of 0.03~\arcsec/pixel and covered a
-    total area of $\sim320$~arcmin$^2$ (160~arcmin$^2$ per north/south field). The
+    total area of $\sim320$~arcmin$^2$ (160~arcmin$^2$ each for the north and south fieldss). The
     $5\sigma$ limiting magnitude for extended sources was 25.7 for \Vband{} and
@@
 %Selection of galaxies from these samples is described in Section \ref{ssec:galselect} below. 
-In the ACS-GC \citep{gri12}, individual galaxies were identified using a
+In the ACS-GC, individual galaxies were identified using a
 combination of \sextractor{} \citep{ber96} and the galaxy-profile fitting
@@
 set of 30,339~images. Of the images in the co-added sample, 5144 (17~percent)
-were dimmer than the initial magnitude cut of 17.77.
+were dimmer than the initial cut of 17.77~mag.
 
@@
 combining stars in the GOODS fields using the PSF creation tools in
-\texttt{daophot}.  The second set (version~2) was assembled from 96~galaxies in
+\texttt{daophot} \citep{ste87}.  The second set (version~2) was assembled from 96~galaxies in
 GOODS-S; this version used simulated PSFs from \texttt{TinyTim} \citep{kri93},
@@
 applicable, these pages contained further information regarding image
-modifications. \citet{sim13} uses the simulated AGN host galaxy images for
+modifications. \citet{sim13} used the simulated AGN host galaxy images for
 more reliable identification of bulgeless galaxies hosting AGN in SDSS data.
@@
 saturating galaxy centres. The relative scalings of the filter bands were
-chosen while trying to reproduce the colour appearance of the SDSS images in
+chosen to reproduce the colour appearance of the SDSS images in
 previous iterations of Galaxy Zoo.
@@
 mapped to the blue channel, the longer-wavelength band to the red channel, and
-the green channel created by taking the arithmetic mean of the two. The bands
+the green channel created by taking the arithmetic mean of the red and blue. The bands
 used in each of the surveys are listed in Table~\ref{tbl:gzh_numbers}.
@@
 used to create the original 2-epoch images, for consistency with AEGIS and
-GEMS. The 2-epoch GOODS-N and GOODS-S images were created using different
+GEMS. The 2-epoch GOODS-N and GOODS-S images were created using differing
 filters --- this was a deliberate choice made so that the GEMS images could be
@@
 Only 2-epoch GOODS images were included at the launch of GZH.  Deeper, 5-epoch 
-GOODS images were added into GZH later (in March 2015). These images made
+GOODS images were added into GZH in March 2015. The deeper images made
 use of the full four-band data by using the arithmetic mean of \Bband{} and
@@
 images resulted in the sky noise taking the appearance of brightly-coloured
-speckles. This impaired the aesthetics of the images and might have been a
+speckles. This impaired the aesthetics of the images and was considered a potential
 distraction to visual classification.  To counteract this, a soft-edged object
@@
 saturation, and the second has reversed the colours so that the blue and red
-filters have exchanged places in the RGB image. The `faded' galaxy set
+filters have exchanged places in the RGB image. The ``faded'' galaxy set
 facilitates measuring of possible variations in classification due to the
-presence or absence of colour features. The `recoloured' set enables an
+presence or absence of colour features. The ``recoloured'' set enables an
 alternative test of potential colour biases in classifications.
@@
 galaxy, the primary redshift is in the $\tt Z\_BEST$ column of
-Table~\ref{tbl:catalogue_hst}. The redshift type (spectroscopic: $\tt SPEC\_Z$,
+Table~\ref{tbl:catalog_hst}. The redshift type (spectroscopic: $\tt SPEC\_Z$,
 photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column
@@
 inconsistent spectroscopic redshifts between any pair of catalogues are marked
-with a flag in Table~\ref{tbl:catalogue_hst}.  If no spectroscopic redshifts were
+with a flag in Table~\ref{tbl:catalog_hst}.  If no spectroscopic redshifts were
 available, the 1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST,
@@
 tree (Figure~\ref{fig:decisiontree}). Every classification began with the step of
-identifying whether the object at the centre of the image was a smooth galaxy,
+identifying whether the object at the centre of the image was a ``smooth'' galaxy,
 a galaxy with a disk or other features, or a star/artifact. Subsequent
@@
 
-The GZH decision tree was designed to remain close to that used by GZ2 while
-taking account of the likely differences in high redshift systems, and has four
-broad sets of morphologies classified by the users.  The first set
+The GZH decision tree was designed to be similar to that used by GZ2 while
+taking account of the likely differences in the morphologies of high redshift galaxies. There are four
+broad sets of morphologies classified by the users in GZH.  The first set
 identified stars or image artifacts (the result of either bad data or incorrect
-identification as a galaxy by the ACS pipeline); in this case, the
+identification of an object as a galaxy by the ACS pipeline); in this case, the
 classification process ended and no further questions were asked. The second
-set was smooth galaxies, intended to select ellipticals/early-types;
+set was for ``smooth'' galaxies, intended to select ellipticals/early-types;
 volunteers also indicate the relative axial ratio (roundness) for these
@@
 galaxies included assessing the number, arrangement, relative brightness, and
-location of the clumps within the galaxy. Finally, every classification of a
-galaxy gave the option of identifying ``odd'' features within the image; these
+location of the clumps within the galaxy. Finally, every classification 
+had the option of identifying ``odd'' features within the image; these
 labels were for relatively rare $(\lesssim1\%)$ phenomena, including dust
@@
 distant galaxies. Images from the \main{} AEGIS, GEMS, and GOODS data sets had
-a median of 122~independent classifications per image. The remainder of the
-images either had a later activation date (\main{} COSMOS, \simagn) or a lower
+a median of 122~independent classifications per image. The remaining
+images had fewer classifications either due to a later activation date (\main{} COSMOS, \simagn) or a lower
 retirement limit (\stripe{} and \coadd). Images from these samples had a median
@@
 for the GOODS 5-epoch images were separately obtained from Mar-Jun 2015 using
-the fourth version of the Galaxy~Zoo site and the same GZH decision tree.
-The GZH project had a total of 10,349,357~classifications from
+a new version of the Galaxy~Zoo site but the same GZH decision tree.
+The GZH project finished with a total of 10,349,357~classifications from
 93,898~registered participants. 
@@
 downweighting classifiers who frequently disagreed with others. The weighting
-factor $w$ was 1 for the top 95\% of classifiers, as ranked by consistency.
-For the bottom 5\% of classifiers, $w$ was designed to drop smoothly and was
-effectively zero for the bottom 1\% in the distribution function. Since
+factor $w$ was 1 for the top 95\% of classifiers as ranked by consistency.
+For the bottom 5\% of classifiers, $w$ drops smoothly and is
+effectively zero for the bottom 1\% of the distribution function. Since
 downweighting only occurs for the bottom few percent of classifiers (and an even smaller
@@
 classification accuracy (\ie, galaxies of a given mass/size will appear smaller
-and dimmer at higher redshifts).  This bias is not unique to the crowdsourcing
-technique; its dependence in data quality is a potential problem for
+and dimmer at higher redshifts).  This bias is not unique to crowdsourcing
+techniques; its dependence in data quality is a potential problem for
 \emph{both} automated and visual classifications, and must be addressed in
@@
 and its relative orientation. The combination of all
-such parameters forms a high-dimensional space, and it is not clear how to
-separate this into individual effects. Instead, the method used here employs
+such parameters forms a high-dimensional space, \changes{and there is no obvious technique
+for separating these into individual effects}. Instead, the method used here employs
 only two parameters as a simple model of the effect of redshift brightness on classification: the
@@
 the measured value of \ffeatures, determined by the $\zeta$ function described
-in the following section. A reliable predicted value can be obtained so long as
+in the following section (Equation~\ref{eqn:fzeta_mod}). A reliable predicted value can be obtained so long as
 the relationship between \ffeaturesz{} and \ffeaturesrest{} is single-valued;
@@
 appropriate to correct galaxies that lie in certain regions of surface
-brightness/redshift/\ffeatures{} space. These regions tend to have low
+brightness/redshift/\ffeatures{} space. Such regions tend to have low
 \ffeatures{} values at high redshift, but a wide range of values at $z=0.3$.
@@
 Figure~\ref{fig:f_vs_f}. Flat regions of the bins are areas in which there is
-not a clear single-valued relationship between \ffeaturesz{} and
+\emph{not} a clear single-valued relationship between \ffeaturesz{} and
 \ffeaturesrest. We quantify this by measuring the slope of the best-fit
-polynomial; regions of the bins with a slope less than 0.4 are considered
+polynomial to the vote fractions; regions of the bins with a slope less than 0.4 are considered
 \emph{not} one-to-one, and therefore \ffeaturesz{} cannot be boosted to its
@@
 cannot be confidently assigned, the \emph{range} of debiased values is
-estimated using a method visualised in Figure~\ref{fig:f_vs_f_zoom}. This uses the
+estimated and included as a data product. This uses the
 \ferengi{} simulated data to analyse the range of intrinsic \ffeaturesrest{}
@@
 changes in \ffeatures. To examine whether a better fit should involve
-additional parameters, we examine the global dependence of $\zeta$ on the
+additional parameters, we tested the global dependence of $\zeta$ on the
 galaxy surface brightness. This is motivated by the fact that brighter galaxies
@@
 absolute magnitude. To simplify our model, we subsume these into a single
-parameter $\mu$.
+parameter of surface brightness, $\mu$.
 
@@
 a function of surface brightness. The best-fit parameters to the linear fit
-(from least-squares optimization) are $\zeta_0=0.50$, $\zeta_1=-0.03$. To make the
-final debiased correction \changes{for the genuine \hst{} data, we apply Equation~\ref{eqn:fzeta}:}
+from least-squares optimization are $\zeta_0=0.50$, $\zeta_1=-0.03$. To make the
+final debiased correction \changes{for the genuine \hst{} data, we apply a 
+correction similar to Equation~\ref{eqn:fzeta}:}
 
@@
 \noindent where $f_\mathrm{features,weighted}$ is the weighted vote fraction
-described in Section~\ref{ssec:weighting}, and here $f_{\rm features,debiased}$ is bounded 
+described in Section~\ref{ssec:weighting}, and $f_{\rm features,debiased}$ is bounded 
 between $f_{\rm features,weighted}$ and 1.
@@
 were strongly boosted (\ffeatures$<0.25$ and \fbest$>0.50$) in GZH also
-appear in the CANDELS expert sample. Of those, \citet{kar15}
-classify 4 as spheroids/disky, 2 as disks, 1 as a spheroid, 1 as
+appear in the CANDELS expert sample. Of those, the CANDELS expert sample
+classifies 4 as spheroids/disky, 2 as disks, 1 as a spheroid, 1 as
 irregular/disky and 1 as unclassifiable. The \fbest{} values for GZH are all
@@
 morphologies are highly difficult (see
-Sections~\ref{ssec:comparisons}--\ref{ssec:gzh_gzc}).
+Sections~\ref{ssec:gzh_gzc}--\ref{ssec:comparisons}).
 
@@
 
-Tables~\ref{tbl:catalogue_hst}-\ref{tbl:simulated_agn} also contain flags for
+Tables~\ref{tbl:catalog_hst}-\ref{tbl:simulated_agn} also contain flags for
 Task 01 that identify clean (but not complete) samples of galaxies with high
@@
 sample in Section~\ref{ssec:sample_labels} corresponds to the data in
-Tables~\ref{tbl:catalogue_hst}-\ref{tbl:simulated_agn}.
+Tables~\ref{tbl:catalog_hst}-\ref{tbl:simulated_agn}.
 
@@
 
-\section{Using the catalogue}\label{sec:cookbook}
+\section{Using the GZH catalogue}\label{sec:cookbook}
 
@@
 
-As an example of how to use Table~\ref{tbl:thresholds} to create a sample of
+To use data from Table~\ref{tbl:thresholds} to create, for example, a sample of  
 3-armed spiral galaxies, we suggest selecting objects with $N_{arm~number} \ge
@@
 candidates''; \ie, galaxies for which answering the arm number question makes
-physical sense and the vote fraction $f_{\rm arm~number}$ is well-sampled. In
-this example, such galaxies are featured, non-clumpy, non-edge~on spirals. At
-this point a cut can be made on $f_{\rm arm~number=3}$ to select spirals with
+physical sense and the vote fraction $f_{\rm arm~number}$ is well-sampled. 
+Such galaxies will be featured, non-clumpy, non-edge~on spirals. At
+this point a final cut can be made on $f_{\rm arm~number=3}$ to select spirals with
 three arms.
@@
 Figure~\ref{fig:sankey} only includes images from a volume-limited sample
-($z<1.0, m_\mathrm{I}<22.5$) in a single \hst{} survey (COSMOS, which has the
+($z<1.0, m<22.5$ in $I$-band) in a single \hst{} survey (COSMOS, which has the
 largest number of total galaxies).  We use a simple plurality vote for the
@@
 approach to that described in Section~\ref{sec:debiasing}; the correlation
-between other tasks, such as edge-on galaxies is significantly stronger
-($r=0.9$). So while the raw vote fractions are not directly comparable, the
+between other tasks, such as edge-on galaxies, is significantly stronger
+($r=0.9$). While the raw vote fractions are not directly comparable, the
 initial analysis indicates that the broad morphologies are at least consistent.
@@
 the methods used for measuring morphology. These catalogues have been
-cross-matched to GZH to compare the results. 
+cross-matched to GZH to compare results. 
 %This is not presented as an
@@
 categories: bulge-dominated/elliptical/smooth, disk-dominated/spiral, and
-irregular/clumpy. These categories are compared to two parameters in GZH:
+irregular/clumpy. These categories are matched to two GZH parameters:
 \fbest, which identifies disk-dominated and clumpy galaxies, and \fodd, which
@@
 ($n$) to quantify morphology; a principal component analysis is used to assign
-galaxies to categories. All three methods use discrete morphological categories
+galaxies to categories. All three COSMOS catalogs use discrete morphological categories
 of ellipticals, spirals, and peculiar/irregulars. We use the same categories
@@
 
-Galaxies from the COSMOS morphology catalogues all have morphologies that are
+Galaxies from the COSMOS catalogues all have morphologies that are
 reasonably well-predicted by the GZH based on \fbest. The relation is strongest
@@
 compact objects (stars or quasars) that would be classified as artifacts in
-GZH, explaining the dip in \fbest.
+GZH.
 
@@
 paper, but we emphasise only that it is impossible for any catalogue to be fully
-consistent with all of the previously published datasets (for example, only
+consistent with \emph{all} of the previously published datasets (for example, only
 64\% of the galaxies in \citealt{tas11} have the same morphological class as
@@
 
-It has been argued that automated methods are preferable to visual
+It has been proposed that automated methods are preferable to visual
 classification due to being quantified and more easily reproducible
@@
 
-The data for the GZH catalogues has been extensively tested and reduced. The
-dominant effect is a known bias against identifying disky and asymmetric
+The data in the GZH catalogues have been extensively reduced and tested. A
+dominant effect is the known bias against identifying disky and asymmetric
 sub-structures at either low resolution or surface brightness. This can be the

### 2016-09-07 response.md
Input for the response from @chrislintott.

@@
 The anonymous users have slightly broader wings, with slightly more addresses at the lowest and highest levels of consistency, but the overall behavior is similar.
+
 The roughly 50-50 split between logged-in users and non-logged-in IP addresses is typical of the ratio for Zooniverse crowdsourced projects as a group.
+Similar results have been published for the Planet Hunters project (Schwamb et al.
+2012) and have been seen in unpublished data for Pulsar Hunters (https://www.zooniverse.org/projects/zooniverse/pulsar-hunters).
 
@@
 
-We chose to evaluate the distribution of f_features in 5 (not 4; a typo in the earlier manuscript has been corrected) bins to match the common ranges of vote fractions used in previous GZ morphological studies: 0.0-0.2 is typically used to indicate weak/no detection of the feature in question, 0.2-0.4, 0.4-0.6, and 0.6-0.8 represent ranges of increasing likelihood of detection, and 0.8-1.0 represents a very strong detection.
-This explanation has been added to the text at the end of Section 4.1.
+We chose to evaluate the distribution of f_features in 5 (not 4; a typo in the earlier manuscript has been corrected) bins to match some of the common ranges of vote fractions used in previous GZ morphological studies.
+The bin size is chosen to be roughly twice the size of the typical scatter for any individual galaxy (which has been measured using repeat image classifications in several phases of Galaxy Zoo), and so any finer grained intervals will begin to simply fit the noise.
+
+Some clarification has been added to the text at the end of Section 4.1.
 
@@
 
-The threshold of 80% was initially a somewhat arbitrary choice to represent the distribution of f_features in a given bin; the authors agree with the referee that a more typical statistical range would be more appropriate.
+The authors agree with the referee that a more typical statistical range would be appropriate.
 We have changed the range to upper and lower 1 sigma limits, or the inner 68% of the data.

### 2016-09-07 response.md

@@
 
-We thank the referee for the very thorough analysis of this method and for the detailed suggestions.
-We used this input to review and revise the fitting of the artificially-redshifted images (from FERENGI) and construction of the debiasing equation for the Hubble data, as follows:
+We used the referee's input to review and revise the fitting of the artificially-redshifted images (from FERENGI) and construction of the debiasing equation for the Hubble data, as follows:
 

### 2016-09-07 response.md
Update response.md

@@
 
-1) While the FERENGI data can be fit relatively well using any of the above models, the exponential is ideal because it is the only form which allows f_features to be simply and continuously bound between 0 and 1.
+1) While the FERENGI data can be fit relatively well using any of the above models, the exponential is ideal because it is the only form whose limiting behaviour can be set to approach 0 and 1.
 This is a key requirement for the debiased votes so that they can be interpreted as normalized fractions.

### 2016-09-08 response.md
Update response.md

@@
 We thank the referee for the very thorough analysis and for the detailed suggestions that helped to improve the analysis and the paper overall.
-In the following, we report the original comment by the referee, followed by our response.
+In the following, we provide the original comment by the referee, followed by our response.
 In the manuscript, we highlighted our changes in boldface.
@@
 2016, submitted), which is nearly identical in design to Galaxy Zoo: Hubble and shares a large fraction of the same user base, the distribution of the classifier consistency for both the logged-in and non-logged-in populations peak at the same value (kappa = 0.7).
-The anonymous users have slightly broader wings, with slightly more addresses at the lowest and highest levels of consistency, but the overall behavior is similar.
+The anonymous users have slightly broader wings, with slightly more IP addresses at the lowest and highest levels of consistency, but the overall behavior is similar.
 

### 2016-09-08 response.md
Update response.md

@@
 This is a combination of both a finite-volume sample at low redshift in addition to some evolution in the stellar populations and size-magnitude relation over cosmic time.
-We deal with this issue partially by applying the evolutionary correction described in Section 2.3.2, but this still results in a sample spans (but does not reproduce) the surface brightness-redshift distribution of the real data.
+We deal with this issue partially by applying the evolutionary correction described in Section 2.3.2, but this still results in a sample that spans (but does not reproduce) the surface brightness-redshift distribution of the real data.
 The mismatch does not affect the overall calibration accuracy as we are not correcting the population as a whole, but only galaxies at particular bins of surface brightness and redshift.

### 2016-09-08 response.md
Update response.md

@@
 Rather than comparing the fits of the polynomials for Task 1 vs the rest of the tasks, we compare the available data per bin.
-For Task 1, an average of 59 points were fit in each z-mu bin (Figure 9).
+For Task 1, an average of 59 points were fit in each z-mu bin (now Figure 7).
 Fitting parameters for any other task is significantly limited by the number of galaxies in each z-mu bin; the higher-order tasks have an average of only 9 galaxies per bin.
 This is driven by the fact that the tasks do not meet the minimum threshold of 10 individual classifications (this threshold is exceeded for every galaxy in Task 1, however).
-This simpler evaluation should make it more evident to the reader that the FERENGI data was not well-fit for questions beyond Task 01.
+This simpler evaluation should make it more evident to the reader that the FERENGI data was not well-fit for questions beyond Task 1.
 
@@
 
-Typo has been fixed in the text.
+Thank you, this typo has been fixed in the text.

### 2016-09-08 writeup/gz_hubble_data.tex
Most major and minor changes added back to primary manuscript.

--- 2016-08-12 writeup/gz_hubble_data.tex
@@
 participation). Classifications by participants who were not logged in were marked as
-``Anonymous'' and receive the same $w=1$ weighting as the vast majority
-of logged-in classifiers.
+``Anonymous'' and receive the same $w=1$ weighting as the vast majority of
+logged-in classifiers. \changes{Results from the Galaxy Zoo: CANDELS project (Simmons et~al., submitted)
+show that the distributions of weights for anonymous and
+logged-in users are similar, supporting the default technique of GZH.}
 % We should also try to estimate how many anonymous classifiers there were, if possible. 
@@
 cannot be confidently assigned, the \emph{range} of debiased values is
-estimated using a method visualised in Figure~\ref{fig:f_vs_f_zoom}. This uses the
+estimated and included as a data product. This uses the
 \ferengi{} simulated data to analyse the range of intrinsic \ffeaturesrest{}
 values for any given observed \ffeatures{} value, again as a function of
-surface brightness and redshift. In each unclassifiable (shaded blue) $z$,$\mu$ bin, 
+surface brightness and redshift. \changes{In each unclassifiable (shaded blue) $z$,$\mu$ bin, 
 we compute the spread of
@@
 (corresponding to the ``clean'' thresholds used in prior GZ publications).
-The range of intrinsic values for GZH is defined as the inner 80\% of the data,
-represented by the orange bars in Figure~\ref{fig:f_vs_f_zoom}. For any galaxy which
+The range of intrinsic values for GZH is defined by the upper and lower 1~$\sigma$ limits,
+enclosing the inner 68\% of the data. This range is represented by the orange bars in 
+Figure}~\ref{fig:f_vs_f_zoom}. For any galaxy which
 cannot be directly debiased by the $\zeta$ method, these ranges are used to
@@
 \includegraphics[width=\textwidth]{figures/zeta_examples_sorted.pdf}
-\caption{Behaviour of the normalised, weighted vote fractions of features
+\caption{]Behaviour of the normalised, weighted vote fractions of features
 visible in a galaxy ($f_\textrm{features}$) as a function of redshift in the
@@
 a function of surface brightness. The best-fit parameters to the linear fit
-(from least-squares optimization) are $\zeta_0=0.50$, $\zeta_1=-0.03$. To make the
-final debiased correction, we use Equation~\ref{eqn:fzeta}, rearranged for clarity:
+from least-squares optimization are $\zeta_0=0.50$, $\zeta_1=-0.03$. To make the
+final debiased correction \changes{for the genuine \hst{} data, we apply a 
+correction similar to Equation~\ref{eqn:fzeta}:}
 
@@
 sufficient data to measure a correction, as compared to 2.0\% achieved for
-Task~01 (Table~\ref{tbl:ferengi_corrections}). Of the remaining
-\ferengi{} galaxies which did meet this requirement, polynomials were fit to
-the data in each redshift-surface brightness bin, as was done for Task~01. The
-goodness-of-fit was evaluated in each bin, for each Task, using a normalised
-$\chi^2$ metric. The mean $\chi^2$ for all higher-order tasks was
-$0.10\pm0.04$, significantly larger than the Task~01 value of $0.04$. Based on
-this statistic, the data cannot not be modelled with sufficient confidence for
-the higher order tasks. An example of the debiasing technique applied to
-\fbar{} is shown in Section~\ref{sec:ferengi_bar}; visual inspection of
-Figure~\ref{fig:f_vs_fbar} confirms that the points in each bin are scattered
-to a degree at which no strong correlation is present.  For these reasons,
-debiased vote fractions are only offered in the GZH catalogue for Task~01
-(smooth/features).
+Task~01 (Table~\ref{tbl:ferengi_corrections}). \changes{This leaves the average
+surface brightness/redshift bin 
+with insufficient data points to confidently measure the change in vote fraction ($\lesssim10$~galaxies per bin). 
+For these reasons, debiased vote fractions are only provided in the GZH catalogue for Task~01
+(smooth/features). We suggest that use of morphological data for higher order tasks should instead use
+the weighted vote fractions (see Section~\ref{sec:cookbook}).}
 
@@
 \includegraphics[width=0.90\textwidth]{figures/sankey_cosmos.pdf}
-\caption{Demographics of the morphologies for GZH from a volume-limited
-sample ($z<1.0, m_\mathrm{I}<22.5$) of the COSMOS galaxies. Each node in the diagram (dark blue horizontal
-bars of uniform height) represents a task in the tree (Figure~\ref{fig:decisiontree}). The left diagram shows
+\caption{Demographics of the morphologies for a volume-limited
+sample ($z<1.0, m_\mathrm{I}<22.5$) of the COSMOS galaxies in GZH. Each node in the diagram (dark blue horizontal
+bars) represents a task in the tree (Figure~\ref{fig:decisiontree}). The left diagram shows
 the full decision tree. The right diagram zooms in on the features/clumpy
-tasks, which are otherwise difficult to see. Paths between tasks represent
+tasks only. Paths between tasks represent
 each possible answer to the task, flowing from top to bottom between their
 origin and the subsequent task in the tree. Labels are assigned to
-each galaxy based on the plurality answer for each task. A galaxy is assigned
-only one label at each node. Widths of the paths are proportional to the number
+galaxies based on the plurality answer for each task, with each galaxy assigned
+only one label per node. Widths of the paths are proportional to the number
 of galaxies assigned to that path. The widths of the nodes are proportional to
@@
 We repeated all analyses comparing morphologies between GZH and external
-pulblications on the entire GZH dataset, rather than the volume-limited sample
+\changes{publications} on the entire GZH dataset, rather than the volume-limited sample
 ($z<1.0,m<22.5$) discussed above. If galaxies at all redshifts and at the

### 2016-09-09 writeup/gz_hubble_data.tex
Updated caption and response for Figure 8. Closes #185.

@@
 surface brightnesses between $20.3 < \mu < 21.0$ $\rm (mag/arcsec^2)$. The orange bars represent the inner
-80$^\mathrm{th}$ percentiles of the data, the boundaries of which are the lower
-and upper limits of the debiased values.}
+68\% (1$\sigma$) of the uncorrectable \ffeatures{} quantiles, which are used
+to compute the limits on the range of debiased values.}
 \label{fig:f_vs_f_zoom}

### 2016-09-09 writeup/gz_hubble_data.tex

--- 2016-09-08 writeup/gz_hubble_data.tex
@@
 parameter $\zeta$ for \ffeatures{} as a function of surface brightness. This
-includes only galaxies with a bounded range on the dropoff
-\changes{($-10<\zeta<10$)} and sufficient points to fit each function (37~original
-galaxies, each artificially redshifted in eight bins over a range from $0.3\lesssim z_\mathrm{sim}\lesssim1.0$).}
+includes only the simulated galaxies with a bounded range on the dropoff
+\changes{($-10<\zeta<10$)} and sufficient points to fit each function (\changes{28~original
+galaxies, each with varying images artificially redshifted in one to eight bins over a range from} $0.3\lesssim z_\mathrm{sim}\lesssim1.0$). 
+}
 \label{fig:zeta_mu}

### 2016-09-09 writeup/gz_hubble_data.tex

@@
 
-Of the 11,157 galaxies in the GOODS-N and GOODS-S full depth sample, 4,461
+Of the 11,157 galaxies in the GOODS-N and GOODS-S full depth sample, 4,460
 are also in the shallow-depth sample. Figure~\ref{fig:shallow_vs_full} shows a
-strong correlation between \ffeatures{} for both sets of images. The mean
+strong correlation between \ffeatures{} for both sets of images. \changes{The mean
 change in \ffeatures{} from the shallow to full depth images
-$f_\mathrm{features,full} - f_{features,shallow} \equiv \Delta f = 0.00$, with
-a standard deviation of $\sigma = 0.17$. While there is some variance in
+$f_\mathrm{features,full} - f_{features,shallow} \equiv \Delta f = -0.01$, with
+a standard deviation of $\sigma = 0.18$.} While there is some variance in
 $\Delta f$ in the whole sample, the change is usually small and not often
@@
 75\% of the sample would not change morphology. Of the remaining 25\% that
-would change morphology, only 0.3\% (10~galaxies)
+would change morphology, only \changes{0.2\% (9~galaxies)}
 drastically change morphology either from smooth to featured or vice versa, while the
@@
 \includegraphics[width=0.50\textwidth]{figures/full_shallow_p_plot.pdf}
-\caption{Distribution of \ffeatures{} for the 4,461 GOODS galaxies with both
+\caption{Distribution of \ffeatures{} for the 4,460 GOODS galaxies with both
 shallow (2-epoch; \goods) and full-depth (5-epoch; \main) images
@@
 \hline
-smooth to smooth              & 758     & 17.0     & $-$0.00      &  0.69   \\
-smooth to intermediate        & 367     & 8.2      &    0.18      &  0.69   \\
-smooth to featured            & 7       & 0.2      &    0.76      &  0.57   \\ 
-intermediate to smooth        & 214     & 4.8      & $-$0.18      &  0.65   \\
-intermediate to intermediate  & 2,303   & 51.6     &    0.01      &  0.78   \\
-intermediate to featured      & 168     & 3.8      &    0.19      &  0.83   \\
-featured to smooth            & 3       & 0.1      & $-$0.74      &  0.71   \\
-featured to intermediate      & 337     & 7.6      & $-$0.18      &  0.68   \\
-featured to featured          & 301     & 6.8      & $-$0.05      &  0.71   \\
+smooth to smooth              & 708     & 15.9     &    0.00      &  0.72   \\
+smooth to intermediate        & 346     & 7.8      &    0.21      &  0.70   \\
+smooth to featured            & 6       & 0.1      &    0.80      &  0.45   \\ 
+intermediate to smooth        & 266     & 6.0      & $-$0.24      &  0.66   \\
+intermediate to intermediate  & 2,363   & 53.0     &    0.00      &  0.75   \\
+intermediate to featured      & 121     & 2.7      &    0.17      &  0.82   \\
+featured to smooth            & 3       & 0.1      & $-$0.73      &  0.71   \\
+featured to intermediate      & 370     & 8.3      & $-$0.15      &  0.69   \\
+featured to featured          & 277     & 6.2      & $-$0.05      &  0.71   \\
 \hline
-Total                         & 4,461   & 100      &              &         \\
+Total                         & 4,460   & 100      &              &         \\
 \hline\hline

### 2016-09-09 response.md
Updated caption and response for Figure 8. Closes #185.
New figure on correctable fractions and evolving thresholds. Closes #187.

@@
 In the following, we provide the original comment by the referee, followed by our response.
-In the manuscript, we highlighted our changes in boldface.
+
+The major changes in the manuscript have been marked in red boldface.
+We note that the reorganization of Section 4 (Major Issue I) is not marked.
+There has also been a mild amount of reordering of tables and figures as a result.
+We have added a single figure (Figure 11) that shows the fraction of correctable galaxies distributed over the sample, and a short amount of explanatory text in Sections 4.2 and 8.
 
@@
 Equation 2 was originally left unbounded because the raw data being fit was inherently bounded between vote fractions of 0 and 1.
-However, the original verseion of Equation 4 could produce vote fractions greater than 1 if left in the same form as Equation 2.
+However, the original version of Equation 4 could produce vote fractions greater than 1 for certain combinations of z and f_0 if left in the same form as Equation 2.
 We have realized that the difference in normalization, while having only a small effect on the fitting of the data, is inconsistent and may be confusing to a reader.
@@
 
-Correct, thank you. This typo has been edited in the figure caption.
+Correct, thank you. This typo has been edited in the caption (now Figure 10).
 
@@
 
-***response pending final fit ***
+The final version of this figure (now Figure 10; changed slightly based on the new form of Equation 4) has 28 unique galaxies, each with multiple images that have been artificially redshifted in between three to eight bins.
 
@@
 The regions in Figure 9 (now Figure 7) can be nearly perfectly separated in f_features-redshift space, but there are a few regions near the edges in which there is overlap between the two populations.
-This is affected slightly in Figure 9 by the choice of bin size and location.
+This is affected slightly in the figure by the choice of bin size and location.
 However, our analysis makes the assumption that a true/physical separation should be a smooth function of z-mu-f.

### 2016-09-09 writeup/gz_hubble_data.tex
New figure on correctable fractions and evolving thresholds. Closes #187.

--- 2016-09-09 writeup/gz_hubble_data.tex
@@
 redshift or insufficient numbers of \ferengi{} images in their $z$-$\mu$ bin
-to determine a reliable correction term ($\zeta$, described in section ~\ref{ssec:zeta}).
+to determine a reliable correction term ($\zeta$, described in Section~\ref{ssec:zeta}).
 
@@
 
-\begin{figure*}
-\center
-\includegraphics[width=\textwidth]{figures/debiased_corrections.pdf}
-\caption{Debiased \ffeatures{} corrected to $z=0.3$ vs weighted \ffeatures{}
-for the correctable (left), lower-limit (middle), and ``not enough
-information'' (NEI; right) galaxies in the GZH sample.}
-\label{fig:debiased_corrections}
-\end{figure*}
-
 \subsection{Correcting morphologies for classification bias}\label{ssec:zeta}
@@
 \includegraphics[width=\textwidth]{figures/zeta_examples_sorted.pdf}
-\caption{]Behaviour of the normalised, weighted vote fractions of features
+\caption{Behaviour of the normalised, weighted vote fractions of features
 visible in a galaxy ($f_\textrm{features}$) as a function of redshift in the
@@
 parameter of surface brightness, $\mu$.
+
+\begin{figure}
+\center
+\includegraphics[width=0.5\textwidth]{figures/zeta_mu.pdf}
+\caption{All fits for the \ferengi{} galaxies of the vote fraction dropoff
+parameter $\zeta$ for \ffeatures{} as a function of surface brightness. This
+includes only the simulated galaxies with a bounded range on the dropoff
+\changes{($-10<\zeta<10$)} and sufficient points to fit each function (\changes{28~original
+galaxies, each with varying images artificially redshifted in one to eight bins over a range from} $0.3\lesssim z_\mathrm{sim}\lesssim1.0$). 
+}
+\label{fig:zeta_mu}
+\end{figure}
 
@@
 
-\begin{figure}
-\center
-\includegraphics[width=0.5\textwidth]{figures/zeta_mu.pdf}
-\caption{All fits for the \ferengi{} galaxies of the vote fraction dropoff
-parameter $\zeta$ for \ffeatures{} as a function of surface brightness. This
-includes only the simulated galaxies with a bounded range on the dropoff
-\changes{($-10<\zeta<10$)} and sufficient points to fit each function (\changes{28~original
-galaxies, each with varying images artificially redshifted in one to eight bins over a range from} $0.3\lesssim z_\mathrm{sim}\lesssim1.0$). 
-}
-\label{fig:zeta_mu}
-\end{figure}
-
 Since there is little evidence for any strong systematic dependence of $\zeta$
@@
 between $f_{\rm features,weighted}$ and 1.
+
+\begin{figure}
+\center
+\includegraphics[width=0.5\textwidth]{figures/correctable_fraction.pdf}
+\caption{\changes{Histogram showing the fraction of galaxies that have a finite correction
+for the debiased vote fractions \ffeaturesdebiased{} as a function of \ffeatures{}
+and redshift. The parameter space for corrections is limited to $0.3 \leq z \leq 1.0$
+due to the sampling of the parent SDSS galaxies and detectability in the \ferengi{} images.}
+}
+\label{fig:correctable_fraction}
+\end{figure}
+
+\changes{Figure~\ref{fig:correctable_fraction} shows the
+distribution of the fraction of galaxies that are ultimately correctable as a function
+of \ffeatures{} and redshift. The distributions for individual samples (AEGIS, COSMOS,
+GEMS, GOODS) are individually very similar. We emphasize that a correction is more likely to be derived
+and applied for galaxies at higher redshift and with higher weighted values of \ffeatures.
+This has important consequences for selection of physically meaningful samples from GZH
+(see Section~\ref{sec:cookbook}), meaning that comparative studies of galaxies
+should use a threshold on the likelihood of features that evolves as a function of redshift.}
+
+\begin{figure*}
+\center
+\includegraphics[width=\textwidth]{figures/debiased_corrections.pdf}
+\caption{Debiased \ffeatures{} corrected to $z=0.3$ vs weighted \ffeatures{}
+for the correctable (left), lower-limit (middle), and ``not enough
+information'' (NEI; right) galaxies in the GZH sample.}
+\label{fig:debiased_corrections}
+\end{figure*}
 
@@
 applied as a multiplicative correction to the top-level vote fractions for
-$\sim50\%$ of the GZH galaxies.
+$\sim50\%$ of the GZH galaxies. \changes{However, any population studies using
+GZH morphological data must use a combination of debiased vote fractions
+and upper limits from the ``uncorrectable'' galaxies, due to the evolving nature
+of the thresholds as a function of redshift.}
 

### 2016-09-09 writeup/gz_hubble_data.tex
Highlight changes

@@
 
-\subsection{Effects of morphological debiasing}\label{ssec:zeta_results}
+\changes{\subsection{Effects of morphological debiasing}\label{ssec:zeta_results}}
 The approach used in GZH for correcting the weighted classifications for
@@
 
-\subsection{Correcting morphologies for classification bias}\label{ssec:zeta}
+\changes{\subsection{Correcting morphologies for classification bias}\label{ssec:zeta}}
 
@@
 
+\changes{
 \begin{equation}
@@
 \end{equation}
-
+}
 %old equation
@@
 
-\noindent where $f_{\mu,z=0.3}$ is the vote fraction at the lowest redshift in
+\noindent \changes{where $f_{\mu,z=0.3}$ is the vote fraction at the lowest redshift in
 the artificially-redshifted sample ($z_0=0.3$). Here, $\zeta$ is a parameter that
@@
 than $f_{\mu,z=0.3}$ (which is almost always true of the data), and 2) the
-vote fractions cannot be less than zero (which is always true).
+vote fractions cannot be less than zero (which is always true).}
 

### 2016-09-09 response.md
Update response.md

@@
 ------------------------------------------
+
+***I spent an inordinate amount of time trying to piece together the analysis of Section 4 before discovering that important information was given later (in Section 4.2) rather than earlier (in Section 4.1).***
+
+***I believe that Section 4.2 should come first: present the FERENGI sample, and discuss the scheme used to select those data that are to be analyzed to determine the debiasing correction.
+Then the details of the statistical model for debiasing (currently in Section 4.1) should come next.***
+
+***Section 4.3 is fine where it is placed. (However, see minor comment 10 below, which actually is not quite as minor as the other comments.)***
+
 Section 4 has been re-organized in the manner suggested by the reviewer. The authors agree this structure will be more clear to the readers.
@@
 ------------------------------------------
+
+***Due to the length of Major Issue II, it is placed at the end of this response.***
 
@@
 
+The edges of the 1-sigma range in each bin are used to determine the lower and upper limits for the debiased vote fractions of f_features.
+In the middle panel of what is now Figure 9, we show only the lower limits.
+
 ----------------------------------
@@
 Thank you, this typo has been fixed in the text.
+
+-------------------------------
+***Major Issue II***
+
+***The authors currently apply a two-step sequential linear regression model. The first step is to fit***
+
+***f = f_o exp[-(z-z_o)/xi]***
+
+***which is equivalent to the fitting a linear regression after alog-transformation:***
+
+***log(f) = log(f_o) + z_o/xi - z/xi = beta_0 + beta_1 z .***
+
+***(Important note: there was a minus sign left out of the exponential terms in equations (2) and (4), no?
+The plotted results of Figure 7 don't make sense otherwise.) The derived xi's for each galaxy are then placed into another regression as the response, with surface brightness mu as the predictor, and the linear model***
+
+***log_10(hat_xi) = xi_0 + xi_1 mu***
+
+***is fit.
+For the second linear model, the xi_1 term is not actually statistically significant, but the authors sweep this under the rug and simply use the point estimate as is to drive their debiasing correction.
+(I did combine the steps into one linear regression model with interaction but discovered that the model could not be fit directly.
+It could perhaps be fit via iteration but I did not explore this further.)***
+
+***The model appears to be a bit contrived, and there is no evidence presented that the model actually generates good results [other than a vague mention of chi^2 = 0.04 in Section 4.3 that may or may not be applicable here]).
+Since there is no physical motivation for the model, I would suggest two alternatives that are simpler and may perform just as well or better.
+(At a minimum I would want to see a metric of fit defined [*] and computed for the current model and the alternatives, if for no other reason to show that the current model is just as good or better than the others.
+If it is "just as good," I'd go with a simpler alternative.) It may seem that I am asking for too much here, but since the whole goal of this paper is to provide a catalog with good estimates of f_features that one can use to select galaxy samples, the authors need to do more to show that their debiased values of f_features are actually valid!
+(Estimates of uncertainty would help too; the models below would be able to provide them.)***
+
+***[*] Is the normalized chi^2 considered a metric of fit? It is not completely clear. See minor comment 10 below. Perhaps the mean-squared error would work better here; it is a standard estimator.***
+
+***1) Linear regression, with interactions; perhaps***
+
+***log(f/f_o) = beta_0 + beta_1 z + beta_2 mu + beta_12 z mu ,***
+
+***although one should check other tranformations (e.g., sqrt(f/f_o), log(mu), etc.)***
+
+***2) Forego parametrization, and apply a regression tree (or its related cousin random forest regression) to log(f/f_o)(mu,z).
+Play with the tree settings to achieve a proper trade-off between bias and variance (i.e., to make sure the nodes are numerous enough to capture the true dependence of log(f/f_o) on mu and z, but not so numerous that each node only has a few galaxies, making the estimates of log(f/f_o) unduly noisy).
+A good book to use to learn about regression trees (and linear regression too) is "An Introduction to Statistical Learning" by Gareth James et al.
+The authors should not worry about the "Applications in R" part, although they might find doing the analysis in R (assuming it is not already done there) might be simplest.
+Note that a PDF of the book is available for free from James' website.***
+
+***Another issue in Section 4.1 is the statement "The combination of all such parameters forms a high-dimensional space, and it is not clear how to separate this into individual effects." (1) I'm not sure why the individual effects are important here: the goal is to derive a debiasing correction, not to understand how the debiasing correction works.
+(2) There are many methods that one can use to deal with higher-dimensional regression problems, such as PCA regression, the Lasso, best subset selection, etc.; the book mentioned above gives more details on these.
+I'm not going to demand that the authors work with the high-dimensional data now, but they should begin to learn these statistical methods for future work.***

### 2016-09-11 writeup/gz_hubble_data.tex
Funding support for @vrooje.

@@
 KW, MG, CS, MB, and LF gratefully acknowledge support from the US National
-Science Foundation Grant AST1413610. KS gratefully acknowledges support from
+Science Foundation Grant AST1413610.
+Support for BDS was provided by the National Aeronautics and Space
+Administration through Einstein Postdoctoral Fellowship Award Number PF5-160143
+issued by the Chandra X-ray Observatory Center, which is operated by the
+Smithsonian Astrophysical Observatory for and on behalf of the National
+Aeronautics Space Administration under contract NAS8-03060.
+KS gratefully acknowledges support from
 Swiss National Science Foundation Grant PP00P2\_138979/1. TM acknowledges

### 2016-09-12 response.md
Update response.md

@@
 All data in the tables and catalog have been updated to account for these small changes.
+
+The attached figure displays the effect of this change.
+Shown is the distribution of the change in debiased f_features between this draft (new normalization) and the previous draft (old normalization).
+For the correctable sample of galaxies, the new debiased f_features vote fractions are on average 0.02 greater than the previous draft, and at maximum 0.06 greater.
+These changes are too small to significantly affect any final morphologies.
+
+ATTACH: https://github.com/willettk/gzhubble/blob/master/python/notebooks/compare_new_debiased_fraction_hist.png
 

### 2016-09-15 response.md
Update response.md
Wrapping at 80 characters

@@
-We thank the referee for the very thorough analysis and for the detailed suggestions that helped to improve the analysis and the paper overall.
-In the following, we provide the original comment by the referee, followed by our response.
+We thank the referee for the very thorough analysis and for the detailed
+suggestions that helped to improve the analysis and the paper overall. In the
+following, we provide the original comment by the referee, followed by our
+response.
 
-The major changes in the manuscript have been marked in red boldface.
-We note that the reorganization of Section 4 (Major Issue I) is not marked.
-There has also been a mild amount of reordering of tables and figures as a result.
-We have added a single figure (Figure 11) that shows the fraction of correctable galaxies distributed over the sample, and a short amount of explanatory text in Sections 4.2 and 8.
+The major changes in the manuscript have been marked in red boldface. We note
+that the reorganization of Section 4 (Major Issue I) is not marked. There has
+also been a mild amount of reordering of tables and figures as a result. We
+have added a single figure (Figure 11) that shows the fraction of correctable
+galaxies distributed over the sample, and a short amount of explanatory text in
+Sections 4.2 and 8.
 
-==========
-Major Issue I: Reorganization of Section 4
+========== Major Issue I: Reorganization of Section 4
 ------------------------------------------
 
-***I spent an inordinate amount of time trying to piece together the analysis of Section 4 before discovering that important information was given later (in Section 4.2) rather than earlier (in Section 4.1).***
+***I spent an inordinate amount of time trying to piece together the analysis
+of Section 4 before discovering that important information was given later (in
+Section 4.2) rather than earlier (in Section 4.1).***
 
-***I believe that Section 4.2 should come first: present the FERENGI sample, and discuss the scheme used to select those data that are to be analyzed to determine the debiasing correction.
-Then the details of the statistical model for debiasing (currently in Section 4.1) should come next.***
+***I believe that Section 4.2 should come first: present the FERENGI sample,
+and discuss the scheme used to select those data that are to be analyzed to
+determine the debiasing correction. Then the details of the statistical model
+for debiasing (currently in Section 4.1) should come next.***
 
-***Section 4.3 is fine where it is placed. (However, see minor comment 10 below, which actually is not quite as minor as the other comments.)***
+***Section 4.3 is fine where it is placed. (However, see minor comment 10
+below, which actually is not quite as minor as the other comments.)***
 
-Section 4 has been re-organized in the manner suggested by the reviewer. The authors agree this structure will be more clear to the readers.
+Section 4 has been re-organized in the manner suggested by the reviewer. The
+authors agree this structure will be more clear to the readers.
 
-------------------------------------------
-Major Issue II: Statistical Model
+========== Major Issue II: Statistical Model
 ------------------------------------------
 
-***Due to the length of Major Issue II, it is placed at the end of this response.***
+***Due to the length of Major Issue II, it is placed at the end of this
+response.***
 
-We used the referee's input to review and revise the fitting of the artificially-redshifted images (from FERENGI) and construction of the debiasing equation for the Hubble data, as follows:
+We used the referee's input to review and revise the fitting of the
+artificially-redshifted images (from FERENGI) and construction of the debiasing
+equation for the Hubble data, as follows:
 
-We tested a variety of models for fitting f/f_0, including linear, quadratic, cubic, and exponential dependences on redshift; for each of these functional forms, we also tested combinations using either a constant zeta parameter or a zeta function that linearly depends on surface brightness.
-We compared the relative quality of fits using the Akaike information criteria (AIC); for each case, we found no significant differences in the results based on the choice of model.
-Full details and code for these tests can be viewed in this Python notebook: https://github.com/willettk/gzhubble/blob/master/python/notebooks/zeta_models_compared.ipynb.
+We tested a variety of models for fitting f/f_0, including linear, quadratic,
+cubic, and exponential dependences on redshift; for each of these functional
+forms, we also tested combinations using either a constant zeta parameter or a
+zeta function that linearly depends on surface brightness. We compared the
+relative quality of fits using the Akaike information criteria (AIC); for each
+case, we found no significant differences in the results based on the choice of
+model. Full details and code for these tests can be viewed in this Python
+notebook:
 
-Of all the models tested, we believe the best model is an exponential fit for f_features vs redshift using a linear dependence on zeta. This decision is based on the following points:
+https://github.com/willettk/gzhubble/blob/master/python/notebooks/zeta_models_compared.ipynb
 
-1) While the FERENGI data can be fit relatively well using any of the above models, the exponential is ideal because it is the only form whose limiting behaviour can be set to approach 0 and 1.
-This is a key requirement for the debiased votes so that they can be interpreted as normalized fractions.
-Furthermore, the results of the AIC test show that the exponential fit is either better than, or had similar support to the other models tested.
+Of all the models tested, we believe the best model is an exponential fit for
+f_features vs redshift using a linear dependence on zeta. This decision is
+based on the following points:
 
-2) We choose a linear equation to represent zeta as a function of surface brightness.
-In terms of goodness-of-fit, the AIC test showed both models were of equal quality.
-While this and the small slope in zeta shows that there is no significant surface brightness dependence in the GZH data, we still opt to keep the more general, linear form.
-As similar debiasing methods are planned for future GZ projects with a greater quantity of calibration images (and for which there may exist stronger dependencies on surface brightness), keeping the general form for this project will allow for a closer comparison of the two iterations of the method.
-We have added an emphasis on this reasoning in the manuscript so as not to lead the readers to the conclusion that we are claiming a strong surface brightness depedence detection in this run.
+1) While the FERENGI data can be fit relatively well using any of the above
+models, the exponential is ideal because it is the only form whose limiting
+behaviour can be set to approach 0 and 1. This is a key requirement for the
+debiased votes so that they can be interpreted as normalized fractions.
+Furthermore, the results of the AIC test show that the exponential fit is
+either better than, or had similar support to the other models tested.
 
-Finally, we have modified Equation 2 to match the normalization of Equation 4 (as suggested in minor comment 4).
+2) We choose a linear equation to represent zeta as a function of surface
+brightness. In terms of goodness-of-fit, the AIC test showed both models were
+of equal quality. While this and the small slope in zeta shows that there is no
+significant surface brightness dependence in the GZH data, we still opt to keep
+the more general, linear form. As similar debiasing methods are planned for
+future GZ projects with a greater quantity of calibration images (and for which
+there may exist stronger dependencies on surface brightness), keeping the
+general form for this project will allow for a closer comparison of the two
+iterations of the method. We have added an emphasis on this reasoning in the
+manuscript so as not to lead the readers to the conclusion that we are claiming
+a strong surface brightness depedence detection in this run.
 
------------------------------------
-Minor Comment 1
+Finally, we have modified Equation 2 to match the normalization of Equation 4
+(as suggested in minor comment 4).
+
+----------------------------------- Minor Comment 1
 -----------------------------------
 
-***1) Section 3.2: what checking did the authors do to indicate that giving all anonymous classifications a weight of 1 is valid?***
+***1) Section 3.2: what checking did the authors do to indicate that giving all
+anonymous classifications a weight of 1 is valid?***
 
-From a strict sense, it is impossible to tell a priori if giving the anonymous classifiers a weight of 1 is valid (since the grouping within the anonymous data is unknown).
-However, there are large amounts of data from similar projects that support this approach.
-For the Galaxy Zoo: CANDELS project (Simmons et al.
-2016, submitted), which is nearly identical in design to Galaxy Zoo: Hubble and shares a large fraction of the same user base, the distribution of the classifier consistency for both the logged-in and non-logged-in populations peak at the same value (kappa = 0.7).
-The anonymous users have slightly broader wings, with slightly more IP addresses at the lowest and highest levels of consistency, but the overall behavior is similar.
+From a strict sense, it is impossible to tell a priori if giving the anonymous
+classifiers a weight of 1 is valid (since the grouping within the anonymous
+data is unknown). However, there are large amounts of data from similar
+projects that support this approach. For the Galaxy Zoo: CANDELS project
+(Simmons et al. 2016, submitted), which is nearly identical in design to Galaxy
+Zoo: Hubble and shares a large fraction of the same user base, the distribution
+of the classifier consistency for both the logged-in and non-logged-in
+populations peak at the same value (kappa = 0.7). The anonymous users have
+slightly broader wings, with slightly more IP addresses at the lowest and
+highest levels of consistency, but the overall behavior is similar.
 
-The roughly 50-50 split between logged-in users and non-logged-in IP addresses is typical of the ratio for Zooniverse crowdsourced projects as a group.
-Similar results have been published for the Planet Hunters project (Schwamb et al.
-2012) and have been seen in unpublished data for Pulsar Hunters (https://www.zooniverse.org/projects/zooniverse/pulsar-hunters).
+The roughly 50-50 split between logged-in users and non-logged-in IP addresses
+is typical of the ratio for Zooniverse crowdsourced projects as a group.
+Similar results have been published for the Planet Hunters project (Schwamb et
+al. 2012) and have been seen in unpublished data for Pulsar Hunters
+(https://www.zooniverse.org/projects/zooniverse/pulsar-hunters).
 
-ATTACH: Figure from https://cloud.githubusercontent.com/assets/2357126/17576650/cfc59fbe-5f29-11e6-99b7-c39a43c013b6.png
+ATTACH: Figure from
+https://cloud.githubusercontent.com/assets/2357126/17576650/cfc59fbe-5f29-11e6-99b7-c39a43c013b6.png
 
------------------------------------
-Minor Comment 2
+----------------------------------- Minor Comment 2
 -----------------------------------
 
-***2) Figure 6: the authors should comment (unless I missed the comment) on why the bivariate distribution of the FERENGI galaxies in (mu,z) does not match the bivariate distribution for the main sample.***
+***2) Figure 6: the authors should comment (unless I missed the comment) on why
+the bivariate distribution of the FERENGI galaxies in (mu,z) does not match the
+bivariate distribution for the main sample.***
 
-The FERENGI sample is biased in including examples of galaxies that have lower surface brightnesses than any images found in the real Hubble data, simply because the local Universe has no examples of galaxies at the high surface brightness end.
-This is a combination of both a finite-volume sample at low redshift in addition to some evolution in the stellar populations and size-magnitude relation over cosmic time.
-We deal with this issue partially by applying the evolutionary correction described in Section 2.3.2, but this still results in a sample that spans (but does not reproduce) the surface brightness-redshift distribution of the real data.
-The mismatch does not affect the overall calibration accuracy as we are not correcting the population as a whole, but only galaxies at particular bins of surface brightness and redshift.
+The FERENGI sample is biased in including examples of galaxies that have lower
+surface brightnesses than any images found in the real Hubble data, simply
+because the local Universe has no examples of galaxies at the high surface
+brightness end. This is a combination of both a finite-volume sample at low
+redshift in addition to some evolution in the stellar populations and
+size-magnitude relation over cosmic time.  We deal with this issue partially by
+applying the evolutionary correction described in Section 2.3.2, but this still
+results in a sample that spans (but does not reproduce) the surface
+brightness-redshift distribution of the real data. The mismatch does not affect
+the overall calibration accuracy as we are not correcting the population as a
+whole, but only galaxies at particular bins of surface brightness and redshift.
 
@@
 
------------------------------------
-Minor Comment 3
+----------------------------------- Minor Comment 3
 -----------------------------------
 
-***3) In parts of Section 4.1, there is a confusing mix of f_mu,z and f_features, which appear to represent the same thing.
-Some clean-up (or additional explanation as to why they are different quantities) would be useful here.***
+***3) In parts of Section 4.1, there is a confusing mix of f_mu,z and
+f_features, which appear to represent the same thing. Some clean-up (or
+additional explanation as to why they are different quantities) would be useful
+here.***
 
-The main difference between Equations 2 and 4 is that the former is applied to the FERENGI calibration images and used to fit the normalization and zeta parameters.
-The latter uses the parameters to apply corrections to individual galaxies from the true data, and is the form implemented throughout the text.
+The main difference between Equations 2 and 4 is that the former is applied to
+the FERENGI calibration images and used to fit the normalization and zeta
+parameters. The latter uses the parameters to apply corrections to individual
+galaxies from the true data, and is the form implemented throughout the text.
 
-We have added text to explicitly mark the difference between the two equations in what is now Section 4.2.
+We have added text to explicitly mark the difference between the two equations
+in what is now Section 4.2.
 
------------------------------------
-Minor Comment 4
+----------------------------------- Minor Comment 4
 -----------------------------------
 
-***4) I probably should have mentioned this above, but why are the authors not working with equation (4) as the basis of their regression model?***
+***4) I probably should have mentioned this above, but why are the authors not
+working with equation (4) as the basis of their regression model?***
 
-Equation 2 was originally left unbounded because the raw data being fit was inherently bounded between vote fractions of 0 and 1.
-However, the original version of Equation 4 could produce vote fractions greater than 1 for certain combinations of z and f_0 if left in the same form as Equation 2.
-We have realized that the difference in normalization, while having only a small effect on the fitting of the data, is inconsistent and may be confusing to a reader.
-Therefore, we have changed Equation 2 to match Equation 4 (see response to Major Comment II, as well as Minor Comment 3).
-All data in the tables and catalog have been updated to account for these small changes.
+Equation 2 was originally left unbounded because the raw data being fit was
+inherently bounded between vote fractions of 0 and 1. However, the original
+version of Equation 4 could produce vote fractions greater than 1 for certain
+combinations of z and f_0 if left in the same form as Equation 2. We have
+realized that the difference in normalization, while having only a small effect
+on the fitting of the data, is inconsistent and may be confusing to a reader.
+Therefore, we have changed Equation 2 to match Equation 4 (see response to
+Major Comment II, as well as Minor Comment 3). All data in the tables and
+catalog have been updated to account for these small changes.
 
-The attached figure displays the effect of this change.
-Shown is the distribution of the change in debiased f_features between this draft (new normalization) and the previous draft (old normalization).
-For the correctable sample of galaxies, the new debiased f_features vote fractions are on average 0.02 greater than the previous draft, and at maximum 0.06 greater.
-These changes are too small to significantly affect any final morphologies.
+The attached figure displays the effect of this change. Shown is the
+distribution of the change in debiased f_features between this draft (new
+normalization) and the previous draft (old normalization). For the correctable
+sample of galaxies, the new debiased f_features vote fractions are on average
+0.02 greater than the previous draft, and at maximum 0.06 greater. These
+changes are too small to significantly affect any final morphologies.
 
-ATTACH: https://github.com/willettk/gzhubble/blob/master/python/notebooks/compare_new_debiased_fraction_hist.png
+ATTACH:
+https://github.com/willettk/gzhubble/blob/master/python/notebooks/compare_new_debiased_fraction.png
 
-----------------------------------
-Minor Comment 5
+---------------------------------- Minor Comment 5
 ----------------------------------
@@
 
----------------------------------
-Minor Comment 6
+--------------------------------- Minor Comment 6
 ----------------------------------
 
-***6) How many data points are there in Figure 8? Obviously more than 37, but fewer than 37 x 8.***
+***6) How many data points are there in Figure 8? Obviously more than 37, but
+fewer than 37 x 8.***
 
-The final version of this figure (now Figure 10; changed slightly based on the new form of Equation 4) has 28 unique galaxies, each with multiple images that have been artificially redshifted in between three to eight bins.
+The final version of this figure (now Figure 10; changed slightly based on the
+new form of Equation 4) has 28 unique galaxies, each with multiple images that
+have been artificially redshifted in between three to eight bins.
 
-----------------------------------
-Minor Comment 7
+---------------------------------- Minor Comment 7
 ----------------------------------
 
-***7) Section 4.2: "The boundaries [of the convex hull] are then adjusted until the contamination from both groups is minimized." If I look at Figure 9, it would appear that the correctable and lower-limit regions can be perfectly separated (using a tree, for instance).
-Am I wrong about this?***
+***7) Section 4.2: "The boundaries [of the convex hull] are then adjusted until
+the contamination from both groups is minimized." If I look at Figure 9, it
+would appear that the correctable and lower-limit regions can be perfectly
+separated (using a tree, for instance). Am I wrong about this?***
 
-The regions in Figure 9 (now Figure 7) can be nearly perfectly separated in f_features-redshift space, but there are a few regions near the edges in which there is overlap between the two populations.
-This is affected slightly in the figure by the choice of bin size and location.
-However, our analysis makes the assumption that a true/physical separation should be a smooth function of z-mu-f.
-Implementing a convex hull in this space created a very small volume near the edge of the inner convex hull that had overlapping positive and negative data points; we optimize the overall accuracy of the hull by adjusting the outer boundaries as described in what is now Section 4.1.
+The regions in Figure 9 (now Figure 7) can be nearly perfectly separated in
+f_features-redshift space, but there are a few regions near the edges in which
+there is overlap between the two populations. This is affected slightly in the
+figure by the choice of bin size and location. However, our analysis makes the
+assumption that a true/physical separation should be a smooth function of
+z-mu-f. Implementing a convex hull in this space created a very small volume
+near the edge of the inner convex hull that had overlapping positive and
+negative data points; we optimize the overall accuracy of the hull by adjusting
+the outer boundaries as described in what is now Section 4.1.
 
-Use of a different method such as a tree could potentially prove to be a superior separator.
-However, the new normalization technique used in this draft results in very clean separation based on the convex hull, with only a single adjustment (see https://github.com/willettk/gzhubble/blob/master/python/creating_debiased_catalog/STEP_3_ferengi_smooth_function.ipynb).
-Further optimization would have an extremely minimal effect on the overall results.
+Use of a different method such as a tree could potentially prove to be a
+superior separator. However, the new normalization technique used in this draft
+results in very clean separation based on the convex hull, with only a single
+adjustment; see:
 
-----------------------------------
-Minor Comment 8
+https://github.com/willettk/gzhubble/blob/master/python/creating_debiased_catalog/STEP_3_ferengi_smooth_function.ipynb
+
+Further optimization would have an extremely minimal effect on the overall
+results.
+
+---------------------------------- Minor Comment 8
 ----------------------------------
 
-***8) Section 4.2: "In each unclassifiable (shaded blue) z,mu bin, the spread of intrinsic values for f_features,z=0.3 for four ranges of observed f_features is computed." Where did the "four" come from?
-More explanation needed.***
+***8) Section 4.2: "In each unclassifiable (shaded blue) z,mu bin, the spread
+of intrinsic values for f_features,z=0.3 for four ranges of observed f_features
+is computed." Where did the "four" come from? More explanation needed.***
 
-We chose to evaluate the distribution of f_features in 5 (not 4; a typo in the earlier manuscript has been corrected) bins to match some of the common ranges of vote fractions used in previous GZ morphological studies.
-The bin size is chosen to be roughly twice the size of the typical scatter for any individual galaxy (which has been measured using repeat image classifications in several phases of Galaxy Zoo), and so any finer grained intervals will begin to simply fit the noise.
+We chose to evaluate the distribution of f_features in 5 (not 4; a typo in the
+earlier manuscript has been corrected) bins to match some of the common ranges
+of vote fractions used in previous GZ morphological studies. The bin size is
+chosen to be roughly twice the size of the typical scatter for any individual
+galaxy (which has been measured using repeat image classifications in several
+phases of Galaxy Zoo), and so any finer grained intervals will begin to simply
+fit the noise.
 
@@
 
-----------------------------------
-Minor Comment 9
+---------------------------------- Minor Comment 9
 ----------------------------------
 
-***9) Why 80% of the data (orange bars, Figure 10)?
-This is an ad hoc choice that doesn't correspond to any typical statistical practice (except perhaps a 10% trimmed mean, but the authors are not computing means here).
-And how is this information applied in Figure 11, middle panel?
-This is not clear.***
+***9) Why 80% of the data (orange bars, Figure 10)? This is an ad hoc choice
+that doesn't correspond to any typical statistical practice (except perhaps a
+10% trimmed mean, but the authors are not computing means here). And how is
+this information applied in Figure 11, middle panel? This is not clear.***
 
-The authors agree with the referee that a more typical statistical range would be appropriate.
-We have changed the range to upper and lower 1 sigma limits, or the inner 68% of the data.
-The figure (now Figure 8) has been modified and text added to the end of Section 4.1.
+The authors agree with the referee that a more typical statistical range would
+be appropriate. We have changed the range to upper and lower 1 sigma limits, or
+the inner 68% of the data. The figure (now Figure 8) has been modified and text
+added to the end of Section 4.1.
 
-The edges of the 1-sigma range in each bin are used to determine the lower and upper limits for the debiased vote fractions of f_features.
-In the middle panel of what is now Figure 9, we show only the lower limits.
+The edges of the 1-sigma range in each bin are used to determine the lower and
+upper limits for the debiased vote fractions of f_features. In the middle panel
+of what is now Figure 9, we show only the lower limits.
 
-----------------------------------
-Minor Comment 10
+---------------------------------- Minor Comment 10
 ----------------------------------
 
-***10) Section 4.3: "The goodness-of-fit was evaluated in each bin, for each Task, using a normalized chi^2 metric." The authors need to provide the formula for this; the numbers don't make sense, if one assumes "normalized" is the same
-as "reduced chi^2" (where the typical value for a good fit is approximately 1).***
+***10) Section 4.3: "The goodness-of-fit was evaluated in each bin, for each
+Task, using a normalized chi^2 metric." The authors need to provide the formula
+for this; the numbers don't make sense, if one assumes "normalized" is the same
+    as "reduced chi^2" (where the typical value for a good fit is approximately
+    1).***
 
-We agree that the normalized chi-squared is not the ideal metric for evaluating the goodness-of-fit here.
-Rather than comparing the fits of the polynomials for Task 1 vs the rest of the tasks, we compare the available data per bin.
-For Task 1, an average of 59 points were fit in each z-mu bin (now Figure 7).
-Fitting parameters for any other task is significantly limited by the number of galaxies in each z-mu bin; the higher-order tasks have an average of only 9 galaxies per bin.
-This is driven by the fact that the tasks do not meet the minimum threshold of 10 individual classifications (this threshold is exceeded for every galaxy in Task 1, however).
-This simpler evaluation should make it more evident to the reader that the FERENGI data was not well-fit for questions beyond Task 1.
+We agree that the normalized chi-squared is not the ideal metric for evaluating
+the goodness-of-fit here. Rather than comparing the fits of the polynomials for
+Task 1 vs the rest of the tasks, we compare the available data per bin. For
+Task 1, an average of 59 points were fit in each z-mu bin (now Figure 7).
+Fitting parameters for any other task is significantly limited by the number of
+galaxies in each z-mu bin; the higher-order tasks have an average of only 9
+galaxies per bin. This is driven by the fact that the tasks do not meet the
+minimum threshold of 10 individual classifications (this threshold is exceeded
+for every galaxy in Task 1, however). This simpler evaluation should make it
+    more evident to the reader that the FERENGI data was not well-fit for
+    questions beyond Task 1.
 
-As this is not a key product of the paper, we have removed Figures A5 and A6 from the manuscript to avoid confusion and extraneous discussion. Additional text has been added at the end of Section 4.3.
+As this is not a key product of the paper, we have removed Figures A5 and A6
+from the manuscript to avoid confusion and extraneous discussion. Additional
+text has been added at the end of Section 4.3.
 
-----------------------------------
-Minor Comment 11
+---------------------------------- Minor Comment 11
 ----------------------------------
@@
 
--------------------------------
-***Major Issue II***
+------------------------------- ***Major Issue II***
+----------------------------------
 
-***The authors currently apply a two-step sequential linear regression model. The first step is to fit***
+***The authors currently apply a two-step sequential linear regression model.
+The first step is to fit***
 
@@
 
-***which is equivalent to the fitting a linear regression after alog-transformation:***
+***which is equivalent to the fitting a linear regression after
+alog-transformation:***
 
@@
 
-***(Important note: there was a minus sign left out of the exponential terms in equations (2) and (4), no?
-The plotted results of Figure 7 don't make sense otherwise.) The derived xi's for each galaxy are then placed into another regression as the response, with surface brightness mu as the predictor, and the linear model***
+***is fit. For the second linear model, the xi_1 term is not actually
+statistically significant, but the authors sweep this under the rug and simply
+use the point estimate as is to drive their debiasing correction. (I did
+combine the steps into one linear regression model with interaction but
+discovered that the model could not be fit directly. It could perhaps be fit
+via iteration but I did not explore this further.)***
 
-***log_10(hat_xi) = xi_0 + xi_1 mu***
+***The model appears to be a bit contrived, and there is no evidence presented
+that the model actually generates good results [other than a vague mention of
+chi^2 = 0.04 in Section 4.3 that may or may not be applicable here]). Since
+there is no physical motivation for the model, I would suggest two alternatives
+that are simpler and may perform just as well or better. (At a minimum I would
+want to see a metric of fit defined [*] and computed for the current model and
+the alternatives, if for no other reason to show that the current model is just
+as good or better than the others. If it is "just as good," I'd go with a
+simpler alternative.) It may seem that I am asking for too much here, but since
+the whole goal of this paper is to provide a catalog with good estimates of
+f_features that one can use to select galaxy samples, the authors need to do
+more to show that their debiased values of f_features are actually valid!
+(Estimates of uncertainty would help too; the models below would be able to
+provide them.)***
 
-***is fit.
-For the second linear model, the xi_1 term is not actually statistically significant, but the authors sweep this under the rug and simply use the point estimate as is to drive their debiasing correction.
-(I did combine the steps into one linear regression model with interaction but discovered that the model could not be fit directly.
-It could perhaps be fit via iteration but I did not explore this further.)***
-
-***The model appears to be a bit contrived, and there is no evidence presented that the model actually generates good results [other than a vague mention of chi^2 = 0.04 in Section 4.3 that may or may not be applicable here]).
-Since there is no physical motivation for the model, I would suggest two alternatives that are simpler and may perform just as well or better.
-(At a minimum I would want to see a metric of fit defined [*] and computed for the current model and the alternatives, if for no other reason to show that the current model is just as good or better than the others.
-If it is "just as good," I'd go with a simpler alternative.) It may seem that I am asking for too much here, but since the whole goal of this paper is to provide a catalog with good estimates of f_features that one can use to select galaxy samples, the authors need to do more to show that their debiased values of f_features are actually valid!
-(Estimates of uncertainty would help too; the models below would be able to provide them.)***
-
-***[*] Is the normalized chi^2 considered a metric of fit? It is not completely clear. See minor comment 10 below. Perhaps the mean-squared error would work better here; it is a standard estimator.***
+***[*] Is the normalized chi^2 considered a metric of fit? It is not completely
+clear. See minor comment 10 below. Perhaps the mean-squared error would work
+better here; it is a standard estimator.***
 
@@
 
-***although one should check other tranformations (e.g., sqrt(f/f_o), log(mu), etc.)***
+***although one should check other tranformations (e.g., sqrt(f/f_o), log(mu),
+etc.)***
 
-***2) Forego parametrization, and apply a regression tree (or its related cousin random forest regression) to log(f/f_o)(mu,z).
-Play with the tree settings to achieve a proper trade-off between bias and variance (i.e., to make sure the nodes are numerous enough to capture the true dependence of log(f/f_o) on mu and z, but not so numerous that each node only has a few galaxies, making the estimates of log(f/f_o) unduly noisy).
-A good book to use to learn about regression trees (and linear regression too) is "An Introduction to Statistical Learning" by Gareth James et al.
-The authors should not worry about the "Applications in R" part, although they might find doing the analysis in R (assuming it is not already done there) might be simplest.
-Note that a PDF of the book is available for free from James' website.***
+***2) Forego parametrization, and apply a regression tree (or its related
+cousin random forest regression) to log(f/f_o)(mu,z). Play with the tree
+settings to achieve a proper trade-off between bias and variance (i.e., to make
+sure the nodes are numerous enough to capture the true dependence of log(f/f_o)
+on mu and z, but not so numerous that each node only has a few galaxies, making
+the estimates of log(f/f_o) unduly noisy). A good book to use to learn about
+regression trees (and linear regression too) is "An Introduction to Statistical
+Learning" by Gareth James et al. The authors should not worry about the
+"Applications in R" part, although they might find doing the analysis in R
+(assuming it is not already done there) might be simplest. Note that a PDF of
+the book is available for free from James' website.***
 
-***Another issue in Section 4.1 is the statement "The combination of all such parameters forms a high-dimensional space, and it is not clear how to separate this into individual effects." (1) I'm not sure why the individual effects are important here: the goal is to derive a debiasing correction, not to understand how the debiasing correction works.
-(2) There are many methods that one can use to deal with higher-dimensional regression problems, such as PCA regression, the Lasso, best subset selection, etc.; the book mentioned above gives more details on these.
-I'm not going to demand that the authors work with the high-dimensional data now, but they should begin to learn these statistical methods for future work.***
+***Another issue in Section 4.1 is the statement "The combination of all such
+parameters forms a high-dimensional space, and it is not clear how to separate
+this into individual effects." (1) I'm not sure why the individual effects are
+important here: the goal is to derive a debiasing correction, not to understand
+how the debiasing correction works. (2) There are many methods that one can use
+to deal with higher-dimensional regression problems, such as PCA regression,
+the Lasso, best subset selection, etc.; the book mentioned above gives more
+details on these. I'm not going to demand that the authors work with the
+high-dimensional data now, but they should begin to learn these statistical
+methods for future work.***

### 2016-09-30 writeup/gz_hubble_data.tex
adding referee acknowledgement
addressing minor comments 3 and 4 on figure 9

@@
 artificial \ferengi{} images. Galaxies in this plot were randomly selected from
-a distribution with $e=0$ and at least three detectable images in redshift bins
-of $z\ge0.3$, and are sorted by \ffeaturesrest. Measured vote fractions (blue
+a distribution with evolutionary correction $e=0$ and at least three detectable images 
+in redshift bins of $z\ge0.3$. The displayed bins are sorted by \ffeaturesrest, 
+labeled above each plot. Measured vote fractions (blue
 solid line) are fit with an exponential function (red dashed line;
@@
 measurements for the AEGIS sample. We thank Coleman Krawczyk for his assistance
-in producing Figure~\ref{fig:decisiontree}.
+in producing Figure~\ref{fig:decisiontree}. We thank Nathan Cloutier and Brent
+Hilgart for useful discussions. We also thank the referee for thoughtful comments
+which improved the quality of this paper.
 

### 2016-09-30 writeup/gz_hubble_data.tex
Slight caveat on slope limit. Minor comment 2; closes #203.

@@
 \ffeaturesrest. We quantify this by measuring the slope of the best-fit
-polynomial to the vote fractions; regions of the bins with a slope less than 0.4 are considered
+polynomial to the vote fractions. Regions within the bins with a slope less than 0.4
+(a boundary selected through manual inspection and testing) are considered
 \emph{not} one-to-one, and therefore \ffeaturesz{} cannot be boosted to its

### 2016-09-30 writeup/gz_hubble_data.tex
Added another sentence for interpreting Figure 9. Closes #204.
One change of f_best -> f_debiased. Closes #206.

@@
 visible in a galaxy ($f_\textrm{features}$) as a function of redshift in the
-artificial \ferengi{} images. Galaxies in this plot were randomly selected from
+artificial \ferengi{} images. These plots demonstrate overall trends
+in the sensitivity to feature detection as a function of redshift.
+Galaxies in this plot were randomly selected from
 a distribution with evolutionary correction $e=0$ and at least three detectable images 
@@
 classifications in CANDELS \citep{kar15}.  Only nine galaxies that
-were strongly boosted (\ffeatures$<0.25$ and \fbest$>0.50$) in GZH also
+were strongly boosted (\ffeatures$<0.25$ and \ffeaturesdebiased$>0.50$) in GZH also
 appear in the CANDELS expert sample. Of those, the CANDELS expert sample

### 2016-09-30 writeup/gz_hubble_data.tex

@@
 ``Anonymous'' and receive the same $w=1$ weighting as the vast majority of
-logged-in classifiers. \changes{Results from the Galaxy Zoo: CANDELS project (Simmons et~al., submitted)
+logged-in classifiers. Results from the Galaxy Zoo: CANDELS project (Simmons et~al., submitted)
 show that the distributions of weights for anonymous and
-logged-in users are similar, supporting the default technique of GZH.}
+logged-in users are similar, supporting the default technique of GZH.
 % We should also try to estimate how many anonymous classifiers there were, if possible. 
@@
 
-\changes{Figure~\ref{fig:sb_redshift} shows the distribution in $\mu$ and $z$ of
+Figure~\ref{fig:sb_redshift} shows the distribution in $\mu$ and $z$ of
 the artificially-redshifted \textsc{FERENGI} images compared to the genuine
@@
 examples of comparable \textsc{FERENGI} images, correspond to galaxies for
-which the debiased correction is expected to be minor.}
+which the debiased correction is expected to be minor.
 
@@
 
-\changes{\subsection{Effects of morphological debiasing}\label{ssec:zeta_results}}
+\subsection{Effects of morphological debiasing}\label{ssec:zeta_results}
 The approach used in GZH for correcting the weighted classifications for
@@
 and its relative orientation. The combination of all
-such parameters forms a high-dimensional space, \changes{and there is no obvious technique
-for separating these into individual effects}. Instead, the method used here employs
+such parameters forms a high-dimensional space, and there is no obvious technique
+for separating these into individual effects. Instead, the method used here employs
 only two parameters as a simple model of the effect of redshift brightness on classification: the
@@
 values for any given observed \ffeatures{} value, again as a function of
-surface brightness and redshift. \changes{In each unclassifiable (shaded blue) $z$,$\mu$ bin, 
+surface brightness and redshift. In each unclassifiable (shaded blue) $z$,$\mu$ bin, 
 we compute the spread of
@@
 enclosing the inner 68\% of the data. This range is represented by the orange bars in 
-Figure}~\ref{fig:f_vs_f_zoom}. For any galaxy which
+Figure~\ref{fig:f_vs_f_zoom}. For any galaxy which
 cannot be directly debiased by the $\zeta$ method, these ranges are used to
@@
 
-\changes{\subsection{Correcting morphologies for classification bias}\label{ssec:zeta}}
+\subsection{Correcting morphologies for classification bias}\label{ssec:zeta}
 
@@
 \ffeatures{} with increasing simulated redshift for each unique galaxy. 
-We model this relationship \changes{for artificially-redshifted images} with a simple exponential
+We model this relationship for artificially-redshifted images with a simple exponential
 function which bounds $f_{\mu, z>0.3}$  between $f_{\mu, z=0.3}$ and 0:
 
-\changes{
 \begin{equation}
@@
 \end{equation}
-}
 %old equation
@@
 
-\noindent \changes{where $f_{\mu,z=0.3}$ is the vote fraction at the lowest redshift in
+\noindent where $f_{\mu,z=0.3}$ is the vote fraction at the lowest redshift in
 the artificially-redshifted sample ($z_0=0.3$). Here, $\zeta$ is a parameter that
@@
 than $f_{\mu,z=0.3}$ (which is almost always true of the data), and 2) the
-vote fractions cannot be less than zero (which is always true).}
+vote fractions cannot be less than zero (which is always true).
 
@@
 includes only the simulated galaxies with a bounded range on the dropoff
-\changes{($-10<\zeta<10$)} and sufficient points to fit each function (\changes{28~original
-galaxies, each with varying images artificially redshifted in one to eight bins over a range from} $0.3\lesssim z_\mathrm{sim}\lesssim1.0$). 
+($-10<\zeta<10$) and sufficient points to fit each function (28~original
+galaxies, each with varying images artificially redshifted in one to eight bins over a range from $0.3\lesssim z_\mathrm{sim}\lesssim1.0$). 
 }
@@
 from least-squares optimization are $\zeta_0=0.50$, $\zeta_1=-0.03$. To make the
-final debiased correction \changes{for the genuine \hst{} data, we apply a 
-correction similar to Equation~\ref{eqn:fzeta}:}
+final debiased correction for the genuine \hst{} data, we apply a 
+correction similar to Equation~\ref{eqn:fzeta}:
 
@@
 \includegraphics[width=0.5\textwidth]{figures/correctable_fraction.pdf}
-\caption{\changes{Histogram showing the fraction of galaxies that have a finite correction
+\caption{Histogram showing the fraction of galaxies that have a finite correction
 for the debiased vote fractions \ffeaturesdebiased{} as a function of \ffeatures{}
 and redshift. The parameter space for corrections is limited to $0.3 \leq z \leq 1.0$
-due to the sampling of the parent SDSS galaxies and detectability in the \ferengi{} images.}
+due to the sampling of the parent SDSS galaxies and detectability in the \ferengi{} images.
 }
@@
 
-\changes{Figure~\ref{fig:correctable_fraction} shows the
+Figure~\ref{fig:correctable_fraction} shows the
 distribution of the fraction of galaxies that are ultimately correctable as a function
@@
 (see Section~\ref{sec:cookbook}), meaning that comparative studies of galaxies
-should use a threshold on the likelihood of features that evolves as a function of redshift.}
+should use a threshold on the likelihood of features that evolves as a function of redshift.
 
@@
 sufficient data to measure a correction, as compared to 2.0\% achieved for
-Task~01 (Table~\ref{tbl:ferengi_corrections}). \changes{This leaves the average
+Task~01 (Table~\ref{tbl:ferengi_corrections}). This leaves the average
 surface brightness/redshift bin 
@@
 (smooth/features). We suggest that use of morphological data for higher order tasks should instead use
-the weighted vote fractions (see Section~\ref{sec:cookbook}).}
+the weighted vote fractions (see Section~\ref{sec:cookbook}).
 
@@
 We repeated all analyses comparing morphologies between GZH and external
-\changes{publications} on the entire GZH dataset, rather than the volume-limited sample
+publications on the entire GZH dataset, rather than the volume-limited sample
 ($z<1.0,m<22.5$) discussed above. If galaxies at all redshifts and at the
@@
 applied as a multiplicative correction to the top-level vote fractions for
-$\sim50\%$ of the GZH galaxies. \changes{However, any population studies using
+$\sim50\%$ of the GZH galaxies. However, any population studies using
 GZH morphological data must use a combination of debiased vote fractions
 and upper limits from the ``uncorrectable'' galaxies, due to the evolving nature
-of the thresholds as a function of redshift.}
+of the thresholds as a function of redshift.
 
@@
 are also in the shallow-depth sample. Figure~\ref{fig:shallow_vs_full} shows a
-strong correlation between \ffeatures{} for both sets of images. \changes{The mean
+strong correlation between \ffeatures{} for both sets of images. The mean
 change in \ffeatures{} from the shallow to full depth images
 $f_\mathrm{features,full} - f_{features,shallow} \equiv \Delta f = -0.01$, with
-a standard deviation of $\sigma = 0.18$.} While there is some variance in
+a standard deviation of $\sigma = 0.18$. While there is some variance in
 $\Delta f$ in the whole sample, the change is usually small and not often
@@
 75\% of the sample would not change morphology. Of the remaining 25\% that
-would change morphology, only \changes{0.2\% (9~galaxies)}
+would change morphology, only 0.2\% (9~galaxies)
 drastically change morphology either from smooth to featured or vice versa, while the

### 2016-10-12 movie/papermovie.sh
Final submitted version is 32 pages, so 6x6 geometry

@@ -39,7 +39,7 @@ while read p; do
         cp $filename $revpad.pdf
         
         # Use ImageMagick to turn the paginated PDF into a single image
-        montage $revpad.pdf -tile 6x4 -background white -geometry 213x275-15+4 frames/$revpad.png
+        montage $revpad.pdf -tile 6x6 -background white -geometry 213x275-15+4 frames/$revpad.png
 
         let rev+=1
     fi
@@ -51,7 +51,7 @@ rev=0
 for f in `ls -1 frames/*.png | grep -v "movie\-1.png" | sort -nr`; do
     n=`printf "%03d" $rev`
     # Rename frames for ffmpeg's format style
-    convert $f -crop 1280x1320+0+0 $n.png
+    convert $f -crop 1280x1630+0+0 $n.png
     let rev+=1
 done
 

### 2016-10-14 writeup/gz_hubble_data.tex
Adding references to Koekemoer et al. (2007,2011).

@@
 Observations of fields with very deep imaging
-\citep[eg,][]{wil96,gia04,bec06,dav07,sco07,gro11} give the photometric
+\citep[eg,][]{wil96,gia04,bec06,dav07,sco07,gro11,koe11} give the photometric
 sensitivity necessary to detect $L^\star$ galaxies at $z>1$, while also
@@
 
-\item The Cosmic Evolution Survey \citep[COSMOS;][]{sco07} covered an area of
+\item The Cosmic Evolution Survey \citep[COSMOS;][]{sco07,koe07} covered an area of
     $\sim1.8$~deg$^2$ centred at $\alpha=10^\textrm{h}00^\textrm{m},
